### 2023-06-16 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
Update

---
title: "TKT RNAseq Experiment: Differential Expression Analysis"
author: "John Santiago"
date: "2022-03-23"
output: 
  bookdown::html_document2:
    number_sections: false
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## [Return to Home Page](https://johncsantiago.github.io/TKT_RNAseq_preliminary.html)

<br /><br />
\newpage

## <span style="text-decoration:underline">Table of Contents</span>

- #### Figure \@ref(fig:fig1): MDS plot

- #### Figure \@ref(fig:fig2): Barplot of Total DEGs

### TKT effect in female G85R
- #### Figure \@ref(fig:fig3): Heatmaps of Total DEGs in GR.FC x GR.FDf

- #### Figure \@ref(fig:fig4): Heatmaps of Total DEGs in GR.FC x GR.FOE

### TKT effect in female WT
- #### Figure \@ref(fig:fig5): Heatmaps of Total DEGs in WT.FC x WT.FDf

- #### Figure \@ref(fig:fig6): Heatmaps of Total DEGs in WT.FC x WT.FOE

### Genotype effect between female G85R and WT
- #### Figure \@ref(fig:fig7): Heatmaps of Total DEGs in GR.FC x WT.FC

- #### Figure \@ref(fig:fig8): Heatmaps of Total DEGs in GR.FDf x WT.FDf

- #### Figure \@ref(fig:fig9): Heatmaps of Total DEGs in GR.FOE x WT.FOE

### TKT effect in Male G85R
- #### Figure \@ref(fig:fig10): Heatmaps of Total DEGs in GR.MC x GR.MDf

- #### Figure \@ref(fig:fig11): Heatmaps of Total DEGs in GR.MC x GR.MOE

### TKT effect in Male WT
- #### Figure \@ref(fig:fig12): Heatmaps of Total DEGs in WT.MC x WT.MDf

- #### Figure \@ref(fig:fig13): Heatmaps of Total DEGs in WT.MC x WT.MOE

### Genotype effect between Male G85R and WT
- #### Figure \@ref(fig:fig14): Heatmaps of Total DEGs in GR.MC x WT.MC

- #### Figure \@ref(fig:fig15): Heatmaps of Total DEGs in GR.MDf x WT.MDf

- #### Figure \@ref(fig:fig16): Heatmaps of Total DEGs in GR.MOE x WT.MOE

<br /><br /><br />
\newpage

```{r echo=F, include=FALSE}

library(edgeR)
library(plotly)
library(heatmaply)

##Clean Trait Data and calculate CPMs
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)
groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv",row.names=1)

convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)

##normalize data
countdata=countdata[, row.names(groups)]
x <- countdata
gr <- factor(groups$Group)
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
cpmdata=cpm(z)

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)

fit <- glmQLFit(z, design)
plotQLDisp(fit)

##Will calculate fold-change with the first over the second

##GR.F TKT control vs TKT altered
compare = makeContrasts(TktDfGR.F-GR.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.F.CxDf=DEout
sGR.F.CxDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.F-GR.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.F.CxOE=DEout
sGR.F.CxOE=DEout[DEout$FDR<.05,]

##WT.F TKT control vs TKT altered
compare = makeContrasts(TktDfWT.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.F.CxDf=DEout
sWT.F.CxDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEWT.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.F.CxOE=DEout
sWT.F.CxOE=DEout[DEout$FDR<.05,]

##WT.F vs GR.F
compare = makeContrasts(GR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.F=DEout
sGRxWT.F=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfGR.F-TktDfWT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.FDf=DEout
sGRxWT.FDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.F-TktOEWT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.FOE=DEout
sGRxWT.FOE=DEout[DEout$FDR<.05,]

##GR.M TKT control vs TKT altered
compare = makeContrasts(TktDfGR.M-GR.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.M.CxDf=DEout
sGR.M.CxDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.M-GR.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.M.CxOE=DEout
sGR.M.CxOE=DEout[DEout$FDR<.05,]

##WT.M TKT control vs TKT altered
compare = makeContrasts(TktDfWT.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.M.CxDf=DEout
sWT.M.CxDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEWT.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.M.CxOE=DEout
sWT.M.CxOE=DEout[DEout$FDR<.05,]

##WT.M vs GR.M
compare = makeContrasts(GR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.M=DEout
sGRxWT.M=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.MDf=DEout
sGRxWT.MDf=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.M-TktOEWT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.MOE=DEout
sGRxWT.MOE=DEout[DEout$FDR<.05,]

MDSdata = plotMDS(z, col=as.numeric(factor(gr)))

temp=convert[,"Symbol"]
temp2=setdiff(row.names(cpmdata),convert[,2])
names(temp)=convert[,2]
names(temp2)=temp2
convert=c(temp,temp2)

```

```{r fig1, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot.'}

MDSplot = data.frame(x = MDSdata$x,
                     y = MDSdata$y,
                     sample = row.names(groups))
MDSplot = cbind(MDSplot, groups[MDSplot$sample,])
MDSplot$GenoSex = paste0(MDSplot$Genotype,MDSplot$Sex)
MDSplot = MDSplot[order(MDSplot$TKT),]
MDSplot = MDSplot[order(MDSplot$Sex),]
MDSplot = MDSplot[order(MDSplot$GenoSex),]
MDSplot$Group = factor(MDSplot$Group, levels = unique(MDSplot$Group))
##MDSplot$GenoSex = factor(MDSplot$GenoSex, levels = unique(MDSplot$GenoSex))

  fig  = plot_ly(data = MDSplot, 
                 x = ~x, 
                 y = ~y,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Group,
                 ##legendrank = ~ as.numeric(Group),
                 symbols = rep(c('circle', 'triangle-down', 'triangle-up'),4),
                 colors = c("red","firebrick3","deeppink",
                            "lightskyblue","royalblue","cyan",
                            "gold", "darkgoldenrod1", "yellow",
                            "limegreen", "darkgreen", "chartreuse"),
                 marker = list(size = 25,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", MDSplot$Sample)) %>%
    layout(xaxis = list(title = paste0("Leading logFC dim 1 ", "(", round((MDSdata$var.explained[1]*100),1), "%)")),
           yaxis = list(title = paste0("Leading logFC dim 2 ", "(", round((MDSdata$var.explained[2]*100),1), "%)")))

fig

```

<br /><br /><br />
\newpage

```{r fig2, echo = F, fig.cap='Barplot of Total DEGs.'}

Female = c(nrow(sGR.F.CxDf), nrow(sGR.F.CxOE),
           nrow(sWT.F.CxDf), nrow(sWT.F.CxOE),
           nrow(sGRxWT.F), nrow(sGRxWT.FDf), nrow(sGRxWT.FOE))

Male = c(nrow(sGR.M.CxDf), nrow(sGR.M.CxOE),
         nrow(sWT.M.CxDf), nrow(sWT.M.CxOE),
         nrow(sGRxWT.M), nrow(sGRxWT.MDf), nrow(sGRxWT.MOE))

Comparison = c("GR.C x GR.Df", "GR.C x GR.OE",
               "WT.C x WT.Df", "WT.C x WT.OE",
               "GR.C x WT.C", "GR.Df x WT.Df", "GR.OE x WT.OE")

data = data.frame(Female, Male, Comparison)

data$Comparison = factor(data$Comparison, levels = data$Comparison)

fig <- plot_ly(data, 
               x = ~Comparison, y = ~Female, 
               type = 'bar',
               name = "Female",
               marker = list(color =c("firebrick"),
                             line = list(color = "black", width = 1.5)))

fig <- fig %>% add_trace(y = ~Male, name = 'Males',
                         marker = list(color = c("royalblue"),
                                       line = list(color = "black", width = 1.5)))

fig <- fig %>% layout(yaxis = list(title ="Total DEGs"),
                      xaxis = list(title = NA),
                      title = "Total DEGs")

fig

```

<br /><br /><br />
\newpage

```{r echo = F}

Comparisons = list(row.names(sGR.F.CxDf), row.names(sGR.F.CxOE),
                row.names(sWT.F.CxDf), row.names(sWT.F.CxOE),
                row.names(sGRxWT.F), row.names(sGRxWT.FDf), row.names(sGRxWT.FOE),
                row.names(sGR.M.CxDf), row.names(sGR.M.CxOE),
                row.names(sWT.M.CxDf), row.names(sWT.M.CxOE),
                row.names(sGRxWT.M), row.names(sGRxWT.MDf), row.names(sGRxWT.MOE))

```

<br /><br /><br />
\newpage

```{r fig3, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$Genotype == 'GR']

hmdata = cpmdata[Comparisons[[1]],Samples]
##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.FC x GR.FDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig4, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FOE.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$Genotype == 'GR']

hmdata = cpmdata[Comparisons[[2]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.FC x GR.FOE",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig5, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.FC x WT.FDf.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$Genotype == 'WT']

hmdata = cpmdata[Comparisons[[3]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "WT.FC x WT.FDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig6, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.FC x WT.FOE.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$Genotype == 'WT']

hmdata = cpmdata[Comparisons[[4]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "WT.FC x WT.FOE",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig7, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x WT.FC.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$TKT == 'Control']

hmdata = cpmdata[Comparisons[[5]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.FC x WT.FC",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig8, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FDf x WT.FDf.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$TKT == 'DF']

hmdata = cpmdata[Comparisons[[6]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.FDf x WT.FDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig9, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FOE x WT.FOE.'}

Samples = row.names(groups)[groups$Sex =='F'
                            & groups$TKT == 'OE']

hmdata = cpmdata[Comparisons[[7]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.FOE x WT.FOE",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig10, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x GR.MDf.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$Genotype == 'GR']

hmdata = cpmdata[Comparisons[[8]],Samples]
##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.MC x GR.MDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig11, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x GR.MOE.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$Genotype == 'GR']

hmdata = cpmdata[Comparisons[[9]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.MC x GR.MOE",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig12, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.MC x WT.MDf.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$Genotype == 'WT']

hmdata = cpmdata[Comparisons[[10]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "WT.MC x WT.MDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig13, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.MC x WT.MOE.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$Genotype == 'WT']

hmdata = cpmdata[Comparisons[[11]],Samples]

##max.hmdata = apply(hmdata, 1, max)
##hmdata = hmdata[max.hmdata > 5,]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "WT.MC x WT.MOE",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig14, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x WT.MC.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$TKT == 'Control']

hmdata = cpmdata[Comparisons[[12]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.MC x WT.MC",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig15, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MDf x WT.MDf.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$TKT == 'DF']

hmdata = cpmdata[Comparisons[[13]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.MDf x WT.MDf",
            custom_hovertext = cpm.text)

```

<br /><br /><br />
\newpage

```{r fig16, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MOE x WT.MOE.'}

Samples = row.names(groups)[groups$Sex =='M'
                            & groups$TKT == 'OE']

hmdata = cpmdata[Comparisons[[14]],Samples]

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = row.names(hmdata),
            key = T,
            column_text_angle = 90,
            col_side_colors=groups[Samples,1:3],
            col_side_palette=Spectral,
            main= "GR.MOE x WT.MOE",
            custom_hovertext = cpm.text)

```

### 2023-06-16 TKT_RNAseq/R Code/EdgeR_Analysis.R

@@ -1,0 +1,38 @@
+if (!require("BiocManager", quietly = TRUE))
+  install.packages("BiocManager")
+
+BiocManager::install("edgeR")
+
+library(edgeR)
+
+##Clean Trait Data and calculate CPMs
+countdata=read.csv("/Users/johncsantiago/Documents/TKT RNAseq/CountTables/TKT.counttable.csv",row.names=1)
+groups=read.csv("/Users/johncsantiago/Documents/TKT RNAseq/CountTables/TKT.metadata.csv",row.names=1)
+
+##normalize data
+countdata=countdata[, row.names(groups)]
+x <- countdata
+gr <- factor(groups$Groups)
+y <- DGEList(counts=x,group=gr)
+keep <- filterByExpr(y)
+y <- y[keep,,keep.lib.sizes=FALSE]
+z <- calcNormFactors(y, method = "TMM")
+##normalized cpm
+cpmdata=cpm(z)
+
+plotMDS(z, col=as.numeric(factor(gr)))
+
+##updated edger analysis pipeline
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design)
+fit <- glmQLFit(z, design)
+
+
+##compare = makeContrasts(Lactate, levels=design)
+##lrt = glmQLFTest(fit,contrast=as.vector(compare))
+
+##lrt <- glmLRT(fit,contrast=as.vector(compare))		
+##G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+##AFLF=G_X_E$table
+##sigsAFLF=AFLF[AFLF$FDR<.05,]

### 2023-06-17 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
TKT Heatmap app

@@
 sGRxWT.MOE=DEout[DEout$FDR<.05,]
+
+TKT.EdgeR = data.frame(GRF.CxDf = GR.F.CxDf[row.names(cpmdata),'FDR'],
+                       GRF.CxOE = GR.F.CxOE[row.names(cpmdata),'FDR'],
+
+                       WTF.CxDf = WT.F.CxDf[row.names(cpmdata),'FDR'],
+                       WTF.CxOE = WT.F.CxOE[row.names(cpmdata),'FDR'],
+
+                       GRxWT.FC = GRxWT.F[row.names(cpmdata),'FDR'],
+                       GRxWT.FDf = GRxWT.FDf[row.names(cpmdata),'FDR'],
+                       GRxWT.FOE = GRxWT.FOE[row.names(cpmdata),'FDR'],
+
+                       GRM.CxDf = GR.M.CxDf[row.names(cpmdata),'FDR'],
+                       GRM.CxOE = GR.M.CxOE[row.names(cpmdata),'FDR'],
+
+                       WTM.CxDf = WT.M.CxDf[row.names(cpmdata),'FDR'],
+                       WTM.CxOE = WT.M.CxOE[row.names(cpmdata),'FDR'],
+
+                       GRxWT.MC = GRxWT.M[row.names(cpmdata),'FDR'],
+                       GRxWT.MDf = GRxWT.MDf[row.names(cpmdata),'FDR'],
+                       GRxWT.MOE = GRxWT.MOE[row.names(cpmdata),'FDR'])
+
+row.names(TKT.EdgeR) = row.names(cpmdata)
+##write.csv(TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
+
+Female = c(nrow(sGR.F.CxDf), nrow(sGR.F.CxOE),
+           nrow(sWT.F.CxDf), nrow(sWT.F.CxOE),
+           nrow(sGRxWT.F), nrow(sGRxWT.FDf), nrow(sGRxWT.FOE))
+
+Male = c(nrow(sGR.M.CxDf), nrow(sGR.M.CxOE),
+         nrow(sWT.M.CxDf), nrow(sWT.M.CxOE),
+         nrow(sGRxWT.M), nrow(sGRxWT.MDf), nrow(sGRxWT.MOE))
 

### 2023-06-17 TKT_RNAseq/Apps/DEG Heatmap/app.R

@@ -8,12 +8,12 @@ if(length(new.packages)>0){
 library(shiny)
 library(ggfortify)
 library(heatmaply)
-library(plotly)
-library(colourpicker)
 
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
 cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
 groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
+TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
+
 convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)
 temp=convert[,"Symbol"]
 temp2=setdiff(row.names(cpmdata),convert[,2])
@@ -21,113 +21,69 @@ names(temp)=convert[,2]
 names(temp2)=temp2
 convert=c(temp,temp2)
 
+comparison.groups = data.frame(GRF.CxDf  = c("^GR.F","Tkt..GR.F"),
+                               GRF.CxOE  = c("^GR.F", "Tkt..GR.F"),
+                               WTF.CxDf  = c("^WT.F", "Tkt..WT.F"),
+                               WTF.CxOE  = c("^WT.F", "Tkt..WT.F"),
+                               GRxWT.FC  = c("^GR.F", "^WT.F"),
+                               GRxWT.FDf = c("TktDfGR.F", "TktDfWT.F"),
+                               GRxWT.FOE = c("TktOEGR.F", "TktOEWT.F"),
+                               GRM.CxDf  = c("^GR.M","Tkt..GR.M"),
+                               GRM.CxOE  = c("^GR.M","Tkt..GR.M"),
+                               WTM.CxDf  = c("^WT.M", "Tkt..WT.M"),
+                               WTM.CxOE  = c("^WT.M", "Tkt..WT.M"),
+                               GRxWT.MC  = c("^GR.M", "^WT.M"),
+                               GRxWT.MDf = c("TktDfGR.M", "TktDfWT.M"),
[…]

### 2023-06-17 TKT_RNAseq/Apps/DEG Heatmap/app.R
update TKT heatmap app

@@ -100,7 +100,7 @@ server <- function(input, output) {
     
     use.FDR = TKT.EdgeR[,as.numeric(input$comparison)]
     names(use.FDR) = row.names(TKT.EdgeR)
-    use.FDR = use.FDR[order(use.FDR)]
+    use.FDR = signif(use.FDR[order(use.FDR)],3)
     
     use.genes = use.FDR[1:as.numeric(input$tophits)]
     
@@ -145,6 +145,7 @@ output$DEG.Heatmap <- renderPlotly({
             col=RdYlBu(100)[100:1],
             scale="row",
             dendrogram = "both",
+            show_dendrogram = c(F,T),
             Rowv=T,
             Colv=T,
             cexRow = 1/(as.numeric(input$tophits)/25),
@@ -153,15 +154,14 @@ output$DEG.Heatmap <- renderPlotly({
             ##cexCol = col.text,
             cexCol = 1,
             key = T,
+            ##margins = c(50,350,NA,0),
+            ##row_dend_left = T,
             column_text_angle = 90,
             col_side_colors=color.groups,
             col_side_palette=Spectral,
             main=paste0("Top ",input$tophits, " DEGs for ", Titles[as.numeric(input$comparison)]),
             custom_hovertext = hover.text)
-})##, function() {
-  ##height = as.numeric(input$tophits)
-##})
-
+})
 }
 
 

### 2023-06-17 TKT_RNAseq/Apps/TKT PCA/app.R

@@ -1,0 +1,338 @@
+list.of.packages <- c("shiny", "ggfortify")
+new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
+if(length(new.packages)>0){
+  install.packages('shiny')
+  install.packages("ggfortify")
+}
+
+library(shiny)
+library(ggfortify)
+library(heatmaply)
+library(plotly)
+library(colourpicker)
+
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
+cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
+groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
+convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)
+temp=convert[,"Symbol"]
+temp2=setdiff(row.names(cpmdata),convert[,2])
+names(temp)=convert[,2]
+names(temp2)=temp2
+convert=c(temp,temp2)
+
+# Define UI for app that draws a histogram ----
+ui <- fluidPage(
+  titlePanel("TKT RNAseq Experiment: Custom PCA Figure"),
+  sidebarLayout(position="left", sidebarPanel(
+    
+    fluidRow(
+      column(6,
+    checkboxGroupInput("genotype",
+                       h5("Genotype"),
+                       choices = list("G85R" = "GR",
+                                      "WT" = "WT"),
+                       selected = ""),
+      ),
+    
+    column(6,
+    checkboxGroupInput("sex",
+                       h5("Sex"),
+                       choices = list("Male"   = "M",
+                                      "Female" = "F"),
+                       selected = ""),
+    ),),
+    
+    
+    fluidRow(
+      column(6,
+    checkboxGroupInput("tkt",
+                       h5("TKT"),
+                       choices = list("Control" = "Control",
+                                      "Deficient"    = "DF",
+                                      "Over Expression" = "OE"),
+                       selected = ""),
+      ),
+    
+    column(6,
+           radioButtons("pc",
+                              h5("PC"),
+                              choices = list("PC1/2" = 1,
[…]

### 2023-06-20 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
Update with refined normalization

@@
 author: "John Santiago"
-date: "2022-03-23"
+date: "2022-06-20"
 output: 
@@
 
-- #### Figure \@ref(fig:fig1): MDS plot
+### All samples processed together
+- #### Figure \@ref(fig:fig1): MDS plot, all samples
 
@@
 
-### TKT effect in female G85R
-- #### Figure \@ref(fig:fig3): Heatmaps of Total DEGs in GR.FC x GR.FDf
+### Male and female samples processed together with TEs and outlier libraries removed
+- #### Figure \@ref(fig:fig3): MDS plot, all samples
 
-- #### Figure \@ref(fig:fig4): Heatmaps of Total DEGs in GR.FC x GR.FOE
+- #### Figure \@ref(fig:fig4): Barplot of Total DEGs
 
-### TKT effect in female WT
-- #### Figure \@ref(fig:fig5): Heatmaps of Total DEGs in WT.FC x WT.FDf
+### Male and Female samples processed separately with TEs and outlier libraries removed
+- #### Figure \@ref(fig:fig5): MDS plot of female samples only
 
-- #### Figure \@ref(fig:fig6): Heatmaps of Total DEGs in WT.FC x WT.FOE
+- #### Figure \@ref(fig:fig6): MDS plot of male samples only
 
-### Genotype effect between female G85R and WT
-- #### Figure \@ref(fig:fig7): Heatmaps of Total DEGs in GR.FC x WT.FC
-
-- #### Figure \@ref(fig:fig8): Heatmaps of Total DEGs in GR.FDf x WT.FDf
-
-- #### Figure \@ref(fig:fig9): Heatmaps of Total DEGs in GR.FOE x WT.FOE
-
-### TKT effect in Male G85R
-- #### Figure \@ref(fig:fig10): Heatmaps of Total DEGs in GR.MC x GR.MDf
-
-- #### Figure \@ref(fig:fig11): Heatmaps of Total DEGs in GR.MC x GR.MOE
-
-### TKT effect in Male WT
-- #### Figure \@ref(fig:fig12): Heatmaps of Total DEGs in WT.MC x WT.MDf
-
-- #### Figure \@ref(fig:fig13): Heatmaps of Total DEGs in WT.MC x WT.MOE
-
-### Genotype effect between Male G85R and WT
-- #### Figure \@ref(fig:fig14): Heatmaps of Total DEGs in GR.MC x WT.MC
-
-- #### Figure \@ref(fig:fig15): Heatmaps of Total DEGs in GR.MDf x WT.MDf
-
-- #### Figure \@ref(fig:fig16): Heatmaps of Total DEGs in GR.MOE x WT.MOE
+- #### Figure \@ref(fig:fig7): Barplot of Total DEGs
 
@@
 
-MDSdata = plotMDS(z, col=as.numeric(factor(gr)))
+MDSdata = plotMDS(z, top = 13582, col=as.numeric(factor(gr)))
 
 temp=convert[,"Symbol"]
-temp2=setdiff(row.names(cpmdata),convert[,2])
+temp2=setdiff(row.names(countdata),convert[,2])
 names(temp)=convert[,2]
@@
 
+Comparisons = list(row.names(sGR.F.CxDf), row.names(sGR.F.CxOE),
+                row.names(sWT.F.CxDf), row.names(sWT.F.CxOE),
+                row.names(sGRxWT.F), row.names(sGRxWT.FDf), row.names(sGRxWT.FOE),
+                row.names(sGR.M.CxDf), row.names(sGR.M.CxOE),
+                row.names(sWT.M.CxDf), row.names(sWT.M.CxOE),
+                row.names(sGRxWT.M), row.names(sGRxWT.MDf), row.names(sGRxWT.MOE))
+
 ```
 
-```{r fig1, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot.'}
+```{r fig1, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, all samples.'}
 
@@
 
-```{r fig2, echo = F, fig.cap='Barplot of Total DEGs.'}
+```{r fig2, echo = F, fig.cap='Barplot of Total DEGs, all samples.'}
 
@@
 
-<br /><br /><br />
-\newpage
+```{r, include = F}
+###EdgeR with TEs and outlier libraries removed
 
-```{r echo = F}
+groups2 = groups[setdiff(row.names(groups), c("GR.F3", "TktDfWT.F3")),]##"WT.F3",
 
-Comparisons = list(row.names(sGR.F.CxDf), row.names(sGR.F.CxOE),
-                row.names(sWT.F.CxDf), row.names(sWT.F.CxOE),
-                row.names(sGRxWT.F), row.names(sGRxWT.FDf), row.names(sGRxWT.FOE),
-                row.names(sGR.M.CxDf), row.names(sGR.M.CxOE),
-                row.names(sWT.M.CxDf), row.names(sWT.M.CxOE),
-                row.names(sGRxWT.M), row.names(sGRxWT.MDf), row.names(sGRxWT.MOE))
+countdata2 = countdata[, row.names(groups2)]
+
+countdata2 = countdata2[-(grep("ti",row.names(countdata2))),]
+countdata2 = countdata2[-(grep("trans",row.names(countdata2))),]
+
+x <- countdata2
+gr <- factor(groups2$Group)
+y <- DGEList(counts=x,group=gr)
+keep <- filterByExpr(y)
+y <- y[keep,,keep.lib.sizes=FALSE]
+z <- calcNormFactors(y, method = "TMM")
+##normalized cpm
+cpmdata2=cpm(z)
+
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design, robust = T)
+
+fit <- glmQLFit(z, design)
+plotQLDisp(fit)
+
+##Will calculate fold-change with the first over the second
+
+##GR.F TKT control vs TKT altered
+compare = makeContrasts(TktDfGR.F-GR.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.F.CxDf2=DEout
+sGR.F.CxDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.F-GR.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.F.CxOE2=DEout
+sGR.F.CxOE2=DEout[DEout$FDR<.05,]
+
+##WT.F TKT control vs TKT altered
+compare = makeContrasts(TktDfWT.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.F.CxDf2=DEout
+sWT.F.CxDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEWT.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.F.CxOE2=DEout
+sWT.F.CxOE2=DEout[DEout$FDR<.05,]
+
+##WT.F vs GR.F
+compare = makeContrasts(GR.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.F2=DEout
+sGRxWT.F2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.F-TktDfWT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.FDf2=DEout
+sGRxWT.FDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.F-TktOEWT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.FOE2=DEout
+sGRxWT.FOE2=DEout[DEout$FDR<.05,]
+
+##GR.M TKT control vs TKT altered
+compare = makeContrasts(TktDfGR.M-GR.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.M.CxDf2=DEout
+sGR.M.CxDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.M-GR.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.M.CxOE2=DEout
+sGR.M.CxOE2=DEout[DEout$FDR<.05,]
+
+##WT.M TKT control vs TKT altered
+compare = makeContrasts(TktDfWT.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.M.CxDf2=DEout
+sWT.M.CxDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEWT.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.M.CxOE2=DEout
+sWT.M.CxOE2=DEout[DEout$FDR<.05,]
+
+##WT.M vs GR.M
+compare = makeContrasts(GR.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.M2=DEout
+sGRxWT.M2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.MDf2=DEout
+sGRxWT.MDf2=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.M-TktOEWT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.MOE2=DEout
+sGRxWT.MOE2=DEout[DEout$FDR<.05,]
+
+MDSdata2 = plotMDS(z, top = 13086, col=as.numeric(factor(gr)))
+
+Comparisons2 = list(row.names(sGR.F.CxDf2), row.names(sGR.F.CxOE2),
+                row.names(sWT.F.CxDf2), row.names(sWT.F.CxOE2),
+                row.names(sGRxWT.F2), row.names(sGRxWT.FDf2), row.names(sGRxWT.FOE2),
+                row.names(sGR.M.CxDf2), row.names(sGR.M.CxOE2),
+                row.names(sWT.M.CxDf2), row.names(sWT.M.CxOE2),
+                row.names(sGRxWT.M2), row.names(sGRxWT.MDf2), row.names(sGRxWT.MOE2))
+
+```
+
+```{r fig3, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, all samples, TEs and outlier libraries removed.'}
+
+MDSplot = data.frame(x = MDSdata2$x,
+                     y = MDSdata2$y,
+                     sample = row.names(groups2))
+MDSplot = cbind(MDSplot, groups[MDSplot$sample,])
+MDSplot$GenoSex = paste0(MDSplot$Genotype,MDSplot$Sex)
+MDSplot = MDSplot[order(MDSplot$TKT),]
+MDSplot = MDSplot[order(MDSplot$Sex),]
+MDSplot = MDSplot[order(MDSplot$GenoSex),]
+MDSplot$Group = factor(MDSplot$Group, levels = unique(MDSplot$Group))
+##MDSplot$GenoSex = factor(MDSplot$GenoSex, levels = unique(MDSplot$GenoSex))
+
+  fig  = plot_ly(data = MDSplot, 
+                 x = ~x, 
+                 y = ~y,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Group,
+                 ##legendrank = ~ as.numeric(Group),
+                 symbols = rep(c('circle', 'triangle-down', 'triangle-up'),4),
+                 colors = c("red","firebrick3","deeppink",
+                            "lightskyblue","royalblue","cyan",
+                            "gold", "darkgoldenrod1", "yellow",
+                            "limegreen", "darkgreen", "chartreuse"),
+                 marker = list(size = 25,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", MDSplot$Sample)) %>%
+    layout(xaxis = list(title = paste0("Leading logFC dim 1 ", "(", round((MDSdata2$var.explained[1]*100),1), "%)")),
+           yaxis = list(title = paste0("Leading logFC dim 2 ", "(", round((MDSdata2$var.explained[2]*100),1), "%)")))
+
+fig
 
@@
 
-```{r fig3, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
+```{r fig4, echo = F, fig.cap='Barplot of Total DEGs, all samples, TEs and outlier libraries removed.'}
 
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$Genotype == 'GR']
+Female = c(nrow(sGR.F.CxDf2), nrow(sGR.F.CxOE2),
+           nrow(sWT.F.CxDf2), nrow(sWT.F.CxOE2),
+           nrow(sGRxWT.F2), nrow(sGRxWT.FDf2), nrow(sGRxWT.FOE2))
 
-hmdata = cpmdata[Comparisons[[1]],Samples]
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
+Male = c(nrow(sGR.M.CxDf2), nrow(sGR.M.CxOE2),
+         nrow(sWT.M.CxDf2), nrow(sWT.M.CxOE2),
+         nrow(sGRxWT.M2), nrow(sGRxWT.MDf2), nrow(sGRxWT.MOE2))
+
+Comparison = c("GR.C x GR.Df", "GR.C x GR.OE",
+               "WT.C x WT.Df", "WT.C x WT.OE",
+               "GR.C x WT.C", "GR.Df x WT.Df", "GR.OE x WT.OE")
+
+data = data.frame(Female, Male, Comparison)
+
+data$Comparison = factor(data$Comparison, levels = data$Comparison)
+
+fig <- plot_ly(data, 
+               x = ~Comparison, y = ~Female, 
+               type = 'bar',
+               name = "Female",
+               marker = list(color =c("firebrick"),
+                             line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Male, name = 'Males',
+                         marker = list(color = c("royalblue"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% layout(yaxis = list(title ="Total DEGs"),
+                      xaxis = list(title = NA),
+                      title = "Total DEGs")
+
+fig
+
+```
+
+```{r, include = F}
+###EdgeR with TEs and outlier libraries removed, Females only
+
+groups3 = groups[setdiff(row.names(groups), c("GR.F3", "WT.F3","TktDfWT.F3")),]##
+
+groups3 = groups3[groups3$Sex == "F",]
+
+countdata3 = countdata[, row.names(groups3)]
+
+countdata3 = countdata3[-(grep("ti",row.names(countdata3))),]
+countdata3 = countdata3[-(grep("trans",row.names(countdata3))),]
+
+x <- countdata3
+gr <- factor(groups3$Group)
+y <- DGEList(counts=x,group=gr)
+keep <- filterByExpr(y)
+y <- y[keep,,keep.lib.sizes=FALSE]
+z <- calcNormFactors(y, method = "TMM")
+##normalized cpm
+cpmdata3=cpm(z)
+
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design, robust = T)
+
+fit <- glmQLFit(z, design)
+plotQLDisp(fit)
+
+##Will calculate fold-change with the first over the second
+
+##GR.F TKT control vs TKT altered
+compare = makeContrasts(TktDfGR.F-GR.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.F.CxDf3=DEout
+sGR.F.CxDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.F-GR.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.F.CxOE3=DEout
+sGR.F.CxOE3=DEout[DEout$FDR<.05,]
+
+##WT.F TKT control vs TKT altered
+compare = makeContrasts(TktDfWT.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.F.CxDf3=DEout
+sWT.F.CxDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEWT.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.F.CxOE3=DEout
+sWT.F.CxOE3=DEout[DEout$FDR<.05,]
+
+##WT.F vs GR.F
+compare = makeContrasts(GR.F-WT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.F3=DEout
+sGRxWT.F3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.F-TktDfWT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.FDf3=DEout
+sGRxWT.FDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.F-TktOEWT.F, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.FOE3=DEout
+sGRxWT.FOE3=DEout[DEout$FDR<.05,]
+
+MDSdata3 = plotMDS(z, top = 10968, col=as.numeric(factor(gr)))
+
+```
+
+```{r fig5, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, females only, TEs and outliers removed.'}
+
+MDSplot = data.frame(x = MDSdata3$x,
+                     y = MDSdata3$y,
+                     sample = row.names(groups3))
+MDSplot = cbind(MDSplot, groups[MDSplot$sample,])
+MDSplot$GenoSex = paste0(MDSplot$Genotype,MDSplot$Sex)
+MDSplot = MDSplot[order(MDSplot$TKT),]
+MDSplot = MDSplot[order(MDSplot$Sex),]
+MDSplot = MDSplot[order(MDSplot$GenoSex),]
+MDSplot$Group = factor(MDSplot$Group, levels = unique(MDSplot$Group))
+##MDSplot$GenoSex = factor(MDSplot$GenoSex, levels = unique(MDSplot$GenoSex))
+
+  fig  = plot_ly(data = MDSplot, 
+                 x = ~x, 
+                 y = ~y,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Group,
+                 ##legendrank = ~ as.numeric(Group),
+                 symbols = rep(c('circle', 'triangle-down', 'triangle-up'),4),
+                 colors = c("red","firebrick3","deeppink",
+                            "gold", "darkgoldenrod1", "yellow"),
+                 marker = list(size = 25,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", MDSplot$Sample)) %>%
+    layout(xaxis = list(title = paste0("Leading logFC dim 1 ", "(", round((MDSdata3$var.explained[1]*100),1), "%)")),
+           yaxis = list(title = paste0("Leading logFC dim 2 ", "(", round((MDSdata3$var.explained[2]*100),1), "%)")))
+
+fig
+
+```
+
+```{r, include = F}
+###EdgeR with TEs and outlier libraries removed, Males only
+
+groups4 = groups[groups$Sex == "M",]
+
+countdata4 = countdata[, row.names(groups4)]
+
+countdata4 = countdata4[-(grep("ti",row.names(countdata4))),]
+countdata4 = countdata4[-(grep("trans",row.names(countdata4))),]
+
+x <- countdata4
+gr <- factor(groups4$Group)
+y <- DGEList(counts=x,group=gr)
+keep <- filterByExpr(y)
+y <- y[keep,,keep.lib.sizes=FALSE]
+z <- calcNormFactors(y, method = "TMM")
+##normalized cpm
+cpmdata4=cpm(z)
+
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design, robust = T)
+
+fit <- glmQLFit(z, design)
+plotQLDisp(fit)
+
+##Will calculate fold-change with the first over the second
+
+##GR.M TKT control vs TKT altered
+compare = makeContrasts(TktDfGR.M-GR.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.M.CxDf3=DEout
+sGR.M.CxDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.M-GR.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.M.CxOE3=DEout
+sGR.M.CxOE3=DEout[DEout$FDR<.05,]
+
+##WT.F TKT control vs TKT altered
+compare = makeContrasts(TktDfWT.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.M.CxDf3=DEout
+sWT.M.CxDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEWT.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.M.CxOE3=DEout
+sWT.M.CxOE3=DEout[DEout$FDR<.05,]
+
+##WT.F vs GR.F
+compare = makeContrasts(GR.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.M3=DEout
+sGRxWT.M3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.MDf3=DEout
+sGRxWT.MDf3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktOEGR.M-TktOEWT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRxWT.MOE3=DEout
+sGRxWT.MOE3=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRMDfxWTM=DEout
+sGRMDfxWTM=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GRMDfxWTMDf=DEout
+sGRMDfxWTMDf=DEout[DEout$FDR<.05,]
+
+MDSdata4 = plotMDS(z, top = 12764, col=as.numeric(factor(gr)))
+
+```
+
+```{r fig6, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, males, TEs and outlier libraries removed.'}
+
+MDSplot = data.frame(x = MDSdata4$x,
+                     y = MDSdata4$y,
+                     sample = row.names(groups4))
+MDSplot = cbind(MDSplot, groups[MDSplot$sample,])
+MDSplot$GenoSex = paste0(MDSplot$Genotype,MDSplot$Sex)
+MDSplot = MDSplot[order(MDSplot$TKT),]
+MDSplot = MDSplot[order(MDSplot$Sex),]
+MDSplot = MDSplot[order(MDSplot$GenoSex),]
+MDSplot$Group = factor(MDSplot$Group, levels = unique(MDSplot$Group))
+##MDSplot$GenoSex = factor(MDSplot$GenoSex, levels = unique(MDSplot$GenoSex))
+
+  fig  = plot_ly(data = MDSplot, 
+                 x = ~x, 
+                 y = ~y,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Group,
+                 ##legendrank = ~ as.numeric(Group),
+                 symbols = rep(c('circle', 'triangle-down', 'triangle-up'),4),
+                 colors = c("lightskyblue","royalblue","cyan",
+                            "limegreen", "darkgreen", "chartreuse"),
+                 marker = list(size = 25,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", MDSplot$Sample)) %>%
+    layout(xaxis = list(title = paste0("Leading logFC dim 1 ", "(", round((MDSdata4$var.explained[1]*100),1), "%)")),
+           yaxis = list(title = paste0("Leading logFC dim 2 ", "(", round((MDSdata4$var.explained[2]*100),1), "%)")))
+
+fig
+
+```
+
+```{r fig7, echo = F, fig.cap='Barplot of Total DEGs, males and females processed separately, TEs and outlier libraries removed.'}
+
+Female = c(nrow(sGR.F.CxDf3), nrow(sGR.F.CxOE3),
+           nrow(sWT.F.CxDf3), nrow(sWT.F.CxOE3),
+           nrow(sGRxWT.F3), nrow(sGRxWT.FDf3), nrow(sGRxWT.FOE3))
+
+Male = c(nrow(sGR.M.CxDf3), nrow(sGR.M.CxOE3),
+         nrow(sWT.M.CxDf3), nrow(sWT.M.CxOE3),
+         nrow(sGRxWT.M3), nrow(sGRxWT.MDf3), nrow(sGRxWT.MOE3))
+
+Comparison = c("GR.C x GR.Df", "GR.C x GR.OE",
+               "WT.C x WT.Df", "WT.C x WT.OE",
+               "GR.C x WT.C", "GR.Df x WT.Df", "GR.OE x WT.OE")
+
+data = data.frame(Female, Male, Comparison)
+
+data$Comparison = factor(data$Comparison, levels = data$Comparison)
+
+fig <- plot_ly(data, 
+               x = ~Comparison, y = ~Female, 
+               type = 'bar',
+               name = "Female",
+               marker = list(color =c("firebrick"),
+                             line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Male, name = 'Males',
+                         marker = list(color = c("royalblue"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% layout(yaxis = list(title ="Total DEGs"),
+                      xaxis = list(title = NA),
+                      title = "Total DEGs")
+
+fig
+
+```
+
+```{r echo = F, fig.cap='Barplot of Total DEGs excluding TEs.'}
+
+Female.trim = c(nrow(sGR.F.CxDf2), nrow(sGR.F.CxOE2),
+           nrow(sWT.F.CxDf2), nrow(sWT.F.CxOE2),
+           nrow(sGRxWT.F2), nrow(sGRxWT.FDf2), nrow(sGRxWT.FOE2))
+
+Male.trim = c(nrow(sGR.M.CxDf2), nrow(sGR.M.CxOE2),
+         nrow(sWT.M.CxDf2), nrow(sWT.M.CxOE2),
+         nrow(sGRxWT.M2), nrow(sGRxWT.MDf2), nrow(sGRxWT.MOE2))
+
+Female = c(nrow(sGR.F.CxDf), nrow(sGR.F.CxOE),
+           nrow(sWT.F.CxDf), nrow(sWT.F.CxOE),
+           nrow(sGRxWT.F), nrow(sGRxWT.FDf), nrow(sGRxWT.FOE))
+
+Male = c(nrow(sGR.M.CxDf), nrow(sGR.M.CxOE),
+         nrow(sWT.M.CxDf), nrow(sWT.M.CxOE),
+         nrow(sGRxWT.M), nrow(sGRxWT.MDf), nrow(sGRxWT.MOE))
+
+Comparison = c("GR.C x GR.Df", "GR.C x GR.OE",
+               "WT.C x WT.Df", "WT.C x WT.OE",
+               "GR.C x WT.C", "GR.Df x WT.Df", "GR.OE x WT.OE")
+
+data = data.frame(Female, Female.trim, Male, Male.trim, Comparison)
+
+data$Comparison = factor(data$Comparison, levels = data$Comparison)
+
+fig <- plot_ly(data, 
+               x = ~Comparison, y = ~Female, 
+               type = 'bar',
+               name = "Female",
+               marker = list(color =c("firebrick"),
+                             line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Female.trim, name = 'Trim Female',
+                         marker = list(color = c("pink"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Male, name = 'Males',
+                         marker = list(color = c("royalblue"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Male.trim, name = 'Trim Males',
+                         marker = list(color = c("skyblue"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% layout(yaxis = list(title ="Total DEGs"),
+                      xaxis = list(title = NA),
+                      title = "Total DEGs")
+
+fig
+
+```
+
+<br /><br /><br />
+\newpage
+
+```{r echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
+
+Samples = row.names(groups2)[groups2$Sex =='M'
+                            & groups2$Genotype == 'GR']
+
+hmdata = cpmdata2[Comparisons2[[8]],Samples]
+
+hmdata=hmdata[2500:3000,]
+
+hmdata=hmdata[intersect(row.names(hmdata),row.names(cpmdata)),]
+
+hmdata=cbind(hmdata, cpmdata[row.names(hmdata),colnames(hmdata)])
+
+colnames(hmdata)[10:18] = paste0("Old.",colnames(hmdata)[10:18])
 
@@
             cexCol = .75,
-            labRow = row.names(hmdata),
+            labRow = as.character(row.names(hmdata)),
             key = T,
             column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
+            ##col_side_colors=groups[Samples,1:3],
+            ##col_side_palette=Spectral,
             main= "GR.FC x GR.FDf",
@@
 ```
-
-<br /><br /><br />
-\newpage
-
-```{r fig4, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FOE.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$Genotype == 'GR']
-
-hmdata = cpmdata[Comparisons[[2]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.FC x GR.FOE",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig5, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.FC x WT.FDf.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$Genotype == 'WT']
-
-hmdata = cpmdata[Comparisons[[3]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "WT.FC x WT.FDf",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig6, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.FC x WT.FOE.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$Genotype == 'WT']
-
-hmdata = cpmdata[Comparisons[[4]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "WT.FC x WT.FOE",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig7, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x WT.FC.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$TKT == 'Control']
-
-hmdata = cpmdata[Comparisons[[5]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.FC x WT.FC",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig8, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FDf x WT.FDf.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$TKT == 'DF']
-
-hmdata = cpmdata[Comparisons[[6]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.FDf x WT.FDf",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig9, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FOE x WT.FOE.'}
-
-Samples = row.names(groups)[groups$Sex =='F'
-                            & groups$TKT == 'OE']
-
-hmdata = cpmdata[Comparisons[[7]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.FOE x WT.FOE",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig10, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x GR.MDf.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$Genotype == 'GR']
-
-hmdata = cpmdata[Comparisons[[8]],Samples]
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.MC x GR.MDf",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig11, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x GR.MOE.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$Genotype == 'GR']
-
-hmdata = cpmdata[Comparisons[[9]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.MC x GR.MOE",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig12, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.MC x WT.MDf.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$Genotype == 'WT']
-
-hmdata = cpmdata[Comparisons[[10]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "WT.MC x WT.MDf",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig13, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in WT.MC x WT.MOE.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$Genotype == 'WT']
-
-hmdata = cpmdata[Comparisons[[11]],Samples]
-
-##max.hmdata = apply(hmdata, 1, max)
-##hmdata = hmdata[max.hmdata > 5,]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "WT.MC x WT.MOE",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig14, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MC x WT.MC.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$TKT == 'Control']
-
-hmdata = cpmdata[Comparisons[[12]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.MC x WT.MC",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig15, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MDf x WT.MDf.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$TKT == 'DF']
-
-hmdata = cpmdata[Comparisons[[13]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.MDf x WT.MDf",
-            custom_hovertext = cpm.text)
-
-```
-
-<br /><br /><br />
-\newpage
-
-```{r fig16, echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.MOE x WT.MOE.'}
-
-Samples = row.names(groups)[groups$Sex =='M'
-                            & groups$TKT == 'OE']
-
-hmdata = cpmdata[Comparisons[[14]],Samples]
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = row.names(hmdata),
-            key = T,
-            column_text_angle = 90,
-            col_side_colors=groups[Samples,1:3],
-            col_side_palette=Spectral,
-            main= "GR.MOE x WT.MOE",
-            custom_hovertext = cpm.text)
-
-```

### 2023-06-20 TKT_RNAseq/R Code/EdgeR_Analysis.R

@@ -9,6 +9,10 @@ library(edgeR)
 countdata=read.csv("/Users/johncsantiago/Documents/TKT RNAseq/CountTables/TKT.counttable.csv",row.names=1)
 groups=read.csv("/Users/johncsantiago/Documents/TKT RNAseq/CountTables/TKT.metadata.csv",row.names=1)
 
+##GR.F1.US = read.csv("/Users/johncsantiago/Downloads/GR-F1_CountTable_UnsortedBAM.txt", sep = "\t", row.names = 1, header = F)
+##countdata$GR.F1.US = GR.F1.US [row.names(countdata),1]
+##groups['GR.F1.US',] = c("GR.F1.US", "GR", "F", "4", "GR.F")
+
 ##normalize data
 countdata=countdata[, row.names(groups)]
 x <- countdata

### 2023-06-20 TKT_RNAseq/ShellScripts/GR-F1_STAR_UnsortedBAM.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+#SBATCH -J GR-F1_STAR_UnsortedBAM.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-840029517/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-840029517/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G GR-F1_STAR_UnsortedBAM.sh
+
+sampledir="/gpfs/data/kwharton/jsantiago/30-840029517/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-840029517/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+sample="GR-F1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+module load fastqc/0.11.5
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+
+module load star/2.7.3a
+
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+        
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20 --outSAMtype BAM Unsorted --outFileNamePrefix $stardir"Output_Files/BAM/"$sample
+
+module load samtools/1.3.1
+samtools index $stardir"Output_Files/BAM/"$sample"Aligned.out.bam"
+
+module load python/3.7.4
[…]

### 2023-06-21 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
fixed metadata table

@@
 groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv",row.names=1)
+
+write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
 
@@
 
+all.cpmgenes = unique(c(row.names(cpmdata3),row.names(cpmdata4)))
+
+all.cpmdata = matrix(NA, ncol = 33, nrow = length(all.cpmgenes))
+colnames(all.cpmdata) = c(colnames(cpmdata3),colnames(cpmdata4))
+row.names(all.cpmdata) = all.cpmgenes
+
+all.cpmdata[row.names(cpmdata3),colnames(cpmdata3)] = cpmdata3
+all.cpmdata[row.names(cpmdata4),colnames(cpmdata4)] = cpmdata4
+
+all.groups = groups[colnames(all.cpmdata),]
+
+all.TKT.EdgeR = all.cpmdata[, 1:14]
+colnames(all.TKT.EdgeR) = c('GRF.CxDf', 'GRF.CxOE', 
+                            'WTF.CxDf', 'WTF.CxOE', 
+                            'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
+                            'GRM.CxDf', 'GRM.CxOE', 
+                            'WTM.CxDf', 'WTM.CxOE', 
+                            'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')
+
+row.names(all.TKT.EdgeR) = row.names(all.cpmdata)
+
+all.TKT.EdgeR[,1] = GR.F.CxDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,2] = GR.F.CxOE3[row.names(all.cpmdata),'FDR']
+
+all.TKT.EdgeR[,3] = WTF.CxDf = WT.F.CxDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,4] = WTF.CxOE = WT.F.CxOE3[row.names(all.cpmdata),'FDR']
+
+all.TKT.EdgeR[,5] = GRxWT.FC = GRxWT.F3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,6] = GRxWT.FDf = GRxWT.FDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,7] = GRxWT.FOE = GRxWT.FOE3[row.names(all.cpmdata),'FDR']
+
+all.TKT.EdgeR[,8] = GRM.CxDf = GR.M.CxDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,9] = GRM.CxOE = GR.M.CxOE3[row.names(all.cpmdata),'FDR']
+
+all.TKT.EdgeR[,10] = WTM.CxDf = WT.M.CxDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,11] = WTM.CxOE = WT.M.CxOE3[row.names(all.cpmdata),'FDR']
+
+all.TKT.EdgeR[,12] = GRxWT.MC = GRxWT.M3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,13] = GRxWT.MDf = GRxWT.MDf3[row.names(all.cpmdata),'FDR']
+all.TKT.EdgeR[,14] = GRxWT.MOE = GRxWT.MOE3[row.names(all.cpmdata),'FDR']
+
+##write.csv(all.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
+##write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
+##write.csv(all.TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
+
 ```
@@
 
+Female.Only.trim = c(nrow(sGR.F.CxDf3), nrow(sGR.F.CxOE3),
+           nrow(sWT.F.CxDf3), nrow(sWT.F.CxOE3),
+           nrow(sGRxWT.F3), nrow(sGRxWT.FDf3), nrow(sGRxWT.FOE3))
+
+Male.Only.trim = c(nrow(sGR.M.CxDf3), nrow(sGR.M.CxOE3),
+         nrow(sWT.M.CxDf3), nrow(sWT.M.CxOE3),
+         nrow(sGRxWT.M3), nrow(sGRxWT.MDf3), nrow(sGRxWT.MOE3))
+
 Female = c(nrow(sGR.F.CxDf), nrow(sGR.F.CxOE),
@@
 
+fig <- fig %>% add_trace(y = ~Female.Only.trim, name = 'Trim Only Female',
+                         marker = list(color = c("red"),
+                                       line = list(color = "black", width = 1.5)))
+
 fig <- fig %>% add_trace(y = ~Male, name = 'Males',
@@
                          marker = list(color = c("skyblue"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Male.Only.trim, name = 'Trim Only Males',
+                         marker = list(color = c("blue"),
                                        line = list(color = "black", width = 1.5)))
@@
 
-```{r echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
+```{r echo = F, include = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
 

### 2023-06-21 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
TKT edgeR analysis update

@@
 
+### Testing potential outlier samples
+
+- #### Figure \@ref(fig:fig3): PCA of GR.F CxDf DEGs
+
+- #### Figure \@ref(fig:fig4): PCA of GR.F CxOE DEGs
+
+- #### Figure \@ref(fig:fig5): PCA of GR.FC x WT.FC DEGs
+
+- #### Figure \@ref(fig:fig6): PCA of WT.F CxDf DEGs
+
+- #### Figure \@ref(fig:fig7): PCA of WT.F CxOE DEGs
+
+- #### Figure \@ref(fig:fig8): PCA of TktDfGR.F x TktDfWT.F DEGs
+
 ### Male and female samples processed together with TEs and outlier libraries removed
-- #### Figure \@ref(fig:fig3): MDS plot, all samples
-
-- #### Figure \@ref(fig:fig4): Barplot of Total DEGs
+- #### Figure \@ref(fig:fig9): MDS plot, all samples
+
+- #### Figure \@ref(fig:fig10): Barplot of Total DEGs
 
 ### Male and Female samples processed separately with TEs and outlier libraries removed
-- #### Figure \@ref(fig:fig5): MDS plot of female samples only
-
-- #### Figure \@ref(fig:fig6): MDS plot of male samples only
-
-- #### Figure \@ref(fig:fig7): Barplot of Total DEGs
+- #### Figure \@ref(fig:fig11): MDS plot of female samples only
+
+- #### Figure \@ref(fig:fig12): MDS plot of male samples only
+
+- #### Figure \@ref(fig:fig13): Barplot of Total DEGs
+
+- #### Figure \@ref(fig:fig14): Barplot of Total DEGs for each comparison under the different trimming conditions
 
 <br /><br /><br />
+\newpage
+
+### Conclusion: GR.F3, WT.F3 and TktDfWT.F3 are outlier libraries that should be removed before further analysis but there is no need to process male and female samples separately
+
+<br /><br /><br /><br /><br /><br />
 \newpage
@@
 countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)
-groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv",row.names=1)
-
-write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
+groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/All.TKT.metadata.csv",row.names=1)
 
@@
 
-```
-
-```{r fig1, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, all samples.'}
+GroupsToDEGs = matrix("", nrow = 28, ncol = 3)
+
+GroupsToDEGs[,1] = c("GR.F", "TktDfGR.F",
+                     "GR.F", "TktOEGR.F",
+                     "WT.F", "TktDfWT.F",
+                     "WT.F", "TktOEWT.F",
+                     "GR.F", "WT.F",
+                     "TktDfGR.F", "TktDfWT.F",
+                     "TktOEGR.F", "TktOEWT.F",
+                     "GR.M", "TktDfGR.M",
+                     "GR.M", "TktOEGR.M",
+                     "WT.M", "TktDfWT.M",
+                     "WT.M", "TktOEWT.M",
+                     "GR.M", "WT.M",
+                     "TktDfGR.M", "TktDfWT.M",
+                     "TktOEGR.M", "TktOEWT.M")
+
+GroupsToDEGs[,2] = c("TktDfGR.F", "GR.F",
+                     "TktOEGR.F", "GR.F", 
+                     "TktDfWT.F", "WT.F", 
+                     "TktOEWT.F", "WT.F", 
+                     "WT.F", "GR.F", 
+                     "TktDfWT.F", "TktDfGR.F", 
+                     "TktOEWT.F", "TktOEGR.F", 
+                     "TktDfGR.M", "GR.M", 
+                     "TktOEGR.M", "GR.M", 
+                     "TktDfWT.M", "WT.M", 
+                     "TktOEWT.M", "WT.M", 
+                     "WT.M", "GR.M", 
+                     "TktDfWT.M", "TktDfGR.M", 
+                     "TktOEWT.M", "TktOEGR.M")
+
+GroupsToDEGs[,3] = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,
+                     8,8,9,9,10,10,11,11,12,12,13,13,14,14)
+
+```
+
+## <span style="text-decoration:underline">Do the samples group by condition?</span> 
+```{r fig1, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot using all samples. Of these, samples GR.F3, WT.F3 and TktDfWT.F3 stand out as potential outliers.'}
 
@@
 
-<br /><br /><br />
-\newpage
-
-```{r fig2, echo = F, fig.cap='Barplot of Total DEGs, all samples.'}
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+```{r fig2, echo = F, fig.cap='Barplot of Total DEGs observed with edgeR when using all samples.'}
 
@@
 
-```{r, include = F}
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+```{r, echo =F, include=F}
+##Supervised PCAs
+
+##Samples to plot
+##genotype = "GR"                       ##options = "GR", "WT", or "all"
+##sex      = "F"                         ##options = "M", "F", or "all"
+##tkt      = c("Control", "DF")                    ##options = "Control", "DF", "OE", or "all"
+
+                                       ##must choose genotype of first and second condition
+##DEGs.genotypes = c("GR", "GR")         ##length = 2; options = "GR", "WT", or "all"
+
+                                       ##a single sex, won't compare between sexs
+##DEGs.sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                       ##choose tkt expression of first and second condition
+##DEGs.tkt       = c("Control", "DF")    ##length = 1; "Control", "DF", "OE"
+
+                                  ##must choose genotype of first and second condition
+genotypes = c("GR", "GR")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "DF")    ##length = 1; "Control", "DF", "OE"
+
+##SupervisedPCA = function(genotype, sex, tkt, DEGs.genotypes, DEGs.sex, DEGs.tkt){
+SupervisedPCA = function(genotypes, sex, tkt){
+Group1=unique(groups[(groups$Genotype == genotypes[1] & ##DEGs.genotypes[1] &
+                      groups$Sex == sex & ##DEGs.sex &
+                      groups$TKT == tkt[1]), ##DEGs.tkt[1]), 
+                      "Group"])
+
+Group2=unique(groups[(groups$Genotype == genotypes[2] & ##DEGs.genotypes[2] &
+                      groups$Sex == sex & ##DEGs.sex &
+                      groups$TKT == tkt[2]), ##DEGs.tkt[2]), 
+                      "Group"])
+
+DEGs = GroupsToDEGs[(GroupsToDEGs[,1] == Group1 &
+                     GroupsToDEGs[,2] == Group2),
+                    3]
+
+DEGs = Comparisons[[as.numeric(DEGs)]]
+
+    use.groups =  groups[groups$Group == Group1 |
+                         groups$Group == Group2,]
+
+    ##if(genotype == "GR" | genotype == "WT"){
+      ##use.groups = use.groups[use.groups$Genotype == genotype,]
+    ##}
+
+    ##if(sex == "M" | sex == "F"){
+      ##use.groups = use.groups[use.groups$Sex == sex,]
+    ##}
+
+    ##if(length(tkt) == 1 & length(intersect(tkt, "all")) == 0){
+      ##use.groups = use.groups[use.groups$TKT == tkt,]
+    ##}
+
+    ##if(length(tkt) == 2){
+      ##use.groups = use.groups[use.groups$TKT == tkt[1]|
+                                ##use.groups$TKT == tkt[2],]
+    ##}
+
+    use.data   = cpmdata[DEGs,row.names(use.groups)]
+    pca <- prcomp(t(use.data), scale.=TRUE) 
+    gr <- as.data.frame(use.groups)
+    PC1=scale(pca$x[,1])
+    PC2=scale(pca$x[,2])
+    eigs <- pca$sdev^2
+    ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=row.names(gr),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=gr$Genotype, 
+                        Sex=gr$Sex, 
+                        TKT=gr$TKT,
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group=gr$Group)
+
+  fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~TKT,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 colors = c("firebrick","gold","deepskyblue"),
+                 marker = list(size = 25,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
+           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")))
+  return(fig)
+  }
+
+```
+
+## <span style="text-decoration:underline">Is the expression profile for GR.F3 an outlier in genes found DE GR.FC and GR.FDf?</span> 
+```{r fig3, echo = F, warning=F, fig.height=8, fig.width=8, echo = F, fig.cap='PCA of GR.F CxDf DEGs. Testing if GR.F3 is an outlier library.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("GR", "GR")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "DF")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">Is the expression profile for GR.F3 an outlier in genes found DE GR.FC and GR.FOE?</span> 
+```{r fig4, echo = F, warning=F, fig.height=8, fig.width=8, fig.cap='PCA of GR.F CxOE DEGs. Testing if GR.F3 is an outlier library.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("GR", "GR")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "OE")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">Are the expression profiles for GR.F3 and WT.F3 outliers in genes found DE GR.FC and WT.FC?</span> 
+```{r fig5, echo = F, warning=F, fig.height=8, fig.width=8, fig.cap='PCA of GR.FC x WT.FC DEGs. Testing if GR.F3 and WT.F3 are outlier libraries.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("GR", "WT")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "Control")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">Are the expression profiles for WT.F3 and TktDfWT.F3 outliers in genes found WT.FC and TktDfWT.F?</span> 
+```{r fig6, echo = F, warning=F, fig.height=8, fig.width=8, fig.cap='PCA of WT.F CxDf DEGs. Testing if WT.F3 and TktDfWT.F3 are outlier libraries.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("WT", "WT")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "DF")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">Is the expression profile for WT.F3 an outlier in genes found DE WT.FC and WT.FOE?</span> 
+```{r fig7, echo = F, warning=F, fig.height=8, fig.width=8, fig.cap='PCA of WT.F CxOE DEGs. Testing if WT.F3 is an outlier library.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("WT", "WT")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("Control", "OE")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">Is the expression profile for TktDfWT.F3 an outlier in genes found DE TktDfGR.F and TktDfWT.F?</span> 
+```{r fig8, echo = F, warning=F, fig.height=8, fig.width=8, fig.cap='PCA of TktDfGR.F x TktDfWT.F DEGs. Testing if TktDfWT.F3 is an outlier library.'}
+##Supervised PCAs
+##Samples to plot
+                                  ##must choose genotype of first and second condition
+genotypes = c("GR", "WT")         ##length = 2; options = "GR", "WT", or "all"
+
+                                  ##a single sex, won't compare between sexs
+sex       = "F"                   ##length = 1; options = "M", "F"
+
+                                  ##choose tkt expression of first and second condition
+tkt       = c("DF", "DF")    ##length = 1; "Control", "DF", "OE"
+
+SupervisedPCA(genotypes, sex, tkt)
+
+```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+```{r, echo = F, include = F}
 ###EdgeR with TEs and outlier libraries removed
@@
 
-```{r fig3, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, all samples, TEs and outlier libraries removed.'}
+## <span style="text-decoration:underline">Does processing the samples after removing the 3 outlier libraries and TEs improve sample normalization?</span> 
+```{r fig9, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot using all samples, with the TEs and outlier libraries removed.'}
 
@@
 
-<br /><br /><br />
-\newpage
-
-```{r fig4, echo = F, fig.cap='Barplot of Total DEGs, all samples, TEs and outlier libraries removed.'}
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+```{r fig10, echo = F, fig.cap='Barplot of Total DEGs found when using all samples with the TEs and outlier libraries removed.'}
 
@@
 ```
+
+<br /><br /><br /><br /><br /><br />
+\newpage
 
@@
 
-```{r fig5, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, females only, TEs and outliers removed.'}
+## <span style="text-decoration:underline">Does sex specifically processing the samples after removing the 3 outlier libraries and TEs improve sample normalization?</span> 
+```{r fig11, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot when the female samples are processed alone. The TEs and outlier libraries are removed.'}
 
@@
 
+<br /><br /><br /><br /><br /><br />
+\newpage
+
 ```{r, include = F}
@@
 
-```{r fig6, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot, males, TEs and outlier libraries removed.'}
+```{r fig12, echo = F, warning=F, fig.height=10, fig.width=10, fig.cap= 'MDS plot when the male samples are process alone only. The TEs are removed.'}
 
@@
 
-```{r fig7, echo = F, fig.cap='Barplot of Total DEGs, males and females processed separately, TEs and outlier libraries removed.'}
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+```{r fig13, echo = F, fig.cap='Barplot of Total DEGs when male and female samples are processed separately. The TEs and outlier libraries were removed.'}
 
@@
 
-```{r echo = F, fig.cap='Barplot of Total DEGs excluding TEs.'}
+<br /><br /><br /><br /><br /><br />
+\newpage
+
+## <span style="text-decoration:underline">How do the different processing methods alter the number of total DEGs?</span> 
+```{r fig14, echo = F, fig.cap='Barplot of Total DEGs for each comparison under the different trimming conditions.
+Different trimming conditions were: (1) all samples processed together with no TEs or outlier libraries removed; (2) trimmed data with TEs and outlier libraries removed, male and female samples processed together; (3) trimmed data with TEs and outlier libraries removed, male and female samples processed separately.'}
 
@@
 fig <- fig %>% add_trace(y = ~Female.trim, name = 'Trim Female',
+                         marker = list(color = c("red"),
+                                       line = list(color = "black", width = 1.5)))
+
+fig <- fig %>% add_trace(y = ~Female.Only.trim, name = 'Trim Only Female',
                          marker = list(color = c("pink"),
@@
 
-fig <- fig %>% add_trace(y = ~Female.Only.trim, name = 'Trim Only Female',
-                         marker = list(color = c("red"),
+fig <- fig %>% add_trace(y = ~Male, name = 'Males',
+                         marker = list(color = c("blue"),
                                        line = list(color = "black", width = 1.5)))
 
-fig <- fig %>% add_trace(y = ~Male, name = 'Males',
-                         marker = list(color = c("royalblue"),
+fig <- fig %>% add_trace(y = ~Male.trim, name = 'Trim Males',
+                         marker = list(color = c("cornflowerblue"),
                                        line = list(color = "black", width = 1.5)))
 
-fig <- fig %>% add_trace(y = ~Male.trim, name = 'Trim Males',
+fig <- fig %>% add_trace(y = ~Male.Only.trim, name = 'Trim Only Males',
                          marker = list(color = c("skyblue"),
-                                       line = list(color = "black", width = 1.5)))
-
-fig <- fig %>% add_trace(y = ~Male.Only.trim, name = 'Trim Only Males',
-                         marker = list(color = c("blue"),
                                        line = list(color = "black", width = 1.5)))
@@
 ```
-
-<br /><br /><br />
-\newpage
 

### 2023-06-21 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
Count and metadata using trimmed data
Fixed row names on TKT.EdgeR.Table.csv

@@
 
-groups2 = groups[setdiff(row.names(groups), c("GR.F3", "TktDfWT.F3")),]##"WT.F3",
+groups2 = groups[setdiff(row.names(groups), c("GR.F3", "WT.F3", "TktDfWT.F3")),]
 
@@
                 row.names(sGRxWT.M2), row.names(sGRxWT.MDf2), row.names(sGRxWT.MOE2))
+
+TKT.EdgeR2 = data.frame(GRF.CxDf = GR.F.CxDf2[row.names(cpmdata2),'FDR'],
+                        GRF.CxOE = GR.F.CxOE2[row.names(cpmdata2),'FDR'],
+
+                        WTF.CxDf = WT.F.CxDf2[row.names(cpmdata2),'FDR'],
+                        WTF.CxOE = WT.F.CxOE2[row.names(cpmdata2),'FDR'],
+
+                        GRxWT.FC = GRxWT.F2[row.names(cpmdata2),'FDR'],
+                        GRxWT.FDf = GRxWT.FDf2[row.names(cpmdata2),'FDR'],
+                        GRxWT.FOE = GRxWT.FOE2[row.names(cpmdata2),'FDR'],
+
+                        GRM.CxDf = GR.M.CxDf2[row.names(cpmdata2),'FDR'],
+                        GRM.CxOE = GR.M.CxOE2[row.names(cpmdata2),'FDR'],
+
+                        WTM.CxDf = WT.M.CxDf2[row.names(cpmdata2),'FDR'],
+                        WTM.CxOE = WT.M.CxOE2[row.names(cpmdata2),'FDR'],
+
+                        GRxWT.MC = GRxWT.M2[row.names(cpmdata2),'FDR'],
+                        GRxWT.MDf = GRxWT.MDf2[row.names(cpmdata2),'FDR'],
+                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'])
+
+##write.csv(cpmdata2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
+##write.csv(groups2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
+##write.csv(TKT.EdgeR2, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
 

### 2023-06-21 TKT_RNAseq/Apps/DEG Heatmap/app.R

@@ -98,6 +98,8 @@ server <- function(input, output) {
                                       grep(use.samples[2],colnames(cpmdata)))]
     use.cpm = cpmdata[,use.samples]
     
+    print(head(use.cpm))
+    
     use.FDR = TKT.EdgeR[,as.numeric(input$comparison)]
     names(use.FDR) = row.names(TKT.EdgeR)
     use.FDR = signif(use.FDR[order(use.FDR)],3)
@@ -107,7 +109,7 @@ server <- function(input, output) {
     use.cpm = use.cpm[names(use.genes),]
     
     use.data = cbind(use.genes, use.cpm)
-    
+
     return(use.data)
   })
 
@@ -131,7 +133,7 @@ output$DEG.Heatmap <- renderPlotly({
   
   FBgn = hmdata
   FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-  
+
   i=1
   while(i<ncol(hover.text)){
     hover.text[,i] = paste("CPM = ", hover.text[,i],

### 2023-06-22 TKT_RNAseq/Apps/TKT DEG Heatmap/app.R
TKT app finished

@@ -82,7 +82,7 @@ ui <- fluidPage(
     
     
     mainPanel(
-      plotlyOutput(outputId = "DEG.Heatmap", , height = 1000),
+      plotlyOutput(outputId = "DEG.Heatmap", height = 1000),
       ),
   )
 )
@@ -135,7 +135,7 @@ output$DEG.Heatmap <- renderPlotly({
   FBgn[,1:ncol(FBgn)] = row.names(FBgn)
 
   i=1
-  while(i<ncol(hover.text)){
+  while(i<=ncol(hover.text)){
     hover.text[,i] = paste("CPM = ", hover.text[,i],
                            "\nFDR = ", FDR[,i],
                            "\nFBgn = ", FBgn[,i])

### 2023-06-22 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R

@@ -1,0 +1,301 @@
+list.of.packages <- c("shiny", "ggfortify")
+new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
+if(length(new.packages)>0){
+  install.packages('shiny')
+  install.packages("ggfortify")
+}
+
+library(shiny)
+library(ggfortify)
+library(heatmaply)
+library(plotly)
+library(colourpicker)
+library(DT)
+
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
+cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
+groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
+TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
+convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)
+
+groups$GxS = paste0(groups$Genotype, groups$Sex)
+groups$GxTKT = paste0(groups$Genotype, groups$TKT)
+
+groups.use = matrix(0,nrow = nrow(groups), ncol = 8)
+row.names(groups.use) = row.names(groups)
+colnames(groups.use) = c("ALL","GR", "WT", "M", "F", "C", "DF", "OE")
+groups.use[                       ,      "ALL"] = 0
+groups.use[groups$Genotype == "GR",      "GR"]  = 1
+groups.use[groups$Genotype == "WT",      "WT"]  = 1
+groups.use[groups$Sex      == "M",       "M"]   = 1
+groups.use[groups$Sex      == "F",       "F"]   = 1
+groups.use[groups$TKT      == "Control", "C"]   = 1
+groups.use[groups$TKT      == "DF",      "DF"]  = 1
+groups.use[groups$TKT      == "OE",      "OE"]  = 1
+
+temp                   = convert[,c("updated.FBgn","Symbol")]
+temp2                  = setdiff(row.names(cpmdata),row.names(convert))
+temp2                  = matrix(rep(temp2,2), ncol=2)
+row.names(temp2)       = temp2[,1]
+colnames(temp2)        = colnames(temp)
+FBgn2Symbol            = rbind(temp,temp2)
[…]

### 2023-06-23 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
TKT app finished
added FxM Venn

@@
 library(heatmaply)
+library(VennDiagram)
 
@@
 
+compare = makeContrasts(GR.F-GR.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+GR.FxM=DEout
+sGR.FxM=DEout[DEout$FDR<.05,]
+
+compare = makeContrasts(WT.F-WT.M, levels=design)
+lrt = glmQLFTest(fit,contrast=as.vector(compare))
+G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEout=G_X_E$table
+WT.FxM=DEout
+sWT.FxM=DEout[DEout$FDR<.05,]
+
 MDSdata2 = plotMDS(z, top = 13086, col=as.numeric(factor(gr)))
@@
                         GRxWT.MDf = GRxWT.MDf2[row.names(cpmdata2),'FDR'],
-                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'])
+                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'],
+
+                        GR.FxM = GR.FxM[row.names(cpmdata2),'FDR'],
+                        WT.FxM = WT.FxM[row.names(cpmdata2),'FDR'])
+
+row.names(TKT.EdgeR2) = row.names(cpmdata2)
 
@@
 
-```{r echo = F, include = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
-
-Samples = row.names(groups2)[groups2$Sex =='M'
-                            & groups2$Genotype == 'GR']
-
-hmdata = cpmdata2[Comparisons2[[8]],Samples]
-
-hmdata=hmdata[2500:3000,]
-
-hmdata=hmdata[intersect(row.names(hmdata),row.names(cpmdata)),]
-
-hmdata=cbind(hmdata, cpmdata[row.names(hmdata),colnames(hmdata)])
-
-colnames(hmdata)[10:18] = paste0("Old.",colnames(hmdata)[10:18])
-
-row.names(hmdata) = convert[row.names(hmdata)]
-
-cpm.text = round(hmdata,1)
-i=1
-while(i<=ncol(cpm.text)){
-  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
-  i = i+1
-}
-
-  heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            Rowv=T,
-            Colv=T,
-            cexRow = .75, 
-            na.color="grey",
-            cexCol = .75,
-            labRow = as.character(row.names(hmdata)),
-            key = T,
-            column_text_angle = 90,
-            ##col_side_colors=groups[Samples,1:3],
-            ##col_side_palette=Spectral,
-            main= "GR.FC x GR.FDf",
-            custom_hovertext = cpm.text)
-
-```
+```{r fig15, echo = F, fig.cap='Venn Diagram of total DEGs between male and female samples in a G85R and WT background.'}
+
+GR.Up   = row.names(GR.FxM)[GR.FxM$logFC > 0 & GR.FxM$FDR <= .05]
+GR.Down = row.names(GR.FxM)[GR.FxM$logFC < 0 & GR.FxM$FDR <= .05]
+WT.Up   = row.names(WT.FxM)[WT.FxM$logFC > 0 & WT.FxM$FDR <= .05]
+WT.Down = row.names(WT.FxM)[WT.FxM$logFC < 0 & WT.FxM$FDR <= .05]
+
+##Sample titles as strings. Only fill in up to your number of selected categories
+set1="G85R - F > M"
+set2="G85R - M > F"
+set3="WT - F > M"
+set4="WT - F < M"
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=GR.Up
+s2=GR.Down
+s3=WT.Up
+s4=WT.Down
+
+#Quad Venn
+grid.newpage()
+tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)
+
+```

### 2023-06-23 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R
Made low count female reads FDR .05

@@ -72,7 +72,9 @@ ui <- fluidPage(
                                         
                                         "GR.MC~WT.MC"     = "GRxWT.MC",
                                         "GR.MDf~WT.MDf"   = "GRxWT.MDf",
-                                        "GR.MOE~WT.MOE"   = "GRxWT.MOE"),
+                                        "GR.MOE~WT.MOE"   = "GRxWT.MOE",
+                                        "GR.FC~GR.MC"     = "GR.FxM",
+                                        "WT.FC~WT.MC"     = "WT.FxM"),
                          selected="GRF.CxDf"),
              p("Choose Signifigance Order: Organize the 'Select Gene' drop down menu order by FDR observed for a comparison between specific conditions"),
              br(),
@@ -138,7 +140,7 @@ ui <- fluidPage(
     
     mainPanel(
       plotlyOutput(outputId = "plot",
-                   height=700, width=1300),
+                   height=600, width=1300),
       br(),
       DTOutput('data'),
       tableOutput("data1"),

### 2023-06-23 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R
upsdated app

@@ -144,7 +144,7 @@ ui <- fluidPage(
       br(),
       DTOutput('data'),
       tableOutput("data1"),
-      p("Table of FDR values generated in the indicated comparison")
+      p("Table of FDR values generated in the indicated comparison. NOTE: Since many genes were not expressed in females only, their FDRs were altered to reduce emphasis in DEG order. Expression cutoff was mean(GR.F1, GR.F2, WT.F1, Wt.F2) < 4")
 
     ),
 ),)
@@ -241,16 +241,16 @@ server <- function(input, output) {
     Table.names = Table.names[order(Table.names$Genotype),]
     Table.names = Table.names[order(Table.names$Sex),]
     
-    FDR.table = data.frame(GR.F      = FDR[c(NA, "GRF.CxDf", "GRF.CxOE", "GRxWT.FC", NA, NA)],
+    FDR.table = data.frame(GR.F      = FDR[c("GR.FxM", "GRF.CxDf", "GRF.CxOE", "GRxWT.FC", NA, NA)],
                            TktDfGR.F = FDR[c("GRF.CxDf", NA, NA, NA, "GRxWT.FDf", NA)],
                            TktOEGR.F = FDR[c("GRF.CxOE", NA, NA, NA, "GRxWT.FOE", NA)],
-                           WT.F      = FDR[c("GRxWT.FC", NA, NA, NA, "WTF.CxDf", "WTF.CxOE")],
+                           WT.F      = FDR[c("GRxWT.FC", NA, NA, "WT.FxM", "WTF.CxDf", "WTF.CxOE")],
                            TktDfWT.F = FDR[c(NA, "GRxWT.FDf", NA, "WTF.CxDf", NA, NA)],
                            TktOEWT.F = FDR[c(NA, NA, "GRxWT.FOE", "WTF.CxOE", NA, NA)],
-                           GR.M      = FDR[c(NA, "GRF.CxDf", "GRF.CxOE", "GRxWT.FC", NA, NA)],
+                           GR.M      = FDR[c("GR.FxM", "GRF.CxDf", "GRF.CxOE", "GRxWT.FC", NA, NA)],
                            TktDfGR.M = FDR[c("GRF.CxDf", NA, NA, NA, "GRxWT.FDf", NA)],
                            TktOEGR.M = FDR[c("GRF.CxOE", NA, NA, NA, "GRxWT.FOE", NA)],
[…]

### 2023-06-23 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
upsdated app
fixed edger html

@@
 
+- #### Figure \@ref(fig:fig15): Venn Diagram of total DEGs between male and female samples
+
+Venn Diagram of total DEGs between male and female samples
 <br /><br /><br />
@@
 
+##Removing genes that are too low expressed in Females frome the FxM DEGs
+temp = apply(cpmdata2[, c(1:2,29:30)], 1, mean)
+temp = temp[temp<4]
+GR.FxM[names(temp),"FDR"] = .05
+WT.FxM[names(temp),"FDR"] = .05
+
 MDSdata2 = plotMDS(z, top = 13086, col=as.numeric(factor(gr)))

### 2023-06-23 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R
updated app

@@ -41,6 +41,10 @@ colnames(temp2)        = colnames(temp)
 FBgn2Symbol            = rbind(temp,temp2)
 colnames(FBgn2Symbol)  = c("FBgn", "Symbol")
 
+filter1.genes = row.names(TKT.EdgeR)
+filter2.genes = row.names(TKT.EdgeR)
+url = "flybase.org"
+
 # Define UI for app that draws a histogram ----
 ui <- fluidPage(
   titlePanel("TKT RNAseq Experiment: Custom PCA Figure"),
@@ -49,8 +53,8 @@ ui <- fluidPage(
     br(),
     uiOutput("geneControls"),
     p("Select Gene: Use gene symbol if available. autocompletes"),
-    ##br(), 
-    
+    uiOutput("url"),
+
     fluidRow(
       column(6,
              selectInput("choice.order", h5("DEG Order"),
@@ -79,6 +83,7 @@ ui <- fluidPage(
              p("Choose Signifigance Order: Organize the 'Select Gene' drop down menu order by FDR observed for a comparison between specific conditions"),
              br(),
       ),
+      
       column(6,
              
              checkboxGroupInput("cond.select", h5("Select Conditions to Exclude"), 
@@ -91,7 +96,110 @@ ui <- fluidPage(
                                                "TKT OE"           = 8)),
              ##p("Select Any Conditions to Exclude"),
              ##br(), 
-      ),),
+      ),
+      
+      ),
+
+    fluidRow(
+      column(12,
+      h4("Select a Significance Filter Condition")
+    ),),
+    
+    
+    fluidRow(
+    
+    column(6,
+           radioButtons("fdr.filter1",
+                        h5(""),
+                        choices = list("none"                = 1,
+                                       "Significant in"      = 2,
+                                       "Not Significant in"  = 3),
+                        selected = 1),
+    ),
+    
+    column(6,
+           selectInput("deg.condition1", h5(""),
+                       choices = list("No Filter"       = "none",
+                                      "GR.FC~GR.FDf"    = "GRF.CxDf",
+                                      "GR.FC~GR.FOE"    = "GRF.CxOE",
+                                      
+                                      "WT.FC~WT.FDf"    = "WTF.CxDf",
[…]

### 2023-07-07 CamiCode.Rmd
Cami Stuff

---
title: "Defficiency Screen Functional Analysis"
author: "John Santiago"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r echo = F, include=F}
##Load Libraries

library(biomaRt)
library(org.Dm.eg.db)
library(goseq)
library(GO.db)
library(visNetwork)
library(rrvgo)
library(plotly)
library(KEGGREST)
library(pathview)
##library(RColorBrewer)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")

##background = setNames(unique(CamiData$Background), unique(CamiData$Background))

##moderate = setNames(rep(0, length(background)), names(background))

##moderate[unique(CamiData$Moderate)] = 1

##strong = setNames(rep(0, length(background)), names(background))

##strong[unique(CamiData$Strong)] = 1

##lethal = setNames(rep(0, length(background)), names(background))

##lethal[unique(CamiData$Lethal)] = 1

##enhancer = setNames(rep(0, length(background)), names(background))

##enhancer[unique(CamiData$Enhancers)] = 1

##no.effect = setNames(rep(0, length(background)), names(background))

##no.effect[unique(CamiData$No.Effect)] = 1

##FB2Ensembl
##x1=as.list(org.Dm.egENSEMBL2EG)
##Ensembl2Symbol
##x2=as.list(org.Dm.egSYMBOL)
##Symbol2Ensembl
##x3=as.list(org.Dm.egSYMBOL2EG)
##Ensembl2FB
##x4=as.list(org.Dm.egENSEMBL)
##ensembl to FBgn
##x5=as.list(org.Dm.egFLYBASE)

##FBgn2ensembl = row.names(CamiData)
##names(FBgn2ensembl) = row.names(CamiData)
##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
##FBgn2ensembl[names(tempEG)]=tempEG

##ensembl2symbol = row.names(CamiData)
##names(ensembl2symbol) = FBgn2ensembl
##tempSymbol = unlist(x2[FBgn2ensembl])
##ensembl2symbol[names(tempSymbol)]=tempSymbol
##symbol2ensembl = names(ensembl2symbol)
##names(symbol2ensembl) = ensembl2symbol

##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")

##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
##ensembl2symbol[row.names(extras)] = extras$SYMBOL

##symbol = ensembl2symbol

##symbol = background

##symbol[intersect(GeneIDKey$FBgn, background)] = 
##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]

##CamiData = data.frame(FBgn       = background[1:14674],
##                      Symbol     = symbol[1:14674],
##                      Moderate   = moderate[1:14674],
##                      Strong     = strong[1:14674],
##                      Lethal     = lethal[1:14674],
##                      Enhancer   = enhancer[1:14674],
##                      No.Effect  = no.effect[1:14674])

##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")

Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)

```

```{r include=F, echo=F}

kegg=keggLink("pathway","dme")
names(kegg)=gsub("dme:Dmel_","",names(kegg))

##i=1
##kegg.names=unique(substr(kegg,6,13))
##names(kegg.names)=as.vector(kegg.names)
##while(i<=length(kegg.names)){
##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
##  i=i+1
##}

##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)

temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
temp = temp[intersect(names(kegg),names(temp))]
kegg = kegg[intersect(names(kegg),names(temp))]
names(kegg) = temp[names(kegg)]
kegg = as.list(kegg)
keggID=keggConv("dme","ncbi-geneid")

##sigs = Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Repress.GO = GO.wall
##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Repress.KEGG = KEGG
##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Lethal.GO = GO.wall
##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Lethal.KEGG = KEGG
##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Enhance.GO = GO.wall
##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##EGG$Name=kegg.names[row.names(KEGG),1]
##Enhance.KEGG = KEGG
##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv")

Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)

Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)

```

```{r}

PathwayID = "04141"

download.kegg(pathway.id= PathwayID, species = "dme")
xml.file=paste0("dme",PathwayID,".xml")
node.data=node.info(xml.file)

all.path = names(kegg[grep(PathwayID,kegg)])

Moderate = Df.data[Df.data$Moderate == 1, "Symbol"]
Moderate = intersect(Moderate, all.path)
Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")

Strong = Df.data[Df.data$Strong == 1, "Symbol"]
Strong = intersect(Strong, all.path)
Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
Enhancer = intersect(Enhancer, all.path)
Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")

Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
Lethal = intersect(Lethal, all.path)
Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

plot.data.gene=node.map(mol.data=c(Moderate, Strong, Enhancer, Lethal), node.data, node.types="gene")
cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
cols.ts.gene[1:length(cols.ts.gene)] = 0

pdg.moderate=node.map(mol.data=Moderate, node.data, node.types="gene")
temp = node.color(pdg.moderate, limit=2, bins=2)
ctg.moderate = cols.ts.gene
ctg.moderate[temp!="#FFFFFF"]= 1 ##"gold2"

pdg.strong=node.map(mol.data=Strong, node.data, node.types="gene")
temp = node.color(pdg.strong, limit=2, bins=2)
ctg.strong = cols.ts.gene
ctg.strong[temp!="#FFFFFF"]= 1 ##"brown2"

pdg.enhancer=node.map(mol.data=Enhancer, node.data, node.types="gene")
temp = node.color(pdg.enhancer, limit=2, bins=2)
ctg.enhancer = cols.ts.gene
ctg.enhancer[temp!="#FFFFFF"]= 1 ##"deepskyblue"

pdg.lethal=node.map(mol.data=Lethal, node.data, node.types="gene")
temp = node.color(pdg.lethal, limit=2, bins=2)
ctg.lethal = cols.ts.gene
ctg.lethal[temp!="#FFFFFF"]= 1 ##"navyblue"

color.combos = data.frame(Moderate = as.numeric(ctg.moderate),
                          Strong = as.numeric(ctg.strong),
                          Enhancer = as.numeric(ctg.enhancer),
                          Lethal = as.numeric(ctg.lethal))
row.names(color.combos)= names(cols.ts.gene)

cols.ts.gene[cols.ts.gene=="0"]="darkseagreen1"

cols.ts.gene[row.names(color.combos)[color.combos$Moderate == 1]] = "gold2"
cols.ts.gene[row.names(color.combos)[color.combos$Strong   == 1]] = "brown1"
cols.ts.gene[row.names(color.combos)[color.combos$Enhancer   == 1]] = "lightsteelblue"
cols.ts.gene[row.names(color.combos)[color.combos$Lethal   == 1]] = "cornflowerblue"
cols.ts.gene[row.names(color.combos)[(color.combos$Moderate   == 1 | color.combos$Strong   == 1) & (color.combos$Enhancer   == 1 | color.combos$Lethal   == 1) ]] = "grey60"

pv.pars= keggview.native(plot.data.gene=plot.data.gene,
                         cols.ts.gene=cols.ts.gene, 
                         node.data=node.data,
                         pathway.name=paste0("dme", PathwayID),
                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1])

knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/dme04141.", kegg.names[paste0("dme", PathwayID),1], ".png"))

```

```{r include=F, echo=F}

GO.data = Repress.GO[Repress.GO$adjp <= .05 &
                     Repress.GO$ontology == 'BP',
                     c("category", "term","adjp", "numDEInCat", "numInCat")]

go_analysis = GO.data$category
scores = setNames(-log10(GO.data$adjp), go_analysis)

##simMatrix <- calculateSimMatrix(go_analysis,
##                                orgdb="org.Dm.eg.db",
##                                ont="BP",
##                                method="Rel")

##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")

##reducedTerms <- reduceSimMatrix(simMatrix,
##                                scores,
##                                threshold=0.7,
##                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)

```

```{r, fig.width= 10}

data = GO.data[,c("term","adjp","numDEInCat", "numInCat", "category")]
data = data[order(data$adjp, decreasing = T),]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Significantly Enriched GO term Summary",
           margin = m)

fig

```

```{r fig.height=7, fig.width=10}

heatmapPlot(simMatrix,
            reducedTerms,
            annotateParent=TRUE,
            annotationLabel="parentTerm",
            fontsize=6,
            main = "Repressor Gene Enriched Biological Process GO terms")

```

```{r, fig.align='left', include=F}

scatterPlot(simMatrix, reducedTerms)

```

```{r, fig.width=10}
 use.data   = simMatrix
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = reducedTerms[row.names(use.data), "parentTerm"],
                        Score = reducedTerms[row.names(use.data), "score"],
                        Term = reducedTerms[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 ##symbol = ~Group,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c("firebrick","gold","deepskyblue"),
                 marker = list(size = pca.data$Score,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Term, 
                                   "\nTotal DE: ", pca.data$TotalDE, 
                                   "\nTotal in Cat.: ", pca.data$Total, 
                                   "\nFDR: ", pca.data$SigVal)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "Enriched GO term similarity")

  fig

```

```{r fig.align='left'}

treemapPlot(reducedTerms)

```

```{r, include=F, echo=F}
GO2Gene   = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GenesInGOTerms.csv", row.names = 1)

ccpar=as.list(GOCCPARENTS)
ccchild=as.list(GOCCCHILDREN)

bppar=as.list(GOBPPARENTS)
bpchild=as.list(GOBPCHILDREN)

mfpar=as.list(GOMFPARENTS)
mfchild=as.list(GOMFCHILDREN)
```

```{r, include=F, echo=F}

compare = "GRM.CxDf"
filter.samples = c("GR.M", "TktDfGR.M")

sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,compare]<=.05]
sigs = sigs[apply(cpmdata[sigs,groups$Group %in% filter.samples], 1, min) > 10]

genes=c(rep(0, nrow(cpmdata)))
names(genes) = row.names(cpmdata)
genes[sigs] = 1
names(genes) = GeneIDKey[names(genes), "Symbol"]

pwf=nullp(genes,"dm3","geneSymbol")

GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category

GO.wall$Significant = "not"
GO.wall[GO.wall$adjp <= .05, "Significant"] = "sig"
sigGO = GO.wall[GO.wall$adjp<.05,]

##Biological Processes
bpGO = sigGO[sigGO$ontology == 'BP',]

##parent terms are those directly above in hierarchy
## isa implies a defining relationship; part of implies they contribute to the category

parents = bppar[bpGO$category]

parents = data.frame(from = unlist(parents),
                     label = substring(names(unlist(parents)),12),
                     to = substring(names(unlist(parents)),1,10))

parents = parents[parents$to %in% row.names(GO.wall),]

children = bpchild[bpGO$category]

children = data.frame(from = substring(names(unlist(children)),1,10),
                      label = substring(names(unlist(children)),12),
                      to = unlist(children))

children = children[children$to %in% row.names(GO.wall),]

edges = rbind(parents, children)
edges = edges[edges$label == "isa",]
edges = unique(edges)

edges = edges[GO.wall[edges$to, "numDEInCat"]>0,]

node.id = unique(c(edges$from, edges$to))
node.label = GO.wall[node.id, "term"]
node.group = GO.wall[node.id, "Significant"]
node.value = 100*(GO.wall[node.id, "numDEInCat"]/GO.wall[node.id, "numInCat"])

nodes = data.frame(id = node.id,
                   label = node.label,
                   group = node.group,
                   value = node.value)
```

```{r include=F}

visNetwork(nodes, edges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-70),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "sig", shape = "box", color = list(background = "gold", border="black", groupname="black"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "not", shape = "dot", color = list(background = "grey", border="black", groupname="black"),physics=T,font=list(color="black"))

```

### 2023-07-07 CamiData.Rmd
Cami Stuff

---
title: "Lean Top PC1 Function Figures"
author: "John Santiago"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r include=F}
##Load Libraries
library(tidyverse)
library(edgeR)
library(pca3d) # Requires XQuartz on macOS X
library(ggfortify)
library(directlabels)
library(plot3D)
library(rgl)
library(plot3Drgl)
library(heatmaply)
library(gplots)
library(biomaRt)
library(scatterplot3d)
library(org.Hs.eg.db)
library(goseq)
library(reshape2)
library(GO.db)
library(igraph)
library(clusterProfiler)
library(visNetwork)
library(circlize)
```

```{r}
x1=as.list(org.Hs.egENSEMBL2EG)
x2=as.list(org.Hs.egSYMBOL)
x3=as.list(org.Hs.egSYMBOL2EG)
x4=as.list(org.Hs.egENSEMBL)

ccpar=as.list(GOCCPARENTS)
ccchild=as.list(GOCCCHILDREN)

bppar=as.list(GOBPPARENTS)
bpchild=as.list(GOBPCHILDREN)

mfpar=as.list(GOMFPARENTS)
mfchild=as.list(GOMFCHILDREN)

term=as.list(GOTERM)

genesingo=as.list(org.Hs.egGO2ALLEGS)

##bm = useMart("ensembl")
##bm = useDataset("hsapiens_gene_ensembl", mart=bm)
##EG2GO = getBM(mart=bm, attributes=c('ensembl_gene_id','go_id'))

##geneID2GO = by(EG2GO$go_id,
                ##EG2GO$ensembl_gene_id,
                ##function(x) as.character(x))

##GO2geneID = by(EG2GO$ensembl_gene_id,
                ##EG2GO$go_id,
                ##function(x) as.character(x))

##save(geneID2GO, file="/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/geneID2GO.RData")
##save(GO2geneID, file="/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/GO2geneID.RData")
##save(GO2geneID, file="/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/GO2geneID.RData")
load("/Users/johncsantiago/Google Drive/My Drive/Sanders Lab Files/All Code/geneID2GO.RData")
load("/Users/johncsantiago/Google Drive/My Drive/Sanders Lab Files/All Code/GO2geneID.RData")

GOnetwork=function(ont,parent,child,GOlist,goi){
##generates a vector of all genes in the GOlist with associated GOterms as names
  GOterms=GOlist$category[GOlist$ontology==ont&GOlist$adjp<.5]
  allgogenes=unlist(GO2geneID[GOterms])
  gogenes=intersect(allgogenes,goi)
  edge.data=c(allgogenes[allgogenes==gogenes[1]])
  i=2
  while(i<=length(gogenes)){
    edge.data=c(edge.data,allgogenes[allgogenes==gogenes[i]])
    i=i+1
  }
  names(edge.data)=substring(names(edge.data),1,10)

##generates a table with all parent terms for each significant GO term
  temp=GOlist$category[GOlist$adjp<.05&GOlist$ontology==ont]
  temp2=parent[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp4
  temp7[,2]=temp6
  temp7[,3]=temp5
  colnames(temp7)=c("parent","relationship","child")
  edges=temp7

##generates a table with all child terms for each significant GO term
  temp=GOlist$category[GOlist$adjp<.05&GOlist$ontology==ont]
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")

edges=rbind(edges,temp7)

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont][1:5]))>0){
    nodegroups[i]="Top 5 Sig. Enriched"
  }
  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Top 5 Sig. Enriched", shape = "dot", color = list(background = "red", border="firebrick", groupname="white"),physics=T,font=list(color="black"))%>%
  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)
}

childGOnetwork=function(ont,parent,child,GOlist,goi){
##generates a vector of all genes in the GOlist with associated GOterms as names
  GOterms=GOlist$category[GOlist$ontology==ont&GOlist$adjp<.5]
  allgogenes=unlist(GO2geneID[GOterms])
  gogenes=intersect(allgogenes,goi)
  edge.data=c(allgogenes[allgogenes==gogenes[1]])
  i=2
  while(i<=length(gogenes)){
    edge.data=c(edge.data,allgogenes[allgogenes==gogenes[i]])
    i=i+1
  }
  names(edge.data)=substring(names(edge.data),1,10)

##generates a table with all child terms for each significant GO term
  temp=GOlist$category[GOlist$adjp<.05&GOlist$ontology==ont]
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")

edges=temp7

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }

  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%

  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)
}

```

```{r include =F}
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/SandersLab/MGH_2020/RNA-Seq Data Files/mgh_raw_countdata.csv",row.names=1)
groups=read.csv("/Users/johncsantiago/Documents/GitHub/SandersLab/MGH_2020/RNA-Seq Data Files/mgh_metadata.csv",row.names=1)

LiverMetrics = read.csv("https://raw.githubusercontent.com/johncsantiago/Lactate-Correlation-Manuscript/master/Data/AllLiverTraitData.csv", row.names=1)
LiverMetrics=LiverMetrics[-na.action(na.omit(LiverMetrics$RNAseq.ID)),]
LiverMetrics = LiverMetrics[-na.action(na.omit(LiverMetrics$Function)),]
countdata = countdata[,LiverMetrics$RNAseq.ID]
groups=groups[LiverMetrics$RNAseq.ID,]

##EdgeR comparisons
countdata=countdata[,row.names(groups)]
##countdata=countdata[,groups$fat=="F"]
##groups=groups[groups$fat=="F",]
countdata=countdata[,row.names(groups)]
x <- countdata
group <- factor(groups$Group)
y <- DGEList(counts=x,group=group)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE] 
z <- calcNormFactors(y, method = "TMM") 
cpmdata=cpm(z)

##updated edger analysis pipeline
design<-model.matrix(~LiverMetrics$alactate)
colnames(design)[2] <- "Lactate"

design<-model.matrix(~0 + LiverMetrics$Function)
colnames(design) <- c('AF', 'IF', 'LF')

##z = estimateGLMCommonDisp(z,design, verbose=T)
##z = estimateGLMTrendedDisp(z,design)
##z = estimateGLMTagwiseDisp(z,design)
z = estimateDisp(z, design)
fit <- glmQLFit(z, design)

compare = makeContrasts(Lactate, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))

##lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
AFLF=G_X_E$table
sigsAFLF=AFLF[AFLF$FDR<.05,]
plot(data[colnames(cpm.0H),'LacTime3H'], cpm.0H[row.names(sigsAFLF)[1],])

design<-model.matrix(~0+groups$Group)
colnames(design) <- levels(group)
z = estimateGLMCommonDisp(z,design, verbose=T)
z = estimateGLMTrendedDisp(z,design)
z = estimateGLMTagwiseDisp(z,design)
fit <- glmFit(z, design)

##comparisons
##3 hour NV vs 0 hour NV
compare = makeContrasts((LN2-LN1), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
LN2=G_X_E$table

##6 hour NV vs 0 hour NV
compare = makeContrasts((LN3-LN1), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
LN3=G_X_E$table

##3 hour V vs 0 hour V
compare = makeContrasts((LV2-LV1), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
LV2=G_X_E$table

##6 hour V vs 0 hour V
compare = makeContrasts((LV3-LV1), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
LV3=G_X_E$table

##0 hour V vs 0 hour NV
compare = makeContrasts((LV1-LN1), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
L1=G_X_E$table

##3 hour V vs 3 hour NV
compare = makeContrasts((LV2-LN2), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
L2=G_X_E$table

##6 hour V vs 6 hour NV
compare = makeContrasts((LV3-LN3), levels=design)
lrt <- glmLRT(fit,contrast=as.vector(compare))		
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
L3=G_X_E$table

sLV2=LV2[LV2$FDR<.05,]
sLV3=LV3[LV3$FDR<.05,]
sLN2=LN2[LN2$FDR<.05,]
sLN3=LN3[LN3$FDR<.05,]
sL1=L1[L1$FDR<.05,]
sL2=L2[L2$FDR<.05,]
sL3=L3[L3$FDR<.05,]

cpmmean=cpmdata[,18:35]
colnames(cpmmean)[1:6]=c("LV 0H","LV 3H","LV 6H","LN 0H","LN 3H","LN 6H")
cpmmean[,1]=(cpmmean[,1]+cpmmean[,2]+cpmmean[,3])/3
cpmmean[,2]=(cpmmean[,4]+cpmmean[,5]+cpmmean[,6])/3
cpmmean[,3]=(cpmmean[,7]+cpmmean[,8]+cpmmean[,9])/3
cpmmean[,4]=(cpmmean[,10]+cpmmean[,11]+cpmmean[,12])/3
cpmmean[,5]=(cpmmean[,13]+cpmmean[,14]+cpmmean[,15])/3
cpmmean[,6]=(cpmmean[,16]+cpmmean[,17]+cpmmean[,18])/3
cpmmean=cpmmean[,1:6]

scalecpm=t(apply(cpmdata[,18:35], MARGIN = 1, FUN = scale ))
colnames(scalecpm)=colnames(cpmdata)[18:35]
scalemeancpm=t(apply(cpmmean, MARGIN = 1, FUN = scale ))
colnames(scalemeancpm)=c("LV 0H","LV 3H","LV 6H","LN 0H","LN 3H","LN 6H")

pca <- prcomp(t(cpmdata[,18:35]), scale.=TRUE) 
gr <- factor(row.names(groups))
contribution=pca$rotation

##Because the sum of the squares of all loadings for an individual principal component must sum to one, we can calculate what the loadings would be if all variables contributed equally to that principal component.

##Any variable that has a larger loading than this value (positive or negative) contributes more than one variable’s worth of information and would be regarded as an important contributor to that principal component.
equalloading.cutoff=sqrt(1/nrow(contribution))

PC1contribute=contribution[,1]
PC1contribute=PC1contribute[order(PC1contribute,decreasing=T)]

PC2contribute=contribution[,2]
PC2contribute=PC2contribute[order(PC2contribute,decreasing=T)]

PC3contribute=contribution[,3]
PC3contribute=PC3contribute[order(PC3contribute,decreasing=T)]

```

```{r , fig.align="center"}

xcoords=pca$x[,1]
ycoords=pca$x[,3]

eigs <- pca$sdev^2
ve=(eigs / sum(eigs))*100
ve=signif(ve,3)

pcacolors=c("darkgreen","red4")
text2D(x=xcoords,y=ycoords,labels = c(rep("",18)), 
       col=c(pcacolors[c(rep(1,9),rep(2,9))]),
       xlab=paste("PC1 (",ve[1],"%)",sep=""),ylab=paste("PC3 (",ve[3],"%)",sep=""),xlim=c(-150,150),ylim=c(-75,100))

lines2D(x=xcoords[c(1,4,7)],y=ycoords[c(1,4,7)],col=pcacolors[1],add=T,lty=1)
lines2D(x=xcoords[c(2,5,8)],y=ycoords[c(2,5,8)],col=pcacolors[1],add=T,lty=2)
lines2D(x=xcoords[c(3,6,9)],y=ycoords[c(3,6,9)],col=pcacolors[1],add=T,lty=3)
lines2D(x=xcoords[c(10,13,16)],y=ycoords[c(10,13,16)],col=pcacolors[2],add=T,lty=1)
lines2D(x=xcoords[c(11,14,17)],y=ycoords[c(11,14,17)],col=pcacolors[2],add=T,lty=2)
lines2D(x=xcoords[c(12,15,18)],y=ycoords[c(12,15,18)],col=pcacolors[2],add=T,lty=3)

points2D(x=xcoords[1:3],y=ycoords[1:3],type="p",colkey=F,col="darkgreen",add=T,pch=21,bg="green",cex=2)
points2D(x=xcoords[4:6],y=ycoords[4:6],type="p",colkey=F,col="darkgreen",add=T,pch=24,bg="green",cex=2)
points2D(x=xcoords[7:9],y=ycoords[7:9],type="p",colkey=F,col="darkgreen",add=T,pch=22,bg="green",cex=2)

points2D(x=xcoords[10:12],y=ycoords[10:12],type="p",colkey=F,col="red4",add=T,pch=21,bg="red",cex=2)
points2D(x=xcoords[13:15],y=ycoords[13:15],type="p",colkey=F,col="red4",add=T,pch=24,bg="red",cex=2)
points2D(x=xcoords[16:18],y=ycoords[16:18],type="p",colkey=F,col="red4",add=T,pch=22,bg="red",cex=2)

abline(h=0,lty=2)
abline(v=0,lty=2)

legend("topleft", legend=c("Lean Viable","Lean Non-Viable"),col=c("green3","red"),lty=1,bty="n",lwd=2)
```

```{r include=F}

PCcontribute=PC1contribute
loading=(PCcontribute)
eigs <- pca$sdev^2
ve=(eigs / sum(eigs))*100
percent.variation=signif(ve,4)

##The column sum of squares of the loadings (pca$rotation) are the variances of PCs.
percents=(PCcontribute*PCcontribute)
percents=percents[order(percents,decreasing=T)]
loading=loading[names(percents)]
percent2=percents
temppercent=0
i=1
while(i<=length(percents)){
  percents[i]=percents[i]+temppercent
  temppercent=percents[i]
  i=i+1
}

percents=percents[loading[names(percents)]>0]
hmd=names(percents)[percents<=.1]
toppc1=hmd
hmd=cpmdata[(hmd),18:35]

hmcolors=colorpanel(100,"royalblue4","white","firebrick4")
```

```{r include=F}
sigs=row.names(hmd)
bg=cpmdata[,1:2]
bg[,1]=0
bg[sigs,1]=1
genes=bg[,1]
names(genes)=row.names(bg)
table(genes)
pwf=nullp(genes,"hg19","ensGene")
head(pwf)

  GO.wall=goseq(pwf,"hg19","ensGene")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")

PC1GO=GO.wall

id2name=PC1GO$term
names(id2name)=PC1GO$category

name2id=PC1GO$category
names(name2id)=PC1GO$term

getGeneLists <- function(pwf, goterms, genome, ids){
  gene2cat <- getgo(rownames(pwf), genome, ids)
  cat2gene <- split(rep(names(gene2cat), sapply(gene2cat, length)),
                    unlist(gene2cat, use.names = FALSE))
  out <- list()
  for(term in goterms){
    tmp <- pwf[cat2gene[[term]],]
    tmp <- rownames(tmp[tmp$DEgenes > 0, ])
    out[[term]] <- tmp
  }
  out
}
PC1gtg <- getGeneLists(pwf, GO.wall$category, "hg19", "ensGene")
PC1hasgo=intersect(sigs,unlist(PC1gtg))
PC1nogo=setdiff(sigs,unlist(PC1gtg))
```

```{r fig.width=8,fig.height=8, fig.align="center"}
heatmaply(hmd[c(PC1hasgo,PC1nogo),],scale="row",trace="none",Colv = F,Rowv=F,cexRow = .1,main="Top 10% PC1 Contribution",col=hmcolors, dendrogram = "none",row_side_colors = c(rep("In Sig. GO",length(PC1hasgo)),rep("No Sig. GO",length(PC1nogo))),row_side_palette = c("In Sig. GO"="gold","No Sig. GO"="forestgreen"))
```

```{r fig.width=8,fig.height=8, fig.align="center"}
hmd.mean=hmd[,1:6]
colnames(hmd.mean)=c("LV 0H","LV 3H","LV 6H","LN 0H","LN 3H","LN 6H")
hmd.mean[,1]=(hmd[,1]+hmd[,2]+hmd[,3])/3
hmd.mean[,2]=(hmd[,4]+hmd[,5]+hmd[,6])/3
hmd.mean[,3]=(hmd[,7]+hmd[,8]+hmd[,9])/3
hmd.mean[,4]=(hmd[,10]+hmd[,11]+hmd[,12])/3
hmd.mean[,5]=(hmd[,13]+hmd[,14]+hmd[,15])/3
hmd.mean[,6]=(hmd[,16]+hmd[,17]+hmd[,18])/3

heatmaply(hmd.mean,scale="row",trace="none",Colv = F,cexRow = .1,main="Top 10% PC1 Contribution",col=hmcolors, dendrogram = "none",row_side_colors = c(rep("In Sig. GO",length(PC1hasgo)),rep("No Sig. GO",length(PC1nogo))),row_side_palette = c("In Sig. GO"="gold","No Sig. GO"="forestgreen"))
```

PC1 CC
Super general: nucleus, cytosol, protein containing complex, intracellular
```{r}
##"CC" "MF" "BP"
ont="CC"
##ccpar mfpar bppar
parent=ccpar
##ccchild mfchild bpchild
child=ccchild
##a GOseq output table
GOlist=PC1GO
goi=toppc1

##GOnetwork(ont,parent,child,GOlist,goi)

```

PC1 BP
ribosomal biogenesis, , regulation of translation, transcription, DNA-templated, Gene expression, RNA processing
PC1BPgroup 1: protein and rna export to and from the nucleus
                protein localization to nucleus/chromosome (transcription regulation)
                RNA transport to/from nucleus
PC1BPgroup 2: gene expression
                regulation of RNA splicing
                translation
                transcription, DNA templated
```{r}
##"CC" "MF" "BP"
ont="BP"
##ccpar mfpar bppar
parent=bppar
##ccchild mfchild bpchild
child=bpchild
##a GOseq output table
GOlist=PC1GO
goi=toppc1

##generates a vector of all genes in the GOlist with associated GOterms as names
  GOterms=GOlist$category[GOlist$ontology==ont&GOlist$adjp<.5]
  allgogenes=unlist(GO2geneID[GOterms])
  gogenes=intersect(allgogenes,goi)
  edge.data=c(allgogenes[allgogenes==gogenes[1]])
  i=2
  while(i<=length(gogenes)){
    edge.data=c(edge.data,allgogenes[allgogenes==gogenes[i]])
    i=i+1
  }
  names(edge.data)=substring(names(edge.data),1,10)

##generates a table with all parent terms for each significant GO term
  temp=GOlist$category[GOlist$adjp<.05&GOlist$ontology==ont]
  temp2=parent[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp4
  temp7[,2]=temp6
  temp7[,3]=temp5
  colnames(temp7)=c("parent","relationship","child")
  edges=temp7

##generates a table with all child terms for each significant GO term
  temp=GOlist$category[GOlist$adjp<.05&GOlist$ontology==ont]
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")

edges=rbind(edges,temp7)

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont][1:5]))>0){
    nodegroups[i]="Top 5 Sig. Enriched"
  }
  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Top 5 Sig. Enriched", shape = "dot", color = list(background = "red", border="firebrick", groupname="white"),physics=T,font=list(color="black"))%>%
  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

##GOnetwork(ont,parent,child,GOlist,goi)

PC1nodeid=nodeid
PC1groups=nodegroups
PC1size=nodesize
PC1edges=gooiedges

```

transport
  establishment of localization
    establishment of RNA localization
    establishment of

```{r}

##"CC" "MF" "BP"
ont="BP"
##ccpar mfpar bppar
parent=bppar
##ccchild mfchild bpchild
child=bpchild
##a GOseq output table
tPC1=PC1GO
row.names(tPC1)=PC1GO$term
allsiggo=PC1GO$category[PC1GO$adjp<.05]
GOlist=tPC1["establishment of localization","category"]
goi=toppc1

##generates a table with all child terms for each significant GO term
  temp=tPC1["establishment of localization","category"]
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")
  allchildren=temp7
  tested=unique(allchildren[,1])
  while(length(setdiff(unique(allchildren[,3]),tested))>0){
    temp=setdiff(unique(allchildren[,3]),tested)[1]
    temp2=child[temp]
    temp3=unlist(temp2)
    temp4=as.vector(temp3)
    temp5=as.vector(substring(names(temp3),1,10))
    temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
    temp7=matrix(0,nrow=length(temp3),ncol=3)
    temp7[,1]=temp5
    temp7[,2]=temp6
    temp7[,3]=temp4
    colnames(temp7)=c("parent","relationship","child")
    tested=unique(c(tested,temp))
    allchildren=rbind(allchildren,temp7)
    temp=c(rep(0,nrow(allchildren)))
    i=1
    while(i<=length(temp)){
      temp[i]=length(intersect(allchildren[i,],allsiggo))
      i=i+1
    }
    allchildren=allchildren[temp>0,]

  }

  temp=c(rep(0,nrow(allchildren)))
  i=1
while(i<=length(temp)){
  temp[i]=length(intersect(allchildren[,3],allsiggo))
  i=i+1
}

allchildren=allchildren[temp>0,]

edges=allchildren

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

GOlist=PC1GO
i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }

  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%

  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

```

PC1BP group 1
protein and rna export to and from the nucleus
```{r}
PC1g1nodes=nodeid
PC1BPg1=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP",1])
PC1BPg1=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP"&PC1GO[,8]<.05,1])
##write.csv(na.omit(id2name[PC1BPg1]),"/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/PC1BPg1.csv")
PC1BPg1=as.character(unique(unlist(PC1gtg[PC1BPg1])))

```

```{r}

##"CC" "MF" "BP"
ont="BP"
##ccpar mfpar bppar
parent=bppar
##ccchild mfchild bpchild
child=bpchild
##a GOseq output table
tPC1=PC1GO
row.names(tPC1)=PC1GO$term
allsiggo=PC1GO$category[PC1GO$adjp<.05]
GOlist=tPC1["gene expression","category"]
goi=toppc1

##generates a table with all child terms for each significant GO term
  temp=GOlist
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")
  allchildren=temp7
  tested=unique(allchildren[,1])
  while(length(setdiff(unique(allchildren[,3]),tested))>0){
    temp=setdiff(unique(allchildren[,3]),tested)[1]
    temp2=child[temp]
    temp3=unlist(temp2)
    temp4=as.vector(temp3)
    temp5=as.vector(substring(names(temp3),1,10))
    temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
    temp7=matrix(0,nrow=length(temp3),ncol=3)
    temp7[,1]=temp5
    temp7[,2]=temp6
    temp7[,3]=temp4
    colnames(temp7)=c("parent","relationship","child")
    tested=unique(c(tested,temp))
    allchildren=rbind(allchildren,temp7)
    temp=c(rep(0,nrow(allchildren)))
    i=1
    while(i<=length(temp)){
      temp[i]=length(intersect(allchildren[i,],allsiggo))
      i=i+1
    }
    allchildren=allchildren[temp>0,]

  }

  temp=c(rep(0,nrow(allchildren)))
  i=1
while(i<=length(temp)){
  temp[i]=length(intersect(allchildren[,3],allsiggo))
  i=i+1
}

allchildren=allchildren[temp>0,]

edges=allchildren

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

GOlist=PC1GO
i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }

  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%

  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

```

PC1BP group 2
gene expression
  regulation of RNA splicing
  translation
  transcription, DNA templated

```{r}
PC1g2nodes=nodeid
PC1BPg2=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP",1])
PC1BPg2=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP"&PC1GO[,8]<.05,1])
##write.csv(na.omit(id2name[PC1BPg2]),"/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/PC1BPg2.csv")
PC1BPg2=as.character(unique(unlist(PC1gtg[PC1BPg2])))

```

```{r}

##"CC" "MF" "BP"
ont="BP"
##ccpar mfpar bppar
parent=bppar
##ccchild mfchild bpchild
child=bpchild
##a GOseq output table
tPC1=PC1GO
row.names(tPC1)=PC1GO$term
allsiggo=PC1GO$category[PC1GO$adjp<.05]
GOlist=tPC1["cellular metabolic process","category"]
goi=toppc1

##generates a table with all child terms for each significant GO term
  temp=GOlist
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")
  allchildren=temp7
  tested=unique(allchildren[,1])
  while(length(setdiff(unique(allchildren[,3]),tested))>0){
    temp=setdiff(unique(allchildren[,3]),tested)[1]
    temp2=child[temp]
    temp3=unlist(temp2)
    temp4=as.vector(temp3)
    temp5=as.vector(substring(names(temp3),1,10))
    temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
    temp7=matrix(0,nrow=length(temp3),ncol=3)
    temp7[,1]=temp5
    temp7[,2]=temp6
    temp7[,3]=temp4
    colnames(temp7)=c("parent","relationship","child")
    tested=unique(c(tested,temp))
    allchildren=rbind(allchildren,temp7)
    temp=c(rep(0,nrow(allchildren)))
    i=1
    while(i<=length(temp)){
      temp[i]=length(intersect(allchildren[i,],allsiggo))
      i=i+1
    }
    allchildren=allchildren[temp>0,]

  }

  temp=c(rep(0,nrow(allchildren)))
  i=1
while(i<=length(temp)){
  temp[i]=length(intersect(allchildren[,3],allsiggo))
  i=i+1
}

allchildren=allchildren[temp>0,]

edges=allchildren

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

GOlist=PC1GO
i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }

  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%

  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

```

PC1BP group 3
  cellular metabolic process
    RNA metabolic process

```{r}
PC1g3nodes=nodeid
PC1BPg3=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP",1])
PC1BPg3=intersect(unique(c(allchildren[,1],allchildren[,3])),PC1GO[PC1GO[,7]=="BP"&PC1GO[,8]<.05,1])

##write.csv(na.omit(id2name[PC1BPg3]),"/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/PC1BPg3.csv")

PC1BPg3=as.character(unique(unlist(PC1gtg[PC1BPg3])))

```

##Coloring the original network by groups
```{r}

names(PC1groups)=PC1nodeid
PC1groups[setdiff(PC1g1nodes,c(PC1g2nodes,PC1g3nodes))]="group1"
PC1groups[setdiff(PC1g2nodes,c(PC1g1nodes,PC1g3nodes))]="group2"
PC1groups[setdiff(PC1g3nodes,c(PC1g2nodes,PC1g1nodes))]="group3"
PC1groups[intersect(PC1g1nodes,PC1g2nodes)]="group1 and group2"
PC1groups[intersect(PC1g1nodes,PC1g3nodes)]="group1 and group3"
PC1groups[intersect(PC1g3nodes,PC1g2nodes)]="group2 and group3"
PC1groups[grep("Not",PC1groups)]="not sig."
PC1groups[grep("Top 5 Sig. Enriched",PC1groups)]="Significantly Enriched"
PC1groups=as.vector(PC1groups)

nodes=data.frame(id=PC1nodeid,group=PC1groups,value=PC1size)
visedges=as.data.frame(PC1edges)
colnames(visedges)=c("from","to")

visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "group1", shape = "dot", color = list(background = "red", border="firebrick", groupname="white"),physics=T,font=list(color="black"))%>%
    visGroups(groupname = "group2", shape = "dot", color = list(background = "dodgerblue", border="royalblue", groupname="white"),physics=T,font=list(color="black"))%>%
    visGroups(groupname = "group3", shape = "dot", color = list(background = "yellow", border="gold3", groupname="white"),physics=T,font=list(color="black"))%>%

      visGroups(groupname = "group2 and group3", shape = "dot", color = list(background = "green", border="darkgreen", groupname="white"),physics=T,font=list(color="black"))%>%
      visGroups(groupname = "group1 and group2", shape = "dot", color = list(background = "violet", border="darkviolet", groupname="white"),physics=T,font=list(color="black"))%>%

  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "white", border="black", groupname="black"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

```

```{r}

##"CC" "MF" "BP"
ont="BP"
##ccpar mfpar bppar
parent=bppar
##ccchild mfchild bpchild
child=bpchild
##a GOseq output table
tPC1=PC1GO
row.names(tPC1)=PC1GO$term
allsiggo=PC1GO$category[PC1GO$adjp<.05]
GOlist=tPC1["I-kappaB kinase/NF-kappaB signaling","category"]
goi=toppc1

##generates a table with all child terms for each significant GO term
  temp=GOlist
  temp2=child[temp]
  temp3=unlist(temp2)
  temp4=as.vector(temp3)
  temp5=as.vector(substring(names(temp3),1,10))
  temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
  temp7=matrix(0,nrow=length(temp3),ncol=3)
  temp7[,1]=temp5
  temp7[,2]=temp6
  temp7[,3]=temp4
  colnames(temp7)=c("parent","relationship","child")
  allchildren=temp7
  tested=unique(allchildren[,1])
  while(length(setdiff(unique(allchildren[,3]),tested))>0){
    temp=setdiff(unique(allchildren[,3]),tested)[1]
    temp2=child[temp]
    temp3=unlist(temp2)
    temp4=as.vector(temp3)
    temp5=as.vector(substring(names(temp3),1,10))
    temp6=as.vector(substring(names(temp3),12,nchar(names(temp3))))
    temp7=matrix(0,nrow=length(temp3),ncol=3)
    temp7[,1]=temp5
    temp7[,2]=temp6
    temp7[,3]=temp4
    colnames(temp7)=c("parent","relationship","child")
    tested=unique(c(tested,temp))
    allchildren=rbind(allchildren,temp7)
    temp=c(rep(0,nrow(allchildren)))
    i=1
    while(i<=length(temp)){
      temp[i]=length(intersect(allchildren[i,],allsiggo))
      i=i+1
    }
    allchildren=allchildren[temp>0,]

  }

  temp=c(rep(0,nrow(allchildren)))
  i=1
while(i<=length(temp)){
  temp[i]=length(intersect(allchildren[,3],allsiggo))
  i=i+1
}

allchildren=allchildren[temp>0,]

edges=allchildren

gooiedges=unique(edges[,c(1,3)])
colnames(gooiedges)=c("from","to")
gooiedges=na.omit(gooiedges)

GOlist=PC1GO
i=1
while(i<=nrow(gooiedges)){
  if(length(GOlist$term[GOlist$category==gooiedges[i,1]])>0){
    gooiedges[i,1]=GOlist$term[GOlist$category==gooiedges[i,1]]
  }else{
      gooiedges[i,1]=Term(term[[as.character(gooiedges[i,1])]])
  }

  if(length(GOlist$term[GOlist$category==gooiedges[i,2]])>0){
    gooiedges[i,2]=GOlist$term[GOlist$category==gooiedges[i,2]]
  }else{
    gooiedges[i,2]=Term(term[[as.character(gooiedges[i,2])]])
  }
  i=i+1
}

nodeid=unique(c(gooiedges[,1],gooiedges[,2]))

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<length(nodegroups)){
  if(length(intersect(
    gooiedges[,1],
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

  if(length(intersect(
    intersect( setdiff(gooiedges[,1],gooiedges[,2]),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }  
  i=i+1
}

notsigs=nodeid[nodegroups=="not sig."]
nodeid=nodeid[nodegroups!="not sig."]
nodegroups=nodegroups[nodegroups!="not sig."]

nodegroups=rep("not sig.",length(nodeid))
i=1
while(i<=length(nodegroups)){
  if(length(intersect(
    setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),
    nodeid[i]))>0){
    nodegroups[i]="Not sig. Parent Term"
  }

  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodegroups[i]="Significantly Enriched"
  }

    if(length(intersect(
    intersect( setdiff(gooiedges[,1],setdiff(gooiedges[,2],notsigs)),GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]),
    nodeid[i]))>0){
    nodegroups[i]="Parent Term"
  }

  i=i+1
}

nodesize=c(rep(.1,length(nodeid)))
i=1
while(i<=length(nodeid)){
  if(length(intersect(nodeid[i],GOlist$term[GOlist$adjp<.05&GOlist$ontology==ont]))>0){
    nodesize[i]=GOlist[GOlist$term==nodeid[i],4]
  }
  i=i+1
}

nodes=data.frame(id=nodeid,group=nodegroups,value=nodesize)
visedges=as.data.frame(gooiedges)
colnames(visedges)=c("from","to")
visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows='to')%>%
  visGroups(groupname = "Parent Term", shape = "square", color = list(background = "yellow", border="black", groupname="white"),physics=F,font=list(color="black"))%>%

  visGroups(groupname = "Not sig. Parent Term", shape = "square", color = list(background = "grey", border="black", groupname="white"),physics=F,font=list(color="black"))%>%
  visGroups(groupname = "Significantly Enriched", shape = "dot", color = list(background = "yellow", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visGroups(groupname = "not sig.", shape = "dot", color = list(background = "grey", border="black", groupname="white"),physics=T,font=list(color="black"),mass=3.5)%>%
  visLegend(width=.2)

```

```{r}
PC1BPg4=unique(c(allchildren[,1],allchildren[,3]))
PC1BPg4=as.character(unique(unlist(PC1gtg[PC1BPg4])))

```

```{r}

##Venn Code
library(VennDiagram)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Group 1"
set2="Group 2"
set3="Group 3"
set4="All Top 10 Percent"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=PC1BPg1
s2=PC1BPg2
s3=PC1BPg3
s4=row.names(hmd)

##Quad Venn

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)

##Triple Venn

grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```

```{r include=F}

hmorder=c((setdiff(s1,c(s2,s3))),
          (intersect(s1,intersect(s2,s3))),
          (setdiff(intersect(s3,s2),s1)),
          (setdiff(s3,c(s1,s2))),
          (setdiff(intersect(s3,s1),s2)))
split=c(rep("A",length(setdiff(s1,c(s2,s3)))),
          rep("B",length(intersect(s1,intersect(s2,s3)))),
          rep("C",length(setdiff(intersect(s3,s2),s1))),
          rep("D",length(setdiff(s3,c(s1,s2)))),
          rep("E",length(setdiff(intersect(s3,s1),s2))))
colgroups=c(rep("A",length(setdiff(s1,c(s2,s3)))),
          rep("B",length(intersect(s1,intersect(s2,s3)))),
          rep("C",length(setdiff(intersect(s3,s2),s1))),
          rep("D",length(setdiff(s3,c(s1,s2)))),
          rep("E",length(setdiff(intersect(s3,s1),s2))))
mat1 = (scalemeancpm)[hmorder,]
sigs=bitr(row.names(mat1),fromType = "ENSEMBL", toType = "SYMBOL",  OrgDb="org.Hs.eg.db")
sigs1=sigs[,2]
names(sigs1)=sigs[,1]
row.names(mat1)=sigs1[row.names(mat1)]
mat2 = mat1[,c(6,5,4)]
mat1=mat1[,c(3,2,1)]

##write.csv(mat1,"/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/PC1mat1")
##write.csv(mat2,"/Users/johncsantiago/Google Drive File Stream/My Drive/Sanders Lab Files/All Code/PC1mat2")

##split = sample(letters[1:6], 100, replace = TRUE)
split = factor(split, levels = unique(split))
```

```{r fig.height=6,fig.width=6}
circos.clear()
circos.par(gap.after = c(2, 2, 2, 2, 7))
col_fun1 = colorRamp2(c(-2, 0, 2), c("royalblue4","white","firebrick4"))
circos.heatmap(mat1, col = col_fun1, rownames.cex=.2,track.height=.2, split = split, rownames.side = "outside")
col_direction = c("A" = "forestgreen", "B" = "forestgreen","C" = "white","D" = "white","E" = "forestgreen")
colgroups=as.vector(split)
circos.heatmap(colgroups,col = col_direction,track.height=.025)
col_direction = c("A" = "white", "B" = "cornflowerblue","C" = "cornflowerblue","D" = "white","E" = "white")
circos.heatmap(colgroups,col = col_direction,track.height=.025)
col_direction = c("A" = "white", "B" = "gold","C" = "gold","D" = "gold","E" = "gold")
circos.heatmap(colgroups,col = col_direction,track.height=.025)
legend(x=-.5,y=.4,legend=c("Protein and RNA transport \nto and from the nucleus","gene expression: Transcription, \nRNA splicing, and Translation","DNA, RNA, and Protein Biosynthesis"),fill=c("forestgreen","cornflowerblue","gold"),bty="n",title="Viable",cex=.8,y.intersp=2)
arrows(x0=.7,y0=0.02,x1=.9,y1=0.02,length=.05)

text(x=.72,y=.05,labels="0H",cex=.5)
text(x=.80,y=.05,labels="3H",cex=.5)
text(x=.87,y=.05,labels="6H",cex=.5)

```

```{r fig.height=6,fig.width=6}
circos.clear()
circos.par(gap.after = c(2, 2, 2, 2, 7))
col_fun1 = colorRamp2(c(-2, 0, 2), c("royalblue4","white","firebrick4"))
circos.heatmap(mat2, col = col_fun1, rownames.cex=.2,track.height=.2, split = split, rownames.side = "outside")
col_direction = c("A" = "forestgreen", "B" = "forestgreen","C" = "white","D" = "white","E" = "forestgreen")
colgroups=as.vector(split)
circos.heatmap(colgroups,col = col_direction,track.height=.025)
col_direction = c("A" = "white", "B" = "cornflowerblue","C" = "cornflowerblue","D" = "white","E" = "white")
circos.heatmap(colgroups,col = col_direction,track.height=.025)
col_direction = c("A" = "white", "B" = "gold","C" = "gold","D" = "gold","E" = "gold")
circos.heatmap(colgroups,col = col_direction,track.height=.025)
legend(x=-.5,y=.4,legend=c("Protein and RNA transport \nto and from the nucleus","gene expression: Transcription, \nRNA splicing, and Translation","DNA, RNA, and Protein Biosynthesis"),fill=c("forestgreen","cornflowerblue","gold"),bty="n",title="Non-Viable",cex=.8,y.intersp=2)
arrows(x0=.7,y0=0.02,x1=.9,y1=0.02,length=.05)

text(x=.72,y=.05,labels="0H",cex=.5)
text(x=.80,y=.05,labels="3H",cex=.5)
text(x=.87,y=.05,labels="6H",cex=.5)
```

PC1 MF
Looks like transcription and translation function (RNA and protein binding )
```{r}
##"CC" "MF" "BP"
ont="MF"
##ccpar mfpar bppar
parent=mfpar
##ccchild mfchild bpchild
child=mfchild
##a GOseq output table
GOlist=PC1GO
goi=toppc1
GOnetwork(ont,parent,child,GOlist,goi)

```

### 2023-07-07 GeneralDataFiles/GenesInGOTerms.Rmd
Cami Stuff

---
title: "Lean Top PC1 Function Figures"
author: "John Santiago"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r include=F}
##Load Libraries

library(biomaRt)

library(org.Dm.eg.db)

library(GO.db)

```

```{r}
##FB2Ensembl
x1=as.list(org.Dm.egENSEMBL2EG)
##Ensembl2Symbol
x2=as.list(org.Dm.egSYMBOL)
##Symbol2Ensembl
x3=as.list(org.Dm.egSYMBOL2EG)
##Ensembl2FB
x4=as.list(org.Dm.egENSEMBL)
##ensembl to FBgn
x5=as.list(org.Dm.egFLYBASE)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)

FBgn2ensembl = row.names(cpmdata)
names(FBgn2ensembl) = row.names(cpmdata)
tempEG = unlist(x1[lengths(x1)==1][row.names(cpmdata)])
FBgn2ensembl[names(tempEG)]=tempEG

ensembl2symbol = row.names(cpmdata)
names(ensembl2symbol) = FBgn2ensembl
tempSymbol = unlist(x2[FBgn2ensembl])
ensembl2symbol[names(tempSymbol)]=tempSymbol
symbol2ensembl = names(ensembl2symbol)
names(symbol2ensembl) = ensembl2symbol

extras = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/UnknownIDGenes.csv")
row.names(extras)=extras$Symbol
extras$ensembl = extras$FBgn
tempExtras = unlist(x3[extras$Symbol])
extras[names(tempExtras), "ensembl"] = tempExtras
row.names(extras) = extras$FBgn

ensembl = FBgn2ensembl
ensembl[row.names(extras)] = extras$ensembl

symbol = ensembl2symbol
symbol[row.names(extras)] = extras$Symbol

KEY = data.frame(FBgn = row.names(cpmdata),
                 Symbol = symbol,
                 ensembl = ensembl)
row.names(KEY) = KEY$FBgn

##write.csv(KEY,"/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneIDKey.csv")

ccpar=as.list(GOCCPARENTS)
ccchild=as.list(GOCCCHILDREN)

bppar=as.list(GOBPPARENTS)
bpchild=as.list(GOBPCHILDREN)

mfpar=as.list(GOMFPARENTS)
mfchild=as.list(GOMFCHILDREN)

term=as.list(GOTERM)

genesingo=as.list(org.Dm.egGO2ALLEGS)

GOi = names(genesingo)[1]
genesingoi = intersect(row.names(KEY),unlist(x4[genesingo[[1]]]))

GO2FBgn = data.frame(FB.ID = genesingoi,
                     Symbol = KEY[genesingoi,"Symbol"],
                     GO.ID = GOi,
                     GO.Term = term[[names(genesingo)[1]]]@'Term',
                     Ontology = term[[names(genesingo)[1]]]@'Ontology',
                     GO.Definition = term[[names(genesingo)[1]]]@'Definition')

i=2
while(i<=length(genesingo)){
  GOi = names(genesingo)[i]
  genesingoi = intersect(row.names(KEY),unlist(x4[genesingo[[i]]]))

  if(length(genesingoi) > 0){
    tempGO2FBgn = data.frame(FB.ID = genesingoi,
                             Symbol = KEY[genesingoi,"Symbol"],
                             GO.ID = GOi,
                             GO.Term = term[[names(genesingo)[i]]]@'Term',
                             Ontology = term[[names(genesingo)[i]]]@'Ontology',
                             GO.Definition = term[[names(genesingo)[i]]]@'Definition')
    GO2FBgn = rbind(GO2FBgn, tempGO2FBgn)
  }
  i=i+1
}

##write.csv(GO2FBgn, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GenesInGOTerms.csv")

Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

kegg=keggLink("pathway","dme")
names(kegg)=gsub("dme:Dmel_","",names(kegg))
i=1
temp = as.list(kegg[(unique(names(kegg)))])
while(i<=length(temp)){
  temp[[i]] = as.character(kegg[grep(names(temp)[i], names(kegg))])
  i = i+1
}
kegg = temp
x=as.list(org.Dm.egFLYBASECG2EG)
xx=as.list(org.Dm.egSYMBOL)
names(kegg)=as.vector(unlist(xx[unlist(x[names(kegg)])]))

##saveRDS(kegg, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

```

### 2023-07-07 TKT_RNAseq/R Code/GO_Analysis.Rmd
Cami Stuff

--- 2023-07-07 CamiCode.Rmd
@@
 
+##sigs = Df.data[Df.data$Moderate == 1 , "Symbol"]
+##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
+##genes[sigs] = 1
+##pwf=nullp(genes,"dm3","geneSymbol")
+##GO.wall=goseq(pwf,"dm3","geneSymbol")
+##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+##row.names(GO.wall) = GO.wall$category
+##Moderate.GO = GO.wall
+##write.csv(Moderate.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv")
+
+##KEGG term enrichment is KEGG
+##KEGG=goseq(pwf,gene2cat=kegg)
+##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+##KEGG$Name=kegg.names[row.names(KEGG),1]
+##Moderate.KEGG = KEGG
+##write.csv(Moderate.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateKEGGAnalysis.csv")
+
+##sigs = Df.data[Df.data$Strong == 1 , "Symbol"]
+##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
+##genes[sigs] = 1
+##pwf=nullp(genes,"dm3","geneSymbol")
+##GO.wall=goseq(pwf,"dm3","geneSymbol")
+##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+##row.names(GO.wall) = GO.wall$category
+##Strong.GO = GO.wall
+##write.csv(Strong.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv")
+
+##KEGG term enrichment is KEGG
+##KEGG=goseq(pwf,gene2cat=kegg)
+##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+##KEGG$Name=kegg.names[row.names(KEGG),1]
+##Strong.KEGG = KEGG
+##write.csv(Strong.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongKEGGAnalysis.csv")
+
 ##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
@@
 
+Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
+Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RStrongGOAnalysis.csv", row.names = 1)
+
 Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
@@
 Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)
-
-Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
-Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
-Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)
-
-```
-
-```{r}
-
-PathwayID = "04141"
-
-download.kegg(pathway.id= PathwayID, species = "dme")
-xml.file=paste0("dme",PathwayID,".xml")
-node.data=node.info(xml.file)
-
-all.path = names(kegg[grep(PathwayID,kegg)])
-
-Moderate = Df.data[Df.data$Moderate == 1, "Symbol"]
-Moderate = intersect(Moderate, all.path)
-Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")
-
-Strong = Df.data[Df.data$Strong == 1, "Symbol"]
-Strong = intersect(Strong, all.path)
-Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
-
-Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
-Enhancer = intersect(Enhancer, all.path)
-Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")
-
-Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
-Lethal = intersect(Lethal, all.path)
-Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
-
-plot.data.gene=node.map(mol.data=c(Moderate, Strong, Enhancer, Lethal), node.data, node.types="gene")
-cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
-cols.ts.gene[1:length(cols.ts.gene)] = 0
-
-pdg.moderate=node.map(mol.data=Moderate, node.data, node.types="gene")
-temp = node.color(pdg.moderate, limit=2, bins=2)
-ctg.moderate = cols.ts.gene
-ctg.moderate[temp!="#FFFFFF"]= 1 ##"gold2"
-
-pdg.strong=node.map(mol.data=Strong, node.data, node.types="gene")
-temp = node.color(pdg.strong, limit=2, bins=2)
-ctg.strong = cols.ts.gene
-ctg.strong[temp!="#FFFFFF"]= 1 ##"brown2"
-
-pdg.enhancer=node.map(mol.data=Enhancer, node.data, node.types="gene")
-temp = node.color(pdg.enhancer, limit=2, bins=2)
-ctg.enhancer = cols.ts.gene
-ctg.enhancer[temp!="#FFFFFF"]= 1 ##"deepskyblue"
-
-pdg.lethal=node.map(mol.data=Lethal, node.data, node.types="gene")
-temp = node.color(pdg.lethal, limit=2, bins=2)
-ctg.lethal = cols.ts.gene
-ctg.lethal[temp!="#FFFFFF"]= 1 ##"navyblue"
-
-color.combos = data.frame(Moderate = as.numeric(ctg.moderate),
-                          Strong = as.numeric(ctg.strong),
-                          Enhancer = as.numeric(ctg.enhancer),
-                          Lethal = as.numeric(ctg.lethal))
-row.names(color.combos)= names(cols.ts.gene)
-
-cols.ts.gene[cols.ts.gene=="0"]="darkseagreen1"
-
-cols.ts.gene[row.names(color.combos)[color.combos$Moderate == 1]] = "gold2"
-cols.ts.gene[row.names(color.combos)[color.combos$Strong   == 1]] = "brown1"
-cols.ts.gene[row.names(color.combos)[color.combos$Enhancer   == 1]] = "lightsteelblue"
-cols.ts.gene[row.names(color.combos)[color.combos$Lethal   == 1]] = "cornflowerblue"
-cols.ts.gene[row.names(color.combos)[(color.combos$Moderate   == 1 | color.combos$Strong   == 1) & (color.combos$Enhancer   == 1 | color.combos$Lethal   == 1) ]] = "grey60"
-
-pv.pars= keggview.native(plot.data.gene=plot.data.gene,
-                         cols.ts.gene=cols.ts.gene, 
-                         node.data=node.data,
-                         pathway.name=paste0("dme", PathwayID),
-                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1])
-
-knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/dme04141.", kegg.names[paste0("dme", PathwayID),1], ".png"))
 

### 2023-07-07 TKT_RNAseq/R Code/KEGG_Analysis.Rmd
Cami Stuff

--- 2023-07-07 CamiCode.Rmd
@@
 ##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
-cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
-groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
 
-##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")
+Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
+Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
 
-##background = setNames(unique(CamiData$Background), unique(CamiData$Background))
+kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
 
-##moderate = setNames(rep(0, length(background)), names(background))
+keggID=keggConv("dme","ncbi-geneid")
 
-##moderate[unique(CamiData$Moderate)] = 1
-
-##strong = setNames(rep(0, length(background)), names(background))
-
-##strong[unique(CamiData$Strong)] = 1
-
-##lethal = setNames(rep(0, length(background)), names(background))
-
-##lethal[unique(CamiData$Lethal)] = 1
-
-##enhancer = setNames(rep(0, length(background)), names(background))
-
-##enhancer[unique(CamiData$Enhancers)] = 1
-
-##no.effect = setNames(rep(0, length(background)), names(background))
-
-##no.effect[unique(CamiData$No.Effect)] = 1
-
-##FB2Ensembl
-##x1=as.list(org.Dm.egENSEMBL2EG)
-##Ensembl2Symbol
-##x2=as.list(org.Dm.egSYMBOL)
-##Symbol2Ensembl
-##x3=as.list(org.Dm.egSYMBOL2EG)
-##Ensembl2FB
-##x4=as.list(org.Dm.egENSEMBL)
-##ensembl to FBgn
-##x5=as.list(org.Dm.egFLYBASE)
-
-##FBgn2ensembl = row.names(CamiData)
-##names(FBgn2ensembl) = row.names(CamiData)
-##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
-##FBgn2ensembl[names(tempEG)]=tempEG
-
-##ensembl2symbol = row.names(CamiData)
-##names(ensembl2symbol) = FBgn2ensembl
-##tempSymbol = unlist(x2[FBgn2ensembl])
-##ensembl2symbol[names(tempSymbol)]=tempSymbol
-##symbol2ensembl = names(ensembl2symbol)
-##names(symbol2ensembl) = ensembl2symbol
-
-##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")
-
-##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
-##ensembl2symbol[row.names(extras)] = extras$SYMBOL
-
-##symbol = ensembl2symbol
-
-##symbol = background
-
-##symbol[intersect(GeneIDKey$FBgn, background)] = 
-##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]
-
-##CamiData = data.frame(FBgn       = background[1:14674],
-##                      Symbol     = symbol[1:14674],
-##                      Moderate   = moderate[1:14674],
-##                      Strong     = strong[1:14674],
-##                      Lethal     = lethal[1:14674],
-##                      Enhancer   = enhancer[1:14674],
-##                      No.Effect  = no.effect[1:14674])
-
-##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")
-
-Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
-
-```
-
-```{r include=F, echo=F}
-
-kegg=keggLink("pathway","dme")
-names(kegg)=gsub("dme:Dmel_","",names(kegg))
-
-##i=1
-##kegg.names=unique(substr(kegg,6,13))
-##names(kegg.names)=as.vector(kegg.names)
-##while(i<=length(kegg.names)){
-##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
-##  i=i+1
-##}
-
-##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
 kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
 
-temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
-temp = temp[intersect(names(kegg),names(temp))]
-kegg = kegg[intersect(names(kegg),names(temp))]
-names(kegg) = temp[names(kegg)]
-kegg = as.list(kegg)
-keggID=keggConv("dme","ncbi-geneid")
+Moderate.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateKEGGAnalysis.csv", row.names = 1)
 
-##sigs = Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Repress.GO = GO.wall
-##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Repress.KEGG = KEGG
-##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Lethal.GO = GO.wall
-##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Lethal.KEGG = KEGG
-##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Enhance.GO = GO.wall
-##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##EGG$Name=kegg.names[row.names(KEGG),1]
-##Enhance.KEGG = KEGG
-##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv")
-
-Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
-Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
-Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)
+Strong.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongKEGGAnalysis.csv", row.names = 1)
 
 Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
+
 Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
+
 Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)
@@
 
-```{r}
+```{r, include = F, echo = F}
 
-PathwayID = "04141"
-
+ShowKEGG = function(PathwayID){
 download.kegg(pathway.id= PathwayID, species = "dme")
@@
 
-knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/dme04141.", kegg.names[paste0("dme", PathwayID),1], ".png"))
+}
 
@@
 
-```{r include=F, echo=F}
+```{r, echo = F, include = F}
 
-GO.data = Repress.GO[Repress.GO$adjp <= .05 &
-                     Repress.GO$ontology == 'BP',
-                     c("category", "term","adjp", "numDEInCat", "numInCat")]
+KEGG20 = function(data){
 
-go_analysis = GO.data$category
-scores = setNames(-log10(GO.data$adjp), go_analysis)
+  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
 
-##simMatrix <- calculateSimMatrix(go_analysis,
-##                                orgdb="org.Dm.eg.db",
-##                                ont="BP",
-##                                method="Rel")
-
-##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")
-
-##reducedTerms <- reduceSimMatrix(simMatrix,
-##                                scores,
-##                                threshold=0.7,
-##                                orgdb="org.Dm.eg.db")
-##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
-
-simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
-reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
-
-```
-
-```{r, fig.width= 10}
-
-data = GO.data[,c("term","adjp","numDEInCat", "numInCat", "category")]
-data = data[order(data$adjp, decreasing = T),]
+data = data[20:1,]
 data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
+data$term = factor(data$Name, levels = c(unique(data$Name)))
 
@@
                type = 'bar',
-               name = "term",
+               name = "Name",
                marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
@@
     hoverinfo = "text",
-    hovertext = paste("Sample:", data$term,
+    hovertext = paste("Sample:", data$Name,
                       "\nGO ID: ", data$category,
@@
            yaxis = list(title = ""),
-           title = "Significantly Enriched GO term Summary",
+           title = "Top 20 Most Enriched KEGG Terms",
            margin = m)
 
-fig
+return(fig)
+
+}
 
@@
 
-```{r fig.height=7, fig.width=10}
+```{r fig.width=10}
 
-heatmapPlot(simMatrix,
-            reducedTerms,
-            annotateParent=TRUE,
-            annotationLabel="parentTerm",
-            fontsize=6,
-            main = "Repressor Gene Enriched Biological Process GO terms")
+data = Moderate.KEGG
+
+KEGG20(data)
 
@@
 
-```{r, fig.align='left', include=F}
+```{r echo = F, include = F}
+PathwayID = "04150"
 
-scatterPlot(simMatrix, reducedTerms)
+ShowKEGG(PathwayID)
 
@@
 
-```{r, fig.width=10}
- use.data   = simMatrix
-    pca <- prcomp(t(use.data), scale.=TRUE) 
-    pc1=scale(pca$x[,1])
-    pc2=scale(pca$x[,2])
-    eigs <- pca$sdev^2
-    ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(PC1=pc1,
-                        PC2=pc2,
-                        sdev=pca$sdev,
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group = reducedTerms[row.names(use.data), "parentTerm"],
-                        Score = reducedTerms[row.names(use.data), "score"],
-                        Term = reducedTerms[row.names(use.data), "term"],
-                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
-                        Total = GO.data[row.names(use.data), "numInCat"],
-                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))
-
-    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
-    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))
-
-  fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~Group,
-                 ##symbol = ~Group,
-                 ##symbols = as.character(seq_along(unique(point.data$Set))),
-                 ##colors = c("firebrick","gold","deepskyblue"),
-                 marker = list(size = pca.data$Score,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Sample:", pca.data$Term, 
-                                   "\nTotal DE: ", pca.data$TotalDE, 
-                                   "\nTotal in Cat.: ", pca.data$Total, 
-                                   "\nFDR: ", pca.data$SigVal)) %>%
-    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
-           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
-           title = "Enriched GO term similarity")
-
-  fig
-
+```{r}
+knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
 ```
-
-```{r fig.align='left'}
-
-treemapPlot(reducedTerms)
-
-```
-
-```{r, include=F, echo=F}
-GO2Gene   = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GenesInGOTerms.csv", row.names = 1)
-
-ccpar=as.list(GOCCPARENTS)
-ccchild=as.list(GOCCCHILDREN)
-
-bppar=as.list(GOBPPARENTS)
-bpchild=as.list(GOBPCHILDREN)
-
-mfpar=as.list(GOMFPARENTS)
-mfchild=as.list(GOMFCHILDREN)
-```
-
-```{r, include=F, echo=F}
-
-compare = "GRM.CxDf"
-filter.samples = c("GR.M", "TktDfGR.M")
-
-sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,compare]<=.05]
-sigs = sigs[apply(cpmdata[sigs,groups$Group %in% filter.samples], 1, min) > 10]
-
-genes=c(rep(0, nrow(cpmdata)))
-names(genes) = row.names(cpmdata)
-genes[sigs] = 1
-names(genes) = GeneIDKey[names(genes), "Symbol"]
-
-pwf=nullp(genes,"dm3","geneSymbol")
-
-GO.wall=goseq(pwf,"dm3","geneSymbol")
-GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-row.names(GO.wall) = GO.wall$category
-
-GO.wall$Significant = "not"
-GO.wall[GO.wall$adjp <= .05, "Significant"] = "sig"
-sigGO = GO.wall[GO.wall$adjp<.05,]
-
-##Biological Processes
-bpGO = sigGO[sigGO$ontology == 'BP',]
-
-##parent terms are those directly above in hierarchy
-## isa implies a defining relationship; part of implies they contribute to the category
-
-parents = bppar[bpGO$category]
-
-parents = data.frame(from = unlist(parents),
-                     label = substring(names(unlist(parents)),12),
-                     to = substring(names(unlist(parents)),1,10))
-
-parents = parents[parents$to %in% row.names(GO.wall),]
-
-children = bpchild[bpGO$category]
-
-children = data.frame(from = substring(names(unlist(children)),1,10),
-                      label = substring(names(unlist(children)),12),
-                      to = unlist(children))
-
-children = children[children$to %in% row.names(GO.wall),]
-
-edges = rbind(parents, children)
-edges = edges[edges$label == "isa",]
-edges = unique(edges)
-
-edges = edges[GO.wall[edges$to, "numDEInCat"]>0,]
-
-node.id = unique(c(edges$from, edges$to))
-node.label = GO.wall[node.id, "term"]
-node.group = GO.wall[node.id, "Significant"]
-node.value = 100*(GO.wall[node.id, "numDEInCat"]/GO.wall[node.id, "numInCat"])
-
-nodes = data.frame(id = node.id,
-                   label = node.label,
-                   group = node.group,
-                   value = node.value)
-```
-
-```{r include=F}
-
-visNetwork(nodes, edges)%>%
-  visLayout(hierarchical=F, improvedLayout=T)%>%
-  visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-70),enabled=T)%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows='to')%>%
-  visGroups(groupname = "sig", shape = "box", color = list(background = "gold", border="black", groupname="black"),physics=F,font=list(color="black"))%>%
-  visGroups(groupname = "not", shape = "dot", color = list(background = "grey", border="black", groupname="black"),physics=T,font=list(color="black"))
-
-```

### 2023-07-07 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R

@@ -5,6 +5,7 @@ if(length(new.packages)>0){
   install.packages("ggfortify")
 }
 
+##Load necessary libraries
 library(shiny)
 library(ggfortify)
 library(heatmaply)
@@ -13,15 +14,27 @@ library(colourpicker)
 library(DT)
 library(rclipboard)
 
+##load all files from github
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
 cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
 groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
 TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
 convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)
 
+##Add additional groups for color factors
 groups$GxS = paste0(groups$Genotype, groups$Sex)
 groups$GxTKT = paste0(groups$Genotype, groups$TKT)
 
+##FBgn2Symbol; Variable for converting FBgn to symbol
+temp                   = convert[,c("updated.FBgn","Symbol")]
+temp2                  = setdiff(row.names(cpmdata),row.names(convert))
+temp2                  = matrix(rep(temp2,2), ncol=2)
+row.names(temp2)       = temp2[,1]
+colnames(temp2)        = colnames(temp)
+FBgn2Symbol            = rbind(temp,temp2)
+colnames(FBgn2Symbol)  = c("FBgn", "Symbol")
+
+##groups. use; Variable used by the "Filter gene set" options 
 groups.use = matrix(0,nrow = nrow(groups), ncol = 8)
 row.names(groups.use) = row.names(groups)
 colnames(groups.use) = c("ALL","GR", "WT", "M", "F", "C", "DF", "OE")
@@ -34,14 +47,7 @@ groups.use[groups$TKT      == "Control", "C"]   = 1
 groups.use[groups$TKT      == "DF",      "DF"]  = 1
 groups.use[groups$TKT      == "OE",      "OE"]  = 1
 
-temp                   = convert[,c("updated.FBgn","Symbol")]
[…]

### 2023-07-10 DeficiencyScreen/GO_Analysis.Rmd
update

--- 2023-07-07 TKT_RNAseq/R Code/GO_Analysis.Rmd
@@
 
-kegg=keggLink("pathway","dme")
-names(kegg)=gsub("dme:Dmel_","",names(kegg))
-
-##i=1
-##kegg.names=unique(substr(kegg,6,13))
-##names(kegg.names)=as.vector(kegg.names)
-##while(i<=length(kegg.names)){
-##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
-##  i=i+1
-##}
-
 ##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
@@
 
-temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
-temp = temp[intersect(names(kegg),names(temp))]
-kegg = kegg[intersect(names(kegg),names(temp))]
-names(kegg) = temp[names(kegg)]
-kegg = as.list(kegg)
 keggID=keggConv("dme","ncbi-geneid")
+
+kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
 
@@
 Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
-Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RStrongGOAnalysis.csv", row.names = 1)
+Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv", row.names = 1)
 
@@
 
-```{r include=F, echo=F}
+```{r, fig.width= 10}
 
-GO.data = Repress.GO[Repress.GO$adjp <= .05 &
-                     Repress.GO$ontology == 'BP',
+GO.data = Moderate.GO
+GO.data = GO.data[GO.data$ontology == 'BP',
                   c("category", "term","adjp", "numDEInCat", "numInCat")]
 
-go_analysis = GO.data$category
-scores = setNames(-log10(GO.data$adjp), go_analysis)
-
-##simMatrix <- calculateSimMatrix(go_analysis,
-##                                orgdb="org.Dm.eg.db",
-##                                ont="BP",
-##                                method="Rel")
-
-##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")
-
-##reducedTerms <- reduceSimMatrix(simMatrix,
-##                                scores,
-##                                threshold=0.7,
-##                                orgdb="org.Dm.eg.db")
-##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
-
-simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
-reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
-
-```
-
-```{r, fig.width= 10}
-
-data = GO.data[,c("term","adjp","numDEInCat", "numInCat", "category")]
-data = data[order(data$adjp, decreasing = T),]
+data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
 data$Score = -log10(data$adjp)
@@
            yaxis = list(title = ""),
-           title = "Significantly Enriched GO term Summary",
+           title = "Top 20 Most Enriched GO Terms",
            margin = m)
@@
 fig
+
+```
+
+```{r include=F, echo=F}
+
+go_analysis = GO.data$category[GO.data$adjp <= .05]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont="BP",
+                                method="Rel")
+
+##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
+
+##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
+##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
 

### 2023-07-10 TKT_RNAseq/R Code/GO_Analysis.Rmd
update

--- 2023-07-07 CamiCode.Rmd
@@
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
-
-##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")
-
-##background = setNames(unique(CamiData$Background), unique(CamiData$Background))
-
-##moderate = setNames(rep(0, length(background)), names(background))
-
-##moderate[unique(CamiData$Moderate)] = 1
-
-##strong = setNames(rep(0, length(background)), names(background))
-
-##strong[unique(CamiData$Strong)] = 1
-
-##lethal = setNames(rep(0, length(background)), names(background))
-
-##lethal[unique(CamiData$Lethal)] = 1
-
-##enhancer = setNames(rep(0, length(background)), names(background))
-
-##enhancer[unique(CamiData$Enhancers)] = 1
-
-##no.effect = setNames(rep(0, length(background)), names(background))
-
-##no.effect[unique(CamiData$No.Effect)] = 1
-
-##FB2Ensembl
-##x1=as.list(org.Dm.egENSEMBL2EG)
-##Ensembl2Symbol
-##x2=as.list(org.Dm.egSYMBOL)
-##Symbol2Ensembl
-##x3=as.list(org.Dm.egSYMBOL2EG)
-##Ensembl2FB
-##x4=as.list(org.Dm.egENSEMBL)
-##ensembl to FBgn
-##x5=as.list(org.Dm.egFLYBASE)
-
-##FBgn2ensembl = row.names(CamiData)
-##names(FBgn2ensembl) = row.names(CamiData)
-##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
-##FBgn2ensembl[names(tempEG)]=tempEG
-
-##ensembl2symbol = row.names(CamiData)
-##names(ensembl2symbol) = FBgn2ensembl
-##tempSymbol = unlist(x2[FBgn2ensembl])
-##ensembl2symbol[names(tempSymbol)]=tempSymbol
-##symbol2ensembl = names(ensembl2symbol)
-##names(symbol2ensembl) = ensembl2symbol
-
-##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")
-
-##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
-##ensembl2symbol[row.names(extras)] = extras$SYMBOL
-
-##symbol = ensembl2symbol
-
-##symbol = background
-
-##symbol[intersect(GeneIDKey$FBgn, background)] = 
-##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]
-
-##CamiData = data.frame(FBgn       = background[1:14674],
-##                      Symbol     = symbol[1:14674],
-##                      Moderate   = moderate[1:14674],
-##                      Strong     = strong[1:14674],
-##                      Lethal     = lethal[1:14674],
-##                      Enhancer   = enhancer[1:14674],
-##                      No.Effect  = no.effect[1:14674])
-
-##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")
-
-Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
-
-```
-
-```{r include=F, echo=F}
-
-kegg=keggLink("pathway","dme")
-names(kegg)=gsub("dme:Dmel_","",names(kegg))
+kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
+kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
 
@@
 ##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
-kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
 
-temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
-temp = temp[intersect(names(kegg),names(temp))]
-kegg = kegg[intersect(names(kegg),names(temp))]
-names(kegg) = temp[names(kegg)]
-kegg = as.list(kegg)
 keggID=keggConv("dme","ncbi-geneid")
-
-##sigs = Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Repress.GO = GO.wall
-##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Repress.KEGG = KEGG
-##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Lethal.GO = GO.wall
-##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Lethal.KEGG = KEGG
-##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Enhance.GO = GO.wall
-##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv")
-
-##KEGG term enrichment is KEGG
-##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##EGG$Name=kegg.names[row.names(KEGG),1]
-##Enhance.KEGG = KEGG
-##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv")
-
-Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
-Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
-Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)
-
-Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
-Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
-Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)
 
@@
 
-```{r}
+```{r include=F, echo=F}
 
-PathwayID = "04141"
+sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
+sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
+                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
+                           "Symbol"]
+genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRF.CxDf.GO = GO.wall
+write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")
+
+##KEGG term enrichment is KEGG
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRF.CxDf.KEGG = KEGG
+write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")
+
+sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
+sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
+                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
+                           "Symbol"]
+genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRF.CxDf.GO = GO.wall
+write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")
+
+##KEGG term enrichment is KEGG
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRF.CxDf.KEGG = KEGG
+write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")
+
+```
+
+```{r, fig.width= 10}
+
+GO.data = GRF.CxDf.GO
+GO.data = GO.data[GO.data$ontology == 'BP',
+                  c("category", "term","adjp", "numDEInCat", "numInCat")]
+
+data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
+data$Score = -log10(data$adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+
+m <- list(
+  l = 50,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 4
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "term",
+               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$term,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3))) %>%
+    layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Top 20 Most Enriched GO Terms",
+           margin = m)
+
+fig
+
+```
+
+```{r, echo = F, include = F}
+
+KEGG20 = function(data){
+
+  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
+
+data = data[20:1,]
+data$Score = -log10(data$adjp)
+data$term = factor(data$Name, levels = c(unique(data$Name)))
+
+m <- list(
+  l = 50,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 4
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "Name",
+               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$Name,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3))) %>%
+    layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Top 20 Most Enriched KEGG Terms",
+           margin = m)
+
+return(fig)
+
+}
+
+```
+
+```{r fig.width=10}
+
+data = GRF.CxDf.KEGG
+
+KEGG20(data)
+
+```
+
+```{r echo = F, include = F}
+PathwayID = "03050"
 
@@
 
-Moderate = Df.data[Df.data$Moderate == 1, "Symbol"]
-Moderate = intersect(Moderate, all.path)
-Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")
+Df = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
+                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
+                         "Symbol"]
+Df = intersect(Df, all.path)
+Df = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Df, "CG"],sep="")
 
-Strong = Df.data[Df.data$Strong == 1, "Symbol"]
-Strong = intersect(Strong, all.path)
-Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
-
-Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
-Enhancer = intersect(Enhancer, all.path)
-Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")
-
-Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
-Lethal = intersect(Lethal, all.path)
-Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
+OE = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxOE <= .05],
+                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktOEGR.F1","TktOEGR.F2","TktOEGR.F3")], 1, min) >5]), 
+                         "Symbol"]
+OE = intersect(OE, all.path)
+OE = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% OE, "CG"],sep="")
 
@@
 
-knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/dme04141.", kegg.names[paste0("dme", PathwayID),1], ".png"))
+```
 
+```{r}
+knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
 ```
@@
 
-GO.data = Repress.GO[Repress.GO$adjp <= .05 &
-                     Repress.GO$ontology == 'BP',
-                     c("category", "term","adjp", "numDEInCat", "numInCat")]
-
-go_analysis = GO.data$category
+go_analysis = GO.data$category[GO.data$adjp <= .05]
 scores = setNames(-log10(GO.data$adjp), go_analysis)
 
-##simMatrix <- calculateSimMatrix(go_analysis,
-##                                orgdb="org.Dm.eg.db",
-##                                ont="BP",
-##                                method="Rel")
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont="BP",
+                                method="Rel")
 
@@
 
-##reducedTerms <- reduceSimMatrix(simMatrix,
-##                                scores,
-##                                threshold=0.7,
-##                                orgdb="org.Dm.eg.db")
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
 ##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
 
-simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
-reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
+##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
+##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
 

### 2023-07-10 DeficiencyScreen/KEGG_Analysis.Rmd
update

--- 2023-07-07 TKT_RNAseq/R Code/KEGG_Analysis.Rmd
@@
 ```{r setup, include=FALSE}
-library(rgl)
-knitr::opts_chunk$set(echo = FALSE, fig.align="center")
-knitr::knit_hooks$set(webgl = hook_webgl)
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 ##Load Libraries
-
-library(biomaRt)
-library(org.Dm.eg.db)
-library(goseq)
-library(GO.db)
-library(visNetwork)
-library(rrvgo)
 library(plotly)
-library(KEGGREST)
 library(pathview)
-##library(RColorBrewer)
 ```
@@
 ##load all files from github
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+Df.data = read.csv(paste0(git.dir,"GeneralDataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
+Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
+Df.data$Repress = 0
+Df.data$Repress[Df.data$Moderate == 1|Df.data$Strong == 1] = 1
+kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
+kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)
 
-Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
-Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
-
-kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
-
-keggID=keggConv("dme","ncbi-geneid")
-
-kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
-
-Moderate.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateKEGGAnalysis.csv", row.names = 1)
-
-Strong.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongKEGGAnalysis.csv", row.names = 1)
-
-Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
-
-Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
-
-Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)
+Moderate.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateKEGGAnalysis.csv"), row.names = 1)
+Strong.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongKEGGAnalysis.csv"), row.names = 1)
+Repress.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorKEGGAnalysis.csv"), row.names = 1)
+Lethal.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalKEGGAnalysis.csv"), row.names = 1)
+Enhancer.KEGG = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerKEGGAnalysis.csv"), row.names = 1)
 
@@
 
+if(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files"){
+  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+}
+
+Home = dirname(rstudioapi::getSourceEditorContext()$path)
+OutputDir = paste0(Home, "/KEGG_Image_Files/")
+
 ShowKEGG = function(PathwayID){
-download.kegg(pathway.id= PathwayID, species = "dme")
-xml.file=paste0("dme",PathwayID,".xml")
+
+download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
+xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
 node.data=node.info(xml.file)
@@
 
+setwd(OutputDir)
 pv.pars= keggview.native(plot.data.gene=plot.data.gene,
@@
                          pathway.name=paste0("dme", PathwayID),
-                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1])
-
+                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1],
+                         kegg.dir = OutputDir)
+setwd(Home)
 }
@@
 
-data = Moderate.KEGG
+##Options: Moderate.KEGG, Strong.KEGG, Repress.KEGG, Lethal.KEGG, Enhancer.KEGG
+data = Repress.KEGG
 
@@
 ```{r echo = F, include = F}
-PathwayID = "04150"
+
+PathwayID = "04141"
 
@@
 
-```{r}
-knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
+```{r echo = F}
+
+knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
+
 ```
+
+```{r include = F, echo = F}
+
+GenesInKEGG = Df.data[Df.data$Symbol %in% names(kegg[grep(PathwayID, kegg)]),]
+write.csv(GenesInKEGG, paste0(OutputDir,"GenesInKEGG_dme", PathwayID,".csv"))
+
+```

### 2023-07-10 DeficiencyScreen/GO_Analysis.Rmd
update

@@
 
-library(biomaRt)
-library(org.Dm.eg.db)
-library(goseq)
-library(GO.db)
-library(visNetwork)
+##library(biomaRt)
+##library(org.Dm.eg.db)
+##library(goseq)
+##library(GO.db)
+##library(visNetwork)
 library(rrvgo)
 library(plotly)
-library(KEGGREST)
-library(pathview)
+##library(KEGGREST)
+##library(pathview)
 ##library(RColorBrewer)
@@
 ##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
-cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
-groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
+##kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
+##kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)
 
-##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")
-
-##background = setNames(unique(CamiData$Background), unique(CamiData$Background))
-
-##moderate = setNames(rep(0, length(background)), names(background))
-
-##moderate[unique(CamiData$Moderate)] = 1
-
-##strong = setNames(rep(0, length(background)), names(background))
-
-##strong[unique(CamiData$Strong)] = 1
-
-##lethal = setNames(rep(0, length(background)), names(background))
-
-##lethal[unique(CamiData$Lethal)] = 1
-
-##enhancer = setNames(rep(0, length(background)), names(background))
-
-##enhancer[unique(CamiData$Enhancers)] = 1
-
-##no.effect = setNames(rep(0, length(background)), names(background))
-
-##no.effect[unique(CamiData$No.Effect)] = 1
-
-##FB2Ensembl
-##x1=as.list(org.Dm.egENSEMBL2EG)
-##Ensembl2Symbol
-##x2=as.list(org.Dm.egSYMBOL)
-##Symbol2Ensembl
-##x3=as.list(org.Dm.egSYMBOL2EG)
-##Ensembl2FB
-##x4=as.list(org.Dm.egENSEMBL)
-##ensembl to FBgn
-##x5=as.list(org.Dm.egFLYBASE)
-
-##FBgn2ensembl = row.names(CamiData)
-##names(FBgn2ensembl) = row.names(CamiData)
-##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
-##FBgn2ensembl[names(tempEG)]=tempEG
-
-##ensembl2symbol = row.names(CamiData)
-##names(ensembl2symbol) = FBgn2ensembl
-##tempSymbol = unlist(x2[FBgn2ensembl])
-##ensembl2symbol[names(tempSymbol)]=tempSymbol
-##symbol2ensembl = names(ensembl2symbol)
-##names(symbol2ensembl) = ensembl2symbol
-
-##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")
-
-##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
-##ensembl2symbol[row.names(extras)] = extras$SYMBOL
-
-##symbol = ensembl2symbol
-
-##symbol = background
-
-##symbol[intersect(GeneIDKey$FBgn, background)] = 
-##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]
-
-##CamiData = data.frame(FBgn       = background[1:14674],
-##                      Symbol     = symbol[1:14674],
-##                      Moderate   = moderate[1:14674],
-##                      Strong     = strong[1:14674],
-##                      Lethal     = lethal[1:14674],
-##                      Enhancer   = enhancer[1:14674],
-##                      No.Effect  = no.effect[1:14674])
-
-##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")
-
-Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)
+Moderate.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv"), row.names = 1)
+Strong.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongGOAnalysis.csv"), row.names = 1)
+Repress.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv"), row.names = 1)
+Lethal.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalGOAnalysis.csv"), row.names = 1)
+Enhancer.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv"), row.names = 1)
 
@@
 ```{r include=F, echo=F}
-
-##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
-kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
-
-keggID=keggConv("dme","ncbi-geneid")
-
-kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
 
@@
 
-Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
-Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv", row.names = 1)
-
-Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
-Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
-Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)
-
 ```
 
-```{r, fig.width= 10}
+```{r echo = F, include =F}
 
-GO.data = Moderate.GO
-GO.data = GO.data[GO.data$ontology == 'BP',
+GO20 = function(GO.data, GO.ontology){
+GO.data = GO.data[GO.data$ontology == GO.ontology,
                   c("category", "term","adjp", "numDEInCat", "numInCat")]
@@
 
-fig
+  return(fig)
+}
+
+```
+
+```{r echo = F, include =F}
+
+GO.data = Repress.GO
+GO.ontology = "BP"
+
+GO.fig = GO20(GO.data, GO.ontology)
+
+```
+
+```{r, fig.width= 10}
+
+GO.fig
 
@@
                                 orgdb="org.Dm.eg.db",
-                                ont="BP",
+                                ont=GO.ontology,
                                 method="Rel")
-
-##write.csv(simMatrix, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv")
 
@@
                                 orgdb="org.Dm.eg.db")
-##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
-
-##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
-##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
 
@@
             main = "Repressor Gene Enriched Biological Process GO terms")
-
-```
-
-```{r, fig.align='left', include=F}
-
-scatterPlot(simMatrix, reducedTerms)
 
@@
 ```
-
-```{r, include=F, echo=F}
-GO2Gene   = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GenesInGOTerms.csv", row.names = 1)
-
-ccpar=as.list(GOCCPARENTS)
-ccchild=as.list(GOCCCHILDREN)
-
-bppar=as.list(GOBPPARENTS)
-bpchild=as.list(GOBPCHILDREN)
-
-mfpar=as.list(GOMFPARENTS)
-mfchild=as.list(GOMFCHILDREN)
-```
-
-```{r, include=F, echo=F}
-
-compare = "GRM.CxDf"
-filter.samples = c("GR.M", "TktDfGR.M")
-
-sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,compare]<=.05]
-sigs = sigs[apply(cpmdata[sigs,groups$Group %in% filter.samples], 1, min) > 10]
-
-genes=c(rep(0, nrow(cpmdata)))
-names(genes) = row.names(cpmdata)
-genes[sigs] = 1
-names(genes) = GeneIDKey[names(genes), "Symbol"]
-
-pwf=nullp(genes,"dm3","geneSymbol")
-
-GO.wall=goseq(pwf,"dm3","geneSymbol")
-GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-row.names(GO.wall) = GO.wall$category
-
-GO.wall$Significant = "not"
-GO.wall[GO.wall$adjp <= .05, "Significant"] = "sig"
-sigGO = GO.wall[GO.wall$adjp<.05,]
-
-##Biological Processes
-bpGO = sigGO[sigGO$ontology == 'BP',]
-
-##parent terms are those directly above in hierarchy
-## isa implies a defining relationship; part of implies they contribute to the category
-
-parents = bppar[bpGO$category]
-
-parents = data.frame(from = unlist(parents),
-                     label = substring(names(unlist(parents)),12),
-                     to = substring(names(unlist(parents)),1,10))
-
-parents = parents[parents$to %in% row.names(GO.wall),]
-
-children = bpchild[bpGO$category]
-
-children = data.frame(from = substring(names(unlist(children)),1,10),
-                      label = substring(names(unlist(children)),12),
-                      to = unlist(children))
-
-children = children[children$to %in% row.names(GO.wall),]
-
-edges = rbind(parents, children)
-edges = edges[edges$label == "isa",]
-edges = unique(edges)
-
-edges = edges[GO.wall[edges$to, "numDEInCat"]>0,]
-
-node.id = unique(c(edges$from, edges$to))
-node.label = GO.wall[node.id, "term"]
-node.group = GO.wall[node.id, "Significant"]
-node.value = 100*(GO.wall[node.id, "numDEInCat"]/GO.wall[node.id, "numInCat"])
-
-nodes = data.frame(id = node.id,
-                   label = node.label,
-                   group = node.group,
-                   value = node.value)
-```
-
-```{r include=F}
-
-visNetwork(nodes, edges)%>%
-  visLayout(hierarchical=F, improvedLayout=T)%>%
-  visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-70),enabled=T)%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows='to')%>%
-  visGroups(groupname = "sig", shape = "box", color = list(background = "gold", border="black", groupname="black"),physics=F,font=list(color="black"))%>%
-  visGroups(groupname = "not", shape = "dot", color = list(background = "grey", border="black", groupname="black"),physics=T,font=list(color="black"))
-
-```

### 2023-07-10 DeficiencyScreen/KEGG_Analysis.Rmd
update

@@
 GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
-Df.data = read.csv(paste0(git.dir,"GeneralDataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
-Df.data$CG = GeneIDKey[row.names(Df.data),"CG"]
-Df.data$Repress = 0
-Df.data$Repress[Df.data$Moderate == 1|Df.data$Strong == 1] = 1
+Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
 kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
@@
 
-```{r fig.width=10}
+```{r echo = F, fig.width=10}
 
@@
 
-```{r echo = F}
+```{r echo = F, fig.align='center'}
 

### 2023-07-10 DeficiencyScreen/GO_Analysis.Rmd
update

@@
 
-##library(biomaRt)
-##library(org.Dm.eg.db)
+library(org.Dm.eg.db)
 ##library(goseq)
-##library(GO.db)
-##library(visNetwork)
 library(rrvgo)
 library(plotly)
-##library(KEGGREST)
-##library(pathview)
-##library(RColorBrewer)
 ```
@@
 
+genesingo=as.list(org.Dm.egGO2ALLEGS)
+
 ```
@@
 
-##sigs = Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
+##sigs = unique(Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"])
+##genes = setNames(rep(0, length(unique(Df.data$Symbol))), unique(Df.data$Symbol))
 ##genes[sigs] = 1
@@
 ##Repress.GO = GO.wall
-##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv")
+##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv")
 
@@
 ##Repress.KEGG = KEGG
-##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv")
+##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/RepressorKEGGAnalysis.csv")
 
@@
 ##Moderate.GO = GO.wall
-##write.csv(Moderate.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv")
+##write.csv(Moderate.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 ##KEGG=goseq(pwf,gene2cat=kegg)
@@
 ##Moderate.KEGG = KEGG
-##write.csv(Moderate.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateKEGGAnalysis.csv")
+##write.csv(Moderate.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateKEGGAnalysis.csv")
 
@@
 ##Strong.GO = GO.wall
-##write.csv(Strong.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv")
+##write.csv(Strong.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongGOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 ##KEGG=goseq(pwf,gene2cat=kegg)
@@
 ##Strong.KEGG = KEGG
-##write.csv(Strong.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongKEGGAnalysis.csv")
+##write.csv(Strong.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongKEGGAnalysis.csv")
 
@@
 ##Lethal.GO = GO.wall
-##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv")
+##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalGOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 ##KEGG=goseq(pwf,gene2cat=kegg)
@@
 ##Lethal.KEGG = KEGG
-##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv")
+##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalKEGGAnalysis.csv")
 
@@
 ##Enhance.GO = GO.wall
-##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv")
+##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 ##KEGG=goseq(pwf,gene2cat=kegg)
@@
 ##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##EGG$Name=kegg.names[row.names(KEGG),1]
+##KEGG$Name=kegg.names[row.names(KEGG),1]
 ##Enhance.KEGG = KEGG
-##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv")
+##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerKEGGAnalysis.csv")
 
@@
 
-go_analysis = GO.data$category[GO.data$adjp <= .05]
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
 scores = setNames(-log10(GO.data$adjp), go_analysis)
@@
 ```
+
+```{r include = F, echo = F}
+
+GOID = "0006334"
+GenesInGO = genesingo[paste0("GO:", GOID)]
+
+GenesInGO = Df.data[Df.data$ensembl %in% GenesInGO[[1]],]
+
+```

### 2023-07-17 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
update

---
title: "G85R vs WT (M + F)"
author: "John Santiago"
date: "2023-07-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include=F}
##Load Libraries

library(biomaRt)
library(org.Dm.eg.db)
library(goseq)
library(GO.db)
library(visNetwork)
library(rrvgo)
library(plotly)
library(KEGGREST)
library(pathview)
library(VennDiagram)
library(heatmaply)
```

```{r, echo = F, include = F}

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

genesingo=as.list(org.Dm.egGO2ALLEGS)

Enrichment = function(sigs){
  genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")
  return(enrichment.data)
}

```

##GO.Sim.PCA function
```{r echo = F, include = F}
GO.Sim.PCA = function(use.data){
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = reducedTerms[row.names(use.data), "parentTerm"],
                        Score = reducedTerms[row.names(use.data), "score"],
                        Term = reducedTerms[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 ##symbol = ~Group,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c("firebrick","gold","deepskyblue"),
                 marker = list(size = pca.data$Score,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Parent Group: ", pca.data$Group,
                                   "\nSample: ", pca.data$Term, 
                                   "\nTotal DE: ", pca.data$TotalDE, 
                                   "\nTotal in Cat.: ", pca.data$Total, 
                                   "\nFDR: ", pca.data$SigVal)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "Enriched GO term similarity")

  return(fig)
}

```

##GO20 Function
```{r echo = F, include =F}

GO20 = function(GO.data, GO.ontology){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

  return(fig)
}

```

##KEGG20 Function
```{r, echo = F, include = F}

KEGG20 = function(data){

  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]

data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$Name, levels = c(unique(data$Name)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Name",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$Name,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched KEGG Terms",
           margin = m)

return(fig)

}

```

```{r echo = F, include = F}

comparison1 = "GRxWT.FC"
comparison2 = "GRxWT.MC"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "WT.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

##sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRF.CxDf"]<=.05]

sigsKEY = GeneIDKey[sigs,]

sigs = sigsKEY$Symbol

sig.cats = Enrichment(sigs)

```

```{r echo =F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r echo = F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology)

KEGG.fig = KEGG20(sig.cats[["KEGG"]])

```

```{r, fig.width= 10}

BP.GO.fig

```

```{r, fig.width= 10}

CC.GO.fig

```

```{r, fig.width= 10}

MF.GO.fig

```

```{r, fig.width= 10}

KEGG.fig

```

```{r fig.height=7, fig.width=10}

heatmapPlot(simMatrix,
            reducedTerms,
            annotateParent=TRUE,
            annotationLabel="parentTerm",
            fontsize=6,
            main = "Repressor Gene Enriched Biological Process GO terms")

```

```{r warning=F, fig.width=10}

use.data   = simMatrix
GO.Sim.PCA(use.data)

```

```{r fig.align='left'}

treemapPlot(reducedTerms)

```

```{r include = F, echo = F}

GOID = "GO:0005634"
GenesInGO = genesingo[GOID]

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]

```

```{r include = F, echo = F}
ParentID = "GO:0044271"
GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
GOID = GOIDs[1]
GenesInParent= unique(genesingo[[GOID]])
i=2
while(i<=length(GOIDs)){
  GOID = GOIDs[i]
  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
  i=i+1
}

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]

```

```{r echo =F, warnings = F}

comparison = "GRxWT.FC"
comparison2 = "GRxWT.MC"

hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

```

##############
## GRxWT Df ##
##############

```{r echo = F, include = F}

comparison1 = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

sigs = sigsKEY$Symbol

sig.cats = Enrichment(sigs)

```

```{r echo = F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology)

KEGG.fig = KEGG20(sig.cats[["KEGG"]])

```

```{r, fig.width= 10}

BP.GO.fig

```

```{r, fig.width= 10}

CC.GO.fig

```

```{r, fig.width= 10}

MF.GO.fig

```

```{r, fig.width= 10}

KEGG.fig

```

```{r echo =F, warnings = F}

comparison = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

##hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

##hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

```

##############
## GRxWT OE ##
##############

```{r echo = F, include = F}

comparison1 = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

sigs = sigsKEY$Symbol

sig.cats = Enrichment(sigs)

```

```{r echo =F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r echo = F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology)

KEGG.fig = KEGG20(sig.cats[["KEGG"]])

```

```{r, fig.width= 10}

BP.GO.fig

```

```{r, fig.width= 10}

CC.GO.fig

```

```{r, fig.width= 10}

MF.GO.fig

```

```{r, fig.width= 10}

KEGG.fig

```

```{r fig.height=7, fig.width=10}

heatmapPlot(simMatrix,
            reducedTerms,
            annotateParent=TRUE,
            annotationLabel="parentTerm",
            fontsize=6,
            main = "Repressor Gene Enriched Biological Process GO terms")

```

```{r warning=F, fig.width=10}

use.data   = simMatrix
GO.Sim.PCA(use.data)

```

```{r fig.align='left'}

treemapPlot(reducedTerms)

```

```{r include = F, echo = F}

GOID = "GO:0003723"
GenesInGO = genesingo[GOID]

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]

```

```{r include = F, echo = F}
ParentID = "GO:0034249"
GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
GOID = GOIDs[1]
GenesInParent= unique(genesingo[[GOID]])
i=2
while(i<=length(GOIDs)){
  GOID = GOIDs[i]
  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
  i=i+1
}

GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]

```

```{r echo =F, warnings = F}

comparison = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

hmdata = cpmdata[GenesInGO, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]

hover.text = round(hmdata, digits = 1)

FDR = hmdata
FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]

FBgn = hmdata
FBgn[,1:ncol(FBgn)] = row.names(FBgn)

i=1
while(i<=ncol(hover.text)){
  hover.text[,i] = paste("CPM = ", hover.text[,i],
                         "\nFDR = ", FDR[,i],
                         "\nFBgn = ", FBgn[,i])
  i=i+1
}

hmdata2 = cpmdata[GenesInGO, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]

hover.text2 = round(hmdata2, digits = 1)

FDR2 = hmdata2
FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]

FBgn2 = hmdata2
FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)

i=1
while(i<=ncol(hover.text2)){
  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
                         "\nFDR = ", FDR2[,i],
                         "\nFBgn = ", FBgn2[,i])
  i=i+1
}

hmdata = cbind(hmdata, hmdata2)
hover.text = cbind(hover.text, hover.text2)

heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            show_dendrogram = c(F,T),
            Rowv=T,
            Colv=T,
            ##cexRow = 1/(as.numeric(input$tophits)/25),
            na.color="grey",
            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
            ##cexCol = col.text,
            cexCol = 1,
            key = T,
            ##margins = c(50,350,NA,0),
            ##row_dend_left = T,
            column_text_angle = 90,

            ##col_side_colors=color.groups,
            ##col_side_palette=Spectral,
            ##main= "",
            custom_hovertext = hover.text)

```

#########################
## Comparing the three ##
#########################

```{r include = F, echo = F}

comparison1 = "GRxWT.FC"
comparison2 = "GRxWT.MC"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "GR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

C.sigs = sigsKEY$Symbol

comparison1 = "GRxWT.FDf"
comparison2 = "GRxWT.MDf"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

Df.sigs = sigsKEY$Symbol

comparison1 = "GRxWT.FOE"
comparison2 = "GRxWT.MOE"

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]

sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]

sigs= intersect(sigs1, sigs2)

sigsKEY = GeneIDKey[sigs,]

OE.sigs = sigsKEY$Symbol

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Control"
set2="Defficient"
set3="Over Expression"
##set4="GSC2.Stem"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = C.sigs
s2 = Df.sigs
s3 = OE.sigs
##s4=row.names(temp)[temp[,4]==1]

```

```{r}

data = data.frame(Condition = c("Control", "Defficient", "Over Expression"), DEGs = c(length(C.sigs), length(Df.sigs), length(OE.sigs)))

fig <- plot_ly(data, 
               x = ~Condition, y = ~DEGs, 
               type = 'bar',
               name = ~Condition,
               color = ~Condition,
               colors = c("coral3","gold2", "steelblue3"),
               marker = list(line = list(color = "black", width = 1.5)))

fig

```

```{r}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("brown1","gold2", "steelblue2"),cex=1.5,cat.cex = 1)

```

### 2023-07-17 TKT_RNAseq/R Code/GO_Analysis.Rmd
update

@@
 ##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
-cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
-groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv"),row.names = 1)
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
-kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
-kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")
+kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
+kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)
 
-##i=1
-##kegg.names=unique(substr(kegg,6,13))
-##names(kegg.names)=as.vector(kegg.names)
-##while(i<=length(kegg.names)){
-##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
-##  i=i+1
-##}
+##keggID=keggConv("dme","ncbi-geneid")
 
-##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
+datadir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/"
 
-keggID=keggConv("dme","ncbi-geneid")
+GRF.CxDf.GO  = read.csv(paste0(datadir, "GRF.CxDf.GOAnalysis.csv"), row.names =1)
+GRF.CxOE.GO  = read.csv(paste0(datadir, "GRF.CxOE.GOAnalysis.csv"), row.names =1)
+WTF.CxDf.GO  = read.csv(paste0(datadir, "WTF.CxDf.GOAnalysis.csv"), row.names =1)
+WTF.CxOE.GO  = read.csv(paste0(datadir, "WTF.CxOE.GOAnalysis.csv"), row.names =1)
 
+GRM.CxDf.GO  = read.csv(paste0(datadir, "GRM.CxDf.GOAnalysis.csv"), row.names =1)
+GRM.CxOE.GO  = read.csv(paste0(datadir, "GRM.CxOE.GOAnalysis.csv"), row.names =1)
+WTM.CxDf.GO  = read.csv(paste0(datadir, "WTM.CxDf.GOAnalysis.csv"), row.names =1)
+WTM.CxOE.GO  = read.csv(paste0(datadir, "WTM.CxOE.GOAnalysis.csv"), row.names =1)
+
+GR.FxM.GO    = read.csv(paste0(datadir, "GR.FxM.GOAnalysis.csv"), row.names =1)
+WT.FxM.GO    = read.csv(paste0(datadir, "WT.FxM.GOAnalysis.csv"), row.names =1)
+
+GRxWT.FC.GO  = read.csv(paste0(datadir, "GRxWT.FC.GOAnalysis.csv"), row.names =1)
+GRxWT.FDf.GO = read.csv(paste0(datadir, "GRxWT.FDf.GOAnalysis.csv"), row.names =1)
+GRxWT.FOE.GO = read.csv(paste0(datadir, "GRxWT.FOE.GOAnalysis.csv"), row.names =1)
+
+GRxWT.MC.GO  = read.csv(paste0(datadir, "GRxWT.MC.GOAnalysis.csv"), row.names =1)
+GRxWT.MDf.GO = read.csv(paste0(datadir, "GRxWT.MDf.GOAnalysis.csv"), row.names =1)
+GRxWT.MOE.GO = read.csv(paste0(datadir, "GRxWT.MOE.GOAnalysis.csv"), row.names =1)
+
+SigDEGs = TKT.EdgeR
+SigDEGs[,] = 0
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktDfGR.F"],1,min) > 5)], "GRF.CxDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktOEGR.F"],1,min) > 5)], "GRF.CxOE"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "WTF.CxDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "WTF.CxOE"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FC <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "WT.F"],1,min) > 5)], "GRxWT.FC"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "GRxWT.FDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "WTF.CxOE"] =1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktDfGR.M"],1,min) > 5)], "GRM.CxDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktOEGR.M"],1,min) > 5)], "GRM.CxOE"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "WTM.CxDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "WTM.CxOE"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MC <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "WT.F"],1,min) > 5)], "GRxWT.MC"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "GRxWT.MDf"] = 1
+
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "GRxWT.MOE"] = 1
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GR.FxM  <= .05)], "GR.FxM"] = 1
+SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WT.FxM  <= .05)], "WT.FxM"] = 1
 ```
 
-```{r include=F, echo=F}
+##GOterm and KEGG enrichment analysis for all EdgeR comparisons
+##```{r include=F, echo=F}
 
-sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
-sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
-                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
-                           "Symbol"]
-genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
+##############
+## GRF.CxDf ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktDfGR.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
 genes[sigs] = 1
@@
 GRF.CxDf.GO = GO.wall
-write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")
+write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.GOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 KEGG=goseq(pwf,gene2cat=kegg)
@@
 
-sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
-sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
-                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
-                           "Symbol"]
-genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
+##############
+## GRF.CxOE ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktOEGR.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
 genes[sigs] = 1
@@
 row.names(GO.wall) = GO.wall$category
-GRF.CxDf.GO = GO.wall
-write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")
+GRF.CxOE.GO = GO.wall
+write.csv(GRF.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxOE.GOAnalysis.csv")
 
-##KEGG term enrichment is KEGG
 KEGG=goseq(pwf,gene2cat=kegg)
@@
 KEGG$Name=kegg.names[row.names(KEGG),1]
-GRF.CxDf.KEGG = KEGG
-write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")
+GRF.CxOE.KEGG = KEGG
+write.csv(GRF.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxOE.KEGGAnalysis.csv")
 
-```
+##############
+## WTF.CxDf ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+WTF.CxDf.GO = GO.wall
+write.csv(WTF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxDf.GOAnalysis.csv")
 
-```{r, fig.width= 10}
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+WTF.CxDf.KEGG = KEGG
+write.csv(WTF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxDf.KEGGAnalysis.csv")
 
-GO.data = GRF.CxDf.GO
-GO.data = GO.data[GO.data$ontology == 'BP',
+##############
+## WTF.CxOE ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+WTF.CxOE.GO = GO.wall
+write.csv(WTF.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxOE.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+WTF.CxOE.KEGG = KEGG
+write.csv(WTF.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxOE.KEGGAnalysis.csv")
+
+##############
+## GRM.CxDf ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktDfGR.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRM.CxDf.GO = GO.wall
+write.csv(GRM.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxDf.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRM.CxDf.KEGG = KEGG
+write.csv(GRM.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxDf.KEGGAnalysis.csv")
+
+##############
+## GRM.CxOE ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktOEGR.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRM.CxOE.GO = GO.wall
+write.csv(GRM.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxOE.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRM.CxOE.KEGG = KEGG
+write.csv(GRM.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxOE.KEGGAnalysis.csv")
+
+##############
+## WTM.CxDf ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+WTM.CxDf.GO = GO.wall
+write.csv(WTM.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxDf.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+WTM.CxDf.KEGG = KEGG
+write.csv(WTM.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxDf.KEGGAnalysis.csv")
+
+##############
+## WTM.CxOE ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+WTM.CxOE.GO = GO.wall
+write.csv(WTM.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxOE.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+WTM.CxOE.KEGG = KEGG
+write.csv(WTM.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxOE.KEGGAnalysis.csv")
+
+##############
+## GRxWT.FC ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FC <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "WT.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.FC.GO = GO.wall
+write.csv(GRxWT.FC.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FC.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.FC.KEGG = KEGG
+write.csv(GRxWT.FC.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FC.KEGGAnalysis.csv")
+
+###############
+## GRxWT.FDf ##
+###############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.FDf.GO = GO.wall
+write.csv(GRxWT.FDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FDf.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.FDf.KEGG = KEGG
+write.csv(GRxWT.FDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FDf.KEGGAnalysis.csv")
+
+###############
+## GRxWT.FOE ##
+###############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.FOE.GO = GO.wall
+write.csv(GRxWT.FOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FOE.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.FOE.KEGG = KEGG
+write.csv(GRxWT.FOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FOE.KEGGAnalysis.csv")
+
+##############
+## GRxWT.MC ##
+##############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MC <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "WT.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.MC.GO = GO.wall
+write.csv(GRxWT.MC.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MC.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.MC.KEGG = KEGG
+write.csv(GRxWT.MC.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MC.KEGGAnalysis.csv")
+
+###############
+## GRxWT.MDf ##
+###############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MDf  <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.MDf.GO = GO.wall
+write.csv(GRxWT.MDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MDf.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.MDf.KEGG = KEGG
+write.csv(GRxWT.MDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MDf.KEGGAnalysis.csv")
+
+###############
+## GRxWT.MOE ##
+###############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MOE  <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GRxWT.MOE.GO = GO.wall
+write.csv(GRxWT.MOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MOE.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GRxWT.MOE.KEGG = KEGG
+write.csv(GRxWT.MOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MOE.KEGGAnalysis.csv")
+
+############
+## GR.FxM ##
+############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GR.FxM  <= .05)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+GR.FxM.GO = GO.wall
+write.csv(GR.FxM.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GR.FxM.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+GR.FxM.KEGG = KEGG
+write.csv(GR.FxM.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GR.FxM.KEGGAnalysis.csv")
+
+############
+## WT.FxM ##
+############
+sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WT.FxM  <= .05)], "Symbol"]
+genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+WT.FxM.GO = GO.wall
+write.csv(WT.FxM.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WT.FxM.GOAnalysis.csv")
+
+KEGG=goseq(pwf,gene2cat=kegg)
+KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+KEGG$Name=kegg.names[row.names(KEGG),1]
+WT.FxM.KEGG = KEGG
+write.csv(WT.FxM.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WT.FxM.KEGGAnalysis.csv")
+
+##```
+
+##GO20 Function
+```{r echo = F, include =F}
+
+GO20 = function(GO.data, GO.ontology){
+GO.data = GO.data[GO.data$ontology == GO.ontology,
                   c("category", "term","adjp", "numDEInCat", "numInCat")]
@@
 
-fig
+  return(fig)
+}
 
@@
 
+##KEGG20 Function
 ```{r, echo = F, include = F}
@@
 
+##Pathview function
+```{r, include = F, echo = F}
+
+if(length(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files") == 0){
+  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+}
+
+Home = dirname(rstudioapi::getSourceEditorContext()$path)
+OutputDir = paste0(Home, "/KEGG_Image_Files/")
+
+ShowKEGG = function(PathwayID, DEG1, DEG2){
+
+  if(length(intersect(list.files(OutputDir), paste0("dme",PathwayID,".xml")))==0){
+    download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
+  }  
+  xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
+  node.data=node.info(xml.file)
+
+  all.path = names(kegg[grep(PathwayID,kegg)])
+  all.path = intersect(GeneIDKey[row.names(TKT.EdgeR),"Symbol"],all.path)
+
+  DEG1 = GeneIDKey[row.names(SigDEGs)[SigDEGs[,DEG1] == 1], "Symbol"]
+  DEG1 = intersect(DEG1, all.path)
+  DEG1 = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% DEG1, "CG"],sep="")
+
+  if(length(intersect(DEG2, colnames(SigDEGs))) ==1 ){
+  DEG2 = GeneIDKey[row.names(SigDEGs)[SigDEGs[,DEG2] == 1], "Symbol"]
+  DEG2 = intersect(DEG2, all.path)
+  DEG2 = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% DEG2, "CG"],sep="")    
+  }
+
+plot.data.gene=node.map(mol.data=c(DEG1, DEG2), node.data, node.types="gene")
+cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
+cols.ts.gene[1:length(cols.ts.gene)] = 0
+
+pdg.DEG1 = node.map(mol.data = DEG1, node.data, node.types="gene")
+temp = node.color(pdg.DEG1, limit=2, bins=2)
+ctg.DEG1 = cols.ts.gene
+ctg.DEG1[temp!="#FFFFFF"]= 1
+
+pdg.DEG2 = node.map(mol.data = DEG2, node.data, node.types="gene")
+temp = node.color(pdg.DEG2, limit=2, bins=2)
+ctg.DEG2 = cols.ts.gene
+ctg.DEG2[temp!="#FFFFFF"]= 1
+
+color.combos = data.frame(DEG1 = as.numeric(ctg.DEG1),
+                          DEG2 = as.numeric(ctg.DEG2))
+row.names(color.combos)= names(cols.ts.gene)
+
+cols.ts.gene[cols.ts.gene=="0"]="gainsboro"
+
+cols.ts.gene[row.names(color.combos)[color.combos$DEG1 == 1]] = "cornflowerblue"
+cols.ts.gene[row.names(color.combos)[color.combos$DEG2   == 1]] = "firebrick"
+cols.ts.gene[row.names(color.combos)[color.combos$DEG2   == 1 & color.combos$DEG1 == 1]] = "gold"
+
+setwd(OutputDir)
+pv.pars= keggview.native(plot.data.gene=plot.data.gene,
+                         cols.ts.gene=cols.ts.gene, 
+                         node.data=node.data,
+                         pathway.name=paste0("dme", PathwayID),
+                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1],
+                         kegg.dir = OutputDir)
+setwd(Home)
+}
+
+```
+
+```{r echo = F, include =F}
+
+GO.data = GRF.CxDf.GO
+GO.ontology = "BP"
+BP.GO.fig = GO20(GO.data, GO.ontology)
+
+GO.ontology = "CC"
+CC.GO.fig = GO20(GO.data, GO.ontology)
+
+GO.ontology = "MF"
+MF.GO.fig = GO20(GO.data, GO.ontology)
+
+KEGG.data = GRxWT.FDf.KEGG
+KEGG.fig = KEGG20(KEGG.data)
+
+```
+
+```{r, fig.width= 10}
+
+BP.GO.fig
+
+```
+
+```{r, fig.width= 10}
+
+CC.GO.fig
+
+```
+
+```{r, fig.width= 10}
+
+MF.GO.fig
+
+```
+
 ```{r fig.width=10}
 
-data = GRF.CxDf.KEGG
-
-KEGG20(data)
+KEGG.fig
 
@@
 ```{r echo = F, include = F}
-PathwayID = "03050"
-
-download.kegg(pathway.id= PathwayID, species = "dme")
-xml.file=paste0("dme",PathwayID,".xml")
-node.data=node.info(xml.file)
-
-all.path = names(kegg[grep(PathwayID,kegg)])
-
-Df = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
-                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
-                         "Symbol"]
-Df = intersect(Df, all.path)
-Df = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Df, "CG"],sep="")
-
-OE = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxOE <= .05],
-                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktOEGR.F1","TktOEGR.F2","TktOEGR.F3")], 1, min) >5]), 
-                         "Symbol"]
-OE = intersect(OE, all.path)
-OE = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% OE, "CG"],sep="")
-
-plot.data.gene=node.map(mol.data=c(Moderate, Strong, Enhancer, Lethal), node.data, node.types="gene")
-cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
-cols.ts.gene[1:length(cols.ts.gene)] = 0
-
-pdg.moderate=node.map(mol.data=Moderate, node.data, node.types="gene")
-temp = node.color(pdg.moderate, limit=2, bins=2)
-ctg.moderate = cols.ts.gene
-ctg.moderate[temp!="#FFFFFF"]= 1 ##"gold2"
-
-pdg.strong=node.map(mol.data=Strong, node.data, node.types="gene")
-temp = node.color(pdg.strong, limit=2, bins=2)
-ctg.strong = cols.ts.gene
-ctg.strong[temp!="#FFFFFF"]= 1 ##"brown2"
-
-pdg.enhancer=node.map(mol.data=Enhancer, node.data, node.types="gene")
-temp = node.color(pdg.enhancer, limit=2, bins=2)
-ctg.enhancer = cols.ts.gene
-ctg.enhancer[temp!="#FFFFFF"]= 1 ##"deepskyblue"
-
-pdg.lethal=node.map(mol.data=Lethal, node.data, node.types="gene")
-temp = node.color(pdg.lethal, limit=2, bins=2)
-ctg.lethal = cols.ts.gene
-ctg.lethal[temp!="#FFFFFF"]= 1 ##"navyblue"
-
-color.combos = data.frame(Moderate = as.numeric(ctg.moderate),
-                          Strong = as.numeric(ctg.strong),
-                          Enhancer = as.numeric(ctg.enhancer),
-                          Lethal = as.numeric(ctg.lethal))
-row.names(color.combos)= names(cols.ts.gene)
-
-cols.ts.gene[cols.ts.gene=="0"]="darkseagreen1"
-
-cols.ts.gene[row.names(color.combos)[color.combos$Moderate == 1]] = "gold2"
-cols.ts.gene[row.names(color.combos)[color.combos$Strong   == 1]] = "brown1"
-cols.ts.gene[row.names(color.combos)[color.combos$Enhancer   == 1]] = "lightsteelblue"
-cols.ts.gene[row.names(color.combos)[color.combos$Lethal   == 1]] = "cornflowerblue"
-cols.ts.gene[row.names(color.combos)[(color.combos$Moderate   == 1 | color.combos$Strong   == 1) & (color.combos$Enhancer   == 1 | color.combos$Lethal   == 1) ]] = "grey60"
-
-pv.pars= keggview.native(plot.data.gene=plot.data.gene,
-                         cols.ts.gene=cols.ts.gene, 
-                         node.data=node.data,
-                         pathway.name=paste0("dme", PathwayID),
-                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1])
+PathwayID = "04310"
+PathwayID = "00480" ##Glutathione Metabolism
+PathwayID = "00230" ##Purine metabolism
+DEG1 = "GRF.CxDf"
+DEG2 = "GRF.CxOE"
+ShowKEGG(PathwayID, DEG1, DEG2)
 
@@
 ```{r}
-knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
+knitr::include_graphics(paste0(OutputDir,"/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
 ```
 
-```{r include=F, echo=F}
+```{r  echo = F}
 
-go_analysis = GO.data$category[GO.data$adjp <= .05]
+geneset = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],]
+
+GenesInKEGG = geneset[geneset$Symbol %in% names(kegg[grep(PathwayID, kegg)]), ]
+
+hmdata = cpmdata[row.names(GenesInKEGG), groups$Group %in% c("GR.F",  "TktDfGR.F")]##, "TktDfGR.F","TktDfWT.F")]
+
+heatmaply(hmdata,
+            trace="none",
+            col=RdYlBu(100)[100:1],
+            scale="row",
+            dendrogram = "both",
+            show_dendrogram = c(F,T),
+            Rowv=T,
+            Colv=T,
+            na.color="grey",
+            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
+            cexCol = 1,
+            key = T,
+            column_text_angle = 90)
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = GRxWT.FC.GO
+GO.ontology = "BP"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
 scores = setNames(-log10(GO.data$adjp), go_analysis)
@@
                                 orgdb="org.Dm.eg.db")
-##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")
-
-##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
-##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
-
-```
-
-```{r, fig.width= 10}
-
-data = GO.data[,c("term","adjp","numDEInCat", "numInCat", "category")]
-data = data[order(data$adjp, decreasing = T),]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 4
-)
-
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "term",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$term,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3))) %>%
-    layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Significantly Enriched GO term Summary",
-           margin = m)
-
-fig
 

### 2023-07-26 Metabolomics/MetaboanalystRCode.Rmd
update

---
title: "Metaboanalyst"
author: "John Santiago"
date: "2023-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include = F}

library("MetaboAnalystR")

mSet<-InitDataObjects("pktable", "stat", FALSE)

mSet = Read.TextData(mSet, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", "colu", "disc")

mSet = SanityCheckData(mSet)

mSet<-ReplaceMin(mSet)
mSet<-SanityCheckData(mSet)
mSet<-FilterVariable(mSet, "none", -1, "F", 25, F)
mSet<-PreparePrenormData(mSet)

mSet<-Normalization(mSet, "CompNorm", "NULL", "NULL", "TIC", ratio=FALSE, ratioNum=20)
##mSet<-PlotNormSummary(mSet, "norm_0_", "png", 72, width=NA)
##mSet<-PlotSampleNormSummary(mSet, "snorm_0_", "png", 72, width=NA)

```

```{r}

mSet<-GetGroupNames(mSet, "")
feature.nm.vec <- c("")
smpl.nm.vec <- c("")
grp.nm.vec <- c("C","E")
mSet<-UpdateData(mSet)
mSet<-PreparePrenormData(mSet)
mSet<-Normalization(mSet, "CompNorm", "NULL", "NULL", "TIC", ratio=FALSE, ratioNum=20)
##mSet<-PlotNormSummary(mSet, "norm_1_", "png", 72, width=NA)
##mSet<-PlotSampleNormSummary(mSet, "snorm_1_", "png", 72, width=NA)
mSet<-FC.Anal(mSet, 2.0, 0, FALSE)
##mSet<-PlotFC(mSet, "fc_0_", "png", 72, width=NA)

mSet$analSet$fc
```

### 2023-07-26 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
update

@@
 DEout=G_X_E$table
-GRMDfxWTM=DEout
-sGRMDfxWTM=DEout[DEout$FDR<.05,]
+GRMDfxWTM3=DEout
+sGRMDfxWTM3=DEout[DEout$FDR<.05,]
 
@@
 DEout=G_X_E$table
-GRMDfxWTMDf=DEout
-sGRMDfxWTMDf=DEout[DEout$FDR<.05,]
+GRMDfxWTMDf3=DEout
+sGRMDfxWTMDf3=DEout[DEout$FDR<.05,]
 
 MDSdata4 = plotMDS(z, top = 12764, col=as.numeric(factor(gr)))
-
-all.cpmgenes = unique(c(row.names(cpmdata3),row.names(cpmdata4)))
-
-all.cpmdata = matrix(NA, ncol = 33, nrow = length(all.cpmgenes))
-colnames(all.cpmdata) = c(colnames(cpmdata3),colnames(cpmdata4))
-row.names(all.cpmdata) = all.cpmgenes
-
-all.cpmdata[row.names(cpmdata3),colnames(cpmdata3)] = cpmdata3
-all.cpmdata[row.names(cpmdata4),colnames(cpmdata4)] = cpmdata4
-
-all.groups = groups[colnames(all.cpmdata),]
-
-all.TKT.EdgeR = all.cpmdata[, 1:14]
-colnames(all.TKT.EdgeR) = c('GRF.CxDf', 'GRF.CxOE', 
-                            'WTF.CxDf', 'WTF.CxOE', 
-                            'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
-                            'GRM.CxDf', 'GRM.CxOE', 
-                            'WTM.CxDf', 'WTM.CxOE', 
-                            'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')
-
-row.names(all.TKT.EdgeR) = row.names(all.cpmdata)
-
-all.TKT.EdgeR[,1] = GR.F.CxDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,2] = GR.F.CxOE3[row.names(all.cpmdata),'FDR']
-
-all.TKT.EdgeR[,3] = WTF.CxDf = WT.F.CxDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,4] = WTF.CxOE = WT.F.CxOE3[row.names(all.cpmdata),'FDR']
-
-all.TKT.EdgeR[,5] = GRxWT.FC = GRxWT.F3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,6] = GRxWT.FDf = GRxWT.FDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,7] = GRxWT.FOE = GRxWT.FOE3[row.names(all.cpmdata),'FDR']
-
-all.TKT.EdgeR[,8] = GRM.CxDf = GR.M.CxDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,9] = GRM.CxOE = GR.M.CxOE3[row.names(all.cpmdata),'FDR']
-
-all.TKT.EdgeR[,10] = WTM.CxDf = WT.M.CxDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,11] = WTM.CxOE = WT.M.CxOE3[row.names(all.cpmdata),'FDR']
-
-all.TKT.EdgeR[,12] = GRxWT.MC = GRxWT.M3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,13] = GRxWT.MDf = GRxWT.MDf3[row.names(all.cpmdata),'FDR']
-all.TKT.EdgeR[,14] = GRxWT.MOE = GRxWT.MOE3[row.names(all.cpmdata),'FDR']
-
-##write.csv(all.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
-##write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
-##write.csv(all.TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
 
@@
 
+```{r echo = F, include = F}
+###Generating new CPM, FDR and FC tables with males and females processed seperately
+
+combined.cpmdata = matrix(0, ncol = ncol(cpmdata2), nrow = nrow(cpmdata2))
+colnames(combined.cpmdata) = colnames(cpmdata2)
+row.names(combined.cpmdata) = row.names(cpmdata2)
+
+combined.cpmdata[row.names(cpmdata3), colnames(cpmdata3)] = cpmdata3
+combined.cpmdata[row.names(cpmdata4), colnames(cpmdata4)] = cpmdata4
+
+combined.FDR = matrix(0, ncol = 14, nrow = nrow(combined.cpmdata))
+row.names(combined.FDR) = row.names(combined.cpmdata)
+
+colnames(combined.FDR) = c('GRF.CxDf', 'GRF.CxOE', 
+                           'WTF.CxDf', 'WTF.CxOE', 
+                           'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
+                           'GRM.CxDf', 'GRM.CxOE', 
+                           'WTM.CxDf', 'WTM.CxOE', 
+                           'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')
+
+combined.FDR[row.names(GR.F.CxDf3), 1] = GR.F.CxDf3[,'FDR']
+combined.FDR[row.names(GR.F.CxOE3), 2] = GR.F.CxOE3[,'FDR']
+
+combined.FDR[row.names(WT.F.CxDf3), 3] = WT.F.CxDf3[,'FDR']
+combined.FDR[row.names(WT.F.CxOE3), 4] = WT.F.CxOE3[,'FDR']
+
+combined.FDR[row.names(GRxWT.F3), 5] = GRxWT.F3[,'FDR']
+combined.FDR[row.names(GRxWT.FDf3), 6] = GRxWT.FDf3[,'FDR']
+combined.FDR[row.names(GRxWT.FOE3), 7] = GRxWT.FOE3[,'FDR']
+
+combined.FDR[row.names(GR.M.CxDf3), 8] = GR.M.CxDf3[,'FDR']
+combined.FDR[row.names(GR.M.CxOE3), 9] = GR.M.CxOE3[,'FDR']
+
+combined.FDR[row.names(WT.M.CxDf3), 10] = WT.M.CxDf3[,'FDR']
+combined.FDR[row.names(WT.M.CxOE3), 11] = WT.M.CxOE3[,'FDR']
+
+combined.FDR[row.names(GRxWT.M3), 12] = GRxWT.M3[,'FDR']
+combined.FDR[row.names(GRxWT.MDf3), 13] = GRxWT.MDf3[,'FDR']
+combined.FDR[row.names(GRxWT.MOE3), 14] = GRxWT.MOE3[,'FDR']
+
+combined.FC = matrix(0, ncol = 14, nrow = nrow(combined.cpmdata))
+row.names(combined.FC) = row.names(combined.cpmdata)
+
+colnames(combined.FC) = c('GRF.CxDf', 'GRF.CxOE', 
+                          'WTF.CxDf', 'WTF.CxOE', 
+                          'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
+                          'GRM.CxDf', 'GRM.CxOE', 
+                          'WTM.CxDf', 'WTM.CxOE', 
+                          'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')
+
+combined.FC[row.names(GR.F.CxDf3), 1] = GR.F.CxDf3[,'logFC']
+combined.FC[row.names(GR.F.CxOE3), 2] = GR.F.CxOE3[,'logFC']
+
+combined.FC[row.names(WT.F.CxDf3), 3] = WT.F.CxDf3[,'logFC']
+combined.FC[row.names(WT.F.CxOE3), 4] = WT.F.CxOE3[,'logFC']
+
+combined.FC[row.names(GRxWT.F3), 5] = GRxWT.F3[,'logFC']
+combined.FC[row.names(GRxWT.FDf3), 6] = GRxWT.FDf3[,'logFC']
+combined.FC[row.names(GRxWT.FOE3), 7] = GRxWT.FOE3[,'logFC']
+
+combined.FC[row.names(GR.M.CxDf3), 8] = GR.M.CxDf3[,'logFC']
+combined.FC[row.names(GR.M.CxOE3), 9] = GR.M.CxOE3[,'logFC']
+
+combined.FC[row.names(WT.M.CxDf3), 10] = WT.M.CxDf3[,'logFC']
+combined.FC[row.names(WT.M.CxOE3), 11] = WT.M.CxOE3[,'logFC']
+
+combined.FC[row.names(GRxWT.M3), 12] = GRxWT.M3[,'logFC']
+combined.FC[row.names(GRxWT.MDf3), 13] = GRxWT.MDf3[,'logFC']
+combined.FC[row.names(GRxWT.MOE3), 14] = GRxWT.MOE3[,'logFC']
+
+##write.csv(combined.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
+##write.csv(combined.FDR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv")
+##write.csv(combined.FC, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv")
+
+```
+
 <br /><br /><br /><br /><br /><br />

### 2023-07-26 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
update

@@
 groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv"),row.names = 1)
+TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
+
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
@@
 
-Enrichment = function(sigs){
-  genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
+##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
+mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
+colnames(mean.cpm) = unique(groups$Group)
+row.names(mean.cpm) = row.names(cpmdata)
+i=1
+while(i<=ncol(mean.cpm)){
+  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
+  i=i+1
+}
+
+i=1
+for(i in 1:ncol(TKT.EdgeR)){
+  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
+  i=i+1
+}
+
+```
+
+##GO and KEGG Enrichment function
+
+```{r echo = F, include = F}
+
+Enrichment = function(sigs, bg){
+  genes = setNames(rep(0, length(bg)), bg)
   genes[sigs] = 1
@@
 
-comparison1 = "GRxWT.FC"
-comparison2 = "GRxWT.MC"
+##GR vs WT Females
 
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
+sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
+bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]
 
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]
+sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
+bg2 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]
 
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "WT.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-##sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRF.CxDf"]<=.05]
+sigs = intersect(sigs1, sigs2)
+bg = unique(c(bg1, bg2))
 
 sigsKEY = GeneIDKey[sigs,]
+sigs = sigsKEY$Symbol
+bgKEY = GeneIDKey[bg,]
+bg = bgKEY$Symbol
 
-sigs = sigsKEY$Symbol
-
-sig.cats = Enrichment(sigs)
+sig.cats = Enrichment(sigs, bg)
 

### 2023-08-07 DeficiencyScreen/GO_Analysis.Rmd
updated GO

@@
 
-GO.data = Repress.GO
+GO.data = Enhancer.GO
 GO.ontology = "BP"
+GOBP.fig = GO20(GO.data, GO.ontology)
 
-GO.fig = GO20(GO.data, GO.ontology)
+GO.ontology = "CC"
+GOCC.fig = GO20(GO.data, GO.ontology)
+
+GO.ontology = "MF"
+GOMF.fig = GO20(GO.data, GO.ontology)
 
@@
 
-GO.fig
+GOBP.fig
+
+```
+
+```{r, fig.width= 10}
+
+GOCC.fig
+
+```
+
+```{r, fig.width= 10}
+
+GOMF.fig
 
@@
 ```{r include=F, echo=F}
+
+GO.data = Enhancer.GO
+GO.ontology = "BP"
 
@@
             main = "Repressor Gene Enriched Biological Process GO terms")
+
+```
+
+```{r}
+
+scatterPlot(simMatrix, reducedTerms)
 
@@
 ```
+
+```{r}
+
+go2gene = setNames(list(as.character(genesingo[[1]])), names(genesingo)[1])
+i=2
+while(i<=length(genesingo)){
+  temp = setNames(list(as.character(genesingo[[i]])), names(genesingo)[i])
+  go2gene = c(go2gene, temp)
+  i=i+1
+}
+
+```

### 2023-08-07 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
updated GO

---
title: "Defficiency Screen Functional Analysis"
author: "John Santiago"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r echo = F, include=F}
##Load Libraries

library(org.Dm.eg.db)
##library(goseq)
library(rrvgo)
library(plotly)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
##kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
##kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

Moderate.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv"), row.names = 1)
Strong.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongGOAnalysis.csv"), row.names = 1)
Repress.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv"), row.names = 1)
Lethal.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalGOAnalysis.csv"), row.names = 1)
Enhancer.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv"), row.names = 1)

genesingo=as.list(org.Dm.egGO2ALLEGS)

```

```{r echo = F}

sigGO = Repress.GO[Repress.GO$adjp<=.05,]
sigGO = sigGO[order(sigGO$ontology),]
sigGO = sigGO[row.names(sigGO)!="GO:0032991",]

sigGO = sigGO[, c("category", "term","adjp", "numDEInCat", "numInCat", "ontology")]

sigGO$notInCat = sigGO$numInCat - sigGO$numDEInCat

data = sigGO[nrow(sigGO):1,c("term","adjp","numDEInCat", "numInCat", "category", "ontology", "notInCat")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 10
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Suppressor",
               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0, xpad = 10),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3)))

fig2 <- fig %>% add_trace(fig, data, x = ~notInCat, y = ~term,
                       type = 'bar',
                       name = "Total",
                       ##colors = rep("lightgrey", nrow(data)),
                       marker = list(color = "lightgrey",line = list(color = "black", width = 1.5), colorbar = F),
               hoverinfo = "text",
               hovertext = "")

fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Suppressor Enriched GO Terms",
           margin = m,
           barmode = 'stack',
           shapes = list(
                         list(type = "rect",
                              fillcolor = "coral", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = -.5, y1 = 15.5, yref = "y",
                              layer = "below"),
                         list(type = "rect",
                              fillcolor = "lightblue", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 15.5, y1 = 22.5, yref = "y"),
                         list(type = "rect",
                              fillcolor = "lightgreen", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 22.5, y1 = 35.5, yref = "y")
                         ))

fig4 <- fig3 %>% add_annotations(x = -17.5,
                        y = 7.5,
                        text = "Molecular Function",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

fig5 <- fig4 %>% add_annotations(x = -17.5,
                        y = 19,
                        text = "Cellular Component",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

fig6 <- fig5 %>% add_annotations(x = -17.5,
                        y = 29,
                        text = "Biological Process",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))
```

```{r fig.height=12, fig.width=15, fig.align='left'}

fig6

```

```{r echo = F}

sigGO = Enhancer.GO[Enhancer.GO$adjp<=.05,]
sigGO = sigGO[order(sigGO$ontology),]
##sigGO = sigGO[row.names(sigGO)!="GO:0032991",]

sigGO = sigGO[, c("category", "term","adjp", "numDEInCat", "numInCat", "ontology")]

sigGO$notInCat = sigGO$numInCat - sigGO$numDEInCat

data = sigGO[nrow(sigGO):1,c("term","adjp","numDEInCat", "numInCat", "category", "ontology", "notInCat")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 10
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Enhancer",
               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3)))

fig2 <- fig %>% add_trace(fig, data, x = ~notInCat, y = ~term,
                       type = 'bar',
                       name = "Total",
                       marker = list(color = "lightgrey",line = list(color = "black", width = 1.5), colorbar = F),
               hoverinfo = "text",
               hovertext = "")

fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Enhancer Enriched GO Terms",
           margin = m,
           barmode = 'stack',
           shapes = list(
                         list(type = "rect",
                              fillcolor = "coral", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -10, x1 = -2.5, xref = "x",
                              y0 = -.5, y1 = 2.5, yref = "y",
                              layer = "below"),
                         list(type = "rect",
                              fillcolor = "lightblue", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -10, x1 = -2.5, xref = "x",
                              y0 = 2.5, y1 = 5.5, yref = "y"),
                         list(type = "rect",
                              fillcolor = "lightgreen", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -10, x1 = -2.5, xref = "x",
                              y0 = 5.5, y1 = 9.5, yref = "y")
                         ))

fig4 <- fig3 %>% add_annotations(x = -6.5,
                        y = 1,
                        text = "Molecular Function",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

fig5 <- fig4 %>% add_annotations(x = -6.5,
                        y = 4,
                        text = "Cellular Component",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

fig6 <- fig5 %>% add_annotations(x = -6.5,
                        y = 7.5,
                        text = "Biological Process",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

```

```{r fig.height=8, fig.width=15, fig.align='left'}

fig6

```

```{r echo=F, include=F}

GO.data = Enhancer.GO
GO.ontology = "BP"

go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

Sup.BP.SM = simMatrix
Sup.BP.RT = reducedTerms

GO.ontology = "CC"

go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

Sup.CC.SM = simMatrix
Sup.CC.RT = reducedTerms

GO.ontology = "MF"

go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

Sup.MF.SM = simMatrix
Sup.MF.RT = reducedTerms

```

### 2023-08-07 GeneralDataFiles/GenesInGOTerms.Rmd
updated GO

@@
 
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
+unknown = setdiff(row.names(Df.data),row.names(GeneIDKey))
+
+FBgn2ensembl = (unknown)
+names(FBgn2ensembl) = (unknown)
+tempEG = unlist(x1[lengths(x1)==1][(unknown)])
+FBgn2ensembl[names(tempEG)]=tempEG
+
+ensembl2symbol = (unknown)
+names(ensembl2symbol) = FBgn2ensembl
+tempSymbol = unlist(x2[FBgn2ensembl])
+ensembl2symbol[names(tempSymbol)]=tempSymbol
+symbol2ensembl = names(ensembl2symbol)
+names(symbol2ensembl) = ensembl2symbol
+
+unknowns.forFlybase = symbol2ensembl[grep("FBgn", names(symbol2ensembl))]
+unknown.key = read.csv("/Users/johncsantiago/Documents/CamiExtraGenes.csv", header = F, row.names = 1)
+
+KEY2 = data.frame(FBgn = unknown, Symbol = ensembl2symbol, ensembl = FBgn2ensembl)
+row.names(KEY2) = unknown
+KEY2[row.names(unknown.key),"Symbol"]= unknown.key[,1]
+
+unknown.sym2ens = unlist(x3[KEY2[grep("FBgn",KEY2$ensembl),"Symbol"]])
+
+unknown.KEY2 = KEY2[grep("FBgn",KEY2$ensembl),]
+
+unknown.KEY2[unknown.KEY2$Symbol %in% names(unknown.sym2ens), "ensembl"] = unknown.sym2ens
+
+KEY2[row.names(unknown.KEY2), "ensembl"] = unknown.KEY2$ensembl
+
+KEY2$CG = row.names(KEY2)
+
+x=as.list(org.Dm.egFLYBASECG)
+
+temp = (x[KEY2$ensembl])
+
+temp2 = unlist(temp[lengths(temp)==1])
+
+KEY2[KEY2$ensembl %in% names(temp2), "CG"] = temp2
+
+KEY = rbind(GeneIDKey, KEY2)
+
+write.csv(KEY, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv")
+
 ccpar=as.list(GOCCPARENTS)

### 2023-08-07 Metabolomics/MetaboanalystRCode.Rmd
updated GO

@@
 
+rm(mSet)
+
 mSet<-InitDataObjects("pktable", "stat", FALSE)
@@
 
+##Normalization just takes the value, divides by TIC and multiply by 1000
 mSet<-Normalization(mSet, "CompNorm", "NULL", "NULL", "TIC", ratio=FALSE, ratioNum=20)
@@
 ##mSet<-PlotSampleNormSummary(mSet, "snorm_1_", "png", 72, width=NA)
+
+##FC.Anal takes the mean for the group and divides by the mean from the other group
 mSet<-FC.Anal(mSet, 2.0, 0, FALSE)
@@
 
-mSet$analSet$fc
+mSet<-Ttests.Anal(mSet, F, .05, F, T, "fdr", F)
+
+##can use t.test(x= cond1 ,y = cond2, paired = F, var.equal = T) to get the t and p values
+tempt = function(data){
+  p = t.test(data[1:4], data[5:8], paired = F, var.equal = T)
+  return(p[[3]])
+}
+temp = apply(tempdata, 2, tempt)
+tempfdr = p.adjust(temp, "BH", length(temp))
+
 ```
+
+```{r}
+
+rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
+
+KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
+
+genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))
+
+metadata = data.frame(Sample = colnames(rawdata), 
+                      Group = as.character(rawdata[1,]), 
+                      TIC = as.numeric(rawdata[2,]), 
+                      Genotypes = genotypes[as.character(rawdata[1,])])
+
+norm.func = function(data){
+  nd = (as.numeric(data)/metadata$TIC)*1000
+  return(nd)
+}
+
+norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
+colnames(norm.data) = colnames(rawdata)
+
+group.mean=function(data){
+  gm = mean(na.omit(data))
+}
+
+mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
+row.names(mean.data) = row.names(norm.data)
+colnames(mean.data) = unique(metadata$Group)
+
+i=1
+while(i<=ncol(mean.data)){
+  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
+  i = i+1
+}
+
+compare.conditions = function(condition1, condition2){
+  columns1 = metadata[metadata$Group == condition1, "Sample"]
+  columns2 = metadata[metadata$Group == condition2, "Sample"]
+  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
+  i=1
+  while(i<=length(p)){
+    if(length(na.omit(norm.data[i,columns1]))>2 & 
+       length(na.omit(norm.data[i,columns2]))>2){
+      temp = t.test(na.omit(norm.data[i,columns1]),
+                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
+      p[i] = temp[[3]]
+      }
+    i=i+1
+    }
+
+  fdr = p.adjust(p, "BH", length(p))
+
+  fc = mean.data[,condition1]/mean.data[,condition2]
+
+  comparison.table = data.frame(p = p, 
+                                FDR = fdr, 
+                                FC = fc, 
+                                KEGG = KEGG.Key[row.names(mean.data)])
+
+  comparison.table = comparison.table[order(comparison.table$FDR),]
+}
+
+GRxWT.C = compare.conditions("E", "C")
+GRxWT.Df = compare.conditions("D", "B")
+GRxWT.OE = compare.conditions("F", "A")
+
+KEGGID = na.omit(GRxWT.C[GRxWT.C$FDR<=.1, "KEGG"])
+KEGGID.C = KEGGID[-grep(" / ", KEGGID)]
+
+KEGGID = na.omit(GRxWT.Df[GRxWT.Df$FDR<=.1, "KEGG"])
+KEGGID.Df = KEGGID[-grep(" / ", KEGGID)]
+
+KEGGID = na.omit(GRxWT.OE[GRxWT.OE$FDR<=.1, "KEGG"])
+KEGGID.OE = KEGGID[-grep(" / ", KEGGID)]
+
+```
+
+```{r echo = F}
+KEGGID = KEGGID.Df
+
+rm(mSet)
+mSet<-InitDataObjects("conc", "pathora", FALSE)
+cmpd.vec<-KEGGID
+mSet<-Setup.MapData(mSet, cmpd.vec)
+mSet<-CrossReferencing(mSet, "kegg")
+mSet<-CreateMappingResultTable(mSet)
+mSet<-SetKEGG.PathLib(mSet, "dme", "current")
+mSet<-SetMetabolomeFilter(mSet, F)
+mSet<-CalculateOraScore(mSet, "rbc", "hyperg")
+
+##pathway plot data
+ppd = mSet$api$ora.results
+colnames(ppd)[4:5] = c("p","neg.log.p")
+
+ppd = as.data.frame(ppd)
+ppd$Pathway = row.names(ppd)    
+ppd$Pathway = factor(ppd$Pathway, levels= unique(ppd$Pathway))
+ppd$Size = 5*log(100*ppd$Impact +1)+10
+
+col.gradient=colorRampPalette(c("white", "yellow","red", "red3"), space = "Lab", bias = 3)
+
+  fig  = plot_ly(data = ppd, 
+                 x = ~Impact, 
+                 y = ~neg.log.p,
+                 name = ~Pathway,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = F,
+                 color = ~neg.log.p,
+                 colors = col.gradient(nrow(ppd)),
+                 marker = list(size = as.numeric(ppd$Size), opacity = 0.75, line = list(color = "black", width = 1)),
+                 hoverinfo = "text",
+                 hovertext = paste("Pathway:", ppd$Pathway, 
+                                   "\nHits: ", ppd$Hits, 
+                                   "\nTotal in Cat.: ", ppd$Total, 
+                                   "\nFDR: ", ppd$FDR)) %>%
+    hide_colorbar()
+
+fig
+```
+
+```{r}
+
+```

### 2023-08-07 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
updated GO

@@
 ```{r include = F, echo = F}
+
 ParentID = "GO:0044271"

### 2023-08-22 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
deficiency mapper app

@@
 
+```{r echo=F, include=F}
+
+GO.data = Repress.GO
+GO.ontology = "BP"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Sup.BP.SM = simMatrix
+Sup.BP.RT = reducedTerms
+Sup.BP.RT$Freq = 1
+i=1
+while(i<=nrow(Sup.BP.RT)){
+  Sup.BP.RT$Freq[i] =  sum(Sup.BP.RT$parentTerm == Sup.BP.RT$parentTerm[i])
+  i=i+1
+}
+Sup.BP.RT = Sup.BP.RT[order(Sup.BP.RT$Freq, decreasing = T),]
+
+GO.ontology = "CC"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Sup.CC.SM = simMatrix
+Sup.CC.RT = reducedTerms
+Sup.CC.RT$Freq = 1
+i=1
+while(i<=nrow(Sup.CC.RT)){
+  Sup.CC.RT$Freq[i] =  sum(Sup.CC.RT$parentTerm == Sup.CC.RT$parentTerm[i])
+  i=i+1
+}
+Sup.CC.RT = Sup.CC.RT[order(Sup.CC.RT$Freq, decreasing = T),]
+
+GO.ontology = "MF"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Sup.MF.SM = simMatrix
+Sup.MF.RT = reducedTerms
+Sup.MF.RT$Freq = 1
+i=1
+while(i<=nrow(Sup.MF.RT)){
+  Sup.MF.RT$Freq[i] =  sum(Sup.MF.RT$parentTerm == Sup.MF.RT$parentTerm[i])
+  i=i+1
+}
+Sup.MF.RT = Sup.MF.RT[order(Sup.MF.RT$Freq, decreasing = T),]
+
+```
+
 ```{r echo = F}
 
-sigGO = Repress.GO[Repress.GO$adjp<=.05,]
-sigGO = sigGO[order(sigGO$ontology),]
+sigGO = Repress.GO[c(row.names(Sup.BP.RT), 
+                     row.names(Sup.CC.RT), 
+                     row.names(Sup.MF.RT)), ]
 sigGO = sigGO[row.names(sigGO)!="GO:0032991",]
@@
 m <- list(
-  l = 50,
+  l = 100,
   r = 50,
@@
                type = 'bar',
-               name = "Suppressor",
+               name = "Candidate Suppressor Genes",
                marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
@@
                        type = 'bar',
-                       name = "Total",
+                       name = "Total Genes",
                        ##colors = rep("lightgrey", nrow(data)),
@@
                          list(type = "rect",
-                              fillcolor = "coral", 
+                              fillcolor = "white", 
                               line = list(color = "black", width = 2.5), 
@@
                          list(type = "rect",
-                              fillcolor = "lightblue", 
+                              fillcolor = "white", 
                               line = list(color = "black", width = 2.5), 
@@
                          list(type = "rect",
-                              fillcolor = "lightgreen", 
+                              fillcolor = "white", 
                               line = list(color = "black", width = 2.5), 
@@
                               x0 = -30, x1 = -5, xref = "x",
-                              y0 = 22.5, y1 = 35.5, yref = "y")
+                              y0 = 22.5, y1 = 34.5, yref = "y")
                          ))
@@
                         font = list(size = 15))
+
 ```
@@
 
-```{r echo = F}
+```{r}
 
-sigGO = Enhancer.GO[Enhancer.GO$adjp<=.05,]
-sigGO = sigGO[order(sigGO$ontology),]
-##sigGO = sigGO[row.names(sigGO)!="GO:0032991",]
-
-sigGO = sigGO[, c("category", "term","adjp", "numDEInCat", "numInCat", "ontology")]
-
-sigGO$notInCat = sigGO$numInCat - sigGO$numDEInCat
-
-data = sigGO[nrow(sigGO):1,c("term","adjp","numDEInCat", "numInCat", "category", "ontology", "notInCat")]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 10
-)
-
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "Enhancer",
-               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$term,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3)))
-
-fig2 <- fig %>% add_trace(fig, data, x = ~notInCat, y = ~term,
-                       type = 'bar',
-                       name = "Total",
-                       marker = list(color = "lightgrey",line = list(color = "black", width = 1.5), colorbar = F),
-               hoverinfo = "text",
-               hovertext = "")
-
-fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Enhancer Enriched GO Terms",
-           margin = m,
-           barmode = 'stack',
-           shapes = list(
-                         list(type = "rect",
-                              fillcolor = "coral", 
-                              line = list(color = "black", width = 2.5), 
-                              opacity = 1,
-                              x0 = -10, x1 = -2.5, xref = "x",
-                              y0 = -.5, y1 = 2.5, yref = "y",
-                              layer = "below"),
-                         list(type = "rect",
-                              fillcolor = "lightblue", 
-                              line = list(color = "black", width = 2.5), 
-                              opacity = 1,
-                              x0 = -10, x1 = -2.5, xref = "x",
-                              y0 = 2.5, y1 = 5.5, yref = "y"),
-                         list(type = "rect",
-                              fillcolor = "lightgreen", 
-                              line = list(color = "black", width = 2.5), 
-                              opacity = 1,
-                              x0 = -10, x1 = -2.5, xref = "x",
-                              y0 = 5.5, y1 = 9.5, yref = "y")
-                         ))
-
-fig4 <- fig3 %>% add_annotations(x = -6.5,
-                        y = 1,
-                        text = "Molecular Function",
-                        showarrow = F,
-                        textangle = -90,
-                        font = list(size = 15))
-
-fig5 <- fig4 %>% add_annotations(x = -6.5,
-                        y = 4,
-                        text = "Cellular Component",
-                        showarrow = F,
-                        textangle = -90,
-                        font = list(size = 15))
-
-fig6 <- fig5 %>% add_annotations(x = -6.5,
-                        y = 7.5,
-                        text = "Biological Process",
-                        showarrow = F,
-                        textangle = -90,
-                        font = list(size = 15))
-
-```
-
-```{r fig.height=8, fig.width=15, fig.align='left'}
-
-fig6
+color.function <- colorRampPalette( c( "steelblue" , "gold", "brown" ) )
+order = c(1:17, NA, 18:23, NA, 24:35)
+par(mar = c(3,12,1,3))
+barplot(height = data$numInCat[order],
+        names.arg = data$term[order],
+        horiz = T, 
+        cex.names = .5,
+        xlim = c(0,900),
+        axes =F)
+barplot(height = data$numDEInCat[order],
+        names.arg = "",
+        add = T,
+        horiz = T,
+        col = "gold",
+        xlim = c(0,900),
+        axes = F)
+axis(1, seq(0, 1000, by=100), labels=T, las = 2, cex.axis = .5)
+axis(1, seq(0, 1000, by=25), labels=FALSE, tck=-.01)
 
@@
 
-Sup.BP.SM = simMatrix
-Sup.BP.RT = reducedTerms
+Enh.BP.SM = simMatrix
+Enh.BP.RT = reducedTerms
+
+Enh.BP.RT$Freq = 1
+i=1
+while(i<=nrow(Enh.BP.RT)){
+  Enh.BP.RT$Freq[i] =  sum(Enh.BP.RT$parentTerm == Enh.BP.RT$parentTerm[i])
+  i=i+1
+}
+Enh.BP.RT = Enh.BP.RT[order(Enh.BP.RT$Freq, decreasing = T),]
 
@@
 
-Sup.CC.SM = simMatrix
-Sup.CC.RT = reducedTerms
+Enh.CC.SM = simMatrix
+Enh.CC.RT = reducedTerms
+
+Enh.CC.RT$Freq = 1
+i=1
+while(i<=nrow(Enh.CC.RT)){
+  Enh.CC.RT$Freq[i] =  sum(Enh.CC.RT$parentTerm == Enh.CC.RT$parentTerm[i])
+  i=i+1
+}
+Enh.CC.RT = Enh.CC.RT[order(Enh.CC.RT$Freq, decreasing = T),]
 
@@
 
-Sup.MF.SM = simMatrix
-Sup.MF.RT = reducedTerms
+Enh.MF.SM = simMatrix
+Enh.MF.RT = reducedTerms
+
+Enh.MF.RT$Freq = 1
+i=1
+while(i<=nrow(Enh.MF.RT)){
+  Enh.MF.RT$Freq[i] =  sum(Enh.MF.RT$parentTerm == Enh.MF.RT$parentTerm[i])
+  i=i+1
+}
+Enh.MF.RT = Enh.MF.RT[order(Enh.MF.RT$Freq, decreasing = T),]
 
 ```
+
+```{r echo = F}
+
+sigGO = Enhance.GO[c(row.names(Enh.BP.RT), 
+                     row.names(Enh.CC.RT), 
+                     row.names(Enh.MF.RT)), ]
+
+sigGO = sigGO[, c("category", "term","adjp", "numDEInCat", "numInCat", "ontology")]
+
+sigGO$notInCat = sigGO$numInCat - sigGO$numDEInCat
+
+data = sigGO[nrow(sigGO):1,c("term","adjp","numDEInCat", "numInCat", "category", "ontology", "notInCat")]
+data$Score = -log10(data$adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+
+m <- list(
+  l = 50,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 10
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "Candidate Enhancer Genes",
+               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$term,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3)))
+
+fig2 <- fig %>% add_trace(fig, data, x = ~notInCat, y = ~term,
+                       type = 'bar',
+                       name = "Total Genes",
+                       marker = list(color = "lightgrey",line = list(color = "black", width = 1.5), colorbar = F),
+               hoverinfo = "text",
+               hovertext = "")
+
+fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Enhancer Enriched GO Terms",
+           margin = m,
+           barmode = 'stack',
+           shapes = list(
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -10, x1 = -2.5, xref = "x",
+                              y0 = -.5, y1 = 2.5, yref = "y",
+                              layer = "below"),
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -10, x1 = -2.5, xref = "x",
+                              y0 = 2.5, y1 = 5.5, yref = "y"),
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -10, x1 = -2.5, xref = "x",
+                              y0 = 5.5, y1 = 9.5, yref = "y")
+                         ))
+
+fig4 <- fig3 %>% add_annotations(x = -6.5,
+                        y = 1,
+                        text = "Molecular Function",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 12))
+
+fig5 <- fig4 %>% add_annotations(x = -6.5,
+                        y = 4,
+                        text = "Cellular Component",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 12))
+
+fig6 <- fig5 %>% add_annotations(x = -6.5,
+                        y = 7.5,
+                        text = "Biological Process",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 12))
+
+```
+
+```{r fig.height=8, fig.width=15, fig.align='left'}
+
+fig6
+
+```

### 2023-08-22 DeficiencyScreen/DeficiencyMapViewer/app.R

@@ -1,0 +1,423 @@
+library(shiny)
+library(plotly)
+
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.names = 1)
+row.names(DfKey) = DfKey$Deficiency
+DfKey[DfKey$MLE == 0, "MLE"] = .05
+GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+
+fbID = data.frame(FBgn = c(rep(GeneIDKey$FBgn, 2)),
+                  Symbol = c(rep(GeneIDKey$Symbol, 2)),
+                  Position = c(GeneIDKey$Start, GeneIDKey$End))
+
+plot.pos = function(chr, start, end){
+  goi = data.frame(Start = start,
+                   End = end,
+                   CHR = chr)
+  range.min = start
+  range.max = end
+  
+  ##genes in range
+  gir = na.omit(GeneIDKey[(GeneIDKey$CHR == goi$CHR),])
+  gir = na.omit(gir[(((gir$Start >= range.min) & (gir$Start <= range.max)) | 
+                       ((gir$End >= range.min) & (gir$End <= range.max)) |
+                       ((gir$End >= range.max) & (gir$Start <= range.min))), ])
+  gir$x1 = gir$Start
+  gir$x2 = gir$End
+  
+  Dfir = na.omit(DfKey[DfKey$Chr == goi$CHR,])
+  Dfir = na.omit(Dfir[(((Dfir$Start >= range.min) & (Dfir$Start <= range.max)) | 
+                         ((Dfir$End >= range.min) & (Dfir$End <= range.max)) |
+                         ((Dfir$End >= range.max) & (Dfir$Start <= range.min))), ])
+  Dfir$x1 = Dfir$Start
+  Dfir$x2 = Dfir$End
+  
+  line.data = gir
+  if(min(line.data$Start) < range.min){
+    line.data$x2[line.data$Start < range.min] = range.min
+  }
+  
+  if(max(line.data$End) > range.max){
+    line.data$x2[line.data$End > range.max] = range.max
+  }
+  
+  bar.data = Dfir
+  if(min(bar.data$Start) < range.min){
+    bar.data$x1[bar.data$Start < range.min] = range.min
+  }
+  
[…]

### 2023-08-22 DeficiencyScreen/DeficiencyMappingFunction.R

@@ -1,0 +1,596 @@
+##library(org.Dm.eg.db)
+
+##gene.start = abs(unlist(as.list(org.Dm.egCHRLOC)))
+##gene.end   = abs(unlist(as.list(org.Dm.egCHRLOCEND)))
+
+##gene.dir = unlist(as.list(org.Dm.egCHRLOC))/abs(unlist(as.list(org.Dm.egCHRLOC)))
+
+##gene.info = data.frame(Start = gene.start, End = gene.end, Strand = gene.dir, CHR = "", Name = "")
+
+##i = 1
+##while(i<=length(gene.start)){
+  ##temp = strsplit(names(gene.start)[i], "\\.")
+  ##gene.info[i, c("Name", "CHR")] = temp[[1]]
+  ##i = i + 1
+##}
+
+##i = 1
+##while(i<=length(unique(gene.info$Name))){
+  ##gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"Start"] =
+  ##min(gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"Start"])
+  ##gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"End"] =
+  ##  max(gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"End"])
+  ##if(length(unique(gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"Strand"])) == 2){
+  ##  gene.info[gene.info$Name %in% unique(gene.info$Name)[i],"Strand"] = 0
+  ##}
+  ##i = i + 1
+##}
+
+##gene.info = unique(gene.info)
+
+##use.genes = setdiff(unique(gene.info$Name), gene.info[duplicated(gene.info$Name),"Name"])
+##gene.info = gene.info[gene.info$Name %in% use.genes, ]
+##row.names(gene.info) = gene.info$Name
+##git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+##GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+##gene.info = gene.info[GeneIDKey$ensembl,]
+##row.names(gene.info) = row.names(GeneIDKey)
+##GeneIDKey = cbind(GeneIDKey, gene.info)
[…]

### 2023-09-13 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
update

@@
 ##GO and KEGG Enrichment function
-
 ```{r echo = F, include = F}
@@
 
+data$term = data$Name
+if(length(unique(data$term)) < length(data$term)){
+  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
+}  
 data = data[20:1,]
 data$Score = -log10(data$adjp)
-data$term = factor(data$Name, levels = c(unique(data$Name)))
+data$term = factor(data$term, levels = c(unique(data$term)))
 
@@
 ##GR vs WT Females
-
 sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
@@
 
-```{r include = F, echo = F}
+```{r}
 
-GOID = "GO:0005634"
-GenesInGO = genesingo[GOID]
+##GR.F vs WT.F specific volcano
 
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]
+specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')
 
-```
+specific.cat = specific.cat[2]
+parent.category = 'neurogenesis'
+specific.kegg = "DNA replication"
+specific.go =  '32553'
 
-```{r include = F, echo = F}
+set.size = F
 
-ParentID = "GO:0044271"
-GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
-GOID = GOIDs[1]
-GenesInParent= unique(genesingo[[GOID]])
-i=2
-while(i<=length(GOIDs)){
-  GOID = GOIDs[i]
-  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
-  i=i+1
+GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
+names(GOterm.genes) = unique(reducedTerms$parent)
+i=1
+while(i<=length(GOterm.genes)){
+  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
+  genesinparent = unlist(genesingo[goinparent])
+  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
+  i = i +1
 }
 
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]
+volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
+                          FDR = -log2(TKT.EdgeR[, 'GRxWT.FC']),
+                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.FC'],
+                          ##Color = 0)
+                          Color = 'grey',
+                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.F"]),
+                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.F"],
+                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.F"],
+                          GO.terms = "none")
 
-```
+main.title = "Significant DEG in G85R Females vs. WT Females"
 
-```{r echo =F, warnings = F}
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
 
-comparison = "GRxWT.FC"
-comparison2 = "GRxWT.MC"
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
 
-hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]
+volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
 
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
+if(set.size == T){
+  volcano.data$size = 15
+  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
 }
 
-hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
+if(specific.cat == 'parent.category'){
+  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
+  volcano.data$Color = 'honeydew'
+  volcano.data[parent.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
 }
 
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
-
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
-
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
-
-```
-
-##############
-## GRxWT Df ##
-##############
-
-```{r echo = F, include = F}
-
-comparison1 = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-sigs = sigsKEY$Symbol
-
-sig.cats = Enrichment(sigs)
-
-```
-
-```{r echo = F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
-
-```
-
-```{r, fig.width= 10}
-
-BP.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-CC.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-MF.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-KEGG.fig
-
-```
-
-```{r echo =F, warnings = F}
-
-comparison = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-##hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]
-
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
+if(specific.cat == 'specific.kegg'){
+  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
+  kegg.genes = names(kegg[grep(kegg.id, kegg)])
+  volcano.data$Color = 'honeydew'
+  row.names(volcano.data) = volcano.data$Symbol
+    volcano.data[kegg.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
 }
 
-##hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
+if(specific.cat == 'specific.go'){
+  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
+  volcano.data$Color = 'honeydew'
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  go.genes = intersect(go.genes, row.names(volcano.data))
+  volcano.data[go.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
 }
 
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
+##volcano.data
 
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
+fig = plot_ly(data = volcano.data,
+              x = ~FC,
+              y = ~FDR,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
+                            line = list(color = 'black', width = .5)),
+              hoverinfo = "text",
+              hovertext = paste("Gene:", volcano.data$Symbol,
+                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
+                      "\nFC: ", round(volcano.data$FC,2),
+                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
+                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
+fig = fig %>% layout(title = main.title)
 
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
+              ##color = ~Color,
+              ##colors = 'Spectral')
+              ##color = ~Color,
+              ##colors = ~Color)
+              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))
 
-```
-
-##############
-## GRxWT OE ##
-##############
-
-```{r echo = F, include = F}
-
-comparison1 = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-sigs = sigsKEY$Symbol
-
-sig.cats = Enrichment(sigs)
-
-```
-
-```{r echo =F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$adjp), go_analysis)
-
-simMatrix <- calculateSimMatrix(go_analysis,
-                                orgdb="org.Dm.eg.db",
-                                ont=GO.ontology,
-                                method="Rel")
-
-reducedTerms <- reduceSimMatrix(simMatrix,
-                                scores,
-                                threshold=0.7,
-                                orgdb="org.Dm.eg.db")
-
-```
-
-```{r echo = F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
-
-```
-
-```{r, fig.width= 10}
-
-BP.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-CC.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-MF.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-KEGG.fig
-
-```
-
-```{r fig.height=7, fig.width=10}
-
-heatmapPlot(simMatrix,
-            reducedTerms,
-            annotateParent=TRUE,
-            annotationLabel="parentTerm",
-            fontsize=6,
-            main = "Repressor Gene Enriched Biological Process GO terms")
-
-```
-
-```{r warning=F, fig.width=10}
-
-use.data   = simMatrix
-GO.Sim.PCA(use.data)
-
-```
-
-```{r fig.align='left'}
-
-treemapPlot(reducedTerms)
-
-```
-
-```{r include = F, echo = F}
-
-GOID = "GO:0003723"
-GenesInGO = genesingo[GOID]
-
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]
-
-```
-
-```{r include = F, echo = F}
-ParentID = "GO:0034249"
-GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
-GOID = GOIDs[1]
-GenesInParent= unique(genesingo[[GOID]])
-i=2
-while(i<=length(GOIDs)){
-  GOID = GOIDs[i]
-  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
-  i=i+1
-}
-
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]
-
-```
-
-```{r echo =F, warnings = F}
-
-comparison = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-hmdata = cpmdata[GenesInGO, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
-
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
-}
-
-hmdata2 = cpmdata[GenesInGO, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
-}
-
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
-
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
-
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
-
-```
-
-#########################
-## Comparing the three ##
-#########################
-
-```{r include = F, echo = F}
-
-comparison1 = "GRxWT.FC"
-comparison2 = "GRxWT.MC"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "GR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-C.sigs = sigsKEY$Symbol
-
-comparison1 = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-Df.sigs = sigsKEY$Symbol
-
-comparison1 = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-OE.sigs = sigsKEY$Symbol
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="Control"
-set2="Defficient"
-set3="Over Expression"
-##set4="GSC2.Stem"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = C.sigs
-s2 = Df.sigs
-s3 = OE.sigs
-##s4=row.names(temp)[temp[,4]==1]
+fig
 
@@
 ```{r}
+specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')
 
-data = data.frame(Condition = c("Control", "Defficient", "Over Expression"), DEGs = c(length(C.sigs), length(Df.sigs), length(OE.sigs)))
+specific.cat = specific.cat[1]
+parent.category = 'chromosome organization'
+specific.kegg = "DNA replication"
+specific.go =  '006457'
 
-fig <- plot_ly(data, 
-               x = ~Condition, y = ~DEGs, 
-               type = 'bar',
-               name = ~Condition,
-               color = ~Condition,
-               colors = c("coral3","gold2", "steelblue3"),
-               marker = list(line = list(color = "black", width = 1.5)))
+set.size = F
+
+GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
+names(GOterm.genes) = unique(reducedTerms$parent)
+i=1
+while(i<=length(GOterm.genes)){
+  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
+  genesinparent = unlist(genesingo[goinparent])
+  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
+  i = i +1
+}
+
+volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
+                          FDR = -log2(TKT.EdgeR[, 'GRxWT.MC']),
+                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.MC'],
+                          ##Color = 0)
+                          Color = 'grey',
+                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.M"]),
+                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.M"],
+                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.M"],
+                          GO.terms = "none")
+
+main.title = "Significant DEG in G85R Males vs. WT Males"
+
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
+
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
+
+volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
+
+if(set.size == T){
+  volcano.data$size = 15
+  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
+}
+
+if(specific.cat == 'parent.category'){
+  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
+  volcano.data$Color = 'honeydew'
+  volcano.data[parent.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
+}
+
+if(specific.cat == 'specific.kegg'){
+  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
+  kegg.genes = names(kegg[grep(kegg.id, kegg)])
+  volcano.data$Color = 'honeydew'
+  row.names(volcano.data) = volcano.data$Symbol
+    volcano.data[kegg.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
+}
+
+if(specific.cat == 'specific.go'){
+  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
+  volcano.data$Color = 'honeydew'
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  go.genes = intersect(go.genes, row.names(volcano.data))
+  volcano.data[go.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
+}
+
+##volcano.data
+
+fig = plot_ly(data = volcano.data,
+              x = ~FC,
+              y = ~FDR,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
+                            line = list(color = 'black', width = .5)),
+              hoverinfo = "text",
+              hovertext = paste("Gene:", volcano.data$Symbol,
+                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
+                      "\nFC: ", round(volcano.data$FC,2),
+                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
+                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
+fig = fig %>% layout(title = main.title)
 
@@
 
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("brown1","gold2", "steelblue2"),cex=1.5,cat.cex = 1)
+rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
+
+KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
+
+genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))
+
+metadata = data.frame(Sample = colnames(rawdata), 
+                      Group = as.character(rawdata[1,]), 
+                      TIC = as.numeric(rawdata[2,]), 
+                      Genotypes = genotypes[as.character(rawdata[1,])])
+
+norm.func = function(data){
+  nd = (as.numeric(data)/metadata$TIC)*1000
+  return(nd)
+}
+
+norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
+colnames(norm.data) = colnames(rawdata)
+
+group.mean=function(data){
+  gm = mean(na.omit(data))
+}
+
+mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
+row.names(mean.data) = row.names(norm.data)
+colnames(mean.data) = unique(metadata$Group)
+
+i=1
+while(i<=ncol(mean.data)){
+  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
+  i = i+1
+}
+
+compare.conditions = function(condition1, condition2){
+  columns1 = metadata[metadata$Group == condition1, "Sample"]
+  columns2 = metadata[metadata$Group == condition2, "Sample"]
+  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
+  i=1
+  while(i<=length(p)){
+    if(length(na.omit(norm.data[i,columns1]))>2 & 
+       length(na.omit(norm.data[i,columns2]))>2){
+      temp = t.test(na.omit(norm.data[i,columns1]),
+                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
+      p[i] = temp[[3]]
+      }
+    i=i+1
+    }
+
+  fdr = p.adjust(p, "BH", length(p))
+
+  fc = mean.data[,condition1]/mean.data[,condition2]
+
+  comparison.table = data.frame(p = p, 
+                                FDR = fdr, 
+                                FC = fc, 
+                                KEGG = KEGG.Key[row.names(mean.data)])
+
+  comparison.table = comparison.table[order(comparison.table$FDR),]
+}
+d
+GRxWT.C = compare.conditions("E", "C")
+GRxWT.Df = compare.conditions("D", "B")
+GRxWT.OE = compare.conditions("F", "A")
 
 ```
+
+```{r}
+
+set.size == F
+volcano.data = data.frame(Symbol = row.names(GRxWT.C), 
+                          FDR = -log2(GRxWT.C$FDR),
+                          FC = log2(GRxWT.C$FC),
+                          Color = 'honeydew',
+                          size = log(mean.data[row.names(GRxWT.C),'E']),
+                          GR.Level = mean.data[row.names(GRxWT.C), "E"],
+                          WT.Level = mean.data[row.names(GRxWT.C), "C"],
+                          GO.terms = "none")
+
+main.title = "Metabolites in G85R Males vs. WT Males"
+
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
+
+volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
+volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
+volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
+
+##volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
+
+if(set.size == T){
+  volcano.data$size = 15
+  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
+}
+
+fig = plot_ly(data = volcano.data,
+              x = ~FC,
+              y = ~FDR,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
+                            line = list(color = 'black', width = .5)),
+              hoverinfo = "text",
+              hovertext = paste("Metabolite:", volcano.data$Symbol,
+                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
+                      "\nFC: ", round(volcano.data$FC,2),
+                      "\nG85R mean cpm: ", round(volcano.data$GR.Level, 1),
+                      "\nWT mean cpm: ", round(volcano.data$WT.Level, 1)))
+fig = fig %>% layout(title = main.title)
+
+fig
+
+```
+
+```{r, include = F, echo = F}
+
+if(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files"){
+  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+}
+
+Home = dirname(rstudioapi::getSourceEditorContext()$path)
+OutputDir = paste0(Home, "/KEGG_Image_Files/")
+
+ShowKEGG = function(PathwayID){
+
+download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
+xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
+node.data=node.info(xml.file)
+
+all.path = names(kegg[grep(PathwayID,kegg)])
+
+up = TKT.EdgeR.FC[TKT.EdgeR.FC$Moderate == 1, "Symbol"]
+Moderate = intersect(Moderate, all.path)
+Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")
+
+Strong = Df.data[Df.data$Strong == 1, "Symbol"]
+Strong = intersect(Strong, all.path)
+Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
+
+Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
+Enhancer = intersect(Enhancer, all.path)
+Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")
+
+Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
+Lethal = intersect(Lethal, all.path)
+Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")
+
+plot.data.gene=node.map(mol.data=c(Moderate, Strong, Enhancer, Lethal), node.data, node.types="gene")
+cols.ts.gene = node.color(plot.data.gene, limit=2, bins=2)
+cols.ts.gene[1:length(cols.ts.gene)] = 0
+
+pdg.moderate=node.map(mol.data=Moderate, node.data, node.types="gene")
+temp = node.color(pdg.moderate, limit=2, bins=2)
+ctg.moderate = cols.ts.gene
+ctg.moderate[temp!="#FFFFFF"]= 1 ##"gold2"
+
+pdg.strong=node.map(mol.data=Strong, node.data, node.types="gene")
+temp = node.color(pdg.strong, limit=2, bins=2)
+ctg.strong = cols.ts.gene
+ctg.strong[temp!="#FFFFFF"]= 1 ##"brown2"
+
+pdg.enhancer=node.map(mol.data=Enhancer, node.data, node.types="gene")
+temp = node.color(pdg.enhancer, limit=2, bins=2)
+ctg.enhancer = cols.ts.gene
+ctg.enhancer[temp!="#FFFFFF"]= 1 ##"deepskyblue"
+
+pdg.lethal=node.map(mol.data=Lethal, node.data, node.types="gene")
+temp = node.color(pdg.lethal, limit=2, bins=2)
+ctg.lethal = cols.ts.gene
+ctg.lethal[temp!="#FFFFFF"]= 1 ##"navyblue"
+
+color.combos = data.frame(Moderate = as.numeric(ctg.moderate),
+                          Strong = as.numeric(ctg.strong),
+                          Enhancer = as.numeric(ctg.enhancer),
+                          Lethal = as.numeric(ctg.lethal))
+row.names(color.combos)= names(cols.ts.gene)
+
+cols.ts.gene[cols.ts.gene=="0"]="darkseagreen1"
+
+cols.ts.gene[row.names(color.combos)[color.combos$Moderate == 1]] = "gold2"
+cols.ts.gene[row.names(color.combos)[color.combos$Strong   == 1]] = "brown1"
+cols.ts.gene[row.names(color.combos)[color.combos$Enhancer   == 1]] = "lightsteelblue"
+cols.ts.gene[row.names(color.combos)[color.combos$Lethal   == 1]] = "cornflowerblue"
+cols.ts.gene[row.names(color.combos)[(color.combos$Moderate   == 1 | color.combos$Strong   == 1) & (color.combos$Enhancer   == 1 | color.combos$Lethal   == 1) ]] = "grey60"
+
+setwd(OutputDir)
+pv.pars= keggview.native(plot.data.gene=plot.data.gene,
+                         cols.ts.gene=cols.ts.gene, 
+                         node.data=node.data,
+                         pathway.name=paste0("dme", PathwayID),
+                         same.layer=T, plot.col.key=F, out.suffix = kegg.names[paste0("dme", PathwayID),1],
+                         kegg.dir = OutputDir)
+setwd(Home)
+}
+
+```
+
+```{r echo = F, include = F}
+
+PathwayID = "04150"
+
+ShowKEGG(PathwayID)
+
+```
+
+```{r echo = F, fig.align='center'}
+
+knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
+
+```

### 2023-09-13 DeficiencyScreen/DeficiencyMapViewer/app.R

@@ -1,3 +1,6 @@
+##library(rsconnect)
+
+
 library(shiny)
 library(plotly)
 
@@ -183,12 +186,14 @@ plot.gene = function(gene.symbol, start.range, end.range){
   }
   
   bar.data = Dfir
-  if(min(bar.data$Start) < range.min){
-    bar.data$x1[bar.data$Start < range.min] = range.min
-  }
-  
-  if(max(bar.data$End) > range.max){
-    bar.data$x2[bar.data$End > range.max] = range.max
+  if(nrow(Dfir)>0){
+    if(min(bar.data$Start) < range.min){
+      bar.data$x1[bar.data$Start < range.min] = range.min
+    }
+    
+    if(max(bar.data$End) > range.max){
+      bar.data$x2[bar.data$End > range.max] = range.max
+    }
   }
   
   line.data$Strand = line.data$Strand/10
@@ -242,7 +247,9 @@ plot.gene = function(gene.symbol, start.range, end.range){
                        dfStart = NA,
                        dfEnd = NA)
   pdata = rbind(p1.data,p2.data)
-  df.line[1:nrow(pdata),] = pdata
+  if(nrow(pdata)>0){
+    df.line[1:nrow(pdata),] = pdata
+  }
   data = cbind(data,df.line)
   data$Symbol = factor(data$Symbol, levels = unique(data$Symbol))
   
@@ -284,7 +291,13 @@ plot.gene = function(gene.symbol, start.range, end.range){
   
   fig = layout(fig,
                xaxis = list(title = goi$CHR, range = c(range.min, range.max)),
-               yaxis = list(title = "Mean Lifespan Extension", range = c(-4,6)))##,
+               yaxis = list(title = "Mean Lifespan Extension", range = c(-4,6)),
+               shapes = list(
+                 type = "rect",
+                 line = list(color = "green", dash = 'dash', width = 2),
+                 x0 = data[data$Symbol == gene.symbol, "Start"][1], 
+                 x1 = data[data$Symbol == gene.symbol, "End"][1],
+                 y0 = -5, y1 = 7))##,
   ##hovermode = "x unified")
   
   return(fig)

### 2023-09-13 DeficiencyScreen/DeficiencyMappingFunction.R

@@ -99,15 +99,18 @@ plot.pos = function(chr, start, end){
     line.data$x2[line.data$End > range.max] = range.max
   }
 
+  
   bar.data = Dfir
-  if(min(bar.data$Start) < range.min){
-    bar.data$x1[bar.data$Start < range.min] = range.min
-  }
+  if(nrow(bar.data >0)){
+    if(min(bar.data$Start) < range.min){
+      bar.data$x1[bar.data$Start < range.min] = range.min
+    }
 
-  if(max(bar.data$End) > range.max){
-    bar.data$x2[bar.data$End > range.max] = range.max
+    if(max(bar.data$End) > range.max){
+      bar.data$x2[bar.data$End > range.max] = range.max
+    }
   }
-
+  
   line.data$Strand = line.data$Strand/10
   line.data = line.data[order(line.data$Start),]
   line.data = line.data[, c("Symbol", "Start", "Strand", "End", "x1", "x2")]
@@ -248,12 +251,14 @@ plot.gene = function(gene.symbol, start.range, end.range){
   }
   
   bar.data = Dfir
-  if(min(bar.data$Start) < range.min){
-    bar.data$x1[bar.data$Start < range.min] = range.min
-  }
+  if(nrow(Dfir)>0){
+    if(min(bar.data$Start) < range.min){
+      bar.data$x1[bar.data$Start < range.min] = range.min
+    }
   
-  if(max(bar.data$End) > range.max){
-    bar.data$x2[bar.data$End > range.max] = range.max
+    if(max(bar.data$End) > range.max){
+      bar.data$x2[bar.data$End > range.max] = range.max
+    }
   }
   
   line.data$Strand = line.data$Strand/10
@@ -290,6 +295,8 @@ plot.gene = function(gene.symbol, start.range, end.range){
   data$color[data$y < 0] = "blue"
   data = data[order(data$Symbol),]
   
+  data[data$Symbol == gene.symbol, 'color'] = 'green'
+  
   bar.data$color = bar.data$Modifier
   
   bar.data$color[bar.data$color == "Strong Suppressor"] = adjustcolor("brown", alpha.f = 0.3)
@@ -307,7 +314,9 @@ plot.gene = function(gene.symbol, start.range, end.range){
                        dfStart = NA,
                        dfEnd = NA)
   pdata = rbind(p1.data,p2.data)
-  df.line[1:nrow(pdata),] = pdata
[…]

### 2023-11-07 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
cami stuff

@@
 kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)
+
+Synaptic = read.csv("/Users/johncsantiago/Documents/SynapticGenesandTFs.csv")
 
@@
 
-specific.cat = specific.cat[2]
+specific.cat = specific.cat[1]
 parent.category = 'neurogenesis'
@@
 specific.go =  '32553'
+Synaptic.genes = F
 
@@
 }
+
+volcano.data$Color = 'grey'
+volcano.data$Color[volcano.data$Symbol %in% Synaptic$Symbol] = 'deeppink'
 
@@
 }
-d
+
 GRxWT.C = compare.conditions("E", "C")
@@
 
-main.title = "Metabolites in G85R Males vs. WT Males"
+main.title = "FC for metabolites in G85R vs. WT"
 
@@
 ```
-
-```{r echo = F, include = F}
-
-PathwayID = "04150"
-
-ShowKEGG(PathwayID)
-
-```
-
-```{r echo = F, fig.align='center'}
-
-knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
-
-```

### 2024-01-17 Anna qPCR data/20231116_Anna_WTG85R_IDGF6_PrimerEfficiency.Rmd
update

---
title: "Anna IDGF6 Efficiency Plate"
author: "John Santiago"
date: "2023-12-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include = F}
library(plotly)
IDGF6.data = read.csv("/Users/johncsantiago/Documents/20231116_Anna_WTG85R_IDGF6_PrimerEfficiency.csv")
IDGF6.data$Genotype = "WT"

IDGF6.data$Concentration = as.numeric(substr(IDGF6.data$Sample, 5, (nchar(IDGF6.data$Sample)-3)))

IDGF6.data$log.Conc = log2(IDGF6.data$Concentration)

IDGF6.data$SampleID = substr(IDGF6.data$Sample, 1,3)

```

```{r echo = F}

IDGF6.1 = IDGF6.data[IDGF6.data$SampleID == "WT1", c("Cq", "SampleID", "Well", 'log.Conc', 'Concentration')]
IDGF6.1$color = 'brown'
IDGF6.1 = IDGF6.1[IDGF6.1$Concentration > 0,]
IDGF6.2 = IDGF6.data[IDGF6.data$SampleID == "WT2", c("Cq", "SampleID", "Well", 'log.Conc', 'Concentration')]
IDGF6.2$color = 'steelblue'
IDGF6.2 = IDGF6.2[IDGF6.2$Concentration > 0,]

plot(x = IDGF6.1$log.Conc, 
     y = IDGF6.1$Cq, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "firebrick",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)")

points(x = IDGF6.2$log.Conc,
       y = IDGF6.2$Cq,
       cex = 1,
       pch = 21,
       bg = "steelblue",
       col = "black")

linearmodel=lm(as.numeric(IDGF6.1$Cq)~IDGF6.1$log.Conc)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="firebrick",lwd=2)
text(x = 0, y = 21.5,paste0("IDGF6 1 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(IDGF6.2$Cq)~IDGF6.2$log.Conc)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="steelblue",lwd=2)
text(x = 0, y = 21.2,paste0("IDGF6 2 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

legend("topright", legend = c("IDGF6 1", "IDGF6 2"), pch = 21, col = "black", pt.bg = c("firebrick", "steelblue"), bty = "n")

```

```{r echo = F}

plot(x = IDGF6.1$log.Conc, 
     y = IDGF6.1$Cq, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "firebrick",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)")

linearmodel=lm(as.numeric(IDGF6.1$Cq)~IDGF6.1$log.Conc)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="firebrick",lwd=2)
text(x = 0, y = 21.5,paste0("IDGF6 1 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

legend("topright", legend = c("IDGF6 1"), pch = 21, col = "black", pt.bg = c("firebrick"), bty = "n")

IDGF6.1.slope = linearmodel[[1]][2]

```

```{r echo = F}

plot(x = IDGF6.2$log.Conc, 
     y = IDGF6.2$Cq, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "steelblue",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)")

linearmodel=lm(as.numeric(IDGF6.2$Cq)~IDGF6.2$log.Conc)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="steelblue",lwd=2)
text(x = 0, y = 22.2,paste0("IDGF6 2 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

legend("topright", legend = c("IDGF6 2"), pch = 21, col = "black", pt.bg = c("steelblue"), bty = "n")

IDGF6.2.slope = linearmodel[[1]][2]

```

```{r echo = F}

IDGF6.1.E = (-1+2^(-1/IDGF6.1.slope))*100
IDGF6.2.E = (-1+2^(-1/IDGF6.2.slope))*100

Mean.E = mean(c(IDGF6.1.E, IDGF6.2.E))

barplot(height = c(IDGF6.1.E, IDGF6.2.E, Mean.E), 
        col = c("firebrick", "steelblue", "gold"), 
        names = c("IDGF6 1", "IDGF6 2", "Mean E"), 
        ylab = "Percent Efficiency (E)", 
        ylim = c(0, 150))
abline(h = 90, lty = 2, lwd = 1)
abline(h = 110, lty = 2, lwd = 1)
abline(h = 100, lty = 2, lwd = 2)

```

### 2024-01-17 Anna qPCR data/20231220_Anna_GRWT_IDGF6.PEPCK.RP49.Rmd
update

---
title: "Anna IDGF6 and PEPCK Primer qPCR Plate"
author: "John Santiago"
date: "2023-12-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include = F}
library(plotly)
IDGF6.data = read.csv("/Users/johncsantiago/Documents/20231220_Anna_GRWT_IDGF6.csv")
IDGF6.data$Genotype = substr(IDGF6.data$Sample,1,2)
IDGF6.data$Concentration = substr(IDGF6.data$Sample,5,nchar(IDGF6.data$Sample))
IDGF6.data$Rep = substr(IDGF6.data$Sample,3,3)
IDGF6.data$Primer = 'IDGF6'

IDGF6.data = IDGF6.data[IDGF6.data$Well != "A7", c('Well', 'Sample', 'Cq', 'Genotype', 'Primer', 'Rep', 'Concentration')]

RP49.PEPCK.data = read.csv("/Users/johncsantiago/Documents/20231220_Anna_GRWT_RP49.PEPCK.csv")
RP49.PEPCK.data$Genotype = substr(RP49.PEPCK.data$Sample,1,2)
RP49.PEPCK.data$Concentration = substr(RP49.PEPCK.data$Sample,6,(nchar(RP49.PEPCK.data$Sample)-3))
RP49.PEPCK.data$Rep = substr(RP49.PEPCK.data$Sample,3,3)
RP49.PEPCK.data$Primer = RP49.PEPCK.data$Target

RP49.PEPCK.data = RP49.PEPCK.data[RP49.PEPCK.data$Well != "A6" &
                                    RP49.PEPCK.data$Well != "A7" &
                                    RP49.PEPCK.data$Well != "G3" &
                                    RP49.PEPCK.data$Well != "G4" &
                                    RP49.PEPCK.data$Well != "G5" &
                                    RP49.PEPCK.data$Well != "G6" &
                                    RP49.PEPCK.data$Well != "C9", 
                                  c('Well', 'Sample', 'Cq', 'Genotype', 'Primer', 'Rep', 'Concentration')]

RP49.PEPCK.data$Cq = as.numeric(RP49.PEPCK.data$Cq)

LDH.PDH.PCB.data = read.csv("/Users/johncsantiago/Documents/20231221_Anna_GRWT_PCB.PDH.LDH.csv")

LDH.PDH.PCB.data[grep('idgf', LDH.PDH.PCB.data$Sample), 'Sample'] = paste0('KD', substr(LDH.PDH.PCB.data[grep('idgf', LDH.PDH.PCB.data$Sample), 'Sample'] , 12, 18))

LDH.PDH.PCB.data[grep('GR13', LDH.PDH.PCB.data$Sample), 'Sample'] = paste0('GR3', substr(LDH.PDH.PCB.data[grep('GR13', LDH.PDH.PCB.data$Sample), 'Sample'],5, 10))

LDH.PDH.PCB.data$Genotype = substr(LDH.PDH.PCB.data$Sample,1,2)
LDH.PDH.PCB.data$Concentration = substr(LDH.PDH.PCB.data$Sample,6,(nchar(LDH.PDH.PCB.data$Sample)-3))
LDH.PDH.PCB.data$Rep = substr(LDH.PDH.PCB.data$Sample,3,3)
LDH.PDH.PCB.data$Primer = LDH.PDH.PCB.data$Target

LDH.PDH.PCB.data = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Well != "D6" &
                                    LDH.PDH.PCB.data$Well != "D1" &
                                    LDH.PDH.PCB.data$Well != "D10" &
                                    LDH.PDH.PCB.data$Well != "D12" &
                                    LDH.PDH.PCB.data$Well != "E4", 
                                  c('Well', 'Sample', 'Cq', 'Genotype', 'Primer', 'Rep', 'Concentration')]

LDH.PDH.PCB.data$Cq = as.numeric(LDH.PDH.PCB.data$Cq)

```

```{r echo = F}

plotdata = IDGF6.data
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "IDGF6",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "steelblue",
       col = "black")

```

```{r echo = F}

mean.cq = c(1:18)
names(mean.cq) = unique(IDGF6.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(IDGF6.data[IDGF6.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

idgf.mean.cq = mean.cq[-grep(' 2.5', names(mean.cq))]
names(idgf.mean.cq) = substr(names(idgf.mean.cq), 1,3)

dCq = c(1:9)
names(dCq) = unique(paste0(IDGF6.data$Genotype, IDGF6.data$Rep))
i = 1
while(i <= length(dCq)){
  temp = mean.cq[substr(names(mean.cq),1,3) == names(dCq)[i]]
  dCq[i] = temp[2] - temp[1]
  i=i+1
}

FC = 2^dCq

barplot(names = names(FC),
     height = FC,
     ylab = "Fold Change",
     xlab = "",
     main = "IDGF6 FC between 2.5ng and 5ng cDNA",
     las = 2,
     col = "steelblue",
     ylim = c(0,2))

```

```{r echo = F}

plotdata = RP49.PEPCK.data[RP49.PEPCK.data$Primer == 'RP49',]
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "RP49",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "firebrick",
       col = "black")

```

```{r echo = F}

plotdata = RP49.PEPCK.data[RP49.PEPCK.data$Primer == 'Pepck-1',]
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "PEPCK",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "darkgreen",
       col = "black")

```

```{r echo = F}

plotdata = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'PCB',]
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "PCB",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "gold",
       col = "black")

```

```{r echo = F}

plotdata = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'PDH',]
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "PDH",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "orchid4",
       col = "black")

```

```{r echo = F}

plotdata = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'LDH',]
plotdata = plotdata[order(paste0(plotdata$Genotype, plotdata$Rep)),]

plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample)))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "LDH",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "darkorange",
       col = "black")

```

```{r echo = F}

rp49.data = RP49.PEPCK.data[RP49.PEPCK.data$Primer == 'RP49',]

mean.cq = c(1:9)
names(mean.cq) = unique(rp49.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(rp49.data[rp49.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

rp49.mean.cq = mean.cq
names(rp49.mean.cq) = substr(names(rp49.mean.cq),1,3)

pepck.data = RP49.PEPCK.data[RP49.PEPCK.data$Primer == 'Pepck-1',]

mean.cq = c(1:10)
names(mean.cq) = unique(pepck.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(pepck.data[pepck.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

pepck.mean.cq = mean.cq
names(pepck.mean.cq) = substr(names(pepck.mean.cq),1,3)
pepck.FC = 2^(pepck.mean.cq[10] - pepck.mean.cq[9])
pepck.mean.cq = pepck.mean.cq[1:8]
pepck.mean.cq = pepck.mean.cq[names(rp49.mean.cq)]
names(pepck.mean.cq) = names(rp49.mean.cq)

ldh.data = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'LDH',]

mean.cq = c(1:10)
names(mean.cq) = unique(ldh.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(ldh.data[ldh.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

ldh.mean.cq = mean.cq
ldh.FC = 2^(ldh.mean.cq['Wt1 (2.5ng)'] - ldh.mean.cq['WT1 (5ng)'])
ldh.mean.cq = ldh.mean.cq[names(ldh.mean.cq) != 'Wt1 (2.5ng)']
names(ldh.mean.cq) = substr(names(ldh.mean.cq),1,3)
ldh.mean.cq = ldh.mean.cq[names(rp49.mean.cq)]
names(ldh.mean.cq) = names(rp49.mean.cq)

pdh.data = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'PDH',]

mean.cq = c(1:10)
names(mean.cq) = unique(pdh.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(pdh.data[pdh.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

pdh.mean.cq = mean.cq
pdh.FC = 2^(pdh.mean.cq['Wt1 (2.5ng)'] - pdh.mean.cq['WT1 (5ng)'])
pdh.mean.cq = pdh.mean.cq[names(pdh.mean.cq) != 'Wt1 (2.5ng)']
names(pdh.mean.cq) = substr(names(pdh.mean.cq),1,3)
pdh.mean.cq = pdh.mean.cq[names(rp49.mean.cq)]
names(pdh.mean.cq) = names(rp49.mean.cq)

pcb.data = LDH.PDH.PCB.data[LDH.PDH.PCB.data$Primer == 'PCB',]

mean.cq = c(1:10)
names(mean.cq) = unique(pcb.data$Sample)
i = 1
while(i <= length(mean.cq)){
  mean.cq[i] = mean(pcb.data[pcb.data$Sample == names(mean.cq)[i], 'Cq'])
  i = i+1
}

pcb.mean.cq = mean.cq
pcb.FC = 2^(pcb.mean.cq['Wt1 (2.5ng)'] - pcb.mean.cq['WT1 (5ng)'])
pcb.mean.cq = pcb.mean.cq[names(pcb.mean.cq) != 'Wt1 (2.5ng)']
names(pcb.mean.cq) = substr(names(pcb.mean.cq),1,3)
pcb.mean.cq = pcb.mean.cq[names(rp49.mean.cq)]
names(pcb.mean.cq) = names(rp49.mean.cq)

```

```{r echo = F}

barplotdata = c(pepck.FC, pcb.FC, pdh.FC, ldh.FC)
names(barplotdata) = c ('PEPCK', 'PCB', 'PDH', 'LDH')

barplot(height = barplotdata,
     ylab = "Fold Change",
     xlab = "",
     main = "Pepck-1 FC between 2.5ng and 10ng cDNA",
     las = 1,
     col = c("darkgreen", 'gold', 'orchid4', 'darkorange'),
     ylim = c(0,4.1))
abline(h = 4, lty = 2, lwd = 2)
abline(h = 2, lty = 2, lwd = 2)

```

```{r echo = F}

plotdata = rbind(IDGF6.data, RP49.PEPCK.data, LDH.PDH.PCB.data)
plotdata = plotdata[plotdata$Genotype == "GR" & plotdata$Concentration == 5,]

plotdata$x = factor(paste0(plotdata$Primer, '-', plotdata$Rep), 
                    levels = c(unique(paste0(plotdata$Primer, '-', plotdata$Rep))[order(unique(paste0(plotdata$Primer, '-', plotdata$Rep)))]))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "G85R",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',8), 
              rep('firebrick',7),
              rep("darkgreen",9),
              rep("gold", 9),
              rep('orchid4', 9),
              rep('darkorange', 9)),
       col = "black")

```

```{r echo = F}

plotdata = rbind(IDGF6.data, RP49.PEPCK.data, LDH.PDH.PCB.data)
plotdata = plotdata[plotdata$Genotype == "WT" & plotdata$Concentration == 5,]

plotdata$x = factor(paste0(plotdata$Primer, '-', plotdata$Rep), 
                    levels = c(unique(paste0(plotdata$Primer, '-', plotdata$Rep))[order(unique(paste0(plotdata$Primer, '-', plotdata$Rep)))]))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "WT",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',9), 
              rep('firebrick',9),
              rep("darkgreen",6),
              rep("gold", 7),
              rep('orchid4', 9),
              rep('darkorange', 9)),
       col = "black")
```

```{r echo = F}

plotdata = rbind(IDGF6.data, RP49.PEPCK.data, LDH.PDH.PCB.data)
plotdata = plotdata[plotdata$Genotype == "KD" & plotdata$Concentration == 5,]

plotdata$x = factor(paste0(plotdata$Primer, '-', plotdata$Rep), 
                    levels = c(unique(paste0(plotdata$Primer, '-', plotdata$Rep))[order(unique(paste0(plotdata$Primer, '-', plotdata$Rep)))]))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "KD",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',9), 
              rep('firebrick',8),
              rep("darkgreen",9),
              rep("gold", 9),
              rep('orchid4', 9),
              rep('darkorange', 9)),
       col = "black")
```

```{r echo = F}

dCt = data.frame(Genotype = substr(names(idgf.mean.cq),1,2),
                 IDGF6 = idgf.mean.cq,
                 RP49 = rp49.mean.cq,
                 PEPCK = pepck.mean.cq,
                 PDH = pdh.mean.cq,
                 PCB = pcb.mean.cq,
                 LDH = ldh.mean.cq)
dCt$Genotype = factor(dCt$Genotype, levels = c('WT', 'GR', 'KD'))

dCt$IDGF6.dCt = dCt$IDGF6 - dCt$RP49
dCt$IDGF6.FC = 2^-dCt$IDGF6.dCt

dCt$PEPCK.dCt = dCt$PEPCK - dCt$RP49
dCt$PEPCK.FC = 2^-dCt$PEPCK.dCt

dCt$PDH.dCt = dCt$PDH - dCt$RP49
dCt$PDH.FC = 2^-dCt$PDH.dCt

dCt$PCB.dCt = dCt$PCB - dCt$RP49
dCt$PCB.FC = 2^-dCt$PCB.dCt

dCt$LDH.dCt = dCt$LDH - dCt$RP49
dCt$LDH.FC = 2^-dCt$LDH.dCt

GRvsWT = t.test(dCt$IDGF6.dCt[dCt$Genotype == "WT"], dCt$IDGF6.dCt[dCt$Genotype == "GR"])[[3]]
KDvsWT = t.test(dCt$IDGF6.dCt[dCt$Genotype == "WT"], dCt$IDGF6.dCt[dCt$Genotype == "KD"])[[3]]

boxplot(IDGF6.dCt~Genotype, data = dCt, ylim = c(2,7))

points(x = dCt$Genotype,
       y = dCt$IDGF6.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")

text(x=c(2,3),y=c(6.75,6.75), labels = c(paste0('pval = ', signif(GRvsWT,3)), 
                                   paste0('pval = ', signif(KDvsWT,3))))

```

```{r echo = F}

GRvsWT = t.test(dCt$PEPCK.dCt[dCt$Genotype == "WT"], dCt$PEPCK.dCt[dCt$Genotype == "GR"])[[3]]
KDvsWT = t.test(dCt$PEPCK.dCt[dCt$Genotype == "WT"], dCt$PEPCK.dCt[dCt$Genotype == "KD"])[[3]]

boxplot(PEPCK.dCt~Genotype, data = dCt, ylim = c(4, 7))

points(x = dCt$Genotype,
       y = dCt$PEPCK.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")

text(x=c(2,3),y=c(6.75,6.75), labels = c(paste0('pval = ', signif(GRvsWT,3)), 
                                   paste0('pval = ', signif(KDvsWT,3))))

```

```{r echo = F}

GRvsWT = t.test(dCt$PDH.dCt[dCt$Genotype == "WT"], dCt$PDH.dCt[dCt$Genotype == "GR"])[[3]]
KDvsWT = t.test(dCt$PDH.dCt[dCt$Genotype == "WT"], dCt$PDH.dCt[dCt$Genotype == "KD"])[[3]]

KDvsGR = t.test(dCt$PDH.dCt[dCt$Genotype == "GR"], dCt$PDH.dCt[dCt$Genotype == "KD"])[[3]]

boxplot(PDH.dCt~Genotype, data = dCt)

points(x = dCt$Genotype,
       y = dCt$PDH.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")

text(x=c(2,3,2.5),y=c(11,11, 14), labels = c(paste0('pval = ', signif(GRvsWT,3)), 
                                   paste0('pval = ', signif(KDvsWT,3)),
                                   paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

GRvsWT = t.test(dCt$PCB.dCt[dCt$Genotype == "WT"], dCt$PCB.dCt[dCt$Genotype == "GR"])[[3]]
KDvsWT = t.test(dCt$PCB.dCt[dCt$Genotype == "WT"], dCt$PCB.dCt[dCt$Genotype == "KD"])[[3]]

KDvsGR = t.test(dCt$PCB.dCt[dCt$Genotype == "GR"], dCt$PCB.dCt[dCt$Genotype == "KD"])[[3]]

boxplot(PCB.dCt~Genotype, data = dCt)

points(x = dCt$Genotype,
       y = dCt$PCB.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")

text(x=c(2,3, 2.5),y=c(9, 9, 14), labels = c(paste0('pval = ', signif(GRvsWT,3)), 
                                   paste0('pval = ', signif(KDvsWT,3)),
                                   paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

GRvsWT = t.test(dCt$LDH.dCt[dCt$Genotype == "WT"], dCt$LDH.dCt[dCt$Genotype == "GR"])[[3]]
KDvsWT = t.test(dCt$LDH.dCt[dCt$Genotype == "WT"], dCt$LDH.dCt[dCt$Genotype == "KD"])[[3]]

KDvsGR = t.test(dCt$LDH.dCt[dCt$Genotype == "GR"], dCt$LDH.dCt[dCt$Genotype == "KD"])[[3]]

boxplot(LDH.dCt~Genotype, data = dCt)

points(x = dCt$Genotype,
       y = dCt$LDH.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")

text(x=c(2,3, 2.5),y=c(8, 8, 11), labels = c(paste0('pval = ', signif(GRvsWT,3)), 
                                   paste0('pval = ', signif(KDvsWT,3)),
                                   paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

KDvsGR = t.test(dCt$PDH.dCt[dCt$Genotype == "GR"], dCt$PDH.dCt[dCt$Genotype == "KD"])[[3]]

boxplotdata = dCt[row.names(dCt) != 'WT1' & row.names(dCt) != 'WT2',]

boxplot(PDH.dCt~Genotype, data = boxplotdata, ylim = c(7.5,11))

points(x = dCt$Genotype,
       y = dCt$PDH.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")
text(x=c(2.5),y=c(10.5), labels = c(paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

KDvsGR = t.test(dCt$PCB.dCt[dCt$Genotype == "GR"], dCt$PCB.dCt[dCt$Genotype == "KD"])[[3]]

GRvsWT = t.test(dCt$PCB.dCt[dCt$Genotype == "GR"], dCt$PCB.dCt[dCt$Genotype == "WT"])[[3]]

boxplotdata = dCt[row.names(dCt) != 'WT1' & row.names(dCt) != 'WT2',]

boxplot(PCB.dCt~Genotype, data = boxplotdata, ylim = c(6,9))

points(x = dCt$Genotype,
       y = dCt$PCB.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")
text(x=c(2.5),y=c(8.5), labels = c(paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

KDvsGR = t.test(dCt$LDH.dCt[dCt$Genotype == "GR"], dCt$LDH.dCt[dCt$Genotype == "KD"])[[3]]

boxplotdata = dCt[row.names(dCt) != 'WT1' & row.names(dCt) != 'WT2',]

boxplot(LDH.dCt~Genotype, data = boxplotdata, ylim = c(4.5,8))

points(x = dCt$Genotype,
       y = dCt$LDH.dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep('steelblue',3), 
              rep('firebrick',3),
              rep("darkgreen",3)),
       col = "black")
text(x=c(2.5),y=c(7.5), labels = c(paste0('KD vs GR\npval = ', signif(KDvsGR,3))))

```

```{r echo = F}

mean.dCt = data.frame(Genotype = c('WT','GR', 'KD'),
                     IDGF6.dCT = c(mean(dCt$IDGF6.dCt[dCt$Genotype == 'WT']),
                                   mean(dCt$IDGF6.dCt[dCt$Genotype == 'GR']),
                                   mean(dCt$IDGF6.dCt[dCt$Genotype == 'KD'])),
                     PEPCK.dCT = c(mean(na.omit(dCt$PEPCK.dCt[dCt$Genotype == 'WT'])),
                                   mean(dCt$PEPCK.dCt[dCt$Genotype == 'GR']),
                                   mean(dCt$PEPCK.dCt[dCt$Genotype == 'KD'])),
                     PDH.dCT = c(dCt['WT3', 'PDH.dCt'],
                                   mean(dCt$PDH.dCt[dCt$Genotype == 'GR']),
                                   mean(dCt$PDH.dCt[dCt$Genotype == 'KD'])),
                     PCB.dCT = c(dCt['WT3', 'PCB.dCt'],
                                   mean(dCt$PCB.dCt[dCt$Genotype == 'GR']),
                                   mean(dCt$PCB.dCt[dCt$Genotype == 'KD'])),
                     LDH.dCT = c(dCt['WT3', 'LDH.dCt'],
                                   mean(dCt$LDH.dCt[dCt$Genotype == 'GR']),
                                   mean(na.omit(dCt$LDH.dCt[dCt$Genotype == 'KD']))))

IDGF6.ddCT = c((mean.dCt$IDGF6.dCT[2] - mean.dCt$IDGF6.dCT[1]),
               (mean.dCt$IDGF6.dCT[3] - mean.dCt$IDGF6.dCT[1]))
names(IDGF6.ddCT) = c('GR/WT', 'KD/WT')

PEPCK.ddCT = c((mean.dCt$PEPCK.dCT[2] - mean.dCt$PEPCK.dCT[1]),
               (mean.dCt$PEPCK.dCT[3] - mean.dCt$PEPCK.dCT[1]))
names(PEPCK.ddCT) = c('GR/WT', 'KD/WT')

PDH.ddCT = c((mean.dCt$PDH.dCT[2] - mean.dCt$PDH.dCT[1]),
               (mean.dCt$PDH.dCT[3] - mean.dCt$PDH.dCT[1]))
names(PDH.ddCT) = c('GR/WT', 'KD/WT')

PCB.ddCT = c((mean.dCt$PCB.dCT[2] - mean.dCt$PCB.dCT[1]),
               (mean.dCt$PCB.dCT[3] - mean.dCt$PCB.dCT[1]))
names(PCB.ddCT) = c('GR/WT', 'KD/WT')

LDH.ddCT = c((mean.dCt$LDH.dCT[2] - mean.dCt$LDH.dCT[1]),
               (mean.dCt$LDH.dCT[3] - mean.dCt$LDH.dCT[1]))
names(PDH.ddCT) = c('GR/WT', 'KD/WT')

barplot(height = c(2^-IDGF6.ddCT, NA, 
                   2^-PEPCK.ddCT, NA, 
                   2^-PDH.ddCT, NA, 
                   2^-PCB.ddCT, NA, 
                   2^-LDH.ddCT),
        names.arg = c('GR IDGF6', 'KD IDGF6', NA, 
                      'GR PEPCK', 'KD PEPCK', NA,
                      'GR PDH', 'KD PDH', NA,
                      'GR PCB', 'KD PCB', NA,
                      'GR LDH', 'KD LDH'),
        ylab = 'Fold Change (relative to WT)',
        ylim = c(0,2.5),
        las = 2,
        cex.names = .9)
abline(h = 1, lty = 2)

```

### 2024-01-17 GeneExpressionBoxPlots.Rmd
update

---
title: "Box Plots Using All Data"
author: "John Santiago"
date: "2023-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

groups = groups[colnames(cpmdata),]

gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
gbbOE = gbbOE[,row.names(gbbOE.groups)]
gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)

##normalize data
countdata=gbbOE
x <- countdata
gr <- factor(gbbOE.groups$group, levels=c(unique(gbbOE.groups$group)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbOE.cpmdata=cpm(z)

gbbOEmean = gbbOE.cpmdata[,1:6]
colnames(gbbOEmean) = unique(gr)
i=1
while(i<=6){
  temp= gbbOE.cpmdata[,row.names(gbbOE.groups[gbbOE.groups$group == colnames(gbbOEmean)[i],])]
  gbbOEmean[,i] = apply(temp, 1, mean)
  i=i+1
}

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)

fit <- glmQLFit(z, design)
plotQLDisp(fit)

compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.LL3=DEout
sGRxWT.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_ML3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.ML3=DEout
sGRxWT.ML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_LL3-G85R_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.LL3xML3=DEout
sGR.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(LoxP_LL3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.LL3xML3=DEout
sWT.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-G85R_gbb_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbb.LL3xML3=DEout
sG85R_gbb.LL3xML3=DEout[DEout$FDR<.05,]

gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)

##normalize data
countdata=gbbKO
x <- countdata
gr <- factor(gbbKO.groups$Genotype, levels=c(unique(gbbKO.groups$Genotype)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbKO.cpmdata=cpm(z)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

```

```{r}

##relish FBgn0014018
##attacin FBgn0041579
##cecropin FBgn0000276
##diptericin FBgn0004240
##drosocin FBgn0010388
##defensin FBgn0010385
##drosomycin FBgn0283461
##metchnikowin FBgn0014865
##sod1 FBgn0003462
##sod2 FBgn0010213
##catalase FBgn0000261
##gstd1 FBgn0001149

##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')

FBgn = 'FBgn0004362'
name = ''

gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), condition = groups$Group, group = paste0(groups$Genotype, groups$Sex))

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F", "TktOEGR.F",
                                                 'WT.F', "TktDfWT.F", "TktOEWT.F",
                                                 'GR.M', "TktDfGR.M", "TktOEGR.M",
                                                 'WT.M', "TktDfWT.M", "TktOEWT.M"))

boxplot(gene$cpm~gene$condition, xlab="",     
        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])

```

```{r}

gene = data.frame(cpm = as.numeric(gbbOE.cpmdata[FBgn,]), condition = gbbOE.groups$group, group = gbbOE.groups$genotype)

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('LoxP_ML3', "LoxP_LL3",
                                                 'G85R_ML3', "G85R_LL3",
                                                 'G85R_gbb_ML3', "G85R_gbb_LL3"))

boxplot(gene$cpm~gene$condition, xlab="",     
        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])

```

```{r}

## WT = W1118
## KO = GBB1/GBB2 (both null alleles)
## Aaron and Catherine legend for RNAseq
## Whole larvae

gene = data.frame(cpm = as.numeric(gbbKO.cpmdata[FBgn,]), condition = gbbKO.groups$Genotype)

gene$condition = factor(gene$condition, levels = c('WT', "KO"))

boxplot(gene$cpm~gene$condition, xlab="",     
        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$condition))])

```

### 2024-01-17 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
update

---
title: "Glycolysis Network"
author: "John Santiago"
date: "2023-12-06"
output: 
  bookdown::pdf_document2:
    number_sections: false
---

```{r setup, include=FALSE}
##knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev='svg', fig.width=9, fig.height=12, out.width = "9in", out.height = "12in")
```

- #### Figure \@ref(fig:fig1): GR.FC vs WT.FC

- #### Figure \@ref(fig:fig2): GR.MC vs WT.MC

- #### Figure \@ref(fig:fig3): GR.FDf vs WT.FDf

- #### Figure \@ref(fig:fig4): GR.MDf vs WT.MDf

- #### Figure \@ref(fig:fig5): GR.FOE vs WT.FOE

- #### Figure \@ref(fig:fig6): GR.MOE vs WT.MOE

- #### Figure \@ref(fig:fig7): GRF: C vs Df

- #### Figure \@ref(fig:fig8): GRM: C vs Df

- #### Figure \@ref(fig:fig9): WTF: C vs Df

- #### Figure \@ref(fig:fig10): WTM: C vs Df

- #### Figure \@ref(fig:fig11): GRF: C vs OE

- #### Figure \@ref(fig:fig12): GRM: C vs OE

- #### Figure \@ref(fig:fig13): WTF: C vs OE

- #### Figure \@ref(fig:fig14): WTM: C vs OE

<br><br><br>

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(ggpubr)
library(performance)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

genesingo=as.list(org.Dm.egGO2ALLEGS)

##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
colnames(mean.cpm) = unique(groups$Group)
row.names(mean.cpm) = row.names(cpmdata)
i=1
while(i<=ncol(mean.cpm)){
  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
  i=i+1
}

i=1
for(i in 1:ncol(TKT.EdgeR)){
  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
  i=i+1
}

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.cpm = as.data.frame(mean.cpm)

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.data[,condition1]/mean.data[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.data)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

GR.CxDf = compare.conditions("D", "E")
WT.CxDf = compare.conditions("B", "C")

GR.CxOE = compare.conditions("F", "E")
WT.CxOE = compare.conditions("A", "C")

##Comparison cpm means
ccm = data.frame(GRF.CxDf = apply(mean.cpm[,c("TktDfGR.F","GR.F")], MARGIN = 1, mean), 
                 GRF.CxOE = apply(mean.cpm[,c("TktOEGR.F","GR.F")], MARGIN = 1, mean),
                 WTF.CxDf = apply(mean.cpm[,c("TktDfWT.F","WT.F")], MARGIN = 1, mean),
                 WTF.CxOE = apply(mean.cpm[,c("TktOEWT.F","WT.F")], MARGIN = 1, mean),
                 GRxWT.FC = apply(mean.cpm[,c("GR.F","WT.F")], MARGIN = 1, mean), 
                 GRxWT.FDf = apply(mean.cpm[,c("TktDfGR.F","TktDfWT.F")], MARGIN = 1, mean),
                 GRxWT.FOE = apply(mean.cpm[,c("TktOEGR.F","TktOEWT.F")], MARGIN = 1, mean), 
                 GRM.CxDf = apply(mean.cpm[,c("TktDfGR.M","GR.M")], MARGIN = 1, mean), 
                 GRM.CxOE = apply(mean.cpm[,c("TktOEGR.M","GR.M")], MARGIN = 1, mean),
                 WTM.CxDf = apply(mean.cpm[,c("TktDfWT.M","WT.M")], MARGIN = 1, mean),
                 WTM.CxOE = apply(mean.cpm[,c("TktOEWT.M","WT.M")], MARGIN = 1, mean),
                 GRxWT.MC = apply(mean.cpm[,c("GR.M","WT.M")], MARGIN = 1, mean), 
                 GRxWT.MDf = apply(mean.cpm[,c("TktDfGR.M","TktDfWT.M")], MARGIN = 1, mean),
                 GRxWT.MOE = apply(mean.cpm[,c("TktOEGR.M","TktOEWT.M")], MARGIN = 1, mean),
                 GR.FxM = apply(mean.cpm[,c("GR.F","GR.M")], MARGIN = 1, mean),
                 WT.FxM = apply(mean.cpm[,c("WT.F","WT.M")], MARGIN = 1, mean),
                 row.names = row.names(mean.cpm))

comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
                 GRF.CxOE = c("TktOEGR.F","GR.F"),
                 WTF.CxDf = c("TktDfWT.F","WT.F"),
                 WTF.CxOE = c("TktOEWT.F","WT.F"),
                 GRxWT.FC = c("GR.F","WT.F"), 
                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
                 GRM.CxOE = c("TktOEGR.M","GR.M"),
                 WTM.CxDf = c("TktDfWT.M","WT.M"),
                 WTM.CxOE = c("TktOEWT.M","WT.M"),
                 GRxWT.MC = c("GR.M","WT.M"), 
                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
                 GR.FxM = c("GR.F","GR.M"),
                 WT.FxM = c("WT.F","WT.M"))

```

```{r include = F}

##genes in the kegg pathway and their enzyme IDs
glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
##Edge data for genes connecting metabolites
glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
##Metabolites in the KEGG pathway with their ID
glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')

node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')

glycolysis.network = function(comparison.T, comparison.M){

##extracting position data for nodes
node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
                       number = rep(names(node.data$kegg.names),
                                    lengths(node.data$kegg.names)),
                       x = 0,
                       y = 0,
                       color = 0,
                       names = "")
node.info$x = node.data$x[node.info$number]
node.info$y = node.data$y[node.info$number]

##make new columns for transcriptomic data
glycolysis.genes$FBgn = ""
glycolysis.genes$Symbol = ""
glycolysis.genes$FC = 0
glycolysis.genes$pval = 1

##Isolate gene ID info for goi
temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
row.names(temp) = temp$CG

##fill in new columns with transcriptomic data
glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
glycolysis.genes$FC = TKT.EdgeR.FC[glycolysis.genes$FBgn, comparison.T]
glycolysis.genes$FC = TKT.EdgeR[glycolysis.genes$FBgn, comparison.T]

##make new columns for metabolomic data
row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
glycolysis.metabs$metabolomicsID = ""
glycolysis.metabs$FC = 0
glycolysis.metabs$pval = 1

##retrieve name used in metabolomic data for metabolite IDs in path
##including IDs associated with multiple metabolomic names
i = 1
while(i<=nrow(glycolysis.metabs)){
  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
  }
  i = i +1
}

##retrieve metabolite fold change and pvalue data
glycolysis.metabs$FC = log2(comparison.M[glycolysis.metabs$metabolomicsID, "FC"])
glycolysis.metabs$pval = -log10(comparison.M[glycolysis.metabs$metabolomicsID, "p"])

##using the positions for nodes (metabolites) only
metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]

metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']

color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)

metab.info$color[metab.info$color > 1] = 1
metab.info$color[metab.info$color < -1] = -1
metab.info$color = (metab.info$color * 200) +201
metab.info$color = color.pallette[metab.info$color]
metab.info$color[is.na(metab.info$color)] = 'dimgrey'

metab.info$size = 10 + 10*abs(metab.info$size)
metab.info$size[is.na(metab.info$size)] = 10

metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
                          "<br>log2(FC): ", signif(metab.info$FC,3),
                          "<br>pval: ", signif(10^-metab.info$pval,3))

nodes = data.frame(id = paste0(metab.info$names),
                   color = metab.info$color,
                   size = metab.info$size,
                   x = 2*metab.info$x,
                   y = 2*metab.info$y,
                   physics = F,
                   group = "",
                   title = metab.info$title)

glycolysis.edges$FBgn = ''
temp.glycolysis.path = glycolysis.edges

i = 1
while(i<=nrow(glycolysis.edges)){
  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
    temp2 = glycolysis.edges[rep(i, length(temp)),]
    temp2$FBgn = temp
  }else{
    temp2 = glycolysis.edges[i,]
  }
  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)

  i = i +1
}

glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]

glycolysis.edges$size = log10(ccm[glycolysis.edges[,'FBgn'], comparison.T])
glycolysis.edges$size[glycolysis.edges$size <1] = 1
glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
glycolysis.edges$size = 2*glycolysis.edges$size

glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
## max color intensity is at FC of 2
glycolysis.edges$color[glycolysis.edges$color>2] = 2
glycolysis.edges$color[glycolysis.edges$color<(-2)] = -2
glycolysis.edges$color = 201+(glycolysis.edges$color *100)
glycolysis.edges$color = color.pallette[glycolysis.edges$color]
glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))

edges = data.frame(from = glycolysis.edges$from.name,
                   to = glycolysis.edges$to.name,
                   arrows = glycolysis.edges$arrow,
                   color = glycolysis.edges$color,
                   width = glycolysis.edges$size,
                   title = glycolysis.edges$title,
                   physics = T)

nodes = data.frame(id = paste0(nodes$id),
                   color = nodes$color,
                   size = nodes$size,
                   x = nodes$x,
                   y = nodes$y,
                   physics = F,
                   group = "",
                   title = nodes$title)

OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
                               'Propanoate Metabolism',
                               'Starch and Sucrose Metabolism',
                               'Citrate Cycle'),
                        color = "black",
                        size = 15,
                        x= c(1350,1254,966,175),
                        y=c(1112,1822,110,1700),
                        physics = F,
                        group = 'Outside Path',
                        title = "")

nodes = rbind(nodes, OutsidePath)

visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = edges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))

}

```

```{r echo = F, fig.height=12, fig.width=9, fig.align='left', fig1, fig.cap = 'G85R relative to WT. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FC', comparison.M = GRxWT.C)

```

<br><br><br>

```{r, echo =F, fig2, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R relative to WT. Transcriptomic data is from males and metabolomic data is from both sexes.Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GR.CxDf)

```

<br><br><br>

```{r, echo =F, fig3, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FDf', comparison.M = GRxWT.Df)

```

<br><br><br>

```{r, echo =F, fig4, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MDf', comparison.M = GRxWT.Df)

```

<br><br><br>

```{r, echo =F, fig5, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.FOE', comparison.M = GRxWT.OE)

```

<br><br><br>

```{r, echo =F, fig6, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRxWT.MOE', comparison.M = GRxWT.OE)

```

<br><br><br>

```{r, echo =F, fig7, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRF.CxDf', comparison.M = GR.CxDf)

```

<br><br><br>

```{r, echo =F, fig8, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRM.CxDf', comparison.M = GR.CxDf)

```

<br><br><br>

```{r, echo =F, fig9, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTF.CxDf', comparison.M = WT.CxDf)

```

<br><br><br>

```{r, echo =F, fig10, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTM.CxDf', comparison.M = WT.CxDf)

```

<br><br><br>

```{r, echo =F, fig11, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRF.CxOE', comparison.M = GR.CxOE)

```

<br><br><br>

```{r, echo =F, fig12, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'GRM.CxOE', comparison.M = GR.CxOE)

```

<br><br><br>

```{r, echo =F, fig13, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTF.CxOE', comparison.M = WT.CxOE)

```

<br><br><br>

```{r, echo =F, fig14, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}

glycolysis.network(comparison.T = 'WTM.CxOE', comparison.M = WT.CxOE)

```

<br><br><br>

### 2024-01-17 TKT_RNAseq/R Code/PurineMetabolismNetwork.Rmd
update

---
title: "TKT_MetabPaper_Analyses"
author: "John Santiago"
date: "2023-09-29"
output: 
  bookdown::html_document2:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- #### Figure \@ref(fig:fig1): GR.FC vs WT.FC

- #### Figure \@ref(fig:fig2): GR.MC vs WT.MC

- #### Figure \@ref(fig:fig3): GR.FDf vs WT.FDf

- #### Figure \@ref(fig:fig4): GR.MDf vs WT.MDf

- #### Figure \@ref(fig:fig5): GR.FOE vs WT.FOE

- #### Figure \@ref(fig:fig6): GR.MOE vs WT.MOE

- #### Figure \@ref(fig:fig7): GRF: C vs Df

- #### Figure \@ref(fig:fig8): GRM: C vs Df

- #### Figure \@ref(fig:fig9): WTF: C vs Df

- #### Figure \@ref(fig:fig10): WTM: C vs Df

- #### Figure \@ref(fig:fig11): GRF: C vs OE

- #### Figure \@ref(fig:fig12): GRM: C vs OE

- #### Figure \@ref(fig:fig13): WTF: C vs OE

- #### Figure \@ref(fig:fig14): WTM: C vs OE

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
library(ggpubr)
library(performance)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

Synaptic = read.csv("/Users/johncsantiago/Documents/SynapticGenesandTFs.csv")

genesingo=as.list(org.Dm.egGO2ALLEGS)

##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
colnames(mean.cpm) = unique(groups$Group)
row.names(mean.cpm) = row.names(cpmdata)
i=1
while(i<=ncol(mean.cpm)){
  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
  i=i+1
}

i=1
for(i in 1:ncol(TKT.EdgeR)){
  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
  i=i+1
}

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.cpm = as.data.frame(mean.cpm)

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.data[,condition1]/mean.data[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.data)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

GR.CxDf = compare.conditions("D", "E")
WT.CxDf = compare.conditions("B", "C")

GR.CxOE = compare.conditions("F", "E")
WT.CxOE = compare.conditions("A", "C")

```

```{r echo = F, include = F}

tempF = apply(mean.cpm[,c("GR.F", "WT.F")], MARGIN = 1, mean)
tempM = apply(mean.cpm[,c("GR.M", "WT.M")], MARGIN = 1, mean)
tempF = names(tempF)[tempF>10]
tempM = names(tempM)[tempM>10]
cutoff.genes = unique(c(tempF, tempM))

subset.genes = row.names(TKT.EdgeR)[TKT.EdgeR$GRxWT.FC < .05 | TKT.EdgeR$GRxWT.MC < .05]
subset.genes = setdiff(subset.genes, row.names(TKT.EdgeR)[TKT.EdgeR$GRxWT.FC < .05 & TKT.EdgeR$GRxWT.MC < .05])
subset.genes = intersect(subset.genes, cutoff.genes)

FCx = TKT.EdgeR.FC[subset.genes, "GRxWT.FC"]
FCy = TKT.EdgeR.FC[subset.genes, "GRxWT.MC"]

set.size = F

volcano.data = data.frame(Symbol = GeneIDKey[subset.genes, "Symbol"], 
                          FCx = FCx,
                          FCy = FCy,
                          Color = 'grey',
                          size = 2.5,
                          FDR.F = TKT.EdgeR[subset.genes, "GRxWT.FC"],
                          FDR.M = TKT.EdgeR[subset.genes, "GRxWT.MC"],
                          GR.FC.cpm = mean.cpm[subset.genes, "GR.F"],
                          WT.FC.cpm = mean.cpm[subset.genes, "WT.F"],
                          GR.MC.cpm = mean.cpm[subset.genes, "GR.M"],
                          WT.MC.cpm = mean.cpm[subset.genes, "WT.M"],
                          tempcolor = FCx - FCy)

row.names(volcano.data) = subset.genes

volcano.data$Symbol[is.na(volcano.data$Symbol)] = row.names(volcano.data)[is.na(volcano.data$Symbol)]

main.title = "Female and Male G85R/WT FC, Sig. DEG in Males and Females G85R vs WT"

maxx= max(c(abs(min(FCx)),abs(max(FCx))))
maxy= max(c(abs(min(FCy)),abs(max(FCy))))

fig = plot_ly(data = volcano.data,
              x = ~FCx,
              y = ~FCy,
              type = 'scatter',
              mode = 'markers',
              marker = list(colorscale = list(c(0,.7,1), c("firebrick","ivory", "royalblue")),
                            reversescale =T,
                             colorbar = list(title = "delta FC",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                            color = ~tempcolor,
                            line = list(color = "black", width = 1.5),
                            size = 5*volcano.data$size),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\nFemale FDR: ", round(volcano.data$FDR.F,4),
                      "\nMale FDR: ", round(volcano.data$FDR.M,4),
                      "\nFemale mean cpm (G85R/WT): ", round(volcano.data$GR.FC.cpm, 1),
                      "/", round(volcano.data$WT.FC.cpm, 1),
                      "\nMale mean cpm(G85R/WT): ", round(volcano.data$GR.MC.cpm, 1),
                      "/", round(volcano.data$WT.MC.cpm, 1)))
fig = fig %>% layout(xaxis = list(title = "Female log2(FC)"),
                     yaxis = list(title = "Male log2(FC)"),
                     title = main.title,
                     shapes = list(
                       type = "line",
                       line = list(color = "black", dash = 'dash', width = 2),
                       x0 = floor(-maxx),
                       x1 = ceiling(maxx),
                       y0 = floor(-maxy),
                       y1 = ceiling(maxy)))

fig

```

```{r include = F}

library(visNetwork)
library(org.Dm.eg.db)
keggpath = as.list(org.Dm.egPATH2EG)
nodeID = as.list(org.Dm.egENZYME)
nodeID['40528'] = '3.5.4.3'
nodeID['41318'] = '2.7.4.10'
nodeID['42273'] = '2.7.1.145'
nodeID['33924'] = '3.1.3.89'
nodeID[['31309']] = c("3.1.4.17", '3.1.4.53')
nodeID['37741'] = '3.1.4.53'

purine.path = data.frame(enzyme = c('1.17.1.4', '1.17.3.2'),
                         from = c('xanthine', 'xanthine'),
                         to = c(rep('uric acid',2)))

xanthine = data.frame(enzyme = c('1.17.1.4', '1.17.3.2', '2.4.2.1', '3.5.4.3'),
                      from = c('hypoxanthine', 'hypoxanthine', 'xanthosine', 'guanine'),
                      to = c(rep('xanthine',4)))
purine.path = rbind(purine.path, xanthine)

hypoxanthine = data.frame(enzyme = c('2.4.2.1', '2.4.2.1'),
                          from = c('deoxyinosine', 'inosine'),
                          to = c(rep('hypoxanthine', 2)))
purine.path = rbind(purine.path, hypoxanthine)

xanthosine = data.frame(enzyme = c('3.1.3.5'),
                        from = c('XMP'),
                        to = 'xanthosine')
purine.path = rbind(purine.path, xanthosine)

XMP = data.frame(enzyme = c('1.1.1.205'),
                 from = c('IMP'),
                 to = 'XMP')
purine.path = rbind(purine.path, XMP)

IMP = data.frame(enzyme = c('3.6.1.6', '3.5.4.6'),
                 from = c('IDP', 'AMP'),
                 to = c(rep('IMP', 2)))
purine.path = rbind(purine.path, IMP)

adenylosuccinate = data.frame(enzyme = c('6.3.4.4'),
                              from = c('IMP'),
                              to = 'adenylosuccinate')
purine.path = rbind(purine.path, adenylosuccinate)

inosine = data.frame(enzyme = c('2.4.2.1', '3.5.4.4', '3.1.3.5'),
                     from = c('hypoxanthine', 'adenosine', 'IMP'),
                     to = c(rep('inosine', 3)))
purine.path = rbind(purine.path, inosine)

deoxyinosine = data.frame(enzyme = c('2.4.2.1', '3.5.4.4'),
                          from = c('hypoxanthine', 'deoxyadenosine'),
                          to = c(rep('deoxyinosine', 2)))
purine.path = rbind(purine.path, deoxyinosine)

adenosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5', '2.7.1.20'),
                       from = c('adenine', 'AMP', 'AMP'),
                       to = c(rep('adenosine', 3)))
purine.path = rbind(purine.path, adenosine)

AMP = data.frame(enzyme = c('4.3.2.2', '2.7.1.20', '2.4.2.7', '2.7.4.3', '2.7.4.10', '3.1.4.17', '3.1.4.53'),
                 from = c('adenylosuccinate', 'adenosine', 'adenine', 'ADP', 'ADP', 'cAMP', 'cAMP'),
                 to = c(rep('AMP', 7)))
purine.path = rbind(purine.path, AMP)

adenine = data.frame(enzyme = c('2.4.2.1', '2.4.2.7', '2.4.2.1'),
                     from = c('adenosine', 'AMP', 'deoxyadenosine'),
                     to = c(rep('adenine', 3)))
purine.path = rbind(purine.path, adenine)

ATP = data.frame(enzyme = c('2.7.4.6'),
                 from = c('ADP'),
                 to = c(rep('ATP', 1)))
purine.path = rbind(purine.path, ATP)

dATP = data.frame(enzyme = c('2.7.4.6'),
                  from = c('dADP'),
                  to = c(rep('dATP', 1)))
purine.path = rbind(purine.path, dATP)

ADP = data.frame(enzyme = c('2.7.4.3', '2.7.4.10', '2.7.4.6', '3.6.1.15'),
                 from = c('AMP', 'AMP', 'ATP', 'ATP'),
                 to = c(rep('ADP', 4)))
purine.path = rbind(purine.path, ADP)

dADP = data.frame(enzyme = c('2.7.4.3', '1.17.4.1', '2.7.4.6'),
                  from = c('dAMP', 'ADP', 'dATP'),
                  to = c(rep('dADP', 3)))
purine.path = rbind(purine.path, dADP)

dAMP = data.frame(enzyme = c('2.7.1.145', '2.7.4.3'),
                  from = c('deoxyadenosine', 'dADP'),
                  to = c(rep('dAMP', 2)))
purine.path = rbind(purine.path, dAMP)

deoxyadenosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5', '3.1.3.89'),
                            from = c('adenine', 'dAMP', 'dAMP'),
                            to = c(rep('deoxyadenosine', 3)))
purine.path = rbind(purine.path, deoxyadenosine)

dGTP = data.frame(enzyme = c('2.7.4.6'),
                  from = c('dGDP'),
                  to = c('dGTP'))
purine.path = rbind(purine.path, dGTP)

guanine = data.frame(enzyme = c('2.4.2.1', '2.4.2.1'),
                     from = c('guanosine', 'deoxyguanosine'),
                     to = c(rep('guanine', 2)))
purine.path = rbind(purine.path, guanine)

dGDP = data.frame(enzyme = c('2.7.4.6', '1.17.4.1', '2.7.4.8'),
                  from = c('dGTP', 'GDP', 'dGMP'),
                  to = c(rep('dGDP', 3)))
purine.path = rbind(purine.path, dGDP)

guanosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5'),
                       from = c('guanine', 'GMP'),
                       to = c(rep('guanosine', 2)))
purine.path = rbind(purine.path, guanosine)

GTP = data.frame(enzyme = c('2.7.4.6'),
                 from = c('GDP'),
                 to = c(rep('GTP', 1)))
purine.path = rbind(purine.path, GTP)

GDP = data.frame(enzyme = c('2.7.4.6', '2.7.4.8'),
                 from = c('GTP', 'GMP'),
                 to = c(rep('GDP', 2)))
purine.path = rbind(purine.path, GDP)

GMP = data.frame(enzyme = c('6.3.5.2','3.6.1.6', '2.7.4.8'),
                 from = c('XMP', 'GDP', 'GDP'),
                 to = c(rep('GMP', 3)))
purine.path = rbind(purine.path, GMP)

dGMP = data.frame(enzyme = c('2.7.4.8', '2.7.1.145'),
                  from = c('dGDP', 'deoxyguanosine'),
                  to = c(rep('dGMP', 2)))
purine.path = rbind(purine.path, dGMP)

cAMP = data.frame(enzyme = '4.6.1.1',
                  from = 'ATP',
                  to = 'cAMP')
purine.path = rbind(purine.path, cAMP)

FGAM = data.frame(c(),
               c())

purine.path$arrows = 'to'
temp = purine.path
temp[,5] = paste0(purine.path[,1], purine.path[,2], purine.path[,3])
temp[,6] = paste0(purine.path[,1], purine.path[,3], purine.path[,2])
temp$keep = TRUE

i=1
while(i<=nrow(temp)){
  if(length(intersect(temp[i,6], temp[temp$keep==TRUE,5]))==1){
        temp$keep[i] = FALSE
        temp[temp[,5] == temp[i,6], 'arrows'] = 'to;from'
  }
  i=i+1
}

purine.path = temp[temp$keep, 1:4]
purine.path$FBgn = ''

temp.purine.path = purine.path

i=1
while(i<=nrow(purine.path)){  
  enzymeID = purine.path$enzyme[i]
  temp = names(nodeID[grep(enzymeID, nodeID)])
  temp = setNames(unlist(nodeID[temp], use.names = F), rep(names(nodeID[temp]), lengths(nodeID[temp])))
  temp = names(temp[temp == enzymeID])
  temp = row.names(GeneIDKey[GeneIDKey$ensembl %in% temp, ])
  temp2 = purine.path[rep(i, length(temp)),]
  temp2$FBgn = temp
  temp.purine.path = rbind(temp.purine.path,temp2)
  i = i +1
}

purine.path = temp.purine.path[(nrow(purine.path)+1):nrow(temp.purine.path),]
purine.path = purine.path[!duplicated(purine.path[,2:5]),]

TerminalPoints = data.frame(enzyme = "Excretion",
                            from = 'uric acid',
                            to = 'Excretion')

DNA.A = data.frame(enzyme = c('DNA.A'),
                 from = c('dATP'),
                 to = c('DNA.A'))
TerminalPoints = rbind(TerminalPoints, DNA.A)

DNA.G = data.frame(enzyme = c('DNA.G'),
                 from = c('dGTP'),
                 to = c('DNA.G'))
TerminalPoints = rbind(TerminalPoints, DNA.G)

RNA.A = data.frame(enzyme = c('RNA.A'),
                 from = c('ATP'),
                 to = c('RNA.A'))
TerminalPoints = rbind(TerminalPoints, RNA.A)

RNA.G = data.frame(enzyme = c('RNA.G'),
                 from = c('GTP'),
                 to = c('RNA.G'))
TerminalPoints = rbind(TerminalPoints, RNA.G)

Riboflavin.Metabolism = data.frame(enzyme = c('Riboflavin.Metabolism'),
                 from = c('GTP'),
                 to = c('Riboflavin.Metabolism'))
TerminalPoints = rbind(TerminalPoints, Riboflavin.Metabolism)

Folate.Biosynthesis = data.frame(enzyme = c('Folate.Biosynthesis'),
                 from = c('GTP'),
                 to = c('Folate.Biosynthesis'))
TerminalPoints = rbind(TerminalPoints, Folate.Biosynthesis)

PPP = data.frame(enzyme = c('Pentose Phosphate'),
                 from = c('Pentose Phosphate'),
                 to = c('IMP'))
TerminalPoints = rbind(TerminalPoints, PPP)

TerminalPoints = data.frame(enzyme = TerminalPoints$enzyme,
                            from = TerminalPoints$from,
                            to = TerminalPoints$to,
                            arrows = 'to',
                            FBgn = NA,
                            color = 'black',
                            width = 1,
                            symbol = NA,
                            fdr = NA,
                            GR = NA,
                            WT = NA,
                            title = '')

```

```{r include = F}

network.fun = function(comparison.T, comparison.M, cond1, cond2){
temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

visedges = purine.path
visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))

visedges$title = paste0(visedges$symbol,
                        "<br>FDR: ", visedges$fdr, 
                        "<br>",cond1," CPM: ", visedges$GR, 
                        "<br>",cond2," CPM: ", visedges$WT)
visedges = na.omit(visedges)
visedges = rbind(visedges, TerminalPoints)

node.names = unique(c(visedges$from, visedges$to))
node.data = data.frame(id = node.names,
                       color = 'dimgrey',
                       size = 10,
                       FC = NA,
                       pval = NA,
                       row.names = node.names)

row.names(comparison.M)[row.names(comparison.M) == "cAMP(2',3') / cAMP(3',5')"] = 'cAMP'

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = 
  node.data[names(node.colors),'size'] + 7.5*abs(node.colors)
node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2

node.colors = (node.colors*100)+201

node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color'] = node.colors

node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)

node.data[unique(TerminalPoints$enzyme), 'color'] = 'black'

node.data$group = 'metabolite'
node.data[node.data$color == 'black', 'group'] = "Outside Path"
node.data[node.data$color == 'dimgrey', 'group'] = "no data"

node.data$x = 1
node.data$y = 1
node.data["Excretion", 'x'] = -200
node.data["Excretion", 'y'] = 500

node.data["Pentose Phosphate" , 'x'] = 50
node.data["Pentose Phosphate" , 'y'] = -400

node.data["RNA.A", 'x'] = 850
node.data["RNA.A", 'y'] = -250

node.data["RNA.G", 'x'] = -1000
node.data["RNA.G", 'y'] = -250

node.data["Folate.Biosynthesis", 'x'] = -1000
node.data["Folate.Biosynthesis", 'y'] = -350

node.data["Riboflavin.Metabolism", 'x'] = -1000
node.data["Riboflavin.Metabolism", 'y'] = -150

node.data["DNA.A", 'x'] = 850
node.data["DNA.A", 'y'] = 250

node.data["DNA.G", 'x'] = -1000
node.data["DNA.G", 'y'] = 250

# passing custom nodes and/or edges
lnodes <- data.frame(label = c("Increased", "Decreased", "No Data"), 
shape = 'dot', color = c("firebrick", "royalblue",'dimgrey'),
 title = "")

nodes = node.data
visedges = visedges[,c('from', 'to', 'arrows', 'color', 'width', 'title')]

visNetwork(nodes,visedges,
                  main = paste0(cond1, " vs ", cond2))%>%
  visNodes(physics = T)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T, minVelocity = .5)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))%>%
    visLegend(addNodes = lnodes, useGroups = FALSE, width = .115)

}

```

```{r echo = F}

##tempF = apply(mean.cpm[,c("GR.F", "WT.F")], MARGIN = 1, mean)
##tempM = apply(mean.cpm[,c("GR.M", "WT.M")], MARGIN = 1, mean)
##tempF = names(tempF)[tempF>10]
##tempM = names(tempM)[tempM>10]
##cutoff.genes = unique(c(tempF, tempM))

##subset.genes = row.names(TKT.EdgeR)[TKT.EdgeR$GRxWT.FC < .05 | TKT.EdgeR$GRxWT.MC < .05]
##subset.genes = setdiff(subset.genes, row.names(TKT.EdgeR)[TKT.EdgeR$GRxWT.FC < .05 & TKT.EdgeR$GRxWT.MC < .05])
##subset.genes = intersect(subset.genes, cutoff.genes)

subset.genes = intersect(row.names(TKT.EdgeR.FC), unique(purine.path$FBgn))

FCx = TKT.EdgeR.FC[subset.genes, "GRxWT.FC"]
FCy = TKT.EdgeR.FC[subset.genes, "GRxWT.MC"]

set.size = F

volcano.data = data.frame(Symbol = GeneIDKey[subset.genes, "Symbol"], 
                          FCx = FCx,
                          FCy = FCy,
                          Color = 'grey',
                          size = 2.5,
                          FDR.F = TKT.EdgeR[subset.genes, "GRxWT.FC"],
                          FDR.M = TKT.EdgeR[subset.genes, "GRxWT.MC"],
                          GR.FC.cpm = mean.cpm[subset.genes, "GR.F"],
                          WT.FC.cpm = mean.cpm[subset.genes, "WT.F"],
                          GR.MC.cpm = mean.cpm[subset.genes, "GR.M"],
                          WT.MC.cpm = mean.cpm[subset.genes, "WT.M"],
                          tempcolor = FCx - FCy)

row.names(volcano.data) = subset.genes

volcano.data$Symbol[is.na(volcano.data$Symbol)] = row.names(volcano.data)[is.na(volcano.data$Symbol)]

main.title = "Female and Male G85R/WT FC, Sig. DEG in Males and Females G85R vs WT"

maxx= max(c(abs(min(FCx)),abs(max(FCx))))
maxy= max(c(abs(min(FCy)),abs(max(FCy))))

fig = plot_ly(data = volcano.data,
              x = ~FCx,
              y = ~FCy,
              type = 'scatter',
              mode = 'markers',
              marker = list(colorscale = list(c(0,.7,1), c("firebrick","ivory", "royalblue")),
                            reversescale =T,
                             colorbar = list(title = "delta FC",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                            color = ~tempcolor,
                            line = list(color = "black", width = 1.5),
                            size = 5*volcano.data$size),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\nFemale FDR: ", round(volcano.data$FDR.F,4),
                      "\nMale FDR: ", round(volcano.data$FDR.M,4),
                      "\nFemale mean cpm (G85R/WT): ", round(volcano.data$GR.FC.cpm, 1),
                      "/", round(volcano.data$WT.FC.cpm, 1),
                      "\nMale mean cpm(G85R/WT): ", round(volcano.data$GR.MC.cpm, 1),
                      "/", round(volcano.data$WT.MC.cpm, 1)))
fig = fig %>% layout(xaxis = list(title = "Female log2(FC)"),
                     yaxis = list(title = "Male log2(FC)"),
                     title = main.title,
                     shapes = list(
                       type = "line",
                       line = list(color = "black", dash = 'dash', width = 2),
                       x0 = floor(-maxx),
                       x1 = ceiling(maxx),
                       y0 = floor(-maxy),
                       y1 = ceiling(maxy)))

fig

```

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig1, fig.cap = 'G85R relative to WT. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.FC"
cond1 = 'GR.F'
cond2 = "WT.F"
comparison.M = GRxWT.C

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig2, fig.cap = 'G85R relative to WT. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.MC"
cond1 = 'GR.M'
cond2 = "WT.M"
comparison.M = GRxWT.C

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig3, fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.FDf"
cond1 = "TktDfGR.F"
cond2 = "TktDfWT.F"
comparison.M = GRxWT.Df

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig4, fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.MDf"
cond1 = "TktDfGR.M"
cond2 = "TktDfWT.M"
comparison.M = GRxWT.Df

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig5, fig.cap = 'G85R TKT-OE relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.FOE"
cond1 = "TktOEGR.F"
cond2 = "TktOEWT.F"
comparison.M = GRxWT.OE

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig6, fig.cap = 'G85R TKT-Df relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRxWT.MOE"
cond1 = "TktOEGR.M"
cond2 = "TktOEWT.M"
comparison.M = GRxWT.OE

network.fun(comparison.T, comparison.M, cond1, cond2)

```
<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig7, fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRF.CxDf"
cond2 = 'GR.F'
cond1 = "TktDfGR.F"
comparison.M = GR.CxDf

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig8, fig.cap = 'G85R control relative to G85R TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRM.CxDf"
cond2 = 'GR.M'
cond1 = "TktDfGR.M"
comparison.M = GR.CxDf

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig9, fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "WTF.CxDf"
cond2 = 'WT.F'
cond1 = "TktDfWT.F"
comparison.M = WT.CxDf

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig10, fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "WTM.CxDf"
cond2 = 'WT.M'
cond1 = "TktDfWT.M"
comparison.M = WT.CxDf

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig11, fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRF.CxOE"
cond2 = 'GR.F'
cond1 = "TktOEGR.F"
comparison.M = GR.CxOE

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig12, fig.cap = 'G85R control relative to G85R TKT-OE. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "GRM.CxOE"
cond2 = 'GR.M'
cond1 = "TktOEGR.M"
comparison.M = GR.CxOE

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig13, fig.cap = 'WT control relative to WT TKT-OE. Transcriptomic data is from females and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "WTF.CxOE"
cond2 = 'WT.F'
cond1 = "TktOEWT.F"
comparison.M = WT.CxOE

network.fun(comparison.T, comparison.M, cond1, cond2)

```

<br><br><br>

```{r echo = F, fig.height=9, fig.width=12, fig.align='left', fig14, fig.cap = 'WT control relative to WT TKT-Df. Transcriptomic data is from males and metabolomic data is from both sexes. Node and arrow size and color '}

comparison.T = "WTM.CxOE"
cond2 = 'WT.M'
cond1 = "TktOEWT.M"
comparison.M = WT.CxOE

network.fun(comparison.T, comparison.M, cond1, cond2)

```

### 2024-01-17 mtDNA-nucDNA analysis/20231214_John_WT.GR_RpL32.mtCoI.Rmd
update

---
title: "John CoI and RpL32 in G85R and WT Analysis"
author: "John Santiago"
date: "2023-12-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, include = F}
library(plotly)
CoI.data = read.csv("/Users/johncsantiago/Documents/20231214_John_WT.GR_RpL32.mtCoI.csv")
CoI.data$Genotype = substr(CoI.data$Sample,1,2)
CoI.data$Sex = substr(CoI.data$Sample,3,3)
CoI.data$Rep = substr(CoI.data$Sample,4,nchar(CoI.data$Sample))
CoI.data$Primer = CoI.data$Target

CoI.data = CoI.data[CoI.data$Well != 'F1',]

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Target == "RpL32" & nchar(CoI.data$Rep) == 1,]

plotdata$x = factor(paste0(plotdata$Genotype, plotdata$Sex, plotdata$Rep), 
                    levels = c(unique(paste0(plotdata$Genotype, plotdata$Sex, plotdata$Rep))))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "Genotype",
     main = "RpL32",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "firebrick",
       col = "black")

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Target == "CoI" & nchar(CoI.data$Rep) == 1,]

plotdata$x = factor(paste0(plotdata$Genotype, plotdata$Sex, plotdata$Rep), 
                    levels = c(unique(paste0(plotdata$Genotype, plotdata$Sex, plotdata$Rep))))

plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "Genotype",
     main = "CoI",
     las = 2)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "steelblue",
       col = "black")

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Genotype == "WT" & 
                      CoI.data$Sex == "M" &
                      CoI.data$Rep != '2' &
                      CoI.data$Rep != '3' &
                      CoI.data$Primer == 'RpL32',]
plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample, plotdata$Primer)))
plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "RpL32 Efficiency",
     las = 2,
     cex = .1)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "firebrick",
       col = "black")

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Genotype == "WT" & 
                      CoI.data$Sex == "M" &
                      CoI.data$Rep != '2' &
                      CoI.data$Rep != '3' &
                      CoI.data$Primer == 'RpL32',]
plotdata$concentration = plotdata$Rep
plotdata$concentration[plotdata$Rep == 1] = 5
plotdata$concentration[plotdata$Rep == '1_2.5'] = 2.5
plotdata$concentration[plotdata$Rep == '1_10'] = 10

plotdata$x = log2(as.numeric(plotdata$concentration))
plotdata$Cq = as.numeric(plotdata$Cq)

plot(y = plotdata$Cq,
     x = plotdata$x, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "firebrick",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)")

linearmodel=lm(as.numeric(plotdata$Cq)~plotdata$x)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="firebrick",lwd=2)
text(x = 1.75, y = 20,paste0("RpL32 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)
RpL32.slope = linearmodel[[1]][2]

RpL32.E = (-1+2^(-1/RpL32.slope))*100
text(x = 1.75, y = 19.85,paste0("RpL32 Efficiency = ", signif(RpL32.E,3)),cex=.8)

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Genotype == "WT" & 
                      CoI.data$Sex == "M" &
                      CoI.data$Rep != '2' &
                      CoI.data$Rep != '3' &
                      CoI.data$Primer == 'CoI',]
plotdata$x = factor(plotdata$Sample, 
                    levels = c(unique(plotdata$Sample, plotdata$Primer)))
plotdata$Cq = as.numeric(plotdata$Cq)

boxplot(plotdata$Cq~plotdata$x,
     ylab = "Quantification Cycle (Cq)",
     xlab = "",
     main = "CoI Efficiency",
     las = 2,
     cex = .1)

points(x = plotdata$x,
       y = plotdata$Cq,
       cex = 1.5,
       pch = 21,
       bg = "steelblue",
       col = "black")

```

```{r echo = F}

plotdata = CoI.data[CoI.data$Genotype == "WT" & 
                      CoI.data$Sex == "M" &
                      CoI.data$Rep != '2' &
                      CoI.data$Rep != '3' &
                      CoI.data$Primer == 'CoI',]
plotdata$concentration = plotdata$Rep
plotdata$concentration[plotdata$Rep == 1] = 5
plotdata$concentration[plotdata$Rep == '1_2.5'] = 2.5
plotdata$concentration[plotdata$Rep == '1_10'] = 10

plotdata$x = log2(as.numeric(plotdata$concentration))
plotdata$Cq = as.numeric(plotdata$Cq)

plot(y = plotdata$Cq,
     x = plotdata$x, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "steelblue",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)")

linearmodel=lm(as.numeric(plotdata$Cq)~plotdata$x)
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="steelblue",lwd=2)
text(x = 1.75, y = 13.65,paste0("CoI slope = ", signif(linearmodel[[1]][2],3)),cex=.8)
CoI.slope = linearmodel[[1]][2]

CoI.E = (-1+2^(-1/CoI.slope))*100
text(x = 1.75, y = 13.5,paste0("CoI Efficiency = ", signif(CoI.E,3)),cex=.8)

```

```{r echo = F, include = F}

CoI.only = CoI.data[CoI.data$Primer == "CoI" & nchar(CoI.data$Rep) == 1,
                    c("Sample", "Cq", "Primer")]
RpL32.only = CoI.data[CoI.data$Primer == "RpL32" & nchar(CoI.data$Rep) == 1,
                      c("Sample", "Cq", "Primer")]

plotdata = rbind(CoI.only, RpL32.only)

plotdata$Cq = as.numeric(plotdata$Cq)
plotdata$Primer = as.factor(plotdata$Primer)

plot.colors = c("steelblue", "firebrick")

fig =  plot_ly(data = plotdata,
          x = ~Sample,
          y = ~Cq,
          name = ~Primer,
          type = 'scatter',
          mode = 'markers',
          color = ~Primer,
          colors = plot.colors,
          marker = list(size = 10,
                        line = list(color = 'black', width = .5)))

fig

```

```{r echo = F}

plotdata = CoI.data[nchar(CoI.data$Rep) == 1,
                    c("Sample", "Cq", "Primer")]
plotdata$SP = paste0(plotdata$Sample, plotdata$Primer)
plotdata$Cq = as.numeric(plotdata$Cq)
mean.Ct = data.frame(Sample = unique(plotdata$Sample),
                     Genotype = factor(substr(unique(plotdata$Sample),1,3), 
                                       levels = c('WTF', 'WTM', 'GRF', 'GRM')),
                     Sex = substr(unique(plotdata$Sample), 3,3),
                     CoI = 0,
                     RpL32 = 0)
mean.Ct = mean.Ct[order(mean.Ct$Genotype),]

i=1
while(i <= nrow(mean.Ct)){
  mean.Ct$CoI[i] = mean(plotdata[plotdata$SP == paste0(mean.Ct$Sample[i], 'CoI'),'Cq'])
  mean.Ct$RpL32[i] = mean(plotdata[plotdata$SP == paste0(mean.Ct$Sample[i], 'RpL32'),'Cq'])
  i = i + 1
}

mean.Ct$dCt = mean.Ct$CoI - mean.Ct$RpL32
mean.Ct$FC = 2^-mean.Ct$dCt

boxplot(mean.Ct$dCt~mean.Ct$Genotype,
     ylab = "dCT",
     xlab = "Genotype",
     main = "dCT")

points(x = mean.Ct$Genotype,
       y = mean.Ct$dCt,
       cex = 1.5,
       pch = 21,
       bg = c(rep("firebrick", 6), rep('steelblue', 6)),
       col = "black")

```

```{r echo = F}

boxplot(mean.Ct$FC~mean.Ct$Genotype,
     ylab = "FC",
     xlab = "Genotype",
     main = "FC")

points(x = mean.Ct$Genotype,
       y = mean.Ct$FC,
       cex = 1.5,
       pch = 21,
       bg = c(rep("firebrick", 6), rep('steelblue', 6)),
       col = "black")

```
\newpage

```{r}

dCT.aov = aov(mean.Ct$dCt~mean.Ct$Genotype)

summary(dCT.aov)
```

```{r}

TukeyHSD(dCT.aov)

```

```{r echo = F}

mean.dCt = data.frame(Genotype = unique(mean.Ct$Genotype), 
                      mean.dCt = 0)
mean.dCt$mean.dCt[1] = mean(mean.Ct[mean.Ct$Genotype == mean.dCt$Genotype[1], 'dCt'])
mean.dCt$mean.dCt[2] = mean(mean.Ct[mean.Ct$Genotype == mean.dCt$Genotype[2], 'dCt'])
mean.dCt$mean.dCt[3] = mean(mean.Ct[mean.Ct$Genotype == mean.dCt$Genotype[3], 'dCt'])
mean.dCt$mean.dCt[4] = mean(mean.Ct[mean.Ct$Genotype == mean.dCt$Genotype[4], 'dCt'])
row.names(mean.dCt) = mean.dCt$Genotype

Male_fc = 2^-(mean.dCt['GRM',2] - mean.dCt['WTM',2])
Female_fc = 2^-(mean.dCt['GRF',2] - mean.dCt['WTF',2])

print(paste0("Relative mtDNA levels in Male G85R/WT = ", signif(Male_fc, 3)))

print(paste0("Relative mtDNA levels in Female G85R/WT = ", signif(Female_fc, 3)))

```

### 2024-01-17 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FA1_STAR.sh

@@ -1,0 +1,45 @@
+#!/bin/bash
+
+#SBATCH -J A3FA1_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G A3FA1_STAR.sh
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+sample="A3FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20 --outSAMtype BAM SortedByCoordinate --outFileNamePrefix $stardir"Output_Files/BAM/"$sample
[…]

### 2024-01-17 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FA2_A3FA3_STAR.sh

@@ -1,0 +1,80 @@
+#!/bin/bash
+
+#SBATCH -J A3FA2_A3FA3_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G A3FA2_A3FA3_STAR.sh
+
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="A3FA2"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-17 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FH1_A3FH2_A3FH3_STAR.sh

@@ -1,0 +1,111 @@
+#!/bin/bash
+
+#SBATCH -J A3FH1_A3FH2_A3FH3_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G A3FH1_A3FH2_A3FH3_STAR.sh
+
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="A3FH1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-17 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FT_A3MA_A3MH_A3MT_STAR.sh

@@ -1,0 +1,427 @@
+#!/bin/bash
+
+#SBATCH -J A3FT_A3MA_A3MH_A3MT_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 --mem=64G A3FT_A3MA_A3MH_A3MT_STAR.sh
+
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="A3FT1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A40FA_A40FH_A40FT_STAR.sh
a4v temp update

@@ -1,0 +1,323 @@
+#!/bin/bash
+
+
+#SBATCH -J A40FA_A40FH_A40FT_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 -N 2 --mem=64G A40FA_A40FH_A40FT_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="A40FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A9F_A9M_STAR.sh

@@ -1,0 +1,634 @@
+#!/bin/bash
+
+
+#SBATCH -J A9F_A9M_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 -N 2 --mem=64G A9F_A9M_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="A9FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S3F_S3M_STAR.sh

@@ -1,0 +1,634 @@
+#!/bin/bash
+
+
+#SBATCH -J S3F_S3M_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 -N 2 --mem=64G S3F_S3M_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="S3FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-01-22 A4V_BodySections_RNAseq/R code/A4V_PCA.Rmd
PCA

---
title: "A4V PCA"
author: "John Santiago"
date: "2024-01-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=F, include=F}

library(plotly)
library(edgeR)

sample.names = list.files("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/")

temp = read.csv(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/", sample.names[1]), sep = '\t', row.names = 1)

countdata = data.frame(temp = temp)
colnames(countdata)[1] = substr(sample.names[1], 1, nchar(sample.names[1])-15)

i=2
while(i <= length(sample.names)){
  temp = read.csv(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/", sample.names[i]), sep = '\t', row.names = 1)
  countdata = cbind(countdata, temp[row.names(countdata),1])
  colnames(countdata)[i] = substr(sample.names[i], 1, nchar(sample.names[i])-15)
  i=i+1
}

##normalize data
x <- countdata
gr <- factor(substr(colnames(countdata), 1, nchar(colnames(countdata))-1))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
cpmdata=cpm(z)

```

```{r echo=F, include=F}

pca <- prcomp(t(cpmdata), scale.=TRUE) 
gr <- colnames(cpmdata)
PC1=scale(pca$x[,1])
PC2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=gr,
                        ##PC1=scale(pca$x[,1]),
                        ##PC2=scale(pca$x[,2]),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=substr(gr, 1, 1), 
                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
                        Age=substr(gr, 2, nchar(gr)-3),
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group= paste0(substr(gr, 1, 1),
                                      substr(gr, nchar(gr)-2, nchar(gr)-1)),
                        pca.color = substr(gr, nchar(gr)-1, nchar(gr)-1),
                        pca.shape = substr(gr, nchar(gr)-2, nchar(gr)-2))

fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~pca.color,
                 symbol = ~pca.shape,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
                 marker = list(size = 15,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
```

```{r}

  fig

```

### 2024-03-22 A4V BMP Signaling Genes Analysis.Rmd
overdue update

---
title: "BMP Signaling Genes"
author: "John Santiago"
date: "2024-02-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, message = F}

library(heatmaply)
library(dendextend)

counts = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.countdata.csv", row.names = 1)

cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)

meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)

FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)

FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)

meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)

bmp = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/BMP Signaling Genes.csv', row.names = 1, header = F)

bmp$fb = row.names(bmp)

bmpcpm = cpm[intersect(row.names(bmp), row.names(cpm)),]

GR.bmp = GR.cpm[intersect(row.names(GR.cpm), row.names(bmp)),]

GR.mean = matrix(rep(0, 12*nrow(GR.bmp)), ncol = 12)
colnames(GR.mean) = unique(GR.meta$Group)
row.names(GR.mean) = row.names(GR.bmp)

i = 1
while(i <= ncol(GR.mean)){
  GR.mean[,i] = apply(GR.bmp[,row.names(GR.meta)[GR.meta$Group == colnames(GR.mean)[i]]], 1, mean)
  i = i +1
}

GR.mean.meta = GR.meta[GR.meta$Replicate == 1, c(1:3,5)]
row.names(GR.mean.meta) = GR.mean.meta$Group

```

```{r echo = F}

hmgroups = meta[meta$Section=='Thorax' & meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "T_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Fhmdata=t(scale(t(hmdata)))
Fsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Fsidecols)=colnames(Fhmdata)

hmgroups = meta[meta$Section=='Thorax' & meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "T_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Mhmdata=t(scale(t(hmdata)))
Msidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Msidecols)=colnames(Mhmdata)

Thmdata = cbind(Fhmdata, Mhmdata)
row.names(Thmdata) = bmp[row.names(Thmdata),1]
Tsidecols = rbind(Fsidecols, Msidecols)

hmgroups = meta[meta$Section=='Head' & meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "H_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Fhmdata=t(scale(t(hmdata)))
Fsidecols=data.frame("Tissue" = "Head",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Fsidecols)=colnames(Fhmdata)

hmgroups = meta[meta$Section=='Head' & meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "H_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Mhmdata=t(scale(t(hmdata)))
Msidecols=data.frame("Tissue" = "Head",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Msidecols)=colnames(Mhmdata)

Hhmdata = cbind(Fhmdata, Mhmdata)
row.names(Hhmdata) = bmp[row.names(Hhmdata),1]
Hsidecols = rbind(Fsidecols, Msidecols)

hmgroups = meta[meta$Section=='Abdomen' & meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "A_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Fhmdata=t(scale(t(hmdata)))
Fsidecols=data.frame("Tissue" = "Abdomen",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Fsidecols)=colnames(Fhmdata)

hmgroups = meta[meta$Section=='Abdomen' & meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, "A_rep", hmgroups$Replicate)
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpcpm[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID
Mhmdata=t(scale(t(hmdata)))
Msidecols=data.frame("Tissue" = "Abdomen",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(Msidecols)=colnames(Mhmdata)

Ahmdata = cbind(Fhmdata, Mhmdata)
row.names(Ahmdata) = bmp[row.names(Ahmdata),1]
Asidecols = rbind(Fsidecols, Msidecols)

```

```{r echo = F, include = F}

hmdata = cbind(cbind(Hhmdata, Thmdata), Ahmdata)
sidecols = rbind(rbind(Hsidecols, Tsidecols), Asidecols)

heatmaply(hmdata,
          trace="none",
          col=RdYlBu(100)[100:1],
          scale="none",
          dendrogram = "row",
          Rowv=T,
          Colv=F,
          cexRow = .75,
          na.value="black",
          labRow = row.names(hmdata),
          col_side_colors = sidecols)

```

```{r echo = F}

mean.meta = meta[meta$Replicate == '1', c(1:4,6)]
row.names(mean.meta) = mean.meta$Group
bmpmean = meancpm[intersect(row.names(meancpm),row.names(bmp)),]

hmgroups = mean.meta[mean.meta$Section=='Thorax' & mean.meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

TFhmdata=t(scale(t(hmdata)))
TFsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(TFsidecols)=colnames(TFhmdata)

hmgroups = mean.meta[mean.meta$Section=='Thorax' & mean.meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

TMhmdata=t(scale(t(hmdata)))
TMsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(TMsidecols)=colnames(TMhmdata)

Thmdata = cbind(TFhmdata, TMhmdata)
row.names(Thmdata) = bmp[row.names(Thmdata),1]
Tsidecols = rbind(TFsidecols, TMsidecols)

hmgroups = mean.meta[mean.meta$Section=='Head' & mean.meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

HFhmdata=t(scale(t(hmdata)))
HFsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(HFsidecols)=colnames(HFhmdata)

hmgroups = mean.meta[mean.meta$Section=='Head' & mean.meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

HMhmdata=t(scale(t(hmdata)))
HMsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(HMsidecols)=colnames(HMhmdata)

Hhmdata = cbind(HFhmdata, HMhmdata)
row.names(Hhmdata) = bmp[row.names(Hhmdata),1]
Hsidecols = rbind(HFsidecols, HMsidecols)

hmgroups = mean.meta[mean.meta$Section=='Abdomen' & mean.meta$Sex == "F",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

AFhmdata=t(scale(t(hmdata)))
AFsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(AFsidecols)=colnames(AFhmdata)

hmgroups = mean.meta[mean.meta$Section=='Abdomen' & mean.meta$Sex == "M",]
hmgroups$Age[nchar(hmgroups$Age) ==1] = paste0("0",hmgroups$Age[nchar(hmgroups$Age) ==1])
hmgroups$ID = paste0(substr(hmgroups$Genotype,1,1), hmgroups$Age, hmgroups$Sex, substr(hmgroups$Section,1,1))
hmgroups=hmgroups[order(hmgroups$ID),]
hmdata = bmpmean[, row.names(hmgroups)]
colnames(hmdata) = hmgroups$ID

AMhmdata=t(scale(t(hmdata)))
AMsidecols=data.frame("Tissue" = "Thorax",
                     "Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype,
                     "Age" = hmgroups$Age)
row.names(AMsidecols)=colnames(AMhmdata)

Ahmdata = cbind(AFhmdata, AMhmdata)
row.names(Ahmdata) = bmp[row.names(Ahmdata),1]
Asidecols = rbind(AFsidecols, AMsidecols)

```

```{r echo = F, include = F}

hmdata = TMhmdata
row.names(hmdata) = bmp[row.names(hmdata),1]
sidecols = TMsidecols

heatmaply(hmdata,
          trace="none",
          col=RdYlBu(100)[100:1],
          scale="none",
          dendrogram = "row",
          Rowv=T,
          Colv=F,
          cexRow = .75,
          na.value="black",
          labRow = row.names(hmdata),
          col_side_colors = sidecols)

```

```{r echo = F}

hmcluster = function(clusternum, allscaled, Title){

dnd=cut(as.dendrogram(hc),h=cutheight)
cluster=row.names(scaled)[unlist(dnd$lower[[clusternum]])]

row.names(allscaled) = bmp[row.names(allscaled), 1]
df = allscaled[cluster[length(cluster):1],] %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

meandf = bmpmean
row.names(meandf) = bmp[row.names(meandf),1]
meandf = meandf[cluster[length(cluster):1],]
temp = hm.meta[hm.meta$Replicate == 1,]
row.names(temp) = temp$Group
colnames(meandf) = temp[colnames(meandf), 'ID']
meandf =  as.matrix(meandf[, colnames(allscaled)])
meandf = meandf %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

rep1df = bmpcpm
row.names(rep1df) = bmp[row.names(rep1df),1]
rep1df = rep1df[cluster[length(cluster):1], row.names(hm.meta)[hm.meta$Replicate == 1]]
colnames(rep1df) = hm.meta[colnames(rep1df), 'ID']
rep1df =  as.matrix(rep1df[, colnames(allscaled)])
rep1df = rep1df %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

rep2df = bmpcpm
row.names(rep2df) = bmp[row.names(rep2df),1]
rep2df = rep2df[cluster[length(cluster):1], row.names(hm.meta)[hm.meta$Replicate == 2]]
colnames(rep2df) = hm.meta[colnames(rep2df), 'ID']
rep2df =  as.matrix(rep2df[, colnames(allscaled)])
rep2df = rep2df %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

rep3df = bmpcpm
row.names(rep3df) = bmp[row.names(rep3df),1]
rep3df = rep3df[cluster[length(cluster):1], row.names(hm.meta)[hm.meta$Replicate == 3]]
colnames(rep3df) = hm.meta[colnames(rep3df), 'ID']
rep3df =  as.matrix(rep3df[, colnames(allscaled)])
rep3df = rep3df %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

FBgn = bmp
row.names(FBgn) = FBgn[,1]

df$mean = meandf$value
df$rep1 = rep1df$value
df$rep2 = rep2df$value
df$rep3 = rep3df$value
df$fbgn = FBgn[as.character(df$row), 'fb']

fig = plot_ly(x = df$col, 
              y = df$row,
              z = df$value,
              type = "heatmap",
              colors = RdYlBu(100)[100:1],
              hoverinfo = "text",
              hovertext = paste("Sample:", df$col,
                                "\nGene Symbol: ", df$row,
                                "\nGene FBgn: ", df$fbgn,
                                "\nMean CPM: ", signif(df$mean, 3),
                                "\nRep1 CPM: ", signif(df$rep1, 3),
                                "\nRep2 CPM: ", signif(df$rep2, 3),
                                "\nRep3 CPM: ", signif(df$rep3, 3)))

fig = fig %>% layout(title = paste(Title, " cluster ",clusternum, " genes"),
                     xaxis = list(title = ""),
                     yaxis = list(title = ""),
                     shapes = list(
                       list(
                         type = "rect",
                         fillcolor = 'deeppink',
                         line = list(color = "deeppink", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = -.5,
                         x1 = 2.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1,
                         textposition = "inside",
                         textinfo = "label"),
                       list(
                         type = "rect",
                         fillcolor = 'khaki',
                         line = list(color = "khaki", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 2.5,
                         x1 = 5.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         fillcolor = 'deepskyblue',
                         line = list(color = "deepskyblue", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 5.5,
                         x1 = 7.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         fillcolor = 'slategray',
                         line = list(color = "slategray", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 7.5,
                         x1 = 9.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         line = list(color = "black", dash = 'none', width = 6),
                         opacity = 1,
                         x0 = -.5,
                         x1 = 9.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = -.5,
                         x1 = 9.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)-.5),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 2.5,
                         x1 = 2.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 7.5,
                         x1 = 7.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 5.5,
                         x1 = 5.5,
                         y0 = -.5,
                         y1 = length(cluster)+1)))

fig = fig %>% add_annotations(x = c(1, 4, 6.5, 8.5), 
                              y = length(cluster)+.25, 
                              text = c("A4V Females", 
                                       "Silent Females", 
                                       "A4V Males", 
                                       "Silent Males"), 
                              font = list(color = '#000000', size = 14), 
                              showarrow = F)

return(fig)

}

```

```{r echo = F, fig.height=10}

scaled = HFhmdata
allscaled = cbind(HFhmdata, HMhmdata)
Title = "Female Head"
branches=3

hm.meta = meta
hm.meta$Age[nchar(hm.meta$Age) ==1] = paste0("0",hm.meta$Age[nchar(hm.meta$Age) ==1])
hm.meta$ID = paste0(substr(hm.meta$Genotype,1,1), hm.meta$Age, hm.meta$Sex, substr(hm.meta$Section,1,1))

row.names(scaled) = bmp[row.names(scaled),1]

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

scaled = HMhmdata
Title = "Male Head"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

scaled = TFhmdata
allscaled = cbind(TFhmdata, TMhmdata)
Title = "Female Thorax"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

scaled = TMhmdata
Title = "Male Thorax"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

scaled = AFhmdata
allscaled = cbind(AFhmdata, AMhmdata)
Title = "Female Abdomen"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

scaled = AMhmdata
Title = "Male Abdomen"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('GR.M', 'TktDfGR.M', 'TktOEGR.M',
                      'WT.M', 'TktDfWT.M', 'TktOEWT.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('GR.F', 'TktDfGR.F', 'TktOEGR.F',
                      'WT.F', 'TktDfWT.F', 'TktOEWT.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata,Mhmdata)

Fsidecols=data.frame("Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype)
row.names(Fsidecols)=colnames(Fhmdata)

scaled = Fhmdata
Title = "Female Larvae"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

GR.hmcluster = function(clusternum, allscaled, Title){
dnd=cut(as.dendrogram(hc),h=cutheight)
cluster=row.names(scaled)[unlist(dnd$lower[[clusternum]])]

row.names(allscaled) = bmp[row.names(allscaled), 1]
df = allscaled[cluster[length(cluster):1],] %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

meandf = GR.mean
row.names(meandf) = bmp[row.names(meandf),1]
meandf = meandf[cluster[length(cluster):1],]
meandf =  as.matrix(meandf[, colnames(allscaled)])
meandf = meandf %>%
  reshape2::melt() %>%
  dplyr::rename(row=Var1,col=Var2)

FBgn = bmp
row.names(FBgn) = FBgn[,1]

df$mean = meandf$value
df$fbgn = FBgn[as.character(df$row), 'fb']

fig = plot_ly(x = df$col, 
              y = df$row,
              z = df$value,
              type = "heatmap",
              colors = RdYlBu(100)[100:1],
              hoverinfo = "text",
              hovertext = paste("Sample:", df$col,
                                "\nGene Symbol: ", df$row,
                                "\nGene FBgn: ", df$fbgn,
                                "\nMean CPM: ", signif(df$mean, 3)))

fig = fig %>% layout(title = paste(Title, " cluster ",clusternum, " genes"),
                     xaxis = list(title = ""),
                     yaxis = list(title = ""),
                     shapes = list(
                       list(
                         type = "rect",
                         fillcolor = 'deeppink',
                         line = list(color = "deeppink", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = -.5,
                         x1 = 2.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         fillcolor = 'khaki',
                         line = list(color = "khaki", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 2.5,
                         x1 = 5.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         fillcolor = 'deepskyblue',
                         line = list(color = "deepskyblue", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 5.5,
                         x1 = 8.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         fillcolor = 'slategray',
                         line = list(color = "slategray", dash = 'none', width = 1),
                         opacity = 1,
                         x0 = 8.5,
                         x1 = 11.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)+1),
                       list(
                         type = "rect",
                         line = list(color = "black", dash = 'none', width = 6),
                         opacity = 1,
                         x0 = -.5,
                         x1 = 11.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = -.5,
                         x1 = 11.5,
                         y0 = length(cluster)-.5,
                         y1 = length(cluster)-.5),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 2.5,
                         x1 = 2.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 8.5,
                         x1 = 8.5,
                         y0 = -.5,
                         y1 = length(cluster)+1),
                       list(
                         type = 'line',
                         line = list(color = "black", dash = 'none', width = 6),
                         x0 = 5.5,
                         x1 = 5.5,
                         y0 = -.5,
                         y1 = length(cluster)+1)))

fig = fig %>% add_annotations(x = c(1, 4, 7, 10), 
                              y = length(cluster)+.25, 
                              text = c("G85R Females", 
                                       "Silent Females", 
                                       "G85R Males", 
                                       "Silent Males"), 
                              font = list(color = '#000000', size = 14), 
                              showarrow = F)

return(fig)

}

```

```{r echo = F}

GR.hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

GR.hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

GR.hmcluster(clusternum = 3, allscaled, Title)

```

```{r echo = F, fig.height=10}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('GR.F', 'TktDfGR.F', 'TktOEGR.F',
                      'WT.F', 'TktDfWT.F', 'TktOEWT.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('GR.M', 'TktDfGR.M', 'TktOEGR.M',
                      'WT.M', 'TktDfWT.M', 'TktOEWT.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata,Mhmdata)

Msidecols=data.frame("Sex" = hmgroups$Sex,
                     "Genotype" = hmgroups$Genotype)
row.names(Msidecols)=colnames(Mhmdata)

scaled = Mhmdata
Title = "Male Larvae"
branches=3

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r echo = F}

GR.hmcluster(clusternum = 1, allscaled, Title)

```

```{r echo = F}

GR.hmcluster(clusternum = 2, allscaled, Title)

```

```{r echo = F}

GR.hmcluster(clusternum = 3, allscaled, Title)

```

##Heatmap of Fold Changes
```{r echo = F, fig.height=10}

hmdata = FC[intersect(row.names(FC), row.names(bmp)), c("AvS3FH", "AvS9FH", "AvS40FH",
                                                        "AvS3MH", "AvS9MH",
                                                        "AvS3FT", "AvS9FT", "AvS40FT",
                                                        "AvS3MT", "AvS9MT",
                                                        "AvS3FA", "AvS9FA", "AvS40FA",
                                                        "AvS3MA", "AvS9MA")]

hmFDR = FDR[row.names(hmdata), colnames(hmdata)]

colnames(hmdata) = c('A3FH', 'A9FH', 'A40FH',
                     'A3MH', 'A9MH',
                     'A3FT', 'A9FT', 'A40FT',
                     'A3MT', 'A9MT',
                     'A3FA', 'A9FA', 'A40FA',
                     'A3MA', 'A9MA')
scaled=t(scale(t(hmdata)))

Title = "Fold Change Data"
branches=6

row.names(scaled) = bmp[row.names(scaled),1]

colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

scaled[hmFDR>.05] = NA

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_DEG_Analyses.Rmd
overdue update

--- 2023-08-07 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
@@
 ---
-title: "G85R vs WT (M + F)"
+title: "A4V PCA"
 author: "John Santiago"
-date: "2023-07-11"
+date: "2024-01-22"
 output: html_document
@@
 
-```{r echo = F, include=F}
-##Load Libraries
+```{r echo=F, include=F}
 
-library(biomaRt)
+library(plotly)
+library(edgeR)
+library(goseq)
 library(org.Dm.eg.db)
-library(goseq)
-library(GO.db)
-library(visNetwork)
 library(rrvgo)
-library(plotly)
-library(KEGGREST)
-library(pathview)
 library(VennDiagram)
-library(heatmaply)
+
 ```
 
-```{r, echo = F, include = F}
+```{r}
 
-##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
-cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
-groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
-TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
+cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
+
+meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
+
+FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
+
+FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
+
+meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
 
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
-kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
-kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)
-
-genesingo=as.list(org.Dm.egGO2ALLEGS)
-
-##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
-mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
-colnames(mean.cpm) = unique(groups$Group)
-row.names(mean.cpm) = row.names(cpmdata)
-i=1
-while(i<=ncol(mean.cpm)){
-  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
-  i=i+1
-}
-
-i=1
-for(i in 1:ncol(TKT.EdgeR)){
-  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
-  i=i+1
-}
 
@@
 
+```{r echo = F}
+
+sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
+sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
+sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
+sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]
+
+GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+
+sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
+sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
+
+A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
+A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
+GR = setdiff(sigsGR.FxM, sigsWT.FxM)
+
+##Sample titles as strings. Only fill in up to your number of selected categories
+set1="A4V 3-day"
+set2="A4V 9-day"
+set3="G85R Larvae"
+set4=""
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=A3
+s2=A9
+s3=GR
+s4=""
+
+T3 = A3
+T9 = A9
+
+```
+
+```{r}
+
+##Triple Venn
+grid.newpage()
+draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
+
+```
+
+```{r echo = F}
+
+sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
+sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
+sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
+sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]
+
+GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+
+sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
+sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
+
+A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
+A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
+GR = setdiff(sigsGR.FxM, sigsWT.FxM)
+
+##Sample titles as strings. Only fill in up to your number of selected categories
+set1="A4V 3-day"
+set2="A4V 9-day"
+set3="G85R Larvae"
+set4=""
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=A3
+s2=A9
+s3=GR
+s4=""
+
+H3=A3
+H9=A9
+
+```
+
+```{r}
+
+##Triple Venn
+grid.newpage()
+draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
+
+```
+
+```{r echo = F}
+
+sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
+sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
+sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
+sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]
+
+GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+
+sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
+sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
+
+A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
+A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
+GR = setdiff(sigsGR.FxM, sigsWT.FxM)
+
+##Sample titles as strings. Only fill in up to your number of selected categories
+set1="A4V 3-day"
+set2="A4V 9-day"
+set3="G85R Larvae"
+set4=""
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=A3
+s2=A9
+s3=GR
+s4=""
+
+A3=A3
+A9=A9
+
+```
+
+```{r}
+
+##Triple Venn
+grid.newpage()
+draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
+
+```
+
 ```{r echo = F, include = F}
 
-##GR vs WT Females
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
-bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
-bg2 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]
-
-sigs = intersect(sigs1, sigs2)
-bg = unique(c(bg1, bg2))
+sigs = setdiff(setdiff(T9,T3),GR)
+bg = row.names(FDR)
 
 sigsKEY = GeneIDKey[sigs,]
-sigs = sigsKEY$Symbol
+sigs = na.omit(sigsKEY$Symbol)
 bgKEY = GeneIDKey[bg,]
-bg = bgKEY$Symbol
+bg = na.omit(bgKEY$Symbol)
 
@@
 GO.ontology = "BP"
-go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$adjp), go_analysis)
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
 
@@
 
-```{r include = F, echo = F}
+```{r echo=F, include=F}
 
-GOID = "GO:0005634"
-GenesInGO = genesingo[GOID]
+pca <- prcomp(t(A4V.cpm), scale.=TRUE) 
+gr <- colnames(A4V.cpm)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
 
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)),
+                        pca.color = substr(gr, nchar(gr)-1, nchar(gr)-1),
+                        pca.shape = substr(gr, nchar(gr)-2, nchar(gr)-2))
 
-```
-
-```{r include = F, echo = F}
-
-ParentID = "GO:0044271"
-GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
-GOID = GOIDs[1]
-GenesInParent= unique(genesingo[[GOID]])
-i=2
-while(i<=length(GOIDs)){
-  GOID = GOIDs[i]
-  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
-  i=i+1
-}
-
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]
-
-```
-
-```{r echo =F, warnings = F}
-
-comparison = "GRxWT.FC"
-comparison2 = "GRxWT.MC"
-
-hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]
-
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
-}
-
-hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
-}
-
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
-
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
-
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
-
-```
-
-##############
-## GRxWT Df ##
-##############
-
-```{r echo = F, include = F}
-
-comparison1 = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-sigs = sigsKEY$Symbol
-
-sig.cats = Enrichment(sigs)
-
-```
-
-```{r echo = F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
-
-```
-
-```{r, fig.width= 10}
-
-BP.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-CC.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-MF.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-KEGG.fig
-
-```
-
-```{r echo =F, warnings = F}
-
-comparison = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-##hmdata = cpmdata[GenesInGO, groups$Group == "GR.F" | groups$Group == "WT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "GR.F" | groups$Group == "WT.F"]
-
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
-}
-
-##hmdata2 = cpmdata[GenesInGO, groups$Group == "GR.M" | groups$Group == "WT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "GR.M" | groups$Group == "WT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
-}
-
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
-
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
-
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
-
-```
-
-##############
-## GRxWT OE ##
-##############
-
-```{r echo = F, include = F}
-
-comparison1 = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-sigs = sigsKEY$Symbol
-
-sig.cats = Enrichment(sigs)
-
-```
-
-```{r echo =F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$adjp), go_analysis)
-
-simMatrix <- calculateSimMatrix(go_analysis,
-                                orgdb="org.Dm.eg.db",
-                                ont=GO.ontology,
-                                method="Rel")
-
-reducedTerms <- reduceSimMatrix(simMatrix,
-                                scores,
-                                threshold=0.7,
-                                orgdb="org.Dm.eg.db")
-
-```
-
-```{r echo = F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
-
-```
-
-```{r, fig.width= 10}
-
-BP.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-CC.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-MF.GO.fig
-
-```
-
-```{r, fig.width= 10}
-
-KEGG.fig
-
-```
-
-```{r fig.height=7, fig.width=10}
-
-heatmapPlot(simMatrix,
-            reducedTerms,
-            annotateParent=TRUE,
-            annotationLabel="parentTerm",
-            fontsize=6,
-            main = "Repressor Gene Enriched Biological Process GO terms")
-
-```
-
-```{r warning=F, fig.width=10}
-
-use.data   = simMatrix
-GO.Sim.PCA(use.data)
-
-```
-
-```{r fig.align='left'}
-
-treemapPlot(reducedTerms)
-
-```
-
-```{r include = F, echo = F}
-
-GOID = "GO:0003723"
-GenesInGO = genesingo[GOID]
-
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInGO[[1]], "FBgn"]
-
-```
-
-```{r include = F, echo = F}
-ParentID = "GO:0034249"
-GOIDs = row.names(reducedTerms)[reducedTerms$parent == ParentID]
-GOID = GOIDs[1]
-GenesInParent= unique(genesingo[[GOID]])
-i=2
-while(i<=length(GOIDs)){
-  GOID = GOIDs[i]
-  GenesInParent= unique(GenesInParent, genesingo[[GOID]])
-  i=i+1
-}
-
-GenesInGO = sigsKEY[sigsKEY$ensembl %in% GenesInParent, "FBgn"]
-
-```
-
-```{r echo =F, warnings = F}
-
-comparison = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-hmdata = cpmdata[GenesInGO, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
-hmdata = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"]
-
-hover.text = round(hmdata, digits = 1)
-
-FDR = hmdata
-FDR[,1:ncol(FDR)] = TKT.EdgeR[row.names(hmdata), comparison]
-
-FBgn = hmdata
-FBgn[,1:ncol(FBgn)] = row.names(FBgn)
-
-i=1
-while(i<=ncol(hover.text)){
-  hover.text[,i] = paste("CPM = ", hover.text[,i],
-                         "\nFDR = ", FDR[,i],
-                         "\nFBgn = ", FBgn[,i])
-  i=i+1
-}
-
-hmdata2 = cpmdata[GenesInGO, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
-hmdata2 = cpmdata[sigsKEY$FBgn, groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"]
-
-hover.text2 = round(hmdata2, digits = 1)
-
-FDR2 = hmdata2
-FDR2[,1:ncol(FDR2)] = TKT.EdgeR[row.names(hmdata2), comparison2]
-
-FBgn2 = hmdata2
-FBgn2[,1:ncol(FBgn2)] = row.names(FBgn2)
-
-i=1
-while(i<=ncol(hover.text2)){
-  hover.text2[,i] = paste("CPM = ", hover.text2[,i],
-                         "\nFDR = ", FDR2[,i],
-                         "\nFBgn = ", FBgn2[,i])
-  i=i+1
-}
-
-hmdata = cbind(hmdata, hmdata2)
-hover.text = cbind(hover.text, hover.text2)
-
-heatmaply(hmdata,
-            trace="none",
-            col=RdYlBu(100)[100:1],
-            scale="row",
-            dendrogram = "both",
-            show_dendrogram = c(F,T),
-            Rowv=T,
-            Colv=T,
-            ##cexRow = 1/(as.numeric(input$tophits)/25),
-            na.color="grey",
-            labRow = GeneIDKey[row.names(hmdata), "Symbol"],
-            ##cexCol = col.text,
-            cexCol = 1,
-            key = T,
-            ##margins = c(50,350,NA,0),
-            ##row_dend_left = T,
-            column_text_angle = 90,
-
-            ##col_side_colors=color.groups,
-            ##col_side_palette=Spectral,
-            ##main= "",
-            custom_hovertext = hover.text)
-
-```
-
-#########################
-## Comparing the three ##
-#########################
-
-```{r include = F, echo = F}
-
-comparison1 = "GRxWT.FC"
-comparison2 = "GRxWT.MC"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "GR.F" | groups$Group == "WT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "GR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-C.sigs = sigsKEY$Symbol
-
-comparison1 = "GRxWT.FDf"
-comparison2 = "GRxWT.MDf"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktDfGR.M" | groups$Group == "TktDfGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-Df.sigs = sigsKEY$Symbol
-
-comparison1 = "GRxWT.FOE"
-comparison2 = "GRxWT.MOE"
-
-sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison1] <= .05]
-
-sigs1 = sigs1[apply(cpmdata[sigs1,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"], 1, min) > 5]
-
-sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,comparison2] <= .05]
-
-sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "TktOEGR.M" | groups$Group == "TktOEGR.M"], 1, min) > 5]
-
-sigs= intersect(sigs1, sigs2)
-
-sigsKEY = GeneIDKey[sigs,]
-
-OE.sigs = sigsKEY$Symbol
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="Control"
-set2="Defficient"
-set3="Over Expression"
-##set4="GSC2.Stem"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = C.sigs
-s2 = Df.sigs
-s3 = OE.sigs
-##s4=row.names(temp)[temp[,4]==1]
-
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~pca.color,
+                 symbol = ~pca.shape,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
 ```
@@
 ```{r}
-
-data = data.frame(Condition = c("Control", "Defficient", "Over Expression"), DEGs = c(length(C.sigs), length(Df.sigs), length(OE.sigs)))
-
-fig <- plot_ly(data, 
-               x = ~Condition, y = ~DEGs, 
-               type = 'bar',
-               name = ~Condition,
-               color = ~Condition,
-               colors = c("coral3","gold2", "steelblue3"),
-               marker = list(line = list(color = "black", width = 1.5)))
 
@@
 
+```{r echo=F, include=F}
+
+pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "H"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Genotype,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
 ```{r}
 
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("brown1","gold2", "steelblue2"),cex=1.5,cat.cex = 1)
+  fig
 
 ```
+
+```{r echo=F, include=F}
+
+pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "T"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Genotype,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
+```{r}
+
+  fig
+
+```
+
+```{r echo=F, include=F}
+
+pca.data = A4V.cpm[,substr(colnames(A4V.cpm), nchar(colnames(A4V.cpm))-1, nchar(colnames(A4V.cpm))-1) == "A"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Genotype,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
+```{r}
+
+  fig
+
+```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_PCA.Rmd
overdue update

@@
 library(edgeR)
+library(goseq)
+library(org.Dm.eg.db)
+library(rrvgo)
+library(VennDiagram)
 
+```
+
+```{r include =F}
 sample.names = list.files("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/")
+
+meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
 
@@
 
+countdata = countdata[-(grep("ti",row.names(countdata))),]
+countdata = countdata[-(grep("trans",row.names(countdata))),]
+
 ##normalize data
@@
 y <- y[keep,,keep.lib.sizes=FALSE]
-z <- calcNormFactors(y, method = "TMM")
+z <- normLibSizes(y)
 ##normalized cpm
 cpmdata=cpm(z)
+
+##updated edger analysis pipeline
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design)
+fit <- glmQLFit(z, design)
+
+contr = makeContrasts(A3FH - S3FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3FH = DEdata
+sigAvS3FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MH - S3MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3MH = DEdata
+sigAvS3MH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FH - S9FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9FH = DEdata
+sigAvS9FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9MH - S9MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9MH = DEdata
+sigAvS9MH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A40FH - S40FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS40FH = DEdata
+sigAvS40FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FH - S9FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9FH = DEdata
+sigS3v9FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FH - A9FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9FH = DEdata
+sigA3v9FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3MH - S9MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9MH = DEdata
+sigS3v9MH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MH - A9MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9MH = DEdata
+sigA3v9MH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FH - S40FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9v40FH = DEdata
+sigS9v40FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FH - A40FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9v40FH = DEdata
+sigA9v40FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FH - S40FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v40FH = DEdata
+sigS3v40FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FH - A40FH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v40FH = DEdata
+sigA3v40FH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FT - S3FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3FT = DEdata
+sigAvS3FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MT - S3MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3MT = DEdata
+sigAvS3MT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FT - S9FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9FT = DEdata
+sigAvS9FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9MT - S9MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9MT = DEdata
+sigAvS9MT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A40FT - S40FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS40FT = DEdata
+sigAvS40FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FT - S9FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9FT = DEdata
+sigS3v9FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FT - A9FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9FT = DEdata
+sigA3v9FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3MT - S9MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9MT = DEdata
+sigS3v9MT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MT - A9MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9MT = DEdata
+sigA3v9MT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FT - S40FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9v40FT = DEdata
+sigS9v40FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FT - A40FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9v40FT = DEdata
+sigA9v40FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FT - S40FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v40FT = DEdata
+sigS3v40FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FT - A40FT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v40FT = DEdata
+sigA3v40FT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FA - S3FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3FA = DEdata
+sigAvS3FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MA - S3MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS3MA = DEdata
+sigAvS3MA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FA - S9FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9FA = DEdata
+sigAvS9FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9MA - S9MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS9MA = DEdata
+sigAvS9MA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A40FA - S40FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+AvS40FA = DEdata
+sigAvS40FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FA - S9FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9FA = DEdata
+sigS3v9FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FA - A9FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9FA = DEdata
+sigA3v9FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3MA - S9MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v9MA = DEdata
+sigS3v9MA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3MA - A9MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v9MA = DEdata
+sigA3v9MA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FA - S40FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9v40FA = DEdata
+sigS9v40FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FA - A40FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9v40FA = DEdata
+sigA9v40FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FA - S40FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3v40FA = DEdata
+sigS3v40FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FA - A40FA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3v40FA = DEdata
+sigA3v40FA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FH - A3MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3FvMH = DEdata
+sigA3FvMH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FH - S3MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3FvMH = DEdata
+sigS3FvMH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FH - A9MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9FvMH = DEdata
+sigA9FvMH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FH - S9MH, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9FvMH = DEdata
+sigS9FvMH = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FT - A3MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3FvMT = DEdata
+sigA3FvMT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FT - S3MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3FvMT = DEdata
+sigS3FvMT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FT - A9MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9FvMT = DEdata
+sigA9FvMT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FT - S9MT, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9FvMT = DEdata
+sigS9FvMT = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A3FA - A3MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A3FvMA = DEdata
+sigA3FvMA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S3FA - S3MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S3FvMA = DEdata
+sigS3FvMA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(A9FA - A9MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+A9FvMA = DEdata
+sigA9FvMA = DEdata[DEdata$FDR < 0.05, ]
+
+contr = makeContrasts(S9FA - S9MA, levels=design)
+qlf = glmQLFTest(fit, contrast=contr)
+DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+DEdata = DEdata$table
+S9FvMA = DEdata
+sigS9FvMA = DEdata[DEdata$FDR < 0.05, ]
+
+order = row.names(cpmdata)
+A4V.FDR = data.frame(AvS3FH = AvS3FH[order, "FDR"],
+                     AvS3MH = AvS3MH[order, "FDR"],
+                     AvS9FH = AvS9FH[order, "FDR"],
+                     AvS9MH = AvS9MH[order, "FDR"],
+                     AvS40FH = AvS40FH[order, "FDR"],
+                     A3v9FH = A3v9FH[order, "FDR"],
+                     S3v9FH = S3v9FH[order, "FDR"],
+                     A3v9MH = A3v9MH[order, "FDR"],
+                     S3v9MH = S3v9MH[order, "FDR"],
+                     A9v40FH = A9v40FH[order, "FDR"],
+                     S9v40FH = S9v40FH[order, "FDR"],
+                     A3v40FH = A3v40FH[order, "FDR"],
+                     S3v40FH = S3v40FH[order, "FDR"],
+
+                     AvS3FT = AvS3FT[order, "FDR"],
+                     AvS3MT = AvS3MT[order, "FDR"],
+                     AvS9FT = AvS9FT[order, "FDR"],
+                     AvS9MT = AvS9MT[order, "FDR"],
+                     AvS40FT = AvS40FT[order, "FDR"],
+                     A3v9FT = A3v9FT[order, "FDR"],
+                     S3v9FT = S3v9FT[order, "FDR"],
+                     A3v9MT = A3v9MT[order, "FDR"],
+                     S3v9MT = S3v9MT[order, "FDR"],
+                     A9v40FT = A9v40FT[order, "FDR"],
+                     S9v40FT = S9v40FT[order, "FDR"],
+                     A3v40FT = A3v40FT[order, "FDR"],
+                     S3v40FT = S3v40FT[order, "FDR"],
+
+                     AvS3FA = AvS3FA[order, "FDR"],
+                     AvS3MA = AvS3MA[order, "FDR"],
+                     AvS9FA = AvS9FA[order, "FDR"],
+                     AvS9MA = AvS9MA[order, "FDR"],
+                     AvS40FA = AvS40FA[order, "FDR"],
+                     A3v9FA = A3v9FA[order, "FDR"],
+                     S3v9FA = S3v9FA[order, "FDR"],
+                     A3v9MA = A3v9MA[order, "FDR"],
+                     S3v9MA = S3v9MA[order, "FDR"],
+                     A9v40FA = A9v40FA[order, "FDR"],
+                     S9v40FA = S9v40FA[order, "FDR"],
+                     A3v40FA = A3v40FA[order, "FDR"],
+                     S3v40FA = S3v40FA[order, "FDR"],
+
+                     A3FvMH = A3FvMH[order, "FDR"],
+                     S3FvMH = S3FvMH[order, "FDR"],
+                     A9FvMH = A9FvMH[order, "FDR"],
+                     S9FvMH = S9FvMH[order, "FDR"],
+                     A3FvMT = A3FvMT[order, "FDR"],
+                     S3FvMT = S3FvMT[order, "FDR"],
+                     A9FvMT = A9FvMT[order, "FDR"],
+                     S9FvMT = S9FvMT[order, "FDR"],
+                     A3FvMA = A3FvMA[order, "FDR"],
+                     S3FvMA = S3FvMA[order, "FDR"],
+                     A9FvMA = A9FvMA[order, "FDR"],
+                     S9FvMA = S9FvMA[order, "FDR"])
+row.names(A4V.FDR) = order
+
+A4V.FC = data.frame(AvS3FH = AvS3FH[order, "logFC"],
+                     AvS3MH = AvS3MH[order, "logFC"],
+                     AvS9FH = AvS9FH[order, "logFC"],
+                     AvS9MH = AvS9MH[order, "logFC"],
+                     AvS40FH = AvS40FH[order, "logFC"],
+                     A3v9FH = A3v9FH[order, "logFC"],
+                     S3v9FH = S3v9FH[order, "logFC"],
+                     A3v9MH = A3v9MH[order, "logFC"],
+                     S3v9MH = S3v9MH[order, "logFC"],
+                     A9v40FH = A9v40FH[order, "logFC"],
+                     S9v40FH = S9v40FH[order, "logFC"],
+                     A3v40FH = A3v40FH[order, "logFC"],
+                     S3v40FH = S3v40FH[order, "logFC"],
+
+                     AvS3FT = AvS3FT[order, "logFC"],
+                     AvS3MT = AvS3MT[order, "logFC"],
+                     AvS9FT = AvS9FT[order, "logFC"],
+                     AvS9MT = AvS9MT[order, "logFC"],
+                     AvS40FT = AvS40FT[order, "logFC"],
+                     A3v9FT = A3v9FT[order, "logFC"],
+                     S3v9FT = S3v9FT[order, "logFC"],
+                     A3v9MT = A3v9MT[order, "logFC"],
+                     S3v9MT = S3v9MT[order, "logFC"],
+                     A9v40FT = A9v40FT[order, "logFC"],
+                     S9v40FT = S9v40FT[order, "logFC"],
+                     A3v40FT = A3v40FT[order, "logFC"],
+                     S3v40FT = S3v40FT[order, "logFC"],
+
+                     AvS3FA = AvS3FA[order, "logFC"],
+                     AvS3MA = AvS3MA[order, "logFC"],
+                     AvS9FA = AvS9FA[order, "logFC"],
+                     AvS9MA = AvS9MA[order, "logFC"],
+                     AvS40FA = AvS40FA[order, "logFC"],
+                     A3v9FA = A3v9FA[order, "logFC"],
+                     S3v9FA = S3v9FA[order, "logFC"],
+                     A3v9MA = A3v9MA[order, "logFC"],
+                     S3v9MA = S3v9MA[order, "logFC"],
+                     A9v40FA = A9v40FA[order, "logFC"],
+                     S9v40FA = S9v40FA[order, "logFC"],
+                     A3v40FA = A3v40FA[order, "logFC"],
+                     S3v40FA = S3v40FA[order, "logFC"],
+
+                     A3FvMH = A3FvMH[order, "logFC"],
+                     S3FvMH = S3FvMH[order, "logFC"],
+                     A9FvMH = A9FvMH[order, "logFC"],
+                     S9FvMH = S9FvMH[order, "logFC"],
+                     A3FvMT = A3FvMT[order, "logFC"],
+                     S3FvMT = S3FvMT[order, "logFC"],
+                     A9FvMT = A9FvMT[order, "logFC"],
+                     S9FvMT = S9FvMT[order, "logFC"],
+                     A3FvMA = A3FvMA[order, "logFC"],
+                     S3FvMA = S3FvMA[order, "logFC"],
+                     A9FvMA = A9FvMA[order, "logFC"],
+                     S9FvMA = S9FvMA[order, "logFC"])
+row.names(A4V.FC) = order
+
+cpmdata = cpmdata[grep("FBgn",row.names(cpmdata)),]
+A4V.FDR = A4V.FDR[row.names(cpmdata),]
+
+A4V.meancpm = cpmdata[,1:30]
+colnames(A4V.meancpm) = unique(meta$Group)
+i=1
+while(i<=nrow(A4V.meancpm)){
+  j=1
+  while(j<=ncol(A4V.meancpm)){
+    A4V.meancpm[i,j]=mean(cpmdata[i,row.names(meta)[meta$Group == colnames(A4V.meancpm)[j]]])
+    j=j+1
+  }
+  i=i+1
+}
+
+##write.csv(cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv")
+##write.csv(A4V.FDR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
+##write.csv(A4V.meancpm, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv")
+##write.csv(A4V.FC, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv")
+
+```
+
+```{r}
+
+cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
+
+meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
+
+FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
+
+FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
+
+meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
+
+GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+
+```
+
+```{r echo = F}
+
+## arc1 FBgn = 'FBgn0033926'
+##spn FBgn = 'FBgn0010905'
+FBgn = 'FBgn0035348'
+name = ''
+
+par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+gene = data.frame(cpm = as.numeric(cpm[FBgn,]), 
+                  condition = substr(row.names(meta),1, nchar(row.names(meta))-1), 
+                  group = paste(meta$Genotype, meta$Sex))
+
+gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
+                                                   "S3FH", "S9FH", "S40FH",
+                                                   "A3FT", "A9FT", "A40FT",
+                                                   "S3FT", "S9FT", "S40FT",
+                                                   "A3FA", "A9FA", "A40FA",
+                                                   "S3FA", "S9FA", "S40FA",
+                                                   "A3MH", "A9MH",
+                                                   "S3MH", "S9MH",
+                                                   "A3MT", "A9MT",
+                                                   "S3MT", "S9MT",
+                                                   "A3MA", "A9MA",
+                                                   "S3MA", "S9MA"))
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+
+boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
+       fill = c('firebrick',"darkgreen","gold","dodgerblue"),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5)
+
+```
+
+##GO and KEGG Enrichment function
+```{r echo = F, include = F}
+
+Enrichment = function(sigs, bg){
+  genes = setNames(rep(0, length(bg)), bg)
+  genes[sigs] = 1
+  pwf=nullp(genes,"dm3","geneSymbol")
+  GO.wall=goseq(pwf,"dm3","geneSymbol")
+  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+  row.names(GO.wall) = GO.wall$category
+  KEGG=goseq(pwf,gene2cat=kegg)
+  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
+  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
+  KEGG$Name=kegg.names[row.names(KEGG),1]
+
+  enrichment.data = list(GO.wall, KEGG)
+  names(enrichment.data) = c("GO", "KEGG")
+  return(enrichment.data)
+}
+
+```
+
+##GO.Sim.PCA function
+```{r echo = F, include = F}
+GO.Sim.PCA = function(use.data){
+    pca <- prcomp(t(use.data), scale.=TRUE) 
+    pc1=scale(pca$x[,1])
+    pc2=scale(pca$x[,2])
+    eigs <- pca$sdev^2
+    ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(PC1=pc1,
+                        PC2=pc2,
+                        sdev=pca$sdev,
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group = reducedTerms[row.names(use.data), "parentTerm"],
+                        Score = reducedTerms[row.names(use.data), "score"],
+                        Term = reducedTerms[row.names(use.data), "term"],
+                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
+                        Total = GO.data[row.names(use.data), "numInCat"],
+                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))
+
+    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
+    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))
+
+  fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 ##symbol = ~Group,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c("firebrick","gold","deepskyblue"),
+                 marker = list(size = pca.data$Score,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Parent Group: ", pca.data$Group,
+                                   "\nSample: ", pca.data$Term, 
+                                   "\nTotal DE: ", pca.data$TotalDE, 
+                                   "\nTotal in Cat.: ", pca.data$Total, 
+                                   "\nFDR: ", pca.data$SigVal)) %>%
+    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
+           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
+           title = "Enriched GO term similarity")
+
+  return(fig)
+}
+
+```
+
+##GO20 Function
+```{r echo = F, include =F}
+
+GO20 = function(GO.data, GO.ontology){
+GO.data = GO.data[GO.data$ontology == GO.ontology,
+                  c("category", "term","adjp", "numDEInCat", "numInCat")]
+
+data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
+data$Score = -log10(data$adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+
+m <- list(
+  l = 50,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 4
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "term",
+               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$term,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3))) %>%
+    layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Top 20 Most Enriched GO Terms",
+           margin = m)
+
+  return(fig)
+}
+
+```
+
+##KEGG20 Function
+```{r, echo = F, include = F}
+
+KEGG20 = function(data){
+
+  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
+
+data$term = data$Name
+if(length(unique(data$term)) < length(data$term)){
+  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
+}  
+data = data[20:1,]
+data$Score = -log10(data$adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+
+m <- list(
+  l = 50,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 4
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "Name",
+               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$Name,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3))) %>%
+    layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Top 20 Most Enriched KEGG Terms",
+           margin = m)
+
+return(fig)
+
+}
+
+```
+
+```{r echo = F, include = F}
+
+i=1
+
+while(i<=ncol(FDR)){
+compare = colnames(FDR)[i]
+
+sigs = row.names(FDR)[FDR[,i]<.05]
+bg = row.names(FDR)
+
+sigsKEY = GeneIDKey[sigs,]
+sigs = na.omit(sigsKEY$Symbol)
+bgKEY = GeneIDKey[bg,]
+bg = na.omit(bgKEY$Symbol)
+
+sig.cats = Enrichment(sigs, bg)
+
+##write.csv(sig.cats[[1]], paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/GOterm Enrichment/", colnames(FDR)[i],"_GOTermAnalysis.csv"))
+
+##write.csv(sig.cats[[2]], paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/KEGG Enrichment/", colnames(FDR)[i],"KEGGAnalysis.csv"))
+
+i = i +1
+
+}
+
+```
+
+```{r}
+
+sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
+sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
+sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
+sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]
+
+GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+
+sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
+sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
+
+A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
+A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
+GR = setdiff(sigsGR.FxM, sigsWT.FxM)
+
+##Sample titles as strings. Only fill in up to your number of selected categories
+set1="A4V 3-day"
+set2="A4V 9-day"
+set3="G85R Larvae"
+set4=""
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=A3
+s2=A9
+s3=GR
+s4=""
+
+T3 = A3
+T9 = A9
 
@@
 
-pca <- prcomp(t(cpmdata), scale.=TRUE) 
-gr <- colnames(cpmdata)
+FC.subset = FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
+                   "AvS3MH", "AvS9MH",
+                   "AvS3FT", "AvS9FT", "AvS40FT",
+                   "AvS3MT", "AvS9MT",
+                   "AvS3FA", "AvS9FA", "AvS40FA",
+                   "AvS3MA", "AvS9MA")]
+gr <- c("03FH", "09FH", "40FH",
+        "03MH", "09MH",
+        "03FT", "09FT", "40FT",
+        "03MT", "09MT",
+        "03FA", "09FA", "40FA",
+        "03MA", "09MA")
+colnames(FC.subset) = gr
+
+pca <- prcomp(t(FC.subset), scale.=TRUE)
+
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Tissue=substr(gr, 4, 4), 
+                        Sex=substr(gr, 3, 3), 
+                        Age=substr(gr, 1, 2),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 3, 3),
+                                      substr(gr, 4, 4)),
+                        pca.color = substr(gr, 3, 3),
+                        pca.shape = substr(gr, 4, 4))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~pca.color,
+                 symbol = ~pca.shape,
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
+```{r}
+
+  fig
+
+```
+
+```{r echo=F, include=F}
+
+pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "H"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
 PC1=scale(pca$x[,1])
@@
                         Group= paste0(substr(gr, 1, 1),
-                                      substr(gr, nchar(gr)-2, nchar(gr)-1)),
-                        pca.color = substr(gr, nchar(gr)-1, nchar(gr)-1),
-                        pca.shape = substr(gr, nchar(gr)-2, nchar(gr)-2))
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
 
@@
                  showlegend = T,
-                 color = ~pca.color,
-                 symbol = ~pca.shape,
+                 color = ~Group,
+                 symbol = ~Genotype,
                  ##symbols = as.character(seq_along(unique(point.data$Set))),
@@
 ```
+
+```{r echo=F, include=F}
+
+pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "T"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Genotype,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
+```{r}
+
+  fig
+
+```
+
+```{r echo=F, include=F}
+
+pca.data = A4V.cpm[,substr(colnames(A4V.cpm), nchar(colnames(A4V.cpm))-1, nchar(colnames(A4V.cpm))-1) == "A"]
+
+remove = apply(pca.data, MARGIN = 1, sum) != 0
+
+pca.data = pca.data[remove,]
+
+pca <- prcomp(t(pca.data), scale.=TRUE) 
+gr <- colnames(pca.data)
+PC1=scale(pca$x[,1])
+PC2=scale(pca$x[,2])
+eigs <- pca$sdev^2
+ve=signif(((eigs / sum(eigs))*100)[1:3],4)
+
+    pca.data=data.frame(Sample=gr,
+                        ##PC1=scale(pca$x[,1]),
+                        ##PC2=scale(pca$x[,2]),
+                        PC1=scale(pca$x[,1]),
+                        PC2=scale(pca$x[,2]),
+                        sdev=pca$sdev,
+                        Genotype=substr(gr, 1, 1), 
+                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
+                        Age=substr(gr, 2, nchar(gr)-3),
+                        Percent1=ve[1],
+                        Percent2=ve[2],
+                        Group= paste0(substr(gr, 1, 1),
+                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
+
+fig  = plot_ly(data = pca.data, 
+                 x = ~PC1, 
+                 y = ~PC2,
+                 name = ~Group,
+                 type = 'scatter',
+                 mode = 'markers',
+                 showlegend = T,
+                 color = ~Group,
+                 symbol = ~Genotype,
+                 ##symbols = as.character(seq_along(unique(point.data$Set))),
+                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
+                 marker = list(size = 15,
+                               line = list(color = "black", width = 1.5)),
+                 hoverinfo = "text",
+                 hovertext = paste("Sample:", pca.data$Sample)) %>%
+    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
+           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
+```
+
+```{r}
+
+  fig
+
+```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.Rmd
overdue update

---
title: "A4V PCA"
author: "John Santiago"
date: "2024-01-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=F, include=F}

library(plotly)
library(edgeR)
library(goseq)
library(org.Dm.eg.db)
library(rrvgo)
library(VennDiagram)
library(pathview)
library(visNetwork)

```

```{r echo = F}
counts = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.countdata.csv", row.names = 1)

cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)

meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)

FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)

FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)

meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

```

```{r echo = F, include = F}

Enrichment = function(sigs, bg){
  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")
  return(enrichment.data)
}

```

```{r echo = F, include = F}
GO.Sim.PCA = function(use.data){
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = reducedTerms[row.names(use.data), "parentTerm"],
                        Score = reducedTerms[row.names(use.data), "score"],
                        Term = reducedTerms[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 ##symbol = ~Group,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c("firebrick","gold","deepskyblue"),
                 marker = list(size = pca.data$Score,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Parent Group: ", pca.data$Group,
                                   "\nSample: ", pca.data$Term, 
                                   "\nTotal DE: ", pca.data$TotalDE, 
                                   "\nTotal in Cat.: ", pca.data$Total, 
                                   "\nFDR: ", pca.data$SigVal)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "Enriched GO term similarity")

  return(fig)
}

```

```{r echo = F, include =F}

GO20 = function(GO.data, GO.ontology){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

  return(fig)
}

```

```{r, echo = F, include = F}

KEGG20 = function(data){

  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]

data$term = data$Name
if(length(unique(data$term)) < length(data$term)){
  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
}  
data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Name",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$Name,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched KEGG Terms",
           margin = m)

return(fig)

}

```

```{r echo = F}

cutoff=0

sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
A3 = A3[apply(meancpm[A3, c("A3FT", "A3MT", "S3FT", "S3MT")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MT < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FT < 0.05])

A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
A9 = A9[apply(meancpm[A9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MT < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FT < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

T3 = A3
T9 = A9

```

Thorax Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```

```{r echo = F}

sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
A3 = A3[apply(meancpm[A3, c("A3FH", "A3MH", "S3FH", "S3MH")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MH < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FH < 0.05])

A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
A9 = A9[apply(meancpm[A9, c("A9FH", "A9MH", "S9FH", "S9MH")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MH < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FH < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

H3=A3
H9=A9

```

Head Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```

```{r echo = F}

sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
A3 = A3[apply(meancpm[A3, c("A3FA", "A3MA", "S3FA", "S3MA")],MARGIN = 1, mean)>cutoff]
A3 = intersect(A3, row.names(FDR)[FDR$AvS3MA < 0.05])
A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FA < 0.05])

A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
A9 = A9[apply(meancpm[A9, c("A9FA", "A9MA", "S9FA", "S9MA")],MARGIN = 1, mean)>cutoff]
A9 = intersect(A9, row.names(FDR)[FDR$AvS9MA < 0.05])
A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FA < 0.05])

GR = setdiff(sigsGR.FxM, sigsWT.FxM)
GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
                           "GR.M1","GR.M2","GR.M3",
                           "WT.F1","WT.F2",
                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

A3=A3
A9=A9

```

Abdomen Sex Specific DEGs
```{r echo = F}

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```

```{r include = F, echo = F}

sigs = T9##setdiff(T9,T3)
bg = row.names(FDR)

sigsKEY = GeneIDKey[sigs,]
sigs = na.omit(sigsKEY$Symbol)
bgKEY = GeneIDKey[bg,]
bg = na.omit(bgKEY$Symbol)

sig.cats = Enrichment(sigs, bg)
thorax.cats = sig.cats

```

```{r echo =F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "CC"
go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r echo =F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

BP.simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

BP.reducedTerms <- reduceSimMatrix(BP.simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r echo =F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "MF"
go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

MF.simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

MF.reducedTerms <- reduceSimMatrix(MF.simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r echo = F, include =F}

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
BP.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
CC.GO.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
MF.GO.fig = GO20(GO.data, GO.ontology)

KEGG.fig = KEGG20(sig.cats[["KEGG"]])

```

9 Day Thorax Biological Process GO Terms
```{r, echo = F,  fig.width= 10}

BP.GO.fig

```

9 Day Thorax Cellular Component GO Terms
```{r, echo = F,  fig.width= 10}

CC.GO.fig

```

9 Day Thorax Molecular Function GO Terms
```{r, echo = F,  fig.width= 10}

MF.GO.fig

```

9 Day Thorax KEGG Pathways
```{r, echo = F,  fig.width= 10}

KEGG.fig

```

9 Day Thorax Cellular Component GO Terms
```{r  echo = F, fig.align='left'}

treemapPlot(reducedTerms)

```

9 Day Thorax Biological Process GO Terms
```{r  echo = F, fig.align='left'}

treemapPlot(BP.reducedTerms)

```

9 Day Thorax Molecular Function GO Terms
```{r  echo = F, fig.align='left'}

treemapPlot(MF.reducedTerms)

```

```{r}

x <- counts
gr <- factor(substr(colnames(counts), 1, nchar(colnames(counts))-1))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- normLibSizes(y)
design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design)
fit <- glmQLFit(z, design)

contr = makeContrasts(A9MT - A9FT, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
A9MvFT = DEdata

```

```{r}

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'A9FvMT']),
                          FC = A9MvFT[T9, 'logFC'],
                          Color = 'grey',
                          size = 3*log(meancpm[T9,"A9MT"]),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none")

main.title = ""

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
fig = fig %>% layout(title = main.title)

              ##color = ~Color,
              ##colors = 'Spectral')
              ##color = ~Color,
              ##colors = ~Color)
              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))

fig

```

```{r}

##NMJ = GO:0031594
##synapse = GO:0045202

specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go', "BP.parent.category", "MF.parent.category")

specific.cat = specific.cat[5]
parent.category = 'response to biotic stimulus'
specific.kegg = "none"
specific.go =  '0031594'

set.size = F

if(specific.cat ==  'parent.category'){
  rt = reducedTerms
}

if(specific.cat ==  'BP.parent.category'){
  rt = BP.reducedTerms
}

if(specific.cat ==  'MF.parent.category'){
  rt = MF.reducedTerms
}

GOterm.genes = vector('list', length = length(unique(rt$parent)))
names(GOterm.genes) = unique(rt$parent)
i=1
while(i<=length(GOterm.genes)){
  goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
  genesinparent = unlist(genesingo[goinparent])
  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
  i = i +1
}

volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
                          FDR = -log2(FDR[T9, 'A9FvMT']),
                          FC = A9MvFT[T9, 'logFC'],
                          Color = 'grey',
                          size = 3*log(meancpm[T9,"A9MT"]),
                          M.cpm = meancpm[T9,"A9MT"],
                          F.cpm = meancpm[T9,"A9FT"],
                          SM.cpm = meancpm[T9,"S9MT"],
                          SF.cpm = meancpm[T9,"S9FT"],
                          GO.terms = "none")

main.title = ""

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

if(specific.cat == 'parent.category' | specific.cat == 'BP.parent.category' | specific.cat == 'MF.parent.category'){
  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  parent.genes = intersect(parent.genes, row.names(volcano.data))
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
  main.title = parent.category
}

if(specific.cat == 'specific.kegg'){
  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  volcano.data$Color = 'honeydew'
  row.names(volcano.data) = volcano.data$Symbol
    volcano.data[kegg.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
}

if(specific.cat == 'specific.go'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

##volcano.data

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
fig = fig %>% layout(title = main.title)

              ##color = ~Color,
              ##colors = 'Spectral')
              ##color = ~Color,
              ##colors = ~Color)
              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))

fig

```

```{r include = F}

##genes in the kegg pathway and their enzyme IDs
glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
##Edge data for genes connecting metabolites
glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
##Metabolites in the KEGG pathway with their ID
glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')

node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')

##extracting position data for nodes
node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
                       number = rep(names(node.data$kegg.names),
                                    lengths(node.data$kegg.names)),
                       x = 0,
                       y = 0,
                       color = 0,
                       names = "")
node.info$x = node.data$x[node.info$number]
node.info$y = node.data$y[node.info$number]

##make new columns for transcriptomic data
glycolysis.genes$FBgn = ""
glycolysis.genes$Symbol = ""
glycolysis.genes$FC = 0
glycolysis.genes$pval = 1

##Isolate gene ID info for goi
temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
row.names(temp) = temp$CG

##fill in new columns with transcriptomic data
glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
glycolysis.genes$FC = A9MvFT[glycolysis.genes$FBgn, 'logFC']
glycolysis.genes$FDr = A9MvFT[glycolysis.genes$FBgn, 'FDR']

##make new columns for metabolomic data
row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
glycolysis.metabs$metabolomicsID = ""
glycolysis.metabs$FC = 0
glycolysis.metabs$pval = 1

##retrieve name used in metabolomic data for metabolite IDs in path
##including IDs associated with multiple metabolomic names
i = 1
while(i<=nrow(glycolysis.metabs)){
  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
  }
  i = i +1
}

##using the positions for nodes (metabolites) only
metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]

metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']

color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)

metab.info$color[metab.info$color > 1] = 1
metab.info$color[metab.info$color < -1] = -1
metab.info$color = (metab.info$color * 200) +201
metab.info$color = color.pallette[metab.info$color]
metab.info$color[is.na(metab.info$color)] = 'dimgrey'

metab.info$size = 10 + 10*abs(metab.info$size)
metab.info$size[is.na(metab.info$size)] = 10

metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
                          "<br>log2(FC): ", signif(metab.info$FC,3),
                          "<br>pval: ", signif(10^-metab.info$pval,3))

nodes = data.frame(id = paste0(metab.info$names),
                   color = metab.info$color,
                   size = metab.info$size,
                   x = 2*metab.info$x,
                   y = 2*metab.info$y,
                   physics = F,
                   group = "",
                   title = metab.info$title)

glycolysis.edges$FBgn = ''
temp.glycolysis.path = glycolysis.edges

i = 1
while(i<=nrow(glycolysis.edges)){
  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
    temp2 = glycolysis.edges[rep(i, length(temp)),]
    temp2$FBgn = temp
  }else{
    temp2 = glycolysis.edges[i,]
  }
  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)

  i = i +1
}

glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]

glycolysis.edges$size = log10(meancpm[glycolysis.edges[,'FBgn'], 'A9MT'])
glycolysis.edges$size[glycolysis.edges$size <1] = 1
glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
glycolysis.edges$size = 2*glycolysis.edges$size

glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
## max color intensity is at FC of 2
glycolysis.edges$color[glycolysis.edges$color>1] = 1
glycolysis.edges$color[glycolysis.edges$color<(-1)] = -1
glycolysis.edges$color = 201+(glycolysis.edges$color *200)
glycolysis.edges$color = color.pallette[glycolysis.edges$color]
glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'

glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))

edges = data.frame(from = glycolysis.edges$from.name,
                   to = glycolysis.edges$to.name,
                   arrows = glycolysis.edges$arrow,
                   color = glycolysis.edges$color,
                   width = glycolysis.edges$size,
                   title = glycolysis.edges$title,
                   physics = T)

nodes = data.frame(id = paste0(nodes$id),
                   color = nodes$color,
                   size = nodes$size,
                   x = nodes$x,
                   y = nodes$y,
                   physics = F,
                   group = "",
                   title = nodes$title)

OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
                               'Propanoate Metabolism',
                               'Starch and Sucrose Metabolism',
                               'Citrate Cycle'),
                        color = "black",
                        size = 15,
                        x= c(1350,1254,966,175),
                        y=c(1112,1822,110,1700),
                        physics = F,
                        group = 'Outside Path',
                        title = "")

nodes = rbind(nodes, OutsidePath)

visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = edges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))

```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.V2.Rmd
overdue update

--- 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.Rmd
@@
 library(visNetwork)
+library(pathview)
+library(rstudioapi)
+library(clusterProfiler)
 
@@
 GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+
+KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
+
+genesingo=as.list(org.Dm.egGO2ALLEGS)
 
@@
 Enrichment = function(sigs, bg){
+  sigsKEY = GeneIDKey[sigs,]
+  sigs = na.omit(sigsKEY$Symbol)
+  bgKEY = GeneIDKey[bg,]
+  bg = na.omit(bgKEY$Symbol)
+
   genes = setNames(rep(0, length(bg)), bg)
@@
 ```{r echo = F, include = F}
+
 GO.Sim.PCA = function(use.data){
@@
                         Percent2=ve[2],
-                        Group = reducedTerms[row.names(use.data), "parentTerm"],
-                        Score = reducedTerms[row.names(use.data), "score"],
-                        Term = reducedTerms[row.names(use.data), "term"],
+                        Group = use.data[row.names(use.data), "parentTerm"],
+                        Score = use.data[row.names(use.data), "score"],
+                        Term = use.data[row.names(use.data), "term"],
                         TotalDE = GO.data[row.names(use.data), "numDEInCat"],
@@
 
-GO20 = function(GO.data, GO.ontology){
+GO20 = function(GO.data, GO.ontology, FC.data, FDR.data){
 GO.data = GO.data[GO.data$ontology == GO.ontology,
@@
 data$Score = -log10(data$adjp)
+
+temp = nchar(data$term)
+data$label = data$term
+data$label[temp > 40] = paste0(substr(data$term[temp>40], 1 ,35), "...")
+
 data$term = factor(data$term, levels = c(unique(data$term)))
+data$up = 0
+data$down = 0
+data$allup = 0
+data$alldown = 0
+
+sigs = names(FDR.data[FDR.data <= 0.05])
+
+i = 1
+while(i <= nrow(data)){
+  go.id = row.names(data)[i]
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  go.genes = intersect(go.genes, names(FC.data))
+  sig.go.genes = intersect(go.genes, sigs)
+  go.FC = FC.data[go.genes]
+  sig.go.FC = FC.data[sig.go.genes]
+
+  data$allup[i] = length(go.FC[go.FC>0])
+  data$alldown[i] = length(go.FC[go.FC<0])
+  data$up[i] = length(sig.go.FC[sig.go.FC>0])
+  data$down[i] = length(sig.go.FC[sig.go.FC<0])
+  i = i +1
+}
+
+data$down = data$down * -1
+data$alldown = data$alldown * -1
 
@@
 fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
+               x = ~up, y = ~label, 
                type = 'bar',
-               name = "term",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
+               name = "Sig. Increased FC",
+               marker = list(color = 'brown',
                              line = list(color = "black", width = 1.5)),
@@
                       "\nTotal in Cat.: ", data$numInCat,
+                      "\nDE up: ", data$up,
+                      "\nDE down: ", data$down,
                       "\nFDR: ", signif(data$adjp, 3))) %>%
+    add_trace(x = ~down, 
+              y ~term, 
+              marker = list(color = 'steelblue', 
+                            line = list(color = "black", width = 1.5)), 
+              name = "Sig. Decreased FC")%>%
+
     layout(xaxis = list(title = "Number of Genes"),
            yaxis = list(title = ""),
-           title = "Top 20 Most Enriched GO Terms",
-           margin = m)
+           title = paste0("Top 20 Most Enriched ",GO.ontology, " GO Terms"),
+           margin = m, barmode = 'overlay')
 
@@
 
-KEGG20 = function(data){
-
-  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
+KEGG20 = function(KEGG.data, FC.data, FDR.data){
+
+data = KEGG.data[, c("category", "Name","adjp", "numDEInCat", "numInCat")]
 
@@
 }  
+data = na.omit(data[data$Name != 'Metabolic pathways',])
 data = data[20:1,]
@@
 data$term = factor(data$term, levels = c(unique(data$term)))
+data$up = 0
+data$down = 0
+data$allup = 0
+data$alldown = 0
+
+sigs = names(FDR.data[FDR.data <= 0.05])
+
+i = 1
+while(i <= nrow(data)){
+  kegg.id = data$category[i]
+  kegg.genes = names(kegg[grep(kegg.id, kegg)])
+  kegg.genes = GeneIDKey[GeneIDKey$Symbol %in% kegg.genes, "FBgn"]
+  kegg.genes = intersect(kegg.genes, names(FC.data))
+  sig.kegg.genes = intersect(kegg.genes, sigs)
+  kegg.FC = FC.data[kegg.genes]
+  sig.kegg.FC = FC.data[sig.kegg.genes]
+  data$allup[i] = length(kegg.FC[kegg.FC>0])
+  data$alldown[i] = length(kegg.FC[kegg.FC<0])
+  data$up[i] = length(sig.kegg.FC[sig.kegg.FC>0])
+  data$down[i] = length(sig.kegg.FC[sig.kegg.FC<0])
+  i = i +1
+}
+
+data$down = data$down * -1
+data$alldown = data$alldown * -1
 
@@
 fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
+               x = ~up, y = ~term, 
                type = 'bar',
-               name = "Name",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
+               name = "Sig. Increased FC",
+               marker = list(color = 'brown',
                              line = list(color = "black", width = 1.5)),
     hoverinfo = "text",
-    hovertext = paste("Sample:", data$Name,
+    hovertext = paste("Sample:", data$term,
                       "\nGO ID: ", data$category,
@@
                       "\nTotal in Cat.: ", data$numInCat,
+                      "\nDE up: ", data$up,
+                      "\nDE down: ", data$down,
                       "\nFDR: ", signif(data$adjp, 3))) %>%
+    add_trace(x = ~down, 
+              y ~term, 
+              marker = list(color = 'steelblue', 
+                            line = list(color = "black", width = 1.5)), 
+              name = "Sig. Decreased FC")%>%
     layout(xaxis = list(title = "Number of Genes"),
            yaxis = list(title = ""),
-           title = "Top 20 Most Enriched KEGG Terms",
-           margin = m)
+           title = paste0("Top 20 Most Enriched ", GO.ontology, " GO Terms"),
+           margin = m, barmode = 'overlay')
 
@@
 
+KEGG.diagram = function(PathwayID, out.id, FC.data, FDR.data){
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+    }
+  Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  OutputDir = paste0(Home, "/KEGG_Image_Files/")
+  setwd(OutputDir)
+  sigs = names(FDR.data[FDR.data <= .05])
+  deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
+
+  pv.out <- pathview(gene.data =  deg.data,
+                   pathway.id = PathwayID,
+                   species = "dme",
+                   kegg.native = T,
+                   limit=list(gene=c(-2,2)),
+                   node.sum="max.abs",
+                   low="royalblue",mid = "grey",high="firebrick",
+                   out.suffix = out.id,
+                   bins=list(genes=30))
+  setwd(Home)
+  knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png"))
+}
+
+```
+
+##Using all DEGs from the A9MT vs S9MT comparison
+### (no minimum mean cpm cutoff or background factor DEG exclusion)
+```{r echo = F}
+
 cutoff=0
 
-sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
-sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
-sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
-sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
-A3 = A3[apply(meancpm[A3, c("A3FT", "A3MT", "S3FT", "S3MT")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MT < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FT < 0.05])
-
-A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
-A9 = A9[apply(meancpm[A9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MT < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FT < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-T3 = A3
-T9 = A9
-
-```
-
-Thorax Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
-
-```
-
-```{r echo = F}
-
-sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
-sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
-sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
-sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
-A3 = A3[apply(meancpm[A3, c("A3FH", "A3MH", "S3FH", "S3MH")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MH < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FH < 0.05])
-
-A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
-A9 = A9[apply(meancpm[A9, c("A9FH", "A9MH", "S9FH", "S9MH")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MH < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FH < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-H3=A3
-H9=A9
-
-```
-
-Head Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
-
-```
-
-```{r echo = F}
-
-sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
-sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
-sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
-sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
-A3 = A3[apply(meancpm[A3, c("A3FA", "A3MA", "S3FA", "S3MA")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MA < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FA < 0.05])
-
-A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
-A9 = A9[apply(meancpm[A9, c("A9FA", "A9MA", "S9FA", "S9MA")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MA < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FA < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-A3=A3
-A9=A9
-
-```
-
-Abdomen Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
+##T9 = setdiff(row.names(FDR)[FDR[,'AvS9MT']<.05], row.names(FDR)[FDR[,'AvS9FT']<.05])
+T9 = row.names(FDR)[FDR[,'AvS9MT']<.05]
+T9 = T9[apply(meancpm[T9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
 
@@
 
-sigs = T9##setdiff(T9,T3)
+sigs = T9
 bg = row.names(FDR)
-
-sigsKEY = GeneIDKey[sigs,]
-sigs = na.omit(sigsKEY$Symbol)
-bgKEY = GeneIDKey[bg,]
-bg = na.omit(bgKEY$Symbol)
 
@@
 
-simMatrix <- calculateSimMatrix(go_analysis,
+CC.simMatrix <- calculateSimMatrix(go_analysis,
                                 orgdb="org.Dm.eg.db",
@@
 
-reducedTerms <- reduceSimMatrix(simMatrix,
+CC.reducedTerms <- reduceSimMatrix(CC.simMatrix,
                                 scores,
@@
 
+FC.data = setNames(FC$AvS9MT, row.names(FC))
+FDR.data = setNames(FDR$AvS9MT, row.names(FDR))
+
 GO.data = sig.cats[["GO"]]
 GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
+BP.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
 
 GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
+CC.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
 
 GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
+MF.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+KEGG.data = sig.cats[["KEGG"]]
+KEGG.fig = KEGG20(KEGG.data, FC.data, FDR.data)
 
@@
 
+9 Day Thorax Biological Process GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(BP.reducedTerms)
+
+```
+
 9 Day Thorax Cellular Component GO Terms
@@
 
+9 Day Thorax Cellular Component GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(CC.reducedTerms)
+
+```
+
 9 Day Thorax Molecular Function GO Terms
@@
 
+9 Day Thorax Molecular Function GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(MF.reducedTerms)
+
+```
+
 9 Day Thorax KEGG Pathways
@@
 
-9 Day Thorax Cellular Component GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(reducedTerms)
-
-```
-
-9 Day Thorax Biological Process GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(BP.reducedTerms)
-
-```
-
-9 Day Thorax Molecular Function GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(MF.reducedTerms)
-
-```
-
-```{r}
-
-x <- counts
-gr <- factor(substr(colnames(counts), 1, nchar(colnames(counts))-1))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- normLibSizes(y)
-design<-model.matrix(~0 + gr)
-colnames(design) = unique(gr)
-z = estimateDisp(z, design)
-fit <- glmQLFit(z, design)
-
-contr = makeContrasts(A9MT - A9FT, levels=design)
-qlf = glmQLFTest(fit, contrast=contr)
-DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEdata = DEdata$table
-A9MvFT = DEdata
-
-```
-
-```{r}
+```{r echo = F, include=T, message = F, fig.align='center'}
+
+PathwayID = "04146"
+out.id = 'AvS9T'
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
+
+```
+
+```{r echo = F, include = F}
+
+##NMJ = GO:0031594
+##synapse = GO:0045202
+
+specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go', "BP.parent.category", "MF.parent.category")
+
+specific.cat = specific.cat[2]
+parent.category = 'peroxisome'
+specific.kegg = "none"
+specific.go =  '0042579'
+
+set.size = F
+
+specific.cat = 'none'
+
+if(length(intersect(parent.category, CC.reducedTerms$parentTerm))){
+  rt = CC.reducedTerms
+  specific.cat = 'parent.category'
+}
+
+if(length(intersect(parent.category, BP.reducedTerms$parentTerm))){
+  rt = BP.reducedTerms
+  specific.cat = 'parent.category'
+}
+
+if(length(intersect(parent.category, MF.reducedTerms$parentTerm))){
+  rt = MF.reducedTerms
+  specific.cat = 'parent.category'
+}
+
+GOterm.genes = vector('list', length = length(unique(rt$parent)))
+names(GOterm.genes) = unique(rt$parent)
+i=1
+while(i<=length(GOterm.genes)){
+  goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
+  genesinparent = unlist(genesingo[goinparent])
+  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
+  i = i +1
+}
 
 volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'A9FvMT']),
-                          FC = A9MvFT[T9, 'logFC'],
+                          FDR = -log2(FDR[T9, 'AvS9MT']),
+                          FC = FC[T9, 'AvS9MT'],
                           Color = 'grey',
@@
 volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
+
+if(set.size == T){
+  volcano.data$size = 15
+  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
+}
+
+if(specific.cat == 'parent.category'){
+  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
+  parent.genes = intersect(parent.genes, row.names(volcano.data))
+  volcano.data$Color = 'honeydew'
+  volcano.data[parent.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
+  main.title = parent.category
+}
+
+if(specific.cat == 'specific.kegg'){
+  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
+  kegg.genes = names(kegg[grep(kegg.id, kegg)])
+  volcano.data$Color = 'honeydew'
+  row.names(volcano.data) = volcano.data$Symbol
+    volcano.data[kegg.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
+}
+
+if(specific.cat == 'none'){
+  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
+  volcano.data$Color = 'honeydew'
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  go.genes = intersect(go.genes, row.names(volcano.data))
+  volcano.data[go.genes, 'Color'] = 'deeppink'
+  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
+  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
+}
+
+##volcano.data
 
@@
 
-```{r}
-
-##NMJ = GO:0031594
-##synapse = GO:0045202
-
-specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go', "BP.parent.category", "MF.parent.category")
-
-specific.cat = specific.cat[5]
-parent.category = 'response to biotic stimulus'
-specific.kegg = "none"
-specific.go =  '0031594'
-
+```{r echo = F, include = T}
+
+category = 'neuromuscular junction'
+plot.all = F
 set.size = F
 
-if(specific.cat ==  'parent.category'){
-  rt = reducedTerms
-}
-
-if(specific.cat ==  'BP.parent.category'){
+volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
+                          FDR = -log2(FDR[T9, 'AvS9MT']),
+                          MFC = FC[T9, 'AvS9MT'],
+                          FFC = FC[T9, 'AvS9FT'],
+                          ##size = 3*log(meancpm[T9,"A9MT"]),
+                          size = -log2(FDR[T9, 'AvS9MT']),
+                          M.cpm = meancpm[T9,"A9MT"],
+                          F.cpm = meancpm[T9,"A9FT"],
+                          SM.cpm = meancpm[T9,"S9MT"],
+                          SF.cpm = meancpm[T9,"S9FT"],
+                          GO.terms = "none",
+                          Color = FC[T9, 'AvS9MT'] - FC[T9, 'AvS9FT'])
+row.names(volcano.data) = T9
+
+main.title = ""
+
+specific.cat = 'none'
+
+if(length(intersect(category, sig.cats$GO$category))){
+  specific.cat = 'specific.go'
+  specific.go = sig.cats$GO$category[sig.cats$GO$category == category]
+}
+
+if(length(intersect(category, sig.cats$GO$term))){
+  specific.cat = 'specific.go'
+  specific.go = sig.cats$GO$category[sig.cats$GO$term == category]
+}
+
+if(length(grep(category, sig.cats$KEGG$Name))){
+  specific.cat = 'specific.kegg'
+  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$Name)]
+}
+
+if(length(grep(category, sig.cats$KEGG$category))){
+  specific.cat = 'specific.kegg'
+  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$category)]
+}
+
+if(length(intersect(category, CC.reducedTerms$parentTerm))){
+  rt = CC.reducedTerms
+  specific.cat = 'parent.category'
+}
+
+if(length(intersect(category, BP.reducedTerms$parentTerm))){
   rt = BP.reducedTerms
-}
-
-if(specific.cat ==  'MF.parent.category'){
+  specific.cat = 'parent.category'
+}
+
+if(length(intersect(category, MF.reducedTerms$parentTerm))){
   rt = MF.reducedTerms
+  specific.cat = 'parent.category'
 }
@@
 
-volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'A9FvMT']),
-                          FC = A9MvFT[T9, 'logFC'],
-                          Color = 'grey',
-                          size = 3*log(meancpm[T9,"A9MT"]),
-                          M.cpm = meancpm[T9,"A9MT"],
-                          F.cpm = meancpm[T9,"A9FT"],
-                          SM.cpm = meancpm[T9,"S9MT"],
-                          SF.cpm = meancpm[T9,"S9FT"],
-                          GO.terms = "none")
-
-main.title = ""
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
-
 volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
@@
 
-if(specific.cat == 'parent.category' | specific.cat == 'BP.parent.category' | specific.cat == 'MF.parent.category'){
+if(specific.cat == 'parent.category'){
   parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
@@
 
-##volcano.data
+if(plot.all == F){
+  volcano.data = volcano.data[volcano.data$Color == "deeppink",]
+}
 
 fig = plot_ly(data = volcano.data,
-              x = ~FC,
-              y = ~FDR,
+              x = ~MFC,
+              y = ~FFC,
               type = 'scatter',
               mode = 'markers',
-              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
-                            line = list(color = 'black', width = .5)),
+              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
+                            reversescale =T,
+                             colorbar = list(title = "delta FC",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Color,
+                             line = list(color = "black", width = 1.5),
+                             size = volcano.data$size),
               hoverinfo = "text",
@@
                       "\n-log2(FDR): ", round(volcano.data$FDR,2),
-                      "\nFC: ", round(volcano.data$FC,2),
+                      "\nMale FC: ", round(volcano.data$MFC,2),
+                      "\nFemale FC: ", round(volcano.data$FFC,2),
                       "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
@@
                       "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
-fig = fig %>% layout(title = main.title)
+fig = fig %>% layout(title = main.title,
+                     shapes = list(
+                       type = "line",
+                       line = list(color = "black", dash = 'dash', width = 2),
+                       x0 = -10,
+                       x1 = 10,
+                       y0 = -10,
+                       y1 = 10))
 
@@
 
-```{r include = F}
+```{r echo = F, message = F}
+
+FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
+MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
+
+ontology = "CC"
+GO.data = MGO.data[MGO.data$ontology == ontology,
+                  c("category", "term","adjp", "numDEInCat", "numInCat")]
+GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
+
+data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
+data$MaleScore = -log10(GO.data$adjp)
+data$FemaleScore = -log10(GO.data$Female.adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+data$Fup = 0
+data$Fdown = 0
+data$Mup = 0
+data$Mdown = 0
+data$FmeanFC = 0
+data$MmeanFC = 0
+
+M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
+F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
+MFC = setNames(FC$AvS9MT, row.names(FC))
+FFC = setNames(FC$AvS9FT, row.names(FC))
+
+i = 1
+while(i <= nrow(data)){
+  go.id = row.names(data)[i]
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  Mgo.genes = intersect(go.genes, M.sigs)
+  Fgo.genes = intersect(go.genes, F.sigs)
+  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
+  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
+  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
+  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
+  if(length(Fgo.genes)>0){
+    data$FmeanFC[i] = mean(FFC[Fgo.genes])
+  }
+  if(length(Mgo.genes)>0){
+    data$MmeanFC[i] = mean(MFC[Mgo.genes])
+  }
+  i = i +1
+}
+
+data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
+data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
+
+data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
+data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
+
+data$Color = data$MTotalxFC - data$FTotalxFC
+data$Size = 5*log(data$numDEInCat)
+
+fig = plot_ly(data = data,
+              x = ~MTotalxFC,
+              y = ~FTotalxFC,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
+                            reversescale =T,
+                             colorbar = list(title = "delta FC",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Color,
+                             line = list(color = "black", width = 1.5),
+                             size = ~Size),
+              hoverinfo = "text",
+              hovertext = paste("GOterm:", data$term,
+                                "\nGO ID:", data$category,
+                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
+                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
+                      "\nMale meanFC: ", round(data$MmeanFC,2),
+                      "\nFemale meanFC: ", round(data$FmeanFC,2),
+                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
+                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
+                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
+                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
+fig = fig %>% layout(title = "",
+                     shapes = list(
+                       type = "line",
+                       line = list(color = "black", dash = 'dash', width = 2),
+                       x0 = -10,
+                       x1 = 4,
+                       y0 = -10,
+                       y1 = 4))
+
+fig
+
+```
+
+```{r echo = F, message = F}
+
+##FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
+##MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
+
+ontology = "BP"
+GO.data = MGO.data[MGO.data$ontology == ontology,
+                  c("category", "term","adjp", "numDEInCat", "numInCat")]
+GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
+
+data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
+data$MaleScore = -log10(GO.data$adjp)
+data$FemaleScore = -log10(GO.data$Female.adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+data$Fup = 0
+data$Fdown = 0
+data$Mup = 0
+data$Mdown = 0
+data$FmeanFC = 0
+data$MmeanFC = 0
+
+M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
+F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
+MFC = setNames(FC$AvS9MT, row.names(FC))
+FFC = setNames(FC$AvS9FT, row.names(FC))
+
+i = 1
+while(i <= nrow(data)){
+  go.id = row.names(data)[i]
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  Mgo.genes = intersect(go.genes, M.sigs)
+  Fgo.genes = intersect(go.genes, F.sigs)
+  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
+  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
+  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
+  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
+  if(length(Fgo.genes)>0){
+    data$FmeanFC[i] = mean(FFC[Fgo.genes])
+  }
+  if(length(Mgo.genes)>0){
+    data$MmeanFC[i] = mean(MFC[Mgo.genes])
+  }
+  i = i +1
+}
+
+data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
+data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
+
+data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
+data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
+
+data$Color = data$MTotalxFC - data$FTotalxFC
+data$Size = 10*log10(data$numDEInCat)
+
+fig = plot_ly(data = data,
+              x = ~MTotalxFC,
+              y = ~FTotalxFC,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(colorscale = list(c(0,.5,1), c("firebrick","ivory", "royalblue")),
+                            reversescale =T,
+                             colorbar = list(title = "delta FC",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Color,
+                             line = list(color = "black", width = 1.5),
+                             size = ~Size),
+              hoverinfo = "text",
+              hovertext = paste("GOterm:", data$term,
+                                "\nGO ID:", data$category,
+                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
+                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
+                      "\nMale meanFC: ", round(data$MmeanFC,2),
+                      "\nFemale meanFC: ", round(data$FmeanFC,2),
+                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
+                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
+                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
+                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
+fig = fig %>% layout(title = "",
+                     shapes = list(
+                       type = "line",
+                       line = list(color = "black", dash = 'dash', width = 2),
+                       x0 = -10,
+                       x1 = 6,
+                       y0 = -10,
+                       y1 = 6))
+
+fig
+
+```
+
+```{r echo = F, message = F}
+
+##FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
+##MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
+
+ontology = "MF"
+GO.data = MGO.data[MGO.data$ontology == ontology,
+                  c("category", "term","adjp", "numDEInCat", "numInCat")]
+GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
+
+data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
+data$MaleScore = -log10(GO.data$adjp)
+data$FemaleScore = -log10(GO.data$Female.adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+data$Fup = 0
+data$Fdown = 0
+data$Mup = 0
+data$Mdown = 0
+data$FmeanFC = 0
+data$MmeanFC = 0
+
+M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
+F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
+MFC = setNames(FC$AvS9MT, row.names(FC))
+FFC = setNames(FC$AvS9FT, row.names(FC))
+
+i = 1
+while(i <= nrow(data)){
+  go.id = row.names(data)[i]
+  go.genes = genesingo[[go.id]]
+  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
+  Mgo.genes = intersect(go.genes, M.sigs)
+  Fgo.genes = intersect(go.genes, F.sigs)
+  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
+  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
+  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
+  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
+  if(length(Fgo.genes)>0){
+    data$FmeanFC[i] = mean(FFC[Fgo.genes])
+  }
+  if(length(Mgo.genes)>0){
+    data$MmeanFC[i] = mean(MFC[Mgo.genes])
+  }
+  i = i +1
+}
+
+data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
+data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
+
+data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
+data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
+
+data$Color = data$MTotalxFC - data$FTotalxFC
+data$Size = 5*log(data$numDEInCat)
+
+fig = plot_ly(data = data,
+              x = ~MTotalxFC,
+              y = ~FTotalxFC,
+              type = 'scatter',
+              mode = 'markers',
+              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
+                            reversescale =T,
+                             colorbar = list(title = "delta FC",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0),##, dtick = .01),
+                             color = ~Color,
+                             line = list(color = "black", width = 1.5),
+                             size = ~Size),
+              hoverinfo = "text",
+              hovertext = paste("GOterm:", data$term,
+                                "\nGO ID:", data$category,
+                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
+                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
+                      "\nMale meanFC: ", round(data$MmeanFC,2),
+                      "\nFemale meanFC: ", round(data$FmeanFC,2),
+                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
+                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
+                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
+                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
+fig = fig %>% layout(title = "",
+                     shapes = list(
+                       type = "line",
+                       line = list(color = "black", dash = 'dash', width = 2),
+                       x0 = -10,
+                       x1 = 4,
+                       y0 = -10,
+                       y1 = 4))
+
+fig
+
+```
+
+```{r echo = F, include = F}
 
@@
 glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
-glycolysis.genes$FC = A9MvFT[glycolysis.genes$FBgn, 'logFC']
-glycolysis.genes$FDr = A9MvFT[glycolysis.genes$FBgn, 'FDR']
+glycolysis.genes$FC = FC[glycolysis.genes$FBgn, 'AvS9MT']
+glycolysis.genes$FDr = FDR[glycolysis.genes$FBgn, 'AvS9MT']
 
@@
 
-glycolysis.edges$size = log10(meancpm[glycolysis.edges[,'FBgn'], 'A9MT'])
+temp = setNames(meancpm[,'S9MT'], row.names(meancpm))
+glycolysis.edges$mean.S = temp[glycolysis.edges[,'FBgn']]
+
+temp = setNames(meancpm[,'A9MT'], row.names(meancpm))
+glycolysis.edges$mean.A = temp[glycolysis.edges[,'FBgn']]
+
+glycolysis.edges$size = log10(temp[glycolysis.edges[,'FBgn']])
 glycolysis.edges$size[glycolysis.edges$size <1] = 1
@@
 
-glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
+glycolysis.edges$FC = FC[glycolysis.edges[,'FBgn'], 'AvS9MT']
+glycolysis.edges$FDR = FDR[glycolysis.edges[,'FBgn'], 'AvS9MT']
+
+glycolysis.edges$color = FC[glycolysis.edges[,'FBgn'], 'AvS9MT']
 ## max color intensity is at FC of 2
@@
 glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
-                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
-                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))
+                          "<br>log2(FC): ", signif(glycolysis.edges$FC,3),
+                          "<br>FDR: ", signif(glycolysis.edges$FDR,3),
+                          "<br> A9MT cpm: ", signif(glycolysis.edges$mean.A,3),
+                          "<br>S9MT cpm: ", signif(glycolysis.edges$mean.S,3))
 
@@
 
-visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
+visNetwork(nodes, edges, main = "AvS9MT")%>%
   visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
@@
 ```
+
+```{r echo = F, message = F}
+
+geneList = setNames(FC$AvS9MT, row.names(FC))
+geneList = geneList[order(geneList, decreasing = T)]
+
+```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.V3.Rmd
overdue update

--- 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.Rmd
@@
 library(visNetwork)
+library(pathview)
+library(rstudioapi)
+library(clusterProfiler)
+library(UpSetR)
 
@@
 
+KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
+
+genesingo=as.list(org.Dm.egGO2ALLEGS)
+
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
@@
 
-```{r echo = F, include =F}
+```{r echo = F, message = F}
 
-GO20 = function(GO.data, GO.ontology){
-GO.data = GO.data[GO.data$ontology == GO.ontology,
-                  c("category", "term","adjp", "numDEInCat", "numInCat")]
-
-data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 4
+Male_DEGs<- list(
+  "Male Thorax 3 Day" = row.names(FDR)[FDR$AvS3MT < 0.05], 
+  "Female Thorax 3 Day" = row.names(FDR)[FDR$AvS3FT < 0.05],
+  "Male Thorax 9 Day" = row.names(FDR)[FDR$AvS9MT < 0.05], 
+  "Female Thorax 9 Day" = row.names(FDR)[FDR$AvS9FT < 0.05],
+  "Female Thorax 40 Day" = row.names(FDR)[FDR$AvS40FT < 0.05]
   )
 
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "term",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$term,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3))) %>%
-    layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Top 20 Most Enriched GO Terms",
-           margin = m)
+degs_intersection_upset = upset(
+                                fromList(Male_DEGs),
+                                nsets = length(Male_DEGs),
+                                nintersects = NA,
+                                empty.intersections = "on", 
+                                main.bar.color = "cyan4", 
+                                sets.bar.color = 'coral1',
+                                matrix.color = 'cyan4',
+                                keep.order=T,
+                                set_size.show =T,
+                                group.by = 'sets',
+                                set_size.scale_max = max(lengths(Male_DEGs))*1.25,
+                                sets.x.label = 'Total DEGs',
+                                  queries = list(
+                                    list(
+                                      query = intersects,
+                                      params = list("Male Thorax 3 Day"),
+                                      active = T,
+                                      query.name = "Male 3 Day",
+                                      color = "orange"
+                                      ))
+                                )
 
-  return(fig)
-}
+degs_intersection_upset
 
 ```
-
-```{r, echo = F, include = F}
-
-KEGG20 = function(data){
-
-  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
-
-data$term = data$Name
-if(length(unique(data$term)) < length(data$term)){
-  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
-}  
-data = data[20:1,]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 4
-)
-
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "Name",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$Name,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3))) %>%
-    layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Top 20 Most Enriched KEGG Terms",
-           margin = m)
-
-return(fig)
-
-}
-
-```
-
-```{r echo = F}
-
-cutoff=0
-
-sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
-sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
-sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
-sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
-A3 = A3[apply(meancpm[A3, c("A3FT", "A3MT", "S3FT", "S3MT")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MT < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FT < 0.05])
-
-A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
-A9 = A9[apply(meancpm[A9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MT < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FT < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-T3 = A3
-T9 = A9
-
-```
-
-Thorax Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
-
-```
-
-```{r echo = F}
-
-sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
-sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
-sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
-sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
-A3 = A3[apply(meancpm[A3, c("A3FH", "A3MH", "S3FH", "S3MH")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MH < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FH < 0.05])
-
-A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
-A9 = A9[apply(meancpm[A9, c("A9FH", "A9MH", "S9FH", "S9MH")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MH < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FH < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-H3=A3
-H9=A9
-
-```
-
-Head Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
-
-```
-
-```{r echo = F}
-
-sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
-sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
-sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
-sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
-A3 = A3[apply(meancpm[A3, c("A3FA", "A3MA", "S3FA", "S3MA")],MARGIN = 1, mean)>cutoff]
-A3 = intersect(A3, row.names(FDR)[FDR$AvS3MA < 0.05])
-A3 = setdiff(A3, row.names(FDR)[FDR$AvS3FA < 0.05])
-
-A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
-A9 = A9[apply(meancpm[A9, c("A9FA", "A9MA", "S9FA", "S9MA")],MARGIN = 1, mean)>cutoff]
-A9 = intersect(A9, row.names(FDR)[FDR$AvS9MA < 0.05])
-A9 = setdiff(A9, row.names(FDR)[FDR$AvS9FA < 0.05])
-
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-GR = GR[apply(GR.cpm[GR, c("GR.F1", "GR.F2",
-                           "GR.M1","GR.M2","GR.M3",
-                           "WT.F1","WT.F2",
-                           "WT.M1","WT.M2","WT.M3")],MARGIN = 1, mean)>cutoff]
-GR=intersect(GR, row.names(GR.FDR)[GR.FDR$GRxWT.MC < 0.05])
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-A3=A3
-A9=A9
-
-```
-
-Abdomen Sex Specific DEGs
-```{r echo = F}
-
-##Triple Venn
-grid.newpage()
-draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)
-
-```
-
-```{r include = F, echo = F}
-
-sigs = T9##setdiff(T9,T3)
-bg = row.names(FDR)
-
-sigsKEY = GeneIDKey[sigs,]
-sigs = na.omit(sigsKEY$Symbol)
-bgKEY = GeneIDKey[bg,]
-bg = na.omit(bgKEY$Symbol)
-
-sig.cats = Enrichment(sigs, bg)
-thorax.cats = sig.cats
-
-```
-
-```{r echo =F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "CC"
-go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
-
-simMatrix <- calculateSimMatrix(go_analysis,
-                                orgdb="org.Dm.eg.db",
-                                ont=GO.ontology,
-                                method="Rel")
-
-reducedTerms <- reduceSimMatrix(simMatrix,
-                                scores,
-                                threshold=0.7,
-                                orgdb="org.Dm.eg.db")
-
-```
-
-```{r echo =F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
-
-BP.simMatrix <- calculateSimMatrix(go_analysis,
-                                orgdb="org.Dm.eg.db",
-                                ont=GO.ontology,
-                                method="Rel")
-
-BP.reducedTerms <- reduceSimMatrix(BP.simMatrix,
-                                scores,
-                                threshold=0.7,
-                                orgdb="org.Dm.eg.db")
-
-```
-
-```{r echo =F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "MF"
-go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
-scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
-
-MF.simMatrix <- calculateSimMatrix(go_analysis,
-                                orgdb="org.Dm.eg.db",
-                                ont=GO.ontology,
-                                method="Rel")
-
-MF.reducedTerms <- reduceSimMatrix(MF.simMatrix,
-                                scores,
-                                threshold=0.7,
-                                orgdb="org.Dm.eg.db")
-
-```
-
-```{r echo = F, include =F}
-
-GO.data = sig.cats[["GO"]]
-GO.ontology = "BP"
-BP.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "CC"
-CC.GO.fig = GO20(GO.data, GO.ontology)
-
-GO.ontology = "MF"
-MF.GO.fig = GO20(GO.data, GO.ontology)
-
-KEGG.fig = KEGG20(sig.cats[["KEGG"]])
-
-```
-
-9 Day Thorax Biological Process GO Terms
-```{r, echo = F,  fig.width= 10}
-
-BP.GO.fig
-
-```
-
-9 Day Thorax Cellular Component GO Terms
-```{r, echo = F,  fig.width= 10}
-
-CC.GO.fig
-
-```
-
-9 Day Thorax Molecular Function GO Terms
-```{r, echo = F,  fig.width= 10}
-
-MF.GO.fig
-
-```
-
-9 Day Thorax KEGG Pathways
-```{r, echo = F,  fig.width= 10}
-
-KEGG.fig
-
-```
-
-9 Day Thorax Cellular Component GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(reducedTerms)
-
-```
-
-9 Day Thorax Biological Process GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(BP.reducedTerms)
-
-```
-
-9 Day Thorax Molecular Function GO Terms
-```{r  echo = F, fig.align='left'}
-
-treemapPlot(MF.reducedTerms)
-
-```
-
-```{r}
-
-x <- counts
-gr <- factor(substr(colnames(counts), 1, nchar(colnames(counts))-1))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- normLibSizes(y)
-design<-model.matrix(~0 + gr)
-colnames(design) = unique(gr)
-z = estimateDisp(z, design)
-fit <- glmQLFit(z, design)
-
-contr = makeContrasts(A9MT - A9FT, levels=design)
-qlf = glmQLFTest(fit, contrast=contr)
-DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEdata = DEdata$table
-A9MvFT = DEdata
-
-```
-
-```{r}
-
-volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'A9FvMT']),
-                          FC = A9MvFT[T9, 'logFC'],
-                          Color = 'grey',
-                          size = 3*log(meancpm[T9,"A9MT"]),
-                          M.cpm = meancpm[T9,"A9MT"],
-                          F.cpm = meancpm[T9,"A9FT"],
-                          SM.cpm = meancpm[T9,"S9MT"],
-                          SF.cpm = meancpm[T9,"S9FT"],
-                          GO.terms = "none")
-
-main.title = ""
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
-
-volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
-
-fig = plot_ly(data = volcano.data,
-              x = ~FC,
-              y = ~FDR,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
-                            line = list(color = 'black', width = .5)),
-              hoverinfo = "text",
-              hovertext = paste("Gene:", volcano.data$Symbol,
-                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
-                      "\nFC: ", round(volcano.data$FC,2),
-                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
-                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
-                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
-                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
-fig = fig %>% layout(title = main.title)
-
-              ##color = ~Color,
-              ##colors = 'Spectral')
-              ##color = ~Color,
-              ##colors = ~Color)
-              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))
-
-fig
-
-```
-
-```{r}
-
-##NMJ = GO:0031594
-##synapse = GO:0045202
-
-specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go', "BP.parent.category", "MF.parent.category")
-
-specific.cat = specific.cat[5]
-parent.category = 'response to biotic stimulus'
-specific.kegg = "none"
-specific.go =  '0031594'
-
-set.size = F
-
-if(specific.cat ==  'parent.category'){
-  rt = reducedTerms
-}
-
-if(specific.cat ==  'BP.parent.category'){
-  rt = BP.reducedTerms
-}
-
-if(specific.cat ==  'MF.parent.category'){
-  rt = MF.reducedTerms
-}
-
-GOterm.genes = vector('list', length = length(unique(rt$parent)))
-names(GOterm.genes) = unique(rt$parent)
-i=1
-while(i<=length(GOterm.genes)){
-  goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
-  genesinparent = unlist(genesingo[goinparent])
-  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
-  i = i +1
-}
-
-volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'A9FvMT']),
-                          FC = A9MvFT[T9, 'logFC'],
-                          Color = 'grey',
-                          size = 3*log(meancpm[T9,"A9MT"]),
-                          M.cpm = meancpm[T9,"A9MT"],
-                          F.cpm = meancpm[T9,"A9FT"],
-                          SM.cpm = meancpm[T9,"S9MT"],
-                          SF.cpm = meancpm[T9,"S9FT"],
-                          GO.terms = "none")
-
-main.title = ""
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
-
-volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
-
-if(set.size == T){
-  volcano.data$size = 15
-  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
-}
-
-if(specific.cat == 'parent.category' | specific.cat == 'BP.parent.category' | specific.cat == 'MF.parent.category'){
-  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
-  parent.genes = intersect(parent.genes, row.names(volcano.data))
-  volcano.data$Color = 'honeydew'
-  volcano.data[parent.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
-  main.title = parent.category
-}
-
-if(specific.cat == 'specific.kegg'){
-  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
-  kegg.genes = names(kegg[grep(kegg.id, kegg)])
-  volcano.data$Color = 'honeydew'
-  row.names(volcano.data) = volcano.data$Symbol
-    volcano.data[kegg.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
-}
-
-if(specific.cat == 'specific.go'){
-  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
-  volcano.data$Color = 'honeydew'
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  go.genes = intersect(go.genes, row.names(volcano.data))
-  volcano.data[go.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
-}
-
-##volcano.data
-
-fig = plot_ly(data = volcano.data,
-              x = ~FC,
-              y = ~FDR,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
-                            line = list(color = 'black', width = .5)),
-              hoverinfo = "text",
-              hovertext = paste("Gene:", volcano.data$Symbol,
-                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
-                      "\nFC: ", round(volcano.data$FC,2),
-                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
-                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
-                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
-                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
-fig = fig %>% layout(title = main.title)
-
-              ##color = ~Color,
-              ##colors = 'Spectral')
-              ##color = ~Color,
-              ##colors = ~Color)
-              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))
-
-fig
-
-```
-
-```{r include = F}
-
-##genes in the kegg pathway and their enzyme IDs
-glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
-##Edge data for genes connecting metabolites
-glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
-##Metabolites in the KEGG pathway with their ID
-glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')
-
-node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')
-
-##extracting position data for nodes
-node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
-                       number = rep(names(node.data$kegg.names),
-                                    lengths(node.data$kegg.names)),
-                       x = 0,
-                       y = 0,
-                       color = 0,
-                       names = "")
-node.info$x = node.data$x[node.info$number]
-node.info$y = node.data$y[node.info$number]
-
-##make new columns for transcriptomic data
-glycolysis.genes$FBgn = ""
-glycolysis.genes$Symbol = ""
-glycolysis.genes$FC = 0
-glycolysis.genes$pval = 1
-
-##Isolate gene ID info for goi
-temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
-row.names(temp) = temp$CG
-
-##fill in new columns with transcriptomic data
-glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
-glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
-glycolysis.genes$FC = A9MvFT[glycolysis.genes$FBgn, 'logFC']
-glycolysis.genes$FDr = A9MvFT[glycolysis.genes$FBgn, 'FDR']
-
-##make new columns for metabolomic data
-row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
-glycolysis.metabs$metabolomicsID = ""
-glycolysis.metabs$FC = 0
-glycolysis.metabs$pval = 1
-
-##retrieve name used in metabolomic data for metabolite IDs in path
-##including IDs associated with multiple metabolomic names
-i = 1
-while(i<=nrow(glycolysis.metabs)){
-  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
-    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
-  }
-  i = i +1
-}
-
-##using the positions for nodes (metabolites) only
-metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]
-
-metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
-metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
-metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']
-
-color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)
-
-metab.info$color[metab.info$color > 1] = 1
-metab.info$color[metab.info$color < -1] = -1
-metab.info$color = (metab.info$color * 200) +201
-metab.info$color = color.pallette[metab.info$color]
-metab.info$color[is.na(metab.info$color)] = 'dimgrey'
-
-metab.info$size = 10 + 10*abs(metab.info$size)
-metab.info$size[is.na(metab.info$size)] = 10
-
-metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
-                          "<br>log2(FC): ", signif(metab.info$FC,3),
-                          "<br>pval: ", signif(10^-metab.info$pval,3))
-
-nodes = data.frame(id = paste0(metab.info$names),
-                   color = metab.info$color,
-                   size = metab.info$size,
-                   x = 2*metab.info$x,
-                   y = 2*metab.info$y,
-                   physics = F,
-                   group = "",
-                   title = metab.info$title)
-
-glycolysis.edges$FBgn = ''
-temp.glycolysis.path = glycolysis.edges
-
-i = 1
-while(i<=nrow(glycolysis.edges)){
-  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
-  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
-    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
-    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
-    temp2 = glycolysis.edges[rep(i, length(temp)),]
-    temp2$FBgn = temp
-  }else{
-    temp2 = glycolysis.edges[i,]
-  }
-  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)
-
-  i = i +1
-}
-
-glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]
-
-glycolysis.edges$size = log10(meancpm[glycolysis.edges[,'FBgn'], 'A9MT'])
-glycolysis.edges$size[glycolysis.edges$size <1] = 1
-glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
-glycolysis.edges$size = 2*glycolysis.edges$size
-
-glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
-## max color intensity is at FC of 2
-glycolysis.edges$color[glycolysis.edges$color>1] = 1
-glycolysis.edges$color[glycolysis.edges$color<(-1)] = -1
-glycolysis.edges$color = 201+(glycolysis.edges$color *200)
-glycolysis.edges$color = color.pallette[glycolysis.edges$color]
-glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'
-
-glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
-                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
-                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))
-
-edges = data.frame(from = glycolysis.edges$from.name,
-                   to = glycolysis.edges$to.name,
-                   arrows = glycolysis.edges$arrow,
-                   color = glycolysis.edges$color,
-                   width = glycolysis.edges$size,
-                   title = glycolysis.edges$title,
-                   physics = T)
-
-nodes = data.frame(id = paste0(nodes$id),
-                   color = nodes$color,
-                   size = nodes$size,
-                   x = nodes$x,
-                   y = nodes$y,
-                   physics = F,
-                   group = "",
-                   title = nodes$title)
-
-OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
-                               'Propanoate Metabolism',
-                               'Starch and Sucrose Metabolism',
-                               'Citrate Cycle'),
-                        color = "black",
-                        size = 15,
-                        x= c(1350,1254,966,175),
-                        y=c(1112,1822,110,1700),
-                        physics = F,
-                        group = 'Outside Path',
-                        title = "")
-
-nodes = rbind(nodes, OutsidePath)
-
-visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows = edges$arrows)%>%
-  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))
-
-```

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_Tables.Rmd
overdue update

--- 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_PCA.Rmd
@@
 
-library(plotly)
 library(edgeR)
@@
 library(org.Dm.eg.db)
-library(rrvgo)
-library(VennDiagram)
 
@@
 countdata = countdata[-(grep("trans",row.names(countdata))),]
+
+countdata=countdata[substr(row.names(countdata),1,2)=="FB",]
 
@@
 ##write.csv(cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv")
+##write.csv(countdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.countdata.csv")
 ##write.csv(A4V.FDR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
@@
 ##write.csv(A4V.FC, "/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv")
-
-```
-
-```{r}
-
-cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
-
-meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
-
-FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
-
-FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
-
-meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
-
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
-
-```
-
-```{r echo = F}
-
-## arc1 FBgn = 'FBgn0033926'
-##spn FBgn = 'FBgn0010905'
-FBgn = 'FBgn0035348'
-name = ''
-
-par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
-gene = data.frame(cpm = as.numeric(cpm[FBgn,]), 
-                  condition = substr(row.names(meta),1, nchar(row.names(meta))-1), 
-                  group = paste(meta$Genotype, meta$Sex))
-
-gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
-                                                   "S3FH", "S9FH", "S40FH",
-                                                   "A3FT", "A9FT", "A40FT",
-                                                   "S3FT", "S9FT", "S40FT",
-                                                   "A3FA", "A9FA", "A40FA",
-                                                   "S3FA", "S9FA", "S40FA",
-                                                   "A3MH", "A9MH",
-                                                   "S3MH", "S9MH",
-                                                   "A3MT", "A9MT",
-                                                   "S3MT", "S9MT",
-                                                   "A3MA", "A9MA",
-                                                   "S3MA", "S9MA"))
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-legend('topright',
-       inset=c(-0.175,0),
-       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
-       fill = c('firebrick',"darkgreen","gold","dodgerblue"),
-       cex = .65,
-       bty = 'n',
-       pt.cex = .5)
 
@@
   return(enrichment.data)
-}
-
-```
-
-##GO.Sim.PCA function
-```{r echo = F, include = F}
-GO.Sim.PCA = function(use.data){
-    pca <- prcomp(t(use.data), scale.=TRUE) 
-    pc1=scale(pca$x[,1])
-    pc2=scale(pca$x[,2])
-    eigs <- pca$sdev^2
-    ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(PC1=pc1,
-                        PC2=pc2,
-                        sdev=pca$sdev,
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group = reducedTerms[row.names(use.data), "parentTerm"],
-                        Score = reducedTerms[row.names(use.data), "score"],
-                        Term = reducedTerms[row.names(use.data), "term"],
-                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
-                        Total = GO.data[row.names(use.data), "numInCat"],
-                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))
-
-    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
-    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))
-
-  fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~Group,
-                 ##symbol = ~Group,
-                 ##symbols = as.character(seq_along(unique(point.data$Set))),
-                 ##colors = c("firebrick","gold","deepskyblue"),
-                 marker = list(size = pca.data$Score,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Parent Group: ", pca.data$Group,
-                                   "\nSample: ", pca.data$Term, 
-                                   "\nTotal DE: ", pca.data$TotalDE, 
-                                   "\nTotal in Cat.: ", pca.data$Total, 
-                                   "\nFDR: ", pca.data$SigVal)) %>%
-    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
-           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
-           title = "Enriched GO term similarity")
-
-  return(fig)
-}
-
-```
-
-##GO20 Function
-```{r echo = F, include =F}
-
-GO20 = function(GO.data, GO.ontology){
-GO.data = GO.data[GO.data$ontology == GO.ontology,
-                  c("category", "term","adjp", "numDEInCat", "numInCat")]
-
-data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 4
-)
-
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "term",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$term,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3))) %>%
-    layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Top 20 Most Enriched GO Terms",
-           margin = m)
-
-  return(fig)
-}
-
-```
-
-##KEGG20 Function
-```{r, echo = F, include = F}
-
-KEGG20 = function(data){
-
-  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]
-
-data$term = data$Name
-if(length(unique(data$term)) < length(data$term)){
-  data$term[duplicated(data$term)] = paste(data$term[duplicated(data$term)], "2")
-}  
-data = data[20:1,]
-data$Score = -log10(data$adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-
-m <- list(
-  l = 50,
-  r = 50,
-  b = 100,
-  t = 100,
-  pad = 4
-)
-
-fig <- plot_ly(data, 
-               x = ~numDEInCat, y = ~term, 
-               type = 'bar',
-               name = "Name",
-               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
-    reversescale =T,
-                             colorbar = list(title = "-log10(FDR)",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Score,
-                             line = list(color = "black", width = 1.5)),
-    hoverinfo = "text",
-    hovertext = paste("Sample:", data$Name,
-                      "\nGO ID: ", data$category,
-                      "\nTotal DE: ", data$numDEInCat,
-                      "\nTotal in Cat.: ", data$numInCat,
-                      "\nFDR: ", signif(data$adjp, 3))) %>%
-    layout(xaxis = list(title = "Number of Genes"),
-           yaxis = list(title = ""),
-           title = "Top 20 Most Enriched KEGG Terms",
-           margin = m)
-
-return(fig)
-
 }
@@
 ```
-
-```{r}
-
-sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
-sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
-sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
-sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]
-
-GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
-GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
-
-sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
-sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]
-
-A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
-A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
-GR = setdiff(sigsGR.FxM, sigsWT.FxM)
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1="A4V 3-day"
-set2="A4V 9-day"
-set3="G85R Larvae"
-set4=""
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1=A3
-s2=A9
-s3=GR
-s4=""
-
-T3 = A3
-T9 = A9
-
-```
-
-```{r echo=F, include=F}
-
-FC.subset = FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
-                   "AvS3MH", "AvS9MH",
-                   "AvS3FT", "AvS9FT", "AvS40FT",
-                   "AvS3MT", "AvS9MT",
-                   "AvS3FA", "AvS9FA", "AvS40FA",
-                   "AvS3MA", "AvS9MA")]
-gr <- c("03FH", "09FH", "40FH",
-        "03MH", "09MH",
-        "03FT", "09FT", "40FT",
-        "03MT", "09MT",
-        "03FA", "09FA", "40FA",
-        "03MA", "09MA")
-colnames(FC.subset) = gr
-
-pca <- prcomp(t(FC.subset), scale.=TRUE)
-
-PC1=scale(pca$x[,1])
-PC2=scale(pca$x[,2])
-eigs <- pca$sdev^2
-ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(Sample=gr,
-                        ##PC1=scale(pca$x[,1]),
-                        ##PC2=scale(pca$x[,2]),
-                        PC1=scale(pca$x[,1]),
-                        PC2=scale(pca$x[,2]),
-                        sdev=pca$sdev,
-                        Tissue=substr(gr, 4, 4), 
-                        Sex=substr(gr, 3, 3), 
-                        Age=substr(gr, 1, 2),
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group= paste0(substr(gr, 3, 3),
-                                      substr(gr, 4, 4)),
-                        pca.color = substr(gr, 3, 3),
-                        pca.shape = substr(gr, 4, 4))
-
-fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~pca.color,
-                 symbol = ~pca.shape,
-                 marker = list(size = 15,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Sample:", pca.data$Sample)) %>%
-    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
-           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
-```
-
-```{r}
-
-  fig
-
-```
-
-```{r echo=F, include=F}
-
-pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "H"]
-
-remove = apply(pca.data, MARGIN = 1, sum) != 0
-
-pca.data = pca.data[remove,]
-
-pca <- prcomp(t(pca.data), scale.=TRUE) 
-gr <- colnames(pca.data)
-PC1=scale(pca$x[,1])
-PC2=scale(pca$x[,2])
-eigs <- pca$sdev^2
-ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(Sample=gr,
-                        ##PC1=scale(pca$x[,1]),
-                        ##PC2=scale(pca$x[,2]),
-                        PC1=scale(pca$x[,1]),
-                        PC2=scale(pca$x[,2]),
-                        sdev=pca$sdev,
-                        Genotype=substr(gr, 1, 1), 
-                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
-                        Age=substr(gr, 2, nchar(gr)-3),
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group= paste0(substr(gr, 1, 1),
-                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
-
-fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~Group,
-                 symbol = ~Genotype,
-                 ##symbols = as.character(seq_along(unique(point.data$Set))),
-                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
-                 marker = list(size = 15,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Sample:", pca.data$Sample)) %>%
-    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
-           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
-```
-
-```{r}
-
-  fig
-
-```
-
-```{r echo=F, include=F}
-
-pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "T"]
-
-remove = apply(pca.data, MARGIN = 1, sum) != 0
-
-pca.data = pca.data[remove,]
-
-pca <- prcomp(t(pca.data), scale.=TRUE) 
-gr <- colnames(pca.data)
-PC1=scale(pca$x[,1])
-PC2=scale(pca$x[,2])
-eigs <- pca$sdev^2
-ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(Sample=gr,
-                        ##PC1=scale(pca$x[,1]),
-                        ##PC2=scale(pca$x[,2]),
-                        PC1=scale(pca$x[,1]),
-                        PC2=scale(pca$x[,2]),
-                        sdev=pca$sdev,
-                        Genotype=substr(gr, 1, 1), 
-                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
-                        Age=substr(gr, 2, nchar(gr)-3),
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group= paste0(substr(gr, 1, 1),
-                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
-
-fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~Group,
-                 symbol = ~Genotype,
-                 ##symbols = as.character(seq_along(unique(point.data$Set))),
-                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
-                 marker = list(size = 15,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Sample:", pca.data$Sample)) %>%
-    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
-           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
-```
-
-```{r}
-
-  fig
-
-```
-
-```{r echo=F, include=F}
-
-pca.data = A4V.cpm[,substr(colnames(A4V.cpm), nchar(colnames(A4V.cpm))-1, nchar(colnames(A4V.cpm))-1) == "A"]
-
-remove = apply(pca.data, MARGIN = 1, sum) != 0
-
-pca.data = pca.data[remove,]
-
-pca <- prcomp(t(pca.data), scale.=TRUE) 
-gr <- colnames(pca.data)
-PC1=scale(pca$x[,1])
-PC2=scale(pca$x[,2])
-eigs <- pca$sdev^2
-ve=signif(((eigs / sum(eigs))*100)[1:3],4)
-
-    pca.data=data.frame(Sample=gr,
-                        ##PC1=scale(pca$x[,1]),
-                        ##PC2=scale(pca$x[,2]),
-                        PC1=scale(pca$x[,1]),
-                        PC2=scale(pca$x[,2]),
-                        sdev=pca$sdev,
-                        Genotype=substr(gr, 1, 1), 
-                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
-                        Age=substr(gr, 2, nchar(gr)-3),
-                        Percent1=ve[1],
-                        Percent2=ve[2],
-                        Group= paste0(substr(gr, 1, 1),
-                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
-
-fig  = plot_ly(data = pca.data, 
-                 x = ~PC1, 
-                 y = ~PC2,
-                 name = ~Group,
-                 type = 'scatter',
-                 mode = 'markers',
-                 showlegend = T,
-                 color = ~Group,
-                 symbol = ~Genotype,
-                 ##symbols = as.character(seq_along(unique(point.data$Set))),
-                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
-                 marker = list(size = 15,
-                               line = list(color = "black", width = 1.5)),
-                 hoverinfo = "text",
-                 hovertext = paste("Sample:", pca.data$Sample)) %>%
-    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
-           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
-```
-
-```{r}
-
-  fig
-
-```

### 2024-03-22 Cami_qpcr 2_28_24 - Sheet1.Rmd
overdue update

---
title: "Cami qPCR 20240228"
author: "John Santiago"
date: "2024-02-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

cami = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Cami_qpcr 2_28_24 - Sheet1.csv", header = T)

```

```{r}

plotdata1 = cami[cami$Genotype=='OK371>G4C2' & cami$Primer == 'vap33',]
plotdata2 = cami[cami$Genotype=='OK371>G4C2' & cami$Primer == 'Rp49',]
plotdata3 = cami[cami$Genotype=='OK371>G4C2' & cami$Primer == 'xbp1',] 
plotdata4 = cami[cami$Genotype=='OK371>G4C2' & cami$Primer == 'atf4',] 
plotdata5 = cami[cami$Genotype=='OK371>G4C2' & cami$Primer == 'atf6',]

plot(x = log2(plotdata1$Concentration), 
     y = plotdata1$Cq.Mean, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "firebrick",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)",
     ylim = c(16,28))

points(x = log2(plotdata2$Concentration),
       y = plotdata2$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "steelblue",
       col = "black")

points(x = log2(plotdata3$Concentration),
       y = plotdata3$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "gold",
       col = "black")

points(x = log2(plotdata4$Concentration),
       y = plotdata4$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "darkgreen",
       col = "black")

points(x = log2(plotdata5$Concentration),
       y = plotdata5$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "grey",
       col = "black")

linearmodel=lm(as.numeric(plotdata1$Cq.Mean)~log2(plotdata1$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="firebrick",lwd=2)
text(x = 2, y = 21,paste0("vap33 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata2$Cq.Mean)~log2(plotdata2$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="steelblue",lwd=2)
text(x = 2, y = 20.5,paste0("Rp49 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata3$Cq.Mean)~log2(plotdata3$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="gold",lwd=2)
text(x = 2, y = 20,paste0("xbp1 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata4$Cq.Mean)~log2(plotdata4$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="darkgreen",lwd=2)
text(x = 2, y = 19.5,paste0("atf4 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata5$Cq.Mean)~log2(plotdata5$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="grey",lwd=2)
text(x = 2, y = 19,paste0("atf6 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

legend("topright", legend = c("vap33", "Rp49", 'xbp1', 'atf4', 'atf5'), pch = 21, col = "black", pt.bg = c("firebrick", "steelblue", 'gold', 'darkgreen', 'grey'), bty = "n")

```

```{r}

cami2 = cami
cami2$Concentration[cami2$Concentration == 5] = 0
cami2$Concentration[cami2$Concentration == 2.5] = 5
cami2$Concentration[cami2$Concentration == 0] = 2.5

plotdata1 = cami2[cami2$Genotype=='OK371>G4C2' & cami2$Primer == 'vap33',]
plotdata2 = cami2[cami2$Genotype=='OK371>G4C2' & cami2$Primer == 'Rp49',]
plotdata3 = cami2[cami2$Genotype=='OK371>G4C2' & cami2$Primer == 'xbp1',] 
plotdata4 = cami2[cami2$Genotype=='OK371>G4C2' & cami2$Primer == 'atf4',] 
plotdata5 = cami2[cami2$Genotype=='OK371>G4C2' & cami2$Primer == 'atf6',]

plot(x = log2(plotdata1$Concentration), 
     y = plotdata1$Cq.Mean, 
     type = "p",  
     cex = 1, 
     pch = 21, 
     bg = "firebrick",
     col = "black",
     ylab = "Quantification Cycle (Cq)",
     xlab = "log2(cDNA Conc. (ng/uL)",
     ylim = c(16,28))

points(x = log2(plotdata2$Concentration),
       y = plotdata2$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "steelblue",
       col = "black")

points(x = log2(plotdata3$Concentration),
       y = plotdata3$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "gold",
       col = "black")

points(x = log2(plotdata4$Concentration),
       y = plotdata4$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "darkgreen",
       col = "black")

points(x = log2(plotdata5$Concentration),
       y = plotdata5$Cq.Mean,
       cex = 1,
       pch = 21,
       bg = "grey",
       col = "black")

linearmodel=lm(as.numeric(plotdata1$Cq.Mean)~log2(plotdata1$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="firebrick",lwd=2)
text(x = 2, y = 21,paste0("vap33 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata2$Cq.Mean)~log2(plotdata2$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="steelblue",lwd=2)
text(x = 2, y = 20.5,paste0("Rp49 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata3$Cq.Mean)~log2(plotdata3$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="gold",lwd=2)
text(x = 2, y = 20,paste0("xbp1 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata4$Cq.Mean)~log2(plotdata4$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="darkgreen",lwd=2)
text(x = 2, y = 19.5,paste0("atf4 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

linearmodel=lm(as.numeric(plotdata5$Cq.Mean)~log2(plotdata5$Concentration))
abline(a=linearmodel[[1]][[1]],b=linearmodel[[1]][2],lty=2,col="grey",lwd=2)
text(x = 2, y = 19,paste0("atf6 slope = ", signif(linearmodel[[1]][2],3)),cex=.8)

legend("topright", legend = c("vap33", "Rp49", 'xbp1', 'atf4', 'atf5'), pch = 21, col = "black", pt.bg = c("firebrick", "steelblue", 'gold', 'darkgreen', 'grey'), bty = "n")

```

### 2024-03-22 GeneExpressionBoxPlots.Rmd
overdue update

@@
 
+A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)
+
+A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
+
 ```
@@
 ##gstd1 FBgn0001149
+## arc1 FBgn0033926
 
@@
 
-FBgn = 'FBgn0004362'
+FBgn = 'FBgn0033926'
 name = ''
@@
 points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+
+```
+
+```{r echo = F}
+
+A4V.groups = as.vector(colnames(A4V.cpm))
+
+A4V.groups = substr(A4V.groups,1, nchar(A4V.groups)-1)
+
+par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
+                  condition = A4V.groups, 
+                  group = paste0(substr(A4V.groups, 1,1), substr(A4V.groups, nchar(as.vector(A4V.groups))-1,nchar(as.vector(A4V.groups))-1)))
+
+gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
+                                                   "S3FH", "S9FH", "S40FH",
+                                                   "A3FT", "A9FT", "A40FT",
+                                                   "S3FT", "S9FT", "S40FT",
+                                                   "A3FA", "A9FA", "A40FA",
+                                                   "S3FA", "S9FA", "S40FA",
+                                                   "A3MH", "A9MH",
+                                                   "S3MH", "S9MH",
+                                                   "A3MT", "A9MT",
+                                                   "S3MT", "S9MT",
+                                                   "A3MA", "A9MA",
+                                                   "S3MA", "S9MA"))
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+
+boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
+       fill = c('firebrick',"gold","darkgreen","dodgerblue"),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5)
 

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FT1_S3MH_S3MT_STAR.sh

@@ -1,0 +1,255 @@
+#!/bin/bash
+
+
+#SBATCH -J A3FT1_S3MH_S3MT_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G A3FT1_S3MH_S3MT_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="A3FT1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/A3FT_S3F_STAR.sh

@@ -1,0 +1,395 @@
+#!/bin/bash
+
+
+#SBATCH -J A3FT_S3F_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G A3FT_S3F_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="A3FT1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S3FA_S3FH_STAR.sh

@@ -1,0 +1,217 @@
+#!/bin/bash
+
+
+#SBATCH -J S3FA_S3FH_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 -N 2 --mem=64G S3FA_S3FH_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+sample="S3FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S3FT_S3MA_STAR.sh

@@ -1,0 +1,183 @@
+#!/bin/bash
+
+
+#SBATCH -J S3FT_S3MA_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G S3FT_S3MA_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S3FT2"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S3FT_S3M_STAR.sh

@@ -1,0 +1,425 @@
+#!/bin/bash
+
+
+#SBATCH -J S3FT_S3M_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 48:00:00 -N 2 --mem=64G S3FT_S3M_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S3FT1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S3F_STAR.sh

@@ -1,0 +1,315 @@
+#!/bin/bash
+
+
+#SBATCH -J S3F_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G S3F_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S3FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S40F_STAR.sh

@@ -1,0 +1,315 @@
+#!/bin/bash
+
+
+#SBATCH -J S40F_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G S40F_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S40FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S9F_STAR.sh

@@ -1,0 +1,315 @@
+#!/bin/bash
+
+
+#SBATCH -J S9F_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G S9F_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S9FA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/S9M_STAR.sh

@@ -1,0 +1,315 @@
+#!/bin/bash
+
+
+#SBATCH -J S9M_STAR.sh
+
+#SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 30 -t 24:00:00 -N 2 --mem=64G S9M_STAR.sh
+#/oscar/data/kwharton/jsantiago
+
+shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq/"
+stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+module load fastqc
+module load star
+module load samtools
+module load python
+
+
+
+
+
+
+
+sample="S9MA1"
+sample1=$sampledir$sample"_R1_001"
+sample2=$sampledir$sample"_R2_001"
+
+fastqc $sample1".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+fastqc $sample2".fastq.gz" -o $stardir"Output_Files/FastQC/" -t 16
+gzip -d $sample1".fastq.gz"
+gzip -d $sample2".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
[…]

### 2024-03-22 Anna qPCR data/PlottingImageFromPython.R

@@ -1,0 +1,35 @@
+library(dplyr)
+temp = read.csv("/Users/johncsantiago/Documents/Image.csv", header = F)
+temp = as.matrix(temp)
+
+##temp = t(temp)
+row.names(temp) = c(1:nrow(temp))
+##x = c(1:nrow(temp))
+##temp = cbind(x,temp)
+##colnames(temp) = c("x", 1:(ncol(temp)-1))
+
+colnames(temp)= c(1:ncol(temp))
+
+##temp = data.frame(temp)
+df = temp %>%
+  reshape2::melt() %>%
+  rename(y=Var1,x=Var2)
+
+##df$value[df$value >-50] = 50
+##df$value[df$value < (-25)] = -50
+##df$color = df$value
+##df$color[df$color ==(-50)] = 'orange'
+##df$color[df$color ==50] = 'navy'
+
+df$color = ceiling(df$value + abs(min(df$value))+1)
+
+color.pallette = colorRampPalette(c('orange','blue3', "navy"))(max(df$color))
+
+df$color = color.pallette[df$color]
+
+plot(x = df$x,
+     y = df$y,
+     col = df$color,
+     ylim = c(max(df$y),1),
+     ylab = NA,
+     xlab = NA)

### 2024-03-23 Anna qPCR data/AnnaThesisAnalyses.Rmd
update qPCR

---
title: "Anna Analysis with John"
author: "John Santiago"
date: "2024-03-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

qPCR = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/Anna%20qPCR%20data/Anna_qPCR_allData.csv")

```

```{r echo = F}

pcb = qPCR[qPCR$Primer == "PCB",]
pcb = pcb[pcb$Censor != 'yes',]
pcb = pcb[pcb$Concentration == 5,]
pcb = pcb[pcb$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(pcb$Genotype, pcb$Biological.replicate))

pcb.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  pcb.mean[i] = mean(na.omit(as.numeric(pcb[paste(pcb$Genotype, pcb$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.pcb = data.frame(Sample = temp,
                     pcb = pcb.mean,
                     rp49 = rp49.mean)

mean.pcb$dCT = mean.pcb$pcb - mean.pcb$rp49

```

```{r echo = F}

ldh = qPCR[qPCR$Primer == "LDH",]
ldh = ldh[ldh$Censor != 'yes',]
ldh = ldh[ldh$Concentration == 5,]
ldh = ldh[ldh$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(ldh$Genotype, ldh$Biological.replicate))

ldh.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  ldh.mean[i] = mean(na.omit(as.numeric(ldh[paste(ldh$Genotype, ldh$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.ldh = data.frame(Sample = temp,
                     ldh = ldh.mean,
                     rp49 = rp49.mean)

mean.ldh$dCT = mean.ldh$ldh - mean.ldh$rp49

```

```{r echo = F}

pdh = qPCR[qPCR$Primer == "PDH",]
pdh = pdh[pdh$Censor != 'yes',]
pdh = pdh[pdh$Concentration == 5,]
pdh = pdh[pdh$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(pdh$Genotype, pdh$Biological.replicate))

pdh.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  pdh.mean[i] = mean(na.omit(as.numeric(pdh[paste(pdh$Genotype, pdh$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.pdh = data.frame(Sample = temp,
                     pdh = pdh.mean,
                     rp49 = rp49.mean)

mean.pdh$dCT = mean.pdh$pdh - mean.pdh$rp49

```

```{r echo = F}

pepck = qPCR[qPCR$Primer == "Pepck-1",]
pepck = pepck[pepck$Censor != 'yes',]
pepck = pepck[pepck$Concentration == 5,]
pepck = pepck[pepck$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(pepck$Genotype, pepck$Biological.replicate))

pepck.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  pepck.mean[i] = mean(na.omit(as.numeric(pepck[paste(pepck$Genotype, pepck$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.pepck = data.frame(Sample = temp,
                     pepck = pepck.mean,
                     rp49 = rp49.mean)

mean.pepck$dCT = mean.pepck$pepck - mean.pepck$rp49

```

```{r echo = F}

idgf = qPCR[qPCR$Primer == "Idgf6",]
idgf = idgf[idgf$Censor != 'yes',]
idgf = idgf[idgf$Concentration == 5,]
idgf = idgf[idgf$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(idgf$Genotype, idgf$Biological.replicate))

idgf.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  idgf.mean[i] = mean(na.omit(as.numeric(idgf[paste(idgf$Genotype, idgf$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.idgf = data.frame(Sample = temp,
                     idgf = idgf.mean,
                     rp49 = rp49.mean)

mean.idgf$dCT = mean.idgf$idgf - mean.idgf$rp49

```

```{r echo = F}

p53 = qPCR[qPCR$Primer == "p53",]
p53 = p53[p53$Censor != 'yes',]
p53 = p53[p53$Concentration == 5,]
p53 = p53[p53$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(p53$Genotype, p53$Biological.replicate))

p53.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  p53.mean[i] = mean(na.omit(as.numeric(p53[paste(p53$Genotype, p53$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.p53 = data.frame(Sample = temp,
                     p53 = p53.mean,
                     rp49 = rp49.mean)

mean.p53$dCT = mean.p53$p53 - mean.p53$rp49

```

```{r echo = F}

PyK = qPCR[qPCR$Primer == "PyK",]
PyK = PyK[PyK$Censor != 'yes',]
PyK = PyK[PyK$Concentration == 5,]
PyK = PyK[PyK$Efficiency == 'no',]

rp49 = qPCR[qPCR$Primer == "RP49",]
rp49 = rp49[rp49$Censor != 'yes',]
rp49 = rp49[rp49$Concentration == 5,]
rp49 = rp49[rp49$Efficiency == 'no',]

temp = unique(paste(PyK$Genotype, PyK$Biological.replicate))

PyK.mean = rep(0, length(temp))
rp49.mean = rep(0, length(temp)) 
i=1
while(i<=length(temp)){
  PyK.mean[i] = mean(na.omit(as.numeric(PyK[paste(PyK$Genotype, PyK$Biological.replicate) == temp[i], "Cq"])))
  rp49.mean[i] = mean(na.omit(as.numeric(rp49[paste(rp49$Genotype, rp49$Biological.replicate) == temp[i], "Cq"])))
  i=i+1
}

mean.PyK = data.frame(Sample = temp,
                     PyK = PyK.mean,
                     rp49 = rp49.mean)

mean.PyK$dCT = mean.PyK$PyK - mean.PyK$rp49

```

```{r echo = F}

plotdata = mean.pcb
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "cornflowerblue"
main = "PCB"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.ldh
keep = T
color = "gold"
main = "LDH"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.pdh
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "brown"
main = "PDH"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.p53
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "black"
main = "p53"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.PyK
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "deeppink"
main = "PyK"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.idgf
keep = T
color = "limegreen"
main = "idgf6"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

```{r echo = F}

plotdata = mean.pepck
keep = T
color = "orange"
main = "PEPCK-1"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

boxplot(plotdata$dCT~plotdata$Sample,
     ylab = "dCT",
     xlab = "",
     main = main,
     las = 2)

points(x = plotdata$Sample,
       y = plotdata$dCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```

```{r echo = F}

dCT.aov = aov(plotdata$dCT~plotdata$Sample)

TukeyHSD(dCT.aov)

```

### 2024-03-26 Aleah_Thesis_Figures.Rmd
aleah data

--- 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_SexSpecificDEGs.V2.Rmd
@@
 ---
-title: "A4V PCA"
+title: "Aleah Thesis Analyses"
 author: "John Santiago"
-date: "2024-01-22"
+date: "2024-03-24"
 output: html_document
@@
 
-```{r echo=F, include=F}
-
+```{r echo = F}
+
+library(org.Dm.eg.db)
+library(goseq)
+library(rrvgo)
 library(plotly)
-library(edgeR)
-library(goseq)
-library(org.Dm.eg.db)
-library(rrvgo)
-library(VennDiagram)
-library(pathview)
-library(visNetwork)
-library(pathview)
-library(rstudioapi)
-library(clusterProfiler)
-
-```
-
-```{r echo = F}
+
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+
 counts = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.countdata.csv", row.names = 1)
@@
 
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
-GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
-GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
 kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
 kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)
+
+```
+
+```{r echo = F}
+
+total.DEGs = c(length(FDR$AvS3FH[FDR$AvS3FH < .05]),
+               length(FDR$AvS9FH[FDR$AvS9FH < .05]),
+               length(FDR$AvS40FH[FDR$AvS40FH < .05]),
+               length(FDR$AvS3FT[FDR$AvS3FT < .05]),
+               length(FDR$AvS9FT[FDR$AvS9FT < .05]),
+               length(FDR$AvS40FT[FDR$AvS40FT < .05]),
+               length(FDR$AvS3FA[FDR$AvS3FA < .05]),
+               length(FDR$AvS9FA[FDR$AvS9FA < .05]),
+               length(FDR$AvS40FA[FDR$AvS40FA < .05]),
+               NA,
+               length(FDR$AvS3MH[FDR$AvS3MH < .05]),
+               length(FDR$AvS9MH[FDR$AvS9MH < .05]),
+               length(FDR$AvS3MT[FDR$AvS3MT < .05]),
+               length(FDR$AvS9MT[FDR$AvS9MT < .05]),
+               length(FDR$AvS3MA[FDR$AvS3MA < .05]),
+               length(FDR$AvS9MA[FDR$AvS9MA < .05]))
+
+names(total.DEGs) = c('FH3', 'FH9', 'FH40',
+                      'FT3', 'FT9', 'FT40',
+                      'FA3', 'FA9', 'FA40',
+                      NA,
+                      'MH3', 'MH9',
+                      'MT3', 'MT9',
+                      'MA3', 'MA9')
+xlabel = names(total.DEGs)
+
+bp.color = c(rep("steelblue", 3), rep("gold2", 3), rep("brown3", 3),
+             NA,
+             rep("steelblue", 2), rep("gold2", 2), rep("brown3", 2))
+
+```
+
+```{r echo = F}
+
+par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+
+barplot(height = total.DEGs,
+        names.arg = xlabel,
+        beside = T,
+        col = bp.color,
+        las = 2,
+        xlab = "Sample",
+        ylab = "Total DEGs",
+        main = "Total DEGs in A4V vs Silent",
+        ylim = c(0, 4700))
+##abline(v = 11.5, lty =2)
+legend('topright',
+       inset=c(-.35,0),
+       bty = 'n',
+       legend = c('Head', 'Thorax', 'Abdomen'), 
+       fill = c('steelblue', 'gold2', 'brown3'),
+       pt.cex = 1,
+       cex = 1)
+text(x = c(5,16), 
+     y = c(4700, 4700),
+     labels = c("Female", "Male"))
+
+```
+
+```{r echo = F, warning=FALSE, message=F}
+library(VennDiagram)
+
+set1="Male 3 Day"
+set2="Female 3 Day"
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=row.names(FDR[FDR$AvS3MT <.05,])
+s2=row.names(FDR[FDR$AvS3FT <.05,])
+
+main = "3 Day Thorax DEGs"
+
+grid.newpage()
+draw.pairwise.venn(area1=length(s1),area2=length(s2),
+                   cross.area=length(intersect(s1,s2)),
+                   fill = c("royalblue1","brown1"),
+                   cex=1.5,
+                   cat.cex = 1,
+                   category = c(set1,set2),
+                   main = "main",
+                   cat.dist = c(.065,.05),
+                   cat.pos = c(-20,20))
 
@@
 data$label = data$term
-data$label[temp > 40] = paste0(substr(data$term[temp>40], 1 ,35), "...")
+##data$label[temp > 40] = paste0(substr(data$term[temp>40], 1 ,35), "...")
 
@@
 )
+
+data$label = factor(data$label, levels = data$label)
 
@@
            yaxis = list(title = ""),
-           title = paste0("Top 20 Most Enriched ", GO.ontology, " GO Terms"),
+           title = paste0("Top 20 Most Enriched KEGG Terms"),
            margin = m, barmode = 'overlay')
@@
 
-```{r echo = F}
-
-KEGG.diagram = function(PathwayID, out.id, FC.data, FDR.data){
-  ##KEGG Mapping Function
-  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
-    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
-    }
-  Home = dirname(rstudioapi::getSourceEditorContext()$path)
-  OutputDir = paste0(Home, "/KEGG_Image_Files/")
-  setwd(OutputDir)
-  sigs = names(FDR.data[FDR.data <= .05])
-  deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
-
-  pv.out <- pathview(gene.data =  deg.data,
-                   pathway.id = PathwayID,
-                   species = "dme",
-                   kegg.native = T,
-                   limit=list(gene=c(-2,2)),
-                   node.sum="max.abs",
-                   low="royalblue",mid = "grey",high="firebrick",
-                   out.suffix = out.id,
-                   bins=list(genes=30))
-  setwd(Home)
-  knitr::include_graphics(paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png"))
-}
-
-```
-
-##Using all DEGs from the A9MT vs S9MT comparison
-### (no minimum mean cpm cutoff or background factor DEG exclusion)
-```{r echo = F}
-
-cutoff=0
-
-##T9 = setdiff(row.names(FDR)[FDR[,'AvS9MT']<.05], row.names(FDR)[FDR[,'AvS9FT']<.05])
-T9 = row.names(FDR)[FDR[,'AvS9MT']<.05]
-T9 = T9[apply(meancpm[T9, c("A9FT", "A9MT", "S9FT", "S9MT")],MARGIN = 1, mean)>cutoff]
-
-```
-
 ```{r include = F, echo = F}
 
-sigs = T9
+sigs = row.names(FDR)[FDR$AvS3MT < 0.05]
+FC.data = setNames(FC$AvS3MT, row.names(FC))
+FDR.data = setNames(FDR$AvS3MT, row.names(FDR))
+
 bg = row.names(FDR)
-
 sig.cats = Enrichment(sigs, bg)
-thorax.cats = sig.cats
+mt3.cats = sig.cats
 
@@
 
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+BP.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "CC"
+CC.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "MF"
+MF.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+KEGG.data = sig.cats[["KEGG"]]
+KEGG.fig = KEGG20(KEGG.data, FC.data, FDR.data)
+
+```
+
+Male 3 Day Thorax Biological Process GO Terms
+```{r, echo = F,  fig.width= 10}
+
+BP.GO.fig
+
+```
+
+Male 3 Day Thorax Biological Process GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(BP.reducedTerms)
+
+```
+
+Male 3 Day Thorax Cellular Component GO Terms
+```{r, echo = F,  fig.width= 10}
+
+CC.GO.fig
+
+```
+
+Male 3 Day Thorax Cellular Component GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(CC.reducedTerms)
+
+```
+
+Male 3 Day Thorax Molecular Function GO Terms
+```{r, echo = F,  fig.width= 10}
+
+MF.GO.fig
+
+```
+
+Male 3 Day Thorax Molecular Function GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(MF.reducedTerms)
+
+```
+
+Male 3 Day Thorax KEGG Pathways
+```{r, echo = F,  fig.width= 10}
+
+KEGG.fig
+
+```
+
+```{r include = F, echo = F}
+
+sigs = row.names(FDR)[FDR$AvS3FT < 0.05]
+FC.data = setNames(FC$AvS3FT, row.names(FC))
+FDR.data = setNames(FDR$AvS3FT, row.names(FDR))
+
+bg = row.names(FDR)
+sig.cats = Enrichment(sigs, bg)
+ft3.cats = sig.cats
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "CC"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+CC.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+CC.reducedTerms <- reduceSimMatrix(CC.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+BP.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+BP.reducedTerms <- reduceSimMatrix(BP.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "MF"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+MF.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+MF.reducedTerms <- reduceSimMatrix(MF.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo = F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+BP.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "CC"
+CC.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "MF"
+MF.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+KEGG.data = sig.cats[["KEGG"]]
+KEGG.fig = KEGG20(KEGG.data, FC.data, FDR.data)
+
+```
+
+Female 3 Day Thorax Biological Process GO Terms
+```{r, echo = F,  fig.width= 10}
+
+BP.GO.fig
+
+```
+
+Female 3 Day Thorax Biological Process GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(BP.reducedTerms)
+
+```
+
+Female 3 Day Thorax Cellular Component GO Terms
+```{r, echo = F,  fig.width= 10}
+
+CC.GO.fig
+
+```
+
+Female 3 Day Thorax Cellular Component GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(CC.reducedTerms)
+
+```
+
+Female 3 Day Thorax Molecular Function GO Terms
+```{r, echo = F,  fig.width= 10}
+
+MF.GO.fig
+
+```
+
+Female 3 Day Thorax Molecular Function GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(MF.reducedTerms)
+
+```
+
+Female 3 Day Thorax KEGG Pathways
+```{r, echo = F,  fig.width= 10}
+
+KEGG.fig
+
+```
+
+```{r echo = F, warning=FALSE, message=F}
+library(VennDiagram)
+
+set1="Male 9 Day"
+set2="Female 9 Day"
+
+##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+s1=row.names(FDR[FDR$AvS9MT <.05,])
+s2=row.names(FDR[FDR$AvS9FT <.05,])
+
+main = "9 Day Thorax DEGs"
+
+grid.newpage()
+draw.pairwise.venn(area1=length(s1),area2=length(s2),
+                   cross.area=length(intersect(s1,s2)),
+                   fill = c("royalblue1","brown1"),
+                   cex=1.5,
+                   cat.cex = 1,
+                   category = c(set1,set2),
+                   main = "main",
+                   cat.dist = c(.065,.05),
+                   cat.pos = c(-20,20))
+
+```
+
+```{r include = F, echo = F}
+
+sigs = row.names(FDR)[FDR$AvS9MT < 0.05]
 FC.data = setNames(FC$AvS9MT, row.names(FC))
@@
 
+bg = row.names(FDR)
+sig.cats = Enrichment(sigs, bg)
+mt9.cats = sig.cats
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "CC"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+CC.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+CC.reducedTerms <- reduceSimMatrix(CC.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+BP.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+BP.reducedTerms <- reduceSimMatrix(BP.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "MF"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+MF.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+MF.reducedTerms <- reduceSimMatrix(MF.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo = F, include =F}
+
 GO.data = sig.cats[["GO"]]
@@
 
-9 Day Thorax Biological Process GO Terms
+Male 9 Day Thorax Biological Process GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-9 Day Thorax Biological Process GO Terms
+Male 9 Day Thorax Biological Process GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-9 Day Thorax Cellular Component GO Terms
+Male 3 Day Thorax Cellular Component GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-9 Day Thorax Cellular Component GO Terms
+Male 9 Day Thorax Cellular Component GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-9 Day Thorax Molecular Function GO Terms
+Male 9 Day Thorax Molecular Function GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-9 Day Thorax Molecular Function GO Terms
+Male 9 Day Thorax Molecular Function GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-9 Day Thorax KEGG Pathways
+Male 9 Day Thorax KEGG Pathways
 ```{r, echo = F,  fig.width= 10}
@@
 
-```{r echo = F, include=T, message = F, fig.align='center'}
-
-PathwayID = "04146"
-out.id = 'AvS9T'
-KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
-
-```
-
-```{r echo = F, include = F}
-
-##NMJ = GO:0031594
-##synapse = GO:0045202
-
-specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go', "BP.parent.category", "MF.parent.category")
-
-specific.cat = specific.cat[2]
-parent.category = 'peroxisome'
-specific.kegg = "none"
-specific.go =  '0042579'
-
-set.size = F
-
-specific.cat = 'none'
-
-if(length(intersect(parent.category, CC.reducedTerms$parentTerm))){
-  rt = CC.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-if(length(intersect(parent.category, BP.reducedTerms$parentTerm))){
-  rt = BP.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-if(length(intersect(parent.category, MF.reducedTerms$parentTerm))){
-  rt = MF.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-GOterm.genes = vector('list', length = length(unique(rt$parent)))
-names(GOterm.genes) = unique(rt$parent)
-i=1
-while(i<=length(GOterm.genes)){
-  goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
-  genesinparent = unlist(genesingo[goinparent])
-  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
-  i = i +1
-}
-
-volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'AvS9MT']),
-                          FC = FC[T9, 'AvS9MT'],
-                          Color = 'grey',
-                          size = 3*log(meancpm[T9,"A9MT"]),
-                          M.cpm = meancpm[T9,"A9MT"],
-                          F.cpm = meancpm[T9,"A9FT"],
-                          SM.cpm = meancpm[T9,"S9MT"],
-                          SF.cpm = meancpm[T9,"S9FT"],
-                          GO.terms = "none")
-
-main.title = ""
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'
-
-volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
-volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
-volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'
-
-volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
-
-if(set.size == T){
-  volcano.data$size = 15
-  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
-}
-
-if(specific.cat == 'parent.category'){
-  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
-  parent.genes = intersect(parent.genes, row.names(volcano.data))
-  volcano.data$Color = 'honeydew'
-  volcano.data[parent.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
-  main.title = parent.category
-}
-
-if(specific.cat == 'specific.kegg'){
-  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
-  kegg.genes = names(kegg[grep(kegg.id, kegg)])
-  volcano.data$Color = 'honeydew'
-  row.names(volcano.data) = volcano.data$Symbol
-    volcano.data[kegg.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
-}
-
-if(specific.cat == 'none'){
-  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
-  volcano.data$Color = 'honeydew'
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  go.genes = intersect(go.genes, row.names(volcano.data))
-  volcano.data[go.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
-}
-
-##volcano.data
-
-fig = plot_ly(data = volcano.data,
-              x = ~FC,
-              y = ~FDR,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
-                            line = list(color = 'black', width = .5)),
-              hoverinfo = "text",
-              hovertext = paste("Gene:", volcano.data$Symbol,
-                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
-                      "\nFC: ", round(volcano.data$FC,2),
-                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
-                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
-                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
-                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
-fig = fig %>% layout(title = main.title)
-
-              ##color = ~Color,
-              ##colors = 'Spectral')
-              ##color = ~Color,
-              ##colors = ~Color)
-              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))
-
-fig
-
-```
-
-```{r echo = F, include = T}
-
-category = 'neuromuscular junction'
-plot.all = F
-set.size = F
-
-volcano.data = data.frame(Symbol = GeneIDKey[T9, "Symbol"], 
-                          FDR = -log2(FDR[T9, 'AvS9MT']),
-                          MFC = FC[T9, 'AvS9MT'],
-                          FFC = FC[T9, 'AvS9FT'],
-                          ##size = 3*log(meancpm[T9,"A9MT"]),
-                          size = -log2(FDR[T9, 'AvS9MT']),
-                          M.cpm = meancpm[T9,"A9MT"],
-                          F.cpm = meancpm[T9,"A9FT"],
-                          SM.cpm = meancpm[T9,"S9MT"],
-                          SF.cpm = meancpm[T9,"S9FT"],
-                          GO.terms = "none",
-                          Color = FC[T9, 'AvS9MT'] - FC[T9, 'AvS9FT'])
-row.names(volcano.data) = T9
-
-main.title = ""
-
-specific.cat = 'none'
-
-if(length(intersect(category, sig.cats$GO$category))){
-  specific.cat = 'specific.go'
-  specific.go = sig.cats$GO$category[sig.cats$GO$category == category]
-}
-
-if(length(intersect(category, sig.cats$GO$term))){
-  specific.cat = 'specific.go'
-  specific.go = sig.cats$GO$category[sig.cats$GO$term == category]
-}
-
-if(length(grep(category, sig.cats$KEGG$Name))){
-  specific.cat = 'specific.kegg'
-  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$Name)]
-}
-
-if(length(grep(category, sig.cats$KEGG$category))){
-  specific.cat = 'specific.kegg'
-  specific.kegg = sig.cats$KEGG$category[grep(category, sig.cats$KEGG$category)]
-}
-
-if(length(intersect(category, CC.reducedTerms$parentTerm))){
-  rt = CC.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-if(length(intersect(category, BP.reducedTerms$parentTerm))){
-  rt = BP.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-if(length(intersect(category, MF.reducedTerms$parentTerm))){
-  rt = MF.reducedTerms
-  specific.cat = 'parent.category'
-}
-
-GOterm.genes = vector('list', length = length(unique(rt$parent)))
-names(GOterm.genes) = unique(rt$parent)
-i=1
-while(i<=length(GOterm.genes)){
-  goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
-  genesinparent = unlist(genesingo[goinparent])
-  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
-  i = i +1
-}
-
-volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3
-
-if(set.size == T){
-  volcano.data$size = 15
-  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
-}
-
-if(specific.cat == 'parent.category'){
-  parent.genes = GOterm.genes[[intersect(rt[rt$parentTerm == parent.category, "go"], names(GOterm.genes))]]
-  parent.genes = intersect(parent.genes, row.names(volcano.data))
-  volcano.data$Color = 'honeydew'
-  volcano.data[parent.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
-  main.title = parent.category
-}
-
-if(specific.cat == 'specific.kegg'){
-  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
-  kegg.genes = names(kegg[grep(kegg.id, kegg)])
-  volcano.data$Color = 'honeydew'
-  row.names(volcano.data) = volcano.data$Symbol
-    volcano.data[kegg.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
-}
-
-if(specific.cat == 'specific.go'){
-  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
-  volcano.data$Color = 'honeydew'
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  go.genes = intersect(go.genes, row.names(volcano.data))
-  volcano.data[go.genes, 'Color'] = 'deeppink'
-  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
-  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
-}
-
-if(plot.all == F){
-  volcano.data = volcano.data[volcano.data$Color == "deeppink",]
-}
-
-fig = plot_ly(data = volcano.data,
-              x = ~MFC,
-              y = ~FFC,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
-                            reversescale =T,
-                             colorbar = list(title = "delta FC",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Color,
-                             line = list(color = "black", width = 1.5),
-                             size = volcano.data$size),
-              hoverinfo = "text",
-              hovertext = paste("Gene:", volcano.data$Symbol,
-                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
-                      "\nMale FC: ", round(volcano.data$MFC,2),
-                      "\nFemale FC: ", round(volcano.data$FFC,2),
-                      "\nA4V Male Thorax mean cpm: ", round(volcano.data$M.cpm, 1),
-                      "\nA4V Female Thorax mean cpm: ", round(volcano.data$F.cpm, 1),
-                      "\nSilent Male Thorax mean cpm: ", round(volcano.data$SM.cpm, 1),
-                      "\nSilent Female Thorax mean cpm: ", round(volcano.data$SF.cpm, 1)))
-fig = fig %>% layout(title = main.title,
-                     shapes = list(
-                       type = "line",
-                       line = list(color = "black", dash = 'dash', width = 2),
-                       x0 = -10,
-                       x1 = 10,
-                       y0 = -10,
-                       y1 = 10))
-
-              ##color = ~Color,
-              ##colors = 'Spectral')
-              ##color = ~Color,
-              ##colors = ~Color)
-              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))
-
-fig
-
-```
-
-```{r echo = F, message = F}
-
-FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
-MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
-
-ontology = "CC"
-GO.data = MGO.data[MGO.data$ontology == ontology,
-                  c("category", "term","adjp", "numDEInCat", "numInCat")]
-GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
-
-data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
-data$MaleScore = -log10(GO.data$adjp)
-data$FemaleScore = -log10(GO.data$Female.adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-data$Fup = 0
-data$Fdown = 0
-data$Mup = 0
-data$Mdown = 0
-data$FmeanFC = 0
-data$MmeanFC = 0
-
-M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
-F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
-MFC = setNames(FC$AvS9MT, row.names(FC))
-FFC = setNames(FC$AvS9FT, row.names(FC))
-
-i = 1
-while(i <= nrow(data)){
-  go.id = row.names(data)[i]
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  Mgo.genes = intersect(go.genes, M.sigs)
-  Fgo.genes = intersect(go.genes, F.sigs)
-  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
-  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
-  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
-  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
-  if(length(Fgo.genes)>0){
-    data$FmeanFC[i] = mean(FFC[Fgo.genes])
-  }
-  if(length(Mgo.genes)>0){
-    data$MmeanFC[i] = mean(MFC[Mgo.genes])
-  }
-  i = i +1
-}
-
-data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
-data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
-
-data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
-data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
-
-data$Color = data$MTotalxFC - data$FTotalxFC
-data$Size = 5*log(data$numDEInCat)
-
-fig = plot_ly(data = data,
-              x = ~MTotalxFC,
-              y = ~FTotalxFC,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
-                            reversescale =T,
-                             colorbar = list(title = "delta FC",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Color,
-                             line = list(color = "black", width = 1.5),
-                             size = ~Size),
-              hoverinfo = "text",
-              hovertext = paste("GOterm:", data$term,
-                                "\nGO ID:", data$category,
-                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
-                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
-                      "\nMale meanFC: ", round(data$MmeanFC,2),
-                      "\nFemale meanFC: ", round(data$FmeanFC,2),
-                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
-                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
-                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
-                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
-fig = fig %>% layout(title = "",
-                     shapes = list(
-                       type = "line",
-                       line = list(color = "black", dash = 'dash', width = 2),
-                       x0 = -10,
-                       x1 = 4,
-                       y0 = -10,
-                       y1 = 4))
-
-fig
-
-```
-
-```{r echo = F, message = F}
-
-##FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
-##MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
-
-ontology = "BP"
-GO.data = MGO.data[MGO.data$ontology == ontology,
-                  c("category", "term","adjp", "numDEInCat", "numInCat")]
-GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
-
-data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
-data$MaleScore = -log10(GO.data$adjp)
-data$FemaleScore = -log10(GO.data$Female.adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-data$Fup = 0
-data$Fdown = 0
-data$Mup = 0
-data$Mdown = 0
-data$FmeanFC = 0
-data$MmeanFC = 0
-
-M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
-F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
-MFC = setNames(FC$AvS9MT, row.names(FC))
-FFC = setNames(FC$AvS9FT, row.names(FC))
-
-i = 1
-while(i <= nrow(data)){
-  go.id = row.names(data)[i]
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  Mgo.genes = intersect(go.genes, M.sigs)
-  Fgo.genes = intersect(go.genes, F.sigs)
-  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
-  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
-  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
-  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
-  if(length(Fgo.genes)>0){
-    data$FmeanFC[i] = mean(FFC[Fgo.genes])
-  }
-  if(length(Mgo.genes)>0){
-    data$MmeanFC[i] = mean(MFC[Mgo.genes])
-  }
-  i = i +1
-}
-
-data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
-data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
-
-data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
-data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
-
-data$Color = data$MTotalxFC - data$FTotalxFC
-data$Size = 10*log10(data$numDEInCat)
-
-fig = plot_ly(data = data,
-              x = ~MTotalxFC,
-              y = ~FTotalxFC,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(colorscale = list(c(0,.5,1), c("firebrick","ivory", "royalblue")),
-                            reversescale =T,
-                             colorbar = list(title = "delta FC",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Color,
-                             line = list(color = "black", width = 1.5),
-                             size = ~Size),
-              hoverinfo = "text",
-              hovertext = paste("GOterm:", data$term,
-                                "\nGO ID:", data$category,
-                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
-                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
-                      "\nMale meanFC: ", round(data$MmeanFC,2),
-                      "\nFemale meanFC: ", round(data$FmeanFC,2),
-                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
-                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
-                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
-                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
-fig = fig %>% layout(title = "",
-                     shapes = list(
-                       type = "line",
-                       line = list(color = "black", dash = 'dash', width = 2),
-                       x0 = -10,
-                       x1 = 6,
-                       y0 = -10,
-                       y1 = 6))
-
-fig
-
-```
-
-```{r echo = F, message = F}
-
-##FGO.data = Enrichment(row.names(FDR)[FDR$AvS9FT<.05], row.names(FDR))$GO
-##MGO.data = Enrichment(row.names(FDR)[FDR$AvS9MT<.05], row.names(FDR))$GO
-
-ontology = "MF"
-GO.data = MGO.data[MGO.data$ontology == ontology,
-                  c("category", "term","adjp", "numDEInCat", "numInCat")]
-GO.data$Female.adjp = FGO.data[row.names(GO.data), 'adjp']
-
-data = GO.data[,c("term","numDEInCat", "numInCat", "category")]
-data$MaleScore = -log10(GO.data$adjp)
-data$FemaleScore = -log10(GO.data$Female.adjp)
-data$term = factor(data$term, levels = c(unique(data$term)))
-data$Fup = 0
-data$Fdown = 0
-data$Mup = 0
-data$Mdown = 0
-data$FmeanFC = 0
-data$MmeanFC = 0
-
-M.sigs = row.names(FDR[FDR$AvS9MT <= 0.05,])
-F.sigs = row.names(FDR[FDR$AvS9FT <= 0.05,])
-MFC = setNames(FC$AvS9MT, row.names(FC))
-FFC = setNames(FC$AvS9FT, row.names(FC))
-
-i = 1
-while(i <= nrow(data)){
-  go.id = row.names(data)[i]
-  go.genes = genesingo[[go.id]]
-  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
-  Mgo.genes = intersect(go.genes, M.sigs)
-  Fgo.genes = intersect(go.genes, F.sigs)
-  data$Fup[i] = length(Fgo.genes[FFC[Fgo.genes]>0])
-  data$Fdown[i] = length(Fgo.genes[FFC[Fgo.genes]<0])
-  data$Mup[i] = length(Mgo.genes[MFC[Mgo.genes]>0])
-  data$Mdown[i] = length(Mgo.genes[MFC[Mgo.genes]<0])
-  if(length(Fgo.genes)>0){
-    data$FmeanFC[i] = mean(FFC[Fgo.genes])
-  }
-  if(length(Mgo.genes)>0){
-    data$MmeanFC[i] = mean(MFC[Mgo.genes])
-  }
-  i = i +1
-}
-
-data$MTotalxFC = (data$MmeanFC*(data$Mup + data$Mdown))
-data$FTotalxFC = (data$FmeanFC*(data$Fup + data$Fdown))
-
-data$MTotalxFC[data$MTotalxFC != 0] = log(abs(data$MTotalxFC[data$MTotalxFC != 0]))*(data$MTotalxFC[data$MTotalxFC != 0]/abs(data$MTotalxFC[data$MTotalxFC != 0]))
-data$FTotalxFC[data$FTotalxFC != 0] = log(abs(data$FTotalxFC[data$FTotalxFC != 0]))*(data$FTotalxFC[data$FTotalxFC != 0]/abs(data$FTotalxFC[data$FTotalxFC != 0]))
-
-data$Color = data$MTotalxFC - data$FTotalxFC
-data$Size = 5*log(data$numDEInCat)
-
-fig = plot_ly(data = data,
-              x = ~MTotalxFC,
-              y = ~FTotalxFC,
-              type = 'scatter',
-              mode = 'markers',
-              marker = list(colorscale = list(c(0,.45,1), c("firebrick","ivory", "royalblue")),
-                            reversescale =T,
-                             colorbar = list(title = "delta FC",
-                                      len = .8, outlinewidth = 0,
-                                      tickformat = ".2f",
-                                      tick0 = 0),##, dtick = .01),
-                             color = ~Color,
-                             line = list(color = "black", width = 1.5),
-                             size = ~Size),
-              hoverinfo = "text",
-              hovertext = paste("GOterm:", data$term,
-                                "\nGO ID:", data$category,
-                      "\nMale -log2(FDR): ", round(data$MaleScore,2),
-                      "\nFemale -log2(FDR): ", round(data$FemaleScore,2),
-                      "\nMale meanFC: ", round(data$MmeanFC,2),
-                      "\nFemale meanFC: ", round(data$FmeanFC,2),
-                      "\nIncrease FC DEG Males: ", round(data$Mup, 1),
-                      "\nDecrease FC DEG Males: ", round(data$Mdown, 1),
-                      "\nIncrease FC DEG Females: ", round(data$Fup, 1),
-                      "\nDecrease FC DEG Females: ", round(data$Fdown, 1)))
-fig = fig %>% layout(title = "",
-                     shapes = list(
-                       type = "line",
-                       line = list(color = "black", dash = 'dash', width = 2),
-                       x0 = -10,
-                       x1 = 4,
-                       y0 = -10,
-                       y1 = 4))
-
-fig
-
-```
-
-```{r echo = F, include = F}
-
-##genes in the kegg pathway and their enzyme IDs
-glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
-##Edge data for genes connecting metabolites
-glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
-##Metabolites in the KEGG pathway with their ID
-glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')
-
-node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')
-
-##extracting position data for nodes
-node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
-                       number = rep(names(node.data$kegg.names),
-                                    lengths(node.data$kegg.names)),
-                       x = 0,
-                       y = 0,
-                       color = 0,
-                       names = "")
-node.info$x = node.data$x[node.info$number]
-node.info$y = node.data$y[node.info$number]
-
-##make new columns for transcriptomic data
-glycolysis.genes$FBgn = ""
-glycolysis.genes$Symbol = ""
-glycolysis.genes$FC = 0
-glycolysis.genes$pval = 1
-
-##Isolate gene ID info for goi
-temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
-row.names(temp) = temp$CG
-
-##fill in new columns with transcriptomic data
-glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
-glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
-glycolysis.genes$FC = FC[glycolysis.genes$FBgn, 'AvS9MT']
-glycolysis.genes$FDr = FDR[glycolysis.genes$FBgn, 'AvS9MT']
-
-##make new columns for metabolomic data
-row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
-glycolysis.metabs$metabolomicsID = ""
-glycolysis.metabs$FC = 0
-glycolysis.metabs$pval = 1
-
-##retrieve name used in metabolomic data for metabolite IDs in path
-##including IDs associated with multiple metabolomic names
-i = 1
-while(i<=nrow(glycolysis.metabs)){
-  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
-    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
-  }
-  i = i +1
-}
-
-##using the positions for nodes (metabolites) only
-metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]
-
-metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
-metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
-metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']
-
-color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)
-
-metab.info$color[metab.info$color > 1] = 1
-metab.info$color[metab.info$color < -1] = -1
-metab.info$color = (metab.info$color * 200) +201
-metab.info$color = color.pallette[metab.info$color]
-metab.info$color[is.na(metab.info$color)] = 'dimgrey'
-
-metab.info$size = 10 + 10*abs(metab.info$size)
-metab.info$size[is.na(metab.info$size)] = 10
-
-metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
-                          "<br>log2(FC): ", signif(metab.info$FC,3),
-                          "<br>pval: ", signif(10^-metab.info$pval,3))
-
-nodes = data.frame(id = paste0(metab.info$names),
-                   color = metab.info$color,
-                   size = metab.info$size,
-                   x = 2*metab.info$x,
-                   y = 2*metab.info$y,
-                   physics = F,
-                   group = "",
-                   title = metab.info$title)
-
-glycolysis.edges$FBgn = ''
-temp.glycolysis.path = glycolysis.edges
-
-i = 1
-while(i<=nrow(glycolysis.edges)){
-  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
-  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
-    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
-    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
-    temp2 = glycolysis.edges[rep(i, length(temp)),]
-    temp2$FBgn = temp
-  }else{
-    temp2 = glycolysis.edges[i,]
-  }
-  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)
-
-  i = i +1
-}
-
-glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]
-
-temp = setNames(meancpm[,'S9MT'], row.names(meancpm))
-glycolysis.edges$mean.S = temp[glycolysis.edges[,'FBgn']]
-
-temp = setNames(meancpm[,'A9MT'], row.names(meancpm))
-glycolysis.edges$mean.A = temp[glycolysis.edges[,'FBgn']]
-
-glycolysis.edges$size = log10(temp[glycolysis.edges[,'FBgn']])
-glycolysis.edges$size[glycolysis.edges$size <1] = 1
-glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
-glycolysis.edges$size = 2*glycolysis.edges$size
-
-glycolysis.edges$FC = FC[glycolysis.edges[,'FBgn'], 'AvS9MT']
-glycolysis.edges$FDR = FDR[glycolysis.edges[,'FBgn'], 'AvS9MT']
-
-glycolysis.edges$color = FC[glycolysis.edges[,'FBgn'], 'AvS9MT']
-## max color intensity is at FC of 2
-glycolysis.edges$color[glycolysis.edges$color>1] = 1
-glycolysis.edges$color[glycolysis.edges$color<(-1)] = -1
-glycolysis.edges$color = 201+(glycolysis.edges$color *200)
-glycolysis.edges$color = color.pallette[glycolysis.edges$color]
-glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'
-
-glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
-                          "<br>log2(FC): ", signif(glycolysis.edges$FC,3),
-                          "<br>FDR: ", signif(glycolysis.edges$FDR,3),
-                          "<br> A9MT cpm: ", signif(glycolysis.edges$mean.A,3),
-                          "<br>S9MT cpm: ", signif(glycolysis.edges$mean.S,3))
-
-edges = data.frame(from = glycolysis.edges$from.name,
-                   to = glycolysis.edges$to.name,
-                   arrows = glycolysis.edges$arrow,
-                   color = glycolysis.edges$color,
-                   width = glycolysis.edges$size,
-                   title = glycolysis.edges$title,
-                   physics = T)
-
-nodes = data.frame(id = paste0(nodes$id),
-                   color = nodes$color,
-                   size = nodes$size,
-                   x = nodes$x,
-                   y = nodes$y,
-                   physics = F,
-                   group = "",
-                   title = nodes$title)
-
-OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
-                               'Propanoate Metabolism',
-                               'Starch and Sucrose Metabolism',
-                               'Citrate Cycle'),
-                        color = "black",
-                        size = 15,
-                        x= c(1350,1254,966,175),
-                        y=c(1112,1822,110,1700),
-                        physics = F,
-                        group = 'Outside Path',
-                        title = "")
-
-nodes = rbind(nodes, OutsidePath)
-
-visNetwork(nodes, edges, main = "AvS9MT")%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows = edges$arrows)%>%
-  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))
-
-```
-
-```{r echo = F, message = F}
-
-geneList = setNames(FC$AvS9MT, row.names(FC))
-geneList = geneList[order(geneList, decreasing = T)]
-
-```
+```{r include = F, echo = F}
+
+sigs = row.names(FDR)[FDR$AvS9FT < 0.05]
+FC.data = setNames(FC$AvS9FT, row.names(FC))
+FDR.data = setNames(FDR$AvS9FT, row.names(FDR))
+
+bg = row.names(FDR)
+sig.cats = Enrichment(sigs, bg)
+ft9.cats = sig.cats
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "CC"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+CC.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+CC.reducedTerms <- reduceSimMatrix(CC.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+BP.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+BP.reducedTerms <- reduceSimMatrix(BP.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo =F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "MF"
+go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)
+
+MF.simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+MF.reducedTerms <- reduceSimMatrix(MF.simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+```
+
+```{r echo = F, include =F}
+
+GO.data = sig.cats[["GO"]]
+GO.ontology = "BP"
+BP.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "CC"
+CC.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+GO.ontology = "MF"
+MF.GO.fig = GO20(GO.data, GO.ontology, FC.data, FDR.data)
+
+KEGG.data = sig.cats[["KEGG"]]
+KEGG.fig = KEGG20(KEGG.data, FC.data, FDR.data)
+
+```
+
+Female 9 Day Thorax Biological Process GO Terms
+```{r, echo = F,  fig.width= 10}
+
+BP.GO.fig
+
+```
+
+Female 9 Day Thorax Biological Process GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(BP.reducedTerms)
+
+```
+
+Female 9 Day Thorax Cellular Component GO Terms
+```{r, echo = F,  fig.width= 10}
+
+CC.GO.fig
+
+```
+
+Female 9 Day Thorax Cellular Component GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(CC.reducedTerms)
+
+```
+
+Female 9 Day Thorax Molecular Function GO Terms
+```{r, echo = F,  fig.width= 10}
+
+MF.GO.fig
+
+```
+
+Female 9 Day Thorax Molecular Function GO Terms
+```{r  echo = F, fig.align='left'}
+
+treemapPlot(MF.reducedTerms)
+
+```
+
+Female 9 Day Thorax KEGG Pathways
+```{r, echo = F,  fig.width= 10}
+
+KEGG.fig
+
+```
+
+```{r echo = F}
+
+set1="Male 3 Day"
+set2="Female 3 Day"
+set3="Male 9 Day"
+set4="Female 40 Day"
+
+s1=row.names(FDR[FDR$AvS3MT <.05,])
+s2=row.names(FDR[FDR$AvS3FT <.05,])
+s3=row.names(FDR[FDR$AvS9MT <.05,])
+s4=row.names(FDR[FDR$AvS40FT <.05,])
+
+main = "3 and 9 Day Thorax "
+
+grid.newpage()
+tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("royalblue1", "brown1","forestgreen","yellow2"),cex=2,cat.cex = 1, title = "main")
+
+```

### 2024-03-26 Anna qPCR data/AnnaThesisAnalyses.Rmd
aleah data

@@
 
+library(reshape2)
 qPCR = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/Anna%20qPCR%20data/Anna_qPCR_allData.csv")
@@
 
-pepck = qPCR[qPCR$Primer == "Pepck-1",]
+pepck = qPCR[qPCR$Primer == "Pepck1",]
 pepck = pepck[pepck$Censor != 'yes',]
@@
 
-idgf = qPCR[qPCR$Primer == "Idgf6",]
+idgf = qPCR[qPCR$Primer == "IDGF6",]
 idgf = idgf[idgf$Censor != 'yes',]
@@
 plotdata = mean.pcb
-keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
 color = "cornflowerblue"
 main = "PCB"
-plotdata = plotdata[keep,]
+
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+plotdata = plotdata[order(plotdata$Rep),]
+
+G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
+                plotdata[plotdata$Sample == "G85R", 'Rep'])
+WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
+                plotdata[plotdata$Sample == "WT", 'Rep'])
+RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
+                plotdata[plotdata$Sample == "RNAi", 'Rep'])
+
+paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
+                         WT = WT[unique(plotdata$Rep)],
+                         RNAi = RNAi[unique(plotdata$Rep)])
+row.names(paired.data) = unique(plotdata$Rep)
+
+paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
+                      'paired_p-val' = c(0,0,0))
+
+paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
+paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
+paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]
+
+paired.p
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == i, ]
+  ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+  ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT']   
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+
+```{r echo = F}
+
 plotdata = mean.ldh
@@
 main = "LDH"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+plotdata = plotdata[order(plotdata$Rep),]
+
+G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
+                plotdata[plotdata$Sample == "G85R", 'Rep'])
+WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
+                plotdata[plotdata$Sample == "WT", 'Rep'])
+RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
+                plotdata[plotdata$Sample == "RNAi", 'Rep'])
+
+paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
+                         WT = WT[unique(plotdata$Rep)],
+                         RNAi = RNAi[unique(plotdata$Rep)])
+row.names(paired.data) = unique(plotdata$Rep)
+
+paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
+                      'paired_p-val' = c(0,0,0))
+
+paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
+paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
+paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]
+
+paired.p
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(NA, length(unique(plotdata$Rep))),
+                  RNAi = rep(NA, length(unique(plotdata$Rep))))
+
+i=3
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+
+```{r echo = F}
+
 plotdata = mean.pdh
-keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
+keep = T
 color = "brown"
 main = "PDH"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+plotdata = plotdata[order(plotdata$Rep),]
+
+G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
+                plotdata[plotdata$Sample == "G85R", 'Rep'])
+WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
+                plotdata[plotdata$Sample == "WT", 'Rep'])
+RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
+                plotdata[plotdata$Sample == "RNAi", 'Rep'])
+
+paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
+                         WT = WT[unique(plotdata$Rep)],
+                         RNAi = RNAi[unique(plotdata$Rep)])
+row.names(paired.data) = unique(plotdata$Rep)
+
+paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
+                      'paired_p-val' = c(0,0,0))
+
+paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
+paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
+paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]
+
+paired.p
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+```{r echo = F}
+
 plotdata = mean.p53
@@
 main = "p53"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+
+```{r echo = F}
+
 plotdata = mean.PyK
@@
 main = "PyK"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+
+```{r echo = F}
+
 plotdata = mean.idgf
@@
 main = "idgf6"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+plotdata = plotdata[order(plotdata$Rep),]
+
+G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
+                plotdata[plotdata$Sample == "G85R", 'Rep'])
+WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
+                plotdata[plotdata$Sample == "WT", 'Rep'])
+RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
+                plotdata[plotdata$Sample == "RNAi", 'Rep'])
+
+paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
+                         WT = WT[unique(plotdata$Rep)],
+                         RNAi = RNAi[unique(plotdata$Rep)])
+row.names(paired.data) = unique(plotdata$Rep)
+
+paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
+                      'paired_p-val' = c(0,0,0))
+
+paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
+paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
+paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]
+
+paired.p
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```
+
+```{r echo = F}
+
 plotdata = mean.pepck
@@
 main = "PEPCK-1"
+
 plotdata = plotdata[keep,]
+plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
 plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
@@
 ```
+
+```{r echo = F}
+
+summary(aov(dCT ~ Sample + Rep, data = plotdata))
+
+```
+
+```{r echo = F}
+plotdata = plotdata[order(plotdata$Rep),]
+
+G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
+                plotdata[plotdata$Sample == "G85R", 'Rep'])
+WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
+                plotdata[plotdata$Sample == "WT", 'Rep'])
+RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
+                plotdata[plotdata$Sample == "RNAi", 'Rep'])
+
+paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
+                         WT = WT[unique(plotdata$Rep)],
+                         RNAi = RNAi[unique(plotdata$Rep)])
+row.names(paired.data) = unique(plotdata$Rep)
+
+paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
+                      'paired_p-val' = c(0,0,0))
+
+paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
+paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
+paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]
+
+paired.p
+```
+
+```{r echo = F}
+
+ddCT = data.frame(Rep = unique(plotdata$Rep),
+                  G85R = rep(0, length(unique(plotdata$Rep))),
+                  RNAi = rep(0, length(unique(plotdata$Rep))))
+
+i=1
+while(i <= length(unique(plotdata$Rep))){
+  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
+  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
+    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
+  }
+    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
+      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
+    }
+  i=i+1
+}
+
+ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')
+
+boxplot(ddCT$ddCT~ddCT$Sample,
+     ylab = "ddCT",
+     xlab = "",
+     main = main,
+     las = 2)
+
+points(x = ddCT$Sample,
+       y = ddCT$ddCT,
+       cex = 1.5,
+       pch = 21,
+       bg = color,
+       col = "black")
+
+```

### 2024-05-08 20240507_pharate_axonal_branching.Rmd
update

---
title: "20240507_pharate_axonal_branching"
author: "John Santiago"
date: "2024-05-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)

```

```{r echo = F}

plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
                      y = ab$X.Primary,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(ab$Sex),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Number of Primary Branches", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

```

```{r echo = F}

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$X.Primary,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, ab$Leg.Location)),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Number of Primary Branches", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

```

### 2024-05-08 Aleah_Thesis_Figures.Rmd
update

@@
      labels = c("Female", "Male"))
+
+```
+
+```{r echo = F}
+
+total.DEGs = c(length(FDR$AvS3FH[FDR$AvS3FH < .05]),
+               length(FDR$AvS9FH[FDR$AvS9FH < .05]),
+               length(FDR$AvS40FH[FDR$AvS40FH < .05]),
+               length(FDR$AvS3FT[FDR$AvS3FT < .05]),
+               length(FDR$AvS9FT[FDR$AvS9FT < .05]),
+               length(FDR$AvS40FT[FDR$AvS40FT < .05]),
+               length(FDR$AvS3FA[FDR$AvS3FA < .05]),
+               length(FDR$AvS9FA[FDR$AvS9FA < .05]),
+               length(FDR$AvS40FA[FDR$AvS40FA < .05]),
+               NA,
+               length(FDR$AvS3MH[FDR$AvS3MH < .05]),
+               length(FDR$AvS9MH[FDR$AvS9MH < .05]),
+               length(FDR$AvS3MT[FDR$AvS3MT < .05]),
+               length(FDR$AvS9MT[FDR$AvS9MT < .05]),
+               length(FDR$AvS3MA[FDR$AvS3MA < .05]),
+               length(FDR$AvS9MA[FDR$AvS9MA < .05]))
+
+names(total.DEGs) = c('FH3', 'FH9', 'FH40',
+                      'FT3', 'FT9', 'FT40',
+                      'FA3', 'FA9', 'FA40',
+                      NA,
+                      'MH3', 'MH9',
+                      'MT3', 'MT9',
+                      'MA3', 'MA9')
+
+total.DEGs = total.DEGs[c('FH3', 'MH3','FH9', 'MH9','FH40',
+                      NA,
+                      'FT3', 'MT3', 'FT9', 'MT9', 'FT40',
+                      NA,
+                      'FA3', 'MA3', 'FA9', 'MA9', 'FA40')]
+
+xlabel = names(total.DEGs)
+
+bp.color = c(rep("steelblue", 5), NA, 
+             rep("gold2", 5), NA,
+             rep("brown3", 5))
+
+```
+
+```{r echo = F}
+
+par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+
+barplot(height = total.DEGs,
+        names.arg = xlabel,
+        beside = T,
+        density = c(1000,50,1000,50,1000,0,1000,50,1000,50,1000,0,1000,50,1000,50,1000),
+        col = bp.color,
+        las = 2,
+        xlab = "Sample",
+        ylab = "Total DEGs",
+        main = "Total DEGs in A4V vs Silent",
+        ylim = c(0, 4700))
+##abline(v = 11.5, lty =2)
+legend('topright',
+       inset=c(-.35,0),
+       bty = 'n',
+       legend = c('Head', 'Thorax', 'Abdomen'), 
+       fill = c('steelblue', 'gold2', 'brown3'),
+       pt.cex = 1,
+       cex = 1)
+
+```
+
+```{r echo = F}
+
+reorder = c(1,3,5,2,4,6,
+            7,9,11,8,10,12,
+            13,15,17,14,16)
+
+par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+
+barplot(height = total.DEGs[reorder],
+        names.arg = xlabel[reorder],
+        beside = T,
+        density = c(1000,1000,1000, 75,75,0,
+                    1000,1000,1000, 75,75,0,
+                    1000,1000,1000, 75,75,0),
+        col = bp.color,
+        las = 2,
+        xlab = "Sample",
+        ylab = "Total DEGs",
+        main = "Total DEGs in A4V vs Silent",
+        ylim = c(0, 4700))
+##abline(v = 11.5, lty =2)
+legend('topright',
+       inset=c(-.3,0),
+       bty = 'n',
+       legend = c('Head', 'Thorax', 'Abdomen'), 
+       fill = c('steelblue', 'gold2', 'brown3'),
+       pt.cex = 1,
+       cex = 1)
 
@@
 set1="Male 9 Day"
-set2="Female 9 Day"
+set2="Female 40 Day"
 
@@
 s1=row.names(FDR[FDR$AvS9MT <.05,])
-s2=row.names(FDR[FDR$AvS9FT <.05,])
+s2=row.names(FDR[FDR$AvS40FT <.05,])
 
-main = "9 Day Thorax DEGs"
+main = "DEGs from 9 Day Male Thorax and 40 Day Female Thorax"
 
@@
 
-Male 3 Day Thorax Cellular Component GO Terms
+Male 9 Day Thorax Cellular Component GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-sigs = row.names(FDR)[FDR$AvS9FT < 0.05]
-FC.data = setNames(FC$AvS9FT, row.names(FC))
-FDR.data = setNames(FDR$AvS9FT, row.names(FDR))
+sigs = row.names(FDR)[FDR$AvS40FT < 0.05]
+FC.data = setNames(FC$AvS40FT, row.names(FC))
+FDR.data = setNames(FDR$AvS40FT, row.names(FDR))
 
@@
 
-Female 9 Day Thorax Biological Process GO Terms
+Female 40 Day Thorax Biological Process GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-Female 9 Day Thorax Biological Process GO Terms
+Female 40 Day Thorax Biological Process GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-Female 9 Day Thorax Cellular Component GO Terms
+Female 40 Day Thorax Cellular Component GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-Female 9 Day Thorax Cellular Component GO Terms
+Female 40 Day Thorax Cellular Component GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-Female 9 Day Thorax Molecular Function GO Terms
+Female 40 Day Thorax Molecular Function GO Terms
 ```{r, echo = F,  fig.width= 10}
@@
 
-Female 9 Day Thorax Molecular Function GO Terms
+Female 40 Day Thorax Molecular Function GO Terms
 ```{r  echo = F, fig.align='left'}
@@
 
-Female 9 Day Thorax KEGG Pathways
+Female 40 Day Thorax KEGG Pathways
 ```{r, echo = F,  fig.width= 10}

### 2024-05-08 Anna qPCR data/AnnaThesisA4VRNAseqFigures.Rmd
update

--- 2024-01-17 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
@@
 ---
-title: "Glycolysis Network"
+title: "Anna Thesis A4V RNAseq KEGG Pathway Figures"
 author: "John Santiago"
-date: "2023-12-06"
-output: 
-  bookdown::pdf_document2:
-    number_sections: false
+date: "2024-03-27"
+output: pdf_document
 ---
@@
 ```{r setup, include=FALSE}
-##knitr::opts_chunk$set(echo = TRUE)
-knitr::opts_chunk$set(dev='svg', fig.width=9, fig.height=12, out.width = "9in", out.height = "12in")
+knitr::opts_chunk$set(echo = TRUE)
 ```
-
-- #### Figure \@ref(fig:fig1): GR.FC vs WT.FC
-
-- #### Figure \@ref(fig:fig2): GR.MC vs WT.MC
-
-- #### Figure \@ref(fig:fig3): GR.FDf vs WT.FDf
-
-- #### Figure \@ref(fig:fig4): GR.MDf vs WT.MDf
-
-- #### Figure \@ref(fig:fig5): GR.FOE vs WT.FOE
-
-- #### Figure \@ref(fig:fig6): GR.MOE vs WT.MOE
-
-- #### Figure \@ref(fig:fig7): GRF: C vs Df
-
-- #### Figure \@ref(fig:fig8): GRM: C vs Df
-
-- #### Figure \@ref(fig:fig9): WTF: C vs Df
-
-- #### Figure \@ref(fig:fig10): WTM: C vs Df
-
-- #### Figure \@ref(fig:fig11): GRF: C vs OE
-
-- #### Figure \@ref(fig:fig12): GRM: C vs OE
-
-- #### Figure \@ref(fig:fig13): WTF: C vs OE
-
-- #### Figure \@ref(fig:fig14): WTM: C vs OE
 
@@
 library(org.Dm.eg.db)
-library(ggpubr)
-library(performance)
 library(pathview)
@@
 
-```
+metab.id = setNames(row.names(GRxWT.C), GRxWT.C$KEGG)
+mixed.id = unlist(strsplit(names(metab.id)[grep(" / ", names(metab.id))], " / "))
+mixed.id = mixed.id[mixed.id != "n/a"]
+mixed.id = setNames(rep("", length(mixed.id)), mixed.id)
 
-```{r include = F}
-
-##genes in the kegg pathway and their enzyme IDs
-glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
-##Edge data for genes connecting metabolites
-glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
-##Metabolites in the KEGG pathway with their ID
-glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')
-
-node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')
-
-glycolysis.network = function(comparison.T, comparison.M){
-
-##extracting position data for nodes
-node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
-                       number = rep(names(node.data$kegg.names),
-                                    lengths(node.data$kegg.names)),
-                       x = 0,
-                       y = 0,
-                       color = 0,
-                       names = "")
-node.info$x = node.data$x[node.info$number]
-node.info$y = node.data$y[node.info$number]
-
-##make new columns for transcriptomic data
-glycolysis.genes$FBgn = ""
-glycolysis.genes$Symbol = ""
-glycolysis.genes$FC = 0
-glycolysis.genes$pval = 1
-
-##Isolate gene ID info for goi
-temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
-row.names(temp) = temp$CG
-
-##fill in new columns with transcriptomic data
-glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
-glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
-glycolysis.genes$FC = TKT.EdgeR.FC[glycolysis.genes$FBgn, comparison.T]
-glycolysis.genes$FC = TKT.EdgeR[glycolysis.genes$FBgn, comparison.T]
-
-##make new columns for metabolomic data
-row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
-glycolysis.metabs$metabolomicsID = ""
-glycolysis.metabs$FC = 0
-glycolysis.metabs$pval = 1
-
-##retrieve name used in metabolomic data for metabolite IDs in path
-##including IDs associated with multiple metabolomic names
 i = 1
-while(i<=nrow(glycolysis.metabs)){
-  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
-    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
-  }
+while(i<=length(mixed.id)){
+  mixed.id[i] = metab.id[grep(names(mixed.id)[i], names(metab.id))]
   i = i +1
@@
 
-##retrieve metabolite fold change and pvalue data
-glycolysis.metabs$FC = log2(comparison.M[glycolysis.metabs$metabolomicsID, "FC"])
-glycolysis.metabs$pval = -log10(comparison.M[glycolysis.metabs$metabolomicsID, "p"])
+metab.id = metab.id[-grep(" / ", names(metab.id))]
 
-##using the positions for nodes (metabolites) only
-metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]
+metab.id = c(metab.id, mixed.id)
 
-metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
-metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
-metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
-metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']
+```
 
-color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)
+```{r echo = F}
+KEGG.diagram = function(PathwayID, out.id, FC.data, FDR.data){
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+    }
+  Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  OutputDir = paste0(Home, "/KEGG_Image_Files/")
+  setwd(OutputDir)
+  sigs = names(FDR.data)
+  ##sigs = names(FDR.data[FDR.data <= .05])
 
-metab.info$color[metab.info$color > 1] = 1
-metab.info$color[metab.info$color < -1] = -1
-metab.info$color = (metab.info$color * 200) +201
-metab.info$color = color.pallette[metab.info$color]
-metab.info$color[is.na(metab.info$color)] = 'dimgrey'
-
-metab.info$size = 10 + 10*abs(metab.info$size)
-metab.info$size[is.na(metab.info$size)] = 10
-
-metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
-                          "<br>log2(FC): ", signif(metab.info$FC,3),
-                          "<br>pval: ", signif(10^-metab.info$pval,3))
-
-nodes = data.frame(id = paste0(metab.info$names),
-                   color = metab.info$color,
-                   size = metab.info$size,
-                   x = 2*metab.info$x,
-                   y = 2*metab.info$y,
-                   physics = F,
-                   group = "",
-                   title = metab.info$title)
-
-glycolysis.edges$FBgn = ''
-temp.glycolysis.path = glycolysis.edges
-
-i = 1
-while(i<=nrow(glycolysis.edges)){
-  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
-  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
-    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
-    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
-    temp2 = glycolysis.edges[rep(i, length(temp)),]
-    temp2$FBgn = temp
-  }else{
-    temp2 = glycolysis.edges[i,]
-  }
-  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)
-
-  i = i +1
+  if(class(FC.data)=="numeric"){
+    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
   }
 
-glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]
+  if(class(FC.data)=="data.frame"){
+    deg.data = as.matrix(FC.data)
+    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
+  }
 
-glycolysis.edges$size = log10(ccm[glycolysis.edges[,'FBgn'], comparison.T])
-glycolysis.edges$size[glycolysis.edges$size <1] = 1
-glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
-glycolysis.edges$size = 2*glycolysis.edges$size
+  metab.data = setNames(log2(metab.data[metab.id, 'FC']), names(metab.id))
 
-glycolysis.edges$color = TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T]
-## max color intensity is at FC of 2
-glycolysis.edges$color[glycolysis.edges$color>2] = 2
-glycolysis.edges$color[glycolysis.edges$color<(-2)] = -2
-glycolysis.edges$color = 201+(glycolysis.edges$color *100)
-glycolysis.edges$color = color.pallette[glycolysis.edges$color]
-glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'
+  pv.out <- pathview(gene.data =  deg.data,
+                     ##cpd.data = metab.data,
+                   pathway.id = PathwayID,
+                   species = "dme",
+                   kegg.native = T,
+                   limit=list(gene=c(-2,2)),
+                   node.sum="max.abs",
+                   low="royalblue",mid = "grey",high="firebrick",
+                   out.suffix = out.id,
+                   bins=list(genes=30),
+                   plot.col.key = F,
+                   match.data = F)
+  setwd(Home)
 
-glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
-                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
-                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))
+    if(class(FC.data)=="numeric"){
+      img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
+    }
 
-edges = data.frame(from = glycolysis.edges$from.name,
-                   to = glycolysis.edges$to.name,
-                   arrows = glycolysis.edges$arrow,
-                   color = glycolysis.edges$color,
-                   width = glycolysis.edges$size,
-                   title = glycolysis.edges$title,
-                   physics = T)
-
-nodes = data.frame(id = paste0(nodes$id),
-                   color = nodes$color,
-                   size = nodes$size,
-                   x = nodes$x,
-                   y = nodes$y,
-                   physics = F,
-                   group = "",
-                   title = nodes$title)
-
-OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
-                               'Propanoate Metabolism',
-                               'Starch and Sucrose Metabolism',
-                               'Citrate Cycle'),
-                        color = "black",
-                        size = 15,
-                        x= c(1350,1254,966,175),
-                        y=c(1112,1822,110,1700),
-                        physics = F,
-                        group = 'Outside Path',
-                        title = "")
-
-nodes = rbind(nodes, OutsidePath)
-
-visNetwork(nodes, edges, main = paste0(comparison.means[[comparison.T]][1], " vs ", comparison.means[[comparison.T]][2]))%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows = edges$arrows)%>%
-  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))
-
+    if(class(FC.data)=="data.frame"){
+      img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
+    }
+  knitr::include_graphics(img.file)
 }
@@
 
-```{r echo = F, fig.height=12, fig.width=9, fig.align='left', fig1, fig.cap = 'G85R relative to WT.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
+```{r echo = F, message=F, fig.width=7}
 
-glycolysis.network(comparison.T = 'GRxWT.FC', comparison.M = GRxWT.C)
+PathwayID = "00010"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
+
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
 
@@
 
-<br><br><br>
+```{r echo = F, message=F, fig.width=7}
 
-```{r, echo =F, fig2, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R relative to WT.
-Transcriptomic data is from males and metabolomic data is from both sexes.Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
+PathwayID = "00020"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
 
-glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GR.CxDf)
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
 
@@
 
-<br><br><br>
+```{r echo = F, message=F, fig.width=7}
 
-```{r, echo =F, fig3, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
+PathwayID = "00061"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
 
-glycolysis.network(comparison.T = 'GRxWT.FDf', comparison.M = GRxWT.Df)
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
 
@@
 
-<br><br><br>
+```{r echo = F, message=F, fig.width=7}
 
-```{r, echo =F, fig4, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-Df relative to WT TKT-Df.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
+PathwayID = "04214"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
 
-glycolysis.network(comparison.T = 'GRxWT.MDf', comparison.M = GRxWT.Df)
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
 
@@
 
-<br><br><br>
+```{r echo = F, message=F}
 
-```{r, echo =F, fig5, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
+PathwayID = "04137"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
 
-glycolysis.network(comparison.T = 'GRxWT.FOE', comparison.M = GRxWT.OE)
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
 
 ```
-
-<br><br><br>
-
-```{r, echo =F, fig6, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R TKT-OE relative to WT TKT-OE.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'GRxWT.MOE', comparison.M = GRxWT.OE)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig7, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'GRF.CxDf', comparison.M = GR.CxDf)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig8, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-Df.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'GRM.CxDf', comparison.M = GR.CxDf)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig9, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'WTF.CxDf', comparison.M = WT.CxDf)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig10, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-Df.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'WTM.CxDf', comparison.M = WT.CxDf)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig11, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'GRF.CxOE', comparison.M = GR.CxOE)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig12, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'G85R control relative to G85R TKT-OE.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'GRM.CxOE', comparison.M = GR.CxOE)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig13, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE.
-Transcriptomic data is from females and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'WTF.CxOE', comparison.M = WT.CxOE)
-
-```
-
-<br><br><br>
-
-```{r, echo =F, fig14, fig.height=12, fig.width=9, fig.align='left', fig.cap = 'WT control relative to WT TKT-OE.
-Transcriptomic data is from males and metabolomic data is from both sexes.
-Grey is no data; Red is increase; Blue is decreae; Node size is relative to pval; Node color is relative to fold change (range: -1 to 1); Edge width is relative to FDR (max -log10(4)); edge color is relative to fold change (range: -2 to 2)'}
-
-glycolysis.network(comparison.T = 'WTM.CxOE', comparison.M = WT.CxOE)
-
-```
-
-<br><br><br>

### 2024-05-08 RussoPaper/RussoClimbingPlots.Rmd
update

---
title: "Russo Manuscript Climbing Plot"
author: "John Santiago"
date: "2024-03-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)

```

```{r include = F, echo = F}

fig4ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4AB Climbing Data ok371 cha gbb climbing cm_sec.csv", header = T)

female = fig4ab[grep('f', fig4ab$vial_ID),]
male = fig4ab[grep('m', fig4ab$vial_ID),]

f.con = na.omit(female[female$geno == 'silent' | female$geno == 'A4V',])
f.cha = na.omit(female[grep('cha', female$geno),])

fallcha = rbind(f.con, f.cha)
fallcha$sample = paste0(fallcha$geno, fallcha$day)

fcha.mean = unique(fallcha[,c('geno', 'day')])
fcha.mean$sample = paste0(fcha.mean$geno, fcha.mean$day)
fcha.mean$mean = 0

i=1
while(i<=nrow(fcha.mean)){
  fcha.mean$mean[i] = mean(fallcha[fallcha$sample == fcha.mean$sample[i], 'corrected.values'])
  i = i+1
}

fcha.mean = fcha.mean[order(fcha.mean$day),]

```

```{r echo = F, include = F}

plot_ly(x = fallcha$day,
        y = fallcha$corrected.values,
        name = fallcha$geno,
        type = 'scatter',
        color = fallcha$color,
        marker = list(colors = fallcha$color)) %>%
  add_lines(x = fcha.mean$day,
            y = fcha.mean$mean,
            name = fcha.mean$geno,
            color = fcha.mean$color,
            line = list(color = fcha.mean$color))

```

```{r echo = F}

female = fig4ab[grep('f', fig4ab$vial_ID),]
female$sample = paste0(female$geno, female$day)

fmean = unique(female[,c('geno', 'day', 'sample')])
fstd = fmean
eb = fmean
fmean$mean = 0
fstd$std = 0

i=1
while(i<=nrow(fmean)){
  fmean$mean[i] = mean(na.omit(female[female$sample == fmean$sample[i], 'corrected.values']))

  fstd$std[i] = (var(na.omit(female[female$sample == fmean$sample[i], 'corrected.values'])))

  i = i+1
}

flm = data.frame(geno = unique(female$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(flm)){
  temp=na.omit(female[female$geno == flm$geno[i], ])
  temp.lm = lm(temp$corrected.values~temp$day)
  flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(flm) = flm$geno

fmean = fmean[order(fmean$day),]
fstd = fstd[order(fstd$day),]
eb = eb[order(eb$day),]

eb$y0 = fmean$mean - fstd$std
eb$y1 = fmean$mean + fstd$std

```

```{r echo = F}

norm.female = na.omit(female)
norm.female$normval = 0
i=1
while(i <= nrow(norm.female)){
  norm.female$normval[i] = norm.female$corrected.values[i]/
    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
  i = i +1
}

norm.fmean = unique(norm.female[,c('geno', 'day', 'sample')])
norm.fstd = norm.fmean
norm.feb = norm.fmean
norm.fmean$mean = 0
norm.fstd$std = 0

i=1
while(i<=nrow(norm.fmean)){
  norm.fmean$mean[i] = mean(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval']))

  norm.fstd$std[i] = (var(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval'])))

  i = i+1
}

norm.fmean = norm.fmean[order(norm.fmean$day),]
norm.fstd = norm.fstd[order(norm.fstd$day),]
norm.feb = norm.feb[order(norm.feb$day),]

norm.feb$y0 = norm.fmean$mean - norm.fstd$std
norm.feb$y1 = norm.fmean$mean + norm.fstd$std

norm.flm = data.frame(geno = unique(norm.female$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(norm.flm)){
  temp=na.omit(norm.female[norm.female$geno == norm.flm$geno[i], ])
  temp.lm = lm(temp$normval~temp$day)
  norm.flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  norm.flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(norm.flm) = norm.flm$geno

```

```{r echo = F, fig.height=10}

silent = norm.fmean[norm.fmean$geno == "silent", ]
a4v = norm.fmean[norm.fmean$geno == "A4V", ]
silentcha = norm.fmean[norm.fmean$geno == "silentcha", ]
a4vcha = norm.fmean[norm.fmean$geno == "A4Vcha", ]
silentok = norm.fmean[norm.fmean$geno == "silentok", ]
a4vok = norm.fmean[norm.fmean$geno == "A4Vok", ]

ls = norm.fmean[norm.fmean$geno == 'silent',]
la = norm.fmean[norm.fmean$geno == 'A4V',]
lsc = norm.fmean[norm.fmean$geno == 'silentcha',]
lac = norm.fmean[norm.fmean$geno == 'A4Vcha',]
lso = norm.fmean[norm.fmean$geno == 'silentok',]
lao = norm.fmean[norm.fmean$geno == 'A4Vok',]

pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 9.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0,1.85),
     xlim = c(2,27),
     ylab = 'Relative Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Females")

axis(1, at=silent$day)

abline(v = 2, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 6, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 9, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 13, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 19, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 22, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 27, lty =2, lwd = 1, col = hex(pcol[7], .5))

lines(x = norm.flm['silent', c("x0", "x1")],
      y = norm.flm['silent', c("y0", "y1")],
      type = 'l',
      col = pcol[1],
      lwd = 2)

lines(x = norm.flm['A4V', c("x0", "x1")],
      y = norm.flm['A4V', c("y0", "y1")],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = norm.flm['silentcha', c("x0", "x1")],
      y = norm.flm['silentcha', c("y0", "y1")],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = norm.flm['A4Vcha', c("x0", "x1")],
      y = norm.flm['A4Vcha', c("y0", "y1")],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = norm.flm['silentok', c("x0", "x1")],
      y = norm.flm['silentok', c("y0", "y1")],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = norm.flm['A4Vok', c("x0", "x1")],
      y = norm.flm['A4Vok', c("y0", "y1")],
      type = 'l',
      col = pcol[6],
      lwd = 2)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silent'],
       x1 = norm.feb$day[norm.feb$geno == 'silent'],
       y0 = norm.feb$y0[norm.feb$geno == 'silent'],
       y1 = norm.feb$y1[norm.feb$geno == 'silent'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[1], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4V'],
       x1 = norm.feb$day[norm.feb$geno == 'A4V'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4V'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4V'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[2], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silentcha'],
       x1 = norm.feb$day[norm.feb$geno == 'silentcha'],
       y0 = norm.feb$y0[norm.feb$geno == 'silentcha'],
       y1 = norm.feb$y1[norm.feb$geno == 'silentcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[3], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
       x1 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4Vcha'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4Vcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[4], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silentok'],
       x1 = norm.feb$day[norm.feb$geno == 'silentok'],
       y0 = norm.feb$y0[norm.feb$geno == 'silentok'],
       y1 = norm.feb$y1[norm.feb$geno == 'silentok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[5], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vok'],
       x1 = norm.feb$day[norm.feb$geno == 'A4Vok'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4Vok'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4Vok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[6], 
       lwd=1)

points(x = silent$day,
       y = silent$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4v$day,
       y = a4v$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = silent$day,
       y = silent$mean,
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

points(x = a4v$day,
       y = a4v$mean,
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = hex(pcol[5], .5),
       col = pcol[5],
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = hex(pcol[6], .5),
       col = pcol[6],
       pch = 21,
       cex =2)

legend(x = 29,
       y = 1.8,
       legend = c('Silent', 'A4V',
                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(pcol[1], pcol[2], pcol[3],
                pcol[4], pcol[5], pcol[6]),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

```

```{r echo = F}

male$sample = paste0(male$geno, male$day)

norm.male = na.omit(male)
norm.male$normval = 0

mmean = unique(male[,c('geno', 'day', 'sample')])
mstd = mmean
eb = mmean
mmean$mean = 0
mstd$std = 0

i=1
while(i<=nrow(mmean)){
  mmean$mean[i] = mean(na.omit(male[male$sample == mmean$sample[i], 'corrected.values']))

  mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))

  i = i+1
}

mlm = data.frame(geno = unique(male$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(mlm)){
  temp=na.omit(male[male$geno == mlm$geno[i], ])
  temp.lm = lm(temp$corrected.values~temp$day)
  mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(mlm) = mlm$geno

mmean = mmean[order(mmean$day),]
mstd = mstd[order(mstd$day),]
eb = eb[order(eb$day),]

eb$y0 = mmean$mean - mstd$std
eb$y1 = mmean$mean + mstd$std

i=1
while(i <= nrow(norm.male)){
  norm.male$normval[i] = norm.male$corrected.values[i]/
    mmean$mean[mmean$geno == 'silent' & mmean$day == norm.male$day[i]]
  i = i +1
}

norm.mmean = unique(norm.male[,c('geno', 'day', 'sample')])
norm.mstd = norm.mmean
norm.eb = norm.mmean
norm.mmean$mean = 0
norm.mstd$std = 0

i=1
while(i<=nrow(norm.mmean)){
  norm.mmean$mean[i] = mean(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval']))

  norm.mstd$std[i] = (var(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval'])))

  i = i+1
}

norm.mmean = norm.mmean[order(norm.mmean$day),]
norm.mstd = norm.mstd[order(norm.mstd$day),]
norm.eb = norm.eb[order(norm.eb$day),]

norm.eb$y0 = norm.mmean$mean - norm.mstd$std
norm.eb$y1 = norm.mmean$mean + norm.mstd$std

norm.mlm = data.frame(geno = unique(norm.male$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(norm.mlm)){
  temp=na.omit(norm.male[norm.male$geno == norm.mlm$geno[i], ])
  temp.lm = lm(temp$normval~temp$day)
  norm.mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  norm.mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(norm.mlm) = norm.mlm$geno

```

```{r echo = F, fig.height=10}

silent = norm.mmean[norm.mmean$geno == "silent", ]
a4v = norm.mmean[norm.mmean$geno == "A4V", ]
silentcha = norm.mmean[norm.mmean$geno == "silentcha", ]
a4vcha = norm.mmean[norm.mmean$geno == "A4Vcha", ]
silentok = norm.mmean[norm.mmean$geno == "silentok", ]
a4vok = norm.mmean[norm.mmean$geno == "A4Vok", ]

ls = norm.mmean[norm.mmean$geno == 'silent',]
la = norm.mmean[norm.mmean$geno == 'A4V',]
lsc = norm.mmean[norm.mmean$geno == 'silentcha',]
lac = norm.mmean[norm.mmean$geno == 'A4Vcha',]
lso = norm.mmean[norm.mmean$geno == 'silentok',]
lao = norm.mmean[norm.mmean$geno == 'A4Vok',]

pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 9.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0,1.85),
     xlim = c(2,27),
     ylab = 'Relative Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Males")

axis(1, at=silent$day)

abline(v = 2, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 6, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 9, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 13, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 19, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 22, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 27, lty =2, lwd = 1, col = hex(pcol[7], .5))

lines(x = norm.mlm['silent', c("x0", "x1")],
      y = norm.mlm['silent', c("y0", "y1")],
      type = 'l',
      col = pcol[1],
      lwd = 2)

lines(x = norm.mlm['A4V', c("x0", "x1")],
      y = norm.mlm['A4V', c("y0", "y1")],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = norm.mlm['silentcha', c("x0", "x1")],
      y = norm.mlm['silentcha', c("y0", "y1")],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = norm.mlm['A4Vcha', c("x0", "x1")],
      y = norm.mlm['A4Vcha', c("y0", "y1")],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = norm.mlm['silentok', c("x0", "x1")],
      y = norm.mlm['silentok', c("y0", "y1")],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = norm.mlm['A4Vok', c("x0", "x1")],
      y = norm.mlm['A4Vok', c("y0", "y1")],
      type = 'l',
      col = pcol[6],
      lwd = 2)

arrows(x0 = norm.eb$day[norm.eb$geno == 'silent'],
       x1 = norm.eb$day[norm.eb$geno == 'silent'],
       y0 = norm.eb$y0[norm.eb$geno == 'silent'],
       y1 = norm.eb$y1[norm.eb$geno == 'silent'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[1], 
       lwd=1)

arrows(x0 = norm.eb$day[norm.eb$geno == 'A4V'],
       x1 = norm.eb$day[norm.eb$geno == 'A4V'],
       y0 = norm.eb$y0[norm.eb$geno == 'A4V'],
       y1 = norm.eb$y1[norm.eb$geno == 'A4V'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[2], 
       lwd=1)

arrows(x0 = norm.eb$day[norm.eb$geno == 'silentcha'],
       x1 = norm.eb$day[norm.eb$geno == 'silentcha'],
       y0 = norm.eb$y0[norm.eb$geno == 'silentcha'],
       y1 = norm.eb$y1[norm.eb$geno == 'silentcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[3], 
       lwd=1)

arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
       x1 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
       y0 = norm.eb$y0[norm.eb$geno == 'A4Vcha'],
       y1 = norm.eb$y1[norm.eb$geno == 'A4Vcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[4], 
       lwd=1)

arrows(x0 = norm.eb$day[norm.eb$geno == 'silentok'],
       x1 = norm.eb$day[norm.eb$geno == 'silentok'],
       y0 = norm.eb$y0[norm.eb$geno == 'silentok'],
       y1 = norm.eb$y1[norm.eb$geno == 'silentok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[5], 
       lwd=1)

arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vok'],
       x1 = norm.eb$day[norm.eb$geno == 'A4Vok'],
       y0 = norm.eb$y0[norm.eb$geno == 'A4Vok'],
       y1 = norm.eb$y1[norm.eb$geno == 'A4Vok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[6], 
       lwd=1)

points(x = silent$day,
       y = silent$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4v$day,
       y = a4v$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = silent$day,
       y = silent$mean,
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

points(x = a4v$day,
       y = a4v$mean,
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = hex(pcol[5], .5),
       col = pcol[5],
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = hex(pcol[6], .5),
       col = pcol[6],
       pch = 21,
       cex =2)

legend(x = 29,
       y = 1.8,
       legend = c('Silent', 'A4V',
                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(pcol[1], pcol[2], pcol[3],
                pcol[4], pcol[5], pcol[6]),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

```

```{r  echo = F}

fig4cd = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4CD.csv", header = T)

fig4cd = fig4cd[fig4cd$day != 9,]
fig4cd = fig4cd[fig4cd$day != 32,]

female = fig4cd[grep('f', fig4cd$vial_ID),]
male = fig4cd[grep('m', fig4cd$vial_ID),]

female$sample = paste0(female$geno, female$day)
male$sample = paste0(male$geno, male$day)

norm.female = na.omit(female)
norm.female$normval = 0

fmean = unique(female[,c('geno', 'day', 'sample')])
fstd = fmean
feb = fmean
fmean$mean = 0
fstd$std = 0

norm.male = na.omit(male)
norm.male$normval = 0

mmean = unique(male[,c('geno', 'day', 'sample')])
mstd = mmean
meb = mmean
mmean$mean = 0
mstd$std = 0

i=1
while(i<=nrow(mmean)){
  mmean$mean[i] = mean(na.omit(male[male$sample == mmean$sample[i], 'corrected.values']))

  mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))

  i = i+1
}

i=1
while(i<=nrow(fmean)){
  fmean$mean[i] = mean(na.omit(female[female$sample == fmean$sample[i], 'corrected.values']))

  fstd$std[i] = (var(na.omit(female[female$sample == fmean$sample[i], 'corrected.values'])))

  i = i+1
}

mlm = data.frame(geno = unique(male$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(mlm)){
  temp=na.omit(male[male$geno == mlm$geno[i], ])
  temp.lm = lm(temp$corrected.values~temp$day)
  mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(mlm) = mlm$geno

flm = data.frame(geno = unique(female$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(flm)){
  temp=na.omit(female[female$geno == flm$geno[i], ])
  temp.lm = lm(temp$corrected.values~temp$day)
  flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(flm) = flm$geno

mmean = mmean[order(mmean$day),]
mstd = mstd[order(mstd$day),]
meb = meb[order(meb$day),]

meb$y0 = mmean$mean - mstd$std
meb$y1 = mmean$mean + mstd$std

fmean = fmean[order(fmean$day),]
fstd = fstd[order(fstd$day),]
feb = feb[order(feb$day),]

feb$y0 = fmean$mean - fstd$std
feb$y1 = fmean$mean + fstd$std

i=1
while(i <= nrow(norm.male)){
  norm.male$normval[i] = norm.male$corrected.values[i]/
    mmean$mean[mmean$geno == 'silent' & mmean$day == norm.male$day[i]]
  i = i +1
}

norm.mmean = unique(norm.male[,c('geno', 'day', 'sample')])
norm.mstd = norm.mmean
norm.meb = norm.mmean
norm.mmean$mean = 0
norm.mstd$std = 0

i=1
while(i <= nrow(norm.female)){
  norm.female$normval[i] = norm.female$corrected.values[i]/
    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
  i = i +1
}

norm.fmean = unique(norm.female[,c('geno', 'day', 'sample')])
norm.fstd = norm.fmean
norm.feb = norm.fmean
norm.fmean$mean = 0
norm.fstd$std = 0

i=1
while(i<=nrow(norm.mmean)){
  norm.mmean$mean[i] = mean(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval']))

  norm.mstd$std[i] = (var(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval'])))

  i = i+1
}

i=1
while(i<=nrow(norm.fmean)){
  norm.fmean$mean[i] = mean(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval']))

  norm.fstd$std[i] = (var(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval'])))

  i = i+1
}

norm.mmean = norm.mmean[order(norm.mmean$day),]
norm.mstd = norm.mstd[order(norm.mstd$day),]
norm.meb = norm.meb[order(norm.meb$day),]

norm.meb$y0 = norm.mmean$mean - norm.mstd$std
norm.meb$y1 = norm.mmean$mean + norm.mstd$std

norm.mlm = data.frame(geno = unique(norm.male$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(norm.mlm)){
  temp=na.omit(norm.male[norm.male$geno == norm.mlm$geno[i], ])
  temp.lm = lm(temp$normval~temp$day)
  norm.mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  norm.mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(norm.mlm) = norm.mlm$geno

norm.fmean = norm.fmean[order(norm.fmean$day),]
norm.fstd = norm.fstd[order(norm.fstd$day),]
norm.feb = norm.feb[order(norm.feb$day),]

norm.feb$y0 = norm.fmean$mean - norm.fstd$std
norm.feb$y1 = norm.fmean$mean + norm.fstd$std

norm.flm = data.frame(geno = unique(norm.female$geno),
                x0 = 2,
                x1 = 27,
                y0 = 0,
                y1 = 0)

i=1
while(i<=nrow(norm.flm)){
  temp=na.omit(norm.female[norm.female$geno == norm.flm$geno[i], ])
  temp.lm = lm(temp$normval~temp$day)
  norm.flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
  norm.flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
  i = i +1
}

row.names(norm.flm) = norm.flm$geno

```

```{r echo = F, fig.height=10}

silent = norm.fmean[norm.fmean$geno == "silent", ]
a4v = norm.fmean[norm.fmean$geno == "A4V", ]
silentcha = norm.fmean[norm.fmean$geno == "silentcha", ]
a4vcha = norm.fmean[norm.fmean$geno == "A4Vcha", ]
silentok = norm.fmean[norm.fmean$geno == "silentok", ]
a4vok = norm.fmean[norm.fmean$geno == "A4Vok", ]

ls = norm.fmean[norm.fmean$geno == 'silent',]
la = norm.fmean[norm.fmean$geno == 'A4V',]
lsc = norm.fmean[norm.fmean$geno == 'silentcha',]
lac = norm.fmean[norm.fmean$geno == 'A4Vcha',]
lso = norm.fmean[norm.fmean$geno == 'silentok',]
lao = norm.fmean[norm.fmean$geno == 'A4Vok',]

pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 9.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0,2.5),
     xlim = c(2,27),
     ylab = 'Relative Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Females")

axis(1, at=silent$day)

abline(v = 2, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 6, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 9, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 13, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 19, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 22, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 27, lty =2, lwd = 1, col = hex(pcol[7], .5))

lines(x = norm.flm['silent', c("x0", "x1")],
      y = norm.flm['silent', c("y0", "y1")],
      type = 'l',
      col = pcol[1],
      lwd = 2)

lines(x = norm.flm['A4V', c("x0", "x1")],
      y = norm.flm['A4V', c("y0", "y1")],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = norm.flm['silentcha', c("x0", "x1")],
      y = norm.flm['silentcha', c("y0", "y1")],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = norm.flm['A4Vcha', c("x0", "x1")],
      y = norm.flm['A4Vcha', c("y0", "y1")],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = norm.flm['silentok', c("x0", "x1")],
      y = norm.flm['silentok', c("y0", "y1")],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = norm.flm['A4Vok', c("x0", "x1")],
      y = norm.flm['A4Vok', c("y0", "y1")],
      type = 'l',
      col = pcol[6],
      lwd = 2)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silent'],
       x1 = norm.feb$day[norm.feb$geno == 'silent'],
       y0 = norm.feb$y0[norm.feb$geno == 'silent'],
       y1 = norm.feb$y1[norm.feb$geno == 'silent'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[1], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4V'],
       x1 = norm.feb$day[norm.feb$geno == 'A4V'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4V'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4V'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[2], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silentcha'],
       x1 = norm.feb$day[norm.feb$geno == 'silentcha'],
       y0 = norm.feb$y0[norm.feb$geno == 'silentcha'],
       y1 = norm.feb$y1[norm.feb$geno == 'silentcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[3], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
       x1 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4Vcha'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4Vcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[4], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'silentok'],
       x1 = norm.feb$day[norm.feb$geno == 'silentok'],
       y0 = norm.feb$y0[norm.feb$geno == 'silentok'],
       y1 = norm.feb$y1[norm.feb$geno == 'silentok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[5], 
       lwd=1)

arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vok'],
       x1 = norm.feb$day[norm.feb$geno == 'A4Vok'],
       y0 = norm.feb$y0[norm.feb$geno == 'A4Vok'],
       y1 = norm.feb$y1[norm.feb$geno == 'A4Vok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[6], 
       lwd=1)

points(x = silent$day,
       y = silent$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4v$day,
       y = a4v$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = silent$day,
       y = silent$mean,
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

points(x = a4v$day,
       y = a4v$mean,
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = hex(pcol[5], .5),
       col = pcol[5],
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = hex(pcol[6], .5),
       col = pcol[6],
       pch = 21,
       cex =2)

legend(x = 29,
       y = 2.5,
       legend = c('Silent', 'A4V',
                  'ChAT>SaxA;Silent', 'ChAT>SaxA;A4V', 
                  'OK371>SaxA;Silent', 'OK371>SaxA;A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(pcol[1], pcol[2], pcol[3],
                pcol[4], pcol[5], pcol[6]),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

```

```{r echo = F, fig.height=10}

silent = norm.mmean[norm.mmean$geno == "silent", ]
a4v = norm.mmean[norm.mmean$geno == "A4V", ]
silentcha = norm.mmean[norm.mmean$geno == "silentcha", ]
a4vcha = norm.mmean[norm.mmean$geno == "A4Vcha", ]
silentok = norm.mmean[norm.mmean$geno == "silentok", ]
a4vok = norm.mmean[norm.mmean$geno == "A4Vok", ]

ls = norm.mmean[norm.mmean$geno == 'silent',]
la = norm.mmean[norm.mmean$geno == 'A4V',]
lsc = norm.mmean[norm.mmean$geno == 'silentcha',]
lac = norm.mmean[norm.mmean$geno == 'A4Vcha',]
lso = norm.mmean[norm.mmean$geno == 'silentok',]
lao = norm.mmean[norm.mmean$geno == 'A4Vok',]

pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 9.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0,2.5),
     xlim = c(2,27),
     ylab = 'Relative Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Males")

axis(1, at=silent$day)

abline(v = 2, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 6, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 9, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 13, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 19, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 22, lty =2, lwd = 1, col = hex(pcol[7], .5))
abline(v = 27, lty =2, lwd = 1, col = hex(pcol[7], .5))

lines(x = norm.mlm['silent', c("x0", "x1")],
      y = norm.mlm['silent', c("y0", "y1")],
      type = 'l',
      col = pcol[1],
      lwd = 2)

lines(x = norm.mlm['A4V', c("x0", "x1")],
      y = norm.mlm['A4V', c("y0", "y1")],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = norm.mlm['silentcha', c("x0", "x1")],
      y = norm.mlm['silentcha', c("y0", "y1")],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = norm.mlm['A4Vcha', c("x0", "x1")],
      y = norm.mlm['A4Vcha', c("y0", "y1")],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = norm.mlm['silentok', c("x0", "x1")],
      y = norm.mlm['silentok', c("y0", "y1")],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = norm.mlm['A4Vok', c("x0", "x1")],
      y = norm.mlm['A4Vok', c("y0", "y1")],
      type = 'l',
      col = pcol[6],
      lwd = 2)

arrows(x0 = norm.meb$day[norm.meb$geno == 'silent'],
       x1 = norm.meb$day[norm.meb$geno == 'silent'],
       y0 = norm.meb$y0[norm.meb$geno == 'silent'],
       y1 = norm.meb$y1[norm.meb$geno == 'silent'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[1], 
       lwd=1)

arrows(x0 = norm.meb$day[norm.meb$geno == 'A4V'],
       x1 = norm.meb$day[norm.meb$geno == 'A4V'],
       y0 = norm.meb$y0[norm.meb$geno == 'A4V'],
       y1 = norm.meb$y1[norm.meb$geno == 'A4V'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[2], 
       lwd=1)

arrows(x0 = norm.meb$day[norm.meb$geno == 'silentcha'],
       x1 = norm.meb$day[norm.meb$geno == 'silentcha'],
       y0 = norm.meb$y0[norm.meb$geno == 'silentcha'],
       y1 = norm.meb$y1[norm.meb$geno == 'silentcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[3], 
       lwd=1)

arrows(x0 = norm.meb$day[norm.meb$geno == 'A4Vcha'],
       x1 = norm.meb$day[norm.meb$geno == 'A4Vcha'],
       y0 = norm.meb$y0[norm.meb$geno == 'A4Vcha'],
       y1 = norm.meb$y1[norm.meb$geno == 'A4Vcha'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[4], 
       lwd=1)

arrows(x0 = norm.meb$day[norm.meb$geno == 'silentok'],
       x1 = norm.meb$day[norm.meb$geno == 'silentok'],
       y0 = norm.meb$y0[norm.meb$geno == 'silentok'],
       y1 = norm.meb$y1[norm.meb$geno == 'silentok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[5], 
       lwd=1)

arrows(x0 = norm.meb$day[norm.meb$geno == 'A4Vok'],
       x1 = norm.meb$day[norm.meb$geno == 'A4Vok'],
       y0 = norm.meb$y0[norm.meb$geno == 'A4Vok'],
       y1 = norm.meb$y1[norm.meb$geno == 'A4Vok'], 
       code = 3, 
       angle = 90, 
       length = 0.1, 
       col = pcol[6], 
       lwd=1)

points(x = silent$day,
       y = silent$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4v$day,
       y = a4v$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = silent$day,
       y = silent$mean,
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

points(x = a4v$day,
       y = a4v$mean,
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 21,
       cex =2)
points(x = silentcha$day,
       y = silentcha$mean,
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 23,
       cex =2)
points(x = a4vcha$day,
       y = a4vcha$mean,
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 21,
       cex =2)
points(x = silentok$day,
       y = silentok$mean,
       bg = hex(pcol[5], .5),
       col = pcol[5],
       pch = 23,
       cex =2)
points(x = a4vok$day,
       y = a4vok$mean,
       bg = hex(pcol[6], .5),
       col = pcol[6],
       pch = 21,
       cex =2)

legend(x = 29,
       y = 2.5,
       legend = c('Silent', 'A4V',
                  'ChAT>SaxA;Silent', 'ChAT>SaxA;A4V', 
                  'OK371>SaxA;Silent', 'OK371>SaxA;A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(pcol[1], pcol[2], pcol[3],
                pcol[4], pcol[5], pcol[6]),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

```

### 2024-05-08 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
update

@@
 library(org.Dm.eg.db)
-library(ggpubr)
-library(performance)
+##library(ggpubr)
+##library(performance)
 library(pathview)
@@
 
-glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GR.CxDf)
+glycolysis.network(comparison.T = 'GRxWT.MC', comparison.M = GRxWT.C)
 

### 2024-05-08 TKT_RNAseq/R Code/PurineMetabolismNetwork.Rmd
update

@@
 date: "2023-09-29"
-output: 
-  bookdown::html_document2:
-    number_sections: false
+output: html_document
 ---
@@
 library(org.Dm.eg.db)
-library(ggpubr)
-library(performance)
+##library(ggpubr)
+##library(performance)
 

### 2024-05-08 20240507_pharate_axonal_branching.Rmd
Update 20240507_pharate_axonal_branching.Rmd
unaisa code

@@
 
-ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)
+ab = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)
 
@@
                       color = as.numeric(factor(ab$Genotype)))
-plotdata = plotdata[order(paste0(ab$Sex, ab$Leg.Location)),]
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
 plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
@@
 ```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Primary.Avg.Mito.Branch,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Primary.Avg.Mito.Branch,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Longest.Primary.Branch.um,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Longest.Primary.Branch.um,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Shortest.Primary.Branch.um,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Shortest.Primary.Branch.um,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```

### 2024-09-27 20240507_pharate_axonal_branching.Rmd
Dina Folder Update

--- 2024-05-08 20240507_pharate_axonal_branching.Rmd
@@
 
-ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)
+ab = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)
+
+morph = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240513_pharate_axonal_morphology_Raw_Data.csv")
+
+ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/UB7 - G85R Pharate Leg Axonal Branching & Mitochondria  - CSV_Branching.csv", header = T)
 
@@
                       color = as.numeric(factor(ab$Genotype)))
-plotdata = plotdata[order(paste0(ab$Sex, ab$Leg.Location)),]
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
 plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+
+par(mar = c(8,5,2,2))
 boxplot(plotdata$y~plotdata$x, xlab="",     
@@
 ```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Avg.Mito.Branch.Length,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Avg.Mito.Branch.Length,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+
+par(mar = c(8,5,2,2))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Longest.Primary.Branch..um.,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Longest.Primary.Branch..um.,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+
+par(mar = c(8,5,2,2))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
+                      y = ab$Shortest.Primary.Branch..um.,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(ab$Sex),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```
+
+```{r echo = F}
+
+plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
+                      y = ab$Shortest.Primary.Branch..um.,
+                      color = as.numeric(factor(ab$Genotype)))
+plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
+plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
+
+par(mar = c(8,5,2,2))
+boxplot(plotdata$y~plotdata$x, xlab="",     
+        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(plotdata$x)),
+       y=plotdata$y,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])
+
+```

### 2024-09-27 20240514_AxonalMorphologyResults.Rmd
Dina Folder Update

---
title: "20240514_AxonalMorphologyResults"
author: "John Santiago"
date: "2024-05-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

morph = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240513_pharate_axonal_morphology_Raw_Data.csv")

```

```{r echo = F, warning= F}

conditions = unique(morph$Genotype)

sig.data = as.list(6:17)
names(sig.data) = colnames(morph)[6:17]

pvals = setNames(c(0,0,0), c('G85Rcr vs WT', 'G85Rcr vs G85Rhet', 'G85Rhet vs WT'))

j = 6
while(j <= 17){
  morph.data = colnames(morph)[j]
  sig.data[[morph.data]] = pvals
k = 1
while(k<4){

  comp.mat = matrix(c(1,1,2,3,2,3), ncol = 2)

  x = morph[morph$Genotype == conditions[comp.mat[k,1]], morph.data]
  y = morph[morph$Genotype == conditions[comp.mat[k,2]], morph.data]

  if(j != 8 & j != 17){
    cont.table = data.frame(t = c(sum(x), sum(y)),
             f = c((length(x)- sum(x)), (length(y)- sum(y))))
    row.names(cont.table) = conditions[c(comp.mat[k,1],comp.mat[k,2])]
    sig.data[[morph.data]][[k]]= signif(as.numeric(chisq.test(cont.table)[3]),2)
  }

  if(j == 8 | j == 17){
    sig.data[[morph.data]][[k]]= signif(as.numeric(t.test(x, y)[3]),2)
  }
  k = k + 1
}
j=j+1
}

```

```{r echo = F}

j = 6

while(j<=ncol(morph)){
mean.cat = setNames(morph[,j],
                    morph$Genotype)

mean.data = setNames(rep(0, length(unique(names(mean.cat)))), unique(names(mean.cat)))

i=1
while(i<=length(mean.data)){
  mean.data[i] = mean(mean.cat[names(mean.cat) == names(mean.data)[i]])
  i=i+1
}

if(j != 8 & j != 17){
barplot(height = mean.data,
        names.arg = names(mean.data),
        las = 2, 
        main = colnames(morph)[j], 
        cex.names = .8,
        col = c('brown', 'gold', 'steelblue'), 
        density = c(50),
        ylim = c(0,1))
}

if(j == 8 | j == 17){
barplot(height = mean.data,
        names.arg = names(mean.data),
        las = 2, 
        main = colnames(morph)[j], 
        cex.names = .8,
        col = c('brown', 'gold', 'steelblue'), 
        density = c(50))
}

print(sig.data[colnames(morph)[j]])

j=j+1
}

```

### 2024-09-27 A4V BMP Signaling Genes Analysis.Rmd
Dina Folder Update

@@
 row.names(scaled) = bmp[row.names(scaled),1]
-
+allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
 colors = allcolors[1:branches]
@@
 
-```{r echo = F}
-
-GR.hmcluster(clusternum = 1, allscaled, Title)
-
-```
-
-```{r echo = F}
-
-GR.hmcluster(clusternum = 2, allscaled, Title)
-
-```
-
-```{r echo = F}
-
-GR.hmcluster(clusternum = 3, allscaled, Title)
-
-```
-
-```{r echo = F, fig.height=10}
+```{r}
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
+hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Mhmdata=t(scale(t(hmdata)))
 
 hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
-hmgroups = hmgroups[c('GR.F', 'TktDfGR.F', 'TktOEGR.F',
-                      'WT.F', 'TktDfWT.F', 'TktOEWT.F'),]
+hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]
 
@@
 
-hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
-hmgroups = hmgroups[c('GR.M', 'TktDfGR.M', 'TktOEGR.M',
-                      'WT.M', 'TktDfWT.M', 'TktOEWT.M'),]
-
-hmdata = GR.mean[, row.names(hmgroups)]
-Mhmdata=t(scale(t(hmdata)))
-
 allscaled = cbind(Fhmdata,Mhmdata)
-
-Msidecols=data.frame("Sex" = hmgroups$Sex,
-                     "Genotype" = hmgroups$Genotype)
-row.names(Msidecols)=colnames(Mhmdata)
-
-scaled = Mhmdata
-Title = "Male Larvae"
+allmean = GR.mean[,colnames(allscaled)]
+row.names(allmean) = bmp[row.names(allmean),1]
+
+scaled = allscaled
+Title = " "
 branches=3
@@
 
-```{r echo = F}
-
-GR.hmcluster(clusternum = 1, allscaled, Title)
-
-```
-
-```{r echo = F}
-
-GR.hmcluster(clusternum = 2, allscaled, Title)
-
-```
-
-```{r echo = F}
-
-GR.hmcluster(clusternum = 3, allscaled, Title)
-
-```
-
-##Heatmap of Fold Changes
-```{r echo = F, fig.height=10}
-
-hmdata = FC[intersect(row.names(FC), row.names(bmp)), c("AvS3FH", "AvS9FH", "AvS40FH",
-                                                        "AvS3MH", "AvS9MH",
-                                                        "AvS3FT", "AvS9FT", "AvS40FT",
-                                                        "AvS3MT", "AvS9MT",
-                                                        "AvS3FA", "AvS9FA", "AvS40FA",
-                                                        "AvS3MA", "AvS9MA")]
-
-hmFDR = FDR[row.names(hmdata), colnames(hmdata)]
-
-colnames(hmdata) = c('A3FH', 'A9FH', 'A40FH',
-                     'A3MH', 'A9MH',
-                     'A3FT', 'A9FT', 'A40FT',
-                     'A3MT', 'A9MT',
-                     'A3FA', 'A9FA', 'A40FA',
-                     'A3MA', 'A9MA')
-scaled=t(scale(t(hmdata)))
-
-Title = "Fold Change Data"
-branches=6
+```{r}
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
+hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Mhmdata=t(scale(t(hmdata)))
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
+hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Fhmdata=t(scale(t(hmdata)))
+
+allscaled = cbind(Fhmdata)
+allmean = GR.mean[,colnames(allscaled)]
+row.names(allmean) = bmp[row.names(allmean),1]
+
+scaled = allscaled
+Title = " "
+branches=3
 
 row.names(scaled) = bmp[row.names(scaled),1]
-
+allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
 colors = allcolors[1:branches]
@@
 colordend=(color_branches(hc, h=cutheight, col=branchcolors))
-
-scaled[hmFDR>.05] = NA
 
@@
 ```
+
+```{r}
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
+hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktDfGR.M', 'TktDfWT.M'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Mhmdata=t(scale(t(hmdata)))
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
+hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktDfGR.F', 'TktDfWT.F'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Fhmdata=t(scale(t(hmdata)))
+
+allscaled = cbind(Fhmdata,Mhmdata)
+allmean = GR.mean[,colnames(allscaled)]
+row.names(allmean) = bmp[row.names(allmean),1]
+
+scaled = allscaled
+Title = " "
+branches=3
+
+row.names(scaled) = bmp[row.names(scaled),1]
+allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
+colors = allcolors[1:branches]
+
+hc <- hclust(dist(scaled), "complete")
+heights=sort(hc$height,decreasing = T)
+
+if(branches>1){
+  cutheight=heights[branches]
+}
+
+if(branches==1){
+  cutheight=max(heights)+1
+}
+
+dnd=cut(as.dendrogram(hc),h=cutheight)
+
+if(branches>1){
+  branchcolors=colors[1:length(dnd$lower)]
+}
+if(branches==1){
+  branchcolors="black"
+}
+
+colordend=(color_branches(hc, h=cutheight, col=branchcolors))
+
+heatmaply(scaled,
+          trace="none",
+          col=RdYlBu(100)[100:1],
+          dendrogram = "row",
+          Rowv=colordend,
+          Colv="NA",
+          cexRow = 1,
+          main = Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 1, allscaled, Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 2, allscaled, Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 3, allscaled, Title)
+
+```
+
+```{r echo = F, fig.height=10}
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
+hmgroups = hmgroups[c('GR.F', 'TktDfGR.F', 'TktOEGR.F',
+                      'WT.F', 'TktDfWT.F', 'TktOEWT.F'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Fhmdata=t(scale(t(hmdata)))
+
+hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
+hmgroups = hmgroups[c('GR.M', 'TktDfGR.M', 'TktOEGR.M',
+                      'WT.M', 'TktDfWT.M', 'TktOEWT.M'),]
+
+hmdata = GR.mean[, row.names(hmgroups)]
+Mhmdata=t(scale(t(hmdata)))
+
+allscaled = cbind(Fhmdata,Mhmdata)
+
+Msidecols=data.frame("Sex" = hmgroups$Sex,
+                     "Genotype" = hmgroups$Genotype)
+row.names(Msidecols)=colnames(Mhmdata)
+
+scaled = Mhmdata
+Title = "Male Larvae"
+branches=3
+
+row.names(scaled) = bmp[row.names(scaled),1]
+
+colors = allcolors[1:branches]
+
+hc <- hclust(dist(scaled), "complete")
+heights=sort(hc$height,decreasing = T)
+
+if(branches>1){
+  cutheight=heights[branches]
+}
+
+if(branches==1){
+  cutheight=max(heights)+1
+}
+
+dnd=cut(as.dendrogram(hc),h=cutheight)
+
+if(branches>1){
+  branchcolors=colors[1:length(dnd$lower)]
+}
+if(branches==1){
+  branchcolors="black"
+}
+
+colordend=(color_branches(hc, h=cutheight, col=branchcolors))
+
+heatmaply(scaled,
+          trace="none",
+          col=RdYlBu(100)[100:1],
+          dendrogram = "row",
+          Rowv=colordend,
+          Colv="NA",
+          cexRow = 1,
+          main = Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 1, allscaled, Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 2, allscaled, Title)
+
+```
+
+```{r echo = F}
+
+GR.hmcluster(clusternum = 3, allscaled, Title)
+
+```
+
+##Heatmap of Fold Changes
+```{r echo = F, fig.height=10}
+
+hmdata = FC[intersect(row.names(FC), row.names(bmp)), c("AvS3FH", "AvS9FH", "AvS40FH",
+                                                        "AvS3MH", "AvS9MH",
+                                                        "AvS3FT", "AvS9FT", "AvS40FT",
+                                                        "AvS3MT", "AvS9MT",
+                                                        "AvS3FA", "AvS9FA", "AvS40FA",
+                                                        "AvS3MA", "AvS9MA")]
+
+hmFDR = FDR[row.names(hmdata), colnames(hmdata)]
+
+colnames(hmdata) = c('A3FH', 'A9FH', 'A40FH',
+                     'A3MH', 'A9MH',
+                     'A3FT', 'A9FT', 'A40FT',
+                     'A3MT', 'A9MT',
+                     'A3FA', 'A9FA', 'A40FA',
+                     'A3MA', 'A9MA')
+scaled=t(scale(t(hmdata)))
+
+Title = "Fold Change Data"
+branches=6
+
+row.names(scaled) = bmp[row.names(scaled),1]
+
+colors = allcolors[1:branches]
+
+hc <- hclust(dist(scaled), "complete")
+heights=sort(hc$height,decreasing = T)
+
+if(branches>1){
+  cutheight=heights[branches]
+}
+
+if(branches==1){
+  cutheight=max(heights)+1
+}
+
+dnd=cut(as.dendrogram(hc),h=cutheight)
+
+if(branches>1){
+  branchcolors=colors[1:length(dnd$lower)]
+}
+if(branches==1){
+  branchcolors="black"
+}
+
+colordend=(color_branches(hc, h=cutheight, col=branchcolors))
+
+scaled[hmFDR>.05] = NA
+
+heatmaply(scaled,
+          trace="none",
+          col=RdYlBu(100)[100:1],
+          dendrogram = "row",
+          Rowv=colordend,
+          Colv="NA",
+          cexRow = 1,
+          main = Title)
+
+```

### 2024-09-27 Anna qPCR data/AnnaThesisA4VRNAseqFigures.Rmd
Dina Folder Update

@@
 
+metab.p = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
+                     GRxWT.C =  GRxWT.C[mo, "p"],
+                     GRxWT.Df =  GRxWT.Df[mo, "p"],
+                     GRxWT.OE =  GRxWT.OE[mo, "p"],
+                     GR.CxDf =  GR.CxDf[mo, "p"],
+                     WT.CxDf =  WT.CxDf[mo, "p"],
+                     GR.CxOE =  GR.CxOE[mo, "p"],
+                     WT.CxOE =  WT.CxOE[mo, "p"])
+row.names(metab.p) = mo
+
+metab.FDR = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
+                     GRxWT.C =  GRxWT.C[mo, "FDR"],
+                     GRxWT.Df =  GRxWT.Df[mo, "FDR"],
+                     GRxWT.OE =  GRxWT.OE[mo, "FDR"],
+                     GR.CxDf =  GR.CxDf[mo, "FDR"],
+                     WT.CxDf =  WT.CxDf[mo, "FDR"],
+                     GR.CxOE =  GR.CxOE[mo, "FDR"],
+                     WT.CxOE =  WT.CxOE[mo, "FDR"])
+row.names(metab.FDR) = mo
+
+metab.FC = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
+                     GRxWT.C =  GRxWT.C[mo, "FC"],
+                     GRxWT.Df =  GRxWT.Df[mo, "FC"],
+                     GRxWT.OE =  GRxWT.OE[mo, "FC"],
+                     GR.CxDf =  GR.CxDf[mo, "FC"],
+                     WT.CxDf =  WT.CxDf[mo, "FC"],
+                     GR.CxOE =  GR.CxOE[mo, "FC"],
+                     WT.CxOE =  WT.CxOE[mo, "FC"])
+row.names(metab.FC) = mo
+
 ##Comparison cpm means
@@
 metab.id = c(metab.id, mixed.id)
+
+metab.id = data.frame(KEGG = names(metab.id),
+                      metab = metab.id)
 
@@
 ```
+
+```{r echo = F, message=F}
+
+PathwayID = "04146"
+out.id = 'G85R_F'
+FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
+FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))
+
+FC.data = TKT.EdgeR.FC[,c('GRxWT.FC', 'GRxWT.MC')]
+FDR.data = setNames(TKT.EdgeR$GRxWT.MC, row.names(TKT.EdgeR))
+
+metab.data = GRxWT.C
+KEGG.diagram(PathwayID, out.id, FC.data, FDR.data)
+
+```

### 2024-09-27 Arc1CcsNetwork.Rmd
Dina Folder Update

---
title: "Arc1/Ccs/Sod1 Network"
author: "John Santiago"
date: "2024-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, fig.width = 12, fig.height = 12}

library(visNetwork)

networkdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Arc1Sod1Network.csv", header = T)

networkdata[networkdata == ''] = NA

networkdata = networkdata[networkdata$from != "Sod1",]

nodes = data.frame(id = na.omit(unique(c(networkdata[, 1], networkdata[, 2]))))
parent = unique(networkdata$from)
nodes$group = 'interacting'
nodes[nodes$id %in% networkdata$to[duplicated(networkdata$to)], 'group'] = 'intersecting'
nodes[nodes$id %in% parent, 'group'] = 'target'

visedges = na.omit(networkdata[, 1:2])
visedges$color = 'black'

visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visGroups(groupname = 'interacting', 
            shape = 'box', 
            color = list(background = 'darkblue', border = 'black'), 
            font = list(color= 'white',size=20))%>%
    visGroups(groupname = 'intersecting', 
            shape = 'box', 
            color = list(background = 'deeppink', border = 'black'), 
            font = list(color= 'black',size=20))%>%
  visGroups(groupname = 'target',
            shape = 'box', 
            color = list(background = 'goldenrod', border = 'black'), 
            font=list(color= 'black',size=20),
            physics = FALSE)

```

### 2024-09-27 Arc1MeetingFigures.Rmd
Dina Folder Update

---
title: "arc1 gene expression"
author: "John Santiago"
date: "2024-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

G85R.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)

groups = groups[colnames(cpmdata),]

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)

A4V.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)

A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)

A4V.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)

A4V.meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

```

```{r}

  FC.data = TKT.EdgeR.FC[, c("GRxWT.FC", "GRxWT.MC")]
  FDR.data = TKT.EdgeR[, c("GRxWT.FC", "GRxWT.MC")]
  mean.data = G85R.meancpm[, c('GRFC', 'WTFC', 'GRMC', 'WTMC')]

  go.genes = row.names(FDR.data[FDR.data$GRxWT.FC < .05 &
                             FDR.data$GRxWT.MC < .05 ,])

data = data.frame(Symbol = GeneIDKey[go.genes, "Symbol"],
                  FBgn = go.genes,
                  FDR1 = -log2(FDR.data[go.genes, 1]),
                  FDR2 = -log2(FDR.data[go.genes, 2]),
                  FC1 = FC.data[go.genes, 1],
                  FC2 = FC.data[go.genes, 2],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[go.genes,1],
                  Control1.cpm = mean.data[go.genes,2],
                  Variable2.cpm = mean.data[go.genes,3],
                  Control2.cpm = mean.data[go.genes,4])

  main.title = "Female vs Male DEGs"

  ##data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  ##data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[go.genes,c(1,3)], 1, mean),
                    WT = apply(mean.data[go.genes,c(2,4)], 1, mean))
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  ##data = data[data$size > log2(20),]
  data$size = 5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

    fig = fig %>% add_markers(data = data[data$Symbol == "Arc1",],
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol[data$Symbol == "Arc1"],
                                  "\nFBgn:", data$FBgn[data$Symbol == "Arc1"],
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1[data$Symbol == "Arc1"], 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1[data$Symbol == "Arc1"], 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2[data$Symbol == "Arc1"],2)))
  fig
```

```{r echo = F}

gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), 
                  condition = groups$Group, 
                  group = paste0(groups$Genotype, groups$Sex),
                  TKT = groups$TKT)

gene = gene[gene$TKT != 'OE',]

gene$group = factor(gene$group, levels = c("WTF", "GRF", "WTM", "GRM"))
gene$condition = factor(gene$condition, levels = c('WT.F','GR.F',
                                                   'WT.M','GR.M'))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(5,7,4,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(150, 2900),
     xlim = c(.5, 4.5),
     xaxt = "n",
     yaxt = "n",
     ylab = NA,
     xlab = NA)
rect(0, 0, 4.75, 3050, col = hex('whitesmoke', .5))
boxplot(gene$cpm~gene$condition,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(10, 3000),
        xlim = c(0,4.5),
        col = c("grey90", hex("hotpink", .25), 
                "grey90", hex("deepskyblue", .2)),
        add = T)

box(lwd = 3)
axis(1, 
     at = c(1:4), 
     cex.axis = 1.5,
     labels = c("Control", "G85R", "Control", "G85R"), 
     las=1)
points(x=as.numeric(factor(gene$condition)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey65',"firebrick","grey65","deepskyblue")[as.numeric(factor(gene$group))])
abline(v=2.5, lty = 2, lwd = 3)
text(x = c(1.5, 3.5), y = c(3100,3100), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 3.5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
                  condition = A4V.groups$Group, 
                  group = paste0(groups$Genotype, groups$Sex),
                  TKT = groups$TKT)

gene$group = factor(gene$group, levels = c("WTF", "GRF", "WTM", "GRM"))
gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",

                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$condition,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(100, 3500),
        xlim = c(.945, 12.055),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:12), 
     cex.axis = 1,
     labels = rep(c("Control", "TKT Df", "TKT OE"),4), 
     las=1)
text(x = c(2, 5, 8, 11), 
     y = c(-300,-300, -300, -300), 
     c("Control", "G85R", "Control", "G85R"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$condition)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$group))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-40,-350), lty = 1, lwd = 3, xpd = T)
lines(x=c(.5,.5), y = c(-40,-350), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-40,-350), lty = 1, lwd = 3, xpd = T)
lines(x=c(9.5,9.5), y = c(-40,-350), lty = 1, lwd = 3, xpd = T)
lines(x=c(12.5,12.5), y = c(-40,-350), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 9.5), y = c(3750,3750), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F, fig.width=10}

fs = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 1F left_females.csv", header = T)

ms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 1G left_males.csv", header = T)

lcol = c('brown1', 'firebrick','steelblue', 'navy', 'limegreen', 'darkgreen',  'grey')
pcol = c('brown1', 'firebrick','steelblue', 'navy', 'limegreen', 'darkgreen',  'grey')
hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 6))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0, 100),
     xlim = c(0,82),
     ylab = 'Percent Alive',
     xlab = 'Day',
     xaxt = 'n',
     main = "A4V Survival")

axis(1, at= 1:82, lwd.ticks = .5, labels = NA)
axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
     lwd.ticks = 1, cex.axis = 1,
     col.axis = 'lightgrey')
axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
     lwd.ticks = 1, cex.axis = 1,
     col.axis = 'black')

lines(x = fs$day,
      y = fs$dsodWT,
      type = 'l',
      col = lcol[1],
      lwd = 2)

lines(x = fs$day,
      y = fs$A4V,
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = ms$day,
      y = ms$dsodWT,
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = ms$day,
      y = ms$A4V,
      type = 'l',
      col = pcol[4],
      lwd = 2)

points(x = fs$day,
       y = fs$dsodWT,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = fs$day,
       y = fs$A4V,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = ms$day,
       y = ms$dsodWT,
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = ms$day,
       y = ms$A4V,
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)

points(x = fs$day,
       y = fs$dsodWT,
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 21,
       cex =2)

points(x = fs$day,
       y = fs$A4V,
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 23,
       cex =2)
points(x = ms$day,
       y = ms$dsodWT,
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 21,
       cex =2)
points(x = ms$day,
       y = ms$A4V,
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 23,
       cex =2)

legend('topright',
       legend = c('Female Silent', 'Female A4V',
                  'Male Silent', 'Male A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

#abline(v = 3, lty = 2, lwd = 2, col = 'black')
#abline(v = 9, lty = 2, lwd = 2, col = 'black')
#abline(v = 40, lty = 2, lwd = 2, col = 'black')

#points(x = c(3,9,40),
#       y = c(-11.75,-11.75,-11.75),
#       pch = 21,
#       cex = 4,
#       bg = hex('gold', .25),
#       col = 'grey25',
#       xpd = T)

#axis(1, at= c(3, 9, 40), lwd.ticks = 2, labels = c(3,9,40))

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Head',]

gene$group = factor(gene$group, levels = c("S3FH", "S9FH", "S40FH",
                                           "A3FH", "A9FH", "A40FH",
                                           "S3MH", "S9MH",
                                           "A3MH", "A9MH"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 750),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-125,-125, -125, -125), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-33,-125), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-33,-125), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-33,-125), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-33,-125), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-33,-125), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(825,825), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Abdomen',]

gene$group = factor(gene$group, levels = c("S3FA", "S9FA", "S40FA",
                                           "A3FA", "A9FA", "A40FA",
                                           "S3MA", "S9MA",
                                           "A3MA", "A9MA"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 1450),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-250,-250, -250, -250), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-60,-250), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-60,-250), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-60,-250), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-60,-250), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-60,-250), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(1600,1600), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Thorax',]

gene$group = factor(gene$group, levels = c("S3FT", "S9FT", "S40FT",
                                           "A3FT", "A9FT", "A40FT",
                                           "S3MT", "S9MT",
                                           "A3MT", "A9MT"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 8500),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-1400,-1400, -1400, -1400), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-370,-1500), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-370,-1500), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-370,-1500), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-370,-1500), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-370,-1500), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(9500,9500), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Head',]

gene$group = factor(gene$group, levels = c("S3FH", "S9FH", "S40FH",
                                           "A3FH", "A9FH", "A40FH",
                                           "S3MH", "S9MH",
                                           "A3MH", "A9MH"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 8500),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-1000,-1000, -1000, -1000), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(9200,9200), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Abdomen',]

gene$group = factor(gene$group, levels = c("S3FA", "S9FA", "S40FA",
                                           "A3FA", "A9FA", "A40FA",
                                           "S3MA", "S9MA",
                                           "A3MA", "A9MA"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 8500),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-1000,-1000, -1000, -1000), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(9200,9200), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r echo = F}

gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Thorax',]

gene$group = factor(gene$group, levels = c("S3FT", "S9FT", "S40FT",
                                           "A3FT", "A9FT", "A40FT",
                                           "S3MT", "S9MT",
                                           "A3MT", "A9MT"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 8500),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-1000,-1000, -1000, -1000), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(9200,9200), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

```{r}

  FC.data = A4V.FC[, c("AvS9FT", "AvS9MT")]
  FDR.data = A4V.FDR[, c("AvS9FT", "AvS9MT")]
  mean.data = A4V.meancpm[, c('A9FT', 'S9FT', 'A9MT', 'S9MT')]

  go.genes = row.names(FDR.data[FDR.data$AvS9FT < .05 |
                             FDR.data$AvS9MT < .05 ,])

data = data.frame(Symbol = GeneIDKey[go.genes, "Symbol"],
                  FBgn = go.genes,
                  FDR1 = -log2(FDR.data[go.genes, 1]),
                  FDR2 = -log2(FDR.data[go.genes, 2]),
                  FC1 = FC.data[go.genes, 1],
                  FC2 = FC.data[go.genes, 2],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[go.genes,1],
                  Control1.cpm = mean.data[go.genes,2],
                  Variable2.cpm = mean.data[go.genes,3],
                  Control2.cpm = mean.data[go.genes,4])

  main.title = "Female vs Male DEGs"

  ##data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  ##data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[go.genes,c(1,3)], 1, mean),
                    WT = apply(mean.data[go.genes,c(2,4)], 1, mean))
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(10),]
  data$size = 5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

    fig = fig %>% add_markers(data = data[data$Symbol == "Arc1",],
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol[data$Symbol == "Arc1"],
                                  "\nFBgn:", data$FBgn[data$Symbol == "Arc1"],
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1[data$Symbol == "Arc1"], 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1[data$Symbol == "Arc1"], 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2[data$Symbol == "Arc1"],2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2[data$Symbol == "Arc1"],2)))
  fig
```

```{r echo = F}

sun = "FBgn0014391"
mbl = "FBgn0265487"
  ##could not find mblA, just mbl
NimC1 = "FBgn0259896"

gene = data.frame(cpm = as.numeric(A4V.cpm[sun, row.names(A4V.meta)]),
                  group = A4V.meta$Group,
                  condition = paste(substring(A4V.meta$Genotype,1,1),
                                    substring(A4V.meta$Sex,1,1)))

gene = gene[A4V.meta$Section == 'Thorax',]

gene$group = factor(gene$group, levels = c("S3FT", "S9FT", "S40FT",
                                           "A3FT", "A9FT", "A40FT",
                                           "S3MT", "S9MT",
                                           "A3MT", "A9MT"))

gene$condition = factor(gene$condition, levels = c("S F", "A F", "S M", "A M"))

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar = c(6,7,4,2))
boxplot(gene$cpm~gene$group,    
        main = "",
        ylab="",
        xlab = "",
        las = 2,
        cex.axis = 1.5,
        boxlwd = 3,
        lwd = 3,
        xaxt="n",
        ylim = c(0, 8500),
        xlim = c(.75, 10.25),
        col = c(rep(hex("lightgrey", .5),3), rep(hex("mistyrose", .5),3), 
                rep(hex("lightgrey", .5),3), rep(hex("lightcyan", .5),3)))
box(lwd = 3)
axis(1, 
     at = c(1:10), 
     cex.axis = 1,
     labels = c(rep(c("3 Day", "9 Day", "40 Day"),2),
                rep(c("3 Day", "9 Day"),2)),
     las=1)
text(x = c(2, 5, 7.5, 9.5), 
     y = c(-1000,-1000, -1000, -1000), 
     c("Control", "A4V", "Control", "A4V"),
     cex= 1.25, xpd = T)
points(x=as.numeric(factor(gene$group)),
       y=gene$cpm,
       cex=2,
       pch=21,
       lwd = 2,
       bg=c('grey25',"firebrick","grey25","deepskyblue")[as.numeric(factor(gene$condition))])
abline(v=6.5, lty = 2, lwd = 3)
lines(x=c(3.5,3.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(.37,.37), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(6.5,6.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(8.5,8.5), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
lines(x=c(10.63,10.63), y = c(-370,-1100), lty = 1, lwd = 3, xpd = T)
text(x = c(3.5, 8.5), y = c(9200,9200), c("Female", "Male"),cex= 2, xpd = T)
title(ylab="Counts per Million", line=5, cex.lab=2)
title(xlab = "Genotype", line = 5, cex.lab=2)

```

### 2024-09-27 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
Dina Folder Update

@@
                               x0 = -30, x1 = -5, xref = "x",
-                              y0 = 15.5, y1 = 22.5, yref = "y"),
+                              y0 = 15.5, y1 = 21.5, yref = "y"),
                          list(type = "rect",
@@
                               x0 = -30, x1 = -5, xref = "x",
-                              y0 = 22.5, y1 = 34.5, yref = "y")
+                              y0 = 21.5, y1 = 31.5, yref = "y")
                          ))
@@
 fig5 <- fig4 %>% add_annotations(x = -17.5,
-                        y = 19,
+                        y = 18.5,
                         text = "Cellular Component",
@@
 fig6 <- fig5 %>% add_annotations(x = -17.5,
-                        y = 29,
+                        y = 27,
                         text = "Biological Process",
@@
                         font = list(size = 15))
+
+```
+
+```{r}
+
+treemapPlot(Sup.CC.RT)
+
+```
+
+```{r}
+
+scatterPlot(Sup.CC.SM, Sup.CC.RT)
+
+```
+
+```{r}
+
+treemapPlot(Sup.BP.RT)
+
+```
+
+```{r}
+
+scatterPlot(Sup.BP.SM, Sup.BP.RT)
+
+```
+
+```{r}
+
+treemapPlot(Sup.MF.RT)
+
+```
+
+```{r}
+
+scatterPlot(Sup.MF.SM, Sup.MF.RT)
 
@@
 
-```{r}
+```{r include = FALSE}
 
@@
 
-sigGO = Enhance.GO[c(row.names(Enh.BP.RT), 
+sigGO = Enhancer.GO[c(row.names(Enh.BP.RT), 
                      row.names(Enh.CC.RT), 
@@
 
+##All Suppressors
+```{r}
+
+treemapPlot(Enh.CC.RT)
+
+```
+
+```{r}
+
+scatterPlot(Enh.CC.SM, Enh.CC.RT)
+
+```
+
+```{r}
+
+treemapPlot(Enh.BP.RT)
+
+```
+
+```{r}
+
+scatterPlot(Enh.BP.SM, Enh.BP.RT)
+
+```
+
+```{r}
+
+treemapPlot(Enh.MF.RT)
+
+```
+
+```{r}
+
+scatterPlot(Enh.MF.SM, Enh.MF.RT)
+
+```
+
 ```{r fig.height=8, fig.width=15, fig.align='left'}
@@
 ```
+
+#Enhancers
+```{r echo=F, include=F}
+
+GO.data = Moderate.GO
+GO.ontology = "BP"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Mod.BP.SM = simMatrix
+Mod.BP.RT = reducedTerms
+Mod.BP.RT$Freq = 1
+i=1
+while(i<=nrow(Mod.BP.RT)){
+  Mod.BP.RT$Freq[i] =  sum(Mod.BP.RT$parentTerm == Mod.BP.RT$parentTerm[i])
+  i=i+1
+}
+Mod.BP.RT = Mod.BP.RT[order(Mod.BP.RT$Freq, decreasing = T),]
+
+GO.ontology = "CC"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Mod.CC.SM = simMatrix
+Mod.CC.RT = reducedTerms
+Mod.CC.RT$Freq = 1
+i=1
+while(i<=nrow(Mod.CC.RT)){
+  Mod.CC.RT$Freq[i] =  sum(Mod.CC.RT$parentTerm == Mod.CC.RT$parentTerm[i])
+  i=i+1
+}
+Mod.CC.RT = Mod.CC.RT[order(Mod.CC.RT$Freq, decreasing = T),]
+
+GO.ontology = "MF"
+
+go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
+scores = setNames(-log10(GO.data$adjp), go_analysis)
+
+simMatrix <- calculateSimMatrix(go_analysis,
+                                orgdb="org.Dm.eg.db",
+                                ont=GO.ontology,
+                                method="Rel")
+
+reducedTerms <- reduceSimMatrix(simMatrix,
+                                scores,
+                                threshold=0.7,
+                                orgdb="org.Dm.eg.db")
+
+Mod.MF.SM = simMatrix
+Mod.MF.RT = reducedTerms
+Mod.MF.RT$Freq = 1
+i=1
+while(i<=nrow(Mod.MF.RT)){
+  Mod.MF.RT$Freq[i] =  sum(Mod.MF.RT$parentTerm == Mod.MF.RT$parentTerm[i])
+  i=i+1
+}
+Mod.MF.RT = Mod.MF.RT[order(Mod.MF.RT$Freq, decreasing = T),]
+
+```
+
+```{r echo = F}
+
+sigGO = Repress.GO[c(row.names(Mod.BP.RT), 
+                     row.names(Mod.CC.RT), 
+                     row.names(Mod.MF.RT)), ]
+sigGO = sigGO[row.names(sigGO)!="GO:0032991",]
+
+sigGO = sigGO[, c("category", "term","adjp", "numDEInCat", "numInCat", "ontology")]
+
+sigGO$notInCat = sigGO$numInCat - sigGO$numDEInCat
+
+data = sigGO[nrow(sigGO):1,c("term","adjp","numDEInCat", "numInCat", "category", "ontology", "notInCat")]
+data$Score = -log10(data$adjp)
+data$term = factor(data$term, levels = c(unique(data$term)))
+
+m <- list(
+  l = 100,
+  r = 50,
+  b = 100,
+  t = 100,
+  pad = 10
+)
+
+fig <- plot_ly(data, 
+               x = ~numDEInCat, y = ~term, 
+               type = 'bar',
+               name = "Candidate Modpressor Genes",
+               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
+    reversescale =T,
+                             colorbar = list(title = "-log10(FDR)",
+                                      len = .8, outlinewidth = 0,
+                                      tickformat = ".2f",
+                                      tick0 = 0, xpad = 10),
+                             color = ~Score,
+                             line = list(color = "black", width = 1.5)),
+    hoverinfo = "text",
+    hovertext = paste("Sample:", data$term,
+                      "\nGO ID: ", data$category,
+                      "\nTotal DE: ", data$numDEInCat,
+                      "\nTotal in Cat.: ", data$numInCat,
+                      "\nFDR: ", signif(data$adjp, 3)))
+
+fig2 <- fig %>% add_trace(fig, data, x = ~notInCat, y = ~term,
+                       type = 'bar',
+                       name = "Total Genes",
+                       ##colors = rep("lightgrey", nrow(data)),
+                       marker = list(color = "lightgrey",line = list(color = "black", width = 1.5), colorbar = F),
+               hoverinfo = "text",
+               hovertext = "")
+
+fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
+           yaxis = list(title = ""),
+           title = "Modpressor Enriched GO Terms",
+           margin = m,
+           barmode = 'stack',
+           shapes = list(
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -30, x1 = -5, xref = "x",
+                              y0 = -.5, y1 = 15.5, yref = "y",
+                              layer = "below"),
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -30, x1 = -5, xref = "x",
+                              y0 = 15.5, y1 = 22.5, yref = "y"),
+                         list(type = "rect",
+                              fillcolor = "white", 
+                              line = list(color = "black", width = 2.5), 
+                              opacity = 1,
+                              x0 = -30, x1 = -5, xref = "x",
+                              y0 = 22.5, y1 = 34.5, yref = "y")
+                         ))
+
+fig4 <- fig3 %>% add_annotations(x = -17.5,
+                        y = 7.5,
+                        text = "Molecular Function",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 15))
+
+fig5 <- fig4 %>% add_annotations(x = -17.5,
+                        y = 19,
+                        text = "Cellular Component",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 15))
+
+fig6 <- fig5 %>% add_annotations(x = -17.5,
+                        y = 29,
+                        text = "Biological Process",
+                        showarrow = F,
+                        textangle = -90,
+                        font = list(size = 15))
+
+```
+
+#Moderate Suppressors
+```{r}
+
+treemapPlot(Mod.CC.RT)
+
+```
+
+```{r}
+
+treemapPlot(Mod.BP.RT)
+
+```
+
+```{r}
+
+treemapPlot(Mod.MF.RT)
+
+```
+
+```{r fig.height=12, fig.width=15, fig.align='left'}
+
+fig6
+
+```

### 2024-09-27 EmilyNetwork.Rmd
Dina Folder Update

---
title: "Emily Network"
author: "John Santiago"
date: "2024-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, fig.width = 12, fig.height = 12}

library(visNetwork)
networkdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/ConspiracyNetwork/ConspiracyNetwork.csv", header = T)

networkdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/NewEmilyNetwork.csv", header = T)

allSGs = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/SG Kankel.csv", header = T)
SGs = allSGs$FBGN
SGs = intersect(SGs, networkdata$FGbn)
SGs = unique(c(networkdata[networkdata$FGbn %in% SGs, 'to'], intersect(allSGs$GENE, networkdata$from)))

networkdata[networkdata == ''] = NA

nodes = data.frame(id = na.omit(unique(c(networkdata[, 1], networkdata[, 2]))))
parent = unique(networkdata$from)
nodes$group = 'interacting'
nodes[nodes$id %in% networkdata$to[duplicated(networkdata$to)], 'group'] = 'intersecting'
nodes[nodes$id %in% parent, 'group'] = 'target'
nodes[nodes$id %in% SGs, 'group'] = 'SG gene'

visedges = na.omit(networkdata[, 1:2])
visedges$color = 'black'

visNetwork(nodes,visedges)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visGroups(groupname = 'interacting', 
            shape = 'box', 
            color = list(background = 'darkblue', border = 'black'), 
            font = list(color= 'white',size=20))%>%
    visGroups(groupname = 'intersecting', 
            shape = 'box', 
            color = list(background = 'deeppink', border = 'black'), 
            font = list(color= 'black',size=20))%>%
  visGroups(groupname = 'target',
            shape = 'box', 
            color = list(background = 'goldenrod', border = 'black'), 
            font=list(color= 'black',size=20),
            physics = FALSE)%>%
  visGroups(groupname = 'SG gene',
            shape = 'box', 
            color = list(background = 'limegreen', border = 'black'), 
            font=list(color= 'black',size=20),
            physics = FALSE)

```

### 2024-09-27 EmilyTBPHanalysis.Rmd
Dina Folder Update

---
title: "Emily TBPH Analysis"
author: "John Santiago"
date: "2024-02-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

Emily = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/EmilyTBPH_qPCR.csv', header = T)

data = Emily[Emily$Genotype != 'tbph',]

orer = data[data$Genotype=='OreR',]
otu = data[data$Genotype=='otu-RNAi',]
tudor = data[data$Genotype=='Tudor-SN-RNAi',]
lacz = data[data$Genotype=='LacZ',]
rnai = data[data$Genotype=='tbph-RNAi',]

sig.values = data.frame(Genotype = c("otu-RNAi", "Tudor-SN-RNAi", 'tbph-RNAi', 'LacZ'),
                        RelativeOreR = c(t.test(orer$dCT, otu$dCT, 
                                                paired = T, alternative = "g")[[3]],
                                         t.test(orer$dCT, tudor$dCT, 
                                                paired = T, alternative = "g")[[3]],
                                         t.test(orer$dCT, rnai$dCT, 
                                                paired = T, alternative = "g")[[3]],
                                         t.test(orer$dCT, lacz$dCT, 
                                                paired = T, alternative = "g")[[3]]),
                        RelativeLacZ = c(t.test(lacz$dCT, otu$dCT, paired = T)[[3]],
                                         t.test(lacz$dCT, tudor$dCT, paired = T)[[3]],
                                         t.test(lacz$dCT, rnai$dCT, paired = T)[[3]],
                                         NA))

```

```{r}

boxdata = na.omit(data)

boxdata = boxdata[boxdata$Genotype != 'Tudor-SN-RNAi',]

boxplot(boxdata$ddCT.FC ~ boxdata$Genotype, 
        xlab="",     
        main= "FC relative to OreR",
        ylab="FC (2^-ddCT)", 
        las = 1, 
        cex.axis = .8,
        ylim = c(0, 5))

points(x=as.numeric(factor(boxdata$Genotype)),
       y=boxdata$ddCT.FC,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue", 'mediumorchid')[as.numeric(factor(boxdata$Genotype))])

abline(h = 1, lty = 2)

#lines(x= )

text(x = c(2:4), y = c(5,5,5), labels = paste0("p = ", signif(sig.values[c(1,3,2),3],3)))

legend('topright',
       inset=c(-0.175,0),
       legend = c('OreR', 'Otu-RNAi', 'Tudor-SN-RNAi', 'tbph-RNAi', 'LacZ'), 
       fill = c('firebrick',"darkgreen","gold","dodgerblue", 'mediumorchid'),
       cex = .65,
       bty = 'n',
       pt.cex = .5)

```

```{r}

bardata = setNames(c(mean(data$ddCT.FC[data$Genotype == 'LacZ']),
                     mean(data$ddCT.FC[data$Genotype == 'otu-RNAi']),
                     mean(data$ddCT.FC[data$Genotype == 'Tudor-SN-RNAi']),
                     mean(data$ddCT.FC[data$Genotype == 'tbph-RNAi'])), 
                   c('LacZ', 'otu-RNAi', 'Tudor-SN-RNAi', 'tbph-RNAi'))

barplot(height = bardata, 
        xlab="",     
        main= "FC relative to OreR",
        ylab="FC (2^-ddCT)", 
        las = 1, 
        cex.axis = .8,
        col = c('brown',"gold2","darkgreen","steelblue"),
        ylim = c(0,5))

abline(h = 1, lty = 2)

text(x = c(2:4), y = c(4.5,4.5,4.5), labels = paste0("p = ", signif(sig.values[c(1,3,2),3],3)))

legend('topright',
       inset=c(-0.175,0),
       legend = c('OreR', 'Otu-RNAi', 'Tudor-SN-RNAi', 'tbph-RNAi', 'LacZ'), 
       fill = c('brown',"gold2","darkgreen","steelblue"),
       cex = .65,
       bty = 'n',
       pt.cex = .5)

```

```{r echo = F}

temp = read.csv("/Users/johncsantiago/Documents/track.csv", header = F)

plot(x=temp$V1, y=temp$V2, xlim = c(25, 225), pch = 21, bg='gold', cex = .5)
points(x=temp$V3, y=temp$V4, pch = 21, bg='brown', cex = .5)
```

````{r echo = F}
library(reshape2)
eclosion = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Russo Fig 1 eclosion.csv", header = T)

eclosion = na.omit(melt(eclosion, variable.name = 'Genotype', value.name = "PercentEclosed"))

eclosion.aov = aov(eclosion$PercentEclosed~eclosion$Genotype)

eclosion.Tukey = TukeyHSD(eclosion.aov)

write.csv(eclosion.Tukey$`eclosion$Genotype`, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Russo Fig 1 eclosion_TukeyDATA.csv")

```

### 2024-09-27 G85R_OXPHOS_KEGG_Pathways.Rmd
Dina Folder Update

---
title: "OXPHOS KEGG Genes"
author: "John Santiago"
date: "2024-06-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F,include = F}

library(plotly)
library(edgeR)
library(heatmaply)
library(pathview)
library(org.Dm.eg.db)

A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
A4V.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
A4V.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
A4V.meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

A4V.comparekey = setNames(colnames(A4V.FDR),
                          c('A3FHvS3FH', 'A3MHvS3MH', 'A9FHvS9FH', 'A9MHvS9MH', 'A40FHvS40FH',
                            'A3FHvA9FH', 'S3FHvS9FH', 'A3MHvA9MH', 'S3FHvS9MH',
                            'A9FHvA40FH', 'S9FHvS40FH', 'A3FHvA40FH', 'S3FHvS40FH',

                            'A3FTvS3FT', 'A3MTvS3MT', 'A9FTvS9FT', 'A9MTvS9MT', 'A40FTvS40FT',
                            'A3FTvA9FT', 'S3FTvS9FT', 'A3MTvA9MT', 'S3FTvS9MT',
                            'A9FTvA40FT', 'S9FTvS40FT', 'A3FTvA40FT', 'S3FTvS40FT',

                            'A3FAvS3FA', 'A3MAvS3MA', 'A9FAvS9FA', 'A9MAvS9MA', 'A40FAvS40FA',
                            'A3FAvA9FA', 'S3FAvS9FA', 'A3MAvA9MA', 'S3FAvS9MA',
                            'A9FAvA40FA', 'S9FAvS40FA', 'A3FAvA40FA', 'S3FAvS40FA',

                            'A3FHvA3MH', 'S3FHvS3MH', 'A9FHvA9MH', 'S9FHvS9MH',
                            'A3FTvA3MT', 'S3FTvS3MT', 'A9FTvA9MT', 'S9FTvS9MT',
                            'A3FAvA3MA', 'S3FAvS3MA', 'A9FAvA9MA', 'S9FAvS9MA'))

G85R.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv",row.names = 1)
G85R.cpm = G85R.cpm[grep('FBgn', row.names(G85R.cpm)),]
G85R.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)
colnames(G85R.meancpm) = c('GRFC', 'GRMC', 
                           'GRFDf', 'GRMDf', 'WTFDf', 'WTMDf',
                           'GRFOE', 'GRMOE', 'WTFOE', 'WTMOE',
                           'WTFC', 'WTMC')
G85R.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv",row.names = 1)
G85R.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv", row.names = 1)
G85R.meta  = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv",row.names = 1)

G85R.comparekey = setNames(colnames(G85R.FDR),
                           c('GRFCvGRFDf', 'GRFCvGRFOE', 'WTFCvWTFDf', 'WTFCvWTFOE', 
                             'GRFCvWTFC', 'GRFDfvWTFDf', 'GRFOEvWTFOE',
                             'GRMCvGRMDf', 'GRMCvGRMOE', 'WTMCvWTMDf', 'WTMCvWTMOE', 
                             'GRMCvWTMC', 'GRMDfvWTMFDf', 'GRMOEvWTMOE',
                             'GRFCvGRMC', 'WTFCvWTMC'))

G85R.metab.comparekey = setNames(c("GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE",
                                   "GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE"), names(G85R.comparekey)[1:14])

G85R.metabnorm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/NormalizedMetabolomicData.csv", row.names = 1)
G85R.metabmean = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MeanNormalizedMetabolomicData.csv", row.names = 1)
metab.id = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteMultiKEGGIDKey.csv", row.names = 1)
metab.id = setNames(metab.id$metab, metab.id$KEGG)
G85R.metabFC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFCs.csv", row.names = 1)
G85R.metabFDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFDRs.csv", row.names = 1)
G85R.metabp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/Metabolitepvals.csv", row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
KEGG.MetabKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.MetabKey = setNames(KEGG.MetabKey[-c(1:2), 2], row.names(KEGG.MetabKey)[-c(1:2)])
genesingo = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/genesingo.RData")
GenesInKegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/kegg.symbol2path.RData")
KEGG.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/KEGG.names.csv", row.names = 1)
GO.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GO.names.csv", row.names = 1)

git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))

nodeID = as.list(org.Dm.egENZYME)

gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
gbbOE = gbbOE[,row.names(gbbOE.groups)]
gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)

##normalize data
countdata=gbbOE
x <- countdata
gr <- factor(gbbOE.groups$group, levels=c(unique(gbbOE.groups$group)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbOE.cpmdata=cpm(z)

gbbOEmean = gbbOE.cpmdata[,1:6]
colnames(gbbOEmean) = unique(gr)
i=1
while(i<=6){
  temp= gbbOE.cpmdata[,row.names(gbbOE.groups[gbbOE.groups$group == colnames(gbbOEmean)[i],])]
  gbbOEmean[,i] = apply(temp, 1, mean)
  i=i+1
}

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)

fit <- glmQLFit(z, design)
plotQLDisp(fit)

compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.LL3=DEout
sGRxWT.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_ML3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.ML3=DEout
sGRxWT.ML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_LL3-G85R_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.LL3xML3=DEout
sGR.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(LoxP_LL3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.LL3xML3=DEout
sWT.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-G85R_gbb_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbb.LL3xML3=DEout
sG85R_gbb.LL3xML3=DEout[DEout$FDR<.05,]

gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)

##normalize data
countdata=gbbKO
x <- countdata
gr <- factor(gbbKO.groups$Genotype, levels=c(unique(gbbKO.groups$Genotype)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbKO.cpmdata=cpm(z)

gbbKOmean = gbbKO.cpmdata[,1:2]
colnames(gbbKOmean) = c('WT', 'KO')
i=1
while(i<=2){
  temp= gbbKO.cpmdata[,row.names(gbbKO.groups)[gbbKO.groups$Genotype == colnames(gbbKOmean)[i]]]
  gbbKOmean[,i] = apply(temp, 1, mean)
  i=i+1
}

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)

fit <- glmQLFit(z, design)
plotQLDisp(fit)

compare = makeContrasts(KO-WT, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
KOxWT=DEout
sKOxWT=DEout[DEout$FDR<.05,]

```

```{r echo = F, fig.height= 12}

NADmetab = names(kegg[grep('00190', kegg)])
NADmetab = row.names(GeneIDKey[GeneIDKey$Symbol %in% NADmetab, ])

geneset = NADmetab

hmdata = A4V.meancpm[geneset,]

A4V.order = c("S3FH", "S9FH", "S40FH", "A3FH", "A9FH", "A40FH",
              "S3FT", "S9FT", "S40FT", "A3FT", "A9FT", "A40FT",
              "S3FA", "S9FA", "S40FA", "A3FA", "A9FA", "A40FA",
              "S3MH", "S9MH", "A3MH", "A9MH",
              "S3MT", "S9MT", "A3MT", "A9MT",
              "S3MA", "S9MA", "A3MA", "A9MA")

hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),A4V.order])
row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']

heatmaply(hmdata,
          scale = 'row',
          Colv = F,
          cexRow = .5)

```

```{r echo = F, fig.height= 12}

hmdata = G85R.meancpm[geneset,]
G85R.order = c("WTFC", "WTFDf", "WTFOE",
          "GRFC", "GRFDf", "GRFOE",
          "WTMC", "WTMDf", "WTMOE",
          "GRMC", "GRMDf", "GRMOE")

hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),G85R.order])
row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']

heatmaply(hmdata,
          scale = 'row',
          Colv = F,
          cexRow = .5)

```

```{r echo = F, fig.height= 12}

hmdata = gbbOEmean[intersect(row.names(gbbOEmean),geneset),]
gbbOE.order = c("LoxP_ML3", "LoxP_LL3",
          "G85R_ML3", "G85R_LL3",
          "G85R_gbb_ML3", "G85R_gbb_LL3")

hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),gbbOE.order])
row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']

heatmaply(hmdata,
          scale = 'row',
          Colv = F,
          cexRow = .5)

```

```{r echo = F, fig.height= 12}

hmdata = gbbKO.cpmdata[intersect(row.names(gbbKOmean),geneset), row.names(gbbKO.groups)]
colnames(hmdata) = c("WT1", "WT2", "WT3", "KO1", "KO2", "KO3")

hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),])
row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']

heatmaply(hmdata,
          scale = 'row',
          Colv = F,
          cexRow = .5)

```

```{r warning=F,  echo = F, include = F}

##colnames(G85R.FC) = "GRF.CxDf"  "GRF.CxOE"  "WTF.CxDf" "WTF.CxOE"  "GRxWT.FC"  "GRxWT.FDf" "GRxWT.FOE" "GRM.CxDf"  "GRM.CxOE" "WTM.CxDf"  "WTM.CxOE"  "GRxWT.MC" "GRxWT.MDf" "GRxWT.MOE" "GR.FxM" "WT.FxM"

##colnames(G85R.metabFC) = "KEGG" "GRxWT.C" "GRxWT.Df" "GRxWT.OE" "GR.CxDf"  "WT.CxDf" "GR.CxOE"  "WT.CxOE"

FC.data = G85R.FC[,c("WTF.CxDf", "WTM.CxDf")]
metab.data = setNames(G85R.metabFC[,"WT.CxDf"], G85R.metabFC$KEGG)
out.id = "WT_ControlxDeficient_FandM_Genes with WT_ControlxDeficient_Metab"

PathwayID = "00190"
sigs = row.names(FC.data)

##File name

OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
setwd(OutputDir)
img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")

  if(class(FC.data)=="numeric"){
    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
  }

  if(class(FC.data)=="data.frame"){
    deg.data = as.matrix(FC.data)
    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
  }

  pv.out <- pathview(gene.data =  deg.data,
                     cpd.data = metab.data,
                     pathway.id = PathwayID,
                     species = "dme",
                     kegg.native = T,
                     limit=list(gene=c(-2,2)),
                     node.sum="max.abs",
                     low="royalblue",mid = "grey",high="firebrick",
                     out.suffix = out.id,
                     bins=list(genes=30),
                     plot.col.key = T,
                     match.data = F)

  #knitr::include_graphics(img.file)

```

```{r warning=F,  echo = F, include = F}

##EdgeR Comparisons  = GRxWT.ML3 GR.LL3xML3 WT.LL3xML3 G85R_gbb.LL3xML3

FC.data = data.frame(FC1 = GR.LL3xML3[row.names(GRxWT.ML3), "logFC"],
                     FC2 = G85R_gbb.LL3xML3[row.names(GRxWT.ML3), "logFC"])
row.names(FC.data) = row.names(GRxWT.ML3)

out.id = "G85RandG85R.gbbOE_LL3xML3"

PathwayID = "00190"
sigs = row.names(FC.data)

##File name

OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
setwd(OutputDir)
img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")

    deg.data = as.matrix(FC.data)
    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]

  pv.out <- pathview(gene.data =  deg.data,
                     pathway.id = PathwayID,
                     species = "dme",
                     kegg.native = T,
                     limit=list(gene=c(-2,2)),
                     node.sum="max.abs",
                     low="royalblue",mid = "grey",high="firebrick",
                     out.suffix = out.id,
                     bins=list(genes=30),
                     plot.col.key = T,
                     match.data = F)

  #knitr::include_graphics(img.file)

```

```{r warning=F,  echo = F, include = F}

##EdgeR Comparisons  = KOxWT

FC.data = setNames(KOxWT$logFC, row.names(KOxWT))

out.id = "gbbKOxgbbWT"

PathwayID = "00190"
sigs = names(FC.data)

##File name

OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
setwd(OutputDir)
img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")

    deg.data = as.vector(FC.data)
    names(deg.data) = GeneIDKey[names(FC.data), "ensembl"]

  pv.out <- pathview(gene.data =  deg.data,
                     pathway.id = PathwayID,
                     species = "dme",
                     kegg.native = T,
                     limit=list(gene=c(-2,2)),
                     node.sum="max.abs",
                     low="royalblue",mid = "grey",high="firebrick",
                     out.suffix = out.id,
                     bins=list(genes=30),
                     plot.col.key = T,
                     match.data = F)

  #knitr::include_graphics(img.file)

```

### 2024-09-27 GOandKEGGTermEnrichment.Rmd
Dina Folder Update

---
title: "GO and KEGG Term Enrichment"
author: "John Santiago"
date: "2024-05-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, message = F}

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')

```

```{r echo = F, message = F}

Variable.Condition = "A9MT" 
Control.Condition = "S9MT"
secondary.Variable.Condition = "A40FT"
secondary.Control.Condition = "S40FT"

comparison = paste0(Variable.Condition, 'v', Control.Condition)
secondary.comparison = paste0(secondary.Variable.Condition, 'v', secondary.Control.Condition)

if(length(intersect(comparison, names(A4V.comparekey))) == 1){
  FC = A4V.FC[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
  FDR = A4V.FDR[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
  mean.data = A4V.meancpm[,c(Variable.Condition, Control.Condition, 
                             secondary.Variable.Condition, secondary.Control.Condition)]
  metab.data = 'none'
}

if(length(intersect(comparison, names(G85R.comparekey))) == 1){
  FC = G85R.FC[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
  FDR = G85R.FDR[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
  mean.data = G85R.meancpm[,c(Variable.Condition, Control.Condition, 
                              secondary.Variable.Condition, secondary.Control.Condition)]
  metab.data = G85R.metab.comparekey[c(comparison, secondary.comparison)]
  if(G85R.metab.comparekey[c(comparison)] == G85R.metab.comparekey[c(secondary.comparison)]){
    metab.data = G85R.metab.comparekey[c(comparison)]
  }
}

subset = T

s1 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] < 0,]))
s2 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] < 0,]))
s3 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] > 0,]))
s4 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] > 0,]))

biomarkers = row.names(A4V.FDR[(A4V.FDR$AvS3FT > .05 &
                       A4V.FDR$AvS9FT > .05 &
                       A4V.FDR$AvS40FT < .05 &
                       A4V.FDR$AvS3MT > .05 &
                       A4V.FDR$AvS9MT < .05),])
expression.max = apply(A4V.meancpm[biomarkers, c("A40FT","S40FT","A9MT","S9MT")], MARGIN = 1, max)[biomarkers]
biomarkers = biomarkers[expression.max > 20]

NADmetab = names(kegg[grep('00760', kegg)])
biomarkers = row.names(GeneIDKey[GeneIDKey$Symbol %in% NADmetab, ])

if(subset == T){
  geneset = biomarkers
  s1 = intersect(s1, geneset)
  s2 = intersect(s2, geneset)
  s3 = intersect(s3, geneset)
  s4 = intersect(s4, geneset)
  FC[setdiff(row.names(FC),geneset),] = 1 
  FDR[setdiff(row.names(FDR),geneset),] = 1 
}

```

```{r echo = F}

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
volcano(FC, FDR, mean.data)

```

```{r echo = F}

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
compare.genes(FC, FDR, mean.data)

```

```{r echo = F}
library(heatmaply)
hmdata = mean.data[geneset,]
row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
hmdata = na.omit(hmdata)

heatmaply(hmdata,
          scale = 'row',
          Colv = F)

```

```{r echo = F}

##Uses data from primary comparison
##point size is relative to mean expression in variable condition
DEG.venn(FDR, FC)

```

```{r echo = F, include = F}

####Uses sigDEGs from primary comparison
cat.data = Enrichment(FDR)

```

```{r echo = F}

##which ranks of categories to use
##a vector of numbers specifying which ranks to use
##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
##can also just type 'sigs.only' 
usecats=c(1:20)
#usecats = 'sigs.only'

KEGG20(cat.data, FC, FDR, usecats)

```

```{r echo = F, include = T}

##can be the exact name or 5 digit code in quotes
specific.kegg = "00980"

plotkegg.genes(specific.kegg, FC, FDR, mean.data)

```

```{r echo = F, message=F, fig.width=7}

##5 digits from KEGG ID
PathwayID = "00010"

#options include 'primary' or 'both'
use = 'both'

KEGG.diagram(PathwayID, FC, use, metab.data)

```

```{r echo = F, include = T, warnings = F}

##can be the exact name or 5 digit code in quotes
specific.kegg = "00010"

comparekegg.genes(specific.kegg, FC, FDR, mean.data)

```

```{r echo = F}

## BP, CC, or MF
GO.ontology = 'BP'

##can select which categories ot include or say 'sigs.only'
usecats=c(1:20)
#usecats = 'sigs.only'

GO20(cat.data, GO.ontology, FC, FDR, usecats)

```

```{r echo = F}

##the 7 digits of a GOterm id or the exact term name
specific.go = '0005811'

plotgo.genes(specific.go, FC, FDR, mean.data)

```

```{r echo = F, warning = F}

##the 7 digits of a GOterm id or the exact term name
specific.go = '0005811'

comparego.genes(specific.go, FC, FDR, mean.data)

```

```{r echo = F, warning = F, message = F}

## BP, CC, or MF
GO.ontology = 'BP'

rt = tree(cat.data, GO.ontology)

treemapPlot(rt)

```

```{r echo = F, warning = F}

##a parent category generated in the treemapPlot function
parent.category = 'membrane lipid biosynthetic process'

plotparentcat.genes(parent.category, FC, FDR, mean.data)

```

```{r echo = F}

##a parent category generated in the treemapPlot function
##parent.category = 'small molecule biosynthetic process'

compareparent.genes(parent.category, FC, FDR, mean.data)
##dot size is relative to the max FDR of either condition

```

### 2024-09-27 GeneExpressionBoxPlots.Rmd
update
Dina Folder Update

@@
 ---
-title: "Box Plots Using All Data"
+title: "rac1 gene expression"
 author: "John Santiago"
-date: "2023-11-28"
+date: "2024-05-24"
 output: html_document
@@
 library(edgeR)
+library(heatmaply)
+library(org.Dm.eg.db)
+library(KEGGREST)
 
@@
 
+nodeID = as.list(org.Dm.egENZYME)
+
 ```
 
-```{r}
+```{r echo = F}
+
+##subsetting genes for patterns
+
+```
+
+```{r echo = F}
 
@@
 ## arc1 FBgn0033926
+##rac1
+##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')
+##mle 'FBgn0002774'
+##gstD FBgn0001149
+##Tudor-SN FBgn0035121
+##atf4 FBgn0000370
+##thor FBgn0261560
+##sdhbl FBgn0030975
+##ND-51L FBgn0034251
+##kayak (AP-1) FBgn0001297
+## Jra (AP-1) FBgn0001291
+#sad FBgn0003312
 
-##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')
+##Specific enzyme
+enzyme.ens = nodeID[grep('3.1.3.5',nodeID)]
+enzyme.genes = GeneIDKey[GeneIDKey$ensembl %in% names(enzyme.ens)[c(1,3:5,7)],]
 
-FBgn = 'FBgn0033926'
-name = ''
+```
+
+> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'Symbol']
+ [1] "Cyp4p1"  "CG13962" "Cpr51A"  "CG11438" "Sgs5bis" "sad"    
+ [7] "Lip2"    "CG4757"  "CG14229" "CG15406" "CG3270"  "CG9877" 
+[13] "CG13905" "Zip71B"  "CG17027" "nom"     "CG16727" "CG9702" 
+[19] "CG43740"
+> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'FBgn']
+ [1] "FBgn0015037" "FBgn0032824" "FBgn0033942" "FBgn0037164"
+ [5] "FBgn0038523" "FBgn0003312" "FBgn0024740" "FBgn0027584"
+ [9] "FBgn0031059" "FBgn0031517" "FBgn0033093" "FBgn0034819"
+[13] "FBgn0035176" "FBgn0036461" "FBgn0036553" "FBgn0037617"
+[17] "FBgn0038719" "FBgn0039787" "FBgn0263997"
+
+```{r echo = F}
+FBgn = 'FBgn0011817'
+name = 'FBgn0011817: nmo'
 
@@
 gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F", "TktOEGR.F",
-                                                 'WT.F', "TktDfWT.F", "TktOEWT.F",
-                                                 'GR.M', "TktDfGR.M", "TktOEGR.M",
-                                                 'WT.M', "TktDfWT.M", "TktOEWT.M"))
+gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
+                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
+                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
+                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))
+
+par(mar = c(5,7,5,2))
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(min(gene$cpm), max(gene$cpm)),
+     xlim = c(.5, 12.5),
+     xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = NA)
+
+rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
+
+boxplot(gene$cpm~gene$condition, 
+        xlab="",
+        las = 2, 
+        cex.axis = .8,
+        xaxt = 'none',
+        yaxt = 'none',
+        boxwex = .75,
+        boxlwd = 2,
+        lwd = 2,
+        cex.ticks = 2,
+        add = T,
+        col = c(rep("honeydew", 3),
+                rep("thistle1", 3),
+                rep("lightcyan", 3),
+                rep("lightyellow", 3)))
+
+box(lwd = 2)
+
+points(x=as.numeric(factor(gene$condition)),
+       y=gene$cpm,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+
+axis(side = 1,
+     at = 1:12,
+     labels = rep(c("Control", "Df", "OE"), 4),
+     line = 0,
+     cex.axis = .75,
+     lwd.ticks = 2)
+
+axis(side = 2,
+     line = 0,
+     cex.axis = 1,
+     lwd.ticks = 2,
+     las = 2)
+
+axis(side = 2,
+     at = .5*(max(gene$cpm) + min(gene$cpm)),
+     label = "Counts per million reads",
+     tick = F,
+     padj = -3,
+     cex.axis = 1.25)
+
+axis(side = 1,
+     at = c(2, 5, 8, 11),
+     labels = c("Silent", "G85R","Silent", "G85R"),
+     tick = F,
+     padj = 2,
+     cex.axis = 1)
+axis(side = 3,
+     at = c(3.5, 9.5),
+     labels = c("Female", "Male"),
+     tick = F,
+     padj = .5,
+     cex.axis = 1.5)
+
+axis(side = 3,
+     at = 6.5,
+     labels = name,
+     tick = F,
+     padj = -1.5,
+     cex.axis = 2)
+
+axis(side = 3,
+     at = c(3.5,9.5),
+     tick = T,
+     outer = T,
+     labels = F,
+     line = -2.25,
+     lwd.ticks = 0)
+
+xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
+xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
+lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+abline(v = 6.5, lty = 2, lwd = 2)
+
+```
+
+```{r echo = F}
+
+gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), 
+                  condition = groups$Group, 
+                  group = paste0(groups$Genotype, groups$Sex),
+                  TKT = groups$TKT)
+
+gene = gene[gene$TKT != 'OE',]
+
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F",
+                                                 'WT.F', "TktDfWT.F",
+                                                 'GR.M', "TktDfGR.M",
+                                                 'WT.M', "TktDfWT.M"))
 
@@
 legend('topright',
-       inset=c(-0.175,0),
+       inset=c(-0.275,0),
        legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
-       fill = c('firebrick',"gold","darkgreen","dodgerblue"),
+       fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
        cex = .65,

### 2024-09-27 KristiPresentationData.Rmd
Dina Folder Update

--- 2024-09-27 G85R_OXPHOS_KEGG_Pathways.Rmd
@@
 ---
-title: "OXPHOS KEGG Genes"
+title: "Kristi Meeting"
 author: "John Santiago"
-date: "2024-06-22"
+date: "2024-06-18"
 output: html_document
@@
 
-```{r echo = F,include = F}
+```{r echo = F}
 
@@
 
-gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
-gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
-gbbOE = gbbOE[,row.names(gbbOE.groups)]
-gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
-
-##normalize data
-countdata=gbbOE
-x <- countdata
-gr <- factor(gbbOE.groups$group, levels=c(unique(gbbOE.groups$group)))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- calcNormFactors(y, method = "TMM")
-##normalized cpm
-gbbOE.cpmdata=cpm(z)
-
-gbbOEmean = gbbOE.cpmdata[,1:6]
-colnames(gbbOEmean) = unique(gr)
-i=1
-while(i<=6){
-  temp= gbbOE.cpmdata[,row.names(gbbOE.groups[gbbOE.groups$group == colnames(gbbOEmean)[i],])]
-  gbbOEmean[,i] = apply(temp, 1, mean)
-  i=i+1
-}
-
-design<-model.matrix(~0 + gr)
-colnames(design) = unique(gr)
-z = estimateDisp(z, design, robust = T)
-
-fit <- glmQLFit(z, design)
-plotQLDisp(fit)
-
-compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.LL3=DEout
-sGRxWT.LL3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_ML3-LoxP_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.ML3=DEout
-sGRxWT.ML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_LL3-G85R_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.LL3xML3=DEout
-sGR.LL3xML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(LoxP_LL3-LoxP_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.LL3xML3=DEout
-sWT.LL3xML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_gbb_LL3-G85R_gbb_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-G85R_gbb.LL3xML3=DEout
-sG85R_gbb.LL3xML3=DEout[DEout$FDR<.05,]
-
-gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
-gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)
-
-##normalize data
-countdata=gbbKO
-x <- countdata
-gr <- factor(gbbKO.groups$Genotype, levels=c(unique(gbbKO.groups$Genotype)))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- calcNormFactors(y, method = "TMM")
-##normalized cpm
-gbbKO.cpmdata=cpm(z)
-
-gbbKOmean = gbbKO.cpmdata[,1:2]
-colnames(gbbKOmean) = c('WT', 'KO')
-i=1
-while(i<=2){
-  temp= gbbKO.cpmdata[,row.names(gbbKO.groups)[gbbKO.groups$Genotype == colnames(gbbKOmean)[i]]]
-  gbbKOmean[,i] = apply(temp, 1, mean)
-  i=i+1
-}
-
-design<-model.matrix(~0 + gr)
-colnames(design) = unique(gr)
-z = estimateDisp(z, design, robust = T)
-
-fit <- glmQLFit(z, design)
-plotQLDisp(fit)
-
-compare = makeContrasts(KO-WT, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-KOxWT=DEout
-sKOxWT=DEout[DEout$FDR<.05,]
-
 ```
@@
 
-```{r echo = F, fig.height= 12}
+```{r warning=F,  echo = F}
 
-hmdata = gbbOEmean[intersect(row.names(gbbOEmean),geneset),]
-gbbOE.order = c("LoxP_ML3", "LoxP_LL3",
-          "G85R_ML3", "G85R_LL3",
-          "G85R_gbb_ML3", "G85R_gbb_LL3")
-
-hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),gbbOE.order])
-row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']
-
-heatmaply(hmdata,
-          scale = 'row',
-          Colv = F,
-          cexRow = .5)
-
-```
-
-```{r echo = F, fig.height= 12}
-
-hmdata = gbbKO.cpmdata[intersect(row.names(gbbKOmean),geneset), row.names(gbbKO.groups)]
-colnames(hmdata) = c("WT1", "WT2", "WT3", "KO1", "KO2", "KO3")
-
-hmdata = (hmdata[!is.na((GeneIDKey[row.names(hmdata), 'Symbol'])),])
-row.names(hmdata) = GeneIDKey[row.names(hmdata), 'Symbol']
-
-heatmaply(hmdata,
-          scale = 'row',
-          Colv = F,
-          cexRow = .5)
-
-```
-
-```{r warning=F,  echo = F, include = F}
-
-##colnames(G85R.FC) = "GRF.CxDf"  "GRF.CxOE"  "WTF.CxDf" "WTF.CxOE"  "GRxWT.FC"  "GRxWT.FDf" "GRxWT.FOE" "GRM.CxDf"  "GRM.CxOE" "WTM.CxDf"  "WTM.CxOE"  "GRxWT.MC" "GRxWT.MDf" "GRxWT.MOE" "GR.FxM" "WT.FxM"
-
-##colnames(G85R.metabFC) = "KEGG" "GRxWT.C" "GRxWT.Df" "GRxWT.OE" "GR.CxDf"  "WT.CxDf" "GR.CxOE"  "WT.CxOE"
-
-FC.data = G85R.FC[,c("WTF.CxDf", "WTM.CxDf")]
-metab.data = setNames(G85R.metabFC[,"WT.CxDf"], G85R.metabFC$KEGG)
-out.id = "WT_ControlxDeficient_FandM_Genes with WT_ControlxDeficient_Metab"
-
+FC.data = G85R.FC[,c("GRF.CxOE", "WTF.CxOE")]
+metab.data = setNames(G85R.metabFC[,"GR.CxOE"], G85R.metabFC$KEGG)
 PathwayID = "00190"
@@
 ##File name
-
+out.id = "G85RandWT_CxOE_Genes with GR.CxOE_Metab"
 OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
@@
 
-  #knitr::include_graphics(img.file)
+  knitr::include_graphics(img.file)
 
@@
 
-```{r warning=F,  echo = F, include = F}
+```{r echo = F}
 
-##EdgeR Comparisons  = GRxWT.ML3 GR.LL3xML3 WT.LL3xML3 G85R_gbb.LL3xML3
+heatmaply(G85R.metabmean[c('nicotinamide', 'nicotinic acid', "NAD+", "NADH"),
+                         c('WT', 'TktDfWT', 'TktOEWT', 'GR', 'TktDfGR', 'TktOEGR')],
+          scale = 'row',
+          Colv = F,
+                 custom_hovertext = signif(G85R.metabmean[c('nicotinamide', 'nicotinic acid', "NAD+", "NADH"),
+                         c('WT', 'TktDfWT', 'TktOEWT', 'GR', 'TktDfGR', 'TktOEGR')], 3))
 
-FC.data = data.frame(FC1 = GR.LL3xML3[row.names(GRxWT.ML3), "logFC"],
-                     FC2 = G85R_gbb.LL3xML3[row.names(GRxWT.ML3), "logFC"])
-row.names(FC.data) = row.names(GRxWT.ML3)
+```
 
-out.id = "G85RandG85R.gbbOE_LL3xML3"
+```{r echo = F}
 
-PathwayID = "00190"
-sigs = row.names(FC.data)
+PPP = names(kegg[grep('00030', kegg)])
+PPP = row.names(GeneIDKey[GeneIDKey$Symbol %in% PPP, ])
 
-##File name
+geneset = PPP
 
-OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
+hmdata = A4V.meancpm[geneset,]
+row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
+A4V.order = c("S3FH", "S9FH", "S40FH", "A3FH", "A9FH", "A40FH",
+              "S3FT", "S9FT", "S40FT", "A3FT", "A9FT", "A40FT",
+              "S3FA", "S9FA", "S40FA", "A3FA", "A9FA", "A40FA",
+              "S3MH", "S9MH", "A3MH", "A9MH",
+              "S3MT", "S9MT", "A3MT", "A9MT",
+              "S3MA", "S9MA", "A3MA", "A9MA")
+
+hmdata = na.omit(hmdata[,A4V.order])
+
+heatmaply(hmdata,
+          scale = 'row',
+          Colv = F)
+
+```
+
+```{r echo = F}
+
+hmdata = G85R.meancpm[geneset,]
+row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
+order = c("WTFC", "WTFDf", "WTFOE",
+          "GRFC", "GRFDf", "GRFOE",
+          "WTMC", "WTMDf", "WTMOE",
+          "GRMC", "GRMDf", "GRMOE")
+
+hmdata = na.omit(hmdata[,order])
+
+heatmaply(hmdata,
+          scale = 'row',
+          Colv = F)
+
+```
+
+```{r warning=F,  echo = F}
+
+FC = G85R.FC[,c("GRxWT.FC", "GRxWT.MC")]
+metab.data = setNames(G85R.metabFC[,"GRxWT.C"], G85R.metabFC$KEGG)
+PathwayID = "00030"
+use = 'both'
+
+  ##File name prefix
+  out.id = paste("G85RvsWT_FemaleandMale")
+
+  ##table with the FC data you want to use for coloring with FBgn for row names 
+  ##if only analyzing 1 condition, use setNames to make a named vector
+  ##A4V.FC or G85R.FC
+
+  FC.data =  FC
+
+  ##all or a subset of row.names used in FC.data
+  usegenes = row.names(FC)
+
+  #Any column name from G85R.metabFC or 'none'
+  metab.data = metab.data
+
+  if(use == 'primary'){
+
+    ##File name prefix
+    out.id = comparison
+
+    ##table with the FC data you want to use for coloring with FBgn for row names 
+    ##if only analyzing 1 condition, use setNames to make a named vector
+    ##A4V.FC or G85R.FC
+
+    FC.data =  FC[,1]
+
+    #Any column name from G85R.metabFC or 'none'
+    metab.data = metab.data
+  }
+
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+  }
+  Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  OutputDir = paste0(Home, "/KEGG_Image_Files/")
   setwd(OutputDir)
-img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
+  sigs = usegenes
+  ##sigs = names(FDR.data[FDR.data <= .05])
 
+  if(class(FC.data)=="numeric"){
+    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
+  }
+
+  if(class(FC.data)=="data.frame"){
     deg.data = as.matrix(FC.data)
     row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
+  }
+
+  #if(length(G85R.metabFC[metab.id, names(metab.data)]) > 1 ){
+   # metab.data = setNames(log2(G85R.metabFC[metab.id, metab.data]), names(metab.id))
+  #}
 
   pv.out <- pathview(gene.data =  deg.data,
+                     cpd.data = metab.data,
                      pathway.id = PathwayID,
@@
                      match.data = F)
+  setwd(Home)
 
-  #knitr::include_graphics(img.file)
+  if(class(FC.data)=="numeric"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
+  }
+
+  if(class(FC.data)=="data.frame"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
+  }
+  knitr::include_graphics(img.file)
 
@@
 
-```{r warning=F,  echo = F, include = F}
+```{r warning=F,  echo = F}
 
-##EdgeR Comparisons  = KOxWT
+FC = G85R.FC[,c("GRF.CxDf", "WTF.CxDf")]
+metab.data = setNames(G85R.metabFC[,"GR.CxDf"], G85R.metabFC$KEGG)
+PathwayID = "00030"
+use = 'both'
 
-FC.data = setNames(KOxWT$logFC, row.names(KOxWT))
+  ##File name prefix
+  out.id = paste("G85RvsWT_FemaleandMale")
 
-out.id = "gbbKOxgbbWT"
+  ##table with the FC data you want to use for coloring with FBgn for row names 
+  ##if only analyzing 1 condition, use setNames to make a named vector
+  ##A4V.FC or G85R.FC
 
-PathwayID = "00190"
-sigs = names(FC.data)
+  FC.data =  FC
 
-##File name
+  ##all or a subset of row.names used in FC.data
+  usegenes = row.names(FC)
 
-OutputDir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R OXPHOS KEGG Pathways/"
+  #Any column name from G85R.metabFC or 'none'
+  metab.data = metab.data
+
+  if(use == 'primary'){
+
+    ##File name prefix
+    out.id = comparison
+
+    ##table with the FC data you want to use for coloring with FBgn for row names 
+    ##if only analyzing 1 condition, use setNames to make a named vector
+    ##A4V.FC or G85R.FC
+
+    FC.data =  FC[,1]
+
+    #Any column name from G85R.metabFC or 'none'
+    metab.data = metab.data
+  }
+
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+  }
+  Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  OutputDir = paste0(Home, "/KEGG_Image_Files/")
   setwd(OutputDir)
-img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
+  sigs = usegenes
+  ##sigs = names(FDR.data[FDR.data <= .05])
 
-    deg.data = as.vector(FC.data)
-    names(deg.data) = GeneIDKey[names(FC.data), "ensembl"]
+  if(class(FC.data)=="numeric"){
+    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
+  }
+
+  if(class(FC.data)=="data.frame"){
+    deg.data = as.matrix(FC.data)
+    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
+  }
+
+  #if(length(G85R.metabFC[metab.id, names(metab.data)]) > 1 ){
+   # metab.data = setNames(log2(G85R.metabFC[metab.id, metab.data]), names(metab.id))
+  #}
 
   pv.out <- pathview(gene.data =  deg.data,
+                     cpd.data = metab.data,
                      pathway.id = PathwayID,
@@
                      match.data = F)
+  setwd(Home)
 
-  #knitr::include_graphics(img.file)
+  if(class(FC.data)=="numeric"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
+  }
+
+  if(class(FC.data)=="data.frame"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
+  }
+  knitr::include_graphics(img.file)
 
 ```
+
+```{r warning=F,  echo = F}
+
+FC = G85R.FC[,c("GRF.CxOE", "WTF.CxOE")]
+metab.data = setNames(G85R.metabFC[,"GR.CxOE"], G85R.metabFC$KEGG)
+
+PathwayID = "00030"
+use = 'both'
+
+  ##File name prefix
+  out.id = paste("G85RvsWT_FemaleandMale")
+
+  ##table with the FC data you want to use for coloring with FBgn for row names 
+  ##if only analyzing 1 condition, use setNames to make a named vector
+  ##A4V.FC or G85R.FC
+
+  FC.data =  FC
+
+  ##all or a subset of row.names used in FC.data
+  usegenes = row.names(FC)
+
+  #Any column name from G85R.metabFC or 'none'
+  metab.data = metab.data
+
+  if(use == 'primary'){
+
+    ##File name prefix
+    out.id = comparison
+
+    ##table with the FC data you want to use for coloring with FBgn for row names 
+    ##if only analyzing 1 condition, use setNames to make a named vector
+    ##A4V.FC or G85R.FC
+
+    FC.data =  FC[,1]
+
+    #Any column name from G85R.metabFC or 'none'
+    metab.data = metab.data
+  }
+
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
+  }
+  Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  OutputDir = paste0(Home, "/KEGG_Image_Files/")
+  setwd(OutputDir)
+  sigs = usegenes
+  ##sigs = names(FDR.data[FDR.data <= .05])
+
+  if(class(FC.data)=="numeric"){
+    deg.data=setNames(FC.data[sigs],GeneIDKey[sigs, "ensembl"])
+  }
+
+  if(class(FC.data)=="data.frame"){
+    deg.data = as.matrix(FC.data)
+    row.names(deg.data) = GeneIDKey[row.names(FC.data), "ensembl"]
+  }
+
+  #if(length(G85R.metabFC[metab.id, names(metab.data)]) > 1 ){
+   # metab.data = setNames(log2(G85R.metabFC[metab.id, metab.data]), names(metab.id))
+  #}
+
+  pv.out <- pathview(gene.data =  deg.data,
+                     cpd.data = metab.data,
+                     pathway.id = PathwayID,
+                     species = "dme",
+                     kegg.native = T,
+                     limit=list(gene=c(-2,2)),
+                     node.sum="max.abs",
+                     low="royalblue",mid = "grey",high="firebrick",
+                     out.suffix = out.id,
+                     bins=list(genes=30),
+                     plot.col.key = T,
+                     match.data = F)
+  setwd(Home)
+
+  if(class(FC.data)=="numeric"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".png")
+  }
+
+  if(class(FC.data)=="data.frame"){
+    img.file = paste0(OutputDir, "dme",PathwayID, ".", out.id, ".multi.png")
+  }
+  knitr::include_graphics(img.file)
+
+```

### 2024-09-27 PunnettSquareApp.Rmd
Dina Folder Update

---
title: "Punnett Square"
author: "John Santiago"
date: "2024-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

##Genotypes
male.genotype = 'w/w;arc1/arc1;+/+'
female.genotype = 'elav-Gal4/Y;+/+;TM6c/UAS-lacz'

##allele or combination of alleles separated by commas
##eg c('x', 'CyO/CyO, 'x/y')
##cells meeting multiple criteria will be colored in order
allele1 = c('Y')
allele2 = c('arc1', 'UAS-lacz', 'elav-Gal4')
allele3 = 'CyO/CyO'
##color for each different allele set listed
color1 = 'lightblue'
color2 = 'gold'
color3 = 'black'

```

```{r echo = F}

library(DT)

male = strsplit(male.genotype, split = ";")[[1]]
male = strsplit(male, split = "/")

female = strsplit(female.genotype, split = ";")[[1]]
female = strsplit(female, split = "/")

nchroms = length(male)

chr1 = male[[1]]
chrdata = chr1
if(nchroms > 1){
  chr1 = c(chr1, chr1)
  chr2 = c(rep(male[[2]][1], 2), rep(male[[2]][2], 2))
  chr12 = paste(paste0(chr1, ";"),chr2)
  chrdata = data.frame(chr1 = chr1,
                       chr2 = chr2,
                       chr12 = chr12)
  if(nchroms > 2){
    chr1 = c(chr1, chr1)
    chr2 = c(chr2, chr2)
    chr12 = paste0(c(chr12, chr12), ";")
    chr3 = c(rep(male[[3]][1], 4), rep(male[[3]][2], 4))
    chr123 = paste(chr12, chr3)
    chrdata = data.frame(chr1 = chr1,
                         chr2 = chr2,
                         chr3 = chr3,
                         chr123 = chr123)
  }
}

male.chr = unique(chrdata)

chr1 = female[[1]]
chrdata = chr1
if(nchroms > 1){
  chr1 = c(chr1, chr1)
  chr2 = c(rep(female[[2]][1], 2), rep(female[[2]][2], 2))
  chr12 = paste(paste0(chr1, ";"),chr2)
  chrdata = data.frame(chr1 = chr1,
                       chr2 = chr2,
                       chr12 = chr12)
  if(nchroms > 2){
    chr1 = c(chr1, chr1)
    chr2 = c(chr2, chr2)
    chr12 = paste0(c(chr12, chr12), ";")
    chr3 = c(rep(female[[3]][1], 4), rep(female[[3]][2], 4))
    chr123 = paste(chr12, chr3)
    chrdata = data.frame(chr1 = chr1,
                         chr2 = chr2,
                         chr3 = chr3,
                         chr123 = chr123)
  }
}

female.chr = unique(chrdata)

ps = matrix("", nrow = nrow(female.chr), ncol = nrow(male.chr))
row.names(ps) = female.chr[, nchroms+1]
colnames(ps) = male.chr[, nchroms+1]
ps.print = ps
i=1
while(i <= ncol(ps)){
  temp.ps = paste0(female.chr[,1], "/", male.chr[i,1])
  if(nchroms > 1){
    temp.ps2 = paste0(female.chr[,2], "/", male.chr[i,2])
    temp.ps = paste0(temp.ps, ";", temp.ps2)
    temp.print = paste0(temp.ps, ";\n", temp.ps2)
  }
  if(nchroms > 2){
    temp.ps3 = paste0(female.chr[,3], "/", male.chr[i,3])
    temp.ps = paste0(temp.ps, ";", temp.ps3)
    temp.print = paste0(temp.ps3, ";\n", temp.ps3)
  }
  ps[,i] = temp.ps
  ps.print[,i] = temp.print
  i=i+1
}

allele.colors = ps
allele.colors[1:nrow(ps),] = ''

i = 1
while(i<=3){
  if(length(allele1)>1)){
    j=1
    temp = ps[grep(allele1[j], ps)]
    j=2
    while(j<=length(allele1)){
      temp = intersect(temp, ps[grep(allele1[j], ps)])
      j=j+1
    }
    if(length(temp) == 1){
      allele.colors[ps == temp] = color1
    }
    if(length(temp) > 1){
      j=1
      while(j <= length(temp)){
        allele.colors[ps == temp[j]] = color1
        j = j+1
      }
    }
  i=i+1
  }

write.csv(ps, "/Users/johncsantiago/Desktop/cross.csv")

```

```{r echo = F}

df = datatable(ps) %>% 
  formatStyle(1:ncol(ps), backgroundColor = styleEqual(ps, c(allele.colors)))

df
```

### 2024-09-27 RussoPaper/RussoClimbingPlots.Rmd
Dina Folder Update

@@
 date: "2024-03-29"
-output: pdf_document
+output: html_document
 ---
@@
 
+```{r include = F, echo = F, include = F}
+
+fig2ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 2AB.csv", header = T)
+fig2ab$Sample = paste(fig2ab$Genotype, paste(fig2ab$Sex, fig2ab$Day))
+
+mean.fig2 = rep(0, length(unique(fig2ab$Sample)))
+names(mean.fig2) = unique(fig2ab$Sample)
+var.fig2 = mean.fig2
+
+i=1
+while(i<=length(mean.fig2)){
+  mean.fig2[i] = mean(as.numeric(na.omit(fig2ab[fig2ab$Sample == names(mean.fig2)[i], 'Rate'])))
+
+    var.fig2[i] = var(as.numeric(na.omit(fig2ab[fig2ab$Sample == names(mean.fig2)[i], 'Rate'])))
+
+  i = i+1
+}
+
+eb = data.frame(sample = names(mean.fig2),
+                y0 = mean.fig2 - var.fig2,
+                y1 = mean.fig2 + var.fig2)
+
+```
+
+```{r echo = F, include = F}
+
+f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
+                  (fig2ab$Day == 3 |
+                  fig2ab$Day == 28 |
+                  fig2ab$Day == 35) &
+                  fig2ab$Genotype != 'w1118',]
+
+f.fig2ab = f.fig2ab[order(fig2ab$Day),]
+f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
+f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
+                                                     'dSodWT 28', 'A4V 28',
+                                                     'dSodWT 35', 'A4V 35'))
+f.fig2ab = na.omit(f.fig2ab)
+f.fig2ab$x = as.numeric(f.fig2ab$Sample)
+f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
+f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
+f.fig2ab$color = 'brown'
+f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
+f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
+f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
+f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 12)
+f.fig2ab$x.adj = c(0, -.15, .15, -.1, .1, 0,
+                   0, -.1, .1, -.1, .1, 0,
+
+                   -.15, .15, 0, 0, 0, 0,
+                   -.15, .15, 0, 0, 0, 0,
+
+                   -.15, .15, 0, -.15, .15, 0,
+                   -.15, .15, 0, -.15, .15, 0)
+
+f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity")
+points(x = f.fig2ab$x,
+       y = f.fig2ab$Rate,
+       pch = 21,
+       bg = f.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5),
+     labels = c(3, 28,35))
+
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('Silent', 'A4V'), 
+       fill = c('steelblue', 'brown'),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F, include = F}
+
+m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
+                  (fig2ab$Day == 3 |
+                  fig2ab$Day == 10 |
+                  fig2ab$Day == 16) &
+                  fig2ab$Genotype != 'w1118',]
+
+m.fig2ab = m.fig2ab[order(fig2ab$Day),]
+m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
+m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
+                                                     'dSodWT 10', 'A4V 10',
+                                                     'dSodWT 16', 'A4V 16'))
+m.fig2ab = na.omit(m.fig2ab)
+m.fig2ab$x = as.numeric(m.fig2ab$Sample)
+m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
+m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1
+m.fig2ab$color = 'brown'
+m.fig2ab$color[m.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
+
+m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
+m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
+m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 12)
+m.fig2ab$x.adj = c(0, -.25, 0, .25, .15, 0,
+                   0, -.25, 0, .25, -.15, .15,
+
+                   0, 0, 0, -.1, .1, 0,
+                   0, 0, -.1, .1, -.1, .1,
+
+                   0, 0, 0, 0, 0, 0,
+                   0, -.25, .25, 0, 0, 0)
+
+m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Male Climbing Velocity")
+points(x = m.fig2ab$x,
+       y = m.fig2ab$Rate,
+       pch = 21,
+       bg = m.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5),
+     labels = c(3, 10, 16))
+
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('Silent', 'A4V'), 
+       fill = c('steelblue', 'brown'),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F, include = F}
+
+f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
+                 (fig2ab$Day == 3 |
+                  fig2ab$Day == 14 |
+                  fig2ab$Day == 24 |
+                  fig2ab$Day == 35) &
+                  fig2ab$Genotype != 'w1118',]
+
+f.fig2ab = f.fig2ab[order(fig2ab$Day),]
+f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
+f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
+                                                     'dSodWT 14', 'A4V 14',
+                                                     'dSodWT 24', 'A4V 24',
+                                                     'dSodWT 35', 'A4V 35'))
+f.fig2ab = na.omit(f.fig2ab)
+f.fig2ab$x = as.numeric(f.fig2ab$Sample)
+f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
+f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
+f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
+f.fig2ab$color = 'brown'
+f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
+f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
+f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
+f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
+f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
+                   0, -.15, .15, -.15, .15, 0,
+
+                   0, 0, .2, -.2, 0, 0,
+                   -.15, .15, 0, 0, -.15, .15,
+
+                   0, 0, -.15, .15, 0, 0,
+                   0, .2, -.2, 0, -.15, .15,
+
+                   0, -.25, .25, -.15, .15, 0,
+                   -.25, .25, 0, -.25, .25, 0)
+
+f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8, 10,11),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity")
+points(x = f.fig2ab$x,
+       y = f.fig2ab$Rate,
+       pch = 21,
+       bg = f.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5, 10.5),
+     labels = c(3, 14, 24, 35))
+
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('Silent', 'A4V'), 
+       fill = c('steelblue', 'brown'),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F, fig.width=7.5}
+
+f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
+                 (fig2ab$Day == 3 |
+                  fig2ab$Day == 14 |
+                  fig2ab$Day == 20 |
+                  fig2ab$Day == 28 |
+                  fig2ab$Day == 35) &
+                  fig2ab$Genotype != 'w1118',]
+
+f.fig2ab = f.fig2ab[order(fig2ab$Day),]
+f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
+f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
+                                                     'dSodWT 14', 'A4V 14',
+                                                     'dSodWT 20', 'A4V 20',
+                                                     'dSodWT 28', 'A4V 28',
+                                                     'dSodWT 35', 'A4V 35'))
+f.fig2ab = na.omit(f.fig2ab)
+f.fig2ab$x = as.numeric(f.fig2ab$Sample)
+f.fig2ab$x[f.fig2ab$x > 8] = f.fig2ab$x[f.fig2ab$x > 8] + 1
+f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
+f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
+f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
+f.fig2ab$color = 'brown'
+f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
+f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
+f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
+f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 20)
+f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
+                   0, -.15, .15, -.15, .15, 0,
+
+                   0, 0, .2, -.2, 0, 0,
+                   -.15, .15, 0, 0, -.15, .15,
+
+                   0, 0, -.15, .15, 0, 0,
+                   0, 0, -.25, .25, 0, 0,
+
+                   0, -.25, .25, 0, 0, 0,
+                   -.15, .15, 0, 0, 0, 0,
+
+                   0, -.25, .25, -.15, .15, 0,
+                   -.25, .25, 0, -.25, .25, 0)
+
+f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8, 10,11, 13,14),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity")
+points(x = f.fig2ab$x,
+       y = f.fig2ab$Rate,
+       pch = 21,
+       bg = f.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5, 10.5, 13.5),
+     labels = c(3, 14, 20, 28, 35))
+
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('Silent', 'A4V'), 
+       fill = c('steelblue', 'brown'),
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F, fig.width=7.5}
+
+m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
+                 (fig2ab$Day == 3 |
+                  fig2ab$Day == 7 |
+                  fig2ab$Day == 12 |
+                  fig2ab$Day == 16) &
+                  fig2ab$Genotype != 'w1118',]
+
+m.fig2ab = m.fig2ab[order(fig2ab$Day),]
+m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
+m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
+                                                     'dSodWT 7', 'A4V 7',
+                                                     'dSodWT 12', 'A4V 12',
+                                                     'dSodWT 16', 'A4V 16'))
+m.fig2ab = na.omit(m.fig2ab)
+m.fig2ab$x = as.numeric(m.fig2ab$Sample)
+m.fig2ab$x[m.fig2ab$x > 6] = m.fig2ab$x[m.fig2ab$x > 6] + 1
+m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
+m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1
+m.fig2ab$color = 'brown'
+m.fig2ab$color[m.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
+
+m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
+m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
+m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
+m.fig2ab$x.adj = c(0, -.25, .25, 0, -.1, .1,
+                   0, -.25, .25, .0, -.1, .1,
+
+                   0, 0, -.1, .1, 0, 0,
+                   0, -.1, .1, 0, 0, 0,
+
+                   0, -.1, .1, 0, 0, 0,
+                   0, -.1, .1, 0, -.1, .1,
+
+                   0, -.25, 0, .25, .15, 0,
+                   0, -.25, 0, .25, -.15, .15)
+
+m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8, 10,11),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Male Climbing Velocity")
+points(x = m.fig2ab$x,
+       y = m.fig2ab$Rate,
+       pch = 21,
+       bg = m.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5, 10.5),
+     labels = c(3, 7, 12, 16))
+
+legend('topright',
+       inset=c(-0.175,0),
+       legend = c('Silent', 'A4V'), 
+       fill = c('steelblue', 'brown'),
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
 ```{r include = F, echo = F}
 
-fig4ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4AB Climbing Data ok371 cha gbb climbing cm_sec.csv", header = T)
+fig4ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4AB.csv", header = T)
 
@@
 fcha.mean = fcha.mean[order(fcha.mean$day),]
+
+m.con = na.omit(male[male$geno == 'silent' | male$geno == 'A4V',])
+m.cha = na.omit(male[grep('cha', male$geno),])
+
+mallcha = rbind(m.con, m.cha)
+mallcha$sample = paste0(mallcha$geno, mallcha$day)
+
+mcha.mean = unique(mallcha[,c('geno', 'day')])
+mcha.mean$sample = paste0(mcha.mean$geno, mcha.mean$day)
+mcha.mean$mean = 0
+
+i=1
+while(i<=nrow(mcha.mean)){
+  mcha.mean$mean[i] = mean(mallcha[mallcha$sample == mcha.mean$sample[i], 'corrected.values'])
+  i = i+1
+}
+
+mcha.mean = mcha.mean[order(mcha.mean$day),]
+
+```
+
+```{r echo = F, include = F}
+
+f.fig4a = fig4ab[grep('f', fig4ab$vial_ID),]
+f.fig4a = f.fig4a[f.fig4a$day == 6 |
+                  f.fig4a$day == 13 |
+                  #f.fig4a$day == 19 |
+                  f.fig4a$day == 27,]
+
+f.fig4a$Sample = paste(f.fig4a$geno, f.fig4a$day)
+f.fig4a$geno = factor(f.fig4a$geno, levels = c("silent", 'silentcha', 'silentok',
+                                               'A4V', 'A4Vcha', 'A4Vok'))
+
+f.fig4a = f.fig4a[order(f.fig4a$day),]
+f.fig4a = f.fig4a[order(f.fig4a$geno),]
+f.fig4a$Sample = factor(f.fig4a$Sample, levels = unique(f.fig4a$Sample))
+
+f.fig4a = na.omit(f.fig4a)
+f.fig4a$x = as.numeric(f.fig4a$Sample)
+f.fig4a$x[f.fig4a$x > 15] = f.fig4a$x[f.fig4a$x > 15] + 1
+f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
+f.fig4a$x[f.fig4a$x > 9] = f.fig4a$x[f.fig4a$x > 9] + 2
+f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
+f.fig4a$x[f.fig4a$x > 3] = f.fig4a$x[f.fig4a$x > 3] + 1
+#f.fig4a$x[f.fig4a$x > 18] = f.fig4a$x[f.fig4a$x > 18] + 1
+#f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
+#f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
+f.fig4a$color = 'steelblue'
+f.fig4a$color[f.fig4a$geno == 'A4V'] = 'navy'
+f.fig4a$color[f.fig4a$geno == 'silentcha'] = 'limegreen'
+f.fig4a$color[f.fig4a$geno == 'A4Vcha'] = 'darkgreen'
+f.fig4a$color[f.fig4a$geno == 'silentok'] = 'brown1'
+f.fig4a$color[f.fig4a$geno == 'A4Vok'] = 'firebrick'
+
+f.fig4a = f.fig4a[order(f.fig4a$corrected.values),]
+f.fig4a = f.fig4a[order(f.fig4a$Sample),]
+f.fig4a$x.adj = rep(c(-.25, .25 ,0), 36)
+
+f.fig4a$x = f.fig4a$x + f.fig4a$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig4a$corrected.values~f.fig4a$Sample,
+        ##at = c(1:6, 8:13, 15:20, 22:27),
+        at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity")
+points(x = f.fig4a$x,
+       y = f.fig4a$corrected.values,
+       pch = 21,
+       bg = f.fig4a$color,
+       cex = 1)
+axis(side = 1,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
+     labels = c(rep("", 18)),
+     cex.axis = .5,
+     line = 0)
+
+axis(side = 1,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
+     labels = c(rep(c(6, 13, 27), 6)),
+     cex.axis = .5,
+     tick = F,
+     line = -.5)
+
+axis(side = 3,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(6, 19),
+     labels = c('Silent', 'A4V'),
+     cex.axis = 1,
+     tick = F,
+     line = -.75)
+
+legend('topright',
+       inset=c(-0.225,0),
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V',
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'), 
+       fill = c('steelblue', 'limegreen', 'brown1',
+                'navy', 'darkgreen', 'firebrick'),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .75,
+       xpd = T)
+
+abline(v = 12.5, lty = 2, lwd =2)
+
+```
+
+```{r echo = F, include = F}
+
+f.fig4a = fig4ab[grep('f', fig4ab$vial_ID),]
+f.fig4a = f.fig4a[f.fig4a$day == 6 |
+                  f.fig4a$day == 13 |
+                  #f.fig4a$day == 19 |
+                  f.fig4a$day == 27,]
+
+f.fig4a$Sample = paste(f.fig4a$geno, f.fig4a$day)
+f.fig4a$geno = factor(f.fig4a$geno, levels = c("silent", 'A4V',
+                                               'silentcha', 'A4Vcha',
+                                               'silentok', 'A4Vok'))
+
+f.fig4a = f.fig4a[order(f.fig4a$day),]
+f.fig4a = f.fig4a[order(f.fig4a$geno),]
+f.fig4a$Sample = factor(f.fig4a$Sample, levels = unique(f.fig4a$Sample))
+
+f.fig4a = na.omit(f.fig4a)
+f.fig4a$x = as.numeric(f.fig4a$Sample)
+f.fig4a$x[f.fig4a$x > 15] = f.fig4a$x[f.fig4a$x > 15] + 1
+f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 2
+f.fig4a$x[f.fig4a$x > 9] = f.fig4a$x[f.fig4a$x > 9] + 1
+f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 2
+f.fig4a$x[f.fig4a$x > 3] = f.fig4a$x[f.fig4a$x > 3] + 1
+#f.fig4a$x[f.fig4a$x > 18] = f.fig4a$x[f.fig4a$x > 18] + 1
+#f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
+#f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
+f.fig4a$color = 'steelblue'
+f.fig4a$color[f.fig4a$geno == 'A4V'] = 'navy'
+f.fig4a$color[f.fig4a$geno == 'silentcha'] = 'limegreen'
+f.fig4a$color[f.fig4a$geno == 'A4Vcha'] = 'darkgreen'
+f.fig4a$color[f.fig4a$geno == 'silentok'] = 'brown1'
+f.fig4a$color[f.fig4a$geno == 'A4Vok'] = 'firebrick'
+
+f.fig4a = f.fig4a[order(f.fig4a$corrected.values),]
+f.fig4a = f.fig4a[order(f.fig4a$Sample),]
+f.fig4a$x.adj = rep(c(-.25, .25 ,0), 36)
+
+f.fig4a$x = f.fig4a$x + f.fig4a$x.adj
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig4a$corrected.values~f.fig4a$Sample,
+        ##at = c(1:6, 8:13, 15:20, 22:27),
+        at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
+        xaxt = 'none',
+        xlab = "Day",
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity")
+points(x = f.fig4a$x,
+       y = f.fig4a$corrected.values,
+       pch = 21,
+       bg = f.fig4a$color,
+       cex = 1)
+axis(side = 1,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
+     labels = c(rep("", 18)),
+     cex.axis = .5,
+     line = 0)
+
+axis(side = 1,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
+     labels = c(rep(c(6, 13, 27), 6)),
+     cex.axis = .75,
+     tick = F,
+     line = -.5)
+axis(side = 1,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(2, 6, 11, 15, 20, 24),
+     labels = c(rep(c('Silent', 'A4V'), 3)),
+     cex.axis = 1,
+     tick = F,
+     line = .5)
+
+axis(side = 3,
+     #at = c(3.5, 10.5, 17.5, 24.5),
+     at = c(4, 13, 22),
+     labels = c('Control', 'ChAT>gbb', 'OK371>gbb'),
+     cex.axis = 1,
+     tick = F,
+     line = -.75)
+
+legend('topright',
+       inset=c(-0.225,0),
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V',
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'), 
+       fill = c('steelblue', 'navy',
+                'limegreen', 'darkgreen',
+                'brown1', 'firebrick'),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .75,
+       xpd = T)
+
+abline(v = c(8.5, 17.5), lty = 2, lwd =2)
 
@@
 
-```{r echo = F}
+```{r echo = F, include = F}
 
@@
 
-```{r echo = F}
-
-norm.female = na.omit(female)
-norm.female$normval = 0
+```{r echo = F, include = F}
+
+male = fig4ab[grep('m', fig4ab$vial_ID),]
+male$sample = paste0(male$geno, male$day)
+
+mmean = unique(male[,c('geno', 'day', 'sample')])
+mstd = mmean
+eb = mmean
+mmean$mean = 0
+mstd$std = 0
+
 i=1
-while(i <= nrow(norm.female)){
-  norm.female$normval[i] = norm.female$corrected.values[i]/
-    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
-  i = i +1
-}
-
-norm.fmean = unique(norm.female[,c('geno', 'day', 'sample')])
-norm.fstd = norm.fmean
-norm.feb = norm.fmean
-norm.fmean$mean = 0
-norm.fstd$std = 0
-
-i=1
-while(i<=nrow(norm.fmean)){
-  norm.fmean$mean[i] = mean(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval']))
-
-  norm.fstd$std[i] = (var(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval'])))
+while(i<=nrow(mmean)){
+  mmean$mean[i] = mean(na.omit(male[male$sample == mmean$sample[i], 'corrected.values']))
+
+  mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))
 
@@
 
-norm.fmean = norm.fmean[order(norm.fmean$day),]
-norm.fstd = norm.fstd[order(norm.fstd$day),]
-norm.feb = norm.feb[order(norm.feb$day),]
-
-norm.feb$y0 = norm.fmean$mean - norm.fstd$std
-norm.feb$y1 = norm.fmean$mean + norm.fstd$std
-
-norm.flm = data.frame(geno = unique(norm.female$geno),
+mlm = data.frame(geno = unique(male$geno),
                 x0 = 2,
@@
 i=1
-while(i<=nrow(norm.flm)){
-  temp=na.omit(norm.female[norm.female$geno == norm.flm$geno[i], ])
+while(i<=nrow(mlm)){
+  temp=na.omit(male[male$geno == mlm$geno[i], ])
+  temp.lm = lm(temp$corrected.values~temp$day)
+  mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  i = i +1
+}
+
+row.names(mlm) = mlm$geno
+
+mmean = mmean[order(mmean$day),]
+mstd = mstd[order(mstd$day),]
+eb = eb[order(eb$day),]
+
+eb$y0 = mmean$mean - mstd$std
+eb$y1 = mmean$mean + mstd$std
+
+```
+
+```{r echo = F, fig.width=10}
+
+lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+hex = function(color, alpha){
+  rgbvals = col2rgb(color)
+  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+  return(rgb2hex)
+}
+
+par(mar=c(5.1, 4.1, 4.1, 15.1))
+
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(0, max(c(fmean$mean, mmean$mean))),
+     xlim = c(2,27),
+     ylab = 'Mean Velocity (cm/s)',
+     xlab = 'Day',
+     xaxt = 'n',
+     main = "Females")
+
+axis(1, at = fmean[fmean$geno == 'silent', 'day'])
+
+lines(x = fmean[fmean$geno == 'silent', 'day'],
+      y = fmean[fmean$geno == 'silent', 'mean'],
+      type = 'l',
+      col = lcol[1],
+      lwd = 2)
+
+lines(x = fmean[fmean$geno == 'A4V', 'day'],
+      y = fmean[fmean$geno == 'A4V', 'mean'],
+      type = 'l',
+      col = pcol[2],
+      lwd = 2)
+
+lines(x = fmean[fmean$geno == 'silentcha', 'day'],
+      y = fmean[fmean$geno == 'silentcha', 'mean'],
+      type = 'l',
+      col = pcol[3],
+      lwd = 2)
+
+lines(x = fmean[fmean$geno == 'A4Vcha', 'day'],
+      y = fmean[fmean$geno == 'A4Vcha', 'mean'],
+      type = 'l',
+      col = pcol[4],
+      lwd = 2)
+
+lines(x = fmean[fmean$geno == 'silentok', 'day'],
+      y = fmean[fmean$geno == 'silentok', 'mean'],
+      type = 'l',
+      col = pcol[5],
+      lwd = 2)
+
+lines(x = fmean[fmean$geno == 'A4Vok', 'day'],
+      y = fmean[fmean$geno == 'A4Vok', 'mean'],
+      type = 'l',
+      col = pcol[6],
+      lwd = 2)
+
+points(x = fmean[fmean$geno == 'silent', 'day'],
+       y = fmean[fmean$geno == 'silent', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean[fmean$geno == 'A4V', 'day'],
+       y = fmean[fmean$geno == 'A4V', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = fmean[fmean$geno == 'silentcha', 'day'],
+       y = fmean[fmean$geno == 'silentcha', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean[fmean$geno == 'A4Vcha', 'day'],
+       y = fmean[fmean$geno == 'A4Vcha', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = fmean[fmean$geno == 'silentok', 'day'],
+       y = fmean[fmean$geno == 'silentok', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean[fmean$geno == 'A4Vok', 'day'],
+       y = fmean[fmean$geno == 'A4Vok', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+
+points(x = fmean[fmean$geno == 'silent', 'day'],
+       y = fmean[fmean$geno == 'silent', 'mean'],
+       bg = hex(pcol[1], .5),
+       col = pcol[1],
+       pch = 23,
+       cex =2)
+
+points(x = fmean[fmean$geno == 'A4V', 'day'],
+       y = fmean[fmean$geno == 'A4V', 'mean'],
+       bg = hex(pcol[2], .5),
+       col = pcol[2],
+       pch = 21,
+       cex =2)
+points(x = fmean[fmean$geno == 'silentcha', 'day'],
+       y = fmean[fmean$geno == 'silentcha', 'mean'],
+       bg = hex(pcol[3], .5),
+       col = pcol[3],
+       pch = 23,
+       cex =2)
+points(x = fmean[fmean$geno == 'A4Vcha', 'day'],
+       y = fmean[fmean$geno == 'A4Vcha', 'mean'],
+       bg = hex(pcol[4], .5),
+       col = pcol[4],
+       pch = 21,
+       cex =2)
+points(x = fmean[fmean$geno == 'silentok', 'day'],
+       y = fmean[fmean$geno == 'silentok', 'mean'],
+       bg = hex(pcol[5], .5),
+       col = pcol[5],
+       pch = 23,
+       cex =2)
+points(x = fmean[fmean$geno == 'A4Vok', 'day'],
+       y = fmean[fmean$geno == 'A4Vok', 'mean'],
+       bg = hex(pcol[6], .5),
+       col = pcol[6],
+       pch = 21,
+       cex =2)
+
+legend(x = 29,
+       y = 1.8,
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
+       pch = c(23,21,23,21,23,21),
+       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
+                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
+       bty = 'n',
+       y.intersp = 1,
+       pt.cex = 2,
+       xpd=TRUE)
+
+```
+
+```{r echo = F, fig.width=10}
+
+lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+hex = function(color, alpha){
+  rgbvals = col2rgb(color)
+  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+  return(rgb2hex)
+}
+
+par(mar=c(5.1, 4.1, 4.1, 15.1))
+
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(0, max(c(fmean$mean, mmean$mean))),
+     xlim = c(2,27),
+     ylab = 'Mean Velocity (cm/s)',
+     xlab = 'Day',
+     xaxt = 'n',
+     main = "Males")
+
+axis(1, at = mmean[mmean$geno == 'silent', 'day'])
+
+lines(x = mmean[mmean$geno == 'silent', 'day'],
+      y = mmean[mmean$geno == 'silent', 'mean'],
+      type = 'l',
+      col = lcol[1],
+      lwd = 2)
+
+lines(x = mmean[mmean$geno == 'A4V', 'day'],
+      y = mmean[mmean$geno == 'A4V', 'mean'],
+      type = 'l',
+      col = pcol[2],
+      lwd = 2)
+
+lines(x = mmean[mmean$geno == 'silentcha', 'day'],
+      y = mmean[mmean$geno == 'silentcha', 'mean'],
+      type = 'l',
+      col = pcol[3],
+      lwd = 2)
+
+lines(x = mmean[mmean$geno == 'A4Vcha', 'day'],
+      y = mmean[mmean$geno == 'A4Vcha', 'mean'],
+      type = 'l',
+      col = pcol[4],
+      lwd = 2)
+
+lines(x = mmean[mmean$geno == 'silentok', 'day'],
+      y = mmean[mmean$geno == 'silentok', 'mean'],
+      type = 'l',
+      col = pcol[5],
+      lwd = 2)
+
+lines(x = mmean[mmean$geno == 'A4Vok', 'day'],
+      y = mmean[mmean$geno == 'A4Vok', 'mean'],
+      type = 'l',
+      col = pcol[6],
+      lwd = 2)
+
+points(x = mmean[mmean$geno == 'silent', 'day'],
+       y = mmean[mmean$geno == 'silent', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean[mmean$geno == 'A4V', 'day'],
+       y = mmean[mmean$geno == 'A4V', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = mmean[mmean$geno == 'silentcha', 'day'],
+       y = mmean[mmean$geno == 'silentcha', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean[mmean$geno == 'A4Vcha', 'day'],
+       y = mmean[mmean$geno == 'A4Vcha', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = mmean[mmean$geno == 'silentok', 'day'],
+       y = mmean[mmean$geno == 'silentok', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean[mmean$geno == 'A4Vok', 'day'],
+       y = mmean[mmean$geno == 'A4Vok', 'mean'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+
+points(x = mmean[mmean$geno == 'silent', 'day'],
+       y = mmean[mmean$geno == 'silent', 'mean'],
+       bg = hex(pcol[1], .5),
+       col = pcol[1],
+       pch = 23,
+       cex =2)
+
+points(x = mmean[mmean$geno == 'A4V', 'day'],
+       y = mmean[mmean$geno == 'A4V', 'mean'],
+       bg = hex(pcol[2], .5),
+       col = pcol[2],
+       pch = 21,
+       cex =2)
+points(x = mmean[mmean$geno == 'silentcha', 'day'],
+       y = mmean[mmean$geno == 'silentcha', 'mean'],
+       bg = hex(pcol[3], .5),
+       col = pcol[3],
+       pch = 23,
+       cex =2)
+points(x = mmean[mmean$geno == 'A4Vcha', 'day'],
+       y = mmean[mmean$geno == 'A4Vcha', 'mean'],
+       bg = hex(pcol[4], .5),
+       col = pcol[4],
+       pch = 21,
+       cex =2)
+points(x = mmean[mmean$geno == 'silentok', 'day'],
+       y = mmean[mmean$geno == 'silentok', 'mean'],
+       bg = hex(pcol[5], .5),
+       col = pcol[5],
+       pch = 23,
+       cex =2)
+points(x = mmean[mmean$geno == 'A4Vok', 'day'],
+       y = mmean[mmean$geno == 'A4Vok', 'mean'],
+       bg = hex(pcol[6], .5),
+       col = pcol[6],
+       pch = 21,
+       cex =2)
+
+legend(x = 29,
+       y = 1.8,
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
+       pch = c(23,21,23,21,23,21),
+       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
+                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
+       bty = 'n',
+       y.intersp = 1,
+       pt.cex = 2,
+       xpd=TRUE)
+
+```
+
+```{r echo = F, fig.width=10}
+
+lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+hex = function(color, alpha){
+  rgbvals = col2rgb(color)
+  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+  return(rgb2hex)
+}
+
+fmean.percent = fmean
+fmean.percent$percent = 0
+
+fmean.percent = fmean.percent[fmean.percent$day != 2, ]
+
+fmean.percent[fmean.percent$geno == 'silent', 'percent'] = fmean.percent[fmean.percent$geno == 'silent', 'mean']/fmean.percent[fmean.percent$geno == 'silent' & fmean.percent$day == 6, 'mean']
+
+fmean.percent[fmean.percent$geno == 'A4V', 'percent'] = fmean.percent[fmean.percent$geno == 'A4V', 'mean']/fmean.percent[fmean.percent$geno == 'A4V' & fmean.percent$day == 6, 'mean']
+
+fmean.percent[fmean.percent$geno == 'silentok', 'percent'] = fmean.percent[fmean.percent$geno == 'silentok', 'mean']/fmean.percent[fmean.percent$geno == 'silentok' & fmean.percent$day == 6, 'mean']
+
+fmean.percent[fmean.percent$geno == 'A4Vok', 'percent'] = fmean.percent[fmean.percent$geno == 'A4Vok', 'mean']/fmean.percent[fmean.percent$geno == 'A4Vok' & fmean.percent$day == 6, 'mean']
+
+fmean.percent[fmean.percent$geno == 'A4Vcha', 'percent'] = fmean.percent[fmean.percent$geno == 'A4Vcha', 'mean']/fmean.percent[fmean.percent$geno == 'A4Vcha' & fmean.percent$day == 6, 'mean']
+
+fmean.percent[fmean.percent$geno == 'silentcha', 'percent'] = fmean.percent[fmean.percent$geno == 'silentcha', 'mean']/fmean.percent[fmean.percent$geno == 'silentcha' & fmean.percent$day == 6, 'mean']
+
+par(mar=c(5.1, 4.1, 4.1, 15.1))
+
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(0, 1.25),
+     xlim = c(6,27),
+     ylab = 'Percent of Initial Mean Velocity',
+     xlab = 'Day',
+     xaxt = 'n',
+     main = "Females")
+
+axis(1, at = fmean.percent[fmean.percent$geno == 'silent', 'day'])
+
+lines(x = fmean.percent[fmean.percent$geno == 'silent', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'silent', 'percent'],
+      type = 'l',
+      col = lcol[1],
+      lwd = 2)
+
+lines(x = fmean.percent[fmean.percent$geno == 'A4V', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'A4V', 'percent'],
+      type = 'l',
+      col = pcol[2],
+      lwd = 2)
+
+lines(x = fmean.percent[fmean.percent$geno == 'silentcha', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'silentcha', 'percent'],
+      type = 'l',
+      col = pcol[3],
+      lwd = 2)
+
+lines(x = fmean.percent[fmean.percent$geno == 'A4Vcha', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'A4Vcha', 'percent'],
+      type = 'l',
+      col = pcol[4],
+      lwd = 2)
+
+lines(x = fmean.percent[fmean.percent$geno == 'silentok', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'silentok', 'percent'],
+      type = 'l',
+      col = pcol[5],
+      lwd = 2)
+
+lines(x = fmean.percent[fmean.percent$geno == 'A4Vok', 'day'],
+      y = fmean.percent[fmean.percent$geno == 'A4Vok', 'percent'],
+      type = 'l',
+      col = pcol[6],
+      lwd = 2)
+
+points(x = fmean.percent[fmean.percent$geno == 'silent', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silent', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'A4V', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4V', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'silentcha', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silentcha', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'A4Vcha', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4Vcha', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'silentok', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silentok', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'A4Vok', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4Vok', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+
+points(x = fmean.percent[fmean.percent$geno == 'silent', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silent', 'percent'],
+       bg = hex(pcol[1], .5),
+       col = pcol[1],
+       pch = 23,
+       cex =2)
+
+points(x = fmean.percent[fmean.percent$geno == 'A4V', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4V', 'percent'],
+       bg = hex(pcol[2], .5),
+       col = pcol[2],
+       pch = 21,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'silentcha', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silentcha', 'percent'],
+       bg = hex(pcol[3], .5),
+       col = pcol[3],
+       pch = 23,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'A4Vcha', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4Vcha', 'percent'],
+       bg = hex(pcol[4], .5),
+       col = pcol[4],
+       pch = 21,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'silentok', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'silentok', 'percent'],
+       bg = hex(pcol[5], .5),
+       col = pcol[5],
+       pch = 23,
+       cex =2)
+points(x = fmean.percent[fmean.percent$geno == 'A4Vok', 'day'],
+       y = fmean.percent[fmean.percent$geno == 'A4Vok', 'percent'],
+       bg = hex(pcol[6], .5),
+       col = pcol[6],
+       pch = 21,
+       cex =2)
+
+legend(x = 29,
+       y = 1,
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
+       pch = c(23,21,23,21,23,21),
+       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
+                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
+       bty = 'n',
+       y.intersp = 1,
+       pt.cex = 2,
+       xpd=TRUE)
+
+```
+
+```{r echo = F, fig.width=10}
+
+lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
+hex = function(color, alpha){
+  rgbvals = col2rgb(color)
+  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+  return(rgb2hex)
+}
+
+mmean.percent = mmean
+mmean.percent$percent = 0
+
+mmean.percent[mmean.percent$geno == 'silent', 'percent'] = mmean.percent[mmean.percent$geno == 'silent', 'mean']/mmean.percent[mmean.percent$geno == 'silent' & mmean.percent$day == 2, 'mean']
+
+mmean.percent[mmean.percent$geno == 'A4V', 'percent'] = mmean.percent[mmean.percent$geno == 'A4V', 'mean']/mmean.percent[mmean.percent$geno == 'A4V' & mmean.percent$day == 2, 'mean']
+
+mmean.percent[mmean.percent$geno == 'silentok', 'percent'] = mmean.percent[mmean.percent$geno == 'silentok', 'mean']/mmean.percent[mmean.percent$geno == 'silentok' & mmean.percent$day == 2, 'mean']
+
+mmean.percent[mmean.percent$geno == 'A4Vok', 'percent'] = mmean.percent[mmean.percent$geno == 'A4Vok', 'mean']/mmean.percent[mmean.percent$geno == 'A4Vok' & mmean.percent$day == 2, 'mean']
+
+mmean.percent[mmean.percent$geno == 'A4Vcha', 'percent'] = mmean.percent[mmean.percent$geno == 'A4Vcha', 'mean']/mmean.percent[mmean.percent$geno == 'A4Vcha' & mmean.percent$day == 2, 'mean']
+
+mmean.percent[mmean.percent$geno == 'silentcha', 'percent'] = mmean.percent[mmean.percent$geno == 'silentcha', 'mean']/mmean.percent[mmean.percent$geno == 'silentcha' & mmean.percent$day == 2, 'mean']
+
+par(mar=c(5.1, 4.1, 4.1, 15.1))
+
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(0, 1.25),
+     xlim = c(2,27),
+     ylab = 'Percent of Initial Mean Velocity',
+     xlab = 'Day',
+     xaxt = 'n',
+     main = "Males")
+
+axis(1, at = mmean.percent[mmean.percent$geno == 'silent', 'day'])
+
+lines(x = mmean.percent[mmean.percent$geno == 'silent', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'silent', 'percent'],
+      type = 'l',
+      col = lcol[1],
+      lwd = 2)
+
+lines(x = mmean.percent[mmean.percent$geno == 'A4V', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'A4V', 'percent'],
+      type = 'l',
+      col = pcol[2],
+      lwd = 2)
+
+lines(x = mmean.percent[mmean.percent$geno == 'silentcha', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'silentcha', 'percent'],
+      type = 'l',
+      col = pcol[3],
+      lwd = 2)
+
+lines(x = mmean.percent[mmean.percent$geno == 'A4Vcha', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'A4Vcha', 'percent'],
+      type = 'l',
+      col = pcol[4],
+      lwd = 2)
+
+lines(x = mmean.percent[mmean.percent$geno == 'silentok', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'silentok', 'percent'],
+      type = 'l',
+      col = pcol[5],
+      lwd = 2)
+
+lines(x = mmean.percent[mmean.percent$geno == 'A4Vok', 'day'],
+      y = mmean.percent[mmean.percent$geno == 'A4Vok', 'percent'],
+      type = 'l',
+      col = pcol[6],
+      lwd = 2)
+
+points(x = mmean.percent[mmean.percent$geno == 'silent', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silent', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'A4V', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4V', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'silentcha', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silentcha', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'A4Vcha', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4Vcha', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'silentok', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silentok', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 23,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'A4Vok', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4Vok', 'percent'],
+       bg = 'white',
+       col = 'white',
+       pch = 21,
+       cex =2)
+
+points(x = mmean.percent[mmean.percent$geno == 'silent', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silent', 'percent'],
+       bg = hex(pcol[1], .5),
+       col = pcol[1],
+       pch = 23,
+       cex =2)
+
+points(x = mmean.percent[mmean.percent$geno == 'A4V', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4V', 'percent'],
+       bg = hex(pcol[2], .5),
+       col = pcol[2],
+       pch = 21,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'silentcha', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silentcha', 'percent'],
+       bg = hex(pcol[3], .5),
+       col = pcol[3],
+       pch = 23,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'A4Vcha', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4Vcha', 'percent'],
+       bg = hex(pcol[4], .5),
+       col = pcol[4],
+       pch = 21,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'silentok', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'silentok', 'percent'],
+       bg = hex(pcol[5], .5),
+       col = pcol[5],
+       pch = 23,
+       cex =2)
+points(x = mmean.percent[mmean.percent$geno == 'A4Vok', 'day'],
+       y = mmean.percent[mmean.percent$geno == 'A4Vok', 'percent'],
+       bg = hex(pcol[6], .5),
+       col = pcol[6],
+       pch = 21,
+       cex =2)
+
+legend(x = 29,
+       y = 1,
+       legend = c('Silent', 'A4V',
+                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
+                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
+       pch = c(23,21,23,21,23,21),
+       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
+                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
+       bty = 'n',
+       y.intersp = 1,
+       pt.cex = 2,
+       xpd=TRUE)
+
+```
+
+```{r echo = F, include = F}
+
+norm.male = na.omit(male)
+norm.male$normval = 0
+i=1
+while(i <= nrow(norm.male)){
+  norm.male$normval[i] = norm.male$corrected.values[i]/
+    mmean$mean[mmean$geno == 'silent' & mmean$day == norm.male$day[i]]
+  i = i +1
+}
+
+norm.mmean = unique(norm.male[,c('geno', 'day', 'sample')])
+norm.mstd = norm.mmean
+norm.meb = norm.mmean
+norm.mmean$mean = 0
+norm.mstd$std = 0
+
+i=1
+while(i<=nrow(norm.mmean)){
+  norm.mmean$mean[i] = mean(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval']))
+
+  norm.mstd$std[i] = (var(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval'])))
+
+  i = i+1
+}
+
+norm.mmean = norm.mmean[order(norm.mmean$day),]
+norm.mstd = norm.mstd[order(norm.mstd$day),]
+norm.meb = norm.meb[order(norm.meb$day),]
+
+norm.meb$y0 = norm.mmean$mean - norm.mstd$std
+norm.meb$y1 = norm.mmean$mean + norm.mstd$std
+
+norm.mlm = data.frame(geno = unique(norm.male$geno),
+                x0 = 2,
+                x1 = 27,
+                y0 = 0,
+                y1 = 0)
+
+i=1
+while(i<=nrow(norm.mlm)){
+  temp=na.omit(norm.male[norm.male$geno == norm.mlm$geno[i], ])
   temp.lm = lm(temp$normval~temp$day)
-  norm.flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
-  norm.flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  norm.mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  norm.mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
   i = i +1
@@
 
-row.names(norm.flm) = norm.flm$geno
+row.names(norm.mlm) = norm.mlm$geno
 
@@
 
-```{r echo = F, fig.height=10}
-
-silent = norm.fmean[norm.fmean$geno == "silent", ]
-a4v = norm.fmean[norm.fmean$geno == "A4V", ]
-silentcha = norm.fmean[norm.fmean$geno == "silentcha", ]
-a4vcha = norm.fmean[norm.fmean$geno == "A4Vcha", ]
-silentok = norm.fmean[norm.fmean$geno == "silentok", ]
-a4vok = norm.fmean[norm.fmean$geno == "A4Vok", ]
-
-ls = norm.fmean[norm.fmean$geno == 'silent',]
-la = norm.fmean[norm.fmean$geno == 'A4V',]
-lsc = norm.fmean[norm.fmean$geno == 'silentcha',]
-lac = norm.fmean[norm.fmean$geno == 'A4Vcha',]
-lso = norm.fmean[norm.fmean$geno == 'silentok',]
-lao = norm.fmean[norm.fmean$geno == 'A4Vok',]
+```{r echo = F, include = F}
+
+male$sample = paste0(male$geno, male$day)
+
+norm.male = na.omit(male)
+norm.male$normval = 0
+
+mmean = unique(male[,c('geno', 'day', 'sample')])
+mstd = mmean
+eb = mmean
+mmean$mean = 0
+mstd$std = 0
+
+i=1
+while(i<=nrow(mmean)){
+  mmean$mean[i] = mean(na.omit(male[male$sample == mmean$sample[i], 'corrected.values']))
+
+  mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))
+
+  i = i+1
+}
+
+mlm = data.frame(geno = unique(male$geno),
+                x0 = 2,
+                x1 = 27,
+                y0 = 0,
+                y1 = 0)
+
+i=1
+while(i<=nrow(mlm)){
+  temp=na.omit(male[male$geno == mlm$geno[i], ])
+  temp.lm = lm(temp$corrected.values~temp$day)
+  mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  i = i +1
+}
+
+row.names(mlm) = mlm$geno
+
+mmean = mmean[order(mmean$day),]
+mstd = mstd[order(mstd$day),]
+eb = eb[order(eb$day),]
+
+eb$y0 = mmean$mean - mstd$std
+eb$y1 = mmean$mean + mstd$std
+
+i=1
+while(i <= nrow(norm.male)){
+  norm.male$normval[i] = norm.male$corrected.values[i]/
+    mmean$mean[mmean$geno == 'silent' & mmean$day == norm.male$day[i]]
+  i = i +1
+}
+
+norm.mmean = unique(norm.male[,c('geno', 'day', 'sample')])
+norm.mstd = norm.mmean
+norm.eb = norm.mmean
+norm.mmean$mean = 0
+norm.mstd$std = 0
+
+i=1
+while(i<=nrow(norm.mmean)){
+  norm.mmean$mean[i] = mean(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval']))
+
+  norm.mstd$std[i] = (var(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval'])))
+
+  i = i+1
+}
+
+norm.mmean = norm.mmean[order(norm.mmean$day),]
+norm.mstd = norm.mstd[order(norm.mstd$day),]
+norm.eb = norm.eb[order(norm.eb$day),]
+
+norm.eb$y0 = norm.mmean$mean - norm.mstd$std
+norm.eb$y1 = norm.mmean$mean + norm.mstd$std
+
+norm.mlm = data.frame(geno = unique(norm.male$geno),
+                x0 = 2,
+                x1 = 27,
+                y0 = 0,
+                y1 = 0)
+
+i=1
+while(i<=nrow(norm.mlm)){
+  temp=na.omit(norm.male[norm.male$geno == norm.mlm$geno[i], ])
+  temp.lm = lm(temp$normval~temp$day)
+  norm.mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  norm.mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  i = i +1
+}
+
+row.names(norm.mlm) = norm.mlm$geno
+
+```
+
+```{r echo = F, fig.height=10, include = F}
+
+silent = norm.mmean[norm.mmean$geno == "silent", ]
+a4v = norm.mmean[norm.mmean$geno == "A4V", ]
+silentcha = norm.mmean[norm.mmean$geno == "silentcha", ]
+a4vcha = norm.mmean[norm.mmean$geno == "A4Vcha", ]
+silentok = norm.mmean[norm.mmean$geno == "silentok", ]
+a4vok = norm.mmean[norm.mmean$geno == "A4Vok", ]
+
+ls = norm.mmean[norm.mmean$geno == 'silent',]
+la = norm.mmean[norm.mmean$geno == 'A4V',]
+lsc = norm.mmean[norm.mmean$geno == 'silentcha',]
+lac = norm.mmean[norm.mmean$geno == 'A4Vcha',]
+lso = norm.mmean[norm.mmean$geno == 'silentok',]
+lao = norm.mmean[norm.mmean$geno == 'A4Vok',]
 
@@
      xaxt = 'n',
-     main = "Females")
+     main = "Males")
 
@@
 
-lines(x = norm.flm['silent', c("x0", "x1")],
-      y = norm.flm['silent', c("y0", "y1")],
+lines(x = norm.mlm['silent', c("x0", "x1")],
+      y = norm.mlm['silent', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.flm['A4V', c("x0", "x1")],
-      y = norm.flm['A4V', c("y0", "y1")],
+lines(x = norm.mlm['A4V', c("x0", "x1")],
+      y = norm.mlm['A4V', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.flm['silentcha', c("x0", "x1")],
-      y = norm.flm['silentcha', c("y0", "y1")],
+lines(x = norm.mlm['silentcha', c("x0", "x1")],
+      y = norm.mlm['silentcha', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.flm['A4Vcha', c("x0", "x1")],
-      y = norm.flm['A4Vcha', c("y0", "y1")],
+lines(x = norm.mlm['A4Vcha', c("x0", "x1")],
+      y = norm.mlm['A4Vcha', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.flm['silentok', c("x0", "x1")],
-      y = norm.flm['silentok', c("y0", "y1")],
+lines(x = norm.mlm['silentok', c("x0", "x1")],
+      y = norm.mlm['silentok', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.flm['A4Vok', c("x0", "x1")],
-      y = norm.flm['A4Vok', c("y0", "y1")],
+lines(x = norm.mlm['A4Vok', c("x0", "x1")],
+      y = norm.mlm['A4Vok', c("y0", "y1")],
       type = 'l',
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'silent'],
-       x1 = norm.feb$day[norm.feb$geno == 'silent'],
-       y0 = norm.feb$y0[norm.feb$geno == 'silent'],
-       y1 = norm.feb$y1[norm.feb$geno == 'silent'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'silent'],
+       x1 = norm.eb$day[norm.eb$geno == 'silent'],
+       y0 = norm.eb$y0[norm.eb$geno == 'silent'],
+       y1 = norm.eb$y1[norm.eb$geno == 'silent'], 
        code = 3, 
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'A4V'],
-       x1 = norm.feb$day[norm.feb$geno == 'A4V'],
-       y0 = norm.feb$y0[norm.feb$geno == 'A4V'],
-       y1 = norm.feb$y1[norm.feb$geno == 'A4V'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'A4V'],
+       x1 = norm.eb$day[norm.eb$geno == 'A4V'],
+       y0 = norm.eb$y0[norm.eb$geno == 'A4V'],
+       y1 = norm.eb$y1[norm.eb$geno == 'A4V'], 
        code = 3, 
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'silentcha'],
-       x1 = norm.feb$day[norm.feb$geno == 'silentcha'],
-       y0 = norm.feb$y0[norm.feb$geno == 'silentcha'],
-       y1 = norm.feb$y1[norm.feb$geno == 'silentcha'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'silentcha'],
+       x1 = norm.eb$day[norm.eb$geno == 'silentcha'],
+       y0 = norm.eb$y0[norm.eb$geno == 'silentcha'],
+       y1 = norm.eb$y1[norm.eb$geno == 'silentcha'], 
        code = 3, 
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
-       x1 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
-       y0 = norm.feb$y0[norm.feb$geno == 'A4Vcha'],
-       y1 = norm.feb$y1[norm.feb$geno == 'A4Vcha'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
+       x1 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
+       y0 = norm.eb$y0[norm.eb$geno == 'A4Vcha'],
+       y1 = norm.eb$y1[norm.eb$geno == 'A4Vcha'], 
        code = 3, 
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'silentok'],
-       x1 = norm.feb$day[norm.feb$geno == 'silentok'],
-       y0 = norm.feb$y0[norm.feb$geno == 'silentok'],
-       y1 = norm.feb$y1[norm.feb$geno == 'silentok'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'silentok'],
+       x1 = norm.eb$day[norm.eb$geno == 'silentok'],
+       y0 = norm.eb$y0[norm.eb$geno == 'silentok'],
+       y1 = norm.eb$y1[norm.eb$geno == 'silentok'], 
        code = 3, 
@@
 
-arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vok'],
-       x1 = norm.feb$day[norm.feb$geno == 'A4Vok'],
-       y0 = norm.feb$y0[norm.feb$geno == 'A4Vok'],
-       y1 = norm.feb$y1[norm.feb$geno == 'A4Vok'], 
+arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vok'],
+       x1 = norm.eb$day[norm.eb$geno == 'A4Vok'],
+       y0 = norm.eb$y0[norm.eb$geno == 'A4Vok'],
+       y1 = norm.eb$y1[norm.eb$geno == 'A4Vok'], 
        code = 3, 
@@
 
-```{r echo = F}
-
+```{r  echo = F, include = F}
+
+fig4cd = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4CD.csv", header = T)
+
+fig4cd = fig4cd[fig4cd$day != 9,]
+fig4cd = fig4cd[fig4cd$day != 32,]
+
+female = fig4cd[grep('f', fig4cd$vial_ID),]
+male = fig4cd[grep('m', fig4cd$vial_ID),]
+
+female$sample = paste0(female$geno, female$day)
 male$sample = paste0(male$geno, male$day)
+
+norm.female = na.omit(female)
+norm.female$normval = 0
+
+fmean = unique(female[,c('geno', 'day', 'sample')])
+fstd = fmean
+feb = fmean
+fmean$mean = 0
+fstd$std = 0
 
@@
 mstd = mmean
-eb = mmean
+meb = mmean
 mmean$mean = 0
@@
   mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))
+
+  i = i+1
+}
+
+i=1
+while(i<=nrow(fmean)){
+  fmean$mean[i] = mean(na.omit(female[female$sample == fmean$sample[i], 'corrected.values']))
+
+  fstd$std[i] = (var(na.omit(female[female$sample == fmean$sample[i], 'corrected.values'])))
 
@@
 
+flm = data.frame(geno = unique(female$geno),
+                x0 = 2,
+                x1 = 27,
+                y0 = 0,
+                y1 = 0)
+
+i=1
+while(i<=nrow(flm)){
+  temp=na.omit(female[female$geno == flm$geno[i], ])
+  temp.lm = lm(temp$corrected.values~temp$day)
+  flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  i = i +1
+}
+
+row.names(flm) = flm$geno
+
 mmean = mmean[order(mmean$day),]
 mstd = mstd[order(mstd$day),]
-eb = eb[order(eb$day),]
-
-eb$y0 = mmean$mean - mstd$std
-eb$y1 = mmean$mean + mstd$std
+meb = meb[order(meb$day),]
+
+meb$y0 = mmean$mean - mstd$std
+meb$y1 = mmean$mean + mstd$std
+
+fmean = fmean[order(fmean$day),]
+fstd = fstd[order(fstd$day),]
+feb = feb[order(feb$day),]
+
+feb$y0 = fmean$mean - fstd$std
+feb$y1 = fmean$mean + fstd$std
 
@@
 norm.mstd = norm.mmean
-norm.eb = norm.mmean
+norm.meb = norm.mmean
 norm.mmean$mean = 0
 norm.mstd$std = 0
+
+i=1
+while(i <= nrow(norm.female)){
+  norm.female$normval[i] = norm.female$corrected.values[i]/
+    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
+  i = i +1
+}
+
+norm.fmean = unique(norm.female[,c('geno', 'day', 'sample')])
+norm.fstd = norm.fmean
+norm.feb = norm.fmean
+norm.fmean$mean = 0
+norm.fstd$std = 0
 
@@
 
+i=1
+while(i<=nrow(norm.fmean)){
+  norm.fmean$mean[i] = mean(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval']))
+
+  norm.fstd$std[i] = (var(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval'])))
+
+  i = i+1
+}
+
 norm.mmean = norm.mmean[order(norm.mmean$day),]
 norm.mstd = norm.mstd[order(norm.mstd$day),]
-norm.eb = norm.eb[order(norm.eb$day),]
-
-norm.eb$y0 = norm.mmean$mean - norm.mstd$std
-norm.eb$y1 = norm.mmean$mean + norm.mstd$std
+norm.meb = norm.meb[order(norm.meb$day),]
+
+norm.meb$y0 = norm.mmean$mean - norm.mstd$std
+norm.meb$y1 = norm.mmean$mean + norm.mstd$std
 
@@
 
+norm.fmean = norm.fmean[order(norm.fmean$day),]
+norm.fstd = norm.fstd[order(norm.fstd$day),]
+norm.feb = norm.feb[order(norm.feb$day),]
+
+norm.feb$y0 = norm.fmean$mean - norm.fstd$std
+norm.feb$y1 = norm.fmean$mean + norm.fstd$std
+
+norm.flm = data.frame(geno = unique(norm.female$geno),
+                x0 = 2,
+                x1 = 27,
+                y0 = 0,
+                y1 = 0)
+
+i=1
+while(i<=nrow(norm.flm)){
+  temp=na.omit(norm.female[norm.female$geno == norm.flm$geno[i], ])
+  temp.lm = lm(temp$normval~temp$day)
+  norm.flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
+  norm.flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
+  i = i +1
+}
+
+row.names(norm.flm) = norm.flm$geno
+
 ```
 
-```{r echo = F, fig.height=10}
-
-silent = norm.mmean[norm.mmean$geno == "silent", ]
-a4v = norm.mmean[norm.mmean$geno == "A4V", ]
-silentcha = norm.mmean[norm.mmean$geno == "silentcha", ]
-a4vcha = norm.mmean[norm.mmean$geno == "A4Vcha", ]
-silentok = norm.mmean[norm.mmean$geno == "silentok", ]
-a4vok = norm.mmean[norm.mmean$geno == "A4Vok", ]
-
-ls = norm.mmean[norm.mmean$geno == 'silent',]
-la = norm.mmean[norm.mmean$geno == 'A4V',]
-lsc = norm.mmean[norm.mmean$geno == 'silentcha',]
-lac = norm.mmean[norm.mmean$geno == 'A4Vcha',]
-lso = norm.mmean[norm.mmean$geno == 'silentok',]
-lao = norm.mmean[norm.mmean$geno == 'A4Vok',]
+```{r echo = F, fig.height=10, include = F}
+
+silent = norm.fmean[norm.fmean$geno == "silent", ]
+a4v = norm.fmean[norm.fmean$geno == "A4V", ]
+silentcha = norm.fmean[norm.fmean$geno == "silentcha", ]
+a4vcha = norm.fmean[norm.fmean$geno == "A4Vcha", ]
+silentok = norm.fmean[norm.fmean$geno == "silentok", ]
+a4vok = norm.fmean[norm.fmean$geno == "A4Vok", ]
+
+ls = norm.fmean[norm.fmean$geno == 'silent',]
+la = norm.fmean[norm.fmean$geno == 'A4V',]
+lsc = norm.fmean[norm.fmean$geno == 'silentcha',]
+lac = norm.fmean[norm.fmean$geno == 'A4Vcha',]
+lso = norm.fmean[norm.fmean$geno == 'silentok',]
+lao = norm.fmean[norm.fmean$geno == 'A4Vok',]
 
@@
      xaxt = 'n',
-     main = "Males")
+     main = "Females")
 
@@
 
-lines(x = norm.mlm['silent', c("x0", "x1")],
-      y = norm.mlm['silent', c("y0", "y1")],
+lines(x = norm.flm['silent', c("x0", "x1")],
+      y = norm.flm['silent', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.mlm['A4V', c("x0", "x1")],
-      y = norm.mlm['A4V', c("y0", "y1")],
+lines(x = norm.flm['A4V', c("x0", "x1")],
+      y = norm.flm['A4V', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.mlm['silentcha', c("x0", "x1")],
-      y = norm.mlm['silentcha', c("y0", "y1")],
+lines(x = norm.flm['silentcha', c("x0", "x1")],
+      y = norm.flm['silentcha', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.mlm['A4Vcha', c("x0", "x1")],
-      y = norm.mlm['A4Vcha', c("y0", "y1")],
+lines(x = norm.flm['A4Vcha', c("x0", "x1")],
+      y = norm.flm['A4Vcha', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.mlm['silentok', c("x0", "x1")],
-      y = norm.mlm['silentok', c("y0", "y1")],
+lines(x = norm.flm['silentok', c("x0", "x1")],
+      y = norm.flm['silentok', c("y0", "y1")],
       type = 'l',
@@
 
-lines(x = norm.mlm['A4Vok', c("x0", "x1")],
-      y = norm.mlm['A4Vok', c("y0", "y1")],
+lines(x = norm.flm['A4Vok', c("x0", "x1")],
+      y = norm.flm['A4Vok', c("y0", "y1")],
       type = 'l',
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'silent'],
-       x1 = norm.eb$day[norm.eb$geno == 'silent'],
-       y0 = norm.eb$y0[norm.eb$geno == 'silent'],
-       y1 = norm.eb$y1[norm.eb$geno == 'silent'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'silent'],
+       x1 = norm.feb$day[norm.feb$geno == 'silent'],
+       y0 = norm.feb$y0[norm.feb$geno == 'silent'],
+       y1 = norm.feb$y1[norm.feb$geno == 'silent'], 
        code = 3, 
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'A4V'],
-       x1 = norm.eb$day[norm.eb$geno == 'A4V'],
-       y0 = norm.eb$y0[norm.eb$geno == 'A4V'],
-       y1 = norm.eb$y1[norm.eb$geno == 'A4V'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'A4V'],
+       x1 = norm.feb$day[norm.feb$geno == 'A4V'],
+       y0 = norm.feb$y0[norm.feb$geno == 'A4V'],
+       y1 = norm.feb$y1[norm.feb$geno == 'A4V'], 
        code = 3, 
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'silentcha'],
-       x1 = norm.eb$day[norm.eb$geno == 'silentcha'],
-       y0 = norm.eb$y0[norm.eb$geno == 'silentcha'],
-       y1 = norm.eb$y1[norm.eb$geno == 'silentcha'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'silentcha'],
+       x1 = norm.feb$day[norm.feb$geno == 'silentcha'],
+       y0 = norm.feb$y0[norm.feb$geno == 'silentcha'],
+       y1 = norm.feb$y1[norm.feb$geno == 'silentcha'], 
        code = 3, 
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
-       x1 = norm.eb$day[norm.eb$geno == 'A4Vcha'],
-       y0 = norm.eb$y0[norm.eb$geno == 'A4Vcha'],
-       y1 = norm.eb$y1[norm.eb$geno == 'A4Vcha'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
+       x1 = norm.feb$day[norm.feb$geno == 'A4Vcha'],
+       y0 = norm.feb$y0[norm.feb$geno == 'A4Vcha'],
+       y1 = norm.feb$y1[norm.feb$geno == 'A4Vcha'], 
        code = 3, 
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'silentok'],
-       x1 = norm.eb$day[norm.eb$geno == 'silentok'],
-       y0 = norm.eb$y0[norm.eb$geno == 'silentok'],
-       y1 = norm.eb$y1[norm.eb$geno == 'silentok'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'silentok'],
+       x1 = norm.feb$day[norm.feb$geno == 'silentok'],
+       y0 = norm.feb$y0[norm.feb$geno == 'silentok'],
+       y1 = norm.feb$y1[norm.feb$geno == 'silentok'], 
        code = 3, 
@@
 
-arrows(x0 = norm.eb$day[norm.eb$geno == 'A4Vok'],
-       x1 = norm.eb$day[norm.eb$geno == 'A4Vok'],
-       y0 = norm.eb$y0[norm.eb$geno == 'A4Vok'],
-       y1 = norm.eb$y1[norm.eb$geno == 'A4Vok'], 
+arrows(x0 = norm.feb$day[norm.feb$geno == 'A4Vok'],
+       x1 = norm.feb$day[norm.feb$geno == 'A4Vok'],
+       y0 = norm.feb$y0[norm.feb$geno == 'A4Vok'],
+       y1 = norm.feb$y1[norm.feb$geno == 'A4Vok'], 
        code = 3, 
@@
 
-```{r  echo = F}
-
-fig4cd = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4CD.csv", header = T)
-
-fig4cd = fig4cd[fig4cd$day != 9,]
-fig4cd = fig4cd[fig4cd$day != 32,]
-
-female = fig4cd[grep('f', fig4cd$vial_ID),]
-male = fig4cd[grep('m', fig4cd$vial_ID),]
-
-female$sample = paste0(female$geno, female$day)
-male$sample = paste0(male$geno, male$day)
-
-norm.female = na.omit(female)
-norm.female$normval = 0
-
-fmean = unique(female[,c('geno', 'day', 'sample')])
-fstd = fmean
-feb = fmean
-fmean$mean = 0
-fstd$std = 0
-
-norm.male = na.omit(male)
-norm.male$normval = 0
-
-mmean = unique(male[,c('geno', 'day', 'sample')])
-mstd = mmean
-meb = mmean
-mmean$mean = 0
-mstd$std = 0
-
-i=1
-while(i<=nrow(mmean)){
-  mmean$mean[i] = mean(na.omit(male[male$sample == mmean$sample[i], 'corrected.values']))
-
-  mstd$std[i] = (var(na.omit(male[male$sample == mmean$sample[i], 'corrected.values'])))
-
-  i = i+1
-}
-
-i=1
-while(i<=nrow(fmean)){
-  fmean$mean[i] = mean(na.omit(female[female$sample == fmean$sample[i], 'corrected.values']))
-
-  fstd$std[i] = (var(na.omit(female[female$sample == fmean$sample[i], 'corrected.values'])))
-
-  i = i+1
-}
-
-mlm = data.frame(geno = unique(male$geno),
-                x0 = 2,
-                x1 = 27,
-                y0 = 0,
-                y1 = 0)
-
-i=1
-while(i<=nrow(mlm)){
-  temp=na.omit(male[male$geno == mlm$geno[i], ])
-  temp.lm = lm(temp$corrected.values~temp$day)
-  mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
-  mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
-  i = i +1
-}
-
-row.names(mlm) = mlm$geno
-
-flm = data.frame(geno = unique(female$geno),
-                x0 = 2,
-                x1 = 27,
-                y0 = 0,
-                y1 = 0)
-
-i=1
-while(i<=nrow(flm)){
-  temp=na.omit(female[female$geno == flm$geno[i], ])
-  temp.lm = lm(temp$corrected.values~temp$day)
-  flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
-  flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
-  i = i +1
-}
-
-row.names(flm) = flm$geno
-
-mmean = mmean[order(mmean$day),]
-mstd = mstd[order(mstd$day),]
-meb = meb[order(meb$day),]
-
-meb$y0 = mmean$mean - mstd$std
-meb$y1 = mmean$mean + mstd$std
-
-fmean = fmean[order(fmean$day),]
-fstd = fstd[order(fstd$day),]
-feb = feb[order(feb$day),]
-
-feb$y0 = fmean$mean - fstd$std
-feb$y1 = fmean$mean + fstd$std
-
-i=1
-while(i <= nrow(norm.male)){
-  norm.male$normval[i] = norm.male$corrected.values[i]/
-    mmean$mean[mmean$geno == 'silent' & mmean$day == norm.male$day[i]]
-  i = i +1
-}
-
-norm.mmean = unique(norm.male[,c('geno', 'day', 'sample')])
-norm.mstd = norm.mmean
-norm.meb = norm.mmean
-norm.mmean$mean = 0
-norm.mstd$std = 0
-
-i=1
-while(i <= nrow(norm.female)){
-  norm.female$normval[i] = norm.female$corrected.values[i]/
-    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
-  i = i +1
-}
-
-norm.fmean = unique(norm.female[,c('geno', 'day', 'sample')])
-norm.fstd = norm.fmean
-norm.feb = norm.fmean
-norm.fmean$mean = 0
-norm.fstd$std = 0
-
-i=1
-while(i<=nrow(norm.mmean)){
-  norm.mmean$mean[i] = mean(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval']))
-
-  norm.mstd$std[i] = (var(na.omit(norm.male[norm.male$sample == norm.mmean$sample[i], 'normval'])))
-
-  i = i+1
-}
-
-i=1
-while(i<=nrow(norm.fmean)){
-  norm.fmean$mean[i] = mean(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval']))
-
-  norm.fstd$std[i] = (var(na.omit(norm.female[norm.female$sample == norm.fmean$sample[i], 'normval'])))
-
-  i = i+1
-}
-
-norm.mmean = norm.mmean[order(norm.mmean$day),]
-norm.mstd = norm.mstd[order(norm.mstd$day),]
-norm.meb = norm.meb[order(norm.meb$day),]
-
-norm.meb$y0 = norm.mmean$mean - norm.mstd$std
-norm.meb$y1 = norm.mmean$mean + norm.mstd$std
-
-norm.mlm = data.frame(geno = unique(norm.male$geno),
-                x0 = 2,
-                x1 = 27,
-                y0 = 0,
-                y1 = 0)
-
-i=1
-while(i<=nrow(norm.mlm)){
-  temp=na.omit(norm.male[norm.male$geno == norm.mlm$geno[i], ])
-  temp.lm = lm(temp$normval~temp$day)
-  norm.mlm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
-  norm.mlm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
-  i = i +1
-}
-
-row.names(norm.mlm) = norm.mlm$geno
-
-norm.fmean = norm.fmean[order(norm.fmean$day),]
-norm.fstd = norm.fstd[order(norm.fstd$day),]
-norm.feb = norm.feb[order(norm.feb$day),]
-
-norm.feb$y0 = norm.fmean$mean - norm.fstd$std
-norm.feb$y1 = norm.fmean$mean + norm.fstd$std
-
-norm.flm = data.frame(geno = unique(norm.female$geno),
-                x0 = 2,
-                x1 = 27,
-                y0 = 0,
-                y1 = 0)
-
-i=1
-while(i<=nrow(norm.flm)){
-  temp=na.omit(norm.female[norm.female$geno == norm.flm$geno[i], ])
-  temp.lm = lm(temp$normval~temp$day)
-  norm.flm$y0[i] = temp.lm[[1]][2]*2 + temp.lm[[1]][1]
-  norm.flm$y1[i] = temp.lm[[1]][2]*27 + temp.lm[[1]][1]
-  i = i +1
-}
-
-row.names(norm.flm) = norm.flm$geno
-
-```
-
-```{r echo = F, fig.height=10}
+```{r echo = F, fig.height=10, include = F}
 
@@
 
-```{r echo = F, fig.height=10}
+```{r echo = F, fig.height=10, include = F}
 
@@
        xpd=TRUE)
-
 ```

### 2024-09-27 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
Dina Folder Update

@@
 library(visNetwork)
-library(org.Dm.eg.db)
 

### 2024-09-27 TKT_RNAseq/R Code/TKTRNAseqRescueResponse.Rmd
Dina Folder Update

---
title: "G85R Analysis: Rescue Response"
author: "John Santiago"
date: "2024-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)
library(RcisTarget)
library(DT)
##source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
library(VennDiagram)

```

```{r include = F, echo = F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

G85R.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)

groups = groups[colnames(cpmdata),]

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##Clean Trait Data and calculate CPMs
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)

##normalize data
countdata=countdata[, row.names(groups)]
x <- countdata
gr <- factor(groups$Group)
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)

compare = makeContrasts(TktDfGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FDfxWT.FC=DEout
sGR.FDfxWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FDfxWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[17] = 'GR.FDfxWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FDfxWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[17] = 'GR.FDfxWT.FC'

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MDfxWT.MC=DEout
sGR.MDfxWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MDfxWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[18] = 'GR.MDfxWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MDfxWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[18] = 'GR.MDfxWT.MC'

compare = makeContrasts(TktOEGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FOExWT.FC=DEout
sGR.FOExWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FOExWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[19] = 'GR.FOExWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FOExWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[19] = 'GR.FOExWT.FC'

compare = makeContrasts(TktOEGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MOExWT.MC=DEout
sGR.MOExWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MOExWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[20] = 'GR.MOExWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MOExWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[20] = 'GR.MOExWT.MC'

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.metab = mean.data

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.metab[,condition1]/mean.metab[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.metab)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")[row.names(GRxWT.C),]
GRxWT.OE = compare.conditions("F", "A")[row.names(GRxWT.C),]

GR.CxDf = compare.conditions("D", "E")[row.names(GRxWT.C),]
WT.CxDf = compare.conditions("B", "C")[row.names(GRxWT.C),]

GR.CxOE = compare.conditions("F", "E")[row.names(GRxWT.C),]
WT.CxOE = compare.conditions("A", "C")[row.names(GRxWT.C),]

GR.DfxWT.C = compare.conditions("D", "C")[row.names(GRxWT.C),]
GR.OExWT.C = compare.conditions("F", "C")[row.names(GRxWT.C),]

comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
                 GRF.CxOE = c("TktOEGR.F","GR.F"),
                 WTF.CxDf = c("TktDfWT.F","WT.F"),
                 WTF.CxOE = c("TktOEWT.F","WT.F"),
                 GRxWT.FC = c("GR.F","WT.F"), 
                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
                 GRM.CxOE = c("TktOEGR.M","GR.M"),
                 WTM.CxDf = c("TktDfWT.M","WT.M"),
                 WTM.CxOE = c("TktOEWT.M","WT.M"),
                 GRxWT.MC = c("GR.M","WT.M"), 
                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
                 GR.FxM = c("GR.F","GR.M"),
                 WT.FxM = c("WT.F","WT.M"))

metab.FC = data.frame('GRxWT.C' = GRxWT.C$FC,
                      'GRxWT.Df' = GRxWT.Df$FC,
                      'GRxWT.OE' = GRxWT.OE$FC,
                      'GR.CxDf' = GR.CxDf$FC,
                      'WT.CxDf' = WT.CxDf$FC,
                      'GR.CxOE' = GR.CxOE$FC,
                      'WT.CxOE' = WT.CxOE$FC,
                      'GR.DfxWT.C' = GR.DfxWT.C$FC,
                      'GR.OExWT.C' = GR.OExWT.C$FC)
row.names(metab.FC) = row.names(GRxWT.C)
metab.FC = log2(metab.FC)

metab.FDR = data.frame(GRxWT.C = GRxWT.C$p,
                       GRxWT.Df = GRxWT.Df$p,
                       GRxWT.OE = GRxWT.OE$p,
                       GR.CxDf = GR.CxDf$p,
                       WT.CxDf = WT.CxDf$p,
                       GR.CxOE = GR.CxOE$p,
                       WT.CxOE = WT.CxOE$p,
                       GR.DfxWT.C = GR.DfxWT.C$p,
                       GR.OExWT.C = GR.OExWT.C$p)
row.names(metab.FDR) = row.names(GRxWT.C)

colnames(mean.metab) = as.character(genotypes[colnames(mean.metab)])

enzyme2KEGG = as.list(org.Dm.egENZYME2EG)

```

```{r echo = F}

TKT.biplot = function(x, y, mean.data, main.title){
min.expression = 10

FDR.data = TKT.EdgeR[, c(x, y)]
x.genes = row.names(FDR.data[FDR.data[,x] < 0.05,])
y.genes = row.names(FDR.data[FDR.data[,y] < 0.05,])
xy.genes = intersect(x.genes, y.genes)
DEGs = unique(c(x.genes, y.genes))

FC.data = TKT.EdgeR.FC[DEGs, c(x, y)]
FDR.data = TKT.EdgeR[DEGs, c(x, y)]
mean.data = mean.data[DEGs, ]

data = data.frame(Symbol = GeneIDKey[DEGs, "Symbol"],
                  FBgn = DEGs,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  data[x.genes, 'Color'] = 'royalblue'
  data[y.genes, 'Color'] = 'firebrick' 
  data[xy.genes, 'Color'] = 'gold'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r include = F, echo = F}
Subset.Enrichment = function(bg, geneset){

  sigs = geneset

  sigsKEY = GeneIDKey[sigs,]
  sigs = na.omit(sigsKEY$Symbol)
  bgKEY = GeneIDKey[bg,]
  bg = na.omit(bgKEY$Symbol)

  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=GenesInKegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=KEGG.Names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")
  return(enrichment.data)
}

```

```{r echo = F}

compoundandgenes = function(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean){
KEGG.ID = unlist(strsplit(CompoundData$compoundID, " / "))
KEGG.ID = unlist(strsplit(KEGG.ID, "-"))

symbols = schema(F)$traces$scatter$attributes$marker$symbol$values
symbols = symbols[c(3, 15, 27, 63, 39, 51, 159, 207, 75, 87, 99)]
i = 1
enzymes = keggGet(KEGG.ID[i])[[1]]$ENZYME
if(length(enzymes > 0)){
  enzymes = unlist(enzyme2KEGG[intersect(enzymes, names(enzyme2KEGG))])
  if(length(enzymes > 0)){
    enzymes = GeneIDKey[GeneIDKey$Name %in% enzymes,]
    enzymes$Compound = CompoundData[grep(KEGG.ID[i], CompoundData$compoundID),'Metab']
  }
}

if(length(KEGG.ID)>1){
  i = 2
  while(i <= length(KEGG.ID)){
    temp.enzymes = keggGet(KEGG.ID[i])[[1]]$ENZYME
    if(length(temp.enzymes > 0)){
      temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
      if(length(temp.enzymes > 0)){
        temp.enzymes = GeneIDKey[GeneIDKey$Name %in% temp.enzymes,]
        temp.enzymes$Compound = CompoundData[grep(KEGG.ID[i], CompoundData$compoundID),'Metab']
        enzymes = rbind(enzymes, temp.enzymes)
      }
    }
    i = i + 1
  }
}

enzymes$symbol = symbols[as.numeric(factor(enzymes$Symbol))]

colnames(CompoundData)[1:2] = c('Molecule', 'ID')
bg = setNames(c('firebrick',"gold","darkgreen","dodgerblue", 'deeppink', 'grey', 'darkorange')[as.numeric(factor(CompoundData$Molecule))], factor(CompoundData$Molecule))
CompoundData$shape = 'hexagon'
#CompoundData$Color = bg[CompoundData$Molecule]
CompoundData$Color = 'grey'
CompoundData$size = 35
CompoundData$group = 'Metabolite'

enzymes = data.frame(Molecule = enzymes$Symbol,
                     ID = enzymes$FBgn,
                     FDR1 = TKT.EdgeR[enzymes$FBgn, Fx],
                     FDR2 = TKT.EdgeR[enzymes$FBgn, My],
                     FC1 = TKT.EdgeR.FC[enzymes$FBgn, Fx],
                     FC2 = TKT.EdgeR.FC[enzymes$FBgn, My],
                     Color = 'gold',
                     size = 20,
                     Variable1.mean = Fmean[enzymes$FBgn,1],
                     Control1.mean  = Fmean[enzymes$FBgn,2],
                     Variable2.mean = Mmean[enzymes$FBgn,1],
                     Control2.mean  = Mmean[enzymes$FBgn,2],
                     shape = enzymes$symbol,
                     group = 'Enzyme')

GeneData = na.omit(enzymes)

metabs = data.frame(Molecule = CompoundData$Molecule,
                     ID = CompoundData$ID,
                     FDR1 = CompoundData$FDR,
                     FDR2 = CompoundData$FDR,
                     FC1 = CompoundData$FC,
                     FC2 = CompoundData$FC,
                     Color = CompoundData$Color,
                     size = CompoundData$size,
                     Variable1.mean = CompoundData$Variable1.mean,
                     Control1.mean  = CompoundData$Control1.mean,
                     Variable2.mean = CompoundData$Variable1.mean,
                     Control2.mean  = CompoundData$Variable1.mean,
                     shape = 'hexagon',
                     group = 'Metabolite')

CompoundData = na.omit(metabs)

data = rbind(CompoundData, GeneData)

  fig = plot_ly(type = 'scatter',
                mode = 'markers')
  fig = fig %>% add_trace(x = enzymes$FC1,
                          y = enzymes$FC2,
                          name = 'Genes',
                          marker = list(
                            color = enzymes$Color,
                            size = enzymes$size,
                            symbol = enzymes$shape,
                            line = list(
                              color = 'black',
                              width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Gene Symbol:", enzymes$Molecule,
                                  "\nCompound ID:", enzymes$ID,
                                  "\n", Fx, "p: ", round(2^-enzymes$FDR1, 2),
                                  "\n", My, "p: ", round(2^-enzymes$FDR2,2),
                                  "\n", Fx, "FC: ", round(enzymes$FC1, 2),
                                  "\n", My, "FC: ", round(enzymes$FC2,2),
                                  "\n", Fx, "mean: ", signif(enzymes$Variable1,2),
                                  "\n ", My, "mean: ", signif(enzymes$Control1,2)))

      fig = fig %>% add_trace(x = CompoundData$FC1,
                          y = CompoundData$FC2,
                          name = 'Metabolites',
                          marker = list(
                            color = CompoundData$Color,
                            size = CompoundData$size,
                            symbol = CompoundData$shape,
                            line = list(
                              color = 'black',
                              width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Gene Symbol:", CompoundData$Molecule,
                                  "\nCompound ID:", CompoundData$ID,
                                  "\nSex: Male",
                                  "\n", x, "p: ", round(2^-CompoundData$FDR1, 2),
                                  "\n", y, "p: ", round(2^-CompoundData$FDR2,2),
                                  "\n", x, "FC: ", round(CompoundData$FC1, 2),
                                  "\n", y, "FC: ", round(CompoundData$FC2,2),
                                  "\n", colnames(mean.data)[1], "mean: ", signif(CompoundData$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(CompoundData$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(CompoundData$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(CompoundData$Control2,2)))

        fig = fig %>% layout(title = data$Molecule[1],
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(Fx, "FC")),
                       yaxis = list(title = paste(My, "FC")),
                       showlegend = T)

   fig

}
```

## Response Genes in G85R relative to WT

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'GR.F', 'GR.M')]
main.title = "G85R vs WT: Female and Male DE Genes"

##RG = Response Genes
GRxWT.RG = TKT.biplot(x, y, mean.data, main.title)

GRxWT.RG[[1]]

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Female Increased"
set2 = "Female Decreased"
set3 = "Male Increased"
set4 = "Male Decreased"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

NormalResponse = data.frame(Female = c(length(s2), length(s1)),
                            Male =  c(length(s4), length(s3)))
row.names(NormalResponse) = c("Decreased", "Increased")
NormalResponse = as.matrix(NormalResponse)

par(mar = c(2,4,2,7.5))
barplot(NormalResponse,
        beside = T,
        ylab = "Total DEGs",
        main = "G85R vs Silent",
        col = c('navy', 'firebrick'),
        angle = c(45, 45, 315, 315), density = 50,
        legend.text = c("Decreased", "Increased"),
        args.legend = list(x = 8,
                           y = 700,
                           bty = 'n'))
#legend(x = 6.25, 
#       y = 700, 
#       legend = c("Increased", "Decreased"),
#       pt.bg = c('grey35', 'lightgrey'),
#       xpd = T, 
#       bty = "o",
#       pch = 22,
#       pt.cex = 1.5)

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set3 = "Female Increased"
set1 = "Female Decreased"
set4 = "Male Increased"
set2 = "Male Decreased"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("navy", "darkgreen","gold","firebrick"),cex=2,cat.cex = 1, title = "main")

```

##Female and Male Shared DEGs
```{r echo = F, include = F}

s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

MF.shared.DEGs = c(intersect(s1,s3), intersect(s2,s4))

bg = row.names(TKT.EdgeR)
GRWTMF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)

```

```{r echo = F}

RTCC.GRWTMF = tree(GRWTMF.Enr, "CC")
treemapPlot(RTCC.GRWTMF)

```

```{r echo = F}

RTCC.GRWTMF = tree(GRWTMF.Enr, "BP")
treemapPlot(RTCC.GRWTMF)

```

```{r echo = F}

RTCC.GRWTMF = tree(GRWTMF.Enr, "MF")
treemapPlot(RTCC.GRWTMF)

```

```{r echo = F}

cat.data = GRWTMF.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTMF.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:39)
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTMF.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:30)
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

##Female Only DEGs
```{r echo = F, include = F}

F.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTFonly.Enr = Subset.Enrichment(bg, F.only.DEGs)

```

```{r echo = F}

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "CC")
treemapPlot(RTCC.GRWTFonly)

```

```{r echo = F}

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "BP")
treemapPlot(RTCC.GRWTFonly)

```

```{r echo = F}

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "MF")
treemapPlot(RTCC.GRWTFonly)
```

```{r echo = F}

cat.data = GRWTFonly.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTFonly.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTFonly.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

##Male Only DEGs
```{r echo = F, include = F}

M.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTMonly.Enr = Subset.Enrichment(bg, M.only.DEGs)
```

```{r echo = F}

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "CC")
treemapPlot(RTCC.GRWTMonly)

```

```{r echo = F}

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "BP")
treemapPlot(RTCC.GRWTMonly)

```

```{r echo = F}

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "MF")
treemapPlot(RTCC.GRWTMonly)

```

```{r echo = F}

cat.data = GRWTMonly.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:28)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTMonly.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:50)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

cat.data = GRWTMonly.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:50)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Female"
set2 = "Male"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GRWTFonly.Enr$GO[GRWTFonly.Enr$GO$adjp <= 0.05, "term"]
s2 = GRWTMonly.Enr$GO[GRWTMonly.Enr$GO$adjp <= 0.05, "term"]

main = ""

grid.newpage()
tempvenn=draw.pairwise.venn(area1 = length(s1),
                            area2 = length(s2),
                            cross.area = length(intersect(s1,s2)),
                            fill = c("blue", "red"),
                            cex = 2,
                            cat.cex = 1,
                            category = c(set1, set2),
                            title = "main")

```

```{r echo = F, include = F}

data("motifAnnotations_dmel_v9")
motifRankings = importRankings("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/dm6_v10_clust.genes_vs_motifs.rankings.feather")
motifAnnotations = motifAnnotations_dmel_v9

##motif rankings table for every TF
motif.data = getRanking(motifRankings)
##motifs associated with a TF
##TF.data = motifAnnotations[motifAnnotations$TF == 'Tudor-SN',]
###TF.data = motifAnnotations[motifAnnotations$TF == 'Mad',]

##TF.motif.data = motif.data[motif.data$motifs %in% TF.data$motif,]

##Motif collection data directory
motif.collection.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/DrosophilaMotifsSingletonData/"

##geneLists = GeneIDKey[MF.shared.DEGs, 'Symbol']
geneLists = GeneIDKey[F.only.DEGs, 'Symbol']
geneLists = GeneIDKey[M.only.DEGs, 'Symbol']

motifEnrichmentTable_wGenes <- cisTarget(geneLists, 
         motifRankings,
         motifAnnot=motifAnnotations)

motifs_AUC <- calcAUC(geneLists, motifRankings, nCores=1)

auc <- getAUC(motifs_AUC)
hist(auc, xlab="dAUC histogram",
     breaks=100, col="#ff000050", border="darkred")
nes3 <- (3*sd(auc)) + mean(auc)
abline(v=nes3, col="red")

motifEnrichmentTable <- addMotifAnnotation(motifs_AUC, nesThreshold=3,
     motifAnnot=motifAnnotations)

motifEnrichmentTable_wGenes <- addSignificantGenes(motifEnrichmentTable,
                      rankings=motifRankings, 
                      geneSets=geneLists)
dim(motifEnrichmentTable_wGenes)

resultsSubset <- motifEnrichmentTable_wGenes

```

```{r echo = F}

showLogo(resultsSubset)

```

```{r echo = F, include = F}

anotatedTfs <- lapply(split(motifEnrichmentTable_wGenes$TF_highConf,
                            motifEnrichmentTable$geneSet),
                      function(x) {
                        genes <- gsub(" \\(.*\\). ", "; ", x, fixed=FALSE)
                        genesSplit <- unique(unlist(strsplit(genes, "; ")))
                        return(genesSplit)
                        })

anotatedTfs$hypoxia

```

```{r echo = F}

##comparisons
primary = 'GRxWT.C'

x = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

min.expression = 0

##Reversal pattern
FC.data = metab.FC[, c(primary)]
FC.data = na.omit(FC.data)

##Sig cutoff. Currently, at least 1 significant change
sig.metab = metab.FDR[metab.FDR[,primary]  < .05, ]
sig.metab = na.omit(sig.metab)
sig.metab = row.names(sig.metab)

FC.data = metab.FC[sig.metab, c(x)]
FDR.data = metab.FDR[sig.metab, c(x)]
mean.data = mean.data[sig.metab, ]

data = data.frame(Metab = sig.metab,
                  compoundID = KEGG.Key[sig.metab],
                  FDR = -log2(FDR.data),
                  FC = FC.data,
                  Color = 'grey',
                  size = 1,
                  Variable1.mean = mean.data[,1],
                  Control1.mean = mean.data[,2])

sig.metabs = data

main.title = "G85R Metabolites"

  data$Color[data$FC < 0] = 'royalblue'
  data$Color[data$FC > 0] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  data$size = log10(apply(mean.data[,c(1,2)], 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = data$size

  fig = plot_ly(data = data,
                x = ~FC,
                y = ~FDR,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Metabolite:", data$Metab,
                                  "\n Compound ID:", data$compoundID,
                                  "\n ", x, "p: ", round(2^-data$FDR, 2),
                                  "\n ", x, "FC: ", round(data$FC, 2),
                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2)))

  fig = fig %>% layout(title = main.title,
                       xaxis = list(title = paste(x, "FC")),
                       yaxis = list(title = paste(x, "-log2(p-value)")),
                       showlegend = F)

  fig

```

```{r echo = F}

CompoundData = sig.metabs[1,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = sig.metabs[2,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = sig.metabs[3,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = sig.metabs[4,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = sig.metabs[5,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = sig.metabs[41,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

```

##  Are there genes that respond to rescue in Silent and G85R for both sexes?

##  TKT-Df Response
```{r echo = F}

x = "GRF.CxDf"
y = "WTF.CxDf"

mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
                             'TktDfGR.F', 'TktDfWT.F')]
main.title = "Female TKT-Df DE Genes"

##RG = Response Genes
FDf.RG = TKT.biplot(x, y, mean.data, main.title)

FDf.RG[[1]]

```

```{r echo = F}

x = "GRM.CxDf"
y = "WTM.CxDf"

mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
                             'TktDfGR.M', 'TktDfWT.M')]
main.title = "Male TKT-Df DE Genes"

##RG = Response Genes
MDf.RG = TKT.biplot(x, y, mean.data, main.title)

MDf.RG[[1]]

```

```{r echo = F}

x = "GRF.CxDf"
y = "GRM.CxDf"

mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
                             'TktDfGR.F', 'TktDfGR.M')]
main.title = "G85R TKT-Df DE Genes"

##RG = Response Genes
GRDf.RG = TKT.biplot(x, y, mean.data, main.title)

GRDf.RG[[1]]

```

```{r echo = F}

x = "WTF.CxDf"
y = "WTM.CxDf"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'TktDfWT.F', 'TktDfWT.M')]
main.title = "Silent TKT-Df DE Genes"

##RG = Response Genes
WTDf.RG = TKT.biplot(x, y, mean.data, main.title)

WTDf.RG[[1]]

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female Df"
set2 = "Silent Male Df"
set3 = "G85R Female Df"
set4 = "G85R Male Df"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

NormalResponse = data.frame(Rescue = c(set1, set2, set3, set4),
                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))

fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes (Control vs TKT-Df'))

fig

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female Df"
set2 = "Silent Male Df"
set3 = "G85R Female Df"
set4 = "G85R Male Df"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

##WTF.C vs WTF.TKT-Df
```{r echo = F, include = F}

bg = row.names(TKT.EdgeR)
WTF.Df.Enr = Subset.Enrichment(bg, FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"])

```

```{r echo = F}

RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
treemapPlot(RTCC.WTF.Df)

```

```{r echo = F}

RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
treemapPlot(RTBP.WTF.Df)

```

```{r echo = F}

RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
treemapPlot(RTMF.WTF.Df)

```

##WTM.C vs WTM.TKT-Df
```{r echo = F, include = F}

bg = row.names(TKT.EdgeR)
WTM.Df.Enr = Subset.Enrichment(bg, MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"])

```

```{r echo = F}

RTCC.WTM.Df = tree(WTM.Df.Enr, "CC")
treemapPlot(RTCC.WTM.Df)

```

```{r echo = F}

RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
treemapPlot(RTBP.WTF.Df)

```

```{r echo = F}

RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
treemapPlot(RTMF.WTF.Df)

```

##GRF.C vs GRF.TKT-Df
```{r echo = F, include = F}

bg = row.names(TKT.EdgeR)
GRF.Df.Enr = Subset.Enrichment(bg, FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])

```

```{r echo = F}

RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
treemapPlot(RTCC.WTF.Df)

```

```{r echo = F}

RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
treemapPlot(RTBP.WTF.Df)

```

```{r echo = F}

RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
treemapPlot(RTMF.WTF.Df)

```

##GRM.C vs GRM.TKT-Df
```{r echo = F, include = F}

bg = row.names(TKT.EdgeR)
GRM.Df.Enr = Subset.Enrichment(bg, MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])

```

```{r echo = F}

RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
treemapPlot(RTCC.WTF.Df)

```

```{r echo = F}

RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
treemapPlot(RTBP.WTF.Df)

```

```{r echo = F}

RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
treemapPlot(RTMF.WTF.Df)

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female Df"
set2 = "Silent Male Df"
set3 = "G85R Female Df"
set4 = "G85R Male Df"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = WTF.Df.Enr$GO$term[WTF.Df.Enr$GO$adjp <= .05]
s2 = WTM.Df.Enr$GO$term[WTM.Df.Enr$GO$adjp <= .05]
s3 = GRF.Df.Enr$GO$term[GRF.Df.Enr$GO$adjp <= .05]
s4 = GRM.Df.Enr$GO$term[GRM.Df.Enr$GO$adjp <= .05]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

###################################

###################################

###################################

## TKT-OE Response
```{r echo = F}

x = "GRF.CxOE"
y = "WTF.CxOE"

mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
                             'TktOEGR.F', 'TktOEWT.F')]
main.title = "Female TKT-OE DE Genes"

##RG = Response Genes
FOE.RG = TKT.biplot(x, y, mean.data, main.title)

FOE.RG[[1]]

```

```{r echo = F}

x = "GRM.CxOE"
y = "WTM.CxOE"

mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
                             'TktOEGR.M', 'TktOEWT.M')]
main.title = "Male TKT-OE DE Genes"

##RG = Response Genes
MOE.RG = TKT.biplot(x, y, mean.data, main.title)

MOE.RG[[1]]

```

```{r echo = F}

x = "GRF.CxOE"
y = "GRM.CxOE"

mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
                             'TktOEGR.F', 'TktOEGR.M')]
main.title = "G85R TKT-OE DE Genes"

##RG = Response Genes
GROE.RG = TKT.biplot(x, y, mean.data, main.title)

GROE.RG[[1]]

```

```{r echo = F}

x = "WTF.CxOE"
y = "WTM.CxOE"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'TktOEWT.F', 'TktOEWT.M')]
main.title = "Silent TKT-OE DE Genes"

##RG = Response Genes
WTOE.RG = TKT.biplot(x, y, mean.data, main.title)

WTOE.RG[[1]]

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female OE"
set2 = "Silent Male OE"
set3 = "G85R Female OE"
set4 = "G85R Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FOE.RG[[2]][FOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MOE.RG[[2]][MOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FOE.RG[[2]][FOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MOE.RG[[2]][MOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

NormalResponse = data.frame(Rescue = c(set1, set2, set3, set4),
                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))

fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes (Control vs TKT-Df'))

fig

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female OE"
set2 = "Silent Male OE"
set3 = "G85R Female OE"
set4 = "G85R Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FOE.RG[[2]][FOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MOE.RG[[2]][MOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FOE.RG[[2]][FOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MOE.RG[[2]][MOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

### 2024-09-27 TKT_RNAseq/R Code/TKTRNAseqReversalGenes.Rmd
Dina Folder Update

---
title: "G85R Analysis: Reversal Genes"
author: "John Santiago"
date: "2024-08-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)
library(RcisTarget)
library(DT)
source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

G85R.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)

groups = groups[colnames(cpmdata),]

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##Clean Trait Data and calculate CPMs
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)

##normalize data
countdata=countdata[, row.names(groups)]
x <- countdata
gr <- factor(groups$Group)
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)

compare = makeContrasts(TktDfGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FDfxWT.FC=DEout
sGR.FDfxWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FDfxWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[17] = 'GR.FDfxWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FDfxWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[17] = 'GR.FDfxWT.FC'

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MDfxWT.MC=DEout
sGR.MDfxWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MDfxWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[18] = 'GR.MDfxWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MDfxWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[18] = 'GR.MDfxWT.MC'

compare = makeContrasts(TktOEGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FOExWT.FC=DEout
sGR.FOExWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FOExWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[19] = 'GR.FOExWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FOExWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[19] = 'GR.FOExWT.FC'

compare = makeContrasts(TktOEGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MOExWT.MC=DEout
sGR.MOExWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MOExWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[20] = 'GR.MOExWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MOExWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[20] = 'GR.MOExWT.MC'

```

##  Are there genes with 'corrected' expression in response to rescue?
```{r echo = F}

##comparisons
primary = "GRxWT.FC"
rescue = "GRF.CxDf"

x = "GRxWT.FC"
y = "GR.FDfxWT.FC"

mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
                             'TktDfGR.F', 'TktDfWT.F')]

min.expression = 10

##Reversal pattern
FC.data = TKT.EdgeR.FC[, c(primary, rescue)]
FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = TKT.EdgeR[TKT.EdgeR[,primary]  < .05 |
                       TKT.EdgeR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)

reversal.genes = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = TKT.EdgeR.FC[reversal.genes, c(primary, rescue)]

  FC.data = TKT.EdgeR.FC[reversal.genes, c(x, y)]
  FDR.data = TKT.EdgeR[reversal.genes, c(x, y)]
  mean.data = mean.data[reversal.genes, ]

data = data.frame(Symbol = GeneIDKey[reversal.genes, "Symbol"],
                  FBgn = reversal.genes,
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  main.title = "Female TKT-Df Reversal Genes"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = 5*data$size

  female.Df.reverse = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig
```

```{r echo = F}

##comparisons
primary = "GRxWT.MC"
rescue = "GRM.CxDf"

x = "GRxWT.MC"
y = "GR.MDfxWT.MC"

mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
                             'TktDfGR.M', 'TktDfWT.M')]

min.expression = 10

##Reversal pattern
FC.data = TKT.EdgeR.FC[, c(primary, rescue)]
FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = TKT.EdgeR[TKT.EdgeR[,primary]  < .05 |
                       TKT.EdgeR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)

reversal.genes = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = TKT.EdgeR.FC[reversal.genes, c(primary, rescue)]

  FC.data = TKT.EdgeR.FC[reversal.genes, c(x, y)]
  FDR.data = TKT.EdgeR[reversal.genes, c(x, y)]
  mean.data = mean.data[reversal.genes, ]

data = data.frame(Symbol = GeneIDKey[reversal.genes, "Symbol"],
                  FBgn = reversal.genes,
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  main.title = "Male TKT-Df Reversal Genes"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = 5*data$size

  male.Df.reverse = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig
```

```{r echo = F}

##comparisons
primary = "GRxWT.FC"
rescue = "GRF.CxOE"

x = "GRxWT.FC"
y = "GR.FOExWT.FC"

mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
                             'TktOEGR.F', 'TktOEWT.F')]

min.expression = 10

##Reversal pattern
FC.data = TKT.EdgeR.FC[, c(primary, rescue)]
FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = TKT.EdgeR[TKT.EdgeR[,primary]  < .05 |
                       TKT.EdgeR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)

reversal.genes = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = TKT.EdgeR.FC[reversal.genes, c(primary, rescue)]

  FC.data = TKT.EdgeR.FC[reversal.genes, c(x, y)]
  FDR.data = TKT.EdgeR[reversal.genes, c(x, y)]
  mean.data = mean.data[reversal.genes, ]

data = data.frame(Symbol = GeneIDKey[reversal.genes, "Symbol"],
                  FBgn = reversal.genes,
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  main.title = "Female TKT-OE Reversal Genes"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = 5*data$size

  female.OE.reverse = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig
```

```{r echo = F}

##comparisons
primary = "GRxWT.MC"
rescue = "GRM.CxOE"

x = "GRxWT.MC"
y = "GR.MOExWT.MC"

mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
                             'TktOEGR.M', 'TktOEWT.M')]

min.expression = 10

##Reversal pattern
FC.data = TKT.EdgeR.FC[, c(primary, rescue)]
FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = TKT.EdgeR[TKT.EdgeR[,primary]  < .05 |
                       TKT.EdgeR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)

reversal.genes = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = TKT.EdgeR.FC[reversal.genes, c(primary, rescue)]

  FC.data = TKT.EdgeR.FC[reversal.genes, c(x, y)]
  FDR.data = TKT.EdgeR[reversal.genes, c(x, y)]
  mean.data = mean.data[reversal.genes, ]

data = data.frame(Symbol = GeneIDKey[reversal.genes, "Symbol"],
                  FBgn = reversal.genes,
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  main.title = "Male TKT-OE Reversal Genes"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = 5*data$size

  male.OE.reverse = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig
```

##Looking for common reversal genes
```{r echo = F}
library(VennDiagram)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df"
set2="Male Df"
set3="Female OE"
set4="Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=(female.Df.reverse$FBgn)
s2=(male.Df.reverse$FBgn)
s3=(female.OE.reverse$FBgn)
s4=(male.OE.reverse$FBgn)

main = "Reversal Genes"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

##The 19 common genes:

```{r echo = F}

G85R.gene = function(FBgn, name){
gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), condition = groups$Group, group = paste0(groups$Genotype, groups$Sex))

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$cpm), max(gene$cpm)),
     xlim = c(.5, 12.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')

boxplot(gene$cpm~gene$condition, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("honeydew", 3),
                rep("thistle1", 3),
                rep("lightcyan", 3),
                rep("lightyellow", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$condition)),
       y=gene$cpm,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:12,
     labels = rep(c("Control", "Df", "OE"), 4),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$cpm) + min(gene$cpm)),
     label = "Counts per million reads",
     tick = F,
     padj = -3,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5, 8, 11),
     labels = c("Silent", "G85R","Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)
axis(side = 3,
     at = c(3.5, 9.5),
     labels = c("Female", "Male"),
     tick = F,
     padj = .5,
     cex.axis = 1.5)

axis(side = 3,
     at = 6.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

axis(side = 3,
     at = c(3.5,9.5),
     tick = T,
     outer = T,
     labels = F,
     line = -2.25,
     lwd.ticks = 0)

xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
abline(v = 6.5, lty = 2, lwd = 2)

}

```

```{r echo = F}
common.symbol = GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'Symbol']

common.FBgn = GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'FBgn']

```

```{r echo = F, fig.width=8}
i=1
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##Cyp4p1; Cytochrome P450 4p1; May be involved in the metabolism of insect hormones and in the breakdown of synthetic insecticides.

```{r echo = F, fig.width=8}
i=2
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG13962; Unknown function

```{r echo = F, fig.width=8}
i=3
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##Cpr51A; Cuticular protein 51A; Predicted to be a structural constituent of chitin-based larval cuticle. Involved in sexual reproduction. Located in extracellular space.

```{r echo = F, fig.width=8}
i=4
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG11438; Predicted to enable phosphatidate phosphatase activity. Predicted to be involved in phospholipid dephosphorylation; phospholipid metabolic process; and signal transduction. Predicted to be active in plasma membrane.

```{r echo = F, fig.width=8}
i=5
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##Sgs5bis; Predicted to be involved in puparial adhesion. Predicted to be located in adhesive extracellular matrix.

```{r echo = F, fig.width=8}
i=6
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##sad; shadow; shadow (sad) encodes a cytochrome P450 involved in ecdysteroid biosynthesis. It shows a mitochondrial localization and catalyzes the addition of a hydroxyl group to the 2 carbon of the cholesterol ring. sad mutants fail to undergo head involution, dorsal closure or to secrete cuticle.

```{r echo = F, fig.width=8}
i=7
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##Lip2; Lipase 2; Predicted to enable triglyceride lipase activity. Predicted to be involved in lipid metabolic process. Human ortholog(s) of this gene implicated in Wolman disease; autosomal recessive congenital ichthyosis 8; and cholesterol ester storage disease.

```{r echo = F, fig.width=8}
i=8
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG4757; Enables serine hydrolase activity. Is expressed in adult head. Human ortholog(s) of this gene implicated in colorectal cancer and gastrointestinal system cancer.

```{r echo = F, fig.width=8}
i=9
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG14229; Is expressed in organism.

```{r echo = F, fig.width=8}
i=10
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG15406; Predicted to enable transmembrane transporter activity. Predicted to be involved in transmembrane transport. Predicted to be active in membrane.

```{r echo = F, fig.width=8}
i=11
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG3270; Predicted to be involved in mitochondrial respiratory chain complex I assembly. Predicted to be active in cytoplasm. Is expressed in adult head. Human ortholog(s) of this gene implicated in nuclear type mitochondrial complex I deficiency 19.

```{r echo = F, fig.width=8}
i=12
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG9877; Unknown function

```{r echo = F, fig.width=8}
i=13
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG13905; mat; materazzi; Enables lipid binding activity. Is expressed in adult head.

```{r echo = F, fig.width=8}
i=14
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##Zip71B; Zinc/iron regulated transporter-related protein 71B; Zinc/iron regulated transporter-related protein 71B (Zip71B) encodes a protein involved in zinc detoxification and zinc transmembrane import.

```{r echo = F, fig.width=8}
i=15
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG17027; Predicted to enable inositol monophosphate 1-phosphatase activity. Predicted to be involved in inositol metabolic process and signal transduction. Predicted to be located in cytoplasm. Is expressed in embryonic Malpighian tubule and embryonic proventriculus.

```{r echo = F, fig.width=8}
i=16
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##nom; numerous disordered muscles; Enables DNA binding activity. Involved in larval somatic muscle development. Predicted to be located in nucleus. Is expressed in embryonic/larval fat body; organism; and ring gland primordium.

```{r echo = F, fig.width=8}
i=17
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG16727; Predicted to enable transmembrane transporter activity. Predicted to be involved in transmembrane transport. Predicted to be located in membrane. Orthologous to human SLC22A24

```{r echo = F, fig.width=8}
i=18
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG9702; Predicted to enable sulfate transmembrane transporter activity. Predicted to be involved in transmembrane transport. Predicted to be located in membrane. Predicted to be active in plasma membrane. Is expressed in adult head. Orthologous to human SLC26A11

```{r echo = F, fig.width=8}
i=19
FBgn = common.FBgn[i]
name = paste0(common.FBgn[i], ": ", common.symbol[i])
G85R.gene(FBgn, name)
```

##CG43740; Located in nucleoplasm. Is expressed in adult brain cell body rind.

```{r echo = F, include = F}

bg = row.names(G85R.cpm)
geneset = female.Df.reverse$FBgn

FDf.functions = Subset.Enrichment(bg, geneset)

```

## GO Term analysis of reversals in each condition

```{r echo = F, include = F}

RTCC.FDf = tree(FDf.functions, "CC")
treemapPlot(RTCC.FDf)

```

##Female DF CC

```{r echo = F}

treemapPlot(RTCC.FDf)

```

```{r echo = F, include = F}

RTBP.FDf = tree(FDf.functions, "BP")

```

##Female DF BP

```{r echo = F}

treemapPlot(RTBP.FDf)

```

```{r echo = F, include = F}

RTMF.FDf = tree(FDf.functions, "MF")

```

##Female DF MF

```{r echo = F}

treemapPlot(RTMF.FDf)

```

```{r echo = F, include = F}

bg = row.names(G85R.cpm)
geneset = male.Df.reverse$FBgn

MDf.functions = Subset.Enrichment(bg, geneset)

```

```{r echo = F, include = F}

RTCC.MDf = tree(MDf.functions, "CC")

```

##Male DF CC

```{r echo = F}

treemapPlot(RTCC.MDf)

```

```{r echo = F, include = F}

RTBP.MDf = tree(MDf.functions, "BP")

```

```{r echo = F}

Df.FC = setNames(G85R.FC[, 'GRF.CxDf'], row.names(G85R.FC))
Df.FDR = setNames(G85R.FDR[, 'GRF.CxDf'], row.names(G85R.FDR))
sigs = male.Df.reverse$FBgn

cat.data = MDf.functions
GO.ontology = 'CC'
FC = Df.FC
FDR = Df.FDR
usecats = 'sigs.only'

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

##Male DF BP

```{r echo = F}

treemapPlot(RTBP.MDf)

```

```{r echo = F}

Df.FC = setNames(G85R.FC[, 'GRF.CxDf'], row.names(G85R.FC))
Df.FDR = setNames(G85R.FDR[, 'GRF.CxDf'], row.names(G85R.FDR))
sigs = male.Df.reverse$FBgn

cat.data = MDf.functions
GO.ontology = 'BP'
FC = Df.FC
FDR = Df.FDR
usecats = 'sigs.only'

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F, include = F}

RTMF.MDf = tree(MDf.functions, "MF")

```

##Male DF MF

```{r echo = F}

treemapPlot(RTMF.MDf)

```

```{r echo = F}

Df.FC = setNames(G85R.FC[, 'GRF.CxDf'], row.names(G85R.FC))
Df.FDR = setNames(G85R.FDR[, 'GRF.CxDf'], row.names(G85R.FDR))
sigs = male.Df.reverse$FBgn

cat.data = MDf.functions
GO.ontology = 'MF'
FC = Df.FC
FDR = Df.FDR
usecats = 'sigs.only'

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

```

```{r echo = F, include = F}

data("motifAnnotations_dmel_v9")
motifRankings = importRankings("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/dm6_v10_clust.genes_vs_motifs.rankings.feather")
motifAnnotations = motifAnnotations_dmel_v9

##motif rankings table for every TF
motif.data = getRanking(motifRankings)
##motifs associated with a TF
##TF.data = motifAnnotations[motifAnnotations$TF == 'Tudor-SN',]
###TF.data = motifAnnotations[motifAnnotations$TF == 'Mad',]

##TF.motif.data = motif.data[motif.data$motifs %in% TF.data$motif,]

##Motif collection data directory
motif.collection.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/DrosophilaMotifsSingletonData/"

geneLists = male.Df.reverse$Symbol

motifEnrichmentTable_wGenes <- cisTarget(geneLists, 
         motifRankings,
         motifAnnot=motifAnnotations)

motifs_AUC <- calcAUC(geneLists, motifRankings, nCores=1)

auc <- getAUC(motifs_AUC)
hist(auc, xlab="dAUC histogram",
     breaks=100, col="#ff000050", border="darkred")
nes3 <- (3*sd(auc)) + mean(auc)
abline(v=nes3, col="red")

motifEnrichmentTable <- addMotifAnnotation(motifs_AUC, nesThreshold=3,
     motifAnnot=motifAnnotations)

motifEnrichmentTable_wGenes <- addSignificantGenes(motifEnrichmentTable,
                      rankings=motifRankings, 
                      geneSets=geneLists)
dim(motifEnrichmentTable_wGenes)

resultsSubset <- motifEnrichmentTable_wGenes[1:3,]

```

```{r echo = F}

showLogo(resultsSubset)

```

```{r echo = F, include = F}

anotatedTfs <- lapply(split(motifEnrichmentTable_wGenes$TF_highConf,
                            motifEnrichmentTable$geneSet),
                      function(x) {
                        genes <- gsub(" \\(.*\\). ", "; ", x, fixed=FALSE)
                        genesSplit <- unique(unlist(strsplit(genes, "; ")))
                        return(genesSplit)
                        })

anotatedTfs$hypoxia

```

```{r echo = F, include = F}

bg = row.names(G85R.cpm)
geneset = female.OE.reverse$FBgn

FOE.functions = Subset.Enrichment(bg, geneset)

```

```{r echo = F, include = F}

RTCC.FOE = tree(FOE.functions, "CC")

```

##Female OE CC

```{r echo = F}

treemapPlot(RTCC.FOE)

```

```{r echo = F, include = F}

RTBP.FOE = tree(FOE.functions, "BP")

```

##Female OE BP

```{r echo = F}

treemapPlot(RTBP.FOE)

```

```{r echo = F, include = F}

RTMF.FOE = tree(FOE.functions, "MF")

```

##Female OE MF

```{r echo = F}

treemapPlot(RTMF.FOE)

```

```{r echo = F, include = F}

bg = row.names(G85R.cpm)
geneset = male.OE.reverse$FBgn

MOE.functions = Subset.Enrichment(bg, geneset)

```

```{r echo = F, include = F}

RTCC.MOE = tree(MOE.functions, "CC")

```

##Male OE CC

```{r echo = F}

treemapPlot(RTCC.MOE)

```

```{r echo = F, include = F}

RTBP.MOE = tree(MOE.functions, "BP")

```

##Male OE BP

```{r echo = F}

treemapPlot(RTBP.MOE)

```

```{r echo = F, include = F}

RTMF.MOE = tree(MOE.functions, "MF")

```

##Male OE MF

```{r echo = F}

treemapPlot(RTMF.MOE)

```

##Common significantly enriched GO Terms in each condition

```{r echo = F}
library(VennDiagram)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df GO Terms"
set2="Male Df GO Terms"
set3="Female OE GO Terms"
set4="Male OE GO Terms"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.functions$GO[FDf.functions$GO$adjp<.05, 'term']
s2 = MDf.functions$GO[MDf.functions$GO$adjp<.05, 'term']
s3 = FOE.functions$GO[FOE.functions$GO$adjp<.05, 'term']
s4 = MOE.functions$GO[MOE.functions$GO$adjp<.05, 'term']

main = "Reversal Genes"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

##Significantly enriched GO Terms in Male Df

```{r echo = F}
library(VennDiagram)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df GO Terms"
set2="Male Df GO Terms"
set3="Female OE GO Terms"
set4="Male OE GO Terms"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.functions$GO[1:37, 'term']
s2 = MDf.functions$GO[MDf.functions$GO$adjp<.05, 'term']
s3 = FOE.functions$GO[1:37, 'term']
s4 = MOE.functions$GO[1:37, 'term']

main = "Reversal Genes"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

```{r echo = F}

data = MDf.functions$GO[MDf.functions$GO$adjp<.05,]
data = data[data$numDEInCat < 100,]
data$adjp = -log10(data$adjp)
data$FDf = FDf.functions$GO[row.names(data), "numDEInCat"]
##data$MOE = MOE.functions$GO[row.names(data), "numDEInCat"]
##data$FOE = FOE.functions$GO[row.names(data), "numDEInCat"]

fig = plot_ly(data = data,
              x = ~numDEInCat,
              y = ~FDf,
              type = 'scatter',
              mode = 'markers',
              marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "grey")),
                            reversescale =T,
                            colorbar = list(title = "-log10(FDR)",
                                            len = .8, outlinewidth = 0,
                                            tickformat = ".2f",
                                            tick0 = 0),##, dtick = .01),
                            color = ~adjp,
                            size = 15,
                            line = list(color = "black", width = 1.5)),
                hoverinfo = "text",
                hovertext = paste("Term:", data$term,
                                  "\n Ontology:", data$ontology,
                                  "\n Number in Cat: ", data$numDEInCat,
                                  "\n adjusted p: ", data$adjp))

  fig = fig %>% layout(title = "Male and Female Df",
                       xaxis = list(title = 'Male numDEInCat'),
                       yaxis = list(title = 'Female numDEInCat'),
                       showlegend = F)

  fig

```

```{r echo = F}

data = MDf.functions$GO[MDf.functions$GO$adjp<.05,]
data = data[data$numDEInCat < 100,]
data$adjp = -log10(data$adjp)
data$FDf = FDf.functions$GO[row.names(data), "numDEInCat"]
data$MOE = MOE.functions$GO[row.names(data), "numDEInCat"]
data$FOE = FOE.functions$GO[row.names(data), "numDEInCat"]

data$FDf.adjp = FDf.functions$GO[row.names(data), "adjp"]
data$MOE.adjp = MOE.functions$GO[row.names(data), "adjp"]
data$FOE.adjp = FOE.functions$GO[row.names(data), "adjp"]

fig = plot_ly(type = 'scatter',
              mode = 'markers')
fig = fig %>% add_trace(x = data$numDEInCat,
                        y = data$FDf,
                        name = 'Female Df',
                        marker = list(
                          color = 'steelblue',
                          size = 10,
                          symbol = 'circle',
                          line = list(
                            color = 'black',
                            width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Term:", data$term,
                                  "\n Ontology:", data$ontology,
                                  "\n Number in Cat: ", data$FDf,
                                  "\n adjusted p: ", data$FDf.adjp))
fig = fig %>% add_trace(x = data$numDEInCat,
                        y = data$FOE,
                        name = 'Female OE',
                        marker = list(
                          color = 'gold',
                          size = 10,
                          symbol = 'hexagon',
                          line = list(
                            color = 'black',
                            width = 2
                            )
                          ),
                        hoverinfo = "text",
                        hovertext = paste("Term:", data$term,
                                  "\n Ontology:", data$ontology,
                                  "\n Number in Cat: ", data$FOE,
                                  "\n adjusted p: ", data$FOE.adjp))
fig = fig %>% add_trace(x = data$numDEInCat,
                        y = data$MOE,
                        name = 'Male OE',
                        marker = list(
                          color = 'firebrick',
                          size = 10,
                          symbol = 'square',
                          line = list(
                            color = 'black',
                            width = 2
                            )
                          ),
                        hoverinfo = "text",
                        hovertext = paste("Term:", data$term,
                                  "\n Ontology:", data$ontology,
                                  "\n Number in Cat: ", data$MOE,
                                  "\n adjusted p: ", data$MOE.adjp))

        fig = fig %>% layout(title = data$Molecule[1],
                             xaxis = list(title = paste(x, "Male Df NumDEInCat")),
                             yaxis = list(title = paste(y, "Other NumDEInCat")),
                             showlegend = T)

   fig

```

##  Is there normally significant similarity in the rescue response and could the rescue phenotype be due to normal changes observed in response to TKT modulations.
```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df"
set2="Male Df"
set3="Female OE"
set4="Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = row.names(TKT.EdgeR[TKT.EdgeR$WTF.CxDf < .05, ])
s2 = row.names(TKT.EdgeR[TKT.EdgeR$WTM.CxDf < .05, ])
s3 = row.names(TKT.EdgeR[TKT.EdgeR$WTF.CxOE < .05, ])
s4 = row.names(TKT.EdgeR[TKT.EdgeR$WTM.CxOE < .05, ])

s1 = G85R.meancpm[s1, c('WT.F', 'TktDfWT.F')]
s2 = G85R.meancpm[s2, c('WT.M', 'TktDfWT.M')]
s3 = G85R.meancpm[s3, c('WT.F', 'TktOEWT.F')]
s4 = G85R.meancpm[s4, c('WT.M', 'TktOEWT.M')]

s1 = row.names(s1[apply(s1,1,max)>10,])
s2 = row.names(s2[apply(s2,1,max)>10,])
s3 = row.names(s3[apply(s3,1,max)>10,])
s4 = row.names(s4[apply(s4,1,max)>10,])

NormalResponse = data.frame(Rescue = c("FemaleDf", "MaleDf", "FemaleOE", "MaleOE"),
                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))

fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes in Silent-Rescue vs Silent'))

fig

```

##Overlap in Total Response Genes in Silent-Rescue vs Silent
```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df"
set2="Male Df"
set3="Female OE"
set4="Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = row.names(TKT.EdgeR[TKT.EdgeR$WTF.CxDf < .05, ])
s2 = row.names(TKT.EdgeR[TKT.EdgeR$WTM.CxDf < .05, ])
s3 = row.names(TKT.EdgeR[TKT.EdgeR$WTF.CxOE < .05, ])
s4 = row.names(TKT.EdgeR[TKT.EdgeR$WTM.CxOE < .05, ])

s1 = G85R.meancpm[s1, c('WT.F', 'TktDfWT.F')]
s2 = G85R.meancpm[s2, c('WT.M', 'TktDfWT.M')]
s3 = G85R.meancpm[s3, c('WT.F', 'TktOEWT.F')]
s4 = G85R.meancpm[s4, c('WT.M', 'TktOEWT.M')]

s1 = row.names(s1[apply(s1,1,max)>10,])
s2 = row.names(s2[apply(s2,1,max)>10,])
s3 = row.names(s3[apply(s3,1,max)>10,])
s4 = row.names(s4[apply(s4,1,max)>10,])

CF.Df = s1
CM.Df = s2
CF.OE = s3
CM.OE = s4

main = "Total Response Genes in Silent-Rescue vs Silent"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = main)

```

##Genes that are Reversal Genes in the "Silent-Rescue vs Silent"
##Reversal genes that normally respond to the rescue
```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df"
set2="Male Df"
set3="Female OE"
set4="Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = intersect(female.Df.reverse$FBgn, CF.Df)
s2 = intersect(male.Df.reverse$FBgn, CM.Df)
s3 = intersect(female.OE.reverse$FBgn, CF.OE)
s4 = intersect(male.OE.reverse$FBgn, CM.OE)

main = "Reversal Genes in the Normal Response Genes"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

##Identifying reversal genes that are also sDEG in WT 'rescue' condition

###Grey points should indicate a 'conserved response gene'. That is G85R-rescue with FC similar to the obeserved FC in WT-rescue. Same direction and similar magnitude (within 50% of FC). 
##Red and Blue indicates Reversal genes that are not following a 'conserved response gene'
##Gold are any 'conserved response genes' that are sDEG in WT Rescue
##Pink and Cyan are any Reversal genes that are not 'conserved response' but are sDEG in WT response

```{r echo = F}

conserved.reversalgenes = function(x, y, mean.data, reversal.genes, sWT, main.title){
FC.data = TKT.EdgeR.FC[reversal.genes, c(x, y)]
FDR.data = TKT.EdgeR[reversal.genes, c(x, y)]
mean.data = mean.data[reversal.genes, ]

data = data.frame(Symbol = GeneIDKey[reversal.genes, "Symbol"],
                  FBgn = reversal.genes,
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4],
                  Conserved.genes = F)

  data$Color[(data$FC1 - (.5*abs(data$FC1))) > data$FC2] = 'royalblue'

  data$Color[data$FC1 > 0 & data$FC2 < 0] = 'royalblue'

  data$Color[(data$FC1 + (.5*abs(data$FC1))) < data$FC2] = 'firebrick' 
  data$Color[data$FC1 < 0 & data$FC2 > 0] = 'firebrick'
  data[data$Color == 'grey', 'Conserved.genes'] = T

  data[data$FBgn %in% sWT & data$Color == 'grey', 'Color'] = 'gold'
    data[data$FBgn %in% sWT & data$Color == 'royalblue', 'Color'] = 'cyan'
      data[data$FBgn %in% sWT & data$Color == 'firebrick', 'Color'] = 'deeppink'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data$size = 3*data$size

  Conserved.Fdf = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r echo = F}

##comparisons
x = "GRF.CxDf"
y = "WTF.CxDf"

mean.data = G85R.meancpm[, c('GR.F', 'TktDfGR.F',
                             'WT.F', 'TktDfWT.F')]

reversal.genes = female.Df.reverse$FBgn
sWT = CF.Df
main.title = "Female TKT-Df Reversal Genes"

Conserved.Fdf = conserved.reversalgenes(x, y, mean.data, reversal.genes, sWT, main.title)

Conserved.Fdf[[1]]

Conserved.Fdf = Conserved.Fdf[[2]]

```

```{r echo = F}

data = Conserved.Fdf

conserved = nrow(data[data$Color == 'grey',])
conserved.DEGs = nrow(data[data$Color == 'gold',])
altered.down = nrow(data[data$Color == 'deeppink',])
altered.up = nrow(data[data$Color == 'cyan',])

pie(c((nrow(data)-conserved), altered.down, altered.up, conserved.DEGs, conserved),
    col = c(rgb(158/255,202/255,225/255, .75), 'deeppink', 'cyan', 'gold', 'grey'),
    labels = NA)
legend("topright",
       legend = c("Altered Response", "Conserved Response", "Conserved DEGs", "Altered DEGs: Increased", "Altered DEGs: Decreased"),
       pt.bg = c(rgb(158/255,202/255,225/255, .75), 'grey', 'gold', 'cyan', 'deeppink'),
       bty = 'n',
       cex = .85,
       pch = 22,
       pt.cex = 1.5)

```

```{r echo = F}

##comparisons
x = "GRM.CxDf"
y = "WTM.CxDf"

mean.data = G85R.meancpm[, c('GR.M', 'TktDfGR.M',
                             'WT.M', 'TktDfWT.M')]

reversal.genes = male.Df.reverse$FBgn
sWT = CM.Df

main.title = "Male TKT-Df Reversal Genes"

Conserved.Mdf = conserved.reversalgenes(x, y, mean.data, reversal.genes, sWT, main.title)

Conserved.Mdf[[1]]

Conserved.Mdf = Conserved.Mdf[[2]]

```

```{r echo = F}

data = Conserved.Mdf

conserved = nrow(data[data$Color == 'grey',])
conserved.DEGs = nrow(data[data$Color == 'gold',])
altered.down = nrow(data[data$Color == 'deeppink',])
altered.up = nrow(data[data$Color == 'cyan',])

pie(c((nrow(data)-conserved), altered.down, altered.up, conserved.DEGs, conserved),
    col = c(rgb(158/255,202/255,225/255, .75), 'deeppink', 'cyan', 'gold', 'grey'),
    labels = NA)
legend("topright",
       legend = c("Altered Response", "Conserved Response", "Conserved DEGs", "Altered DEGs: Increased", "Altered DEGs: Decreased"),
       pt.bg = c(rgb(158/255,202/255,225/255, .75), 'grey', 'gold', 'cyan', 'deeppink'),
       bty = 'n',
       cex = .85,
       pch = 22,
       pt.cex = 1.5)

```

```{r echo = F}

##comparisons
x = "GRF.CxOE"
y = "WTF.CxOE"

mean.data = G85R.meancpm[, c('GR.F', 'TktOEGR.F',
                             'WT.F', 'TktOEWT.F')]

reversal.genes = female.OE.reverse$FBgn
sWT = CF.OE

main.title = "Female TKT-OE Reversal Genes"

Conserved.FOE = conserved.reversalgenes(x, y, mean.data, reversal.genes, sWT, main.title)

Conserved.FOE[[1]]

Conserved.FOE = Conserved.FOE[[2]]

```

```{r echo = F}

data = Conserved.FOE

conserved = nrow(data[data$Color == 'grey',])
conserved.DEGs = nrow(data[data$Color == 'gold',])
altered.down = nrow(data[data$Color == 'deeppink',])
altered.up = nrow(data[data$Color == 'cyan',])

pie(c((nrow(data)-conserved), altered.down, altered.up, conserved.DEGs, conserved),
    col = c(rgb(158/255,202/255,225/255, .75), 'deeppink', 'cyan', 'gold', 'grey'),
    labels = NA)
legend("topright",
       legend = c("Altered Response", "Conserved Response", "Conserved DEGs", "Altered DEGs: Increased", "Altered DEGs: Decreased"),
       pt.bg = c(rgb(158/255,202/255,225/255, .75), 'grey', 'gold', 'cyan', 'deeppink'),
       bty = 'n',
       cex = .85,
       pch = 22,
       pt.cex = 1.5)

```

```{r echo = F}

##comparisons
x = "GRM.CxOE"
y = "WTM.CxOE"

mean.data = G85R.meancpm[, c('GR.M', 'TktOEGR.M',
                             'WT.M', 'TktOEWT.M')]

reversal.genes = male.OE.reverse$FBgn
sWT = CM.OE

main.title = "Male TKT-OE Reversal Genes"

Conserved.MOE = conserved.reversalgenes(x, y, mean.data, reversal.genes, sWT, main.title)

Conserved.MOE[[1]]

Conserved.MOE = Conserved.MOE[[2]]

```

```{r echo = F}

data = Conserved.MOE

conserved = nrow(data[data$Color == 'grey',])
conserved.DEGs = nrow(data[data$Color == 'gold',])
altered.down = nrow(data[data$Color == 'deeppink',])
altered.up = nrow(data[data$Color == 'cyan',])

pie(c((nrow(data)-conserved), altered.down, altered.up, conserved.DEGs, conserved),
    col = c(rgb(158/255,202/255,225/255, .75), 'deeppink', 'cyan', 'gold', 'grey'),
    labels = NA)
legend("topright",
       legend = c("Altered Response", "Conserved Response", "Conserved DEGs", "Altered DEGs: Increased", "Altered DEGs: Decreased"),
       pt.bg = c(rgb(158/255,202/255,225/255, .75), 'grey', 'gold', 'cyan', 'deeppink'),
       bty = 'n',
       cex = .85,
       pch = 22,
       pt.cex = 1.5)

```

##Assessing the number of Conserved Response genes in the Reversal Genes

##Distinguishing Conserved Response genes between control DEGs and control sDEGs

```{r echo = F}

response = data.frame(Rescue = c("FemaleDf", "MaleDf", "FemaleOE", "MaleOE"),
                      NormalResponse =  c(nrow(Conserved.Fdf[Conserved.Fdf$Color == "grey",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color == "grey",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color == "grey",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color == "grey",])),
                      AlteredResponse = c(nrow(Conserved.Fdf[Conserved.Fdf$Color != "grey",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color != "grey",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color != "grey",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color != "grey",])),
                      WTResponse      = c(nrow(Conserved.Fdf[Conserved.Fdf$Color == "gold",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color == "gold",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color == "gold",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color == "gold",])))

fig <- plot_ly(data = response, x = ~Rescue, y = ~NormalResponse, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% add_trace(y = ~WTResponse, name = 'Silent DEG Response',
               marker = list(color = 'gold'))
fig <- fig %>% add_trace(y = ~AlteredResponse, name = 'Altered Response',
               marker = list(color = 'rgb(158,202,225)'))
fig <- fig %>% layout(yaxis = list(title = 'Total Reversal Response Genes'), barmode = 'stack')

fig

```

```{r echo = F}

response = data.frame(Rescue = c("FemaleDf", "MaleDf", "FemaleOE", "MaleOE"),
                      NormalResponse =  c(nrow(Conserved.Fdf[Conserved.Fdf$Color == "grey",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color == "grey",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color == "grey",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color == "grey",])),
                      AlteredResponse = c(nrow(Conserved.Fdf[Conserved.Fdf$Color != "grey",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color != "grey",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color != "grey",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color != "grey",])),
                      WTResponse      = c(nrow(Conserved.Fdf[Conserved.Fdf$Color == "gold",]),
                                          nrow(Conserved.Mdf[Conserved.Mdf$Color == "gold",]),
                                          nrow(Conserved.FOE[Conserved.FOE$Color == "gold",]),
                                          nrow(Conserved.MOE[Conserved.MOE$Color == "gold",])),
                      TotalResponse =   c(nrow(Conserved.Fdf),
                                          nrow(Conserved.Mdf),
                                          nrow(Conserved.FOE),
                                          nrow(Conserved.MOE)))

percent.response = response
percent.response$NormalResponse = 100*percent.response$NormalResponse/percent.response$TotalResponse
percent.response$WTResponse = 100*percent.response$WTResponse/percent.response$TotalResponse
percent.response$AlteredResponse = 100*percent.response$AlteredResponse/percent.response$TotalResponse
fig <- plot_ly(data = percent.response, x = ~Rescue, y = ~NormalResponse, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% add_trace(y = ~WTResponse, name = 'Silent DEG Response',
               marker = list(color = 'gold'))
fig <- fig %>% add_trace(y = ~AlteredResponse, name = 'Altered Response',
               marker = list(color = 'rgb(158,202,225)'))
fig <- fig %>% layout(yaxis = list(title = 'Percent of Total Reversal Response Genes'), barmode = 'stack')

fig

```

##Conserved Reversal Genes

##Can be sDEG or not in Control response

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Female Df"
set2="Male Df"
set3="Female OE"
set4="Male OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = (Conserved.Fdf[Conserved.Fdf$Color == "grey" | Conserved.Fdf$Color == "gold", "FBgn"])
s2 = (Conserved.Mdf[Conserved.Mdf$Color == "grey" | Conserved.Mdf$Color == "gold", "FBgn"])
s3 = (Conserved.FOE[Conserved.FOE$Color == "grey" | Conserved.FOE$Color == "gold", "FBgn"])
s4 = (Conserved.MOE[Conserved.MOE$Color == "grey" | Conserved.MOE$Color == "gold", "FBgn"])

main = "Conserved Reversal Genes"

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

##Common conserved reversal genes

##Is in all groups

##Cpr51A; Cuticular protein 51A; Predicted to be a structural constituent of chitin-based larval cuticle. Involved in sexual reproduction. Located in extracellular space.

##Is in male and female Df but not OE

##vir-1; virus-induced RNA 1; virus-induced RNA 1 (vir-1) is produced from a promoter that is induced by viral infection. It can be used as a marker of the induction of an antiviral response. Its expression is regulated by the Jak/STAT pathway.

##CG34136; Unknown function

##  Are there metabolites with 'corrected' expression in response to rescue and can this response be associated with related gene expression?

```{r echo = F}

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.metab = mean.data

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.metab[,condition1]/mean.metab[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.metab)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")[row.names(GRxWT.C),]
GRxWT.OE = compare.conditions("F", "A")[row.names(GRxWT.C),]

GR.CxDf = compare.conditions("D", "E")[row.names(GRxWT.C),]
WT.CxDf = compare.conditions("B", "C")[row.names(GRxWT.C),]

GR.CxOE = compare.conditions("F", "E")[row.names(GRxWT.C),]
WT.CxOE = compare.conditions("A", "C")[row.names(GRxWT.C),]

GR.DfxWT.C = compare.conditions("D", "C")[row.names(GRxWT.C),]
GR.OExWT.C = compare.conditions("F", "C")[row.names(GRxWT.C),]

comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
                 GRF.CxOE = c("TktOEGR.F","GR.F"),
                 WTF.CxDf = c("TktDfWT.F","WT.F"),
                 WTF.CxOE = c("TktOEWT.F","WT.F"),
                 GRxWT.FC = c("GR.F","WT.F"), 
                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
                 GRM.CxOE = c("TktOEGR.M","GR.M"),
                 WTM.CxDf = c("TktDfWT.M","WT.M"),
                 WTM.CxOE = c("TktOEWT.M","WT.M"),
                 GRxWT.MC = c("GR.M","WT.M"), 
                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
                 GR.FxM = c("GR.F","GR.M"),
                 WT.FxM = c("WT.F","WT.M"))

metab.FC = data.frame('GRxWT.C' = GRxWT.C$FC,
                      'GRxWT.Df' = GRxWT.Df$FC,
                      'GRxWT.OE' = GRxWT.OE$FC,
                      'GR.CxDf' = GR.CxDf$FC,
                      'WT.CxDf' = WT.CxDf$FC,
                      'GR.CxOE' = GR.CxOE$FC,
                      'WT.CxOE' = WT.CxOE$FC,
                      'GR.DfxWT.C' = GR.DfxWT.C$FC,
                      'GR.OExWT.C' = GR.OExWT.C$FC)
row.names(metab.FC) = row.names(GRxWT.C)
metab.FC = log2(metab.FC)

metab.FDR = data.frame(GRxWT.C = GRxWT.C$p,
                       GRxWT.Df = GRxWT.Df$p,
                       GRxWT.OE = GRxWT.OE$p,
                       GR.CxDf = GR.CxDf$p,
                       WT.CxDf = WT.CxDf$p,
                       GR.CxOE = GR.CxOE$p,
                       WT.CxOE = WT.CxOE$p,
                       GR.DfxWT.C = GR.DfxWT.C$p,
                       GR.OExWT.C = GR.OExWT.C$p)
row.names(metab.FDR) = row.names(GRxWT.C)

colnames(mean.metab) = as.character(genotypes[colnames(mean.metab)])

enzyme2KEGG = as.list(org.Dm.egENZYME2EG)

```

```{r echo = F}

##comparisons
primary = 'GRxWT.C'
rescue  = 'GR.CxDf'

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

min.expression = 0

##Reversal pattern
FC.data = metab.FC[, c(primary, rescue)]

FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
FC.data = na.omit(FC.data)
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)
FC.cutoff = na.omit(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = metab.FDR[metab.FDR[,primary]  < .05 |
                       metab.FDR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)
sig.rescue = na.omit(sig.rescue)

reversal.metabs = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = metab.FC[reversal.metabs, c(primary, rescue)]

  FC.data = metab.FC[reversal.metabs, c(x, y)]
  FDR.data = metab.FDR[reversal.metabs, c(x, y)]
  mean.data = mean.data[reversal.metabs, ]

data = data.frame(Metab = reversal.metabs,
                  compoundID = KEGG.Key[reversal.metabs],
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.mean = mean.data[,1],
                  Control1.mean = mean.data[,2],
                  Variable2.mean = mean.data[,3],
                  Control2.mean = mean.data[,4])

  main.title = "TKT-Df Reversal Metabolites"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = data$size

  Df.reverse.metabs = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Metabolite:", data$Metab,
                                  "\n Compound ID:", data$compoundID,
                                  "\n ", colnames(FDR.data)[1], "p: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "p: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig

```

```{r echo = F}

compoundandgenes = function(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean){
KEGG.ID = unlist(strsplit(CompoundData$compoundID, " / "))
KEGG.ID = unlist(strsplit(KEGG.ID, "-"))

symbols = schema(F)$traces$scatter$attributes$marker$symbol$values
symbols = symbols[c(3, 15, 27, 63, 39, 51, 159, 207, 75, 87, 99)]
i = 1
enzymes = keggGet(KEGG.ID[i])[[1]]$ENZYME
if(length(enzymes > 0)){
  enzymes = unlist(enzyme2KEGG[intersect(enzymes, names(enzyme2KEGG))])
  if(length(enzymes > 0)){
    enzymes = GeneIDKey[GeneIDKey$Name %in% enzymes,]
    enzymes$Compound = CompoundData[grep(KEGG.ID[i], CompoundData$compoundID),'Metab']
  }
}

if(length(KEGG.ID)>1){
  i = 2
  while(i <= length(KEGG.ID)){
    temp.enzymes = keggGet(KEGG.ID[i])[[1]]$ENZYME
    if(length(temp.enzymes > 0)){
      temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
      if(length(temp.enzymes > 0)){
        temp.enzymes = GeneIDKey[GeneIDKey$Name %in% temp.enzymes,]
        temp.enzymes$Compound = CompoundData[grep(KEGG.ID[i], CompoundData$compoundID),'Metab']
        enzymes = rbind(enzymes, temp.enzymes)
      }
    }
    i = i + 1
  }
}

enzymes$symbol = symbols[as.numeric(factor(enzymes$Symbol))]

colnames(CompoundData)[1:2] = c('Molecule', 'ID')
bg = setNames(c('firebrick',"gold","darkgreen","dodgerblue", 'deeppink', 'grey', 'darkorange')[as.numeric(factor(CompoundData$Molecule))], factor(CompoundData$Molecule))
CompoundData$shape = 'hexagon'
#CompoundData$Color = bg[CompoundData$Molecule]
CompoundData$Color = 'grey'
CompoundData$size = 35
CompoundData$group = 'Metabolite'

Fenzymes = data.frame(Molecule = enzymes$Symbol,
                      ID = enzymes$FBgn,
                      FDR1 = TKT.EdgeR[enzymes$FBgn, Fx],
                      FDR2 = TKT.EdgeR[enzymes$FBgn, Fy],
                      FC1 = TKT.EdgeR.FC[enzymes$FBgn, Fx],
                      FC2 = TKT.EdgeR.FC[enzymes$FBgn, Fy],
                      #Color = bg[enzymes$Compound],
                      Color = 'deeppink',
                      size = 20,
                      Variable1.mean = Fmean.data[enzymes$FBgn,1],
                      Control1.mean  = Fmean.data[enzymes$FBgn,2],
                      Variable2.mean = Fmean.data[enzymes$FBgn,3],
                      Control2.mean  = Fmean.data[enzymes$FBgn,4],
                      shape = enzymes$symbol,
                      group = 'Female Enzyme')
Fenzymes = na.omit(Fenzymes)

Menzymes = data.frame(Molecule = enzymes$Symbol,
                      ID = enzymes$FBgn,
                      FDR1 = TKT.EdgeR[enzymes$FBgn, Mx],
                      FDR2 = TKT.EdgeR[enzymes$FBgn, My],
                      FC1 = TKT.EdgeR.FC[enzymes$FBgn, Mx],
                      FC2 = TKT.EdgeR.FC[enzymes$FBgn, My],
                      #Color = bg[enzymes$Compound],
                      Color = 'dodgerblue',
                      size = 20,
                      Variable1.mean = Mmean.data[enzymes$FBgn,1],
                      Control1.mean  = Mmean.data[enzymes$FBgn,2],
                      Variable2.mean = Mmean.data[enzymes$FBgn,3],
                      Control2.mean  = Mmean.data[enzymes$FBgn,4],
                      shape = enzymes$symbol,
                      group = 'Male Enzyme')
Menzymes = na.omit(Menzymes)

GeneData = (rbind(Fenzymes, Menzymes))

data = rbind(CompoundData, GeneData)

  fig = plot_ly(type = 'scatter',
                mode = 'markers')
  fig = fig %>% add_trace(x = Fenzymes$FC1,
                          y = Fenzymes$FC2,
                          name = 'Female Genes',
                          marker = list(
                            color = Fenzymes$Color,
                            size = Fenzymes$size,
                            symbol = Fenzymes$shape,
                            line = list(
                              color = 'black',
                              width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Gene Symbol:", Fenzymes$Molecule,
                                  "\nCompound ID:", Fenzymes$ID,
                                  "\nSex: Female",
                                  "\n", x, "p: ", round(2^-Fenzymes$FDR1, 2),
                                  "\n", y, "p: ", round(2^-Fenzymes$FDR2,2),
                                  "\n", x, "FC: ", round(Fenzymes$FC1, 2),
                                  "\n", y, "FC: ", round(Fenzymes$FC2,2),
                                  "\n", colnames(mean.data)[1], "mean: ", signif(Fenzymes$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(Fenzymes$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(Fenzymes$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(Fenzymes$Control2,2)))

    fig = fig %>% add_trace(x = Menzymes$FC1,
                          y = Menzymes$FC2,
                          name = 'Male Genes',
                          marker = list(
                            color = Menzymes$Color,
                            size = Menzymes$size,
                            symbol = Menzymes$shape,
                            line = list(
                              color = 'black',
                              width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Gene Symbol:", Menzymes$Molecule,
                                  "\nCompound ID:", Menzymes$ID,
                                  "\nSex: Male",
                                  "\n", x, "p: ", round(2^-Menzymes$FDR1, 2),
                                  "\n", y, "p: ", round(2^-Menzymes$FDR2,2),
                                  "\n", x, "FC: ", round(Menzymes$FC1, 2),
                                  "\n", y, "FC: ", round(Menzymes$FC2,2),
                                  "\n", colnames(mean.data)[1], "mean: ", signif(Menzymes$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(Menzymes$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(Menzymes$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(Menzymes$Control2,2)))

      fig = fig %>% add_trace(x = CompoundData$FC1,
                          y = CompoundData$FC2,
                          name = 'Metabolites',
                          marker = list(
                            color = CompoundData$Color,
                            size = CompoundData$size,
                            symbol = CompoundData$shape,
                            line = list(
                              color = 'black',
                              width = 2
                            )
                          ),
                hoverinfo = "text",
                hovertext = paste("Gene Symbol:", CompoundData$Molecule,
                                  "\nCompound ID:", CompoundData$ID,
                                  "\nSex: Male",
                                  "\n", x, "p: ", round(2^-CompoundData$FDR1, 2),
                                  "\n", y, "p: ", round(2^-CompoundData$FDR2,2),
                                  "\n", x, "FC: ", round(CompoundData$FC1, 2),
                                  "\n", y, "FC: ", round(CompoundData$FC2,2),
                                  "\n", colnames(mean.data)[1], "mean: ", signif(CompoundData$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(CompoundData$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(CompoundData$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(CompoundData$Control2,2)))

        fig = fig %>% layout(title = data$Molecule[1],
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(x, "FC")),
                       yaxis = list(title = paste(y, "FC")),
                       showlegend = T)

   fig

}
```

```{r echo = F}

CompoundData = Df.reverse.metabs[1,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[2,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[3,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[4,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[6,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[7,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[8,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[10,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[14,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[15,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[16,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[17,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[18,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[20,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[21,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[22,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = Df.reverse.metabs[23,]

x = 'GRxWT.C'
y = 'GR.DfxWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktDfWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FDfxWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MDfxWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktDfGR.F', 'TktDfWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktDfGR.M', 'TktDfWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

##comparisons
primary = 'GRxWT.C'
rescue  = 'GR.CxOE'

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

min.expression = 0

##Reversal pattern
FC.data = metab.FC[, c(primary, rescue)]

FC.data = rbind(FC.data[FC.data[,primary] < 0 & FC.data[,rescue] > 0,],
                FC.data[FC.data[,primary] > 0 & FC.data[,rescue] < 0,])
FC.data = na.omit(FC.data)
reversals = row.names(FC.data)

##FC cutoff (currently a 25% increase or decrease in at least 1 condition)
FC.cutoff = rbind(FC.data[FC.data[,primary]  < -log2(1.25) & FC.data[,rescue] > log2(1.25),],
              FC.data[FC.data[,primary]  > log2(1.25) & FC.data[,rescue] < -log2(1.25),])
FC.cutoff = row.names(FC.cutoff)
FC.cutoff = na.omit(FC.cutoff)

##Sig cutoff. Currently, at least 1 significant change
sig.rescue = metab.FDR[metab.FDR[,primary]  < .05 |
                       metab.FDR[,rescue] < .05, ]
sig.rescue = row.names(sig.rescue)
sig.rescue = na.omit(sig.rescue)

reversal.metabs = intersect(intersect(reversals, FC.cutoff),sig.rescue)

FC.data = metab.FC[reversal.metabs, c(primary, rescue)]

  FC.data = metab.FC[reversal.metabs, c(x, y)]
  FDR.data = metab.FDR[reversal.metabs, c(x, y)]
  mean.data = mean.data[reversal.metabs, ]

data = data.frame(Metab = reversal.metabs,
                  compoundID = KEGG.Key[reversal.metabs],
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.mean = mean.data[,1],
                  Control1.mean = mean.data[,2],
                  Variable2.mean = mean.data[,3],
                  Control2.mean = mean.data[,4])

  main.title = "TKT-OE Reversal Metabolites"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = data$size

 OE.reverse.metabs = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Metabolite:", data$Metab,
                                  "\n ", colnames(FDR.data)[1], "p: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "p: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig

```

```{r echo = F}

CompoundData = OE.reverse.metabs[1,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[2,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[3,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[4,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[5,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[7,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[8,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[9,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[10,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[11,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

CompoundData = OE.reverse.metabs[12,]

x = 'GRxWT.C'
y = 'GR.OExWT.C'

mean.data = mean.metab[, c('GR', 'WT', 'TktOEGR', 'TktOEWT')]

Fx = 'GRxWT.FC'
Fy = 'GR.FOExWT.FC'

Mx = 'GRxWT.MC'
My = 'GR.MOExWT.MC'

Fmean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'TktOEGR.F', 'TktOEWT.F')]
Mmean.data = G85R.meancpm[, c('GR.M', 'WT.M', 'TktOEGR.M', 'TktOEWT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, Fy, Mx, My, Fmean, Mmean)

```

```{r echo = F}

##Sample titles as strings. Only fill in up to your number of selected categories
set1="Df"
set2="OE"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = row.names(Df.reverse.metabs)
s2 = row.names(OE.reverse.metabs)

main = "Reversal Metabolites"

  grid.newpage()
draw.pairwise.venn(area1=length(s1),area2=length(s2),cross.area=length(intersect(s1,s2)),fill = c("blue","red"),cex=1.5,cat.cex = 1,category = c(set1,set2), main = "main")

```

```{r echo = F}

##comparisons
primary = 'GR.CxDf'
rescue  = 'GR.CxOE'

x = 'GR.CxDf'
y = 'GR.CxOE'

mean.data = mean.metab[, c('GR', 'WT', 'TktDfGR', 'TktOEGR')]

min.expression = 0

reversal.metabs = intersect(row.names(Df.reverse.metabs), row.names(OE.reverse.metabs))

  FC.data = metab.FC[reversal.metabs, c(x, y)]
  FDR.data = metab.FDR[reversal.metabs, c(x, y)]
  mean.data = mean.data[reversal.metabs, ]

data = data.frame(Metab = reversal.metabs,
                  compoundID = KEGG.Key[reversal.metabs],
                  FDR1 = -log2(FDR.data[, x]),
                  FDR2 = -log2(FDR.data[, y]),
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.mean = mean.data[,1],
                  Control1.mean = mean.data[,2],
                  Variable2.mean = mean.data[,3],
                  Control2.mean = mean.data[,4])

  main.title = "TKT-Rescue Common Reversal Metabolites"

  data$Color[(data$FC1 - 1) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  size = data.frame(G85R = apply(mean.data[,c(1,3)], 1, mean),
                    WT = mean.data[,c(2)])
  size = size + .001
  data$size = log2(apply(size, 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = data$size

 OE.reverse.metabs = data

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Metabolite:", data$Metab,
                                  "\n ", colnames(FDR.data)[1], "p: ", round(2^-data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "p: ", round(2^-data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - 1,
                         x1 = max(data$FC1, data$FC2) + 1,
                         y0 = min(data$FC1, data$FC2) - 1,
                         y1 = max(data$FC1, data$FC2) + 1),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  fig

```

##Common Reversal Metabolites:

##pyridoxal, D-sedoheptulose-7-phosphate, 2,3-bisphospho-D-glycerate, NAD+, hydroxyphenyllactic acid / HVA, adenine, urea

### 2024-09-27 gbbmeetingfigures.Rmd
Dina Folder Update

---
title: "gbb conference analyses"
author: "John Santiago"
date: "2024-07-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F, echo = F}

library(plotly)
library(edgeR)
library(org.Dm.eg.db)
library(VennDiagram)

gbb.genes = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/BMP Signaling Genes.csv",row.names=1)

##Clean Trait Data and calculate CPMs
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)
groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/All.TKT.metadata.csv",row.names=1)

groups = groups[setdiff(row.names(groups), c("GR.F3", "WT.F3", "TktDfWT.F3")),]
##normalize data
countdata=countdata[, row.names(groups)]
countdata = countdata[-(grep("ti",row.names(countdata))),]
countdata = countdata[-(grep("trans",row.names(countdata))),]

x <- countdata
gr <- factor(groups$Group)
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
GR.cpmdata=cpm(z)

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)
plotQLDisp(fit)

##Will calculate fold-change with the first over the second
compare = makeContrasts(TktDfGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.FCxGR.FDf  = DEout
sWT.FCxGR.FDf = DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.MCxGR.MDf  = DEout
sWT.MCxGR.MDf = DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.F-GR.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FOExGR.F  = DEout
sGR.FOExGR.F = DEout[DEout$FDR<.05,]

compare = makeContrasts(TktOEGR.M-GR.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MOExGR.M  = DEout
sGR.MOExGR.M = DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfWT.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.FDfxWT.F  = DEout
sWT.FDfxWT.F = DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfWT.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.MDfxWT.M  = DEout
sWT.MDfxWT.M = DEout[DEout$FDR<.05,]

compare = makeContrasts(GR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.F = DEout

compare = makeContrasts(GR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.M  = DEout

compare = makeContrasts(TktOEGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRDf.F  = DEout

compare = makeContrasts(TktOEGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRDf.M  = DEout

compare = makeContrasts(TktOEWT.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WTDf.F  = DEout

compare = makeContrasts(TktOEWT.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WTDf.M  = DEout

gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
gbbOE = gbbOE[,row.names(gbbOE.groups)]
gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)

#anqi.sampletrim = c("AHH0001",	"AHH0002",	"AHH0003",	"AHH0004",	"AHH0007",	#"AHH0008",	"AHH0009",	"AHH0011",	"AHH0012",	"AHH0015",	"AHH0016",	#"AHH0018",	"AHH0019",	"AHH0026")
#gbbOE= gbbOE[,anqi.sampletrim]
#gbbOE.groups = gbbOE.groups[anqi.sampletrim,]

#anqi.genetrim = row.names(read.csv('/Users/johncsantiago/Documents/gbbOE.CPM_c#ounts_all samples.csv', row.names =1))

#gbbOE= na.omit(gbbOE[anqi.genetrim,anqi.sampletrim])
#gbbOE.groups = gbbOE.groups[anqi.sampletrim,]

##normalize data
countdata=gbbOE
x <- countdata
gr <- factor(gbbOE.groups$group, levels=c(unique(gbbOE.groups$group)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbOE.cpmdata=cpm(z)

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)
plotQLDisp(fit)

compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.LL3=DEout
sGRxWT.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(LoxP_LL3-G85R_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WTxGR.LL3=DEout
sWTxGR.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_ML3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRxWT.ML3=DEout
sGRxWT.ML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_LL3-G85R_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.LL3xML3=DEout
sGR.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(LoxP_LL3-LoxP_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.LL3xML3=DEout
sWT.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-G85R_gbb_ML3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbb.LL3xML3=DEout
sG85R_gbb.LL3xML3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-G85R_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbbxGR.LL3=DEout
sG85R_gbbxGR.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbbxWT.LL3=DEout
sG85R_gbbxWT.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-G85R_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbbxG85R.LL3=DEout
sG85R_gbbxG85R.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85RxLoxP.LL3=DEout
sG85RxLoxP.LL3=DEout[DEout$FDR<.05,]

compare = makeContrasts(G85R_gbb_LL3-LoxP_LL3, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
G85R_gbbxLoxP.LL3=DEout
sG85R_gbbxLoxP.LL3=DEout[DEout$FDR<.05,]

gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)

gbbKO = gbbKO[,colnames(gbbKO)!= 'AHH0025']
##gbbKO.groups = gbbKO.groups[row.names(gbbKO.groups)!= 'AHH0025',]

anqi.genetrim = row.names(read.csv('/Users/johncsantiago/Documents/gbbKO.CPM_170629_gbbKnockout.csv', row.names =1))

gbbKO = (gbbKO[anqi.genetrim,])

##normalize data
countdata=gbbKO
x <- countdata
gr <- factor(gbbKO.groups$Genotype[1:5], levels=c(unique(gbbKO.groups$Genotype[1:5])))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
##normalized cpm
gbbKO.cpmdata=cpm(z)

design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)
plotQLDisp(fit)

compare = makeContrasts(KO-WT, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
gbbKO.DEG=DEout
sgbbKO.DEG=DEout[DEout$FDR<.05,]

gbbKO.mean = data.frame(gbbKO.DEG[,1:2])
gbbKO.mean[,1] = apply(gbbKO.cpmdata[row.names(gbbKO.mean),
                                     c('AHH0020', 'AHH0021', 'AHH0027')], MARGIN = 1, mean)
gbbKO.mean[,2] = apply(gbbKO.cpmdata[row.names(gbbKO.mean),
                                     c('AHH0023', 'AHH0024')], MARGIN = 1, mean)
                                     ##c('AHH0023', 'AHH0024', 'AHH0025')], MARGIN = 1, mean)
colnames(gbbKO.mean) = c("WT", "KO")

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

```

```{r echo = F}

gbbKOGRxWT = row.names(gbbKO.DEG[gbbKO.DEG$FDR <.1,])
tktDfWTxWT.F = row.names(WT.FDfxWT.F[WT.FDfxWT.F$FDR <.05,])
tktDfWTxWT.M = row.names(WT.MDfxWT.M[WT.MDfxWT.M$FDR <.05,])

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "G85R-gbbKO vs WT (pvalue < .05)"
set2 = "Female WT-TKT.Df vs WT (FDR < .05)"
set3 = "Male WT-TKT.Df vs WT (FDR < .05)"
set4 = "BMP Pathway"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = gbbKOGRxWT
s2 = tktDfWTxWT.F
s3 = tktDfWTxWT.M
s4 = row.names(gbb.genes)

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)

```

```{r echo = F}

gbbKOGRxWT = row.names(G85R_gbbxG85R.LL3[G85R_gbbxG85R.LL3$PValue <.05,])
tktOEGRxGR.F = row.names(GR.FOExGR.F[GR.FOExGR.F$FDR <.05,])
tktOEGRxGR.M = row.names(GR.MOExGR.M[GR.MOExGR.M$FDR <.05,])

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "G85R-gbbKO vs WT (p-value < .05)"
set2 = "Female G85R-TKT.OE vs WT (FDR < .05)"
set3 = "Male G85R-TKT.OE vs WT (FDR < .05)"
set4 = "BMP Pathway"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = gbbKOGRxWT
s2 = tktOEGRxGR.F
s3 = tktOEGRxGR.M
s4 = row.names(gbb.genes)

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)

```

```{r echo = F}

gbbOExWT = row.names(G85R_gbbxLoxP.LL3[G85R_gbbxLoxP.LL3$PValue <.05,])
GRxWT = row.names(G85RxLoxP.LL3[G85RxLoxP.LL3$PValue <.05,])
gbbOExG85R = row.names(G85R_gbbxG85R.LL3[G85R_gbbxG85R.LL3$PValue <.05,])

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "G85R-gbbOE vs WT (pvalue < .05)"
set2 = "G85R vs WT (FDR < .05)"
set3 = "G85R-gbbOE vs G85R (FDR < .05)"
set4 = "BMP Pathway"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = gbbOExWT
s2 = GRxWT
s3 = gbbOExG85R
s4 = row.names(gbb.genes)

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)

```

```{r echo = F}

grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

#Quad Venn
grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)

```

```{r}

  FC.data = setNames(gbbKO.DEG[,1], row.names(gbbKO.DEG))
  FDR.data = setNames(gbbKO.DEG[,4], row.names(gbbKO.DEG))
  mean.data = gbbKO.mean[,1:2]

  ##select F if you want point size to scale with mean cpm of variable data
  set.size = F
  ##select T if you only want the genes in category to show
  catgenes.only = T

  volcano.data = data.frame(Symbol = GeneIDKey[names(FDR.data), "Symbol"], 
                            FDR = -log2(FDR.data),
                            FC = FC.data,
                            Color = 'grey',
                            size = 5*log(mean.data[,1]+2),
                            Variable.cpm = mean.data[,1],
                            Control.cpm = mean.data[,2])

  if(set.size == T){
    volcano.data$size = 15
    volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
  }

  volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
  volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
  volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

  volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
  volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
  volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

  main.title = paste(colnames(mean.data)[1], "vs. ", colnames(mean.data)[2])

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

volcano.data = volcano.data[volcano.data$FDR >= -log2(.1),]

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                                "\n-log2(FDR): ", round(volcano.data$FDR,2),
                                "\nFC: ", round(volcano.data$FC,2),
                                "\n ", colnames(mean.data)[1], "mean cpm: ",
                                round(volcano.data$Variable.cpm, 1),
                                "\n ", colnames(mean.data)[2], "mean cpm: ",
                                round(volcano.data$Control.cpm, 1)))
fig = fig %>% layout(title = main.title,
                     yaxis = list(ymin = 0, ymax = 9))

fig

```

```{r echo = F, warning = F}

library(goseq)

FDR = gbbKO.DEG
  sigs = row.names(FDR)[FDR[,'FDR'] < .05]
  bg = row.names(FDR)

  sigsKEY = GeneIDKey[sigs,]
  sigs = na.omit(sigsKEY$Symbol)
  bgKEY = GeneIDKey[bg,]
  bg = na.omit(bgKEY$Symbol)

  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=GenesInKegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=KEGG.Names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")

```

```{r}

  GO.data = enrichment.data$GO
  GO.ontology = "BP"

  go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .05 & 
                                   GO.data$ontology == GO.ontology]
  scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

  simMatrix <- calculateSimMatrix(go_analysis,
                                  orgdb="org.Dm.eg.db",
                                  ont=GO.ontology,
                                  method="Rel")

  reducedTerms <- reduceSimMatrix(simMatrix,
                                  scores,
                                  threshold=0.7,
                                  orgdb="org.Dm.eg.db")

```

```{r}

treemapPlot(reducedTerms)

```

```{r echo = F, warning = F}

library(goseq)

FDR = G85R_gbbxG85R.LL3
  sigs = row.names(FDR)[FDR[,'FDR'] < .1]
  bg = row.names(FDR)

  sigsKEY = GeneIDKey[sigs,]
  sigs = na.omit(sigsKEY$Symbol)
  bgKEY = GeneIDKey[bg,]
  bg = na.omit(bgKEY$Symbol)

  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=GenesInKegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=KEGG.Names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")

```

```{r}

  GO.data = enrichment.data$GO
  GO.ontology = "BP"

  go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .05 & 
                                   GO.data$ontology == GO.ontology]
  scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

  simMatrix <- calculateSimMatrix(go_analysis,
                                  orgdb="org.Dm.eg.db",
                                  ont=GO.ontology,
                                  method="Rel")

  reducedTerms <- reduceSimMatrix(simMatrix,
                                  scores,
                                  threshold=0.7,
                                  orgdb="org.Dm.eg.db")

```

```{r}

treemapPlot(reducedTerms)

```

```{r echo = F, warning = F}

library(goseq)
temp = read.csv('/Users/johncsantiago/Downloads/LoxP-G85R_LL3.csv',
                row.names = 1, header = T)

FDR = G85RxLoxP.LL3
  sigs = row.names(FDR)[FDR[,'FDR'] < .1]
  bg = row.names(FDR)

  sigsKEY = GeneIDKey[sigs,]
  sigs = na.omit(sigsKEY$Symbol)
  bgKEY = GeneIDKey[bg,]
  bg = na.omit(bgKEY$Symbol)

  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=GenesInKegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=KEGG.Names[row.names(KEGG),1]

  enrichment.data = list(GO.wall, KEGG)
  names(enrichment.data) = c("GO", "KEGG")

```

```{r}

  GO.data = enrichment.data$GO
  GO.ontology = "BP"

  go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .05 & 
                                   GO.data$ontology == GO.ontology]
  scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

  simMatrix <- calculateSimMatrix(go_analysis,
                                  orgdb="org.Dm.eg.db",
                                  ont=GO.ontology,
                                  method="Rel")

  reducedTerms <- reduceSimMatrix(simMatrix,
                                  scores,
                                  threshold=0.7,
                                  orgdb="org.Dm.eg.db")

```

```{r}

treemapPlot(reducedTerms)

```

```{r echo = F, message = F}

library(heatmaply)
library(dendextend)

counts = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.countdata.csv", row.names = 1)

cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)

meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)

FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)

FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)

meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)

bmp = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/BMP Signaling Genes annotated.csv', row.names = 1, header = T)
#bmp = bmp[intersect(row.names(bmp), row.names(GR.cpm)),]

bmp$fb = row.names(bmp)

bmp = bmp[,1:4]

bmp.set = GeneIDKey[GeneIDKey$Symbol %in% setdiff(c("cmpy", "nmo", "Neto", "LIMK1", 'trio',
                                            "spartin", "GluRIIA", 'GluRIIB', 'Rac1',
                                            'spin', 'hiw', 'faf'), bmp$X.1),]
bmp.set = bmp.set[,2:5]
colnames(bmp.set) =  colnames(bmp)
bmp.set[,2] = "Others"
bmp.set[,3] = ""
bmp.set[,4] = ""

bmp=rbind(bmp, bmp.set)

bmpcpm = cpm[intersect(row.names(bmp), row.names(cpm)),]

GR.bmp = GR.cpm[intersect(row.names(GR.cpm), row.names(bmp)),]

GR.mean = matrix(rep(0, 12*nrow(GR.bmp)), ncol = 12)
colnames(GR.mean) = unique(GR.meta$Group)
row.names(GR.mean) = row.names(GR.bmp)

i = 1
while(i <= ncol(GR.mean)){
  GR.mean[,i] = apply(GR.bmp[,row.names(GR.meta)[GR.meta$Group == colnames(GR.mean)[i]]], 1, mean)
  i = i +1
}

GR.mean.meta = GR.meta[GR.meta$Replicate == 1, c(1:3,5)]
row.names(GR.mean.meta) = GR.mean.meta$Group

```

```{r}

GR.FC = data.frame(GR.F = GR.F[row.names(bmp), 'logFC'],
                   GRDf.F = GRDf.F[row.names(bmp), 'logFC'],
                   WTDf.F = WTDf.F[row.names(bmp), 'logFC'],
                   GR.M = GR.M[row.names(bmp), 'logFC'],
                   GRDf.M = GRDf.M[row.names(bmp), 'logFC'],
                   WTDf.M = WTDf.M[row.names(bmp), 'logFC'])
row.names(GR.FC) = bmp[,1]
GR.FC = na.omit(GR.FC)

##scaled = (2^(abs(GR.FC)))*(GR.FC/abs(GR.FC))
scaled = GR.FC
Title = " "
branches=3

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdBu(5)[5:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))
#Mhmdata=hmdata

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
#Fhmdata=hmdata

allscaled = cbind(Fhmdata,Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "both",
          Rowv=colordend,
          ##Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

A4V.groups = A4V.meta[A4V.meta$Replicate == 1,]
row.names(A4V.groups) = A4V.groups$Group
A4V.groups = A4V.groups[colnames(A4V.meancpm),]

hmgroups = A4V.groups[A4V.groups$Sex == "M",]
hmgroups = hmgroups[c('S3MT', 'S9MT', 'A3MT', 'A9MT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = A4V.groups[A4V.groups$Sex == "F",]
hmgroups = hmgroups[c('S3FT', 'S9FT', 'S40FT', 'A3FT', 'A9FT', 'A40FT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
#Fhmdata=hmdata

allscaled = cbind(Fhmdata,Mhmdata)

scaled = allscaled[intersect(row.names(bmp), row.names(allscaled)),]
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

A4V.groups = A4V.meta[A4V.meta$Replicate == 1,]
row.names(A4V.groups) = A4V.groups$Group
A4V.groups = A4V.groups[colnames(A4V.meancpm),]

hmgroups = A4V.groups[A4V.groups$Sex == "M",]
hmgroups = hmgroups[c('S3MT', 'S9MT', 'A3MT', 'A9MT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = A4V.groups[A4V.groups$Sex == "F",]
hmgroups = hmgroups[c('S3FT', 'S9FT', 'S40FT', 'A3FT', 'A9FT', 'A40FT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
#Fhmdata=hmdata

allscaled = cbind(Fhmdata)

scaled = allscaled[intersect(row.names(bmp), row.names(allscaled)),]
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

A4V.groups = A4V.meta[A4V.meta$Replicate == 1,]
row.names(A4V.groups) = A4V.groups$Group
A4V.groups = A4V.groups[colnames(A4V.meancpm),]

hmgroups = A4V.groups[A4V.groups$Sex == "M",]
hmgroups = hmgroups[c('S3MT', 'S9MT', 'A3MT', 'A9MT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = A4V.groups[A4V.groups$Sex == "F",]
hmgroups = hmgroups[c('S3FT', 'S9FT', 'S40FT', 'A3FT', 'A9FT', 'A40FT'),]

hmdata = A4V.meancpm[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
#Fhmdata=hmdata

allscaled = cbind(Mhmdata)

scaled = allscaled[intersect(row.names(bmp), row.names(allscaled)),]
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

hmgroups = gbbOE.groups[gbbOE.groups$stage == "LL3",]
hmgroups = setNames(unique(hmgroups$group), unique(hmgroups$genotype))

hmdata = gbbOEmean[, hmgroups]
colnames(hmdata) = names(hmgroups)
hmdata=t(scale(t(hmdata)))
hmdata = hmdata[intersect(row.names(bmp), row.names(hmdata)),]
row.names(hmdata) = bmp[row.names(hmdata), 1]

scaled = hmdata
Title = " "
branches=3

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

gbb.plotdata = data.frame(genotype = gbbOE.groups[colnames(gbbOE.cpmdata), 'group'],
                          gbb = gbbOE.cpmdata["FBgn0037607",])
                          ##gbb = gbbOE.cpmdata["FBgn0024234",])

gbb.plotdata$genotype = factor(gbb.plotdata$genotype,
                               levels = c("LoxP_ML3", "LoxP_LL3",
                                          "G85R_ML3", "G85R_LL3",
                                          "G85R_gbb_ML3", "G85R_gbb_LL3"))

boxplot(gbb.plotdata$gbb ~ gbb.plotdata$genotype, 
        xlab="",     
        main= "",
        ylab="gbb cpm", 
        las = 1, 
        cex.axis = .8)

points(x=as.numeric(factor(gbb.plotdata$genotype)),
       y=gbb.plotdata$gbb,
       cex=2,
       pch=21,
       bg=c('red', 'firebrick',
            'dodgerblue', "steelblue", 
            "limegreen", 'darkgreen')
       [as.numeric(factor(gbb.plotdata$genotype))])

```

```{r}

gbbOE.plotdata = data.frame(GR.FC = G85RxLoxP.LL3[intersect(row.names(bmp), row.names(G85RxLoxP.LL3)), "logFC"],
                            OE.FC = G85R_gbbxLoxP.LL3[intersect(row.names(bmp), row.names(G85RxLoxP.LL3)), "logFC"])
row.names(gbbOE.plotdata) = bmp[intersect(row.names(bmp), row.names(G85RxLoxP.LL3)), 1]

data = data.frame(Symbol = row.names(gbbOE.plotdata),
                  FC1 = gbbOE.plotdata$GR.FC,
                  FC2 = gbbOE.plotdata$OE.FC,
                  Color = 'grey',
                  size = gbbOEmean[intersect(row.names(bmp), row.names(G85RxLoxP.LL3)), 'LoxP_LL3'],
                  LoxP = gbbOEmean[intersect(row.names(bmp), row.names(G85RxLoxP.LL3)), 'LoxP_LL3'])

  main.title = 'FC relative to LoxP'

  data$Color[(data$FC1 - log2(1.5)) > data$FC2] = 'royalblue'
  data$Color[(data$FC2 - log2(1.5)) > data$FC1] = 'firebrick' 
  data$size = log2(data$size)
  data$size[data$size < 2] = 2

fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2, 2),
              "\n LoxP mean cpm: ", round(data$LoxP, 2)))
  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = -1,
                         x1 = 1,
                         y0 = -1.2,
                         y1 = 1.2),
                       xaxis = list(title = "G85R FC"),
                       yaxis = list(title = "gbbOE FC"))

  fig

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))
#Mhmdata=hmdata

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
#Fhmdata=hmdata

allscaled = cbind(Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

hmgroups = gbbOE.groups[gbbOE.groups$stage == "LL3",]
hmgroups = setNames(unique(hmgroups$group), unique(hmgroups$genotype))

hmdata = gbbOEmean[, hmgroups]
colnames(hmdata) = names(hmgroups)
hmdata=t(scale(t(hmdata)))
hmdata = hmdata[intersect(row.names(bmp), row.names(hmdata)),]
row.names(hmdata) = bmp[row.names(hmdata), 1]
hmdata = hmdata[intersect(row.names(Fhmdata),row.names(hmdata)),]

heatmaply(hmdata,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = Title)

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$X.2 == 'BMP binding',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'BMP binding')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = "BMP Binding")

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Mhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'BMP Binding')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
#Mhmdata=t(scale(t(hmdata)))
Mhmdata=hmdata

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
#Fhmdata=t(scale(t(hmdata)))
Fhmdata=hmdata

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$X.2 == 'ligand',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Ligand')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Ligands')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Mhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Ligands')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$X.2 == 'receptor',]
scaled = scaled[bmp.set$X.1,]
scaled = scaled[row.names(scaled)!='lili',]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Receptor')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Receptors')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Mhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Receptors')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = c("Mad", "Med", 'smox', 'Dad')
scaled = scaled[bmp.set,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Smads')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Smads')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Mhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Smads')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
#Mhmdata=t(scale(t(hmdata)))
Mhmdata=hmdata

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
#Fhmdata=t(scale(t(hmdata)))
Fhmdata=hmdata

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]

allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = c("cmpy", "nmo", "Neto", "LIMK1", 'trio',
            "spartin", "GluRIIA", 'GluRIIB', 'Rac1',
            'spin', 'hiw', 'faf')

scaled = scaled[bmp.set,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Others')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Fhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Others')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

row.names(Mhmdata) = bmp[row.names(Mhmdata),1]
Mhmdata = Mhmdata[row.names(scaled),]
Mhmdata = Mhmdata[hc$order,]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

row.names(Fhmdata) = bmp[row.names(Fhmdata),1]
Fhmdata = Fhmdata[row.names(scaled),]
Fhmdata = Fhmdata[hc$order,]

heatmaply(Mhmdata[row.names(scaled),],
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "none",
          Rowv= "NA",
          Colv="NA",
          cexRow = .9,
          main = 'Others')

```
```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$X.2 == 'TF',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Transcription Factor')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'negative',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Negative Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'positive',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Positive Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'negative',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Negative Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'positive',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Positive Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'negative',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Negative Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

bmp.set = bmp[row.names(scaled),]

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

bmp.set = bmp.set[bmp.set$pathway.regulator == 'positive',]
scaled = scaled[bmp.set$X.1,]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = 'Positive Regulators')

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]
Mhmgroups = hmgroups

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]
Fhmgroups = hmgroups

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata,Mhmdata)
allgroups = rbind(Fhmgroups, Mhmgroups)
allgroups$Group = paste(allgroups$Genotype, allgroups$TKT)
allgroups$Labels = paste(row.names(allgroups), allgroups$TKT)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

    use.data   = allscaled
    use.groups = allgroups
    pca <- prcomp(t(use.data), scale.=TRUE) 
    gr <- as.data.frame(use.groups)
    PC1=scale(pca$x[,1])
    PC2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=row.names(gr),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=gr$Genotype, 
                        Sex=gr$Sex, 
                        TKT=gr$TKT,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group=gr$Group,
                        Label = gr$Label)

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Label,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Sex,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 colors = c("firebrick","gold","royalblue", 'darkgreen'),
                 marker = list(size = 25,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")))

fig

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]
hmgroups = GR.meta[GR.meta$Group %in% row.names(hmgroups),]

hmdata = GR.bmp[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))
Mhmgroups = hmgroups

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]
hmgroups = GR.meta[GR.meta$Group %in% row.names(hmgroups),]

hmdata = GR.bmp[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))
Fhmgroups = hmgroups

allscaled = cbind(Fhmdata,Mhmdata)
allgroups = rbind(Fhmgroups, Mhmgroups)
allgroups$Group = paste(allgroups$Genotype, allgroups$TKT)
allgroups$Labels = paste(allgroups$Genotype, paste(allgroups$Sex, allgroups$TKT))
alldata = GR.bmp[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

    use.data   = allscaled
    use.groups = allgroups
    pca <- prcomp(t(use.data), scale.=TRUE) 
    gr <- as.data.frame(use.groups)
    PC1=scale(pca$x[,1])
    PC2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=row.names(gr),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=gr$Genotype, 
                        Sex=gr$Sex, 
                        TKT=gr$TKT,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group=gr$Group,
                        Label = gr$Label)

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Label,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Sex,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 colors = c("firebrick","gold","royalblue", 'darkgreen'),
                 marker = list(size = 25,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")))

fig

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]
hmgroups = GR.meta[GR.meta$Group %in% row.names(hmgroups),]

hmdata = GR.bmp[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]
hmgroups = GR.meta[GR.meta$Group %in% row.names(hmgroups),]

hmdata = GR.bmp[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Fhmdata, Mhmdata)
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmdata = GR.mean[, row.names(hmgroups)]
Mhmdata=t(scale(t(hmdata)))

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

hmdata = GR.mean[, row.names(hmgroups)]
Fhmdata=t(scale(t(hmdata)))

allscaled = cbind(Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

hc <- hclust(dist(scaled), "complete")
heights=sort(hc$height,decreasing = T)

if(branches>1){
  cutheight=heights[branches]
}

if(branches==1){
  cutheight=max(heights)+1
}

dnd=cut(as.dendrogram(hc),h=cutheight)

if(branches>1){
  branchcolors=colors[1:length(dnd$lower)]
}
if(branches==1){
  branchcolors="black"
}

colordend=(color_branches(hc, h=cutheight, col=branchcolors))

heatmaply(scaled,
          trace="none",
          col=RdYlBu(100)[100:1],
          dendrogram = "row",
          Rowv=colordend,
          Colv="NA",
          cexRow = 1,
          main = Title)

```

```{r}

GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
Df.data = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
Df.key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/DfKey.csv", row.names = 1)

bmp.df = Df.data[row.names(Df.data) %in% row.names(bmp),]

bmp.df = bmp.df[bmp.df$Repress == 1 | bmp.df$Enhancer == 1,]

bmp.df.info = GeneIDKey[row.names(GeneIDKey) %in% row.names(bmp.df),]

bmp.df.info$MLE = 0
i = 1
while(i<=nrow(bmp.df.info)){
  temp = Df.key[Df.key$Chr == bmp.df.info$CHR[i],]
  temp = temp[(temp$Start < bmp.df.info$Start[i] & temp$End > bmp.df.info$Start[i]) | 
                (temp$Start < bmp.df.info$End[i] & temp$End > bmp.df.info$End[i]) |
                (temp$Start > bmp.df.info$Start[i] & temp$End < bmp.df.info$End[i]),]
  bmp.df.info[i, 'MLE'] = max(as.numeric(temp$MLE))
  i = i + 1
}

bmp.df.info = na.omit(bmp.df.info)
bmp.df.info = bmp.df.info[order(bmp.df.info$MLE),]
bmp.df.info = bmp.df.info[abs(bmp.df.info$MLE)>=2 & abs(bmp.df.info$MLE)<=100, ]
bmp.df.info$color = 'brown'
bmp.df.info$color[bmp.df.info$MLE <= 5] = "orangered3"
bmp.df.info$color[bmp.df.info$MLE <= 3] = "orange3"
bmp.df.info$color[bmp.df.info$MLE <= 2.5] = "orange"
bmp.df.info$color[bmp.df.info$MLE <= 2] = "goldenrod1"
bmp.df.info$color[bmp.df.info$MLE < 0] = "steelblue"

barplot(height = bmp.df.info$MLE,
        names.arg = bmp.df.info$Symbol,
        beside =T,
        horiz = T,
        las = 1,
        cex.names = .55,
        cex.axis = .55,
        col = bmp.df.info$color,
        xlim = c(-4,8))

```

```{r warning=FALSE}

bmp.df.info = GeneIDKey[row.names(GeneIDKey) %in% row.names(bmp),]

bmp.df.info$MLE = 0
i = 1
while(i<=nrow(bmp.df.info)){
  temp = Df.key[Df.key$Chr == bmp.df.info$CHR[i],]
  temp = temp[(temp$Start < bmp.df.info$Start[i] & temp$End > bmp.df.info$Start[i]) | 
                (temp$Start < bmp.df.info$End[i] & temp$End > bmp.df.info$End[i]) |
                (temp$Start > bmp.df.info$Start[i] & temp$End < bmp.df.info$End[i]),]
  bmp.df.info[i, 'MLE'] = max(as.numeric(temp$MLE))
  i = i + 1
}

bmp.df.info = na.omit(bmp.df.info)
bmp.df.info = bmp.df.info[order(bmp.df.info$MLE),]
bmp.df.info = bmp.df.info[abs(bmp.df.info$MLE)<=100, ]
bmp.df.info$color = 'green4'
bmp.df.info$color[bmp.df.info$MLE <= 5] = "limegreen"
bmp.df.info$color[bmp.df.info$MLE <= 3] = "yellowgreen"
bmp.df.info$color[bmp.df.info$MLE <= 2.5] = "gold"
bmp.df.info$color[bmp.df.info$MLE <= 2] = "yellow2"
bmp.df.info$color[bmp.df.info$MLE <= 1.5] = "antiquewhite2"
bmp.df.info$color[bmp.df.info$MLE <= 1] = "antiquewhite"
bmp.df.info$color[bmp.df.info$MLE <= .5] = "white"
bmp.df.info$color[bmp.df.info$MLE < -1] = "antiquewhite"
bmp.df.info$color[bmp.df.info$MLE <= -1.5] = "antiquewhite2"
bmp.df.info$color[bmp.df.info$MLE < -2] = "firebrick"

barplot(height = bmp.df.info$MLE,
        names.arg = bmp.df.info$Symbol,
        beside =T,
        horiz = T,
        las = 1,
        cex.names = .75,
        cex.axis = .75,
        col = bmp.df.info$color,
        xlim = c(-4,8),
        xlab = "MLE")

```

### 2024-09-27 GOandKEGGPlottingFunctions.R

@@ -1,0 +1,1097 @@
+
+library(plotly)
+library(goseq)
+library(org.Dm.eg.db)
+library(rrvgo)
+library(pathview)
+library(VennDiagram)
+
+A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
+A4V.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
+A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
+A4V.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
+A4V.meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
+
+A4V.comparekey = setNames(colnames(A4V.FDR),
+                          c('A3FHvS3FH', 'A3MHvS3MH', 'A9FHvS9FH', 'A9MHvS9MH', 'A40FHvS40FH',
+                            'A3FHvA9FH', 'S3FHvS9FH', 'A3MHvA9MH', 'S3FHvS9MH',
+                            'A9FHvA40FH', 'S9FHvS40FH', 'A3FHvA40FH', 'S3FHvS40FH',
+                            
+                            'A3FTvS3FT', 'A3MTvS3MT', 'A9FTvS9FT', 'A9MTvS9MT', 'A40FTvS40FT',
+                            'A3FTvA9FT', 'S3FTvS9FT', 'A3MTvA9MT', 'S3FTvS9MT',
+                            'A9FTvA40FT', 'S9FTvS40FT', 'A3FTvA40FT', 'S3FTvS40FT',
+                            
+                            'A3FAvS3FA', 'A3MAvS3MA', 'A9FAvS9FA', 'A9MAvS9MA', 'A40FAvS40FA',
+                            'A3FAvA9FA', 'S3FAvS9FA', 'A3MAvA9MA', 'S3FAvS9MA',
+                            'A9FAvA40FA', 'S9FAvS40FA', 'A3FAvA40FA', 'S3FAvS40FA',
[…]

### 2024-11-06 Arc1MeetingFigures.Rmd
pca

@@
   FDR.data = TKT.EdgeR[, c("GRxWT.FC", "GRxWT.MC")]
-  mean.data = G85R.meancpm[, c('GRFC', 'WTFC', 'GRMC', 'WTMC')]
+  mean.data = G85R.meancpm[, c('GR.F', 'WT.F', 'GR.M', 'WT.M')]
 
@@
   ##data$Color[(data$FC2 - 1) > data$FC1] = 'firebrick' 
-  data$Color[data$Symbol == "Arc1"] = 'gold'
+  #data$Color[data$Symbol == "Arc1"] = 'gold'
   size = data.frame(G85R = apply(mean.data[go.genes,c(1,3)], 1, mean),
@@
 gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
-                  condition = A4V.groups$Group, 
+                  condition = A4V.meta$Group, 
                   group = paste0(groups$Genotype, groups$Sex),
@@
      col.axis = 'lightgrey')
-axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
-     lwd.ticks = 1, cex.axis = 1,
-     col.axis = 'black')
+#axis(1, at= c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90), 
+#     lwd.ticks = 1, cex.axis = 1,
+#     col.axis = 'black')
 
@@
                   'Male Silent', 'Male A4V'),
-       pch = c(23,21,23,21,23,21),
-       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
-                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
+       pch = c(21,23,21,23),
+       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), 
+                 hex(pcol[3], .5), hex(pcol[4], .5)),
        bty = 'n',
@@
 
-#abline(v = 3, lty = 2, lwd = 2, col = 'black')
-#abline(v = 9, lty = 2, lwd = 2, col = 'black')
-#abline(v = 40, lty = 2, lwd = 2, col = 'black')
+abline(v = 3, lty = 2, lwd = 2, col = 'black')
+abline(v = 9, lty = 2, lwd = 2, col = 'black')
+abline(v = 40, lty = 2, lwd = 2, col = 'black')
 
-#points(x = c(3,9,40),
-#       y = c(-11.75,-11.75,-11.75),
-#       pch = 21,
-#       cex = 4,
-#       bg = hex('gold', .25),
-#       col = 'grey25',
-#       xpd = T)
+points(x = c(3,9,40),
+       y = c(-11.75,-11.75,-11.75),
+       pch = 21,
+       cex = 4,
+       bg = hex('gold', .25),
+       col = 'grey25',
+       xpd = T)
 
-#axis(1, at= c(3, 9, 40), lwd.ticks = 2, labels = c(3,9,40))
+axis(1, at= c(3, 9, 40), lwd.ticks = 2, labels = c(3,9,40))
 

### 2024-11-06 GeneExpressionBoxPlots.Rmd
pca

@@
 ```{r echo = F}
-FBgn = 'FBgn0011817'
-name = 'FBgn0011817: nmo'
+
+FBgn = 'FBgn0032513'
+name = 'STARD7'
+FBgn = 'FBgn0028932'
+name = 'CG16890'
 
@@
 ```
+
+```{r echo = F}
+
+rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
+KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
+
+genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))
+
+metadata = data.frame(Sample = colnames(rawdata), 
+                      Group = as.character(rawdata[1,]), 
+                      TIC = as.numeric(rawdata[2,]), 
+                      Genotypes = genotypes[as.character(rawdata[1,])])
+
+row.names(metadata) = metadata$Sample
+
+norm.func = function(data){
+  nd = (as.numeric(data)/metadata$TIC)*1000
+  return(nd)
+}
+
+norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
+colnames(norm.data) = colnames(rawdata)
+
+group.mean=function(data){
+  gm = mean(na.omit(data))
+}
+
+mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
+row.names(mean.data) = row.names(norm.data)
+colnames(mean.data) = unique(metadata$Group)
+
+i=1
+while(i<=ncol(mean.data)){
+  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
+  i = i+1
+}
+
+mean.metab = mean.data
+
+compare.conditions = function(condition1, condition2){
+  columns1 = metadata[metadata$Group == condition1, "Sample"]
+  columns2 = metadata[metadata$Group == condition2, "Sample"]
+  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
+  i=1
+  while(i<=length(p)){
+    if(length(na.omit(norm.data[i,columns1]))>2 & 
+       length(na.omit(norm.data[i,columns2]))>2){
+      temp = t.test(na.omit(norm.data[i,columns1]),
+                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
+      p[i] = temp[[3]]
+      }
+    i=i+1
+    }
+
+  fdr = p.adjust(p, "BH", length(p))
+
+  fc = mean.metab[,condition1]/mean.metab[,condition2]
+
+  comparison.table = data.frame(p = p, 
+                                FDR = fdr, 
+                                FC = fc, 
+                                KEGG = KEGG.Key[row.names(mean.metab)])
+
+  comparison.table = comparison.table[order(comparison.table$FDR),]
+}
+
+GRxWT.C = compare.conditions("E", "C")
+GRxWT.Df = compare.conditions("D", "B")[row.names(GRxWT.C),]
+GRxWT.OE = compare.conditions("F", "A")[row.names(GRxWT.C),]
+
+GR.CxDf = compare.conditions("D", "E")[row.names(GRxWT.C),]
+WT.CxDf = compare.conditions("B", "C")[row.names(GRxWT.C),]
+
+GR.CxOE = compare.conditions("F", "E")[row.names(GRxWT.C),]
+WT.CxOE = compare.conditions("A", "C")[row.names(GRxWT.C),]
+
+GR.DfxWT.C = compare.conditions("D", "C")[row.names(GRxWT.C),]
+GR.OExWT.C = compare.conditions("F", "C")[row.names(GRxWT.C),]
+
+comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
+                 GRF.CxOE = c("TktOEGR.F","GR.F"),
+                 WTF.CxDf = c("TktDfWT.F","WT.F"),
+                 WTF.CxOE = c("TktOEWT.F","WT.F"),
+                 GRxWT.FC = c("GR.F","WT.F"), 
+                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
+                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
+                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
+                 GRM.CxOE = c("TktOEGR.M","GR.M"),
+                 WTM.CxDf = c("TktDfWT.M","WT.M"),
+                 WTM.CxOE = c("TktOEWT.M","WT.M"),
+                 GRxWT.MC = c("GR.M","WT.M"), 
+                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
+                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
+                 GR.FxM = c("GR.F","GR.M"),
+                 WT.FxM = c("WT.F","WT.M"))
+
+metab.FC = data.frame('GRxWT.C' = GRxWT.C$FC,
+                      'GRxWT.Df' = GRxWT.Df$FC,
+                      'GRxWT.OE' = GRxWT.OE$FC,
+                      'GR.CxDf' = GR.CxDf$FC,
+                      'WT.CxDf' = WT.CxDf$FC,
+                      'GR.CxOE' = GR.CxOE$FC,
+                      'WT.CxOE' = WT.CxOE$FC,
+                      'GR.DfxWT.C' = GR.DfxWT.C$FC,
+                      'GR.OExWT.C' = GR.OExWT.C$FC)
+row.names(metab.FC) = row.names(GRxWT.C)
+metab.FC = log2(metab.FC)
+
+metab.FDR = data.frame(GRxWT.C = GRxWT.C$p,
+                       GRxWT.Df = GRxWT.Df$p,
+                       GRxWT.OE = GRxWT.OE$p,
+                       GR.CxDf = GR.CxDf$p,
+                       WT.CxDf = WT.CxDf$p,
+                       GR.CxOE = GR.CxOE$p,
+                       WT.CxOE = WT.CxOE$p,
+                       GR.DfxWT.C = GR.DfxWT.C$p,
+                       GR.OExWT.C = GR.OExWT.C$p)
+row.names(metab.FDR) = row.names(GRxWT.C)
+
+colnames(mean.metab) = as.character(genotypes[colnames(mean.metab)])
+
+colnames(norm.data) = as.character(genotypes[substr(colnames(norm.data),1,1)])
+
+```
+
+```{r echo = F}
+
+metab = 'D-sedoheptulose-7-phosphate'
+name = 'D-sedoheptulose-7-phosphate'
+
+metab = data.frame(data = as.numeric(norm.data[metab,]), 
+                   group = colnames(norm.data), 
+                   geno = colnames(norm.data))
+
+metab$group = factor(metab$group, levels = c("WT", "TktDfWT", "TktOEWT",
+                                             "GR", "TktDfGR", "TktOEGR"))
+
+metab$geno = factor(substr(metab$group, (nchar(as.character(metab$group)) -1), nchar(as.character(metab$group))), 
+                     levels = c("WT", "GR"))
+
+par(mar = c(5,7,5,2))
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(min(metab$data), max(metab$data)),
+     xlim = c(.5, 6.5),
+     xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = NA)
+
+rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
+
+boxplot(metab$data~metab$group, 
+        xlab="",
+        las = 2, 
+        cex.axis = .8,
+        xaxt = 'none',
+        yaxt = 'none',
+        boxwex = .75,
+        boxlwd = 2,
+        lwd = 2,
+        cex.ticks = 2,
+        add = T,
+        col = c(rep("lightyellow", 3),
+                rep("lightgreen", 3)))
+
+box(lwd = 2)
+
+points(x=as.numeric(factor(metab$group)),
+       y=metab$data,
+       cex=1.25,
+       pch=21,
+       bg=c('gold3',"darkgreen")[as.numeric(factor(metab$geno))])
+
+axis(side = 1,
+     at = 1:12,
+     labels = rep(c("Control", "Df", "OE"), 4),
+     line = 0,
+     cex.axis = .75,
+     lwd.ticks = 2)
+
+axis(side = 2,
+     line = 0,
+     cex.axis = 1,
+     lwd.ticks = 2,
+     las = 2)
+
+axis(side = 2,
+     at = .5*(max(gene$cpm) + min(gene$cpm)),
+     label = "Counts per million reads",
+     tick = F,
+     padj = -3,
+     cex.axis = 1.25)
+
+axis(side = 1,
+     at = c(2, 5, 8, 11),
+     labels = c("Silent", "G85R","Silent", "G85R"),
+     tick = F,
+     padj = 2,
+     cex.axis = 1)
+
+axis(side = 3,
+     at = 3.5,
+     labels = name,
+     tick = F,
+     padj = -.5,
+     cex.axis = 2)
+
+xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
+xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
+lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+
+```

### 2024-11-06 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
pca

@@
 
+sigs = row.names(A4V.FDR)[A4V.FDR[, "AvS40FT"] <= .05]
+bg = row.names(A4V.FDR)[A4V.FDR[, "AvS40FT"] <= 1]
+
+sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
+bg = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]
+
 sigsKEY = GeneIDKey[sigs,]
-sigs = sigsKEY$Symbol
+sigs = unique(na.omit(sigsKEY$Symbol))
 bgKEY = GeneIDKey[bg,]
-bg = bgKEY$Symbol
+bg = unique(na.omit(bgKEY$Symbol))
 
 sig.cats = Enrichment(sigs, bg)
+
+##GFsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+##GMsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+#AF3Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+#AF9Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+#AF40Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+#AM3Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
+#AM9Tsigs = sig.cats$GO[sig.cats$GO$adjp < 0.05, c(4,5,6,8)]
 

### 2024-11-06 TKT_RNAseq/R Code/TKT Signaling Pathway.Rmd
pca

--- 2024-09-27 TKT_RNAseq/R Code/TKTRNAseqRescueResponse.Rmd
@@
 ---
-title: "G85R Analysis: Rescue Response"
+title: "G85R Analysis: TKT Signaling Pathway"
 author: "John Santiago"
@@
 library(DT)
-##source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
+source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
 library(VennDiagram)
@@
 enzyme2KEGG = as.list(org.Dm.egENZYME2EG)
+enzyme2KEGG$'3.6.1.77' = "35231"
+enzyme2KEGG = enzyme2KEGG[names(enzyme2KEGG) != "`3.6.1.-`"]
 
@@
 
-## Response Genes in G85R relative to WT
-
 ```{r echo = F}
 
-x = "GRxWT.FC"
-y = "GRxWT.MC"
-
-mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
-                             'GR.F', 'GR.M')]
-main.title = "G85R vs WT: Female and Male DE Genes"
-
-##RG = Response Genes
-GRxWT.RG = TKT.biplot(x, y, mean.data, main.title)
-
-GRxWT.RG[[1]]
+#TKT = FBgn0036784
+
+FBgn = "FBgn0036784"
+Name = GeneIDKey[FBgn, "Symbol"]
+TKT = GeneIDKey[FBgn, "Name"]
+enzymeID = names(enzyme2KEGG)[grep(TKT, enzyme2KEGG)]
+reactions <- keggGet(c(enzymeID))
+
+temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
+temp.substrate = strsplit(temp.substrate, split = ":")
+substrates = c(1:length(temp.substrate))
+i=1
+while(i<=length(temp.substrate)){
+  substrates[i] = substring(temp.substrate[[i]][2], 1,6)
+  names(substrates)[i] = substring(temp.substrate[[i]][1], 1, (nchar(temp.substrate[[i]][1]) - 4))
+  i=i+1
+}
+
+temp.product = reactions[[1]]["PRODUCT"][[1]]
+temp.product = strsplit(temp.product, split = ":")
+products = c(1:length(temp.product))
+i=1
+while(i<=length(temp.product)){
+  products[i] = substring(temp.product[[i]][2], 1,6)
+  names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
+  i=i+1
+}
+
+TKTmap = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
+                    from.ID = c(substrates, rep(TKT, length(products))),
+                    to.Name = c(rep(Name, length(substrates)), names(products)),
+                    to.ID = c(rep(TKT, length(substrates)), products))
+
+secondary = c(substrates, products)
+
+secondary.enzymes = as.character()
+
+i=1
+while( i<= length(secondary)){
+  temp.enzymes = keggGet(secondary[i])[[1]]["ENZYME"][[1]]
+  temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
+  secondary.enzymes = c(secondary.enzymes, temp.enzymes)
+  i = i +1
+}
+
+secondary.enzymes = unique(secondary.enzymes)
+
+secondary.enzymes = row.names(GeneIDKey[GeneIDKey$Name %in% unlist(secondary.enzymes),])
+
+tertiary.enzymes = as.character()
+
+j = 1
+
+while(j <= length(secondary.enzymes)){
+  FBgn = secondary.enzymes[j]
+  Name = GeneIDKey[FBgn, "Symbol"]
+  ID = GeneIDKey[FBgn, "Name"]
+  enzymeID = names(enzyme2KEGG)[grep(ID, enzyme2KEGG)]
+  reactions <- keggGet(c(enzymeID))
+
+  temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
+  temp.substrate = strsplit(temp.substrate, split = ":")
+  substrates = c(1:length(temp.substrate))
+  i=1
+  while(i<=length(temp.substrate)){
+    substrates[i] = substring(temp.substrate[[i]][2], 1,6)
+    names(substrates)[i] = substring(temp.substrate[[i]][1], 1,
+                                     (nchar(temp.substrate[[i]][1]) - 4))
+    i=i+1
+  }
+
+  temp.product = reactions[[1]]["PRODUCT"][[1]]
+  temp.product = strsplit(temp.product, split = ":")
+  products = c(1:length(temp.product))
+  i=1
+  while(i<=length(temp.product)){
+    products[i] = substring(temp.product[[i]][2], 1,6)
+    names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
+    i=i+1
+  }
+
+  temp.map = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
+                        from.ID = c(substrates, rep(ID, length(products))),
+                        to.Name = c(rep(Name, length(substrates)), names(products)),
+                        to.ID = c(rep(ID, length(substrates)), products))
+  row.names(temp.map) =  1:nrow(temp.map)
+  TKTmap = rbind(TKTmap, temp.map)
+  tertiary.enzymes = c(tertiary.enzymes, substrates, products)
+
+  j=j+1
+  }
 
@@
 
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Female Increased"
-set2 = "Female Decreased"
-set3 = "Male Increased"
-set4 = "Male Decreased"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
-
-NormalResponse = data.frame(Female = c(length(s2), length(s1)),
-                            Male =  c(length(s4), length(s3)))
-row.names(NormalResponse) = c("Decreased", "Increased")
-NormalResponse = as.matrix(NormalResponse)
-
-par(mar = c(2,4,2,7.5))
-barplot(NormalResponse,
-        beside = T,
-        ylab = "Total DEGs",
-        main = "G85R vs Silent",
-        col = c('navy', 'firebrick'),
-        angle = c(45, 45, 315, 315), density = 50,
-        legend.text = c("Decreased", "Increased"),
-        args.legend = list(x = 8,
-                           y = 700,
-                           bty = 'n'))
-#legend(x = 6.25, 
-#       y = 700, 
-#       legend = c("Increased", "Decreased"),
-#       pt.bg = c('grey35', 'lightgrey'),
-#       xpd = T, 
-#       bty = "o",
-#       pch = 22,
-#       pt.cex = 1.5)
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set3 = "Female Increased"
-set1 = "Female Decreased"
-set4 = "Male Increased"
-set2 = "Male Decreased"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
-
-main = ""
-
-grid.newpage()
-tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("navy", "darkgreen","gold","firebrick"),cex=2,cat.cex = 1, title = "main")
-
-```
-
-##Female and Male Shared DEGs
-```{r echo = F, include = F}
-
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
-
-MF.shared.DEGs = c(intersect(s1,s3), intersect(s2,s4))
-
-bg = row.names(TKT.EdgeR)
-GRWTMF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "CC")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "BP")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "MF")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "CC"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "BP"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:39)
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "MF"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:30)
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-##Female Only DEGs
-```{r echo = F, include = F}
-
-F.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
-                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))
-
-bg = row.names(TKT.EdgeR)
-GRWTFonly.Enr = Subset.Enrichment(bg, F.only.DEGs)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "CC")
-treemapPlot(RTCC.GRWTFonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "BP")
-treemapPlot(RTCC.GRWTFonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "MF")
-treemapPlot(RTCC.GRWTFonly)
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "CC"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "BP"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "MF"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-##Male Only DEGs
-```{r echo = F, include = F}
-
-M.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
-                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))
-
-bg = row.names(TKT.EdgeR)
-GRWTMonly.Enr = Subset.Enrichment(bg, M.only.DEGs)
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "CC")
-treemapPlot(RTCC.GRWTMonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "BP")
-treemapPlot(RTCC.GRWTMonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "MF")
-treemapPlot(RTCC.GRWTMonly)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMonly.Enr
-GO.ontology = "CC"
-FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:28)
-sigs = M.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMonly.Enr
-GO.ontology = "BP"
-FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:50)
-sigs = M.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMonly.Enr
-GO.ontology = "MF"
-FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:50)
-sigs = M.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Female"
-set2 = "Male"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = GRWTFonly.Enr$GO[GRWTFonly.Enr$GO$adjp <= 0.05, "term"]
-s2 = GRWTMonly.Enr$GO[GRWTMonly.Enr$GO$adjp <= 0.05, "term"]
-
-main = ""
-
-grid.newpage()
-tempvenn=draw.pairwise.venn(area1 = length(s1),
-                            area2 = length(s2),
-                            cross.area = length(intersect(s1,s2)),
-                            fill = c("blue", "red"),
-                            cex = 2,
-                            cat.cex = 1,
-                            category = c(set1, set2),
-                            title = "main")
-
-```
-
-```{r echo = F, include = F}
-
-data("motifAnnotations_dmel_v9")
-motifRankings = importRankings("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/dm6_v10_clust.genes_vs_motifs.rankings.feather")
-motifAnnotations = motifAnnotations_dmel_v9
-
-##motif rankings table for every TF
-motif.data = getRanking(motifRankings)
-##motifs associated with a TF
-##TF.data = motifAnnotations[motifAnnotations$TF == 'Tudor-SN',]
-###TF.data = motifAnnotations[motifAnnotations$TF == 'Mad',]
-
-##TF.motif.data = motif.data[motif.data$motifs %in% TF.data$motif,]
-
-##Motif collection data directory
-motif.collection.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/DrosophilaMotifsSingletonData/"
-
-##geneLists = GeneIDKey[MF.shared.DEGs, 'Symbol']
-geneLists = GeneIDKey[F.only.DEGs, 'Symbol']
-geneLists = GeneIDKey[M.only.DEGs, 'Symbol']
-
-motifEnrichmentTable_wGenes <- cisTarget(geneLists, 
-         motifRankings,
-         motifAnnot=motifAnnotations)
-
-motifs_AUC <- calcAUC(geneLists, motifRankings, nCores=1)
-
-auc <- getAUC(motifs_AUC)
-hist(auc, xlab="dAUC histogram",
-     breaks=100, col="#ff000050", border="darkred")
-nes3 <- (3*sd(auc)) + mean(auc)
-abline(v=nes3, col="red")
-
-motifEnrichmentTable <- addMotifAnnotation(motifs_AUC, nesThreshold=3,
-     motifAnnot=motifAnnotations)
-
-motifEnrichmentTable_wGenes <- addSignificantGenes(motifEnrichmentTable,
-                      rankings=motifRankings, 
-                      geneSets=geneLists)
-dim(motifEnrichmentTable_wGenes)
-
-resultsSubset <- motifEnrichmentTable_wGenes
-
-```
-
-```{r echo = F}
-
-showLogo(resultsSubset)
-
-```
-
-```{r echo = F, include = F}
-
-anotatedTfs <- lapply(split(motifEnrichmentTable_wGenes$TF_highConf,
-                            motifEnrichmentTable$geneSet),
-                      function(x) {
-                        genes <- gsub(" \\(.*\\). ", "; ", x, fixed=FALSE)
-                        genesSplit <- unique(unlist(strsplit(genes, "; ")))
-                        return(genesSplit)
-                        })
-
-anotatedTfs$hypoxia
-
-```
-
-```{r echo = F}
-
-##comparisons
-primary = 'GRxWT.C'
-
-x = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-min.expression = 0
-
-##Reversal pattern
-FC.data = metab.FC[, c(primary)]
-FC.data = na.omit(FC.data)
-
-##Sig cutoff. Currently, at least 1 significant change
-sig.metab = metab.FDR[metab.FDR[,primary]  < .05, ]
-sig.metab = na.omit(sig.metab)
-sig.metab = row.names(sig.metab)
-
-FC.data = metab.FC[sig.metab, c(x)]
-FDR.data = metab.FDR[sig.metab, c(x)]
-mean.data = mean.data[sig.metab, ]
-
-data = data.frame(Metab = sig.metab,
-                  compoundID = KEGG.Key[sig.metab],
-                  FDR = -log2(FDR.data),
-                  FC = FC.data,
-                  Color = 'grey',
-                  size = 1,
-                  Variable1.mean = mean.data[,1],
-                  Control1.mean = mean.data[,2])
-
-sig.metabs = data
-
-main.title = "G85R Metabolites"
-
-  data$Color[data$FC < 0] = 'royalblue'
-  data$Color[data$FC > 0] = 'firebrick' 
-  #data$Color[data$Symbol == "Arc1"] = 'gold'
-  data$size = log10(apply(mean.data[,c(1,2)], 1, max))
-  data$size[data$size<3] = 1
-
-  data = na.omit(data)
-  data = data[data$size > log2(min.expression),]
-  data$size = data$size
-
-  fig = plot_ly(data = data,
-                x = ~FC,
-                y = ~FDR,
-                type = 'scatter',
-                mode = 'markers',
-                marker = list(color = ~Color,
-                              colors = ~Color,
-                              line = list(color = "black", width = 1.5),
-                              size = ~size),
-                hoverinfo = "text",
-                hovertext = paste("Metabolite:", data$Metab,
-                                  "\n Compound ID:", data$compoundID,
-                                  "\n ", x, "p: ", round(2^-data$FDR, 2),
-                                  "\n ", x, "FC: ", round(data$FC, 2),
-                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
-                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2)))
-
-  fig = fig %>% layout(title = main.title,
-                       xaxis = list(title = paste(x, "FC")),
-                       yaxis = list(title = paste(x, "-log2(p-value)")),
-                       showlegend = F)
-
-  fig
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[1,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[2,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[3,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[4,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[5,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-```{r echo = F}
-
-CompoundData = sig.metabs[41,]
-
-x = 'GRxWT.C'
-y = 'GRxWT.C'
-
-mean.data = mean.metab[, c('GR', 'WT')]
-
-Fx = 'GRxWT.FC'
-My = 'GRxWT.MC'
-
-Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
-Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]
-
-compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)
-
-```
-
-##  Are there genes that respond to rescue in Silent and G85R for both sexes?
-
-##  TKT-Df Response
-```{r echo = F}
-
-x = "GRF.CxDf"
-y = "WTF.CxDf"
-
-mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
-                             'TktDfGR.F', 'TktDfWT.F')]
-main.title = "Female TKT-Df DE Genes"
-
-##RG = Response Genes
-FDf.RG = TKT.biplot(x, y, mean.data, main.title)
-
-FDf.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "GRM.CxDf"
-y = "WTM.CxDf"
-
-mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
-                             'TktDfGR.M', 'TktDfWT.M')]
-main.title = "Male TKT-Df DE Genes"
-
-##RG = Response Genes
-MDf.RG = TKT.biplot(x, y, mean.data, main.title)
-
-MDf.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "GRF.CxDf"
-y = "GRM.CxDf"
-
-mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
-                             'TktDfGR.F', 'TktDfGR.M')]
-main.title = "G85R TKT-Df DE Genes"
-
-##RG = Response Genes
-GRDf.RG = TKT.biplot(x, y, mean.data, main.title)
-
-GRDf.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "WTF.CxDf"
-y = "WTM.CxDf"
-
-mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
-                             'TktDfWT.F', 'TktDfWT.M')]
-main.title = "Silent TKT-Df DE Genes"
-
-##RG = Response Genes
-WTDf.RG = TKT.biplot(x, y, mean.data, main.title)
-
-WTDf.RG[[1]]
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Silent Female Df"
-set2 = "Silent Male Df"
-set3 = "G85R Female Df"
-set4 = "G85R Male Df"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-
-NormalResponse = data.frame(Rescue = c(set1, set2, set3, set4),
-                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))
-
-fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
-               marker = list(color = 'lightgrey',
-                      line = list(color = 'rgb(8,48,107)',
-                                  width = 3)))
-fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes (Control vs TKT-Df'))
-
-fig
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Silent Female Df"
-set2 = "Silent Male Df"
-set3 = "G85R Female Df"
-set4 = "G85R Male Df"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-
-main = ""
-
-grid.newpage()
-tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")
-
-```
-
-##WTF.C vs WTF.TKT-Df
-```{r echo = F, include = F}
-
-bg = row.names(TKT.EdgeR)
-WTF.Df.Enr = Subset.Enrichment(bg, FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"])
-
-```
-
-```{r echo = F}
-
-RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
-treemapPlot(RTCC.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
-treemapPlot(RTBP.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
-treemapPlot(RTMF.WTF.Df)
-
-```
-
-##WTM.C vs WTM.TKT-Df
-```{r echo = F, include = F}
-
-bg = row.names(TKT.EdgeR)
-WTM.Df.Enr = Subset.Enrichment(bg, MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"])
-
-```
-
-```{r echo = F}
-
-RTCC.WTM.Df = tree(WTM.Df.Enr, "CC")
-treemapPlot(RTCC.WTM.Df)
-
-```
-
-```{r echo = F}
-
-RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
-treemapPlot(RTBP.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
-treemapPlot(RTMF.WTF.Df)
-
-```
-
-##GRF.C vs GRF.TKT-Df
-```{r echo = F, include = F}
-
-bg = row.names(TKT.EdgeR)
-GRF.Df.Enr = Subset.Enrichment(bg, FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])
-
-```
-
-```{r echo = F}
-
-RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
-treemapPlot(RTCC.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
-treemapPlot(RTBP.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
-treemapPlot(RTMF.WTF.Df)
-
-```
-
-##GRM.C vs GRM.TKT-Df
-```{r echo = F, include = F}
-
-bg = row.names(TKT.EdgeR)
-GRM.Df.Enr = Subset.Enrichment(bg, MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])
-
-```
-
-```{r echo = F}
-
-RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
-treemapPlot(RTCC.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
-treemapPlot(RTBP.WTF.Df)
-
-```
-
-```{r echo = F}
-
-RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
-treemapPlot(RTMF.WTF.Df)
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Silent Female Df"
-set2 = "Silent Male Df"
-set3 = "G85R Female Df"
-set4 = "G85R Male Df"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = WTF.Df.Enr$GO$term[WTF.Df.Enr$GO$adjp <= .05]
-s2 = WTM.Df.Enr$GO$term[WTM.Df.Enr$GO$adjp <= .05]
-s3 = GRF.Df.Enr$GO$term[GRF.Df.Enr$GO$adjp <= .05]
-s4 = GRM.Df.Enr$GO$term[GRM.Df.Enr$GO$adjp <= .05]
-
-main = ""
-
-grid.newpage()
-tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")
-
-```
-
-###################################
-
-###################################
-
-###################################
-
-## TKT-OE Response
-```{r echo = F}
-
-x = "GRF.CxOE"
-y = "WTF.CxOE"
-
-mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
-                             'TktOEGR.F', 'TktOEWT.F')]
-main.title = "Female TKT-OE DE Genes"
-
-##RG = Response Genes
-FOE.RG = TKT.biplot(x, y, mean.data, main.title)
-
-FOE.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "GRM.CxOE"
-y = "WTM.CxOE"
-
-mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
-                             'TktOEGR.M', 'TktOEWT.M')]
-main.title = "Male TKT-OE DE Genes"
-
-##RG = Response Genes
-MOE.RG = TKT.biplot(x, y, mean.data, main.title)
-
-MOE.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "GRF.CxOE"
-y = "GRM.CxOE"
-
-mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
-                             'TktOEGR.F', 'TktOEGR.M')]
-main.title = "G85R TKT-OE DE Genes"
-
-##RG = Response Genes
-GROE.RG = TKT.biplot(x, y, mean.data, main.title)
-
-GROE.RG[[1]]
-
-```
-
-```{r echo = F}
-
-x = "WTF.CxOE"
-y = "WTM.CxOE"
-
-mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
-                             'TktOEWT.F', 'TktOEWT.M')]
-main.title = "Silent TKT-OE DE Genes"
-
-##RG = Response Genes
-WTOE.RG = TKT.biplot(x, y, mean.data, main.title)
-
-WTOE.RG[[1]]
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Silent Female OE"
-set2 = "Silent Male OE"
-set3 = "G85R Female OE"
-set4 = "G85R Male OE"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = FOE.RG[[2]][FOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s2 = MOE.RG[[2]][MOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s3 = FOE.RG[[2]][FOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-s4 = MOE.RG[[2]][MOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-
-NormalResponse = data.frame(Rescue = c(set1, set2, set3, set4),
-                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))
-
-fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
-               marker = list(color = 'lightgrey',
-                      line = list(color = 'rgb(8,48,107)',
-                                  width = 3)))
-fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes (Control vs TKT-Df'))
-
-fig
-
-```
-
-```{r echo = F}
-
-##Sample titles as strings. Only fill in up to your number of selected categories
-set1 = "Silent Female OE"
-set2 = "Silent Male OE"
-set3 = "G85R Female OE"
-set4 = "G85R Male OE"
-
-##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = FOE.RG[[2]][FOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s2 = MOE.RG[[2]][MOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
-s3 = FOE.RG[[2]][FOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-s4 = MOE.RG[[2]][MOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
-
-main = ""
-
-grid.newpage()
-tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")
-
-```
+visedges = TKTmap[, c("from.Name", "to.Name")]
+colnames(visedges) = c("from", "to")
+
+temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)
+
+visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
+##visedges$width = .5 + abs(visedges$color)
+visedges$color[visedges$color < (-2)] = -2
+visedges$color[visedges$color > (2)] = 2
+visedges$color = (visedges$color * 100) +201
+visedges$color = temp[visedges$color]
+visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
+visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
+visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
+visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
+visedges$width = .01 + (1*abs(log10(visedges$WT)))
+
+groups = setNames(c(TKTmap$from.ID, TKTmap$to.ID),
+                  c(TKTmap$from.Name, TKTmap$to.Name))
+groups[substr(groups, 1,1) == "C"] = "metabolite"
+groups[groups != "metabolite"] = "enzyme"
+groups['CG8036'] = "TKT"
+
+nodes = data.frame(id = unique(c(TKTmap$from.Name, TKTmap$to.Name)),
+                   label = unique(c(TKTmap$from.Name, TKTmap$to.Name)),
+                   group = groups[unique(c(TKTmap$from.Name, TKTmap$to.Name))])
+
+nodes$label[nodes$label == "CG8036"] = "TKT"
+
+nodes$color = round(TKT.EdgeR.FC[p, comparison.T],2)
+##visedges$width = .5 + abs(visedges$color)
+visedges$color[visedges$color < (-2)] = -2
+visedges$color[visedges$color > (2)] = 2
+visedges$color = (visedges$color * 100) +201
+visedges$color = temp[visedges$color]
+visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
+visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
+visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
+visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
+visedges$width = .01 + (1*abs(log10(visedges$WT)))
+
+visNetwork(nodes,visedges)%>%
+  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
+  #visEdges(arrows = visedges$arrows)#%>%
+  visGroups(groupname = "metabolite", 
+            shape = 'box', color = "gold",
+            physics=T, size = 25, 
+            font=list(color="black"))%>%
+  visGroups(groupname = "TKT", 
+            shape = 'circle', color = "firebrick",
+            physics=F, size = 25, 
+            font=list(color="white"))
+
+```
+
+```{r}
+
+PPP = keggGet('dme00030')[[1]]
+PPP.enz = PPP$GENE
+PPP.met = PPP$COMPOUND
+
+download.kegg(pathway.id = "00030",
+              species = "dme",
+              kegg.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/")
+
+node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00030.xml')
+
+node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
+                       number = rep(names(node.data$kegg.names),
+                                    lengths(node.data$kegg.names)),
+                       x = 0,
+                       y = 0,
+                       color = 0,
+                       names = "")
+node.info$x = node.data$x[node.info$number]
+node.info$y = node.data$y[node.info$number]
+
+node.info = node.info[grep("C", node.info$ID),]
+node.info = node.info[grep("CG", node.info$ID, invert = T),]
+
+enzymes = as.character()
+
+i=1
+while( i<= nrow(node.info)){
+  temp.enzymes = keggGet(node.info$ID[i])[[1]]["ENZYME"][[1]]
+  temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
+  enzymes = c(enzymes, temp.enzymes)
+  i = i +1
+}
+
+edges = data.frame(from.Name = as.character(),
+                   from.ID = as.character(),
+                   to.Name = as.character(),
+                   to.ID = as.character())
+
+j = 1
+
+while(j <= length(enzymes)){
+  FBgn = na.omit(GeneIDKey[GeneIDKey$Name == enzymes[j], "FBgn"])
+  Name = GeneIDKey[FBgn, "Symbol"]
+  ID = GeneIDKey[FBgn, "Name"]
+  enzymeID = names(enzymes)[i]
+  reactions <- keggGet(c(enzymeID))
+
+  temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
+  temp.substrate = strsplit(temp.substrate, split = ":")
+  substrates = c(1:length(temp.substrate))
+  i=1
+  while(i<=length(temp.substrate)){
+    substrates[i] = substring(temp.substrate[[i]][2], 1,6)
+    names(substrates)[i] = substring(temp.substrate[[i]][1], 1,
+                                     (nchar(temp.substrate[[i]][1]) - 4))
+    i=i+1
+  }
+
+  temp.product = reactions[[1]]["PRODUCT"][[1]]
+  temp.product = strsplit(temp.product, split = ":")
+  products = c(1:length(temp.product))
+  i=1
+  while(i<=length(temp.product)){
+    products[i] = substring(temp.product[[i]][2], 1,6)
+    names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
+    i=i+1
+  }
+
+  temp.edges = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
+                          from.ID = c(substrates, rep(ID, length(products))),
+                          to.Name = c(rep(Name, length(substrates)), names(products)),
+                          to.ID = c(rep(ID, length(substrates)), products))
+  row.names(temp.edges) =  1:nrow(temp.edges)
+  edges = rbind(edges, temp.edges)
+  j=j+1
+  }
+
+edges = unique(edges)
+
+edges = rbind(edges[edges$from.ID %in% node.info$ID, ],
+              edges[edges$to.ID %in% node.info$ID, ])
+
+```
+
+```{r}
+
+visedges = edges[, c("from.Name", "to.Name")]
+colnames(visedges) = c("from", "to")
+
+nodes = data.frame(id = unique(node.info$ID))
+
+visNetwork(nodes,visedges)
+
+```

### 2024-11-06 TKT_RNAseq/R Code/TKT-OE_RNAseqRescueResponse.Rmd
pca

--- 2024-09-27 TKT_RNAseq/R Code/TKTRNAseqRescueResponse.Rmd
@@
 
-x = "GRxWT.FC"
-y = "GRxWT.MC"
-
-mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
-                             'GR.F', 'GR.M')]
-main.title = "G85R vs WT: Female and Male DE Genes"
+x = "GRF.CxOE"
+y = "GRM.CxOE"
+
+mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
+                             'TktOEGR.F', 'TktOEGR.M')]
+main.title = "G85R Control vs TKT-OE: Female and Male DE Genes"
 
 ##RG = Response Genes
-GRxWT.RG = TKT.biplot(x, y, mean.data, main.title)
-
-GRxWT.RG[[1]]
+GR.CxOE.RG = TKT.biplot(x, y, mean.data, main.title)
+
+GR.CxOE.RG[[1]]
 
@@
 ##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
+s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
+s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
+s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
+s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]
 
@@
         ylab = "Total DEGs",
-        main = "G85R vs Silent",
+        main = "G85R Control vs TKT-OE",
         col = c('navy', 'firebrick'),
@@
 ##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
+s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
+s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
+s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
+s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]
 
@@
 
-s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
-s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
-s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
-s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
-                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]
+s1 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] > 0, "FBgn"]
+s2 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC1'] < 0, "FBgn"]
+s3 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] > 0, "FBgn"]
+s4 = GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05 &
+                     GR.CxOE.RG[[2]][,'FC2'] < 0, "FBgn"]
 
@@
 bg = row.names(TKT.EdgeR)
-GRWTMF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "CC")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "BP")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMF = tree(GRWTMF.Enr, "MF")
-treemapPlot(RTCC.GRWTMF)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "CC"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "BP"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:39)
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTMF.Enr
-GO.ontology = "MF"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = c(1:30)
-sigs = MF.shared.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
+GR.CxOE.MF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)
 
@@
 
-F.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
-                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))
+F.only.DEGs = c(setdiff(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
+                        GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))
 
 bg = row.names(TKT.EdgeR)
-GRWTFonly.Enr = Subset.Enrichment(bg, F.only.DEGs)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "CC")
-treemapPlot(RTCC.GRWTFonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "BP")
-treemapPlot(RTCC.GRWTFonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTFonly = tree(GRWTFonly.Enr, "MF")
-treemapPlot(RTCC.GRWTFonly)
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "CC"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "BP"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
-
-```
-
-```{r echo = F}
-
-cat.data = GRWTFonly.Enr
-GO.ontology = "MF"
-FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
-FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
-usecats = "sigs.only"
-sigs = F.only.DEGs
-
-reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)
+GR.CxOE.Fonly.Enr = Subset.Enrichment(bg, F.only.DEGs)
 
@@
 
-M.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
-                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))
+M.only.DEGs = c(setdiff(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
+                        GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))
 
 bg = row.names(TKT.EdgeR)
-GRWTMonly.Enr = Subset.Enrichment(bg, M.only.DEGs)
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "CC")
-treemapPlot(RTCC.GRWTMonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "BP")
-treemapPlot(RTCC.GRWTMonly)
-
-```
-
-```{r echo = F}
-
-RTCC.GRWTMonly = tree(GRWTMonly.Enr, "MF")
-treemapPlot(RTCC.GRWTMonly)
+GR.CxOE.Monly.Enr = Subset.Enrichment(bg, M.only.DEGs)
+
+```
+
+##no significantly enriched GO terms in sex independent or sex dependent DEG sets
+
+##All Female DEGs
+
+##Female Only DEGs
+```{r echo = F, include = F}
+
+F.DEGs = c(GR.CxOE.RG[[2]][GR.CxOE.RG[[2]][,'FDR1'] <= 0.05, "FBgn"])
+
+bg = row.names(TKT.EdgeR)
+GR.CxOE.F.Enr = Subset.Enrichment(bg, F.DEGs)
+
+```
+
+```{r echo = F, include = F}
+
+RTCC.GR.CxOE.F = tree(GR.CxOE.F.Enr, "CC")
+treemapPlot(RTCC.GR.CxOE.F)
 

### 2024-11-06 TKT_RNAseq/R Code/TKTRNAseqMitochondrialAssessment.Rmd
pca

---
title: "G85R and A4V OXPHOS Genes"
author: "John Santiago"
date: "2024-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r echo = F, include = F}

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)
library(RcisTarget)
library(DT)
source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
TKT.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

G85R.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)

groups = groups[colnames(cpmdata),]

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##Clean Trait Data and calculate CPMs
countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)

##normalize data
countdata=countdata[, row.names(groups)]
x <- countdata
gr <- factor(groups$Group)
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- calcNormFactors(y, method = "TMM")
design<-model.matrix(~0 + gr)
colnames(design) = unique(gr)
z = estimateDisp(z, design, robust = T)
fit <- glmQLFit(z, design)

compare = makeContrasts(TktDfGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FDfxWT.FC=DEout
sGR.FDfxWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FDfxWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[17] = 'GR.FDfxWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FDfxWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[17] = 'GR.FDfxWT.FC'

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MDfxWT.MC=DEout
sGR.MDfxWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MDfxWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[18] = 'GR.MDfxWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MDfxWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[18] = 'GR.MDfxWT.MC'

compare = makeContrasts(TktOEGR.F-WT.F, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FOExWT.FC=DEout
sGR.FOExWT.FC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.FOExWT.FC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[19] = 'GR.FOExWT.FC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.FOExWT.FC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[19] = 'GR.FOExWT.FC'

compare = makeContrasts(TktOEGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.MOExWT.MC=DEout
sGR.MOExWT.MC=DEout[DEout$FDR<.05,]

TKT.EdgeR = cbind(TKT.EdgeR, GR.MOExWT.MC[row.names(TKT.EdgeR), "FDR"])
colnames(TKT.EdgeR)[20] = 'GR.MOExWT.MC'

TKT.EdgeR.FC = cbind(TKT.EdgeR.FC, GR.MOExWT.MC[row.names(TKT.EdgeR), "logFC"])
colnames(TKT.EdgeR.FC)[20] = 'GR.MOExWT.MC'

genesingo = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/genesingo.RData")
GO.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GO.names.csv", row.names = 1)

A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
A4V.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
A4V.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
A4V.meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

sample.names = list.files("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/")

meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

temp = read.csv(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/", sample.names[1]), sep = '\t', row.names = 1)

countdata = data.frame(temp = temp)
colnames(countdata)[1] = substr(sample.names[1], 1, nchar(sample.names[1])-15)

i=2
while(i <= length(sample.names)){
  temp = read.csv(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/Count_Tables/", sample.names[i]), sep = '\t', row.names = 1)
  countdata = cbind(countdata, temp[row.names(countdata),1])
  colnames(countdata)[i] = substr(sample.names[i], 1, nchar(sample.names[i])-15)
  i=i+1
}

countdata = countdata[-(grep("ti",row.names(countdata))),]
countdata = countdata[-(grep("trans",row.names(countdata))),]

##normalize data
x <- countdata
gr <- factor(substr(colnames(countdata), 1, nchar(colnames(countdata))-1))
gr2 = factor(paste0(substr(colnames(countdata), 1, 1), 
                    substr(colnames(countdata),
                           nchar(colnames(countdata))-2,
                           nchar(colnames(countdata))-1)))
y <- DGEList(counts=x,group=gr)
keep <- filterByExpr(y)
y <- y[keep,,keep.lib.sizes=FALSE]
z <- normLibSizes(y)
##normalized cpm
#cpmdata=cpm(z)

#z$samples$group = gr2

##updated edger analysis pipeline
design<-model.matrix(~0 + gr2)
colnames(design) = unique(gr2)
z = estimateDisp(z, design)
fit <- glmQLFit(z, design)

contr = makeContrasts(AFH - SFH, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
AvSFH = DEdata
sigAvSFH = DEdata[DEdata$FDR < 0.05, ]

A4V.FDR = cbind(A4V.FDR, AvSFH[row.names(A4V.FDR), "FDR"])
A4V.FC = cbind(A4V.FC, AvSFH[row.names(A4V.FC), "logFC"])

contr = makeContrasts(AMH - SMH, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
AvSMH = DEdata
sigAvSMH = DEdata[DEdata$FDR < 0.05, ]

A4V.FDR = cbind(A4V.FDR, AvSMH[row.names(A4V.FDR), "FDR"])
A4V.FC = cbind(A4V.FC, AvSMH[row.names(A4V.FC), "logFC"])

colnames(A4V.FDR)[52:53] = c("AvSFH", "AvSMH")
colnames(A4V.FC)[52:53] = c("AvSFH", "AvSMH")

contr = makeContrasts(AFT - SFT, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
AvSFT = DEdata
sigAvSFT = DEdata[DEdata$FDR < 0.05, ]

A4V.FDR = cbind(A4V.FDR, AvSFT[row.names(A4V.FDR), "FDR"])
A4V.FC = cbind(A4V.FC, AvSFT[row.names(A4V.FC), "logFC"])

contr = makeContrasts(AMT - SMT, levels=design)
qlf = glmQLFTest(fit, contrast=contr)
DEdata = topTags(qlf,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEdata = DEdata$table
AvSMT = DEdata
sigAvSMT = DEdata[DEdata$FDR < 0.05, ]

A4V.FDR = cbind(A4V.FDR, AvSMT[row.names(A4V.FDR), "FDR"])
A4V.FC = cbind(A4V.FC, AvSMT[row.names(A4V.FC), "logFC"])

colnames(A4V.FDR)[54:55] = c("AvSFT", "AvSMT")
colnames(A4V.FC)[54:55] = c("AvSFT", "AvSMT")

A4V.meancpm$AFH = apply((A4V.cpm[,gr2=="AFH"]), 1, mean)
A4V.meancpm$SFH = apply((A4V.cpm[,gr2=="SFH"]), 1, mean)
A4V.meancpm$AMH = apply((A4V.cpm[,gr2=="AMH"]), 1, mean)
A4V.meancpm$SMH = apply((A4V.cpm[,gr2=="SMH"]), 1, mean)

A4V.meancpm$AFT = apply((A4V.cpm[,gr2=="AFT"]), 1, mean)
A4V.meancpm$SFT = apply((A4V.cpm[,gr2=="SFT"]), 1, mean)
A4V.meancpm$AMT = apply((A4V.cpm[,gr2=="AMT"]), 1, mean)
A4V.meancpm$SMT = apply((A4V.cpm[,gr2=="SMT"]), 1, mean)

A4V.meancpm$AFA = apply((A4V.cpm[,gr2=="AFA"]), 1, mean)
A4V.meancpm$SFA = apply((A4V.cpm[,gr2=="SFA"]), 1, mean)
A4V.meancpm$AMA = apply((A4V.cpm[,gr2=="AMA"]), 1, mean)
A4V.meancpm$SMA = apply((A4V.cpm[,gr2=="SMA"]), 1, mean)

```

```{r echo = F}

mt = c("FBgn0013680",
       "FBgn0013674",
       "FBgn0013675",
       "FBgn0013673",
       "FBgn0013672",
       "FBgn0013676",
       "FBgn0013681",
       "FBgn0013684",
       "FBgn0262952",
       "FBgn0013683",
       "FBgn0013685",
       "FBgn0013678",
       "FBgn0013679")

oxphos.term = "GO:0006119"

oxphos.genes = genesingo[oxphos.term]
oxphos.genes = GeneIDKey[GeneIDKey$ensembl %in% oxphos.genes[[1]],]

oxphos = row.names(oxphos.genes)

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

```

```{r echo = F}

GR.SpecificGenes.biplot = function(genes, x, y, mean.data, main.title){

FC.data = TKT.EdgeR.FC[genes, c(x, y)]
FDR.data = TKT.EdgeR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  #data[x.genes, 'Color'] = 'royalblue'
  #data[y.genes, 'Color'] = 'firebrick' 
  #data[xy.genes, 'Color'] = 'gold'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  ##data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r echo = F}

AV.SpecificGenes.biplot = function(genes, x, y, mean.data, main.title){

FC.data = A4V.FC[genes, c(x, y)]
FDR.data = A4V.FDR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  #data[x.genes, 'Color'] = 'royalblue'
  #data[y.genes, 'Color'] = 'firebrick' 
  #data[xy.genes, 'Color'] = 'gold'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  ##data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

## G85R

```{r echo = F}

GR.mt = na.omit(cpmdata[mt, c(groups[groups$Group == 'WT.F', 'SampleID'],
                              groups[groups$Group == 'GR.F', 'SampleID'],
                              groups[groups$Group == 'WT.M', 'SampleID'],
                              groups[groups$Group == 'GR.M', 'SampleID'])])

row.names(GR.mt) = GeneIDKey[row.names(GR.mt), "Symbol"]
colnames(GR.mt) = groups[colnames(GR.mt), "Group"]
GR.mt = t(GR.mt)

mt.Group = rep(row.names(GR.mt), 12)
mt.Geno = rep(row.names(GR.mt), 12)
mt.Group[mt.Group ==  "WT.F"] = 1
mt.Group[mt.Group ==  "GR.F"] = 2
mt.Group[mt.Group ==  "WT.M"] = 3
mt.Group[mt.Group ==  "GR.M"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(GR.mt), nrow(GR.mt)), ncol = nrow(GR.mt))))
mt.cpm = as.numeric(GR.mt)

GR.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(GR.mt$cpm~GR.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 1",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(GR.mt$Group))],
       y=GR.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(GR.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(GR.mt$gene)[order(unique(GR.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "G85R F", "Silent M", "G85R M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig1. mtDNA Genes cpm in G85R and Silent

</br></br>

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = na.omit(G85R.meancpm[, c('GR.F', 'WT.F',
                                       'GR.M', 'WT.M')])

main.title = "Fig 2"

##RG = Response Genes
mtGRxWT.C.RG = GR.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig2 mtDNA Genes FC in G85R and Silent: log2(FC) for G85R/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

OXPHOS.FC.cutoff = abs(apply(na.omit(TKT.EdgeR.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

GR.ofc = na.omit(cpmdata[ofc, c(groups[groups$Group == 'WT.F', 'SampleID'],
                                groups[groups$Group == 'GR.F', 'SampleID'],
                                groups[groups$Group == 'WT.M', 'SampleID'],
                                groups[groups$Group == 'GR.M', 'SampleID'])])

cpm.cutoff = apply(GR.ofc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10])

GR.ofc = GR.ofc[ofc,]

row.names(GR.ofc) = GeneIDKey[row.names(GR.ofc), "Symbol"]
colnames(GR.ofc) = groups[colnames(GR.ofc), "Group"]
GR.ofc = t(GR.ofc)

ofc.Group = rep(row.names(GR.ofc), length(ofc))
ofc.Geno = rep(row.names(GR.ofc), length(ofc))
ofc.Group[ofc.Group ==  "WT.F"] = 1
ofc.Group[ofc.Group ==  "GR.F"] = 2
ofc.Group[ofc.Group ==  "WT.M"] = 3
ofc.Group[ofc.Group ==  "GR.M"] = 4

ofc.Gene = as.character(t(matrix(rep(colnames(GR.ofc), nrow(GR.ofc)), ncol = nrow(GR.ofc))))
ofc.cpm = as.numeric(GR.ofc)

GR.ofc = data.frame(Group = paste(ofc.Gene, ofc.Group),
                   cpm = ofc.cpm,
                   geno = ofc.Group,
                   gene = ofc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(GR.ofc$cpm~GR.ofc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 3",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(GR.ofc$Group))],
       y=GR.ofc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(GR.ofc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(GR.ofc$gene)[order(unique(GR.ofc$gene))]), cex.axis = .75, las = 2)

legend("topright",
       legend = c("Silent F", "G85R F", "Silent M", "G85R M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig3. nucDNA Genes cpm in G85R and Silent: cpm data for nucDNA genes in G85R and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = na.omit(G85R.meancpm[, c('GR.F', 'WT.F',
                                       'GR.M', 'WT.M')])

main.title = "Fig 4"

##RG = Response Genes
nucGRxWT.C.RG = GR.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

nucGRxWT.C.RG[[1]]

```

</br>

Fig4 nucDNA Genes FC in G85R and Silent: log2(FC) for G85R/Silent in Female (xaxis) and Male (yaxis)

</br></br>

## A4V

## mtDNA Genes in Head Samples

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A3FH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'S3MH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A3MH'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FH"] = 1
mt.Group[mt.Group ==  "A3FH"] = 2
mt.Group[mt.Group ==  "S3MH"] = 3
mt.Group[mt.Group ==  "A3MH"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 5",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig5. mtDNA Genes cpm in A4V and Silent 3-Day Heads

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

mean.data = na.omit(A4V.meancpm[, c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])

main.title = "Fig 6"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig6 mtDNA Genes FC in A4V and Silent 3-Day Heads: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 3-Day Heads

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A9FH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'S9MH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A9MH'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S9FH"] = 1
mt.Group[mt.Group ==  "A9FH"] = 2
mt.Group[mt.Group ==  "S9MH"] = 3
mt.Group[mt.Group ==  "A9MH"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 7",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig7. mtDNA Genes cpm in A4V and Silent 9-Day Heads

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

mean.data = na.omit(A4V.meancpm[, c('A9FH', 'S9FH',
                                    'A9MH', 'S9MH')])

main.title = "Fig 8"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig8 mtDNA Genes FC in A4V and Silent 9-Day Heads: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 9-Day Heads

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FH'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A40FH'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S40FH"] = 1
mt.Group[mt.Group ==  "A40FH"] = 2

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*3)), c(1:12)*3)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 9",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig9. mtDNA Genes cpm in A4V and Silent 40-Day Heads

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MH'])

AV.mt = na.omit(A4V.cpm[mt, ])

AV.mt = AV.mt[, Head]

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FH"] = 0
mt.Group[mt.Group ==  "S9FH"] = 1
mt.Group[mt.Group ==  "S40FH"] = 2
mt.Group[mt.Group ==  "A3FH"] = 3
mt.Group[mt.Group ==  "A9FH"] = 4
mt.Group[mt.Group ==  "A40FH"] = 5
mt.Group[mt.Group ==  "S3MH"] = 6
mt.Group[mt.Group ==  "S9MH"] = 7
mt.Group[mt.Group ==  "A3MH"] = 8
mt.Group[mt.Group ==  "A9MH"] = 9

mt.Geno = rep(row.names(AV.mt), 12)
mt.Geno = paste0(substr(mt.Geno, 1,1), substr(mt.Geno, nchar(mt.Geno)-1, nchar(mt.Geno)))
mt.Geno[mt.Geno == "SFH"] = 1
mt.Geno[mt.Geno == "AFH"] = 2
mt.Geno[mt.Geno == "SMH"] = 3
mt.Geno[mt.Geno == "AMH"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Geno,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*11)), c(1:12)*11)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 10",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*11)+5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig9. mtDNA Genes cpm in A4V and Silent heads at all timepoints

</br></br>

## mtDNA Genes in Thorax Samples

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A3MT'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FT"] = 1
mt.Group[mt.Group ==  "A3FT"] = 2
mt.Group[mt.Group ==  "S3MT"] = 3
mt.Group[mt.Group ==  "A3MT"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 10",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig10. mtDNA Genes cpm in A4V and Silent 3-Day Thorax

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

mean.data = na.omit(A4V.meancpm[, c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])

main.title = "Fig 11"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig11 mtDNA Genes FC in A4V and Silent 3-Day Thorax: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 3-Day Thorax

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S9FT"] = 1
mt.Group[mt.Group ==  "A9FT"] = 2
mt.Group[mt.Group ==  "S9MT"] = 3
mt.Group[mt.Group ==  "A9MT"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 12",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig12. mtDNA Genes cpm in A4V and Silent 9-Day Thorax

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

mean.data = na.omit(A4V.meancpm[, c('A9FT', 'S9FT',
                                    'A9MT', 'S9MT')])

main.title = "Fig 13"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig13 mtDNA Genes FC in A4V and Silent 9-Day Thorax: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 9-Day Thorax

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A40FT'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S40FT"] = 1
mt.Group[mt.Group ==  "A40FT"] = 2

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*3)), c(1:12)*3)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 14",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig14. mtDNA Genes cpm in A4V and Silent 40-Day Thorax

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])

AV.mt = na.omit(A4V.cpm[mt, ])

AV.mt = AV.mt[, Head]

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FT"] = 0
mt.Group[mt.Group ==  "S9FT"] = 1
mt.Group[mt.Group ==  "S40FT"] = 2
mt.Group[mt.Group ==  "A3FT"] = 3
mt.Group[mt.Group ==  "A9FT"] = 4
mt.Group[mt.Group ==  "A40FT"] = 5
mt.Group[mt.Group ==  "S3MT"] = 6
mt.Group[mt.Group ==  "S9MT"] = 7
mt.Group[mt.Group ==  "A3MT"] = 8
mt.Group[mt.Group ==  "A9MT"] = 9

mt.Geno = rep(row.names(AV.mt), 12)
mt.Geno = paste0(substr(mt.Geno, 1,1), substr(mt.Geno, nchar(mt.Geno)-1, nchar(mt.Geno)))
mt.Geno[mt.Geno == "SFT"] = 1
mt.Geno[mt.Geno == "AFT"] = 2
mt.Geno[mt.Geno == "SMT"] = 3
mt.Geno[mt.Geno == "AMT"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Geno,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*11)), c(1:12)*11)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 15",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*11)+5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig15. mtDNA Genes cpm in A4V and Silent thorax at all timepoints

</br></br>

## mtDNA Genes in Abdomen Samples

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A3MA'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FA"] = 1
mt.Group[mt.Group ==  "A3FA"] = 2
mt.Group[mt.Group ==  "S3MA"] = 3
mt.Group[mt.Group ==  "A3MA"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 16",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig16. mtDNA Genes cpm in A4V and Silent 3-Day Abdomen

</br></br>

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

mean.data = na.omit(A4V.meancpm[, c('A3FA', 'S3FA',
                                    'A3MA', 'S3MA')])

main.title = "Fig 17"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig17 mtDNA Genes FC in A4V and Silent 3-Day Abdomen: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 3-Day Abdomen

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
                              row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S9FA"] = 1
mt.Group[mt.Group ==  "A9FA"] = 2
mt.Group[mt.Group ==  "S9MA"] = 3
mt.Group[mt.Group ==  "A9MA"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*5)), c(1:12)*5)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 18",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig18. mtDNA Genes cpm in A4V and Silent 9-Day Abdomen

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

mean.data = na.omit(A4V.meancpm[, c('A9FA', 'S9FA',
                                    'A9MA', 'S9MA')])

main.title = "Fig 19"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(mt, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig19. mtDNA Genes FC in A4V and Silent 9-Day Abdomen: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis) 9-Day Abdomen

</br></br>

```{r echo = F}

AV.mt = na.omit(A4V.cpm[mt, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
                          row.names(A4V.meta)[A4V.meta$Group == 'A40FA'])])

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Geno = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S40FA"] = 1
mt.Group[mt.Group ==  "A40FA"] = 2

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Group,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*3)), c(1:12)*3)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 20",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig20. mtDNA Genes cpm in A4V and Silent 40-Day Abdomen

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])

AV.mt = na.omit(A4V.cpm[mt, ])

AV.mt = AV.mt[, Head]

row.names(AV.mt) = GeneIDKey[row.names(AV.mt), "Symbol"]
colnames(AV.mt) = A4V.meta[colnames(AV.mt), "Group"]
AV.mt = t(AV.mt)

mt.Group = rep(row.names(AV.mt), 12)
mt.Group[mt.Group ==  "S3FA"] = 0
mt.Group[mt.Group ==  "S9FA"] = 1
mt.Group[mt.Group ==  "S40FA"] = 2
mt.Group[mt.Group ==  "A3FA"] = 3
mt.Group[mt.Group ==  "A9FA"] = 4
mt.Group[mt.Group ==  "A40FA"] = 5
mt.Group[mt.Group ==  "S3MA"] = 6
mt.Group[mt.Group ==  "S9MA"] = 7
mt.Group[mt.Group ==  "A3MA"] = 8
mt.Group[mt.Group ==  "A9MA"] = 9

mt.Geno = rep(row.names(AV.mt), 12)
mt.Geno = paste0(substr(mt.Geno, 1,1), substr(mt.Geno, nchar(mt.Geno)-1, nchar(mt.Geno)))
mt.Geno[mt.Geno == "SFA"] = 1
mt.Geno[mt.Geno == "AFA"] = 2
mt.Geno[mt.Geno == "SMA"] = 3
mt.Geno[mt.Geno == "AMA"] = 4

mt.Gene = as.character(t(matrix(rep(colnames(AV.mt), nrow(AV.mt)), ncol = nrow(AV.mt))))
mt.cpm = as.numeric(AV.mt)

AV.mt = data.frame(Group = paste(mt.Gene, mt.Group),
                   cpm = mt.cpm,
                   geno = mt.Geno,
                   gene = mt.Gene)

box.at = setdiff(c(1:(12*11)), c(1:12)*11)

boxplot(AV.mt$cpm~AV.mt$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 21",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.mt$Group))],
       y=AV.mt$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.mt$geno))])

axis(1, at= c(c(0:11)*11)+5, tick = F, line = -.5, labels = c(unique(AV.mt$gene)[order(unique(AV.mt$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```
</br>

Fig21. mtDNA Genes cpm in A4V and Silent Abdomen at all timepoints

</br></br>

## nucDNA Genes in Head Samples

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FH"] = 1
nuc.Group[nuc.Group ==  "A3FH"] = 2
nuc.Group[nuc.Group ==  "S3MH"] = 3
nuc.Group[nuc.Group ==  "A3MH"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 22a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig22a. nucDNA Genes cpm in A4V and Silent 3-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FH"] = 1
nuc.Group[nuc.Group ==  "A3FH"] = 2
nuc.Group[nuc.Group ==  "S3MH"] = 3
nuc.Group[nuc.Group ==  "A3MH"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 22b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig22b. nucDNA Genes cpm in A4V and Silent 3-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

mean.data = na.omit(A4V.meancpm[, c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])

main.title = "Fig 23"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig23 nucDNA Genes FC in A4V and Silent 3-Day Heads: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FH"] = 1
nuc.Group[nuc.Group ==  "A9FH"] = 2
nuc.Group[nuc.Group ==  "S9MH"] = 3
nuc.Group[nuc.Group ==  "A9MH"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 24a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig24a. nucDNA Genes cpm in A4V and Silent 9-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FH"] = 1
nuc.Group[nuc.Group ==  "A9FH"] = 2
nuc.Group[nuc.Group ==  "S9MH"] = 3
nuc.Group[nuc.Group ==  "A9MH"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 24b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig24b. nucDNA Genes cpm in A4V and Silent 9-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

mean.data = na.omit(A4V.meancpm[, c('A9FH', 'S9FH',
                                    'A9MH', 'S9MH')])

main.title = "Fig 25"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig25 nucDNA Genes FC in A4V and Silent 9-Day Heads: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS40FH"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S40FH"] = 1
nuc.Group[nuc.Group ==  "A40FH"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 26a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig26a. nucDNA Genes cpm in A4V and Silent 40-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS40FH"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FH'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FH'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FH"] = 1
nuc.Group[nuc.Group ==  "A3FH"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 26b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig26b. nucDNA Genes cpm in A4V and Silent 40-Day Heads: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MH'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MH'])

x = c("AvS3FH", "AvS9FH", "AvS40FH",
      "AvS3MH", "AvS9MH")

OXPHOS.FC.cutoff = apply(abs(na.omit(A4V.FC[oxphos,c(x)])), 1, min)
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = A4V.cpm[ofc, Head]

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10])

AV.nuc = na.omit(AV.nuc[ofc, ])

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FH"] = 0
nuc.Group[nuc.Group ==  "S9FH"] = 1
nuc.Group[nuc.Group ==  "S40FH"] = 2
nuc.Group[nuc.Group ==  "A3FH"] = 3
nuc.Group[nuc.Group ==  "A9FH"] = 4
nuc.Group[nuc.Group ==  "A40FH"] = 5
nuc.Group[nuc.Group ==  "S3MH"] = 6
nuc.Group[nuc.Group ==  "S9MH"] = 7
nuc.Group[nuc.Group ==  "A3MH"] = 8
nuc.Group[nuc.Group ==  "A9MH"] = 9

nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = paste0(substr(nuc.Geno, 1,1), substr(nuc.Geno, nchar(nuc.Geno)-1, nchar(nuc.Geno)))
nuc.Geno[nuc.Geno == "SFH"] = 1
nuc.Geno[nuc.Geno == "AFH"] = 2
nuc.Geno[nuc.Geno == "SMH"] = 3
nuc.Geno[nuc.Geno == "AMH"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))
nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Geno,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(11*length(ofc))), c(1:length(ofc))*11)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 27",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c((c(0:(length(ofc)-1))*11)+5), tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```
</br>

Fig27a. nucDNA Genes cpm in A4V and Silent Head at all timepoints: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female for all comparisons and a mean cpm of at least 10 in 1 of the conditions.

</br></br>

## nucDNA Genes in Thorax Samples

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FT"] = 1
nuc.Group[nuc.Group ==  "A3FT"] = 2
nuc.Group[nuc.Group ==  "S3MT"] = 3
nuc.Group[nuc.Group ==  "A3MT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 28a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig28a. nucDNA Genes cpm in A4V and Silent 3-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FT"] = 1
nuc.Group[nuc.Group ==  "A3FT"] = 2
nuc.Group[nuc.Group ==  "S3MT"] = 3
nuc.Group[nuc.Group ==  "A3MT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 28b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig28b. nucDNA Genes cpm in A4V and Silent 3-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

mean.data = na.omit(A4V.meancpm[, c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])

main.title = "Fig 29"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig29 nucDNA Genes FC in A4V and Silent 3-Day Thorax: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FT"] = 1
nuc.Group[nuc.Group ==  "A9FT"] = 2
nuc.Group[nuc.Group ==  "S9MT"] = 3
nuc.Group[nuc.Group ==  "A9MT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 30a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig30a. nucDNA Genes cpm in A4V and Silent 9-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FT"] = 1
nuc.Group[nuc.Group ==  "A9FT"] = 2
nuc.Group[nuc.Group ==  "S9MT"] = 3
nuc.Group[nuc.Group ==  "A9MT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 30b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig30b. nucDNA Genes cpm in A4V and Silent 9-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

mean.data = na.omit(A4V.meancpm[, c('A9FT', 'S9FT',
                                    'A9MT', 'S9MT')])

main.title = "Fig 31"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig31 nucDNA Genes FC in A4V and Silent 9-Day Thorax: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS40FT"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S40FT"] = 1
nuc.Group[nuc.Group ==  "A40FT"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 32a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig32a. nucDNA Genes cpm in A4V and Silent 40-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS40FT"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FT'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S40FT"] = 1
nuc.Group[nuc.Group ==  "A40FT"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 32b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig32b. nucDNA Genes cpm in A4V and Silent 40-Day Thorax: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])

x = c("AvS3FT", "AvS9FT", "AvS40FT",
      "AvS3MT", "AvS9MT")

OXPHOS.FC.cutoff = apply(abs(na.omit(A4V.FC[oxphos,c(x)])), 1, max)
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = A4V.cpm[ofc, Head]

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = na.omit(AV.nuc[ofc, ])

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FT"] = 0
nuc.Group[nuc.Group ==  "S9FT"] = 1
nuc.Group[nuc.Group ==  "S40FT"] = 2
nuc.Group[nuc.Group ==  "A3FT"] = 3
nuc.Group[nuc.Group ==  "A9FT"] = 4
nuc.Group[nuc.Group ==  "A40FT"] = 5
nuc.Group[nuc.Group ==  "S3MT"] = 6
nuc.Group[nuc.Group ==  "S9MT"] = 7
nuc.Group[nuc.Group ==  "A3MT"] = 8
nuc.Group[nuc.Group ==  "A9MT"] = 9

nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = paste0(substr(nuc.Geno, 1,1), substr(nuc.Geno, nchar(nuc.Geno)-1, nchar(nuc.Geno)))
nuc.Geno[nuc.Geno == "SFT"] = 1
nuc.Geno[nuc.Geno == "AFT"] = 2
nuc.Geno[nuc.Geno == "SMT"] = 3
nuc.Geno[nuc.Geno == "AMT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))
nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Geno,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(11*length(ofc))), c(1:length(ofc))*11)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 33a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c((c(0:(length(ofc)-1))*11)+5), tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig33a. nucDNA Genes cpm in A4V and Silent Thorax at all timepoints: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female for at least 1 comparison and a mean cpm of at least 10 in 1 of the conditionss and less than 1000 in all of the conditions.

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MT'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MT'])

x = c("AvS3FT", "AvS9FT", "AvS40FT",
      "AvS3MT", "AvS9MT")

OXPHOS.FC.cutoff = apply(abs(na.omit(A4V.FC[oxphos,c(x)])), 1, max)
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = A4V.cpm[ofc, Head]

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = na.omit(AV.nuc[ofc, ])

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FT"] = 0
nuc.Group[nuc.Group ==  "S9FT"] = 1
nuc.Group[nuc.Group ==  "S40FT"] = 2
nuc.Group[nuc.Group ==  "A3FT"] = 3
nuc.Group[nuc.Group ==  "A9FT"] = 4
nuc.Group[nuc.Group ==  "A40FT"] = 5
nuc.Group[nuc.Group ==  "S3MT"] = 6
nuc.Group[nuc.Group ==  "S9MT"] = 7
nuc.Group[nuc.Group ==  "A3MT"] = 8
nuc.Group[nuc.Group ==  "A9MT"] = 9

nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = paste0(substr(nuc.Geno, 1,1), substr(nuc.Geno, nchar(nuc.Geno)-1, nchar(nuc.Geno)))
nuc.Geno[nuc.Geno == "SFT"] = 1
nuc.Geno[nuc.Geno == "AFT"] = 2
nuc.Geno[nuc.Geno == "SMT"] = 3
nuc.Geno[nuc.Geno == "AMT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))
nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Geno,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(11*length(ofc))), c(1:length(ofc))*11)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 33b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c((c(0:(length(ofc)-1))*11)+5), tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig33b. nucDNA Genes cpm in A4V and Silent Thorax at all timepoints: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female for at least 1 comparison and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

## nucDNA Genes in Abdomen Samples

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FA"] = 1
nuc.Group[nuc.Group ==  "A3FA"] = 2
nuc.Group[nuc.Group ==  "S3MA"] = 3
nuc.Group[nuc.Group ==  "A3MA"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 34a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig34a. nucDNA Genes cpm in A4V and Silent 3-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A3MA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FA"] = 1
nuc.Group[nuc.Group ==  "A3FA"] = 2
nuc.Group[nuc.Group ==  "S3MA"] = 3
nuc.Group[nuc.Group ==  "A3MT"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 34b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig34b. nucDNA Genes cpm in A4V and Silent 3-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

mean.data = na.omit(A4V.meancpm[, c('A3FA', 'S3FA',
                                    'A3MA', 'S3MA')])

main.title = "Fig 35"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig35 nucDNA Genes FC in A4V and Silent 3-Day Abdomen: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FA"] = 1
nuc.Group[nuc.Group ==  "A9FA"] = 2
nuc.Group[nuc.Group ==  "S9MA"] = 3
nuc.Group[nuc.Group ==  "A9MA"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 36a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig36a. nucDNA Genes cpm in A4V and Silent 9-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

OXPHOS.FC.cutoff = abs(apply(na.omit(A4V.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S9FA"] = 1
nuc.Group[nuc.Group ==  "A9FA"] = 2
nuc.Group[nuc.Group ==  "S9MA"] = 3
nuc.Group[nuc.Group ==  "A9MA"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*5)), c(1:length(ofc))*5)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 36b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*5)+2.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig36b. nucDNA Genes cpm in A4V and Silent 9-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

mean.data = na.omit(A4V.meancpm[, c('A9FA', 'S9FA',
                                    'A9MA', 'S9MA')])

main.title = "Fig 37"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.biplot(oxphos, x, y, mean.data, main.title)

AVxWT.CH.RG[[1]]

```

</br>

Fig37 nucDNA Genes FC in A4V and Silent 9-Day Abdomen: log2(FC) for A4V/Silent in Female (xaxis) and Male (yaxis)

</br></br>

```{r echo = F}

x = "AvS40FA"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S40FA"] = 1
nuc.Group[nuc.Group ==  "A40FA"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 38a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig38a. nucDNA Genes cpm in A4V and Silent 40-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 10 in 1 of the conditions and less than 1000 in all of the conditions.

</br></br>

```{r echo = F}

x = "AvS40FA"

OXPHOS.FC.cutoff = abs(na.omit(setNames(A4V.FC[oxphos,c(x)], oxphos)))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = na.omit(A4V.cpm[ofc, c(row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
                                row.names(A4V.meta)[A4V.meta$Group == 'A40FA'])])

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = AV.nuc[ofc,]

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S40FA"] = 1
nuc.Group[nuc.Group ==  "A40FA"] = 2

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))

nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Group,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(length(ofc)*3)), c(1:length(ofc))*3)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25)),
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 38b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c(c(0:(length(ofc)-1))*3)+1.5, tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig38b. nucDNA Genes cpm in A4V and Silent 40-Day Abdomen: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])

x = c("AvS3FA", "AvS9FA", "AvS40FA",
      "AvS3MA", "AvS9MA")

OXPHOS.FC.cutoff = apply(abs(na.omit(A4V.FC[oxphos,c(x)])), 1, max)
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = A4V.cpm[ofc, Head]

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10 & cpm.cutoff < 1000])

AV.nuc = na.omit(AV.nuc[ofc, ])

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FA"] = 0
nuc.Group[nuc.Group ==  "S9FA"] = 1
nuc.Group[nuc.Group ==  "S40FA"] = 2
nuc.Group[nuc.Group ==  "A3FA"] = 3
nuc.Group[nuc.Group ==  "A9FA"] = 4
nuc.Group[nuc.Group ==  "A40FA"] = 5
nuc.Group[nuc.Group ==  "S3MA"] = 6
nuc.Group[nuc.Group ==  "S9MA"] = 7
nuc.Group[nuc.Group ==  "A3MA"] = 8
nuc.Group[nuc.Group ==  "A9MA"] = 9

nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = paste0(substr(nuc.Geno, 1,1), substr(nuc.Geno, nchar(nuc.Geno)-1, nchar(nuc.Geno)))
nuc.Geno[nuc.Geno == "SFA"] = 1
nuc.Geno[nuc.Geno == "AFA"] = 2
nuc.Geno[nuc.Geno == "SMA"] = 3
nuc.Geno[nuc.Geno == "AMA"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))
nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Geno,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(11*length(ofc))), c(1:length(ofc))*11)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 39a",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c((c(0:(length(ofc)-1))*11)+5), tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig39a. nucDNA Genes cpm in A4V and Silent Abdomen at all timepoints: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female for at least 1 comparison and a mean cpm of at least 10 in 1 of the conditionss and less than 1000 in all of the conditions.

</br></br>

```{r echo = F, fig.width = 15, fig.height = 8}

Head = c(row.names(A4V.meta)[A4V.meta$Group == 'S3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A40FA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'S9MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A3MA'],
         row.names(A4V.meta)[A4V.meta$Group == 'A9MA'])

x = c("AvS3FA", "AvS9FA", "AvS40FA",
      "AvS3MA", "AvS9MA")

OXPHOS.FC.cutoff = apply(abs(na.omit(A4V.FC[oxphos,c(x)])), 1, max)
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

AV.nuc = A4V.cpm[ofc, Head]

cpm.cutoff = apply(AV.nuc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 1000])

AV.nuc = na.omit(AV.nuc[ofc, ])

row.names(AV.nuc) = GeneIDKey[row.names(AV.nuc), "Symbol"]
colnames(AV.nuc) = A4V.meta[colnames(AV.nuc), "Group"]
AV.nuc = t(AV.nuc)

nuc.Group = rep(row.names(AV.nuc), length(ofc))
nuc.Group[nuc.Group ==  "S3FA"] = 0
nuc.Group[nuc.Group ==  "S9FA"] = 1
nuc.Group[nuc.Group ==  "S40FA"] = 2
nuc.Group[nuc.Group ==  "A3FA"] = 3
nuc.Group[nuc.Group ==  "A9FA"] = 4
nuc.Group[nuc.Group ==  "A40FA"] = 5
nuc.Group[nuc.Group ==  "S3MA"] = 6
nuc.Group[nuc.Group ==  "S9MA"] = 7
nuc.Group[nuc.Group ==  "A3MA"] = 8
nuc.Group[nuc.Group ==  "A9MA"] = 9

nuc.Geno = rep(row.names(AV.nuc), length(ofc))
nuc.Geno = paste0(substr(nuc.Geno, 1,1), substr(nuc.Geno, nchar(nuc.Geno)-1, nchar(nuc.Geno)))
nuc.Geno[nuc.Geno == "SFA"] = 1
nuc.Geno[nuc.Geno == "AFA"] = 2
nuc.Geno[nuc.Geno == "SMA"] = 3
nuc.Geno[nuc.Geno == "AMA"] = 4

nuc.Gene = as.character(t(matrix(rep(colnames(AV.nuc), nrow(AV.nuc)), ncol = nrow(AV.nuc))))
nuc.cpm = as.numeric(AV.nuc)

AV.nuc = data.frame(Group = paste(nuc.Gene, nuc.Group),
                   cpm = nuc.cpm,
                   geno = nuc.Geno,
                   gene = nuc.Gene)

box.at = setdiff(c(1:(11*length(ofc))), c(1:length(ofc))*11)

boxplot(AV.nuc$cpm~AV.nuc$Group,
        las = 2,
        col = c(hex("steelblue", .25), hex("darkgreen", .25), 
                hex("firebrick", .25), hex("gold", .2))[c(1,1,1,2,2,2,3,3,4,4)],
        at = box.at,
        xaxt = "none",
        xlab = "Gene",
        ylab = "CPM",
        main = "Fig 39b",
        boxlwd = 1.5,
        lwd = 1.5)

points(x=box.at[as.numeric(factor(AV.nuc$Group))],
       y=AV.nuc$cpm,
       cex=1,
       pch=21,
       bg=c("dodgerblue","darkgreen",'firebrick',"gold")[as.numeric(factor(AV.nuc$geno))])

axis(1, at= c((c(0:(length(ofc)-1))*11)+5), tick = F, line = -.5, labels = c(unique(AV.nuc$gene)[order(unique(AV.nuc$gene))]), las = 2)

legend("topright",
       legend = c("Silent F", "A4V F", "Silent M", "A4V M"),
       pch = 21,
       pt.bg = c("dodgerblue","darkgreen",'firebrick',"gold"),
       bty = 'n',
       y.intersp = 1)

```

</br>

Fig39b. nucDNA Genes cpm in A4V and Silent Abdomen at all timepoints: cpm data for nucDNA genes in A4V and Silent. FC of at least 50% in male or female for at least 1 comparison and a mean cpm of at least 1000 in 1 of the conditions.

</br></br>

## Specific OXPHOS Complex FC plots

```{r echo = F}

AllComplexTerms = GO.Names[grep("respiratory chain complex I", GO.Names$term),]

CI = GeneIDKey[GeneIDKey$ensembl %in% genesingo[["GO:0045271"]], ]
CI$Complex = "Complex I"
CII = GeneIDKey[GeneIDKey$ensembl %in% genesingo[["GO:0045273"]], ]
CII$Complex = "Complex II"
CIII = GeneIDKey[GeneIDKey$ensembl %in% genesingo[["GO:0045275"]], ]
CIII$Complex = "Complex III"
CIV = GeneIDKey[GeneIDKey$ensembl %in% genesingo[["GO:0045277"]], ]
CIV$Complex = "Complex IV"
CV = GeneIDKey[GeneIDKey$ensembl %in% genesingo[["GO:0045259"]], ]
CV$Complex = "Complex V"

complex.genes = rbind(CI, rbind(CII, rbind(CIII, rbind(CIV, CV))))

Other = GeneIDKey[GeneIDKey$FBgn %in% setdiff(oxphos, complex.genes$FBgn),]
Other$Complex = "Other"
complex.genes = rbind(complex.genes, Other)
complex.genes=complex.genes[,c("FBgn", "Symbol", "CHR", "Complex")]

```

```{r echo = F}

GR.ComplexGenes.biplot = function(x, y, mean.data, main.title){

genes = complex.genes[, c("FBgn")]

FC.data = TKT.EdgeR.FC[genes, c(x, y)]
FDR.data = TKT.EdgeR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  Complex = factor(complex.genes[genes, 'Complex']),
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  data[row.names(CI), 'Color'] = 'royalblue'
  data[row.names(CII), 'Color'] = 'firebrick' 
  data[row.names(CIII), 'Color'] = 'gold'
  data[row.names(CIV), 'Color'] = 'darkgreen' 
  data[row.names(CV), 'Color'] = 'orchid'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  ##data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                name = ~Complex,
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n", data$Complex,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = T)

  return(list(fig, data))
}
```

```{r echo = F}

AV.ComplexGenes.biplot = function(x, y, mean.data, main.title){

genes = complex.genes[, c("FBgn")]

FC.data = A4V.FC[genes, c(x, y)]
FDR.data = A4V.FDR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  Complex = factor(complex.genes[genes, 'Complex']),
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  data[row.names(CI), 'Color'] = 'royalblue'
  data[row.names(CII), 'Color'] = 'firebrick' 
  data[row.names(CIII), 'Color'] = 'gold'
  data[row.names(CIV), 'Color'] = 'darkgreen' 
  data[row.names(CV), 'Color'] = 'orchid'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  ##data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                name = ~Complex,
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n", data$Complex,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = T)

  return(list(fig, data))
}
```

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = (G85R.meancpm[, c('GR.F', 'WT.F',
                              'GR.M', 'WT.M')])

main.title = "Fig 40"

##RG = Response Genes
mtGRxWT.C.RG = GR.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig40. OXPHOS Genes cpm in G85R relative to Silent: FC for all OXPHOS with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

mean.data = (A4V.meancpm[, c('A3FH', 'S3FH',
                             'A3MH', 'S3MH')])

main.title = "Fig 41"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig41. OXPHOS Genes cpm in A4V relative to Silent 3-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

mean.data = (A4V.meancpm[, c('A9FH', 'S9FH',
                             'A9MH', 'S9MH')])

main.title = "Fig 42"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig42. OXPHOS Genes cpm in A4V relative to Silent 9-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

mean.data = (A4V.meancpm[, c('A40FH', 'S40FH',
                             'A9MH', 'S9MH')])

main.title = "Fig 43"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig43. OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

mean.data = (A4V.meancpm[, c('A3FT', 'S3FT',
                             'A3MT', 'S3MT')])

main.title = "Fig 44"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig44. OXPHOS Genes cpm in A4V relative to Silent 3-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

mean.data = (A4V.meancpm[, c('A9FT', 'S9FT',
                             'A9MT', 'S9MT')])

main.title = "Fig 45"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig45. OXPHOS Genes cpm in A4V relative to Silent 9-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

mean.data = (A4V.meancpm[, c('A40FT', 'S40FT',
                             'A9MT', 'S9MT')])

main.title = "Fig 46"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig46. OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male thorax: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

mean.data = (A4V.meancpm[, c('A3FA', 'S3FA',
                             'A3MA', 'S3MA')])

main.title = "Fig 47"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig47. OXPHOS Genes cpm in A4V relative to Silent 3-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

mean.data = (A4V.meancpm[, c('A9FA', 'S9FA',
                             'A9MA', 'S9MA')])

main.title = "Fig 48"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig48. OXPHOS Genes cpm in A4V relative to Silent 9-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

```{r echo = F}

x = "AvS40FA"
y = "AvS9MA"

mean.data = (A4V.meancpm[, c('A40FA', 'S40FA',
                             'A9MA', 'S9MA')])

main.title = "Fig 49"

##RG = Response Genes
mtGRxWT.C.RG = AV.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig49. OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male abdomen: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis. Colors indicate if they were in the GO term for that complex. the "Other" category are genes that were in the OXPHOS GO category but not found in any of the individual complex terms.

</br></br>

## Qiagen AD Array Genes

Drosophila Orthologs of the listed Human Genes were collected using GeneCards

```{r echo = F}

Array.Genes = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/QiagenADArrayGenes.csv", header = T)

Array.Genes = Array.Genes[Array.Genes$FBgn != "",]

```

```{r echo = F}

GR.ArrayGenes.biplot = function(x, y, mean.data, main.title){

genes = Array.Genes[, c("FBgn")]

FC.data = TKT.EdgeR.FC[genes, c(x, y)]
FDR.data = TKT.EdgeR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  Human = Array.Genes$HumanSymbol,
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  data$size = 2.5*data$size

  data = unique(data)

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                #name = ~Complex,
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\nHuman Ortholog: ", data$Human,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r echo = F}

AV.ArrayGenes.biplot = function(x, y, mean.data, main.title){

genes = Array.Genes[, c("FBgn")]

FC.data = A4V.FC[genes, c(x, y)]
FDR.data = A4V.FDR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  Human = Array.Genes$HumanSymbol,
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  data$size = 2.5*data$size

  data = unique(data)

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                #name = ~Complex,
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\nHuman Ortholog: ", data$Human,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = (G85R.meancpm[, c('GR.F', 'WT.F',
                              'GR.M', 'WT.M')])

main.title = "Fig 50"

##RG = Response Genes
mtGRxWT.C.RG = GR.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig50. AD Array Genes cpm in G85R relative to Silent: FC for all AD Array Genes with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

mean.data = (A4V.meancpm[, c('A3FH', 'S3FH',
                             'A3MH', 'S3MH')])

main.title = "Fig 51"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig51. AD Array Genes cpm in A4V relative to Silent 3-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

mean.data = (A4V.meancpm[, c('A9FH', 'S9FH',
                             'A9MH', 'S9MH')])

main.title = "Fig 52"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig52. AD Array Genes cpm in A4V relative to Silent 9-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

mean.data = (A4V.meancpm[, c('A40FH', 'S40FH',
                             'A9MH', 'S9MH')])

main.title = "Fig 53"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig53. AD Array Genes cpm in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

mean.data = (A4V.meancpm[, c('A3FT', 'S3FT',
                             'A3MT', 'S3MT')])

main.title = "Fig 54"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig54. AD Array Genes cpm in A4V relative to Silent 3-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

mean.data = (A4V.meancpm[, c('A9FT', 'S9FT',
                             'A9MT', 'S9MT')])

main.title = "Fig 55"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig55. AD Array Genes cpm in A4V relative to Silent 9-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

mean.data = (A4V.meancpm[, c('A40FT', 'S40FT',
                             'A9MT', 'S9MT')])

main.title = "Fig 56"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig56. AD Array Genes cpm in A4V relative to Silent 40-day female thorax and 9-day male thorax: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS3FA"
y = "AvS3MA"

mean.data = (A4V.meancpm[, c('A3FA', 'S3FA',
                             'A3MA', 'S3MA')])

main.title = "Fig 57"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig57. AD Array Genes cpm in A4V relative to Silent 3-Day abdomen: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS9FA"
y = "AvS9MA"

mean.data = (A4V.meancpm[, c('A9FA', 'S9FA',
                             'A9MA', 'S9MA')])

main.title = "Fig 58"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig58. AD Array Genes cpm in A4V relative to Silent 9-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.

</br></br>

```{r echo = F}

x = "AvS40FA"
y = "AvS9MA"

mean.data = (A4V.meancpm[, c('A40FA', 'S40FA',
                             'A9MA', 'S9MA')])

main.title = "Fig 59"

##RG = Response Genes
mtGRxWT.C.RG = AV.ArrayGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

</br>

Fig59. AD Array Genes cpm in A4V relative to Silent 40-day female abdomen and 9-day male abdomen: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.

</br></br>

## Specific OXPHOS subset plots

```{r echo = F}

x = "GRxWT.FC"
y = "GRxWT.MC"

OXPHOS.FC.cutoff = abs(apply(na.omit(TKT.EdgeR.FC[oxphos,c(x,y)]), 1, max))
OXPHOS.FC.cutoff = OXPHOS.FC.cutoff[OXPHOS.FC.cutoff > log2(1.5)]

ofc = names(OXPHOS.FC.cutoff)

GR.ofc = na.omit(cpmdata[ofc, c(groups[groups$Group == 'WT.F', 'SampleID'],
                                groups[groups$Group == 'GR.F', 'SampleID'],
                                groups[groups$Group == 'WT.M', 'SampleID'],
                                groups[groups$Group == 'GR.M', 'SampleID'])])

cpm.cutoff = apply(GR.ofc, 1, max)
ofc = names(cpm.cutoff[cpm.cutoff > 10])

mean.data = na.omit(G85R.meancpm[ofc, c('GR.F', 'WT.F',
                                       'GR.M', 'WT.M')])

main.title = "Fig 60"

##RG = Response Genes
mtGRxWT.C.RG = GR.ComplexGenes.biplot(x, y, mean.data, main.title)

mtGRxWT.C.RG[[1]]

```

Fig. 60 Genes in G85R that have a FC of at least 50% in male or female relative to silent and a mean cpm of at least 10 in 1 of the conditions. NOTES: CG9005 is a transcriptional regulator of key OXPHOS genes. CG14757 is a SDH assembly factor that als modulates copper ion homeostasis.

</br></br>

```{r echo = F}

AV.SpecificGenes.mtvnuc.biplot = function(genes, x, y, mean.data, main.title, color){

FC.data = A4V.FC[genes, c(x, y)]
FDR.data = A4V.FDR[genes, c(x, y)]
mean.data = mean.data[genes, ]

data = data.frame(Symbol = GeneIDKey[genes, "Symbol"],
                  FBgn = genes,
                  FDR1 = FDR.data[, x],
                  FDR2 = FDR.data[, y],
                  FC1 = FC.data[, x],
                  FC2 = FC.data[, y],
                  Color = 'grey',
                  size = 1,
                  Variable1.cpm = mean.data[,1],
                  Control1.cpm = mean.data[,2],
                  Variable2.cpm = mean.data[,3],
                  Control2.cpm = mean.data[,4])
  row.names(data) = data$FBgn

  data[intersect(genes, mt), 'Color'] = color
  #data[y.genes, 'Color'] = 'firebrick' 
  #data[xy.genes, 'Color'] = 'gold'

  data$size = log2(apply(mean.data, 1, max))
  data$size[data$size<3] = 1
  data = na.omit(data)
  ##data = data[data$size > log2(min.expression),]
  data$size = 2.5*data$size

  fig = plot_ly(data = data,
                x = ~FC1,
                y = ~FC2,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Symbol:", data$Symbol,
                                  "\nFBgn:", data$FBgn,
                                  "\n ", colnames(FDR.data)[1], "FDR: ", round(data$FDR1, 2),
                                  "\n ", colnames(FDR.data)[2], "FDR: ", round(data$FDR2,2),
                                  "\n ", colnames(FC.data)[1], "FC: ", round(data$FC1, 2),
                                  "\n ", colnames(FC.data)[2], "FC: ", round(data$FC2,2),
                                  "\n ", colnames(mean.data)[1], "mean CPM: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean CPM: ", signif(data$Control1,2),
                                  "\n ", colnames(mean.data)[3], "mean CPM: ", signif(data$Variable2,2),
                                  "\n ", colnames(mean.data)[4], "mean CPM: ", signif(data$Control2,2)))

  fig = fig %>% layout(title = main.title,
                       shapes = list(
                         type = "line",
                         line = list(color = "black", dash = 'dash', width = 2),
                         x0 = min(data$FC1, data$FC2) - .25,
                         x1 = max(data$FC1, data$FC2) + .25,
                         y0 = min(data$FC1, data$FC2) - .25,
                         y1 = max(data$FC1, data$FC2) + .25),
                       xaxis = list(title = paste(colnames(FC.data)[1], "FC")),
                       yaxis = list(title = paste(colnames(FC.data)[2], "FC")),
                       showlegend = F)

  return(list(fig, data))
}
```

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 61"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 61 FC of Complex I genes in A4V male and female head samples at 3 day relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A9FH', 'S9FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 62"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 62 FC of Complex I genes in A4V male and female head samples at 9 day relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A40FH', 'S40FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 63"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 63 FC of Complex I genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFH"
y = "AvSMH"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('AFH', 'SFH',
                                                 'AMH', 'SMH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 64"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 64 FC of Complex I genes in A4V male and female head samples relative to silent. All time points were combined. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 65"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 65 FC of Complex I genes in A4V male and female thorax samples at 3 day relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A9FT', 'S9FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 66"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 66 FC of Complex I genes in A4V male and female thorax samples at 9 day relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A40FT', 'S40FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 67"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 67 FC of Complex I genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFT"
y = "AvSMT"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('AFT', 'SFT',
                                                 'AMT', 'SMT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 68"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'gold')

AVxWT.CH.RG[[1]]

```

Fig. 68 FC of Complex I genes in A4V male and female thorax samples relative to silent. All time points were combined. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 69"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 69 FC of Complex II genes in A4V male and female head samples at 3 day relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('A9FH', 'S9FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 70"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 70 FC of Complex II genes in A4V male and female head samples at 9 day relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('A40FH', 'S40FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 71"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 71 FC of Complex II genes in A4V male 9 day and female 40 day head samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFH"
y = "AvSMH"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('AFH', 'SFH',
                                                 'AMH', 'SMH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 72"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 72 FC of Complex II genes in A4V male 9 day and female 40 day head samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 73"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 73 FC of Complex II genes in A4V male and female thorax samples at 3 day relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('A9FT', 'S9FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 74"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 74 FC of Complex II genes in A4V male and female thorax samples at 9 day relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('A40FT', 'S40FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 75"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 75 FC of Complex II genes in A4V male 9 day and female 40 day head samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFT"
y = "AvSMT"

genes = row.names(CII)

mean.data = na.omit(A4V.meancpm[row.names(CII), c('AFT', 'SFT',
                                                 'AMT', 'SMT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 76"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'grey')

AVxWT.CH.RG[[1]]

```

Fig. 76 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 77"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 77 FC of Complex III genes in A4V male and female head samples at 3 day relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A9FH', 'S9FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 78"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 78 FC of Complex III genes in A4V male and female head samples at 9 day relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A40FH', 'S40FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 79"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 79 FC of Complex III genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFH"
y = "AvSMH"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('AFH', 'SFH',
                                                 'AMH', 'SMH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 80"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 80 FC of Complex III genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 81"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 81 FC of Complex IV genes in A4V male and female thorax samples at 3 day relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A9FT', 'S9FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 82"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 82 FC of Complex IV genes in A4V male and female thorax samples at 9 day relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('A40FT', 'S40FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 83"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 83 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFT"
y = "AvSMT"

genes = row.names(CIII)

mean.data = na.omit(A4V.meancpm[row.names(CIII), c('AFT', 'SFT',
                                                 'AMT', 'SMT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 84"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'darkgreen')

AVxWT.CH.RG[[1]]

```

Fig. 84 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 85"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 85 FC of Complex IV genes in A4V male and female head samples at 3 day relative to silent. mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A9FH', 'S9FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 86"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 86 FC of Complex IV genes in A4V male and female head samples at 9 day relative to silent. mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A40FH', 'S40FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 87"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 87 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFH"
y = "AvSMH"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('AFH', 'SFH',
                                                 'AMH', 'SMH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 88"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 88 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 89"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 89 FC of Complex IV genes in A4V male and female thorax samples at 3 day relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A9FT', 'S9FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 90"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 90 FC of Complex IV genes in A4V male and female thorax samples at 9 day relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('A40FT', 'S40FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 91"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 91 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFT"
y = "AvSMT"

genes = row.names(CIV)

mean.data = na.omit(A4V.meancpm[row.names(CIV), c('AFT', 'SFT',
                                                 'AMT', 'SMT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 92"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'steelblue')

AVxWT.CH.RG[[1]]

```

Fig. 92 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FH"
y = "AvS3MH"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A3FH', 'S3FH',
                                    'A3MH', 'S3MH')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 93"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 93 FC of Complex V genes in A4V male and female head samples at 3 day relative to silent. mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FH"
y = "AvS9MH"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A9FH', 'S9FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 94"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 94 FC of Complex V genes in A4V male and female head samples at 9 day relative to silent. mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FH"
y = "AvS9MH"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A40FH', 'S40FH',
                                                 'A9MH', 'S9MH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 95"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 95 FC of Complex V genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFH"
y = "AvSMH"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('AFH', 'SFH',
                                                 'AMH', 'SMH')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 96"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 96 FC of Complex V genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 97"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 97 FC of Complex IV genes in A4V male and female thorax samples at 3 day relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS9FT"
y = "AvS9MT"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A9FT', 'S9FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 98"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 98 FC of Complex IV genes in A4V male and female thorax samples at 9 day relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvS40FT"
y = "AvS9MT"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('A40FT', 'S40FT',
                                                 'A9MT', 'S9MT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 99"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 99 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F}

x = "AvSFT"
y = "AvSMT"

genes = row.names(CV)

mean.data = na.omit(A4V.meancpm[row.names(CV), c('AFT', 'SFT',
                                                 'AMT', 'SMT')])

temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 100"

##RG = Response Genes
AVxWT.CH.RG = AV.SpecificGenes.mtvnuc.biplot(genes, x, y, mean.data, main.title, 'brown')

AVxWT.CH.RG[[1]]

```

Fig. 100 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.

</br></br>

```{r echo = F, include = F}

x = "AvS3FT"
y = "AvS3MT"

genes = row.names(CI)

mean.data = na.omit(A4V.meancpm[row.names(CI), c('A3FT', 'S3FT',
                                    'A3MT', 'S3MT')])
temp.cpmcutoff = apply(mean.data, 1, max)
temp.cpmcutoff = temp.cpmcutoff[temp.cpmcutoff >10]
genes = intersect(genes, names(temp.cpmcutoff))

main.title = "Fig 65"

```

```{r echo = F, iclude = F}

complex.genes[row.names(complex.genes) %in% mt, "CHR"] = "mt"

complex.cpm = na.omit(TKT.cpm[row.names(complex.genes),
                              c("GR.F1", "GR.F2", "GR.M1", "GR.M2", "GR.M3",
                                "WT.F1", "WT.F2", "WT.M1", "WT.M2", "WT.M3")])
row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

complex.data = complex.genes
row.names(complex.data) = complex.data$Symbol
complex.data = complex.data[row.names(complex.cpm),]
complex.data = cbind(complex.data[row.names(complex.cpm),], complex.cpm)

pca <- prcomp((complex.cpm), scale.=TRUE) 
pc1=scale(pca$x[,1])
pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    CHR = complex.data[row.names(pc1), "CHR"],
                    Complex = complex.data[row.names(pc1), "Complex"],
                    Group = paste0(complex.data[row.names(pc1), "CHR"],": ",
                                   complex.data[row.names(pc1), "Complex"]))

pca.data$CHR[pca.data$CHR != "mt"] = "nuc"
pca.data$Group = paste0(pca.data$CHR,": ", pca.data$Complex)

    #pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    #pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Complex,
                 symbol = ~CHR,
                 marker = list(size = 10,
                               line = list(color = "black", width = 1.5))) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "Enriched GO term similarity")

  fig
```

```{r echo = F, warning = F, include = F}

complex.genes[row.names(complex.genes) %in% mt, "CHR"] = "mt"

complex.cpm = na.omit(A4V.cpm[row.names(complex.genes),
                              row.names(A4V.meta[A4V.meta$Section == "Head",])])# &
                                                 #A4V.meta$Age == "3",])])
row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
complex.cpm = t(scale(t(complex.cpm)))

complex.data = complex.genes
row.names(complex.data) = complex.data$Symbol
complex.data = complex.data[row.names(complex.cpm),]
complex.data = cbind(complex.data[row.names(complex.cpm),], complex.cpm)

pca <- prcomp((complex.cpm), scale.=TRUE) 
pc1=scale(pca$x[,1])
pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    CHR = complex.data[row.names(pc1), "CHR"],
                    Complex = complex.data[row.names(pc1), "Complex"],
                    Group = paste0(complex.data[row.names(pc1), "CHR"],": ",
                                   complex.data[row.names(pc1), "Complex"]),
                    Color = "royalblue",
                    Symbol = row.names(pc1),
                    FBgn = complex.data[row.names(pc1), "FBgn"])

pca.data$CHR[pca.data$CHR != "mt"] = "nuc"
pca.data$Group = paste0(pca.data$CHR,": ", pca.data$Complex)
pca.data$Color[pca.data$CHR == 'mt'] = 'firebrick'

    #pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    #pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~CHR,
                 symbol = ~CHR,
                 marker = list(size = 10,
                               color = ~Color[order(pca.data$Color)],
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Symbol: ", row.names(pca.data),
                                   "\nFBgn: ", pca.data$FBgn, 
                                   "\nComplex: ", pca.data$Complex)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "A4V/Silent 3 Hour Head OXPHOS Genes")

  fig
```

```{r echo = F, warning = F, include = F}

complex.genes[row.names(complex.genes) %in% mt, "CHR"] = "mt"

complex.cpm = na.omit(A4V.cpm[row.names(complex.genes)[complex.genes$Complex == "Complex I" 
                                                       | complex.genes$Complex == "Complex II" 
                                                       | complex.genes$Complex == "Complex III"
                                                       | complex.genes$Complex == "Complex IV"
                                                       | complex.genes$Complex == "Complex V"],])
                              #row.names(A4V.meta[A4V.meta$Section == "Thorax" &
                              #                   (A4V.meta$Age == "3"),])])

row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
complex.cpm.all = t(scale(t(complex.cpm)))

complex.cpm = complex.cpm.all[,row.names(A4V.meta[A4V.meta$Section == "Thorax" &
                                                  (A4V.meta$Age == "9"),])]
complex.data = complex.genes
row.names(complex.data) = complex.data$Symbol
complex.data = complex.data[row.names(complex.cpm),]
complex.data = cbind(complex.data[row.names(complex.cpm),], complex.cpm)

pca <- prcomp((complex.cpm), scale.=TRUE) 
pc1=scale(pca$x[,1])
pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    CHR = complex.data[row.names(pc1), "CHR"],
                    Complex = complex.data[row.names(pc1), "Complex"],
                    Group = paste0(complex.data[row.names(pc1), "CHR"],": ",
                                   complex.data[row.names(pc1), "Complex"]),
                    Color = "royalblue",
                    Symbol = row.names(pc1),
                    FBgn = complex.data[row.names(pc1), "FBgn"])

pca.data$CHR[pca.data$CHR != "mt"] = "nuc"
pca.data$Group = paste0(pca.data$CHR,": ", pca.data$Complex)
pca.data$Color[pca.data$CHR == 'mt'] = 'firebrick'

    #pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    #pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~CHR,
                 symbol = ~CHR,
                 marker = list(size = 10,
                               color = ~Color[order(pca.data$Color)],
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Symbol: ", row.names(pca.data),
                                   "\nFBgn: ", pca.data$FBgn, 
                                   "\nComplex: ", pca.data$Complex)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "A4V/Silent 3 Hour Head OXPHOS Genes")

  fig
```

```{r echo = F, include = F}

library(gplots)

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
#                                  row.names(A4V.meta[A4V.meta$Section == "Thorax" &
#                                                  (A4V.meta$Age == "9"),])])

hmcolors=colorpanel(50,"steelblue3", "ivory",'red3')

#complex.cpm = na.omit(A4V.cpm[mt,
#                              row.names(A4V.meta[A4V.meta$Section == "Thorax",])])

row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

mt.sym = GeneIDKey[mt, "Symbol"]

complex.hmgenes = complex.cpm
complex.hmgenes = complex.hmgenes[c(setdiff(row.names(complex.hmgenes), mt.sym),
                                    intersect(row.names(complex.hmgenes), mt.sym)),]

complex.hmgenes = complex.hmgenes[c(intersect(row.names(complex.hmgenes), mt.sym)),]

T.complex.hmgenes = complex.hmgenes[,substr(colnames(complex.hmgenes), 
                                            nchar(colnames(complex.hmgenes)), 
                                            nchar(colnames(complex.hmgenes))) == "T"]

T.complex.hmgenes = T.complex.hmgenes[, c("S3FT", "S9FT", "S40FT",
                                          "A3FT", "A9FT", "A40FT",
                                          "S3MT", "S9MT",
                                          "A3MT", "A9MT")]

heatmap.2(as.matrix(T.complex.hmgenes),
          Colv = F,
          Rowv = T,
          dendrogram = "none",
          col = hmcolors,
          trace = "none",
          scale = 'row',
          cexRow = 1)

```

```{r echo = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])

complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

complex.FC = A4V.FC[row.names(complex.cpm),]

complex.FC = complex.FC[c(setdiff(row.names(complex.FC), mt),
                          intersect(row.names(complex.FC), mt)),]

complex.FC = complex.FC[c(intersect(row.names(complex.FC), mt)),]

complex.FC = complex.FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
                            "AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3FA", "AvS9FA", "AvS40FA",
                            "AvS3MH", "AvS9MH",
                            "AvS3MT", "AvS9MT",
                            "AvS3MA", "AvS9MA")]

complex.FC = complex.FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
                            "AvS3MH", "AvS9MH",
                            "AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3MT", "AvS9MT")]

row.names(complex.FC) = GeneIDKey[row.names(complex.FC), "Symbol"]

heatmap.2(as.matrix(complex.FC),
          Colv = F,
          Rowv = T,
          dendrogram = "none",
          col = hmcolors,
          trace = "none",
          ##scale = 'row',
          cexRow = 1)

```

```{r echo = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])

complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

complex.FC = A4V.FC[row.names(complex.cpm),]

complex.FC = complex.FC[c(setdiff(row.names(complex.FC), mt),
                          intersect(row.names(complex.FC), mt)),]

complex.FC = complex.FC[c(setdiff(row.names(complex.FC), mt)),]

complex.FC = complex.FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
                            "AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3FA", "AvS9FA", "AvS40FA",
                            "AvS3MH", "AvS9MH",
                            "AvS3MT", "AvS9MT",
                            "AvS3MA", "AvS9MA")]

complex.FC = complex.FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
                            "AvS3MH", "AvS9MH",
                            "AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3MT", "AvS9MT")]

row.names(complex.FC) = GeneIDKey[row.names(complex.FC), "Symbol"]

complex.FC[complex.FC < -4] = -4

heatmap.2(as.matrix(complex.FC),
          Colv = F,
          Rowv = T,
          dendrogram = "none",
          col = hmcolors,
          trace = "none",
          ##scale = 'row',
          cexRow = .25)

```

```{r echo = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])

complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

complex.FC = A4V.FC[row.names(complex.cpm),]

complex.FC = complex.FC[c(setdiff(row.names(complex.FC), mt),
                          intersect(row.names(complex.FC), mt)),]

complex.FC = complex.FC[c(setdiff(row.names(complex.FC), mt),
                          intersect(row.names(complex.FC), mt)),]

complex.FC = complex.FC[, c("AvS3FH", "AvS9FH", "AvS40FH",
                            "AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3FA", "AvS9FA", "AvS40FA",
                            "AvS3MH", "AvS9MH",
                            "AvS3MT", "AvS9MT",
                            "AvS3MA", "AvS9MA")]

complex.FC = complex.FC[, c("AvS3FT", "AvS9FT", "AvS40FT",
                            "AvS3MT", "AvS9MT")]

pca <- prcomp((complex.FC), scale.=TRUE) 
pc1=scale(pca$x[,1])

pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    CHR = complex.genes[row.names(pc1), "CHR"],
                    Complex = complex.genes[row.names(pc1), "Complex"],
                    Group = paste0(complex.genes[row.names(pc1), "CHR"],": ",
                                   complex.genes[row.names(pc1), "Complex"]),
                    Color = "royalblue",
                    Symbol = complex.genes[row.names(pc1), "Symbol"],
                    FBgn = row.names(pc1))

pca.data$CHR[pca.data$CHR != "mt"] = "nuc"
pca.data$Group = paste0(pca.data$CHR,":", pca.data$Complex)
pca.data$Color[pca.data$CHR == 'mt'] = 'firebrick'

    #pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    #pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~CHR,
                 symbol = ~CHR,
                 marker = list(size = 10,
                               color = ~Color[order(pca.data$Color)],
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Symbol: ", row.names(pca.data),
                                   "\nFBgn: ", pca.data$FBgn, 
                                   "\nComplex: ", pca.data$Complex)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "A4V/Silent 3 Hour Head OXPHOS Genes")

  fig

```

```{r echo = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),
                                  grep("T", colnames(A4V.meancpm))])

complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

complex.cpm = complex.cpm[c(setdiff(row.names(complex.cpm), mt),
                            intersect(row.names(complex.cpm), mt)),]

complex.cpm = complex.cpm[c(intersect(row.names(complex.cpm), mt)),]

complex.FC = complex.cpm[, c("S3FT", "S9FT", "S40FT",
                             "A3FT", "A9FT", "A40FT",
                             "S3MT", "S9MT",
                             "A3MT", "A9MT")]

pca <- prcomp(t(complex.FC), scale.=TRUE) 
pc1=scale(pca$x[,1])
pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    Group = paste0(substr(row.names(pc1), 1,1),
                                  substr(row.names(pc1), nchar(row.names(pc1)), nchar(row.names(pc1)))),
                    Color = "royalblue")

pca.data$Color[grep("A", pca.data$Group)] = "firebrick"

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Color,
                 marker = list(size = 10,
                               color = ~Color[order(pca.data$Color)],
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = row.names(pca.data)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "")

  fig

```

```{r echo = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
complex.cpm = complex.cpm[intersect(row.names(complex.cpm), mt),]

complex.cpm = complex.cpm[,substr(colnames(complex.cpm),
                                  nchar(colnames(complex.cpm)),
                                  nchar(colnames(complex.cpm))) == "T"]

complex.cpm = complex.cpm[, nchar(colnames(complex.cpm)) > 3]

scaled.cpm = t(scale(t(complex.cpm)))

SF = scaled.cpm[,c("S3FT", "S9FT", "S40FT")]
SM = scaled.cpm[,c("S3MT", "S9MT")]
AF = scaled.cpm[,c("A3FT", "A9FT", "A40FT")]
AM = scaled.cpm[,c("A3MT", "A9MT")]

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(-2, 3),
     xlim = c(1,6),
     ylab = '',
     xlab = '',
     xaxt = 'n',
     main = "")
i=1
while(i<= nrow(SF)){
lines(x = c(1:3),
      y = SF[i,],
      col = 'grey')

lines(x = c(1:3),
      y = AF[i,],
      col = 'grey')

  i=i+1

}

```

```{r echo = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
complex.cpm = complex.cpm[intersect(row.names(complex.cpm), mt),]

complex.cpm = complex.cpm[,substr(colnames(complex.cpm),
                                  nchar(colnames(complex.cpm)),
                                  nchar(colnames(complex.cpm))) == "T"]

complex.cpm = complex.cpm[, nchar(colnames(complex.cpm)) > 3]

scaled.cpm = t(scale(t(complex.cpm)))

SF = scaled.cpm[,c("S3FT", "S9FT", "S40FT")]
SM = scaled.cpm[,c("S3MT", "S9MT")]
AF = scaled.cpm[,c("A3FT", "A9FT", "A40FT")]
AM = scaled.cpm[,c("A3MT", "A9MT")]

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(-2, 3),
     xlim = c(1,6),
     ylab = '',
     xlab = '',
     xaxt = 'n',
     main = "")
i=1
while(i<= nrow(SF)){
lines(x = c(1:3),
      y = SF[i,],
      col = 'grey')

lines(x = c(1:3),
      y = AF[i,],
      col = 'grey')

  i=i+1

}

```

```{r echo = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
#                                  row.names(A4V.meta[A4V.meta$Section == "Thorax" &
#                                                  (A4V.meta$Age == "9"),])])

hmcolors=colorpanel(50,"steelblue3", "ivory",'red3')

#complex.cpm = na.omit(A4V.cpm[mt,
#                              row.names(A4V.meta[A4V.meta$Section == "Thorax",])])

row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]

mt.sym = GeneIDKey[mt, "Symbol"]

complex.hmgenes = complex.cpm
complex.hmgenes = complex.hmgenes[c(setdiff(row.names(complex.hmgenes), mt.sym),
                                    intersect(row.names(complex.hmgenes), mt.sym)),]

complex.hmgenes = complex.hmgenes[c(intersect(row.names(complex.hmgenes), mt.sym)),]

T.complex.hmgenes = complex.hmgenes[,substr(colnames(complex.hmgenes), 
                                            nchar(colnames(complex.hmgenes)), 
                                            nchar(colnames(complex.hmgenes))) == "H"]

T.complex.hmgenes = T.complex.hmgenes[, c("S3FH", "S9FH", "S40FH",
                                          "A3FH", "A9FH", "A40FH",
                                          "S3MH", "S9MH",
                                          "A3MH", "A9MH")]

heatmap.2(as.matrix(T.complex.hmgenes),
          Colv = F,
          Rowv = T,
          dendrogram = "none",
          col = hmcolors,
          trace = "none",
          scale = 'row',
          cexRow = .5)

```

```{r echo = F, warning = F, include = F}

complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
complex.cpm = complex.cpm[intersect(row.names(complex.cpm), mt),]

complex.cpm = complex.cpm[,substr(colnames(complex.cpm),
                                  nchar(colnames(complex.cpm)),
                                  nchar(colnames(complex.cpm))) == "T"]

complex.cpm =complex.cpm[, nchar(colnames(complex.cpm)) > 3]

pca <- prcomp(t(complex.cpm), scale.=TRUE) 
pc1=scale(pca$x[,1])
pc2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

pca.data=data.frame(PC1=pc1[row.names(pc1),1],
                    PC2=pc2[row.names(pc1),1],
                    Percent1=ve[1],
                    Percent2=ve[2],
                    Group = paste0(substr(row.names(pc1),1,1),
                                   substr(row.names(pc1),
                                          (nchar(row.names(pc1))-1),
                                          (nchar(row.names(pc1))-1))),
                    Age = substr(row.names(pc1), 2, (nchar(row.names(pc1))-2)),
                    Color = "lightgrey",
                    Symbol = 20)

pca.data$Color[pca.data$Group == "AF"] = 'firebrick'
pca.data$Color[pca.data$Group == "AM"] = 'steelblue'
pca.data$Color[pca.data$Group == "SF"] = 'ivory'

pca.data$Symbol = pca.data$Symbol + as.numeric(factor(pca.data$Group))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Symbol,
                 marker = list(size = 10,
                               color = ~Color[order(pca.data$Color)],
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Group: ", pca.data$Group,
                                   "\nAge: ", pca.data$Age)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "A4V/Silent 3 Hour Head OXPHOS Genes")

  fig
```

```{r, test-rgl, webgl=TRUE,echo=F, fig.height=10, fig.width=10, include = F}
#open3d()
#view3d( theta = -45, phi = 30)

#plot.colors = c("pink","dodgerblue","yellow","green", "grey", "purple1","red","blue","yellow3","darkgreen","black", "purple4")[as.numeric(pca.data$Group)]

#plot3d(x, y, z, col = plot.colors,type='s',size=3,
#       xlab = paste0("PC1 (",pca.data$Percent1[1],"%)"),
#       ylab = paste0("PC2 (",pca.data$Percent2[1],"%)"),
#       zlab = paste0("PC3 (",pca.data$Percent3[1],"%)"))

#plot3d(x=c(-1.2,1.5),y=c(0,0),z=c(0,0),type="l",add=T, lty=2,lwd=2,col="black")
#plot3d(x=c(0,0),y=c(-1.85,2.3),z=c(0,0),type="l",add=T, lty=2,lwd=2,col="black")
#plot3d(x=c(0,0),y=c(0,0),z=c(-2.55,2.55),type="l",add=T, lty=2,lwd=2,col="black")
#legend3d("right",legend = unique(pca.data$Groups), pch=19, col = unique(plot.colors),magnify=2,bty="n",inset=.1)
#grid3d(c("x+","y","z"))
```

### 2024-11-06 qPCR/20241010 G85R and Silent Arc1 Analysis.Rmd
pca

---
title: "G85R Arc1 Analysis"
author: "John Santiago"
date: "2024-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

Arc1 = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/qPCR/G85R and Silent Arc1_2024-10-10.csv', header = T)
Arc1$Group = substr(Arc1$Sample, 1, nchar(Arc1$Sample)-1)
Arc1 = Arc1[Arc1$Well != "A8" & Arc1$Well != "B8" & Arc1$Well != "C8" & Arc1$Well != "D8",]

Rp49 = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/qPCR/G85R and Silent Rp49_2024-10-10.csv', header = T)
Rp49$Group = substr(Rp49$Sample, 1, nchar(Rp49$Sample)-1)
Rp49 = Rp49[Rp49$Well != "A8" & Rp49$Well != "B8" & Rp49$Well != "C8",]

```

```{r}

mean.cq = setNames(rep(0, length(unique(Arc1$Sample))), unique(Arc1$Sample))
i=1
while(i<=length(mean.cq)){
  mean.cq[i] = mean(Arc1$Cq[Arc1$Sample == names(mean.cq)[i]])
  i=i+1
}

boxplotdata = data.frame(Sample = names(mean.cq),
                         Group = substr(names(mean.cq), 1, nchar(names(mean.cq))-1),
                         mean = as.numeric(mean.cq))
boxplotdata$Group = factor(boxplotdata$Group, levels = c("WTLF", "WTLM", 
                                                         "GRLF", "GRLM", 
                                                         "OreR", "Arc1OreR", "Arc1G85R"))

pointdata = data.frame(Cq = Arc1$Cq,
                       Group = Arc1$Group,
                       rep = as.numeric(substr(Arc1$Sample, nchar(Arc1$Sample), nchar(Arc1$Sample))))

Arc1Mean = boxplotdata

boxplot(boxplotdata$mean ~ boxplotdata$Group, 
        xlab="",     
        main= "Arc1 Cq",
        ylab="Cq", 
        las = 1, 
        cex.axis = .8,
        ylim = c(17,20))

points(x=as.numeric(factor(boxplotdata$Group)),
       y=boxplotdata$mean,
       cex=1,
       pch=c(22),
       bg=c('firebrick',"gold","darkgreen","dodgerblue", 'mediumorchid', "orange", "blue")[as.numeric(factor(boxplotdata$Group))])

```

```{r}

mean.cq = setNames(rep(0, length(unique(Rp49$Sample))), unique(Rp49$Sample))
i=1
while(i<=length(mean.cq)){
  mean.cq[i] = mean(Rp49$Cq[Rp49$Sample == names(mean.cq)[i]])
  i=i+1
}

boxplotdata = data.frame(Sample = names(mean.cq),
                         Group = substr(names(mean.cq), 1, nchar(names(mean.cq))-1),
                         mean = as.numeric(mean.cq))
boxplotdata$Group = factor(boxplotdata$Group, levels = c("WTLF", "WTLM", 
                                                         "GRLF", "GRLM", 
                                                         "OreR", "Arc1OreR", "Arc1G85R"))

pointdata = data.frame(Cq = Rp49$Cq,
                       Group = Rp49$Group,
                       rep = as.numeric(substr(Rp49$Sample, nchar(Rp49$Sample), nchar(Rp49$Sample))))

Rp49Mean = boxplotdata

boxplot(boxplotdata$mean ~ boxplotdata$Group, 
        xlab="",     
        main= "Rp49 Cq",
        ylab="Cq", 
        las = 1, 
        cex.axis = .8,
        ylim = c(17,20))

points(x=as.numeric(factor(boxplotdata$Group)),
       y=boxplotdata$mean,
       cex=1,
       pch=c(22),
       bg=c('firebrick',"gold","darkgreen","dodgerblue", 'mediumorchid', "orange", "blue")[as.numeric(factor(boxplotdata$Group))])

```

```{r}

row.names(Rp49Mean) = Rp49Mean$Sample

dCt = data.frame(Sample = Arc1Mean$Sample,
                 Group = Arc1Mean$Group,
                 Arc1 = Arc1Mean$mean,
                 Rp49 = Rp49Mean[Arc1Mean$Sample, "mean"])

dCt$dCt = dCt$Arc1 - dCt$Rp49
dCt$FC = 2^-dCt$dCt

boxplot(dCt$FC ~ dCt$Group, 
        xlab="",     
        main= "Arc1/Rp49 dCt",
        ylab="FC", 
        las = 1, 
        cex.axis = .8)

points(x=as.numeric(factor(dCt$Group)),
       y=dCt$FC,
       cex=1,
       pch=c(22),
       bg=c('firebrick',"gold","darkgreen","dodgerblue", 'mediumorchid', "orange", "blue")[as.numeric(factor(dCt$Group))])

```

```{r}

mean.dCt = data.frame(Group = unique(dCt$Group),
                      mean.dCt = 0)
mean.dCt$Group = factor(mean.dCt$Group, levels = c("WTLF", "WTLM",
                                                   "GRLF", "GRLM",
                                                   "OreR", "Arc1OreR", "Arc1G85R"))

i=1
while(i<=nrow(mean.dCt)){
  mean.dCt$mean.dCt[i] = mean(dCt$dCt[dCt$Group == mean.dCt$Group[i]])
  i = i + 1
}

row.names(mean.dCt) =  mean.dCt$Group

ddCt = setNames(c(mean.dCt["GRLF", "mean.dCt"] - mean.dCt["WTLF", "mean.dCt"],
                  mean.dCt["GRLM", "mean.dCt"] - mean.dCt["WTLM", "mean.dCt"],
                  mean.dCt["Arc1OreR", "mean.dCt"] - mean.dCt["OreR", "mean.dCt"],
                  mean.dCt["Arc1G85R", "mean.dCt"] - mean.dCt["OreR", "mean.dCt"],
                  mean.dCt["Arc1G85R", "mean.dCt"] - mean.dCt["Arc1OreR", "mean.dCt"]),
               nm = c("GRLF/WTLF", "GRLM/WTLM",
                      "Arc1OreR/OreR", "Arc1G85R/OreR", "Arc1G85R/Arc1OreR"))

ddCt.FC = 2^-ddCt

#ddCt.FC = ddCt.FC[substr(names(ddCt.FC),1,3) == "Arc"]

barplot(ddCt.FC,
        names.arg = names(ddCt.FC),
        ylim = c(0, 1.5),
        ylab = "Arc1 Relative Expression")
abline(h = 1, lty = 2, lwd = 1.5)

```

### 2025-01-13 GeneExpressionBoxPlots.Rmd
data files

@@
 ---
-title: "rac1 gene expression"
+title: "Specifgic Gene or Metabolite Levels"
 author: "John Santiago"
@@
 ```{r include = F, echo = F}
+##Load Libraries and Data
 
@@
 library(edgeR)
-library(heatmaply)
-library(org.Dm.eg.db)
-library(KEGGREST)
+
+GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
 
@@
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
-cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
-groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
-TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
 
-groups = groups[colnames(cpmdata),]
+TKT.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+
+TKT.groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
+TKT.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
+TKT.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
+
+TKT.groups = TKT.groups[colnames(TKT.cpm),]
+
+A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)
+
+A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
 
@@
 gbbKO.cpmdata=cpm(z)
-
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
-
-A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)
-
-A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
-
-nodeID = as.list(org.Dm.egENZYME)
-
-```
-
-```{r echo = F}
-
-##subsetting genes for patterns
-
-```
-
-```{r echo = F}
-
-##relish FBgn0014018
-##attacin FBgn0041579
-##cecropin FBgn0000276
-##diptericin FBgn0004240
-##drosocin FBgn0010388
-##defensin FBgn0010385
-##drosomycin FBgn0283461
-##metchnikowin FBgn0014865
-##sod1 FBgn0003462
-##sod2 FBgn0010213
-##catalase FBgn0000261
-##gstd1 FBgn0001149
-## arc1 FBgn0033926
-##rac1
-##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')
-##mle 'FBgn0002774'
-##gstD FBgn0001149
-##Tudor-SN FBgn0035121
-##atf4 FBgn0000370
-##thor FBgn0261560
-##sdhbl FBgn0030975
-##ND-51L FBgn0034251
-##kayak (AP-1) FBgn0001297
-## Jra (AP-1) FBgn0001291
-#sad FBgn0003312
-
-##Specific enzyme
-enzyme.ens = nodeID[grep('3.1.3.5',nodeID)]
-enzyme.genes = GeneIDKey[GeneIDKey$ensembl %in% names(enzyme.ens)[c(1,3:5,7)],]
-
-```
-
-> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'Symbol']
- [1] "Cyp4p1"  "CG13962" "Cpr51A"  "CG11438" "Sgs5bis" "sad"    
- [7] "Lip2"    "CG4757"  "CG14229" "CG15406" "CG3270"  "CG9877" 
-[13] "CG13905" "Zip71B"  "CG17027" "nom"     "CG16727" "CG9702" 
-[19] "CG43740"
-> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'FBgn']
- [1] "FBgn0015037" "FBgn0032824" "FBgn0033942" "FBgn0037164"
- [5] "FBgn0038523" "FBgn0003312" "FBgn0024740" "FBgn0027584"
- [9] "FBgn0031059" "FBgn0031517" "FBgn0033093" "FBgn0034819"
-[13] "FBgn0035176" "FBgn0036461" "FBgn0036553" "FBgn0037617"
-[17] "FBgn0038719" "FBgn0039787" "FBgn0263997"
-
-```{r echo = F}
-
-FBgn = 'FBgn0032513'
-name = 'STARD7'
-FBgn = 'FBgn0028932'
-name = 'CG16890'
-
-gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), condition = groups$Group, group = paste0(groups$Genotype, groups$Sex))
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
-                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
-                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
-                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))
-
-par(mar = c(5,7,5,2))
-plot(x = NA,
-      y = NA,
-     type = 'n',
-     ylim = c(min(gene$cpm), max(gene$cpm)),
-     xlim = c(.5, 12.5),
-     xaxt = "n",
-     ylab="",
-     yaxt = "n",
-     xlab = NA)
-
-rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
-
-boxplot(gene$cpm~gene$condition, 
-        xlab="",
-        las = 2, 
-        cex.axis = .8,
-        xaxt = 'none',
-        yaxt = 'none',
-        boxwex = .75,
-        boxlwd = 2,
-        lwd = 2,
-        cex.ticks = 2,
-        add = T,
-        col = c(rep("honeydew", 3),
-                rep("thistle1", 3),
-                rep("lightcyan", 3),
-                rep("lightyellow", 3)))
-
-box(lwd = 2)
-
-points(x=as.numeric(factor(gene$condition)),
-       y=gene$cpm,
-       cex=1,
-       pch=21,
-       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-
-axis(side = 1,
-     at = 1:12,
-     labels = rep(c("Control", "Df", "OE"), 4),
-     line = 0,
-     cex.axis = .75,
-     lwd.ticks = 2)
-
-axis(side = 2,
-     line = 0,
-     cex.axis = 1,
-     lwd.ticks = 2,
-     las = 2)
-
-axis(side = 2,
-     at = .5*(max(gene$cpm) + min(gene$cpm)),
-     label = "Counts per million reads",
-     tick = F,
-     padj = -3,
-     cex.axis = 1.25)
-
-axis(side = 1,
-     at = c(2, 5, 8, 11),
-     labels = c("Silent", "G85R","Silent", "G85R"),
-     tick = F,
-     padj = 2,
-     cex.axis = 1)
-axis(side = 3,
-     at = c(3.5, 9.5),
-     labels = c("Female", "Male"),
-     tick = F,
-     padj = .5,
-     cex.axis = 1.5)
-
-axis(side = 3,
-     at = 6.5,
-     labels = name,
-     tick = F,
-     padj = -1.5,
-     cex.axis = 2)
-
-axis(side = 3,
-     at = c(3.5,9.5),
-     tick = T,
-     outer = T,
-     labels = F,
-     line = -2.25,
-     lwd.ticks = 0)
-
-xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
-xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
-lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-abline(v = 6.5, lty = 2, lwd = 2)
-
-```
-
-```{r echo = F}
-
-gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), 
-                  condition = groups$Group, 
-                  group = paste0(groups$Genotype, groups$Sex),
-                  TKT = groups$TKT)
-
-gene = gene[gene$TKT != 'OE',]
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F",
-                                                 'WT.F', "TktDfWT.F",
-                                                 'GR.M', "TktDfGR.M",
-                                                 'WT.M', "TktDfWT.M"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-
-```
-
-```{r echo = F}
-
-A4V.groups = as.vector(colnames(A4V.cpm))
-
-A4V.groups = substr(A4V.groups,1, nchar(A4V.groups)-1)
-
-par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
-gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]), 
-                  condition = A4V.groups, 
-                  group = paste0(substr(A4V.groups, 1,1), substr(A4V.groups, nchar(as.vector(A4V.groups))-1,nchar(as.vector(A4V.groups))-1)))
-
-gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
-                                                   "S3FH", "S9FH", "S40FH",
-                                                   "A3FT", "A9FT", "A40FT",
-                                                   "S3FT", "S9FT", "S40FT",
-                                                   "A3FA", "A9FA", "A40FA",
-                                                   "S3FA", "S9FA", "S40FA",
-                                                   "A3MH", "A9MH",
-                                                   "S3MH", "S9MH",
-                                                   "A3MT", "A9MT",
-                                                   "S3MT", "S9MT",
-                                                   "A3MA", "A9MA",
-                                                   "S3MA", "S9MA"))
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-legend('topright',
-       inset=c(-0.275,0),
-       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
-       fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
-       cex = .65,
-       bty = 'n',
-       pt.cex = .5)
-
-```
-
-```{r}
-
-gene = data.frame(cpm = as.numeric(gbbOE.cpmdata[FBgn,]), condition = gbbOE.groups$group, group = gbbOE.groups$genotype)
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('LoxP_ML3', "LoxP_LL3",
-                                                 'G85R_ML3', "G85R_LL3",
-                                                 'G85R_gbb_ML3', "G85R_gbb_LL3"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
-
-```
-
-```{r}
-
-## WT = W1118
-## KO = GBB1/GBB2 (both null alleles)
-## Aaron and Catherine legend for RNAseq
-## Whole larvae
-
-gene = data.frame(cpm = as.numeric(gbbKO.cpmdata[FBgn,]), condition = gbbKO.groups$Genotype)
-
-gene$condition = factor(gene$condition, levels = c('WT', "KO"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$condition))])
-
-```
-
-```{r echo = F}
 
@@
 ```{r echo = F}
+##Function to plot all G85R groups
 
-metab = 'D-sedoheptulose-7-phosphate'
-name = 'D-sedoheptulose-7-phosphate'
+plot.G85R = function(ID){
+ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) == 1){
+FBgn = ID.row$FBgn
+name = ID.row$Symbol
+
+gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), condition = TKT.groups$Group, group = paste0(TKT.groups$Genotype, TKT.groups$Sex))
+
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
+                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
+                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
+                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))
+
+par(mar = c(5,7,5,2))
+plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(min(gene$cpm), max(gene$cpm)),
+     xlim = c(.5, 12.5),
+     xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = NA)
+
+rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
+
+boxplot(gene$cpm~gene$condition, 
+        xlab="",
+        las = 2, 
+        cex.axis = .8,
+        xaxt = 'none',
+        yaxt = 'none',
+        boxwex = .75,
+        boxlwd = 2,
+        lwd = 2,
+        cex.ticks = 2,
+        add = T,
+        col = c(rep("honeydew", 3),
+                rep("thistle1", 3),
+                rep("lightcyan", 3),
+                rep("lightyellow", 3)))
+
+box(lwd = 2)
+
+points(x=as.numeric(factor(gene$condition)),
+       y=gene$cpm,
+       cex=1,
+       pch=21,
+       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+
+axis(side = 1,
+     at = 1:12,
+     labels = rep(c("Control", "Df", "OE"), 4),
+     line = 0,
+     cex.axis = .75,
+     lwd.ticks = 2)
+
+axis(side = 2,
+     line = 0,
+     cex.axis = 1,
+     lwd.ticks = 2,
+     las = 2)
+
+axis(side = 2,
+     at = .5*(max(gene$cpm) + min(gene$cpm)),
+     label = "Counts per million reads",
+     tick = F,
+     padj = -3,
+     cex.axis = 1.25)
+
+axis(side = 1,
+     at = c(2, 5, 8, 11),
+     labels = c("Silent", "G85R","Silent", "G85R"),
+     tick = F,
+     padj = 2,
+     cex.axis = 1)
+axis(side = 3,
+     at = c(3.5, 9.5),
+     labels = c("Female", "Male"),
+     tick = F,
+     padj = .5,
+     cex.axis = 1.5)
+
+axis(side = 3,
+     at = 6.5,
+     labels = name,
+     tick = F,
+     padj = -1.5,
+     cex.axis = 2)
+
+axis(side = 3,
+     at = c(3.5,9.5),
+     tick = T,
+     outer = T,
+     labels = F,
+     line = -2.25,
+     lwd.ticks = 0)
+
+xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
+xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
+lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+abline(v = 6.5, lty = 2, lwd = 2)
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+}
+
+```
+
+```{r echo = F}
+##Function to plot a specific gene expression levels in all A4V groups
+
+plot.A4V = function(ID){
+ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) == 1){
+  FBgn = ID.row$FBgn
+  name = ID.row$Symbol
+  A4V.groups = as.vector(colnames(A4V.cpm))
+
+  A4V.groups = substr(A4V.groups,1, nchar(A4V.groups)-1)
+
+  par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
+  gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]),
+                    condition = A4V.groups,
+                    group = paste0(substr(A4V.groups, 1,1), substr(A4V.groups, start = nchar(as.vector(A4V.groups))-1,nchar(as.vector(A4V.groups))-1)))
+
+  gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
+                                                   "S3FH", "S9FH", "S40FH",
+                                                   "A3FT", "A9FT", "A40FT",
+                                                   "S3FT", "S9FT", "S40FT",
+                                                   "A3FA", "A9FA", "A40FA",
+                                                   "S3FA", "S9FA", "S40FA",
+                                                   "A3MH", "A9MH",
+                                                   "S3MH", "S9MH",
+                                                   "A3MT", "A9MT",
+                                                   "S3MT", "S9MT",
+                                                   "A3MA", "A9MA",
+                                                   "S3MA", "S9MA"))
+  gene$group = factor(gene$group, levels = c(unique(gene$group)))
+
+  boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+  points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+  legend('topright',
+       inset=c(-0.275,0),
+       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
+       fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
+       cex = .65,
+       bty = 'n',
+       pt.cex = .5)
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+}
+
+```
+
+```{r echo = F}
+##Plot levels of a specific metabolite
+
+plot.metab = function(metabID){
+
+ID.row = row.names(norm.data)[grep(ID, row.names(norm.data))]
+
+if(length(ID.row) == 1){
+metab = ID.row
+name = ID.row
 
@@
      type = 'n',
-     ylim = c(min(metab$data), max(metab$data)),
+     ylim = c(min(na.omit(metab$data)), max(na.omit(metab$data))),
      xlim = c(.5, 6.5),
@@
 
-axis(side = 2,
-     at = .5*(max(gene$cpm) + min(gene$cpm)),
-     label = "Counts per million reads",
-     tick = F,
-     padj = -3,
-     cex.axis = 1.25)
-
 axis(side = 1,
@@
 
-xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
-xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
-lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
+}
+
+if(length(ID.row) != 1){
+  ID.row
+}
+
+}
 
 ```
+
+```{r echo = F}
+
+ID = "0000018"
+plot.G85R(ID)
+
+```
+
+```{r echo = F}
+##Tailared code to plot a specific gene expression levels in all A4V groups
+
+ID = "0000018"
+
+plot.A4V(ID)
+```
+
+```{r echo = F}
+
+metabID = 'NADP'
+
+plot.metab(metabID)
+
+```
+
+```{r echo = F}
+##Tailared code to plot a subset of groups in the TKT dataset
+
+##ID = "0000018"
+
+ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) == 1){
+FBgn = ID.row$FBgn
+name = ID.row$Symbol
+
+gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), 
+                  condition = TKT.groups$Group, 
+                  group = paste0(TKT.groups$Genotype, TKT.groups$Sex),
+                  TKT = TKT.groups$TKT)
+
+gene = gene[gene$TKT != 'OE',]
+
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F",
+                                                 'WT.F', "TktDfWT.F",
+                                                 'GR.M', "TktDfGR.M",
+                                                 'WT.M', "TktDfWT.M"))
+
+boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+
+```
+
+```{r echo = F}
+##Plot expression levels for a specific gene in the gbbOE dataset
+
+##ID = "0000018"
+
+ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) == 1){
+FBgn = ID.row$FBgn
+name = ID.row$Symbol
+
+gene = data.frame(cpm = as.numeric(gbbOE.cpmdata[FBgn,]), condition = gbbOE.groups$group, group = gbbOE.groups$genotype)
+
+gene$group = factor(gene$group, levels = c(unique(gene$group)))
+gene$condition = factor(gene$condition, levels = c('LoxP_ML3', "LoxP_LL3",
+                                                 'G85R_ML3', "G85R_LL3",
+                                                 'G85R_gbb_ML3', "G85R_gbb_LL3"))
+
+boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
+
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+```
+
+```{r echo = F}
+##Plot expression levels for a specific gene in the gbb-null dataset
+
+## WT = W1118
+## KO = GBB1/GBB2 (both null alleles)
+## Aaron and Catherine legend for RNAseq
+## Whole larvae
+
+##ID = "0000018"
+
+ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) == 1){
+FBgn = ID.row$FBgn
+name = ID.row$Symbol
+
+gene = data.frame(cpm = as.numeric(gbbKO.cpmdata[FBgn,]), condition = gbbKO.groups$Genotype)
+
+gene$condition = factor(gene$condition, levels = c('WT', "KO"))
+
+boxplot(gene$cpm~gene$condition, xlab="",     
+        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
+points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$condition))])
+
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+```

### 2025-01-13 TKT_RNAseq/R Code/TKTRNAseqMitochondrialAssessment.Rmd
data files

@@
 A4V.meancpm$SMA = apply((A4V.cpm[,gr2=="SMA"]), 1, mean)
+
+KEGG.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/KEGG.names.csv", row.names = 1)
+G85R.metab.comparekey = setNames(c("GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
+                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE",
+                                   "GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
+                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE"), names(G85R.comparekey)[1:14])
+
+G85R.metabnorm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/NormalizedMetabolomicData.csv", row.names = 1)
+G85R.metabmean = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MeanNormalizedMetabolomicData.csv", row.names = 1)
+metab.id = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteMultiKEGGIDKey.csv", row.names = 1)
+metab.id = setNames(metab.id$metab, metab.id$KEGG)
+G85R.metabFC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFCs.csv", row.names = 1)
+G85R.metabFDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFDRs.csv", row.names = 1)
+G85R.metabp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/Metabolitepvals.csv", row.names = 1)
 
@@
 Fig40.
-OXPHOS Genes cpm in G85R relative to Silent: FC for all OXPHOS with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis.
+OXPHOS Genes FC in G85R relative to Silent: FC for all OXPHOS with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig41.
-OXPHOS Genes cpm in A4V relative to Silent 3-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 3-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig42.
-OXPHOS Genes cpm in A4V relative to Silent 9-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 9-Day heads: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig43.
-OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig44.
-OXPHOS Genes cpm in A4V relative to Silent 3-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 3-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig45.
-OXPHOS Genes cpm in A4V relative to Silent 9-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 9-Day thorax: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig46.
-OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male thorax: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 40-day female thorax and 9-day male thorax: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig47.
-OXPHOS Genes cpm in A4V relative to Silent 3-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 3-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig48.
-OXPHOS Genes cpm in A4V relative to Silent 9-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 9-Day abdomen: FC for all OXPHOS with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 Fig49.
-OXPHOS Genes cpm in A4V relative to Silent 40-day female heads and 9-day male abdomen: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
+OXPHOS Genes FC in A4V relative to Silent 40-day female abdomen and 9-day male abdomen: FC for all OXPHOS with 40-day female A4V/WT FC on the x-axis and 9-day male A4V/WT on the y-axis.
 Colors indicate if they were in the GO term for that complex.
@@
 
-Fig50. AD Array Genes cpm in G85R relative to Silent: FC for all AD Array Genes with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis.
+Fig50. AD Array Genes FC in G85R relative to Silent: FC for all AD Array Genes with female G85R/WT FC on the x-axis and male G85R/WT on the y-axis.
 
@@
 
-Fig51. AD Array Genes cpm in A4V relative to Silent 3-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig51. AD Array Genes FC in A4V relative to Silent 3-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 
-Fig52. AD Array Genes cpm in A4V relative to Silent 9-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig52. AD Array Genes FC in A4V relative to Silent 9-Day heads: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 
-Fig53. AD Array Genes cpm in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
+Fig53. AD Array Genes FC in A4V relative to Silent 40-day female heads and 9-day male heads: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
 
@@
 
-Fig54. AD Array Genes cpm in A4V relative to Silent 3-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig54. AD Array Genes FC in A4V relative to Silent 3-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 
-Fig55. AD Array Genes cpm in A4V relative to Silent 9-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig55. AD Array Genes FC in A4V relative to Silent 9-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 
-Fig56.
-AD Array Genes cpm in A4V relative to Silent 40-day female thorax and 9-day male thorax: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
+Fig56. AD Array Genes FC in A4V relative to Silent 40-day female thorax and 9-day male thorax: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
 
@@
 
-Fig57. AD Array Genes cpm in A4V relative to Silent 3-Day abdomen: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig57. AD Array Genes FC in A4V relative to Silent 3-Day abdomen: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 
-Fig58. AD Array Genes cpm in A4V relative to Silent 9-Day thorax: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
+Fig58. AD Array Genes FC in A4V relative to Silent 9-Day abdomen: FC for all AD Array Genes with female A4V/WT FC on the x-axis and male A4V/WT on the y-axis.
 
@@
 Fig59.
-AD Array Genes cpm in A4V relative to Silent 40-day female abdomen and 9-day male abdomen: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
+AD Array Genes FC in A4V relative to Silent 40-day female abdomen and 9-day male abdomen: FC for all AD Array Genes with 40-day female A4V/WT FC on the x-axis and male 9-day A4V/WT on the y-axis.
 
@@
 
-Fig. 67 FC of Complex I genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 67 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in gold. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 72 FC of Complex II genes in A4V male 9 day and female 40 day head samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 72 FC of Complex II genes in A4V male and female head samples relative to silent. All time points were combined. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 75 FC of Complex II genes in A4V male 9 day and female 40 day head samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 75 FC of Complex II genes in A4V male 9 day and female 40 day thorax samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 76 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 76 FC of Complex I genes in A4V male and female thorax samples relative to silent. All time points were combined. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 80 FC of Complex III genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+80 FC of Complex III genes in A4V male and female head samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in green Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 83 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 83 FC of Complex IV genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 84 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in green. Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+84 FC of Complex I genes in A4V male and female thorax samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in green.
+Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 88 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+88 FC of Complex IV genes in A4V male and female head samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in blue Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 91 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 91 FC of Complex IV genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 92 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in blue. Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+92 FC of Complex I genes in A4V male and female thorax samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in blue.
+Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 96 FC of Complex V genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+96 FC of Complex V genes in A4V male and female head samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in red Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 99 FC of Complex IV genes in A4V male 9 day and female 40 day head samples relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.
+Fig. 99 FC of Complex IV genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-Fig. 100 FC of Complex I genes in A4V male 9 day and female 40 day thorax samples relative to silent. mtDNA encoded genes are in red. Genes with mean cpm under 10 for all conditions excluded.
+Fig.
+100 FC of Complex I genes in A4V male and female thorax samples relative to silent.
+All time points were combined.
+mtDNA encoded genes are in red.
+Genes with mean cpm under 10 for all conditions excluded.
 
@@
 
-```{r echo = F, warning = F, include = F}
+```{r echo = F, warning = F}
 
@@
                                                        | complex.genes$Complex == "Complex IV"
-                                                       | complex.genes$Complex == "Complex V"],])
-                              #row.names(A4V.meta[A4V.meta$Section == "Thorax" &
-                              #                   (A4V.meta$Age == "3"),])])
+                                                       | complex.genes$Complex == "Complex V"],
+                              row.names(A4V.meta[A4V.meta$Section == "Head",])])
 
 row.names(complex.cpm) = GeneIDKey[row.names(complex.cpm), "Symbol"]
+
 complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
@@
 
-complex.cpm = complex.cpm.all[,row.names(A4V.meta[A4V.meta$Section == "Thorax" &
-                                                  (A4V.meta$Age == "9"),])]
+complex.cpm = complex.cpm.all##[,row.names(A4V.meta[A4V.meta$Section == "Thorax" &
+                             ##                    (A4V.meta$Age == "9"),])]
 complex.data = complex.genes
@@
 
+```{r}
+library(devtools)
+library(factoextra)
+
+```
+
+```{r}
+
+fviz_pca_ind(pca, 
+             col.ind = pca.data$CHR,
+             addEllipses = T, 
+             label = "none" )
+
+```
+
 ```{r echo = F, include = F}
@@
 
-complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),])
-
-complex.cpm = complex.cpm[apply(complex.cpm, 1, max)>10,]
+complex.cpm = na.omit(A4V.meancpm[row.names(complex.genes),
+                                  nchar(colnames(A4V.meancpm)) > 3])
+
+Hcomplex.cpm = complex.cpm[, grep("H", colnames(complex.cpm))]
+
+Tcomplex.cpm = complex.cpm[, grep("T", colnames(complex.cpm))]
+
+complex.cpm = complex.cpm[apply(Hcomplex.cpm, 1, max)>10 &
+                          apply(Tcomplex.cpm, 1, max)>10,]
 
@@
           ##scale = 'row',
-          cexRow = .25)
+          cexRow = .5)
 
@@
 
+```{r}
+
+KEGG.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/KEGG.names.csv", row.names = 1)
+G85R.metab.comparekey = setNames(c("GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
+                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE",
+                                   "GR.CxDf", "GR.CxOE", "WT.CxDf", "WT.CxOE",
+                                   "GRxWT.C", "GRxWT.Df", "GRxWT.OE"), names(G85R.comparekey)[1:14])
+
+G85R.metabnorm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/NormalizedMetabolomicData.csv", row.names = 1)
+G85R.metabmean = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MeanNormalizedMetabolomicData.csv", row.names = 1)
+metab.id = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteMultiKEGGIDKey.csv", row.names = 1)
+metab.id = setNames(metab.id$metab, metab.id$KEGG)
+G85R.metabFC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFCs.csv", row.names = 1)
+G85R.metabFDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetaboliteFDRs.csv", row.names = 1)
+G85R.metabp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/Metabolitepvals.csv", row.names = 1)
+
+NAD = keggGet('dme00760')[[1]]
+#NAD = keggGet('dme00010')[[1]]
+#NAD = keggGet('dme00230')[[1]]
+NAD = NAD$COMPOUND
+
+temp.metabs = setNames(c(rep(0, length(metab.id))), c(names(metab.id)))
+i=1
+while(i<=length(NAD)){
+  if(length(grep(names(NAD)[i], names(temp.metabs))) >0){
+    temp.metabs[grep(names(NAD)[i], names(temp.metabs))] = 1
+  }
+  i=i+1
+}
+
+NAD.IDs = temp.metabs[temp.metabs == 1]
+NAD.IDs = metab.id[names(NAD.IDs)]
+
+NAD.levels = as.matrix(G85R.metabnorm[NAD.IDs, substr(colnames(G85R.metabnorm), 1,2) == "GR" |
+                                               substr(colnames(G85R.metabnorm), 1,2) == "WT" |
+                                               substr(colnames(G85R.metabnorm), 1,6) == "TktDfG"])
+NAD.levels = NAD.levels[names(na.omit(NAD.levels[,1])),]
+NAD.levels = NAD.levels[,c("WT1", "WT2", "WT3", "WT4",
+                           "GR1", "GR2", "GR3", "GR4")]#,
+                           #"TktDfGR1","TktDfGR2","TktDfGR3","TktDfGR4")]
+
+heatmap.2((NAD.levels),
+          Colv = F,
+          Rowv = T,
+          dendrogram = "none",
+          col = hmcolors,
+          trace = "none",
+          scale = 'row',
+          cexRow = .75)
+
+#boxplot with WT, G85R, G85R-def
+##NAD+, NR, NMW c("nicotinamide riboside+", "NMN", "NAD+")
+##Guanine, Uric Acid, Xanthine, Deoxyinosine c('guanine', 'uric acid', 'xanthine', 'deoxyinosine')
+
+```
+
+```{r}
+
+NAD.bp = as.data.frame(t(NAD.levels[c("nicotinamide riboside+", "NMN", "NAD+"),]))
+NAD.bp$Group = substr(row.names(NAD.bp), 1, 2)
+
+NAD.bp = data.frame(Geno = rep(NAD.bp[, "Group"],3),
+                    Metab = c(rep("nicotinamide riboside+", 8),#12),
+                              rep("NMN", 8),#12),
+                              rep("NAD+", 8)),#12)),
+                    Level = c(NAD.bp[,"nicotinamide riboside+"],
+                              NAD.bp[,"NMN"],
+                              NAD.bp[,"NAD+"]))
+NAD.bp$Group = factor(paste(NAD.bp$Geno, NAD.bp$Metab),
+                      levels = c("WT nicotinamide riboside+", "GR nicotinamide riboside+",# "Tk nicotinamide riboside+", 
+                                 "WT NMN", "GR NMN",# "Tk NMN", 
+                                 "WT NAD+", "GR NAD+"))#, "Tk NAD+" ))
+
+NAD.bp$Geno = factor(NAD.bp$Geno, levels = c("WT", "GR"))#, "Tk"))
+NAD.bp$Level = log10(NAD.bp$Level)
+box.at = c(1:2, 4:5, 7:8)
+
+boxplot(NAD.bp$Level~NAD.bp$Group,
+        las = 2,
+        col = c(hex("firebrick", .25), hex("steelblue", .25)),#, hex("darkgreen", .25)),
+        at = box.at,
+        xaxt = "none",
+        xlab = "Metabolite",
+        ylab = "Peak Intensity (log10)",
+        main = "NAD Biosynthesis",
+        boxlwd = 1.5,
+        lwd = 1.5,
+        ylim = c(9.5, 10.75))
+
+points(x=box.at[as.numeric(factor(NAD.bp$Group))],
+       y=NAD.bp$Level,
+       cex=1,
+       pch=21,
+       #bg=c('firebrick',"dodgerblue","darkgreen")[as.numeric(factor(NAD.bp$Geno))])
+       bg=c('firebrick',"dodgerblue")[as.numeric(factor(NAD.bp$Geno))])
+
+axis(1, at= c(1.5,4.5,7.5),
+     tick = F, 
+     line = -.5, 
+     labels = c(unique(NAD.bp$Metab)), 
+     las = 1)
+
+legend(x = 7.5,
+       y = 10.85,
+       #legend = c("Silent", "G85R", "G85R TKT-Df"),
+       legend = c("Silent", "G85R"),
+       pch = 21,
+       #pt.bg = c('firebrick',"dodgerblue","darkgreen"),
+       pt.bg = c('firebrick',"dodgerblue"),
+       bty = 'n',
+       y.intersp = 0.5)
+
+```
+
+```{r}
+
+NAD = keggGet('dme00760')[[1]]
+#NAD = keggGet('dme00010')[[1]]
+NAD = keggGet('dme00230')[[1]]
+NAD = NAD$COMPOUND
+
+temp.metabs = setNames(c(rep(0, length(metab.id))), c(names(metab.id)))
+i=1
+while(i<=length(NAD)){
+  if(length(grep(names(NAD)[i], names(temp.metabs))) >0){
+    temp.metabs[grep(names(NAD)[i], names(temp.metabs))] = 1
+  }
+  i=i+1
+}
+
+NAD.IDs = temp.metabs[temp.metabs == 1]
+NAD.IDs = metab.id[names(NAD.IDs)]
+
+NAD.levels = as.matrix(G85R.metabnorm[NAD.IDs, substr(colnames(G85R.metabnorm), 1,2) == "GR" |
+                                               substr(colnames(G85R.metabnorm), 1,2) == "WT" |
+                                               substr(colnames(G85R.metabnorm), 1,6) == "TktDfG"])
+NAD.levels = NAD.levels[names(na.omit(NAD.levels[,1])),]
+NAD.levels = NAD.levels[,c("WT1", "WT2", "WT3", "WT4",
+                           "GR1", "GR2", "GR3", "GR4")]#,
+                           #"TktDfGR1","TktDfGR2","TktDfGR3","TktDfGR4")]
+
+heatmap.2((NAD.levels),
+          Colv = F,
+          Rowv = T,
+          dendrogram = "none",
+          col = hmcolors,
+          trace = "none",
+          scale = 'row',
+          cexRow = .75)
+
+```
+
+```{r}
+
+NAD.bp = as.data.frame(t(NAD.levels[c('guanine', 'uric acid', 'xanthine', 'deoxyinosine'),]))
+NAD.bp$Group = substr(row.names(NAD.bp), 1, 2)
+
+NAD.bp = data.frame(Geno = rep(NAD.bp[, "Group"],4),
+                    Metab = c(rep("guanine",8),#12),
+                              rep("deoxyinosine",8),#12),
+                              rep("xanthine",8),#12),
+                              rep("uric acid",8)),#12)),
+                    Level = c(NAD.bp[,"guanine"],
+                              NAD.bp[,"deoxyinosine"],
+                              NAD.bp[,"xanthine"],
+                              NAD.bp[,"uric acid"]))
+NAD.bp$Group = factor(paste(NAD.bp$Geno, NAD.bp$Metab),
+                      levels = c("WT guanine", "GR guanine", #"Tk guanine", 
+                                 "WT deoxyinosine", "GR deoxyinosine", #"Tk deoxyinosine", 
+                                 "WT xanthine", "GR xanthine", #"Tk xanthine", 
+                                 "WT uric acid", "GR uric acid"))#, "Tk uric acid" ))
+
+NAD.bp$Geno = factor(NAD.bp$Geno, levels = c("WT", "GR"))#, "Tk"))
+
+NAD.bp$Level = log10(NAD.bp$Level)
+box.at = c(1:2, 4:5, 7:8, 10:11)
+
+boxplot(NAD.bp$Level~NAD.bp$Group,
+        las = 2,
+        #col = c(hex("firebrick", .25), hex("steelblue", .25), hex("darkgreen", .25)),
+        col = c(hex("firebrick", .25), hex("steelblue", .25)),
+        at = box.at,
+        xaxt = "none",
+        xlab = "Metabolite",
+        ylab = "Peak Intensity (log10)",
+        main = "Purine Metabolism",
+        boxlwd = 1.5,
+        lwd = 1.5)
+
+points(x=box.at[as.numeric(factor(NAD.bp$Group))],
+       y=NAD.bp$Level,
+       cex=1,
+       pch=21,
+       #bg=c('firebrick',"dodgerblue","darkgreen")[as.numeric(factor(NAD.bp$Geno))])
+       bg=c('firebrick',"dodgerblue")[as.numeric(factor(NAD.bp$Geno))])
+
+axis(1, at= c(1.5,4.5,7.5, 10.5),
+     tick = F, 
+     line = -.5, 
+     labels = c(unique(NAD.bp$Metab)), 
+     las = 1)
+
+legend(x = 0,
+       y = 13,
+       #legend = c("Silent", "G85R", "G85R TKT-Df"),
+       legend = c("Silent", "G85R"),
+       pch = 21,
+       #pt.bg = c('firebrick',"dodgerblue","darkgreen"),
+       pt.bg = c('firebrick',"dodgerblue"),
+       bty = 'n',
+       y.intersp = 0.5)
+
+```
+
+```{r}
+
+all.perox = row.names(GO.Names[grep("eroxisome", GO.Names$term),])
+
+perox.genes = as.vector(unlist(genesingo[all.perox]))
+perox.genes = GeneIDKey[GeneIDKey$ensembl %in% unique(perox.genes), "FBgn"]
+
+perox.cpm = TKT.cpm[perox.genes,]
+
+perox.cpm = as.matrix(na.omit(perox.cpm[apply(perox.cpm, 1, max)>20,]))
+
+perox.cpm = perox.cpm[, c("WT.F1", "WT.F2",
+                          "GR.F1", "GR.F2",
+                          "WT.M1", "WT.M2", "WT.M3",
+                          "GR.M1", "GR.M2", "GR.M3")]
+
+perox.fc = TKT.EdgeR.FC[row.names(perox.cpm), c("GRxWT.FC", "GRxWT.MC",
+                                                  "GRxWT.FDf", "GRxWT.MDf")]
+
+perox.fc = as.matrix(na.omit(perox.fc))
+
+perox.hm = perox.fc
+
+row.names(perox.hm) = GeneIDKey[row.names(perox.hm), "Symbol"]
+
+heatmap.2((perox.hm),
+          Colv = F,
+          Rowv = T,
+          dendrogram = "none",
+          col = hmcolors,
+          trace = "none",
+          scale = 'none',
+          cexRow = .5)
+
+```
+
+```{r}
+
+all.purine = (GO.Names[grep("urine", GO.Names$term),])
+all.purine = all.purine[grep("metab", all.purine$term),]
+all.purine = row.names(all.purine)
+
+purine.genes = as.vector(unlist(genesingo[all.purine]))
+purine.genes = GeneIDKey[GeneIDKey$ensembl %in% unique(purine.genes), "FBgn"]
+
+purine.cpm = TKT.cpm[purine.genes,]
+
+purine.cpm = as.matrix(na.omit(purine.cpm[apply(purine.cpm, 1, max)>20,]))
+
+purine.cpm = purine.cpm[, c("WT.F1", "WT.F2",
+                          "GR.F1", "GR.F2",
+                          "WT.M1", "WT.M2", "WT.M3",
+                          "GR.M1", "GR.M2", "GR.M3")]
+
+purine.fc = TKT.EdgeR.FC[row.names(purine.cpm), c("GRxWT.FC", "GRxWT.MC",
+                                                  "GRxWT.FDf", "GRxWT.MDf")]
+
+purine.fc = as.matrix(na.omit(purine.fc))
+
+purine.hm = purine.fc
+
+row.names(purine.hm) = GeneIDKey[row.names(purine.hm), "Symbol"]
+
+heatmap.2((purine.hm),
+          Colv = F,
+          Rowv = T,
+          dendrogram = "none",
+          col = hmcolors,
+          trace = "none",
+          scale = 'none',
+          cexRow = .25,
+          cexCol = .75)
+
+```
+
+```{r echo = F}
+#pentose-phosphate shunt
+GOterm = "GO:0006098"
+
+hmcolors2=colorpanel(25,"steelblue3", "ivory",'red3')
+
+all.purine = (GO.Names[grep("pentose", GO.Names$term),])
+all.purine = row.names(all.purine)
+
+purine.genes = as.vector(unlist(genesingo[all.purine]))
+purine.genes = GeneIDKey[GeneIDKey$ensembl %in% unique(purine.genes), "FBgn"]
+
+purine.cpm = TKT.cpm[purine.genes,]
+
+purine.cpm = as.matrix(na.omit(purine.cpm[apply(purine.cpm, 1, max)>20,]))
+
+purine.cpm = purine.cpm[, c("WT.F1", "WT.F2",
+                          "GR.F1", "GR.F2",
+                          "WT.M1", "WT.M2", "WT.M3",
+                          "GR.M1", "GR.M2", "GR.M3")]
+
+purine.fc = TKT.EdgeR.FC[row.names(purine.cpm), c("GRxWT.FC", "GRxWT.MC",
+                                                  "GRxWT.FDf", "GRxWT.MDf")]
+
+purine.fc = as.matrix(na.omit(purine.fc))
+
+purine.hm = purine.fc
+
+row.names(purine.hm) = GeneIDKey[row.names(purine.hm), "Symbol"]
+
+heatmap.2((purine.hm),
+          Colv = F,
+          Rowv = T,
+          dendrogram = "none",
+          col = hmcolors2,
+          trace = "none",
+          scale = 'none',
+          cexRow = 1,
+          cexCol = .75)
+
+```
+
 ```{r, test-rgl, webgl=TRUE,echo=F, fig.height=10, fig.width=10, include = F}

### 2025-01-13 TKT_RNAseq/R Code/TKTRNAseqPNPAssessment.Rmd
data files

---
title: 'TKT RNAseq: PNP analysis'
author: "John Santiago"
date: "2024-11-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = F}

library(visNetwork)
library(org.Dm.eg.db)
library(KEGGREST)
keggpath = as.list(org.Dm.egPATH2EG)
nodeID = as.list(org.Dm.egENZYME)
nodeID['40528'] = '3.5.4.3'
nodeID['41318'] = '2.7.4.10'
nodeID['42273'] = '2.7.1.145'
nodeID['33924'] = '3.1.3.89'
nodeID[['31309']] = c("3.1.4.17", '3.1.4.53')
nodeID['37741'] = '3.1.4.53'

source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
mean.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)
cpmdata = G85R.cpm
groups = G85R.meta

purine.path = data.frame(enzyme = c('1.17.1.4', '1.17.3.2'),
                         from = c('xanthine', 'xanthine'),
                         to = c(rep('uric acid',2)))

xanthine = data.frame(enzyme = c('1.17.1.4', '1.17.3.2', '2.4.2.1', '3.5.4.3'),
                      from = c('hypoxanthine', 'hypoxanthine', 'xanthosine', 'guanine'),
                      to = c(rep('xanthine',4)))
purine.path = rbind(purine.path, xanthine)

hypoxanthine = data.frame(enzyme = c('2.4.2.1', '2.4.2.1'),
                          from = c('deoxyinosine', 'inosine'),
                          to = c(rep('hypoxanthine', 2)))
purine.path = rbind(purine.path, hypoxanthine)

xanthosine = data.frame(enzyme = c('3.1.3.5'),
                        from = c('XMP'),
                        to = 'xanthosine')
purine.path = rbind(purine.path, xanthosine)

XMP = data.frame(enzyme = c('1.1.1.205'),
                 from = c('IMP'),
                 to = 'XMP')
purine.path = rbind(purine.path, XMP)

IMP = data.frame(enzyme = c('3.6.1.6', '3.5.4.6'),
                 from = c('IDP', 'AMP'),
                 to = c(rep('IMP', 2)))
purine.path = rbind(purine.path, IMP)

adenylosuccinate = data.frame(enzyme = c('6.3.4.4'),
                              from = c('IMP'),
                              to = 'adenylosuccinate')
purine.path = rbind(purine.path, adenylosuccinate)

inosine = data.frame(enzyme = c('2.4.2.1', '3.5.4.4', '3.1.3.5'),
                     from = c('hypoxanthine', 'adenosine', 'IMP'),
                     to = c(rep('inosine', 3)))
purine.path = rbind(purine.path, inosine)

deoxyinosine = data.frame(enzyme = c('2.4.2.1', '3.5.4.4'),
                          from = c('hypoxanthine', 'deoxyadenosine'),
                          to = c(rep('deoxyinosine', 2)))
purine.path = rbind(purine.path, deoxyinosine)

adenosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5', '2.7.1.20'),
                       from = c('adenine', 'AMP', 'AMP'),
                       to = c(rep('adenosine', 3)))
purine.path = rbind(purine.path, adenosine)

AMP = data.frame(enzyme = c('4.3.2.2', '2.7.1.20', '2.4.2.7', '2.7.4.3', '2.7.4.10', '3.1.4.17', '3.1.4.53'),
                 from = c('adenylosuccinate', 'adenosine', 'adenine', 'ADP', 'ADP', 'cAMP', 'cAMP'),
                 to = c(rep('AMP', 7)))
purine.path = rbind(purine.path, AMP)

adenine = data.frame(enzyme = c('2.4.2.1', '2.4.2.7', '2.4.2.1'),
                     from = c('adenosine', 'AMP', 'deoxyadenosine'),
                     to = c(rep('adenine', 3)))
purine.path = rbind(purine.path, adenine)

ATP = data.frame(enzyme = c('2.7.4.6'),
                 from = c('ADP'),
                 to = c(rep('ATP', 1)))
purine.path = rbind(purine.path, ATP)

dATP = data.frame(enzyme = c('2.7.4.6'),
                  from = c('dADP'),
                  to = c(rep('dATP', 1)))
purine.path = rbind(purine.path, dATP)

ADP = data.frame(enzyme = c('2.7.4.3', '2.7.4.10', '2.7.4.6', '3.6.1.15'),
                 from = c('AMP', 'AMP', 'ATP', 'ATP'),
                 to = c(rep('ADP', 4)))
purine.path = rbind(purine.path, ADP)

dADP = data.frame(enzyme = c('2.7.4.3', '1.17.4.1', '2.7.4.6'),
                  from = c('dAMP', 'ADP', 'dATP'),
                  to = c(rep('dADP', 3)))
purine.path = rbind(purine.path, dADP)

dAMP = data.frame(enzyme = c('2.7.1.145', '2.7.4.3'),
                  from = c('deoxyadenosine', 'dADP'),
                  to = c(rep('dAMP', 2)))
purine.path = rbind(purine.path, dAMP)

deoxyadenosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5', '3.1.3.89'),
                            from = c('adenine', 'dAMP', 'dAMP'),
                            to = c(rep('deoxyadenosine', 3)))
purine.path = rbind(purine.path, deoxyadenosine)

dGTP = data.frame(enzyme = c('2.7.4.6'),
                  from = c('dGDP'),
                  to = c('dGTP'))
purine.path = rbind(purine.path, dGTP)

guanine = data.frame(enzyme = c('2.4.2.1', '2.4.2.1'),
                     from = c('guanosine', 'deoxyguanosine'),
                     to = c(rep('guanine', 2)))
purine.path = rbind(purine.path, guanine)

dGDP = data.frame(enzyme = c('2.7.4.6', '1.17.4.1', '2.7.4.8'),
                  from = c('dGTP', 'GDP', 'dGMP'),
                  to = c(rep('dGDP', 3)))
purine.path = rbind(purine.path, dGDP)

guanosine = data.frame(enzyme = c('2.4.2.1', '3.1.3.5'),
                       from = c('guanine', 'GMP'),
                       to = c(rep('guanosine', 2)))
purine.path = rbind(purine.path, guanosine)

GTP = data.frame(enzyme = c('2.7.4.6'),
                 from = c('GDP'),
                 to = c(rep('GTP', 1)))
purine.path = rbind(purine.path, GTP)

GDP = data.frame(enzyme = c('2.7.4.6', '2.7.4.8'),
                 from = c('GTP', 'GMP'),
                 to = c(rep('GDP', 2)))
purine.path = rbind(purine.path, GDP)

GMP = data.frame(enzyme = c('6.3.5.2','3.6.1.6', '2.7.4.8'),
                 from = c('XMP', 'GDP', 'GDP'),
                 to = c(rep('GMP', 3)))
purine.path = rbind(purine.path, GMP)

dGMP = data.frame(enzyme = c('2.7.4.8', '2.7.1.145'),
                  from = c('dGDP', 'deoxyguanosine'),
                  to = c(rep('dGMP', 2)))
purine.path = rbind(purine.path, dGMP)

cAMP = data.frame(enzyme = '4.6.1.1',
                  from = 'ATP',
                  to = 'cAMP')
purine.path = rbind(purine.path, cAMP)

FGAM = data.frame(c(),
               c())

purine.path$arrows = 'to'
temp = purine.path
temp[,5] = paste0(purine.path[,1], purine.path[,2], purine.path[,3])
temp[,6] = paste0(purine.path[,1], purine.path[,3], purine.path[,2])
temp$keep = TRUE

i=1
while(i<=nrow(temp)){
  if(length(intersect(temp[i,6], temp[temp$keep==TRUE,5]))==1){
        temp$keep[i] = FALSE
        temp[temp[,5] == temp[i,6], 'arrows'] = 'to;from'
  }
  i=i+1
}

purine.path = temp[temp$keep, 1:4]
purine.path$FBgn = ''

temp.purine.path = purine.path

i=1
while(i<=nrow(purine.path)){  
  enzymeID = purine.path$enzyme[i]
  temp = names(nodeID[grep(enzymeID, nodeID)])
  temp = setNames(unlist(nodeID[temp], use.names = F), rep(names(nodeID[temp]), lengths(nodeID[temp])))
  temp = names(temp[temp == enzymeID])
  temp = row.names(GeneIDKey[GeneIDKey$ensembl %in% temp, ])
  temp2 = purine.path[rep(i, length(temp)),]
  temp2$FBgn = temp
  temp.purine.path = rbind(temp.purine.path,temp2)
  i = i +1
}

purine.path = temp.purine.path[(nrow(purine.path)+1):nrow(temp.purine.path),]
purine.path = purine.path[!duplicated(purine.path[,2:5]),]

TerminalPoints = data.frame(enzyme = "Excretion",
                            from = 'uric acid',
                            to = 'Excretion')

DNA.A = data.frame(enzyme = c('DNA.A'),
                 from = c('dATP'),
                 to = c('DNA.A'))
TerminalPoints = rbind(TerminalPoints, DNA.A)

DNA.G = data.frame(enzyme = c('DNA.G'),
                 from = c('dGTP'),
                 to = c('DNA.G'))
TerminalPoints = rbind(TerminalPoints, DNA.G)

RNA.A = data.frame(enzyme = c('RNA.A'),
                 from = c('ATP'),
                 to = c('RNA.A'))
TerminalPoints = rbind(TerminalPoints, RNA.A)

RNA.G = data.frame(enzyme = c('RNA.G'),
                 from = c('GTP'),
                 to = c('RNA.G'))
TerminalPoints = rbind(TerminalPoints, RNA.G)

Riboflavin.Metabolism = data.frame(enzyme = c('Riboflavin.Metabolism'),
                 from = c('GTP'),
                 to = c('Riboflavin.Metabolism'))
TerminalPoints = rbind(TerminalPoints, Riboflavin.Metabolism)

Folate.Biosynthesis = data.frame(enzyme = c('Folate.Biosynthesis'),
                 from = c('GTP'),
                 to = c('Folate.Biosynthesis'))
TerminalPoints = rbind(TerminalPoints, Folate.Biosynthesis)

PPP = data.frame(enzyme = c('Pentose Phosphate'),
                 from = c('Pentose Phosphate'),
                 to = c('IMP'))
TerminalPoints = rbind(TerminalPoints, PPP)

TerminalPoints = data.frame(enzyme = TerminalPoints$enzyme,
                            from = TerminalPoints$from,
                            to = TerminalPoints$to,
                            arrows = 'to',
                            FBgn = NA,
                            color = 'black',
                            width = 1,
                            symbol = NA,
                            fdr = NA,
                            GR = NA,
                            WT = NA,
                            title = '')

temp = keggGet("dme:CG16758" )[[1]]

temp = keggGet(names(temp$ORTHOLOGY))[[1]]

temp = names(temp$REACTION)

equation = as.character()
reaction = as.character()

i=1
while(i<= length(temp)){
  equation[i] = keggGet(temp[i])[[1]]["EQUATION"][[1]]
  reaction[i] = keggGet(temp[i])[[1]]["DEFINITION"][[1]]
  i=i+1
}

equation.length = lengths(strsplit(equation, " "))

interactions = matrix("",
                      nrow = length(equation),
                      ncol = max(equation.length))

i=1
while(i<= length(equation)){
  interactions[i, 1:equation.length[i]] = strsplit(equation[i], " ")[[1]]
  i=i+1
}

unique.metabs = unique(as.character(interactions))
unique.metabs = unique.metabs[grep("C", unique.metabs)]

i = 1
while(i <= length(unique.metabs)){
  if(length(metab.id[grep(unique.metabs[i], names(metab.id))])>0){
    interactions[interactions == unique.metabs[i]] = metab.id[grep(unique.metabs[i], names(metab.id))]
    }
  i=i+1
}

interactions = interactions[c(1:5, 7:9), c(1,4,5)]

```

```{r echo = F}

plot(x = G85R.FC$GRxWT.FC,
     y= -log2(G85R.FDR$GRxWT.FC),
     pch = 21,
     bg = 'lightgrey',
     cex = 1.5,
     ylab = "-log2(FDR)",
     xlab = "log2(Fold Change)",
     main = "G85R Females/Silent Females")

points(x = G85R.FC[GeneIDKey[GeneIDKey$Symbol == "CG16758", "FBgn"], 'GRxWT.FC'],
       y= -log2(G85R.FDR[GeneIDKey[GeneIDKey$Symbol == "CG16758", "FBgn"], 'GRxWT.FC']),
       pch = 21,
       bg = 'deeppink',
       cex = 1.5)

```

```{r echo = F}

plot(x = G85R.FC$GRxWT.MC,
     y= -log2(G85R.FDR$GRxWT.MC),
     pch = 21,
     bg = 'lightgrey',
     cex = 1.5,
     ylab = "-log2(FDR)",
     xlab = "log2(Fold Change)",
     main = "G85R Males/Silent Males")

points(x = G85R.FC[GeneIDKey[GeneIDKey$Symbol == "CG16758", "FBgn"], 'GRxWT.MC'],
       y= -log2(G85R.FDR[GeneIDKey[GeneIDKey$Symbol == "CG16758", "FBgn"], 'GRxWT.MC']),
       pch = 21,
       bg = 'cyan',
       cex = 1.5)

```

```{r echo = F}

plot(x = log2(G85R.metabFC$GRxWT.C),
     y= -log2(G85R.metabFDR$GRxWT.C),
     pch = 21,
     bg = 'lightgrey',
     cex = 1.5,
     ylab = "-log2(FDR)",
     xlab = "log2(Fold Change)",
     main = "G85R/Silent Metabolites")

points(x = log2(G85R.metabFC['uric acid', 'GRxWT.C']),
       y= -log2(G85R.metabFDR['uric acid', 'GRxWT.C']),
       pch = 21,
       bg = 'gold',
       cex = 1.5)

points(x = log2(G85R.metabFC['uric acid', 'GRxWT.C']),
       y= -log2(G85R.metabFDR['xanthine', 'GRxWT.C']),
       pch = 21,
       bg = 'orange',
       cex = 1.5)

```

```{r echo = F}

FBgn = 'FBgn0035348'
name = 'PNP (CG16758)'

gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), condition = groups$Group, group = paste0(groups$Genotype, groups$Sex))

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$cpm), max(gene$cpm)),
     xlim = c(.5, 12.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')

boxplot(gene$cpm~gene$condition, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("honeydew", 3),
                rep("thistle1", 3),
                rep("lightcyan", 3),
                rep("lightyellow", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$condition)),
       y=gene$cpm,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:12,
     labels = rep(c("Control", "Df", "OE"), 4),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$cpm) + min(gene$cpm)),
     label = "Counts per million reads",
     tick = F,
     padj = -3,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5, 8, 11),
     labels = c("Silent", "G85R","Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)
axis(side = 3,
     at = c(3.5, 9.5),
     labels = c("Female", "Male"),
     tick = F,
     padj = .5,
     cex.axis = 1.5)

axis(side = 3,
     at = 6.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

axis(side = 3,
     at = c(3.5,9.5),
     tick = T,
     outer = T,
     labels = F,
     line = -2.25,
     lwd.ticks = 0)

xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
abline(v = 6.5, lty = 2, lwd = 2)

```

```{r echo = F}

name = 'uric acid'

gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r echo = F}

name = 'uric acid'
name = 'NAD+'
name = 'NADP+'
name = 'nicotinamide riboside+'
name = 'NMN'

gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

if(name == "NADP+"){
  gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                    group = c(colnames(G85R.metabnorm)))
  gene = gene[gene$group != "WT1",]
  gene$group = substr(gene$group, 1, nchar(gene$group)-1)
}

#gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r echo = F}

name = 'uric acid'

name = 'NADP+'
name = 'nicotinamide riboside+'
name = 'NMN'
name = 'NAD+'

gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

if(name == "NADP+"){
  gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                    group = c(colnames(G85R.metabnorm)))
  gene = gene[gene$group != "WT1",]
  gene$group = substr(gene$group, 1, nchar(gene$group)-1)
}

#gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r echo = F}

name = 'uric acid'

name = 'NADP+'
name = 'nicotinamide riboside+'
name = 'NMN'
name = 'NADH'

gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

if(name == "NADP+"){
  gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                    group = c(colnames(G85R.metabnorm)))
  gene = gene[gene$group != "WT1",]
  gene$group = substr(gene$group, 1, nchar(gene$group)-1)
}

#gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r echo = F}

name = 'uric acid'

name = 'NADP+'
name = 'nicotinamide riboside+'
name = 'NMN'
name = 'NADH'
name = 'NADP+'

gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

if(name == "NADP+"){
  gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                    group = c(colnames(G85R.metabnorm)))
  gene = gene[gene$group != "WT1",]
  gene$group = substr(gene$group, 1, nchar(gene$group)-1)
}

#gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r echo = F}

name = 'uric acid'

name = 'NADP+'
name = 'nicotinamide riboside+'
name = 'NMN'
name = 'NAD+'
name = 'NADPH'
gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                  group = c(substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)))

if(name == "NADP+"){
  gene = data.frame(level = as.numeric(G85R.metabnorm[name,]),
                    group = c(colnames(G85R.metabnorm)))
  gene = gene[gene$group != "WT1",]
  gene$group = substr(gene$group, 1, nchar(gene$group)-1)
}

if(name == "NADPH"){
  gene = na.omit(gene)
}

#gene$group = substr(colnames(G85R.metabnorm), 1, nchar(colnames(G85R.metabnorm))-1)

gene$group = factor(gene$group, levels = c("WT", "TktDfWT", "TktOEWT",
                                           "GR", "TktDfGR", "TktOEGR"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$level), max(gene$level)),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$level)), 13, 1.5*max(gene$level), col = 'gray95')

boxplot(gene$level~gene$group, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("lightcyan", 3),
                rep("thistle1", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$group)),
       y=gene$level,
       cex=1,
       pch=21,
       bg=c(rep("dodgerblue", 3), rep('firebrick', 3))[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:6,
     labels = rep(c("Control", "Df", "OE"), 2),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$level) + min(gene$level)),
     label = "Normalized Metabolite Level",
     tick = F,
     padj = -4,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5),
     labels = c("Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)

axis(side = 3,
     at = 3.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

xline1 = min(gene$level) - (max(gene$level)-min(gene$level))*.04
xline2 = min(gene$level) - (max(gene$level)-min(gene$level))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)

```

```{r include = F}

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

row.names(metadata) = metadata$Sample

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

mean.cpm

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.data[,condition1]/mean.data[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.data)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

GR.CxDf = compare.conditions("D", "E")
WT.CxDf = compare.conditions("B", "C")

GR.CxOE = compare.conditions("F", "E")
WT.CxOE = compare.conditions("A", "C")

TKT.EdgeR.FC = G85R.FC
TKT.EdgeR = G85R.FDR

network.fun = function(comparison.T, comparison.M, cond1, cond2, pnp){
temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

visedges = purine.path
visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))

visedges$title = paste0(visedges$symbol,
                        "<br>FDR: ", visedges$fdr, 
                        "<br>",cond1," CPM: ", visedges$GR, 
                        "<br>",cond2," CPM: ", visedges$WT)
visedges = na.omit(visedges)
visedges = rbind(visedges, TerminalPoints)

node.names = unique(c(visedges$from, visedges$to))
node.data = data.frame(id = node.names,
                       color = 'dimgrey',
                       size = 10,
                       FC = NA,
                       pval = NA,
                       row.names = node.names)

row.names(comparison.M)[row.names(comparison.M) == "cAMP(2',3') / cAMP(3',5')"] = 'cAMP'

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
#node.data[names(node.colors),'size'] = 
#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
node.data[names(node.colors),'size'] = 
  (node.data[names(node.colors),'size'] + 4.5)*7.5

node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2

node.colors = (node.colors*100)+201

node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color'] = node.colors

node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)

node.data[unique(TerminalPoints$enzyme), 'color'] = 'black'

node.data$group = 'metabolite'
node.data[node.data$color == 'black', 'group'] = "Outside Path"
node.data[node.data$color == 'dimgrey', 'group'] = "no data"

node.data$x = 1
node.data$y = 1
node.data["Excretion", 'x'] = -200
node.data["Excretion", 'y'] = 500

node.data["Pentose Phosphate" , 'x'] = 50
node.data["Pentose Phosphate" , 'y'] = -400

node.data["RNA.A", 'x'] = 850
node.data["RNA.A", 'y'] = -250

node.data["RNA.G", 'x'] = -1000
node.data["RNA.G", 'y'] = -250

node.data["Folate.Biosynthesis", 'x'] = -1000
node.data["Folate.Biosynthesis", 'y'] = -350

node.data["Riboflavin.Metabolism", 'x'] = -1000
node.data["Riboflavin.Metabolism", 'y'] = -150

node.data["DNA.A", 'x'] = 850
node.data["DNA.A", 'y'] = 250

node.data["DNA.G", 'x'] = -1000
node.data["DNA.G", 'y'] = 250

# passing custom nodes and/or edges
lnodes <- data.frame(label = c("Increased", "Decreased", "No Data"), 
shape = 'dot', color = c("firebrick", "royalblue",'dimgrey'),
 title = "")

nodes = node.data

##nodes$color[nodes$color != "black"] = 'dimgrey'

colored.nodes = unique(c(interactions[,1], interactions[,3]))
colored.nodes = c(setdiff(row.names(nodes), c(colored.nodes, row.names(nodes)[nodes$color == "black"])))

#nodes[row.names(nodes) %in% colored.nodes, 'color'] = "gold"

visedges = visedges[,c('from', 'to', 'arrows', 'color', 'width', 'title')]
row.names(visedges) = c(1:nrow(visedges))

colored.edges = row.names(visedges[grep("CG16758", visedges$title),])
colored.edges = setdiff(row.names(visedges), colored.edges)

if(pnp == T){
  nodes[row.names(nodes) %in% colored.nodes, 'color'] = "lightgrey"
  visedges[row.names(visedges) %in% colored.edges, "color"] = 'lightgrey'
}

visNetwork(nodes,visedges,
                  main = paste0(cond1, " vs ", cond2))%>%
  visNodes(physics = T)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T, minVelocity = .5)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows)%>%
  visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))%>%
    visLegend(addNodes = lnodes, useGroups = FALSE, width = .115)

}

```

```{r echo = F}

comparison.T = "GRxWT.FC"
cond1 = 'GR.F'
cond2 = "WT.F"
comparison.M = GRxWT.C
pnp = F

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r echo = F}

comparison.T = "GRxWT.FDf"
cond1 = 'TktDfGR.F'
cond2 = "TktDfWT.F"
comparison.M = GRxWT.Df
pnp = F

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r echo = F}

comparison.T = "GRxWT.FOE"
cond1 = 'TktOEGR.F'
cond2 = "TktOEWT.F"
comparison.M = GRxWT.OE
pnp = F

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r echo = F}

comparison.T = "GRxWT.FC"
cond1 = 'GR.F'
cond2 = "WT.F"
comparison.M = GRxWT.C
pnp = T

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r echo = F}

comparison.T = "GRxWT.FDf"
cond1 = 'TktDfGR.F'
cond2 = "TktDfWT.F"
comparison.M = GRxWT.Df
pnp = T

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r echo = F}

comparison.T = "GRxWT.FOE"
cond1 = 'TktOEGR.F'
cond2 = "TktOEWT.F"
comparison.M = GRxWT.OE
pnp = T

network.fun(comparison.T, comparison.M, cond1, cond2, pnp)

```

```{r include = F}

NAD.nodes = data.frame(ID = character(),
                       x = numeric(),
                       y = numeric(),
                       names = character())

NAD.nodes[1,] = c('C03150', 0,  0,    "nicotinamide riboside+")
NAD.nodes[2,] = c('C00153', 0,  5,    "nicotinamide")
NAD.nodes[3,] = c('C00253', 0,  7.5,  "nicotinic acid")
NAD.nodes[4,] = c('C00455', 5,  2.5,  "NMN")
NAD.nodes[5,] = c('C01185', 5,  7.5,  "NAMN")
NAD.nodes[6,] = c('C00006', 10, -2.5, "NADP+")
NAD.nodes[7,] = c('C00003', 10, 2.5,  "NAD+")
NAD.nodes[8,] = c('C00857', 10, 7.5,  "NAAD")
NAD.nodes[9,] = c('C00005', 15, -2.5, "NADPH")
NAD.nodes[10,] = c('C00004', 15, 2.5,  "NADH")

NAD.nodes[11,] = c('C00806', 20, 10,  "tryptophan")
NAD.nodes[12,] = c('C02794', 5, 10,  "3-hydroxykynurenine")
NAD.nodes[13,] = c('C01718', 10, 10,  "kynurenine")
NAD.nodes[14,] = c('C01717', 5, 12.5,  "kynurenic acid")
NAD.nodes[15,] = c('C02700', 15, 10,  "N-Formylkynurenine")

temp = unlist(strsplit(keggGet("C00806")[[1]]["REACTION"][[1]], split = " "))

#NR <=> NMN: "3.1.3.5", "2.7.1.22"
#NR <=> NAM: "2.4.2.1", "3.2.2.3"
#NMN <=> NAM: "3.2.2.14" "2.4.2.12"
#NA <=> NAMN: "2.4.2.55" "6.3.4.21" "2.4.2.21"
#NAMN <=> NAAD: "3.6.1.9"  "3.6.1.22" "2.7.7.1"  "2.7.7.18" 
#NAMN <=> NMN: "3.5.1.42"

#temp = unlist(strsplit(keggGet("C00003")[[1]]["REACTION"][[1]], split = " "))
#i = 1

#NADH = character()
#NADP = character()
#NMN = character()
#NAAD = character()

#while(i <= length(temp)){
#  temp.eq = keggGet(temp[i])[[1]][c("EQUATION")][[1]]
#  temp.enz = keggGet(temp[i])[[1]][c("ENZYME")][[1]]
#  if(length(grep("C00004", temp.eq)) == 1){
#    NADH = unique(c(NADH, temp.enz))
#  }
#  if(length(grep("C00006", temp.eq)) == 1){
#    NADP = unique(c(NADP, temp.enz))
#  }
#  if(length(grep("C00857", temp.eq)) == 1){
#    NAAD = unique(c(NAAD, temp.enz))
#  }
#  if(length(grep("C00455", temp.eq)) == 1){
#    NMN = unique(c(NMN, temp.enz))
#  }
#  i = i +1
#}

#NAD+ <=> NMN: NMN
#NAD+ <=> NADP: NADP
#NAD+ <=> NAAD: NAAD
#NAD+ <=> NADH: NADH

#temp = unlist(strsplit(keggGet("C00006")[[1]]["REACTION"][[1]], split = " "))
#i = 1

#NADPH = character()

#while(i <= length(temp)){
#  temp.eq = keggGet(temp[i])[[1]][c("EQUATION")][[1]]
#  temp.enz = keggGet(temp[i])[[1]][c("ENZYME")][[1]]
#  if(length(grep("C00005", temp.eq)) == 1){
#    NADPH = c(NADPH, temp.enz)
#  }
#  i = i +1
#  temp.eq
#  NADPH
#}

#NADPH = unique(NADPH)

#enzymes = list(NR2NAM  = c("2.4.2.1", "3.2.2.3"),
#               NR2NMN  = c("3.1.3.5", "2.7.1.22"),
#               NAM2NMN = c("3.2.2.14", "2.4.2.12"),
#               NMN2NAD = NMN,
#               NAD2NADP = NADP,
#               NAD2NADH = NADH,
#               NA2NAMN = c("2.4.2.55", "6.3.4.21", "2.4.2.21"),
#               NAMN2NAAD = c("3.6.1.9", "3.6.1.22", "2.7.7.1", "2.7.7.18" ),
#               NAMN2NMN = c("3.5.1.42"),
#               NAAD2NAD = NAAD,
#               NADP2NADPH = NADPH)

#NR2NAM = unique(c(names(nodeID[grep("\\b2.4.2.1\\b", nodeID)]),
#                  names(nodeID[grep("\\b3.2.2.3\\b", nodeID)])))

#NR2NMN = unique(c(names(nodeID[grep("\\b3.1.3.5\\b", nodeID)]),
#                  names(nodeID[grep("\\b2.7.1.22\\b", nodeID)])))

#NAM2NMN = unique(c(names(nodeID[grep("\\b3.2.2.14\\b", nodeID)]),
#                   names(nodeID[grep("\\b2.4.2.12\\b", nodeID)])))

#NA2NAMN = unique(c(names(nodeID[grep("\\b2.4.2.55\\b", nodeID)]),
#                   names(nodeID[grep("\\b6.3.4.21\\b", nodeID)]),
#                   names(nodeID[grep("\\b2.4.2.21\\b", nodeID)])))

#NAMN2NAAD = unique(c(names(nodeID[grep("\\b3.6.1.9\\b", nodeID)]),
#                     names(nodeID[grep("\\b3.6.1.22\\b", nodeID)]),
#                     names(nodeID[grep("\\b2.7.7.1\\b", nodeID)]),
#                     names(nodeID[grep("\\b2.7.7.18\\b", nodeID)])))

#NAMN2NMN = unique(c(names(nodeID[grep("\\b3.5.1.42\\b", nodeID)])))

#NAAD2NAD = unique(c(names(nodeID[grep("\\b6.3.1.5\\b", nodeID)]),
#                    names(nodeID[grep("\\b6.3.5.1\\b", nodeID)])))

#NMN2NAD = character()
#i=1
#while(i <= length(NMN)){
#  NMN2NAD = unique(c(NMN2NAD, names(nodeID[grep(paste0("\\b",NMN[i],"\\b"), nodeID)])))
#  i=i+1
#}

#NAD2NADP = character()
#i=1
#while(i <= length(NADP)){
#  NAD2NADP = unique(c(NAD2NADP, names(nodeID[grep(paste0("\\b",NADP[i],"\\b"), #nodeID)])))
#  i=i+1
#}

#NAD2NADH = character()
#i=1
#while(i <= length(NADH)){
#  NAD2NADH = unique(c(NAD2NADH, names(nodeID[grep(paste0("\\b",NADH[i],"\\b"), nodeID)])))
#  i=i+1
#}

#NADP2NADPH = character()
#i=1
#while(i <= length(NADPH)){
#  NADP2NADPH = unique(c(NADP2NADPH, names(nodeID[grep(paste0("\\b",NADPH[i],"\\b"), #nodeID)])))
#  i=i+1
#}

#NAD.edges = matrix(rep("", (11*length(NAD2NADH))), ncol = 11)

#colnames(NAD.edges) = c("NR2NAM", "NR2NMN", "NAM2NMN", "NMN2NAD", "NAD2NADP", "NAD2NADH",
#                        "NA2NAMN", "NAMN2NAAD", "NAMN2NMN", "NAAD2NAD", "NADP2NADPH")

#NAD.edges[1:length(NR2NAM),    "NR2NAM"]     = NR2NAM
#NAD.edges[1:length(NR2NMN),    "NR2NMN"]     = NR2NMN
#NAD.edges[1:length(NAM2NMN),   "NAM2NMN"]    = NAM2NMN
#NAD.edges[1:length(NMN2NAD),   "NMN2NAD"]    = NMN2NAD
#NAD.edges[1:length(NAD2NADP),  "NAD2NADP"]   = NAD2NADP
#NAD.edges[1:length(NAD2NADH),  "NAD2NADH"]   = NAD2NADH
#NAD.edges[1:length(NA2NAMN),   "NA2NAMN"]    = NA2NAMN
#NAD.edges[1:length(NAMN2NAAD), "NAMN2NAAD"]  = NAMN2NAAD
#NAD.edges[1:length(NAMN2NMN),  "NAMN2NMN"]   = NAMN2NMN
#NAD.edges[1:length(NAAD2NAD),  "NAAD2NAD"]   = NAAD2NAD
#NAD.edges[1:length(NADP2NADPH),"NADP2NADPH"] = NADP2NADPH

#write.csv(NAD.edges, "/Users/johncsantiago/Documents/GitHub/WhartonLab/NAD.edges.csv")

```

```{r echo = F}

NAD.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/NAD.edges.csv", row.names = 1)

NAD.nodes = data.frame(ID = character(),
                       x = numeric(),
                       y = numeric(),
                       names = character())

NAD.nodes[1,] = c('C03150', 0,  0,    "nicotinamide riboside+")
NAD.nodes[2,] = c('C00153', 0,  5,    "nicotinamide")
NAD.nodes[3,] = c('C00253', 0,  7.5,  "nicotinic acid")
NAD.nodes[4,] = c('C00455', 5,  2.5,  "NMN")
NAD.nodes[5,] = c('C01185', 5,  7.5,  "NAMN")
NAD.nodes[6,] = c('C00006', 10, -2.5, "NADP+")
NAD.nodes[7,] = c('C00003', 10, 2.5,  "NAD+")
NAD.nodes[8,] = c('C00857', 10, 7.5,  "NAAD")
NAD.nodes[9,] = c('C00005', 15, -2.5, "NADPH")
NAD.nodes[10,] = c('C00004', 15, 2.5,  "NADH")

NAD.nodes[11,] = c('C00806', 20, 10,  "tryptophan")
NAD.nodes[12,] = c('C02794', 5, 10,  "3-hydroxykynurenine")
NAD.nodes[13,] = c('C01718', 10, 10,  "kynurenine")
NAD.nodes[14,] = c('C01717', 10, 12.5,  "kynurenic acid")
NAD.nodes[15,] = c('C02700', 15, 10,  "N-Formylkynurenine")

row.names(NAD.nodes) = NAD.nodes$names

NAD.genes = data.frame( FBgn = character(),
                        Symbol = character(),
                        FC = numeric(),
                        FDR = numeric())

edges = data.frame(from = character(),
                   to = character(),
                   arrows = character(),
                   FBgn = character(),
                   Symbol = character())

#color = character(),
#                   FDR = numeric(),
#                   GR = numeric(),
#                   WT = numeric(),
#                   FC = numeric())

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NR2NAM), c("FBgn", "Symbol")]
temp$from = "nicotinamide riboside+"
temp$to = "nicotinamide"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NR2NMN), c("FBgn", "Symbol")]
temp$from = "nicotinamide riboside+"
temp$to = "NMN"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = data.frame(FBgn = "",
                  Symbol = "")
temp$from = "nicotinamide"
temp$to = "NMN"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NMN2NAD), c("FBgn", "Symbol")]
temp$from = "NMN"
temp$to = "NAD+"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NAD2NADP), c("FBgn", "Symbol")]
temp$from = "NAD+"
temp$to = "NADP+"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = data.frame(FBgn = "",
                  Symbol = "")
temp$from = "NAD+"
temp$to = "NADH"
temp$arrows = "to;from"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = data.frame(FBgn = "",
                  Symbol = "")
temp$from = "NADP+"
temp$to = "NADPH"
temp$arrows = "to;from"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = data.frame(FBgn = "",
                  Symbol = "")
temp$from = "nicotinic acid"
temp$to = "NAMN"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NAMN2NAAD), c("FBgn", "Symbol")]
temp$from = "NAMN"
temp$to = "NAAD"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

temp = GeneIDKey[GeneIDKey$ensembl %in% na.omit(NAD.edges$NAAD2NAD), c("FBgn", "Symbol")]
temp$from = "NAAD"
temp$to = "NAD+"
temp$arrows = "to"
temp = temp[,colnames(edges)]
edges = rbind(edges, temp)

FBgn0003965 = data.frame(from = "tryptophan",
                         to = "N-Formylkynurenine",
                         arrows = "to",
                         FBgn = "FBgn0003965",
                         Symbol = "v")

FBgn0031821 = data.frame(from = "N-Formylkynurenine",
                         to = "kynurenine",
                         arrows = "to",
                         FBgn = "FBgn0031821",
                         Symbol = "KFase")

FBgn0000337 = data.frame(from = "kynurenine",
                         to = "3-hydroxykynurenine",
                         arrows = "to",
                         FBgn = "FBgn0000337",
                         Symbol = "cn")

FBgn0037955 = data.frame(from = "kynurenine",
                         to = "kynurenic acid",
                         arrows = "to",
                         FBgn = "FBgn0037955",
                         Symbol = "Kyat")

HKY2NAMN = data.frame(from = "3-hydroxykynurenine",
                         to = "NAMN",
                         arrows = "to",
                         FBgn = "",
                         Symbol = "")

edges = rbind(edges, 
              rbind(FBgn0003965, 
                    rbind(FBgn0031821, 
                          rbind(FBgn0000337, 
                                rbind(FBgn0037955, HKY2NAMN)))))

NAD.path = edges

```

```{r echo = F}
NAD.network.fun = function(comparison.T, comparison.M, cond1, cond2){
temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

visedges = NAD.path
visedges$color = round(TKT.EdgeR.FC[NAD.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$color[is.na(visedges$color)] = "black"

#visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
temp.width = data.frame(GR = visedges$GR,
                        WT = visedges$WT)
temp.width$max = apply(temp.width, 1, max)/50
temp.width$max[is.na(temp.width$max)] = .1
visedges$width = temp.width$max
visedges$width[visedges$width <= 1] = 1

visedges$title = paste0(visedges$Symbol,
                        "<br>FDR: ", visedges$fdr, 
                        "<br>",cond1," CPM: ", visedges$GR, 
                        "<br>",cond2," CPM: ", visedges$WT)
#visedges = na.omit(visedges)

node.names = unique(c(visedges$from, visedges$to))
node.data = data.frame(id = node.names,
                       color = 'dimgrey',
                       size = 10.5,
                       FC = NA,
                       pval = NA,
                       row.names = node.names)

#row.names(comparison.M)[row.names(comparison.M) == "cAMP(2',3') / cAMP(3',5')"] = 'cAMP'

node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
node.pval = setNames(signif((node.colors$p),2), row.names(node.colors))
node.data[names(node.pval), 'pval'] = node.pval
node.colors = setNames(round(log2(node.colors$FC),2), row.names(node.colors))
node.data[names(node.colors), "FC"] = node.colors
node.data[names(node.colors),'size'] = node.colors
#node.data[names(node.colors),'size'] = 
#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
node.data[names(node.colors),'size'] = 
  (node.data[names(node.colors),'size'] + 3)*3.5

node.colors[node.colors < (-2)] = -2
node.colors[node.colors>2] = 2

node.colors = (node.colors*100)+201

node.colors = setNames(temp[node.colors], names(node.colors)) 
node.data[names(node.colors), 'color'] = node.colors

node.data$title = paste0(node.data$id,
                         "<br>FC: ", node.data$FC,
                         "<br>pval: ", node.data$pval)

node.data$group = 'metabolite'
#node.data[node.data$color == 'black', 'group'] = "Outside Path"
#node.data[node.data$color == 'dimgrey', 'group'] = "no data"

row.names(NAD.nodes) = NAD.nodes$names

# passing custom nodes and/or edges
lnodes <- data.frame(label = c("Increased", "Decreased", "No Data"), 
shape = 'dot', color = c("firebrick", "royalblue",'dimgrey'),
 title = "")

nodes = node.data

##nodes$color[nodes$color != "black"] = 'dimgrey'

colored.nodes = unique(c(interactions[,1], interactions[,3]))
colored.nodes = c(setdiff(row.names(nodes), c(colored.nodes, row.names(nodes)[nodes$color == "black"])))

#nodes[row.names(nodes) %in% colored.nodes, 'color'] = "gold"

visedges = visedges[,c('from', 'to', 'arrows', 'color', 'width', 'title')]
row.names(visedges) = c(1:nrow(visedges))

colored.edges = row.names(visedges[grep("CG16758", visedges$title),])
colored.edges = setdiff(row.names(visedges), colored.edges)

nodes$x = as.numeric(NAD.nodes[nodes$id, "x"])*50
nodes$y = as.numeric(NAD.nodes[nodes$id, "y"])*50

visNetwork(nodes,visedges,
                  main = paste0(cond1, " vs ", cond2))%>%
  visNodes(physics = F)%>%
  #visLayout(hierarchical=F, improvedLayout=T)%>%
  visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T, minVelocity = .5)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows, physics = T)%>%
  #visGroups(groupname = "Outside Path", shape = 'box', physics=F, size = 25, font=list(color="white"))%>%
    visLegend(addNodes = lnodes, useGroups = FALSE, width = .115)

}

```

```{r echo = F}

comparison.T = "GRxWT.FC"
cond1 = 'GR.F'
cond2 = "WT.F"
comparison.M = GRxWT.C

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

```{r echo = F}

comparison.T = "GRxWT.MC"
cond1 = 'GR.M'
cond2 = "WT.M"
comparison.M = GRxWT.C

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

```{r echo = F}

comparison.T = "GRxWT.FDf"
cond1 = 'TktDfGR.F'
cond2 = "TktDfWT.F"
comparison.M = GRxWT.Df

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

```{r echo = F}

comparison.T = "GRxWT.MDf"
cond1 = 'TktDfGR.M'
cond2 = "TktDfWT.M"
comparison.M = GRxWT.Df

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

```{r echo = F}

comparison.T = "GRxWT.FOE"
cond1 = 'TktOEGR.F'
cond2 = "TktOEWT.F"
comparison.M = GRxWT.OE

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

```{r echo = F}

comparison.T = "GRxWT.MOE"
cond1 = 'TktOEGR.M'
cond2 = "TktOEWT.M"
comparison.M = GRxWT.OE

NAD.network.fun(comparison.T, comparison.M, cond1, cond2)

```

### 2025-01-13 mt.nuc PCA for grant.Rmd
data files

---
title: "mt:nuc PCA for grant"
author: "John Santiago"
date: "2024-11-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, warning = F, include = F}

if(intersect(row.names(installed.packages()), "factoextra") != 'factoextra'){
  # Install
  if(!require(devtools)) install.packages("devtools")
  devtools::install_github("kassambara/survminer")
}

library(devtools)
library(factoextra)

##CPM and other gene info for a subset of OXPHOS genes that met the cpm cutoff
complex.data = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/mt.nuc.OXPHOS_PCAdata.csv", row.names = 1)

##just the cpm data
complex.cpm = complex.data[,5:34]
##scaled the cpm data
complex.cpm = t(scale(t(complex.cpm)))
##pca of the scaled cpm data
pca <- prcomp((complex.cpm), scale.=TRUE)

##other information for each gene besides cpm
gene.info = complex.data[,1:4]
##change non-mt chromosomes to 'nuc' for coloring
gene.info$CHR[gene.info$CHR != "mt"] = 'nuc'

```

```{r echo = F}

fviz_pca_ind(pca, 
             col.ind = gene.info$CHR,
             addEllipses = T, 
             label = "none" )

```

### 2025-01-13 OmicsQuickPlotFunctions.Rmd
updated raw metabolomic data

--- 2025-01-13 GeneExpressionBoxPlots.Rmd
@@
 
-library(plotly)
+##library(plotly)
 library(edgeR)
 
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+##load all files from github
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
 
-##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
 
-TKT.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)
 
-TKT.groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-TKT.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
-TKT.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
+TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)
 
@@
 
-A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)
+A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
 
-A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
+gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
 
-gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
-gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
+gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
+
 gbbOE = gbbOE[,row.names(gbbOE.groups)]
@@
 
-##normalize data
-countdata=gbbOE
-x <- countdata
-gr <- factor(gbbOE.groups$group, levels=c(unique(gbbOE.groups$group)))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- calcNormFactors(y, method = "TMM")
-##normalized cpm
-gbbOE.cpmdata=cpm(z)
+rawdata = read.csv(paste0(git.dir, "MetabolomicsForMetaboanalyst.txt"), sep = "\t", row.names = 1)
 
-gbbOEmean = gbbOE.cpmdata[,1:6]
-colnames(gbbOEmean) = unique(gr)
-i=1
-while(i<=6){
-  temp= gbbOE.cpmdata[,row.names(gbbOE.groups[gbbOE.groups$group == colnames(gbbOEmean)[i],])]
-  gbbOEmean[,i] = apply(temp, 1, mean)
-  i=i+1
-}
+KEGG.Key = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
 
-design<-model.matrix(~0 + gr)
-colnames(design) = unique(gr)
-z = estimateDisp(z, design, robust = T)
-
-fit <- glmQLFit(z, design)
-plotQLDisp(fit)
-
-compare = makeContrasts(G85R_LL3-LoxP_LL3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.LL3=DEout
-sGRxWT.LL3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_ML3-LoxP_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.ML3=DEout
-sGRxWT.ML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_LL3-G85R_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.LL3xML3=DEout
-sGR.LL3xML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(LoxP_LL3-LoxP_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.LL3xML3=DEout
-sWT.LL3xML3=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(G85R_gbb_LL3-G85R_gbb_ML3, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-G85R_gbb.LL3xML3=DEout
-sG85R_gbb.LL3xML3=DEout[DEout$FDR<.05,]
-
-gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
-gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)
-
-##normalize data
-countdata=gbbKO
-x <- countdata
-gr <- factor(gbbKO.groups$Genotype, levels=c(unique(gbbKO.groups$Genotype)))
-y <- DGEList(counts=x,group=gr)
-keep <- filterByExpr(y)
-y <- y[keep,,keep.lib.sizes=FALSE]
-z <- calcNormFactors(y, method = "TMM")
-##normalized cpm
-gbbKO.cpmdata=cpm(z)
-
-rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
-KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
 KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
@@
 
+SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"))
+
 ```
@@
 ##Function to plot all G85R groups
+plot.G85R = function(ID){
+ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
+                     grep(ID, GeneIDKey$Symbol)),]
 
-plot.G85R = function(ID){
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
+if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
 if(nrow(ID.row) == 1){
@@
 }
+}
 
-```
+##Function to plot a specific gene expression levels in all A4V groups
+plot.A4V = function(ID){
+ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
+                     grep(ID, GeneIDKey$Symbol)),]
 
-```{r echo = F}
-##Function to plot a specific gene expression levels in all A4V groups
-
-plot.A4V = function(ID){
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
+if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
 if(nrow(ID.row) == 1){
@@
 }
+}
 
-```
-
-```{r echo = F}
 ##Plot levels of a specific metabolite
-
 plot.metab = function(metabID){
 
-ID.row = row.names(norm.data)[grep(ID, row.names(norm.data))]
+ID.row = grep(metabID, row.names(norm.data))
 
+if(length(ID.row) < 50 & length(ID.row) > 0){
 if(length(ID.row) == 1){
-metab = ID.row
-name = ID.row
+metab = row.names(norm.data)[ID.row]
+name = row.names(norm.data)[ID.row]
 
@@
 
-rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
+rect(0, 0-(1.5*max(na.omit(metab$data))), 13, 1.5*max(na.omit(metab$data)), col = 'gray95')
 
@@
 }
+}
+
+##Function to plot a specific gene expression levels in all cell types for the SCdata
+plot.SC = function(gene.name){
+ID.row = SCdata[grep(gene.name, SCdata$Gene.name),]
+
+if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
+if(nrow(ID.row) == 1){
+
+  gene.name = ID.row$Gene.name
+  gene.levels = setNames(as.numeric(ID.row[,colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
+  gene.levels = gene.levels[18:1]
+  highlight = rep(0, 18)
+  highlight[(gene.levels > 2*(mean(gene.levels)))] = 1
+  highlight = gene.levels * highlight
+
+  nochange = gene.levels
+  nochange[gene.levels > 1.5] = 0
+  nochange = gene.levels * nochange
+
+  label.colors = highlight
+
+  label.colors[label.colors > 0] = "deeppink"
+  label.colors[label.colors == 0] = "black"
+  label.colors[nochange > 0] = 'steelblue'
+
+  if(1.25*(max(gene.levels)) < 5){
+    xmax = 5
+  }
+
+  if(1.25*(max(gene.levels)) >= 5){
+    xmax = 1.25*(max(gene.levels))
+  }
+
+  par(mar=c(5, 12, 4, 6), xpd=TRUE)
+
+  plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(.95, 21),
+     xlim = c(0, xmax),
+     xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = "Mean UMI Counts",
+     bty = "n",
+     main = gene.name)
+
+  barplot(height = gene.levels, 
+          horiz = T, 
+          #las = 2,
+          xlim = c(0, xmax),
+          names.arg = NA,
+          border = T,
+          add = T)
+
+    barplot(height = highlight, 
+          horiz = T, 
+          #las = 2, 
+          names.arg = NA,
+          border = T,
+          col = "deeppink",
+          add = T)
+
+    barplot(height = nochange, 
+          horiz = T, 
+          #las = 2, 
+          names.arg = NA,
+          border = T,
+          col = "lightsteelblue",
+          add = T)
+
+  mtext(side = 2,
+        las = 2,
+        at = .7+(1.2*(0:17)),
+        text = names(gene.levels),
+        col = label.colors,
+        line = 0)
+
+  abline(v = 1,
+         lty = 2,
+         lwd = 2,
+         xpd = F)
+
+  legend(x = .9*xmax,
+         y = 23,
+         legend = c("high", "mid", "low"),
+         fill = c("deeppink", "grey", "lightsteelblue"),
+         bty = "n",
+         xpd = T)
+
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+}
+}
 
@@
 
-ID = "0000018"
+## Plot gene expression from G85R TKT RNAseq experiment
+## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
+
+ID = "Arc1"
+
 plot.G85R(ID)
@@
 ```{r echo = F}
-##Tailared code to plot a specific gene expression levels in all A4V groups
 
-ID = "0000018"
+## Plot gene expression from A4V RNAseq experiment
+## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
+
+ID = "Arc1"
 
@@
 
-metabID = 'NADP'
+## Plot metabolite levels from the G85R TKT metabolomics experiment
+## metabID needs to be the full or partial metabolite name as listed in the table (case sensitive)
+
+metabID = 'NADH'
 
@@
 ```{r echo = F}
-##Tailared code to plot a subset of groups in the TKT dataset
+
+## Plot gene expression from Single Cell RNAseq experiment
+## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)
+
+gene.name = 'gbb'
+
+plot.SC(gene.name)
+
+```
+
+```{r echo = F}
+## Plot a subset of groups in the TKT dataset
 
@@
 
+if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
 if(nrow(ID.row) == 1){
@@
 }
+}
 
@@
 ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
 
@@
 }
+}
+
 ```

### 2025-01-14 Shortcuts_OmicsQuickPlotFunctions.Rmd
finalized omics functions

--- 2025-01-13 OmicsQuickPlotFunctions.Rmd
@@
 
-rawdata = read.csv(paste0(git.dir, "MetabolomicsForMetaboanalyst.txt"), sep = "\t", row.names = 1)
+Metab.data = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
+Metab.Meta = read.csv(paste0(git.dir, "MetabolomicMetadata.csv"), row.names = 1)
 
-KEGG.Key = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
-
-KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
-
-genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))
-
-metadata = data.frame(Sample = colnames(rawdata), 
-                      Group = as.character(rawdata[1,]), 
-                      TIC = as.numeric(rawdata[2,]), 
-                      Genotypes = genotypes[as.character(rawdata[1,])])
-
-row.names(metadata) = metadata$Sample
+KEGG.Key = setNames(Metab.data[-c(1:2), 2], row.names(Metab.data)[-c(1:2)])
 
 norm.func = function(data){
-  nd = (as.numeric(data)/metadata$TIC)*1000
+  nd = (as.numeric(data)/Metab.Meta$TIC)*1000
   return(nd)
@@
 
-norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
-colnames(norm.data) = colnames(rawdata)
+norm.data = t(apply(Metab.data[3:nrow(Metab.data),3:ncol(Metab.data)], 1, norm.func))
 
-group.mean=function(data){
-  gm = mean(na.omit(data))
-}
-
-mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
-row.names(mean.data) = row.names(norm.data)
-colnames(mean.data) = unique(metadata$Group)
-
-i=1
-while(i<=ncol(mean.data)){
-  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
-  i = i+1
-}
-
-mean.metab = mean.data
-
-compare.conditions = function(condition1, condition2){
-  columns1 = metadata[metadata$Group == condition1, "Sample"]
-  columns2 = metadata[metadata$Group == condition2, "Sample"]
-  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
-  i=1
-  while(i<=length(p)){
-    if(length(na.omit(norm.data[i,columns1]))>2 & 
-       length(na.omit(norm.data[i,columns2]))>2){
-      temp = t.test(na.omit(norm.data[i,columns1]),
-                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
-      p[i] = temp[[3]]
-      }
-    i=i+1
-    }
-
-  fdr = p.adjust(p, "BH", length(p))
-
-  fc = mean.metab[,condition1]/mean.metab[,condition2]
-
-  comparison.table = data.frame(p = p, 
-                                FDR = fdr, 
-                                FC = fc, 
-                                KEGG = KEGG.Key[row.names(mean.metab)])
-
-  comparison.table = comparison.table[order(comparison.table$FDR),]
-}
-
-GRxWT.C = compare.conditions("E", "C")
-GRxWT.Df = compare.conditions("D", "B")[row.names(GRxWT.C),]
-GRxWT.OE = compare.conditions("F", "A")[row.names(GRxWT.C),]
-
-GR.CxDf = compare.conditions("D", "E")[row.names(GRxWT.C),]
-WT.CxDf = compare.conditions("B", "C")[row.names(GRxWT.C),]
-
-GR.CxOE = compare.conditions("F", "E")[row.names(GRxWT.C),]
-WT.CxOE = compare.conditions("A", "C")[row.names(GRxWT.C),]
-
-GR.DfxWT.C = compare.conditions("D", "C")[row.names(GRxWT.C),]
-GR.OExWT.C = compare.conditions("F", "C")[row.names(GRxWT.C),]
-
-comparison.means = list(GRF.CxDf = c("TktDfGR.F","GR.F"), 
-                 GRF.CxOE = c("TktOEGR.F","GR.F"),
-                 WTF.CxDf = c("TktDfWT.F","WT.F"),
-                 WTF.CxOE = c("TktOEWT.F","WT.F"),
-                 GRxWT.FC = c("GR.F","WT.F"), 
-                 GRxWT.FDf = c("TktDfGR.F","TktDfWT.F"),
-                 GRxWT.FOE = c("TktOEGR.F","TktOEWT.F"), 
-                 GRM.CxDf = c("TktDfGR.M","GR.M"), 
-                 GRM.CxOE = c("TktOEGR.M","GR.M"),
-                 WTM.CxDf = c("TktDfWT.M","WT.M"),
-                 WTM.CxOE = c("TktOEWT.M","WT.M"),
-                 GRxWT.MC = c("GR.M","WT.M"), 
-                 GRxWT.MDf = c("TktDfGR.M","TktDfWT.M"),
-                 GRxWT.MOE = c("TktOEGR.M","TktOEWT.M"),
-                 GR.FxM = c("GR.F","GR.M"),
-                 WT.FxM = c("WT.F","WT.M"))
-
-metab.FC = data.frame('GRxWT.C' = GRxWT.C$FC,
-                      'GRxWT.Df' = GRxWT.Df$FC,
-                      'GRxWT.OE' = GRxWT.OE$FC,
-                      'GR.CxDf' = GR.CxDf$FC,
-                      'WT.CxDf' = WT.CxDf$FC,
-                      'GR.CxOE' = GR.CxOE$FC,
-                      'WT.CxOE' = WT.CxOE$FC,
-                      'GR.DfxWT.C' = GR.DfxWT.C$FC,
-                      'GR.OExWT.C' = GR.OExWT.C$FC)
-row.names(metab.FC) = row.names(GRxWT.C)
-metab.FC = log2(metab.FC)
-
-metab.FDR = data.frame(GRxWT.C = GRxWT.C$p,
-                       GRxWT.Df = GRxWT.Df$p,
-                       GRxWT.OE = GRxWT.OE$p,
-                       GR.CxDf = GR.CxDf$p,
-                       WT.CxDf = WT.CxDf$p,
-                       GR.CxOE = GR.CxOE$p,
-                       WT.CxOE = WT.CxOE$p,
-                       GR.DfxWT.C = GR.DfxWT.C$p,
-                       GR.OExWT.C = GR.OExWT.C$p)
-row.names(metab.FDR) = row.names(GRxWT.C)
-
-colnames(mean.metab) = as.character(genotypes[colnames(mean.metab)])
-
-colnames(norm.data) = as.character(genotypes[substr(colnames(norm.data),1,1)])
+colnames(norm.data) = colnames(Metab.data)[3:ncol(Metab.data)]
+colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
 
@@
                      grep(ID, GeneIDKey$Symbol)),]
+ID.row = na.omit(ID.row)
 
 if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
+if(nrow(ID.row) == 1
+   | length(intersect(GeneIDKey$FBgn, ID)) == 1
+   | length(intersect(GeneIDKey$Symbol, ID)) == 1){
   if(nrow(ID.row) == 1){
@@
     name = ID.row$Symbol
+  }
+  if(length(intersect(GeneIDKey$FBgn, ID)) == 1){
+    FBgn = ID.row$FBgn[ID.row$FBgn == ID]
+    name = ID.row$Symbol[ID.row$FBgn == ID]
+  }
+  if(length(intersect(GeneIDKey$Symbol, ID)) == 1){
+    FBgn = ID.row$FBgn[ID.row$Symbol == ID]
+    name = ID.row$Symbol[ID.row$Symbol == ID]
+  }
 
@@
 
+if(nrow(na.omit(gene)) > 0){
 par(mar = c(5,7,5,2))
@@
 }
+}
+}
 
-if(nrow(ID.row) != 1){
+if(nrow(ID.row) != 1
+   | length(intersect(GeneIDKey$FBgn, ID)) > 1
+   | length(intersect(GeneIDKey$Symbol, ID)) > 1){
   ID.row
-}
 }
@@
     name = ID.row$Symbol
+  }
+  if(length(intersect(GeneIDKey$FBgn, ID)) == 1){
+    FBgn = ID.row$FBgn[ID.row$FBgn == ID]
+    name = ID.row$Symbol[ID.row$FBgn == ID]
+  }
+  if(length(intersect(GeneIDKey$Symbol, ID)) == 1){
+    FBgn = ID.row$FBgn[ID.row$Symbol == ID]
+    name = ID.row$Symbol[ID.row$Symbol == ID]
+  }
   A4V.groups = as.vector(colnames(A4V.cpm))
@@
 
+  if(nrow(na.omit(A4V.cpm[FBgn,]))){
   par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
@@
 
-  gene$condition = factor(gene$condition, levels = c("A3FH", "A9FH", "A40FH",
-                                                   "S3FH", "S9FH", "S40FH",
+  gene$condition = factor(gene$condition, levels = c("S3FH", "S9FH", "S40FH",
+                                                     "S3FT", "S9FT", "S40FT",
+                                                     "S3FA", "S9FA", "S40FA",
+                                                     "A3FH", "A9FH", "A40FH",
                                                      "A3FT", "A9FT", "A40FT",
-                                                   "S3FT", "S9FT", "S40FT",
                                                      "A3FA", "A9FA", "A40FA",
-                                                   "S3FA", "S9FA", "S40FA",
-                                                   "A3MH", "A9MH",
                                                      "S3MH", "S9MH",
                                                      "A3MT", "A9MT",
+                                                     "A3MA", "A9MA",
+                                                     "A3MH", "A9MH",
                                                      "S3MT", "S9MT",
-                                                   "A3MA", "A9MA",
                                                      "S3MA", "S9MA"))
-  gene$group = factor(gene$group, levels = c(unique(gene$group)))
+  gene$group = factor(gene$group, levels = c("SF", "AF", "SM", "AM"))
 
@@
        inset=c(-0.275,0),
-       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
+       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent M'), 
        fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
@@
   }
+}
 
-if(nrow(ID.row) != 1){
+if(nrow(ID.row) != 1
+   | length(intersect(GeneIDKey$FBgn, ID)) > 1
+   | length(intersect(GeneIDKey$Symbol, ID)) > 1){
   ID.row
@@
 if(length(ID.row) < 50 & length(ID.row) > 0){
+if(length(ID.row) == 1 | length(intersect(row.names(norm.data), metabID)) == 1){
+
   if(length(ID.row) == 1){
@@
     name = row.names(norm.data)[ID.row]
+  }
+
+  if(length(intersect(row.names(norm.data), metabID)) == 1){
+    metab = metabID
+    name = metabID
+  }
 
@@
 
-if(length(ID.row) != 1){
-  ID.row
+if(length(ID.row) != 1 | length(intersect(row.names(norm.data), metabID)) > 1){
+  norm.data[ID.row,]
 }
@@
 
-##Function to plot a specific gene expression levels in all cell types for the SCdata
+##Function to plot a specific gene expression levels in all cell types for the SC data
 plot.SC = function(gene.name){
@@
 if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
+if(nrow(ID.row) == 1 | length(intersect(gene.name, SCdata$Gene.name)) == 1){
+
+  if(length(intersect(gene.name, SCdata$Gene.name)) == 1){
+    gene.levels = setNames(as.numeric(ID.row[ID.row$Gene.name == gene.name, colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
+  }
+
   if(nrow(ID.row) == 1){
-
     gene.name = ID.row$Gene.name
     gene.levels = setNames(as.numeric(ID.row[,colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
+  }
+
   gene.levels = gene.levels[18:1]
@@
 
-if(nrow(ID.row) != 1){
+if(nrow(ID.row) != 1 | length(intersect(gene.name, SCdata$Gene.name)) > 1){
   ID.row
@@
 
-```
-
-```{r echo = F}
-
-## Plot gene expression from G85R TKT RNAseq experiment
-## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
-
-ID = "Arc1"
-
-plot.G85R(ID)
-
-```
-
-```{r echo = F}
-
-## Plot gene expression from A4V RNAseq experiment
-## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
-
-ID = "Arc1"
-
-plot.A4V(ID)
-```
-
-```{r echo = F}
-
-## Plot metabolite levels from the G85R TKT metabolomics experiment
-## metabID needs to be the full or partial metabolite name as listed in the table (case sensitive)
-
-metabID = 'NADH'
-
-plot.metab(metabID)
-
-```
-
-```{r echo = F}
-
-## Plot gene expression from Single Cell RNAseq experiment
-## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)
-
-gene.name = 'gbb'
-
-plot.SC(gene.name)
-
-```
-
-```{r echo = F}
-## Plot a subset of groups in the TKT dataset
-
-##ID = "0000018"
-
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
-if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
-if(nrow(ID.row) == 1){
-FBgn = ID.row$FBgn
-name = ID.row$Symbol
-
-gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), 
-                  condition = TKT.groups$Group, 
-                  group = paste0(TKT.groups$Genotype, TKT.groups$Sex),
-                  TKT = TKT.groups$TKT)
-
-gene = gene[gene$TKT != 'OE',]
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F",
-                                                 'WT.F', "TktDfWT.F",
-                                                 'GR.M', "TktDfGR.M",
-                                                 'WT.M', "TktDfWT.M"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-
-}
-
-if(nrow(ID.row) != 1){
-  ID.row
-}
-}
-
-```
-
-```{r echo = F}
-##Plot expression levels for a specific gene in the gbbOE dataset
-
-##ID = "0000018"
+##Function to plot a specific gene expression levels in the gbbOE transcriptomic data set
+plot.gbbOE = function(ID){
 
@@
 }
+}
 
-```
-
-```{r echo = F}
-##Plot expression levels for a specific gene in the gbb-null dataset
-
-## WT = W1118
-## KO = GBB1/GBB2 (both null alleles)
-## Aaron and Catherine legend for RNAseq
-## Whole larvae
-
-##ID = "0000018"
-
+##Function to plot a specific gene expression levels in the gbbKO transcriptomic data set
+plot.gbbKO = function(ID){
 ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
@@
 }
+}
 
 ```
+
+```{r echo = F}
+
+## Plot gene expression from G85R TKT RNAseq experiment
+## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
+
+ID = "ETH"
+
+plot.G85R(ID)
+
+```
+
+```{r echo = F}
+
+## Plot gene expression from A4V RNAseq experiment
+## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
+
+ID = "ETH"
+
+plot.A4V(ID)
+```
+
+```{r echo = F}
+
+## Plot metabolite levels from the G85R TKT metabolomics experiment
+## metabID needs to be the full or partial metabolite name as listed in the table (case sensitive)
+
+metabID = 'NAD'
+
+plot.metab(metabID)
+
+```
+
+```{r echo = F}
+
+## Plot gene expression from Single Cell RNAseq experiment
+## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)
+
+gene.name = 'CCAP'
+
+plot.SC(gene.name)
+
+```
+
+```{r echo = F}
+##Plot expression levels for a specific gene in the gbbOE dataset
+
+##ID = "0000018"
+
+plot.gbbOE(ID)
+
+```
+
+```{r echo = F}
+##Plot expression levels for a specific gene in the gbb-null dataset
+
+## WT = W1118
+## KO = GBB1/GBB2 (both null alleles)
+## Aaron and Catherine legend for RNAseq
+## Whole larvae
+
+##ID = "0000018"
+
+plot.gbbKO(ID)
+
+```

### 2025-01-14 Functions_OmicsQuickPlotFunctions.R

@@ -1,0 +1,516 @@
+
+##Load Libraries and Data
+
+##library(plotly)
+library(edgeR)
+
+##load all files from github
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
+
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
+
+TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)
+
+TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)
+
+TKT.groups = TKT.groups[colnames(TKT.cpm),]
+
+
+A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
+
+
+
+gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
+
+gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
+
+gbbOE = gbbOE[,row.names(gbbOE.groups)]
+gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
+
+
+Metab.data = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
+Metab.Meta = read.csv(paste0(git.dir, "MetabolomicMetadata.csv"), row.names = 1)
+
+KEGG.Key = setNames(Metab.data[-c(1:2), 2], row.names(Metab.data)[-c(1:2)])
+
+norm.func = function(data){
+  nd = (as.numeric(data)/Metab.Meta$TIC)*1000
+  return(nd)
+}
+
+norm.data = t(apply(Metab.data[3:nrow(Metab.data),3:ncol(Metab.data)], 1, norm.func))
+
+colnames(norm.data) = colnames(Metab.data)[3:ncol(Metab.data)]
+colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
+
+
+SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"))
+
+##Function to plot all G85R groups
+plot.G85R = function(ID){
+  ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
[…]

### 2025-01-14 Shortcuts_OmicsQuickPlotFunctions.Rmd
updated final

@@
 ```{r include = F, echo = F}
-##Load Libraries and Data
-
-##library(plotly)
-library(edgeR)
-
-##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
-
-GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
-
-TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)
-
-TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)
-
-TKT.groups = TKT.groups[colnames(TKT.cpm),]
-
-A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
-
-gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
-
-gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
-
-gbbOE = gbbOE[,row.names(gbbOE.groups)]
-gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
-
-Metab.data = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
-Metab.Meta = read.csv(paste0(git.dir, "MetabolomicMetadata.csv"), row.names = 1)
-
-KEGG.Key = setNames(Metab.data[-c(1:2), 2], row.names(Metab.data)[-c(1:2)])
-
-norm.func = function(data){
-  nd = (as.numeric(data)/Metab.Meta$TIC)*1000
-  return(nd)
-}
-
-norm.data = t(apply(Metab.data[3:nrow(Metab.data),3:ncol(Metab.data)], 1, norm.func))
-
-colnames(norm.data) = colnames(Metab.data)[3:ncol(Metab.data)]
-colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
-
-SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"))
-
-```
-
-```{r echo = F}
-##Function to plot all G85R groups
-plot.G85R = function(ID){
-ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
-                     grep(ID, GeneIDKey$Symbol)),]
-ID.row = na.omit(ID.row)
-
-if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
-if(nrow(ID.row) == 1
-   | length(intersect(GeneIDKey$FBgn, ID)) == 1
-   | length(intersect(GeneIDKey$Symbol, ID)) == 1){
-  if(nrow(ID.row) == 1){
-    FBgn = ID.row$FBgn
-    name = ID.row$Symbol
-  }
-  if(length(intersect(GeneIDKey$FBgn, ID)) == 1){
-    FBgn = ID.row$FBgn[ID.row$FBgn == ID]
-    name = ID.row$Symbol[ID.row$FBgn == ID]
-  }
-  if(length(intersect(GeneIDKey$Symbol, ID)) == 1){
-    FBgn = ID.row$FBgn[ID.row$Symbol == ID]
-    name = ID.row$Symbol[ID.row$Symbol == ID]
-  }
-
-gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), condition = TKT.groups$Group, group = paste0(TKT.groups$Genotype, TKT.groups$Sex))
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
-                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
-                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
-                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))
-
-if(nrow(na.omit(gene)) > 0){
-par(mar = c(5,7,5,2))
-plot(x = NA,
-      y = NA,
-     type = 'n',
-     ylim = c(min(gene$cpm), max(gene$cpm)),
-     xlim = c(.5, 12.5),
-     xaxt = "n",
-     ylab="",
-     yaxt = "n",
-     xlab = NA)
-
-rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')
-
-boxplot(gene$cpm~gene$condition, 
-        xlab="",
-        las = 2, 
-        cex.axis = .8,
-        xaxt = 'none',
-        yaxt = 'none',
-        boxwex = .75,
-        boxlwd = 2,
-        lwd = 2,
-        cex.ticks = 2,
-        add = T,
-        col = c(rep("honeydew", 3),
-                rep("thistle1", 3),
-                rep("lightcyan", 3),
-                rep("lightyellow", 3)))
-
-box(lwd = 2)
-
-points(x=as.numeric(factor(gene$condition)),
-       y=gene$cpm,
-       cex=1,
-       pch=21,
-       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-
-axis(side = 1,
-     at = 1:12,
-     labels = rep(c("Control", "Df", "OE"), 4),
-     line = 0,
-     cex.axis = .75,
-     lwd.ticks = 2)
-
-axis(side = 2,
-     line = 0,
-     cex.axis = 1,
-     lwd.ticks = 2,
-     las = 2)
-
-axis(side = 2,
-     at = .5*(max(gene$cpm) + min(gene$cpm)),
-     label = "Counts per million reads",
-     tick = F,
-     padj = -3,
-     cex.axis = 1.25)
-
-axis(side = 1,
-     at = c(2, 5, 8, 11),
-     labels = c("Silent", "G85R","Silent", "G85R"),
-     tick = F,
-     padj = 2,
-     cex.axis = 1)
-axis(side = 3,
-     at = c(3.5, 9.5),
-     labels = c("Female", "Male"),
-     tick = F,
-     padj = .5,
-     cex.axis = 1.5)
-
-axis(side = 3,
-     at = 6.5,
-     labels = name,
-     tick = F,
-     padj = -1.5,
-     cex.axis = 2)
-
-axis(side = 3,
-     at = c(3.5,9.5),
-     tick = T,
-     outer = T,
-     labels = F,
-     line = -2.25,
-     lwd.ticks = 0)
-
-xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
-xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
-lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
-abline(v = 6.5, lty = 2, lwd = 2)
-}
-}
-}
-
-if(nrow(ID.row) != 1
-   | length(intersect(GeneIDKey$FBgn, ID)) > 1
-   | length(intersect(GeneIDKey$Symbol, ID)) > 1){
-  ID.row
-}
-}
-
-##Function to plot a specific gene expression levels in all A4V groups
-plot.A4V = function(ID){
-ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
-                     grep(ID, GeneIDKey$Symbol)),]
-ID.row = na.omit(ID.row)
-
-if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
-if(nrow(ID.row) == 1
-   | length(intersect(GeneIDKey$FBgn, ID)) == 1
-   | length(intersect(GeneIDKey$Symbol, ID)) == 1){
-  if(nrow(ID.row) == 1){
-    FBgn = ID.row$FBgn
-    name = ID.row$Symbol
-  }
-  if(length(intersect(GeneIDKey$FBgn, ID)) == 1){
-    FBgn = ID.row$FBgn[ID.row$FBgn == ID]
-    name = ID.row$Symbol[ID.row$FBgn == ID]
-  }
-  if(length(intersect(GeneIDKey$Symbol, ID)) == 1){
-    FBgn = ID.row$FBgn[ID.row$Symbol == ID]
-    name = ID.row$Symbol[ID.row$Symbol == ID]
-  }
-  A4V.groups = as.vector(colnames(A4V.cpm))
-
-  A4V.groups = substr(A4V.groups,1, nchar(A4V.groups)-1)
-
-  if(nrow(na.omit(A4V.cpm[FBgn,]))){
-  par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
-  gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]),
-                    condition = A4V.groups,
-                    group = paste0(substr(A4V.groups, 1,1), substr(A4V.groups, start = nchar(as.vector(A4V.groups))-1,nchar(as.vector(A4V.groups))-1)))
-
-  gene$condition = factor(gene$condition, levels = c("S3FH", "S9FH", "S40FH",
-                                                     "S3FT", "S9FT", "S40FT",
-                                                     "S3FA", "S9FA", "S40FA",
-                                                     "A3FH", "A9FH", "A40FH",
-                                                     "A3FT", "A9FT", "A40FT",
-                                                     "A3FA", "A9FA", "A40FA",
-                                                     "S3MH", "S9MH",
-                                                     "A3MT", "A9MT",
-                                                     "A3MA", "A9MA",
-                                                     "A3MH", "A9MH",
-                                                     "S3MT", "S9MT",
-                                                     "S3MA", "S9MA"))
-  gene$group = factor(gene$group, levels = c("SF", "AF", "SM", "AM"))
-
-  boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-  points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
-  legend('topright',
-       inset=c(-0.275,0),
-       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent M'), 
-       fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
-       cex = .65,
-       bty = 'n',
-       pt.cex = .5)
-  }
-}
-
-if(nrow(ID.row) != 1
-   | length(intersect(GeneIDKey$FBgn, ID)) > 1
-   | length(intersect(GeneIDKey$Symbol, ID)) > 1){
-  ID.row
-}
-}
-}
-
-##Plot levels of a specific metabolite
-plot.metab = function(metabID){
-
-ID.row = grep(metabID, row.names(norm.data))
-
-if(length(ID.row) < 50 & length(ID.row) > 0){
-if(length(ID.row) == 1 | length(intersect(row.names(norm.data), metabID)) == 1){
-
-  if(length(ID.row) == 1){
-    metab = row.names(norm.data)[ID.row]
-    name = row.names(norm.data)[ID.row]
-  }
-
-  if(length(intersect(row.names(norm.data), metabID)) == 1){
-    metab = metabID
-    name = metabID
-  }
-
-metab = data.frame(data = as.numeric(norm.data[metab,]), 
-                   group = colnames(norm.data), 
-                   geno = colnames(norm.data))
-
-metab$group = factor(metab$group, levels = c("WT", "TktDfWT", "TktOEWT",
-                                             "GR", "TktDfGR", "TktOEGR"))
-
-metab$geno = factor(substr(metab$group, (nchar(as.character(metab$group)) -1), nchar(as.character(metab$group))), 
-                     levels = c("WT", "GR"))
-
-par(mar = c(5,7,5,2))
-plot(x = NA,
-      y = NA,
-     type = 'n',
-     ylim = c(min(na.omit(metab$data)), max(na.omit(metab$data))),
-     xlim = c(.5, 6.5),
-     xaxt = "n",
-     ylab="",
-     yaxt = "n",
-     xlab = NA)
-
-rect(0, 0-(1.5*max(na.omit(metab$data))), 13, 1.5*max(na.omit(metab$data)), col = 'gray95')
-
-boxplot(metab$data~metab$group, 
-        xlab="",
-        las = 2, 
-        cex.axis = .8,
-        xaxt = 'none',
-        yaxt = 'none',
-        boxwex = .75,
-        boxlwd = 2,
-        lwd = 2,
-        cex.ticks = 2,
-        add = T,
-        col = c(rep("lightyellow", 3),
-                rep("lightgreen", 3)))
-
-box(lwd = 2)
-
-points(x=as.numeric(factor(metab$group)),
-       y=metab$data,
-       cex=1.25,
-       pch=21,
-       bg=c('gold3',"darkgreen")[as.numeric(factor(metab$geno))])
-
-axis(side = 1,
-     at = 1:12,
-     labels = rep(c("Control", "Df", "OE"), 4),
-     line = 0,
-     cex.axis = .75,
-     lwd.ticks = 2)
-
-axis(side = 2,
-     line = 0,
-     cex.axis = 1,
-     lwd.ticks = 2,
-     las = 2)
-
-axis(side = 1,
-     at = c(2, 5, 8, 11),
-     labels = c("Silent", "G85R","Silent", "G85R"),
-     tick = F,
-     padj = 2,
-     cex.axis = 1)
-
-axis(side = 3,
-     at = 3.5,
-     labels = name,
-     tick = F,
-     padj = -.5,
-     cex.axis = 2)
-
-}
-
-if(length(ID.row) != 1 | length(intersect(row.names(norm.data), metabID)) > 1){
-  norm.data[ID.row,]
-}
-
-}
-}
-
-##Function to plot a specific gene expression levels in all cell types for the SC data
-plot.SC = function(gene.name){
-ID.row = SCdata[grep(gene.name, SCdata$Gene.name),]
-
-if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
-if(nrow(ID.row) == 1 | length(intersect(gene.name, SCdata$Gene.name)) == 1){
-
-  if(length(intersect(gene.name, SCdata$Gene.name)) == 1){
-    gene.levels = setNames(as.numeric(ID.row[ID.row$Gene.name == gene.name, colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
-  }
-
-  if(nrow(ID.row) == 1){
-    gene.name = ID.row$Gene.name
-    gene.levels = setNames(as.numeric(ID.row[,colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
-  }
-
-  gene.levels = gene.levels[18:1]
-  highlight = rep(0, 18)
-  highlight[(gene.levels > 2*(mean(gene.levels)))] = 1
-  highlight = gene.levels * highlight
-
-  nochange = gene.levels
-  nochange[gene.levels > 1.5] = 0
-  nochange = gene.levels * nochange
-
-  label.colors = highlight
-
-  label.colors[label.colors > 0] = "deeppink"
-  label.colors[label.colors == 0] = "black"
-  label.colors[nochange > 0] = 'steelblue'
-
-  if(1.25*(max(gene.levels)) < 5){
-    xmax = 5
-  }
-
-  if(1.25*(max(gene.levels)) >= 5){
-    xmax = 1.25*(max(gene.levels))
-  }
-
-  par(mar=c(5, 12, 4, 6), xpd=TRUE)
-
-  plot(x = NA,
-      y = NA,
-     type = 'n',
-     ylim = c(.95, 21),
-     xlim = c(0, xmax),
-     xaxt = "n",
-     ylab="",
-     yaxt = "n",
-     xlab = "Mean UMI Counts",
-     bty = "n",
-     main = gene.name)
-
-  barplot(height = gene.levels, 
-          horiz = T, 
-          #las = 2,
-          xlim = c(0, xmax),
-          names.arg = NA,
-          border = T,
-          add = T)
-
-    barplot(height = highlight, 
-          horiz = T, 
-          #las = 2, 
-          names.arg = NA,
-          border = T,
-          col = "deeppink",
-          add = T)
-
-    barplot(height = nochange, 
-          horiz = T, 
-          #las = 2, 
-          names.arg = NA,
-          border = T,
-          col = "lightsteelblue",
-          add = T)
-
-  mtext(side = 2,
-        las = 2,
-        at = .7+(1.2*(0:17)),
-        text = names(gene.levels),
-        col = label.colors,
-        line = 0)
-
-  abline(v = 1,
-         lty = 2,
-         lwd = 2,
-         xpd = F)
-
-  legend(x = .9*xmax,
-         y = 23,
-         legend = c("high", "mid", "low"),
-         fill = c("deeppink", "grey", "lightsteelblue"),
-         bty = "n",
-         xpd = T)
-
-}
-
-if(nrow(ID.row) != 1 | length(intersect(gene.name, SCdata$Gene.name)) > 1){
-  ID.row
-}
-}
-}
-
-##Function to plot a specific gene expression levels in the gbbOE transcriptomic data set
-plot.gbbOE = function(ID){
-
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
-if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
-
-if(nrow(ID.row) == 1){
-FBgn = ID.row$FBgn
-name = ID.row$Symbol
-
-gene = data.frame(cpm = as.numeric(gbbOE.cpmdata[FBgn,]), condition = gbbOE.groups$group, group = gbbOE.groups$genotype)
-
-gene$group = factor(gene$group, levels = c(unique(gene$group)))
-gene$condition = factor(gene$condition, levels = c('LoxP_ML3', "LoxP_LL3",
-                                                 'G85R_ML3', "G85R_LL3",
-                                                 'G85R_gbb_ML3', "G85R_gbb_LL3"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
-
-}
-
-if(nrow(ID.row) != 1){
-  ID.row
-}
-}
-}
-
-##Function to plot a specific gene expression levels in the gbbKO transcriptomic data set
-plot.gbbKO = function(ID){
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
-if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
-if(nrow(ID.row) == 1){
-FBgn = ID.row$FBgn
-name = ID.row$Symbol
-
-gene = data.frame(cpm = as.numeric(gbbKO.cpmdata[FBgn,]), condition = gbbKO.groups$Genotype)
-
-gene$condition = factor(gene$condition, levels = c('WT', "KO"))
-
-boxplot(gene$cpm~gene$condition, xlab="",     
-        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
-points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"dodgerblue","gold")[as.numeric(factor(gene$condition))])
-
-}
-
-if(nrow(ID.row) != 1){
-  ID.row
-}
-}
-}
+source('https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/Functions_OmicsQuickPlotFunctions.R')
 
@@
 
-ID = "ETH"
+ID = "ETHR"
 
@@
 
-ID = "ETH"
+ID = "Arc1"
 
@@
 
-metabID = 'NAD'
+metabID = 'NADH'
 

### 2025-01-14 Functions_OmicsQuickPlotFunctions.R

@@ -50,7 +50,6 @@ SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv")
 plot.G85R = function(ID){
   ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
                        grep(ID, GeneIDKey$Symbol)),]
-  ID.row = na.omit(ID.row)
   
   if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
     if(nrow(ID.row) == 1
@@ -187,7 +186,6 @@ plot.G85R = function(ID){
 plot.A4V = function(ID){
   ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
                        grep(ID, GeneIDKey$Symbol)),]
-  ID.row = na.omit(ID.row)
   
   if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
     if(nrow(ID.row) == 1
@@ -463,12 +461,25 @@ plot.SC = function(gene.name){
 plot.gbbOE = function(ID){
   
   ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+  ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
+                       grep(ID, GeneIDKey$Symbol)),]
   
-  if(nrow(ID.row) < 500 & nrow(ID.row) > 0){
-    
-    if(nrow(ID.row) == 1){
-      FBgn = ID.row$FBgn
-      name = ID.row$Symbol
+  if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
+    if(nrow(ID.row) == 1
+       | length(intersect(GeneIDKey$FBgn, ID)) == 1
+       | length(intersect(GeneIDKey$Symbol, ID)) == 1){
+      if(nrow(ID.row) == 1){
+        FBgn = ID.row$FBgn
+        name = ID.row$Symbol
+      }
+      if(length(intersect(GeneIDKey$FBgn, ID)) == 1){
+        FBgn = ID.row$FBgn[ID.row$FBgn == ID]
+        name = ID.row$Symbol[ID.row$FBgn == ID]
+      }
+      if(length(intersect(GeneIDKey$Symbol, ID)) == 1){
+        FBgn = ID.row$FBgn[ID.row$Symbol == ID]
+        name = ID.row$Symbol[ID.row$Symbol == ID]
+      }
       
[…]

### 2025-01-14 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -27,6 +27,9 @@ gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
 gbbOE = gbbOE[,row.names(gbbOE.groups)]
 gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
 
+gbbKO.cpm = read.csv(paste0(git.dir, "gbbKO.cpmdata.csv"), row.names = 1)
+gbbKO.groups = read.csv(paste0(git.dir, "gbbKO_Metadata.csv"), row.names = 1)
+
 
 Metab.data = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
 Metab.Meta = read.csv(paste0(git.dir, "MetabolomicMetadata.csv"), row.names = 1)

### 2025-01-14 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -27,7 +27,7 @@ gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
 gbbOE = gbbOE[,row.names(gbbOE.groups)]
 gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
 
-gbbKO.cpm = read.csv(paste0(git.dir, "gbbKO.cpmdata.csv"), row.names = 1)
+gbbKO.cpmdata = read.csv(paste0(git.dir, "gbbKO.cpmdata.csv"), row.names = 1)
 gbbKO.groups = read.csv(paste0(git.dir, "gbbKO_Metadata.csv"), row.names = 1)
 
 

### 2025-01-14 Functions_OmicsQuickPlotFunctions.R
no edger

@@ -2,7 +2,6 @@
 ##Load Libraries and Data
 
 ##library(plotly)
-library(edgeR)
 
 ##load all files from github
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"

### 2025-01-15 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -74,7 +74,7 @@ plot.G85R = function(ID){
       
       gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), condition = TKT.groups$Group, group = paste0(TKT.groups$Genotype, TKT.groups$Sex))
       
-      gene$group = factor(gene$group, levels = c(unique(gene$group)))
+      gene$group = factor(gene$group, levels = c("WT.f", "GR.F", "WT.M", "GR.M"))
       gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                          'GR.F', "TktDfGR.F", "TktOEGR.F",
                                                          'WT.M', "TktDfWT.M", "TktOEWT.M",
@@ -210,7 +210,7 @@ plot.A4V = function(ID){
       A4V.groups = substr(A4V.groups,1, nchar(A4V.groups)-1)
       
       
-      if(nrow(na.omit(A4V.cpm[FBgn,]))){
+      if(nrow(na.omit(A4V.cpm[FBgn,])) > 0){
         par(mar=c(5.1, 4.1, 4.1, 8.1), xpd=TRUE)
         gene = data.frame(cpm = as.numeric(A4V.cpm[FBgn,]),
                           condition = A4V.groups,

### 2025-01-15 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -223,11 +223,11 @@ plot.A4V = function(ID){
                                                            "A3FT", "A9FT", "A40FT",
                                                            "A3FA", "A9FA", "A40FA",
                                                            "S3MH", "S9MH",
-                                                           "A3MT", "A9MT",
-                                                           "A3MA", "A9MA",
-                                                           "A3MH", "A9MH",
                                                            "S3MT", "S9MT",
-                                                           "S3MA", "S9MA"))
+                                                           "S3MA", "S9MA",
+                                                           "A3MH", "A9MH",
+                                                           "A3MT", "A9MT",
+                                                           "A3MA", "A9MA"))
         gene$group = factor(gene$group, levels = c("SF", "AF", "SM", "AM"))
         
         boxplot(gene$cpm~gene$condition, xlab="",     
@@ -235,8 +235,8 @@ plot.A4V = function(ID){
         points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
         legend('topright',
                inset=c(-0.275,0),
-               legend = c('A4V F', 'Silent F', 'A4V M', 'Silent M'), 
-               fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
+               legend = c('Silent F', 'A4V F', 'Silent M' 'A4V M', 'Silent M'), 
+               fill = c('firebrick', "gold", "darkgreen", "dodgerblue"),
                cex = .65,
                bty = 'n',
                pt.cex = .5)

### 2025-01-15 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -235,7 +235,7 @@ plot.A4V = function(ID){
         points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
         legend('topright',
                inset=c(-0.275,0),
-               legend = c('Silent F', 'A4V F', 'Silent M' 'A4V M', 'Silent M'), 
+               legend = c('Silent F', 'A4V F', 'Silent M', 'A4V M', 'Silent M'), 
                fill = c('firebrick', "gold", "darkgreen", "dodgerblue"),
                cex = .65,
                bty = 'n',

### 2025-01-28 G85R GOandKEGGTermEnrichment.Rmd
serpe data

--- 2024-09-27 GOandKEGGTermEnrichment.Rmd
@@
 
-Variable.Condition = "A9MT" 
-Control.Condition = "S9MT"
-secondary.Variable.Condition = "A40FT"
-secondary.Control.Condition = "S40FT"
+# Conditions
+#Geno is WT or GR
+#TKT is either "C", "OE", or "Df"
+#Sex is "F" or "M"
+
+Geno1 = "GR"
+TKT1 = "C"
+Sex1 = "F"
+
+Geno2 = "WT"
+TKT2 = "C"
+Sex2 = "F"
+
+temp.FC = colnames(G85R.FC)
+temp1 = temp.FC[grep(Geno1, temp.FC)]
+
+if(Sex1 != Sex2){
+  temp1 = temp1[intersect(grep(Sex1, temp1), grep(Sex2, temp1))]
+  temp1 = temp1[grep(Geno1)]
+}
+
+if(Sex1 == Sex2){
+  if(Geno1 == Geno2){
+  temp1 = temp1[grep(setdiff(c("WT", "GR"), c(Geno1, Geno2)), temp1, invert = T)]
+  }
+
+  if(Geno1 != Geno2){
+  temp1 = temp1[intersect(grep(Geno1, temp1), grep(Geno2, temp1))]
+  }
+
+  temp1 = temp1[intersect(grep(TKT1, temp1), grep(TKT2, temp1))]
+
+  temp1 = temp1[grep(Sex1, temp1)]
+}
+
+FC = G85R.FC[temp1]
+FDR = G85R.FC[temp1]
+
+Variable.Condition = "GRFC" 
+Control.Condition = "WTFC"
+secondary.Variable.Condition = "GRMC"
+secondary.Control.Condition = "WTMC"
 
@@
 
-subset = T
-
-s1 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] < 0,]))
-s2 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] < 0,]))
-s3 = intersect(row.names(FDR[FDR[1] <.05,]), row.names(FC[FC[1] > 0,]))
-s4 = intersect(row.names(FDR[FDR[2] <.05,]), row.names(FC[FC[2] > 0,]))
-
-biomarkers = row.names(A4V.FDR[(A4V.FDR$AvS3FT > .05 &
-                       A4V.FDR$AvS9FT > .05 &
-                       A4V.FDR$AvS40FT < .05 &
-                       A4V.FDR$AvS3MT > .05 &
-                       A4V.FDR$AvS9MT < .05),])
-expression.max = apply(A4V.meancpm[biomarkers, c("A40FT","S40FT","A9MT","S9MT")], MARGIN = 1, max)[biomarkers]
-biomarkers = biomarkers[expression.max > 20]
-
-NADmetab = names(kegg[grep('00760', kegg)])
-biomarkers = row.names(GeneIDKey[GeneIDKey$Symbol %in% NADmetab, ])
+subset = F
 
@@
   geneset = biomarkers
-  s1 = intersect(s1, geneset)
-  s2 = intersect(s2, geneset)
-  s3 = intersect(s3, geneset)
-  s4 = intersect(s4, geneset)
   FC[setdiff(row.names(FC),geneset),] = 1 
@@
 ```{r echo = F}
-library(heatmaply)
-hmdata = mean.data[geneset,]
-row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
-hmdata = na.omit(hmdata)
+#library(heatmaply)
+#hmdata = mean.data[geneset,]
+#row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
+#hmdata = na.omit(hmdata)
 
-heatmaply(hmdata,
-          scale = 'row',
-          Colv = F)
+#heatmaply(hmdata,
+#          scale = 'row',
+#          Colv = F)
 

### 2025-01-28 GOandKEGGTermEnrichment.Rmd
pca
serpe data

@@
 
-Variable.Condition = "A9MT" 
-Control.Condition = "S9MT"
-secondary.Variable.Condition = "A40FT"
-secondary.Control.Condition = "S40FT"
+Variable.Condition = "GRFC" 
+Control.Condition = "WTFC"
+secondary.Variable.Condition = "GRMC"
+secondary.Control.Condition = "WTMC"
 

### 2025-01-28 GeneExpressionBoxPlots.Rmd
serpe data

@@
 
-GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+##load all files from github
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
 
-##load all files from github
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
 
-TKT.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
+TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)
 
-TKT.groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
-TKT.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
-TKT.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)
+TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)
+
+TKT.FDR = read.csv(paste0(git.dir, "TKT.EdgeR.FDRTable.csv"), row.names = 1)
+
+TKT.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
 
@@
 
-A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv",row.names = 1)
+A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
 
-A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv")
+A4V.FDR = read.csv(paste0(git.dir, "A4V.FDRdata.csv"), row.names = 1)
 
-gbbOE = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_CountTable.csv", row.names = 1)
-gbbOE.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbOE_Metadata.csv", row.names = 1)
+gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
+
+gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
+
 gbbOE = gbbOE[,row.names(gbbOE.groups)]
@@
 
-gbbKO = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_CountTable.csv", row.names = 1)
-gbbKO.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/gbbKO_Metadata.csv", row.names = 1)
+gbbKO = read.csv(paste0(git.dir, "gbbKO_CountTable.csv"), row.names = 1)
+
+gbbKO.groups = read.csv(paste0(git.dir, "gbbKO_Metadata.csv"), row.names = 1)
 
@@
 
-rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)
-KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
+##write.csv(gbbKO.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/gbbKO.cpmdata.csv")
+
+rawdata = read.csv(paste0(git.dir, "MetabolomicsForMetaboanalyst.txt"), sep = "\t", row.names = 1)
+
+KEGG.Key = read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
+
 KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])
@@
 
+SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1)
+
 ```
@@
 ##Function to plot all G85R groups
+plot.G85R = function(ID){
+ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
+                     grep(ID, GeneIDKey$Symbol)),]
 
-plot.G85R = function(ID){
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
+if(nrow(ID.row) < 500){
 if(nrow(ID.row) == 1){
@@
 }
+}
 
-```
+##Function to plot a specific gene expression levels in all A4V groups
+plot.A4V = function(ID){
+ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
+                     grep(ID, GeneIDKey$Symbol)),]
 
-```{r echo = F}
-##Function to plot a specific gene expression levels in all A4V groups
-
-plot.A4V = function(ID){
-ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
-
+if(nrow(ID.row) < 500){
 if(nrow(ID.row) == 1){
@@
 }
+}
 
-```
-
-```{r echo = F}
 ##Plot levels of a specific metabolite
-
 plot.metab = function(metabID){
@@
 
+if(nrow(ID.row) < 500){
 if(length(ID.row) == 1){
@@
 }
+}
+
+##Function to plot a specific gene expression levels in all cell types for the SCdata
+plot.SC = function(gene.name){
+ID.row = SCdata[grep(gene.name, SCdata$Gene.name),]
+
+if(nrow(ID.row) < 500){
+if(nrow(ID.row) == 1){
+
+  gene.name = ID.row$Gene.name
+  gene.levels = setNames(as.numeric(ID.row[,colnames(ID.row) != "Gene.name"]), colnames(ID.row)[colnames(ID.row) != "Gene.name"]) 
+  gene.levels = gene.levels[18:1]
+  highlight = rep(0, 18)
+  highlight[(gene.levels > 2*(mean(gene.levels)))] = 1
+  highlight = gene.levels * highlight
+
+  nochange = gene.levels
+  nochange[gene.levels > 1.5] = 0
+  nochange = gene.levels * nochange
+
+  label.colors = highlight
+
+  label.colors[label.colors > 0] = "deeppink"
+  label.colors[label.colors == 0] = "black"
+  label.colors[nochange > 0] = 'steelblue'
+
+  if(1.25*(max(gene.levels)) < 5){
+    xmax = 5
+  }
+
+  if(1.25*(max(gene.levels)) >= 5){
+    xmax = 1.25*(max(gene.levels))
+  }
+
+  par(mar=c(5, 12, 4, 6), xpd=TRUE)
+
+  plot(x = NA,
+      y = NA,
+     type = 'n',
+     ylim = c(.95, 21),
+     xlim = c(0, xmax),
+     xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = "Mean UMI Counts",
+     bty = "n",
+     main = gene.name)
+
+  barplot(height = gene.levels, 
+          horiz = T, 
+          #las = 2,
+          xlim = c(0, xmax),
+          names.arg = NA,
+          border = T,
+          add = T)
+
+    barplot(height = highlight, 
+          horiz = T, 
+          #las = 2, 
+          names.arg = NA,
+          border = T,
+          col = "deeppink",
+          add = T)
+
+    barplot(height = nochange, 
+          horiz = T, 
+          #las = 2, 
+          names.arg = NA,
+          border = T,
+          col = "lightsteelblue",
+          add = T)
+
+  mtext(side = 2,
+        las = 2,
+        at = .7+(1.2*(0:17)),
+        text = names(gene.levels),
+        col = label.colors,
+        line = 0)
+
+  abline(v = 1,
+         lty = 2,
+         lwd = 2,
+         xpd = F)
+
+  legend(x = .9*xmax,
+         y = 23,
+         legend = c("high", "mid", "low"),
+         fill = c("deeppink", "grey", "lightsteelblue"),
+         bty = "n",
+         xpd = T)
+
+}
+
+if(nrow(ID.row) != 1){
+  ID.row
+}
+}
+}
 
@@
 ```{r echo = F}
-##Tailared code to plot a specific gene expression levels in all A4V groups
+
+## Plot gene expression from A4V RNAseq experiment
+## ID needs to be the full or partial gene symbol or FBgn (case sensitive)
 
@@
 
+## Plot metabolite levels from the G85R TKT metabolomics experiment
+## metabID needs to be the full or partial metabolite name as listed in the table (case sensitive)
+
 metabID = 'NADP'
@@
 
+if(nrow(ID.row) < 500){
 if(nrow(ID.row) == 1){
@@
 ID.row = GeneIDKey[grep(ID, GeneIDKey$FBgn),]
+
+if(nrow(ID.row) < 500){
 

### 2025-01-28 SerpeSCdata.Rmd
serpe data

---
title: "Serpe SC data"
author: "John Santiago"
date: "2025-01-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

#library("hdf5r")
#library(SCopeLoomR)

#loom <- open_loom("/Users/johncsantiago/Downloads/5a3ba000_20180809__Davie_Janssens_Koldere_et_al_2018_Adult_Brain.HARMONY_SCENIC.loom", mode = "r")

##loom = open_loom("/Users/johncsantiago/Downloads/Goodwin_Fly_AdultVNC_elife54074.loom", mode = "r")

#dgem <- get_dgem(loom)
#close_loom(loom)
#dgem[1:5,100:105]

#clustering_annotations_df <- get_clustering_annotations(loom = loom)

```

```{r echo = F}

##manually currated
serpe = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Nguyen Serpe 2024 scRNA-seq VNC.csv", row.names = 1)

serpe.glia = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Serpe 2024 GliaSubtypes.csv", row.names = 1)

serpe.mn = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Serpe 2024 MNClusters.csv", row.names = 1)

serpe.inter = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Serpe 2024 InterneuronClusters.csv", row.names = 1)

serpe.annotated.names = as.character(read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Nguyen Serpe 2024 scRNA-seq VNC.csv", row.names = 1, header = F)[1,])

serpe.glia.names = as.character(read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Serpe 2024 GliaSubtypes.csv", row.names = 1, header = F)[1,])

```

```{r echo = F}

plot.serpe = function(gene.name){
serpe.annotated.gene = data.frame(level = as.numeric(serpe[gene.name,]),
                                  cluster = serpe.annotated.names,
                                  color = "darkgreen")

serpe.mn.gene = data.frame(level = as.numeric(serpe.mn[gene.name,]),
                           cluster = colnames(serpe.mn),
                           color = "brown")

serpe.inter.gene = data.frame(level = as.numeric(serpe.inter[gene.name,]),
                              cluster = colnames(serpe.inter),
                              color = "gold")

serpe.glia.gene = data.frame(level = as.numeric(serpe.glia[gene.name,]),
                             cluster = serpe.glia.names,
                             color = "steelblue")

serpe.all = rbind(serpe.annotated.gene,
                  rbind(serpe.mn.gene,
                        rbind(serpe.inter.gene,
                              serpe.glia.gene)))

par(mar = c(4, 13, 4, 8))
barplot(as.numeric(serpe.all[,"level"])-1,
        names.arg = serpe.all$cluster,
        las = 2, 
        beside = T,
        col = serpe.all$color,
        cex.names = .75,
        main = gene.name,
        horiz = T,
        xlab = "Mean Expression Level per Cell")
      legend(x = max(as.numeric(serpe.all[,"level"])-1),
             y = 125,
             pch = 21,
             legend = c("Glia", "Interneurons", "Motor Neurons", "Manually Curated"),
             pt.bg = c("steelblue", "gold", "brown", "darkgreen"),
             bty = "n",
             xpd = T,
             pt.cex = 1.5,
             y.intersp = 1)
}
```

```{r echo = F, fig.width= 10, fig.height=15}

##gene.name = "gbb"

##plot.serpe(gene.name)

```

```{r echo = F}

##Function to plot a specific gene expression levels in all cell types for the SC data
plot.serpe.allclusters = function(gene.name){

  ID.row = serpe[grep(gene.name, row.names(serpe)),]

  if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
    if(nrow(ID.row) == 1 | length(intersect(gene.name, row.names(serpe))) == 1){

  serpe.annotated.gene = data.frame(level = as.numeric(serpe[gene.name,]),
                                    cluster = serpe.annotated.names,
                                    color = "darkgreen")

  serpe.mn.gene = data.frame(level = as.numeric(serpe.mn[gene.name,]),
                            cluster = colnames(serpe.mn),
                            color = "brown")

  serpe.inter.gene = data.frame(level = as.numeric(serpe.inter[gene.name,]),
                                cluster = colnames(serpe.inter),
                                color = "gold")

  serpe.glia.gene = data.frame(level = as.numeric(serpe.glia[gene.name,]),
                              cluster = serpe.glia.names,
                              color = "steelblue")

  serpe.all = rbind(serpe.annotated.gene,
                    rbind(serpe.mn.gene,
                          rbind(serpe.inter.gene,
                                serpe.glia.gene)))

  #serpe.all$level = serpe.all$level - 1

  #highlight = rep(0, nrow(serpe.all))
  #highlight[(serpe.all$level > highlight.cutoff*(mean(serpe.all$level)))] = 1
  #serpe.all$highlight = serpe.all$level * highlight

  #serpe.all$color[highlight > 0 & serpe.all$color == "lightgreen"] = "darkgreen"
  #serpe.all$color[highlight > 0 & serpe.all$color == "thistle1"] = "brown"
  #serpe.all$color[highlight > 0 & serpe.all$color == "lightyellow"] = "gold"
  #serpe.all$color[highlight > 0 & serpe.all$color == "lightcyan"] = "royalblue"
  serpe.all$color[serpe.all$level < 1.5] = "darkgrey"

  #label.colors = serpe.all$color

  #label.colors[serpe.all$color == "darkgreen"] = "darkgreen"
  #label.colors[serpe.all$color == "brown"] = "brown"
  #label.colors[serpe.all$color == "gold"] = "gold"
  #label.colors[serpe.all$color == "royalblue"] = "royalblue"
  #serpe.all$label.colors = label.colors

  xmax = max(serpe.all$level)
  if(xmax < 10){
    xmax = 10
  }

      par(mar = c(4, 13, 4, 8), xpd=TRUE)

      plot(x = NA,
           y = NA,
           type = 'n',
           ylim = c(4.5, 120),
           xlim = c(0, xmax),
           xaxt = "n",
           ylab="",
           yaxt = "n",
           xlab = "Mean Expression Levels",
           bty = "n",
           main = gene.name)

      barplot(height = serpe.all$level, 
              horiz = T, 
              #las = 2,
              xlim = c(0, xmax),
              names.arg = NA,
              border = T,
              col = serpe.all$color,
              add = T)

      mtext(side = 2,
            las = 2,
            at = .7+(1.2*(0:104)),
            text = serpe.all$cluster,
            col = serpe.all$color,
            line = 0)

      legend(x = xmax,
             y = 125,
             pch = 21,
             legend = c("Glia", "Interneurons", "Motor Neurons", "Manually Curated"),
             pt.bg = c("steelblue", "gold", "brown", "darkgreen"),
             bty = "n",
             xpd = T,
             pt.cex = 1.5,
             y.intersp = 1)

      rect(0 - (xmax/40), 0, 0 - (xmax/100), 18*1.2, col = 'darkgreen')
      rect(0 - (xmax/40), 18*1.2, 0 - (xmax/100), 46*1.2, col = 'brown')
      rect(0 - (xmax/40), 46*1.2, 0 - (xmax/100), 95*1.2, col = 'gold')
      rect(0 - (xmax/40), 95*1.2, 0 - (xmax/100), 105*1.2, col = 'steelblue')

    }

    #if(nrow(ID.row) != 1 | length(intersect(gene.name, row.names(serpe))) > 1){
    #  ID.row
    #}
  }
}

```

```{r echo = F, fig.width= 10, fig.height=16}

gene.name = "gbb"

plot.serpe.allclusters(gene.name)

```

```{r echo = F, fig.width= 10, fig.height=16}

gene.name = "dpp"

plot.serpe.allclusters(gene.name)

```

```{r echo = F, fig.width= 10, fig.height=16}

gene.name = "wit"

plot.serpe.allclusters(gene.name)

```

```{r echo = F, fig.width= 10, fig.height=16}

gene.name = "mav"

plot.serpe.allclusters(gene.name)

```

```{r echo = F, fig.width= 10, fig.height=16}

gene.name = "put"

plot.serpe.allclusters(gene.name)

```

### 2025-01-28 TKT_RNAseq/R Code/TKTRNAseqPNPAssessment.Rmd
serpe data

@@
 source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
+
 mean.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_meancpmdata.csv", row.names = 1)
@@
                             arrows = 'to',
-                            FBgn = NA,
-                            color = 'black',
-                            width = 1,
-                            symbol = NA,
-                            fdr = NA,
-                            GR = NA,
-                            WT = NA,
-                            title = '')
+                            FBgn = NA)
+
+purine.path = rbind(purine.path, TerminalPoints)
+row.names(purine.path) = 1:nrow(purine.path)
+#write.csv(purine.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv")
 
@@
 interactions = interactions[c(1:5, 7:9), c(1,4,5)]
+
+purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)
+
+temp.edges = data.frame(from = purine.path$from,
+                        to = purine.path$to,
+                        arrows = purine.path$arrows,
+                        color = "black",
+                        width = 0,
+                        title = "",
+                        FBgn = purine.path$FBgn)
+
+add.edges = data.frame(enzyme = c("3.5.4.10", 
+                                "2.1.2.3",
+                                "4.3.2.2",
+                                "6.3.2.6",
+                                "4.1.1.21",
+                                "6.3.3.1",
+                                "6.3.5.3",
+                                "2.1.2.2",
+                                "6.3.4.13",
+                                "2.4.2.14",
+                                "2.7.6.1"),
+                       from = c("FAICAR", 
+                                "AICA ribonucleotide", 
+                                "SAICAR",
+                                "CAIR",
+                                "AIR",
+                                "2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine",
+                                "FGAR",
+                                "GAR",
+                                "Ribosylamine-5p",
+                                "PRPP",
+                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
+
+                       to = c("IMP", 
+                              "FAICAR", 
+                              "AICA ribonucleotide",
+                              "SAICAR",
+                              "CAIR",
+                              "AIR",
+                              "2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine",
+                              "FGAR",
+                              "GAR",
+                              "Ribosylamine-5p",
+                              "PRPP"),
+                       arrows = c("to;from", 
+                                  "to", 
+                                  "to;from",
+                                  "to;from",
+                                  "to;from",
+                                  "to",
+                                  "to",
+                                  "to",
+                                  "to",
+                                  "to",
+                                  "to"),
+                       FBgn = "")
+
+#write.csv(temp.edges, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv")
+
+i = 1
+new.edges = data.frame(enzyme = as.character(),
+                       from = as.character(),
+                       to = as.character(),
+                       arrows = as.character(),
+                       FBgn = as.character())
+
+while(i <= nrow(add.edges)){
+  temp.fbgn = names(nodeID[grep(add.edges[i, "enzyme"], nodeID)])
+  temp.fbgn = GeneIDKey[GeneIDKey$ensembl %in% temp.fbgn, "FBgn"]
+  temp.new.edges = add.edges[rep(i, length(temp.fbgn)), ]
+  temp.new.edges$FBgn = temp.fbgn
+  new.edges = rbind(new.edges, temp.new.edges)
+  i = i +1
+}
+
+purine.path = rbind(purine.path, new.edges)
+row.names(purine.path) = 1:nrow(purine.path)
+#write.csv(purine.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv")
+
+temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
+
+new.edges$color = "black"
+new.edges$width = 0
+new.edges$title = ""
+
+new.edges = new.edges[, colnames(temp.edges)]
+
+temp.edges = rbind(temp.edges, new.edges)
+
+#write.csv(temp.edges, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv")
 
@@
 
-mean.cpm
-
 compare.conditions = function(condition1, condition2){
@@
 
+```
+
+```{r echo = F}
+
+temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
+
+purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)
+
+temp.nodes = data.frame(id = unique(c(purine.path$from, purine.path$to)),
+                        group = "metabolite",
+                        color.background = "white",
+                        color.border = "black",
+                        x = 0,
+                        y = 0,
+                        size = 30,
+                        FC = NA,
+                        pval = NA,
+                        title = "")
+temp.nodes$title = temp.nodes$id
+
+row.names(temp.nodes) = temp.nodes$id
+
+temp.nodes[c("Pentose Phosphate", "Excretion", "Riboflavin.Metabolism",
+            "Folate.Biosynthesis", "DNA.A", "DNA.G", "RNA.A", "RNA.G"), "group"] = "Outside Path"
+
+temp.nodes["RNA.G", 'x'] = 0
+temp.nodes["RNA.G", 'y'] = 1.5
+
+temp.nodes["Folate.Biosynthesis", 'x'] = 0
+temp.nodes["Folate.Biosynthesis", 'y'] = 2
+
+temp.nodes["Riboflavin.Metabolism", 'x'] = 0
+temp.nodes["Riboflavin.Metabolism", 'y'] = 2.5
+
+temp.nodes["DNA.G", 'x'] = 0
+temp.nodes["DNA.G", 'y'] = 4
+
+temp.nodes["GTP", 'x'] = 1
+temp.nodes["GTP", 'y'] = 2
+
+temp.nodes["dGTP", 'x'] = 1
+temp.nodes["dGTP", 'y'] = 4
+
+temp.nodes["GDP", 'x'] = 2
+temp.nodes["GDP", 'y'] = 3
+
+temp.nodes["dGDP", 'x'] = 2
+temp.nodes["dGDP", 'y'] = 3
+
+temp.nodes["dGMP", 'x'] = 2
+temp.nodes["dGMP", 'y'] = 4
+
+temp.nodes["deoxyguanosine", 'x'] = 2
+temp.nodes["deoxyguanosine", 'y'] = 5
+
+temp.nodes["GMP", 'x'] = 3
+temp.nodes["GMP", 'y'] = 2
+
+temp.nodes["guanosine", 'x'] = 3
+temp.nodes["guanosine", 'y'] = 3
+
+temp.nodes["guanine", 'x'] = 3
+temp.nodes["guanine", 'y'] = 4
+
+temp.nodes["IDP", 'x'] = 4
+temp.nodes["IDP", 'y'] = 1
+
+temp.nodes["XMP", 'x'] = 4
+temp.nodes["XMP", 'y'] = 2
+
+temp.nodes["xanthosine", 'x'] = 4
+temp.nodes["xanthosine", 'y'] = 3
+
+temp.nodes["xanthine", 'x'] = 4
+temp.nodes["xanthine", 'y'] = 4
+
+temp.nodes["uric acid", 'x'] = 4
+temp.nodes["uric acid", 'y'] = 5
+
+temp.nodes["Excretion", 'x'] = 4
+temp.nodes["Excretion", 'y'] = 6
+
+temp.nodes = temp.nodes[temp.nodes$id != "Pentose Phosphate" ,]
+temp.edges = temp.edges[temp.edges$from != "Pentose Phosphate" & temp.edges$to != "Pentose Phosphate" ,]
+
+temp.nodes["FAICAR", "x"] = 5
+temp.nodes["FAICAR", "y"] = 1
+
+temp.nodes["AICA ribonucleotide", "x"] = 5
+temp.nodes["AICA ribonucleotide", "y"] = 0
+
+temp.nodes["IMP", 'x'] = 5
+temp.nodes["IMP", 'y'] = 2
+
+temp.nodes["inosine", 'x'] = 5
+temp.nodes["inosine", 'y'] = 3
+
+temp.nodes["hypoxanthine", 'x'] = 5
+temp.nodes["hypoxanthine", 'y'] = 4
+
+temp.nodes["deoxyinosine", 'x'] = 5
+temp.nodes["deoxyinosine", 'y'] = 5
+
+temp.nodes["adenylosuccinate", 'x'] = 6
+temp.nodes["adenylosuccinate", 'y'] = 1
+
+temp.nodes["AMP", 'x'] = 6
+temp.nodes["AMP", 'y'] = 2
+
+temp.nodes["adenosine", 'x'] = 6
+temp.nodes["adenosine", 'y'] = 3
+
+temp.nodes["adenine", 'x'] = 6
+temp.nodes["adenine", 'y'] = 4
+
+temp.nodes["deoxyadenosine", 'x'] = 6
+temp.nodes["deoxyadenosine", 'y'] = 5
+
+temp.nodes["cAMP", 'x'] = 7
+temp.nodes["cAMP", 'y'] = 1
+
+temp.nodes["ADP", 'x'] = 7
+temp.nodes["ADP", 'y'] = 3
+
+temp.nodes["dADP", 'x'] = 7
+temp.nodes["dADP", 'y'] = 4
+
+temp.nodes["dAMP", 'x'] = 7
+temp.nodes["dAMP", 'y'] = 5
+
+temp.nodes["ATP", 'x'] = 8
+temp.nodes["ATP", 'y'] = 2
+
+temp.nodes["dATP", 'x'] = 8
+temp.nodes["dATP", 'y'] = 4
+
+temp.nodes["RNA.A", 'x'] = 9
+temp.nodes["RNA.A", 'y'] = 2
+
+temp.nodes["DNA.A", 'x'] = 9
+temp.nodes["DNA.A", 'y'] = 4
+
+temp.nodes$x = temp.nodes$x*150
+temp.nodes$y = temp.nodes$y*150
+
+visNetwork(temp.nodes, temp.edges)%>%
+  visNodes(physics = F)
+
+#write.csv(temp.nodes, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv")
+
+```
+
+```{r}
+temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
+
+temp.edges[temp.edges$from == "Pentose Phosphate", "to"] = "PRPP"
+
+purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)
+
+add.edges = data.frame(enzyme = c("2.2.1.1",
+                                  "5.1.3.1",
+                                  "5.3.1.6",
+                                  "5.4.2.7",
+                                  "5.4.2.2"),
+                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
+                       to = c("D-sedoheptulose-7-phosphate",
+                              "D-Xylulose 5-phosphate",
+                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
+                       arrows = c("to;from",
+                                  "to;from",
+                                  "to;from",
+                                  "to;from",
+                                  "to;from"),
+                       FBgn = "")
+
+```
+
+```{r echo = F}
+
+temp.edges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
+
+temp.edges[temp.edges$from == "Pentose Phosphate", "to"] = "PRPP"
+
+purine.path = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.path.csv", row.names = 1)
+
+temp.nodes = data.frame(id = unique(c(purine.path$from, purine.path$to)),
+                        group = "metabolite",
+                        color.background = "white",
+                        color.border = "black",
+                        x = 0,
+                        y = 0,
+                        size = 0,
+                        FC = NA,
+                        pval = NA,
+                        title = "",
+                        label = "")
+temp.nodes$label = temp.nodes$id
+
+row.names(temp.nodes) = temp.nodes$id
+
+temp.nodes[c("Pentose Phosphate", "Excretion", "Riboflavin.Metabolism",
+            "Folate.Biosynthesis", "DNA.A", "DNA.G", "RNA.A", "RNA.G"), "group"] = "Outside Path"
+
+temp.nodes["Pentose Phosphate" , 'x'] = -2.5
+temp.nodes["Pentose Phosphate" , 'y'] = -1.5
+
+temp.nodes["D-ribose-1/5-phosphate / D-ribulose 5-phosphate", 'x'] = -3.5
+temp.nodes["D-ribose-1/5-phosphate / D-ribulose 5-phosphate", 'y'] = 0.25
+
+temp.nodes["PRPP", 'x'] = -2.5
+temp.nodes["PRPP", 'y'] = 0
+
+temp.nodes["Ribosylamine-5p", 'x'] = -1.5
+temp.nodes["Ribosylamine-5p", 'y'] = 0.25
+
+temp.nodes["GAR", 'x'] = -.5
+temp.nodes["GAR", 'y'] = 0
+
+temp.nodes["RNA.G", 'x'] = -.25
+temp.nodes["RNA.G", 'y'] = 1
+
+temp.nodes["Folate.Biosynthesis", 'x'] = -.25
+temp.nodes["Folate.Biosynthesis", 'y'] = 1.5
+
+temp.nodes["Riboflavin.Metabolism", 'x'] = -.25
+temp.nodes["Riboflavin.Metabolism", 'y'] = 2
+
+temp.nodes["DNA.G", 'x'] = 0
+temp.nodes["DNA.G", 'y'] = 4.5
+
+temp.nodes["FGAR", 'x'] = .5
+temp.nodes["FGAR", 'y'] = 0.25
+
+temp.nodes["GTP", 'x'] = .75
+temp.nodes["GTP", 'y'] = 1.5
+
+temp.nodes["dGTP", 'x'] = .75
+temp.nodes["dGTP", 'y'] = 3.75
+
+temp.nodes["2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine", 'x'] = 1.5
+temp.nodes["2-(Formamido)-N1-(5-phospho-D-ribosyl)acetamidine", 'y'] = 0
+
+temp.nodes["GDP", 'x'] = 1.75
+temp.nodes["GDP", 'y'] = 2.25
+
+temp.nodes["dGDP", 'x'] = 1.5
+temp.nodes["dGDP", 'y'] = 3
+
+temp.nodes["dGMP", 'x'] = 1.75
+temp.nodes["dGMP", 'y'] = 3.75
+
+temp.nodes["AIR", 'x'] = 2.5
+temp.nodes["AIR", 'y'] = 0.25
+
+temp.nodes["deoxyguanosine", 'x'] = 2.75
+temp.nodes["deoxyguanosine", 'y'] = 4.25
+
+temp.nodes["GMP", 'x'] = 2.75
+temp.nodes["GMP", 'y'] = 1.75
+
+temp.nodes["CAIR", 'x'] = 3.5
+temp.nodes["CAIR", 'y'] = 0
+
+temp.nodes["guanosine", 'x'] = 3.5
+temp.nodes["guanosine", 'y'] = 2.5
+
+temp.nodes["guanine", 'x'] = 3.5
+temp.nodes["guanine", 'y'] = 3.5
+
+temp.nodes["IDP", 'x'] = 4.5
+temp.nodes["IDP", 'y'] = 1.25
+
+temp.nodes["SAICAR", 'x'] = 4.5
+temp.nodes["SAICAR", 'y'] = 0.25
+
+temp.nodes["XMP", 'x'] = 4.5
+temp.nodes["XMP", 'y'] = 2
+
+temp.nodes["xanthosine", 'x'] = 4.5
+temp.nodes["xanthosine", 'y'] = 3
+
+temp.nodes["xanthine", 'x'] = 4.5
+temp.nodes["xanthine", 'y'] = 4
+
+temp.nodes["uric acid", 'x'] = 4.5
+temp.nodes["uric acid", 'y'] = 5
+
+temp.nodes["Excretion", 'x'] = 4.5
+temp.nodes["Excretion", 'y'] = 6
+
+temp.nodes["AICA ribonucleotide", "x"] = 5.5
+temp.nodes["AICA ribonucleotide", "y"] = 0
+
+temp.nodes["FAICAR", "x"] = 5.5
+temp.nodes["FAICAR", "y"] = 1
+
+temp.nodes["IMP", 'x'] = 5.5
+temp.nodes["IMP", 'y'] = 2
+
+temp.nodes["inosine", 'x'] = 5.5
+temp.nodes["inosine", 'y'] = 3
+
+temp.nodes["hypoxanthine", 'x'] = 5.5
+temp.nodes["hypoxanthine", 'y'] = 4
+
+temp.nodes["deoxyinosine", 'x'] = 6.5
+temp.nodes["deoxyinosine", 'y'] = 4.5
+
+temp.nodes["adenylosuccinate", 'x'] = 6.5
+temp.nodes["adenylosuccinate", 'y'] = 1.25
+
+temp.nodes["AMP", 'x'] = 7.5
+temp.nodes["AMP", 'y'] = 2
+
+temp.nodes["adenosine", 'x'] = 6.5
+temp.nodes["adenosine", 'y'] = 2.5
+
+temp.nodes["adenine", 'x'] = 7.5
+temp.nodes["adenine", 'y'] = 3
+
+temp.nodes["deoxyadenosine", 'x'] = 7.5
+temp.nodes["deoxyadenosine", 'y'] = 4
+
+temp.nodes["cAMP", 'x'] = 8.25
+temp.nodes["cAMP", 'y'] = 1.25
+
+temp.nodes["ADP", 'x'] = 8.25
+temp.nodes["ADP", 'y'] = 2.5
+
+temp.nodes["dADP", 'x'] = 8.5
+temp.nodes["dADP", 'y'] = 3
+
+temp.nodes["dAMP", 'x'] = 8.5
+temp.nodes["dAMP", 'y'] = 4
+
+temp.nodes["ATP", 'x'] = 9
+temp.nodes["ATP", 'y'] = 1.825
+
+temp.nodes["dATP", 'x'] = 9.25
+temp.nodes["dATP", 'y'] = 3.5
+
+temp.nodes["RNA.A", 'x'] = 10
+temp.nodes["RNA.A", 'y'] = 1.825
+
+temp.nodes["DNA.A", 'x'] = 10
+temp.nodes["DNA.A", 'y'] = 4
+
+temp.nodes$x = temp.nodes$x*150
+temp.nodes$y = temp.nodes$y*150
+
+visNetwork(temp.nodes, temp.edges)%>%
+  visNodes(physics = F, shape = "box")
+
+#write.csv(temp.nodes, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv")
+
+```
+
+```{r}
+
+##genes in the kegg pathway and their enzyme IDs
+glycolysis.genes = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisGenesKEGGinfo.csv')
+##Edge data for genes connecting metabolites
+glycolysis.edges = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisEnzymeEdgesKEGGinfo.csv')
+##Metabolites in the KEGG pathway with their ID
+glycolysis.metabs = read.csv('/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GlycolysisMetaboliteKEGGinfo.csv')
+
+node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00010.xml')
+
+##extracting position data for nodes
+node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
+                       number = rep(names(node.data$kegg.names),
+                                    lengths(node.data$kegg.names)),
+                       x = 0,
+                       y = 0,
+                       color = 0,
+                       names = "")
+node.info$x = node.data$x[node.info$number]
+node.info$y = node.data$y[node.info$number]
+
+##make new columns for transcriptomic data
+glycolysis.genes$FBgn = ""
+glycolysis.genes$Symbol = ""
+glycolysis.genes$FC = 0
+glycolysis.genes$pval = 1
+
+##Isolate gene ID info for goi
+temp = GeneIDKey[GeneIDKey$CG %in% glycolysis.genes$CG,]
+row.names(temp) = temp$CG
+
+##fill in new columns with transcriptomic data
+glycolysis.genes$FBgn = temp[glycolysis.genes$CG,'FBgn']
+glycolysis.genes$Symbol = temp[glycolysis.genes$CG,'Symbol']
+glycolysis.genes$FC = 0
+glycolysis.genes$FC = 0
+
+##make new columns for metabolomic data
+row.names(glycolysis.metabs) = glycolysis.metabs$KEGG.ID
+glycolysis.metabs$metabolomicsID = ""
+glycolysis.metabs$FC = 0
+glycolysis.metabs$pval = 1
+
+##retrieve name used in metabolomic data for metabolite IDs in path
+##including IDs associated with multiple metabolomic names
+i = 1
+while(i<=nrow(glycolysis.metabs)){
+  if(length(grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)) > 0){
+    glycolysis.metabs$metabolomicsID[i]= names(KEGG.Key[grep(glycolysis.metabs$KEGG.ID[i], KEGG.Key)])
+  }
+  i = i +1
+}
+
+##retrieve metabolite fold change and pvalue data
+glycolysis.metabs$FC = 0
+glycolysis.metabs$pval = 0
+
+##using the positions for nodes (metabolites) only
+metab.info = node.info[node.info$ID %in% glycolysis.metabs$KEGG.ID,]
+
+metab.info$FC = glycolysis.metabs[metab.info$ID, 'FC']
+metab.info$pval = glycolysis.metabs[metab.info$ID, 'pval']
+metab.info$names = glycolysis.metabs[metab.info$ID, 'Metabolite']
+metab.info$color = glycolysis.metabs[metab.info$ID, 'FC']
+metab.info$size = glycolysis.metabs[metab.info$ID, 'pval']
+
+color.pallette = colorRampPalette(c('royalblue', 'grey', "firebrick"))(401)
+
+metab.info$color[metab.info$color > 1] = 1
+metab.info$color[metab.info$color < -1] = -1
+metab.info$color = (metab.info$color * 200) +201
+metab.info$color = color.pallette[metab.info$color]
+metab.info$color[is.na(metab.info$color)] = 'dimgrey'
+
+metab.info$size = 10 + 10*abs(metab.info$size)
+metab.info$size[is.na(metab.info$size)] = 10
+
+metab.info$title = paste0(glycolysis.metabs[metab.info$ID, "metabolomicsID"],
+                          "<br>log2(FC): ", signif(metab.info$FC,3),
+                          "<br>pval: ", signif(10^-metab.info$pval,3))
+
+nodes = data.frame(id = paste0(metab.info$names),
+                   color = metab.info$color,
+                   size = metab.info$size,
+                   x = 2*metab.info$x,
+                   y = 2*metab.info$y,
+                   physics = F,
+                   group = "",
+                   title = metab.info$title)
+
+glycolysis.edges$FBgn = ''
+temp.glycolysis.path = glycolysis.edges
+
+i = 1
+while(i<=nrow(glycolysis.edges)){
+  enzymeID = paste0(glycolysis.edges$enzyme[i], "$")
+  if(nrow(glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme),])>0){
+    temp = glycolysis.genes[grep(enzymeID, glycolysis.genes$Enzyme), "CG"]
+    temp = row.names(GeneIDKey[GeneIDKey$CG %in% temp,])
+    temp2 = glycolysis.edges[rep(i, length(temp)),]
+    temp2$FBgn = temp
+  }else{
+    temp2 = glycolysis.edges[i,]
+  }
+  temp.glycolysis.path = rbind(temp.glycolysis.path,temp2)
+
+  i = i +1
+}
+
+glycolysis.edges = temp.glycolysis.path[(nrow(glycolysis.edges)+1):nrow(temp.glycolysis.path),]
+
+glycolysis.edges$size = 0
+glycolysis.edges$size[glycolysis.edges$size <1] = 1
+glycolysis.edges$size[is.na(glycolysis.edges$size)] = 1
+glycolysis.edges$size = 2*glycolysis.edges$size
+
+glycolysis.edges$color = "white"
+## max color intensity is at FC of 2
+#glycolysis.edges$color[glycolysis.edges$color>2] = 2
+#glycolysis.edges$color[glycolysis.edges$color<(-2)] = -2
+#glycolysis.edges$color = 201+(glycolysis.edges$color *100)
+#glycolysis.edges$color = color.pallette[glycolysis.edges$color]
+#glycolysis.edges$color[is.na(glycolysis.edges$color)] = 'dimgrey'
+
+glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
+                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
+                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
+                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
+                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))
+
+glycolysis.edges = data.frame(from = glycolysis.edges$from.name,
+                              to = glycolysis.edges$to.name)
+,
+                              arrows = glycolysis.edges$arrow)
+,
+                              color = glycolysis.edges$color)
+,
+                              width = glycolysis.edges$size)
+,
+                              title = glycolysis.edges$title,
+                              physics = T)
+
+nodes = data.frame(id = paste0(nodes$id),
+                   color = nodes$color,
+                   size = nodes$size,
+                   x = nodes$x,
+                   y = nodes$y,
+                   physics = F,
+                   group = "",
+                   title = nodes$title)
+
+OutsidePath = data.frame(id = c('Pentose Phosphate Pathway',
+                               'Propanoate Metabolism',
+                               'Starch and Sucrose Metabolism',
+                               'Citrate Cycle'),
+                        color = "black",
+                        size = 15,
+                        x= c(1350,1254,966,175),
+                        y=c(1112,1822,110,1700),
+                        physics = F,
+                        group = 'Outside Path',
+                        title = "")
+
+nodes = rbind(nodes, OutsidePath)
+
+```
+
+```{r echo = F}
+
 network.fun = function(comparison.T, comparison.M, cond1, cond2, pnp){
-temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)
-
-visedges = purine.path
+temp = colorRampPalette(c("dodgerblue", 'royalblue', "firebrick",'red'))(401)
+
+visedges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.edges.csv", row.names = 1)
 visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
-##visedges$width = .5 + abs(visedges$color)
 visedges$color[visedges$color < (-2)] = -2
@@
 visedges$width = .01 + (1*abs(log10(visedges$WT)))
-
 visedges$title = paste0(visedges$symbol,
@@
                         "<br>",cond2," CPM: ", visedges$WT)
-visedges = na.omit(visedges)
-visedges = rbind(visedges, TerminalPoints)
-
-node.names = unique(c(visedges$from, visedges$to))
-node.data = data.frame(id = node.names,
-                       color = 'dimgrey',
-                       size = 10,
-                       FC = NA,
-                       pval = NA,
-                       row.names = node.names)
 
@@
 
+node.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv", row.names = 1)
 node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
@@
 node.data[names(node.colors),'size'] = node.colors
-#node.data[names(node.colors),'size'] = 
-#  (node.data[names(node.colors),'size'] + .5 + abs(min(node.colors)))*7.5
-node.data[names(node.colors),'size'] = 
-  (node.data[names(node.colors),'size'] + 4.5)*7.5
-
+node.data[,'size'] = (node.data[,'size'] + 4.5)*7.5
 node.colors[node.colors < (-2)] = -2
 node.colors[node.colors>2] = 2
-
 node.colors = (node.colors*100)+201
-
 node.colors = setNames(temp[node.colors], names(node.colors)) 
-node.data[names(node.colors), 'color'] = node.colors
-
+node.data[names(node.colors), 'color.background'] = node.colors
 node.data$title = paste0(node.data$id,
@@
                          "<br>pval: ", node.data$pval)
-
-node.data[unique(TerminalPoints$enzyme), 'color'] = 'black'
-
-node.data$group = 'metabolite'
-node.data[node.data$color == 'black', 'group'] = "Outside Path"
-node.data[node.data$color == 'dimgrey', 'group'] = "no data"
-
-node.data$x = 1
-node.data$y = 1
-node.data["Excretion", 'x'] = -200
-node.data["Excretion", 'y'] = 500
-
-node.data["Pentose Phosphate" , 'x'] = 50
-node.data["Pentose Phosphate" , 'y'] = -400
-
-node.data["RNA.A", 'x'] = 850
-node.data["RNA.A", 'y'] = -250
-
-node.data["RNA.G", 'x'] = -1000
-node.data["RNA.G", 'y'] = -250
-
-node.data["Folate.Biosynthesis", 'x'] = -1000
-node.data["Folate.Biosynthesis", 'y'] = -350
-
-node.data["Riboflavin.Metabolism", 'x'] = -1000
-node.data["Riboflavin.Metabolism", 'y'] = -150
-
-node.data["DNA.A", 'x'] = 850
-node.data["DNA.A", 'y'] = 250
-
-node.data["DNA.G", 'x'] = -1000
-node.data["DNA.G", 'y'] = 250
-
-# passing custom nodes and/or edges
-lnodes <- data.frame(label = c("Increased", "Decreased", "No Data"), 
-shape = 'dot', color = c("firebrick", "royalblue",'dimgrey'),
- title = "")
+node.data[node.data$group == "Outside Path", 'color.background'] = 'black'
+node.data[node.data$color.background == 'white', 'group'] = "no data"
 
 nodes = node.data
-
-##nodes$color[nodes$color != "black"] = 'dimgrey'
-
-colored.nodes = unique(c(interactions[,1], interactions[,3]))
-colored.nodes = c(setdiff(row.names(nodes), c(colored.nodes, row.names(nodes)[nodes$color == "black"])))
-
-#nodes[row.names(nodes) %in% colored.nodes, 'color'] = "gold"
-
+nodes[names(node.pval[node.pval > 0.05]), "color"] = 'grey'
+
+visedges$color[visedges$from %in% row.names(nodes)[nodes$group == "Outside Path"]] = 'black'
+visedges$color[visedges$to %in% row.names(nodes)[nodes$group == "Outside Path"]] = 'black'
 visedges = visedges[,c('from', 'to', 'arrows', 'color', 'width', 'title')]
 row.names(visedges) = c(1:nrow(visedges))
-
-colored.edges = row.names(visedges[grep("CG16758", visedges$title),])
-colored.edges = setdiff(row.names(visedges), colored.edges)
-
-if(pnp == T){
-  nodes[row.names(nodes) %in% colored.nodes, 'color'] = "lightgrey"
-  visedges[row.names(visedges) %in% colored.edges, "color"] = 'lightgrey'
-}
+visedges = visedges[!is.na(visedges$color),]
+
+lnodes <- data.frame(label = c("Sig. Increased", "Sig. Decreased", "Not. Sig.", "No Data"), 
+shape = 'dot', color = list(background = c("red", "dodgerblue",'dimgrey', 'white'), border = "black"),
+size = c(40, 15, 25, 25),
+ title = "")
 
@@
                   main = paste0(cond1, " vs ", cond2))%>%
-  visNodes(physics = T)%>%
+  visNodes(physics = F)%>%
   visLayout(hierarchical=F, improvedLayout=T)%>%
-  ##visPhysics(solver="forceAtlas2Based", forceAtlas2Based = list(gravitationalConstant=-50),enabled=T, minVelocity = .5)%>%
   visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%

### 2025-01-28 GOandKEGGPlottingFunctions.R

@@ -70,6 +70,72 @@ KEGG.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralD
 GO.Names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GO.names.csv", row.names = 1)
 
 
+G85R.data = function(Geno1, Geno2, Geno3, Geno4,
+                     Sex1, Sex2, Sex3, Sex4,
+                     TKT1, TKT2, TKT3, TKT4){
+  
+  temp.FC = colnames(G85R.FC)
+  temp1 = temp.FC[grep(Geno1, temp.FC)]
+  
+  if(Sex1 != Sex2){
+    temp1 = temp1[intersect(grep(Sex1, temp1), grep(Sex2, temp1))]
+    temp1 = temp1[grep(Geno1)]
+  }
+  
+  if(Sex1 == Sex2){
+    if(Geno1 == Geno2){
+      temp1 = temp1[grep(setdiff(c("WT", "GR"), c(Geno1, Geno2)), temp1, invert = T)]
+    }
+    
+    if(Geno1 != Geno2){
+      temp1 = temp1[intersect(grep(Geno1, temp1), grep(Geno2, temp1))]
+    }
+    
+    temp1 = temp1[intersect(grep(TKT1, temp1), grep(TKT2, temp1))]
+    
+    temp1 = temp1[grep(Sex1, temp1)]
+  }
+  
+  
+  temp2 = temp.FC[grep(Geno3, temp.FC)]
+  
+  if(Sex3 != Sex4){
+    temp2 = temp2[intersect(grep(Sex3, temp2), grep(Sex4, temp2))]
+    temp2 = temp2[grep(Geno3)]
+  }
+  
+  if(Sex3 == Sex4){
+    if(Geno3 == Geno4){
+      temp2 = temp2[grep(setdiff(c("WT", "GR"), c(Geno3, Geno4)), temp2, invert = T)]
+    }
+    
+    if(Geno3 != Geno4){
+      temp2 = temp2[intersect(grep(Geno3, temp2), grep(Geno4, temp2))]
+    }
+    
+    temp2 = temp2[intersect(grep(TKT3, temp2), grep(TKT4, temp2))]
+    
+    temp2 = temp2[grep(Sex3, temp2)]
+  }
+  
+  
+  
[…]

### 2025-01-28 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -3,6 +3,8 @@
 
 ##library(plotly)
 
+library(gplots)
+
 ##load all files from github
 git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
 
@@ -46,7 +48,22 @@ colnames(norm.data) = colnames(Metab.data)[3:ncol(Metab.data)]
 colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
 
 
-SCdata = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"))
+
+
+##manually currated
+serpe = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Nguyen Serpe 2024 scRNA-seq VNC.csv", row.names = 1)
+
+serpe.glia = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1)
+
+serpe.mn = read.csv(paste0(git.dir, "Serpe%202024%20MNClusters.csv"), row.names = 1)
+
+serpe.inter = read.csv(paste0(git.dir, "Serpe%202024%20InterneuronClusters.csv"), row.names = 1)
+
+serpe.annotated.names = as.character(read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1, header = F)[1,])
+
+serpe.glia.names = as.character(read.csv(paste0(git.dir, "Serpe%202024%20GliaSubtypes.csv"), row.names = 1, header = F)[1,])
+
+
 
 ##Function to plot all G85R groups
 plot.G85R = function(ID){
@@ -182,7 +199,6 @@ plot.G85R = function(ID){
     ID.row
   }
 }
-
 
 ##Function to plot a specific gene expression levels in all A4V groups
 plot.A4V = function(ID){
@@ -539,5 +555,154 @@ plot.gbbKO = function(ID){
       ID.row
     }
   }
+}
+
+##Function to plot a specific gene expression levels in all cell types for the SC data
+plot.serpe.allclusters = function(gene.name){
+  
+  ID.row = serpe[grep(gene.name, row.names(serpe)),]
+  
+  if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
+    if(nrow(ID.row) == 1 | length(intersect(gene.name, row.names(serpe))) == 1){
+      
+      
[…]

### 2025-01-28 Functions_OmicsQuickPlotFunctions.R
functions update

@@ -53,7 +53,7 @@ colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
 ##manually currated
 serpe = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Nguyen Serpe 2024 scRNA-seq VNC.csv", row.names = 1)
 
-serpe.glia = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1)
+serpe.glia = read.csv(paste0(git.dir, "Serpe%202024%20GliaSubtypes.csv"), row.names = 1)
 
 serpe.mn = read.csv(paste0(git.dir, "Serpe%202024%20MNClusters.csv"), row.names = 1)
 
@@ -561,6 +561,7 @@ plot.gbbKO = function(ID){
 plot.serpe.allclusters = function(gene.name){
   
   ID.row = serpe[grep(gene.name, row.names(serpe)),]
+  
   
   if(nrow(ID.row) < 50 & nrow(ID.row) > 0){
     if(nrow(ID.row) == 1 | length(intersect(gene.name, row.names(serpe))) == 1){

### 2025-01-29 Functions_OmicsQuickPlotFunctions.R
updated gene plot functions

@@ -196,6 +196,7 @@ plot.G85R = function(ID){
   if(nrow(ID.row) != 1
      | length(intersect(GeneIDKey$FBgn, ID)) > 1
      | length(intersect(GeneIDKey$Symbol, ID)) > 1){
+    print(paste0("Multiple gene symbols match the ID ", ID))
     ID.row
   }
 }
@@ -262,6 +263,7 @@ plot.A4V = function(ID){
     if(nrow(ID.row) != 1
        | length(intersect(GeneIDKey$FBgn, ID)) > 1
        | length(intersect(GeneIDKey$Symbol, ID)) > 1){
+      print(paste0("Multiple gene symbols match the ID ", ID))
       ID.row
     }
   }
@@ -364,6 +366,7 @@ plot.metab = function(metabID){
     }
     
     if(length(ID.row) != 1 | length(intersect(row.names(norm.data), metabID)) > 1){
+      print(paste0("Multiple metabolites match the ID ", ID))
       norm.data[ID.row,]
     }
     
@@ -470,6 +473,7 @@ plot.SC = function(gene.name){
     }
     
     if(nrow(ID.row) != 1 | length(intersect(gene.name, SCdata$Gene.name)) > 1){
+      print(paste0("Multiple gene symbols match the ID ", ID))
       ID.row
     }
   }
@@ -513,6 +517,7 @@ plot.gbbOE = function(ID){
     }
     
     if(nrow(ID.row) != 1){
+      print(paste0("Multiple gene symbols match the ID ", ID))
       ID.row
     }
   }
@@ -552,6 +557,7 @@ plot.gbbKO = function(ID){
     }
     
     if(nrow(ID.row) != 1){
+      print(paste0("Multiple gene symbols match the ID ", ID))
       ID.row
     }
   }

### 2025-01-29 Functions_OmicsQuickPlotFunctions.R
fixed level issue in plot.G85R function

@@ -67,6 +67,7 @@ serpe.glia.names = as.character(read.csv(paste0(git.dir, "Serpe%202024%20GliaSub
 
 ##Function to plot all G85R groups
 plot.G85R = function(ID){
+  
   ID.row = GeneIDKey[c(grep(ID, GeneIDKey$FBgn),
                        grep(ID, GeneIDKey$Symbol)),]
   
@@ -89,9 +90,11 @@ plot.G85R = function(ID){
       
       
       
-      gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), condition = TKT.groups$Group, group = paste0(TKT.groups$Genotype, TKT.groups$Sex))
+      gene = data.frame(cpm = as.numeric(TKT.cpm[FBgn,]), 
+                        condition = TKT.groups$Group, 
+                        group = paste0(TKT.groups$Genotype, TKT.groups$Sex))
       
-      gene$group = factor(gene$group, levels = c("WT.f", "GR.F", "WT.M", "GR.M"))
+      gene$group = factor(gene$group, levels = c("WTF", "GRF", "WTM", "GRM"))
       gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                          'GR.F', "TktDfGR.F", "TktOEGR.F",
                                                          'WT.M', "TktDfWT.M", "TktOEWT.M",

### 2025-01-29 Functions_OmicsQuickPlotFunctions.R
improved functions

@@ -136,7 +136,7 @@ plot.G85R = function(ID){
                y=gene$cpm,
                cex=1,
                pch=21,
-               bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
+               bg=c("darkgreen", 'firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
         
         axis(side = 1,
              at = 1:12,
@@ -255,7 +255,7 @@ plot.A4V = function(ID){
         points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
         legend('topright',
                inset=c(-0.275,0),
-               legend = c('Silent F', 'A4V F', 'Silent M', 'A4V M', 'Silent M'), 
+               legend = c('Silent F', 'A4V F', 'Silent M', 'A4V M'), 
                fill = c('firebrick', "gold", "darkgreen", "dodgerblue"),
                cex = .65,
                bty = 'n',
@@ -295,14 +295,15 @@ plot.metab = function(metabID){
       
       metab = data.frame(data = as.numeric(norm.data[metab,]), 
                          group = colnames(norm.data), 
-                         geno = colnames(norm.data))
+                         geno = "WT")
       
       
       metab$group = factor(metab$group, levels = c("WT", "TktDfWT", "TktOEWT",
-                                                   "GR", "TktDfGR", "TktOEGR"))
+                                                   "G85R", "TktDfGR", "TktOEGR"))
       
-      metab$geno = factor(substr(metab$group, (nchar(as.character(metab$group)) -1), nchar(as.character(metab$group))), 
-                          levels = c("WT", "GR"))
+      metab$geno[grep("G", metab$group)] = "G85R"
+      metab$geno = factor(metab$geno, 
+                          levels = c("WT", "G85R"))
       
       par(mar = c(5,7,5,2))
       plot(x = NA,

### 2025-01-29 Functions_OmicsQuickPlotFunctions.R
another tweak

@@ -21,11 +21,11 @@ A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
 
 
 
-gbbOE = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
+gbbOE.cpmdata = read.csv(paste0(git.dir, "gbbOE_CountTable.csv"), row.names = 1)
 
 gbbOE.groups = read.csv(paste0(git.dir, "gbbOE_Metadata.csv"), row.names = 1)
 
-gbbOE = gbbOE[,row.names(gbbOE.groups)]
+gbbOE.cpmdata = gbbOE.cpmdata[,row.names(gbbOE.groups)]
 gbbOE.groups$group = paste0(gbbOE.groups$genotype, "_",gbbOE.groups$stage)
 
 gbbKO.cpmdata = read.csv(paste0(git.dir, "gbbKO.cpmdata.csv"), row.names = 1)

### 2025-01-30 SerpeSCdata.Rmd
final SC function addition

@@
 
+library(gplots)
+
 ##manually currated
@@
 serpe.glia.names = as.character(read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Serpe 2024 GliaSubtypes.csv", row.names = 1, header = F)[1,])
-
-```
-
-```{r echo = F}
-
-plot.serpe = function(gene.name){
-serpe.annotated.gene = data.frame(level = as.numeric(serpe[gene.name,]),
-                                  cluster = serpe.annotated.names,
-                                  color = "darkgreen")
-
-serpe.mn.gene = data.frame(level = as.numeric(serpe.mn[gene.name,]),
-                           cluster = colnames(serpe.mn),
-                           color = "brown")
-
-serpe.inter.gene = data.frame(level = as.numeric(serpe.inter[gene.name,]),
-                              cluster = colnames(serpe.inter),
-                              color = "gold")
-
-serpe.glia.gene = data.frame(level = as.numeric(serpe.glia[gene.name,]),
-                             cluster = serpe.glia.names,
-                             color = "steelblue")
-
-serpe.all = rbind(serpe.annotated.gene,
-                  rbind(serpe.mn.gene,
-                        rbind(serpe.inter.gene,
-                              serpe.glia.gene)))
-
-par(mar = c(4, 13, 4, 8))
-barplot(as.numeric(serpe.all[,"level"])-1,
-        names.arg = serpe.all$cluster,
-        las = 2, 
-        beside = T,
-        col = serpe.all$color,
-        cex.names = .75,
-        main = gene.name,
-        horiz = T,
-        xlab = "Mean Expression Level per Cell")
-      legend(x = max(as.numeric(serpe.all[,"level"])-1),
-             y = 125,
-             pch = 21,
-             legend = c("Glia", "Interneurons", "Motor Neurons", "Manually Curated"),
-             pt.bg = c("steelblue", "gold", "brown", "darkgreen"),
-             bty = "n",
-             xpd = T,
-             pt.cex = 1.5,
-             y.intersp = 1)
-}
-```
-
-```{r echo = F, fig.width= 10, fig.height=15}
-
-##gene.name = "gbb"
-
-##plot.serpe(gene.name)
 
@@
 
-  #serpe.all$level = serpe.all$level - 1
-
-  #highlight = rep(0, nrow(serpe.all))
-  #highlight[(serpe.all$level > highlight.cutoff*(mean(serpe.all$level)))] = 1
-  #serpe.all$highlight = serpe.all$level * highlight
-
-  #serpe.all$color[highlight > 0 & serpe.all$color == "lightgreen"] = "darkgreen"
-  #serpe.all$color[highlight > 0 & serpe.all$color == "thistle1"] = "brown"
-  #serpe.all$color[highlight > 0 & serpe.all$color == "lightyellow"] = "gold"
-  #serpe.all$color[highlight > 0 & serpe.all$color == "lightcyan"] = "royalblue"
   serpe.all$color[serpe.all$level < 1.5] = "darkgrey"
-
-  #label.colors = serpe.all$color
-
-  #label.colors[serpe.all$color == "darkgreen"] = "darkgreen"
-  #label.colors[serpe.all$color == "brown"] = "brown"
-  #label.colors[serpe.all$color == "gold"] = "gold"
-  #label.colors[serpe.all$color == "royalblue"] = "royalblue"
-  #serpe.all$label.colors = label.colors
 
@@
 
-gene.name = "put"
+gene.name = "burs"
 
@@
 ```
+
+```{r echo = F, fig.width=16, fig.height=10}
+
+heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")
+
+serpe.heatmap = function(heat.genes){
+heat.data = na.omit(cbind(serpe[heat.genes,],
+                          cbind(serpe.mn[heat.genes,],
+                                cbind(serpe.inter[heat.genes,], serpe.glia[heat.genes,]))))
+
+heat.data = apply(heat.data, MARGIN = 2, as.numeric)
+#heat.data = log2(heat.data)
+row.names(heat.data) = heat.genes
+
+#heat.data[heat.data == 0] = NA
+
+Cluster.id = c(serpe.annotated.names,
+               colnames(serpe.mn),
+               colnames(serpe.inter),
+               serpe.glia.names)
+
+Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)),
+                       rep("brown", ncol(serpe.mn)),
+                       rep("orange", ncol(serpe.inter)),
+                       rep("steelblue", length(serpe.glia.names)))
+
+heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
+
+numcols = 100
+
+max.break = log2(max(heat.data))
+
+if(max.break > 7){
+  max.break = 7
+}
+
+color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
+
+heatmap.2(heat.data,
+        Colv = NA,
+        #Rowv = NA,
+        labCol = Cluster.id,
+        scale = 'none',
+        ColSideColors = Cluster.labelcolor,
+        trace = "none",
+        col = heat.colors(numcols),
+        dendrogram = "none",
+        na.color = "white",
+        key.title = "Mean Expression",
+        colCol = Cluster.labelcolor,
+        margins = c(10, 5), 
+        colsep = c(18, 46, 95),
+        sepcolor = "black",
+        breaks = color.breaks)
+legend("left",
+       title = "Cell Types",
+       legend = c("Manually Currated", "Motor Neurons", "Interneurons", "Glia"),
+       fill = c("darkgreen", "brown", "orange", "steelblue"),
+       xpd = T)
+
+}
+
+#library(corrplot)
+#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))
+
+```
+
+```{r echo = F, fig.width=16, fig.height=10}
+
+heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")##, "trio")#, "Rac1")
+
+heat.data = na.omit(cbind(serpe.mn[heat.genes,],
+                          cbind(serpe.inter[heat.genes,], serpe.glia[heat.genes,])))
+
+heat.data = apply(heat.data, MARGIN = 2, as.numeric)
+#heat.data = log2(heat.data)
+row.names(heat.data) = heat.genes
+
+#heat.data[heat.data == 0] = NA
+
+Cluster.id = c(colnames(serpe.mn),
+               colnames(serpe.inter),
+               serpe.glia.names)
+
+Cluster.labelcolor = c(rep("brown", ncol(serpe.mn)),
+                       rep("orange", ncol(serpe.inter)),
+                       rep("steelblue", length(serpe.glia.names)))
+
+heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
+
+numcols = 100
+
+max.break = log2(max(heat.data))
+
+if(max.break > 7){
+  max.break = 7
+}
+
+color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
+
+heatmap.2(heat.data,
+        Colv = NA,
+        #Rowv = NA,
+        labCol = Cluster.id,
+        scale = 'none',
+        ColSideColors = Cluster.labelcolor,
+        trace = "none",
+        col = heat.colors(numcols),
+        dendrogram = "none",
+        na.color = "white",
+        key.title = "Mean Expression",
+        colCol = Cluster.labelcolor,
+        margins = c(10, 5), 
+        colsep = c(28, 77),
+        sepcolor = "black",
+        breaks = color.breaks)
+legend("left",
+       title = "Cell Types",
+       legend = c("Motor Neurons", "Interneurons", "Glia"),
+       fill = c("brown", "orange", "steelblue"),
+       xpd = T)
+#library(corrplot)
+#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))
+
+```
+
+```{r echo = F, fig.width=16, fig.height=10}
+
+heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")
+
+heat.data = na.omit(serpe[heat.genes,])
+
+heat.data = apply(heat.data, MARGIN = 2, as.numeric)
+#heat.data = log2(heat.data)
+row.names(heat.data) = heat.genes
+
+#heat.data[heat.data == 0] = NA
+
+Cluster.id = c(serpe.annotated.names)
+
+Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)))
+
+heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
+
+numcols = 100
+
+max.break = log2(max(heat.data))
+
+if(max.break > 7){
+  max.break = 7
+}
+
+color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
+
+heatmap.2(heat.data,
+        Colv = NA,
+        #Rowv = NA,
+        labCol = Cluster.id,
+        scale = 'none',
+        ColSideColors = Cluster.labelcolor,
+        trace = "none",
+        col = heat.colors(numcols),
+        dendrogram = "none",
+        na.color = "white",
+        key.title = "Mean Expression",
+        colCol = Cluster.labelcolor,
+        margins = c(10, 5), 
+        #colsep = c(18, 46, 95),
+        #sepcolor = "black",
+        breaks = color.breaks)
+legend("left",
+       title = "Cell Types",
+       legend = c("Manually Currated"),
+       fill = c("darkgreen"),
+       xpd = T)
+#library(corrplot)
+#corrplot(heat.data, is.corr = F, col =COL2("RdBu", 200))
+
+```

### 2025-01-30 Functions_OmicsQuickPlotFunctions.R
library

@@ -3,6 +3,10 @@
 
 ##library(plotly)
 
+if(!require(gplots)){
+  install.packages("gplots")
+}
+
 library(gplots)
 
 ##load all files from github

### 2025-01-30 Shortcuts_OmicsQuickPlotFunctions.Rmd
gbbKO
serpe data
functions update
updated gene plot functions
fixed level issue in plot.G85R function
improved functions
another tweak
update

@@
 ---
-title: "Specifgic Gene or Metabolite Levels"
+title: "Specific Gene or Metabolite Levels"
 author: "John Santiago"
@@
 
-ID = "ETHR"
+ID = "gbb"
 
@@
 
-```{r echo = F}
+```{r echo = F, fig.width= 10, fig.height=16}
 
@@
 
-gene.name = 'CCAP'
+gene.name = "gbb"
 
-plot.SC(gene.name)
+plot.serpe.allclusters(gene.name)
+
+```
+
+```{r echo = F, fig.width=16, fig.height=10}
+
+## Plot expression of a gene set from Single Cell RNAseq experiment
+## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)
+
+heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")
+
+serpe.heatmap(heat.genes)
 
@@
 
-##ID = "0000018"
+ID = "Arc1"
 

### 2025-01-30 Functions_OmicsQuickPlotFunctions.R

@@ -55,7 +55,8 @@ colnames(norm.data) = Metab.Meta[colnames(norm.data), "Genotypes"]
 
 
 ##manually currated
-serpe = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Nguyen Serpe 2024 scRNA-seq VNC.csv", row.names = 1)
+serpe = read.csv(paste0(git.dir, "Nguyen%20Serpe%202024%20scRNA-seq%20VNC.csv"), row.names = 1)
+
 
 serpe.glia = read.csv(paste0(git.dir, "Serpe%202024%20GliaSubtypes.csv"), row.names = 1)
 

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
making links

@@ -26,1169 +26,32 @@ library(rrvgo)
 library(pathview)
 library(VennDiagram)
 
-A4V.cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)
-A4V.meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)
-A4V.FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)
-A4V.FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)
-A4V.meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
 
-A4V.comparekey = setNames(colnames(A4V.FDR),
-                          c('A3FHvS3FH', 'A3MHvS3MH', 'A9FHvS9FH', 'A9MHvS9MH', 'A40FHvS40FH',
-                            'A3FHvA9FH', 'S3FHvS9FH', 'A3MHvA9MH', 'S3FHvS9MH',
-                            'A9FHvA40FH', 'S9FHvS40FH', 'A3FHvA40FH', 'S3FHvS40FH',
-                            
-                            'A3FTvS3FT', 'A3MTvS3MT', 'A9FTvS9FT', 'A9MTvS9MT', 'A40FTvS40FT',
-                            'A3FTvA9FT', 'S3FTvS9FT', 'A3MTvA9MT', 'S3FTvS9MT',
-                            'A9FTvA40FT', 'S9FTvS40FT', 'A3FTvA40FT', 'S3FTvS40FT',
-                            
-                            'A3FAvS3FA', 'A3MAvS3MA', 'A9FAvS9FA', 'A9MAvS9MA', 'A40FAvS40FA',
-                            'A3FAvA9FA', 'S3FAvS9FA', 'A3MAvA9MA', 'S3FAvS9MA',
[…]

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
made .csv versions of .rds files

@@ -41,16 +41,13 @@ G85R.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
 
 G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
 
-genesingo = read.csv(paste0(git.dir, "genesingo.RData"))
+genesingo = read.csv(paste0(git.dir, "genesingo.csv"))
 
-GenesInKegg = read.csv(paste0(git.dir, "kegg.symbol2path.RData"))
+GenesInKegg = read.csv(paste0(git.dir, "kegg.symbol2path.csv"))
 
 KEGG.Names = read.csv(paste0(git.dir, "KEGG.names.csv"), row.names = 1)
 
 GO.Names = read.csv(paste0(git.dir, "GO.names.csv"), row.names = 1)
-
-
-
 
 
 G85R.data = function(Geno1, Geno2, Geno3, Geno4,

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -41,9 +41,9 @@ G85R.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
 
 G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
 
-genesingo = read.csv(paste0(git.dir, "genesingo.csv"))
+genesingo = read.csv(paste0(git.dir, "genesingo.csv"), row.names = 1)
 
-GenesInKegg = read.csv(paste0(git.dir, "kegg.symbol2path.csv"))
+GenesInKegg = read.csv(paste0(git.dir, "kegg.symbol2path.csv"), row.names = 1)
 
 KEGG.Names = read.csv(paste0(git.dir, "KEGG.names.csv"), row.names = 1)
 
@@ -397,7 +397,7 @@ G85R.KEGG20 = function(cat.data, plot.data, usecats = 'sigs'){
   i = 1
   while(i <= nrow(data)){
     kegg.id = data$category[i]
-    kegg.genes = names(GenesInKegg[grep(kegg.id, GenesInKegg)])
+    kegg.genes = GenesInKegg$Gene[grep(kegg.id, GenesInKegg$KEGG)]
     kegg.genes = GeneIDKey[GeneIDKey$Symbol %in% kegg.genes, "FBgn"]
     kegg.genes = intersect(kegg.genes, names(FC.data))
     sig.kegg.genes = intersect(kegg.genes, sigs)
@@ -484,7 +484,7 @@ G85R.plotkegg.genes = function(specific.kegg, plot.data){
   
   kegg.id = row.names(KEGG.Names)[c(grep(specific.kegg, KEGG.Names), 
                                     grep(specific.kegg, row.names(KEGG.Names)))]
-  kegg.genes = names(GenesInKegg[grep(kegg.id, GenesInKegg)])
+  kegg.genes = GenesInKegg$Gene[grep(kegg.id, GenesInKegg$KEGG)]
   volcano.data$Color = 'honeydew'
   #row.names(volcano.data) = volcano.data$Symbol
   volcano.data[volcano.data$Symbol %in% kegg.genes, 'Color'] = 'deeppink'
@@ -674,7 +674,7 @@ G85R.comparekegg.genes = function(specific.kegg, plot.data){
   
   kegg.id = row.names(KEGG.Names)[c(grep(specific.kegg, KEGG.Names), 
                                     grep(specific.kegg, row.names(KEGG.Names)))]
[…]

### 2025-02-03 G85R GOandKEGGTermEnrichment.Rmd
fixed a warning

@@
 ```{r setup, include=FALSE}
+
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r echo = F, message = F}
-
-source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
 
@@
 
-temp.FC = colnames(G85R.FC)
-temp1 = temp.FC[grep(Geno1, temp.FC)]
+##Conditions for second comparison
+Geno3 = "GR"
+TKT3 = "C"
+Sex3 = "M"
 
-if(Sex1 != Sex2){
-  temp1 = temp1[intersect(grep(Sex1, temp1), grep(Sex2, temp1))]
-  temp1 = temp1[grep(Geno1)]
-}
+Geno4 = "WT"
+TKT4 = "C"
+Sex4 = "M"
 
-if(Sex1 == Sex2){
-  if(Geno1 == Geno2){
-  temp1 = temp1[grep(setdiff(c("WT", "GR"), c(Geno1, Geno2)), temp1, invert = T)]
-  }
+```
 
-  if(Geno1 != Geno2){
-  temp1 = temp1[intersect(grep(Geno1, temp1), grep(Geno2, temp1))]
-  }
+```{r echo = F, message = F}
 
-  temp1 = temp1[intersect(grep(TKT1, temp1), grep(TKT2, temp1))]
+source('/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R')
 
-  temp1 = temp1[grep(Sex1, temp1)]
-}
+plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
+                      Sex1, Sex2, Sex3, Sex4,
+                      TKT1, TKT2, TKT3, TKT4)
 
-FC = G85R.FC[temp1]
-FDR = G85R.FC[temp1]
+```
 
-Variable.Condition = "GRFC" 
-Control.Condition = "WTFC"
-secondary.Variable.Condition = "GRMC"
-secondary.Control.Condition = "WTMC"
+```{r echo = F}
 
-comparison = paste0(Variable.Condition, 'v', Control.Condition)
-secondary.comparison = paste0(secondary.Variable.Condition, 'v', secondary.Control.Condition)
+##Uses data from primary comparison
+##Plots genes with an FDR <= 0.05
+##point size is relative to maximum mean expression in the two conditions
 
-if(length(intersect(comparison, names(A4V.comparekey))) == 1){
-  FC = A4V.FC[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
-  FDR = A4V.FDR[,c(A4V.comparekey[comparison], A4V.comparekey[secondary.comparison])]
-  mean.data = A4V.meancpm[,c(Variable.Condition, Control.Condition, 
-                             secondary.Variable.Condition, secondary.Control.Condition)]
-  metab.data = 'none'
-}
+G85R.volcano(plot.data)
 
-if(length(intersect(comparison, names(G85R.comparekey))) == 1){
-  FC = G85R.FC[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
-  FDR = G85R.FDR[,c(G85R.comparekey[comparison], G85R.comparekey[secondary.comparison])]
-  mean.data = G85R.meancpm[,c(Variable.Condition, Control.Condition, 
-                              secondary.Variable.Condition, secondary.Control.Condition)]
-  metab.data = G85R.metab.comparekey[c(comparison, secondary.comparison)]
-  if(G85R.metab.comparekey[c(comparison)] == G85R.metab.comparekey[c(secondary.comparison)]){
-    metab.data = G85R.metab.comparekey[c(comparison)]
-  }
-}
+```
 
-subset = F
+```{r echo = F}
 
-if(subset == T){
-  geneset = biomarkers
-  FC[setdiff(row.names(FC),geneset),] = 1 
-  FDR[setdiff(row.names(FDR),geneset),] = 1 
-}
+##Uses data from primary comparison
+##point size is relative to max mean expression in any condition
+##grey points indicate less than 1 fold difference between the comparisons
+G85R.compare.genes(plot.data)
 
@@
 ##point size is relative to mean expression in variable condition
-volcano(FC, FDR, mean.data)
+G85R.DEG.venn(plot.data)
 
@@
 
-```{r echo = F}
-
-##Uses data from primary comparison
-##point size is relative to mean expression in variable condition
-compare.genes(FC, FDR, mean.data)
-
-```
-
-```{r echo = F}
-#library(heatmaply)
-#hmdata = mean.data[geneset,]
-#row.names(hmdata) = GeneIDKey[geneset, 'Symbol']
-#hmdata = na.omit(hmdata)
-
-#heatmaply(hmdata,
-#          scale = 'row',
-#          Colv = F)
-
-```
-
-```{r echo = F}
-
-##Uses data from primary comparison
-##point size is relative to mean expression in variable condition
-DEG.venn(FDR, FC)
-
-```
-
-```{r echo = F, include = F}
+```{r echo = F, include = F, warning = F}
 
 ####Uses sigDEGs from primary comparison
-cat.data = Enrichment(FDR)
+cat.data = G85R.Enrichment(plot.data)
 
@@
 ##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
-##can also just type 'sigs.only' 
+##can also just type 'sigs' 
 usecats=c(1:20)
-#usecats = 'sigs.only'
+#usecats = 'sigs'
 
-KEGG20(cat.data, FC, FDR, usecats)
+G85R.KEGG20(cat.data, plot.data, usecats)
 
@@
 
-plotkegg.genes(specific.kegg, FC, FDR, mean.data)
+G85R.plotkegg.genes(specific.kegg, plot.data)
 
@@
 
-KEGG.diagram(PathwayID, FC, use, metab.data)
+G85R.KEGG.diagram(PathwayID, plot.data, use, sigs.only = F)
 
@@
 
-comparekegg.genes(specific.kegg, FC, FDR, mean.data)
+G85R.comparekegg.genes(specific.kegg, plot.data)
 
@@
 
-GO20(cat.data, GO.ontology, FC, FDR, usecats)
+G85R.GO20(cat.data, GO.ontology, plot.data, usecats)
 
@@
 
-plotgo.genes(specific.go, FC, FDR, mean.data)
+G85R.plotgo.genes(specific.go, plot.data)
 
@@
 
-comparego.genes(specific.go, FC, FDR, mean.data)
+G85R.comparego.genes(specific.go, plot.data)
 
@@
 ##a parent category generated in the treemapPlot function
-parent.category = 'membrane lipid biosynthetic process'
+parent.category = 'neurogenesis'
 
-plotparentcat.genes(parent.category, FC, FDR, mean.data)
+G85R.plotparentcat.genes(parent.category, plot.data)
 
@@
 
-compareparent.genes(parent.category, FC, FDR, mean.data)
+G85R.compareparent.genes(parent.category, plot.data)
 ##dot size is relative to the max FDR of either condition

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R

@@ -1016,7 +1016,7 @@ G85R.plotparentcat.genes = function(parent.category, plot.data){
   i=1
   while(i<=length(GOterm.genes)){
     goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
-    genesinparent = genesingo$Gene[genesingo$GO == goinparent]
+    genesinparent = genesingo$Gene[genesingo$GO %in% goinparent]
     GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
     i = i +1
   }
@@ -1097,7 +1097,7 @@ G85R.compareparent.genes = function(parent.category, plot.data){
   i=1
   while(i<=length(GOterm.genes)){
     goinparent = rt[grep(names(GOterm.genes)[i], rt$parent),'go']
-    genesinparent = genesingo$Gene[genesingo$GO == goinparent]
+    genesinparent = genesingo$Gene[genesingo$GO %in% goinparent]
     GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
     i = i +1
   }

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -990,7 +990,7 @@ tree = function(cat.data, GO.ontology){
   return(reducedTerms)
 }
 
-G85R.plotparentcat.genes = function(parent.category, plot.data){
+G85R.plotparentcat.genes = function(parent.category, plot.data, sigs.only = T){
   
   FC.data = plot.data[, grep("lFC", colnames(plot.data))]
   colnames(FC.data) = substr(colnames(FC.data), 1, (nchar(colnames(FC.data)) - 5))
@@ -1051,6 +1051,11 @@ G85R.plotparentcat.genes = function(parent.category, plot.data){
     volcano.data$Color[volcano.data$FDR < -log2(.05)] = 'honeydew'
   }
   
+  if(sigs.only == T){
+    volcano.data = volcano.data[volcano.data$FDR >= -log(.05), ]
+  }
+  
+  
   fig = plot_ly(data = volcano.data,
                 x = ~FC,
                 y = ~FDR,
@@ -1071,7 +1076,7 @@ G85R.plotparentcat.genes = function(parent.category, plot.data){
   return(fig)
 }
 
-G85R.compareparent.genes = function(parent.category, plot.data){
+G85R.compareparent.genes = function(parent.category, plot.data, sigs.only = T){
   
   FC.data = plot.data[, grep("lFC", colnames(plot.data))]
   colnames(FC.data) = substr(colnames(FC.data), 1, (nchar(colnames(FC.data)) - 5))
@@ -1129,6 +1134,12 @@ G85R.compareparent.genes = function(parent.category, plot.data){
   data$size = 2.5*apply(data[,c('FDR1', 'FDR2')], MARGIN = 1, max)
   data$size[data$size < -2.5*log2(.05)] = 5
   data = na.omit(data)
+  
+  if(sigs.only == T){
+    maxFDR = apply(data[,c("FDR1", "FDR2")], MARGIN = 1, max)
+    data = data[maxFDR >= -log(.05), ]
+  }
+  
   
   fig = plot_ly(data = data,
                 x = ~FC1,

### 2025-02-03 myfile.Rmd
fixed link

<!DOCTYPE html>
<html
  lang="en"

  data-color-mode="auto" data-light-theme="light" data-dark-theme="dark"
  data-a11y-animated-images="system" data-a11y-link-underlines="true"

  >

  <head>
    <meta charset="utf-8">
  <link rel="dns-prefetch" href="https://github.githubassets.com">
  <link rel="dns-prefetch" href="https://avatars.githubusercontent.com">
  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">
  <link rel="preconnect" href="https://github.githubassets.com" crossorigin>
  <link rel="preconnect" href="https://avatars.githubusercontent.com">

  <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/light-7aa84bb7e11e.css" /><link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/dark-f65db3e8d171.css" /><link data-color-theme="dark_dimmed" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/dark_dimmed-a8258e3c6dda.css" /><link data-color-theme="dark_high_contrast" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/dark_high_contrast-7e97d834719c.css" /><link data-color-theme="dark_colorblind" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/dark_colorblind-01d869f460be.css" /><link data-color-theme="light_colorblind" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/light_colorblind-534f3e971240.css" /><link data-color-theme="light_high_contrast" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/light_high_contrast-a8cc7d138001.css" /><link data-color-theme="light_tritanopia" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/light_tritanopia-35e9dfdc4f9f.css" /><link data-color-theme="dark_tritanopia" crossorigin="anonymous" media="all" rel="stylesheet" data-href="https://github.githubassets.com/assets/dark_tritanopia-cf4cc5f62dfe.css" />

    <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/primer-primitives-d9abecd14f1e.css" />
    <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/primer-93aded0ee8a1.css" />
    <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/global-d579f4a5b443.css" />
    <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/github-8049f990d299.css" />
  <link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/repository-4fce88777fa8.css" />
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/code-0210be90f4d3.css" />

  <script type="application/json" id="client-env">{"locale":"en","featureFlags":["bypass_copilot_indexing_quota","copilot_new_references_ui","copilot_beta_features_opt_in","copilot_chat_repo_custom_instructions_preview","copilot_chat_retry_on_error","copilot_chat_persist_submitted_input","copilot_conversational_ux_history_refs","copilot_chat_shared_chat_input","copilot_chat_shared_topic_indicator","copilot_chat_shared_repo_sso_banner","copilot_editor_upsells","copilot_free_limited_user","copilot_implicit_context","copilot_no_floating_button","copilot_smell_icebreaker_ux","experimentation_azure_variant_endpoint","failbot_handle_non_errors","geojson_azure_maps","ghost_pilot_confidence_truncation_25","ghost_pilot_confidence_truncation_40","github_models_o3_mini_streaming","hovercard_accessibility","issues_react_remove_placeholders","issues_react_blur_item_picker_on_close","issues_react_include_bots_in_pickers","marketing_pages_search_explore_provider","react_keyboard_shortcuts_dialog","remove_child_patch","report_hydro_web_vitals","sample_network_conn_type","issues_react_create_milestone","issues_react_cache_fix_workaround","lifecycle_label_name_updates"]}</script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/wp-runtime-ea3cb3d11020.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_oddbird_popover-polyfill_dist_popover_js-9da652f58479.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_arianotify-polyfill_ariaNotify-polyfill_js-node_modules_github_mi-3abb8f-d7e6bc799724.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_failbot_failbot_ts-25697e0f4c47.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/environment-04ca94cb6e8a.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_primer_behaviors_dist_esm_index_mjs-0dbb79f97f8f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_selector-observer_dist_index_esm_js-f690fd9ae3d5.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_relative-time-element_dist_index_js-f6da4b3fa34c.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_auto-complete-element_dist_index_js-node_modules_github_catalyst_-8e9f78-a74b4e0a8a6b.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_text-expander-element_dist_index_js-78748950cb0c.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_filter-input-element_dist_index_js-node_modules_github_remote-inp-b5f1d7-a1760ffda83d.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_markdown-toolbar-element_dist_index_js-ceef33f593fa.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_file-attachment-element_dist_index_js-node_modules_primer_view-co-c44a69-f0c8a795d1fd.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/github-elements-b487d8db3717.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/element-registry-0237e7f19fec.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_braintree_browser-detection_dist_browser-detection_js-node_modules_githu-bb80ec-72267f4e3ff9.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_lit-html_lit-html_js-be8cb88f481b.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_mini-throttle_dist_index_js-node_modules_morphdom_dist_morphdom-e-7c534c-a4a1922eb55f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_turbo_dist_turbo_es2017-esm_js-e3cbe28f1638.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_remote-form_dist_index_js-node_modules_delegated-events_dist_inde-893f9f-6cf3320416b8.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_color-convert_index_js-e3180fe3bcb3.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_quote-selection_dist_index_js-node_modules_github_session-resume_-69cfcc-833249ee3034.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_updatable-content_updatable-content_ts-439f48470426.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/app_assets_modules_github_behaviors_task-list_ts-app_assets_modules_github_sso_ts-ui_packages-900dde-e8bb0b049301.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/app_assets_modules_github_sticky-scroll-into-view_ts-5316a27f9573.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/app_assets_modules_github_behaviors_ajax-error_ts-app_assets_modules_github_behaviors_include-87a4ae-0a6bb0ce2586.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/app_assets_modules_github_behaviors_commenting_edit_ts-app_assets_modules_github_behaviors_ht-83c235-42e06545c1fa.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/behaviors-6af14f7fc2ee.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_delegated-events_dist_index_js-node_modules_github_catalyst_lib_index_js-f6223d90c7ba.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/notifications-global-bd5619ba39ac.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_mini-throttle_dist_index_js-node_modules_github_catalyst_lib_inde-dbbea9-26cce2010167.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/code-menu-bfd00ac7c892.js"></script>

  <script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/primer-react-4f904282b093.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/react-core-5257d05d161f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/react-lib-f09868a8643f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/octicons-react-611691cca2f6.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_emotion_is-prop-valid_dist_emotion-is-prop-valid_esm_js-node_modules_emo-62da9f-2df2f32ec596.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_mini-throttle_dist_index_js-node_modules_stacktrace-parser_dist_s-e7dcdd-f7cc96ebae76.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_oddbird_popover-polyfill_dist_popover-fn_js-55fea94174bf.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_dompurify_dist_purify_js-b89b98661809.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_lodash-es__Stack_js-node_modules_lodash-es__Uint8Array_js-node_modules_l-4faaa6-4a736fde5c2f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_lodash-es__baseIsEqual_js-8929eb9718d5.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_react-reverse-portal_dist_web_index_js-node_modules_primer_live-region-e-18c5ad-0b67a5a18b33.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_aria-live_aria-live_ts-ui_packages_promise-with-resolvers-polyfill_promise-with-r-014121-adb7f840e9e5.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_paths_index_ts-a30153db44f6.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_ref-selector_RefSelector_tsx-9f1e57bbb696.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_commit-attribution_index_ts-ui_packages_commit-checks-status_index_ts-ui_packages-530254-a7bdad87b7b4.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_code-view-shared_hooks_use-canonical-object_ts-ui_packages_code-view-shared_hooks-495298-d9d5efcddd99.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_copilot-chat_utils_copilot-chat-types_ts-ui_packages_repos-file-tree-view_repos-f-894be6-2f648fa9490a.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/app_assets_modules_github_blob-anchor_ts-ui_packages_code-nav_code-nav_ts-ui_packages_filter--8253c1-1320af121fa2.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_diffs_diff-parts_ts-b01c1ac6f203.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/react-code-view-e702702f4734.js"></script>
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/primer-react.1275b2aabc5faff7be57.module.css" />
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/react-code-view.ab7d8fac328c00e5e0cc.module.css" />

  <script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/notifications-subscriptions-menu-7eba7d01e0ba.js"></script>
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/primer-react.1275b2aabc5faff7be57.module.css" />
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/notifications-subscriptions-menu.1bcff9205c241e99cff2.module.css" />

  <title>WhartonLab/G85R GOandKEGGTermEnrichment.Rmd at master · johncsantiago/WhartonLab · GitHub</title>

  <meta name="route-pattern" content="/:user_id/:repository/blob/*name(/*path)" data-turbo-transient>
  <meta name="route-controller" content="blob" data-turbo-transient>
  <meta name="route-action" content="show" data-turbo-transient>

  <meta name="current-catalog-service-hash" content="f3abb0cc802f3d7b95fc8762b94bdcb13bf39634c40c357301c4aa1d67a256fb">

  <meta name="request-id" content="527A:2D1890:763472:A6139F:67A10520" data-pjax-transient="true"/><meta name="html-safe-nonce" content="5d4717541431eeb35e061369830ebefe101e79bcb17f34f9a298ee5ea100ed3c" data-pjax-transient="true"/><meta name="visitor-payload" content="eyJyZWZlcnJlciI6IiIsInJlcXVlc3RfaWQiOiI1MjdBOjJEMTg5MDo3NjM0NzI6QTYxMzlGOjY3QTEwNTIwIiwidmlzaXRvcl9pZCI6IjUwMjY1NDYzNjQ1MDk2NTIyNTYiLCJyZWdpb25fZWRnZSI6ImlhZCIsInJlZ2lvbl9yZW5kZXIiOiJpYWQifQ==" data-pjax-transient="true"/><meta name="visitor-hmac" content="72e28efc0fb87ca24293b07fa3e89a31531256fe0783789bbff5f0a89f7d6f09" data-pjax-transient="true"/>

    <meta name="hovercard-subject-tag" content="repository:652065041" data-turbo-transient>

  <meta name="github-keyboard-shortcuts" content="repository,source-code,file-tree,copilot" data-turbo-transient="true" />

  <meta name="selected-link" value="repo_source" data-turbo-transient>
  <link rel="assets" href="https://github.githubassets.com/">

    <meta name="google-site-verification" content="Apib7-x98H0j5cPqHWwSMm6dNU4GmODRoqxLiDzdx9I">

<meta name="octolytics-url" content="https://collector.github.com/github/collect" />

  <meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-turbo-transient="true" />

    <meta name="user-login" content="">

    <meta name="viewport" content="width=device-width">

      <meta name="description" content="Contribute to johncsantiago/WhartonLab development by creating an account on GitHub.">

      <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">

    <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
    <meta property="fb:app_id" content="1401488693436528">
    <meta name="apple-itunes-app" content="app-id=1477376905, app-argument=https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd" />

      <meta name="twitter:image" content="https://opengraph.githubassets.com/34050d6b9b05b9683112955dd9a2d8ff54e5d7545bfa645f3d53317d007cae20/johncsantiago/WhartonLab" /><meta name="twitter:site" content="@github" /><meta name="twitter:card" content="summary_large_image" /><meta name="twitter:title" content="WhartonLab/G85R GOandKEGGTermEnrichment.Rmd at master · johncsantiago/WhartonLab" /><meta name="twitter:description" content="Contribute to johncsantiago/WhartonLab development by creating an account on GitHub." />
  <meta property="og:image" content="https://opengraph.githubassets.com/34050d6b9b05b9683112955dd9a2d8ff54e5d7545bfa645f3d53317d007cae20/johncsantiago/WhartonLab" /><meta property="og:image:alt" content="Contribute to johncsantiago/WhartonLab development by creating an account on GitHub." /><meta property="og:image:width" content="1200" /><meta property="og:image:height" content="600" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="WhartonLab/G85R GOandKEGGTermEnrichment.Rmd at master · johncsantiago/WhartonLab" /><meta property="og:url" content="https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd" /><meta property="og:description" content="Contribute to johncsantiago/WhartonLab development by creating an account on GitHub." />

      <meta name="hostname" content="github.com">

        <meta name="expected-hostname" content="github.com">

  <meta http-equiv="x-pjax-version" content="c6215f87fd63ac21525a969dd87c6591539570da1056d475d87280da437a52a9" data-turbo-track="reload">
  <meta http-equiv="x-pjax-csp-version" content="ace39c3b6632770952207593607e6e0be0db363435a8b877b1f96abe6430f345" data-turbo-track="reload">
  <meta http-equiv="x-pjax-css-version" content="1176077845c9479908e07e5cf5cf240c66928ac47340d56f202a3cfb9fc04dd3" data-turbo-track="reload">
  <meta http-equiv="x-pjax-js-version" content="923f4ffd6d2be276e59d6be4a93c84674e92d424b9c4051afc7a3806c89c6780" data-turbo-track="reload">

  <meta name="turbo-cache-control" content="no-preview" data-turbo-transient="">

      <meta name="turbo-cache-control" content="no-cache" data-turbo-transient>

    <meta data-hydrostats="publish">
  <meta name="go-import" content="github.com/johncsantiago/WhartonLab git https://github.com/johncsantiago/WhartonLab.git">

  <meta name="octolytics-dimension-user_id" content="61519162" /><meta name="octolytics-dimension-user_login" content="johncsantiago" /><meta name="octolytics-dimension-repository_id" content="652065041" /><meta name="octolytics-dimension-repository_nwo" content="johncsantiago/WhartonLab" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="652065041" /><meta name="octolytics-dimension-repository_network_root_nwo" content="johncsantiago/WhartonLab" />

    <meta name="turbo-body-classes" content="logged-out env-production page-responsive">

  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">

  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">

  <link rel="mask-icon" href="https://github.githubassets.com/assets/pinned-octocat-093da3e6fa40.svg" color="#000000">
  <link rel="alternate icon" class="js-site-favicon" type="image/png" href="https://github.githubassets.com/favicons/favicon.png">
  <link rel="icon" class="js-site-favicon" type="image/svg+xml" href="https://github.githubassets.com/favicons/favicon.svg" data-base-href="https://github.githubassets.com/favicons/favicon">

<meta name="theme-color" content="#1e2327">
<meta name="color-scheme" content="light dark" />

  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">

  </head>

  <body class="logged-out env-production page-responsive" style="word-wrap: break-word;">
    <div data-turbo-body class="logged-out env-production page-responsive" style="word-wrap: break-word;">

    <div class="position-relative header-wrapper js-header-wrapper ">
      <a href="#start-of-content" data-skip-target-assigned="false" class="px-2 py-4 color-bg-accent-emphasis color-fg-on-emphasis show-on-focus js-skip-to-content">Skip to content</a>

      <span data-view-component="true" class="progress-pjax-loader Progress position-fixed width-full">
    <span style="width: 0%;" data-view-component="true" class="Progress-item progress-pjax-loader-bar left-0 top-0 color-bg-accent-emphasis"></span>
</span>

      <script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/ui_packages_ui-commands_ui-commands_ts-ac3420ecd15f.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/keyboard-shortcuts-dialog-4ac6f562b41b.js"></script>
<link crossorigin="anonymous" media="all" rel="stylesheet" href="https://github.githubassets.com/assets/primer-react.1275b2aabc5faff7be57.module.css" />

<react-partial
  partial-name="keyboard-shortcuts-dialog"
  data-ssr="false"
  data-attempted-ssr="false"
>

  <script type="application/json" data-target="react-partial.embeddedData">{"props":{"docsUrl":"https://docs.github.com/get-started/accessibility/keyboard-shortcuts"}}</script>
  <div data-target="react-partial.reactRoot"></div>
</react-partial>

<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/vendors-node_modules_github_remote-form_dist_index_js-node_modules_delegated-events_dist_inde-94fd67-73b675cf164a.js"></script>
<script crossorigin="anonymous" defer="defer" type="application/javascript" src="https://github.githubassets.com/assets/sessions-fc22c41247ca.js"></script>
<header class="HeaderMktg header-logged-out js-details-container js-header Details f4 py-3" role="banner" data-is-top="true" data-color-mode=light data-light-theme=light data-dark-theme=dark>
  <h2 class="sr-only">Navigation Menu</h2>

  <button type="button" class="HeaderMktg-backdrop d-lg-none border-0 position-fixed top-0 left-0 width-full height-full js-details-target" aria-label="Toggle navigation">
    <span class="d-none">Toggle navigation</span>
  </button>

  <div class="d-flex flex-column flex-lg-row flex-items-center px-3 px-md-4 px-lg-5 height-full position-relative z-1">
    <div class="d-flex flex-justify-between flex-items-center width-full width-lg-auto">
      <div class="flex-1">
        <button aria-label="Toggle navigation" aria-expanded="false" type="button" data-view-component="true" class="js-details-target js-nav-padding-recalculate js-header-menu-toggle Button--link Button--medium Button d-lg-none color-fg-inherit p-1">  <span class="Button-content">
    <span class="Button-label"><div class="HeaderMenu-toggle-bar rounded my-1"></div>
            <div class="HeaderMenu-toggle-bar rounded my-1"></div>
            <div class="HeaderMenu-toggle-bar rounded my-1"></div></span>
  </span>
</button>
      </div>

      <a class="mr-lg-3 color-fg-inherit flex-order-2 js-prevent-focus-on-mobile-nav"
        href="/"
        aria-label="Homepage"
        data-analytics-event="{&quot;category&quot;:&quot;Marketing nav&quot;,&quot;action&quot;:&quot;click to go to homepage&quot;,&quot;label&quot;:&quot;ref_page:Marketing;ref_cta:Logomark;ref_loc:Header&quot;}">
        <svg height="32" aria-hidden="true" viewBox="0 0 24 24" version="1.1" width="32" data-view-component="true" class="octicon octicon-mark-github">
    <path d="M12.5.75C6.146.75 1 5.896 1 12.25c0 5.089 3.292 9.387 7.863 10.91.575.101.79-.244.79-.546 0-.273-.014-1.178-.014-2.142-2.889.532-3.636-.704-3.866-1.35-.13-.331-.69-1.352-1.18-1.625-.402-.216-.977-.748-.014-.762.906-.014 1.553.834 1.769 1.179 1.035 1.74 2.688 1.25 3.349.948.1-.747.402-1.25.733-1.538-2.559-.287-5.232-1.279-5.232-5.678 0-1.25.445-2.285 1.178-3.09-.115-.288-.517-1.467.115-3.048 0 0 .963-.302 3.163 1.179.92-.259 1.897-.388 2.875-.388.977 0 1.955.13 2.875.388 2.2-1.495 3.162-1.179 3.162-1.179.633 1.581.23 2.76.115 3.048.733.805 1.179 1.825 1.179 3.09 0 4.413-2.688 5.39-5.247 5.678.417.36.776 1.05.776 2.128 0 1.538-.014 2.774-.014 3.162 0 .302.216.662.79.547C20.709 21.637 24 17.324 24 12.25 24 5.896 18.854.75 12.5.75Z"></path>
</svg>
      </a>

      <div class="flex-1 flex-order-2 text-right">
          <a
            href="/login?return_to=https%3A%2F%2Fgithub.com%2Fjohncsantiago%2FWhartonLab%2Fblob%2Fmaster%2FG85R%2520GOandKEGGTermEnrichment.Rmd"
            class="HeaderMenu-link HeaderMenu-button d-inline-flex d-lg-none flex-order-1 f5 no-underline border color-border-default rounded-2 px-2 py-1 color-fg-inherit js-prevent-focus-on-mobile-nav"
            data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;site header menu&quot;,&quot;repository_id&quot;:null,&quot;auth_type&quot;:&quot;SIGN_UP&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="8157e09adb62d5d215219a237bffb5c7f645d21a9e7ca38ff2b80dd99879c182"
            data-analytics-event="{&quot;category&quot;:&quot;Marketing nav&quot;,&quot;action&quot;:&quot;click to Sign in&quot;,&quot;label&quot;:&quot;ref_page:Marketing;ref_cta:Sign in;ref_loc:Header&quot;}"
          >
            Sign in
          </a>
      </div>
    </div>

    <div class="HeaderMenu js-header-menu height-fit position-lg-relative d-lg-flex flex-column flex-auto top-0">
      <div class="HeaderMenu-wrapper d-flex flex-column flex-self-start flex-lg-row flex-auto rounded rounded-lg-0">
          <nav class="HeaderMenu-nav" aria-label="Global">
            <ul class="d-lg-flex list-style-none">
                <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
      <button type="button" class="HeaderMenu-link border-0 width-full width-lg-auto px-0 px-lg-2 py-lg-2 no-wrap d-flex flex-items-center flex-justify-between js-details-target" aria-expanded="false">
        Product
        <svg opacity="0.5" aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-down HeaderMenu-icon ml-1">
    <path d="M12.78 5.22a.749.749 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.06 0L3.22 6.28a.749.749 0 1 1 1.06-1.06L8 8.939l3.72-3.719a.749.749 0 0 1 1.06 0Z"></path>
</svg>
      </button>
      <div class="HeaderMenu-dropdown dropdown-menu rounded m-0 p-0 pt-2 pt-lg-4 position-relative position-lg-absolute left-0 left-lg-n3 pb-2 pb-lg-4 d-lg-flex flex-wrap dropdown-menu-wide">
          <div class="HeaderMenu-column px-lg-4 border-lg-right mb-4 mb-lg-0 pr-lg-7">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0">
                <ul class="list-style-none f5" >
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;github_copilot&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;github_copilot_link_product_navbar&quot;}" href="https://github.com/features/copilot">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-copilot color-fg-subtle mr-3">
    <path d="M23.922 16.992c-.861 1.495-5.859 5.023-11.922 5.023-6.063 0-11.061-3.528-11.922-5.023A.641.641 0 0 1 0 16.736v-2.869a.841.841 0 0 1 .053-.22c.372-.935 1.347-2.292 2.605-2.656.167-.429.414-1.055.644-1.517a10.195 10.195 0 0 1-.052-1.086c0-1.331.282-2.499 1.132-3.368.397-.406.89-.717 1.474-.952 1.399-1.136 3.392-2.093 6.122-2.093 2.731 0 4.767.957 6.166 2.093.584.235 1.077.546 1.474.952.85.869 1.132 2.037 1.132 3.368 0 .368-.014.733-.052 1.086.23.462.477 1.088.644 1.517 1.258.364 2.233 1.721 2.605 2.656a.832.832 0 0 1 .053.22v2.869a.641.641 0 0 1-.078.256ZM12.172 11h-.344a4.323 4.323 0 0 1-.355.508C10.703 12.455 9.555 13 7.965 13c-1.725 0-2.989-.359-3.782-1.259a2.005 2.005 0 0 1-.085-.104L4 11.741v6.585c1.435.779 4.514 2.179 8 2.179 3.486 0 6.565-1.4 8-2.179v-6.585l-.098-.104s-.033.045-.085.104c-.793.9-2.057 1.259-3.782 1.259-1.59 0-2.738-.545-3.508-1.492a4.323 4.323 0 0 1-.355-.508h-.016.016Zm.641-2.935c.136 1.057.403 1.913.878 2.497.442.544 1.134.938 2.344.938 1.573 0 2.292-.337 2.657-.751.384-.435.558-1.15.558-2.361 0-1.14-.243-1.847-.705-2.319-.477-.488-1.319-.862-2.824-1.025-1.487-.161-2.192.138-2.533.529-.269.307-.437.808-.438 1.578v.021c0 .265.021.562.063.893Zm-1.626 0c.042-.331.063-.628.063-.894v-.02c-.001-.77-.169-1.271-.438-1.578-.341-.391-1.046-.69-2.533-.529-1.505.163-2.347.537-2.824 1.025-.462.472-.705 1.179-.705 2.319 0 1.211.175 1.926.558 2.361.365.414 1.084.751 2.657.751 1.21 0 1.902-.394 2.344-.938.475-.584.742-1.44.878-2.497Z"></path><path d="M14.5 14.25a1 1 0 0 1 1 1v2a1 1 0 0 1-2 0v-2a1 1 0 0 1 1-1Zm-5 0a1 1 0 0 1 1 1v2a1 1 0 0 1-2 0v-2a1 1 0 0 1 1-1Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">GitHub Copilot</div>
        Write better code with AI
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;security&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;security_link_product_navbar&quot;}" href="https://github.com/features/security">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-shield-check color-fg-subtle mr-3">
    <path d="M16.53 9.78a.75.75 0 0 0-1.06-1.06L11 13.19l-1.97-1.97a.75.75 0 0 0-1.06 1.06l2.5 2.5a.75.75 0 0 0 1.06 0l5-5Z"></path><path d="m12.54.637 8.25 2.675A1.75 1.75 0 0 1 22 4.976V10c0 6.19-3.771 10.704-9.401 12.83a1.704 1.704 0 0 1-1.198 0C5.77 20.705 2 16.19 2 10V4.976c0-.758.489-1.43 1.21-1.664L11.46.637a1.748 1.748 0 0 1 1.08 0Zm-.617 1.426-8.25 2.676a.249.249 0 0 0-.173.237V10c0 5.46 3.28 9.483 8.43 11.426a.199.199 0 0 0 .14 0C17.22 19.483 20.5 15.461 20.5 10V4.976a.25.25 0 0 0-.173-.237l-8.25-2.676a.253.253 0 0 0-.154 0Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Security</div>
        Find and fix vulnerabilities
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;actions&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;actions_link_product_navbar&quot;}" href="https://github.com/features/actions">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-workflow color-fg-subtle mr-3">
    <path d="M1 3a2 2 0 0 1 2-2h6.5a2 2 0 0 1 2 2v6.5a2 2 0 0 1-2 2H7v4.063C7 16.355 7.644 17 8.438 17H12.5v-2.5a2 2 0 0 1 2-2H21a2 2 0 0 1 2 2V21a2 2 0 0 1-2 2h-6.5a2 2 0 0 1-2-2v-2.5H8.437A2.939 2.939 0 0 1 5.5 15.562V11.5H3a2 2 0 0 1-2-2Zm2-.5a.5.5 0 0 0-.5.5v6.5a.5.5 0 0 0 .5.5h6.5a.5.5 0 0 0 .5-.5V3a.5.5 0 0 0-.5-.5ZM14.5 14a.5.5 0 0 0-.5.5V21a.5.5 0 0 0 .5.5H21a.5.5 0 0 0 .5-.5v-6.5a.5.5 0 0 0-.5-.5Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Actions</div>
        Automate any workflow
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;codespaces&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;codespaces_link_product_navbar&quot;}" href="https://github.com/features/codespaces">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-codespaces color-fg-subtle mr-3">
    <path d="M3.5 3.75C3.5 2.784 4.284 2 5.25 2h13.5c.966 0 1.75.784 1.75 1.75v7.5A1.75 1.75 0 0 1 18.75 13H5.25a1.75 1.75 0 0 1-1.75-1.75Zm-2 12c0-.966.784-1.75 1.75-1.75h17.5c.966 0 1.75.784 1.75 1.75v4a1.75 1.75 0 0 1-1.75 1.75H3.25a1.75 1.75 0 0 1-1.75-1.75ZM5.25 3.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h13.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Zm-2 12a.25.25 0 0 0-.25.25v4c0 .138.112.25.25.25h17.5a.25.25 0 0 0 .25-.25v-4a.25.25 0 0 0-.25-.25Z"></path><path d="M10 17.75a.75.75 0 0 1 .75-.75h6.5a.75.75 0 0 1 0 1.5h-6.5a.75.75 0 0 1-.75-.75Zm-4 0a.75.75 0 0 1 .75-.75h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1-.75-.75Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Codespaces</div>
        Instant dev environments
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;issues&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;issues_link_product_navbar&quot;}" href="https://github.com/features/issues">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-issue-opened color-fg-subtle mr-3">
    <path d="M12 1c6.075 0 11 4.925 11 11s-4.925 11-11 11S1 18.075 1 12 5.925 1 12 1ZM2.5 12a9.5 9.5 0 0 0 9.5 9.5 9.5 9.5 0 0 0 9.5-9.5A9.5 9.5 0 0 0 12 2.5 9.5 9.5 0 0 0 2.5 12Zm9.5 2a2 2 0 1 1-.001-3.999A2 2 0 0 1 12 14Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Issues</div>
        Plan and track work
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;code_review&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;code_review_link_product_navbar&quot;}" href="https://github.com/features/code-review">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-code-review color-fg-subtle mr-3">
    <path d="M10.3 6.74a.75.75 0 0 1-.04 1.06l-2.908 2.7 2.908 2.7a.75.75 0 1 1-1.02 1.1l-3.5-3.25a.75.75 0 0 1 0-1.1l3.5-3.25a.75.75 0 0 1 1.06.04Zm3.44 1.06a.75.75 0 1 1 1.02-1.1l3.5 3.25a.75.75 0 0 1 0 1.1l-3.5 3.25a.75.75 0 1 1-1.02-1.1l2.908-2.7-2.908-2.7Z"></path><path d="M1.5 4.25c0-.966.784-1.75 1.75-1.75h17.5c.966 0 1.75.784 1.75 1.75v12.5a1.75 1.75 0 0 1-1.75 1.75h-9.69l-3.573 3.573A1.458 1.458 0 0 1 5 21.043V18.5H3.25a1.75 1.75 0 0 1-1.75-1.75ZM3.25 4a.25.25 0 0 0-.25.25v12.5c0 .138.112.25.25.25h2.5a.75.75 0 0 1 .75.75v3.19l3.72-3.72a.749.749 0 0 1 .53-.22h10a.25.25 0 0 0 .25-.25V4.25a.25.25 0 0 0-.25-.25Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Code Review</div>
        Manage code changes
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;discussions&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;discussions_link_product_navbar&quot;}" href="https://github.com/features/discussions">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-comment-discussion color-fg-subtle mr-3">
    <path d="M1.75 1h12.5c.966 0 1.75.784 1.75 1.75v9.5A1.75 1.75 0 0 1 14.25 14H8.061l-2.574 2.573A1.458 1.458 0 0 1 3 15.543V14H1.75A1.75 1.75 0 0 1 0 12.25v-9.5C0 1.784.784 1 1.75 1ZM1.5 2.75v9.5c0 .138.112.25.25.25h2a.75.75 0 0 1 .75.75v2.19l2.72-2.72a.749.749 0 0 1 .53-.22h6.5a.25.25 0 0 0 .25-.25v-9.5a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25Z"></path><path d="M22.5 8.75a.25.25 0 0 0-.25-.25h-3.5a.75.75 0 0 1 0-1.5h3.5c.966 0 1.75.784 1.75 1.75v9.5A1.75 1.75 0 0 1 22.25 20H21v1.543a1.457 1.457 0 0 1-2.487 1.03L15.939 20H10.75A1.75 1.75 0 0 1 9 18.25v-1.465a.75.75 0 0 1 1.5 0v1.465c0 .138.112.25.25.25h5.5a.75.75 0 0 1 .53.22l2.72 2.72v-2.19a.75.75 0 0 1 .75-.75h2a.25.25 0 0 0 .25-.25v-9.5Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Discussions</div>
        Collaborate outside of code
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;code_search&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;code_search_link_product_navbar&quot;}" href="https://github.com/features/code-search">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-code-square color-fg-subtle mr-3">
    <path d="M10.3 8.24a.75.75 0 0 1-.04 1.06L7.352 12l2.908 2.7a.75.75 0 1 1-1.02 1.1l-3.5-3.25a.75.75 0 0 1 0-1.1l3.5-3.25a.75.75 0 0 1 1.06.04Zm3.44 1.06a.75.75 0 1 1 1.02-1.1l3.5 3.25a.75.75 0 0 1 0 1.1l-3.5 3.25a.75.75 0 1 1-1.02-1.1l2.908-2.7-2.908-2.7Z"></path><path d="M2 3.75C2 2.784 2.784 2 3.75 2h16.5c.966 0 1.75.784 1.75 1.75v16.5A1.75 1.75 0 0 1 20.25 22H3.75A1.75 1.75 0 0 1 2 20.25Zm1.75-.25a.25.25 0 0 0-.25.25v16.5c0 .138.112.25.25.25h16.5a.25.25 0 0 0 .25-.25V3.75a.25.25 0 0 0-.25-.25Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Code Search</div>
        Find more, search less
      </div>

</a></li>

                </ul>
              </div>
          </div>
          <div class="HeaderMenu-column px-lg-4">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0 border-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="product-explore-heading">Explore</span>
                <ul class="list-style-none f5" aria-labelledby="product-explore-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;all_features&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;all_features_link_product_navbar&quot;}" href="https://github.com/features">
      All features

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;documentation&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;documentation_link_product_navbar&quot;}" href="https://docs.github.com">
      Documentation

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;github_skills&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;github_skills_link_product_navbar&quot;}" href="https://skills.github.com">
      GitHub Skills

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;blog&quot;,&quot;context&quot;:&quot;product&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;blog_link_product_navbar&quot;}" href="https://github.blog">
      Blog

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                </ul>
              </div>
          </div>
      </div>
</li>

                  <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
      <button type="button" class="HeaderMenu-link border-0 width-full width-lg-auto px-0 px-lg-2 py-lg-2 no-wrap d-flex flex-items-center flex-justify-between js-details-target" aria-expanded="false">
        Solutions
        <svg opacity="0.5" aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-down HeaderMenu-icon ml-1">
    <path d="M12.78 5.22a.749.749 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.06 0L3.22 6.28a.749.749 0 1 1 1.06-1.06L8 8.939l3.72-3.719a.749.749 0 0 1 1.06 0Z"></path>
</svg>
      </button>
      <div class="HeaderMenu-dropdown dropdown-menu rounded m-0 p-0 pt-2 pt-lg-4 position-relative position-lg-absolute left-0 left-lg-n3 d-lg-flex flex-wrap dropdown-menu-wide">
          <div class="HeaderMenu-column px-lg-4 border-lg-right mb-4 mb-lg-0 pr-lg-7">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0 pb-lg-3 mb-3 mb-lg-0">
                    <span class="d-block h4 color-fg-default my-1" id="solutions-by-company-size-heading">By company size</span>
                <ul class="list-style-none f5" aria-labelledby="solutions-by-company-size-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;enterprises&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;enterprises_link_solutions_navbar&quot;}" href="https://github.com/enterprise">
      Enterprises

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;small_and_medium_teams&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;small_and_medium_teams_link_solutions_navbar&quot;}" href="https://github.com/team">
      Small and medium teams

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;startups&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;startups_link_solutions_navbar&quot;}" href="https://github.com/enterprise/startups">
      Startups

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;nonprofits&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;nonprofits_link_solutions_navbar&quot;}" href="/solutions/industry/nonprofits">
      Nonprofits

</a></li>

                </ul>
              </div>
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="solutions-by-use-case-heading">By use case</span>
                <ul class="list-style-none f5" aria-labelledby="solutions-by-use-case-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;devsecops&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;devsecops_link_solutions_navbar&quot;}" href="/solutions/use-case/devsecops">
      DevSecOps

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;devops&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;devops_link_solutions_navbar&quot;}" href="/solutions/use-case/devops">
      DevOps

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;ci_cd&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;ci_cd_link_solutions_navbar&quot;}" href="/solutions/use-case/ci-cd">
      CI/CD

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;view_all_use_cases&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;view_all_use_cases_link_solutions_navbar&quot;}" href="/solutions/use-case">
      View all use cases

</a></li>

                </ul>
              </div>
          </div>
          <div class="HeaderMenu-column px-lg-4">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="solutions-by-industry-heading">By industry</span>
                <ul class="list-style-none f5" aria-labelledby="solutions-by-industry-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;healthcare&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;healthcare_link_solutions_navbar&quot;}" href="/solutions/industry/healthcare">
      Healthcare

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;financial_services&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;financial_services_link_solutions_navbar&quot;}" href="/solutions/industry/financial-services">
      Financial services

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;manufacturing&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;manufacturing_link_solutions_navbar&quot;}" href="/solutions/industry/manufacturing">
      Manufacturing

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;government&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;government_link_solutions_navbar&quot;}" href="/solutions/industry/government">
      Government

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;view_all_industries&quot;,&quot;context&quot;:&quot;solutions&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;view_all_industries_link_solutions_navbar&quot;}" href="/solutions/industry">
      View all industries

</a></li>

                </ul>
              </div>
          </div>
         <div class="HeaderMenu-trailing-link rounded-bottom-2 flex-shrink-0 mt-lg-4 px-lg-4 py-4 py-lg-3 f5 text-semibold">
            <a href="/solutions">
              View all solutions
              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-right HeaderMenu-trailing-link-icon">
    <path d="M6.22 3.22a.75.75 0 0 1 1.06 0l4.25 4.25a.75.75 0 0 1 0 1.06l-4.25 4.25a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L9.94 8 6.22 4.28a.75.75 0 0 1 0-1.06Z"></path>
</svg>
</a>         </div>
      </div>
</li>

                    <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
      <button type="button" class="HeaderMenu-link border-0 width-full width-lg-auto px-0 px-lg-2 py-lg-2 no-wrap d-flex flex-items-center flex-justify-between js-details-target" aria-expanded="false">
        Resources
        <svg opacity="0.5" aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-down HeaderMenu-icon ml-1">
    <path d="M12.78 5.22a.749.749 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.06 0L3.22 6.28a.749.749 0 1 1 1.06-1.06L8 8.939l3.72-3.719a.749.749 0 0 1 1.06 0Z"></path>
</svg>
      </button>
      <div class="HeaderMenu-dropdown dropdown-menu rounded m-0 p-0 pt-2 pt-lg-4 position-relative position-lg-absolute left-0 left-lg-n3 pb-2 pb-lg-4 d-lg-flex flex-wrap dropdown-menu-wide">
          <div class="HeaderMenu-column px-lg-4 border-lg-right mb-4 mb-lg-0 pr-lg-7">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="resources-topics-heading">Topics</span>
                <ul class="list-style-none f5" aria-labelledby="resources-topics-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;ai&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;ai_link_resources_navbar&quot;}" href="/resources/articles/ai">
      AI

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;devops&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;devops_link_resources_navbar&quot;}" href="/resources/articles/devops">
      DevOps

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;security&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;security_link_resources_navbar&quot;}" href="/resources/articles/security">
      Security

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;software_development&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;software_development_link_resources_navbar&quot;}" href="/resources/articles/software-development">
      Software Development

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;view_all&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;view_all_link_resources_navbar&quot;}" href="/resources/articles">
      View all

</a></li>

                </ul>
              </div>
          </div>
          <div class="HeaderMenu-column px-lg-4">
              <div class="border-bottom pb-3 pb-lg-0 border-lg-bottom-0 border-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="resources-explore-heading">Explore</span>
                <ul class="list-style-none f5" aria-labelledby="resources-explore-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;learning_pathways&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;learning_pathways_link_resources_navbar&quot;}" href="https://resources.github.com/learn/pathways">
      Learning Pathways

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;white_papers_ebooks_webinars&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;white_papers_ebooks_webinars_link_resources_navbar&quot;}" href="https://resources.github.com">
      White papers, Ebooks, Webinars

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;customer_stories&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;customer_stories_link_resources_navbar&quot;}" href="https://github.com/customer-stories">
      Customer Stories

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary Link--external" target="_blank" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;partners&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;partners_link_resources_navbar&quot;}" href="https://partner.github.com">
      Partners

    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-link-external HeaderMenu-external-icon color-fg-subtle">
    <path d="M3.75 2h3.5a.75.75 0 0 1 0 1.5h-3.5a.25.25 0 0 0-.25.25v8.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-3.5a.75.75 0 0 1 1.5 0v3.5A1.75 1.75 0 0 1 12.25 14h-8.5A1.75 1.75 0 0 1 2 12.25v-8.5C2 2.784 2.784 2 3.75 2Zm6.854-1h4.146a.25.25 0 0 1 .25.25v4.146a.25.25 0 0 1-.427.177L13.03 4.03 9.28 7.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.75-3.75-1.543-1.543A.25.25 0 0 1 10.604 1Z"></path>
</svg>
</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;executive_insights&quot;,&quot;context&quot;:&quot;resources&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;executive_insights_link_resources_navbar&quot;}" href="https://github.com/solutions/executive-insights">
      Executive Insights

</a></li>

                </ul>
              </div>
          </div>
      </div>
</li>

                <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
      <button type="button" class="HeaderMenu-link border-0 width-full width-lg-auto px-0 px-lg-2 py-lg-2 no-wrap d-flex flex-items-center flex-justify-between js-details-target" aria-expanded="false">
        Open Source
        <svg opacity="0.5" aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-down HeaderMenu-icon ml-1">
    <path d="M12.78 5.22a.749.749 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.06 0L3.22 6.28a.749.749 0 1 1 1.06-1.06L8 8.939l3.72-3.719a.749.749 0 0 1 1.06 0Z"></path>
</svg>
      </button>
      <div class="HeaderMenu-dropdown dropdown-menu rounded m-0 p-0 pt-2 pt-lg-4 position-relative position-lg-absolute left-0 left-lg-n3 pb-2 pb-lg-4 px-lg-4">
          <div class="HeaderMenu-column">
              <div class="border-bottom pb-3 pb-lg-0 pb-lg-3 mb-3 mb-lg-0 mb-lg-3">
                <ul class="list-style-none f5" >
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;github_sponsors&quot;,&quot;context&quot;:&quot;open_source&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;github_sponsors_link_open_source_navbar&quot;}" href="/sponsors">

      <div>
        <div class="color-fg-default h4">GitHub Sponsors</div>
        Fund open source developers
      </div>

</a></li>

                </ul>
              </div>
              <div class="border-bottom pb-3 pb-lg-0 pb-lg-3 mb-3 mb-lg-0 mb-lg-3">
                <ul class="list-style-none f5" >
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;the_readme_project&quot;,&quot;context&quot;:&quot;open_source&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;the_readme_project_link_open_source_navbar&quot;}" href="https://github.com/readme">

      <div>
        <div class="color-fg-default h4">The ReadME Project</div>
        GitHub community articles
      </div>

</a></li>

                </ul>
              </div>
              <div class="border-bottom pb-3 pb-lg-0 border-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="open-source-repositories-heading">Repositories</span>
                <ul class="list-style-none f5" aria-labelledby="open-source-repositories-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;topics&quot;,&quot;context&quot;:&quot;open_source&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;topics_link_open_source_navbar&quot;}" href="https://github.com/topics">
      Topics

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;trending&quot;,&quot;context&quot;:&quot;open_source&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;trending_link_open_source_navbar&quot;}" href="https://github.com/trending">
      Trending

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;collections&quot;,&quot;context&quot;:&quot;open_source&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;collections_link_open_source_navbar&quot;}" href="https://github.com/collections">
      Collections

</a></li>

                </ul>
              </div>
          </div>
      </div>
</li>

                <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
      <button type="button" class="HeaderMenu-link border-0 width-full width-lg-auto px-0 px-lg-2 py-lg-2 no-wrap d-flex flex-items-center flex-justify-between js-details-target" aria-expanded="false">
        Enterprise
        <svg opacity="0.5" aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-chevron-down HeaderMenu-icon ml-1">
    <path d="M12.78 5.22a.749.749 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.06 0L3.22 6.28a.749.749 0 1 1 1.06-1.06L8 8.939l3.72-3.719a.749.749 0 0 1 1.06 0Z"></path>
</svg>
      </button>
      <div class="HeaderMenu-dropdown dropdown-menu rounded m-0 p-0 pt-2 pt-lg-4 position-relative position-lg-absolute left-0 left-lg-n3 pb-2 pb-lg-4 px-lg-4">
          <div class="HeaderMenu-column">
              <div class="border-bottom pb-3 pb-lg-0 pb-lg-3 mb-3 mb-lg-0 mb-lg-3">
                <ul class="list-style-none f5" >
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;enterprise_platform&quot;,&quot;context&quot;:&quot;enterprise&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;enterprise_platform_link_enterprise_navbar&quot;}" href="/enterprise">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-stack color-fg-subtle mr-3">
    <path d="M11.063 1.456a1.749 1.749 0 0 1 1.874 0l8.383 5.316a1.751 1.751 0 0 1 0 2.956l-8.383 5.316a1.749 1.749 0 0 1-1.874 0L2.68 9.728a1.751 1.751 0 0 1 0-2.956Zm1.071 1.267a.25.25 0 0 0-.268 0L3.483 8.039a.25.25 0 0 0 0 .422l8.383 5.316a.25.25 0 0 0 .268 0l8.383-5.316a.25.25 0 0 0 0-.422Z"></path><path d="M1.867 12.324a.75.75 0 0 1 1.035-.232l8.964 5.685a.25.25 0 0 0 .268 0l8.964-5.685a.75.75 0 0 1 .804 1.267l-8.965 5.685a1.749 1.749 0 0 1-1.874 0l-8.965-5.685a.75.75 0 0 1-.231-1.035Z"></path><path d="M1.867 16.324a.75.75 0 0 1 1.035-.232l8.964 5.685a.25.25 0 0 0 .268 0l8.964-5.685a.75.75 0 0 1 .804 1.267l-8.965 5.685a1.749 1.749 0 0 1-1.874 0l-8.965-5.685a.75.75 0 0 1-.231-1.035Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Enterprise platform</div>
        AI-powered developer platform
      </div>

</a></li>

                </ul>
              </div>
              <div class="border-bottom pb-3 pb-lg-0 border-bottom-0">
                    <span class="d-block h4 color-fg-default my-1" id="enterprise-available-add-ons-heading">Available add-ons</span>
                <ul class="list-style-none f5" aria-labelledby="enterprise-available-add-ons-heading">
                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;advanced_security&quot;,&quot;context&quot;:&quot;enterprise&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;advanced_security_link_enterprise_navbar&quot;}" href="https://github.com/enterprise/advanced-security">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-shield-check color-fg-subtle mr-3">
    <path d="M16.53 9.78a.75.75 0 0 0-1.06-1.06L11 13.19l-1.97-1.97a.75.75 0 0 0-1.06 1.06l2.5 2.5a.75.75 0 0 0 1.06 0l5-5Z"></path><path d="m12.54.637 8.25 2.675A1.75 1.75 0 0 1 22 4.976V10c0 6.19-3.771 10.704-9.401 12.83a1.704 1.704 0 0 1-1.198 0C5.77 20.705 2 16.19 2 10V4.976c0-.758.489-1.43 1.21-1.664L11.46.637a1.748 1.748 0 0 1 1.08 0Zm-.617 1.426-8.25 2.676a.249.249 0 0 0-.173.237V10c0 5.46 3.28 9.483 8.43 11.426a.199.199 0 0 0 .14 0C17.22 19.483 20.5 15.461 20.5 10V4.976a.25.25 0 0 0-.173-.237l-8.25-2.676a.253.253 0 0 0-.154 0Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Advanced Security</div>
        Enterprise-grade security features
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description pb-lg-3" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;github_copilot&quot;,&quot;context&quot;:&quot;enterprise&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;github_copilot_link_enterprise_navbar&quot;}" href="/features/copilot#enterprise">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-copilot color-fg-subtle mr-3">
    <path d="M23.922 16.992c-.861 1.495-5.859 5.023-11.922 5.023-6.063 0-11.061-3.528-11.922-5.023A.641.641 0 0 1 0 16.736v-2.869a.841.841 0 0 1 .053-.22c.372-.935 1.347-2.292 2.605-2.656.167-.429.414-1.055.644-1.517a10.195 10.195 0 0 1-.052-1.086c0-1.331.282-2.499 1.132-3.368.397-.406.89-.717 1.474-.952 1.399-1.136 3.392-2.093 6.122-2.093 2.731 0 4.767.957 6.166 2.093.584.235 1.077.546 1.474.952.85.869 1.132 2.037 1.132 3.368 0 .368-.014.733-.052 1.086.23.462.477 1.088.644 1.517 1.258.364 2.233 1.721 2.605 2.656a.832.832 0 0 1 .053.22v2.869a.641.641 0 0 1-.078.256ZM12.172 11h-.344a4.323 4.323 0 0 1-.355.508C10.703 12.455 9.555 13 7.965 13c-1.725 0-2.989-.359-3.782-1.259a2.005 2.005 0 0 1-.085-.104L4 11.741v6.585c1.435.779 4.514 2.179 8 2.179 3.486 0 6.565-1.4 8-2.179v-6.585l-.098-.104s-.033.045-.085.104c-.793.9-2.057 1.259-3.782 1.259-1.59 0-2.738-.545-3.508-1.492a4.323 4.323 0 0 1-.355-.508h-.016.016Zm.641-2.935c.136 1.057.403 1.913.878 2.497.442.544 1.134.938 2.344.938 1.573 0 2.292-.337 2.657-.751.384-.435.558-1.15.558-2.361 0-1.14-.243-1.847-.705-2.319-.477-.488-1.319-.862-2.824-1.025-1.487-.161-2.192.138-2.533.529-.269.307-.437.808-.438 1.578v.021c0 .265.021.562.063.893Zm-1.626 0c.042-.331.063-.628.063-.894v-.02c-.001-.77-.169-1.271-.438-1.578-.341-.391-1.046-.69-2.533-.529-1.505.163-2.347.537-2.824 1.025-.462.472-.705 1.179-.705 2.319 0 1.211.175 1.926.558 2.361.365.414 1.084.751 2.657.751 1.21 0 1.902-.394 2.344-.938.475-.584.742-1.44.878-2.497Z"></path><path d="M14.5 14.25a1 1 0 0 1 1 1v2a1 1 0 0 1-2 0v-2a1 1 0 0 1 1-1Zm-5 0a1 1 0 0 1 1 1v2a1 1 0 0 1-2 0v-2a1 1 0 0 1 1-1Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">GitHub Copilot</div>
        Enterprise-grade AI features
      </div>

</a></li>

                    <li>
  <a class="HeaderMenu-dropdown-link d-block no-underline position-relative py-2 Link--secondary d-flex flex-items-center Link--has-description" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;premium_support&quot;,&quot;context&quot;:&quot;enterprise&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;premium_support_link_enterprise_navbar&quot;}" href="/premium-support">
      <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-comment-discussion color-fg-subtle mr-3">
    <path d="M1.75 1h12.5c.966 0 1.75.784 1.75 1.75v9.5A1.75 1.75 0 0 1 14.25 14H8.061l-2.574 2.573A1.458 1.458 0 0 1 3 15.543V14H1.75A1.75 1.75 0 0 1 0 12.25v-9.5C0 1.784.784 1 1.75 1ZM1.5 2.75v9.5c0 .138.112.25.25.25h2a.75.75 0 0 1 .75.75v2.19l2.72-2.72a.749.749 0 0 1 .53-.22h6.5a.25.25 0 0 0 .25-.25v-9.5a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25Z"></path><path d="M22.5 8.75a.25.25 0 0 0-.25-.25h-3.5a.75.75 0 0 1 0-1.5h3.5c.966 0 1.75.784 1.75 1.75v9.5A1.75 1.75 0 0 1 22.25 20H21v1.543a1.457 1.457 0 0 1-2.487 1.03L15.939 20H10.75A1.75 1.75 0 0 1 9 18.25v-1.465a.75.75 0 0 1 1.5 0v1.465c0 .138.112.25.25.25h5.5a.75.75 0 0 1 .53.22l2.72 2.72v-2.19a.75.75 0 0 1 .75-.75h2a.25.25 0 0 0 .25-.25v-9.5Z"></path>
</svg>
      <div>
        <div class="color-fg-default h4">Premium Support</div>
        Enterprise-grade 24/7 support
      </div>

</a></li>

                </ul>
              </div>
          </div>
      </div>
</li>

                <li class="HeaderMenu-item position-relative flex-wrap flex-justify-between flex-items-center d-block d-lg-flex flex-lg-nowrap flex-lg-items-center js-details-container js-header-menu-item">
    <a class="HeaderMenu-link no-underline px-0 px-lg-2 py-3 py-lg-2 d-block d-lg-inline-block" data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;pricing&quot;,&quot;context&quot;:&quot;global&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;pricing_link_global_navbar&quot;}" href="https://github.com/pricing">Pricing</a>
</li>

            </ul>
          </nav>

        <div class="d-flex flex-column flex-lg-row width-full flex-justify-end flex-lg-items-center text-center mt-3 mt-lg-0 text-lg-left ml-lg-3">

<qbsearch-input class="search-input" data-scope="repo:johncsantiago/WhartonLab" data-custom-scopes-path="/search/custom_scopes" data-delete-custom-scopes-csrf="9svgEqlT_VxbXDi4phRAbDTfc1d0dzxofR1CiTgdkN_mPydL08cLslyRH9eeilBLKshSImMozRVZC2plBer34Q" data-max-custom-scopes="10" data-header-redesign-enabled="false" data-initial-value="" data-blackbird-suggestions-path="/search/suggestions" data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations" data-current-repository="johncsantiago/WhartonLab" data-current-org="" data-current-owner="johncsantiago" data-logged-in="false" data-copilot-chat-enabled="false" data-nl-search-enabled="false" data-retain-scroll-position="true">
  <div
    class="search-input-container search-with-dialog position-relative d-flex flex-row flex-items-center mr-4 rounded"
    data-action="click:qbsearch-input#searchInputContainerClicked"
  >
      <button
        type="button"
        class="header-search-button placeholder  input-button form-control d-flex flex-1 flex-self-stretch flex-items-center no-wrap width-full py-0 pl-2 pr-0 text-left border-0 box-shadow-none"
        data-target="qbsearch-input.inputButton"
        aria-label="Search or jump to…"
        aria-haspopup="dialog"
        placeholder="Search or jump to..."
        data-hotkey=s,/
        autocapitalize="off"
        data-analytics-event="{&quot;location&quot;:&quot;navbar&quot;,&quot;action&quot;:&quot;searchbar&quot;,&quot;context&quot;:&quot;global&quot;,&quot;tag&quot;:&quot;input&quot;,&quot;label&quot;:&quot;searchbar_input_global_navbar&quot;}"
        data-action="click:qbsearch-input#handleExpand"
      >
        <div class="mr-2 color-fg-muted">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-search">
    <path d="M10.68 11.74a6 6 0 0 1-7.922-8.982 6 6 0 0 1 8.982 7.922l3.04 3.04a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215ZM11.5 7a4.499 4.499 0 1 0-8.997 0A4.499 4.499 0 0 0 11.5 7Z"></path>
</svg>
        </div>
        <span class="flex-1" data-target="qbsearch-input.inputButtonText">Search or jump to...</span>
          <div class="d-flex" data-target="qbsearch-input.hotkeyIndicator">
            <svg xmlns="http://www.w3.org/2000/svg" width="22" height="20" aria-hidden="true" class="mr-1"><path fill="none" stroke="#979A9C" opacity=".4" d="M3.5.5h12c1.7 0 3 1.3 3 3v13c0 1.7-1.3 3-3 3h-12c-1.7 0-3-1.3-3-3v-13c0-1.7 1.3-3 3-3z"></path><path fill="#979A9C" d="M11.8 6L8 15.1h-.9L10.8 6h1z"></path></svg>

          </div>
      </button>

    <input type="hidden" name="type" class="js-site-search-type-field">

<div class="Overlay--hidden " data-modal-dialog-overlay>
  <modal-dialog data-action="close:qbsearch-input#handleClose cancel:qbsearch-input#handleClose" data-target="qbsearch-input.searchSuggestionsDialog" role="dialog" id="search-suggestions-dialog" aria-modal="true" aria-labelledby="search-suggestions-dialog-header" data-view-component="true" class="Overlay Overlay--width-large Overlay--height-auto">
      <h1 id="search-suggestions-dialog-header" class="sr-only">Search code, repositories, users, issues, pull requests...</h1>
    <div class="Overlay-body Overlay-body--paddingNone">

          <div data-view-component="true">        <div class="search-suggestions position-fixed width-full color-shadow-large border color-fg-default color-bg-default overflow-hidden d-flex flex-column query-builder-container"
          style="border-radius: 12px;"
          data-target="qbsearch-input.queryBuilderContainer"
          hidden
        >
          <!-- '"` --><!-- </textarea></xmp> --></option></form><form id="query-builder-test-form" action="" accept-charset="UTF-8" method="get">
  <query-builder data-target="qbsearch-input.queryBuilder" id="query-builder-query-builder-test" data-filter-key=":" data-view-component="true" class="QueryBuilder search-query-builder">
    <div class="FormControl FormControl--fullWidth">
      <label id="query-builder-test-label" for="query-builder-test" class="FormControl-label sr-only">
        Search
      </label>
      <div
        class="QueryBuilder-StyledInput width-fit "
        data-target="query-builder.styledInput"
      >
          <span id="query-builder-test-leadingvisual-wrap" class="FormControl-input-leadingVisualWrap QueryBuilder-leadingVisualWrap">
            <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-search FormControl-input-leadingVisual">
    <path d="M10.68 11.74a6 6 0 0 1-7.922-8.982 6 6 0 0 1 8.982 7.922l3.04 3.04a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215ZM11.5 7a4.499 4.499 0 1 0-8.997 0A4.499 4.499 0 0 0 11.5 7Z"></path>
</svg>
          </span>
        <div data-target="query-builder.styledInputContainer" class="QueryBuilder-StyledInputContainer">
          <div
            aria-hidden="true"
            class="QueryBuilder-StyledInputContent"
            data-target="query-builder.styledInputContent"
          ></div>
          <div class="QueryBuilder-InputWrapper">
            <div aria-hidden="true" class="QueryBuilder-Sizer" data-target="query-builder.sizer"></div>
            <input id="query-builder-test" name="query-builder-test" value="" autocomplete="off" type="text" role="combobox" spellcheck="false" aria-expanded="false" aria-describedby="validation-1ce1de90-321f-40a1-becf-61982f7b63ae" data-target="query-builder.input" data-action="
          input:query-builder#inputChange
          blur:query-builder#inputBlur
          keydown:query-builder#inputKeydown
          focus:query-builder#inputFocus
        " data-view-component="true" class="FormControl-input QueryBuilder-Input FormControl-medium" />
          </div>
        </div>
          <span class="sr-only" id="query-builder-test-clear">Clear</span>
          <button role="button" id="query-builder-test-clear-button" aria-labelledby="query-builder-test-clear query-builder-test-label" data-target="query-builder.clearButton" data-action="
                click:query-builder#clear
                focus:query-builder#clearButtonFocus
                blur:query-builder#clearButtonBlur
              " variant="small" hidden="hidden" type="button" data-view-component="true" class="Button Button--iconOnly Button--invisible Button--medium mr-1 px-2 py-0 d-flex flex-items-center rounded-1 color-fg-muted">  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x-circle-fill Button-visual">
    <path d="M2.343 13.657A8 8 0 1 1 13.658 2.343 8 8 0 0 1 2.343 13.657ZM6.03 4.97a.751.751 0 0 0-1.042.018.751.751 0 0 0-.018 1.042L6.94 8 4.97 9.97a.749.749 0 0 0 .326 1.275.749.749 0 0 0 .734-.215L8 9.06l1.97 1.97a.749.749 0 0 0 1.275-.326.749.749 0 0 0-.215-.734L9.06 8l1.97-1.97a.749.749 0 0 0-.326-1.275.749.749 0 0 0-.734.215L8 6.94Z"></path>
</svg>
</button>

      </div>
      <template id="search-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-search">
    <path d="M10.68 11.74a6 6 0 0 1-7.922-8.982 6 6 0 0 1 8.982 7.922l3.04 3.04a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215ZM11.5 7a4.499 4.499 0 1 0-8.997 0A4.499 4.499 0 0 0 11.5 7Z"></path>
</svg>
</template>

<template id="code-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-code">
    <path d="m11.28 3.22 4.25 4.25a.75.75 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734L13.94 8l-3.72-3.72a.749.749 0 0 1 .326-1.275.749.749 0 0 1 .734.215Zm-6.56 0a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042L2.06 8l3.72 3.72a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L.47 8.53a.75.75 0 0 1 0-1.06Z"></path>
</svg>
</template>

<template id="file-code-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-file-code">
    <path d="M4 1.75C4 .784 4.784 0 5.75 0h5.586c.464 0 .909.184 1.237.513l2.914 2.914c.329.328.513.773.513 1.237v8.586A1.75 1.75 0 0 1 14.25 15h-9a.75.75 0 0 1 0-1.5h9a.25.25 0 0 0 .25-.25V6h-2.75A1.75 1.75 0 0 1 10 4.25V1.5H5.75a.25.25 0 0 0-.25.25v2.5a.75.75 0 0 1-1.5 0Zm1.72 4.97a.75.75 0 0 1 1.06 0l2 2a.75.75 0 0 1 0 1.06l-2 2a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734l1.47-1.47-1.47-1.47a.75.75 0 0 1 0-1.06ZM3.28 7.78 1.81 9.25l1.47 1.47a.751.751 0 0 1-.018 1.042.751.751 0 0 1-1.042.018l-2-2a.75.75 0 0 1 0-1.06l2-2a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Zm8.22-6.218V4.25c0 .138.112.25.25.25h2.688l-.011-.013-2.914-2.914-.013-.011Z"></path>
</svg>
</template>

<template id="history-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-history">
    <path d="m.427 1.927 1.215 1.215a8.002 8.002 0 1 1-1.6 5.685.75.75 0 1 1 1.493-.154 6.5 6.5 0 1 0 1.18-4.458l1.358 1.358A.25.25 0 0 1 3.896 6H.25A.25.25 0 0 1 0 5.75V2.104a.25.25 0 0 1 .427-.177ZM7.75 4a.75.75 0 0 1 .75.75v2.992l2.028.812a.75.75 0 0 1-.557 1.392l-2.5-1A.751.751 0 0 1 7 8.25v-3.5A.75.75 0 0 1 7.75 4Z"></path>
</svg>
</template>

<template id="repo-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-repo">
    <path d="M2 2.5A2.5 2.5 0 0 1 4.5 0h8.75a.75.75 0 0 1 .75.75v12.5a.75.75 0 0 1-.75.75h-2.5a.75.75 0 0 1 0-1.5h1.75v-2h-8a1 1 0 0 0-.714 1.7.75.75 0 1 1-1.072 1.05A2.495 2.495 0 0 1 2 11.5Zm10.5-1h-8a1 1 0 0 0-1 1v6.708A2.486 2.486 0 0 1 4.5 9h8ZM5 12.25a.25.25 0 0 1 .25-.25h3.5a.25.25 0 0 1 .25.25v3.25a.25.25 0 0 1-.4.2l-1.45-1.087a.249.249 0 0 0-.3 0L5.4 15.7a.25.25 0 0 1-.4-.2Z"></path>
</svg>
</template>

<template id="bookmark-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-bookmark">
    <path d="M3 2.75C3 1.784 3.784 1 4.75 1h6.5c.966 0 1.75.784 1.75 1.75v11.5a.75.75 0 0 1-1.227.579L8 11.722l-3.773 3.107A.751.751 0 0 1 3 14.25Zm1.75-.25a.25.25 0 0 0-.25.25v9.91l3.023-2.489a.75.75 0 0 1 .954 0l3.023 2.49V2.75a.25.25 0 0 0-.25-.25Z"></path>
</svg>
</template>

<template id="plus-circle-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-plus-circle">
    <path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Zm7.25-3.25v2.5h2.5a.75.75 0 0 1 0 1.5h-2.5v2.5a.75.75 0 0 1-1.5 0v-2.5h-2.5a.75.75 0 0 1 0-1.5h2.5v-2.5a.75.75 0 0 1 1.5 0Z"></path>
</svg>
</template>

<template id="circle-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-dot-fill">
    <path d="M8 4a4 4 0 1 1 0 8 4 4 0 0 1 0-8Z"></path>
</svg>
</template>

<template id="trash-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-trash">
    <path d="M11 1.75V3h2.25a.75.75 0 0 1 0 1.5H2.75a.75.75 0 0 1 0-1.5H5V1.75C5 .784 5.784 0 6.75 0h2.5C10.216 0 11 .784 11 1.75ZM4.496 6.675l.66 6.6a.25.25 0 0 0 .249.225h5.19a.25.25 0 0 0 .249-.225l.66-6.6a.75.75 0 0 1 1.492.149l-.66 6.6A1.748 1.748 0 0 1 10.595 15h-5.19a1.75 1.75 0 0 1-1.741-1.575l-.66-6.6a.75.75 0 1 1 1.492-.15ZM6.5 1.75V3h3V1.75a.25.25 0 0 0-.25-.25h-2.5a.25.25 0 0 0-.25.25Z"></path>
</svg>
</template>

<template id="team-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-people">
    <path d="M2 5.5a3.5 3.5 0 1 1 5.898 2.549 5.508 5.508 0 0 1 3.034 4.084.75.75 0 1 1-1.482.235 4 4 0 0 0-7.9 0 .75.75 0 0 1-1.482-.236A5.507 5.507 0 0 1 3.102 8.05 3.493 3.493 0 0 1 2 5.5ZM11 4a3.001 3.001 0 0 1 2.22 5.018 5.01 5.01 0 0 1 2.56 3.012.749.749 0 0 1-.885.954.752.752 0 0 1-.549-.514 3.507 3.507 0 0 0-2.522-2.372.75.75 0 0 1-.574-.73v-.352a.75.75 0 0 1 .416-.672A1.5 1.5 0 0 0 11 5.5.75.75 0 0 1 11 4Zm-5.5-.5a2 2 0 1 0-.001 3.999A2 2 0 0 0 5.5 3.5Z"></path>
</svg>
</template>

<template id="project-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-project">
    <path d="M1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25V1.75C0 .784.784 0 1.75 0ZM1.5 1.75v12.5c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25ZM11.75 3a.75.75 0 0 1 .75.75v7.5a.75.75 0 0 1-1.5 0v-7.5a.75.75 0 0 1 .75-.75Zm-8.25.75a.75.75 0 0 1 1.5 0v5.5a.75.75 0 0 1-1.5 0ZM8 3a.75.75 0 0 1 .75.75v3.5a.75.75 0 0 1-1.5 0v-3.5A.75.75 0 0 1 8 3Z"></path>
</svg>
</template>

<template id="pencil-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-pencil">
    <path d="M11.013 1.427a1.75 1.75 0 0 1 2.474 0l1.086 1.086a1.75 1.75 0 0 1 0 2.474l-8.61 8.61c-.21.21-.47.364-.756.445l-3.251.93a.75.75 0 0 1-.927-.928l.929-3.25c.081-.286.235-.547.445-.758l8.61-8.61Zm.176 4.823L9.75 4.81l-6.286 6.287a.253.253 0 0 0-.064.108l-.558 1.953 1.953-.558a.253.253 0 0 0 .108-.064Zm1.238-3.763a.25.25 0 0 0-.354 0L10.811 3.75l1.439 1.44 1.263-1.263a.25.25 0 0 0 0-.354Z"></path>
</svg>
</template>

<template id="copilot-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-copilot">
    <path d="M7.998 15.035c-4.562 0-7.873-2.914-7.998-3.749V9.338c.085-.628.677-1.686 1.588-2.065.013-.07.024-.143.036-.218.029-.183.06-.384.126-.612-.201-.508-.254-1.084-.254-1.656 0-.87.128-1.769.693-2.484.579-.733 1.494-1.124 2.724-1.261 1.206-.134 2.262.034 2.944.765.05.053.096.108.139.165.044-.057.094-.112.143-.165.682-.731 1.738-.899 2.944-.765 1.23.137 2.145.528 2.724 1.261.566.715.693 1.614.693 2.484 0 .572-.053 1.148-.254 1.656.066.228.098.429.126.612.012.076.024.148.037.218.924.385 1.522 1.471 1.591 2.095v1.872c0 .766-3.351 3.795-8.002 3.795Zm0-1.485c2.28 0 4.584-1.11 5.002-1.433V7.862l-.023-.116c-.49.21-1.075.291-1.727.291-1.146 0-2.059-.327-2.71-.991A3.222 3.222 0 0 1 8 6.303a3.24 3.24 0 0 1-.544.743c-.65.664-1.563.991-2.71.991-.652 0-1.236-.081-1.727-.291l-.023.116v4.255c.419.323 2.722 1.433 5.002 1.433ZM6.762 2.83c-.193-.206-.637-.413-1.682-.297-1.019.113-1.479.404-1.713.7-.247.312-.369.789-.369 1.554 0 .793.129 1.171.308 1.371.162.181.519.379 1.442.379.853 0 1.339-.235 1.638-.54.315-.322.527-.827.617-1.553.117-.935-.037-1.395-.241-1.614Zm4.155-.297c-1.044-.116-1.488.091-1.681.297-.204.219-.359.679-.242 1.614.091.726.303 1.231.618 1.553.299.305.784.54 1.638.54.922 0 1.28-.198 1.442-.379.179-.2.308-.578.308-1.371 0-.765-.123-1.242-.37-1.554-.233-.296-.693-.587-1.713-.7Z"></path><path d="M6.25 9.037a.75.75 0 0 1 .75.75v1.501a.75.75 0 0 1-1.5 0V9.787a.75.75 0 0 1 .75-.75Zm4.25.75v1.501a.75.75 0 0 1-1.5 0V9.787a.75.75 0 0 1 1.5 0Z"></path>
</svg>
</template>

<template id="copilot-error-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-copilot-error">
    <path d="M16 11.24c0 .112-.072.274-.21.467L13 9.688V7.862l-.023-.116c-.49.21-1.075.291-1.727.291-.198 0-.388-.009-.571-.029L6.833 5.226a4.01 4.01 0 0 0 .17-.782c.117-.935-.037-1.395-.241-1.614-.193-.206-.637-.413-1.682-.297-.683.076-1.115.231-1.395.415l-1.257-.91c.579-.564 1.413-.877 2.485-.996 1.206-.134 2.262.034 2.944.765.05.053.096.108.139.165.044-.057.094-.112.143-.165.682-.731 1.738-.899 2.944-.765 1.23.137 2.145.528 2.724 1.261.566.715.693 1.614.693 2.484 0 .572-.053 1.148-.254 1.656.066.228.098.429.126.612.012.076.024.148.037.218.924.385 1.522 1.471 1.591 2.095Zm-5.083-8.707c-1.044-.116-1.488.091-1.681.297-.204.219-.359.679-.242 1.614.091.726.303 1.231.618 1.553.299.305.784.54 1.638.54.922 0 1.28-.198 1.442-.379.179-.2.308-.578.308-1.371 0-.765-.123-1.242-.37-1.554-.233-.296-.693-.587-1.713-.7Zm2.511 11.074c-1.393.776-3.272 1.428-5.43 1.428-4.562 0-7.873-2.914-7.998-3.749V9.338c.085-.628.677-1.686 1.588-2.065.013-.07.024-.143.036-.218.029-.183.06-.384.126-.612-.18-.455-.241-.963-.252-1.475L.31 4.107A.747.747 0 0 1 0 3.509V3.49a.748.748 0 0 1 .625-.73c.156-.026.306.047.435.139l14.667 10.578a.592.592 0 0 1 .227.264.752.752 0 0 1 .046.249v.022a.75.75 0 0 1-1.19.596Zm-1.367-.991L5.635 7.964a5.128 5.128 0 0 1-.889.073c-.652 0-1.236-.081-1.727-.291l-.023.116v4.255c.419.323 2.722 1.433 5.002 1.433 1.539 0 3.089-.505 4.063-.934Z"></path>
</svg>
</template>

<template id="workflow-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-workflow">
    <path d="M0 1.75C0 .784.784 0 1.75 0h3.5C6.216 0 7 .784 7 1.75v3.5A1.75 1.75 0 0 1 5.25 7H4v4a1 1 0 0 0 1 1h4v-1.25C9 9.784 9.784 9 10.75 9h3.5c.966 0 1.75.784 1.75 1.75v3.5A1.75 1.75 0 0 1 14.25 16h-3.5A1.75 1.75 0 0 1 9 14.25v-.75H5A2.5 2.5 0 0 1 2.5 11V7h-.75A1.75 1.75 0 0 1 0 5.25Zm1.75-.25a.25.25 0 0 0-.25.25v3.5c0 .138.112.25.25.25h3.5a.25.25 0 0 0 .25-.25v-3.5a.25.25 0 0 0-.25-.25Zm9 9a.25.25 0 0 0-.25.25v3.5c0 .138.112.25.25.25h3.5a.25.25 0 0 0 .25-.25v-3.5a.25.25 0 0 0-.25-.25Z"></path>
</svg>
</template>

<template id="book-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-book">
    <path d="M0 1.75A.75.75 0 0 1 .75 1h4.253c1.227 0 2.317.59 3 1.501A3.743 3.743 0 0 1 11.006 1h4.245a.75.75 0 0 1 .75.75v10.5a.75.75 0 0 1-.75.75h-4.507a2.25 2.25 0 0 0-1.591.659l-.622.621a.75.75 0 0 1-1.06 0l-.622-.621A2.25 2.25 0 0 0 5.258 13H.75a.75.75 0 0 1-.75-.75Zm7.251 10.324.004-5.073-.002-2.253A2.25 2.25 0 0 0 5.003 2.5H1.5v9h3.757a3.75 3.75 0 0 1 1.994.574ZM8.755 4.75l-.004 7.322a3.752 3.752 0 0 1 1.992-.572H14.5v-9h-3.495a2.25 2.25 0 0 0-2.25 2.25Z"></path>
</svg>
</template>

<template id="code-review-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-code-review">
    <path d="M1.75 1h12.5c.966 0 1.75.784 1.75 1.75v8.5A1.75 1.75 0 0 1 14.25 13H8.061l-2.574 2.573A1.458 1.458 0 0 1 3 14.543V13H1.75A1.75 1.75 0 0 1 0 11.25v-8.5C0 1.784.784 1 1.75 1ZM1.5 2.75v8.5c0 .138.112.25.25.25h2a.75.75 0 0 1 .75.75v2.19l2.72-2.72a.749.749 0 0 1 .53-.22h6.5a.25.25 0 0 0 .25-.25v-8.5a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25Zm5.28 1.72a.75.75 0 0 1 0 1.06L5.31 7l1.47 1.47a.751.751 0 0 1-.018 1.042.751.751 0 0 1-1.042.018l-2-2a.75.75 0 0 1 0-1.06l2-2a.75.75 0 0 1 1.06 0Zm2.44 0a.75.75 0 0 1 1.06 0l2 2a.75.75 0 0 1 0 1.06l-2 2a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L10.69 7 9.22 5.53a.75.75 0 0 1 0-1.06Z"></path>
</svg>
</template>

<template id="codespaces-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-codespaces">
    <path d="M0 11.25c0-.966.784-1.75 1.75-1.75h12.5c.966 0 1.75.784 1.75 1.75v3A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25Zm2-9.5C2 .784 2.784 0 3.75 0h8.5C13.216 0 14 .784 14 1.75v5a1.75 1.75 0 0 1-1.75 1.75h-8.5A1.75 1.75 0 0 1 2 6.75Zm1.75-.25a.25.25 0 0 0-.25.25v5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25v-5a.25.25 0 0 0-.25-.25Zm-2 9.5a.25.25 0 0 0-.25.25v3c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25v-3a.25.25 0 0 0-.25-.25Z"></path><path d="M7 12.75a.75.75 0 0 1 .75-.75h4.5a.75.75 0 0 1 0 1.5h-4.5a.75.75 0 0 1-.75-.75Zm-4 0a.75.75 0 0 1 .75-.75h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1-.75-.75Z"></path>
</svg>
</template>

<template id="comment-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-comment">
    <path d="M1 2.75C1 1.784 1.784 1 2.75 1h10.5c.966 0 1.75.784 1.75 1.75v7.5A1.75 1.75 0 0 1 13.25 12H9.06l-2.573 2.573A1.458 1.458 0 0 1 4 13.543V12H2.75A1.75 1.75 0 0 1 1 10.25Zm1.75-.25a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h2a.75.75 0 0 1 .75.75v2.19l2.72-2.72a.749.749 0 0 1 .53-.22h4.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Z"></path>
</svg>
</template>

<template id="comment-discussion-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-comment-discussion">
    <path d="M1.75 1h8.5c.966 0 1.75.784 1.75 1.75v5.5A1.75 1.75 0 0 1 10.25 10H7.061l-2.574 2.573A1.458 1.458 0 0 1 2 11.543V10h-.25A1.75 1.75 0 0 1 0 8.25v-5.5C0 1.784.784 1 1.75 1ZM1.5 2.75v5.5c0 .138.112.25.25.25h1a.75.75 0 0 1 .75.75v2.19l2.72-2.72a.749.749 0 0 1 .53-.22h3.5a.25.25 0 0 0 .25-.25v-5.5a.25.25 0 0 0-.25-.25h-8.5a.25.25 0 0 0-.25.25Zm13 2a.25.25 0 0 0-.25-.25h-.5a.75.75 0 0 1 0-1.5h.5c.966 0 1.75.784 1.75 1.75v5.5A1.75 1.75 0 0 1 14.25 12H14v1.543a1.458 1.458 0 0 1-2.487 1.03L9.22 12.28a.749.749 0 0 1 .326-1.275.749.749 0 0 1 .734.215l2.22 2.22v-2.19a.75.75 0 0 1 .75-.75h1a.25.25 0 0 0 .25-.25Z"></path>
</svg>
</template>

<template id="organization-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-organization">
    <path d="M1.75 16A1.75 1.75 0 0 1 0 14.25V1.75C0 .784.784 0 1.75 0h8.5C11.216 0 12 .784 12 1.75v12.5c0 .085-.006.168-.018.25h2.268a.25.25 0 0 0 .25-.25V8.285a.25.25 0 0 0-.111-.208l-1.055-.703a.749.749 0 1 1 .832-1.248l1.055.703c.487.325.779.871.779 1.456v5.965A1.75 1.75 0 0 1 14.25 16h-3.5a.766.766 0 0 1-.197-.026c-.099.017-.2.026-.303.026h-3a.75.75 0 0 1-.75-.75V14h-1v1.25a.75.75 0 0 1-.75.75Zm-.25-1.75c0 .138.112.25.25.25H4v-1.25a.75.75 0 0 1 .75-.75h2.5a.75.75 0 0 1 .75.75v1.25h2.25a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25h-8.5a.25.25 0 0 0-.25.25ZM3.75 6h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1 0-1.5ZM3 3.75A.75.75 0 0 1 3.75 3h.5a.75.75 0 0 1 0 1.5h-.5A.75.75 0 0 1 3 3.75Zm4 3A.75.75 0 0 1 7.75 6h.5a.75.75 0 0 1 0 1.5h-.5A.75.75 0 0 1 7 6.75ZM7.75 3h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1 0-1.5ZM3 9.75A.75.75 0 0 1 3.75 9h.5a.75.75 0 0 1 0 1.5h-.5A.75.75 0 0 1 3 9.75ZM7.75 9h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1 0-1.5Z"></path>
</svg>
</template>

<template id="rocket-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-rocket">
    <path d="M14.064 0h.186C15.216 0 16 .784 16 1.75v.186a8.752 8.752 0 0 1-2.564 6.186l-.458.459c-.314.314-.641.616-.979.904v3.207c0 .608-.315 1.172-.833 1.49l-2.774 1.707a.749.749 0 0 1-1.11-.418l-.954-3.102a1.214 1.214 0 0 1-.145-.125L3.754 9.816a1.218 1.218 0 0 1-.124-.145L.528 8.717a.749.749 0 0 1-.418-1.11l1.71-2.774A1.748 1.748 0 0 1 3.31 4h3.204c.288-.338.59-.665.904-.979l.459-.458A8.749 8.749 0 0 1 14.064 0ZM8.938 3.623h-.002l-.458.458c-.76.76-1.437 1.598-2.02 2.5l-1.5 2.317 2.143 2.143 2.317-1.5c.902-.583 1.74-1.26 2.499-2.02l.459-.458a7.25 7.25 0 0 0 2.123-5.127V1.75a.25.25 0 0 0-.25-.25h-.186a7.249 7.249 0 0 0-5.125 2.123ZM3.56 14.56c-.732.732-2.334 1.045-3.005 1.148a.234.234 0 0 1-.201-.064.234.234 0 0 1-.064-.201c.103-.671.416-2.273 1.15-3.003a1.502 1.502 0 1 1 2.12 2.12Zm6.94-3.935c-.088.06-.177.118-.266.175l-2.35 1.521.548 1.783 1.949-1.2a.25.25 0 0 0 .119-.213ZM3.678 8.116 5.2 5.766c.058-.09.117-.178.176-.266H3.309a.25.25 0 0 0-.213.119l-1.2 1.95ZM12 5a1 1 0 1 1-2 0 1 1 0 0 1 2 0Z"></path>
</svg>
</template>

<template id="shield-check-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-shield-check">
    <path d="m8.533.133 5.25 1.68A1.75 1.75 0 0 1 15 3.48V7c0 1.566-.32 3.182-1.303 4.682-.983 1.498-2.585 2.813-5.032 3.855a1.697 1.697 0 0 1-1.33 0c-2.447-1.042-4.049-2.357-5.032-3.855C1.32 10.182 1 8.566 1 7V3.48a1.75 1.75 0 0 1 1.217-1.667l5.25-1.68a1.748 1.748 0 0 1 1.066 0Zm-.61 1.429.001.001-5.25 1.68a.251.251 0 0 0-.174.237V7c0 1.36.275 2.666 1.057 3.859.784 1.194 2.121 2.342 4.366 3.298a.196.196 0 0 0 .154 0c2.245-.957 3.582-2.103 4.366-3.297C13.225 9.666 13.5 8.358 13.5 7V3.48a.25.25 0 0 0-.174-.238l-5.25-1.68a.25.25 0 0 0-.153 0ZM11.28 6.28l-3.5 3.5a.75.75 0 0 1-1.06 0l-1.5-1.5a.749.749 0 0 1 .326-1.275.749.749 0 0 1 .734.215l.97.97 2.97-2.97a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Z"></path>
</svg>
</template>

<template id="heart-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-heart">
    <path d="m8 14.25.345.666a.75.75 0 0 1-.69 0l-.008-.004-.018-.01a7.152 7.152 0 0 1-.31-.17 22.055 22.055 0 0 1-3.434-2.414C2.045 10.731 0 8.35 0 5.5 0 2.836 2.086 1 4.25 1 5.797 1 7.153 1.802 8 3.02 8.847 1.802 10.203 1 11.75 1 13.914 1 16 2.836 16 5.5c0 2.85-2.045 5.231-3.885 6.818a22.066 22.066 0 0 1-3.744 2.584l-.018.01-.006.003h-.002ZM4.25 2.5c-1.336 0-2.75 1.164-2.75 3 0 2.15 1.58 4.144 3.365 5.682A20.58 20.58 0 0 0 8 13.393a20.58 20.58 0 0 0 3.135-2.211C12.92 9.644 14.5 7.65 14.5 5.5c0-1.836-1.414-3-2.75-3-1.373 0-2.609.986-3.029 2.456a.749.749 0 0 1-1.442 0C6.859 3.486 5.623 2.5 4.25 2.5Z"></path>
</svg>
</template>

<template id="server-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-server">
    <path d="M1.75 1h12.5c.966 0 1.75.784 1.75 1.75v4c0 .372-.116.717-.314 1 .198.283.314.628.314 1v4a1.75 1.75 0 0 1-1.75 1.75H1.75A1.75 1.75 0 0 1 0 12.75v-4c0-.358.109-.707.314-1a1.739 1.739 0 0 1-.314-1v-4C0 1.784.784 1 1.75 1ZM1.5 2.75v4c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25v-4a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25Zm.25 5.75a.25.25 0 0 0-.25.25v4c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25v-4a.25.25 0 0 0-.25-.25ZM7 4.75A.75.75 0 0 1 7.75 4h4.5a.75.75 0 0 1 0 1.5h-4.5A.75.75 0 0 1 7 4.75ZM7.75 10h4.5a.75.75 0 0 1 0 1.5h-4.5a.75.75 0 0 1 0-1.5ZM3 4.75A.75.75 0 0 1 3.75 4h.5a.75.75 0 0 1 0 1.5h-.5A.75.75 0 0 1 3 4.75ZM3.75 10h.5a.75.75 0 0 1 0 1.5h-.5a.75.75 0 0 1 0-1.5Z"></path>
</svg>
</template>

<template id="globe-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-globe">
    <path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM5.78 8.75a9.64 9.64 0 0 0 1.363 4.177c.255.426.542.832.857 1.215.245-.296.551-.705.857-1.215A9.64 9.64 0 0 0 10.22 8.75Zm4.44-1.5a9.64 9.64 0 0 0-1.363-4.177c-.307-.51-.612-.919-.857-1.215a9.927 9.927 0 0 0-.857 1.215A9.64 9.64 0 0 0 5.78 7.25Zm-5.944 1.5H1.543a6.507 6.507 0 0 0 4.666 5.5c-.123-.181-.24-.365-.352-.552-.715-1.192-1.437-2.874-1.581-4.948Zm-2.733-1.5h2.733c.144-2.074.866-3.756 1.58-4.948.12-.197.237-.381.353-.552a6.507 6.507 0 0 0-4.666 5.5Zm10.181 1.5c-.144 2.074-.866 3.756-1.58 4.948-.12.197-.237.381-.353.552a6.507 6.507 0 0 0 4.666-5.5Zm2.733-1.5a6.507 6.507 0 0 0-4.666-5.5c.123.181.24.365.353.552.714 1.192 1.436 2.874 1.58 4.948Z"></path>
</svg>
</template>

<template id="issue-opened-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-issue-opened">
    <path d="M8 9.5a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path><path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Z"></path>
</svg>
</template>

<template id="device-mobile-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-device-mobile">
    <path d="M3.75 0h8.5C13.216 0 14 .784 14 1.75v12.5A1.75 1.75 0 0 1 12.25 16h-8.5A1.75 1.75 0 0 1 2 14.25V1.75C2 .784 2.784 0 3.75 0ZM3.5 1.75v12.5c0 .138.112.25.25.25h8.5a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25h-8.5a.25.25 0 0 0-.25.25ZM8 13a1 1 0 1 1 0-2 1 1 0 0 1 0 2Z"></path>
</svg>
</template>

<template id="package-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-package">
    <path d="m8.878.392 5.25 3.045c.54.314.872.89.872 1.514v6.098a1.75 1.75 0 0 1-.872 1.514l-5.25 3.045a1.75 1.75 0 0 1-1.756 0l-5.25-3.045A1.75 1.75 0 0 1 1 11.049V4.951c0-.624.332-1.201.872-1.514L7.122.392a1.75 1.75 0 0 1 1.756 0ZM7.875 1.69l-4.63 2.685L8 7.133l4.755-2.758-4.63-2.685a.248.248 0 0 0-.25 0ZM2.5 5.677v5.372c0 .09.047.171.125.216l4.625 2.683V8.432Zm6.25 8.271 4.625-2.683a.25.25 0 0 0 .125-.216V5.677L8.75 8.432Z"></path>
</svg>
</template>

<template id="credit-card-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-credit-card">
    <path d="M10.75 9a.75.75 0 0 0 0 1.5h1.5a.75.75 0 0 0 0-1.5h-1.5Z"></path><path d="M0 3.75C0 2.784.784 2 1.75 2h12.5c.966 0 1.75.784 1.75 1.75v8.5A1.75 1.75 0 0 1 14.25 14H1.75A1.75 1.75 0 0 1 0 12.25ZM14.5 6.5h-13v5.75c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25Zm0-2.75a.25.25 0 0 0-.25-.25H1.75a.25.25 0 0 0-.25.25V5h13Z"></path>
</svg>
</template>

<template id="play-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-play">
    <path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Zm4.879-2.773 4.264 2.559a.25.25 0 0 1 0 .428l-4.264 2.559A.25.25 0 0 1 6 10.559V5.442a.25.25 0 0 1 .379-.215Z"></path>
</svg>
</template>

<template id="gift-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-gift">
    <path d="M2 2.75A2.75 2.75 0 0 1 4.75 0c.983 0 1.873.42 2.57 1.232.268.318.497.668.68 1.042.183-.375.411-.725.68-1.044C9.376.42 10.266 0 11.25 0a2.75 2.75 0 0 1 2.45 4h.55c.966 0 1.75.784 1.75 1.75v2c0 .698-.409 1.301-1 1.582v4.918A1.75 1.75 0 0 1 13.25 16H2.75A1.75 1.75 0 0 1 1 14.25V9.332C.409 9.05 0 8.448 0 7.75v-2C0 4.784.784 4 1.75 4h.55c-.192-.375-.3-.8-.3-1.25ZM7.25 9.5H2.5v4.75c0 .138.112.25.25.25h4.5Zm1.5 0v5h4.5a.25.25 0 0 0 .25-.25V9.5Zm0-4V8h5.5a.25.25 0 0 0 .25-.25v-2a.25.25 0 0 0-.25-.25Zm-7 0a.25.25 0 0 0-.25.25v2c0 .138.112.25.25.25h5.5V5.5h-5.5Zm3-4a1.25 1.25 0 0 0 0 2.5h2.309c-.233-.818-.542-1.401-.878-1.793-.43-.502-.915-.707-1.431-.707ZM8.941 4h2.309a1.25 1.25 0 0 0 0-2.5c-.516 0-1 .205-1.43.707-.337.392-.646.975-.879 1.793Z"></path>
</svg>
</template>

<template id="code-square-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-code-square">
    <path d="M0 1.75C0 .784.784 0 1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25Zm1.75-.25a.25.25 0 0 0-.25.25v12.5c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25Zm7.47 3.97a.75.75 0 0 1 1.06 0l2 2a.75.75 0 0 1 0 1.06l-2 2a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734L10.69 8 9.22 6.53a.75.75 0 0 1 0-1.06ZM6.78 6.53 5.31 8l1.47 1.47a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215l-2-2a.75.75 0 0 1 0-1.06l2-2a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Z"></path>
</svg>
</template>

<template id="device-desktop-icon">
  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-device-desktop">
    <path d="M14.25 1c.966 0 1.75.784 1.75 1.75v7.5A1.75 1.75 0 0 1 14.25 12h-3.727c.099 1.041.52 1.872 1.292 2.757A.752.752 0 0 1 11.25 16h-6.5a.75.75 0 0 1-.565-1.243c.772-.885 1.192-1.716 1.292-2.757H1.75A1.75 1.75 0 0 1 0 10.25v-7.5C0 1.784.784 1 1.75 1ZM1.75 2.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25ZM9.018 12H6.982a5.72 5.72 0 0 1-.765 2.5h3.566a5.72 5.72 0 0 1-.765-2.5Z"></path>
</svg>
</template>

        <div class="position-relative">
                <ul
                  role="listbox"
                  class="ActionListWrap QueryBuilder-ListWrap"
                  aria-label="Suggestions"
                  data-action="
                    combobox-commit:query-builder#comboboxCommit
                    mousedown:query-builder#resultsMousedown
                  "
                  data-target="query-builder.resultsList"
                  data-persist-list=false
                  id="query-builder-test-results"
                ></ul>
        </div>
      <div class="FormControl-inlineValidation" id="validation-1ce1de90-321f-40a1-becf-61982f7b63ae" hidden="hidden">
        <span class="FormControl-inlineValidation--visual">
          <svg aria-hidden="true" height="12" viewBox="0 0 12 12" version="1.1" width="12" data-view-component="true" class="octicon octicon-alert-fill">
    <path d="M4.855.708c.5-.896 1.79-.896 2.29 0l4.675 8.351a1.312 1.312 0 0 1-1.146 1.954H1.33A1.313 1.313 0 0 1 .183 9.058ZM7 7V3H5v4Zm-1 3a1 1 0 1 0 0-2 1 1 0 0 0 0 2Z"></path>
</svg>
        </span>
        <span></span>
</div>    </div>
    <div data-target="query-builder.screenReaderFeedback" aria-live="polite" aria-atomic="true" class="sr-only"></div>
</query-builder></form>
          <div class="d-flex flex-row color-fg-muted px-3 text-small color-bg-default search-feedback-prompt">
            <a target="_blank" href="https://docs.github.com/search-github/github-code-search/understanding-github-code-search-syntax" data-view-component="true" class="Link color-fg-accent text-normal ml-2">Search syntax tips</a>            <div class="d-flex flex-1"></div>
          </div>
        </div>
</div>

    </div>
</modal-dialog></div>
  </div>
  <div data-action="click:qbsearch-input#retract" class="dark-backdrop position-fixed" hidden data-target="qbsearch-input.darkBackdrop"></div>
  <div class="color-fg-default">

<dialog-helper>
  <dialog data-target="qbsearch-input.feedbackDialog" data-action="close:qbsearch-input#handleDialogClose cancel:qbsearch-input#handleDialogClose" id="feedback-dialog" aria-modal="true" aria-labelledby="feedback-dialog-title" aria-describedby="feedback-dialog-description" data-view-component="true" class="Overlay Overlay-whenNarrow Overlay--size-medium Overlay--motion-scaleFade Overlay--disableScroll">
    <div data-view-component="true" class="Overlay-header">
  <div class="Overlay-headerContentWrap">
    <div class="Overlay-titleWrap">
      <h1 class="Overlay-title " id="feedback-dialog-title">
        Provide feedback
      </h1>

    </div>
    <div class="Overlay-actionWrap">
      <button data-close-dialog-id="feedback-dialog" aria-label="Close" type="button" data-view-component="true" class="close-button Overlay-closeButton"><svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg></button>
    </div>
  </div>

</div>
      <scrollable-region data-labelled-by="feedback-dialog-title">
        <div data-view-component="true" class="Overlay-body">        <!-- '"` --><!-- </textarea></xmp> --></option></form><form id="code-search-feedback-form" data-turbo="false" action="/search/feedback" accept-charset="UTF-8" method="post"><input type="hidden" data-csrf="true" name="authenticity_token" value="Gnv9J0nc1T6qJOWPayE/tvSbvOMqarncba7luzEjyE4B6HfBqQo1X5oRuQGHd3z96LHyWXPn1FVZuRVJpHJmVA==" />
          <p>We read every piece of feedback, and take your input very seriously.</p>
          <textarea name="feedback" class="form-control width-full mb-2" style="height: 120px" id="feedback"></textarea>
          <input name="include_email" id="include_email" aria-label="Include my email address so I can be contacted" class="form-control mr-2" type="checkbox">
          <label for="include_email" style="font-weight: normal">Include my email address so I can be contacted</label>
</form></div>
      </scrollable-region>
      <div data-view-component="true" class="Overlay-footer Overlay-footer--alignEnd">          <button data-close-dialog-id="feedback-dialog" type="button" data-view-component="true" class="btn">    Cancel
</button>
          <button form="code-search-feedback-form" data-action="click:qbsearch-input#submitFeedback" type="submit" data-view-component="true" class="btn-primary btn">    Submit feedback
</button>
</div>
</dialog></dialog-helper>

    <custom-scopes data-target="qbsearch-input.customScopesManager">

<dialog-helper>
  <dialog data-target="custom-scopes.customScopesModalDialog" data-action="close:qbsearch-input#handleDialogClose cancel:qbsearch-input#handleDialogClose" id="custom-scopes-dialog" aria-modal="true" aria-labelledby="custom-scopes-dialog-title" aria-describedby="custom-scopes-dialog-description" data-view-component="true" class="Overlay Overlay-whenNarrow Overlay--size-medium Overlay--motion-scaleFade Overlay--disableScroll">
    <div data-view-component="true" class="Overlay-header Overlay-header--divided">
  <div class="Overlay-headerContentWrap">
    <div class="Overlay-titleWrap">
      <h1 class="Overlay-title " id="custom-scopes-dialog-title">
        Saved searches
      </h1>
        <h2 id="custom-scopes-dialog-description" class="Overlay-description">Use saved searches to filter your results more quickly</h2>
    </div>
    <div class="Overlay-actionWrap">
      <button data-close-dialog-id="custom-scopes-dialog" aria-label="Close" type="button" data-view-component="true" class="close-button Overlay-closeButton"><svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg></button>
    </div>
  </div>

</div>
      <scrollable-region data-labelled-by="custom-scopes-dialog-title">
        <div data-view-component="true" class="Overlay-body">        <div data-target="custom-scopes.customScopesModalDialogFlash"></div>

        <div hidden class="create-custom-scope-form" data-target="custom-scopes.createCustomScopeForm">
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form id="custom-scopes-dialog-form" data-turbo="false" action="/search/custom_scopes" accept-charset="UTF-8" method="post"><input type="hidden" data-csrf="true" name="authenticity_token" value="gDdkiAcoikPH5ymnEah8LHWkTGbg3eZZhSZi7OSbtsRr0vxheOYGr/0tb0ZDZRe8FbscLH86ws6ez4Re60q2Jg==" />
          <div data-target="custom-scopes.customScopesModalDialogFlash"></div>

          <input type="hidden" id="custom_scope_id" name="custom_scope_id" data-target="custom-scopes.customScopesIdField">

          <div class="form-group">
            <label for="custom_scope_name">Name</label>
            <auto-check src="/search/custom_scopes/check_name" required only-validate-on-blur="false">
              <input
                type="text"
                name="custom_scope_name"
                id="custom_scope_name"
                data-target="custom-scopes.customScopesNameField"
                class="form-control"
                autocomplete="off"
                placeholder="github-ruby"
                required
                maxlength="50">
              <input type="hidden" data-csrf="true" value="ER0njA4SbDKCdcdr29Vt496k8plpZGDOumpXEAg4U+SVZjpVkphBKqvgnzHlQlWDsrN3UfjwSfJw6gQ2hBPQsA==" />
            </auto-check>
          </div>

          <div class="form-group">
            <label for="custom_scope_query">Query</label>
            <input
              type="text"
              name="custom_scope_query"
              id="custom_scope_query"
              data-target="custom-scopes.customScopesQueryField"
              class="form-control"
              autocomplete="off"
              placeholder="(repo:mona/a OR repo:mona/b) AND lang:python"
              required
              maxlength="500">
          </div>

          <p class="text-small color-fg-muted">
            To see all available qualifiers, see our <a class="Link--inTextBlock" href="https://docs.github.com/search-github/github-code-search/understanding-github-code-search-syntax">documentation</a>.
          </p>
</form>        </div>

        <div data-target="custom-scopes.manageCustomScopesForm">
          <div data-target="custom-scopes.list"></div>
        </div>

</div>
      </scrollable-region>
      <div data-view-component="true" class="Overlay-footer Overlay-footer--alignEnd Overlay-footer--divided">          <button data-action="click:custom-scopes#customScopesCancel" type="button" data-view-component="true" class="btn">    Cancel
</button>
          <button form="custom-scopes-dialog-form" data-action="click:custom-scopes#customScopesSubmit" data-target="custom-scopes.customScopesSubmitButton" type="submit" data-view-component="true" class="btn-primary btn">    Create saved search
</button>
</div>
</dialog></dialog-helper>
    </custom-scopes>
  </div>
</qbsearch-input>

            <div class="position-relative HeaderMenu-link-wrap d-lg-inline-block">
              <a
                href="/login?return_to=https%3A%2F%2Fgithub.com%2Fjohncsantiago%2FWhartonLab%2Fblob%2Fmaster%2FG85R%2520GOandKEGGTermEnrichment.Rmd"
                class="HeaderMenu-link HeaderMenu-link--sign-in HeaderMenu-button flex-shrink-0 no-underline d-none d-lg-inline-flex border border-lg-0 rounded rounded-lg-0 px-2 py-1"
                style="margin-left: 12px;"
                data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;site header menu&quot;,&quot;repository_id&quot;:null,&quot;auth_type&quot;:&quot;SIGN_UP&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="8157e09adb62d5d215219a237bffb5c7f645d21a9e7ca38ff2b80dd99879c182"
                data-analytics-event="{&quot;category&quot;:&quot;Marketing nav&quot;,&quot;action&quot;:&quot;click to go to homepage&quot;,&quot;label&quot;:&quot;ref_page:Marketing;ref_cta:Sign in;ref_loc:Header&quot;}"
              >
                Sign in
              </a>
            </div>

              <a href="/signup?ref_cta=Sign+up&amp;ref_loc=header+logged+out&amp;ref_page=%2F%3Cuser-name%3E%2F%3Crepo-name%3E%2Fblob%2Fshow&amp;source=header-repo&amp;source_repo=johncsantiago%2FWhartonLab"
                class="HeaderMenu-link HeaderMenu-link--sign-up HeaderMenu-button flex-shrink-0 d-flex d-lg-inline-flex no-underline border color-border-default rounded px-2 py-1"
                data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;site header menu&quot;,&quot;repository_id&quot;:null,&quot;auth_type&quot;:&quot;SIGN_UP&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="8157e09adb62d5d215219a237bffb5c7f645d21a9e7ca38ff2b80dd99879c182"
                data-analytics-event="{&quot;category&quot;:&quot;Sign up&quot;,&quot;action&quot;:&quot;click to sign up for account&quot;,&quot;label&quot;:&quot;ref_page:/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show;ref_cta:Sign up;ref_loc:header logged out&quot;}"
              >
                Sign up
              </a>
          <button type="button" class="sr-only js-header-menu-focus-trap d-block d-lg-none">Reseting focus</button>
        </div>
      </div>
    </div>
  </div>
</header>

      <div hidden="hidden" data-view-component="true" class="js-stale-session-flash stale-session-flash flash flash-warn flash-full">

        <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-alert">
    <path d="M6.457 1.047c.659-1.234 2.427-1.234 3.086 0l6.082 11.378A1.75 1.75 0 0 1 14.082 15H1.918a1.75 1.75 0 0 1-1.543-2.575Zm1.763.707a.25.25 0 0 0-.44 0L1.698 13.132a.25.25 0 0 0 .22.368h12.164a.25.25 0 0 0 .22-.368Zm.53 3.996v2.5a.75.75 0 0 1-1.5 0v-2.5a.75.75 0 0 1 1.5 0ZM9 11a1 1 0 1 1-2 0 1 1 0 0 1 2 0Z"></path>
</svg>
        <span class="js-stale-session-flash-signed-in" hidden>You signed in with another tab or window. <a class="Link--inTextBlock" href="">Reload</a> to refresh your session.</span>
        <span class="js-stale-session-flash-signed-out" hidden>You signed out in another tab or window. <a class="Link--inTextBlock" href="">Reload</a> to refresh your session.</span>
        <span class="js-stale-session-flash-switched" hidden>You switched accounts on another tab or window. <a class="Link--inTextBlock" href="">Reload</a> to refresh your session.</span>

    <button id="icon-button-8ac41a50-4fb0-4254-a46c-f80af46be707" aria-labelledby="tooltip-9d09fa68-e1a2-483f-a20c-013febb2eba7" type="button" data-view-component="true" class="Button Button--iconOnly Button--invisible Button--medium flash-close js-flash-close">  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x Button-visual">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg>
</button><tool-tip id="tooltip-9d09fa68-e1a2-483f-a20c-013febb2eba7" for="icon-button-8ac41a50-4fb0-4254-a46c-f80af46be707" popover="manual" data-direction="s" data-type="label" data-view-component="true" class="sr-only position-absolute">Dismiss alert</tool-tip>

</div>
    </div>

  <div id="start-of-content" class="show-on-focus"></div>

    <div id="js-flash-container" class="flash-container" data-turbo-replace>

  <template class="js-flash-template">

<div class="flash flash-full   {{ className }}">
  <div >
    <button autofocus class="flash-close js-flash-close" type="button" aria-label="Dismiss this message">
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg>
    </button>
    <div aria-atomic="true" role="alert" class="js-flash-alert">

      <div>{{ message }}</div>

    </div>
  </div>
</div>
  </template>
</div>

  <div
    class="application-main "
    data-commit-hovercards-enabled
    data-discussion-hovercards-enabled
    data-issue-and-pr-hovercards-enabled
    data-project-hovercards-enabled
  >
        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
    <main id="js-repo-pjax-container" >

  <div id="repository-container-header"  class="pt-3 hide-full-screen" style="background-color: var(--page-header-bgColor, var(--color-page-header-bg));" data-turbo-replace>

      <div class="d-flex flex-nowrap flex-justify-end mb-3  px-3 px-lg-5" style="gap: 1rem;">

        <div class="flex-auto min-width-0 width-fit">

  <div class=" d-flex flex-wrap flex-items-center wb-break-word f3 text-normal">
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-repo color-fg-muted mr-2">
    <path d="M2 2.5A2.5 2.5 0 0 1 4.5 0h8.75a.75.75 0 0 1 .75.75v12.5a.75.75 0 0 1-.75.75h-2.5a.75.75 0 0 1 0-1.5h1.75v-2h-8a1 1 0 0 0-.714 1.7.75.75 0 1 1-1.072 1.05A2.495 2.495 0 0 1 2 11.5Zm10.5-1h-8a1 1 0 0 0-1 1v6.708A2.486 2.486 0 0 1 4.5 9h8ZM5 12.25a.25.25 0 0 1 .25-.25h3.5a.25.25 0 0 1 .25.25v3.25a.25.25 0 0 1-.4.2l-1.45-1.087a.249.249 0 0 0-.3 0L5.4 15.7a.25.25 0 0 1-.4-.2Z"></path>
</svg>

    <span class="author flex-self-stretch" itemprop="author">
      <a class="url fn" rel="author" data-hovercard-type="user" data-hovercard-url="/users/johncsantiago/hovercard" data-octo-click="hovercard-link-click" data-octo-dimensions="link_type:self" href="/johncsantiago">
        johncsantiago
</a>    </span>
    <span class="mx-1 flex-self-stretch color-fg-muted">/</span>
    <strong itemprop="name" class="mr-2 flex-self-stretch">
      <a data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" href="/johncsantiago/WhartonLab">WhartonLab</a>
    </strong>

    <span></span><span class="Label Label--secondary v-align-middle mr-1">Public</span>
  </div>

        </div>

        <div id="repository-details-container" class="flex-shrink-0" data-turbo-replace style="max-width: 70%;">
            <ul class="pagehead-actions flex-shrink-0 d-none d-md-inline" style="padding: 2px 0;">

  <li>
            <a href="/login?return_to=%2Fjohncsantiago%2FWhartonLab" rel="nofollow" id="repository-details-watch-button" data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;notification subscription menu watch&quot;,&quot;repository_id&quot;:null,&quot;auth_type&quot;:&quot;LOG_IN&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="8244cbc4c1a4b029c45cd0615ed29bc227ec668b7844c1ca75aab6d397c24db1" aria-label="You must be signed in to change notification settings" data-view-component="true" class="btn-sm btn">    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-bell mr-2">
    <path d="M8 16a2 2 0 0 0 1.985-1.75c.017-.137-.097-.25-.235-.25h-3.5c-.138 0-.252.113-.235.25A2 2 0 0 0 8 16ZM3 5a5 5 0 0 1 10 0v2.947c0 .05.015.098.042.139l1.703 2.555A1.519 1.519 0 0 1 13.482 13H2.518a1.516 1.516 0 0 1-1.263-2.36l1.703-2.554A.255.255 0 0 0 3 7.947Zm5-3.5A3.5 3.5 0 0 0 4.5 5v2.947c0 .346-.102.683-.294.97l-1.703 2.556a.017.017 0 0 0-.003.01l.001.006c0 .002.002.004.004.006l.006.004.007.001h10.964l.007-.001.006-.004.004-.006.001-.007a.017.017 0 0 0-.003-.01l-1.703-2.554a1.745 1.745 0 0 1-.294-.97V5A3.5 3.5 0 0 0 8 1.5Z"></path>
</svg>Notifications
</a>    <tool-tip id="tooltip-b4447439-038d-46a9-bf1c-ee353a2b7ccc" for="repository-details-watch-button" popover="manual" data-direction="s" data-type="description" data-view-component="true" class="sr-only position-absolute">You must be signed in to change notification settings</tool-tip>

  </li>

  <li>
          <a icon="repo-forked" id="fork-button" href="/login?return_to=%2Fjohncsantiago%2FWhartonLab" rel="nofollow" data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;repo details fork button&quot;,&quot;repository_id&quot;:652065041,&quot;auth_type&quot;:&quot;LOG_IN&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="335d006439cb21fbc111dc1e7b4b9a54ac69fd9352fc1100ce32016a28ccd086" data-view-component="true" class="btn-sm btn">    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-repo-forked mr-2">
    <path d="M5 5.372v.878c0 .414.336.75.75.75h4.5a.75.75 0 0 0 .75-.75v-.878a2.25 2.25 0 1 1 1.5 0v.878a2.25 2.25 0 0 1-2.25 2.25h-1.5v2.128a2.251 2.251 0 1 1-1.5 0V8.5h-1.5A2.25 2.25 0 0 1 3.5 6.25v-.878a2.25 2.25 0 1 1 1.5 0ZM5 3.25a.75.75 0 1 0-1.5 0 .75.75 0 0 0 1.5 0Zm6.75.75a.75.75 0 1 0 0-1.5.75.75 0 0 0 0 1.5Zm-3 8.75a.75.75 0 1 0-1.5 0 .75.75 0 0 0 1.5 0Z"></path>
</svg>Fork
    <span id="repo-network-counter" data-pjax-replace="true" data-turbo-replace="true" title="0" data-view-component="true" class="Counter">0</span>
</a>
  </li>

  <li>
        <div data-view-component="true" class="BtnGroup d-flex">
        <a href="/login?return_to=%2Fjohncsantiago%2FWhartonLab" rel="nofollow" data-hydro-click="{&quot;event_type&quot;:&quot;authentication.click&quot;,&quot;payload&quot;:{&quot;location_in_page&quot;:&quot;star button&quot;,&quot;repository_id&quot;:652065041,&quot;auth_type&quot;:&quot;LOG_IN&quot;,&quot;originating_url&quot;:&quot;https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd&quot;,&quot;user_id&quot;:null}}" data-hydro-click-hmac="dd6f8ce3b9985cac24c44f08eb511ee6753cb65ce5b3eebae54c3f0b04ec78c4" aria-label="You must be signed in to star a repository" data-view-component="true" class="tooltipped tooltipped-sw btn-sm btn">    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-star v-align-text-bottom d-inline-block mr-2">
    <path d="M8 .25a.75.75 0 0 1 .673.418l1.882 3.815 4.21.612a.75.75 0 0 1 .416 1.279l-3.046 2.97.719 4.192a.751.751 0 0 1-1.088.791L8 12.347l-3.766 1.98a.75.75 0 0 1-1.088-.79l.72-4.194L.818 6.374a.75.75 0 0 1 .416-1.28l4.21-.611L7.327.668A.75.75 0 0 1 8 .25Zm0 2.445L6.615 5.5a.75.75 0 0 1-.564.41l-3.097.45 2.24 2.184a.75.75 0 0 1 .216.664l-.528 3.084 2.769-1.456a.75.75 0 0 1 .698 0l2.77 1.456-.53-3.084a.75.75 0 0 1 .216-.664l2.24-2.183-3.096-.45a.75.75 0 0 1-.564-.41L8 2.694Z"></path>
</svg><span data-view-component="true" class="d-inline">
          Star
</span>          <span id="repo-stars-counter-star" aria-label="0 users starred this repository" data-singular-suffix="user starred this repository" data-plural-suffix="users starred this repository" data-turbo-replace="true" title="0" data-view-component="true" class="Counter js-social-count">0</span>
</a></div>
  </li>

</ul>

        </div>
      </div>

        <div id="responsive-meta-container" data-turbo-replace>
</div>

          <nav data-pjax="#js-repo-pjax-container" aria-label="Repository" data-view-component="true" class="js-repo-nav js-sidenav-container-pjax js-responsive-underlinenav overflow-hidden UnderlineNav px-3 px-md-4 px-lg-5">

  <ul data-view-component="true" class="UnderlineNav-body list-style-none">
      <li data-view-component="true" class="d-inline-flex">
  <a id="code-tab" href="/johncsantiago/WhartonLab" data-tab-item="i0code-tab" data-selected-links="repo_source repo_downloads repo_commits repo_releases repo_tags repo_branches repo_packages repo_deployments repo_attestations /johncsantiago/WhartonLab" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g c" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Code&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" aria-current="page" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item selected">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-code UnderlineNav-octicon d-none d-sm-inline">
    <path d="m11.28 3.22 4.25 4.25a.75.75 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734L13.94 8l-3.72-3.72a.749.749 0 0 1 .326-1.275.749.749 0 0 1 .734.215Zm-6.56 0a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042L2.06 8l3.72 3.72a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L.47 8.53a.75.75 0 0 1 0-1.06Z"></path>
</svg>
        <span data-content="Code">Code</span>
          <span id="code-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="Not available" data-view-component="true" class="Counter"></span>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="issues-tab" href="/johncsantiago/WhartonLab/issues" data-tab-item="i1issues-tab" data-selected-links="repo_issues repo_labels repo_milestones /johncsantiago/WhartonLab/issues" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g i" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Issues&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-issue-opened UnderlineNav-octicon d-none d-sm-inline">
    <path d="M8 9.5a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path><path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Z"></path>
</svg>
        <span data-content="Issues">Issues</span>
          <span id="issues-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="0" hidden="hidden" data-view-component="true" class="Counter">0</span>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="pull-requests-tab" href="/johncsantiago/WhartonLab/pulls" data-tab-item="i2pull-requests-tab" data-selected-links="repo_pulls checks /johncsantiago/WhartonLab/pulls" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g p" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Pull requests&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-git-pull-request UnderlineNav-octicon d-none d-sm-inline">
    <path d="M1.5 3.25a2.25 2.25 0 1 1 3 2.122v5.256a2.251 2.251 0 1 1-1.5 0V5.372A2.25 2.25 0 0 1 1.5 3.25Zm5.677-.177L9.573.677A.25.25 0 0 1 10 .854V2.5h1A2.5 2.5 0 0 1 13.5 5v5.628a2.251 2.251 0 1 1-1.5 0V5a1 1 0 0 0-1-1h-1v1.646a.25.25 0 0 1-.427.177L7.177 3.427a.25.25 0 0 1 0-.354ZM3.75 2.5a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Zm0 9.5a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Zm8.25.75a.75.75 0 1 0 1.5 0 .75.75 0 0 0-1.5 0Z"></path>
</svg>
        <span data-content="Pull requests">Pull requests</span>
          <span id="pull-requests-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="0" hidden="hidden" data-view-component="true" class="Counter">0</span>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="actions-tab" href="/johncsantiago/WhartonLab/actions" data-tab-item="i3actions-tab" data-selected-links="repo_actions /johncsantiago/WhartonLab/actions" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g a" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Actions&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-play UnderlineNav-octicon d-none d-sm-inline">
    <path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Zm4.879-2.773 4.264 2.559a.25.25 0 0 1 0 .428l-4.264 2.559A.25.25 0 0 1 6 10.559V5.442a.25.25 0 0 1 .379-.215Z"></path>
</svg>
        <span data-content="Actions">Actions</span>
          <span id="actions-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="Not available" data-view-component="true" class="Counter"></span>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="projects-tab" href="/johncsantiago/WhartonLab/projects" data-tab-item="i4projects-tab" data-selected-links="repo_projects new_repo_project repo_project /johncsantiago/WhartonLab/projects" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g b" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Projects&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-table UnderlineNav-octicon d-none d-sm-inline">
    <path d="M0 1.75C0 .784.784 0 1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25ZM6.5 6.5v8h7.75a.25.25 0 0 0 .25-.25V6.5Zm8-1.5V1.75a.25.25 0 0 0-.25-.25H6.5V5Zm-13 1.5v7.75c0 .138.112.25.25.25H5v-8ZM5 5V1.5H1.75a.25.25 0 0 0-.25.25V5Z"></path>
</svg>
        <span data-content="Projects">Projects</span>
          <span id="projects-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="0" hidden="hidden" data-view-component="true" class="Counter">0</span>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="security-tab" href="/johncsantiago/WhartonLab/security" data-tab-item="i5security-tab" data-selected-links="security overview alerts policy token_scanning code_scanning /johncsantiago/WhartonLab/security" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-hotkey="g s" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Security&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-shield UnderlineNav-octicon d-none d-sm-inline">
    <path d="M7.467.133a1.748 1.748 0 0 1 1.066 0l5.25 1.68A1.75 1.75 0 0 1 15 3.48V7c0 1.566-.32 3.182-1.303 4.682-.983 1.498-2.585 2.813-5.032 3.855a1.697 1.697 0 0 1-1.33 0c-2.447-1.042-4.049-2.357-5.032-3.855C1.32 10.182 1 8.566 1 7V3.48a1.75 1.75 0 0 1 1.217-1.667Zm.61 1.429a.25.25 0 0 0-.153 0l-5.25 1.68a.25.25 0 0 0-.174.238V7c0 1.358.275 2.666 1.057 3.86.784 1.194 2.121 2.34 4.366 3.297a.196.196 0 0 0 .154 0c2.245-.956 3.582-2.104 4.366-3.298C13.225 9.666 13.5 8.36 13.5 7V3.48a.251.251 0 0 0-.174-.237l-5.25-1.68ZM8.75 4.75v3a.75.75 0 0 1-1.5 0v-3a.75.75 0 0 1 1.5 0ZM9 10.5a1 1 0 1 1-2 0 1 1 0 0 1 2 0Z"></path>
</svg>
        <span data-content="Security">Security</span>
          <include-fragment src="/johncsantiago/WhartonLab/security/overall-count" accept="text/fragment+html"></include-fragment>

</a></li>
      <li data-view-component="true" class="d-inline-flex">
  <a id="insights-tab" href="/johncsantiago/WhartonLab/pulse" data-tab-item="i6insights-tab" data-selected-links="repo_graphs repo_contributors dependency_graph dependabot_updates pulse people community /johncsantiago/WhartonLab/pulse" data-pjax="#repo-content-pjax-container" data-turbo-frame="repo-content-turbo-frame" data-analytics-event="{&quot;category&quot;:&quot;Underline navbar&quot;,&quot;action&quot;:&quot;Click tab&quot;,&quot;label&quot;:&quot;Insights&quot;,&quot;target&quot;:&quot;UNDERLINE_NAV.TAB&quot;}" data-view-component="true" class="UnderlineNav-item no-wrap js-responsive-underlinenav-item js-selected-navigation-item">

              <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-graph UnderlineNav-octicon d-none d-sm-inline">
    <path d="M1.5 1.75V13.5h13.75a.75.75 0 0 1 0 1.5H.75a.75.75 0 0 1-.75-.75V1.75a.75.75 0 0 1 1.5 0Zm14.28 2.53-5.25 5.25a.75.75 0 0 1-1.06 0L7 7.06 4.28 9.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.25-3.25a.75.75 0 0 1 1.06 0L10 7.94l4.72-4.72a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Z"></path>
</svg>
        <span data-content="Insights">Insights</span>
          <span id="insights-repo-tab-count" data-pjax-replace="" data-turbo-replace="" title="Not available" data-view-component="true" class="Counter"></span>

</a></li>
</ul>
    <div style="visibility:hidden;" data-view-component="true" class="UnderlineNav-actions js-responsive-underlinenav-overflow position-absolute pr-3 pr-md-4 pr-lg-5 right-0">      <action-menu data-select-variant="none" data-view-component="true">
  <focus-group direction="vertical" mnemonics retain>
    <button id="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-button" popovertarget="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-overlay" aria-controls="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-list" aria-haspopup="true" aria-labelledby="tooltip-2edaa656-737c-4dfb-b4c5-e986240a7302" type="button" data-view-component="true" class="Button Button--iconOnly Button--secondary Button--medium UnderlineNav-item">  <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-kebab-horizontal Button-visual">
    <path d="M8 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3ZM1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Zm13 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path>
</svg>
</button><tool-tip id="tooltip-2edaa656-737c-4dfb-b4c5-e986240a7302" for="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-button" popover="manual" data-direction="s" data-type="label" data-view-component="true" class="sr-only position-absolute">Additional navigation options</tool-tip>

<anchored-position data-target="action-menu.overlay" id="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-overlay" anchor="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-button" align="start" side="outside-bottom" anchor-offset="normal" popover="auto" data-view-component="true">
  <div data-view-component="true" class="Overlay Overlay--size-auto">

      <div data-view-component="true" class="Overlay-body Overlay-body--paddingNone">          <action-list>
  <div data-view-component="true">
    <ul aria-labelledby="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-button" id="action-menu-b06f3d73-2e5b-4c9a-8154-7b17f5f33f9a-list" role="menu" data-view-component="true" class="ActionListWrap--inset ActionListWrap">
        <li hidden="hidden" data-menu-item="i0code-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-ffbd1f9f-20d9-4440-b6ff-4b9088c05edf" href="/johncsantiago/WhartonLab" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-code">
    <path d="m11.28 3.22 4.25 4.25a.75.75 0 0 1 0 1.06l-4.25 4.25a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734L13.94 8l-3.72-3.72a.749.749 0 0 1 .326-1.275.749.749 0 0 1 .734.215Zm-6.56 0a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042L2.06 8l3.72 3.72a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L.47 8.53a.75.75 0 0 1 0-1.06Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Code
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i1issues-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-54d1bbaa-754e-49ba-b0b3-4747d0f94401" href="/johncsantiago/WhartonLab/issues" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-issue-opened">
    <path d="M8 9.5a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path><path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Issues
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i2pull-requests-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-a199e744-b7f6-4d15-8672-a7c0cad70009" href="/johncsantiago/WhartonLab/pulls" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-git-pull-request">
    <path d="M1.5 3.25a2.25 2.25 0 1 1 3 2.122v5.256a2.251 2.251 0 1 1-1.5 0V5.372A2.25 2.25 0 0 1 1.5 3.25Zm5.677-.177L9.573.677A.25.25 0 0 1 10 .854V2.5h1A2.5 2.5 0 0 1 13.5 5v5.628a2.251 2.251 0 1 1-1.5 0V5a1 1 0 0 0-1-1h-1v1.646a.25.25 0 0 1-.427.177L7.177 3.427a.25.25 0 0 1 0-.354ZM3.75 2.5a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Zm0 9.5a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Zm8.25.75a.75.75 0 1 0 1.5 0 .75.75 0 0 0-1.5 0Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Pull requests
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i3actions-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-f343815f-09aa-4fef-b51d-fea509f84738" href="/johncsantiago/WhartonLab/actions" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-play">
    <path d="M8 0a8 8 0 1 1 0 16A8 8 0 0 1 8 0ZM1.5 8a6.5 6.5 0 1 0 13 0 6.5 6.5 0 0 0-13 0Zm4.879-2.773 4.264 2.559a.25.25 0 0 1 0 .428l-4.264 2.559A.25.25 0 0 1 6 10.559V5.442a.25.25 0 0 1 .379-.215Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Actions
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i4projects-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-65a98546-9e8a-467e-bf20-732f4f55dc02" href="/johncsantiago/WhartonLab/projects" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-table">
    <path d="M0 1.75C0 .784.784 0 1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25ZM6.5 6.5v8h7.75a.25.25 0 0 0 .25-.25V6.5Zm8-1.5V1.75a.25.25 0 0 0-.25-.25H6.5V5Zm-13 1.5v7.75c0 .138.112.25.25.25H5v-8ZM5 5V1.5H1.75a.25.25 0 0 0-.25.25V5Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Projects
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i5security-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-06043754-6f11-4072-b197-78f6e45bebdc" href="/johncsantiago/WhartonLab/security" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-shield">
    <path d="M7.467.133a1.748 1.748 0 0 1 1.066 0l5.25 1.68A1.75 1.75 0 0 1 15 3.48V7c0 1.566-.32 3.182-1.303 4.682-.983 1.498-2.585 2.813-5.032 3.855a1.697 1.697 0 0 1-1.33 0c-2.447-1.042-4.049-2.357-5.032-3.855C1.32 10.182 1 8.566 1 7V3.48a1.75 1.75 0 0 1 1.217-1.667Zm.61 1.429a.25.25 0 0 0-.153 0l-5.25 1.68a.25.25 0 0 0-.174.238V7c0 1.358.275 2.666 1.057 3.86.784 1.194 2.121 2.34 4.366 3.297a.196.196 0 0 0 .154 0c2.245-.956 3.582-2.104 4.366-3.298C13.225 9.666 13.5 8.36 13.5 7V3.48a.251.251 0 0 0-.174-.237l-5.25-1.68ZM8.75 4.75v3a.75.75 0 0 1-1.5 0v-3a.75.75 0 0 1 1.5 0ZM9 10.5a1 1 0 1 1-2 0 1 1 0 0 1 2 0Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Security
</span>      
</a>

</li>
        <li hidden="hidden" data-menu-item="i6insights-tab" data-targets="action-list.items" role="none" data-view-component="true" class="ActionListItem">

    <a tabindex="-1" id="item-b05a8f3e-1d44-4f52-9a0f-23cd410a2461" href="/johncsantiago/WhartonLab/pulse" role="menuitem" data-view-component="true" class="ActionListContent ActionListContent--visual16">
        <span class="ActionListItem-visual ActionListItem-visual--leading">
          <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-graph">
    <path d="M1.5 1.75V13.5h13.75a.75.75 0 0 1 0 1.5H.75a.75.75 0 0 1-.75-.75V1.75a.75.75 0 0 1 1.5 0Zm14.28 2.53-5.25 5.25a.75.75 0 0 1-1.06 0L7 7.06 4.28 9.78a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042l3.25-3.25a.75.75 0 0 1 1.06 0L10 7.94l4.72-4.72a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Z"></path>
</svg>
        </span>

        <span data-view-component="true" class="ActionListItem-label">
          Insights
</span>      
</a>

</li>
</ul>    
</div></action-list>

</div>

</div></anchored-position>  </focus-group>
</action-menu></div>
</nav>

  </div>

<turbo-frame id="repo-content-turbo-frame" target="_top" data-turbo-action="advance" class="">
    <div id="repo-content-pjax-container" class="repository-content " >

<react-app
  app-name="react-code-view"
  initial-path="/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd"
    style="display: block; min-height: calc(100vh - 64px);"
  data-attempted-ssr="true"
  data-ssr="true"
  data-lazy="false"
  data-alternate="false"
  data-data-router-enabled="false"
>

  <script type="application/json" data-target="react-app.embeddedData">{"payload":{"allShortcutsEnabled":false,"fileTree":{"":{"items":[{"name":"A4V_BodySections_RNAseq","path":"A4V_BodySections_RNAseq","contentType":"directory"},{"name":"Anna qPCR data","path":"Anna qPCR data","contentType":"directory"},{"name":"Barron","path":"Barron","contentType":"directory"},{"name":"ConspiracyNetwork","path":"ConspiracyNetwork","contentType":"directory"},{"name":"DeficiencyScreen","path":"DeficiencyScreen","contentType":"directory"},{"name":"DinaFolder","path":"DinaFolder","contentType":"directory"},{"name":"DrosophilaMotifsSingletonData","path":"DrosophilaMotifsSingletonData","contentType":"directory"},{"name":"G85R OXPHOS KEGG Pathways","path":"G85R OXPHOS KEGG Pathways","contentType":"directory"},{"name":"GeneralDataFiles","path":"GeneralDataFiles","contentType":"directory"},{"name":"Grants","path":"Grants","contentType":"directory"},{"name":"KEGG_Image_Files","path":"KEGG_Image_Files","contentType":"directory"},{"name":"Metabolomics","path":"Metabolomics","contentType":"directory"},{"name":"Papers","path":"Papers","contentType":"directory"},{"name":"RussoPaper","path":"RussoPaper","contentType":"directory"},{"name":"TKT_RNAseq","path":"TKT_RNAseq","contentType":"directory"},{"name":"alexa","path":"alexa","contentType":"directory"},{"name":"gbb_RNAseq","path":"gbb_RNAseq","contentType":"directory"},{"name":"gbbmeetingfigures_files","path":"gbbmeetingfigures_files","contentType":"directory"},{"name":"mtDNA-nucDNA analysis","path":"mtDNA-nucDNA analysis","contentType":"directory"},{"name":"qPCR","path":"qPCR","contentType":"directory"},{"name":".DS_Store","path":".DS_Store","contentType":"file"},{"name":"20240507_pharate_axonal_branching.Rmd","path":"20240507_pharate_axonal_branching.Rmd","contentType":"file"},{"name":"20240507_pharate_axonal_branching.html","path":"20240507_pharate_axonal_branching.html","contentType":"file"},{"name":"20240507_pharate_axonal_branching_Raw_Data.csv","path":"20240507_pharate_axonal_branching_Raw_Data.csv","contentType":"file"},{"name":"20240513_pharate_axonal_morphology_Raw_Data.csv","path":"20240513_pharate_axonal_morphology_Raw_Data.csv","contentType":"file"},{"name":"20240514_AxonalMorphologyResults.Rmd","path":"20240514_AxonalMorphologyResults.Rmd","contentType":"file"},{"name":"20240514_AxonalMorphologyResults.html","path":"20240514_AxonalMorphologyResults.html","contentType":"file"},{"name":"20240514_AxonalMorphologyResults.pdf","path":"20240514_AxonalMorphologyResults.pdf","contentType":"file"},{"name":"20240925_Santiago_LabMeeting.pptx","path":"20240925_Santiago_LabMeeting.pptx","contentType":"file"},{"name":"20241011_arc1presentation.pptx","path":"20241011_arc1presentation.pptx","contentType":"file"},{"name":"A4V BMP Signaling Genes Analysis.Rmd","path":"A4V BMP Signaling Genes Analysis.Rmd","contentType":"file"},{"name":"A4V-BMP-Signaling-Genes-Analysis.html","path":"A4V-BMP-Signaling-Genes-Analysis.html","contentType":"file"},{"name":"A4V_mt_vs_nuc_genesPCA.png","path":"A4V_mt_vs_nuc_genesPCA.png","contentType":"file"},{"name":"Aleah_Thesis_Figures.Rmd","path":"Aleah_Thesis_Figures.Rmd","contentType":"file"},{"name":"Arc1CcsNetwork.Rmd","path":"Arc1CcsNetwork.Rmd","contentType":"file"},{"name":"Arc1CcsNetwork.html","path":"Arc1CcsNetwork.html","contentType":"file"},{"name":"Arc1MeetingFigures.Rmd","path":"Arc1MeetingFigures.Rmd","contentType":"file"},{"name":"Arc1Sod1Network.csv","path":"Arc1Sod1Network.csv","contentType":"file"},{"name":"BMP Signaling Genes annotated.csv","path":"BMP Signaling Genes annotated.csv","contentType":"file"},{"name":"BMP Signaling Genes.csv","path":"BMP Signaling Genes.csv","contentType":"file"},{"name":"Cami qPCR Thesis Figures.Rmd","path":"Cami qPCR Thesis Figures.Rmd","contentType":"file"},{"name":"Cami-qPCR-Thesis-Figures.html","path":"Cami-qPCR-Thesis-Figures.html","contentType":"file"},{"name":"CamiCode.Rmd","path":"CamiCode.Rmd","contentType":"file"},{"name":"CamiCode.html","path":"CamiCode.html","contentType":"file"},{"name":"CamiData.Rmd","path":"CamiData.Rmd","contentType":"file"},{"name":"Cami_qPCR_dCt_data.csv","path":"Cami_qPCR_dCt_data.csv","contentType":"file"},{"name":"Cami_qPCR_dCt_data.xlsx","path":"Cami_qPCR_dCt_data.xlsx","contentType":"file"},{"name":"Cami_qpcr 2_28_24 - Sheet1.Rmd","path":"Cami_qpcr 2_28_24 - Sheet1.Rmd","contentType":"file"},{"name":"Cami_qpcr 2_28_24 - Sheet1.csv","path":"Cami_qpcr 2_28_24 - Sheet1.csv","contentType":"file"},{"name":"Dphalerata_male.tif.png","path":"Dphalerata_male.tif.png","contentType":"file"},{"name":"EmilyNetwork.Rmd","path":"EmilyNetwork.Rmd","contentType":"file"},{"name":"EmilyNetwork.csv","path":"EmilyNetwork.csv","contentType":"file"},{"name":"EmilyNetwork.html","path":"EmilyNetwork.html","contentType":"file"},{"name":"EmilyTBPH_qPCR.csv","path":"EmilyTBPH_qPCR.csv","contentType":"file"},{"name":"EmilyTBPH_qPCR.xlsx","path":"EmilyTBPH_qPCR.xlsx","contentType":"file"},{"name":"EmilyTBPHanalysis.Rmd","path":"EmilyTBPHanalysis.Rmd","contentType":"file"},{"name":"Emily_tbph_eclosion.csv","path":"Emily_tbph_eclosion.csv","contentType":"file"},{"name":"FlashTalkModifierData.csv","path":"FlashTalkModifierData.csv","contentType":"file"},{"name":"FlashTalkModifierFigures.Rmd","path":"FlashTalkModifierFigures.Rmd","contentType":"file"},{"name":"FlashTalkModifierFigures.html","path":"FlashTalkModifierFigures.html","contentType":"file"},{"name":"Functions_OmicsQuickPlotFunctions.R","path":"Functions_OmicsQuickPlotFunctions.R","contentType":"file"},{"name":"G85R GOandKEGGTermEnrichment.Rmd","path":"G85R GOandKEGGTermEnrichment.Rmd","contentType":"file"},{"name":"G85R-GOandKEGGTermEnrichment.html","path":"G85R-GOandKEGGTermEnrichment.html","contentType":"file"},{"name":"G85R.GOandKEGGPlottingFunctions.R","path":"G85R.GOandKEGGPlottingFunctions.R","contentType":"file"},{"name":"G85R_OXPHOS_KEGG_Pathways.Rmd","path":"G85R_OXPHOS_KEGG_Pathways.Rmd","contentType":"file"},{"name":"GOandKEGGPlottingFunctions.R","path":"GOandKEGGPlottingFunctions.R","contentType":"file"},{"name":"GOandKEGGTermEnrichment.Rmd","path":"GOandKEGGTermEnrichment.Rmd","contentType":"file"},{"name":"GOandKEGGTermEnrichment.html","path":"GOandKEGGTermEnrichment.html","contentType":"file"},{"name":"GeneExpressionBoxPlots.Rmd","path":"GeneExpressionBoxPlots.Rmd","contentType":"file"},{"name":"GeneExpressionBoxPlots.html","path":"GeneExpressionBoxPlots.html","contentType":"file"},{"name":"JohnSantiago_mtDNAxnucDNAqPCR_Notes.docx","path":"JohnSantiago_mtDNAxnucDNAqPCR_Notes.docx","contentType":"file"},{"name":"KristiPresentationData.Rmd","path":"KristiPresentationData.Rmd","contentType":"file"},{"name":"KristiPresentationData.html","path":"KristiPresentationData.html","contentType":"file"},{"name":"NAD.edges.csv","path":"NAD.edges.csv","contentType":"file"},{"name":"NewEmilyNetwork.csv","path":"NewEmilyNetwork.csv","contentType":"file"},{"name":"NewEmilyNetwork.xlsx","path":"NewEmilyNetwork.xlsx","contentType":"file"},{"name":"Nguyen Serpe 2024 scRNA-seq VNC.csv","path":"Nguyen Serpe 2024 scRNA-seq VNC.csv","contentType":"file"},{"name":"OmicsQuickPlotFunctions.Rmd","path":"OmicsQuickPlotFunctions.Rmd","contentType":"file"},{"name":"OmicsQuickPlotFunctions.html","path":"OmicsQuickPlotFunctions.html","contentType":"file"},{"name":"Paranhos 2021 SOD1 Review.pdf","path":"Paranhos 2021 SOD1 Review.pdf","contentType":"file"},{"name":"PunnettSquareApp.Rmd","path":"PunnettSquareApp.Rmd","contentType":"file"},{"name":"PunnettSquareApp.html","path":"PunnettSquareApp.html","contentType":"file"},{"name":"QiagenADArrayGenes.csv","path":"QiagenADArrayGenes.csv","contentType":"file"},{"name":"Russo Fig 1 eclosion.csv","path":"Russo Fig 1 eclosion.csv","contentType":"file"},{"name":"Russo Fig 1 eclosion_TukeyDATA.csv","path":"Russo Fig 1 eclosion_TukeyDATA.csv","contentType":"file"},{"name":"SG Kankel.csv","path":"SG Kankel.csv","contentType":"file"},{"name":"SG Kankel.xlsx","path":"SG Kankel.xlsx","contentType":"file"},{"name":"Serpe 2024 GliaSubtypes.csv","path":"Serpe 2024 GliaSubtypes.csv","contentType":"file"},{"name":"Serpe 2024 InterneuronClusters.csv","path":"Serpe 2024 InterneuronClusters.csv","contentType":"file"},{"name":"Serpe 2024 MNClusters.csv","path":"Serpe 2024 MNClusters.csv","contentType":"file"},{"name":"SerpeSCdata.Rmd","path":"SerpeSCdata.Rmd","contentType":"file"},{"name":"SerpeSCdata.html","path":"SerpeSCdata.html","contentType":"file"},{"name":"SerpeSCdata.pdf","path":"SerpeSCdata.pdf","contentType":"file"},{"name":"Shortcuts_OmicsQuickPlotFunctions.Rmd","path":"Shortcuts_OmicsQuickPlotFunctions.Rmd","contentType":"file"},{"name":"Shortcuts_OmicsQuickPlotFunctions.html","path":"Shortcuts_OmicsQuickPlotFunctions.html","contentType":"file"},{"name":"UB7 - G85R Pharate Leg Axonal Branching \u0026 Mitochondria  - CSV_Branching.csv","path":"UB7 - G85R Pharate Leg Axonal Branching \u0026 Mitochondria  - CSV_Branching.csv","contentType":"file"},{"name":"arc1presentation.pptx","path":"arc1presentation.pptx","contentType":"file"},{"name":"dme00010.GRFCvWTFC  and  GRMCvWTMC.multi.png","path":"dme00010.GRFCvWTFC  and  GRMCvWTMC.multi.png","contentType":"file"},{"name":"dme00010.GRxWT.FC_GRxWT.MC.multi.png","path":"dme00010.GRxWT.FC_GRxWT.MC.multi.png","contentType":"file"},{"name":"dme00010.png","path":"dme00010.png","contentType":"file"},{"name":"dme00010.xml","path":"dme00010.xml","contentType":"file"},{"name":"dme00030.G85RvsWT_FemaleandMale.multi.png","path":"dme00030.G85RvsWT_FemaleandMale.multi.png","contentType":"file"},{"name":"dme00030.png","path":"dme00030.png","contentType":"file"},{"name":"dme00030.xml","path":"dme00030.xml","contentType":"file"},{"name":"dme00190.A4V_FandM_9T.png","path":"dme00190.A4V_FandM_9T.png","contentType":"file"},{"name":"dme00190.G85RandWT_CxOE_Genes with GR.CxOE_Metab.multi.png","path":"dme00190.G85RandWT_CxOE_Genes with GR.CxOE_Metab.multi.png","contentType":"file"},{"name":"dme00190.gbbKOxgbbWT.multi.png","path":"dme00190.gbbKOxgbbWT.multi.png","contentType":"file"},{"name":"dme00190.png","path":"dme00190.png","contentType":"file"},{"name":"dme00190.xml","path":"dme00190.xml","contentType":"file"},{"name":"dme00563.A4V_FandM_9T.multi.png","path":"dme00563.A4V_FandM_9T.multi.png","contentType":"file"},{"name":"dme00563.A4V_FandM_9T.png","path":"dme00563.A4V_FandM_9T.png","contentType":"file"},{"name":"dme00563.png","path":"dme00563.png","contentType":"file"},{"name":"dme00563.xml","path":"dme00563.xml","contentType":"file"},{"name":"dme00760.A9MTvS9MT  and  A40FTvS40FT.multi.png","path":"dme00760.A9MTvS9MT  and  A40FTvS40FT.multi.png","contentType":"file"},{"name":"dme00760.GRFCvWTFC  and  GRMCvWTMC.multi.png","path":"dme00760.GRFCvWTFC  and  GRMCvWTMC.multi.png","contentType":"file"},{"name":"dme00760.gbbKOxgbbWT.multi.png","path":"dme00760.gbbKOxgbbWT.multi.png","contentType":"file"},{"name":"dme00760.png","path":"dme00760.png","contentType":"file"},{"name":"dme00760.xml","path":"dme00760.xml","contentType":"file"},{"name":"gbbmeetingfigures.Rmd","path":"gbbmeetingfigures.Rmd","contentType":"file"},{"name":"mt.nuc PCA for grant.Rmd","path":"mt.nuc PCA for grant.Rmd","contentType":"file"},{"name":"mt.nuc-PCA-for-grant.html","path":"mt.nuc-PCA-for-grant.html","contentType":"file"},{"name":"mt.nuc.OXPHOS_PCAdata.csv","path":"mt.nuc.OXPHOS_PCAdata.csv","contentType":"file"},{"name":"~$arc1presentation.pptx","path":"~$arc1presentation.pptx","contentType":"file"}],"totalCount":123}},"fileTreeProcessingTime":17.475392,"foldersToFetch":[],"repo":{"id":652065041,"defaultBranch":"master","name":"WhartonLab","ownerLogin":"johncsantiago","currentUserCanPush":false,"isFork":false,"isEmpty":false,"createdAt":"2023-06-11T01:12:53.000Z","ownerAvatar":"https://avatars.githubusercontent.com/u/61519162?v=4","public":true,"private":false,"isOrgOwned":false},"codeLineWrapEnabled":false,"symbolsExpanded":false,"treeExpanded":true,"refInfo":{"name":"master","listCacheKey":"v0:1686446179.162525","canEdit":false,"refType":"branch","currentOid":"19a37d6cf6739514e404cc231008021c1d4ca7e8"},"path":"G85R GOandKEGGTermEnrichment.Rmd","currentUser":null,"blob":{"rawLines":["---","title: \"GO and KEGG Term Enrichment\"","author: \"John Santiago\"","date: \"2024-05-08\"","output: html_document","---","","```{r setup, include=FALSE}","","knitr::opts_chunk$set(echo = TRUE)","","```","","","","```{r echo = F, message = F}","","# Conditions","#Geno is WT or GR","#TKT is either \"C\", \"OE\", or \"Df\"","#Sex is \"F\" or \"M\"","","Geno1 = \"GR\"","TKT1 = \"C\"","Sex1 = \"F\"","","Geno2 = \"WT\"","TKT2 = \"C\"","Sex2 = \"F\"","","##Conditions for second comparison","Geno3 = \"GR\"","TKT3 = \"C\"","Sex3 = \"M\"","","Geno4 = \"WT\"","TKT4 = \"C\"","Sex4 = \"M\"","","","","","","```","","```{r echo = F, message = F}","","source('/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R')","","plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,","                      Sex1, Sex2, Sex3, Sex4,","                      TKT1, TKT2, TKT3, TKT4)","","```","","","```{r echo = F}","","##Uses data from primary comparison","##Plots genes with an FDR \u003c= 0.05","##point size is relative to maximum mean expression in the two conditions","","G85R.volcano(plot.data)","","```","","","```{r echo = F}","","##Uses data from primary comparison","##point size is relative to max mean expression in any condition","##grey points indicate less than 1 fold difference between the comparisons","G85R.compare.genes(plot.data)","","```","","","```{r echo = F}","","##Uses data from primary comparison","##point size is relative to mean expression in variable condition","G85R.DEG.venn(plot.data)","","```","","```{r echo = F, include = F, warning = F}","","####Uses sigDEGs from primary comparison","cat.data = G85R.Enrichment(plot.data)","","```","","","```{r echo = F}","","","##which ranks of categories to use","##a vector of numbers specifying which ranks to use","##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.","##can also just type 'sigs' ","usecats=c(1:20)","#usecats = 'sigs'  ","","G85R.KEGG20(cat.data, plot.data, usecats)","","```","","","```{r echo = F, include = T}","","##can be the exact name or 5 digit code in quotes","specific.kegg = \"00980\"","","G85R.plotkegg.genes(specific.kegg, plot.data)","","```","","","```{r echo = F, message=F, fig.width=7}","","##5 digits from KEGG ID","PathwayID = \"00010\"","","#options include 'primary' or 'both'","use = 'both'","","","G85R.KEGG.diagram(PathwayID, plot.data, use, sigs.only = F)","","","```","","","```{r echo = F, include = T, warnings = F}","","##can be the exact name or 5 digit code in quotes","specific.kegg = \"00010\"","","G85R.comparekegg.genes(specific.kegg, plot.data)","","```","","","```{r echo = F}","","## BP, CC, or MF","GO.ontology = 'BP'","","##can select which categories ot include or say 'sigs.only'","usecats=c(1:20)","#usecats = 'sigs.only'","","G85R.GO20(cat.data, GO.ontology, plot.data, usecats)","","```","","","```{r echo = F}","","##the 7 digits of a GOterm id or the exact term name","specific.go = '0005811'","","G85R.plotgo.genes(specific.go, plot.data)","","```","","","```{r echo = F, warning = F}","","##the 7 digits of a GOterm id or the exact term name","specific.go = '0005811'","","G85R.comparego.genes(specific.go, plot.data)","","```","","","```{r echo = F, warning = F, message = F}","","","## BP, CC, or MF","GO.ontology = 'BP'","","rt = tree(cat.data, GO.ontology)","  ","treemapPlot(rt)","","```","","","```{r echo = F, warning = F}","","##a parent category generated in the treemapPlot function","parent.category = 'neurogenesis'","","G85R.plotparentcat.genes(parent.category, plot.data)","","```","","","```{r echo = F}","","##a parent category generated in the treemapPlot function","##parent.category = 'small molecule biosynthetic process'","","G85R.compareparent.genes(parent.category, plot.data)","##dot size is relative to the max FDR of either condition","","","```  "],"stylingDirectives":[[[0,3,"pl-s"]],[[0,5,"pl-ent"],[7,36,"pl-s"],[7,8,"pl-pds"],[35,36,"pl-pds"]],[[0,6,"pl-ent"],[8,23,"pl-s"],[8,9,"pl-pds"],[22,23,"pl-pds"]],[[0,4,"pl-ent"],[6,18,"pl-s"],[6,7,"pl-pds"],[17,18,"pl-pds"]],[[0,6,"pl-ent"],[8,21,"pl-s"]],[[0,3,"pl-s"]],[],[[0,3,"pl-s"],[3,5,"pl-en"],[27,27,"pl-c1"]],[[0,0,"pl-c1"]],[[0,34,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[28,28,"pl-c1"]],[[0,0,"pl-c1"]],[[0,12,"pl-c1"]],[[0,17,"pl-c1"]],[[0,33,"pl-c1"]],[[0,18,"pl-c1"]],[[0,0,"pl-c1"]],[[0,12,"pl-c1"]],[[0,10,"pl-c1"]],[[0,10,"pl-c1"]],[[0,0,"pl-c1"]],[[0,12,"pl-c1"]],[[0,10,"pl-c1"]],[[0,10,"pl-c1"]],[[0,0,"pl-c1"]],[[0,34,"pl-c1"]],[[0,12,"pl-c1"]],[[0,10,"pl-c1"]],[[0,10,"pl-c1"]],[[0,0,"pl-c1"]],[[0,12,"pl-c1"]],[[0,10,"pl-c1"]],[[0,10,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[[0,3,"pl-s"],[3,5,"pl-en"],[28,28,"pl-c1"]],[[0,0,"pl-c1"]],[[0,92,"pl-c1"]],[[0,0,"pl-c1"]],[[0,49,"pl-c1"]],[[0,45,"pl-c1"]],[[0,45,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,35,"pl-c1"]],[[0,33,"pl-c1"]],[[0,73,"pl-c1"]],[[0,0,"pl-c1"]],[[0,23,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,35,"pl-c1"]],[[0,64,"pl-c1"]],[[0,74,"pl-c1"]],[[0,29,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,35,"pl-c1"]],[[0,65,"pl-c1"]],[[0,24,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[[0,3,"pl-s"],[3,5,"pl-en"],[41,41,"pl-c1"]],[[0,0,"pl-c1"]],[[0,40,"pl-c1"]],[[0,37,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,34,"pl-c1"]],[[0,51,"pl-c1"]],[[0,67,"pl-c1"]],[[0,28,"pl-c1"]],[[0,15,"pl-c1"]],[[0,19,"pl-c1"]],[[0,0,"pl-c1"]],[[0,41,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[28,28,"pl-c1"]],[[0,0,"pl-c1"]],[[0,49,"pl-c1"]],[[0,23,"pl-c1"]],[[0,0,"pl-c1"]],[[0,45,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[39,39,"pl-c1"]],[[0,0,"pl-c1"]],[[0,23,"pl-c1"]],[[0,19,"pl-c1"]],[[0,0,"pl-c1"]],[[0,36,"pl-c1"]],[[0,12,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,59,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[42,42,"pl-c1"]],[[0,0,"pl-c1"]],[[0,49,"pl-c1"]],[[0,23,"pl-c1"]],[[0,0,"pl-c1"]],[[0,48,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,16,"pl-c1"]],[[0,18,"pl-c1"]],[[0,0,"pl-c1"]],[[0,59,"pl-c1"]],[[0,15,"pl-c1"]],[[0,22,"pl-c1"]],[[0,0,"pl-c1"]],[[0,52,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,52,"pl-c1"]],[[0,23,"pl-c1"]],[[0,0,"pl-c1"]],[[0,41,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[28,28,"pl-c1"]],[[0,0,"pl-c1"]],[[0,52,"pl-c1"]],[[0,23,"pl-c1"]],[[0,0,"pl-c1"]],[[0,44,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[41,41,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,16,"pl-c1"]],[[0,18,"pl-c1"]],[[0,0,"pl-c1"]],[[0,32,"pl-c1"]],[[0,2,"pl-c1"]],[[0,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[28,28,"pl-c1"]],[[0,0,"pl-c1"]],[[0,57,"pl-c1"]],[[0,32,"pl-c1"]],[[0,0,"pl-c1"]],[[0,52,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[[0,3,"pl-s"],[3,5,"pl-en"],[15,15,"pl-c1"]],[[0,0,"pl-c1"]],[[0,57,"pl-c1"]],[[0,57,"pl-c1"]],[[0,0,"pl-c1"]],[[0,52,"pl-c1"]],[[0,57,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"]],[[0,0,"pl-c1"],[0,3,"pl-s"]],[],[],[],[],[],[],[],[],[]],"colorizedLines":null,"csv":null,"csvError":null,"dependabotInfo":{"showConfigurationBanner":false,"configFilePath":null,"networkDependabotPath":"/johncsantiago/WhartonLab/network/updates","dismissConfigurationNoticePath":"/settings/dismiss-notice/dependabot_configuration_notice","configurationNoticeDismissed":null},"displayName":"G85R GOandKEGGTermEnrichment.Rmd","displayUrl":"https://github.com/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd?raw=true","headerInfo":{"blobSize":"3.31 KB","deleteTooltip":"You must be signed in to make or propose changes","editTooltip":"You must be signed in to make or propose changes","ghDesktopPath":"https://desktop.github.com","isGitLfs":false,"onBranch":true,"shortPath":"8d30178","siteNavLoginPath":"/login?return_to=https%3A%2F%2Fgithub.com%2Fjohncsantiago%2FWhartonLab%2Fblob%2Fmaster%2FG85R%2520GOandKEGGTermEnrichment.Rmd","isCSV":false,"isRichtext":false,"toc":null,"lineInfo":{"truncatedLoc":"219","truncatedSloc":"116"},"mode":"file"},"image":false,"isCodeownersFile":null,"isPlain":false,"isValidLegacyIssueTemplate":false,"issueTemplate":null,"discussionTemplate":null,"language":"RMarkdown","languageID":313,"large":false,"planSupportInfo":{"repoIsFork":null,"repoOwnedByCurrentUser":null,"requestFullPath":"/johncsantiago/WhartonLab/blob/master/G85R%20GOandKEGGTermEnrichment.Rmd","showFreeOrgGatedFeatureMessage":null,"showPlanSupportBanner":null,"upgradeDataAttributes":null,"upgradePath":null},"publishBannersInfo":{"dismissActionNoticePath":"/settings/dismiss-notice/publish_action_from_dockerfile","releasePath":"/johncsantiago/WhartonLab/releases/new?marketplace=true","showPublishActionBanner":false},"rawBlobUrl":"https://github.com/johncsantiago/WhartonLab/raw/refs/heads/master/G85R%20GOandKEGGTermEnrichment.Rmd","renderImageOrRaw":false,"richText":null,"renderedFileInfo":null,"shortPath":null,"symbolsEnabled":true,"tabSize":8,"topBannersInfo":{"overridingGlobalFundingFile":false,"globalPreferredFundingPath":null,"showInvalidCitationWarning":false,"citationHelpUrl":"https://docs.github.com/github/creating-cloning-and-archiving-repositories/creating-a-repository-on-github/about-citation-files","actionsOnboardingTip":null},"truncated":false,"viewable":true,"workflowRedirectUrl":null,"symbols":{"timed_out":false,"not_analyzed":true,"symbols":[]}},"copilotInfo":null,"copilotAccessAllowed":false,"modelsAccessAllowed":false,"csrf_tokens":{"/johncsantiago/WhartonLab/branches":{"post":"dIL6kyg-OOr0ZHS6M7LC7kiRDT7np3TS2GwIBfSUt2B5vsrsbfKfr5woixUGZCJbRVCfaPccXby3DapTEFGqnw"},"/repos/preferences":{"post":"EIjR0pOceLytEYQ0FwJp8y50walEA1hiYHc7wmg6bch6XdzoxWJ_nO0sL6fo0cEgYGh9dh2HjCSh2AgxNut1XQ"}}},"title":"WhartonLab/G85R GOandKEGGTermEnrichment.Rmd at master · johncsantiago/WhartonLab","appPayload":{"helpUrl":"https://docs.github.com","findFileWorkerPath":"/assets-cdn/worker/find-file-worker-2e45fb5767a8.js","findInFileWorkerPath":"/assets-cdn/worker/find-in-file-worker-86832803a5fc.js","githubDevUrl":null,"enabled_features":{"code_nav_ui_events":false,"overview_shared_code_dropdown_button":false,"react_blob_overlay":false,"copilot_conversational_ux_embedding_update":false,"copilot_smell_icebreaker_ux":true,"accessible_code_button":true}}}</script>
  <div data-target="react-app.reactRoot"><style data-styled="true" data-styled-version="5.3.11">.hOfjFo{padding:0;}/*!sc*/
.oDGAe{max-width:100%;margin-left:auto;margin-right:auto;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-wrap:wrap;-ms-flex-wrap:wrap;flex-wrap:wrap;}/*!sc*/
.kowOcT{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex:1 1 100%;-ms-flex:1 1 100%;flex:1 1 100%;-webkit-flex-wrap:wrap;-ms-flex-wrap:wrap;flex-wrap:wrap;max-width:100%;}/*!sc*/
.gISSDQ{width:100%;}/*!sc*/
@media screen and (min-width:544px){.gISSDQ{width:100%;}}/*!sc*/
@media screen and (min-width:768px){.gISSDQ{width:auto;}}/*!sc*/
.cEmWSE{display:none;-webkit-order:1;-ms-flex-order:1;order:1;width:100%;margin-left:0;margin-right:0;-webkit-flex-direction:column-reverse;-ms-flex-direction:column-reverse;flex-direction:column-reverse;margin-bottom:0;min-width:0;}/*!sc*/
@media screen and (min-width:768px){.cEmWSE{width:auto;margin-top:0 !important;margin-bottom:0 !important;position:-webkit-sticky;position:sticky;top:0px;max-height:100vh !important;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;margin-right:0;height:100vh;}}/*!sc*/
@media print,screen and (max-width:1011px) and (min-width:768px){.cEmWSE{display:none;}}/*!sc*/
.hPvFuC{margin-left:0;margin-right:0;display:none;margin-top:0;}/*!sc*/
@media screen and (min-width:768px){.hPvFuC{margin-left:0 !important;margin-right:0 !important;}}/*!sc*/
.fFSoPl{--pane-min-width:256px;--pane-max-width-diff:511px;--pane-max-width:calc(100vw - var(--pane-max-width-diff));width:100%;padding:0;}/*!sc*/
@media screen and (min-width:544px){}/*!sc*/
@media screen and (min-width:768px){.fFSoPl{width:clamp(var(--pane-min-width),var(--pane-width),var(--pane-max-width));overflow:auto;}}/*!sc*/
@media screen and (min-width:1280px){.fFSoPl{--pane-max-width-diff:959px;}}/*!sc*/
.bTBnTW{height:100%;position:relative;display:none;margin-left:0;}/*!sc*/
.bHLmSv{position:absolute;inset:0 -2px;cursor:col-resize;background-color:transparent;-webkit-transition-delay:0.1s;transition-delay:0.1s;}/*!sc*/
.bHLmSv:hover{background-color:var(--bgColor-neutral-muted,var(--color-neutral-muted,rgba(175,184,193,0.2)));}/*!sc*/
.iKqMNA{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;-webkit-order:2;-ms-flex-order:2;order:2;-webkit-flex-basis:0;-ms-flex-preferred-size:0;flex-basis:0;-webkit-box-flex:1;-webkit-flex-grow:1;-ms-flex-positive:1;flex-grow:1;-webkit-flex-shrink:1;-ms-flex-negative:1;flex-shrink:1;min-width:1px;margin-right:auto;}/*!sc*/
@media print{.iKqMNA{display:-webkit-box !important;display:-webkit-flex !important;display:-ms-flexbox !important;display:flex !important;}}/*!sc*/
.FxAyp{width:100%;max-width:100%;margin-left:auto;margin-right:auto;-webkit-box-flex:1;-webkit-flex-grow:1;-ms-flex-positive:1;flex-grow:1;padding:0;}/*!sc*/
.leYMvG{margin-left:auto;margin-right:auto;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;padding-bottom:40px;max-width:100%;margin-top:0;}/*!sc*/
.KMPzq{display:inherit;}/*!sc*/
.hfKjHv{width:100%;}/*!sc*/
.gZWyZE{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;gap:8px;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;width:100%;}/*!sc*/
.dwYKDk{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:start;-webkit-box-align:start;-ms-flex-align:start;align-items:start;-webkit-box-pack:justify;-webkit-justify-content:space-between;-ms-flex-pack:justify;justify-content:space-between;gap:8px;}/*!sc*/
.ibcGmb{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:start;-webkit-box-align:start;-ms-flex-align:start;align-items:start;min-width:0;}/*!sc*/
.hKaEJF{display:block;margin-right:8px;}/*!sc*/
@media screen and (min-width:1360px){.hKaEJF{display:block;}}/*!sc*/
.XosP{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;font-size:14px;}/*!sc*/
.bCKfWo[data-size="medium"]{color:var(--fgColor-muted,var(--color-fg-muted,#656d76));padding-left:8px;padding-right:8px;display:none;}/*!sc*/
@media screen and (max-width:768px){.bCKfWo[data-size="medium"]{display:block;}}/*!sc*/
.gUkoLg{-webkit-box-pack:center;-webkit-justify-content:center;-ms-flex-pack:center;justify-content:center;}/*!sc*/
.dmxRgG[data-size="medium"]{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;}/*!sc*/
.dmxRgG[data-size="medium"] svg{color:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.dmxRgG[data-size="medium"] > span{width:inherit;}/*!sc*/
.bZBlpz{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;width:100%;}/*!sc*/
.lhTYNA{margin-right:4px;color:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.dbrgmi{font-size:14px;min-width:0;max-width:125px;overflow:hidden;text-overflow:ellipsis;white-space:nowrap;}/*!sc*/
.dHJiml{-webkit-align-self:center;-ms-flex-item-align:center;align-self:center;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;padding-left:8px;padding-right:8px;min-width:0;}/*!sc*/
.cEytCf{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;font-size:16px;min-width:0;-webkit-flex-shrink:1;-ms-flex-negative:1;flex-shrink:1;-webkit-flex-wrap:wrap;-ms-flex-wrap:wrap;flex-wrap:wrap;max-width:100%;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;}/*!sc*/
.fzFXnm{max-width:100%;}/*!sc*/
.iMnkmv{max-width:100%;list-style:none;display:inline-block;}/*!sc*/
.ghzDag{display:inline-block;max-width:100%;}/*!sc*/
.kHuKdh{font-weight:600;}/*!sc*/
.jGhzSQ{font-weight:600;display:inline-block;max-width:100%;font-size:16px;}/*!sc*/
.faNtbn{min-height:32px;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:start;-webkit-box-align:start;-ms-flex-align:start;align-items:start;}/*!sc*/
.fmQaBv{margin-left:4px;margin-right:4px;}/*!sc*/
.dwNhzn[data-size="medium"][data-no-visuals]{border-top-left-radius:0;border-bottom-left-radius:0;display:none;}/*!sc*/
.fGwBZA[data-size="medium"][data-no-visuals]{color:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.dJxjrT{margin-left:16px;margin-right:16px;}/*!sc*/
.eFxKDQ{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;}/*!sc*/
.dzCJzi{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;-webkit-flex-wrap:wrap;-ms-flex-wrap:wrap;flex-wrap:wrap;-webkit-box-pack:justify;-webkit-justify-content:space-between;-ms-flex-pack:justify;justify-content:space-between;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;gap:8px;min-width:273px;padding:8px;}/*!sc*/
@media screen and (min-width:544px){.dzCJzi{-webkit-flex-wrap:nowrap;-ms-flex-wrap:nowrap;flex-wrap:nowrap;}}/*!sc*/
.ldRxiI{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;}/*!sc*/
.fVkfyA{width:100%;height:-webkit-fit-content;height:-moz-fit-content;height:fit-content;min-width:0;margin-right:0;}/*!sc*/
.gNAmSV{height:40px;padding-left:4px;padding-bottom:16px;}/*!sc*/
.jNEwzY{-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;}/*!sc*/
.bsDwxw{font-size:12px;-webkit-flex:auto;-ms-flex:auto;flex:auto;padding-right:16px;color:var(--fgColor-muted,var(--color-fg-muted,#656d76));min-width:0;}/*!sc*/
.jdLMhu{top:0px;z-index:4;background:var(--bgColor-default,var(--color-canvas-default));position:-webkit-sticky;position:sticky;}/*!sc*/
.tOISc{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;width:100%;position:absolute;}/*!sc*/
.hqwSEx{display:none;min-width:0;padding-top:8px;padding-bottom:8px;}/*!sc*/
.bDVoEr{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;overflow:hidden;margin-left:8px;margin-right:8px;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;-webkit-box-pack:justify;-webkit-justify-content:space-between;-ms-flex-pack:justify;justify-content:space-between;width:100%;}/*!sc*/
.kYLlPM{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;}/*!sc*/
.gYjEmn{margin-left:4px;margin-right:8px;}/*!sc*/
.kGqOLL{text-overflow:ellipsis;overflow:hidden;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;}/*!sc*/
.fHind{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex-direction:row;-ms-flex-direction:row;flex-direction:row;font-size:14px;min-width:0;-webkit-flex-shrink:1;-ms-flex-negative:1;flex-shrink:1;-webkit-flex-wrap:wrap;-ms-flex-wrap:wrap;flex-wrap:wrap;max-width:100%;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;}/*!sc*/
.dnZoUW{font-weight:600;display:inline-block;max-width:100%;font-size:14px;}/*!sc*/
.jRZWlf[data-size="small"]{color:var(--fgColor-default,var(--color-fg-default,#1F2328));margin-left:8px;}/*!sc*/
.kTvpNk{padding-left:8px;padding-top:8px;padding-bottom:8px;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex:1;-ms-flex:1;flex:1;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;-webkit-box-pack:justify;-webkit-justify-content:space-between;-ms-flex-pack:justify;justify-content:space-between;background-color:var(--bgColor-muted,var(--color-canvas-subtle,#f6f8fa));border:1px solid var(--borderColor-default,var(--color-border-default));border-radius:6px 6px 0px 0px;}/*!sc*/
.iNMjfP{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;gap:8px;min-width:0;}/*!sc*/
.fefCSX{display:block;position:relative;-webkit-box-flex:1;-webkit-flex-grow:1;-ms-flex-positive:1;flex-grow:1;margin-top:-1px;margin-bottom:-1px;--separator-color:transparent;}/*!sc*/
.fefCSX:not(:last-child){margin-right:1px;}/*!sc*/
.fefCSX:not(:last-child):after{background-color:var(--separator-color);content:"";position:absolute;right:-2px;top:8px;bottom:8px;width:1px;}/*!sc*/
.fefCSX:focus-within:has(:focus-visible){--separator-color:transparent;}/*!sc*/
.fefCSX:first-child{margin-left:-1px;}/*!sc*/
.fefCSX:last-child{margin-right:-1px;}/*!sc*/
.idgUkN{display:block;position:relative;-webkit-box-flex:1;-webkit-flex-grow:1;-ms-flex-positive:1;flex-grow:1;margin-top:-1px;margin-bottom:-1px;--separator-color:var(--borderColor-default,var(--color-border-default,#d0d7de));}/*!sc*/
.idgUkN:not(:last-child){margin-right:1px;}/*!sc*/
.idgUkN:not(:last-child):after{background-color:var(--separator-color);content:"";position:absolute;right:-2px;top:8px;bottom:8px;width:1px;}/*!sc*/
.idgUkN:focus-within:has(:focus-visible){--separator-color:transparent;}/*!sc*/
.idgUkN:first-child{margin-left:-1px;}/*!sc*/
.idgUkN:last-child{margin-right:-1px;}/*!sc*/
.kcLCKF{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;gap:8px;margin-right:8px;}/*!sc*/
.kVWtTz{gap:8px;}/*!sc*/
.gWqxTd{padding-left:8px;padding-right:8px;}/*!sc*/
.gWqxTd linkButtonSx:hover:not([disabled]){-webkit-text-decoration:none;text-decoration:none;}/*!sc*/
.gWqxTd linkButtonSx:focus:not([disabled]){-webkit-text-decoration:none;text-decoration:none;}/*!sc*/
.gWqxTd linkButtonSx:active:not([disabled]){-webkit-text-decoration:none;text-decoration:none;}/*!sc*/
.ivobqY[data-size="small"][data-no-visuals]{border-top-left-radius:0;border-bottom-left-radius:0;}/*!sc*/
.heuRGy[data-size="small"][data-no-visuals]{color:var(--fgColor-muted,var(--color-fg-muted,#656d76));position:relative;}/*!sc*/
.ffkqe[data-size="small"][data-no-visuals]{color:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.hGyMdv{border:1px solid;border-top:none;border-color:var(--borderColor-default,var(--color-border-default,#d0d7de));border-radius:0px 0px 6px 6px;min-width:273px;}/*!sc*/
.dceWRL{background-color:var(--bgColor-default,var(--color-canvas-default));border:0px;border-width:0;border-radius:0px 0px 6px 6px;padding:0;min-width:0;margin-top:46px;}/*!sc*/
.dGXHv{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-flex:1;-ms-flex:1;flex:1;padding-top:8px;padding-bottom:8px;-webkit-flex-direction:column;-ms-flex-direction:column;flex-direction:column;-webkit-box-pack:justify;-webkit-justify-content:space-between;-ms-flex-pack:justify;justify-content:space-between;min-width:0;position:relative;}/*!sc*/
.bpDFns{position:relative;}/*!sc*/
.iJOeCH{-webkit-flex:1;-ms-flex:1;flex:1;position:relative;min-width:0;}/*!sc*/
.jewUnv{tab-size:8;isolation:isolate;position:relative;overflow:auto;max-width:unset;}/*!sc*/
.cCoXib{position:fixed;top:0;right:0;height:100%;width:15px;-webkit-transition:-webkit-transform 0.3s;-webkit-transition:transform 0.3s;transition:transform 0.3s;z-index:1;}/*!sc*/
.cCoXib:hover{-webkit-transform:scaleX(1.5);-ms-transform:scaleX(1.5);transform:scaleX(1.5);}/*!sc*/
data-styled.g1[id="Box-sc-g0xbh4-0"]{content:"hOfjFo,oDGAe,kowOcT,gISSDQ,cEmWSE,hPvFuC,fFSoPl,bTBnTW,bHLmSv,iKqMNA,FxAyp,leYMvG,KMPzq,hfKjHv,gZWyZE,dwYKDk,ibcGmb,hKaEJF,XosP,bCKfWo,gUkoLg,dmxRgG,bZBlpz,lhTYNA,dbrgmi,dHJiml,cEytCf,fzFXnm,iMnkmv,ghzDag,kHuKdh,jGhzSQ,faNtbn,fmQaBv,dwNhzn,fGwBZA,dJxjrT,eFxKDQ,dzCJzi,ldRxiI,fVkfyA,gNAmSV,jNEwzY,bsDwxw,jdLMhu,tOISc,hqwSEx,bDVoEr,kYLlPM,gYjEmn,kGqOLL,fHind,dnZoUW,jRZWlf,kTvpNk,iNMjfP,fefCSX,idgUkN,kcLCKF,kVWtTz,gWqxTd,ivobqY,heuRGy,ffkqe,hGyMdv,dceWRL,dGXHv,bpDFns,iJOeCH,jewUnv,cCoXib,"}/*!sc*/
.eMMFM{min-width:0;}/*!sc*/
.eMMFM:where([data-size='small']){font-size:var(--text-body-size-small,0.75rem);line-height:var(--text-body-lineHeight-small,1.6666);}/*!sc*/
.eMMFM:where([data-size='medium']){font-size:var(--text-body-size-medium,0.875rem);line-height:var(--text-body-lineHeight-medium,1.4285);}/*!sc*/
.eMMFM:where([data-size='large']){font-size:var(--text-body-size-large,1rem);line-height:var(--text-body-lineHeight-large,1.5);}/*!sc*/
.eMMFM:where([data-weight='light']){font-weight:var(--base-text-weight-light,300);}/*!sc*/
.eMMFM:where([data-weight='normal']){font-weight:var(--base-text-weight-normal,400);}/*!sc*/
.eMMFM:where([data-weight='medium']){font-weight:var(--base-text-weight-medium,500);}/*!sc*/
.eMMFM:where([data-weight='semibold']){font-weight:var(--base-text-weight-semibold,600);}/*!sc*/
.HlHVj{padding-left:4px;padding-right:4px;font-weight:400;color:var(--fgColor-muted,var(--color-fg-muted,#656d76));font-size:16px;}/*!sc*/
.HlHVj:where([data-size='small']){font-size:var(--text-body-size-small,0.75rem);line-height:var(--text-body-lineHeight-small,1.6666);}/*!sc*/
.HlHVj:where([data-size='medium']){font-size:var(--text-body-size-medium,0.875rem);line-height:var(--text-body-lineHeight-medium,1.4285);}/*!sc*/
.HlHVj:where([data-size='large']){font-size:var(--text-body-size-large,1rem);line-height:var(--text-body-lineHeight-large,1.5);}/*!sc*/
.HlHVj:where([data-weight='light']){font-weight:var(--base-text-weight-light,300);}/*!sc*/
.HlHVj:where([data-weight='normal']){font-weight:var(--base-text-weight-normal,400);}/*!sc*/
.HlHVj:where([data-weight='medium']){font-weight:var(--base-text-weight-medium,500);}/*!sc*/
.HlHVj:where([data-weight='semibold']){font-weight:var(--base-text-weight-semibold,600);}/*!sc*/
.lauzFl{padding-left:4px;padding-right:4px;font-weight:400;color:var(--fgColor-muted,var(--color-fg-muted,#656d76));font-size:14px;}/*!sc*/
.lauzFl:where([data-size='small']){font-size:var(--text-body-size-small,0.75rem);line-height:var(--text-body-lineHeight-small,1.6666);}/*!sc*/
.lauzFl:where([data-size='medium']){font-size:var(--text-body-size-medium,0.875rem);line-height:var(--text-body-lineHeight-medium,1.4285);}/*!sc*/
.lauzFl:where([data-size='large']){font-size:var(--text-body-size-large,1rem);line-height:var(--text-body-lineHeight-large,1.5);}/*!sc*/
.lauzFl:where([data-weight='light']){font-weight:var(--base-text-weight-light,300);}/*!sc*/
.lauzFl:where([data-weight='normal']){font-weight:var(--base-text-weight-normal,400);}/*!sc*/
.lauzFl:where([data-weight='medium']){font-weight:var(--base-text-weight-medium,500);}/*!sc*/
.lauzFl:where([data-weight='semibold']){font-weight:var(--base-text-weight-semibold,600);}/*!sc*/
data-styled.g3[id="Text__StyledText-sc-17v1xeu-0"]{content:"eMMFM,HlHVj,lauzFl,"}/*!sc*/
.jkNcAv{border:0;font-size:inherit;font-family:inherit;background-color:transparent;-webkit-appearance:none;color:inherit;width:100%;}/*!sc*/
.jkNcAv:focus{outline:0;}/*!sc*/
data-styled.g14[id="UnstyledTextInput__ToggledUnstyledTextInput-sc-14ypya-0"]{content:"jkNcAv,"}/*!sc*/
.hLzFvi{font-size:14px;line-height:var(--base-size-20);color:var(--fgColor-default,var(--color-fg-default,#1F2328));vertical-align:middle;background-color:var(--bgColor-default,var(--color-canvas-default,#ffffff));border:1px solid var(--control-borderColor-rest,var(--borderColor-default,var(--color-border-default,#d0d7de)));border-radius:6px;outline:none;box-shadow:var(--shadow-inset,var(--color-primer-shadow-inset,inset 0 1px 0 rgba(208,215,222,0.2)));display:-webkit-inline-box;display:-webkit-inline-flex;display:-ms-inline-flexbox;display:inline-flex;-webkit-align-items:stretch;-webkit-box-align:stretch;-ms-flex-align:stretch;align-items:stretch;min-height:var(--base-size-32);overflow:hidden;--inner-action-size:var(--base-size-24);}/*!sc*/
.hLzFvi input,.hLzFvi textarea{cursor:text;}/*!sc*/
.hLzFvi select{cursor:pointer;}/*!sc*/
.hLzFvi input::-webkit-input-placeholder,.hLzFvi textarea::-webkit-input-placeholder,.hLzFvi select::-webkit-input-placeholder{color:var(---control-fgColor-placeholder,var(--fgColor-muted,var(--color-fg-muted,#656d76)));}/*!sc*/
.hLzFvi input::-moz-placeholder,.hLzFvi textarea::-moz-placeholder,.hLzFvi select::-moz-placeholder{color:var(---control-fgColor-placeholder,var(--fgColor-muted,var(--color-fg-muted,#656d76)));}/*!sc*/
.hLzFvi input:-ms-input-placeholder,.hLzFvi textarea:-ms-input-placeholder,.hLzFvi select:-ms-input-placeholder{color:var(---control-fgColor-placeholder,var(--fgColor-muted,var(--color-fg-muted,#656d76)));}/*!sc*/
.hLzFvi input::placeholder,.hLzFvi textarea::placeholder,.hLzFvi select::placeholder{color:var(---control-fgColor-placeholder,var(--fgColor-muted,var(--color-fg-muted,#656d76)));}/*!sc*/
.hLzFvi:where([data-trailing-action][data-focused]),.hLzFvi:where(:not([data-trailing-action]):focus-within){border-color:var(--fgColor-accent,var(--color-accent-fg,#0969da));outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.hLzFvi > textarea{padding:var(--base-size-12);}/*!sc*/
.hLzFvi:where([data-contrast]){background-color:var(--bgColor-inset,var(--color-canvas-inset,#f6f8fa));}/*!sc*/
.hLzFvi:where([data-disabled]){color:var(--fgColor-disabled,var(--color-primer-fg-disabled,#8c959f));background-color:var(--control-bgColor-disabled,var(--color-input-disabled-bg,rgba(175,184,193,0.2)));box-shadow:none;border-color:var(--control-borderColor-disabled,var(--borderColor-default,var(--color-border-default,#d0d7de)));}/*!sc*/
.hLzFvi:where([data-disabled]) input,.hLzFvi:where([data-disabled]) textarea,.hLzFvi:where([data-disabled]) select{cursor:not-allowed;}/*!sc*/
.hLzFvi:where([data-monospace]){font-family:var(--fontStack-monospace,SFMono-Regular,Consolas,"Liberation Mono",Menlo,Courier,monospace);}/*!sc*/
.hLzFvi:where([data-validation='error']){border-color:var(--borderColor-danger-emphasis,var(--color-danger-emphasis,#cf222e));}/*!sc*/
.hLzFvi:where([data-validation='error']):where([data-trailing-action][data-focused]),.hLzFvi:where([data-validation='error']):where(:not([data-trailing-action])):focus-within{border-color:var(--fgColor-accent,var(--color-accent-fg,#0969da));outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.hLzFvi:where([data-validation='success']){border-color:var(--bgColor-success-emphasis,var(--color-success-emphasis,#1f883d));}/*!sc*/
.hLzFvi:where([data-block]){width:100%;display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;-webkit-align-self:stretch;-ms-flex-item-align:stretch;align-self:stretch;}/*!sc*/
@media (min-width:768px){.hLzFvi{font-size:var(--text-body-size-medium);}}/*!sc*/
.hLzFvi:where([data-size='small']){--inner-action-size:var(--base-size-20);min-height:var(--base-size-28);padding-top:3px;padding-right:var(--base-size-8);padding-bottom:3px;padding-left:var(--base-size-8);font-size:var(--text-body-size-small);line-height:var(--base-size-20);}/*!sc*/
.hLzFvi:where([data-size='large']){--inner-action-size:var(--base-size-28);height:var(--base-size-40);padding-top:10px;padding-right:var(--base-size-8);padding-bottom:10px;padding-left:var(--base-size-8);}/*!sc*/
.hLzFvi:where([data-variant='small']){min-height:28px;padding-top:3px;padding-right:var(--base-size-8);padding-bottom:3px;padding-left:var(--base-size-8);font-size:(--text-body-size-small);line-height:var(--base-size-20);}/*!sc*/
.hLzFvi:where([data-variant='large']){padding-top:10px;padding-right:var(--base-size-8);padding-bottom:10px;padding-left:var(--base-size-8);font-size:var(--text-title-size-medium);}/*!sc*/
.hLzFvi{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;min-width:160px;}/*!sc*/
data-styled.g15[id="TextInputWrapper__StyledTextInputBaseWrapper-sc-1mqhpbi-0"]{content:"hLzFvi,"}/*!sc*/
.iHYdQq{background-repeat:no-repeat;background-position:right 8px center;padding-right:0;padding-left:0;}/*!sc*/
.iHYdQq > :not(:last-child){margin-right:8px;}/*!sc*/
.iHYdQq .TextInput-icon,.iHYdQq .TextInput-action{-webkit-align-self:center;-ms-flex-item-align:center;align-self:center;color:var(--fgColor-muted,var(--color-fg-muted,#656d76));-webkit-flex-shrink:0;-ms-flex-negative:0;flex-shrink:0;}/*!sc*/
.iHYdQq > input,.iHYdQq > select{padding-right:0;padding-left:0;}/*!sc*/
.iHYdQq:where([data-leading-visual]){padding-left:var(--base-size-12);}/*!sc*/
.iHYdQq:where([data-trailing-visual]:not([data-trailing-action])){padding-right:var(--base-size-12);}/*!sc*/
.iHYdQq:where(:not([data-leading-visual])) > input,.iHYdQq:where(:not([data-leading-visual])) > select{padding-left:var(--base-size-12);}/*!sc*/
.iHYdQq:where(:not([data-trailing-visual]):not([data-trailing-action])) > input,.iHYdQq:where(:not([data-trailing-visual]):not([data-trailing-action])) > select{padding-right:var(--base-size-12);}/*!sc*/
.iHYdQq{display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;min-width:160px;}/*!sc*/
data-styled.g16[id="TextInputWrapper__StyledTextInputWrapper-sc-1mqhpbi-1"]{content:"iHYdQq,"}/*!sc*/
.jOyaRH{display:none;}/*!sc*/
.jOyaRH[popover]{position:absolute;padding:0.5em 0.75em;width:-webkit-max-content;width:-moz-max-content;width:max-content;margin:auto;-webkit-clip:auto;clip:auto;white-space:normal;font:normal normal 11px/1.5 -apple-system,BlinkMacSystemFont,"Segoe UI","Noto Sans",Helvetica,Arial,sans-serif,"Apple Color Emoji","Segoe UI Emoji";-webkit-font-smoothing:subpixel-antialiased;color:var(--tooltip-fgColor,var(--fgColor-onEmphasis,var(--color-fg-on-emphasis,#ffffff)));text-align:center;word-wrap:break-word;background:var(--tooltip-bgColor,var(--bgColor-emphasis,var(--color-neutral-emphasis-plus,#24292f)));border-radius:6px;border:0;opacity:0;max-width:250px;inset:auto;overflow:visible;}/*!sc*/
.jOyaRH[popover]:popover-open{display:block;}/*!sc*/
.jOyaRH[popover].\:popover-open{display:block;}/*!sc*/
@media (forced-colors:active){.jOyaRH{outline:1px solid transparent;}}/*!sc*/
.jOyaRH::after{position:absolute;display:block;right:0;left:0;height:var(--overlay-offset,0.25rem);content:'';}/*!sc*/
.jOyaRH[data-direction='n']::after,.jOyaRH[data-direction='ne']::after,.jOyaRH[data-direction='nw']::after{top:100%;}/*!sc*/
.jOyaRH[data-direction='s']::after,.jOyaRH[data-direction='se']::after,.jOyaRH[data-direction='sw']::after{bottom:100%;}/*!sc*/
.jOyaRH[data-direction='w']::after{position:absolute;display:block;height:100%;width:8px;content:'';bottom:0;left:100%;}/*!sc*/
.jOyaRH[data-direction='e']::after{position:absolute;display:block;height:100%;width:8px;content:'';bottom:0;right:100%;margin-left:-8px;}/*!sc*/
@-webkit-keyframes tooltip-appear{from{opacity:0;}to{opacity:1;}}/*!sc*/
@keyframes tooltip-appear{from{opacity:0;}to{opacity:1;}}/*!sc*/
.jOyaRH:popover-open,.jOyaRH:popover-open::before{-webkit-animation-name:tooltip-appear;animation-name:tooltip-appear;-webkit-animation-duration:0.1s;animation-duration:0.1s;-webkit-animation-fill-mode:forwards;animation-fill-mode:forwards;-webkit-animation-timing-function:ease-in;animation-timing-function:ease-in;-webkit-animation-delay:0s;animation-delay:0s;}/*!sc*/
.jOyaRH.\:popover-open,.jOyaRH.\:popover-open::before{-webkit-animation-name:tooltip-appear;animation-name:tooltip-appear;-webkit-animation-duration:0.1s;animation-duration:0.1s;-webkit-animation-fill-mode:forwards;animation-fill-mode:forwards;-webkit-animation-timing-function:ease-in;animation-timing-function:ease-in;-webkit-animation-delay:0s;animation-delay:0s;}/*!sc*/
data-styled.g17[id="Tooltip__StyledTooltip-sc-e45c7z-0"]{content:"jOyaRH,"}/*!sc*/
.hWlpPn{position:relative;display:inline-block;}/*!sc*/
.hWlpPn::after{position:absolute;z-index:1000000;display:none;padding:0.5em 0.75em;font:normal normal 11px/1.5 -apple-system,BlinkMacSystemFont,"Segoe UI","Noto Sans",Helvetica,Arial,sans-serif,"Apple Color Emoji","Segoe UI Emoji";-webkit-font-smoothing:subpixel-antialiased;color:var(--tooltip-fgColor,var(--fgColor-onEmphasis,var(--color-fg-on-emphasis,#ffffff)));text-align:center;-webkit-text-decoration:none;text-decoration:none;text-shadow:none;text-transform:none;-webkit-letter-spacing:normal;-moz-letter-spacing:normal;-ms-letter-spacing:normal;letter-spacing:normal;word-wrap:break-word;white-space:pre;pointer-events:none;content:attr(aria-label);background:var(--tooltip-bgColor,var(--bgColor-emphasis,var(--color-neutral-emphasis-plus,#24292f)));border-radius:6px;opacity:0;}/*!sc*/
@-webkit-keyframes tooltip-appear{from{opacity:0;}to{opacity:1;}}/*!sc*/
@keyframes tooltip-appear{from{opacity:0;}to{opacity:1;}}/*!sc*/
.hWlpPn:hover::after,.hWlpPn:active::after,.hWlpPn:focus::after,.hWlpPn:focus-within::after{display:inline-block;-webkit-text-decoration:none;text-decoration:none;-webkit-animation-name:tooltip-appear;animation-name:tooltip-appear;-webkit-animation-duration:0.1s;animation-duration:0.1s;-webkit-animation-fill-mode:forwards;animation-fill-mode:forwards;-webkit-animation-timing-function:ease-in;animation-timing-function:ease-in;-webkit-animation-delay:0s;animation-delay:0s;}/*!sc*/
.hWlpPn.tooltipped-no-delay:hover::after,.hWlpPn.tooltipped-no-delay:active::after,.hWlpPn.tooltipped-no-delay:focus::after,.hWlpPn.tooltipped-no-delay:focus-within::after{-webkit-animation-delay:0s;animation-delay:0s;}/*!sc*/
.hWlpPn.tooltipped-multiline:hover::after,.hWlpPn.tooltipped-multiline:active::after,.hWlpPn.tooltipped-multiline:focus::after,.hWlpPn.tooltipped-multiline:focus-within::after{display:table-cell;}/*!sc*/
.hWlpPn.tooltipped-s::after,.hWlpPn.tooltipped-se::after,.hWlpPn.tooltipped-sw::after{top:100%;right:50%;margin-top:6px;}/*!sc*/
.hWlpPn.tooltipped-se::after{right:auto;left:50%;margin-left:-16px;}/*!sc*/
.hWlpPn.tooltipped-sw::after{margin-right:-16px;}/*!sc*/
.hWlpPn.tooltipped-n::after,.hWlpPn.tooltipped-ne::after,.hWlpPn.tooltipped-nw::after{right:50%;bottom:100%;margin-bottom:6px;}/*!sc*/
.hWlpPn.tooltipped-ne::after{right:auto;left:50%;margin-left:-16px;}/*!sc*/
.hWlpPn.tooltipped-nw::after{margin-right:-16px;}/*!sc*/
.hWlpPn.tooltipped-s::after,.hWlpPn.tooltipped-n::after{-webkit-transform:translateX(50%);-ms-transform:translateX(50%);transform:translateX(50%);}/*!sc*/
.hWlpPn.tooltipped-w::after{right:100%;bottom:50%;margin-right:6px;-webkit-transform:translateY(50%);-ms-transform:translateY(50%);transform:translateY(50%);}/*!sc*/
.hWlpPn.tooltipped-e::after{bottom:50%;left:100%;margin-left:6px;-webkit-transform:translateY(50%);-ms-transform:translateY(50%);transform:translateY(50%);}/*!sc*/
.hWlpPn.tooltipped-multiline::after{width:-webkit-max-content;width:-moz-max-content;width:max-content;max-width:250px;word-wrap:break-word;white-space:pre-line;border-collapse:separate;}/*!sc*/
.hWlpPn.tooltipped-multiline.tooltipped-s::after,.hWlpPn.tooltipped-multiline.tooltipped-n::after{right:auto;left:50%;-webkit-transform:translateX(-50%);-ms-transform:translateX(-50%);transform:translateX(-50%);}/*!sc*/
.hWlpPn.tooltipped-multiline.tooltipped-w::after,.hWlpPn.tooltipped-multiline.tooltipped-e::after{right:100%;}/*!sc*/
.hWlpPn.tooltipped-align-right-2::after{right:0;margin-right:0;}/*!sc*/
.hWlpPn.tooltipped-align-left-2::after{left:0;margin-left:0;}/*!sc*/
data-styled.g18[id="Tooltip__TooltipBase-sc-17tf59c-0"]{content:"hWlpPn,"}/*!sc*/
.eAtkQz{display:inline-block;overflow:hidden;text-overflow:ellipsis;vertical-align:top;white-space:nowrap;max-width:125px;max-width:100%;}/*!sc*/
data-styled.g20[id="Truncate__StyledTruncate-sc-23o1d2-0"]{content:"eAtkQz,"}/*!sc*/
.dbGjOi{--segmented-control-button-inner-padding:12px;--segmented-control-button-bg-inset:4px;--segmented-control-outer-radius:6px;background-color:transparent;border-color:transparent;border-radius:var(--segmented-control-outer-radius);border-width:0;color:currentColor;cursor:pointer;font-family:inherit;font-size:inherit;font-weight:600;padding:0;height:100%;width:100%;}/*!sc*/
.dbGjOi:focus:not(:disabled){box-shadow:none;outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.dbGjOi:focus:not(:disabled):not(:focus-visible){outline:solid 1px transparent;}/*!sc*/
.dbGjOi:focus-visible:not(:disabled){box-shadow:none;outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.dbGjOi .segmentedControl-content{-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;background-color:var(--controlKnob-bgColor-rest,var(--color-segmented-control-button-bg,#ffffff));border-color:var(--controlKnob-borderColor-rest,var(--color-segmented-control-button-hover-active-selected-border,#8c959f));border-style:solid;border-width:1px;border-radius:var(--segmented-control-outer-radius);display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;height:100%;-webkit-box-pack:center;-webkit-justify-content:center;-ms-flex-pack:center;justify-content:center;padding-left:var(--segmented-control-button-inner-padding);padding-right:var(--segmented-control-button-inner-padding);}/*!sc*/
.dbGjOi svg{fill:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.dbGjOi:focus:focus-visible:not(:last-child):after{width:0;}/*!sc*/
.dbGjOi .segmentedControl-text:after{content:"Code";display:block;font-weight:600;height:0;overflow:hidden;pointer-events:none;-webkit-user-select:none;-moz-user-select:none;-ms-user-select:none;user-select:none;visibility:hidden;}/*!sc*/
@media (pointer:coarse){.dbGjOi:before{content:"";position:absolute;left:0;right:0;-webkit-transform:translateY(-50%);-ms-transform:translateY(-50%);transform:translateY(-50%);top:50%;min-height:44px;}}/*!sc*/
.bHmvop{--segmented-control-button-inner-padding:12px;--segmented-control-button-bg-inset:4px;--segmented-control-outer-radius:6px;background-color:transparent;border-color:transparent;border-radius:var(--segmented-control-outer-radius);border-width:0;color:currentColor;cursor:pointer;font-family:inherit;font-size:inherit;font-weight:400;padding:var(--segmented-control-button-bg-inset);height:100%;width:100%;}/*!sc*/
.bHmvop:focus:not(:disabled){box-shadow:none;outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.bHmvop:focus:not(:disabled):not(:focus-visible){outline:solid 1px transparent;}/*!sc*/
.bHmvop:focus-visible:not(:disabled){box-shadow:none;outline:2px solid var(--fgColor-accent,var(--color-accent-fg,#0969da));outline-offset:-1px;}/*!sc*/
.bHmvop .segmentedControl-content{-webkit-align-items:center;-webkit-box-align:center;-ms-flex-align:center;align-items:center;background-color:transparent;border-color:transparent;border-style:solid;border-width:1px;border-radius:calc(var(--segmented-control-outer-radius) - var(--segmented-control-button-bg-inset) / 2);display:-webkit-box;display:-webkit-flex;display:-ms-flexbox;display:flex;height:100%;-webkit-box-pack:center;-webkit-justify-content:center;-ms-flex-pack:center;justify-content:center;padding-left:calc(var(--segmented-control-button-inner-padding) - var(--segmented-control-button-bg-inset));padding-right:calc(var(--segmented-control-button-inner-padding) - var(--segmented-control-button-bg-inset));}/*!sc*/
.bHmvop svg{fill:var(--fgColor-muted,var(--color-fg-muted,#656d76));}/*!sc*/
.bHmvop:hover .segmentedControl-content{background-color:var(--controlTrack-bgColor-hover,var(--color-segmented-control-button-hover-bg,rgba(175,184,193,0.2)));}/*!sc*/
.bHmvop:active .segmentedControl-content{background-color:var(--controlTrack-bgColor-active,var(--color-segmented-control-button-hover-active-bg,rgba(175,184,193,0.4)));}/*!sc*/
.bHmvop:focus:focus-visible:not(:last-child):after{width:0;}/*!sc*/
.bHmvop .segmentedControl-text:after{content:"Blame";display:block;font-weight:600;height:0;overflow:hidden;pointer-events:none;-webkit-user-select:none;-moz-user-select:none;-ms-user-select:none;user-select:none;visibility:hidden;}/*!sc*/
@media (pointer:coarse){.bHmvop:before{content:"";position:absolute;left:0;right:0;-webkit-transform:translateY(-50%);-ms-transform:translateY(-50%);transform:translateY(-50%);top:50%;min-height:44px;}}/*!sc*/
data-styled.g106[id="SegmentedControlButton__SegmentedControlButtonStyled-sc-8lkgxl-0"]{content:"dbGjOi,bHmvop,"}/*!sc*/
.lawgDG{background-color:var(--controlTrack-bgColor-rest,var(--color-segmented-control-bg,#eaeef2));border-radius:6px;border:1px solid;border-color:var(--controlTrack-borderColor-rest,transparent);display:-webkit-inline-box;display:-webkit-inline-flex;display:-ms-inline-flexbox;display:inline-flex;font-size:14px;height:28px;margin:0;padding:0;}/*!sc*/
data-styled.g108[id="SegmentedControl__SegmentedControlList-sc-1rzig82-0"]{content:"lawgDG,"}/*!sc*/
body[data-page-layout-dragging="true"]{cursor:col-resize;}/*!sc*/
body[data-page-layout-dragging="true"] *{-webkit-user-select:none;-moz-user-select:none;-ms-user-select:none;user-select:none;}/*!sc*/
data-styled.g109[id="sc-global-gbKrvU1"]{content:"sc-global-gbKrvU1,"}/*!sc*/
</style><meta data-hydrostats="publish"/> <!-- --> <!-- --> <button hidden="" data-testid="header-permalink-button" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button><div><div style="--sticky-pane-height:100vh;--spacing:var(--spacing-none)" class="Box-sc-g0xbh4-0 hOfjFo"><div class="Box-sc-g0xbh4-0 oDGAe"><div class="Box-sc-g0xbh4-0 kowOcT"><div tabindex="0" class="Box-sc-g0xbh4-0 gISSDQ"><div class="Box-sc-g0xbh4-0 cEmWSE"><div class="Box-sc-g0xbh4-0 hPvFuC"></div><div style="--pane-width:320px" class="Box-sc-g0xbh4-0 fFSoPl"></div><div class="Box-sc-g0xbh4-0 bTBnTW"><div role="slider" aria-label="Draggable pane splitter" aria-valuemin="0" aria-valuemax="0" aria-valuenow="0" aria-valuetext="Pane width 0 pixels" tabindex="0" class="Box-sc-g0xbh4-0 bHLmSv"></div></div></div></div><div class="Box-sc-g0xbh4-0 iKqMNA"><div class="Box-sc-g0xbh4-0"></div><div class="Box-sc-g0xbh4-0 FxAyp"><div data-selector="repos-split-pane-content" tabindex="0" class="Box-sc-g0xbh4-0 leYMvG"><div class="Box-sc-g0xbh4-0 KMPzq"><div class="Box-sc-g0xbh4-0 hfKjHv container"><div class="px-3 pt-3 pb-0" id="StickyHeader"><div class="Box-sc-g0xbh4-0 gZWyZE"><div class="Box-sc-g0xbh4-0 dwYKDk"><div class="Box-sc-g0xbh4-0 ibcGmb react-code-view-header-wrap--narrow"><div class="Box-sc-g0xbh4-0 hKaEJF"><h2 class="Box-sc-g0xbh4-0 XosP prc-Heading-Heading-6CmGO"><button style="--button-color:fg.muted" type="button" aria-label="Expand file tree" data-testid="expand-file-tree-button-mobile" class="Box-sc-g0xbh4-0 bCKfWo prc-Button-ButtonBase-c50BI" data-loading="false" data-size="medium" data-variant="invisible" aria-describedby=":Rld9lab:-loading-announcement"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="leadingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-arrow-left" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M7.78 12.53a.75.75 0 0 1-1.06 0L2.47 8.28a.75.75 0 0 1 0-1.06l4.25-4.25a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042L4.81 7h7.44a.75.75 0 0 1 0 1.5H4.81l2.97 2.97a.75.75 0 0 1 0 1.06Z"></path></svg></span><span data-component="text" class="prc-Button-Label-pTQ3x">Files</span></span></button><span role="tooltip" aria-label="Expand file tree" id="expand-button-file-tree-button" class="Tooltip__TooltipBase-sc-17tf59c-0 hWlpPn tooltipped-se"><button data-component="IconButton" type="button" data-testid="expand-file-tree-button" aria-controls="repos-file-tree" class="prc-Button-ButtonBase-c50BI position-relative ExpandFileTreeButton-module__expandButton--gL4is ExpandFileTreeButton-module__filesButtonBreakpoint--WfX9t fgColor-muted prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="medium" data-variant="invisible" aria-describedby=":R35d9lab:-loading-announcement" aria-labelledby="expand-button-file-tree-button"><svg aria-hidden="true" focusable="false" class="octicon octicon-sidebar-collapse" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M6.823 7.823a.25.25 0 0 1 0 .354l-2.396 2.396A.25.25 0 0 1 4 10.396V5.604a.25.25 0 0 1 .427-.177Z"></path><path d="M1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25V1.75C0 .784.784 0 1.75 0ZM1.5 1.75v12.5c0 .138.112.25.25.25H9.5v-13H1.75a.25.25 0 0 0-.25.25ZM11 14.5h3.25a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25H11Z"></path></svg></button></span><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button></h2></div><div class="react-code-view-header-mb--narrow mr-2"><button type="button" aria-haspopup="true" aria-expanded="false" tabindex="0" aria-label="master branch" data-testid="anchor-button" class="Box-sc-g0xbh4-0 dmxRgG prc-Button-ButtonBase-c50BI ref-selector-class" data-loading="false" data-size="medium" data-variant="default" aria-describedby="branch-picker-repos-header-ref-selector-wide-loading-announcement" id="branch-picker-repos-header-ref-selector-wide"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="text" class="prc-Button-Label-pTQ3x"><div class="Box-sc-g0xbh4-0 bZBlpz"><div class="Box-sc-g0xbh4-0 lhTYNA"><svg aria-hidden="true" focusable="false" class="octicon octicon-git-branch" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M9.5 3.25a2.25 2.25 0 1 1 3 2.122V6A2.5 2.5 0 0 1 10 8.5H6a1 1 0 0 0-1 1v1.128a2.251 2.251 0 1 1-1.5 0V5.372a2.25 2.25 0 1 1 1.5 0v1.836A2.493 2.493 0 0 1 6 7h4a1 1 0 0 0 1-1v-.628A2.25 2.25 0 0 1 9.5 3.25Zm-6 0a.75.75 0 1 0 1.5 0 .75.75 0 0 0-1.5 0Zm8.25-.75a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5ZM4.25 12a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Z"></path></svg></div><div class="Box-sc-g0xbh4-0 dbrgmi ref-selector-button-text-container"><span class="Text__StyledText-sc-17v1xeu-0 eMMFM"> <!-- -->master</span></div></div></span><span data-component="trailingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-triangle-down" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="m4.427 7.427 3.396 3.396a.25.25 0 0 0 .354 0l3.396-3.396A.25.25 0 0 0 11.396 7H4.604a.25.25 0 0 0-.177.427Z"></path></svg></span></span></button><button hidden="" data-hotkey-scope="read-only-cursor-text-area"></button></div><div class="Box-sc-g0xbh4-0 dHJiml react-code-view-header-mb--narrow"><div class="Box-sc-g0xbh4-0 cEytCf"><nav data-testid="breadcrumbs" aria-labelledby="repos-header-breadcrumb-heading" id="repos-header-breadcrumb" class="Box-sc-g0xbh4-0 fzFXnm"><h2 class="sr-only ScreenReaderHeading-module__userSelectNone--vW4Cq prc-Heading-Heading-6CmGO" data-testid="screen-reader-heading" id="repos-header-breadcrumb-heading">Breadcrumbs</h2><ol class="Box-sc-g0xbh4-0 iMnkmv"><li class="Box-sc-g0xbh4-0 ghzDag"><a class="Box-sc-g0xbh4-0 kHuKdh prc-Link-Link-85e08" sx="[object Object]" data-testid="breadcrumbs-repo-link" href="/johncsantiago/WhartonLab/tree/master">WhartonLab</a></li></ol></nav><div data-testid="breadcrumbs-filename" class="Box-sc-g0xbh4-0 ghzDag"><span class="Text__StyledText-sc-17v1xeu-0 HlHVj" aria-hidden="true">/</span><h1 class="Box-sc-g0xbh4-0 jGhzSQ prc-Heading-Heading-6CmGO" tabindex="-1" id="file-name-id">G85R GOandKEGGTermEnrichment.Rmd</h1></div><button data-component="IconButton" type="button" class="prc-Button-ButtonBase-c50BI ml-2 prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="small" data-variant="invisible" aria-describedby=":Rftd9lab:-loading-announcement" aria-labelledby=":R1td9lab:"><svg aria-hidden="true" focusable="false" class="octicon octicon-copy" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M0 6.75C0 5.784.784 5 1.75 5h1.5a.75.75 0 0 1 0 1.5h-1.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-1.5a.75.75 0 0 1 1.5 0v1.5A1.75 1.75 0 0 1 9.25 16h-7.5A1.75 1.75 0 0 1 0 14.25Z"></path><path d="M5 1.75C5 .784 5.784 0 6.75 0h7.5C15.216 0 16 .784 16 1.75v7.5A1.75 1.75 0 0 1 14.25 11h-7.5A1.75 1.75 0 0 1 5 9.25Zm1.75-.25a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Z"></path></svg></button><span class="Tooltip__StyledTooltip-sc-e45c7z-0 jOyaRH CopyToClipboardButton-module__tooltip--Dq1IB" data-direction="nw" aria-label="Copy path" aria-hidden="true" id=":R1td9lab:">Copy path</span></div></div></div><div class="react-code-view-header-element--wide"><div class="Box-sc-g0xbh4-0 faNtbn"><div class="d-flex gap-2"> <div><div class="Box-sc-g0xbh4-0 fmQaBv"><span class="TextInputWrapper__StyledTextInputBaseWrapper-sc-1mqhpbi-0 hLzFvi TextInputWrapper__StyledTextInputWrapper-sc-1mqhpbi-1 iHYdQq TextInput-wrapper" data-leading-visual="true" data-trailing-visual="true" aria-busy="false"><span class="TextInput-icon" id=":R5j6d9lab:" aria-hidden="true"><svg aria-hidden="true" focusable="false" class="octicon octicon-search" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M10.68 11.74a6 6 0 0 1-7.922-8.982 6 6 0 0 1 8.982 7.922l3.04 3.04a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215ZM11.5 7a4.499 4.499 0 1 0-8.997 0A4.499 4.499 0 0 0 11.5 7Z"></path></svg></span><input type="text" aria-label="Go to file" role="combobox" aria-controls="file-results-list" aria-expanded="false" aria-haspopup="dialog" autoCorrect="off" spellcheck="false" placeholder="Go to file" aria-describedby=":R5j6d9lab: :R5j6d9labH1:" data-component="input" class="UnstyledTextInput__ToggledUnstyledTextInput-sc-14ypya-0 jkNcAv" value=""/><span class="TextInput-icon" id=":R5j6d9labH1:" aria-hidden="true"></span></span></div><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button></div><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button><button type="button" class="Box-sc-g0xbh4-0 dwNhzn prc-Button-ButtonBase-c50BI" data-loading="false" data-no-visuals="true" data-size="medium" data-variant="default" aria-describedby=":R2l6d9lab:-loading-announcement"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="text" class="prc-Button-Label-pTQ3x">Blame</span></span></button><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button data-component="IconButton" type="button" aria-label="More file actions" title="More file actions" data-testid="more-file-actions-button-nav-menu-wide" aria-haspopup="true" aria-expanded="false" tabindex="0" class="Box-sc-g0xbh4-0 fGwBZA prc-Button-ButtonBase-c50BI js-blob-dropdown-click prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="medium" data-variant="default" aria-describedby=":R156d9lab:-loading-announcement" id=":R156d9lab:"><svg aria-hidden="true" focusable="false" class="octicon octicon-kebab-horizontal" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M8 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3ZM1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Zm13 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path></svg></button> </div></div></div><div class="react-code-view-header-element--narrow"><div class="Box-sc-g0xbh4-0 faNtbn"><div class="d-flex gap-2"> <button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button><button type="button" class="Box-sc-g0xbh4-0 dwNhzn prc-Button-ButtonBase-c50BI" data-loading="false" data-no-visuals="true" data-size="medium" data-variant="default" aria-describedby=":R2l7d9lab:-loading-announcement"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="text" class="prc-Button-Label-pTQ3x">Blame</span></span></button><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button data-component="IconButton" type="button" aria-label="More file actions" title="More file actions" data-testid="more-file-actions-button-nav-menu-narrow" aria-haspopup="true" aria-expanded="false" tabindex="0" class="Box-sc-g0xbh4-0 fGwBZA prc-Button-ButtonBase-c50BI js-blob-dropdown-click prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="medium" data-variant="default" aria-describedby=":R157d9lab:-loading-announcement" id=":R157d9lab:"><svg aria-hidden="true" focusable="false" class="octicon octicon-kebab-horizontal" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M8 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3ZM1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Zm13 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path></svg></button> </div></div></div></div></div></div></div></div><div class="Box-sc-g0xbh4-0 dJxjrT react-code-view-bottom-padding"> <div class="Box-sc-g0xbh4-0 eFxKDQ"></div> <!-- --> <!-- --> </div><div class="Box-sc-g0xbh4-0 dJxjrT"> <!-- --> <!-- --> <div class="d-flex flex-column border rounded-2 mb-3 pl-1"><div class="Box-sc-g0xbh4-0 dzCJzi"><h2 class="sr-only ScreenReaderHeading-module__userSelectNone--vW4Cq prc-Heading-Heading-6CmGO" data-testid="screen-reader-heading">Latest commit</h2><div style="width:120px" class="Skeleton Skeleton--text" data-testid="loading"> </div><div class="d-flex flex-shrink-0 gap-2"><div data-testid="latest-commit-details" class="d-none d-sm-flex flex-items-center"></div><div class="d-flex gap-2"><h2 class="sr-only ScreenReaderHeading-module__userSelectNone--vW4Cq prc-Heading-Heading-6CmGO" data-testid="screen-reader-heading">History</h2><a href="/johncsantiago/WhartonLab/commits/master/G85R%20GOandKEGGTermEnrichment.Rmd" class="prc-Button-ButtonBase-c50BI d-none d-lg-flex LinkButton-module__code-view-link-button--xvCGA flex-items-center fgColor-default" data-loading="false" data-size="small" data-variant="invisible" aria-describedby=":R5dlal9lab:-loading-announcement"><span data-component="buttonContent" data-align="center" class="prc-Button-ButtonContent-HKbr-"><span data-component="leadingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-history" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="m.427 1.927 1.215 1.215a8.002 8.002 0 1 1-1.6 5.685.75.75 0 1 1 1.493-.154 6.5 6.5 0 1 0 1.18-4.458l1.358 1.358A.25.25 0 0 1 3.896 6H.25A.25.25 0 0 1 0 5.75V2.104a.25.25 0 0 1 .427-.177ZM7.75 4a.75.75 0 0 1 .75.75v2.992l2.028.812a.75.75 0 0 1-.557 1.392l-2.5-1A.751.751 0 0 1 7 8.25v-3.5A.75.75 0 0 1 7.75 4Z"></path></svg></span><span data-component="text" class="prc-Button-Label-pTQ3x"><span class="fgColor-default">History</span></span></span></a><div class="d-sm-none"></div><div class="d-flex d-lg-none"><span role="tooltip" aria-label="History" id="history-icon-button-tooltip" class="Tooltip__TooltipBase-sc-17tf59c-0 hWlpPn tooltipped-n"><a href="/johncsantiago/WhartonLab/commits/master/G85R%20GOandKEGGTermEnrichment.Rmd" class="prc-Button-ButtonBase-c50BI LinkButton-module__code-view-link-button--xvCGA flex-items-center fgColor-default" data-loading="false" data-size="small" data-variant="invisible" aria-describedby=":Rpdlal9lab:-loading-announcement history-icon-button-tooltip"><span data-component="buttonContent" data-align="center" class="prc-Button-ButtonContent-HKbr-"><span data-component="leadingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-history" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="m.427 1.927 1.215 1.215a8.002 8.002 0 1 1-1.6 5.685.75.75 0 1 1 1.493-.154 6.5 6.5 0 1 0 1.18-4.458l1.358 1.358A.25.25 0 0 1 3.896 6H.25A.25.25 0 0 1 0 5.75V2.104a.25.25 0 0 1 .427-.177ZM7.75 4a.75.75 0 0 1 .75.75v2.992l2.028.812a.75.75 0 0 1-.557 1.392l-2.5-1A.751.751 0 0 1 7 8.25v-3.5A.75.75 0 0 1 7.75 4Z"></path></svg></span></span></a></span></div></div></div></div></div><div class="Box-sc-g0xbh4-0 ldRxiI"><div class="Box-sc-g0xbh4-0 fVkfyA container"><div class="Box-sc-g0xbh4-0 gNAmSV react-code-size-details-banner"><div class="Box-sc-g0xbh4-0 jNEwzY react-code-size-details-banner"><div class="Box-sc-g0xbh4-0 bsDwxw text-mono"><div title="3.31 KB" data-testid="blob-size" class="Truncate__StyledTruncate-sc-23o1d2-0 eAtkQz"><span>219 lines (116 loc) · 3.31 KB</span></div></div></div></div><div class="Box-sc-g0xbh4-0 jdLMhu react-blob-view-header-sticky" id="repos-sticky-header"><div class="Box-sc-g0xbh4-0 tOISc"><div class="react-blob-sticky-header"><div class="Box-sc-g0xbh4-0 hqwSEx"><div class="Box-sc-g0xbh4-0 bDVoEr"><div class="Box-sc-g0xbh4-0 kYLlPM"><div class="Box-sc-g0xbh4-0 gYjEmn"><button type="button" aria-haspopup="true" aria-expanded="false" tabindex="0" aria-label="master branch" data-testid="anchor-button" class="Box-sc-g0xbh4-0 dmxRgG prc-Button-ButtonBase-c50BI ref-selector-class" data-loading="false" data-size="medium" data-variant="default" aria-describedby="branch-picker-repos-header-ref-selector-loading-announcement" id="branch-picker-repos-header-ref-selector"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="text" class="prc-Button-Label-pTQ3x"><div class="Box-sc-g0xbh4-0 bZBlpz"><div class="Box-sc-g0xbh4-0 lhTYNA"><svg aria-hidden="true" focusable="false" class="octicon octicon-git-branch" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M9.5 3.25a2.25 2.25 0 1 1 3 2.122V6A2.5 2.5 0 0 1 10 8.5H6a1 1 0 0 0-1 1v1.128a2.251 2.251 0 1 1-1.5 0V5.372a2.25 2.25 0 1 1 1.5 0v1.836A2.493 2.493 0 0 1 6 7h4a1 1 0 0 0 1-1v-.628A2.25 2.25 0 0 1 9.5 3.25Zm-6 0a.75.75 0 1 0 1.5 0 .75.75 0 0 0-1.5 0Zm8.25-.75a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5ZM4.25 12a.75.75 0 1 0 0 1.5.75.75 0 0 0 0-1.5Z"></path></svg></div><div class="Box-sc-g0xbh4-0 dbrgmi ref-selector-button-text-container"><span class="Text__StyledText-sc-17v1xeu-0 eMMFM"> <!-- -->master</span></div></div></span><span data-component="trailingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-triangle-down" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="m4.427 7.427 3.396 3.396a.25.25 0 0 0 .354 0l3.396-3.396A.25.25 0 0 0 11.396 7H4.604a.25.25 0 0 0-.177.427Z"></path></svg></span></span></button><button hidden="" data-hotkey-scope="read-only-cursor-text-area"></button></div><div class="Box-sc-g0xbh4-0 kGqOLL"><div class="Box-sc-g0xbh4-0 fHind"><nav data-testid="breadcrumbs" aria-labelledby="sticky-breadcrumb-heading" id="sticky-breadcrumb" class="Box-sc-g0xbh4-0 fzFXnm"><h2 class="sr-only ScreenReaderHeading-module__userSelectNone--vW4Cq prc-Heading-Heading-6CmGO" data-testid="screen-reader-heading" id="sticky-breadcrumb-heading">Breadcrumbs</h2><ol class="Box-sc-g0xbh4-0 iMnkmv"><li class="Box-sc-g0xbh4-0 ghzDag"><a class="Box-sc-g0xbh4-0 kHuKdh prc-Link-Link-85e08" sx="[object Object]" data-testid="breadcrumbs-repo-link" href="/johncsantiago/WhartonLab/tree/master">WhartonLab</a></li></ol></nav><div data-testid="breadcrumbs-filename" class="Box-sc-g0xbh4-0 ghzDag"><span class="Text__StyledText-sc-17v1xeu-0 lauzFl" aria-hidden="true">/</span><h1 class="Box-sc-g0xbh4-0 dnZoUW prc-Heading-Heading-6CmGO" tabindex="-1" id="sticky-file-name-id">G85R GOandKEGGTermEnrichment.Rmd</h1></div></div></div></div><button style="--button-color:fg.default" type="button" class="Box-sc-g0xbh4-0 jRZWlf prc-Button-ButtonBase-c50BI" data-loading="false" data-size="small" data-variant="invisible" aria-describedby=":Riptal9lab:-loading-announcement"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="leadingVisual" class="prc-Button-Visual-2epfX prc-Button-VisualWrap-Db-eB"><svg aria-hidden="true" focusable="false" class="octicon octicon-arrow-up" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M3.47 7.78a.75.75 0 0 1 0-1.06l4.25-4.25a.75.75 0 0 1 1.06 0l4.25 4.25a.751.751 0 0 1-.018 1.042.751.751 0 0 1-1.042.018L9 4.81v7.44a.75.75 0 0 1-1.5 0V4.81L4.53 7.78a.75.75 0 0 1-1.06 0Z"></path></svg></span><span data-component="text" class="prc-Button-Label-pTQ3x">Top</span></span></button></div></div></div><div class="Box-sc-g0xbh4-0 kTvpNk"><h2 class="sr-only ScreenReaderHeading-module__userSelectNone--vW4Cq prc-Heading-Heading-6CmGO" data-testid="screen-reader-heading">File metadata and controls</h2><div class="Box-sc-g0xbh4-0 iNMjfP"><ul aria-label="File view" class="SegmentedControl__SegmentedControlList-sc-1rzig82-0 lawgDG" data-size="small"><li class="Box-sc-g0xbh4-0 fefCSX" data-selected="true"><button aria-current="true" class="SegmentedControlButton__SegmentedControlButtonStyled-sc-8lkgxl-0 dbGjOi" type="button"><span class="segmentedControl-content"><div class="Box-sc-g0xbh4-0 segmentedControl-text" data-text="Code">Code</div></span></button></li><li class="Box-sc-g0xbh4-0 idgUkN"><button aria-current="false" class="SegmentedControlButton__SegmentedControlButtonStyled-sc-8lkgxl-0 bHmvop" type="button"><span class="segmentedControl-content"><div class="Box-sc-g0xbh4-0 segmentedControl-text" data-text="Blame">Blame</div></span></button></li></ul><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><div class="Box-sc-g0xbh4-0 jNEwzY react-code-size-details-in-header"><div class="Box-sc-g0xbh4-0 bsDwxw text-mono"><div title="3.31 KB" data-testid="blob-size" class="Truncate__StyledTruncate-sc-23o1d2-0 eAtkQz"><span>219 lines (116 loc) · 3.31 KB</span></div></div></div></div><div class="Box-sc-g0xbh4-0 kcLCKF"><div class="Box-sc-g0xbh4-0 kVWtTz react-blob-header-edit-and-raw-actions"><div class="Box-sc-g0xbh4-0 prc-ButtonGroup-ButtonGroup-vcMeG"><div><a href="https://github.com/johncsantiago/WhartonLab/raw/refs/heads/master/G85R%20GOandKEGGTermEnrichment.Rmd" data-testid="raw-button" class="Box-sc-g0xbh4-0 gWqxTd prc-Button-ButtonBase-c50BI" data-loading="false" data-no-visuals="true" data-size="small" data-variant="default" aria-describedby=":R5csptal9lab:-loading-announcement"><span data-component="buttonContent" class="Box-sc-g0xbh4-0 gUkoLg prc-Button-ButtonContent-HKbr-"><span data-component="text" class="prc-Button-Label-pTQ3x">Raw</span></span></a></div><div><button data-component="IconButton" type="button" aria-label="Copy raw content" data-testid="copy-raw-button" class="prc-Button-ButtonBase-c50BI prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="small" data-variant="default" aria-describedby=":Rpcsptal9lab:-loading-announcement"><svg aria-hidden="true" focusable="false" class="octicon octicon-copy" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M0 6.75C0 5.784.784 5 1.75 5h1.5a.75.75 0 0 1 0 1.5h-1.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-1.5a.75.75 0 0 1 1.5 0v1.5A1.75 1.75 0 0 1 9.25 16h-7.5A1.75 1.75 0 0 1 0 14.25Z"></path><path d="M5 1.75C5 .784 5.784 0 6.75 0h7.5C15.216 0 16 .784 16 1.75v7.5A1.75 1.75 0 0 1 14.25 11h-7.5A1.75 1.75 0 0 1 5 9.25Zm1.75-.25a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Z"></path></svg></button></div><div><span role="tooltip" aria-label="Download raw file" id=":Rdcsptal9lab:" class="Tooltip__TooltipBase-sc-17tf59c-0 hWlpPn tooltipped-n"><button data-component="IconButton" type="button" aria-label="Download raw content" data-testid="download-raw-button" class="Box-sc-g0xbh4-0 ivobqY prc-Button-ButtonBase-c50BI prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="small" data-variant="default" aria-describedby=":Rtcsptal9lab:-loading-announcement"><svg aria-hidden="true" focusable="false" class="octicon octicon-download" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M2.75 14A1.75 1.75 0 0 1 1 12.25v-2.5a.75.75 0 0 1 1.5 0v2.5c0 .138.112.25.25.25h10.5a.25.25 0 0 0 .25-.25v-2.5a.75.75 0 0 1 1.5 0v2.5A1.75 1.75 0 0 1 13.25 14Z"></path><path d="M7.25 7.689V2a.75.75 0 0 1 1.5 0v5.689l1.97-1.969a.749.749 0 1 1 1.06 1.06l-3.25 3.25a.749.749 0 0 1-1.06 0L4.22 6.78a.749.749 0 1 1 1.06-1.06l1.97 1.969Z"></path></svg></button></span></div></div><button hidden="" data-testid="raw-button-shortcut" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden="" data-testid="copy-raw-button-shortcut" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden="" data-testid="download-raw-button-shortcut" data-hotkey-scope="read-only-cursor-text-area"></button></div><span role="tooltip" aria-label="Open symbols panel" id=":R5sptal9lab:" class="Tooltip__TooltipBase-sc-17tf59c-0 hWlpPn tooltipped-nw"><button data-component="IconButton" type="button" aria-label="Symbols" aria-pressed="false" aria-expanded="false" aria-controls="symbols-pane" data-testid="symbols-button" class="Box-sc-g0xbh4-0 heuRGy prc-Button-ButtonBase-c50BI prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="small" data-variant="invisible" aria-describedby="symbols-button-loading-announcement" id="symbols-button"><svg aria-hidden="true" focusable="false" class="octicon octicon-code-square" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M0 1.75C0 .784.784 0 1.75 0h12.5C15.216 0 16 .784 16 1.75v12.5A1.75 1.75 0 0 1 14.25 16H1.75A1.75 1.75 0 0 1 0 14.25Zm1.75-.25a.25.25 0 0 0-.25.25v12.5c0 .138.112.25.25.25h12.5a.25.25 0 0 0 .25-.25V1.75a.25.25 0 0 0-.25-.25Zm7.47 3.97a.75.75 0 0 1 1.06 0l2 2a.75.75 0 0 1 0 1.06l-2 2a.749.749 0 0 1-1.275-.326.749.749 0 0 1 .215-.734L10.69 8 9.22 6.53a.75.75 0 0 1 0-1.06ZM6.78 6.53 5.31 8l1.47 1.47a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215l-2-2a.75.75 0 0 1 0-1.06l2-2a.751.751 0 0 1 1.042.018.751.751 0 0 1 .018 1.042Z"></path></svg></button></span><div class="react-blob-header-edit-and-raw-actions-combined"><button data-component="IconButton" type="button" aria-label="Edit and raw actions" title="More file actions" data-testid="more-file-actions-button" aria-haspopup="true" aria-expanded="false" tabindex="0" class="Box-sc-g0xbh4-0 ffkqe prc-Button-ButtonBase-c50BI js-blob-dropdown-click prc-Button-IconButton-szpyj" data-loading="false" data-no-visuals="true" data-size="small" data-variant="invisible" aria-describedby=":Rnsptal9lab:-loading-announcement" id=":Rnsptal9lab:"><svg aria-hidden="true" focusable="false" class="octicon octicon-kebab-horizontal" viewBox="0 0 16 16" width="16" height="16" fill="currentColor" style="display:inline-block;user-select:none;vertical-align:text-bottom;overflow:visible"><path d="M8 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3ZM1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Zm13 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3Z"></path></svg></button></div></div></div></div><div></div></div><div class="Box-sc-g0xbh4-0 hGyMdv"><section aria-labelledby="file-name-id-wide file-name-id-mobile" class="Box-sc-g0xbh4-0 dceWRL"><div class="Box-sc-g0xbh4-0 dGXHv"><div id="highlighted-line-menu-positioner" class="position-relative"><div id="copilot-button-positioner" class="Box-sc-g0xbh4-0 bpDFns"><div class="Box-sc-g0xbh4-0 iJOeCH"><div class="Box-sc-g0xbh4-0 jewUnv react-code-file-contents" role="presentation" aria-hidden="true" data-tab-size="8" data-paste-markdown-skip="true" data-hpc="true"><div class="react-line-numbers" style="pointer-events:auto"><div data-line-number="1" class="react-line-number react-code-text" style="padding-right:16px">1</div><div data-line-number="2" class="react-line-number react-code-text" style="padding-right:16px">2</div><div data-line-number="3" class="react-line-number react-code-text" style="padding-right:16px">3</div><div data-line-number="4" class="react-line-number react-code-text" style="padding-right:16px">4</div><div data-line-number="5" class="react-line-number react-code-text" style="padding-right:16px">5</div><div data-line-number="6" class="react-line-number react-code-text" style="padding-right:16px">6</div><div data-line-number="7" class="react-line-number react-code-text" style="padding-right:16px">7</div><div data-line-number="8" class="react-line-number react-code-text" style="padding-right:16px">8</div><div data-line-number="9" class="react-line-number react-code-text" style="padding-right:16px">9</div><div data-line-number="10" class="react-line-number react-code-text" style="padding-right:16px">10</div><div data-line-number="11" class="react-line-number react-code-text" style="padding-right:16px">11</div><div data-line-number="12" class="react-line-number react-code-text" style="padding-right:16px">12</div><div data-line-number="13" class="react-line-number react-code-text" style="padding-right:16px">13</div><div data-line-number="14" class="react-line-number react-code-text" style="padding-right:16px">14</div><div data-line-number="15" class="react-line-number react-code-text" style="padding-right:16px">15</div><div data-line-number="16" class="react-line-number react-code-text" style="padding-right:16px">16</div><div data-line-number="17" class="react-line-number react-code-text" style="padding-right:16px">17</div><div data-line-number="18" class="react-line-number react-code-text" style="padding-right:16px">18</div><div data-line-number="19" class="react-line-number react-code-text" style="padding-right:16px">19</div><div data-line-number="20" class="react-line-number react-code-text" style="padding-right:16px">20</div><div data-line-number="21" class="react-line-number react-code-text" style="padding-right:16px">21</div><div data-line-number="22" class="react-line-number react-code-text" style="padding-right:16px">22</div><div data-line-number="23" class="react-line-number react-code-text" style="padding-right:16px">23</div><div data-line-number="24" class="react-line-number react-code-text" style="padding-right:16px">24</div><div data-line-number="25" class="react-line-number react-code-text" style="padding-right:16px">25</div><div data-line-number="26" class="react-line-number react-code-text" style="padding-right:16px">26</div><div data-line-number="27" class="react-line-number react-code-text" style="padding-right:16px">27</div><div data-line-number="28" class="react-line-number react-code-text" style="padding-right:16px">28</div><div data-line-number="29" class="react-line-number react-code-text" style="padding-right:16px">29</div><div data-line-number="30" class="react-line-number react-code-text" style="padding-right:16px">30</div><div data-line-number="31" class="react-line-number react-code-text" style="padding-right:16px">31</div><div data-line-number="32" class="react-line-number react-code-text" style="padding-right:16px">32</div><div data-line-number="33" class="react-line-number react-code-text" style="padding-right:16px">33</div><div data-line-number="34" class="react-line-number react-code-text" style="padding-right:16px">34</div><div data-line-number="35" class="react-line-number react-code-text" style="padding-right:16px">35</div><div data-line-number="36" class="react-line-number react-code-text" style="padding-right:16px">36</div><div data-line-number="37" class="react-line-number react-code-text" style="padding-right:16px">37</div><div data-line-number="38" class="react-line-number react-code-text" style="padding-right:16px">38</div><div data-line-number="39" class="react-line-number react-code-text" style="padding-right:16px">39</div><div data-line-number="40" class="react-line-number react-code-text" style="padding-right:16px">40</div><div data-line-number="41" class="react-line-number react-code-text" style="padding-right:16px">41</div><div data-line-number="42" class="react-line-number react-code-text" style="padding-right:16px">42</div><div data-line-number="43" class="react-line-number react-code-text" style="padding-right:16px">43</div><div data-line-number="44" class="react-line-number react-code-text" style="padding-right:16px">44</div><div data-line-number="45" class="react-line-number react-code-text" style="padding-right:16px">45</div><div data-line-number="46" class="react-line-number react-code-text" style="padding-right:16px">46</div><div data-line-number="47" class="react-line-number react-code-text" style="padding-right:16px">47</div><div data-line-number="48" class="react-line-number react-code-text" style="padding-right:16px">48</div><div data-line-number="49" class="react-line-number react-code-text" style="padding-right:16px">49</div><div data-line-number="50" class="react-line-number react-code-text" style="padding-right:16px">50</div><div data-line-number="51" class="react-line-number react-code-text" style="padding-right:16px">51</div><div data-line-number="52" class="react-line-number react-code-text" style="padding-right:16px">52</div><div data-line-number="53" class="react-line-number react-code-text" style="padding-right:16px">53</div><div data-line-number="54" class="react-line-number react-code-text" style="padding-right:16px">54</div><div data-line-number="55" class="react-line-number react-code-text" style="padding-right:16px">55</div><div data-line-number="56" class="react-line-number react-code-text" style="padding-right:16px">56</div><div data-line-number="57" class="react-line-number react-code-text" style="padding-right:16px">57</div><div data-line-number="58" class="react-line-number react-code-text" style="padding-right:16px">58</div><div data-line-number="59" class="react-line-number react-code-text" style="padding-right:16px">59</div><div data-line-number="60" class="react-line-number react-code-text" style="padding-right:16px">60</div><div data-line-number="61" class="react-line-number react-code-text" style="padding-right:16px">61</div><div data-line-number="62" class="react-line-number react-code-text" style="padding-right:16px">62</div><div data-line-number="63" class="react-line-number react-code-text" style="padding-right:16px">63</div><div data-line-number="64" class="react-line-number react-code-text" style="padding-right:16px">64</div><div data-line-number="65" class="react-line-number react-code-text" style="padding-right:16px">65</div><div data-line-number="66" class="react-line-number react-code-text" style="padding-right:16px">66</div><div data-line-number="67" class="react-line-number react-code-text" style="padding-right:16px">67</div><div data-line-number="68" class="react-line-number react-code-text" style="padding-right:16px">68</div><div data-line-number="69" class="react-line-number react-code-text" style="padding-right:16px">69</div><div data-line-number="70" class="react-line-number react-code-text" style="padding-right:16px">70</div><div data-line-number="71" class="react-line-number react-code-text" style="padding-right:16px">71</div><div data-line-number="72" class="react-line-number react-code-text" style="padding-right:16px">72</div><div data-line-number="73" class="react-line-number react-code-text" style="padding-right:16px">73</div><div data-line-number="74" class="react-line-number react-code-text" style="padding-right:16px">74</div><div data-line-number="75" class="react-line-number react-code-text" style="padding-right:16px">75</div><div data-line-number="76" class="react-line-number react-code-text" style="padding-right:16px">76</div><div data-line-number="77" class="react-line-number react-code-text" style="padding-right:16px">77</div><div data-line-number="78" class="react-line-number react-code-text" style="padding-right:16px">78</div><div data-line-number="79" class="react-line-number react-code-text" style="padding-right:16px">79</div><div data-line-number="80" class="react-line-number react-code-text" style="padding-right:16px">80</div><div data-line-number="81" class="react-line-number react-code-text" style="padding-right:16px">81</div><div data-line-number="82" class="react-line-number react-code-text" style="padding-right:16px">82</div><div data-line-number="83" class="react-line-number react-code-text" style="padding-right:16px">83</div><div data-line-number="84" class="react-line-number react-code-text" style="padding-right:16px">84</div><div data-line-number="85" class="react-line-number react-code-text" style="padding-right:16px">85</div><div data-line-number="86" class="react-line-number react-code-text" style="padding-right:16px">86</div><div data-line-number="87" class="react-line-number react-code-text" style="padding-right:16px">87</div><div data-line-number="88" class="react-line-number react-code-text" style="padding-right:16px">88</div><div data-line-number="89" class="react-line-number react-code-text" style="padding-right:16px">89</div><div data-line-number="90" class="react-line-number react-code-text" style="padding-right:16px">90</div><div data-line-number="91" class="react-line-number react-code-text" style="padding-right:16px">91</div><div data-line-number="92" class="react-line-number react-code-text" style="padding-right:16px">92</div><div data-line-number="93" class="react-line-number react-code-text" style="padding-right:16px">93</div><div data-line-number="94" class="react-line-number react-code-text" style="padding-right:16px">94</div><div data-line-number="95" class="react-line-number react-code-text" style="padding-right:16px">95</div><div data-line-number="96" class="react-line-number react-code-text" style="padding-right:16px">96</div><div data-line-number="97" class="react-line-number react-code-text" style="padding-right:16px">97</div><div data-line-number="98" class="react-line-number react-code-text" style="padding-right:16px">98</div><div data-line-number="99" class="react-line-number react-code-text" style="padding-right:16px">99</div><div data-line-number="100" class="react-line-number react-code-text" style="padding-right:16px">100</div><div data-line-number="101" class="react-line-number react-code-text" style="padding-right:16px">101</div><div data-line-number="102" class="react-line-number react-code-text" style="padding-right:16px">102</div><div data-line-number="103" class="react-line-number react-code-text" style="padding-right:16px">103</div><div data-line-number="104" class="react-line-number react-code-text" style="padding-right:16px">104</div><div data-line-number="105" class="react-line-number react-code-text" style="padding-right:16px">105</div><div data-line-number="106" class="react-line-number react-code-text" style="padding-right:16px">106</div><div data-line-number="107" class="react-line-number react-code-text" style="padding-right:16px">107</div><div data-line-number="108" class="react-line-number react-code-text" style="padding-right:16px">108</div><div data-line-number="109" class="react-line-number react-code-text" style="padding-right:16px">109</div><div data-line-number="110" class="react-line-number react-code-text" style="padding-right:16px">110</div><div data-line-number="111" class="react-line-number react-code-text" style="padding-right:16px">111</div><div data-line-number="112" class="react-line-number react-code-text" style="padding-right:16px">112</div><div data-line-number="113" class="react-line-number react-code-text" style="padding-right:16px">113</div><div data-line-number="114" class="react-line-number react-code-text" style="padding-right:16px">114</div><div data-line-number="115" class="react-line-number react-code-text" style="padding-right:16px">115</div><div data-line-number="116" class="react-line-number react-code-text" style="padding-right:16px">116</div><div data-line-number="117" class="react-line-number react-code-text" style="padding-right:16px">117</div><div data-line-number="118" class="react-line-number react-code-text" style="padding-right:16px">118</div><div data-line-number="119" class="react-line-number react-code-text" style="padding-right:16px">119</div><div data-line-number="120" class="react-line-number react-code-text" style="padding-right:16px">120</div><div data-line-number="121" class="react-line-number react-code-text" style="padding-right:16px">121</div><div data-line-number="122" class="react-line-number react-code-text" style="padding-right:16px">122</div><div data-line-number="123" class="react-line-number react-code-text" style="padding-right:16px">123</div><div data-line-number="124" class="react-line-number react-code-text" style="padding-right:16px">124</div><div data-line-number="125" class="react-line-number react-code-text" style="padding-right:16px">125</div><div data-line-number="126" class="react-line-number react-code-text" style="padding-right:16px">126</div><div data-line-number="127" class="react-line-number react-code-text" style="padding-right:16px">127</div><div data-line-number="128" class="react-line-number react-code-text" style="padding-right:16px">128</div><div data-line-number="129" class="react-line-number react-code-text" style="padding-right:16px">129</div><div data-line-number="130" class="react-line-number react-code-text" style="padding-right:16px">130</div><div data-line-number="131" class="react-line-number react-code-text" style="padding-right:16px">131</div><div data-line-number="132" class="react-line-number react-code-text" style="padding-right:16px">132</div><div data-line-number="133" class="react-line-number react-code-text" style="padding-right:16px">133</div><div data-line-number="134" class="react-line-number react-code-text" style="padding-right:16px">134</div><div data-line-number="135" class="react-line-number react-code-text" style="padding-right:16px">135</div><div data-line-number="136" class="react-line-number react-code-text" style="padding-right:16px">136</div><div data-line-number="137" class="react-line-number react-code-text" style="padding-right:16px">137</div><div data-line-number="138" class="react-line-number react-code-text" style="padding-right:16px">138</div><div data-line-number="139" class="react-line-number react-code-text" style="padding-right:16px">139</div><div data-line-number="140" class="react-line-number react-code-text" style="padding-right:16px">140</div><div data-line-number="141" class="react-line-number react-code-text" style="padding-right:16px">141</div><div data-line-number="142" class="react-line-number react-code-text" style="padding-right:16px">142</div><div data-line-number="143" class="react-line-number react-code-text" style="padding-right:16px">143</div><div data-line-number="144" class="react-line-number react-code-text" style="padding-right:16px">144</div><div data-line-number="145" class="react-line-number react-code-text" style="padding-right:16px">145</div><div data-line-number="146" class="react-line-number react-code-text" style="padding-right:16px">146</div><div data-line-number="147" class="react-line-number react-code-text" style="padding-right:16px">147</div><div data-line-number="148" class="react-line-number react-code-text" style="padding-right:16px">148</div><div data-line-number="149" class="react-line-number react-code-text" style="padding-right:16px">149</div><div data-line-number="150" class="react-line-number react-code-text" style="padding-right:16px">150</div><div data-line-number="151" class="react-line-number react-code-text" style="padding-right:16px">151</div><div data-line-number="152" class="react-line-number react-code-text" style="padding-right:16px">152</div><div data-line-number="153" class="react-line-number react-code-text" style="padding-right:16px">153</div><div data-line-number="154" class="react-line-number react-code-text" style="padding-right:16px">154</div><div data-line-number="155" class="react-line-number react-code-text" style="padding-right:16px">155</div><div data-line-number="156" class="react-line-number react-code-text" style="padding-right:16px">156</div><div data-line-number="157" class="react-line-number react-code-text" style="padding-right:16px">157</div><div data-line-number="158" class="react-line-number react-code-text" style="padding-right:16px">158</div><div data-line-number="159" class="react-line-number react-code-text" style="padding-right:16px">159</div><div data-line-number="160" class="react-line-number react-code-text" style="padding-right:16px">160</div><div data-line-number="161" class="react-line-number react-code-text" style="padding-right:16px">161</div><div data-line-number="162" class="react-line-number react-code-text" style="padding-right:16px">162</div><div data-line-number="163" class="react-line-number react-code-text" style="padding-right:16px">163</div><div data-line-number="164" class="react-line-number react-code-text" style="padding-right:16px">164</div><div data-line-number="165" class="react-line-number react-code-text" style="padding-right:16px">165</div><div data-line-number="166" class="react-line-number react-code-text" style="padding-right:16px">166</div><div data-line-number="167" class="react-line-number react-code-text" style="padding-right:16px">167</div><div data-line-number="168" class="react-line-number react-code-text" style="padding-right:16px">168</div><div data-line-number="169" class="react-line-number react-code-text" style="padding-right:16px">169</div><div data-line-number="170" class="react-line-number react-code-text" style="padding-right:16px">170</div><div data-line-number="171" class="react-line-number react-code-text" style="padding-right:16px">171</div><div data-line-number="172" class="react-line-number react-code-text" style="padding-right:16px">172</div><div data-line-number="173" class="react-line-number react-code-text" style="padding-right:16px">173</div><div data-line-number="174" class="react-line-number react-code-text" style="padding-right:16px">174</div><div data-line-number="175" class="react-line-number react-code-text" style="padding-right:16px">175</div><div data-line-number="176" class="react-line-number react-code-text" style="padding-right:16px">176</div><div data-line-number="177" class="react-line-number react-code-text" style="padding-right:16px">177</div><div data-line-number="178" class="react-line-number react-code-text" style="padding-right:16px">178</div><div data-line-number="179" class="react-line-number react-code-text" style="padding-right:16px">179</div><div data-line-number="180" class="react-line-number react-code-text" style="padding-right:16px">180</div><div data-line-number="181" class="react-line-number react-code-text" style="padding-right:16px">181</div><div data-line-number="182" class="react-line-number react-code-text" style="padding-right:16px">182</div><div data-line-number="183" class="react-line-number react-code-text" style="padding-right:16px">183</div><div data-line-number="184" class="react-line-number react-code-text" style="padding-right:16px">184</div><div data-line-number="185" class="react-line-number react-code-text" style="padding-right:16px">185</div><div data-line-number="186" class="react-line-number react-code-text" style="padding-right:16px">186</div><div data-line-number="187" class="react-line-number react-code-text" style="padding-right:16px">187</div><div data-line-number="188" class="react-line-number react-code-text" style="padding-right:16px">188</div><div data-line-number="189" class="react-line-number react-code-text" style="padding-right:16px">189</div><div data-line-number="190" class="react-line-number react-code-text" style="padding-right:16px">190</div><div data-line-number="191" class="react-line-number react-code-text" style="padding-right:16px">191</div><div data-line-number="192" class="react-line-number react-code-text" style="padding-right:16px">192</div><div data-line-number="193" class="react-line-number react-code-text" style="padding-right:16px">193</div><div data-line-number="194" class="react-line-number react-code-text" style="padding-right:16px">194</div><div data-line-number="195" class="react-line-number react-code-text" style="padding-right:16px">195</div><div data-line-number="196" class="react-line-number react-code-text" style="padding-right:16px">196</div><div data-line-number="197" class="react-line-number react-code-text" style="padding-right:16px">197</div><div data-line-number="198" class="react-line-number react-code-text" style="padding-right:16px">198</div><div data-line-number="199" class="react-line-number react-code-text" style="padding-right:16px">199</div><div data-line-number="200" class="react-line-number react-code-text" style="padding-right:16px">200</div><div data-line-number="201" class="react-line-number react-code-text" style="padding-right:16px">201</div><div data-line-number="202" class="react-line-number react-code-text" style="padding-right:16px">202</div><div data-line-number="203" class="react-line-number react-code-text" style="padding-right:16px">203</div><div data-line-number="204" class="react-line-number react-code-text" style="padding-right:16px">204</div><div data-line-number="205" class="react-line-number react-code-text" style="padding-right:16px">205</div><div data-line-number="206" class="react-line-number react-code-text" style="padding-right:16px">206</div><div data-line-number="207" class="react-line-number react-code-text" style="padding-right:16px">207</div><div data-line-number="208" class="react-line-number react-code-text" style="padding-right:16px">208</div><div data-line-number="209" class="react-line-number react-code-text" style="padding-right:16px">209</div><div data-line-number="210" class="react-line-number react-code-text" style="padding-right:16px">210</div></div><div class="react-code-lines"><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC1" class="react-file-line html-div" data-testid="code-cell" data-line-number="1" style="position:relative"><span class="pl-s">---</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC2" class="react-file-line html-div" data-testid="code-cell" data-line-number="2" style="position:relative"><span class="pl-ent">title</span>: <span class="pl-s"><span class="pl-pds">&quot;</span>GO and KEGG Term Enrichment<span class="pl-pds">&quot;</span></span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC3" class="react-file-line html-div" data-testid="code-cell" data-line-number="3" style="position:relative"><span class="pl-ent">author</span>: <span class="pl-s"><span class="pl-pds">&quot;</span>John Santiago<span class="pl-pds">&quot;</span></span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC4" class="react-file-line html-div" data-testid="code-cell" data-line-number="4" style="position:relative"><span class="pl-ent">date</span>: <span class="pl-s"><span class="pl-pds">&quot;</span>2024-05-08<span class="pl-pds">&quot;</span></span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC5" class="react-file-line html-div" data-testid="code-cell" data-line-number="5" style="position:relative"><span class="pl-ent">output</span>: <span class="pl-s">html_document</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC6" class="react-file-line html-div" data-testid="code-cell" data-line-number="6" style="position:relative"><span class="pl-s">---</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC7" class="react-file-line html-div" data-testid="code-cell" data-line-number="7" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC8" class="react-file-line html-div" data-testid="code-cell" data-line-number="8" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> setup, include=FALSE}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC9" class="react-file-line html-div" data-testid="code-cell" data-line-number="9" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC10" class="react-file-line html-div" data-testid="code-cell" data-line-number="10" style="position:relative"><span class="pl-c1">knitr::opts_chunk$set(echo = TRUE)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC11" class="react-file-line html-div" data-testid="code-cell" data-line-number="11" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC12" class="react-file-line html-div" data-testid="code-cell" data-line-number="12" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC13" class="react-file-line html-div" data-testid="code-cell" data-line-number="13" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC14" class="react-file-line html-div" data-testid="code-cell" data-line-number="14" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC15" class="react-file-line html-div" data-testid="code-cell" data-line-number="15" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC16" class="react-file-line html-div" data-testid="code-cell" data-line-number="16" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, message = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC17" class="react-file-line html-div" data-testid="code-cell" data-line-number="17" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC18" class="react-file-line html-div" data-testid="code-cell" data-line-number="18" style="position:relative"><span class="pl-c1"># Conditions</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC19" class="react-file-line html-div" data-testid="code-cell" data-line-number="19" style="position:relative"><span class="pl-c1">#Geno is WT or GR</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC20" class="react-file-line html-div" data-testid="code-cell" data-line-number="20" style="position:relative"><span class="pl-c1">#TKT is either &quot;C&quot;, &quot;OE&quot;, or &quot;Df&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC21" class="react-file-line html-div" data-testid="code-cell" data-line-number="21" style="position:relative"><span class="pl-c1">#Sex is &quot;F&quot; or &quot;M&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC22" class="react-file-line html-div" data-testid="code-cell" data-line-number="22" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC23" class="react-file-line html-div" data-testid="code-cell" data-line-number="23" style="position:relative"><span class="pl-c1">Geno1 = &quot;GR&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC24" class="react-file-line html-div" data-testid="code-cell" data-line-number="24" style="position:relative"><span class="pl-c1">TKT1 = &quot;C&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC25" class="react-file-line html-div" data-testid="code-cell" data-line-number="25" style="position:relative"><span class="pl-c1">Sex1 = &quot;F&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC26" class="react-file-line html-div" data-testid="code-cell" data-line-number="26" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC27" class="react-file-line html-div" data-testid="code-cell" data-line-number="27" style="position:relative"><span class="pl-c1">Geno2 = &quot;WT&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC28" class="react-file-line html-div" data-testid="code-cell" data-line-number="28" style="position:relative"><span class="pl-c1">TKT2 = &quot;C&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC29" class="react-file-line html-div" data-testid="code-cell" data-line-number="29" style="position:relative"><span class="pl-c1">Sex2 = &quot;F&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC30" class="react-file-line html-div" data-testid="code-cell" data-line-number="30" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC31" class="react-file-line html-div" data-testid="code-cell" data-line-number="31" style="position:relative"><span class="pl-c1">##Conditions for second comparison</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC32" class="react-file-line html-div" data-testid="code-cell" data-line-number="32" style="position:relative"><span class="pl-c1">Geno3 = &quot;GR&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC33" class="react-file-line html-div" data-testid="code-cell" data-line-number="33" style="position:relative"><span class="pl-c1">TKT3 = &quot;C&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC34" class="react-file-line html-div" data-testid="code-cell" data-line-number="34" style="position:relative"><span class="pl-c1">Sex3 = &quot;M&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC35" class="react-file-line html-div" data-testid="code-cell" data-line-number="35" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC36" class="react-file-line html-div" data-testid="code-cell" data-line-number="36" style="position:relative"><span class="pl-c1">Geno4 = &quot;WT&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC37" class="react-file-line html-div" data-testid="code-cell" data-line-number="37" style="position:relative"><span class="pl-c1">TKT4 = &quot;C&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC38" class="react-file-line html-div" data-testid="code-cell" data-line-number="38" style="position:relative"><span class="pl-c1">Sex4 = &quot;M&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC39" class="react-file-line html-div" data-testid="code-cell" data-line-number="39" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC40" class="react-file-line html-div" data-testid="code-cell" data-line-number="40" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC41" class="react-file-line html-div" data-testid="code-cell" data-line-number="41" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC42" class="react-file-line html-div" data-testid="code-cell" data-line-number="42" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC43" class="react-file-line html-div" data-testid="code-cell" data-line-number="43" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC44" class="react-file-line html-div" data-testid="code-cell" data-line-number="44" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC45" class="react-file-line html-div" data-testid="code-cell" data-line-number="45" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC46" class="react-file-line html-div" data-testid="code-cell" data-line-number="46" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, message = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC47" class="react-file-line html-div" data-testid="code-cell" data-line-number="47" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC48" class="react-file-line html-div" data-testid="code-cell" data-line-number="48" style="position:relative"><span class="pl-c1">source(&#039;/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R&#039;)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC49" class="react-file-line html-div" data-testid="code-cell" data-line-number="49" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC50" class="react-file-line html-div" data-testid="code-cell" data-line-number="50" style="position:relative"><span class="pl-c1">plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC51" class="react-file-line html-div" data-testid="code-cell" data-line-number="51" style="position:relative"><span class="pl-c1">                      Sex1, Sex2, Sex3, Sex4,</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC52" class="react-file-line html-div" data-testid="code-cell" data-line-number="52" style="position:relative"><span class="pl-c1">                      TKT1, TKT2, TKT3, TKT4)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC53" class="react-file-line html-div" data-testid="code-cell" data-line-number="53" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC54" class="react-file-line html-div" data-testid="code-cell" data-line-number="54" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC55" class="react-file-line html-div" data-testid="code-cell" data-line-number="55" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC56" class="react-file-line html-div" data-testid="code-cell" data-line-number="56" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC57" class="react-file-line html-div" data-testid="code-cell" data-line-number="57" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC58" class="react-file-line html-div" data-testid="code-cell" data-line-number="58" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC59" class="react-file-line html-div" data-testid="code-cell" data-line-number="59" style="position:relative"><span class="pl-c1">##Uses data from primary comparison</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC60" class="react-file-line html-div" data-testid="code-cell" data-line-number="60" style="position:relative"><span class="pl-c1">##Plots genes with an FDR &lt;= 0.05</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC61" class="react-file-line html-div" data-testid="code-cell" data-line-number="61" style="position:relative"><span class="pl-c1">##point size is relative to maximum mean expression in the two conditions</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC62" class="react-file-line html-div" data-testid="code-cell" data-line-number="62" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC63" class="react-file-line html-div" data-testid="code-cell" data-line-number="63" style="position:relative"><span class="pl-c1">G85R.volcano(plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC64" class="react-file-line html-div" data-testid="code-cell" data-line-number="64" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC65" class="react-file-line html-div" data-testid="code-cell" data-line-number="65" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC66" class="react-file-line html-div" data-testid="code-cell" data-line-number="66" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC67" class="react-file-line html-div" data-testid="code-cell" data-line-number="67" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC68" class="react-file-line html-div" data-testid="code-cell" data-line-number="68" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC69" class="react-file-line html-div" data-testid="code-cell" data-line-number="69" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC70" class="react-file-line html-div" data-testid="code-cell" data-line-number="70" style="position:relative"><span class="pl-c1">##Uses data from primary comparison</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC71" class="react-file-line html-div" data-testid="code-cell" data-line-number="71" style="position:relative"><span class="pl-c1">##point size is relative to max mean expression in any condition</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC72" class="react-file-line html-div" data-testid="code-cell" data-line-number="72" style="position:relative"><span class="pl-c1">##grey points indicate less than 1 fold difference between the comparisons</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC73" class="react-file-line html-div" data-testid="code-cell" data-line-number="73" style="position:relative"><span class="pl-c1">G85R.compare.genes(plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC74" class="react-file-line html-div" data-testid="code-cell" data-line-number="74" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC75" class="react-file-line html-div" data-testid="code-cell" data-line-number="75" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC76" class="react-file-line html-div" data-testid="code-cell" data-line-number="76" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC77" class="react-file-line html-div" data-testid="code-cell" data-line-number="77" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC78" class="react-file-line html-div" data-testid="code-cell" data-line-number="78" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC79" class="react-file-line html-div" data-testid="code-cell" data-line-number="79" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC80" class="react-file-line html-div" data-testid="code-cell" data-line-number="80" style="position:relative"><span class="pl-c1">##Uses data from primary comparison</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC81" class="react-file-line html-div" data-testid="code-cell" data-line-number="81" style="position:relative"><span class="pl-c1">##point size is relative to mean expression in variable condition</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC82" class="react-file-line html-div" data-testid="code-cell" data-line-number="82" style="position:relative"><span class="pl-c1">G85R.DEG.venn(plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC83" class="react-file-line html-div" data-testid="code-cell" data-line-number="83" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC84" class="react-file-line html-div" data-testid="code-cell" data-line-number="84" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC85" class="react-file-line html-div" data-testid="code-cell" data-line-number="85" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC86" class="react-file-line html-div" data-testid="code-cell" data-line-number="86" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, include = F, warning = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC87" class="react-file-line html-div" data-testid="code-cell" data-line-number="87" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC88" class="react-file-line html-div" data-testid="code-cell" data-line-number="88" style="position:relative"><span class="pl-c1">####Uses sigDEGs from primary comparison</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC89" class="react-file-line html-div" data-testid="code-cell" data-line-number="89" style="position:relative"><span class="pl-c1">cat.data = G85R.Enrichment(plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC90" class="react-file-line html-div" data-testid="code-cell" data-line-number="90" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC91" class="react-file-line html-div" data-testid="code-cell" data-line-number="91" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC92" class="react-file-line html-div" data-testid="code-cell" data-line-number="92" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC93" class="react-file-line html-div" data-testid="code-cell" data-line-number="93" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC94" class="react-file-line html-div" data-testid="code-cell" data-line-number="94" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC95" class="react-file-line html-div" data-testid="code-cell" data-line-number="95" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC96" class="react-file-line html-div" data-testid="code-cell" data-line-number="96" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC97" class="react-file-line html-div" data-testid="code-cell" data-line-number="97" style="position:relative"><span class="pl-c1">##which ranks of categories to use</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC98" class="react-file-line html-div" data-testid="code-cell" data-line-number="98" style="position:relative"><span class="pl-c1">##a vector of numbers specifying which ranks to use</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC99" class="react-file-line html-div" data-testid="code-cell" data-line-number="99" style="position:relative"><span class="pl-c1">##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC100" class="react-file-line html-div" data-testid="code-cell" data-line-number="100" style="position:relative"><span class="pl-c1">##can also just type &#039;sigs&#039; </span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC101" class="react-file-line html-div" data-testid="code-cell" data-line-number="101" style="position:relative"><span class="pl-c1">usecats=c(1:20)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC102" class="react-file-line html-div" data-testid="code-cell" data-line-number="102" style="position:relative"><span class="pl-c1">#usecats = &#039;sigs&#039;  </span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC103" class="react-file-line html-div" data-testid="code-cell" data-line-number="103" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC104" class="react-file-line html-div" data-testid="code-cell" data-line-number="104" style="position:relative"><span class="pl-c1">G85R.KEGG20(cat.data, plot.data, usecats)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC105" class="react-file-line html-div" data-testid="code-cell" data-line-number="105" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC106" class="react-file-line html-div" data-testid="code-cell" data-line-number="106" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC107" class="react-file-line html-div" data-testid="code-cell" data-line-number="107" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC108" class="react-file-line html-div" data-testid="code-cell" data-line-number="108" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC109" class="react-file-line html-div" data-testid="code-cell" data-line-number="109" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, include = T}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC110" class="react-file-line html-div" data-testid="code-cell" data-line-number="110" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC111" class="react-file-line html-div" data-testid="code-cell" data-line-number="111" style="position:relative"><span class="pl-c1">##can be the exact name or 5 digit code in quotes</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC112" class="react-file-line html-div" data-testid="code-cell" data-line-number="112" style="position:relative"><span class="pl-c1">specific.kegg = &quot;00980&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC113" class="react-file-line html-div" data-testid="code-cell" data-line-number="113" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC114" class="react-file-line html-div" data-testid="code-cell" data-line-number="114" style="position:relative"><span class="pl-c1">G85R.plotkegg.genes(specific.kegg, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC115" class="react-file-line html-div" data-testid="code-cell" data-line-number="115" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC116" class="react-file-line html-div" data-testid="code-cell" data-line-number="116" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC117" class="react-file-line html-div" data-testid="code-cell" data-line-number="117" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC118" class="react-file-line html-div" data-testid="code-cell" data-line-number="118" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC119" class="react-file-line html-div" data-testid="code-cell" data-line-number="119" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, message=F, fig.width=7}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC120" class="react-file-line html-div" data-testid="code-cell" data-line-number="120" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC121" class="react-file-line html-div" data-testid="code-cell" data-line-number="121" style="position:relative"><span class="pl-c1">##5 digits from KEGG ID</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC122" class="react-file-line html-div" data-testid="code-cell" data-line-number="122" style="position:relative"><span class="pl-c1">PathwayID = &quot;00010&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC123" class="react-file-line html-div" data-testid="code-cell" data-line-number="123" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC124" class="react-file-line html-div" data-testid="code-cell" data-line-number="124" style="position:relative"><span class="pl-c1">#options include &#039;primary&#039; or &#039;both&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC125" class="react-file-line html-div" data-testid="code-cell" data-line-number="125" style="position:relative"><span class="pl-c1">use = &#039;both&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC126" class="react-file-line html-div" data-testid="code-cell" data-line-number="126" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC127" class="react-file-line html-div" data-testid="code-cell" data-line-number="127" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC128" class="react-file-line html-div" data-testid="code-cell" data-line-number="128" style="position:relative"><span class="pl-c1">G85R.KEGG.diagram(PathwayID, plot.data, use, sigs.only = F)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC129" class="react-file-line html-div" data-testid="code-cell" data-line-number="129" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC130" class="react-file-line html-div" data-testid="code-cell" data-line-number="130" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC131" class="react-file-line html-div" data-testid="code-cell" data-line-number="131" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC132" class="react-file-line html-div" data-testid="code-cell" data-line-number="132" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC133" class="react-file-line html-div" data-testid="code-cell" data-line-number="133" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC134" class="react-file-line html-div" data-testid="code-cell" data-line-number="134" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, include = T, warnings = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC135" class="react-file-line html-div" data-testid="code-cell" data-line-number="135" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC136" class="react-file-line html-div" data-testid="code-cell" data-line-number="136" style="position:relative"><span class="pl-c1">##can be the exact name or 5 digit code in quotes</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC137" class="react-file-line html-div" data-testid="code-cell" data-line-number="137" style="position:relative"><span class="pl-c1">specific.kegg = &quot;00010&quot;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC138" class="react-file-line html-div" data-testid="code-cell" data-line-number="138" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC139" class="react-file-line html-div" data-testid="code-cell" data-line-number="139" style="position:relative"><span class="pl-c1">G85R.comparekegg.genes(specific.kegg, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC140" class="react-file-line html-div" data-testid="code-cell" data-line-number="140" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC141" class="react-file-line html-div" data-testid="code-cell" data-line-number="141" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC142" class="react-file-line html-div" data-testid="code-cell" data-line-number="142" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC143" class="react-file-line html-div" data-testid="code-cell" data-line-number="143" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC144" class="react-file-line html-div" data-testid="code-cell" data-line-number="144" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC145" class="react-file-line html-div" data-testid="code-cell" data-line-number="145" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC146" class="react-file-line html-div" data-testid="code-cell" data-line-number="146" style="position:relative"><span class="pl-c1">## BP, CC, or MF</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC147" class="react-file-line html-div" data-testid="code-cell" data-line-number="147" style="position:relative"><span class="pl-c1">GO.ontology = &#039;BP&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC148" class="react-file-line html-div" data-testid="code-cell" data-line-number="148" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC149" class="react-file-line html-div" data-testid="code-cell" data-line-number="149" style="position:relative"><span class="pl-c1">##can select which categories ot include or say &#039;sigs.only&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC150" class="react-file-line html-div" data-testid="code-cell" data-line-number="150" style="position:relative"><span class="pl-c1">usecats=c(1:20)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC151" class="react-file-line html-div" data-testid="code-cell" data-line-number="151" style="position:relative"><span class="pl-c1">#usecats = &#039;sigs.only&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC152" class="react-file-line html-div" data-testid="code-cell" data-line-number="152" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC153" class="react-file-line html-div" data-testid="code-cell" data-line-number="153" style="position:relative"><span class="pl-c1">G85R.GO20(cat.data, GO.ontology, plot.data, usecats)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC154" class="react-file-line html-div" data-testid="code-cell" data-line-number="154" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC155" class="react-file-line html-div" data-testid="code-cell" data-line-number="155" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC156" class="react-file-line html-div" data-testid="code-cell" data-line-number="156" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC157" class="react-file-line html-div" data-testid="code-cell" data-line-number="157" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC158" class="react-file-line html-div" data-testid="code-cell" data-line-number="158" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC159" class="react-file-line html-div" data-testid="code-cell" data-line-number="159" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC160" class="react-file-line html-div" data-testid="code-cell" data-line-number="160" style="position:relative"><span class="pl-c1">##the 7 digits of a GOterm id or the exact term name</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC161" class="react-file-line html-div" data-testid="code-cell" data-line-number="161" style="position:relative"><span class="pl-c1">specific.go = &#039;0005811&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC162" class="react-file-line html-div" data-testid="code-cell" data-line-number="162" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC163" class="react-file-line html-div" data-testid="code-cell" data-line-number="163" style="position:relative"><span class="pl-c1">G85R.plotgo.genes(specific.go, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC164" class="react-file-line html-div" data-testid="code-cell" data-line-number="164" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC165" class="react-file-line html-div" data-testid="code-cell" data-line-number="165" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC166" class="react-file-line html-div" data-testid="code-cell" data-line-number="166" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC167" class="react-file-line html-div" data-testid="code-cell" data-line-number="167" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC168" class="react-file-line html-div" data-testid="code-cell" data-line-number="168" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, warning = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC169" class="react-file-line html-div" data-testid="code-cell" data-line-number="169" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC170" class="react-file-line html-div" data-testid="code-cell" data-line-number="170" style="position:relative"><span class="pl-c1">##the 7 digits of a GOterm id or the exact term name</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC171" class="react-file-line html-div" data-testid="code-cell" data-line-number="171" style="position:relative"><span class="pl-c1">specific.go = &#039;0005811&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC172" class="react-file-line html-div" data-testid="code-cell" data-line-number="172" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC173" class="react-file-line html-div" data-testid="code-cell" data-line-number="173" style="position:relative"><span class="pl-c1">G85R.comparego.genes(specific.go, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC174" class="react-file-line html-div" data-testid="code-cell" data-line-number="174" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC175" class="react-file-line html-div" data-testid="code-cell" data-line-number="175" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC176" class="react-file-line html-div" data-testid="code-cell" data-line-number="176" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC177" class="react-file-line html-div" data-testid="code-cell" data-line-number="177" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC178" class="react-file-line html-div" data-testid="code-cell" data-line-number="178" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, warning = F, message = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC179" class="react-file-line html-div" data-testid="code-cell" data-line-number="179" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC180" class="react-file-line html-div" data-testid="code-cell" data-line-number="180" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC181" class="react-file-line html-div" data-testid="code-cell" data-line-number="181" style="position:relative"><span class="pl-c1">## BP, CC, or MF</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC182" class="react-file-line html-div" data-testid="code-cell" data-line-number="182" style="position:relative"><span class="pl-c1">GO.ontology = &#039;BP&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC183" class="react-file-line html-div" data-testid="code-cell" data-line-number="183" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC184" class="react-file-line html-div" data-testid="code-cell" data-line-number="184" style="position:relative"><span class="pl-c1">rt = tree(cat.data, GO.ontology)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC185" class="react-file-line html-div" data-testid="code-cell" data-line-number="185" style="position:relative"><span class="pl-c1">  </span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC186" class="react-file-line html-div" data-testid="code-cell" data-line-number="186" style="position:relative"><span class="pl-c1">treemapPlot(rt)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC187" class="react-file-line html-div" data-testid="code-cell" data-line-number="187" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC188" class="react-file-line html-div" data-testid="code-cell" data-line-number="188" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC189" class="react-file-line html-div" data-testid="code-cell" data-line-number="189" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC190" class="react-file-line html-div" data-testid="code-cell" data-line-number="190" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC191" class="react-file-line html-div" data-testid="code-cell" data-line-number="191" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F, warning = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC192" class="react-file-line html-div" data-testid="code-cell" data-line-number="192" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC193" class="react-file-line html-div" data-testid="code-cell" data-line-number="193" style="position:relative"><span class="pl-c1">##a parent category generated in the treemapPlot function</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC194" class="react-file-line html-div" data-testid="code-cell" data-line-number="194" style="position:relative"><span class="pl-c1">parent.category = &#039;neurogenesis&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC195" class="react-file-line html-div" data-testid="code-cell" data-line-number="195" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC196" class="react-file-line html-div" data-testid="code-cell" data-line-number="196" style="position:relative"><span class="pl-c1">G85R.plotparentcat.genes(parent.category, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC197" class="react-file-line html-div" data-testid="code-cell" data-line-number="197" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC198" class="react-file-line html-div" data-testid="code-cell" data-line-number="198" style="position:relative"><span class="pl-s">```</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC199" class="react-file-line html-div" data-testid="code-cell" data-line-number="199" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC200" class="react-file-line html-div" data-testid="code-cell" data-line-number="200" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC201" class="react-file-line html-div" data-testid="code-cell" data-line-number="201" style="position:relative"><span class="pl-s">```</span><span class="pl-en">{r</span> echo = F}</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC202" class="react-file-line html-div" data-testid="code-cell" data-line-number="202" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC203" class="react-file-line html-div" data-testid="code-cell" data-line-number="203" style="position:relative"><span class="pl-c1">##a parent category generated in the treemapPlot function</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC204" class="react-file-line html-div" data-testid="code-cell" data-line-number="204" style="position:relative"><span class="pl-c1">##parent.category = &#039;small molecule biosynthetic process&#039;</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC205" class="react-file-line html-div" data-testid="code-cell" data-line-number="205" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC206" class="react-file-line html-div" data-testid="code-cell" data-line-number="206" style="position:relative"><span class="pl-c1">G85R.compareparent.genes(parent.category, plot.data)</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC207" class="react-file-line html-div" data-testid="code-cell" data-line-number="207" style="position:relative"><span class="pl-c1">##dot size is relative to the max FDR of either condition</span></div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC208" class="react-file-line html-div" data-testid="code-cell" data-line-number="208" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC209" class="react-file-line html-div" data-testid="code-cell" data-line-number="209" style="position:relative">
</div></div></div><div class="react-code-text react-code-line-contents" style="min-height:auto"><div><div id="LC210" class="react-file-line html-div" data-testid="code-cell" data-line-number="210" style="position:relative"><span class="pl-s">```</span>  </div></div></div></div></div></div><div id="copilot-button-container"></div></div><div id="highlighted-line-menu-container"></div></div></div><button hidden="" data-testid="hotkey-button" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button></section></div></div></div> <!-- --> <!-- --> </div></div></div><div class="Box-sc-g0xbh4-0"></div></div></div></div></div><div id="find-result-marks-container" class="Box-sc-g0xbh4-0 cCoXib"></div><button hidden="" data-testid="" data-hotkey-scope="read-only-cursor-text-area"></button><button hidden=""></button></div> <!-- --> <!-- --> <script type="application/json" id="__PRIMER_DATA_:R0:__">{"resolvedServerColorMode":"day"}</script></div>
</react-app>
</turbo-frame>

  </div>

</turbo-frame>

    </main>
  </div>

  </div>

          <footer class="footer pt-8 pb-6 f6 color-fg-muted p-responsive" role="contentinfo" >
  <h2 class='sr-only'>Footer</h2>

  <div class="d-flex flex-justify-center flex-items-center flex-column-reverse flex-lg-row flex-wrap flex-lg-nowrap">
    <div class="d-flex flex-items-center flex-shrink-0 mx-2">
      <a aria-label="Homepage" title="GitHub" class="footer-octicon mr-2" href="https://github.com">
        <svg aria-hidden="true" height="24" viewBox="0 0 24 24" version="1.1" width="24" data-view-component="true" class="octicon octicon-mark-github">
    <path d="M12.5.75C6.146.75 1 5.896 1 12.25c0 5.089 3.292 9.387 7.863 10.91.575.101.79-.244.79-.546 0-.273-.014-1.178-.014-2.142-2.889.532-3.636-.704-3.866-1.35-.13-.331-.69-1.352-1.18-1.625-.402-.216-.977-.748-.014-.762.906-.014 1.553.834 1.769 1.179 1.035 1.74 2.688 1.25 3.349.948.1-.747.402-1.25.733-1.538-2.559-.287-5.232-1.279-5.232-5.678 0-1.25.445-2.285 1.178-3.09-.115-.288-.517-1.467.115-3.048 0 0 .963-.302 3.163 1.179.92-.259 1.897-.388 2.875-.388.977 0 1.955.13 2.875.388 2.2-1.495 3.162-1.179 3.162-1.179.633 1.581.23 2.76.115 3.048.733.805 1.179 1.825 1.179 3.09 0 4.413-2.688 5.39-5.247 5.678.417.36.776 1.05.776 2.128 0 1.538-.014 2.774-.014 3.162 0 .302.216.662.79.547C20.709 21.637 24 17.324 24 12.25 24 5.896 18.854.75 12.5.75Z"></path>
</svg>
</a>
      <span>
        &copy; 2025 GitHub,&nbsp;Inc.
      </span>
    </div>

    <nav aria-label="Footer">
      <h3 class="sr-only" id="sr-footer-heading">Footer navigation</h3>

      <ul class="list-style-none d-flex flex-justify-center flex-wrap mb-2 mb-lg-0" aria-labelledby="sr-footer-heading">

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to Terms&quot;,&quot;label&quot;:&quot;text:terms&quot;}" href="https://docs.github.com/site-policy/github-terms/github-terms-of-service" data-view-component="true" class="Link--secondary Link">Terms</a>
          </li>

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to privacy&quot;,&quot;label&quot;:&quot;text:privacy&quot;}" href="https://docs.github.com/site-policy/privacy-policies/github-privacy-statement" data-view-component="true" class="Link--secondary Link">Privacy</a>
          </li>

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to security&quot;,&quot;label&quot;:&quot;text:security&quot;}" href="https://github.com/security" data-view-component="true" class="Link--secondary Link">Security</a>
          </li>

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to status&quot;,&quot;label&quot;:&quot;text:status&quot;}" href="https://www.githubstatus.com/" data-view-component="true" class="Link--secondary Link">Status</a>
          </li>

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to docs&quot;,&quot;label&quot;:&quot;text:docs&quot;}" href="https://docs.github.com/" data-view-component="true" class="Link--secondary Link">Docs</a>
          </li>

          <li class="mx-2">
            <a data-analytics-event="{&quot;category&quot;:&quot;Footer&quot;,&quot;action&quot;:&quot;go to contact&quot;,&quot;label&quot;:&quot;text:contact&quot;}" href="https://support.github.com?tags=dotcom-footer" data-view-component="true" class="Link--secondary Link">Contact</a>
          </li>

          <li class="mx-2" >
  <cookie-consent-link>
    <button
      type="button"
      class="Link--secondary underline-on-hover border-0 p-0 color-bg-transparent"
      data-action="click:cookie-consent-link#showConsentManagement"
      data-analytics-event="{&quot;location&quot;:&quot;footer&quot;,&quot;action&quot;:&quot;cookies&quot;,&quot;context&quot;:&quot;subfooter&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;cookies_link_subfooter_footer&quot;}"
    >
      Manage cookies
    </button>
  </cookie-consent-link>
</li>

<li class="mx-2">
  <cookie-consent-link>
    <button
      type="button"
      class="Link--secondary underline-on-hover border-0 p-0 color-bg-transparent"
      data-action="click:cookie-consent-link#showConsentManagement"
      data-analytics-event="{&quot;location&quot;:&quot;footer&quot;,&quot;action&quot;:&quot;dont_share_info&quot;,&quot;context&quot;:&quot;subfooter&quot;,&quot;tag&quot;:&quot;link&quot;,&quot;label&quot;:&quot;dont_share_info_link_subfooter_footer&quot;}"
    >
      Do not share my personal information
    </button>
  </cookie-consent-link>
</li>

      </ul>
    </nav>
  </div>
</footer>

    <ghcc-consent id="ghcc" class="position-fixed bottom-0 left-0" style="z-index: 999999" data-initial-cookie-consent-allowed="" data-cookie-consent-required="false"></ghcc-consent>

  <div id="ajax-error-message" class="ajax-error-message flash flash-error" hidden>
    <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-alert">
    <path d="M6.457 1.047c.659-1.234 2.427-1.234 3.086 0l6.082 11.378A1.75 1.75 0 0 1 14.082 15H1.918a1.75 1.75 0 0 1-1.543-2.575Zm1.763.707a.25.25 0 0 0-.44 0L1.698 13.132a.25.25 0 0 0 .22.368h12.164a.25.25 0 0 0 .22-.368Zm.53 3.996v2.5a.75.75 0 0 1-1.5 0v-2.5a.75.75 0 0 1 1.5 0ZM9 11a1 1 0 1 1-2 0 1 1 0 0 1 2 0Z"></path>
</svg>
    <button type="button" class="flash-close js-ajax-error-dismiss" aria-label="Dismiss error">
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg>
    </button>
    You can’t perform that action at this time.
  </div>

    <template id="site-details-dialog">
  <details class="details-reset details-overlay details-overlay-dark lh-default color-fg-default hx_rsm" open>
    <summary role="button" aria-label="Close dialog"></summary>
    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast hx_rsm-dialog hx_rsm-modal">
      <button class="Box-btn-octicon m-0 btn-octicon position-absolute right-0 top-0" type="button" aria-label="Close dialog" data-close-dialog>
        <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-x">
    <path d="M3.72 3.72a.75.75 0 0 1 1.06 0L8 6.94l3.22-3.22a.749.749 0 0 1 1.275.326.749.749 0 0 1-.215.734L9.06 8l3.22 3.22a.749.749 0 0 1-.326 1.275.749.749 0 0 1-.734-.215L8 9.06l-3.22 3.22a.751.751 0 0 1-1.042-.018.751.751 0 0 1-.018-1.042L6.94 8 3.72 4.78a.75.75 0 0 1 0-1.06Z"></path>
</svg>
      </button>
      <div class="octocat-spinner my-6 js-details-dialog-spinner"></div>
    </details-dialog>
  </details>
</template>

    <div class="Popover js-hovercard-content position-absolute" style="display: none; outline: none;">
  <div class="Popover-message Popover-message--bottom-left Popover-message--large Box color-shadow-large" style="width:360px;">
  </div>
</div>

    <template id="snippet-clipboard-copy-button">
  <div class="zeroclipboard-container position-absolute right-0 top-0">
    <clipboard-copy aria-label="Copy" class="ClipboardButton btn js-clipboard-copy m-2 p-0" data-copy-feedback="Copied!" data-tooltip-direction="w">
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-copy js-clipboard-copy-icon m-2">
    <path d="M0 6.75C0 5.784.784 5 1.75 5h1.5a.75.75 0 0 1 0 1.5h-1.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-1.5a.75.75 0 0 1 1.5 0v1.5A1.75 1.75 0 0 1 9.25 16h-7.5A1.75 1.75 0 0 1 0 14.25Z"></path><path d="M5 1.75C5 .784 5.784 0 6.75 0h7.5C15.216 0 16 .784 16 1.75v7.5A1.75 1.75 0 0 1 14.25 11h-7.5A1.75 1.75 0 0 1 5 9.25Zm1.75-.25a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Z"></path>
</svg>
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-check js-clipboard-check-icon color-fg-success d-none m-2">
    <path d="M13.78 4.22a.75.75 0 0 1 0 1.06l-7.25 7.25a.75.75 0 0 1-1.06 0L2.22 9.28a.751.751 0 0 1 .018-1.042.751.751 0 0 1 1.042-.018L6 10.94l6.72-6.72a.75.75 0 0 1 1.06 0Z"></path>
</svg>
    </clipboard-copy>
  </div>
</template>
<template id="snippet-clipboard-copy-button-unpositioned">
  <div class="zeroclipboard-container">
    <clipboard-copy aria-label="Copy" class="ClipboardButton btn btn-invisible js-clipboard-copy m-2 p-0 d-flex flex-justify-center flex-items-center" data-copy-feedback="Copied!" data-tooltip-direction="w">
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-copy js-clipboard-copy-icon">
    <path d="M0 6.75C0 5.784.784 5 1.75 5h1.5a.75.75 0 0 1 0 1.5h-1.5a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-1.5a.75.75 0 0 1 1.5 0v1.5A1.75 1.75 0 0 1 9.25 16h-7.5A1.75 1.75 0 0 1 0 14.25Z"></path><path d="M5 1.75C5 .784 5.784 0 6.75 0h7.5C15.216 0 16 .784 16 1.75v7.5A1.75 1.75 0 0 1 14.25 11h-7.5A1.75 1.75 0 0 1 5 9.25Zm1.75-.25a.25.25 0 0 0-.25.25v7.5c0 .138.112.25.25.25h7.5a.25.25 0 0 0 .25-.25v-7.5a.25.25 0 0 0-.25-.25Z"></path>
</svg>
      <svg aria-hidden="true" height="16" viewBox="0 0 16 16" version="1.1" width="16" data-view-component="true" class="octicon octicon-check js-clipboard-check-icon color-fg-success d-none">
    <path d="M13.78 4.22a.75.75 0 0 1 0 1.06l-7.25 7.25a.75.75 0 0 1-1.06 0L2.22 9.28a.751.751 0 0 1 .018-1.042.751.751 0 0 1 1.042-.018L6 10.94l6.72-6.72a.75.75 0 0 1 1.06 0Z"></path>
</svg>
    </clipboard-copy>
  </div>
</template>

    </div>

    <div id="js-global-screen-reader-notice" class="sr-only mt-n1" aria-live="polite" aria-atomic="true" ></div>
    <div id="js-global-screen-reader-notice-assertive" class="sr-only mt-n1" aria-live="assertive" aria-atomic="true"></div>
  </body>
</html>

### 2025-02-03 myfile.R

@@ -1,0 +1,1180 @@
+if (!require("BiocManager", quietly = TRUE))
+  install.packages("BiocManager")
+
+if(!require(gplots, quietly = TRUE))
+  install.packages("plotly")
+
+if(!require(gplots, quietly = TRUE))
+  BiocManager::install("goseq")
+
+if(!require(org.Dm.eg.db, quietly = TRUE))
+  BiocManager::install("org.Dm.eg.db")
+
+if(!require(rrvgo, quietly = TRUE))
+  BiocManager::install("rrvgo")
+
+if(!require(pathview, quietly = TRUE))
+  BiocManager::install("pathview")
+
+if(!require(VennDiagram, quietly = TRUE))
+  install.packages("VennDiagram")
+
+library(plotly)
+library(goseq)
+library(org.Dm.eg.db)
+library(rrvgo)
+library(pathview)
+library(VennDiagram)
+
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
+
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
+
+G85R.meancpm = read.csv(paste0(git.dir, "TKT_meancpmdata.csv"), row.names = 1)
+colnames(G85R.meancpm) = c('GRFC', 'GRMC', 
+                           'GRFDf', 'GRMDf', 'WTFDf', 'WTMDf',
+                           'GRFOE', 'GRMOE', 'WTFOE', 'WTMOE',
+                           'WTFC', 'WTMC')
+
+G85R.FDR = read.csv(paste0(git.dir, "TKT.EdgeR.FDRTable.csv"),row.names = 1)
+G85R.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
+
+G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
+
+genesingo = read.csv(paste0(git.dir, "genesingo.csv"), row.names = 1)
+
+GenesInKegg = read.csv(paste0(git.dir, "kegg.symbol2path.csv"), row.names = 1)
+
+KEGG.Names = read.csv(paste0(git.dir, "KEGG.names.csv"), row.names = 1)
+
+GO.Names = read.csv(paste0(git.dir, "GO.names.csv"), row.names = 1)
+
+
[…]

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -1,10 +1,10 @@
 if (!require("BiocManager", quietly = TRUE))
   install.packages("BiocManager")
 
-if(!require(gplots, quietly = TRUE))
+if(!require(plotly, quietly = TRUE))
   install.packages("plotly")
 
-if(!require(gplots, quietly = TRUE))
+if(!require(goseq, quietly = TRUE))
   BiocManager::install("goseq")
 
 if(!require(org.Dm.eg.db, quietly = TRUE))

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -19,6 +19,9 @@ if(!require(pathview, quietly = TRUE))
 if(!require(VennDiagram, quietly = TRUE))
   install.packages("VennDiagram")
 
+if(!require(CollapsABEL, quietly = TRUE))
+  install.packages('CollapsABEL')
+
 library(plotly)
 library(goseq)
 library(org.Dm.eg.db)

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -19,9 +19,6 @@ if(!require(pathview, quietly = TRUE))
 if(!require(VennDiagram, quietly = TRUE))
   install.packages("VennDiagram")
 
-if(!require(CollapsABEL, quietly = TRUE))
-  install.packages('CollapsABEL')
-
 library(plotly)
 library(goseq)
 library(org.Dm.eg.db)

### 2025-02-03 G85R.GOandKEGGPlottingFunctions.R
Update G85R.GOandKEGGPlottingFunctions.R

@@ -19,6 +19,9 @@ if(!require(pathview, quietly = TRUE))
 if(!require(VennDiagram, quietly = TRUE))
   install.packages("VennDiagram")
 
+if(!require(rstudioapi, quietly = TRUE))
+  install.packages('rstudioapi')
+
 library(plotly)
 library(goseq)
 library(org.Dm.eg.db)

### 2025-02-04 G85R GOandKEGGTermEnrichment.Rmd
small patches

@@
 
-```{r echo = F, message = F}
+```{r echo = F, message = F, warning = F}
 
-source('/Users/johncsantiago/Documents/GitHub/WhartonLab/G85R.GOandKEGGPlottingFunctions.R')
+source('https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/G85R.GOandKEGGPlottingFunctions.R')
 
@@
 
+##plots the specified most significantly enriched KEGG categories
 ##which ranks of categories to use
-##a vector of numbers specifying which ranks to use
+##usecats is a vector of numbers specifying which ranks to use
 ##eg. c(1, 5:6) will use the first, fifth and sixth most sig. cats.
@@
 ##can be the exact name or 5 digit code in quotes
-specific.kegg = "00980"
+specific.kegg = "00230"
 
@@
 
+##Color is relative to Fold Change
+
 ##5 digits from KEGG ID
-PathwayID = "00010"
+PathwayID = "00230"
 
@@
 
+##Uses data from both comparisons
+##Plot all of the genes in the selected KEGG category
+##Size is relative to significance
+
 ##can be the exact name or 5 digit code in quotes
-specific.kegg = "00010"
+specific.kegg = "00230"
 
@@
 ##the 7 digits of a GOterm id or the exact term name
-specific.go = '0005811'
+specific.go = '0022008'
 
@@
 
+##This function is very slow
 ## BP, CC, or MF
@@
 
-G85R.plotparentcat.genes(parent.category, plot.data)
+G85R.plotparentcat.genes(parent.category, plot.data, sigs.only = T)
 
@@
 ##a parent category generated in the treemapPlot function
-##parent.category = 'small molecule biosynthetic process'
+##parent.category = 'neurogenesis'
 
-G85R.compareparent.genes(parent.category, plot.data)
+G85R.compareparent.genes(parent.category, plot.data, sigs.only = T)
 ##dot size is relative to the max FDR of either condition

### 2025-02-04 G85R.GOandKEGGPlottingFunctions.R

@@ -639,7 +639,8 @@ G85R.KEGG.diagram = function(PathwayID, plot.data, use, sigs.only = F){
     dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
   }
 
-
+  metab.data = na.omit(metab.data)
+  metab.data = log2(metab.data)
   
   setwd(OutputDir) 
   pv.out <- pathview(gene.data =  deg.data,
@@ -671,9 +672,13 @@ G85R.KEGG.diagram = function(PathwayID, plot.data, use, sigs.only = F){
 G85R.comparekegg.genes = function(specific.kegg, plot.data){
   
   FC.data = plot.data[,grep("lFC", colnames(plot.data))]
+  colnames(FC.data) = substr(colnames(FC.data), 1, (nchar(colnames(FC.data)) - 5))
+  
   FDR.data = plot.data[,grep("FDR", colnames(plot.data))]
+  colnames(FDR.data) = substr(colnames(FDR.data), 1, (nchar(colnames(FDR.data)) - 5))
   
   mean.data = plot.data[,grep("mean", colnames(plot.data))]
+  colnames(mean.data) = substr(colnames(mean.data), 1, (nchar(colnames(mean.data)) - 5))
   
   kegg.id = row.names(KEGG.Names)[c(grep(specific.kegg, KEGG.Names), 
                                     grep(specific.kegg, row.names(KEGG.Names)))]

### 2025-02-10 SerpeSCdata.Rmd
update

@@
 
-gene.name = "burs"
+gene.name = "Burs"
 
@@
 
-```{r echo = F, fig.width=16, fig.height=10}
+```{r echo = F, fig.width=10, fig.height=16}
 
-heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")
+heat.genes = c("VGlut", "ChAT", "VAChT", "VGAT", "Gad1", "DAT", "ple", "SerT", "Hdc", "dimm", "Burs")
 
-heat.data = na.omit(serpe[heat.genes,])
+heat.data = na.omit(serpe.inter[heat.genes,])
 
 heat.data = apply(heat.data, MARGIN = 2, as.numeric)
-#heat.data = log2(heat.data)
+#heat.data = log10(heat.data)
 row.names(heat.data) = heat.genes
@@
 
-Cluster.id = c(serpe.annotated.names)
+Cluster.id = colnames(serpe.inter)
 
-Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)))
+Cluster.labelcolor = c(rep("darkgreen", ncol(serpe.inter)))
 
 heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
+heat.colors = colorRampPalette(c("white", "darkgreen", "darkgreen"))
 
@@
 
-max.break = log2(max(heat.data))
+max.break = log10(max(log10(heat.data)))
 
@@
 
-color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
+color.breaks = 10^(c(0:(numcols))*(max.break/(numcols + 1)))
 
-heatmap.2(heat.data,
+heat.data = t(heat.data)
+
+numcols = 75
+
+heatmap.2(log10(heat.data),
         Colv = NA,
-        #Rowv = NA,
-        labCol = Cluster.id,
-        scale = 'none',
-        ColSideColors = Cluster.labelcolor,
+        Rowv = NA,
+        #labCol = Cluster.id,
+        scale = "none",
+        #ColSideColors = Cluster.labelcolor,
         trace = "none",
@@
         na.color = "white",
-        key.title = "Mean Expression",
-        colCol = Cluster.labelcolor,
-        margins = c(10, 5), 
+        key.title = "Mean Expression")#,
+        #colCol = Cluster.labelcolor,
+        #margins = c(10, 5), 
         #colsep = c(18, 46, 95),
         #sepcolor = "black",
-        breaks = color.breaks)
+        #breaks = color.breaks)
+        #breaks = c(0:numcols))
 legend("left",
        title = "Cell Types",
-       legend = c("Manually Currated"),
+       legend = c("Interneurons"),
        fill = c("darkgreen"),

### 2025-02-10 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -696,23 +696,25 @@ serpe.heatmap = function(heat.genes){
     max.break = 7
   }
   
+  heat.data[heat.data > 1000] =1000
+  
   color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
   
   heatmap.2(heat.data,
-            Colv = NA,
+            Colv = F,
             #Rowv = NA,
             labCol = Cluster.id,
             scale = 'none',
-            ColSideColors = Cluster.labelcolor,
+            #ColSideColors = Cluster.labelcolor,
             trace = "none",
             col = heat.colors(numcols),
             dendrogram = "none",
             na.color = "white",
             key.title = "Mean Expression",
-            colCol = Cluster.labelcolor,
+            #colCol = Cluster.labelcolor,
             margins = c(10, 5), 
-            colsep = c(18, 46, 95),
-            sepcolor = "black",
+            #colsep = c(18, 46, 95),
+            #sepcolor = "black",
             breaks = color.breaks)
   legend("left",
          title = "Cell Types",

### 2025-02-10 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -705,16 +705,16 @@ serpe.heatmap = function(heat.genes){
             #Rowv = NA,
             labCol = Cluster.id,
             scale = 'none',
-            #ColSideColors = Cluster.labelcolor,
+            ColSideColors = Cluster.labelcolor,
             trace = "none",
             col = heat.colors(numcols),
             dendrogram = "none",
             na.color = "white",
             key.title = "Mean Expression",
-            #colCol = Cluster.labelcolor,
+            colCol = Cluster.labelcolor,
             margins = c(10, 5), 
-            #colsep = c(18, 46, 95),
-            #sepcolor = "black",
+            colsep = c(18, 46, 95),
+            sepcolor = "black",
             breaks = color.breaks)
   legend("left",
          title = "Cell Types",

### 2025-02-10 Functions_OmicsQuickPlotFunctions.R
Update Functions_OmicsQuickPlotFunctions.R

@@ -702,7 +702,7 @@ serpe.heatmap = function(heat.genes){
   
   heatmap.2(heat.data,
             Colv = F,
-            #Rowv = NA,
+            Rowv = F,
             labCol = Cluster.id,
             scale = 'none',
             ColSideColors = Cluster.labelcolor,

### 2025-02-11 Functions_OmicsQuickPlotFunctions.R
fixed metabID function

@@ -375,7 +375,7 @@ plot.metab = function(metabID){
     }
     
     if(length(ID.row) != 1 | length(intersect(row.names(norm.data), metabID)) > 1){
-      print(paste0("Multiple metabolites match the ID ", ID))
+      print(paste0("Multiple metabolites match the ID ", metabID))
       norm.data[ID.row,]
     }
     

### 2025-03-17 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
updated files

@@
                marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
+               marker = list(colorscale = list(c(0,.9,1), c("#EA337F","#FEFF54", "#387EF7")),
+               marker = list(colorscale = list(c(0,.9,1), c("#C1607E","#EBE3A4", "#419193")),
+               marker = list(colorscale = list(c(0, .75, 1), c("#E7327F","#FEFE57", "#3A7EF7")),
+
     reversescale =T,

### 2025-03-17 NADHandNADPHMetabolismGenes.Rmd
updated files

---
title: "NADH and NADPH metabolism"
author: "John Santiago"
date: "2025-02-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, message = F}

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "GR"
TKT1 = "C"
Sex1 = "F"

Geno2 = "WT"
TKT2 = "C"
Sex2 = "F"

##Conditions for second comparison
Geno3 = "GR"
TKT3 = "C"
Sex3 = "M"

Geno4 = "WT"
TKT4 = "C"
Sex4 = "M"

```

```{r echo = F, message = F, warning = F}

source('https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/G85R.GOandKEGGPlottingFunctions.R')

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

```

## NADH Genes (Females)
```{r echo = F, warning = F}

##Uses data from primary comparison
##Plots genes with an FDR <= 0.05
##point size is relative to maximum mean expression in the two conditions

NADH.FBgn = row.names(read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NADHGenes.csv", row.names = 1))

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Females)
```{r echo = F, warning = F}

NADPH.FBgn = row.names(read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NADPHGenes.csv", row.names = 1))

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno3, Geno4, Geno1, Geno2,
                      Sex3, Sex4, Sex1, Sex2,
                      TKT3, TKT4, TKT1, TKT2)

```

## NADH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F}

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "GR"
TKT1 = "Df"
Sex1 = "F"

Geno2 = "GR"
TKT2 = "C"
Sex2 = "F"

##Conditions for second comparison
Geno3 = "GR"
TKT3 = "Df"
Sex3 = "M"

Geno4 = "GR"
TKT4 = "C"
Sex4 = "M"

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

```

## NADH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno3, Geno4, Geno1, Geno2,
                      Sex3, Sex4, Sex1, Sex2,
                      TKT3, TKT4, TKT1, TKT2)

```

## NADH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F}

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "WT"
TKT1 = "Df"
Sex1 = "F"

Geno2 = "WT"
TKT2 = "C"
Sex2 = "F"

##Conditions for second comparison
Geno3 = "WT"
TKT3 = "Df"
Sex3 = "M"

Geno4 = "WT"
TKT4 = "C"
Sex4 = "M"

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

```

## NADH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno3, Geno4, Geno1, Geno2,
                      Sex3, Sex4, Sex1, Sex2,
                      TKT3, TKT4, TKT1, TKT2)

```

## NADH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F}

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "GR"
TKT1 = "OE"
Sex1 = "F"

Geno2 = "GR"
TKT2 = "C"
Sex2 = "F"

##Conditions for second comparison
Geno3 = "GR"
TKT3 = "OE"
Sex3 = "M"

Geno4 = "GR"
TKT4 = "C"
Sex4 = "M"

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

```

## NADH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno3, Geno4, Geno1, Geno2,
                      Sex3, Sex4, Sex1, Sex2,
                      TKT3, TKT4, TKT1, TKT2)

```

## NADH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F}

# Conditions
#Geno is WT or GR
#TKT is either "C", "OE", or "Df"
#Sex is "F" or "M"

Geno1 = "WT"
TKT1 = "OE"
Sex1 = "F"

Geno2 = "WT"
TKT2 = "C"
Sex2 = "F"

##Conditions for second comparison
Geno3 = "WT"
TKT3 = "OE"
Sex3 = "M"

Geno4 = "WT"
TKT4 = "C"
Sex4 = "M"

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno1, Geno2, Geno3, Geno4,
                      Sex1, Sex2, Sex3, Sex4,
                      TKT1, TKT2, TKT3, TKT4)

```

## NADH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Females)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

```{r echo = F, message = F, warning = F}

plot.data = G85R.data(Geno3, Geno4, Geno1, Geno2,
                      Sex3, Sex4, Sex1, Sex2,
                      TKT3, TKT4, TKT1, TKT2)

```

## NADH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADH.FBgn)

```

##  NADPH Genes (Males)
```{r echo = F, warning = F}

G85R.volcano(plot.data, subset = NADPH.FBgn)

```

### 2025-03-17 RussoPaper/20250314_RussoManuscript_Fig1Revisions.Rmd
updated files

---
title: "Russo Fig1 Replots"
author: "John Santiago"
date: "2025-03-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

B = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Russo Fig 1 eclosion.csv")

B = B[c("w1118", "WTloxP", "G85Rhr", 
        "WTcr", "G85Rcr", "A4V.A4V",
        "null26.null26", "WTcr.null26",
        "G85Rcr.null26", "A4V.X16",
        "A4V.G85Rcr")]

mean.B = setNames(rep(0, ncol(B)), colnames(B))
i=1
while(i<=ncol(B)){
  mean.B[i] = mean(na.omit(B[,i]))
  i=i+1
}

B.labels = c("w1118",
             "WTLoxP/WTLoxP", "G85R/G85R(HR)",
             "WT/WT(CR)", "G85R/G85R(CR)",
             "A4V/A4V", "Sod1null/Sod1null", 
             "WT/Sod1null", "G85R(CR)/Sod1null",
             "A4V/X16", "A4V/G85R(CR)")

```

```{r echo = F, fig.width=10, fig.height=7}

par(mar = c(9,4,4,2))

barplot(height = mean.B,
        ylim = c(0, 100),
        col = "black",
        las = 2,
        ylab = "Eclosion rate (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:10)*1.2)),
     lwd = 3,
     line = 0,
     labels = B.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)
lines(x = c(-0.5,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

#abline(h = 100, lty = 2, lwd = 3)

```

```{r echo = F}

C = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 1C pharate_bouton_counts.xlsx - counts.csv")

W1118 = data.frame(Genotype = "W1118",
                   Boutons = na.omit(C$W1118),
                   x = 1)
W1118 = W1118[order(W1118$Boutons),]
W1118$x[c(3)] = .85
W1118$x[c(4)] = 1.15

SILENT = data.frame(Genotype = "SILENT",
                   Boutons = na.omit(C$SILENT),
                   x = 2)
SILENT = SILENT[order(SILENT$Boutons),]
SILENT$x[c(3)] = 1.85
SILENT$x[c(4)] = 2.15

G85Rcr = data.frame(Genotype = "G85Rcr",
                   Boutons = na.omit(C$G85Rcr),
                   x = 3)
G85Rcr = G85Rcr[order(G85Rcr$Boutons),]
G85Rcr$x[c(4,10)] = 2.875
G85Rcr$x[c(5,9)] = 3.125
G85Rcr$x[c(1)] = 2.925
G85Rcr$x[c(2)] = 3.075
G85Rcr$x[c(6)] = 2.75
G85Rcr$x[c(7)] = 3.25

A4V = data.frame(Genotype = "A4V",
                   Boutons = na.omit(C$A4V),
                   x = 4)
A4V = A4V[order(A4V$Boutons),]
A4V$x[c(4, 8)] = 3.875
A4V$x[c(5, 9)] = 4.125
A4V$x[c(6)] = 3.75
A4V$x[c(7)] = 4.25
A4V$x[c(1)] = 3.925
A4V$x[c(2)] = 4.075

C = rbind(W1118, rbind(SILENT,
                       rbind(G85Rcr, A4V)))

C$Genotype = factor(C$Genotype, levels = c("W1118", "SILENT", "G85Rcr", "A4V"))

C.labels = c("w1118", "WT(CR)", "G85R", "A4V")

hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

```

```{r echo = F, fig.width=10, fig.height=7}

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 150),
     xlim = c(.5, 4.5),
     xaxt = "n",
     ylab="Bouton Number",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Pharate muscle VM NMJ bouton counts")

boxplot(C$Boutons~C$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = c(hex("navy", .25),
                hex("skyblue", .25),
                hex('orange', .25),
                hex("deeppink", .25)),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(C$x),
       y=C$Boutons,
       cex=2.25,
       pch=21,
       bg=c('navy',"skyblue", 'orange', "deeppink")[as.numeric(C$Genotype)])

axis(side = 1,
     at = c(1:4),
     lwd = 3,
     line = -.9,
     labels = C.labels,
     xpd = T)

axis(side = 2,
     at = c(0, 50, 100, 150),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)

lines(x = c(0.35,4.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

lines(x = c(1, 4),
     y = c(140,140),
     lwd = 3)

lines(x = c(3, 3),
     y = c(60,140),
     lwd = 3)

lines(x = c(1, 1),
     y = c(120,140),
     lwd = 3)

lines(x = c(2, 2),
     y = c(120,140),
     lwd = 3)

lines(x = c(4, 4),
     y = c(120,140),
     lwd = 3)

text(x = 3,
     y = 145,
    labels = "*",
    cex = 2)

```

```{r echo = F}

D = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 1D NMJ_quantification_larva.csv")

w1118 = data.frame(Genotype = "w1118",
                   Boutons = na.omit(D$w1118),
                   x = 1)
w1118 = w1118[order(w1118$Boutons),]
w1118$x[c(3, 8, 15)] = .85
w1118$x[c(4, 9, 16)] = 1.15
w1118$x[c(5, 10, 13)] = .7
w1118$x[c(6, 11, 14)] = 1.3

LoxP = data.frame(Genotype = "LoxP",
                   Boutons = na.omit(D$LoxP),
                   x = 2)
LoxP = LoxP[order(LoxP$Boutons),]
LoxP$x[c(3)] = 1.85
LoxP$x[c(4)] = 2.15
LoxP$x[c(5)] = 1.7
LoxP$x[c(6)] = 2.3

G85R_HR = data.frame(Genotype = "G85R_HR",
                   Boutons = na.omit(D$G85R_HR),
                   x = 3)
G85R_HR = G85R_HR[order(G85R_HR$Boutons),]
G85R_HR$x[c(2, 5, 12)] = 2.85
G85R_HR$x[c(3, 6, 13)] = 3.15
G85R_HR$x[c(7, 10)] = 2.7
G85R_HR$x[c(8, 11)] = 3.3

silent = data.frame(Genotype = "silent",
                   Boutons = na.omit(D$silent),
                   x = 4)
silent = silent[order(silent$Boutons),]
silent$x[c(2, 5, 12, 14, 16)] = 3.85
silent$x[c(3, 6, 11, 15, 17)] = 4.15
silent$x[c(7, 10)] = 3.7
silent$x[c(8, 9)] = 4.3

G85R_WG = data.frame(Genotype = "G85R_WG",
                   Boutons = na.omit(D$G85R_WG),
                   x = 5)
G85R_WG = G85R_WG[order(G85R_WG$Boutons),]
G85R_WG$x[c(2)] = 4.85
G85R_WG$x[c(3)] = 5.15
G85R_WG$x[c(4)] = 4.7
G85R_WG$x[c(5)] = 5.3

A4V = data.frame(Genotype = "A4V",
                   Boutons = na.omit(D$A4V),
                   x = 6)
A4V = A4V[order(A4V$Boutons),]
A4V$x[c(1, 3)] = 5.85
A4V$x[c(2, 4)] = 6.15

D = rbind(w1118, rbind(LoxP,
    rbind(G85R_HR, 
    rbind(silent,
    rbind(G85R_WG, A4V)))))

D$Genotype = factor(D$Genotype, levels = c("w1118", "LoxP", "G85R_HR", "silent", "G85R_WG", "A4V"))

D.labels = c("w1118", "WTLoxP", "G85R(HR)", "WT(CR)", "G85R", "A4V")

```

```{r echo = F, fig.width=10, fig.height=7}

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 150),
     xlim = c(.5, 6.5),
     xaxt = "n",
     ylab="Bouton Number",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Larval muscle 6/7 NMJ bouton counts")

boxplot(D$Boutons~D$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 150),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = c(hex("navy", .25),
                hex("gold2", .25),
                hex("turquoise4", .25),
                hex("skyblue", .25),
                hex('orange', .25),
                hex("deeppink", .25)),
        add = T, 
        xaxt = "n",
        frame = F)

points(x=as.numeric(D$x),
       y=D$Boutons,
       cex=2.25,
       pch=21,
       bg=c('navy', "gold2", "turquoise4", 
            "skyblue", 'orange', "deeppink")[as.numeric(D$Genotype)])

axis(side = 1,
     at = c(1:6),
     lwd = 3,
     line = -.9,
     labels = D.labels,
     xpd = T)

axis(side = 2,
     at = c(0, 50, 100, 150),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)

lines(x = c(0.25,6.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

```

```{r echo = F, fig.width=10, fig.height=7}

E = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 1E LarvalLocomotion.csv")

E = E[c("w1118", "WTLoxP.WTLoxP", "G85R.G85R.HR.", "WT.WT",
        "G85R.G85R.CR.", "A4V.A4V",
        "A4V.X16", "A4V.G85R.CR.")]

E.labels = c("w1118", "WTLoxP", "G85R(HR)", 
             "WT(CR)", "G85R", "A4V",
             "A4V/X16", "A4V/G85R")

n.E = setNames(rep(0, ncol(E)), colnames(E))
mean.E = n.E
sd.E = n.E

i=1
while(i<= ncol(E)){
  mean.E[i] = mean(na.omit(E[,i]))
  sd.E[i] = sd(na.omit(E[,i]))
  n.E[i] = (length(na.omit(E[,i])))
  i=i+1
}

stderr.E = sd.E/(sqrt(n.E))

bar.colors = c(hex("navy", .75),
                hex("gold2", .75),
                hex("turquoise4", .75),
                hex("skyblue", .75),
                hex('orange', .75),
                hex("deeppink", .75),
                hex('grey', .75),
                hex("darkgreen", .75))

border.colors = c('navy', "gold2", "turquoise4",
                  "skyblue", 'orange', "deeppink", 
                  "grey", "green4")

tick.x = c(.7 + (c(0:7)*1.2))

par(mar = c(8,4,4,2), lwd = 3)

barplot(height = mean.E,
        ylim = c(0, 80),
        col = border.colors,
        las = 2,
        ylab = "Distance traveled (mm)",
        main = "Larval locomotion",
        border = border.colors,
        xaxt = "n")

axis(side = 1,
     at = tick.x,
     lwd = 3,
     line = 0,
     labels = E.labels,
     xpd = T)

axis(side = 2,
     at = c(0,20,40,60,80),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)
lines(x = c(-0.2,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

i = 1
while(i <= length(stderr.E)){
  lines(x = tick.x[c(i,i)],
        y = c(mean.E[i], (mean.E[i] + stderr.E[i])),
        lwd = 3,
        col = border.colors[i])

  lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
        y = c((mean.E[i] + stderr.E[i]), (mean.E[i] + stderr.E[i])),
        lwd = 3,
        col = border.colors[i])

  i = i +1
}

text(x = tick.x[3],
     y = (mean.E[3] + stderr.E[3]) + 5,
    labels = "*",
    cex = 2)

```

### 2025-03-17 TKT_RNAseq/R Code/TKTRNAseqPNPAssessment.Rmd
updated files

@@
 
-add.edges = data.frame(enzyme = c("2.2.1.1",
-                                  "5.1.3.1",
-                                  "5.3.1.6",
-                                  "5.4.2.7",
-                                  "5.4.2.2"),
-                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
-                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
-                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
-                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
-                       to = c("D-sedoheptulose-7-phosphate",
-                              "D-Xylulose 5-phosphate",
-                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
-                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
-                       arrows = c("to;from",
-                                  "to;from",
-                                  "to;from",
-                                  "to;from",
-                                  "to;from"),
-                       FBgn = "")
+#add.edges = data.frame(enzyme = c("2.2.1.1",
+#                                  "5.1.3.1",
+#                                  "5.3.1.6",
+#                                  "5.4.2.7",
+#                                  "5.4.2.2"),
+#                       from = c("D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+#                                "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
+#                       to = c("D-sedoheptulose-7-phosphate",
+#                              "D-Xylulose 5-phosphate",
+#                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate",
+#                              "D-ribose-1/5-phosphate / D-ribulose 5-phosphate"),
+#                       arrows = c("to;from",
+#                                  "to;from",
+#                                 "to;from",
+#                                "to;from",
+#                                  "to;from"),
+#                       FBgn = "")
 
@@
 glycolysis.edges$title = paste0(GeneIDKey[glycolysis.edges$FBgn, "Symbol"],
-                          "<br>log2(FC): ", signif(TKT.EdgeR.FC[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>FDR: ", signif(TKT.EdgeR[glycolysis.edges[,'FBgn'], comparison.T],3),
-                          "<br>", comparison.means[[comparison.T]][1], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][1]],3),
-                          "<br>", comparison.means[[comparison.T]][2], " cpm: ", signif(mean.cpm[glycolysis.edges[,'FBgn'],comparison.means[[comparison.T]][2]],3))
+                          "<br>log2(FC): ", 1,
+                          "<br>FDR: ", 1,
+                          "<br>", " cpm: ", 1,
+                          "<br>", " cpm: ", 1)
 
 glycolysis.edges = data.frame(from = glycolysis.edges$from.name,
-                              to = glycolysis.edges$to.name)
-,
-                              arrows = glycolysis.edges$arrow)
-,
-                              color = glycolysis.edges$color)
-,
-                              width = glycolysis.edges$size)
-,
+                              to = glycolysis.edges$to.name,
+                              arrows = glycolysis.edges$arrow,
+                              color = glycolysis.edges$color,
+                              width = glycolysis.edges$size,
                               title = glycolysis.edges$title,
@@
 node.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/purine.nodes.csv", row.names = 1)
+node.names = unique(c(visedges$from, visedges$to))
 node.colors = na.omit(comparison.M[intersect(row.names(comparison.M), node.names),])
@@
 node.data[node.data$group == "Outside Path", 'color.background'] = 'black'
+
 node.data[node.data$color.background == 'white', 'group'] = "no data"
@@
 NAD.path = edges
+#write.csv(NAD.path, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NAD.path.csv")
 
@@
 
-visedges = NAD.path
+visedges = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/NAD.path.csv", row.names = 1)
 visedges$color = round(TKT.EdgeR.FC[NAD.path$FBgn, comparison.T],2)
@@
 node.data[names(node.colors),'size'] = 
-  (node.data[names(node.colors),'size'] + 3)*3.5
+  (abs(node.data[names(node.colors),'size']) + 3)*3.5
 

### 2025-03-17 Functions_OmicsQuickPlotFunctions.R

@@ -724,3 +724,67 @@ serpe.heatmap = function(heat.genes){
   
 }
 
+
+##Function to plot expression levels for a specified set of genes in all cell types for the SC data EXCLUDES MANUALLY CURRATED CATEGORIES
+serpe.heatmap.noman = function(heat.genes){
+  heat.data = na.omit(cbind(serpe[heat.genes,],
+                            cbind(serpe.mn[heat.genes,],
+                                  cbind(serpe.inter[heat.genes,], serpe.glia[heat.genes,]))))
+  
+  heat.data = apply(heat.data, MARGIN = 2, as.numeric)
+  #heat.data = log2(heat.data)
+  row.names(heat.data) = heat.genes
+  
+  #heat.data[heat.data == 0] = NA
+  
+  Cluster.id = c(serpe.annotated.names,
+                 colnames(serpe.mn),
+                 colnames(serpe.inter),
+                 serpe.glia.names)
+  
+  Cluster.labelcolor = c(rep("darkgreen", length(serpe.annotated.names)),
+                         rep("brown", ncol(serpe.mn)),
+                         rep("orange", ncol(serpe.inter)),
+                         rep("steelblue", length(serpe.glia.names)))
+  
+  
+  heat.colors = colorRampPalette(c("grey95", "steelblue", "gold", "red3"))
+  
+  numcols = 100
+  
+  max.break = log2(max(heat.data))
+  
+  if(max.break > 7){
+    max.break = 7
+  }
+  
+  heat.data[heat.data > 1000] =1000
+  
+  color.breaks = 2^(c(0:(numcols))*(max.break/(numcols + 1)))
+
+Cluster.id = Cluster.id[(length(serpe.annotated.names)+1):ncol(heat.data)]
+Cluster.labelcolor = Cluster.labelcolor[(length(serpe.annotated.names)+1):ncol(heat.data)]
+heat.data = heat.data[,(length(serpe.annotated.names)+1):ncol(heat.data)]
+
+heatmap.2(heat.data,
+          Colv = F,
+          Rowv = F,
+          labCol = Cluster.id,
+          scale = 'none',
+          ColSideColors = Cluster.labelcolor,
+          trace = "none",
+          col = heat.colors(numcols),
+          dendrogram = "none",
+          na.color = "white",
+          key.title = "Mean Expression",
+          colCol = Cluster.labelcolor,
+          margins = c(10, 5), 
+          colsep = c(28, 77),
[…]

### 2025-03-17 TKT_RNAseq/Apps/TKT Specific Gene Boxplot/app.R

@@ -79,7 +79,7 @@ filter4.genes = row.names(TKT.EdgeR)
 ui <- fluidPage(
   
 ##Sidebar control code 
-  titlePanel("TKT RNAseq Experiment: Custom PCA Figure"),
+  titlePanel("TKT RNAseq Experiment: Specific Gene Boxplot"),
   sidebarLayout(position="left", sidebarPanel(
     
 ##General plot customization tools 

### 2025-03-17 pUAST_Map.R

@@ -1,0 +1,48 @@
+pUAST.seq = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/pUAST.Sequence.csv", header = F)
+
+pUAST.seq = cbind(pUAST.seq, pUAST.seq)
+colnames(pUAST.seq) = c("top", "bottom")
+
+pUAST.seq$bottom[pUAST.seq$top == "c"] = "g"
+pUAST.seq$bottom[pUAST.seq$top == "g"] = "c"
+pUAST.seq$bottom[pUAST.seq$top == "a"] = "t"
+pUAST.seq$bottom[pUAST.seq$top == "t"] = "a"
+
+three.prime = c(6061,6293)
+five.prime = c(1,587)
+
+plot(x = NA,
+     y = NA,
+     type = 'n',
+     ylim = c(0,3),
+     xlim = c(0, 9100),
+     #xaxt = "n",
+     ylab="",
+     yaxt = "n",
+     xlab = NA)
+lines(x = c(1,9053),
+      y = c(2,2),
+      lwd = 2)
+lines(x = c(1,9053),
+      y = c(1,1),
+      lwd = 2)
+
+lines(x = three.prime,
+      y = c(2,2),
+      lwd = 4,
+      col = "red")
+
+lines(x = three.prime,
+      y = c(1,1),
+      lwd = 4,
+      col = "red")
+
+lines(x = five.prime,
+      y = c(2,2),
+      lwd = 4,
+      col = "green")
+
+lines(x = five.prime,
+      y = c(1,1),
+      lwd = 4,
+      col = "green")

### 2025-03-24 GeneralDataFiles/CompleteMetabolicNetwork.Rmd
fixed edge

---
title: "Full Metabolic Network"
author: "John Santiago"
date: "2025-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F}

library(visNetwork)

git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"

G85R.geneFC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)

raw.nodes = read.csv(paste0(git.dir, "combined.nodes.csv"), row.names = 1)
raw.edges = read.csv(paste0(git.dir, "combined.edges.csv"))

temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

```

```{r echo = F}

nodes = raw.nodes
edges = raw.edges

nodes[nodes$shape == "circle", "size"] = 20
nodes$shape = 'dot'

node.colors = G85R.metabFC[nodes$data.id, "GR.CxOE"]
node.colors = temp[(200*node.colors/max(abs(na.exclude(node.colors)))) + 201]
node.colors[na.action(na.exclude(node.colors))] = "white"

nodes$color.background = node.colors

```

```{r echo = F}

visNetwork(nodes, edges)%>%
  visNodes(physics = F)%>%
  visLayout(hierarchical=F, improvedLayout=T)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  visEdges(arrows = visedges$arrows)

```

### 2025-04-11 GeneralDataFiles/CompleteMetabolicNetwork.Rmd
Updated Russo Data

@@
 
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
 G85R.geneFC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
 G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
+G85R.metabFC[,2:ncol(G85R.metabFC)] = log2(G85R.metabFC[,2:ncol(G85R.metabFC)])
 
@@
 
-temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)
+temp = colorRampPalette(c("dodgerblue", "grey",'red'))(401)
+
+```
+
+```{r echo = F}
+##"GRxWT.C"  "GRxWT.Df" "GRxWT.OE" "GR.CxDf" "WT.CxDf"  "GR.CxOE"  "WT.CxOE"
+metab = "GR.CxDf"
+
+enzyme = "GRF.CxDf"
+
+nodes = raw.nodes
+edges = raw.edges
+
+nodes[nodes$shape == "dot", "label"] = NA
+
+nodes[nodes$shape == "circle", "size"] = 20
+nodes$shape = 'dot'
+
+node.colors = (G85R.metabFC[nodes$data.id, metab])
+node.colors = temp[(200*node.colors/max(abs(na.exclude(node.colors)))) + 201]
+node.colors[na.action(na.exclude(node.colors))] = "white"
+
+nodes$color.background = node.colors
+
+nodes$title = paste0(nodes$id,
+                     "<br>FC: ", 
+                     signif((G85R.metabFC[nodes$data.id, metab]), 3))
+
+edges$title = paste0(GeneIDKey[edges$FBgn, "Symbol"],
+                     "<br>FC: ", 
+                     signif(G85R.geneFC[edges$FBgn,
+                                 enzyme],3))
+
+edges.colors = G85R.geneFC[edges$FBgn, enzyme]
+edges$width = abs(edges.colors) * 10
+
+edges.colors = temp[(200*edges.colors/max(abs(na.exclude(edges.colors)))) + 202]
+edges.colors[na.action(na.exclude(edges.colors))] = "white"
+
+edges$color = edges.colors
+
+#edges = edges[c(224,225, 226,227),]
+#edges$title = c("A","B","C", "D")
+
+```
+
+```{r echo = F}
+
+visNetwork(nodes, edges)%>%
+  visNodes(physics = F)%>%
+  #visLayout(hierarchical=F, improvedLayout=T)%>%
+  visOptions(highlightNearest = TRUE, nodesIdSelection = T)%>%
+  visEdges(arrows = visedges$arrows)
 
@@
 nodes[nodes$shape == "circle", "size"] = 20
-nodes$shape = 'dot'
+nodes$shape = "dot"
 
-node.colors = G85R.metabFC[nodes$data.id, "GR.CxOE"]
-node.colors = temp[(200*node.colors/max(abs(na.exclude(node.colors)))) + 201]
-node.colors[na.action(na.exclude(node.colors))] = "white"
-
-nodes$color.background = node.colors
+visNetwork(nodes, edges)%>%
+  visNodes(physics = F)
 
 ```
-
-```{r echo = F}
-
-visNetwork(nodes, edges)%>%
-  visNodes(physics = F)%>%
-  visLayout(hierarchical=F, improvedLayout=T)%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows = visedges$arrows)
-
-```

### 2025-04-11 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
update
Updated Russo Data

@@
 
+GeneIDKey = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
+
+#raw count data directory
+cd.dir = "/Users/johncsantiago/Documents/GitHub/Datasets/GBB_Count_Tables/"
+
+GBB.countdata = read.csv(paste0(cd.dir, list.files(cd.dir)[1]), 
+                   sep = "\t", row.names = 1)
+colnames(GBB.countdata) = substr(list.files(cd.dir)[1], 1, 7)
+
+i=2
+while(i <= length(list.files(cd.dir))){
+  temp.cd = read.csv(paste0(cd.dir, list.files(cd.dir)[i]), 
+                     sep = "\t", row.names = 1)
+  colnames(temp.cd) = substr(list.files(cd.dir)[i], 1, 7)
+  temp.cd[,1] = temp.cd[row.names(GBB.countdata),]
+  GBB.countdata = cbind(GBB.countdata, temp.cd)
+  i = i + 1
+}
+
+GBB.groups = read.csv("/Users/johncsantiago/Documents/GitHub/Datasets/GBB_Metadata.csv", row.names = 1)
+
 ##Clean Trait Data and calculate CPMs
-countdata=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.counttable.csv",row.names=1)
-groups=read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/All.TKT.metadata.csv",row.names=1)
-
-convert=read.csv("https://raw.githubusercontent.com/DavidRandLab/Santiago-et-al-2021-BMC-Genomics/main/Data%20Files/FBgnConversionTable.csv",row.names=1)
+countdata=GBB.countdata
+groups=GBB.groups
+
+groups = groups[groups$Experiment == "GBB-KO",]
 
 ##normalize data
-countdata=countdata[, row.names(groups)]
+countdata= countdata[,row.names(groups)]
 x <- countdata
@@
 ##GR.F TKT control vs TKT altered
-compare = makeContrasts(TktDfGR.F-GR.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.F.CxDf=DEout
-sGR.F.CxDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEGR.F-GR.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.F.CxOE=DEout
-sGR.F.CxOE=DEout[DEout$FDR<.05,]
-
-##WT.F TKT control vs TKT altered
-compare = makeContrasts(TktDfWT.F-WT.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.F.CxDf=DEout
-sWT.F.CxDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEWT.F-WT.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.F.CxOE=DEout
-sWT.F.CxOE=DEout[DEout$FDR<.05,]
-
-##WT.F vs GR.F
-compare = makeContrasts(GR.F-WT.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.F=DEout
-sGRxWT.F=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktDfGR.F-TktDfWT.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.FDf=DEout
-sGRxWT.FDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEGR.F-TktOEWT.F, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.FOE=DEout
-sGRxWT.FOE=DEout[DEout$FDR<.05,]
-
-##GR.M TKT control vs TKT altered
-compare = makeContrasts(TktDfGR.M-GR.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.M.CxDf=DEout
-sGR.M.CxDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEGR.M-GR.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GR.M.CxOE=DEout
-sGR.M.CxOE=DEout[DEout$FDR<.05,]
-
-##WT.M TKT control vs TKT altered
-compare = makeContrasts(TktDfWT.M-WT.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.M.CxDf=DEout
-sWT.M.CxDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEWT.M-WT.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-WT.M.CxOE=DEout
-sWT.M.CxOE=DEout[DEout$FDR<.05,]
-
-##WT.M vs GR.M
-compare = makeContrasts(GR.M-WT.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.M=DEout
-sGRxWT.M=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.MDf=DEout
-sGRxWT.MDf=DEout[DEout$FDR<.05,]
-
-compare = makeContrasts(TktOEGR.M-TktOEWT.M, levels=design)
-lrt = glmQLFTest(fit,contrast=as.vector(compare))
-G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
-DEout=G_X_E$table
-GRxWT.MOE=DEout
-sGRxWT.MOE=DEout[DEout$FDR<.05,]
-
-TKT.EdgeR = data.frame(GRF.CxDf = GR.F.CxDf[row.names(cpmdata),'FDR'],
-                       GRF.CxOE = GR.F.CxOE[row.names(cpmdata),'FDR'],
-
-                       WTF.CxDf = WT.F.CxDf[row.names(cpmdata),'FDR'],
-                       WTF.CxOE = WT.F.CxOE[row.names(cpmdata),'FDR'],
-
-                       GRxWT.FC = GRxWT.F[row.names(cpmdata),'FDR'],
-                       GRxWT.FDf = GRxWT.FDf[row.names(cpmdata),'FDR'],
-                       GRxWT.FOE = GRxWT.FOE[row.names(cpmdata),'FDR'],
-
-                       GRM.CxDf = GR.M.CxDf[row.names(cpmdata),'FDR'],
-                       GRM.CxOE = GR.M.CxOE[row.names(cpmdata),'FDR'],
-
-                       WTM.CxDf = WT.M.CxDf[row.names(cpmdata),'FDR'],
-                       WTM.CxOE = WT.M.CxOE[row.names(cpmdata),'FDR'],
-
-                       GRxWT.MC = GRxWT.M[row.names(cpmdata),'FDR'],
-                       GRxWT.MDf = GRxWT.MDf[row.names(cpmdata),'FDR'],
-                       GRxWT.MOE = GRxWT.MOE[row.names(cpmdata),'FDR'])
-
-row.names(TKT.EdgeR) = row.names(cpmdata)
-##write.csv(TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
-
-Female = c(nrow(sGR.F.CxDf), nrow(sGR.F.CxOE),
-           nrow(sWT.F.CxDf), nrow(sWT.F.CxOE),
-           nrow(sGRxWT.F), nrow(sGRxWT.FDf), nrow(sGRxWT.FOE))
-
-Male = c(nrow(sGR.M.CxDf), nrow(sGR.M.CxOE),
-         nrow(sWT.M.CxDf), nrow(sWT.M.CxOE),
-         nrow(sGRxWT.M), nrow(sGRxWT.MDf), nrow(sGRxWT.MOE))
-
-MDSdata = plotMDS(z, top = 13582, col=as.numeric(factor(gr)))
-
-temp=convert[,"Symbol"]
-temp2=setdiff(row.names(countdata),convert[,2])
-names(temp)=convert[,2]
-names(temp2)=temp2
-convert=c(temp,temp2)
-
-Comparisons = list(row.names(sGR.F.CxDf), row.names(sGR.F.CxOE),
-                row.names(sWT.F.CxDf), row.names(sWT.F.CxOE),
-                row.names(sGRxWT.F), row.names(sGRxWT.FDf), row.names(sGRxWT.FOE),
-                row.names(sGR.M.CxDf), row.names(sGR.M.CxOE),
-                row.names(sWT.M.CxDf), row.names(sWT.M.CxOE),
-                row.names(sGRxWT.M), row.names(sGRxWT.MDf), row.names(sGRxWT.MOE))
-
-GroupsToDEGs = matrix("", nrow = 28, ncol = 3)
-
-GroupsToDEGs[,1] = c("GR.F", "TktDfGR.F",
-                     "GR.F", "TktOEGR.F",
-                     "WT.F", "TktDfWT.F",
-                     "WT.F", "TktOEWT.F",
-                     "GR.F", "WT.F",
-                     "TktDfGR.F", "TktDfWT.F",
-                     "TktOEGR.F", "TktOEWT.F",
-                     "GR.M", "TktDfGR.M",
-                     "GR.M", "TktOEGR.M",
-                     "WT.M", "TktDfWT.M",
-                     "WT.M", "TktOEWT.M",
-                     "GR.M", "WT.M",
-                     "TktDfGR.M", "TktDfWT.M",
-                     "TktOEGR.M", "TktOEWT.M")
-
-GroupsToDEGs[,2] = c("TktDfGR.F", "GR.F",
-                     "TktOEGR.F", "GR.F", 
-                     "TktDfWT.F", "WT.F", 
-                     "TktOEWT.F", "WT.F", 
-                     "WT.F", "GR.F", 
-                     "TktDfWT.F", "TktDfGR.F", 
-                     "TktOEWT.F", "TktOEGR.F", 
-                     "TktDfGR.M", "GR.M", 
-                     "TktOEGR.M", "GR.M", 
-                     "TktDfWT.M", "WT.M", 
-                     "TktOEWT.M", "WT.M", 
-                     "WT.M", "GR.M", 
-                     "TktDfWT.M", "TktDfGR.M", 
-                     "TktOEWT.M", "TktOEGR.M")
-
-GroupsToDEGs[,3] = c(1,1,2,2,3,3,4,4,5,5,6,6,7,7,
-                     8,8,9,9,10,10,11,11,12,12,13,13,14,14)
+#compare = makeContrasts(TktDfGR.F-GR.F, levels=design)
+#lrt = glmQLFTest(fit,contrast=as.vector(compare))
+#G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
+#DEout=G_X_E$table
+#GR.F.CxDf=DEout
+#sGR.F.CxDf=DEout[DEout$FDR<.05,]
+
+MDSdata = plotMDS(z, 
+                  top = 15000, 
+                  col = as.numeric(factor(gr)), 
+                  labels =  paste(groups$Group, groups$Replicate))
+
+```
+
+```{r echo = F}
+
+countdata=GBB.countdata
+groups=GBB.groups
+
+groups = groups[groups$Experiment == "GBB-OE",]
+
+##normalize data
+countdata= countdata[,row.names(groups)]
+x <- countdata
+gr <- factor(groups$Group)
+y <- DGEList(counts=x,group=gr)
+keep <- filterByExpr(y)
+y <- y[keep,,keep.lib.sizes=FALSE]
+z <- calcNormFactors(y, method = "TMM")
+##normalized cpm
+cpmdata=cpm(z)
+
+design<-model.matrix(~0 + gr)
+colnames(design) = unique(gr)
+z = estimateDisp(z, design, robust = T)
+
+fit <- glmQLFit(z, design)
+
+MDSdata = plotMDS(z, 
+                  top = 15000, 
+                  col = as.numeric(factor(gr)), 
+                  labels =  paste(groups$Group, groups$Replicate))
 

### 2025-04-11 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/AHH0001.sh

@@ -1,13 +1,13 @@
 #!/bin/bash
 
-#SBATCH -J A3FA1_STAR.sh
+#SBATCH -J AHHH0001.sh
 #SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
 #SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
 
-#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G A3FA1_STAR.sh
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0001.sh
 
 shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
-sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq//gpfs/data/kwharton/azhou/ALS_model_gbb"
+sampledir="/gpfs/data/kwharton/azhou/ALS_model_gbb/seq_files/"
 stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
 genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
 
@@ -15,19 +15,19 @@ module load star
 module load samtools
 module load python
 
-sample="A3FA1"
-sample1=$sampledir$sample"_R1_001"
-sample2=$sampledir$sample"_R2_001"
 
-gzip -d $sample1".fastq.gz"
-gzip -d $sample2".fastq.gz"
+sample=$sampledir"AHH0001"
+
+
+gzip -d $sample".fastq.gz"
+
 
 cd $stardir"first_pass"
-STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
 STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
 
[…]

### 2025-04-11 A4V_BodySections_RNAseq/A4V RNAseq Shell Scripts/AHH0001_STAR.sh

@@ -1,13 +1,13 @@
 #!/bin/bash
 
-#SBATCH -J A3FA1_STAR.sh
+#SBATCH -J AHH0001_STAR.sh
 #SBATCH -o /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
 #SBATCH -e /gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/Output_Files/Scratch/error_%j.out
 
-#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G A3FA1_STAR.sh
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0001_STAR.sh
 
 shelldir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/Shell_Scripts/" 
-sampledir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/00_fastq//gpfs/data/kwharton/azhou/ALS_model_gbb"
+sampledir="/gpfs/data/kwharton/azhou/ALS_model_gbb/seq_files/"
 stardir="/gpfs/data/kwharton/jsantiago/30-927564627_A4V_RNAseq/STAR_Alignment/"
 genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
 
@@ -15,19 +15,19 @@ module load star
 module load samtools
 module load python
 
-sample="A3FA1"
-sample1=$sampledir$sample"_R1_001"
-sample2=$sampledir$sample"_R2_001"
 
-gzip -d $sample1".fastq.gz"
-gzip -d $sample2".fastq.gz"
+sample=$sampledir"AHH0001"
+
+
+gzip -d $sample".fastq.gz"
+
 
 cd $stardir"first_pass"
-STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample1".fastq" $sample2".fastq" --runThreadN 20
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
[…]

### 2025-04-11 GBB RNAseq Data/AHH0001_STAR.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+#SBATCH -J AHH0001_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0001_STAR.sh
+
+shelldir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/seq_files/"
+stardir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+
+module load star
+module load samtools
+module load python
+
+
+sampleID="AHH0001"
+sample=$sampledir$sampleID
+
+
+gzip -d $sample".fastq.gz"
+
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample".fastq" --runThreadN 20 --outSAMtype BAM SortedByCoordinate --outFileNamePrefix $stardir"Output_Files/BAM/"$sampleID
+samtools index $stardir"Output_Files/BAM/"$sampleID"Aligned.sortedByCoord.out.bam"
+
+python -m venv $stardir"PythonHTseq/"$sampleID
+source $stardir"PythonHTseq/"$sampleID/bin/activate
+pip install HTSeq
[…]

### 2025-04-11 GBB RNAseq Data/AHH0002-9_STAR.sh

@@ -1,0 +1,205 @@
+#!/bin/bash
+
+#SBATCH -J AHH0002-9_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0002-9_STAR.sh
+
+shelldir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/seq_files/"
+stardir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+
+module load star
+module load samtools
+module load python
+
+
+sampleID="AHH0002"
+sample=$sampledir$sampleID
+
+
+gzip -d $sample".fastq.gz"
+
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample".fastq" --runThreadN 20 --outSAMtype BAM SortedByCoordinate --outFileNamePrefix $stardir"Output_Files/BAM/"$sampleID
+samtools index $stardir"Output_Files/BAM/"$sampleID"Aligned.sortedByCoord.out.bam"
+
+python -m venv $stardir"PythonHTseq/"$sampleID
+source $stardir"PythonHTseq/"$sampleID/bin/activate
+pip install HTSeq
[…]

### 2025-04-11 GBB RNAseq Data/AHH0010-19_STAR.sh

@@ -1,0 +1,282 @@
+#!/bin/bash
+
+#SBATCH -J AHH0010-19_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0010-19_STAR.sh
+
+shelldir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/seq_files/"
+stardir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+
+module load star
+module load samtools
+module load python
+
+
+##10
+
+sampleID="AHH0010"
+sample=$sampledir$sampleID
+
+gzip -d $sample".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample".fastq" --runThreadN 20 --outSAMtype BAM SortedByCoordinate --outFileNamePrefix $stardir"Output_Files/BAM/"$sampleID
+samtools index $stardir"Output_Files/BAM/"$sampleID"Aligned.sortedByCoord.out.bam"
+
+python -m venv $stardir"PythonHTseq/"$sampleID
+source $stardir"PythonHTseq/"$sampleID/bin/activate
+pip install HTSeq
[…]

### 2025-04-11 GBB RNAseq Data/AHH0020-27_STAR.sh

@@ -1,0 +1,222 @@
+#!/bin/bash
+
+#SBATCH -J AHH0020-27_STAR.sh
+#SBATCH -o /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/outfile_%j.out
+#SBATCH -e /gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/Output_Files/Scratch/error_%j.out
+
+#Submit cmd: sbatch -n 26 -t 16:00:00 --mem=64G AHH0020-27_STAR.sh
+
+shelldir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/Shell_Scripts/" 
+sampledir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/seq_files/"
+stardir="/gpfs/data/kwharton/jsantiago/GBB_RNAseq_Data/STAR_Alignment/"
+genomedir="/gpfs/data/kwharton/jsantiago/BDGP6.32/"
+
+
+module load star
+module load samtools
+module load python
+
+
+##20
+
+sampleID="AHH0020"
+sample=$sampledir$sampleID
+
+gzip -d $sample".fastq.gz"
+
+cd $stardir"first_pass"
+STAR --genomeDir $genomedir"STAR_Index" --readFilesIn $sample".fastq" --runThreadN 20
+STAR --runMode genomeGenerate --genomeDir $stardir"second_index" --genomeFastaFiles $genomedir"Drosophila_melanogaster.BDGP6.32.dna.toplevel.fa"* --sjdbFileChrStartEnd $stardir"first_pass/SJ.out.tab" --sjdbOverhang 149 --runThreadN 20 --genomeSAindexNbases 13
+
+cd $stardir"second_pass"
+STAR --genomeDir $stardir"second_index" --readFilesIn $sample".fastq" --runThreadN 20 --outSAMtype BAM SortedByCoordinate --outFileNamePrefix $stardir"Output_Files/BAM/"$sampleID
+samtools index $stardir"Output_Files/BAM/"$sampleID"Aligned.sortedByCoord.out.bam"
+
+python -m venv $stardir"PythonHTseq/"$sampleID
+source $stardir"PythonHTseq/"$sampleID/bin/activate
+pip install HTSeq
[…]

### 2025-04-11 GOandKEGGPlottingFunctions.R

@@ -545,14 +545,16 @@ KEGG.diagram = function(PathwayID, FC, use, metab.data){
     FC.data =  FC[,1]
     
     #Any column name from G85R.metabFC or 'none'
-    metab.data = metab.data[,1]
+    metab.data = metab.data[1]
   }
   
-  ##KEGG Mapping Function
-  if(length(intersect(list.files(), "KEGG_Image_Files")) == 0){
-    dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
-  }
   Home = dirname(rstudioapi::getSourceEditorContext()$path)
+  
+  ##KEGG Mapping Function
+  if(length(intersect(list.files(Home), "KEGG_Image_Files")) == 0){
+    dir.create(paste0(Home, "/KEGG_Image_Files/"))
+  }
+
   OutputDir = paste0(Home, "/KEGG_Image_Files/")
   #setwd(OutputDir)
   sigs = usegenes
@@ -572,8 +574,8 @@ KEGG.diagram = function(PathwayID, FC, use, metab.data){
     metab.data = setNames(log2(G85R.metabFC[metab.id, metab.data]), names(metab.id))
   }
   
-  
-  
+
+  setwd(OutputDir)
   pv.out <- pathview(gene.data =  deg.data,
                      cpd.data = metab.data,
                      pathway.id = PathwayID,
@@ -586,7 +588,7 @@ KEGG.diagram = function(PathwayID, FC, use, metab.data){
                      bins=list(genes=30),
                      plot.col.key = F,
                      match.data = F)
-  #setwd(Home)
+  setwd(Home)
   
   
   if(class(FC.data)=="numeric"){

### 2025-04-17 RussoPaper/20250314_RussoManuscript_Fig1Revisions.Rmd
updated general data files for app

@@
 
-B = B[c("w1118", "WTloxP", "G85Rhr", 
-        "WTcr", "G85Rcr", "A4V.A4V",
-        "null26.null26", "WTcr.null26",
-        "G85Rcr.null26", "A4V.X16",
-        "A4V.G85Rcr")]
-
 mean.B = setNames(rep(0, ncol(B)), colnames(B))
@@
 B.labels = c("w1118",
-             "WTLoxP/WTLoxP", "G85R/G85R(HR)",
-             "WT/WT(CR)", "G85R/G85R(CR)",
-             "A4V/A4V", "Sod1null/Sod1null", 
-             "WT/Sod1null", "G85R(CR)/Sod1null",
-             "A4V/X16", "A4V/G85R(CR)")
+             "WT(LoxP)", "G85R(hr)",
+             "WT(cr)", "G85R(cr)",
+             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
+             "A4V/A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")
 
@@
         las = 2,
-        ylab = "Eclosion rate (%)",
+        ylab = "Eclosion frequency (%)",
         main = "Eclosion from the pupal case",
@@
 axis(side = 1,
-     at = c(.7 + (c(0:10)*1.2)),
+     at = c(.7 + (c(0:11)*1.2)),
      lwd = 3,

### 2025-04-17 Metabolomics/TKTMetabolitePlot/app.R

@@ -1,0 +1,502 @@
+library(shiny)
+library(gplots)
+library(DT)
+
+# Load data from GitHub
+git.dir <- "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
+
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
+
+TKT.cpm = read.csv(paste0(git.dir,"TKT_cpmdata.csv"), row.names = 1)
+
+TKT.groups  = read.csv(paste0(git.dir, "TKT.metadata.csv"), row.names = 1)
+
+TKT.groups = TKT.groups[colnames(TKT.cpm),]
+
+TKT.FC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
+TKT.FDR = read.csv(paste0(git.dir, "TKT.EdgeR.FDRTable.csv"), row.names = 1)
+
+A4V.cpm = read.csv(paste0(git.dir, "A4V.cpmdata.csv"), row.names = 1)
+
+A4V.FC = read.csv(paste0(git.dir, "A4V.FCdata.csv"), row.names = 1)
+
+A4V.FDR = read.csv(paste0(git.dir, "A4V.FDRdata.csv"), row.names = 1)
+
+Metab.data <- read.csv(paste0(git.dir, "RawMetabolomicData.csv"), row.names = 1)
+Metab.Meta <- read.csv(paste0(git.dir, "MetabolomicMetadata.csv"), row.names = 1)
+Metab.FC <- read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
+Metab.FDR <- read.csv(paste0(git.dir, "MetaboliteFDRs.csv"), row.names = 1)
+
+Metab.FC = Metab.FC[,-1]
+Metab.FDR = Metab.FDR[,-1]
+
+# KEGG mapping (optional future use)
+KEGG.Key <- setNames(Metab.data[-c(1:2), 2], row.names(Metab.data)[-c(1:2)])
+
+# Normalize
+norm.func <- function(data) {
+  nd <- (as.numeric(data) / Metab.Meta$TIC) * 1000
+  return(nd)
+}
+norm.data <- t(apply(Metab.data[3:nrow(Metab.data), 3:ncol(Metab.data)], 1, norm.func))
[…]

### 2025-04-17 WhartonLabOmicsDataApp/WhartonLabOmicsDataAppFunctions.R
updated app

@@ -1,7 +1,3 @@
-library(shiny)
-library(gplots)
-library(DT)
-
 # Load data from GitHub
 git.dir <- "https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/GeneralDataFiles/"
 
@@ -41,9 +37,6 @@ norm.func <- function(data) {
 norm.data <- t(apply(Metab.data[3:nrow(Metab.data), 3:ncol(Metab.data)], 1, norm.func))
 colnames(norm.data) <- colnames(Metab.data)[3:ncol(Metab.data)]
 colnames(norm.data) <- Metab.Meta[colnames(norm.data), "Genotypes"]
-
-
-library(gplots)
 
 
 ##Function to plot all G85R groups
@@ -160,12 +153,12 @@ plot.G85R = function(ID){
              cex.axis = 2)
         
         #axis(side = 3,
-         #    at = c(3.5,9.5),
-          #   tick = T,
-           #  outer = T,
-            # labels = F,
-             #line = -2.25,
-             #lwd.ticks = 0)
+        #    at = c(3.5,9.5),
+        #   tick = T,
+        #  outer = T,
+        # labels = F,
+        #line = -2.25,
+        #lwd.ticks = 0)
         
         xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
         xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
@@ -351,165 +344,3 @@ plot.metab = function(metabID){
     
   }
 }
-
-# UI
-ui <- fluidPage(
-  titlePanel("Wharton Lab Omics Data Viewer"),
-  
-  # Move the input above the main panel
-  fluidRow(
-    column(
-      width = 12,
-      selectInput(
-        "datasetType",
-        "Select Data Type:",
-        choices = c("G85R-TKT Metabolomics", "G85R-TKT Transcriptomics", "A4V Transcriptomics"),
-        selected = "G85R-TKT Metabolomics"
-      ),
-      uiOutput("dynamicIDSelector")
-    )
-  ),
-  
-  fluidRow(
-    column(
-      width = 8,
-      div(
-        plotOutput("metabPlot", height = "500px"),
-        style = "max-width: 1100px;"  # Example narrower width
-      )),
-    column(
-      width = 4,
-      h4("Fold Change and FDR Summary"),
-      div(
-        DTOutput("metabTable", height = "300px"),
[…]

### 2025-04-17 WhartonLabOmicsDataApp/WhartonOmicsDataViewer/app.R
point size

@@ -34,7 +34,7 @@ ui <- fluidPage(
       width = 4,
       h4("Fold Change and FDR Summary"),
       div(
-        DTOutput("metabTable", height = "300px"),
+        DTOutput("metabTable", height = "350px"),
         style = "max-width: 400px;"  # Example narrower width
       )
     )
@@ -144,7 +144,7 @@ server <- function(input, output, session) {
         paging = FALSE,
         scrollX = TRUE,
         scrollCollapse = TRUE,
-        scrollY = "300px",  # adjust height as needed
+        scrollY = "350px",  # adjust height as needed
         scroller = TRUE,
         rowCallback = JS(
           'function(row, data) {

### 2025-04-17 WhartonLabOmicsDataApp/WhartonLabOmicsDataAppFunctions.R
Update WhartonLabOmicsDataAppFunctions.R

@@ -108,7 +108,7 @@ plot.G85R = function(ID){
         
         points(x=as.numeric(factor(gene$condition)),
                y=gene$cpm,
-               cex=1,
+               cex=3,
                pch=21,
                bg=c("darkgreen", 'firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
         

### 2025-04-17 WhartonLabOmicsDataApp/WhartonLabOmicsDataAppFunctions.R
Update WhartonLabOmicsDataAppFunctions.R

@@ -108,7 +108,7 @@ plot.G85R = function(ID){
         
         points(x=as.numeric(factor(gene$condition)),
                y=gene$cpm,
-               cex=3,
+               cex=5,
                pch=21,
                bg=c("darkgreen", 'firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
         

### 2025-04-17 WhartonLabOmicsDataApp/WhartonLabOmicsDataAppFunctions.R
Update WhartonLabOmicsDataAppFunctions.R

@@ -108,7 +108,7 @@ plot.G85R = function(ID){
         
         points(x=as.numeric(factor(gene$condition)),
                y=gene$cpm,
-               cex=5,
+               cex=2.5,
                pch=21,
                bg=c("darkgreen", 'firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
         

### 2025-04-17 WhartonLabOmicsDataApp/WhartonLabOmicsDataAppFunctions.R
Update WhartonLabOmicsDataAppFunctions.R

@@ -108,7 +108,7 @@ plot.G85R = function(ID){
         
         points(x=as.numeric(factor(gene$condition)),
                y=gene$cpm,
-               cex=2.5,
+               cex=1.5,
                pch=21,
                bg=c("darkgreen", 'firebrick',"dodgerblue","gold")[as.numeric(factor(gene$group))])
         

### 2025-04-17 DeficiencyScreen/DeficiencyMapViewerFunctions.R
updating deficiency map viewer

@@ -1,0 +1,298 @@
+git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
+DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.names = 1)
+row.names(DfKey) = DfKey$Deficiency
+DfKey[DfKey$MLE == 0, "MLE"] = .05
+GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+
+fbID = data.frame(FBgn = c(rep(GeneIDKey$FBgn, 2)),
+                  Symbol = c(rep(GeneIDKey$Symbol, 2)),
+                  Position = c(GeneIDKey$Start, GeneIDKey$End))
+
+plot.pos = function(chr, start, end){
+  goi = data.frame(Start = start,
+                   End = end,
+                   CHR = chr)
+  range.min = start
+  range.max = end
+  
+  ##genes in range
+  gir = na.omit(GeneIDKey[(GeneIDKey$CHR == goi$CHR),])
+  gir = na.omit(gir[(((gir$Start >= range.min) & (gir$Start <= range.max)) | 
+                       ((gir$End >= range.min) & (gir$End <= range.max)) |
+                       ((gir$End >= range.max) & (gir$Start <= range.min))), ])
+  gir$x1 = gir$Start
+  gir$x2 = gir$End
+  
+  Dfir = na.omit(DfKey[DfKey$Chr == goi$CHR,])
+  Dfir = na.omit(Dfir[(((Dfir$Start >= range.min) & (Dfir$Start <= range.max)) | 
+                         ((Dfir$End >= range.min) & (Dfir$End <= range.max)) |
+                         ((Dfir$End >= range.max) & (Dfir$Start <= range.min))), ])
+  Dfir$x1 = Dfir$Start
+  Dfir$x2 = Dfir$End
+  
+  line.data = gir
+  if(min(line.data$Start) < range.min){
+    line.data$x2[line.data$Start < range.min] = range.min
+  }
+  
+  if(max(line.data$End) > range.max){
+    line.data$x2[line.data$End > range.max] = range.max
+  }
+  
+  bar.data = Dfir
+  if(min(bar.data$Start) < range.min){
+    bar.data$x1[bar.data$Start < range.min] = range.min
+  }
+  
+  if(max(bar.data$End) > range.max){
[…]

### 2025-04-17 DeficiencyScreen/DeficiencyMapViewer/app.R
lines + markers

@@ -1,307 +1,10 @@
 ##library(rsconnect)
-
+##deployapp()
 
 library(shiny)
 library(plotly)
 
-git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
-DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.names = 1)
-row.names(DfKey) = DfKey$Deficiency
-DfKey[DfKey$MLE == 0, "MLE"] = .05
-GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
-
-fbID = data.frame(FBgn = c(rep(GeneIDKey$FBgn, 2)),
-                  Symbol = c(rep(GeneIDKey$Symbol, 2)),
-                  Position = c(GeneIDKey$Start, GeneIDKey$End))
-
-plot.pos = function(chr, start, end){
-  goi = data.frame(Start = start,
-                   End = end,
-                   CHR = chr)
-  range.min = start
-  range.max = end
-  
-  ##genes in range
-  gir = na.omit(GeneIDKey[(GeneIDKey$CHR == goi$CHR),])
-  gir = na.omit(gir[(((gir$Start >= range.min) & (gir$Start <= range.max)) | 
-                       ((gir$End >= range.min) & (gir$End <= range.max)) |
-                       ((gir$End >= range.max) & (gir$Start <= range.min))), ])
-  gir$x1 = gir$Start
-  gir$x2 = gir$End
-  
-  Dfir = na.omit(DfKey[DfKey$Chr == goi$CHR,])
-  Dfir = na.omit(Dfir[(((Dfir$Start >= range.min) & (Dfir$Start <= range.max)) | 
-                         ((Dfir$End >= range.min) & (Dfir$End <= range.max)) |
-                         ((Dfir$End >= range.max) & (Dfir$Start <= range.min))), ])
-  Dfir$x1 = Dfir$Start
-  Dfir$x2 = Dfir$End
-  
-  line.data = gir
-  if(min(line.data$Start) < range.min){
-    line.data$x2[line.data$Start < range.min] = range.min
-  }
-  
-  if(max(line.data$End) > range.max){
-    line.data$x2[line.data$End > range.max] = range.max
-  }
-  
-  bar.data = Dfir
-  if(min(bar.data$Start) < range.min){
-    bar.data$x1[bar.data$Start < range.min] = range.min
[…]

### 2025-04-17 DeficiencyScreen/DeficiencyMapViewerFunctions.R

@@ -123,7 +123,7 @@ plot.pos = function(chr, start, end){
   fig = fig %>% add_lines(x = ~dfx,
                           y = ~dfy,
                           type = 'scatter',
-                          mode = "lines",
+                          mode = "lines + markers",
                           name = ~dfName,
                           showlegend = F,
                           fill = 'tozeroy',

### 2025-04-19 DeficiencyScreen/DeficiencyMapViewer/app.R
updated DF Map Viewer Functions

@@ -6,6 +6,7 @@ library(plotly)
 
 source("https://raw.githubusercontent.com/johncsantiago/WhartonLab/refs/heads/master/DeficiencyScreen/DeficiencyMapViewerFunctions.R")
 
+
 ui <- fluidPage(
   
   ##Sidebar control code 
@@ -74,6 +75,9 @@ ui <- fluidPage(
                             value = 15000000),),
       ),),
     
+    actionButton("updatePlot", "Update Plot"),
+    
+    
     width = 3),
     
     ##Figure display settings    
@@ -90,69 +94,78 @@ ui <- fluidPage(
 # Define server logic required to draw a histogram ----
 server <- function(input, output, session) {
   
-  output$geneControls = renderUI({
-    selectizeInput("gene", label = "Select Gene", 
-                   choices = NULL,  # leave empty for server-side
-                   options = list(
-                     create = TRUE,
-                     placeholder = 'Select a gene name'
-                   ),
-                   selected = "Arc1")
-  })  
   
-  observe({
-    updateSelectizeInput(
-      session, 
-      "gene", 
-      choices = GeneIDKey$Symbol, 
-      server = TRUE
-    )
-  })
-  
-  # Debounced reactive inputs
-  debounced_gene <- debounce(reactive(input$gene), 500)
-  debounced_start <- debounce(reactive(input$start.range), 500)
-  debounced_end <- debounce(reactive(input$end.range), 500)
+  session$onFlushed(function() {
+    # Only trigger once to avoid infinite loops
+    isolate({
+      updateActionButton(session, "updatePlot", label = NULL, icon = NULL)
+      session$sendInputMessage("updatePlot", list(value = 1))
+    })
+  }, once = TRUE)
   
   
-  output$plot <- renderPlotly({
+  updateData <- eventReactive(input$updatePlot, {
     if (input$locfactor == "gene") {
-      req(debounced_gene())  # Wait until gene input stabilizes
-      
-      p = plot.gene(
-        gene.symbol = debounced_gene(),
-        start.range = debounced_start(),
-        end.range = debounced_end()
+      req(input$gene, input$start.range, input$end.range)
+      list(
+        type = "gene",
+        gene = input$gene,
+        start.range = input$start.range,
+        end.range = input$end.range
       )
     } else {
-      p = plot.pos(
+          req(input$CHR, input$start, input$end)
+      list(
+        type = "pos",
[…]

### 2025-04-19 DeficiencyScreen/DeficiencyMapViewerFunctions.R

@@ -4,6 +4,16 @@ row.names(DfKey) = DfKey$Deficiency
 DfKey[DfKey$MLE == 0, "MLE"] = .05
 GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
 
+temp.DFKey = DfKey[, c("FBab..", "Deficiency", "Start", "End", "Chr", "Deficiency")]
+colnames(temp.DFKey) = c("FBgn", "Symbol", "Start", "End", "CHR", "Name")
+temp.DFKey$ensembl = ""
+temp.DFKey$CG = ""
+temp.DFKey$Strand = 0
+
+temp.DFKey = temp.DFKey[, colnames(GeneIDKey)]
+
+GeneIDKey = rbind(GeneIDKey, temp.DFKey)
+
 fbID = data.frame(FBgn = c(rep(GeneIDKey$FBgn, 2)),
                   Symbol = c(rep(GeneIDKey$Symbol, 2)),
                   Position = c(GeneIDKey$Start, GeneIDKey$End))
@@ -267,7 +277,7 @@ plot.gene = function(gene.symbol, start.range, end.range){
   fig = fig %>% add_lines(x = ~dfx,
                           y = ~dfy,
                           type = 'scatter',
-                          mode = "lines",
+                          mode = "lines + markers",
                           name = ~dfName,
                           showlegend = F,
                           fill = 'tozeroy',

### 2025-04-19 DeficiencyScreen/DeficiencyMapViewer/app.R
update

@@ -39,14 +39,14 @@ ui <- fluidPage(
                numericInput("start.range",
                             h5("Upstream Distance from TSS"),
                             min = 0,
-                            value = 1000000),),
+                            value = 100000),),
         
         ##Downstream from gene end
         column(6,
                numericInput("end.range",
                             h5("Downstream Distance from TES"),
                             min = 0,
-                            value = 1000000),),
+                            value = 100000),),
       ),
       ),
     
@@ -72,11 +72,10 @@ ui <- fluidPage(
                numericInput("end",
                             h5("End Position"),
                             min = 0,
-                            value = 15000000),),
+                            value = 14100000),),
       ),),
     
     actionButton("updatePlot", "Update Plot"),
-    
     
     width = 3),
     
@@ -90,20 +89,25 @@ ui <- fluidPage(
     ),),)
 
 
-
 # Define server logic required to draw a histogram ----
 server <- function(input, output, session) {
   
   
-  session$onFlushed(function() {
-    # Only trigger once to avoid infinite loops
-    isolate({
-      updateActionButton(session, "updatePlot", label = NULL, icon = NULL)
-      session$sendInputMessage("updatePlot", list(value = 1))
-    })
-  }, once = TRUE)
+  #session$onFlushed(function() {
+  #  # Only trigger once to avoid infinite loops
+  #  isolate({
+  #    updateActionButton(session, "updatePlot", label = NULL, icon = NULL)
+  #    session$sendInputMessage("updatePlot", list(value = 1))
+  #  })
+  #}, once = TRUE)
   
-  
+  #  session$onFlushed(function() {
+  #  isolate({
+  #    shinyjs::click("updatePlot")
+  #  })
+  #}, once = TRUE)
+
+    
   updateData <- eventReactive(input$updatePlot, {
     if (input$locfactor == "gene") {
       req(input$gene, input$start.range, input$end.range)
@@ -157,19 +161,15 @@ server <- function(input, output, session) {
   })
   
   
-  output$url <- renderUI({
-    req(input$gene)
-    tags$a(href = paste0("http://flybase.org/reports/", 
-                         GeneIDKey[GeneIDKey$Symbol == input$gene, "FBgn"]),
-           "FlyBase Gene Summary Page",
-           target = "_blank")
+  output$click <- renderPrint({
+    d <- event_data("plotly_click")
[…]

### 2025-04-19 DeficiencyScreen/DeficiencyMapViewerFunctions.R

@@ -3,7 +3,7 @@ DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.na
 row.names(DfKey) = DfKey$Deficiency
 DfKey[DfKey$MLE == 0, "MLE"] = .05
 GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
-
+GeneIDKey = GeneIDKey[-grep("_", GeneIDKey$Symbol),]
 temp.DFKey = DfKey[, c("FBab..", "Deficiency", "Start", "End", "Chr", "Deficiency")]
 colnames(temp.DFKey) = c("FBgn", "Symbol", "Start", "End", "CHR", "Name")
 temp.DFKey$ensembl = ""
@@ -17,6 +17,7 @@ GeneIDKey = rbind(GeneIDKey, temp.DFKey)
 fbID = data.frame(FBgn = c(rep(GeneIDKey$FBgn, 2)),
                   Symbol = c(rep(GeneIDKey$Symbol, 2)),
                   Position = c(GeneIDKey$Start, GeneIDKey$End))
+
 
 plot.pos = function(chr, start, end){
   goi = data.frame(Start = start,

### 2025-04-24 DeficiencyScreen/DeficiencyMapViewer/app.R
Russo Data update

@@ -65,17 +65,17 @@ ui <- fluidPage(
                numericInput("start",
                             h5("Start Position"),
                             min = 0,
-                            value = 14000000),),
+                            value = 12650000),),
         
         ##Downstream from gene end
         column(6,
                numericInput("end",
                             h5("End Position"),
                             min = 0,
-                            value = 14100000),),
+                            value = 12850000),),
       ),),
     
-    actionButton("updatePlot", "Update Plot"),
+    actionButton("updatePlot", "Show Genomic Region"),
     
     width = 3),
     
@@ -91,29 +91,14 @@ ui <- fluidPage(
 
 # Define server logic required to draw a histogram ----
 server <- function(input, output, session) {
-  
-  
-  #session$onFlushed(function() {
-  #  # Only trigger once to avoid infinite loops
-  #  isolate({
-  #    updateActionButton(session, "updatePlot", label = NULL, icon = NULL)
-  #    session$sendInputMessage("updatePlot", list(value = 1))
-  #  })
-  #}, once = TRUE)
-  
-  #  session$onFlushed(function() {
-  #  isolate({
-  #    shinyjs::click("updatePlot")
-  #  })
-  #}, once = TRUE)
 
-    
+
   updateData <- eventReactive(input$updatePlot, {
     if (input$locfactor == "gene") {
       req(input$gene, input$start.range, input$end.range)
       list(
         type = "gene",
-        gene = input$gene,
+        gene = strsplit(input$gene, split = " ")[[1]][1],
         start.range = input$start.range,
         end.range = input$end.range
       )
@@ -145,7 +130,7 @@ server <- function(input, output, session) {
     selectizeInput("gene",
                    label = h5("Gene Symbol"),
                    choices = NULL,   # No choices here
-                   selected = "Arc1",
+                   selected = "Atf6",
                    multiple = FALSE)
   })
   
@@ -154,9 +139,9 @@ server <- function(input, output, session) {
     updateSelectizeInput(
       session,
       inputId = "gene",
-      choices = sort(unique(GeneIDKey$Symbol)),
+      choices = sort(unique(paste0(GeneIDKey$Symbol, " (", GeneIDKey$FBgn, ")"))),
       server = TRUE,
-      selected = "Arc1"
+      selected = "Atf6 (FBgn0033010)"
     )
   })
   

### 2025-05-14 RussoPaper/20250314_RussoManuscript_Fig1Revisions.Rmd
update

@@
 
+library(kableExtra)
+
+std.colors = setNames(c('navy', "gold2", "turquoise4", "royalblue",
+                        'orange', "deeppink", "grey", "green4"),
+                      c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)",
+                        "G85R(cr)", "A4V", "A4V/X16", "A4V/G85R(cr)"))
+
+hex = function(color, alpha){
+  rgb2hex = color
+  i = 1
+  while(i <= length(color)){
+    rgbvals = col2rgb(color[i])
+    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+    i = i+1
+  }
+  return(rgb2hex)
+}
+
+```
+
+```{r echo = F}
+
 B = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Russo Fig 1 eclosion.csv")
+B.labels = c("w1118",
+             "WT(LoxP)", "G85R(hr)",
+             "WT(cr)", "G85R(cr)",
+             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
+             "A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")
+
+colnames(B) = B.labels
 
@@
 
-B.labels = c("w1118",
-             "WT(LoxP)", "G85R(hr)",
-             "WT(cr)", "G85R(cr)",
-             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
-             "A4V/A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")
-
 ```
@@
 barplot(height = mean.B,
-        ylim = c(0, 100),
+        ylim = c(0, 120),
         col = "black",
@@
         main = "Eclosion from the pupal case",
-        xaxt = "n")
+        xaxt = "n",
+        yaxt = "n")
 axis(side = 1,
@@
      line = 0,
-     labels = F,
-     xpd = T)
+     labels = T,
+     xpd = T,
+     las = 2)
+
 lines(x = c(-0.5,13.5),
@@
 
-#abline(h = 100, lty = 2, lwd = 3)
+lines(x = c(1.9,3.1),
+      y = c(105, 105),
+      lwd = 3)
+
+lines(x = c(1.9,1.9),
+      y = c(105, 102),
+      lwd = 3)
+lines(x = c(3.1, 3.1),
+      y = c(105, 40),
+      lwd = 3)
+
+text(x = 3.1,
+     y = 109,
+    labels = "*",
+    cex = 2)
+
+lines(x = c(4.3,9.1),
+      y = c(105, 105),
+      lwd = 3)
+
+lines(x = c(4.3,4.3),
+      y = c(105, 102),
+      lwd = 3)
+lines(x = c(5.5, 5.5),
+      y = c(105, 40),
+      lwd = 3)
+lines(x = c(6.7, 6.7),
+      y = c(105, 95),
+      lwd = 3)
+lines(x = c(9.1, 9.1),
+      y = c(105, 95),
+      lwd = 3)
+
+text(x = 5.5,
+     y = 109,
+    labels = "*",
+    cex = 2)
+
+lines(x = c(5.5,11.5),
+      y = c(116, 116),
+      lwd = 3)
+
+lines(x = c(5.5, 5.5),
+      y = c(116, 113),
+      lwd = 3)
+lines(x = c(10.3, 10.3),
+      y = c(116, 100),
+      lwd = 3)
+lines(x = c(11.5, 11.5),
+      y = c(116, 102),
+      lwd = 3)
+
+text(x = 10.3,
+     y = 120,
+    labels = "*",
+    cex = 2,
+    xpd = t)
+
+```
+
+```{r echo = F, include = F}
+
+#B.data = data.frame(Genotype = rep(B.labels[1], length(na.omit(B[,1]))),
+#                    Eclosion = na.omit(B[,1]))
+
+#i = 1
+#while(i <= ncol(B)){
+#  temp.B = data.frame(Genotype = rep(B.labels[i], length(na.omit(B[,i]))),
+#                      Eclosion = na.omit(B[,i]))
+#  B.data = rbind(B.data, temp.B)
+#  i = i+1
+#}
+
+#B.aov = aov(B.data$Eclosion~B.data$Genotype)
+
+#head(summary(B.aov))
+
+#head(TukeyHSD(B.aov))
+
+t.table = data.frame(Genotype1 = B.labels[1],
+                     Genotype2 = B.labels[2],
+                     pval = t.test(x = na.omit(B[,1]),
+                                   y = na.omit(B[,2]),
+                                   paired = F)[[3]])
+
+i=1
+while(i <= ncol(B)){
+  j = i+1
+  while(j <= ncol(B)){
+    if(length(unique(na.omit(B[,i]))) == 1 &
+       length(unique(na.omit(B[,j]))) == 1){
+      t.temp = data.frame(Genotype1 = B.labels[i],
+                          Genotype2 = B.labels[j],
+                          pval = 0)
+      j = j+1
+    }
+
+    if(!(length(unique(na.omit(B[,i]))) == 1 &
+         length(unique(na.omit(B[,j]))) == 1)){
+      t.temp = data.frame(Genotype1 = B.labels[i],
+                          Genotype2 = B.labels[j],
+                          pval = t.test(x = na.omit(B[,i]),
+                                        y = na.omit(B[,j]),
+                                        paired = F)[[3]])
+      t.table = rbind(t.table, t.temp)
+      j = j+1
+    }
+  }
+  i = i+1
+}
+
+t.stripe = t.table$pval <= .05
+#row.names(t.table) = c(1:nrow(t.table))
+
+knitr::kable(t.table,
+             caption = 'All t-tests for figure 1B eclosion data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F}
+
+target.pvals = t.table[c(13, 30, 34, 38, 40, 55, 59),]
+
+knitr::kable(target.pvals,
+             caption = 'All t-tests for figure 1B eclosion data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(target.pvals))[target.pvals$pval <= .05], bold = T, color = "black", background = "gold")
 
@@
 
-C.labels = c("w1118", "WT(CR)", "G85R", "A4V")
-
-hex = function(color, alpha){
-  rgbvals = col2rgb(color)
-  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
-  return(rgb2hex)
-}
+C.labels = c("w1118", "WT(cr)", "G85R(cr)", "A4V")
+C.cols = std.colors[C.labels]
 
@@
         cex.ticks = 2,
-        col = c(hex("navy", .25),
-                hex("skyblue", .25),
-                hex('orange', .25),
-                hex("deeppink", .25)),
+        col = hex(C.cols, .25),
         add = T, 
@@
        pch=21,
-       bg=c('navy',"skyblue", 'orange', "deeppink")[as.numeric(C$Genotype)])
+       bg=C.cols[C$Genotype])
 
@@
 
-D.labels = c("w1118", "WTLoxP", "G85R(HR)", "WT(CR)", "G85R", "A4V")
+D.labels = c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)", "G85R(cr)", "A4V")
+
+D.cols = std.colors[D.labels]
 
@@
         cex.ticks = 2,
-        col = c(hex("navy", .25),
-                hex("gold2", .25),
-                hex("turquoise4", .25),
-                hex("skyblue", .25),
-                hex('orange', .25),
-                hex("deeppink", .25)),
+        col = hex(D.cols, .25),
         add = T, 
@@
        pch=21,
-       bg=c('navy', "gold2", "turquoise4", 
-            "skyblue", 'orange', "deeppink")[as.numeric(D$Genotype)])
+       bg=D.cols[D$Genotype])
 
@@
 
-E.labels = c("w1118", "WTLoxP", "G85R(HR)", 
-             "WT(CR)", "G85R", "A4V",
-             "A4V/X16", "A4V/G85R")
+E.labels = c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)", "G85R(cr)", 
+             "A4V", "A4V/X16", "A4V/G85R(cr)")
+
+E.cols = std.colors[E.labels]
 
@@
 
-bar.colors = c(hex("navy", .75),
-                hex("gold2", .75),
-                hex("turquoise4", .75),
-                hex("skyblue", .75),
-                hex('orange', .75),
-                hex("deeppink", .75),
-                hex('grey', .75),
-                hex("darkgreen", .75))
+bar.colors = hex(E.cols, .75)
 
-border.colors = c('navy', "gold2", "turquoise4",
-                  "skyblue", 'orange', "deeppink", 
-                  "grey", "green4")
+border.colors = E.cols
 
@@
 
-text(x = tick.x[3],
-     y = (mean.E[3] + stderr.E[3]) + 5,
+lines(x = c(1.9,3.1),
+      y = c(63, 63),
+      lwd = 3)
+
+text(x = 2.5,
+     y = 66,
     labels = "*",
-    cex = 2)
+    cex = 2,
+    xpd = t)
 
 ```
+
+```{r echo = F}
+
+colnames(E) = E.labels
+
+t.fE = data.frame(Sample1 = E.labels[2],
+                  Sample2 = E.labels[3],
+                  pval = t.test(x = E[, E.labels[2]],
+                                  y = E[, E.labels[3]],
+                                  paired = F)[[3]])
+
+temp.t.fE = data.frame(Sample1 = E.labels[4],
+                       Sample2 = E.labels[5],
+                       pval = t.test(x = E[, E.labels[4]],
+                                     y = E[, E.labels[5]],
+                                     paired = F)[[3]])
+t.fE = rbind(t.fE, temp.t.fE)
+
+temp.t.fE = data.frame(Sample1 = E.labels[4],
+                       Sample2 = E.labels[6],
+                       pval = t.test(x = E[, E.labels[4]],
+                                     y = E[, E.labels[6]],
+                                     paired = F)[[3]])
+t.fE = rbind(t.fE, temp.t.fE)
+
+knitr::kable(t.fE,
+             caption = 'All t-tests for figure 1E larval locomotion data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.fE))[t.fE$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r include = F, echo = F, include = F}
+
+fig2ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 2AB.csv", header = T)
+fig2ab$Sample = paste(fig2ab$Genotype, paste(fig2ab$Sex, fig2ab$Day))
+
+fig2ab$Genotype[fig2ab$Genotype == "dSodWT"] = "WT(cr)"
+
+```
+
+```{r echo = F, fig.width=7.5}
+
+f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
+                 (fig2ab$Day == 3 |
+                  fig2ab$Day == 14 |
+                  fig2ab$Day == 20 |
+                  fig2ab$Day == 28 |
+                  fig2ab$Day == 35) &
+                  fig2ab$Genotype != 'w1118',]
+
+f.fig2ab = f.fig2ab[order(fig2ab$Day),]
+f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
+f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('WT(cr) 3', 'A4V 3',
+                                                     'WT(cr) 14', 'A4V 14',
+                                                     'WT(cr) 20', 'A4V 20',
+                                                     'WT(cr) 28', 'A4V 28',
+                                                     'WT(cr) 35', 'A4V 35'))
+f.fig2ab = na.omit(f.fig2ab)
+f.fig2ab$x = as.numeric(f.fig2ab$Sample)
+
+##put space between time points
+f.fig2ab$x[f.fig2ab$x > 8] = f.fig2ab$x[f.fig2ab$x > 8] + 1
+f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
+f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
+f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
+
+f2ab.cols = std.colors[c("WT(cr)", "A4V")]
+
+f.fig2ab$color = std.colors[f.fig2ab$Genotype]
+
+f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
+f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
+f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 20)
+f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
+                   0, -.15, .15, -.15, .15, 0,
+
+                   0, 0, .2, -.2, 0, 0,
+                   -.15, .15, 0, 0, -.15, .15,
+
+                   0, 0, -.15, .15, 0, 0,
+                   0, 0, -.25, .25, 0, 0,
+
+                   0, -.25, .25, 0, 0, 0,
+                   -.15, .15, 0, 0, 0, 0,
+
+                   0, -.25, .25, -.15, .15, 0,
+                   -.25, .25, 0, -.25, .25, 0)
+
+f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj
+
+```
+
+```{r echo = F}
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8, 10,11, 13,14),
+        xaxt = 'none',
+        xlab = "Day",
+        col = hex(f2ab.cols, .25),
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Female Climbing Velocity",
+        ylim = c(0,2))
+points(x = f.fig2ab$x,
+       y = f.fig2ab$Rate,
+       pch = 21,
+       bg = f.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5, 10.5, 13.5),
+     labels = c(3, 14, 20, 28, 35))
+
+legend('topright',
+       inset=c(-0.185,0),
+       legend = c('WT(cr)', 'A4V'), 
+       fill = f2ab.cols,
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+lines(x = c(1,2),
+      y = c(1.6, 1.6),
+      lwd = 1.5)
+
+text(x = 1.5,
+     y = 1.7,
+    labels = "*",
+    cex = 1.5,
+    xpd = t)
+
+lines(x = c(10,11),
+      y = c(1.4, 1.4),
+      lwd = 1.5)
+
+text(x = 10.5,
+     y = 1.5,
+    labels = "*",
+    cex = 1.5,
+    xpd = t)
+
+lines(x = c(13,14),
+      y = c(1.0, 1.0),
+      lwd = 1.5)
+
+text(x = 13.5,
+     y = 1.1,
+    labels = "*",
+    cex = 1.5,
+    xpd = t)
+
+```
+
+```{r echo = F}
+
+f2ab.labels = unique(f.fig2ab$Sample)
+t.f2ab = data.frame(Sample1 = f2ab.labels[1],
+                    Sample2 = f2ab.labels[2],
+                    pval = t.test(x = f.fig2ab[f.fig2ab$Sample == f2ab.labels[1], "Rate"],
+                                  y = f.fig2ab[f.fig2ab$Sample == f2ab.labels[2], "Rate"],
+                                  paired = F)[[3]])
+
+i=3
+while(i<=length(unique(f.fig2ab$Sample))){
+  temp = data.frame(Sample1 = f2ab.labels[i],
+                    Sample2 = f2ab.labels[i+1],
+                    pval = t.test(x = f.fig2ab[f.fig2ab$Sample == f2ab.labels[i], "Rate"],
+                                  y = f.fig2ab[f.fig2ab$Sample == f2ab.labels[i+1], "Rate"],
+                                  paired = F)[[3]])
+  t.f2ab = rbind(t.f2ab, temp)
+  i=i+2
+}
+
+knitr::kable(t.f2ab,
+             caption = 'All t-tests for figure 2a climbing data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.f2ab))[t.f2ab$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F, fig.width=7.5}
+
+m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
+                 (fig2ab$Day == 3 |
+                  fig2ab$Day == 7 |
+                  fig2ab$Day == 12 |
+                  fig2ab$Day == 16) &
+                  fig2ab$Genotype != 'w1118',]
+
+m.fig2ab = m.fig2ab[order(fig2ab$Day),]
+m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
+m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('WT(cr) 3', 'A4V 3',
+                                                     'WT(cr) 7', 'A4V 7',
+                                                     'WT(cr) 12', 'A4V 12',
+                                                     'WT(cr) 16', 'A4V 16'))
+m.fig2ab = na.omit(m.fig2ab)
+m.fig2ab$x = as.numeric(m.fig2ab$Sample)
+m.fig2ab$x[m.fig2ab$x > 6] = m.fig2ab$x[m.fig2ab$x > 6] + 1
+m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
+m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1
+
+m2ab.cols = std.colors[c("WT(cr)", "A4V")]
+
+m.fig2ab$color = std.colors[m.fig2ab$Genotype]
+
+m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
+m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
+m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
+m.fig2ab$x.adj = c(0, -.25, .25, 0, -.1, .1,
+                   0, -.25, .25, .0, -.1, .1,
+
+                   0, 0, -.1, .1, 0, 0,
+                   0, -.1, .1, 0, 0, 0,
+
+                   0, -.1, .1, 0, 0, 0,
+                   0, -.1, .1, 0, -.1, .1,
+
+                   0, -.25, 0, .25, .15, 0,
+                   0, -.25, 0, .25, -.15, .15)
+
+m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj
+
+```
+
+```{r echo = F}
+
+par(mar=c(5.1, 4.1, 4.1, 5.6))
+
+boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
+        at = c(1,2, 4,5, 7,8, 10,11),
+        xaxt = 'none',
+        xlab = "Day",
+        col = hex(m2ab.cols, .25),
+        ylab = 'Veloxicty (cm/sec)',
+        main = "Male Climbing Velocity",
+        ylim = c(0,3))
+points(x = m.fig2ab$x,
+       y = m.fig2ab$Rate,
+       pch = 21,
+       bg = m.fig2ab$color)
+axis(side = 1,
+     at = c(1.5, 4.5, 7.5, 10.5),
+     labels = c(3, 7, 12, 16))
+
+legend('topright',
+       inset=c(-0.185,0),
+       legend = c('WT(cr)', 'A4V'), 
+       fill = m2ab.cols,
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+lines(x = c(7,8),
+      y = c(2.7, 2.7),
+      lwd = 1.5)
+
+text(x = 7.5,
+     y = 2.8,
+    labels = "*",
+    cex = 1.5,
+    xpd = t)
+
+lines(x = c(10,11),
+      y = c(2.2, 2.2),
+      lwd = 1.5)
+
+text(x = 10.5,
+     y = 2.3,
+    labels = "*",
+    cex = 1.5,
+    xpd = t)
+
+```
+
+```{r echo = F}
+
+m2ab.labels = unique(m.fig2ab$Sample)
+t.m2ab = data.frame(Sample1 = m2ab.labels[1],
+                    Sample2 = m2ab.labels[2],
+                    pval = t.test(x = m.fig2ab[m.fig2ab$Sample == m2ab.labels[1], "Rate"],
+                                  y = m.fig2ab[m.fig2ab$Sample == m2ab.labels[2], "Rate"],
+                                  paired = F)[[3]])
+
+i=3
+while(i<=length(unique(m.fig2ab$Sample))){
+  temp = data.frame(Sample1 = m2ab.labels[i],
+                    Sample2 = m2ab.labels[i+1],
+                    pval = t.test(x = m.fig2ab[m.fig2ab$Sample == m2ab.labels[i], "Rate"],
+                                  y = m.fig2ab[m.fig2ab$Sample == m2ab.labels[i+1], "Rate"],
+                                  paired = F)[[3]])
+  t.m2ab = rbind(t.m2ab, temp)
+  i=i+2
+}
+
+knitr::kable(t.m2ab,
+             caption = 'All t-tests for figure 2b climbing data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.m2ab))[t.m2ab$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F}
+
+Aleah.1 = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Aleah G85R Pharate Sex Ratio Data.csv")
+
+mean.aleah1 = setNames(c(mean(Aleah.1$PercentM), mean(Aleah.1$PercentF), mean(Aleah.1$PercentU)),
+                       c("Male", "Female", "Indeterminate"))
+stderr.aleah1 = setNames(c(sd(Aleah.1$PercentM)/(sqrt(11)),
+                           sd(Aleah.1$PercentF)/(sqrt(11)),
+                           sd(Aleah.1$PercentU)/(sqrt(11))),
+                       c("Male", "Female", "Indeterminate"))
+
+par(mar = c(8,4,4,2), lwd = 3)
+
+barplot(height = mean.aleah1,
+        ylim = c(0, 100),
+        col = c("royalblue", "deeppink", "grey40"),
+        las = 1,
+        ylab = "Percent Total Pharates",
+        main = "G85R Pharate Sex Ratio",
+        border = "black")
+
+axis(side = 2,
+     at = c(0,20,40,60,80,100),
+     lwd = 3,
+     line = 0,
+     labels = T,
+     las = 2,
+     xpd = T)
+
+lines(x = c(0,3.75),
+     y = c(0,0),
+     lwd = 3,
+     xpd = T)
+
+i = 1
+while(i <= length(stderr.aleah1)){
+  lines(x = tick.x[c(i,i)],
+        y = c(mean.aleah1[i], (mean.aleah1[i] + stderr.aleah1[i])),
+        lwd = 3,
+        col = "black")
+
+  lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
+        y = c((mean.aleah1[i] + stderr.aleah1[i]), (mean.aleah1[i] + stderr.aleah1[i])),
+        lwd = 3,
+        col = "black")
+
+  i = i +1
+}
+
+```
+
+```{r echo = F}
+
+sum.aleah1 = setNames(c(sum(Aleah.1$Male), sum(Aleah.1$Female), sum(Aleah.1$Undetermined)),
+                      c("Males", "Females", "Indeterminate"))
+
+pie(sum.aleah1,
+    labels = c(paste0(names(mean.aleah1), " (", signif(mean.aleah1, 3), "%)")),
+    init.angle = -90,
+    col = c("royalblue", "deeppink", "grey60"),
+    edges = 300,
+    border = T,
+    lwd = 5)
+legend('topright',
+       inset=c(0,0),
+       legend = names(mean.aleah1), 
+       fill = c("royalblue", "deeppink", "grey60"),
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F}
+
+Aleah.2 = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Aleah G85R Larvae Sex Ratio Data.csv")
+
+mean.aleah2 = setNames(c(mean(na.omit(Aleah.2$G85R.M)), 
+                         mean(na.omit(Aleah.2$G85R.F)),
+                         mean(na.omit(Aleah.2$WT.M)), 
+                         mean(na.omit(Aleah.2$WT.F))),
+                       c("G85R Male", "G85R Female", "WT Male", "WT Female"))
+stderr.aleah2 = setNames(c(sd(na.omit(Aleah.2[,1]))/(length(na.omit(Aleah.2[,1]))),
+                           sd(na.omit(Aleah.2[,2]))/(length(na.omit(Aleah.2[,2]))),
+                           sd(na.omit(Aleah.2[,3]))/(length(na.omit(Aleah.2[,3]))),
+                           sd(na.omit(Aleah.2[,4]))/(length(na.omit(Aleah.2[,4])))),
+                         c("G85R Male", "G85R Female", "WT Male", "WT Female"))
+
+tick.x = c(1, 2.15, 3.9, 5.05)
+
+par(mar = c(4,4,4,2), lwd = 3)
+
+barplot(height = mean.aleah2,
+        ylim = c(0, 55),
+        col = c("royalblue", "deeppink", "royalblue", "deeppink"),
+        las = 1,
+        ylab = "Number of larvae",
+        main = "dSod1 third instar sex ratio",
+        border = "black",
+        xaxt = "n",
+        space = c(.5,.15,.75,.15))
+axis(side = 2,
+     at = c(0,10,20,30,40,50),
+     lwd = 3,
+     line = 0,
+     labels = T,
+     las = 2,
+     xpd = T)
+
+axis(side = 1,
+     at = c(1, 2.15, 3.9, 5.05),
+     lwd = 3,
+     line = 0,
+     labels = F,
+     las = 1,
+     xpd = T)
+
+axis(side = 1,
+     at = tick.x,
+     lwd = 0,
+     line = -0.25,
+     labels = c("Male", "Female", "Male", "Female"),
+     las = 1,
+     xpd = T)
+
+axis(side = 1,
+     at = c(1.55, 4.5),
+     lwd = 0,
+     line = .75,
+     labels = c("G85R", "WT"),
+     las = 1,
+     xpd = T)
+
+lines(x = c(0.25, 5.75),
+     y = c(0,0),
+     lwd = 3,
+     xpd = T)
+
+i = 1
+while(i <= length(stderr.aleah2)){
+  lines(x = tick.x[c(i,i)],
+        y = c(mean.aleah2[i], (mean.aleah2[i] + stderr.aleah2[i])),
+        lwd = 3,
+        col = "black")
+
+  lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
+        y = c((mean.aleah2[i] + stderr.aleah2[i]), (mean.aleah2[i] + stderr.aleah2[i])),
+        lwd = 3,
+        col = "black")
+
+  i = i +1
+}
+
+lines(x = c(1,2.15),
+      y = c(22, 22),
+      lwd = 2)
+
+text(x = 1.575,
+     y = 25,
+    labels = "ns",
+    cex = 1.5,
+    xpd = t)
+
+lines(x = c(3.9,5.05),
+      y = c(49, 49),
+      lwd = 2)
+
+text(x = 4.4525,
+     y = 52,
+    labels = "ns",
+    cex = 1.5,
+    xpd = t)
+
+```
+
+```{r echo = F}
+
+t.Aleah2 = data.frame(Sample1 = c("G85R.Males", "WT.Males"),
+                      Sample2 = c("G85R.Females", "WT.Females"),
+                      pval = c(t.test(x = na.omit(Aleah.2$G85R.M),
+                                      y = na.omit(Aleah.2$G85R.F),
+                                      paired = F)[[3]],
+                               t.test(x = na.omit(Aleah.2$WT.M),
+                                    y = na.omit(Aleah.2$WT.F),
+                                    paired = F)[[3]]))
+
+knitr::kable(t.Aleah2,
+             caption = "All t-tests for Aleah's larval sex ratio data.")  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.Aleah2))[t.Aleah2$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F, fig.width=10, fig.height=7}
+
+gbbEcl = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Ana_gbbEclosionData.csv")
+
+gbbEcl.labels = unique(gbbEcl$Genotype)
+
+gbbEcl.means = rep(0, length(gbbEcl.labels))
+
+i = 1
+while(i<=length(gbbEcl.labels)){
+  gbbEcl.means[i] = mean(gbbEcl$PercentEclosion[gbbEcl$Genotype == gbbEcl.labels[i]])
+  i = i+1
+}
+
+stderr.gbbEcl = setNames(c(sd(gbbEcl[gbbEcl==gbbEcl.labels[1],"PercentEclosion"])/4,
+                           sd(gbbEcl[gbbEcl==gbbEcl.labels[2],"PercentEclosion"])/4,
+                           sd(gbbEcl[gbbEcl==gbbEcl.labels[3],"PercentEclosion"])/4,
+                           sd(gbbEcl[gbbEcl==gbbEcl.labels[4],"PercentEclosion"])/4,
+                           sd(gbbEcl[gbbEcl==gbbEcl.labels[5],"PercentEclosion"])/4,
+                           sd(gbbEcl[gbbEcl==gbbEcl.labels[6],"PercentEclosion"])/4),
+                         gbbEcl.labels)
+
+par(mar = c(12,4,4,2))
+
+barplot(height = gbbEcl.means,
+        ylim = c(0, 120),
+        col = "black",
+        las = 2,
+        ylab = "Eclosion frequency (%)",
+        main = "Eclosion from the pupal case",
+        xaxt = "n",
+        yaxt = "n")
+axis(side = 1,
+     at = c(.7 + (c(0:5)*1.2)),
+     lwd = 3,
+     line = 0,
+     labels = gbbEcl.labels,
+     xpd = T,
+     las = 2)
+axis(side = 2,
+     at = c(0,20,40,60,80,100),
+     lwd = 3,
+     line = 0,
+     labels = T,
+     xpd = T,
+     las = 2)
+
+tick.x = c(.7 + (c(0:5)*1.2))
+
+i = 1
+while(i <= length(stderr.gbbEcl)){
+  if(stderr.gbbEcl[i] > 0){
+    lines(x = tick.x[c(i,i)],
+          y = c(gbbEcl.means[i], (gbbEcl.means[i] + stderr.gbbEcl[i])),
+          lwd = 3,
+          col = "black")
+
+    lines(x = c((tick.x[i] - .25), (tick.x[i] + .25)),
+          y = c((gbbEcl.means[i] + stderr.gbbEcl[i]), (gbbEcl.means[i] + stderr.gbbEcl[i])),
+          lwd = 3,
+          col = "black")  
+  }
+  i = i +1
+}
+
+```
+
+```{r echo = F, include = T, warning=F}
+
+##Running a Wilcoxon Rank Sum non parametric test for data that is not normally distributed
+
+t.table = data.frame(Genotype1 = "WT(LoxP/cr)",
+                     Genotype2 = "G85R(hr/cr)" ,
+                     pval = wilcox.test(x = gbbEcl[gbbEcl$Genotype == "WT(LoxP/cr)","PercentEclosion"],
+                                   y = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
+                                   paired = F)[[3]])
+
+ t.temp = data.frame(Genotype1 = "G85R(hr/cr)",
+                     Genotype2 = "OK371-gbb; G85R(hr/cr)",
+                     pval = wilcox.test(x = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
+                                        y = gbbEcl[gbbEcl$Genotype == "OK371-gbb; G85R(hr/cr)","PercentEclosion"],
+                                        paired = F)[[3]])
+t.table = rbind(t.table, t.temp)
+
+t.temp = data.frame(Genotype1 = "G85R(hr/cr)",
+                    Genotype2 = "OK371-SaxA; G85R(hr/cr)",
+                    pval = t.test(x = gbbEcl[gbbEcl$Genotype == "G85R(hr/cr)","PercentEclosion"],
+                                       y = gbbEcl[gbbEcl$Genotype == "OK371-SaxA; G85R(hr/cr)","PercentEclosion"],
+                                       paired = F)[[3]])
+t.table = rbind(t.table, t.temp)
+
+t.stripe = t.table$pval <= .05
+#row.names(t.table) = c(1:nrow(t.table))
+
+knitr::kable(t.table,
+             caption = 'All t-tests for figure 1B eclosion data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F}
+
+temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/UBLegMorphologyData.csv")
+
+temp$Genotype[temp$Genotype == "WT"] = "WT(cr)"
+temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr)"
+
+temp$Genotype = factor(temp$Genotype, levels = unique(temp$Genotype))
+
+morph.data = temp[,c(1:2,7:9,12:14)]
+
+sum.morph = setNames(apply(morph.data[,3:8], MARGIN = 1, sum), morph.data$Genotype)
+
+par(mar = c(5,7,5,2))
+
+plot(x = NA,
+     y = NA,
+     type = 'n',
+     ylim = c(0, 6),
+     xlim = c(.5, 2.5),
+     xaxt = "n",
+     ylab= "Morphology Score",
+     yaxt = "n",
+     xlab = NA,
+     frame = F,
+     main = "Leg Axon Morphology")
+
+grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)
+
+boxplot(sum.morph~temp$Genotype,
+        xlab="",
+        las = 2,
+        cex.axis = 1,
+        ylim = c(0, 6),
+        boxwex = .75,
+        boxlwd = 2,
+        lwd = 2,
+        cex.ticks = 2,
+        col = hex(std.colors[unique(temp$Genotype)], .25),
+        add = T, 
+        xaxt = "n",
+        yaxt = "n",
+        frame = F)
+
+  axis(side = 1,
+       at = c(1,2),
+       lwd = 3,
+       line = -.45,
+       labels = unique(temp$Genotype),
+       xpd = T)
+
+    lines(x = c(0.4, 2.5),
+       y = c(0,0),
+       lwd = 3,
+       xpd = T)
+
+pval = t.test(x = sum.morph[1:9],
+              y = sum.morph[10:18],
+              paired = F)[[3]]
+
+xpos = c(0, -.1, -.05, -.05, .1, -.2, .2, .05, .05,
+         0, -.1, .1, -.2, 0, .2, -.05, .05, 0) + as.numeric(temp$Genotype)
+
+points(x = xpos,
+       y = sum.morph,
+       cex = 2.25,
+       pch = 21,
+       bg= std.colors[temp$Genotype])
+
+      axis(side = 2,
+       at = c(0:6),
+       lwd = 3,
+       line = 0,
+       labels = T,
+       xpd = T,
+       las = 2)
+
+  text(x = 2.25,
+       y = 5.75,
+       label = paste0("pval = ", signif(pval, 3)))
+
+```

### 2025-05-14 RussoPaper/Prelim_UBLegMorphologyDataAnalysis.Rmd
update

---
title: "Jayden Stats Homework"
author: "John Santiago"
date: "2025-04-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, warning=FALSE, message=FALSE}

library(kableExtra)
library(gtools)
library(gplots)

temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/UBLegMorphologyData.csv")

temp$Genotype[temp$Genotype == "WT"] = "WT(cr)"
temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr)"

temp$Genotype = factor(temp$Genotype, levels = unique(temp$Genotype))

temp.titles = c("Is the leg short?",
                "Is there scrunching or curving?",
                "Is the axonal bundle straight?",
                "Does the axonal bundle split or are there chunks missing?",
                "Does the branching look organized?",
                "Is the branching following a pattern tiling?",
                "Is there branching in all aspects of the femur?",
                "Is the mitochonria in the entire axonal bundle?",
                "Do all branches have mitochondria?")

std.colors = setNames(c('navy', "gold2", "turquoise4", "royalblue",
                        'orange', "deeppink", "grey", "green4"),
                      c("w1118", "WT(LoxP)", "G85R(hr)", "WT(cr)",
                        "G85R(cr)", "A4V", "A4V/X16", "A4V/G85R(cr)"))

hex = function(color, alpha){
  rgb2hex = color
  i = 1
  while(i <= length(color)){
    rgbvals = col2rgb(color[i])
    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
    i = i+1
  }
  return(rgb2hex)
}

x.stagger.odd = c(0, -.1, .1, -.2, .2, -.3, .3, -.4, .4)
x.stagger.even = c(-.05, .05, -.15, .15, -.25, .25, -.35, .35)

```

```{r echo = F}
UB.barplot = function(i){
  ##bar temp data
  btd = temp[,i]

  WT = factor(temp[temp$Genotype == "WT(cr)", i], levels = c(0, 1))
  GR = factor(temp[temp$Genotype == "G85R(cr)", i], levels = c(0, 1))
  fish.data = table(WT,
                    GR)
  fish.data

  pval = as.numeric(fisher.test(fish.data)[1][1])

  bar.temp = data.frame(WT = c(length(btd[temp$Genotype == "WT(cr)" &
                                            btd == 0]),
                               length(btd[temp$Genotype == "WT(cr)" &
                                            btd == 1])),
                        GR = c(length(btd[temp$Genotype == "G85R(cr)" &
                                            btd == 0]),
                               length(btd[temp$Genotype == "G85R(cr)" &
                                            btd == 1])))

  bar.temp = as.matrix(bar.temp)
  btd.names = unique(temp$Genotype)

  opar <- par(lwd = 3)

  par(mar = c(3,4,4,5.5))

  plot(x = NA,
       y = NA,
       type = 'n',
       ylim = c(0, 10),
       xlim = c(1, 6),
       xaxt = "n",
       ylab= colnames(temp)[i],
       yaxt = "n",
       xlab = NA,
       frame = F,
       main = temp.titles[i-5])

  grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)

  barplot(height = bar.temp,
          ylim = c(0, 10),
          beside = T,
          col = "white",
          las = 2,
          ylab= colnames(temp)[i],
          main = colnames(temp)[i],
          xaxt = "n",
          yaxt = "n",
          add = T)

  barplot(height = bar.temp,
          ylim = c(0, 10),
          beside = T,
          col = hex(c("firebrick", "royalblue"), .5),
          las = 2,
          ylab= colnames(temp)[i],
          main = colnames(temp)[i],
          xaxt = "n",
          yaxt = "n",
          add = T)

  axis(side = 1,
       at = c(2,5),
       lwd = 0,
       line = -0.5,
       labels = btd.names,
       xpd = T)

  lines(x = c(.75, 6.25),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  axis(side = 2,
       at = c(0:10),
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = c(0, 5, 10),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  legend('topright',
         inset=c(-.15,0),
         legend = c("Yes", "No"), 
         fill = hex(c("firebrick", "royalblue"), .5),
         cex = 1,
         bty = 'n',
         pt.cex = 1,
         xpd = T)

  text(x = 6.35,
       y = 8.0,
      label = paste0("pval = ", signif(pval, 3)),
      xpd = T,
      adj = 0)
}

```

```{r echo = F}
i=5

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(400, 650),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= "Femur Length",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Femur Length")

axis(side = 1,
     at = c(1,2),
     lwd = 3,
     line = -.45,
     labels = unique(temp$Genotype),
     xpd = T)

lines(x = c(0.4, 2.5),
     y = c(400,400),
     lwd = 3,
     xpd = T)

axis(side = 2,
     at = c(400, 450, 500, 550, 600, 650),
     lwd = 3,
     line = 0,
     labels = T,
     las = 2,
     xpd = T)

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(400, 650),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)
points(x = as.numeric(temp$Genotype),
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=6

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

axis(side = 1,
     at = c(1,2),
     lwd = 3,
     line = -.9,
     labels = unique(temp$Genotype),
     xpd = T)

lines(x = c(0.5, 2.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

axis(side = 2,
     at = c(0, .5, 1),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

```

```{r echo = F, warning=F}

i = 6

UB.barplot(i)

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=7

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 7

UB.barplot(i)

```

```{r echo = F}

i=15

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0.5, 2.5),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Leg Length (Total)")

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0.5, 2.5),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 2

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0.5,0.5),
       lwd = 3,
       xpd = T)

      axis(side = 2,
       at = c(0.5, 1, 1.5, 2, 2.5),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 2.5,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=9

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 8

UB.barplot(i)

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=10

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 9

UB.barplot(i)

```

```{r echo = F}

i=16

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.5, 2.5),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Axonal Bundle (Total)")

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.5, 2.5),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0
twos = temp[,i] == 2

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

if(odd(length(xpos[twos & xpos == 1]))){
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.odd[1:length(xpos[twos & xpos == 1])]
}else{
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.even[1:length(xpos[twos & xpos == 1])]  
}

if(odd(length(xpos[twos & xpos == 2]))){
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.odd[1:length(xpos[twos & xpos == 2])]
}else{
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.even[1:length(xpos[twos & xpos == 2])] 
}

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(-0.5,-0.5),
       lwd = 3,
       xpd = T)

      axis(side = 2,
       at = c(-0.5, 0, 0.5, 1, 1.5, 2, 2.5),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 2.5,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F, warning=F}

i = 10

UB.barplot(i)

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=11

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 11

UB.barplot(i)

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=12

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 12

UB.barplot(i)

```

```{r echo = F}

i=17

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0.5, 3.5),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Axonal Branching (Total)")

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0.5, 3.5),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 3
twos = temp[,i] == 2

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

if(odd(length(xpos[twos & xpos == 1]))){
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.odd[1:length(xpos[twos & xpos == 1])]
}else{
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.even[1:length(xpos[twos & xpos == 1])]  
}

if(odd(length(xpos[twos & xpos == 2]))){
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.odd[1:length(xpos[twos & xpos == 2])]
}else{
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.even[1:length(xpos[twos & xpos == 2])] 
}

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0.5,0.5),
       lwd = 3,
       xpd = T)

      axis(side = 2,
       at = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 3.5,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=13

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 13

UB.barplot(i)

```

```{r echo = F, fig.width=10, fig.height=7, include = F}
i=14

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.25, 1.25),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = colnames(temp)[i])

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.25, 1.25),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

```

```{r echo = F, warning=F}

i = 14

UB.barplot(i)

```

```{r echo = F}

i=18

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(-0.5, 2.5),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Mitochondria (Total)")

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(-0.5, 2.5),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0
twos = temp[,i] == 2

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

if(odd(length(xpos[twos & xpos == 1]))){
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.odd[1:length(xpos[twos & xpos == 1])]
}else{
  xpos[twos & xpos == 1] = xpos[twos & xpos == 1] + x.stagger.even[1:length(xpos[twos & xpos == 1])]  
}

if(odd(length(xpos[twos & xpos == 2]))){
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.odd[1:length(xpos[twos & xpos == 2])]
}else{
  xpos[twos & xpos == 2] = xpos[twos & xpos == 2] + x.stagger.even[1:length(xpos[twos & xpos == 2])] 
}

if(odd(length(xpos[ones & xpos == 1]))){
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.odd[1:length(xpos[ones & xpos == 1])]
}else{
  xpos[ones & xpos == 1] = xpos[ones & xpos == 1] + x.stagger.even[1:length(xpos[ones & xpos == 1])]  
}

if(odd(length(xpos[ones & xpos == 2]))){
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.odd[1:length(xpos[ones & xpos == 2])]
}else{
  xpos[ones & xpos == 2] = xpos[ones & xpos == 2] + x.stagger.even[1:length(xpos[ones & xpos == 2])] 
}

if(odd(length(xpos[zeros & xpos == 1]))){
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.odd[1:length(xpos[zeros & xpos == 1])]
}else{
  xpos[zeros & xpos == 1] = xpos[zeros & xpos == 1] + x.stagger.even[1:length(xpos[zeros & xpos == 1])]  
}

if(odd(length(xpos[zeros & xpos == 2]))){
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.odd[1:length(xpos[zeros & xpos == 2])]
}else{
  xpos[zeros & xpos == 2] = xpos[zeros & xpos == 2] + x.stagger.even[1:length(xpos[zeros & xpos == 2])] 
}

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(-0.5,-0.5),
       lwd = 3,
       xpd = T)

      axis(side = 2,
       at = c(-0.5, 0, 0.5, 1, 1.5, 2, 2.5),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 2.5,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F}

i=19

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 10),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Overall Morphology Score")

grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 10),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

xpos = as.numeric(temp$Genotype)
ones = temp[,i] == 1
zeros = temp[,i] == 0
twos = temp[,i] == 2

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

xpos = c(-.05, -.05, -.05, .05, .05, -.15, .15, 0, .05,
         0, -.05, -.05, .05, 0, .05, -.05, .05, 0) + as.numeric(temp$Genotype)

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

      axis(side = 2,
       at = c(0, 5, 10),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 9.5,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F}

i=20

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 4),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= colnames(temp)[i],
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Supervised Morphology Score\n(Axonal Bundle and Mitochondria)")

grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)

boxplot(temp[,i]~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 4),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

pval = t.test(x = temp[1:9, i],
              y = temp[10:18, i],
              paired = F)[[3]]

xpos = c(0, -.1, 0, .1, -.1, .1, -.2, 0, .2,
         -.05, .05, -.15, -.05, -.05, .15, 0, .05, .05) + as.numeric(temp$Genotype)

points(x = xpos,
       y = temp[,i],
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

      axis(side = 2,
       at = c(0:4),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 3.75,
       label = paste0("pval = ", signif(pval, 3)))

```

```{r echo = F, include = F}

heat.data = temp[,6:14]
row.names(heat.data) = paste0(temp$Genotype,temp$Animal..)
heat.data = as.matrix(t(heat.data))

heat.colors = colorRampPalette(c("firebrick", "deepskyblue"))
sample.colors = c(rep("darkgreen", 9), rep("gold2", 9))
category.colors = c(rep("darkgreen", 2), 
                    rep("navy", 2),
                    rep("deeppink", 3), 
                    rep("gold2", 2))

heatmap.2(heat.data,
          Colv = T,
          Rowv = T,
          margins = c(7, 15),
          trace = "none",
          ColSideColors = sample.colors,
          RowSideColors = category.colors,
          col = heat.colors)
```

```{r echo = F}

# Assume:
# - data_matrix: 18 x 9 matrix
# - group_labels: factor of length 18 with two levels (e.g., "WT", "KO")

find_best_category_combos <- function(data_matrix, group_labels, max_k = 9) {
  n_categories <- ncol(data_matrix)
  category_names <- colnames(data_matrix)

  results <- list()

  for (k in 1:max_k) {
    combs <- combn(n_categories, k, simplify = FALSE)
    for (combo in combs) {
      summed <- rowSums(data_matrix[, combo, drop = FALSE])
      test <- t.test(summed ~ group_labels)
      results[[paste(combo, collapse = ",")]] <- list(
        categories = category_names[combo],
        mean_diff = abs(diff(tapply(summed, group_labels, mean))),
        p_value = test$p.value
      )
    }
  }

  # Convert to data frame
  results_df <- do.call(rbind, lapply(results, as.data.frame))
  results_df$combo <- rownames(results_df)
  results_df <- results_df[order(results_df$p_value), ]
  return(results_df)
}

```

```{r echo = F, warning=F}

data_matrix = t(heat.data)
group_labels = temp$Genotype

temp.combos = find_best_category_combos(data_matrix, group_labels, max_k = 9)

row.names(temp.combos) = c(1:nrow(temp.combos))

best.combo = data_matrix[,c(2,3,4,7,8)]

sum.best.combo = apply(best.combo, MARGIN = 1, sum)

best.pval = t.test(sum.best.combo[1:9], sum.best.combo[10:18])[[3]]

supervised.combo = temp.combos[temp.combos$combo == "3,4,8,9.1",]

```

```{r echo = F}

par(mar = c(5,7,5,2))

plot(x = NA,
     y = NA,
     type = 'n',
     ylim = c(0, 5),
     xlim = c(.5, 2.5),
     xaxt = "n",
     ylab= "Morphology Score",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = "Most Significantly Different Combination of Traits")

grid(nx=NA, ny=NULL, col = "grey50", lwd = .75)

boxplot(sum.best.combo~temp$Genotype,
        xlab="",
        las = 2,
        cex.axis = 1,
        ylim = c(0, 5),
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        col = hex(std.colors[unique(temp$Genotype)], .25),
        add = T, 
        xaxt = "n",
        yaxt = "n",
        frame = F)

  axis(side = 1,
       at = c(1,2),
       lwd = 3,
       line = -.45,
       labels = unique(temp$Genotype),
       xpd = T)

    lines(x = c(0.4, 2.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

pval = t.test(x = sum.best.combo[1:9],
              y = sum.best.combo[10:18],
              paired = F)[[3]]

xpos = c(-.05, 0, -.1, -.1, .05, -.1, .1, .1, .1,
         -.05, 0, -.1, .1, 0, .05, -.2, .2, 0) + as.numeric(temp$Genotype)

points(x = xpos,
       y = sum.best.combo,
       cex = 2.25,
       pch = 21,
       bg= std.colors[temp$Genotype])

      axis(side = 2,
       at = c(0:5),
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  text(x = 2.25,
       y = 4.75,
       label = paste0("pval = ", signif(pval, 3)))

```

### 2025-05-14 Shortcuts_OmicsQuickPlotFunctions.Rmd
update
updated files
Updated Russo Data
updated general data files for app
Russo Data update

@@
 
-ID = "gbb"
+ID = "Zw"
 
 plot.G85R(ID)
+G85R.FC[GeneIDKey[GeneIDKey$Symbol == ID, "FBgn"],]
+G85R.FDR[GeneIDKey[GeneIDKey$Symbol == ID, "FBgn"],]
 
@@
 
-ID = "Arc1"
+ID = "FBgn0000635"
 
@@
 
-metabID = 'NADH'
+metabID = "NADPH"
 
@@
 
-gene.name = "gbb"
+gene.name = "Sod1"
 
@@
 
-heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")
+heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv")
 
 serpe.heatmap(heat.genes)
+
+```
+
+```{r echo = F, fig.width=16, fig.height=10}
+
+## Plot expression of a gene set from Single Cell RNAseq experiment
+## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)
+
+heat.genes = c("gbb", "dpp", "wit", "Mad", "put", "sax", "tkv", "mav", "babo", "Smox")
+
+serpe.heatmap.noman(heat.genes)
 

### 2025-06-13 DeficiencyScreen/Prelim_Analysis.Rmd
updated df data

---
title: "Defficiency Screen Functional Analysis"
author: "John Santiago"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(rgl)
knitr::opts_chunk$set(echo = FALSE, fig.align="center")
knitr::knit_hooks$set(webgl = hook_webgl)
```

```{r echo = F, include=F}
##Load Libraries

library(org.Dm.eg.db)
##library(goseq)
library(rrvgo)
library(plotly)
```

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"

DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.names = 1)
old = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)

GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)

dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250602_UpdatedModiferData.csv"))
row.names(dfdata) = dfdata$Fbab
dfgenes = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/GenesInDeficiency.csv"))

fulldf = cbind(dfgenes, dfdata[dfgenes$FBab,])
row.names(fulldf) = 1:nrow(fulldf)
fulldf$Modifier[fulldf$Modifier ==  "Supressor"] = "Suppressor"
fulldf$Modifier[fulldf$Modifier ==  "No effect"] = "No Effect"
new=fulldf

olddf = DfKey$Deficiency
newdf = unique(new$Deficiency)
oldfb = old$FBgn
newfb = unique(new$FBgn)
oldsym = old$Symbol
newsym = unique(new$Symbol)

#old = cbind(old, GeneIDKey[row.names(old), c("Start", "End", "CHR")])
old = GeneIDKey[, c("FBgn", "Start", "End", "CHR")]

old.left = apply(old[,c("Start", "End")], MARGIN = 1, min)
old.right = apply(old[,c("Start", "End")], MARGIN = 1, max)
Df.left = apply(DfKey[,c("Start", "End")], MARGIN = 1, min)
Df.right = apply(DfKey[,c("Start", "End")], MARGIN = 1, max)

genesinolddf = list()
i=1
while(i <= nrow(DfKey)){
  temp = na.omit(old[((old.left <= Df.left[i] & old.right >= Df.right[i]) |
           (old.left >= Df.left[i] & old.left <= Df.right[i]) |
           (old.right >= Df.left[i] & old.right <= Df.right[i])) &
            old$CHR == DfKey$Chr[i],])

  genesinolddf[[DfKey$Deficiency[i]]] = temp$FBgn
  i=i+1
}

#new.loc = GeneIDKey[new$FBgn,c("Start","End","CHR")]
new.loc = GeneIDKey[,c("FBgn", "Start","End","CHR")]
new.left = apply(new.loc[,c("Start", "End")], MARGIN = 1, min)
new.right = apply(new.loc[,c("Start", "End")], MARGIN = 1, max)
newDf.left = apply(new[,c("Start", "End")], MARGIN = 1, min)
newDf.right = apply(new[,c("Start", "End")], MARGIN = 1, max)

new.keep = !duplicated(paste0(new$Deficiency, newDf.left, newDf.right))
newDf.left = newDf.left[new.keep]
newDf.right = newDf.right[new.keep]
newDf = new$Deficiency[new.keep]
newChr = new$Chr[new.keep]

genesinnewdf = list()
i=1
while(i <= length(newDf)){
      temp = na.omit(new.loc[((new.left <= newDf.left[i] & new.right >= newDf.right[i]) |
           (new.left >= newDf.left[i] & new.left <= newDf.right[i]) |
           (new.right >= newDf.left[i] & new.right <= newDf.right[i])) &
            new.loc$CHR == newChr[i],])

    genesinnewdf[[newDf[i]]] = temp$FBgn
  i=i+1
}

```

```{r echo = F}

newdfonly = setdiff(newdf, olddf)
olddfonly = setdiff(olddf, newdf)

newfbonly = setdiff(newfb, oldfb)
oldfbonly = setdiff(oldfb, newfb)

newsymonly = setdiff(newsym, oldsym)
oldsymonly = setdiff(oldsym, newsym)

fbinnewdfonly = unique(fulldf[fulldf$Deficiency %in% newdfonly, "FBgn"])
fbinolddfonly = unique(unlist(genesinolddf[olddfonly]))

```

```{r echo = F}

  ##Sample titles as strings. Only fill in up to your number of selected categories
  set1 = "all old FBgn"
  set2 = "all new FBgn"
  set3 = "FBgn in Old Unique Df"
  set4 = "FBgn in New Unique Df"

  ##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
  s1 = oldfb
  s2 = newfb
  s3 = fbinolddfonly
  s4 = fbinnewdfonly

  main = ""

  grid.newpage()
  tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

```

```{r echo = F}
##kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
##kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)

Moderate.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv"), row.names = 1)
Strong.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongGOAnalysis.csv"), row.names = 1)
Repress.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv"), row.names = 1)
Lethal.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalGOAnalysis.csv"), row.names = 1)
Enhancer.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv"), row.names = 1)

genesingo=as.list(org.Dm.egGO2ALLEGS)

```

```{r echo = F}

##dfbar = data.frame(Enhancer = c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),
##                   NoEffect = c(DfKey[DfKey$Modifier == "No Effect",], dfdata[dfdata$Modifier == "No Effect",]),
##                   Lethal = c(DfKey[DfKey$Modifier == "Lethal",], dfdata[dfdata$Modifier == "Lethal",]),
##                   c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),
##                   Moderate = c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),)

#old = hist(as.numeric(DfKey$MLE))
#new = hist(as.numeric(dfdata$MLE))

hex = function(color, alpha){
  rgb2hex = color
  i = 1
  while(i <= length(color)){
    rgbvals = col2rgb(color[i])
    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
    i = i+1
  }
  return(rgb2hex)
}

```

```{r echo = F, warning=F}

hist(na.omit(as.numeric(dfdata$MLE)), col = hex('yellow', .25),
     breaks = seq(-4, 7, by = 1),
     xlab = "MLE",
     main = "Old Df MLE data vs New")
hist(na.omit(as.numeric(DfKey$MLE)), add = T, col = hex('blue', .2),
     breaks = seq(-4, 7, by = 1))
legend("topright", legend = c("old data", "new data"), fill = c("blue", "yellow"))
```

```{r include=F, echo=F}

sigs = unique(fulldf[fulldf$Modifier == "Enhancer", "Symbol"])
genes = setNames(rep(0, length(unique(fulldf$Symbol))), unique(fulldf$Symbol))
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")

GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
Enhancer.GO = GO.wall
##write.csv(Suppressor.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/SupressorGOAnalysis.csv")

  ##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")

##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Repress.KEGG = KEGG
##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/RepressorKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Moderate == 1 , "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")

##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Moderate.GO = GO.wall
##write.csv(Moderate.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv")

  ##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")

##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Moderate.KEGG = KEGG
##write.csv(Moderate.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Strong == 1 , "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")

##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Strong.GO = GO.wall
##write.csv(Strong.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongGOAnalysis.csv")

  ##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")

##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Strong.KEGG = KEGG
##write.csv(Strong.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")

##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Lethal.GO = GO.wall
##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalGOAnalysis.csv")

  ##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")

##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Lethal.KEGG = KEGG
##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")

##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Enhance.GO = GO.wall
##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv")

  ##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")

##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Enhance.KEGG = KEGG
##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerKEGGAnalysis.csv")

```

```{r echo = F, include =F}

GO20 = function(GO.data, GO.ontology){
GO.data = GO.data[GO.data$ontology == GO.ontology,
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

  return(fig)
}

```

```{r echo = F, include =F}

GO.data = Enhancer.GO
GO.ontology = "BP"
GOBP.fig = GO20(GO.data, GO.ontology)

GO.ontology = "CC"
GOCC.fig = GO20(GO.data, GO.ontology)

GO.ontology = "MF"
GOMF.fig = GO20(GO.data, GO.ontology)

```

```{r, fig.width= 10}

GOBP.fig

```

```{r, fig.width= 10}

GOCC.fig

```

```{r, fig.width= 10}

GOMF.fig

```

```{r include=F, echo=F}

GO.data = Enhancer.GO
GO.ontology = "BP"

go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont=GO.ontology,
                                method="Rel")

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")

```

```{r fig.height=7, fig.width=10}

heatmapPlot(simMatrix,
            reducedTerms,
            annotateParent=TRUE,
            annotationLabel="parentTerm",
            fontsize=6,
            main = "Repressor Gene Enriched Biological Process GO terms")

```

```{r}

scatterPlot(simMatrix, reducedTerms)

```

```{r, fig.width=10}
 use.data   = simMatrix
    pca <- prcomp(t(use.data), scale.=TRUE) 
    pc1=scale(pca$x[,1])
    pc2=scale(pca$x[,2])
    eigs <- pca$sdev^2
    ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(PC1=pc1,
                        PC2=pc2,
                        sdev=pca$sdev,
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group = reducedTerms[row.names(use.data), "parentTerm"],
                        Score = reducedTerms[row.names(use.data), "score"],
                        Term = reducedTerms[row.names(use.data), "term"],
                        TotalDE = GO.data[row.names(use.data), "numDEInCat"],
                        Total = GO.data[row.names(use.data), "numInCat"],
                        SigVal = signif(GO.data[row.names(use.data), "adjp"],3))

    pca.data$Group = factor(pca.data$Group, levels = unique(pca.data$Group))
    pca.data$Score = 20*(1+pca.data$Score/mean(pca.data$Score))

  fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 ##symbol = ~Group,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c("firebrick","gold","deepskyblue"),
                 marker = list(size = pca.data$Score,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Term, 
                                   "\nTotal DE: ", pca.data$TotalDE, 
                                   "\nTotal in Cat.: ", pca.data$Total, 
                                   "\nFDR: ", pca.data$SigVal)) %>%
    layout(xaxis = list(title = paste0("PC1", "(", ve[1], "%)")),
           yaxis = list(title = paste0("PC2", "(", ve[2], "%)")),
           title = "Enriched GO term similarity")

  fig

```

```{r fig.align='left'}

treemapPlot(reducedTerms)

```

```{r include = F, echo = F}

GOID = "0006334"
GenesInGO = genesingo[paste0("GO:", GOID)]

GenesInGO = Df.data[Df.data$ensembl %in% GenesInGO[[1]],]

```

```{r}

go2gene = setNames(list(as.character(genesingo[[1]])), names(genesingo)[1])
i=2
while(i<=length(genesingo)){
  temp = setNames(list(as.character(genesingo[[i]])), names(genesingo)[i])
  go2gene = c(go2gene, temp)
  i=i+1
}

```

### 2025-06-13 Python/DeficiencyData/Genes.py

@@ -1,118 +1,0 @@
-#5.25.23
-
-#Versions
-#Python 3.9.5
-#Pandas 1.3.2
-#Et-xml-file 1.1.0
-#Requests 2.26.0
-
-#Sources
-#https://python-reference.readthedocs.io/en/latest/intro.html
-#https://docs.python.org/3.11/index.html
-#https://docs.python-guide.org/scenarios/scrape/
-#https://pandas.pydata.org/docs/getting_started/index.html 
-#https://requests.readthedocs.io/en/latest/
-#https://flybase.github.io/docs/api/
-
-#Imports
-import pandas as pd
-
-import xml.etree.ElementTree as ET
-import requests
-import time as time
-
-#Initialize variables
-
-#Read in an Excel file of deficencies to analyze
-#The file should contain a list of deficencies formatted as FBab using https://flybase.org/convert/id
-flies = pd.read_excel("/Users/johncsantiago/Documents/GitHub/WhartonLab/Python/DeficiencyData/renewapp/AllModifiers.xlsx", header=None)
-
-#Number of deficencies
-rows = len(flies.index)
-
-#List of FBgns
-genesFBgn = []
-
-#List of gene names
-genesName = []
-
-#List of df for gene names
-genesdf = []
-
-#List of deficencies
-dfs = []
-
-#Initialize the list of deficencies ignoring empty cells
-for i in range(rows):
-    if str(flies.iat[i, 0]) != "nan" and str(flies.iat[i, 0]) != "":
-        dfs.append(flies.iat[i, 0])
-
-#Main for loop to make call to the API and extract data  
-for df in dfs:
-    names = []
-    FBgns = []
-    currentdf = []
-
-    #Call to Flybase API
-    request = requests.get("https://api.flybase.org/api/v1.0/chadoxml/"+str(df))
-    
-    #Import XML Data
-    root = ET.fromstring(request.content)
-
-    #Traversing the XML tree
-    relationships = root.findall("./feature/feature_relationship")
-    for relationship in relationships:
-
-        #Check if relationship is a gene disrupted by deficiency (derived_computed_affected_gene)
-        isgene = False
-
-        for type_id in relationship:
-            if type_id.tag=="type_id":
-                 for cvterm in type_id:
-                    if cvterm.tag=="cvterm":
-                        for name in cvterm:
-                            if name.tag == "name":
-                                if name.text == "derived_computed_affected_gene":
-                                    isgene = True
-
-        #Traverse XML Tree and obtain FBgn and Name
[…]

### 2025-06-13 Python/LarvalLocomotion/PreliminaryCode/analyze_video.py

@@ -1,90 +1,0 @@
-import cv2
-import csv
-import random
-
-# Parameters
-video_path = "./Converted/output_video.mp4"
-bbox_size = 20  # Width and height of each tracking box
-points = []
-
-# Mouse callback to collect click coordinates
-def click_event(event, x, y, flags, param):
-    if event == cv2.EVENT_LBUTTONDOWN:
-        points.append((x, y))
-        cv2.circle(frame_copy, (x, y), 3, (0, 255, 0), -1)
-        cv2.rectangle(frame_copy,
-                      (x - bbox_size // 2, y - bbox_size // 2),
-                      (x + bbox_size // 2, y + bbox_size // 2),
-                      (0, 255, 0), 1)
-        cv2.imshow("Click to Select Objects", frame_copy)
-
-# Load video and first frame
-cap = cv2.VideoCapture(video_path)
-ret, frame = cap.read()
-if not ret:
-    print("Failed to read video")
-    cap.release()
-    exit()
-
-# Let user click objects
-frame_copy = frame.copy()
-cv2.imshow("Click to Select Objects", frame_copy)
-cv2.setMouseCallback("Click to Select Objects", click_event)
-print("Click on each object you want to track, then press any key...")
-
-cv2.waitKey(0)
-cv2.destroyAllWindows()
-
-# Create bounding boxes from click points
-bboxes = [(x - bbox_size // 2, y - bbox_size // 2, bbox_size, bbox_size) for (x, y) in points]
-
-# Create a tracker for each bounding box
-trackers = []
-colors = []  # Store color for each object
-
-for bbox in bboxes:
-    tracker = cv2.TrackerCSRT_create()
-    tracker.init(frame, tuple(bbox))
-    trackers.append(tracker)
-
-    # Assign a random color for each object
-    color = [random.randint(0, 255) for _ in range(3)]  # Random RGB color
-    colors.append(color)
-
-# Open CSV to write tracking data
-with open('tracked_coordinates_click.csv', mode='w', newline='') as file:
-    writer = csv.writer(file)
-    writer.writerow(["Frame", "ObjectID", "X", "Y", "Width", "Height"])
-
-    frame_count = 0
-    while True:
-        ret, frame = cap.read()
-        if not ret:
-            break
-        frame_count += 1
-
-        # Add frame number in the top-right corner
[…]

### 2025-06-13 DeficiencyScreen/Prelim_Analysis.Rmd
fixed Df location on 2

@@
 
-DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"), row.names = 1)
-old = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
+##DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"))
+##colnames(DfKey)[c(1,3)] = c("BDSC", "FBab")
+##DfKey$FollowUp = "FALSE"
+##DfKey$Excluded = "FALSE"
 
-GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
+#old.dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names)
 
-dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250602_UpdatedModiferData.csv"))
-row.names(dfdata) = dfdata$Fbab
-dfgenes = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/GenesInDeficiency.csv"))
+##GeneIDKey = read.csv(paste0(git.dir,"GeneralDataFiles/GeneIDKey.csv"),row.names = 1)
 
-fulldf = cbind(dfgenes, dfdata[dfgenes$FBab,])
-row.names(fulldf) = 1:nrow(fulldf)
-fulldf$Modifier[fulldf$Modifier ==  "Supressor"] = "Suppressor"
-fulldf$Modifier[fulldf$Modifier ==  "No effect"] = "No Effect"
-new=fulldf
+##dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250602_UpdatedModiferData.csv"))
+##colnames(dfdata)[3] = "FBab"
+##dfdata$Excluded = "FALSE"
 
-olddf = DfKey$Deficiency
-newdf = unique(new$Deficiency)
-oldfb = old$FBgn
-newfb = unique(new$FBgn)
-oldsym = old$Symbol
-newsym = unique(new$Symbol)
+##DfKey[DfKey$FBab %in% setdiff(DfKey$FBab, dfdata$FBab), "Excluded"] = "TRUE"
 
-#old = cbind(old, GeneIDKey[row.names(old), c("Start", "End", "CHR")])
-old = GeneIDKey[, c("FBgn", "Start", "End", "CHR")]
+##fullDfKey = rbind(dfdata, DfKey[DfKey$Excluded == TRUE, colnames(dfdata)])
 
-old.left = apply(old[,c("Start", "End")], MARGIN = 1, min)
-old.right = apply(old[,c("Start", "End")], MARGIN = 1, max)
-Df.left = apply(DfKey[,c("Start", "End")], MARGIN = 1, min)
-Df.right = apply(DfKey[,c("Start", "End")], MARGIN = 1, max)
+##fullDfKey$Modifier[fullDfKey$Modifier == "No effect"] = "No Effect"
 
-genesinolddf = list()
+##fullDfKey$Modifier[fullDfKey$Modifier == "Supressor"] = "Suppressor"
+
+##fullDfKey$Modifier[fullDfKey$Modifier == "Strong Suppressor"] = "Suppressor"
+
+##changed start location for FBab0002465
+###was listed as 1 but on Flybase it listed a different start site
+
+##write.csv(fullDfKey, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/20250613_FullDfData.csv")
+
+##dfgenes = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/GenesInDeficiency.csv"))
+
+##fulldf = cbind(dfgenes, dfdata[dfgenes$FBab,])
+##row.names(fulldf) = 1:nrow(fulldf)
+##fulldf$Modifier[fulldf$Modifier ==  "Supressor"] = "Suppressor"
+##fulldf$Modifier[fulldf$Modifier ==  "No effect"] = "No Effect"
+##new=fulldf
+
+##olddf = DfKey$Deficiency
+##newdf = unique(new$Deficiency)
+##oldfb = old$FBgn
+##newfb = unique(new$FBgn)
+##oldsym = old$Symbol
+##newsym = unique(new$Symbol)
+
+fullDfKey = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250613_FullDfData.csv"),row.names = 1)
+
+row.names(fullDfKey) = fullDfKey$FBab
+
+#Build a fresh gene id data table
+gene.chr = as.data.frame(org.Dm.egCHR)
+row.names(gene.chr) = gene.chr$gene_id
+gene.start = as.list(org.Dm.egCHRLOC)
+gene.start = lapply(gene.start, min)
+gene.start = unlist(gene.start)
+gene.end = as.list(org.Dm.egCHRLOCEND)
+gene.end = lapply(gene.end, max)
+gene.end = unlist(gene.end)
+FBid = as.data.frame(org.Dm.egFLYBASE)
+row.names(FBid) = FBid$gene_id
+Symbols = as.data.frame(org.Dm.egSYMBOL)
+row.names(Symbols) = Symbols$gene_id
+
+gene.location = data.frame(FBgn = FBid[names(gene.start), "flybase_id"],
+                           Symbol = Symbols[names(gene.start), "symbol"],
+                           ensembl = names(gene.start),
+                           CHR = gene.chr[names(gene.start), "chromosome"],
+                           Start = abs(gene.start),
+                           End = abs(gene.end[names(gene.start)]),
+                           Strand = gene.start/abs(gene.start))
+
+gl = apply(gene.location[,c("Start", "End")], MARGIN = 1, min)
+gr = apply(gene.location[,c("Start", "End")], MARGIN = 1, max)
+Dfl = apply(fullDfKey[,c("Start", "End")], MARGIN = 1, min)
+Dfr = apply(fullDfKey[,c("Start", "End")], MARGIN = 1, max)
+
+genesindf = list()
 i=1
-while(i <= nrow(DfKey)){
-  temp = na.omit(old[((old.left <= Df.left[i] & old.right >= Df.right[i]) |
-           (old.left >= Df.left[i] & old.left <= Df.right[i]) |
-           (old.right >= Df.left[i] & old.right <= Df.right[i])) &
-            old$CHR == DfKey$Chr[i],])
+while(i <= nrow(fullDfKey)){
+  temp = na.omit(gene.location[((gl <= Dfl[i] & gr >= Dfr[i]) |
+                               (gl >= Dfl[i] & gl <= Dfr[i]) |
+                               (gr >= Dfl[i] & gr <= Dfr[i])) &
+                               gene.location$CHR == fullDfKey$Chr[i],])
 
-  genesinolddf[[DfKey$Deficiency[i]]] = temp$FBgn
-  i=i+1
-}
-
-#new.loc = GeneIDKey[new$FBgn,c("Start","End","CHR")]
-new.loc = GeneIDKey[,c("FBgn", "Start","End","CHR")]
-new.left = apply(new.loc[,c("Start", "End")], MARGIN = 1, min)
-new.right = apply(new.loc[,c("Start", "End")], MARGIN = 1, max)
-newDf.left = apply(new[,c("Start", "End")], MARGIN = 1, min)
-newDf.right = apply(new[,c("Start", "End")], MARGIN = 1, max)
-
-new.keep = !duplicated(paste0(new$Deficiency, newDf.left, newDf.right))
-newDf.left = newDf.left[new.keep]
-newDf.right = newDf.right[new.keep]
-newDf = new$Deficiency[new.keep]
-newChr = new$Chr[new.keep]
-
-genesinnewdf = list()
-i=1
-while(i <= length(newDf)){
-      temp = na.omit(new.loc[((new.left <= newDf.left[i] & new.right >= newDf.right[i]) |
-           (new.left >= newDf.left[i] & new.left <= newDf.right[i]) |
-           (new.right >= newDf.left[i] & new.right <= newDf.right[i])) &
-            new.loc$CHR == newChr[i],])
-
-    genesinnewdf[[newDf[i]]] = temp$FBgn
+  genesindf[[fullDfKey$Deficiency[i]]] = temp$FBgn
   i=i+1

### 2025-06-18 DeficiencyScreen/Prelim_Analysis.Rmd
updated df data

@@
 
-genesindf = list()
+genesindf = data.frame(Df = character(),
+                       FBgn = character(),
+                       Symbol = character())
 i=1
@@
 
-  genesindf[[fullDfKey$Deficiency[i]]] = temp$FBgn
+  if(nrow(temp) > 0){
+    temp$Df = fullDfKey$Deficiency[i]
+    genesindf = rbind(genesindf, temp[, c("Df", "FBgn", "Symbol")])
+  }
+  #genesindf[[fullDfKey$Deficiency[i]]] = temp$FBgn
+
   i=i+1
 }
+
+python.genesindf = read.csv("/Users/johncsantiago/Documents/GitHub/Python/DeficiencyData/Output.csv", row.names = 1)
+
+py.gid = python.genesindf[,c(3,1,2)]
+colnames(py.gid) = c("Df", "FBgn", "Symbol")
+py.gid$Df = fullDfKey[py.gid$Df, "Deficiency"]
+
+##Dealing with nomenclature issues
+##identifying genes with an FBgn found using python method that were not identified using org.Dm.eg.db approach
+
+py.only = py.gid[py.gid$FBgn %in% setdiff(py.gid$FBgn, gene.location$FBgn),]
+
+##of these 23 genes, how many have a symbol only found with python
+
+py.only = py.only[py.only$Symbol %in% setdiff(py.only$Symbol, gene.location$Symbol),]
+
+##only 8 genes that were not found using the org.Dm.eg.db approach by symbol or FBgn
+
+##unique(py.only$Symbol)
+#"Est17" found under CG10175 in R data
+#"Dld" found under CG7430 in R data
+
+##NOT in the R data
+#"lncRNA:CR46532" 
+#"asRNA:PS4"     
+#"lncRNA:CR46530" 
+#"lncRNA:CR46535"
+#"lncRNA:CR46529"
+#"lncRNA:CR46534"
+
+py.only.FBgn = c("lncRNA:CR46532", "FBgn0288728", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.sym = c("lncRNA:CR46532", "asRNA:PS4", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.ens = c("lncRNA:CR46532", "asRNA:PS4", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.CHR = c("lncRNA:CR46532", "3R", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.Start = c("lncRNA:CR46532", 16720127, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.End = c("lncRNA:CR46532", 16729959, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+py.only.Strand = c("lncRNA:CR46532", 1, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+
+add.gene.locations = data.frame(FBgn = py.only.FBgn,
+                                Symbol = py.only.sym,
+                                ensembl = py.only.ens,
+                                CHR = py.only.CHR,
+                                Start = py.only.Start,
+                                End = py.only.End,
+                                Strand = py.only.Strand)
 

### 2025-06-18 GOandKEGGTermEnrichment.Rmd
Updated Russo Data
updated df data

@@
 
+#A4V conditions use 4 parameters:   A or S for genotype
+#                                   3, 9 or 40 for time
+#                                   M or F for sex
+#                                   H, T or A for body section
+#                                   example: A3MT
+
+#G85R conditions use 3 parameters:  GR or WT for genotype
+#                                   M or F for sex
+#                                   C, Df or OE for TKT modulation
+#                                   example: GRMOE
 Variable.Condition = "GRFC" 
@@
 
+cat.data = Subset.Enrichment(row.names(FDR), row.names(FDR)[FDR[,1]<=0.05 & FDR[,2]<=0.05])
+
+cat.data = Subset.Enrichment(row.names(FDR), row.names(FDR)[FDR[,1]>0.05 & FDR[,2]<=0.05])
+
+cat.data = Subset.Enrichment(row.names(FDR), row.names(FDR)[FDR[,1]<=0.05 & FDR[,2]>0.05])
+
 ```
@@
 ##can be the exact name or 5 digit code in quotes
-specific.kegg = "00980"
+specific.kegg = "04146"
 
@@
 ##5 digits from KEGG ID
-PathwayID = "00010"
+PathwayID = "03050"
 
@@
 ##can be the exact name or 5 digit code in quotes
-specific.kegg = "00010"
+specific.kegg = "03050"
 
@@
 ##the 7 digits of a GOterm id or the exact term name
-specific.go = '0005811'
+specific.go = '0043228'
 
@@
 ##a parent category generated in the treemapPlot function
-parent.category = 'membrane lipid biosynthetic process'
+parent.category = 'double-strand break repair via break-induced replication'
 

### 2025-06-18 GeneralDataFiles/CompleteMetabolicNetwork.Rmd
updated df data

--- 2025-03-24 GeneralDataFiles/CompleteMetabolicNetwork.Rmd
@@
 
+GeneIDKey = read.csv(paste0(git.dir, "GeneIDKey.csv"), row.names = 1)
+G85R.geneFDR = read.csv(paste0(git.dir, "TKT.EdgeR.FDRTable.csv"), row.names = 1)
 G85R.geneFC = read.csv(paste0(git.dir, "TKT.EdgeR.FCTable.csv"), row.names = 1)
 G85R.metabFC = read.csv(paste0(git.dir, "MetaboliteFCs.csv"), row.names = 1)
+G85R.metabFC[,2:ncol(G85R.metabFC)] = log2(G85R.metabFC[,2:ncol(G85R.metabFC)])
+G85R.metabFDR = read.csv(paste0(git.dir, "MetaboliteFDRs.csv"), row.names = 1)
 
 raw.nodes = read.csv(paste0(git.dir, "combined.nodes.csv"), row.names = 1)
+raw.nodes$x = raw.nodes$x*1
+raw.nodes$y = raw.nodes$y*1
+
 raw.edges = read.csv(paste0(git.dir, "combined.edges.csv"))
 
-temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)
+temp = colorRampPalette(c("navy", "royalblue","white", "deeppink", "firebrick"))(401)
+temp2 = colorRampPalette(c("turquoise", "grey", "deeppink"))(401)
+
+```
+
+```{r echo = F}
+
+##metabolomics Choices
+##"GRxWT.C"  "GRxWT.Df" "GRxWT.OE" "GR.CxDf" "WT.CxDf"  "GR.CxOE"  "WT.CxOE"
+metab = "GRxWT.C"
+
+##Transcriptome choices
+##"GRF.CxDf" "GRF.CxOE"  "WTF.CxDf" "WTF.CxOE"  "GRxWT.FC" "GRxWT.FDf"
+##"GRxWT.FOE" "GRM.CxDf"  "GRM.CxOE" "WTM.CxDf"  "WTM.CxOE"  "GRxWT.MC"
+##"GRxWT.MDf" "GRxWT.MOE" "GR.FxM" "WT.FxM" 
+enzyme = "GRxWT.FDf"
+
+nodes = raw.nodes
+edges = raw.edges
+
+nodes[nodes$shape == "dot", "label"] = NA
+
+nodes.color = G85R.metabFC[nodes[nodes$shape == "circle", "data.id"], metab]
+nodes.color = temp[((nodes.color/max(abs(na.omit(nodes.color))))*200)+201]
+nodes[nodes$shape == "circle", "color.background"] = nodes.color
+nodes$color.background[na.action(na.exclude(nodes$color.background))] = "white"
+
+node.size = G85R.metabFDR[nodes[nodes$shape == "circle", "data.id"], metab]
+node.size[na.action(na.exclude(node.size))] = 1
+node.size = -log10(node.size)+1
+node.size = node.size*10
+node.size[node.size>80] = 50
+node.size[node.size < (-log10(.2)+1)*10] =10
+nodes[nodes$shape == "circle", "size"] = node.size
+
+nodes$shape = 'dot'
+
+nodes$title = paste0(nodes$id,
+                     "<br>-log2(FC): ", 
+                     signif((G85R.metabFC[nodes$data.id, metab]), 3),
+                     "<br>FDR: ", 
+                     signif((G85R.metabFDR[nodes$data.id, metab]), 3))
+
+edges$title = paste0(GeneIDKey[edges$FBgn, "Symbol"],
+                     "<br>-log2(FC): ", 
+                     signif(G85R.geneFC[edges$FBgn,
+                                 enzyme],3),
+                     "<br>FDR: ", 
+                     signif(G85R.geneFDR[edges$FBgn,
+                                 enzyme],3))
+
+edges.width = G85R.geneFDR[edges$FBgn, enzyme]
+edges.width[na.action(na.exclude(edges.width))] = 1
+edges.width = (-log10(edges.width))+1
+edges.width = edges.width * 2
+
+edges.width[edges.width>6] = 6
+edges.width[edges.width < (-log10(.2)+1)*2] =1
+
+edges$width = edges.width
+
+edges.colors = G85R.geneFC[edges$FBgn, enzyme]
+edges.colors = temp[((edges.colors/max(abs(na.omit(edges.colors))))*200)+201]
+edges.colors[na.action(na.exclude(edges.colors))] = "grey"
+
+edges$color = edges.colors
+
+visNetwork(nodes, edges, background = "black")%>%
+  visNodes(physics = F)%>%
+  #visLayout(hierarchical=F, improvedLayout=T)%>%
+  visOptions(highlightNearest = TRUE, nodesIdSelection = list(enabled = T, values = nodes[nodes$size > 0, "label"]))%>%
+  visNodes(color = list(border = "white"), font = list(color = "gold", size = 14, background = "black"))%>%
+  visEdges(arrows = visedges$arrows, physics = T)
 
@@
 
+nodes[nodes$shape == "dot", "label"] = NA
 nodes[nodes$shape == "circle", "size"] = 20
-nodes$shape = 'dot'
+nodes.color = G85R.metabFC[nodes[nodes$shape == "circle", "data.id"], metab]
+nodes.color = temp[((nodes.color/max(abs(na.omit(nodes.color))))*200)+201]
+nodes[nodes$shape == "circle", "color.background"] = nodes.color
+nodes$color.background[na.action(na.exclude(nodes$color.background))] = "ghostwhite"
+nodes[nodes$shape == "circle", "size"] = 20
+nodes$shape = "dot"
 
-node.colors = G85R.metabFC[nodes$data.id, "GR.CxOE"]
-node.colors = temp[(200*node.colors/max(abs(na.exclude(node.colors)))) + 201]
-node.colors[na.action(na.exclude(node.colors))] = "white"
+edges$color = "black"
 
-nodes$color.background = node.colors
+PPP.genes = c("FBgn0023477",
+              "FBgn0050499",
+              "FBgn0050410",
+              "FBgn0004654",
+              "FBgn0030239",
+              "FBgn0037147",
+              "FBgn0004057",
+              "FBgn0037607",
+              "FBgn0036784")
+
+edges[edges$FBgn %in% c(PPP.genes), "color"] = "black"
+edges[edges$FBgn %in% c(PPP.genes), "width"] = 2.5
+#edges[ grep("FBgn0036784", edges$FBgn), "color"] = "darkgreen"
+#edges[ grep("FBgn0037607", edges$FBgn), "color"] = "darkorange"
+
+visNetwork(nodes, edges)%>%
+  visNodes(physics = F, font = list(size = 18, background = hex("white", .6)))
+
+#edges[grep('red', edges$color),]
 
 ```
-
-```{r echo = F}
-
-visNetwork(nodes, edges)%>%
-  visNodes(physics = F)%>%
-  visLayout(hierarchical=F, improvedLayout=T)%>%
-  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
-  visEdges(arrows = visedges$arrows)
-
-```

### 2025-06-18 RussoPaper/Prelim_UBLegMorphologyDataAnalysis.Rmd
updated df data

@@
 heat.data = temp[,6:14]
+heat.data = temp[,c(7:9,12:14)]
+
 row.names(heat.data) = paste0(temp$Genotype,temp$Animal..)
@@
           Colv = T,
-          Rowv = T,
+          Rowv = F,
+          dendrogram = "column",
           margins = c(7, 15),
@@
           ColSideColors = sample.colors,
-          RowSideColors = category.colors,
+          #RowSideColors = category.colors,
           col = heat.colors)
@@
 
+temp.combos$combo = (substr(temp.combos$combo, 1, nchar(temp.combos$combo)-2))
+temp.combos= temp.combos[!duplicated(temp.combos[, "combo"]),]
+
+temp.combos[1:20, 2:4]
+
 ```
@@
 ```
+
+```{r}
+
+library(ggridges)
+
+#best.combo = data_matrix[,c(2,3,4,7,8,9)]
+
+temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/UBLegMorphologyData.csv")
+
+temp.titles = c("Is the leg short?",
+                "Is there scrunching or curving?",
+                "Is the axonal bundle straight?",
+                "Does the axonal bundle split or are there chunks missing?",
+                "Does the branching look organized?",
+                "Is the branching following a pattern tiling?",
+                "Is there branching in all aspects of the femur?",
+                "Is the mitochonria in the entire axonal bundle?",
+                "Do all branches have mitochondria?")
+
+best.titles = temp.titles[c(2,3,4,7,8,9)]
+
+temp$Genotype[temp$Genotype == "WT"] = "WT(cr)"
+temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr)"
+
+temp$Genotype = factor(temp$Genotype, levels = unique(temp$Genotype))
+
+morph.data = temp[,c(1:2,7:9,12:14)]
+
+WT.morphdata = morph.data[morph.data$Genotype == "WT(cr)",]
+WT.morphdata = t(WT.morphdata[,3:8])
+WT.morphdata = as.data.frame(WT.morphdata)
+WT.morphdata$Morph = best.titles
+wt.morphplot = data.frame(Morph = as.character(),
+                          Score = as.numeric())
+i=1
+while(i<=9){
+  temp.morph = data.frame(Morph = WT.morphdata$Morph,
+                          Score = WT.morphdata[,i])
+  wt.morphplot = rbind(wt.morphplot, temp.morph)
+  i = i +1
+}
+wt.morphplot$Morph = factor(wt.morphplot$Morph, levels = best.titles)
+wt.morphplot$Species = "WT(cr)"
+
+GR.morphdata = morph.data[morph.data$Genotype == "G85R(cr)",]
+GR.morphdata = t(GR.morphdata[,3:8])
+GR.morphdata = as.data.frame(GR.morphdata)
+GR.morphdata$Morph = best.titles
+GR.morphplot = data.frame(Morph = as.character(),
+                          Score = as.numeric())
+i=1
+while(i<=9){
+  temp.morph = data.frame(Morph = GR.morphdata$Morph,
+                          Score = GR.morphdata[,i])
+  GR.morphplot = rbind(GR.morphplot, temp.morph)
+  i = i +1
+}
+GR.morphplot$Morph = factor(GR.morphplot$Morph, levels = best.titles)
+GR.morphplot$Species = "G85R(cr)"
+
+sum.morph = data.frame(Morph = "Total Score",
+                       Score = apply(morph.data[,3:8], MARGIN = 1, sum),
+                       Species = morph.data$Genotype)
+sum.morph$Species = factor(sum.morph$Species, levels = c("WT(cr)", "G85R(cr)"))
+
+all.morphplot = rbind(wt.morphplot, GR.morphplot)
+all.morphplot$Species = factor(all.morphplot$Species, levels = c("WT(cr)", "G85R(cr)"))
+#all.morphplot = rbind(all.morphplot, sum.morph)
+
+ggplot(
+  all.morphplot, 
+  aes(x = `Score`, y = `Morph`)
+  ) +
+  geom_density_ridges_gradient(
+    aes(fill = Species), scale = 1
+    ) +
+  scale_fill_manual(
+    values = alpha(c("royalblue", "orange"), .5)
+  ) +
+  labs(title = 'Morphology Score')
+
+```
+
+```{r echo = F}
+
+ggplot(
+  sum.morph, 
+  aes(x = `Score`, y = `Morph`)
+  ) +
+  geom_density_ridges_gradient(
+    aes(fill = Species), scale = 1
+    ) +
+  scale_fill_manual(
+    values = alpha(c("royalblue", "orange"), .5)
+  ) +
+  labs(title = 'Morphology Score')
+
+```
+
+```{r echo = F}
+all.morphplot %>% 
+  ##pivot_longer(cols = -Species,
+  ##             names_to = "Param",
+  ##             values_to = "Value") %>% 
+      ggplot(aes(x = Score, y = Morph))+
+      geom_density_ridges(aes(fill = Species),
+                          stat = "binline",
+                          alpha = 0.5)
+
+ggplot(
+  all.morphplot, 
+  aes(x = `Score`, y = `Morph`)
+  ) +
+  geom_density_ridges_gradient(
+    #aes(fill = ..x..), scale = 3, size = 0.3
+    aes(fill = Species), alpha = .9, scale = 1
+    ) +
+  #scale_fill_gradientn(
+  #  colours = c("#0D0887FF", "#CC4678FF", "#F0F921FF"),
+  #  name = "Score"
+  #  )+
+  labs(title = 'Morphology Score')
+
+```

### 2025-06-18 Functions_OmicsQuickPlotFunctions.R

@@ -788,3 +788,21 @@ legend("left",
        fill = c("brown", "orange", "steelblue"),
        xpd = T)
 }
+
+
+metab.mean = norm.data[,unique(colnames(norm.data))]
+i=1
+while(i <= nrow(norm.data)){
+  j = 1
+  while(j <= ncol(metab.mean)){
+    metab.mean[i,j] = mean(na.omit(norm.data[i, colnames(norm.data) == colnames(metab.mean)[j]]))
+    j = j+1
+  }
+  i=i+1
+}
+
+metab.mean["NAD+",]/metab.mean["NADH",]
+metab.mean["NADP+",]/metab.mean["NADPH",]
+
+NAD = mean(norm.data["NAD+", colnames(norm.data) == "WT"])
+

### 2025-06-18 GOandKEGGPlottingFunctions.R

@@ -38,7 +38,7 @@ A4V.comparekey = setNames(colnames(A4V.FDR),
                             'A9FHvA40FH', 'S9FHvS40FH', 'A3FHvA40FH', 'S3FHvS40FH',
                             
                             'A3FTvS3FT', 'A3MTvS3MT', 'A9FTvS9FT', 'A9MTvS9MT', 'A40FTvS40FT',
-                            'A3FTvA9FT', 'S3FTvS9FT', 'A3MTvA9MT', 'S3FTvS9MT',
+                            'A3FTvA9FT', 'S3FTvS9FT', 'A3MTvA9MT', 'S3MTvS9MT',
                             'A9FTvA40FT', 'S9FTvS40FT', 'A3FTvA40FT', 'S3FTvS40FT',
                             
                             'A3FAvS3FA', 'A3MAvS3MA', 'A9FAvS9FA', 'A9MAvS9MA', 'A40FAvS40FA',

### 2025-06-24 RussoPaper/AnaDataAnalysis.Rmd
pushing data

---
title: "Ana Data"
author: "John Santiago"
date: "2025-06-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = F, warning=FALSE, message=FALSE}

library(kableExtra)
library(gtools)
library(gplots)
library(beeswarm)

temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250621_AllAnaData.csv")

temp$Genotype[temp$Genotype == "WT-cr/LoxP"] = "WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr/hr)"
temp$Genotype[temp$Genotype == "G85Rcr/G85Rhr"] = "G85R(cr/hr)"

temp$Genotype[temp$Genotype == "OK371 > gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WTcr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85cr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"

temp$Genotype[temp$Genotype == "OK371 > saxA [WT]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > saxA [G85R]"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371> saxA [WT-cr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA G85R"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [WTcr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [G85Rcr/G85Rhr]"] = "OK371-saxA; G85R(cr/LoxP)"

temp$Genotype = factor(temp$Genotype, levels = unique(temp$Genotype))

std.colors = setNames(c('navy', "orange2", 
                        "darkgreen", "turquoise3",
                        "firebrick","deeppink"),
                      c("WT(cr/LoxP)" , "G85R(cr/hr)",
                        "OK371-gbb; WT(cr/LoxP)", "OK371-gbb; G85R(cr/LoxP)",
                        "OK371-saxA; WT(cr/LoxP)", "OK371-saxA; G85R(cr/LoxP)"))

hex = function(color, alpha){
  rgb2hex = color
  i = 1
  while(i <= length(color)){
    rgbvals = col2rgb(color[i])
    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
    i = i+1
  }
  return(rgb2hex)
}

```

```{r echo = F}

plot.bouts = function(boutdata){

boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]))

par(mar=c(6.25, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(boutdata$Boutons)*1.1),
     xlim = c(.5, length(na.omit(boutmeans))+.5),
     xaxt = "n",
     ylab="Bouton Number",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval muscle Segment", unique(boutdata$Segment), "NMJ", unique(boutdata$NMJ), "bouton counts"))

lines(x = c(.65,1.35),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(boutmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

if(length(na.omit(boutmeans)>2)){
lines(x = c(2.65,3.35),
     y = rep(boutmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(3.65,4.35),
     y = rep(boutmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(4.65,5.35),
     y = rep(boutmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(5.65,6.35),
     y = rep(boutmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])
}

beeswarm(boutdata$Boutons~boutdata$Genotype,
       pch = 21,
       method = "center",
       bg = hex(unique(std.colors[as.numeric(boutdata$Genotype)]),.5),
       add = T)

axis(side = 1,
     at = c(1:length(na.omit(boutmeans))),
     labels = c(labels)[1:length(na.omit(boutmeans))],
     las = 2,
     lwd = 0,
     line = -.75)

    lines(x = c(.225 + .3/length(na.omit(boutmeans)), length(na.omit(boutmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = ceiling(max(boutdata$Boutons)*.11)
  y.at = c(0,10*1:y.at)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)
}

```

```{r echo = F, fig.width = 7}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "3",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F}

btd = boutdata

t.data = list("WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "WT(cr/LoxP)"],
                    "G85R(cr/hr)" = btd$Boutons[btd$Genotype == "G85R(cr/hr)"],
                    "OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
                    "OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
                    "OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
                    "OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for segment 3, NMJ 4 Bouton Counts.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F, fig.width = 7}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "3",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F}

btd = boutdata

t.data = list("WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "WT(cr/LoxP)"],
                    "G85R(cr/hr)" = btd$Boutons[btd$Genotype == "G85R(cr/hr)"],
                    "OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
                    "OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
                    "OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
                    "OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for segment 3, NMJ 6-7 Bouton Counts.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "4",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "4",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "5",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "5",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "6",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, include = F}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "6",]

geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

plot.bouts(boutdata)

```

```{r echo = F, fig.width = 7}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)

geno = unique(boutdata$Genotype)
geno = geno[c(1,5,2,6,3,7,4,8)]

boutdata$Genotype = factor(boutdata$Genotype, levels = geno)

boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]))

par(mar=c(4, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(boutdata$Boutons)*1.1),
     xlim = c(.5, length(na.omit(boutmeans))+.5),
     xaxt = "n",
     ylab="Bouton Number",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval muscle NMJ 4 bouton counts, segments 3-6"))

lines(x = c(.65,1.35),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(boutmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(2.65,3.35),
     y = rep(boutmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(3.65,4.35),
     y = rep(boutmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(4.65,5.35),
     y = rep(boutmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(5.65,6.35),
     y = rep(boutmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(6.65,7.35),
     y = rep(boutmeans[7], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(7.65,8.35),
     y = rep(boutmeans[8], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

beeswarm(boutdata$Boutons~boutdata$Genotype,
       pch = 21,
       method = "center",
       bg = hex(std.colors[1:2],.5),
       add = T)

lines(x = c(2.5,2.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

lines(x = c(4.5,4.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

lines(x = c(6.5,6.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

axis(side = 1,
     at = c(1.5, 3.5, 5.5, 7.5),
     labels = c(3,4,5,6),
     las = 1,
     lwd = 0,
     line = -.75)

axis(side = 1,
     at = c(4.5),
     labels = c("Larval Segment"),
     las = 1,
     lwd = 0,
     cex = 2,
     line = 0.5)

    lines(x = c(.2, length(na.omit(boutmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 10*1:5)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  legend('topright',
       inset=c(-0.185,0),
       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)'), 
       fill = std.colors[1:2],
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

```

```{r echo = F}

btd = boutdata

t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for NMJ 4, all segments Bouton Counts.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F, fig.width = 7}

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)

geno = unique(boutdata$Genotype)
geno = geno[c(1,5,2,6,3,7,4,8)]

boutdata$Genotype = factor(boutdata$Genotype, levels = geno)

boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]))

par(mar=c(4, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(boutdata$Boutons)*1.1),
     xlim = c(.5, length(na.omit(boutmeans))+.5),
     xaxt = "n",
     ylab="Bouton Number",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval muscle NMJ 6-7 bouton counts, segments 3-6"))

lines(x = c(.65,1.35),
     y = rep(boutmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(boutmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(2.65,3.35),
     y = rep(boutmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(3.65,4.35),
     y = rep(boutmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(4.65,5.35),
     y = rep(boutmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(5.65,6.35),
     y = rep(boutmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(6.65,7.35),
     y = rep(boutmeans[7], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(7.65,8.35),
     y = rep(boutmeans[8], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

beeswarm(boutdata$Boutons~boutdata$Genotype,
       pch = 21,
       method = "center",
       bg = hex(std.colors[1:2],.5),
       add = T)

lines(x = c(2.5,2.5),
      y = c(-5,100),
      lty = 2,
      xpd = T)

lines(x = c(4.5,4.5),
      y = c(-5,100),
      lty = 2,
      xpd = T)

lines(x = c(6.5,6.5),
      y = c(-5,100),
      lty = 2,
      xpd = T)

axis(side = 1,
     at = c(1.5, 3.5, 5.5, 7.5),
     labels = c(3,4,5,6),
     las = 1,
     lwd = 0,
     line = -.75)

axis(side = 1,
     at = c(4.5),
     labels = c("Larval Segment"),
     las = 1,
     lwd = 0,
     cex = 2,
     line = 0.5)

    lines(x = c(.2, length(na.omit(boutmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 10*1:10)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

  legend('topright',
       inset=c(-0.185,0),
       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)'), 
       fill = std.colors[1:2],
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

```

```{r echo = F}

btd = boutdata

t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for NMJ 6-7, all segments Bouton Counts.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F}

VNC = temp[temp$Data == "VNC",]
VNC$CTCF = VNC$CTCF/1000
geno = unique(VNC$Genotype)
VNC$color = as.numeric(VNC$Genotype) + ((VNC$Experiment -1)*6)
VNC$color = c('navy', "orange2",
               "darkgreen", "turquoise4",
               "firebrick","deeppink3",
               "royalblue", 'gold',
               "green", 'cyan',
               "red", "pink") [VNC$color]

labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

vncmeans = c(mean(VNC[VNC$Genotype == geno[1], "CTCF"]),
              mean(VNC[VNC$Genotype == geno[2], "CTCF"]),
              mean(VNC[VNC$Genotype == geno[3], "CTCF"]),
              mean(VNC[VNC$Genotype == geno[4], "CTCF"]),
              mean(VNC[VNC$Genotype == geno[5], "CTCF"]),
              mean(VNC[VNC$Genotype == geno[6], "CTCF"]))

par(mar=c(6.25, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(vncmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(VNC$CTCF)*1.1),
     xlim = c(.5, length(na.omit(vncmeans))+.5),
     xaxt = "n",
     ylab="Fluorescence Intensity/1000",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval VNC fluorescence"))

lines(x = c(.65,1.35),
     y = rep(vncmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(vncmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

if(length(na.omit(vncmeans)>2)){
lines(x = c(2.65,3.35),
     y = rep(vncmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(3.65,4.35),
     y = rep(vncmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(4.65,5.35),
     y = rep(vncmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(5.65,6.35),
     y = rep(vncmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])
}

beeswarm(VNC$CTCF~VNC$Genotype,
       #pch = 21,
       pwpch = 20+VNC$Experiment,
       method = "center",
       #bg = hex(unique(std.colors[as.numeric(VNC$Genotype)]),.5),
       pwbg = hex(VNC$color, .75),
       add = T)

axis(side = 1,
     at = c(1:length(na.omit(vncmeans))),
     labels = c(labels)[1:length(na.omit(vncmeans))],
     las = 2,
     lwd = 0,
     line = -.75)

    lines(x = c(.225 + .3/length(na.omit(vncmeans)), length(na.omit(vncmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0,500, 1000, 1500)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

```

```{r echo = F}
btd = temp[temp$Data == "VNC",]

t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for VNC data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F}

NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "4",]
NMJ$CTCF = NMJ$CTCF/1000
geno = unique(NMJ$Genotype)
NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
NMJ$color = c('navy', "orange2",
               "darkgreen", "turquoise4",
               "firebrick","deeppink3",
               "royalblue", 'gold',
               "green", 'cyan',
               "red", "pink") [NMJ$color]

labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))

par(mar=c(6.25, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(nmjmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(NMJ$CTCF)*1.1),
     xlim = c(.5, length(na.omit(nmjmeans))+.5),
     xaxt = "n",
     ylab="Fluorescence Intensity/1000",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval segment 3, NMJ 4 fluorescence"))

lines(x = c(.65,1.35),
     y = rep(nmjmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(nmjmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

if(length(na.omit(nmjmeans)>2)){
lines(x = c(2.65,3.35),
     y = rep(nmjmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(3.65,4.35),
     y = rep(nmjmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(4.65,5.35),
     y = rep(nmjmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(5.65,6.35),
     y = rep(nmjmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])
}

beeswarm(NMJ$CTCF~NMJ$Genotype,
       #pch = 21,
       pwpch = 20+NMJ$Experiment,
       method = "center",
       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
       pwbg = hex(NMJ$color, .75),
       add = T)

axis(side = 1,
     at = c(1:length(na.omit(nmjmeans))),
     labels = c(labels)[1:length(na.omit(nmjmeans))],
     las = 2,
     lwd = 0,
     line = -.75)

    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 500, 1000, 1500, 2000)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

```

```{r echo = F}
btd = temp[temp$Data == "NMJ" & temp$NMJ == "4",]

t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for VNC data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

```{r echo = F}

NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]
NMJ$CTCF = NMJ$CTCF/1000
geno = unique(NMJ$Genotype)
NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
NMJ$color = c('navy', "orange2",
               "darkgreen", "turquoise4",
               "firebrick","deeppink3",
               "royalblue", 'gold',
               "green", 'cyan',
               "red", "pink") [NMJ$color]

labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))

par(mar=c(6.25, 4.1, 4.1, 5.6))

plot(x = c(.75,1.25),
     y = rep(nmjmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1],
     ylim = c(0, max(NMJ$CTCF)*1.1),
     xlim = c(.5, length(na.omit(nmjmeans))+.5),
     xaxt = "n",
     ylab="Fluorescence Intensity/1000",
     yaxt = "n",
     xlab = NA,
     frame = F,
     main = paste("Larval segment 3, NMJ 6-7 fluorescence"))

lines(x = c(.65,1.35),
     y = rep(nmjmeans[1], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(1.65,2.35),
     y = rep(nmjmeans[2], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

if(length(na.omit(nmjmeans)>2)){
lines(x = c(2.65,3.35),
     y = rep(nmjmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(3.65,4.35),
     y = rep(nmjmeans[4], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(4.65,5.35),
     y = rep(nmjmeans[5], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(5.65,6.35),
     y = rep(nmjmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])
}

beeswarm(NMJ$CTCF~NMJ$Genotype,
       #pch = 21,
       pwpch = 20+NMJ$Experiment,
       method = "center",
       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
       pwbg = hex(NMJ$color, .75),
       add = T)

axis(side = 1,
     at = c(1:length(na.omit(nmjmeans))),
     labels = c(labels)[1:length(na.omit(nmjmeans))],
     las = 2,
     lwd = 0,
     line = -.75)

    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 1000, 2000, 3000, 4000, 5000)

  axis(side = 2,
       at = y.at,
       lwd = 2,
       line = 0,
       labels = F,
       xpd = T,
       las = 2)

  axis(side = 2,
       at = y.at,
       lwd = 3,
       line = 0,
       labels = T,
       xpd = T,
       las = 2)

```

```{r echo = F}
btd = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]

t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])

t.table = data.frame(Genotype1 = character(),
                     Genotype2 = character(),
                     pval = numeric())

i=1
while(i <= length(t.data)){
  j = i+1
  while(j <= length(t.data)){
    t.temp = data.frame(Genotype1 = geno[i],
                        Genotype2 = geno[j],
                        pval = t.test(x = t.data[[i]],
                                      y = t.data[[j]],
                                      paired = F)[[3]])
    t.table = rbind(t.table, t.temp)
      j = j+1
  }
  i = i+1
}

t.stripe = t.table$pval <= .05
knitr::kable(t.table,
             caption = 'All t-tests for VNC data.')  %>%
kable_styling() %>%
row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")

```

### 2025-08-10 DeficiencyScreen/Prelim_Analysis.Rmd
ana update

@@
 library(org.Dm.eg.db)
-##library(goseq)
+library(goseq)
 library(rrvgo)
 library(plotly)
+library(VennDiagram)
+genesingo=as.list(org.Dm.egGO2ALLEGS)
+
+hex = function(color, alpha){
+  rgb2hex = color
+  i = 1
+  while(i <= length(color)){
+    rgbvals = col2rgb(color[i])
+    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
+    i = i+1
+  }
+  return(rgb2hex)
+}
+
 ```
@@
 
-##DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"))
+DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"))
 ##colnames(DfKey)[c(1,3)] = c("BDSC", "FBab")
@@
 
-#old.dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names)
+old.dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names)
 
@@
 
-fullDfKey = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250613_FullDfData.csv"),row.names = 1)
+fullDfKey = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/20250618_FullDfData.csv"),row.names = 1)
 
@@
 
-py.only.FBgn = c("lncRNA:CR46532", "FBgn0288728", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.FBgn = c("FBgn0289441", "FBgn0288728", "FBgn0289439", "FBgn0289444", "FBgn0289438", "FBgn0289443")
 
@@
 
-py.only.ens = c("lncRNA:CR46532", "asRNA:PS4", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.ens = c("86703978", "86703974", "86703976", "86703981", "86703975", "86703980")
 
-py.only.CHR = c("lncRNA:CR46532", "3R", "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.CHR = c("3R", "3R", "3R", "2L", "2L", "2R")
 
-py.only.Start = c("lncRNA:CR46532", 16720127, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.Start = c(7341783, 16720127, 13056818, 7595504, 9747046, 20149996)
 
-py.only.End = c("lncRNA:CR46532", 16729959, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.End = c(7344884, 16729959, 13057676, 7597500, 9747785, 20150499)
 
-py.only.Strand = c("lncRNA:CR46532", 1, "lncRNA:CR46530", "lncRNA:CR46535", "lncRNA:CR46529", "lncRNA:CR46534")
+py.only.Strand = c(-1, 1, -1, -1, -1, -1)
 
@@
                                 Strand = py.only.Strand)
+gene.location = rbind(gene.location, add.gene.locations)
+
+## redo genes in each Df
+gl = apply(gene.location[,c("Start", "End")], MARGIN = 1, min)
+gr = apply(gene.location[,c("Start", "End")], MARGIN = 1, max)
+Dfl = apply(fullDfKey[,c("Start", "End")], MARGIN = 1, min)
+Dfr = apply(fullDfKey[,c("Start", "End")], MARGIN = 1, max)
+
+genesindf = data.frame(Df = character(),
+                       FBgn = character(),
+                       Symbol = character())
+i=1
+while(i <= nrow(fullDfKey)){
+  temp = na.omit(gene.location[((gl <= Dfl[i] & gr >= Dfr[i]) |
+                               (gl >= Dfl[i] & gl <= Dfr[i]) |
+                               (gr >= Dfl[i] & gr <= Dfr[i])) &
+                               gene.location$CHR == fullDfKey$Chr[i],])
+
+  if(nrow(temp) > 0){
+    temp$Df = fullDfKey$Deficiency[i]
+    genesindf = rbind(genesindf, temp[, c("Df", "FBgn", "Symbol")])
+  }
+  i=i+1
+}
+
+```
+
+```{r echo = F}
+#all the current Df data after Jonah omissions
+#fullDfKey
+
+##genes in the current Df data
+##genesindf
+
+##the old Df data before Jonah omissions
+DfKey = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/DfKey.csv"))
+
+##Genes that were originally associated with the old Df data
+old.dfdata = read.csv(paste0(git.dir,"DeficiencyScreen/DataFiles/DeficiencyModifierGenes.csv"),row.names = 1)
 
@@
 
-newdfonly = setdiff(newdf, olddf)
-olddfonly = setdiff(olddf, newdf)
+  ##Sample titles as strings. Only fill in up to your number of selected categories
+  set1 = "All old Df"
+  set2 = "All new Df"
+  set3 = "Old Suppressors/Strong Suppressors"
+  set4 = "New Suppressors"
 
-newfbonly = setdiff(newfb, oldfb)
-oldfbonly = setdiff(oldfb, newfb)
+  ##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
+  s1 = DfKey$FBab..
+  s2 = fullDfKey$FBab[fullDfKey$Omit == F]
+  s3 = DfKey$FBab..[grep("Sup",DfKey$Modifier)]
+  s4 = fullDfKey[fullDfKey$Omit == F,]
+  s4 = s4$FBab[grep("Sup", s4$Modifier)]
+  main = ""
 
-newsymonly = setdiff(newsym, oldsym)
-oldsymonly = setdiff(oldsym, newsym)
+  grid.newpage()
+  tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")
 
-fbinnewdfonly = unique(fulldf[fulldf$Deficiency %in% newdfonly, "FBgn"])
-fbinolddfonly = unique(unlist(genesinolddf[olddfonly]))
+```
 
+```{r echo = F}
+
+trimmed.Df = fullDfKey[fullDfKey$Omit == "FALSE",]
+trimmed.genes = genesindf[genesindf$Df %in% trimmed.Df$Deficiency,]
+#trimmed.sup = fullDfKey[fullDfKey$Omit == "FALSE" & fullDfKey$MLE >= 2,] 
+trimmed.sup = fullDfKey[(fullDfKey$Omit == "FALSE" & fullDfKey$MLE == 2) &
+                         fullDfKey$Modifier ==  "No Effect",] 
+#trimmed.sup = fullDfKey[fullDfKey$Omit == "FALSE" & fullDfKey$Modifier ==  "Suppressor",] 
+trimmed.supgenes = genesindf[genesindf$Df %in% trimmed.sup$Deficiency,]
+
+sigs = unique(trimmed.supgenes$Symbol)
+genes = setNames(rep(0, length(unique(trimmed.genes$Symbol))), unique(trimmed.genes$Symbol))
+
+#randoms = sample(1:length(genes), 6061)
+
+genes[sigs] = 1
+#genes[randoms] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+##GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
+
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+
+#suppressor.GO = GO.wall
+#twodayplus.GO = GO.wall
+#twotothree.GO = GO.wall
+
+```
+
+```{r echo = F, warning=F, message=F}
+##GO analysis of all Df with MLE 3 or greater, omitting Dfs with escapers
+sigs.Df = fullDfKey[fullDfKey$Omit == "FALSE" & fullDfKey$MLE > 3,]
+sigs = genesindf[genesindf$Df %in% sigs.Df$Deficiency, "Symbol"]
+
+genes.Df = fullDfKey[fullDfKey$Omit == "FALSE",]
+genes = genesindf[genesindf$Df %in% genes.Df$Deficiency, "Symbol"]
+sigs = unique(trimmed.supgenes$Symbol)
+genes = setNames(rep(0, length(unique(genes))), unique(genes))
+
+genes[sigs] = 1
+pwf=nullp(genes,"dm3","geneSymbol")
+GO.wall=goseq(pwf,"dm3","geneSymbol")
+GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
+row.names(GO.wall) = GO.wall$category
+
+sup.GO = GO.wall
+
+```
+
+```{r echo = F}
+
+df.genesingo = gene.location[gene.location$ensembl %in% intersect(gene.location$ensembl, as.character(genesingo[["GO:0030527"]])),]
+
+summary(factor(genesindf[genesindf$FBgn %in% df.genesingo$FBgn, "Df"], levels = unique(genesindf[genesindf$FBgn %in% df.genesingo$FBgn, "Df"])))
+
+fullDfKey[fullDfKey$Deficiency == "Df(2L)ED1473",]
+
+```
+
+```{r echo = F, warning=F, include = F}
+
+hist(na.omit(as.numeric(dfdata$MLE)), col = hex('yellow', .25),
+     breaks = seq(-4, 7, by = 1),
+     xlab = "MLE",
+     main = "Old Df MLE data vs New")
+hist(na.omit(as.numeric(DfKey$MLE)), add = T, col = hex('blue', .2),
+     breaks = seq(-4, 7, by = 1))
+legend("topright", legend = c("old data", "new data"), fill = c("blue", "yellow"))
 ```
@@
   tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")
-
-```
-
-```{r echo = F}
-##kegg = readRDS(gzcon(url(paste0(git.dir,"DeficiencyScreen/DataFiles/kegg.symbol2path.RData"))))
-##kegg.names = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/KEGG.names.csv"), row.names = 1)
-
-Moderate.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv"), row.names = 1)
-Strong.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/StrongGOAnalysis.csv"), row.names = 1)
-Repress.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/RepressorGOAnalysis.csv"), row.names = 1)
-Lethal.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/LethalGOAnalysis.csv"), row.names = 1)
-Enhancer.GO = read.csv(paste0(git.dir, "DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv"), row.names = 1)
-
-genesingo=as.list(org.Dm.egGO2ALLEGS)
-
-```
-
-```{r echo = F}
-
-##dfbar = data.frame(Enhancer = c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),
-##                   NoEffect = c(DfKey[DfKey$Modifier == "No Effect",], dfdata[dfdata$Modifier == "No Effect",]),
-##                   Lethal = c(DfKey[DfKey$Modifier == "Lethal",], dfdata[dfdata$Modifier == "Lethal",]),
-##                   c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),
-##                   Moderate = c(DfKey[DfKey$Modifier == "Enhancer",], dfdata[dfdata$Modifier == "Enhancer",]),)
-
-#old = hist(as.numeric(DfKey$MLE))
-#new = hist(as.numeric(dfdata$MLE))
-
-hex = function(color, alpha){
-  rgb2hex = color
-  i = 1
-  while(i <= length(color)){
-    rgbvals = col2rgb(color[i])
-    rgb2hex[i] = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
-    i = i+1
-  }
-  return(rgb2hex)
-}
-
-```
-
-```{r echo = F, warning=F}
-
-hist(na.omit(as.numeric(dfdata$MLE)), col = hex('yellow', .25),
-     breaks = seq(-4, 7, by = 1),
-     xlab = "MLE",
-     main = "Old Df MLE data vs New")
-hist(na.omit(as.numeric(DfKey$MLE)), add = T, col = hex('blue', .2),
-     breaks = seq(-4, 7, by = 1))
-legend("topright", legend = c("old data", "new data"), fill = c("blue", "yellow"))
-```
-
-```{r include=F, echo=F}
-
-sigs = unique(fulldf[fulldf$Modifier == "Enhancer", "Symbol"])
-genes = setNames(rep(0, length(unique(fulldf$Symbol))), unique(fulldf$Symbol))
-genes[sigs] = 1
-pwf=nullp(genes,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol")
-GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
-
-GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-row.names(GO.wall) = GO.wall$category
-Enhancer.GO = GO.wall
-##write.csv(Suppressor.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/SupressorGOAnalysis.csv")
-
-  ##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")
-
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Repress.KEGG = KEGG
-##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/RepressorKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Moderate == 1 , "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
-
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Moderate.GO = GO.wall
-##write.csv(Moderate.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateGOAnalysis.csv")
-
-  ##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")
-
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Moderate.KEGG = KEGG
-##write.csv(Moderate.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/ModerateKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Strong == 1 , "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
-
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Strong.GO = GO.wall
-##write.csv(Strong.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongGOAnalysis.csv")
-
-  ##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")
-
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Strong.KEGG = KEGG
-##write.csv(Strong.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/StrongKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
-
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Lethal.GO = GO.wall
-##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalGOAnalysis.csv")
-
-  ##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")
-
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Lethal.KEGG = KEGG
-##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/LethalKEGGAnalysis.csv")
-
-##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
-##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
-##genes[sigs] = 1
-##pwf=nullp(genes,"dm3","geneSymbol")
-  ##GO.wall=goseq(pwf,"dm3","geneSymbol")
-##GO.wall=goseq(pwf,"dm3","geneSymbol", method = "Hypergeometric")
-
-##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
-##row.names(GO.wall) = GO.wall$category
-##Enhance.GO = GO.wall
-##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerGOAnalysis.csv")
-
-  ##KEGG=goseq(pwf,gene2cat=kegg)
-##KEGG=goseq(pwf,gene2cat=kegg, method = "Hypergeometric")
-
-##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
-##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
-##KEGG$Name=kegg.names[row.names(KEGG),1]
-##Enhance.KEGG = KEGG
-##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/DeficiencyScreen/DataFiles/EnhancerKEGGAnalysis.csv")
 
@@
 
-GO.data = Enhancer.GO
+GO.data = sup.GO
 GO.ontology = "BP"
@@
 GOMF.fig
+
+```
+
+```{r echo = F}
+
+sig.sup.GOcats = sup.GO[sup.GO$adjp <= .05, "category"]
+
+ss.gocat.genes = genesingo[sig.sup.GOcats]
+
+ss.gocat1.genes = (gene.location[gene.location$ensembl %in% as.character(ss.gocat.genes[[1]]),])
+
+ss.gocat1.dfs = genesindf[genesindf$FBgn %in% ss.gocat1.genes$FBgn,]
+
+(unique(ss.gocat1.dfs$Df))
 

### 2025-08-10 RussoPaper/AnaDataAnalysis.Rmd
ana update

@@
 
-```{r echo = F, warning=FALSE, message=FALSE}
+```{r echo=F, message=FALSE, warning=FALSE}
 
@@
 
-temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250621_AllAnaData.csv")
-
+temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250809_AllAnaData.csv", row.names = 1)
+temp = temp[temp$Boutons != "x",]
+temp$Boutons = as.numeric(temp$Boutons)
 temp$Genotype[temp$Genotype == "WT-cr/LoxP"] = "WT(cr/LoxP)"
@@
 temp$Genotype[temp$Genotype == "OK371>gbb [WTcr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
+temp$Genotype[temp$Genotype == "OK371>gbb [WT-cr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
+temp$Genotype[temp$Genotype == "OK371>gbb [G85Rcr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"
 temp$Genotype[temp$Genotype == "OK371>gbb [G85cr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"
@@
 temp$Genotype[temp$Genotype == "OK371>saxA [WTcr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
+temp$Genotype[temp$Genotype == "OK371>saxA [WT-cr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
 temp$Genotype[temp$Genotype == "OK371>saxA [G85Rcr/G85Rhr]"] = "OK371-saxA; G85R(cr/LoxP)"
@@
                         Boutons$Segment == "3",]
+boutdata$Boutons = as.numeric(boutdata$Boutons)
 
@@
 Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "6-7" &
-                        Boutons$Segment == "3",]
+boutdata = Boutons[Boutons$NMJ == "4" &
+                        Boutons$Segment == "5",]
+boutdata = boutdata[boutdata$Boutons != "x",]
+boutdata$Boutons = as.numeric(boutdata$Boutons)
 
@@
 knitr::kable(t.table,
-             caption = 'All t-tests for segment 3, NMJ 6-7 Bouton Counts.')  %>%
+             caption = 'All t-tests for segment 3, NMJ 4 Bouton Counts.')  %>%
 kable_styling() %>%
@@
 
-```{r echo = F, include = F}
+```{r echo = F, fig.width = 7}
 
 Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "4" &
-                        Boutons$Segment == "4",]
+boutdata = Boutons[Boutons$NMJ == "6-7" &
+                        Boutons$Segment == "3",]
+boutdata$Boutons = as.numeric(boutdata$Boutons)
 
@@
 
-```{r echo = F, include = F}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "6-7" &
-                        Boutons$Segment == "4",]
-
-geno = unique(boutdata$Genotype)
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-plot.bouts(boutdata)
-
-```
-
-```{r echo = F, include = F}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "4" &
-                        Boutons$Segment == "5",]
-
-geno = unique(boutdata$Genotype)
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-plot.bouts(boutdata)
-
-```
-
-```{r echo = F, include = F}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "6-7" &
-                        Boutons$Segment == "5",]
-
-geno = unique(boutdata$Genotype)
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-plot.bouts(boutdata)
-
-```
-
-```{r echo = F, include = F}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "4" &
-                        Boutons$Segment == "6",]
-
-geno = unique(boutdata$Genotype)
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-plot.bouts(boutdata)
-
-```
-
-```{r echo = F, include = F}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "6-7" &
-                        Boutons$Segment == "6",]
-
-geno = unique(boutdata$Genotype)
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-plot.bouts(boutdata)
-
-```
-
-```{r echo = F, fig.width = 7}
-
-Boutons = temp[temp$Data == "Boutons",]
-boutdata = Boutons[Boutons$NMJ == "4" &
-                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
-boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)
-
-geno = unique(boutdata$Genotype)
-geno = geno[c(1,5,2,6,3,7,4,8)]
-
-boutdata$Genotype = factor(boutdata$Genotype, levels = geno)
-
-boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]))
-
-par(mar=c(4, 4.1, 4.1, 5.6))
-
-plot(x = c(.75,1.25),
-     y = rep(boutmeans[1], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1],
-     ylim = c(0, max(boutdata$Boutons)*1.1),
-     xlim = c(.5, length(na.omit(boutmeans))+.5),
-     xaxt = "n",
-     ylab="Bouton Number",
-     yaxt = "n",
-     xlab = NA,
-     frame = F,
-     main = paste("Larval muscle NMJ 4 bouton counts, segments 3-6"))
-
-lines(x = c(.65,1.35),
-     y = rep(boutmeans[1], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(1.65,2.35),
-     y = rep(boutmeans[2], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(2.65,3.35),
-     y = rep(boutmeans[3], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(3.65,4.35),
-     y = rep(boutmeans[4], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(4.65,5.35),
-     y = rep(boutmeans[5], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(5.65,6.35),
-     y = rep(boutmeans[6], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(6.65,7.35),
-     y = rep(boutmeans[7], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(7.65,8.35),
-     y = rep(boutmeans[8], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-beeswarm(boutdata$Boutons~boutdata$Genotype,
-       pch = 21,
-       method = "center",
-       bg = hex(std.colors[1:2],.5),
-       add = T)
-
-lines(x = c(2.5,2.5),
-      y = c(-2.5,50),
-      lty = 2,
-      xpd = T)
-
-lines(x = c(4.5,4.5),
-      y = c(-2.5,50),
-      lty = 2,
-      xpd = T)
-
-lines(x = c(6.5,6.5),
-      y = c(-2.5,50),
-      lty = 2,
-      xpd = T)
-
-axis(side = 1,
-     at = c(1.5, 3.5, 5.5, 7.5),
-     labels = c(3,4,5,6),
-     las = 1,
-     lwd = 0,
-     line = -.75)
-
-axis(side = 1,
-     at = c(4.5),
-     labels = c("Larval Segment"),
-     las = 1,
-     lwd = 0,
-     cex = 2,
-     line = 0.5)
-
-    lines(x = c(.2, length(na.omit(boutmeans))+.5),
-       y = c(0,0),
-       lwd = 3,
-       xpd = T)
-
-  y.at = c(0, 10*1:5)
-
-  axis(side = 2,
-       at = y.at,
-       lwd = 2,
-       line = 0,
-       labels = F,
-       xpd = T,
-       las = 2)
-
-  axis(side = 2,
-       at = y.at,
-       lwd = 3,
-       line = 0,
-       labels = T,
-       xpd = T,
-       las = 2)
-
-  legend('topright',
-       inset=c(-0.185,0),
-       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)'), 
-       fill = std.colors[1:2],
-       cex = 1,
-       bty = 'n',
-       pt.cex = .5,
-       xpd = T)
-
-```
-
 ```{r echo = F}
@@
 
-t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
-              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
-              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
-              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
-              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
-              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
-              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
-              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])
+t.data = list("WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "WT(cr/LoxP)"],
+                    "G85R(cr/hr)" = btd$Boutons[btd$Genotype == "G85R(cr/hr)"],
+                    "OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
+                    "OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
+                    "OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
+                    "OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
 
@@
 knitr::kable(t.table,
-             caption = 'All t-tests for NMJ 4, all segments Bouton Counts.')  %>%
+             caption = 'All t-tests for segment 3, NMJ 6-7 Bouton Counts.')  %>%
 kable_styling() %>%
@@
 boutdata = Boutons[Boutons$NMJ == "6-7" &
-                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
-boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)
-
+                        Boutons$Segment == "5",]
+boutdata = boutdata[boutdata$Boutons != "x",]
+boutdata$Boutons = as.numeric(boutdata$Boutons)
 geno = unique(boutdata$Genotype)
-geno = geno[c(1,5,2,6,3,7,4,8)]
-
-boutdata$Genotype = factor(boutdata$Genotype, levels = geno)
-
-boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
-              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]))
-
-par(mar=c(4, 4.1, 4.1, 5.6))
-
-plot(x = c(.75,1.25),
-     y = rep(boutmeans[1], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1],
-     ylim = c(0, max(boutdata$Boutons)*1.1),
-     xlim = c(.5, length(na.omit(boutmeans))+.5),
-     xaxt = "n",
-     ylab="Bouton Number",
-     yaxt = "n",
-     xlab = NA,
-     frame = F,
-     main = paste("Larval muscle NMJ 6-7 bouton counts, segments 3-6"))
-
-lines(x = c(.65,1.35),
-     y = rep(boutmeans[1], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(1.65,2.35),
-     y = rep(boutmeans[2], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(2.65,3.35),
-     y = rep(boutmeans[3], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(3.65,4.35),
-     y = rep(boutmeans[4], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(4.65,5.35),
-     y = rep(boutmeans[5], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(5.65,6.35),
-     y = rep(boutmeans[6], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-lines(x = c(6.65,7.35),
-     y = rep(boutmeans[7], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[1])
-
-lines(x = c(7.65,8.35),
-     y = rep(boutmeans[8], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[2])
-
-beeswarm(boutdata$Boutons~boutdata$Genotype,
-       pch = 21,
-       method = "center",
-       bg = hex(std.colors[1:2],.5),
-       add = T)
-
-lines(x = c(2.5,2.5),
-      y = c(-5,100),
-      lty = 2,
-      xpd = T)
-
-lines(x = c(4.5,4.5),
-      y = c(-5,100),
-      lty = 2,
-      xpd = T)
-
-lines(x = c(6.5,6.5),
-      y = c(-5,100),
-      lty = 2,
-      xpd = T)
-
-axis(side = 1,
-     at = c(1.5, 3.5, 5.5, 7.5),
-     labels = c(3,4,5,6),
-     las = 1,
-     lwd = 0,
-     line = -.75)
-
-axis(side = 1,
-     at = c(4.5),
-     labels = c("Larval Segment"),
-     las = 1,
-     lwd = 0,
-     cex = 2,
-     line = 0.5)
-
-    lines(x = c(.2, length(na.omit(boutmeans))+.5),
-       y = c(0,0),
-       lwd = 3,
-       xpd = T)
-
-  y.at = c(0, 10*1:10)
-
-  axis(side = 2,
-       at = y.at,
-       lwd = 2,
-       line = 0,
-       labels = F,
-       xpd = T,
-       las = 2)
-
-  axis(side = 2,
-       at = y.at,
-       lwd = 3,
-       line = 0,
-       labels = T,
-       xpd = T,
-       las = 2)
-
-  legend('topright',
-       inset=c(-0.185,0),
-       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)'), 
-       fill = std.colors[1:2],
-       cex = 1,
-       bty = 'n',
-       pt.cex = .5,
-       xpd = T)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
 
@@
 knitr::kable(t.table,
-             caption = 'All t-tests for NMJ 6-7, all segments Bouton Counts.')  %>%
+             caption = 'All t-tests for segment 3, NMJ 6-7 Bouton Counts.')  %>%
 kable_styling() %>%
@@
 
-```{r echo = F}
-
-VNC = temp[temp$Data == "VNC",]
-VNC$CTCF = VNC$CTCF/1000
-geno = unique(VNC$Genotype)
-VNC$color = as.numeric(VNC$Genotype) + ((VNC$Experiment -1)*6)
-VNC$color = c('navy', "orange2",
-               "darkgreen", "turquoise4",
-               "firebrick","deeppink3",
-               "royalblue", 'gold',
-               "green", 'cyan',
-               "red", "pink") [VNC$color]
-
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "4" &
+                        Boutons$Segment == "4",]
+
+geno = unique(boutdata$Genotype)
 labels = c("WT", "G85R",
@@
 
-vncmeans = c(mean(VNC[VNC$Genotype == geno[1], "CTCF"]),
-              mean(VNC[VNC$Genotype == geno[2], "CTCF"]),
-              mean(VNC[VNC$Genotype == geno[3], "CTCF"]),
-              mean(VNC[VNC$Genotype == geno[4], "CTCF"]),
-              mean(VNC[VNC$Genotype == geno[5], "CTCF"]),
-              mean(VNC[VNC$Genotype == geno[6], "CTCF"]))
-
-par(mar=c(6.25, 4.1, 4.1, 5.6))
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "6-7" &
+                        Boutons$Segment == "4",]
+
+geno = unique(boutdata$Genotype)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "4" &
+                        Boutons$Segment == "5",]
+
+geno = unique(boutdata$Genotype)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "6-7" &
+                        Boutons$Segment == "5",]
+
+geno = unique(boutdata$Genotype)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "4" &
+                        Boutons$Segment == "6",]
+
+geno = unique(boutdata$Genotype)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "6-7" &
+                        Boutons$Segment == "6",]
+
+geno = unique(boutdata$Genotype)
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+plot.bouts(boutdata)
+
+```
+
+```{r echo = F, fig.width = 10}
+
+Boutons = temp[temp$Data == "Boutons",]
+
+#boutdata = Boutons[Boutons$NMJ == "4" &
+#                     (Boutons$Genotype == "WT(cr/LoxP)" | #Boutons$Genotype == "G85R(cr/hr)"),]
+
+boutdata = Boutons[Boutons$NMJ == "4",]
+boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)
+
+geno = unique(boutdata$Genotype)
+geno = geno[c(1,5, 9:12, 
+              2,6, 
+              3,7, 13:16,
+              4,8)]
+
+boutdata$Genotype = factor(boutdata$Genotype, levels = geno)
+
+boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[9], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[10], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[11], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[12], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[13], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[14], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[15], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[16], "Boutons"]))
+
+par(mar=c(4, 4.1, 4.1, 5.6))
 
 plot(x = c(.75,1.25),
-     y = rep(vncmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
      col = std.colors[1],
-     ylim = c(0, max(VNC$CTCF)*1.1),
-     xlim = c(.5, length(na.omit(vncmeans))+.5),
+     ylim = c(0, max(boutdata$Boutons)*1.1),
+     xlim = c(.5, length(na.omit(boutmeans))+.5),
      xaxt = "n",
-     ylab="Fluorescence Intensity/1000",
+     ylab="Bouton Number",
      yaxt = "n",
@@
      frame = F,
-     main = paste("Larval VNC fluorescence"))
+     main = paste("Larval muscle NMJ 4 bouton counts, segments 3-6"))
 
 lines(x = c(.65,1.35),
-     y = rep(vncmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
 lines(x = c(1.65,2.35),
-     y = rep(vncmeans[2], 2),
+     y = rep(boutmeans[2], 2),
      type = 'l',
@@
 
-if(length(na.omit(vncmeans)>2)){
 lines(x = c(2.65,3.35),
-     y = rep(vncmeans[3], 2),
+     y = rep(boutmeans[3], 2),
      type = 'l',
@@
 lines(x = c(3.65,4.35),
-     y = rep(vncmeans[4], 2),
+     y = rep(boutmeans[4], 2),
      type = 'l',
@@
 lines(x = c(4.65,5.35),
-     y = rep(vncmeans[5], 2),
+     y = rep(boutmeans[5], 2),
      type = 'l',
@@
 lines(x = c(5.65,6.35),
-     y = rep(vncmeans[6], 2),
+     y = rep(boutmeans[6], 2),
      type = 'l',
@@
      col = std.colors[6])
-}
-
-beeswarm(VNC$CTCF~VNC$Genotype,
-       #pch = 21,
-       pwpch = 20+VNC$Experiment,
+
+lines(x = c(6.65,7.35),
+     y = rep(boutmeans[7], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(7.65,8.35),
+     y = rep(boutmeans[8], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+lines(x = c(8.65,9.35),
+     y = rep(boutmeans[9], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(9.65,10.35),
+     y = rep(boutmeans[10], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+lines(x = c(10.65,11.35),
+     y = rep(boutmeans[11], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[3])
+
+lines(x = c(11.65,12.35),
+     y = rep(boutmeans[12], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[4])
+
+lines(x = c(12.65,13.35),
+     y = rep(boutmeans[13], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[5])
+
+lines(x = c(13.65,14.35),
+     y = rep(boutmeans[14], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[6])
+
+lines(x = c(14.65,15.35),
+     y = rep(boutmeans[15], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(15.65,16.35),
+     y = rep(boutmeans[16], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+beeswarm(boutdata$Boutons~boutdata$Genotype,
+       pch = 21,
        method = "center",
-       #bg = hex(unique(std.colors[as.numeric(VNC$Genotype)]),.5),
-       pwbg = hex(VNC$color, .75),
+       bg = hex(std.colors[c(1:6, 1:2, 1:6, 1:2)],.5),
        add = T)
 
+lines(x = c(6.5,6.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(8.5,8.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(14.5,14.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
 axis(side = 1,
-     at = c(1:length(na.omit(vncmeans))),
-     labels = c(labels)[1:length(na.omit(vncmeans))],
-     las = 2,
+     at = c(3.5, 7.5, 11.5, 15.5),
+     labels = c(3,4,5,6),
+     las = 1,
      lwd = 0,
@@
 
-    lines(x = c(.225 + .3/length(na.omit(vncmeans)), length(na.omit(vncmeans))+.5),
+axis(side = 1,
+     at = c(8.5),
+     labels = c("Larval Segment"),
+     las = 1,
+     lwd = 0,
+     cex = 2,
+     line = 0.5)
+
+    lines(x = c(-.10, length(na.omit(boutmeans))+.5),
        y = c(0,0),
@@
 
-  y.at = c(0,500, 1000, 1500)
+  y.at = c(0, 10*1:7)
 
@@
 
+  legend('topright',
+       inset=c(-0.14,0),
+       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)', 
+                  "OK371-gbb; WT(cr/LoxP)", "OK371-gbb; G85R(cr/LoxP)",
+                  "OK371-saxA; WT(cr/LoxP)","OK371-saxA; G85R(cr/LoxP)"), 
+       fill = std.colors[1:6],
+       cex = .5,
+       bty = 'n',
+       pt.cex = .4,
+       xpd = T)
+
 ```
@@
 ```{r echo = F}
-btd = temp[temp$Data == "VNC",]
-
-t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
-                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
-                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
-                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
-                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
-                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+
+btd = boutdata
+
+t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
+              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
+              "3 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; WT(cr/LoxP)"],
+              "3 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; G85R(cr/LoxP)"],
+              "3 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; WT(cr/LoxP)"],
+              "3 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; G85R(cr/LoxP)"],
+              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
+              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
+              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
+              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
+              "5 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; WT(cr/LoxP)"],
+              "5 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; G85R(cr/LoxP)"],
+              "5 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; WT(cr/LoxP)"],
+              "5 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; G85R(cr/LoxP)"],
+              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
+              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])
 
@@
 knitr::kable(t.table,
-             caption = 'All t-tests for VNC data.')  %>%
+             caption = 'All t-tests for NMJ 4, all segments Bouton Counts.')  %>%
 kable_styling() %>%
@@
 
-```{r echo = F}
-
-NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "4",]
-NMJ$CTCF = NMJ$CTCF/1000
-geno = unique(NMJ$Genotype)
-NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
-NMJ$color = c('navy', "orange2",
-               "darkgreen", "turquoise4",
-               "firebrick","deeppink3",
-               "royalblue", 'gold',
-               "green", 'cyan',
-               "red", "pink") [NMJ$color]
-
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))
-
-par(mar=c(6.25, 4.1, 4.1, 5.6))
+```{r echo = F, fig.width = 7, include = F}
+
+Boutons = temp[temp$Data == "Boutons",]
+boutdata = Boutons[Boutons$NMJ == "6-7" &
+                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
+boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)
+
+geno = unique(boutdata$Genotype)
+geno = geno[c(1,5,2,6,3,7,4,8)]
+
+boutdata$Genotype = factor(boutdata$Genotype, levels = geno)
+
+boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]))
+
+par(mar=c(4, 4.1, 4.1, 5.6))
 
 plot(x = c(.75,1.25),
-     y = rep(nmjmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
      col = std.colors[1],
-     ylim = c(0, max(NMJ$CTCF)*1.1),
-     xlim = c(.5, length(na.omit(nmjmeans))+.5),
+     ylim = c(0, max(boutdata$Boutons)*1.1),
+     xlim = c(.5, length(na.omit(boutmeans))+.5),
      xaxt = "n",
-     ylab="Fluorescence Intensity/1000",
+     ylab="Bouton Number",
      yaxt = "n",
@@
      frame = F,
-     main = paste("Larval segment 3, NMJ 4 fluorescence"))
+     main = paste("Larval muscle NMJ 6-7 bouton counts, segments 3-6"))
 
 lines(x = c(.65,1.35),
-     y = rep(nmjmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
 lines(x = c(1.65,2.35),
-     y = rep(nmjmeans[2], 2),
+     y = rep(boutmeans[2], 2),
      type = 'l',
@@
 
-if(length(na.omit(nmjmeans)>2)){
 lines(x = c(2.65,3.35),
-     y = rep(nmjmeans[3], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[3])
+     y = rep(boutmeans[3], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
 
 lines(x = c(3.65,4.35),
-     y = rep(nmjmeans[4], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[4])
+     y = rep(boutmeans[4], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
 
 lines(x = c(4.65,5.35),
-     y = rep(nmjmeans[5], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[5])
+     y = rep(boutmeans[5], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
 
 lines(x = c(5.65,6.35),
-     y = rep(nmjmeans[6], 2),
-     type = 'l',
-     lwd = 3,
-     col = std.colors[6])
-}
-
-beeswarm(NMJ$CTCF~NMJ$Genotype,
-       #pch = 21,
-       pwpch = 20+NMJ$Experiment,
+     y = rep(boutmeans[6], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+lines(x = c(6.65,7.35),
+     y = rep(boutmeans[7], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(7.65,8.35),
+     y = rep(boutmeans[8], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+beeswarm(boutdata$Boutons~boutdata$Genotype,
+       pch = 21,
        method = "center",
-       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
-       pwbg = hex(NMJ$color, .75),
+       bg = hex(std.colors[1:2],.5),
        add = T)
 
+lines(x = c(2.5,2.5),
+      y = c(-5,100),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(4.5,4.5),
+      y = c(-5,100),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(6.5,6.5),
+      y = c(-5,100),
+      lty = 2,
+      xpd = T)
+
 axis(side = 1,
-     at = c(1:length(na.omit(nmjmeans))),
-     labels = c(labels)[1:length(na.omit(nmjmeans))],
-     las = 2,
+     at = c(1.5, 3.5, 5.5, 7.5),
+     labels = c(3,4,5,6),
+     las = 1,
      lwd = 0,
@@
 
-    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
+axis(side = 1,
+     at = c(4.5),
+     labels = c("Larval Segment"),
+     las = 1,
+     lwd = 0,
+     cex = 2,
+     line = 0.5)
+
+    lines(x = c(.2, length(na.omit(boutmeans))+.5),
        y = c(0,0),
@@
 
-  y.at = c(0, 500, 1000, 1500, 2000)
+  y.at = c(0, 10*1:10)
 
@@
 
-```
-
-```{r echo = F}
-btd = temp[temp$Data == "NMJ" & temp$NMJ == "4",]
-
-t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
-                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
-                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
-                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
-                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
-                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+  legend('topright',
+       inset=c(-0.185,0),
+       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)'), 
+       fill = std.colors[1:2],
+       cex = 1,
+       bty = 'n',
+       pt.cex = .5,
+       xpd = T)
+
+```
+
+```{r echo = F, include = F}
+
+btd = boutdata
+
+t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
+              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
+              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
+              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
+              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
+              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
+              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
+              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])
 
@@
 knitr::kable(t.table,
-             caption = 'All t-tests for VNC data.')  %>%
+             caption = 'All t-tests for NMJ 6-7, all segments Bouton Counts.')  %>%
 kable_styling() %>%
@@
 
-```{r echo = F}
-
-NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]
-NMJ$CTCF = NMJ$CTCF/1000
-geno = unique(NMJ$Genotype)
-NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
-NMJ$color = c('navy', "orange2",
-               "darkgreen", "turquoise4",
-               "firebrick","deeppink3",
-               "royalblue", 'gold',
-               "green", 'cyan',
-               "red", "pink") [NMJ$color]
-
-labels = c("WT", "G85R",
-           "OK-gbb WT", "OK-gbb G85R",
-           "OK-SaxA WT", "OK-SaxA G85R")
-
-nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
-              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))
-
-par(mar=c(6.25, 4.1, 4.1, 5.6))
+```{r echo = F, fig.width = 10}
+
+Boutons = temp[temp$Data == "Boutons",]
+
+#boutdata = Boutons[Boutons$NMJ == "6-7" &
+#                     (Boutons$Genotype == "WT(cr/LoxP)" | #Boutons$Genotype == "G85R(cr/hr)"),]
+
+boutdata = Boutons[Boutons$NMJ == "6-7",]
+boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)
+
+geno = unique(boutdata$Genotype)
+geno = geno[c(1,5, 9:12, 
+              2,6, 
+              3,7, 13:16,
+              4,8)]
+
+boutdata$Genotype = factor(boutdata$Genotype, levels = geno)
+
+boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[9], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[10], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[11], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[12], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[13], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[14], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[15], "Boutons"]),
+              mean(boutdata[boutdata$Genotype == geno[16], "Boutons"]))
+
+par(mar=c(4, 4.1, 4.1, 5.6))
 
 plot(x = c(.75,1.25),
-     y = rep(nmjmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
      frame = F,
-     main = paste("Larval segment 3, NMJ 6-7 fluorescence"))
+     main = paste("Larval muscle NMJ 6-7 bouton counts, segments 3-6"))
 
 lines(x = c(.65,1.35),
-     y = rep(nmjmeans[1], 2),
+     y = rep(boutmeans[1], 2),
      type = 'l',
@@
 
-if(length(na.omit(nmjmeans)>2)){
 lines(x = c(2.65,3.35),
-     y = rep(nmjmeans[3], 2),
+     y = rep(boutmeans[3], 2),
      type = 'l',
@@
 lines(x = c(3.65,4.35),
-     y = rep(nmjmeans[4], 2),
+     y = rep(boutmeans[4], 2),
      type = 'l',
@@
 lines(x = c(4.65,5.35),
-     y = rep(nmjmeans[5], 2),
+     y = rep(boutmeans[5], 2),
      type = 'l',
@@
 lines(x = c(5.65,6.35),
-     y = rep(nmjmeans[6], 2),
+     y = rep(boutmeans[6], 2),
      type = 'l',
@@
      col = std.colors[6])
-}
-
-beeswarm(NMJ$CTCF~NMJ$Genotype,
-       #pch = 21,
-       pwpch = 20+NMJ$Experiment,
+
+lines(x = c(6.65,7.35),
+     y = rep(boutmeans[7], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(7.65,8.35),
+     y = rep(boutmeans[8], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+lines(x = c(8.65,9.35),
+     y = rep(boutmeans[9], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(9.65,10.35),
+     y = rep(boutmeans[10], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+lines(x = c(10.65,11.35),
+     y = rep(boutmeans[11], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[3])
+
+lines(x = c(11.65,12.35),
+     y = rep(boutmeans[12], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[4])
+
+lines(x = c(12.65,13.35),
+     y = rep(boutmeans[13], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[5])
+
+lines(x = c(13.65,14.35),
+     y = rep(boutmeans[14], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[6])
+
+lines(x = c(14.65,15.35),
+     y = rep(boutmeans[15], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(15.65,16.35),
+     y = rep(boutmeans[16], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+beeswarm(boutdata$Boutons~boutdata$Genotype,
+       pch = 21,
        method = "center",
-       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
-       pwbg = hex(NMJ$color, .75),
+       bg = hex(std.colors[c(1:6, 1:2, 1:6, 1:2)],.5),
        add = T)
 
+lines(x = c(6.5,6.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(8.5,8.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
+lines(x = c(14.5,14.5),
+      y = c(-2.5,70),
+      lty = 2,
+      xpd = T)
+
 axis(side = 1,
-     at = c(1:length(na.omit(nmjmeans))),
-     labels = c(labels)[1:length(na.omit(nmjmeans))],
-     las = 2,
+     at = c(3.5, 7.5, 11.5, 15.5),
+     labels = c(3,4,5,6),
+     las = 1,
      lwd = 0,
@@
 
-    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
+axis(side = 1,
+     at = c(8.5),
+     labels = c("Larval Segment"),
+     las = 1,
+     lwd = 0,
+     cex = 2,
+     line = 0.5)
+
+    lines(x = c(-.10, length(na.omit(boutmeans))+.5),
        y = c(0,0),
@@
 
-  y.at = c(0, 1000, 2000, 3000, 4000, 5000)
+  y.at = c(0, 10*1:7)
 
@@
 ```{r echo = F}
-btd = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]
-
-t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
-                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
-                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
-                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
-                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
-                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+
+btd = boutdata
+
+t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
+              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
+              "3 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; WT(cr/LoxP)"],
+              "3 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; G85R(cr/LoxP)"],
+              "3 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; WT(cr/LoxP)"],
+              "3 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; G85R(cr/LoxP)"],
+              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
+              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
+              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
+              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
+              "5 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; WT(cr/LoxP)"],
+              "5 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; G85R(cr/LoxP)"],
+              "5 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; WT(cr/LoxP)"],
+              "5 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; G85R(cr/LoxP)"],
+              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
+              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])
 
@@
 knitr::kable(t.table,
+             caption = 'All t-tests for NMJ 4, all segments Bouton Counts.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F}
+
+VNC = temp[temp$Data == "VNC",]
+VNC$CTCF = VNC$CTCF/1000
+geno = unique(VNC$Genotype)
+VNC$color = as.numeric(VNC$Genotype) + ((VNC$Experiment -1)*6)
+VNC$color = c('navy', "orange2",
+               "darkgreen", "turquoise4",
+               "firebrick","deeppink3",
+               "royalblue", 'gold',
+               "green", 'cyan',
+               "red", "pink") [VNC$color]
+
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+vncmeans = c(mean(VNC[VNC$Genotype == geno[1], "CTCF"]),
+              mean(VNC[VNC$Genotype == geno[2], "CTCF"]),
+              mean(VNC[VNC$Genotype == geno[3], "CTCF"]),
+              mean(VNC[VNC$Genotype == geno[4], "CTCF"]),
+              mean(VNC[VNC$Genotype == geno[5], "CTCF"]),
+              mean(VNC[VNC$Genotype == geno[6], "CTCF"]))
+
+par(mar=c(6.25, 4.1, 4.1, 5.6))
+
+plot(x = c(.75,1.25),
+     y = rep(vncmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1],
+     ylim = c(0, max(VNC$CTCF)*1.1),
+     xlim = c(.5, length(na.omit(vncmeans))+.5),
+     xaxt = "n",
+     ylab="Fluorescence Intensity/1000",
+     yaxt = "n",
+     xlab = NA,
+     frame = F,
+     main = paste("Larval VNC fluorescence"))
+
+lines(x = c(.65,1.35),
+     y = rep(vncmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(1.65,2.35),
+     y = rep(vncmeans[2], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+if(length(na.omit(vncmeans)>2)){
+lines(x = c(2.65,3.35),
+     y = rep(vncmeans[3], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[3])
+
+lines(x = c(3.65,4.35),
+     y = rep(vncmeans[4], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[4])
+
+lines(x = c(4.65,5.35),
+     y = rep(vncmeans[5], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[5])
+
+lines(x = c(5.65,6.35),
+     y = rep(vncmeans[6], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[6])
+}
+
+beeswarm(VNC$CTCF~VNC$Genotype,
+       #pch = 21,
+       pwpch = 20+VNC$Experiment,
+       method = "center",
+       #bg = hex(unique(std.colors[as.numeric(VNC$Genotype)]),.5),
+       pwbg = hex(VNC$color, .75),
+       add = T)
+
+axis(side = 1,
+     at = c(1:length(na.omit(vncmeans))),
+     labels = c(labels)[1:length(na.omit(vncmeans))],
+     las = 2,
+     lwd = 0,
+     line = -.75)
+
+    lines(x = c(.225 + .3/length(na.omit(vncmeans)), length(na.omit(vncmeans))+.5),
+       y = c(0,0),
+       lwd = 3,
+       xpd = T)
+
+  y.at = c(0,500, 1000, 1500)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 2,
+       line = 0,
+       labels = F,
+       xpd = T,
+       las = 2)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 3,
+       line = 0,
+       labels = T,
+       xpd = T,
+       las = 2)
+
+```
+
+```{r echo = F}
+btd = temp[temp$Data == "VNC",]
+
+t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
+                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
+                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
+                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
+                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
+                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+
+t.table = data.frame(Genotype1 = character(),
+                     Genotype2 = character(),
+                     pval = numeric())
+
+i=1
+while(i <= length(t.data)){
+  j = i+1
+  while(j <= length(t.data)){
+    t.temp = data.frame(Genotype1 = geno[i],
+                        Genotype2 = geno[j],
+                        pval = t.test(x = t.data[[i]],
+                                      y = t.data[[j]],
+                                      paired = F)[[3]])
+    t.table = rbind(t.table, t.temp)
+      j = j+1
+  }
+  i = i+1
+}
+
+t.stripe = t.table$pval <= .05
+knitr::kable(t.table,
              caption = 'All t-tests for VNC data.')  %>%
@@
 ```
+
+```{r echo = F}
+
+NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "4",]
+NMJ$CTCF = NMJ$CTCF/1000
+geno = unique(NMJ$Genotype)
+NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
+NMJ$color = c('navy', "orange2",
+               "darkgreen", "turquoise4",
+               "firebrick","deeppink3",
+               "royalblue", 'gold',
+               "green", 'cyan',
+               "red", "pink") [NMJ$color]
+
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))
+
+par(mar=c(6.25, 4.1, 4.1, 5.6))
+
+plot(x = c(.75,1.25),
+     y = rep(nmjmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1],
+     ylim = c(0, max(NMJ$CTCF)*1.1),
+     xlim = c(.5, length(na.omit(nmjmeans))+.5),
+     xaxt = "n",
+     ylab="Fluorescence Intensity/1000",
+     yaxt = "n",
+     xlab = NA,
+     frame = F,
+     main = paste("Larval segment 3, NMJ 4 fluorescence"))
+
+lines(x = c(.65,1.35),
+     y = rep(nmjmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(1.65,2.35),
+     y = rep(nmjmeans[2], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+if(length(na.omit(nmjmeans)>2)){
+lines(x = c(2.65,3.35),
+     y = rep(nmjmeans[3], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[3])
+
+lines(x = c(3.65,4.35),
+     y = rep(nmjmeans[4], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[4])
+
+lines(x = c(4.65,5.35),
+     y = rep(nmjmeans[5], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[5])
+
+lines(x = c(5.65,6.35),
+     y = rep(nmjmeans[6], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[6])
+}
+
+beeswarm(NMJ$CTCF~NMJ$Genotype,
+       #pch = 21,
+       pwpch = 20+NMJ$Experiment,
+       method = "center",
+       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
+       pwbg = hex(NMJ$color, .75),
+       add = T)
+
+axis(side = 1,
+     at = c(1:length(na.omit(nmjmeans))),
+     labels = c(labels)[1:length(na.omit(nmjmeans))],
+     las = 2,
+     lwd = 0,
+     line = -.75)
+
+    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
+       y = c(0,0),
+       lwd = 3,
+       xpd = T)
+
+  y.at = c(0, 500, 1000, 1500, 2000)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 2,
+       line = 0,
+       labels = F,
+       xpd = T,
+       las = 2)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 3,
+       line = 0,
+       labels = T,
+       xpd = T,
+       las = 2)
+
+```
+
+```{r echo = F}
+btd = temp[temp$Data == "NMJ" & temp$NMJ == "4",]
+
+t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
+                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
+                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
+                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
+                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
+                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+
+t.table = data.frame(Genotype1 = character(),
+                     Genotype2 = character(),
+                     pval = numeric())
+
+i=1
+while(i <= length(t.data)){
+  j = i+1
+  while(j <= length(t.data)){
+    t.temp = data.frame(Genotype1 = geno[i],
+                        Genotype2 = geno[j],
+                        pval = t.test(x = t.data[[i]],
+                                      y = t.data[[j]],
+                                      paired = F)[[3]])
+    t.table = rbind(t.table, t.temp)
+      j = j+1
+  }
+  i = i+1
+}
+
+t.stripe = t.table$pval <= .05
+knitr::kable(t.table,
+             caption = 'All t-tests for VNC data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F}
+
+NMJ = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]
+NMJ$CTCF = NMJ$CTCF/1000
+geno = unique(NMJ$Genotype)
+NMJ$color = as.numeric(NMJ$Genotype) + ((NMJ$Experiment -1)*6)
+NMJ$color = c('navy', "orange2",
+               "darkgreen", "turquoise4",
+               "firebrick","deeppink3",
+               "royalblue", 'gold',
+               "green", 'cyan',
+               "red", "pink") [NMJ$color]
+
+labels = c("WT", "G85R",
+           "OK-gbb WT", "OK-gbb G85R",
+           "OK-SaxA WT", "OK-SaxA G85R")
+
+nmjmeans = c(mean(NMJ[NMJ$Genotype == geno[1], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[2], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[3], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[4], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[5], "CTCF"]),
+              mean(NMJ[NMJ$Genotype == geno[6], "CTCF"]))
+
+par(mar=c(6.25, 4.1, 4.1, 5.6))
+
+plot(x = c(.75,1.25),
+     y = rep(nmjmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1],
+     ylim = c(0, max(NMJ$CTCF)*1.1),
+     xlim = c(.5, length(na.omit(nmjmeans))+.5),
+     xaxt = "n",
+     ylab="Fluorescence Intensity/1000",
+     yaxt = "n",
+     xlab = NA,
+     frame = F,
+     main = paste("Larval segment 3, NMJ 6-7 fluorescence"))
+
+lines(x = c(.65,1.35),
+     y = rep(nmjmeans[1], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[1])
+
+lines(x = c(1.65,2.35),
+     y = rep(nmjmeans[2], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[2])
+
+if(length(na.omit(nmjmeans)>2)){
+lines(x = c(2.65,3.35),
+     y = rep(nmjmeans[3], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[3])
+
+lines(x = c(3.65,4.35),
+     y = rep(nmjmeans[4], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[4])
+
+lines(x = c(4.65,5.35),
+     y = rep(nmjmeans[5], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[5])
+
+lines(x = c(5.65,6.35),
+     y = rep(nmjmeans[6], 2),
+     type = 'l',
+     lwd = 3,
+     col = std.colors[6])
+}
+
+beeswarm(NMJ$CTCF~NMJ$Genotype,
+       #pch = 21,
+       pwpch = 20+NMJ$Experiment,
+       method = "center",
+       #bg = hex(unique(std.colors[as.numeric(NMJ$Genotype)]),.5),
+       pwbg = hex(NMJ$color, .75),
+       add = T)
+
+axis(side = 1,
+     at = c(1:length(na.omit(nmjmeans))),
+     labels = c(labels)[1:length(na.omit(nmjmeans))],
+     las = 2,
+     lwd = 0,
+     line = -.75)
+
+    lines(x = c(.225 + .3/length(na.omit(nmjmeans)), length(na.omit(nmjmeans))+.5),
+       y = c(0,0),
+       lwd = 3,
+       xpd = T)
+
+  y.at = c(0, 1000, 2000, 3000, 4000, 5000)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 2,
+       line = 0,
+       labels = F,
+       xpd = T,
+       las = 2)
+
+  axis(side = 2,
+       at = y.at,
+       lwd = 3,
+       line = 0,
+       labels = T,
+       xpd = T,
+       las = 2)
+
+```
+
+```{r echo = F}
+btd = temp[temp$Data == "NMJ" & temp$NMJ == "6-7",]
+
+t.data = list("WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "WT(cr/LoxP)"],
+                    "G85R(cr/hr)" = btd$CTCF[btd$Genotype == "G85R(cr/hr)"],
+                    "OK371-gbb; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; WT(cr/LoxP)"],
+                    "OK371-gbb; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-gbb; G85R(cr/LoxP)"],
+                    "OK371-saxA; WT(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; WT(cr/LoxP)"],
+                    "OK371-saxA; G85R(cr/LoxP)" = btd$CTCF[btd$Genotype == "OK371-saxA; G85R(cr/LoxP)"])
+
+t.table = data.frame(Genotype1 = character(),
+                     Genotype2 = character(),
+                     pval = numeric())
+
+i=1
+while(i <= length(t.data)){
+  j = i+1
+  while(j <= length(t.data)){
+    t.temp = data.frame(Genotype1 = geno[i],
+                        Genotype2 = geno[j],
+                        pval = t.test(x = t.data[[i]],
+                                      y = t.data[[j]],
+                                      paired = F)[[3]])
+    t.table = rbind(t.table, t.temp)
+      j = j+1
+  }
+  i = i+1
+}
+
+t.stripe = t.table$pval <= .05
+knitr::kable(t.table,
+             caption = 'All t-tests for VNC data.')  %>%
+kable_styling() %>%
+row_spec(c(1:nrow(t.table))[t.table$pval <= .05], bold = T, color = "black", background = "gold")
+
+```
+
+```{r echo = F, include=F}
+library(corrplot)
+cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
+row.names(cor.table) = paste0(cor.table[,1], ".", cor.table[,2], ".", cor.table[,3])
+colnames(cor.table) = paste0(cor.table[1,], ".", cor.table[2,], ".", cor.table[3,], ".", cor.table[4,])
+
+cor.table= cor.table[,-grep("Raw", colnames(cor.table))]
+
+cor.table[1,grep("Norm", colnames(cor.table))] = substr(cor.table[1,grep("Norm", colnames(cor.table))], 8, nchar(cor.table[1,grep("Norm", colnames(cor.table))]))
+
+cor.matrix = cor.table[5:nrow(cor.table), 4:ncol(cor.table)]
+cor.matrix = cor.matrix[grep("WT", row.names(cor.matrix)), ]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+WT.cor.data = cor.data
+
+cor.matrix = cor.table[5:nrow(cor.table), 4:ncol(cor.table)]
+cor.matrix = cor.matrix[grep("G85R", row.names(cor.matrix)), ]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+GR.cor.data = cor.data
+
+WT.cor.data = WT.cor.data[as.numeric(WT.cor.data$Factor1) < as.numeric(WT.cor.data$Factor2),]
+WT.cor.data$Geno = "WT"
+GR.cor.data = GR.cor.data[as.numeric(GR.cor.data$Factor1) > as.numeric(GR.cor.data$Factor2),]
+GR.cor.data$Geno = "G85R"
+
+cor.data = rbind(WT.cor.data, GR.cor.data)
+
+```
+
+```{r echo = F, fig.height=8, fig.width=8, include=F}
+bg.colors = colorRampPalette(c("royalblue", "deepskyblue", "yellow", "deeppink", "violetred"))(200)
+
+plot.bg = bg.colors[100*(cor.data$Corr + 1)]
+
+#plot.bg[cor.data$Corr == 2] = "white"
+
+plot.cex = 2*abs(cor.data$Corr)+.5
+
+#plot.cex[cor.data$Corr == 2] = 2.5
+
+par(mar = c(6,6,4,3))
+
+plot(x = as.numeric(cor.data$Factor1),
+     y = as.numeric(cor.data$Factor2),
+     pch = 21,
+     bg = plot.bg,
+     cex = plot.cex,
+     xaxt = "n",
+     yaxt = "n",
+     ylab = "",
+     xlab = "",
+     bty = "n",
+     main = "")
+
+lines(x = c(.5,23),
+      y = c(.5,23),
+      lty = 2,
+      lwd = 2)
+
+lines(x = c(.5, .5),
+      y = c(.5,21.5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(x = c(-0.25, -0.25),
+      y = c(-.25,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(x = c(-1.25, -1.25),
+      y = c(-1.25,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(x = c(-2, -2),
+      y = c(-2,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(x = c(.5,21.5),
+      y = c(.5, .5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(y = c(-.25, -.25),
+      x = c(-.25,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+text(x = 22,
+     y = 0,
+     labels = "Segment",
+     xpd = T,
+     cex = .5)
+
+text(x = 22,
+     y = -.75,
+     labels = "NMJ",
+     xpd = T,
+     cex = .5)
+
+text(x = 22,
+     y = -1.6,
+     labels = "Side",
+     xpd = T,
+     cex = .5)
+
+lines(y = c(-1.25, -1.25),
+      x = c(-1.25,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(y = c(-2, -2),
+      x = c(-2,21.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+axis(side = 1,
+     at = c(8.5, 17, 19.5),
+     lwd = 0,
+     line = 2,
+     labels = c("Boutons", "VNC", "NMJ"),
+     xpd = T,
+     las = 1,
+     cex.axis = .75)
+
+axis(side = 1,
+     at = c(17, 19.5),
+     lwd = 0,
+     line = 3,
+     labels = c("pMad", "pMad"),
+     xpd = T,
+     las = 1,
+     cex.axis = .75)
+
+axis(side = 1,
+     at = c(1:21),
+     lwd = 0,
+     line = 1,
+     labels = cor.table[2, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+axis(side = 1,
+     at = c(1:21),
+     lwd = 0,
+     line = -.25,
+     labels = cor.table[3, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+axis(side = 1,
+     at = c(1:21),
+     lwd = 0,
+     line = -1.5,
+     labels = cor.table[4, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+axis(side = 2,
+     at = c(8.5, 17, 19.5),
+     lwd = 0,
+     line = 3,
+     labels = c("Boutons", "VNC", "NMJ"),
+     xpd = T,
+     srt = 270,
+     cex.axis = .75)
+
+axis(side = 2,
+     at = c(17, 19.5),
+     lwd = 0,
+     line = 2.5,
+     labels = c("pMad", "pMad"),
+     xpd = T,
+     srt = 270,
+     cex.axis = .75)
+
+axis(side = 2,
+     at = c(1:21),
+     lwd = 0,
+     line = 1.5,
+     labels = cor.table[2, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+axis(side = 2,
+     at = c(1:21),
+     lwd = 0,
+     line = 0.25,
+     labels = cor.table[3, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+axis(side = 2,
+     at = c(1:21),
+     lwd = 0,
+     line = -1,
+     labels = cor.table[4, 4:ncol(cor.table)],
+     xpd = T,
+     las = 1,
+     cex.axis = .5)
+
+arrows(x0 = 22,
+       y0 = 21,
+       x1 = 22,
+       y1 = 13,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+arrows(x0 = 21,
+       y0 = 22,
+       x1 = 13,
+       y1 = 22,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+text(x = 17,
+     y = 22.5,
+     labels = ("Silent"),
+     xpd = T)
+
+text(x = 22.5,
+     y = 17,
+     labels = ("G85R"),
+     srt = 270,
+     xpd = T)
+
+axis(side = 3,
+     label = "Correlation for WT and G85R, All Lines",
+     at = 11,
+     line = 1.5,
+     cex = 1.5,
+     lwd = 0)
+
+```
+
+```{r echo = F, include=F}
+
+cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
+
+cor.table= cor.table[,-grep("Raw", cor.table[1,])]
+
+cor.table[1,grep("Norm", cor.table[1,])] = substr(cor.table[1,grep("Norm", cor.table[1,])], 8, nchar(cor.table[1,grep("Norm", cor.table[1,])]))
+
+cor.tablea = cor.table[,cor.table[2,] == "a"]
+cor.tablea = cbind(cor.tablea, cor.table[,20])
+cor.tablea = cbind(cor.tablea, cor.table[,1])
+
+cor.tableb = cor.table[,cor.table[2,] == "b"]
+cor.tableb = cbind(cor.tableb, cor.table[,20])
+cor.tableb = cbind(cor.tableb, cor.table[,1])
+
+colnames(cor.tablea) = paste0(cor.tablea[1,], ".", cor.tablea[3,], ".", cor.tablea[4,])
+colnames(cor.tableb) = paste0(cor.tableb[1,], ".", cor.tableb[3,], ".", cor.tableb[4,])
+
+cor.table = rbind(cor.tablea[c(1,3:nrow(cor.tablea)),],cor.tableb[5:nrow(cor.tableb),])
+
+cor.matrix = cor.table[grep("WT", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+WT.cor.data = cor.data
+
+cor.matrix = cor.table[grep("G85R", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+GR.cor.data = cor.data
+
+WT.cor.data = WT.cor.data[as.numeric(WT.cor.data$Factor1) < as.numeric(WT.cor.data$Factor2),]
+WT.cor.data$Geno = "WT"
+GR.cor.data = GR.cor.data[as.numeric(GR.cor.data$Factor1) > as.numeric(GR.cor.data$Factor2),]
+GR.cor.data$Geno = "G85R"
+
+cor.data = rbind(WT.cor.data, GR.cor.data)
+
+```
+
+```{r echo = F, fig.height=8, fig.width=8, include=F}
+bg.colors = colorRampPalette(c("royalblue", "deepskyblue", "yellow", "deeppink", "violetred"))(200)
+
+plot.bg = bg.colors[100*(cor.data$Corr + 1)]
+
+#plot.bg[cor.data$Corr == 2] = "white"
+
+plot.cex = 2*abs(cor.data$Corr)+.5
+
+#plot.cex[cor.data$Corr == 2] = 2.5
+
+par(mar = c(8,8,4,3))
+
+plot(x = as.numeric(cor.data$Factor1),
+     y = as.numeric(cor.data$Factor2),
+     pch = 21,
+     bg = plot.bg,
+     cex = plot.cex,
+     xaxt = "n",
+     yaxt = "n",
+     ylab = "",
+     xlab = "",
+     bty = "n",
+     main = "")
+
+lines(x = c(.5,14),
+      y = c(.5,14),
+      lty = 2,
+      lwd = 2)
+
+lines(x = c(.5, .5),
+      y = c(.5,11.5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(x = c(.5,11.5),
+      y = c(.5, .5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(x = c(-0.25, -0.25),
+      y = c(-.25,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(x = c(-1, -1),
+      y = c(-1,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(y = c(-.25, -.25),
+      x = c(-.25,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(y = c(-1, -1),
+      x = c(-1,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+text(x = 11.8,
+     y = 0,
+     labels = "NMJ",
+     xpd = T,
+     cex = .8)
+
+text(x = 11.8,
+     y = -.5,
+     labels = "Segment",
+     xpd = T,
+     cex = .8)
+
+arrows(x0 = 11.5,
+       y0 = 10.5,
+       x1 = 11.5,
+       y1 = 7,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+arrows(x0 = 10.5,
+       y0 = 11.5,
+       x1 = 7,
+       y1 = 11.5,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+text(x = 10,
+     y = 11.75,
+     labels = ("Silent"),
+     xpd = T)
+
+text(x = 11.75,
+     y = 10,
+     labels = ("G85R"),
+     srt = 270,
+     xpd = T)
+
+axis(side = 1,
+     at = c(4.5, 9.5, 11),
+     lwd = 0,
+     line = 3.5,
+     labels = c("Boutons", "NMJ", "VNC"),
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(9.5, 11),
+     lwd = 0,
+     line = 5,
+     labels = c("pMad", "pMad"),
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(9.5, 11),
+     lwd = 0,
+     line = 5,
+     labels = c("NMJ", "VNC"),
+     xpd = T,
+     srt = 270,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(4.5, 9.5, 11),
+     lwd = 0,
+     line = 3.5,
+     labels = c("Boutons", "pMad", "pMad"),
+     xpd = T,
+     srt = 270,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(1:11),
+     lwd = 0,
+     line = 0,
+     labels = cor.table[2, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(1:11),
+     lwd = 0,
+     line = 2,
+     labels = cor.table[3, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(1:11),
+     lwd = 0,
+     line = -0.25,
+     labels = cor.table[2, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(1:11),
+     lwd = 0,
+     line = 2,
+     labels = cor.table[3, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 3,
+     label = "Correlation for WT and G85R, All Lines",
+     at = 6,
+     line = 1.5,
+     cex = 1.5,
+     lwd = 0)
+
+```
+
+```{r echo = F, include=F}
+
+cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
+
+cor.table= cor.table[,-grep("Raw", cor.table[1,])]
+
+cor.table[1,grep("Norm", cor.table[1,])] = substr(cor.table[1,grep("Norm", cor.table[1,])], 8, nchar(cor.table[1,grep("Norm", cor.table[1,])]))
+
+cor.tablea = cor.table[,cor.table[2,] == "a"]
+cor.tablea = cbind(cor.tablea, cor.table[,20])
+cor.tablea = cbind(cor.tablea, cor.table[,1])
+
+cor.tableb = cor.table[,cor.table[2,] == "b"]
+cor.tableb = cbind(cor.tableb, cor.table[,20])
+cor.tableb = cbind(cor.tableb, cor.table[,1])
+
+colnames(cor.tablea) = paste0(cor.tablea[1,], ".", cor.tablea[3,], ".", cor.tablea[4,])
+colnames(cor.tableb) = paste0(cor.tableb[1,], ".", cor.tableb[3,], ".", cor.tableb[4,])
+
+cor.table = rbind(cor.tablea[c(1,3:nrow(cor.tablea)),],cor.tableb[5:nrow(cor.tableb),])
+
+##cor.matrix = cor.table[grep("WT-cr/LoxP", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]
+
+cor.matrix = cor.table[cor.table[,ncol(cor.table)] == "WT-cr/LoxP", 1:(ncol(cor.table)-1)]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+WT.cor.data = cor.data
+
+#cor.matrix = cor.table[grep("G85Rcr/G85Rhr", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]
+
+cor.matrix = cor.table[cor.table[,ncol(cor.table)] == "G85Rcr/G85Rhr", 1:(ncol(cor.table)-1)]
+
+i = 1
+while(i<=ncol(cor.matrix)){
+  cor.matrix[,i] = as.numeric(cor.matrix[,i])
+  i = i + 1
+}
+
+cor.data = as.matrix(cor.matrix)
+cor.data[,1:ncol(cor.data)] = 0
+cor.data = cor.data[1:ncol(cor.data),]
+row.names(cor.data) = colnames(cor.data)
+
+cor.data = data.frame(Factor1 = character(),
+                      Factor2 = character(),
+                      Corr = numeric())
+i=1
+while(i<=ncol(cor.matrix)){
+  j=1
+  while(j<=ncol(cor.matrix)){
+    temp = na.omit(cor.matrix[,c(i,j)])
+    #cor.data[j,i] = cor(temp[,1], temp[,2])
+    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
+                               Factor2 = colnames(cor.matrix)[j],
+                               Corr = cor(temp[,1], temp[,2]))
+    cor.data = rbind(cor.data, temp.cor.data)
+    j=j+1
+  }
+  i=i+1
+}
+
+cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA
+
+cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
+cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))
+
+GR.cor.data = cor.data
+
+WT.cor.data = WT.cor.data[as.numeric(WT.cor.data$Factor1) < as.numeric(WT.cor.data$Factor2),]
+WT.cor.data$Geno = "WT"
+GR.cor.data = GR.cor.data[as.numeric(GR.cor.data$Factor1) > as.numeric(GR.cor.data$Factor2),]
+GR.cor.data$Geno = "G85R"
+
+cor.data = rbind(WT.cor.data, GR.cor.data)
+
+```
+
+```{r echo = F, fig.height=8, fig.width=8, include=F}
+bg.colors = colorRampPalette(c("royalblue", "deepskyblue", "yellow", "deeppink", "violetred"))(200)
+
+plot.bg = bg.colors[100*(cor.data$Corr + 1)]
+
+#plot.bg[cor.data$Corr == 2] = "white"
+
+plot.cex = 2*abs(cor.data$Corr)+.5
+
+#plot.cex[cor.data$Corr == 2] = 2.5
+
+par(mar = c(8,8,4,3))
+
+plot(x = as.numeric(cor.data$Factor1),
+     y = as.numeric(cor.data$Factor2),
+     pch = 21,
+     bg = plot.bg,
+     cex = plot.cex,
+     xaxt = "n",
+     yaxt = "n",
+     ylab = "",
+     xlab = "",
+     bty = "n",
+     main = "")
+
+lines(x = c(.5,14),
+      y = c(.5,14),
+      lty = 2,
+      lwd = 2)
+
+lines(x = c(.5, .5),
+      y = c(.5,11.5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(x = c(.5,11.5),
+      y = c(.5, .5),
+      lty = 1,
+      lwd = 1,
+      xpd = T)
+
+lines(x = c(-0.25, -0.25),
+      y = c(-.25,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(x = c(-1, -1),
+      y = c(-1,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(y = c(-.25, -.25),
+      x = c(-.25,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+lines(y = c(-1, -1),
+      x = c(-1,11.5),
+      lty = 2,
+      lwd = .5,
+      xpd = T)
+
+text(x = 11.8,
+     y = 0,
+     labels = "NMJ",
+     xpd = T,
+     cex = .8)
+
+text(x = 11.8,
+     y = -.5,
+     labels = "Segment",
+     xpd = T,
+     cex = .8)
+
+arrows(x0 = 11.5,
+       y0 = 10.5,
+       x1 = 11.5,
+       y1 = 7,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+arrows(x0 = 10.5,
+       y0 = 11.5,
+       x1 = 7,
+       y1 = 11.5,
+       lwd = 2,
+       xpd = T,
+       length = .1)
+
+text(x = 10,
+     y = 11.75,
+     labels = ("Silent"),
+     xpd = T)
+
+text(x = 11.75,
+     y = 10,
+     labels = ("G85R"),
+     srt = 270,
+     xpd = T)
+
+axis(side = 1,
+     at = c(4.5, 9.5, 11),
+     lwd = 0,
+     line = 3.5,
+     labels = c("Boutons", "NMJ", "VNC"),
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(9.5, 11),
+     lwd = 0,
+     line = 5,
+     labels = c("pMad", "pMad"),
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(9.5, 11),
+     lwd = 0,
+     line = 5,
+     labels = c("NMJ", "VNC"),
+     xpd = T,
+     srt = 270,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(4.5, 9.5, 11),
+     lwd = 0,
+     line = 3.5,
+     labels = c("Boutons", "pMad", "pMad"),
+     xpd = T,
+     srt = 270,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(1:11),
+     lwd = 0,
+     line = 0,
+     labels = cor.table[2, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 1,
+     at = c(1:11),
+     lwd = 0,
+     line = 2,
+     labels = cor.table[3, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(1:11),
+     lwd = 0,
+     line = -0.25,
+     labels = cor.table[2, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 2,
+     at = c(1:11),
+     lwd = 0,
+     line = 2,
+     labels = cor.table[3, 1:11],
+     xpd = T,
+     las = 1,
+     cex.axis = 1)
+
+axis(side = 3,
+     label = "Correlation for WT and G85R, No Rescues",
+     at = 6,
+     line = 1.5,
+     cex = 1.5,
+     lwd = 0)
+
+```
+
+```{r echo = F, fig.height= 8, fig.width= 8, include=F}
+
+cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
+
+cor.table= cor.table[,-grep("Raw", cor.table[1,])]
+
+cor.table[1,grep("Norm", cor.table[1,])] = substr(cor.table[1,grep("Norm", cor.table[1,])], 8, nchar(cor.table[1,grep("Norm", cor.table[1,])]))
+
+cor.tablea = cor.table[,cor.table[2,] == "a"]
+cor.tablea = cbind(cor.tablea, cor.table[,20])
+cor.tablea = cbind(cor.tablea, cor.table[,1])
+
+cor.tableb = cor.table[,cor.table[2,] == "b"]
+cor.tableb = cbind(cor.tableb, cor.table[,20])
+cor.tableb = cbind(cor.tableb, cor.table[,1])
+
+colnames(cor.tablea) = paste0(cor.tablea[1,], ".", cor.tablea[3,], ".", cor.tablea[4,])
+colnames(cor.tableb) = paste0(cor.tableb[1,], ".", cor.tableb[3,], ".", cor.tableb[4,])
+
+cor.table = rbind(cor.tablea[c(1,3:nrow(cor.tablea)),],cor.tableb[5:nrow(cor.tableb),])
+
+cor.matrix = cor.table[cor.table[,ncol(cor.table)] == "WT-cr/LoxP" |
+                         cor.table[,ncol(cor.table)] == "G85Rcr/G85Rhr",
+                       1:ncol(cor.table)]
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.4.3")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.6-7.3")]))
+
+temp.cor1 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+#temp[is.na(temp)] = 0
+
+temp = na.omit(temp)
+
+plot(x = temp$NMJ67,
+     y = temp$NMJ4,
+     pch = 21,
+     bg = "deepskyblue",
+     cex = 1,
+     #xaxt = "n",
+     #yaxt = "n",
+     ylab = "",
+     xlab = "",
+     bty = "n",
+     main = "",
+     xlim = c(0, 100),
+     ylim = c(0,50))
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "royalblue")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.4.4")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.6-7.4")]))
+
+temp.cor2 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "deeppink",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "firebrick")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.4.5")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.6-7.5")]))
+
+temp.cor3 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "lightyellow",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "gold")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.4.6")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "WT-cr/LoxP",
+                  c("Boutons.6-7.6")]))
+
+temp.cor4 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "lightgreen",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "darkgreen")
+
+legend("topleft",
+       legend = c(paste0("3 (cor: ", signif(temp.cor1,2),")"), 
+                  paste0("4 (cor: ", signif(temp.cor2,2),")"),
+                  paste0("5 (cor: ", signif(temp.cor3,2),")"),
+                  paste0("6 (cor: ", signif(temp.cor4,2),")")),
+       title = "Segment",
+       pt.bg = c("royalblue", "firebrick", "gold", "darkgreen"),
+       pch = 21)
+
+```
+
+```{r echo = F, fig.height= 8, fig.width= 8, include=F}
+
+cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
+
+cor.table= cor.table[,-grep("Raw", cor.table[1,])]
+
+cor.table[1,grep("Norm", cor.table[1,])] = substr(cor.table[1,grep("Norm", cor.table[1,])], 8, nchar(cor.table[1,grep("Norm", cor.table[1,])]))
+
+cor.tablea = cor.table[,cor.table[2,] == "a"]
+cor.tablea = cbind(cor.tablea, cor.table[,20])
+cor.tablea = cbind(cor.tablea, cor.table[,1])
+
+cor.tableb = cor.table[,cor.table[2,] == "b"]
+cor.tableb = cbind(cor.tableb, cor.table[,20])
+cor.tableb = cbind(cor.tableb, cor.table[,1])
+
+colnames(cor.tablea) = paste0(cor.tablea[1,], ".", cor.tablea[3,], ".", cor.tablea[4,])
+colnames(cor.tableb) = paste0(cor.tableb[1,], ".", cor.tableb[3,], ".", cor.tableb[4,])
+
+cor.table = rbind(cor.tablea[c(1,3:nrow(cor.tablea)),],cor.tableb[5:nrow(cor.tableb),])
+
+cor.matrix = cor.table[cor.table[,ncol(cor.table)] == "WT-cr/LoxP" |
+                         cor.table[,ncol(cor.table)] == "G85Rcr/G85Rhr",
+                       1:ncol(cor.table)]
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.4.3")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.6-7.3")]))
+
+temp.cor1 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+#temp[is.na(temp)] = 0
+
+temp = na.omit(temp)
+
+plot(x = temp$NMJ67,
+     y = temp$NMJ4,
+     pch = 21,
+     bg = "deepskyblue",
+     cex = 1,
+     #xaxt = "n",
+     #yaxt = "n",
+     ylab = "",
+     xlab = "",
+     bty = "n",
+     main = "",
+     xlim = c(0, 100),
+     ylim = c(0,50))
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "royalblue")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.4.4")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.6-7.4")]))
+
+temp.cor2 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "deeppink",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "firebrick")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.4.5")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.6-7.5")]))
+
+temp.cor3 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "lightyellow",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "gold")
+
+temp = data.frame(NMJ4 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.4.6")]),
+                  NMJ67 = as.numeric(cor.matrix[cor.matrix[,12] == "G85Rcr/G85Rhr",
+                  c("Boutons.6-7.6")]))
+
+temp.cor4 = cor(na.omit(temp)[,1], na.omit(temp)[,2])
+
+temp.lm = lm(na.omit(temp)[,1] ~ na.omit(temp)[,2])[[1]]
+
+points(x = temp$NMJ67,
+       y = temp$NMJ4,
+       pch = 21,
+       bg = "lightgreen",
+       cex = 1)
+
+abline(a = temp.lm[1],
+       b = temp.lm[2],
+       lwd = 2,
+       col = "darkgreen")
+
+legend("topleft",
+       legend = c(paste0("3 (cor: ", signif(temp.cor1,2),")"), 
+                  paste0("4 (cor: ", signif(temp.cor2,2),")"),
+                  paste0("5 (cor: ", signif(temp.cor3,2),")"),
+                  paste0("6 (cor: ", signif(temp.cor4,2),")")),
+       title = "Segment",
+       pt.bg = c("royalblue", "firebrick", "gold", "darkgreen"),
+       pch = 21)
+
+```
